### 2018-08-02 rmd/Manuscript.Rmd
Updated manuscript

---
title: "Displacement effects of Large-Scale MPAs in the Pacific Ocean?"
author: |
  Juan Carlos Villaseñor-Derbez ^1^
  John Lynham ^2^
date: |
  ^1^ Bren School of Environmental Science & Management, University of California, Santa Barbara
  ^2^ Department of Economics, Saunders Hall 532, University of Hawai`i at M~anoa, 2424 Maile Way, Honolulu, HI 96822
abstract: ""
output:
  pdf_document:
    toc: yes
    toc_depth: 4
bibliography: references.bib
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
---

** Last update: `r Sys.Date()`**

```{r, echo = F}
suppressPackageStartupMessages({
  library(tidyverse)
})
```

# Introduction

# Methods

## Data

## Analysis

# Results

The current approach is to estimate what percentage of fishing effort from the PNA was displaced by PIPA and use this to infer something about Palau. While this provides a measure of the displacement, it does not fully address the possibility of costs increasing. I believ we can use individual tracks (as opposed to just the gridded effort) and obtain show how their behavior changed (*i.e.* are they fishing further away, are they fishing more, where are they now?).

```{r, echo = F}
pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))

n_prev <- pipa_vessels %>% 
  filter(year < 2015) %>%
  group_by(year, mmsi) %>% 
  summarize(n_points = sum(n_points),
            hours = sum(total_fishing_hours))

mmsis <- unique(n_prev$mmsi)
```

As I mentioned in the call, I have been working with vessels who fished in PIPA as part of my PhD research. In total there are `r length(unique(pipa_vessels$mmsi))`[^3] vessels that have fished within PIPA waters. From these, `r length(unique(n_prev$mmsi))` did so at least once before 2015 and on average exerted `r mean(n_prev$hours)` $\pm$ `r sd(n_prev$hours)` hours each year. A significant number of these vessels fished in PIPA and adjacent waters. We can see where they fished before and track where they went after 2015.

In this section I present some of the preliminary results of regressions similar to what you have conducted for US MNMs using hours as an estimate of fishing effort. First, I explore patterns of fishing effort only inside PIPA (Fig. \ref{fig:blue_para}). Consistent with the blue paradox, we see an increase in the number of vessels, total hours, mean hours, and number of data points between 2014 and 2015. Shortly after that, all measures decrease in 2015[^4].

[^3]: Perhaps some of these vessels only fished there for a couple hours one year. Therefore, I would need to further identify which ones were transient vs local using some cutoff. For now, I use run regressions for all vessels and for vessels that fly the Kiribati flag (n = 12). The true number lies between these two groups, but it provides a starting point.

[^4]: See McDermott et al., (*in review*) for further information

```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect."}
pipa_vessels %>% 
  group_by(year, month, mmsi) %>% 
  summarize(n_points = sum(n_points),
            hours = sum(total_fishing_hours)) %>% 
  group_by(year, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_points = sum(n_points),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
         post = year >= 2015) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

\clearpage

Then, I look at the entire fishing effort of vessels that fished at least once in PIPA before 2015. In other words, I use GFW data to track vessel-level activities inside and outside PIPA before and after 2015. However, all boats included in this case fished at least once in PIPA before 2015 (*i.e.* no control group). First I look at vessels whose `mmsi` code starts with `529`, indicating that they come from Kiribati [^5]. The overall pattern for fishing time (total and mean) show a downward trend that initiated well before 2015 (Fig. \ref{fig:kir_vessels}). The number of vessels as given by unique mmsi numbers shows a maximum near the end of 2014, and then decreases after 2015.

Given the similar trends observed in total fishing hours and mean fishing hours, I calculate total fishing hours at the year-month-vessel level and regress that on a `post` dummy that indicates years before or after 2015. Results of this regression are presented in Table \ref{tab:kir_vessels}. In this table, column (1) presents the regression only against the policy dummy, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and vessel fixed effects. All three specifications show negative coefficients. The full model explains 71% of the variance in monthly fishing hours by vessel. This specification has the lowest policy coefficient (labeled `post`), and it is not different from zero at the $\alpha = 0.05$ level.

[^5]: link: [http://www.vtexplorer.com/mmsi-mid-codes-en/](http://www.vtexplorer.com/mmsi-mid-codes-en/)

```{r, echo = F, fig.cap = "\\label{fig:kir_vessels}Fishing hours and number of 12 Kiribati vessels from 2012 - 2016 that at some point fished inside PIPA."}
effort_by_vessel <- read.csv(here::here("data", "pipa_effort_by_vessel.csv")) %>% 
  # filter(between(year, 2014, 2016)) %>%
  filter(mmsi %in% mmsis) %>%
  mutate(mmsi = as.character(mmsi),
         month = as.character(month),
         year = as.character(year))

effort_by_vessel %>% 
  filter(kir) %>% 
  group_by(year, post, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

```{r, results = "asis", echo = F}
kir_vessel <- effort_by_vessel %>% 
  filter(kir)

m1 <- lm(hours ~ post, data = kir_vessel)
m2 <- lm(hours ~ post + month, data = kir_vessel)
m3 <- lm(hours ~ post + month + year, data = kir_vessel)
m4 <- lm(hours ~ post + month + year + mmsi, data = kir_vessel)

models <- list(m1, m2, m3, m4)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     type = "latex",
                     omit = c("mmsi", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Vessel FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
```

\clearpage

I then repeat a similar analysis but for all fishing vessels that fished at least once inside PIPA before 2015. In this case this likely represents an underestimate of the effect, as it could include vessels who once fished inside PIPA, but are not even in the region any more. The number of unique mmsi codes (Fig. \ref{fig:all_vessels}) follows a similar pattern as in the previous case. However, mean hours and total hours show stable trends before and after. As opposed to only Kiribati vessels who seemed to reduce the number of fishing hours, a similar analysis of all vessels shows positive coefficients that are not statistically significant ($alpha < 0.05$). Results of the regressions are shown in Table \ref{tab:all_vessels}. Like before, column (1) presents the regression only against the policy dummy, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and vessel fixed effects.

```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels that fished inside PIPA at least once."}
effort_by_vessel %>% 
  group_by(year, post, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post)) %>% 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  geom_point(aes(color = post)) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  theme_bw() +
  scale_color_brewer(palette = "Set1")
```

```{r, results = "asis", echo = F}
m1 <- lm(hours ~ post, data = effort_by_vessel)
m2 <- lm(hours ~ post + month, data = effort_by_vessel)
m3 <- lm(hours ~ post + month + year, data = effort_by_vessel)
m4 <- lm(hours ~ post + month + year + mmsi, data = effort_by_vessel)

models <- list(m1, m2, m3, m4)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     type = "latex",
                     omit = c("mmsi", "year", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Year FE", "No", "No", "Yes", "Yes"),
                                      c("Vessel FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.")

```

\clearpage

### Further work

In order to strengthen this analysis, I would like to identify an appropriate sample of vessels that acccurately represent the PNA. This vessels must meet at least these two points: i) belong to the PNA and ii) Have fished for a significant amount of time inside PIPA, to count as "treated". Ideally, this would get rid of vessels that sporadically fished for insignificant time in PIPA, and are therefore unlikely to be affected. This would include between 12 and `r length(unique(n_prev$mmsi))` vessels (number of Kiribati vessels vs. number of all vessels who fished in PIPA at least once before 2015).

I would also like to explore the possibility of identifying a plausible counterfactual. That way we could do something like a DiD. I think it is possible to identify counterfactual boats. I would start by identifying vessels who meet at least these four criteria: i) fish in near-by regions, ii) have same gear as vessels from PIPA, and iii) having similar length of data, and iv) never fished inside PIPA. Perhaps an additional one would be that they belong to the PNA.

Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time.

```{r, echo = F, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:eez-hs} Percentage of catches that come from the high-seas vs. EEZs. (data from [Sea Around Us](www.seaaroundus.org))."}
seaaroundus::eezsvshighseas() %>% 
  magrittr::set_colnames(value = c("year", "EEZ", "High-seas")) %>% 
  gather(source, percent, -year) %>% 
  mutate(source = fct_relevel(source, "High-seas")) %>% 
  ggplot2::ggplot(aes(x = year, y = percent, fill = source)) +
  geom_area(alpha = 0.5) +
  scale_fill_brewer(palette = "Set1") +
  theme_bw() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  geom_hline(yintercept = 94, linetype = "dashed") +
  labs(x = "Year", y = "Percentage", fill = "Source")
```

\clearpage

# Possible contributions

As I understand the efforts made so far, there are two straightforward ways in which I could contribute to this study. For the first one I would help strengthen the analysis of NOAA Observer and GFW data for the US PNMs. The second one would involve conducting the analysis of GFW data for PIPA, and translating the results into implications for Palau. I discuss these two in greater detail in the next paragraphs.

## US Pacific Monuments

In this section I include possible analysis in which I could help. When relevant, I include quotes to provide context. Comments are organized with headings similar to the ones included in the original manuscript. I believe my suggestions would compliment (rather than replace) current analysis, and I acknowledged that you might have already tried some or that due to data constraints not all of them are possible.

### Total revenue

"It is very clear from the figure that total catch of bigeye has not declined as a result of the 2014 or
2016 expansions". Of course, I have not reviewed the data. But is it safe to conclude this? At least through time there isn't an evident decrease, but what would have catches looked like had PMNM not been expanded?

Not sure if the spatial resolution (*i.e.* Catch Blocks) in logbooks allows this comparison, but it would be interesting to see what proportion of catches (or at least sets / hours) originally came from waters inside the PMNM. Perhaps the georeferenced catches from NOAA Observer data can provide insights into this (if not for the entire fleet, at least for the 20% quasi-random subset), or we can use GFW data to see if the proportion of fishing hours inside PMNM roughly corresponds to 10M in revenues (we can test different "catch rates" to account for the fact that catches inside vs outside may not map 1:1). Perhaps this catch efficiency ratio can be extracted from the NOAA Observer data?

On aggregate the fleet brought in more money in 2015 and 1016 than in previous year, but you discuss the possibility that the distributional effects of this might be different. I would assume that vessels who fished the most in the PMNM area were the ones who took the toughest hit. If possible, it might be interesting to birefly look at distributional effects for the discussion.

### Total costs (TC)

So far this section describes the available data, but it it's not clear whether the empirical strategy is fully developed. Just like the datasets, a there isn't a single best analysis that provides the answer, but looking at it from as many was as possible might help paint a full picture of the effects that vLPAs have had.Here I provide some ideas in which we could use the two main datasets (NOAA and GFW data) to indirectly test the claims made by the fleet.

#### TC from NOAA Observer program

You mention that a drawback of this dataset is that you only observe fishing events, and not the entire trip (*i.e.* the search and travel). It might be worth looking into combining this with GFW data. NOAA observer program would provide real fishing events (as opposed to the ones predicted by GFW's neural net), and GFW would provide the entire track. Given that NOAA data cover 20% and GFW only contain 60 boats, we will not get full coverage. If this doesn't yield better data, it would at least help determine if the three-day space between sets is an appropriate way of grouping them into "trips".

Results in your table 3 suggest that there's been a change of ~ 20 miles (positive or negative depending on model specification), and not significant. Perhaps linking this data to GFW would provide full tracks (of a smaller portion of the fleet) to then account for distance between fishing points but also during the search and set activities.

#### TC form GFW Data

We could also test the increased cost claim by looking at the almost 60 vessels and calculate an estimate of fuel consumption (following @sala_2018), which, paired with fuel prices, might provide cost estimates[^1]. Initially this would just be a regression with a policy dummy (and appropriate vessel- and month-level FE's). We could look into GFW data to identify plausible counterfactuals to include  a control group[^2].

[^1]: Of course, there are additional costs (*e.g.* crew, ice, bait, gear), but fuel should represent a large portion of this and should scale with some measures of fishing effort (time and distance). If this is not enough, the previous comparison of catches (sets) that came from PMNM waters before the implementation could provide some insights.

[^2]: GFW increased coverage when they added from more satellites, particularly towards the end of 2016 and throughout 2017, I believe. I think it would be important to use counterfactuals in any GFW-related analyses to account for the expected temporal trend in increased effort.

# Other details

- The introduction states that the main objective is to quantify the economic impacts of vLPAs and compare the cost per hectare to vLPAs on land. I think this would provide an interesting benchmark on cost of conservation per unit area in land vs sea. I would perhaps highlight the part about predicting the possible effects of the Palau MPA.

- I think the novelty of the paper can be highlighted even more. @stevenson_2013 evaluated the consequences of fishing displacement from MPAs in Hawaii (a smaller network and totally different fleet). They show that fishing effort was indeed displaced to places further away from ports representing increased costs, but that CPUE also increased. Overall, they don't find a negative impact on the *perceived* socioeconomic well-being of fishers. However, they do not have plausible counterfacutals and rely on before-after comparisons of perceptions. I think the novelty of this paper is not only the size, resolution, and quality of the data, but the fact that it has a BACI design enabling the identification of the net effect that vLPAs have on fishers. And also the larger contribution to vLPAs (and MPAs in general) literature.
- Recent work by @sala_2018 shows that a large portion of high-seas fishing is only profitable thanks to subsidies. This could compliment @white_2014 and @sumaila_2015 in the introduction.

- "Neither of these datasets is perfect but hopefully combined they will paint a clear picture of what the impact has been". I find this to be a modest (or humble?) and powerful sentence that highlights the efforts made to identify effects from different sources, and that acknowledges possible data limitations. This sentence should be included alongside the "novelty" in the last paragraph of the introduction.

- Findings by @smith_2006 show negative effects, but the reserves were only in place for a short period. I believe they talk about this in their discussion. @edgar_2014-UO and @difranco_2016-Xw show how the effects (at least inside vs outside the reserve) can take up to 10 years.

- I would be cautious on the interpretation of results by @sumaila_2015. They do show that < 0.01% of catch and landed values come *exclusively* from the high seas, but also that 67% and 72% (catch and value) come from Both EEZs and High seas, and the remaining from EEZs only. @pauly_2016 show that ~6% of landings come from the high seas (Fig. \ref{fig:eez-hs}). It's perhaps a minor detail, but thought I'd point it out.

# References

### 2018-09-07 docs/Manuscript.tex
Added new manuscript

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement effects and implications of Large-Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Displacement effects and implications of Large-Scale Marine Protected
Areas}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Juan Carlos Villaseñor-Derbez \textsuperscript{1} John Lynham
\textsuperscript{2}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{\textsuperscript{1} Bren School of Environmental Science \& Management,
University of California, Santa Barbara \textsuperscript{2} Department
of Economics, Saunders Hall 532, University of Hawai`i at Manoa}

\usepackage{float}
\floatplacement{figure}{H}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle
\begin{abstract}
Large-scale Marine Protected Areas (LSMPAs) have seen a significant
increase over the last years. Literature shows that fishing effort is
effectively eliminated in this protected areas upon implementation. The
benefits of reducing effort have been largely studied, and include
increases in abundance, biomass, and diversity within the bounded
regions. In terms of the fishing implication, no-take zones may produce
spillover that provide fish for outside areas. The implications of
displacement of fishing effort are not yet fully understood. Evidence
suggests that fishing effort re-distributes along the borders of the
MPA, following an ideal free distribution. Novel data products allow us
to track fishing effort at the vessel-level, allowing us to identify
changes in behavior at both the fleet and vessel level. This papers
evaluates the implications of implementing a LMPA, the Phoenix Islands
Protected Area (PIPA). We evaluate changes in fishing effort, and track
vessels to see where they go after the implementation of PIPA. Our
results show that vessels in the effected region increase fishing effort
after the implementation of PIPA. THey are redistributed to X. These
findings have major implications for MPA implementation, especially as
countries rush to meet the goals of 10\% ocean protection as mandated by
the SDG.
\end{abstract}

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\emph{Last update: 2018-09-07}

\section{Introduction}\label{introduction}

The rest of the paper is outlined as follows: Section \ref{background}
provides further information about PIPA and Palau, section \ref{methods}
describes our data and empirical strategy, section \ref{results}
presents our results, in section \ref{discussion} we discuss our
findings and provide management recommendations.

\section{Background}\label{background}

\section{Methods}\label{methods}

\subsection{Data}\label{data}

The Global Fishing Watch (GFW) data contain 235 vessels that have fished
within PIPA waters \footnote{Perhaps some of these vessels only fished
  there for a couple hours one year. Therefore, I would need to further
  identify which ones were transient vs constant fishing events using
  some cutoff. For now, I run regressions for all vessels and for
  vessels that fly the Kiribati flag (n = 12). The true number of
  impacted vessels must lie between these two groups, but it provides a
  starting point.}. From these, 206 did so at least once before 2015.

\begin{table}

\caption{\label{tab:unnamed-chunk-3}Mean fishing hours for each gear before and after}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 484.47512 & 470.7382 & 0.9716458\\
\hline
drifting\_longlines & TRUE & 545.68460 & 523.5596 & 0.9594546\\
\hline
purse\_seines & FALSE & 59.64877 & 160.7945 & 2.6956886\\
\hline
purse\_seines & TRUE & 55.30178 & 149.9978 & 2.7123509\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:unnamed-chunk-4}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
\hline
drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
\hline
purse\_seines & FALSE & 49 & 89 & 1.8163265\\
\hline
purse\_seines & TRUE & 78 & 81 & 1.0384615\\
\hline
\end{tabular}
\end{table}

Then, I look at the entire fishing effort of vessels that fished at
least once in PIPA before 2015. In other words, I use GFW data to track
vessel-level activities inside and outside PIPA before and after 2015.
However, all boats included in this case fished at least once in PIPA
before 2015 (\emph{i.e.} no control group). First I look at vessels
whose \texttt{mmsi} code starts with \texttt{529}, indicating that they
come from Kiribati \footnote{link:
  \url{http://www.vtexplorer.com/mmsi-mid-codes-en/}}. The overall
pattern for fishing time (total and mean) show a downward trend that
initiated well before 2015 (Fig. \ref{fig:kir_vessels}). The number of
vessels as given by unique mmsi numbers shows a maximum near the end of
2014, and then decreases after 2015.

\subsection{Analysis}\label{analysis}

\subsubsection{To do}\label{to-do}

\begin{itemize}
\tightlist
\item
  Divide pipa vessels by type of boat (longline vs.~purse seine)
\item
  Identify two counterfactuals:

  \begin{itemize}
  \tightlist
  \item
    A:

    \begin{itemize}
    \tightlist
    \item
      PNA
    \item
      similar vessel
    \item
      never fished inside PIPA -B:
    \item
      Taiwan
    \item
      Never in PNA
    \item
      Similar region?
    \end{itemize}
  \end{itemize}
\end{itemize}

Has effort increased?

\begin{itemize}
\tightlist
\item
  Change in fishing hours before vs after
\item
  Change in total hours before vs after
\item
  Change in distance before vs after
\item
  Where do PIPA vessels go?
\item
  How many were transient vs local?
\end{itemize}

Has search time increased?

\begin{itemize}
\tightlist
\item
  Distance between fishing points before vs.~after
\item
  Prop hour fishing before vs after
\item
  Time between fishing points before vs.~after
\end{itemize}

The current approach is to estimate what percentage of fishing effort
from the PNA was displaced by PIPA and use this to infer something about
Palau. While this provides a measure of the displacement, it does not
fully address the possibility of costs increasing. I believ we can use
individual tracks (as opposed to just the gridded effort) and obtain
show how their behavior changed (\emph{i.e.} are they fishing further
away, are they fishing more, where are they now?).

\subsubsection{Model specifications}\label{model-specifications}

Our model specification uses a difference-in-differences approach. In
this case, we interact the before-after dummy with a treatment dummy.
The treatment-control groups follow our definition in the data
description. The model takes the form of:

\[
H_{ijk} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \epsilon_{ijk}
\]

\section{Results}\label{results}

In this section I present some of the preliminary results of regressions
similar to what you have conducted for US MNMs using hours as an
estimate of fishing effort. First, I explore patterns of fishing effort
only inside PIPA (Fig. \ref{fig:blue_para}). Consistent with the blue
paradox \citep{mcdermott_2018}, we see an increase in the number of
vessels, total hours, mean hours, and number of data points between 2014
and 2015. Shortly after that, all measures decrease in 2015.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}\label{fig:blue_para}Monthly hours,
number of vessels, and data points observed inside PIPA. These clearly
show the blue-paradox effect.}
\end{figure}

\clearpage

Given the similar trends observed in total fishing hours and mean
fishing hours, I calculate total fishing hours at the year-month-vessel
level and regress that on a \texttt{post} dummy that indicates years
before or after 2015, which is interacted with a \texttt{treated} dummy
that indicates if vessels fished at least once within PIPA or only in
PNA waters. Results of this regression are presented in Table
\ref{tab:kir_vessels}. In this table, column (1) presents the regression
only against the policy dummy, column (2) includes month fixed effects,
column (3) includes month and year fixed effects, and column (4)
includes month, year, and vessel fixed effects. All three specifications
show negative coefficients. The full model explains 71\% of the variance
in monthly fishing hours by vessel. This specification has the lowest
policy coefficient (labeled \texttt{post}), and it is not different from
zero at the \(\alpha = 0.05\) level.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:unnamed-chunk-6}\label{fig:kir_vessels}Fishing hours and
number of 12 Kiribati vessels from 2012 - 2016 that at some point fished
inside PIPA.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 70.279$^{***}$ & 71.066$^{***}$ & 83.322$^{***}$ & 54.074$^{***}$ \\ 
  & (8.951) & (8.856) & (11.471) & (12.832) \\ 
  & & & & \\ 
 treated & $-$26.777 & $-$27.119 & $-$30.234$^{*}$ & $-$37.149 \\ 
  & (17.881) & (17.137) & (17.434) & (40.248) \\ 
  & & & & \\ 
 post:treated &  &  &  &  \\ 
  &  &  &  &  \\ 
  & & & & \\ 
 Constant & 81.770$^{***}$ & 88.095$^{***}$ & 70.812$^{***}$ & 126.560$^{***}$ \\ 
  & (18.737) & (23.142) & (24.053) & (34.921) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Vessel FE & No & No & No & Yes \\ 
Observations & 344 & 344 & 344 & 344 \\ 
R$^{2}$ & 0.170 & 0.191 & 0.219 & 0.383 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\clearpage

I then repeat a similar analysis but for all fishing vessels that fished
at least once inside PIPA before 2015. In this case this likely
represents an underestimate of the effect, as it could include vessels
who once fished inside PIPA, but are not even in the region any more.
The number of unique mmsi codes (Fig. \ref{fig:all_vessels}) follows a
similar pattern as in the previous case. However, mean hours and total
hours show stable trends before and after. As opposed to only Kiribati
vessels who seemed to reduce the number of fishing hours, a similar
analysis of all vessels shows positive coefficients that are not
statistically significant (\(alpha < 0.05\)). Results of the regressions
are shown in Table \ref{tab:all_vessels}. Like before, column (1)
presents the regression only against the policy dummy, column (2)
includes month fixed effects, column (3) includes month and year fixed
effects, and column (4) includes month, year, and vessel fixed effects.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels that fished inside PIPA at
least once.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 45.766$^{***}$ & 45.268$^{***}$ & 41.959$^{***}$ & 45.596 \\ 
  & (6.534) & (6.504) & (8.779) &  \\ 
  & & & & \\ 
 treated & 50.000$^{***}$ & 51.321$^{***}$ & 50.749$^{***}$ & $-$457.705 \\ 
  & (6.771) & (6.759) & (6.813) &  \\ 
  & & & & \\ 
 postTRUE:treated & $-$59.473$^{***}$ & $-$58.530$^{***}$ & $-$57.494$^{***}$ & $-$21.059 \\ 
  & (8.463) & (8.432) & (8.491) &  \\ 
  & & & & \\ 
 Constant & 349.582$^{***}$ & 328.470$^{***}$ & 333.794$^{***}$ & 483.665 \\ 
  & (5.635) & (8.833) & (10.226) &  \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Vessel FE & No & No & No & Yes \\ 
Observations & 15,885 & 15,885 & 15,885 & 15,885 \\ 
R$^{2}$ & 0.004 & 0.011 & 0.011 & 0.632 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}

\section{Discusion}\label{discusion}

\clearpage

\subsubsection{Further work}\label{further-work}

\renewcommand\refname{References}
\bibliography{references.bib}

\end{document}

### 2018-09-07 rmd/Manuscript.Rmd
Added new manuscript

@@
 ---
-title: "Displacement effects of Large-Scale MPAs in the Pacific Ocean?"
+title: "Displacement effects and implications of Large-Scale Marine Protected Areas"
 author: |
@@
   ^1^ Bren School of Environmental Science & Management, University of California, Santa Barbara
-  ^2^ Department of Economics, Saunders Hall 532, University of Hawai`i at M~anoa, 2424 Maile Way, Honolulu, HI 96822
-abstract: ""
+  ^2^ Department of Economics, Saunders Hall 532, University of Hawai`i at Manoa
+abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
+Literature shows that fishing effort is effectively eliminated in this protected areas upon implementation.
+The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions.
+In terms of the fishing implication, no-take zones may produce spillover that provide fish for outside areas.
+The implications of displacement of fishing effort are not yet fully understood.
+Evidence suggests that fishing effort re-distributes along the borders of the MPA, following an ideal free distribution.
+Novel data products allow us to track fishing effort at the vessel-level, allowing us to identify changes in behavior at both the fleet and vessel level.
+This papers evaluates the implications of implementing a LMPA, the Phoenix Islands Protected Area (PIPA).
+We evaluate changes in fishing effort, and track vessels to see where they go after the implementation of PIPA.
+Our results show that vessels in the effected region increase fishing effort after the implementation of PIPA.
+THey are redistributed to X.
+These findings have major implications for MPA implementation, especially as countries rush to meet the goals of 10% ocean protection as mandated by the SDG."
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     toc: yes
     toc_depth: 4
-bibliography: references.bib
+    citation_package: natbib
+    keep_tex: yes
+    number_sections: no
 header-includes:
@@
   - \floatplacement{figure}{H}
+bibliography: references.bib
+biblio-style: nature
 ---
 
-** Last update: `r Sys.Date()`**
+*Last update: `r Sys.Date()`*
 
@@
 suppressPackageStartupMessages({
+  library(startR)
   library(tidyverse)
 })
+
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 ```
@@
 # Introduction
+
+The rest of the paper is outlined as follows: Section \ref{background} provides further information about PIPA and Palau, section \ref{methods} describes our data and empirical strategy, section \ref{results} presents our results, in section \ref{discussion} we discuss our findings and provide management recommendations.
+
+# Background
 
@@
 
-## Analysis
+```{r, echo = F}
+vessel_info_pipa <- read.csv(here::here("data", "vessel_info_mmsi_inside_pipa.csv"), stringsAsFactors = F) %>% 
+  mutate(treated = T)
 
-# Results
+vessel_info_pna <- read.csv(here::here("data", "vessel_info_mmsi_inside_pna.csv"), stringsAsFactors = F) %>% 
+  mutate(treated = F)
 
-The current approach is to estimate what percentage of fishing effort from the PNA was displaced by PIPA and use this to infer something about Palau.
-While this provides a measure of the displacement, it does not fully address the possibility of costs increasing.
-I believ we can use individual tracks (as opposed to just the gridded effort) and obtain show how their behavior changed (*i.e.* are they fishing further away, are they fishing more, where are they now?).
+vessel_info <- rbind(vessel_info_pipa, vessel_info_pna) %>% 
+  rename(gear = inferred_label)
 
-```{r, echo = F}
 pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))
@@
 
-As I mentioned in the call, I have been working with vessels who fished in PIPA as part of my PhD research.
-In total there are `r length(unique(pipa_vessels$mmsi))`[^3] vessels that have fished within PIPA waters.
-From these, `r length(unique(n_prev$mmsi))` did so at least once before 2015 and on average exerted `r mean(n_prev$hours)` $\pm$ `r sd(n_prev$hours)` hours each year.
-A significant number of these vessels fished in PIPA and adjacent waters.
-We can see where they fished before and track where they went after 2015.
+The Global Fishing Watch (GFW) data contain `r length(unique(pipa_vessels$mmsi))` vessels that have fished within PIPA waters [^3]. From these, `r length(mmsis)` did so at least once before 2015.
+
+[^3]: Perhaps some of these vessels only fished there for a couple hours one year.
+Therefore, I would need to further identify which ones were transient vs constant fishing events using some cutoff.
+For now, I run regressions for all vessels and for vessels that fly the Kiribati flag (n = 12).
+The true number of impacted vessels must lie between these two groups, but it provides a starting point.
+
+```{r}
+effort_by_vessel <- read.csv(here::here("data", "pipa_effort_by_vessel.csv"), stringsAsFactors = F) %>% 
+  rbind(read.csv(here::here("data", "pna_vessels_outside_pipa.csv"), stringsAsFactors = F)) %>% 
+  left_join(vessel_info, by = c("mmsi", "year")) %>% 
+  filter(gear %in% c("purse_seines", "drifting_longlines")) %>%
+  mutate(mmsi = as.character(mmsi),
+         month = as.character(month),
+         year = as.character(year))
+
+effort_by_vessel %>%  
+  group_by(gear, treated, post) %>% 
+  summarize(hours = mean(hours, na.rm = T)) %>% 
+  spread(post, hours) %>% 
+  mutate(change = `TRUE` / `FALSE`) %>% 
+  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
+               caption = "Mean fishing hours for each gear before and after")
+```
+
+```{r}
+effort_by_vessel %>% 
+  group_by(gear, treated, post, mmsi) %>% 
+  count() %>% 
+  ungroup() %>% 
+  group_by(gear, treated, post) %>% 
+  summarize(boats = n()) %>% 
+  spread(post, boats) %>% 
+  mutate(change = `TRUE` / `FALSE`) %>% 
+  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
+               caption = "Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.")
+```
+
+Then, I look at the entire fishing effort of vessels that fished at least once in PIPA before 2015.
+In other words, I use GFW data to track vessel-level activities inside and outside PIPA before and after 2015.
+However, all boats included in this case fished at least once in PIPA before 2015 (*i.e.* no control group).
+First I look at vessels whose `mmsi` code starts with `529`, indicating that they come from Kiribati [^4].
+The overall pattern for fishing time (total and mean) show a downward trend that initiated well before 2015 (Fig.
+\ref{fig:kir_vessels}).
+The number of vessels as given by unique mmsi numbers shows a maximum near the end of 2014, and then decreases after 2015.
+
+[^4]: link: [http://www.vtexplorer.com/mmsi-mid-codes-en/](http://www.vtexplorer.com/mmsi-mid-codes-en/)
+
+## Analysis
+
+### To do
+
+- Divide pipa vessels by type of boat (longline vs. purse seine)
+- Identify two counterfactuals:
+    - A:
+        - PNA
+        - similar vessel
+        - never fished inside PIPA
+    -B:
+        - Taiwan
+        - Never in PNA
+        - Similar region?
+
+Has effort increased?
+
+- Change in fishing hours before vs after
+- Change in total hours before vs after
+- Change in distance before vs after
+- Where do PIPA vessels go?
+- How many were transient vs local?
+
+Has search time increased?
+
+- Distance between fishing points before vs. after
+- Prop hour fishing before vs after
+- Time between fishing points before vs. after
+
+The current approach is to estimate what percentage of fishing effort from the PNA was displaced by PIPA and use this to infer something about Palau.
+While this provides a measure of the displacement, it does not fully address the possibility of costs increasing.
+I believ we can use individual tracks (as opposed to just the gridded effort) and obtain show how their behavior changed (*i.e.* are they fishing further away, are they fishing more, where are they now?).
+
+### Model specifications
+
+<!-- $$ -->
+<!-- H_{ijk} = \alpha + \beta Post_i + \mu_j + \phi_k + \epsilon_{ijk} -->
+<!-- $$ -->
+
+<!-- Where $H_{ijk}$ is a measure of effort (*.i.e.* total hours, fishing hours, distance traveled), $\beta$ captures the change for before ($Post_i = 0$) and after ($Post_i = 1$) implementation of PIPA, $mu_j$ captures the month fixed-effects, and $\phi_k$ captures vessel-level fixed-effects.
+We use this general model and the nested specifications which drop the month and vessel-level fixed effects to test for differences.
+-->
+
+Our model specification uses a difference-in-differences approach.
+In this case, we interact the before-after dummy with a treatment dummy.
+The treatment-control groups follow our definition in the data description.
+The model takes the form of:
+
+$$
+H_{ijk} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \epsilon_{ijk}
+$$
+
+# Results
 
@@
 \ref{fig:blue_para}).
-Consistent with the blue paradox, we see an increase in the number of vessels, total hours, mean hours, and number of data points between 2014 and 2015.
-Shortly after that, all measures decrease in 2015[^4].
-
-[^3]: Perhaps some of these vessels only fished there for a couple hours one year.
-Therefore, I would need to further identify which ones were transient vs local using some cutoff.
-For now, I use run regressions for all vessels and for vessels that fly the Kiribati flag (n = 12).
-The true number lies between these two groups, but it provides a starting point.
-
-[^4]: See McDermott et al., (*in review*) for further information
+Consistent with the blue paradox \citep{mcdermott_2018}, we see an increase in the number of vessels, total hours, mean hours, and number of data points between 2014 and 2015.
+Shortly after that, all measures decrease in 2015.
 
 ```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect."}
+# This is just to show the blue paradox, no need to include this figure
 pipa_vessels %>% 
@@
 
-Then, I look at the entire fishing effort of vessels that fished at least once in PIPA before 2015.
-In other words, I use GFW data to track vessel-level activities inside and outside PIPA before and after 2015.
-However, all boats included in this case fished at least once in PIPA before 2015 (*i.e.* no control group).
-First I look at vessels whose `mmsi` code starts with `529`, indicating that they come from Kiribati [^5].
-The overall pattern for fishing time (total and mean) show a downward trend that initiated well before 2015 (Fig.
-\ref{fig:kir_vessels}).
-The number of vessels as given by unique mmsi numbers shows a maximum near the end of 2014, and then decreases after 2015.
-
-Given the similar trends observed in total fishing hours and mean fishing hours, I calculate total fishing hours at the year-month-vessel level and regress that on a `post` dummy that indicates years before or after 2015.
+Given the similar trends observed in total fishing hours and mean fishing hours, I calculate total fishing hours at the year-month-vessel level and regress that on a `post` dummy that indicates years before or after 2015, which is interacted with a `treated` dummy that indicates if vessels fished at least once within PIPA or only in PNA waters.
 Results of this regression are presented in Table \ref{tab:kir_vessels}.
@@
 
-[^5]: link: [http://www.vtexplorer.com/mmsi-mid-codes-en/](http://www.vtexplorer.com/mmsi-mid-codes-en/)
-
 ```{r, echo = F, fig.cap = "\\label{fig:kir_vessels}Fishing hours and number of 12 Kiribati vessels from 2012 - 2016 that at some point fished inside PIPA."}
-effort_by_vessel <- read.csv(here::here("data", "pipa_effort_by_vessel.csv")) %>% 
-  # filter(between(year, 2014, 2016)) %>%
-  filter(mmsi %in% mmsis) %>%
-  mutate(mmsi = as.character(mmsi),
-         month = as.character(month),
-         year = as.character(year))
-
 effort_by_vessel %>% 
-  filter(kir) %>% 
-  group_by(year, post, month) %>% 
+  filter(kir, treated) %>% 
+  group_by(year, month, mmsi, gear) %>% 
+  summarize(hours = sum(hours)) %>% 
+  group_by(year, month, gear) %>% 
   summarize(total_hours = sum(hours),
@@
   ungroup() %>% 
-  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
+  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
+         post = year >= 2015) %>% 
   select(-year) %>% 
-  gather(variable, value, -c(date, month, post)) %>% 
+  gather(variable, value, -c(date, month, post, gear)) %>% 
   ggplot(aes(x = date, y = value)) +
@@
   geom_point(aes(color = post)) +
-  facet_wrap(~variable, scales = "free", ncol = 2) +
+  facet_wrap(gear~variable, scales = "free_y", ncol = 3) +
   theme_bw() +
@@
 kir_vessel <- effort_by_vessel %>% 
-  filter(kir)
+  filter(kir, gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1)
 
-m1 <- lm(hours ~ post, data = kir_vessel)
-m2 <- lm(hours ~ post + month, data = kir_vessel)
-m3 <- lm(hours ~ post + month + year, data = kir_vessel)
-m4 <- lm(hours ~ post + month + year + mmsi, data = kir_vessel)
+m1 <- lm(hours ~ post*treated, data = kir_vessel)
+m2 <- lm(hours ~ post*treated + month, data = kir_vessel)
+m3 <- lm(hours ~ post*treated + month + year, data = kir_vessel)
+m4 <- lm(hours ~ post*treated + month + year + mmsi, data = kir_vessel)
 
@@
                      se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
                      type = "latex",
@@
 effort_by_vessel %>% 
-  group_by(year, post, month) %>% 
+  group_by(year, gear, treated, post, month) %>% 
   summarize(total_hours = sum(hours),
@@
   select(-year) %>% 
-  gather(variable, value, -c(date, month, post)) %>% 
-  ggplot(aes(x = date, y = value)) +
-  geom_line() +
+  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
+  ggplot(aes(x = date, y = value, group = treated)) +
+  geom_line(aes(linetype = treated)) +
   geom_point(aes(color = post)) +
-  facet_wrap(~variable, scales = "free", ncol = 2) +
+  facet_wrap(gear~variable, scales = "free", ncol = 3) +
   theme_bw() +
@@
 ```{r, results = "asis", echo = F}
-m1 <- lm(hours ~ post, data = effort_by_vessel)
-m2 <- lm(hours ~ post + month, data = effort_by_vessel)
-m3 <- lm(hours ~ post + month + year, data = effort_by_vessel)
-m4 <- lm(hours ~ post + month + year + mmsi, data = effort_by_vessel)
+
+model_data <- effort_by_vessel %>% 
+  filter(gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1) %>% 
+  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)
+
+m1 <- lm(hours ~ post*treated, data = effort_by_vessel)
+m2 <- lm(hours ~ post*treated + month, data = effort_by_vessel)
+m3 <- lm(hours ~ post*treated + month + year, data = effort_by_vessel)
+m4 <- lm(hours ~ post*treated + month + year + mmsi, data = effort_by_vessel)
 
@@
 
+```{r, echo = F}
+map_df(models, broom::tidy, .id = "model") %>%
+  filter(term %in% c("(Intercept)", "postTRUE", "treatedTRUE", "postTRUE:treatedTRUE")) %>%
+  ggplot(aes(x = model, y = estimate)) +
+  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
+                size = 1,
+                width = 0,
+                color = "red") +
+  geom_point(color = "steelblue", size = 3) +
+  facet_wrap(~term, scale = "free") +
+  theme_bw()
+```
+
+# Discusion
+
 \clearpage
@@
 
-In order to strengthen this analysis, I would like to identify an appropriate sample of vessels that acccurately represent the PNA.
+<!-- In order to strengthen this analysis, I would like to identify an appropriate sample of vessels that acccurately represent the PNA.
 This vessels must meet at least these two points: i) belong to the PNA and ii) Have fished for a significant amount of time inside PIPA, to count as "treated".
@@
 number of all vessels who fished in PIPA at least once before 2015).
+-->
 
-I would also like to explore the possibility of identifying a plausible counterfactual.
+<!-- I would also like to explore the possibility of identifying a plausible counterfactual.
 That way we could do something like a DiD.
@@
 Perhaps an additional one would be that they belong to the PNA.
+-->
 
-Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time.
+<!-- Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time. -->
 
-```{r, echo = F, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:eez-hs} Percentage of catches that come from the high-seas vs. EEZs. (data from [Sea Around Us](www.seaaroundus.org))."}
-seaaroundus::eezsvshighseas() %>% 
-  magrittr::set_colnames(value = c("year", "EEZ", "High-seas")) %>% 
-  gather(source, percent, -year) %>% 
-  mutate(source = fct_relevel(source, "High-seas")) %>% 
-  ggplot2::ggplot(aes(x = year, y = percent, fill = source)) +
-  geom_area(alpha = 0.5) +
-  scale_fill_brewer(palette = "Set1") +
-  theme_bw() +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  geom_hline(yintercept = 94, linetype = "dashed") +
-  labs(x = "Year", y = "Percentage", fill = "Source")
-```
+<!-- \clearpage -->
 
-\clearpage
+<!-- # Possible contributions -->
 
-# Possible contributions
-
-As I understand the efforts made so far, there are two straightforward ways in which I could contribute to this study.
+<!-- As I understand the efforts made so far, there are two straightforward ways in which I could contribute to this study.
 For the first one I would help strengthen the analysis of NOAA Observer and GFW data for the US PNMs.
@@
 I discuss these two in greater detail in the next paragraphs.
+-->
 
-## US Pacific Monuments
+<!-- ## US Pacific Monuments -->
 
-In this section I include possible analysis in which I could help.
+<!-- In this section I include possible analysis in which I could help.
 When relevant, I include quotes to provide context.
@@
 I believe my suggestions would compliment (rather than replace) current analysis, and I acknowledged that you might have already tried some or that due to data constraints not all of them are possible.
+-->
 
-### Total revenue
+<!-- ### Total revenue -->
 
-"It is very clear from the figure that total catch of bigeye has not declined as a result of the 2014 or
-2016 expansions".
+<!-- "It is very clear from the figure that total catch of bigeye has not declined as a result of the 2014 or -->
+<!-- 2016 expansions".
 Of course, I have not reviewed the data.
@@
 At least through time there isn't an evident decrease, but what would have catches looked like had PMNM not been expanded?
+-->
 
-Not sure if the spatial resolution (*i.e.* Catch Blocks) in logbooks allows this comparison, but it would be interesting to see what proportion of catches (or at least sets / hours) originally came from waters inside the PMNM.
+<!-- Not sure if the spatial resolution (*i.e.* Catch Blocks) in logbooks allows this comparison, but it would be interesting to see what proportion of catches (or at least sets / hours) originally came from waters inside the PMNM.
 Perhaps the georeferenced catches from NOAA Observer data can provide insights into this (if not for the entire fleet, at least for the 20% quasi-random subset), or we can use GFW data to see if the proportion of fishing hours inside PMNM roughly corresponds to 10M in revenues (we can test different "catch rates" to account for the fact that catches inside vs outside may not map 1:1).
 Perhaps this catch efficiency ratio can be extracted from the NOAA Observer data?
+-->
 
-On aggregate the fleet brought in more money in 2015 and 1016 than in previous year, but you discuss the possibility that the distributional effects of this might be different.
+<!-- On aggregate the fleet brought in more money in 2015 and 1016 than in previous year, but you discuss the possibility that the distributional effects of this might be different.
 I would assume that vessels who fished the most in the PMNM area were the ones who took the toughest hit.
 If possible, it might be interesting to birefly look at distributional effects for the discussion.
+-->
 
-### Total costs (TC)
+<!-- ### Total costs (TC) -->
 
-So far this section describes the available data, but it it's not clear whether the empirical strategy is fully developed.
+<!-- So far this section describes the available data, but it it's not clear whether the empirical strategy is fully developed.
 Just like the datasets, a there isn't a single best analysis that provides the answer, but looking at it from as many was as possible might help paint a full picture of the effects that vLPAs have had.Here I provide some ideas in which we could use the two main datasets (NOAA and GFW data) to indirectly test the claims made by the fleet.
+-->
 
-#### TC from NOAA Observer program
+<!-- #### TC from NOAA Observer program -->
 
-You mention that a drawback of this dataset is that you only observe fishing events, and not the entire trip (*i.e.* the search and travel).
+<!-- You mention that a drawback of this dataset is that you only observe fishing events, and not the entire trip (*i.e.* the search and travel).
 It might be worth looking into combining this with GFW data.
@@
 If this doesn't yield better data, it would at least help determine if the three-day space between sets is an appropriate way of grouping them into "trips".
+-->
 
-Results in your table 3 suggest that there's been a change of ~ 20 miles (positive or negative depending on model specification), and not significant.
+<!-- Results in your table 3 suggest that there's been a change of ~ 20 miles (positive or negative depending on model specification), and not significant.
 Perhaps linking this data to GFW would provide full tracks (of a smaller portion of the fleet) to then account for distance between fishing points but also during the search and set activities.
+-->
 
-#### TC form GFW Data
+<!-- #### TC form GFW Data -->
 
-We could also test the increased cost claim by looking at the almost 60 vessels and calculate an estimate of fuel consumption (following @sala_2018), which, paired with fuel prices, might provide cost estimates[^1].
+<!-- We could also test the increased cost claim by looking at the almost 60 vessels and calculate an estimate of fuel consumption (following @sala_2018), which, paired with fuel prices, might provide cost estimates[^1].
 Initially this would just be a regression with a policy dummy (and appropriate vessel- and month-level FE's).
 We could look into GFW data to identify plausible counterfactuals to include  a control group[^2].
+-->
 
-[^1]: Of course, there are additional costs (*e.g.* crew, ice, bait, gear), but fuel should represent a large portion of this and should scale with some measures of fishing effort (time and distance).
+<!-- [^1]: Of course, there are additional costs (*e.g.* crew, ice, bait, gear), but fuel should represent a large portion of this and should scale with some measures of fishing effort (time and distance).
 If this is not enough, the previous comparison of catches (sets) that came from PMNM waters before the implementation could provide some insights.
+-->
 
-[^2]: GFW increased coverage when they added from more satellites, particularly towards the end of 2016 and throughout 2017, I believe.
+<!-- [^2]: GFW increased coverage when they added from more satellites, particularly towards the end of 2016 and throughout 2017, I believe.
 I think it would be important to use counterfactuals in any GFW-related analyses to account for the expected temporal trend in increased effort.
+-->
 
-# Other details
+<!-- # Other details -->
 
-- The introduction states that the main objective is to quantify the economic impacts of vLPAs and compare the cost per hectare to vLPAs on land.
+<!-- - The introduction states that the main objective is to quantify the economic impacts of vLPAs and compare the cost per hectare to vLPAs on land.
 I think this would provide an interesting benchmark on cost of conservation per unit area in land vs sea.
 I would perhaps highlight the part about predicting the possible effects of the Palau MPA.
+-->
 
-- I think the novelty of the paper can be highlighted even more.
+<!-- - I think the novelty of the paper can be highlighted even more.
 @stevenson_2013 evaluated the consequences of fishing displacement from MPAs in Hawaii (a smaller network and totally different fleet).
@@
 And also the larger contribution to vLPAs (and MPAs in general) literature.
-- Recent work by @sala_2018 shows that a large portion of high-seas fishing is only profitable thanks to subsidies. This could compliment @white_2014 and @sumaila_2015 in the introduction.
+-->
+<!-- - Recent work by @sala_2018 shows that a large portion of high-seas fishing is only profitable thanks to subsidies. This could compliment @white_2014 and @sumaila_2015 in the introduction. -->
 
-- "Neither of these datasets is perfect but hopefully combined they will paint a clear picture of what the impact has been".
+<!-- - "Neither of these datasets is perfect but hopefully combined they will paint a clear picture of what the impact has been".
 I find this to be a modest (or humble?) and powerful sentence that highlights the efforts made to identify effects from different sources, and that acknowledges possible data limitations.
 This sentence should be included alongside the "novelty" in the last paragraph of the introduction.
+-->
 
-- Findings by @smith_2006 show negative effects, but the reserves were only in place for a short period.
+<!-- - Findings by @smith_2006 show negative effects, but the reserves were only in place for a short period.
 I believe they talk about this in their discussion.
 @edgar_2014-UO and @difranco_2016-Xw show how the effects (at least inside vs outside the reserve) can take up to 10 years.
+-->
 
-- I would be cautious on the interpretation of results by @sumaila_2015.
+<!-- - I would be cautious on the interpretation of results by @sumaila_2015.
 They do show that < 0.01% of catch and landed values come *exclusively* from the high seas, but also that 67% and 72% (catch and value) come from Both EEZs and High seas, and the remaining from EEZs only.
@@
 It's perhaps a minor detail, but thought I'd point it out.
+-->
 

### 2018-09-14 docs/Manuscript.tex
Updated file

@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\usepackage[normalem]{ulem}
+% avoid problems with \sout in headers with hyperref:
+\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
 \IfFileExists{parskip.sty}{%
@@
 }
-\emph{Last update: 2018-09-07}
+\emph{Last update: 2018-09-13}
 
@@
 
+Number of vessels
+
+Explain BACI strict
+
+Analyses being run
+
+Correct number of vessels in tables
+
+Add figure legends
+
 The Global Fishing Watch (GFW) data contain 235 vessels that have fished
@@
 
-\caption{\label{tab:unnamed-chunk-3}Mean fishing hours for each gear before and after}
-\centering
-\begin{tabular}[t]{l|l|r|r|r}
-\hline
-Gear & Treated & Before & After & Change (A / B)\\
-\hline
-drifting\_longlines & FALSE & 484.47512 & 470.7382 & 0.9716458\\
-\hline
-drifting\_longlines & TRUE & 545.68460 & 523.5596 & 0.9594546\\
-\hline
-purse\_seines & FALSE & 59.64877 & 160.7945 & 2.6956886\\
-\hline
-purse\_seines & TRUE & 55.30178 & 149.9978 & 2.7123509\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-4}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-33}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
 \centering
@@
 purse\_seines & TRUE & 78 & 81 & 1.0384615\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-34}Mean fishing hours for each gear before and after}
+\centering
+\begin{tabular}[t]{l|l|r|r|r}
+\hline
+Gear & Treated & Before & After & Change (A / B)\\
+\hline
+drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
+\hline
+drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
+\hline
+purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
+\hline
+purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
 \hline
@@
 \item
-  Divide pipa vessels by type of boat (longline vs.~purse seine)
+  {[}x{]} Divide pipa vessels by type of boat (longline vs.~purse seine)
 \item
-  Identify two counterfactuals:
+  {[}x{]} Identify two counterfactuals:
 
@@
   \item
-    A:
-
-    \begin{itemize}
-    \tightlist
+    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
   \item
-      PNA
+    {[} {]} B: Taiwan, Never in PNA, Similar region
+  \end{itemize}
 \item
-      similar vessel
+  {[}x{]} Change in fishing hours before vs after
 \item
-      never fished inside PIPA -B:
+  {[} {]} \sout{Change in total hours before vs after}
 \item
-      Taiwan
+  {[} {]} Change in distance before vs after
 \item
-      Never in PNA
-    \item
-      Similar region?
-    \end{itemize}
-  \end{itemize}
-\end{itemize}
-
-Has effort increased?
-
-\begin{itemize}
-\tightlist
-\item
-  Change in fishing hours before vs after
-\item
-  Change in total hours before vs after
-\item
-  Change in distance before vs after
-\item
-  Where do PIPA vessels go?
-\item
-  How many were transient vs local?
-\end{itemize}
-
-Has search time increased?
-
-\begin{itemize}
-\tightlist
-\item
-  Distance between fishing points before vs.~after
-\item
-  Prop hour fishing before vs after
-\item
-  Time between fishing points before vs.~after
+  {[} {]} Where do PIPA vessels go?
 \end{itemize}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}\label{fig:blue_para}Monthly hours,
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
+\caption{\label{fig:unnamed-chunk-35}\label{fig:blue_para}Monthly hours,
 number of vessels, and data points observed inside PIPA. These clearly
@@
 
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}\label{fig:kir_vessels}Fishing hours and
-number of 12 Kiribati vessels from 2012 - 2016 that at some point fished
-inside PIPA.}
-\end{figure}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- post & 70.279$^{***}$ & 71.066$^{***}$ & 83.322$^{***}$ & 54.074$^{***}$ \\ 
-  & (8.951) & (8.856) & (11.471) & (12.832) \\ 
-  & & & & \\ 
- treated & $-$26.777 & $-$27.119 & $-$30.234$^{*}$ & $-$37.149 \\ 
-  & (17.881) & (17.137) & (17.434) & (40.248) \\ 
-  & & & & \\ 
- post:treated &  &  &  &  \\ 
-  &  &  &  &  \\ 
-  & & & & \\ 
- Constant & 81.770$^{***}$ & 88.095$^{***}$ & 70.812$^{***}$ & 126.560$^{***}$ \\ 
-  & (18.737) & (23.142) & (24.053) & (34.921) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & No & Yes & Yes & Yes \\ 
-Year FE & No & No & Yes & Yes \\ 
-Vessel FE & No & No & No & Yes \\ 
-Observations & 344 & 344 & 344 & 344 \\ 
-R$^{2}$ & 0.170 & 0.191 & 0.219 & 0.383 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
 \clearpage
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels that fished inside PIPA at
-least once.}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
+\caption{\label{fig:unnamed-chunk-36}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels that fished inside PIPA
+at least once.}
 \end{figure}
+
+\subsection{Purse seiners}\label{purse-seiners}
 
@@
 \hline \\[-1.8ex] 
- post & 45.766$^{***}$ & 45.268$^{***}$ & 41.959$^{***}$ & 45.596 \\ 
-  & (6.534) & (6.504) & (8.779) &  \\ 
+ post & 105.873$^{***}$ & 107.859$^{***}$ & 113.466$^{***}$ & 102.890$^{***}$ \\ 
+  & (5.532) & (5.364) & (5.887) & (6.076) \\ 
   & & & & \\ 
- treated & 50.000$^{***}$ & 51.321$^{***}$ & 50.749$^{***}$ & $-$457.705 \\ 
-  & (6.771) & (6.759) & (6.813) &  \\ 
+ treated & $-$9.632$^{**}$ & $-$8.924$^{**}$ & $-$8.334$^{**}$ & $-$3.076 \\ 
+  & (4.257) & (4.023) & (3.725) & (4.540) \\ 
   & & & & \\ 
- postTRUE:treated & $-$59.473$^{***}$ & $-$58.530$^{***}$ & $-$57.494$^{***}$ & $-$21.059 \\ 
-  & (8.463) & (8.432) & (8.491) &  \\ 
+ post:treated & $-$16.544$^{**}$ & $-$16.889$^{***}$ & $-$17.235$^{***}$ & $-$11.150$^{*}$ \\ 
+  & (6.481) & (6.358) & (6.126) & (6.162) \\ 
   & & & & \\ 
- Constant & 349.582$^{***}$ & 328.470$^{***}$ & 333.794$^{***}$ & 483.665 \\ 
-  & (5.635) & (8.833) & (10.226) &  \\ 
+ Constant & 66.505$^{***}$ & 61.758$^{***}$ & 40.085$^{***}$ & 61.569$^{***}$ \\ 
+  & (3.780) & (5.352) & (5.699) & (9.753) \\ 
   & & & & \\ 
@@
 Year FE & No & No & Yes & Yes \\ 
-Vessel FE & No & No & No & Yes \\ 
-Observations & 15,885 & 15,885 & 15,885 & 15,885 \\ 
-R$^{2}$ & 0.004 & 0.011 & 0.011 & 0.632 \\ 
+Flag FE & No & No & No & Yes \\ 
+Observations & 3,692 & 3,692 & 3,692 & 3,692 \\ 
+R$^{2}$ & 0.238 & 0.262 & 0.312 & 0.339 \\ 
 \hline 
@@
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
+
+\subsection{Longliners}\label{longliners}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robuste standard errors.}
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ post & $-$7.843 & $-$4.894 & $-$7.580 & 24.708$^{***}$ \\ 
+  & (7.514) & (7.480) & (9.336) & (9.315) \\ 
+  & & & & \\ 
+ treated & 66.801$^{***}$ & 69.434$^{***}$ & 69.959$^{***}$ & 18.878$^{***}$ \\ 
+  & (6.541) & (6.549) & (6.603) & (7.257) \\ 
+  & & & & \\ 
+ post:treated & $-$15.571$^{*}$ & $-$17.806$^{**}$ & $-$18.340$^{**}$ & $-$25.775$^{***}$ \\ 
+  & (8.958) & (8.899) & (8.936) & (8.743) \\ 
+  & & & & \\ 
+ Constant & 481.425$^{***}$ & 450.475$^{***}$ & 447.866$^{***}$ & 430.947$^{***}$ \\ 
+  & (5.733) & (9.239) & (10.280) & (24.476) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & No & Yes & Yes & Yes \\ 
+Year FE & No & No & Yes & Yes \\ 
+Flag FE & No & No & No & Yes \\ 
+Observations & 8,558 & 8,558 & 8,558 & 8,558 \\ 
+R$^{2}$ & 0.026 & 0.044 & 0.044 & 0.107 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
 

### 2018-09-14 rmd/Manuscript.Rmd
Updated file

@@
 
-```{r, echo = F}
+```{r, echo = F, message = F, warning = F}
 suppressPackageStartupMessages({
@@
 
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      message = FALSE)
 ```
@@
 
-```{r, echo = F}
-vessel_info_pipa <- read.csv(here::here("data", "vessel_info_mmsi_inside_pipa.csv"), stringsAsFactors = F) %>% 
-  mutate(treated = T)
+Number of vessels
 
-vessel_info_pna <- read.csv(here::here("data", "vessel_info_mmsi_inside_pna.csv"), stringsAsFactors = F) %>% 
-  mutate(treated = F)
+Explain BACI strict
 
-vessel_info <- rbind(vessel_info_pipa, vessel_info_pna) %>% 
-  rename(gear = inferred_label)
+Analyses being run
 
+Correct number of vessels in tables
+
+Add figure legends
+
+```{r}
+effort_by_vessel <- read.csv(file = here::here("data", "effort_by_vessel.csv"))
+```
+
+```{r}
+# Just to get pipa vessels that fished inside pipa before 2015
 pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))
@@
 ```{r}
-effort_by_vessel <- read.csv(here::here("data", "pipa_effort_by_vessel.csv"), stringsAsFactors = F) %>% 
-  rbind(read.csv(here::here("data", "pna_vessels_outside_pipa.csv"), stringsAsFactors = F)) %>% 
-  left_join(vessel_info, by = c("mmsi", "year")) %>% 
-  filter(gear %in% c("purse_seines", "drifting_longlines")) %>%
-  mutate(mmsi = as.character(mmsi),
-         month = as.character(month),
-         year = as.character(year))
-
-effort_by_vessel %>%  
-  group_by(gear, treated, post) %>% 
-  summarize(hours = mean(hours, na.rm = T)) %>% 
-  spread(post, hours) %>% 
-  mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
-               caption = "Mean fishing hours for each gear before and after")
-```
-
-```{r}
 effort_by_vessel %>% 
@@
                caption = "Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.")
+```
+
+```{r}
+effort_by_vessel %>%
+  filter(baci_strict) %>%
+  group_by(gear, treated, post) %>% 
+  summarize(hours = mean(hours, na.rm = T)) %>% 
+  spread(post, hours) %>% 
+  mutate(change = `TRUE` / `FALSE`) %>% 
+  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
+               caption = "Mean fishing hours for each gear before and after")
 ```
@@
 
-- Divide pipa vessels by type of boat (longline vs. purse seine)
-- Identify two counterfactuals:
-    - A:
-        - PNA
-        - similar vessel
-        - never fished inside PIPA
-    -B:
-        - Taiwan
-        - Never in PNA
-        - Similar region?
-
-Has effort increased?
-
-- Change in fishing hours before vs after
-- Change in total hours before vs after
-- Change in distance before vs after
-- Where do PIPA vessels go?
-- How many were transient vs local?
-
-Has search time increased?
-
-- Distance between fishing points before vs. after
-- Prop hour fishing before vs after
-- Time between fishing points before vs. after
+- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
+- [x] Identify two counterfactuals:
+    -  [x] A: PNA, similar vessel, never fished inside PIPA
+    - [ ] B: Taiwan, Never in PNA, Similar region
+- [x] Change in fishing hours before vs after
+- [ ] ~~Change in total hours before vs after~~
+- [ ] Change in distance before vs after
+- [ ] Where do PIPA vessels go?
 
@@
 
-```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect."}
+```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect.", fig.height = 3, fig.width = 6}
 # This is just to show the blue paradox, no need to include this figure
@@
 
-```{r, echo = F, fig.cap = "\\label{fig:kir_vessels}Fishing hours and number of 12 Kiribati vessels from 2012 - 2016 that at some point fished inside PIPA."}
-effort_by_vessel %>% 
-  filter(kir, treated) %>% 
-  group_by(year, month, mmsi, gear) %>% 
-  summarize(hours = sum(hours)) %>% 
-  group_by(year, month, gear) %>% 
-  summarize(total_hours = sum(hours),
-            mean_hours = mean(hours),
-            n_mmsi = n()) %>% 
-  ungroup() %>% 
-  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
-         post = year >= 2015) %>% 
-  select(-year) %>% 
-  gather(variable, value, -c(date, month, post, gear)) %>% 
-  ggplot(aes(x = date, y = value)) +
-  geom_line() +
-  geom_point(aes(color = post)) +
-  facet_wrap(gear~variable, scales = "free_y", ncol = 3) +
-  theme_bw() +
-  scale_color_brewer(palette = "Set1")
-```
-
-```{r, results = "asis", echo = F}
-kir_vessel <- effort_by_vessel %>% 
-  filter(kir, gear == "purse_seines") %>% 
-  mutate(post = post * 1,
-         treated = treated * 1)
-
-m1 <- lm(hours ~ post*treated, data = kir_vessel)
-m2 <- lm(hours ~ post*treated + month, data = kir_vessel)
-m3 <- lm(hours ~ post*treated + month + year, data = kir_vessel)
-m4 <- lm(hours ~ post*treated + month + year + mmsi, data = kir_vessel)
-
-models <- list(m1, m2, m3, m4)
-
-stargazer::stargazer(models,
-                     se = commarobust::makerobustseslist(models),
-                     t.auto = T,
-                     p.auto = T,
-                     type = "latex",
-                     omit = c("mmsi", "year", "month"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
-                                      c("Year FE", "No", "No", "Yes", "Yes"),
-                                      c("Vessel FE", "No", "No", "No", "Yes")),
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     title = "\\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
-```
-
 \clearpage
@@
 effort_by_vessel %>% 
+  filter(baci_strict) %>%
   group_by(year, gear, treated, post, month) %>% 
@@
 
+## Purse seiners
+
 ```{r, results = "asis", echo = F}
@@
 model_data <- effort_by_vessel %>% 
-  filter(gear == "purse_seines") %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
   mutate(post = post * 1,
@@
 
-m1 <- lm(hours ~ post*treated, data = effort_by_vessel)
-m2 <- lm(hours ~ post*treated + month, data = effort_by_vessel)
-m3 <- lm(hours ~ post*treated + month + year, data = effort_by_vessel)
-m4 <- lm(hours ~ post*treated + month + year + mmsi, data = effort_by_vessel)
+m1 <- lm(hours ~ post*treated, data = model_data)
+m2 <- lm(hours ~ post*treated + month, data = model_data)
+m3 <- lm(hours ~ post*treated + month + year, data = model_data)
+m4 <- lm(hours ~ post*treated + month + year + flag, data = model_data)
 
@@
                      type = "latex",
-                     omit = c("mmsi", "year", "month"),
+                     omit = c("flag", "year", "month"),
                      add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                       c("Year FE", "No", "No", "Yes", "Yes"),
-                                      c("Vessel FE", "No", "No", "No", "Yes")),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
                      omit.stat = c("adj.rsq", "f", "ser"),
@@
 
+map_df(models, broom::tidy, .id = "model") %>%
+  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
+  ggplot(aes(x = model, y = estimate)) +
+  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
+                size = 1,
+                width = 0,
+                color = "red") +
+  geom_point(color = "steelblue", size = 3) +
+  facet_wrap(~term, scale = "free") +
+  theme_bw()
 ```
 
-```{r, echo = F}
+## Longliners
+
+```{r, results = "asis"}
+
+model_data <- effort_by_vessel %>% 
+  filter(baci_strict,
+         !gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1) %>% 
+  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)
+
+m1 <- lm(hours ~ post*treated, data = model_data)
+m2 <- lm(hours ~ post*treated + month, data = model_data)
+m3 <- lm(hours ~ post*treated + month + year, data = model_data)
+m4 <- lm(hours ~ post*treated + month + year + flag, data = model_data)
+
+models <- list(m1, m2, m3, m4)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("flag", "year", "month"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
+                                      c("Year FE", "No", "No", "Yes", "Yes"),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
+
 map_df(models, broom::tidy, .id = "model") %>%
-  filter(term %in% c("(Intercept)", "postTRUE", "treatedTRUE", "postTRUE:treatedTRUE")) %>%
+  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
   ggplot(aes(x = model, y = estimate)) +

### 2018-09-14 docs/Manuscript.tex
Updated analyses

@@
 \hypersetup{unicode=true,
-            pdftitle={Displacement effects and implications of Large-Scale Marine Protected Areas},
+            pdftitle={Displacement effects in PIPA},
+            pdfauthor={Juan Carlos Villaseñor-Derbez},
             pdfborder={0 0 0},
@@
 \setlength{\droptitle}{-2em}
-  \title{Displacement effects and implications of Large-Scale Marine Protected
-Areas}
+  \title{Displacement effects in PIPA}
   \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-  \author{Juan Carlos Villaseñor-Derbez \textsuperscript{1} John Lynham
-\textsuperscript{2}}
+  \author{Juan Carlos Villaseñor-Derbez}
   \preauthor{\centering\large\emph}
   \postauthor{\par}
-  \predate{\centering\large\emph}
-  \postdate{\par}
-  \date{\textsuperscript{1} Bren School of Environmental Science \& Management,
-University of California, Santa Barbara \textsuperscript{2} Department
-of Economics, Saunders Hall 532, University of Hawai`i at Manoa}
+  \date{}
+  \predate{}\postdate{}
 
 \usepackage{float}
-\floatplacement{figure}{H}
+\floatplacement{figure,table}{H}
 
@@
 \maketitle
-\begin{abstract}
-Large-scale Marine Protected Areas (LSMPAs) have seen a significant
-increase over the last years. Literature shows that fishing effort is
-effectively eliminated in this protected areas upon implementation. The
-benefits of reducing effort have been largely studied, and include
-increases in abundance, biomass, and diversity within the bounded
-regions. In terms of the fishing implication, no-take zones may produce
-spillover that provide fish for outside areas. The implications of
-displacement of fishing effort are not yet fully understood. Evidence
-suggests that fishing effort re-distributes along the borders of the
-MPA, following an ideal free distribution. Novel data products allow us
-to track fishing effort at the vessel-level, allowing us to identify
-changes in behavior at both the fleet and vessel level. This papers
-evaluates the implications of implementing a LMPA, the Phoenix Islands
-Protected Area (PIPA). We evaluate changes in fishing effort, and track
-vessels to see where they go after the implementation of PIPA. Our
-results show that vessels in the effected region increase fishing effort
-after the implementation of PIPA. THey are redistributed to X. These
-findings have major implications for MPA implementation, especially as
-countries rush to meet the goals of 10\% ocean protection as mandated by
-the SDG.
-\end{abstract}
 
@@
 }
-\emph{Last update: 2018-09-13}
+\emph{Last update: 2018-09-14}
 
-\section{Introduction}\label{introduction}
-
-The rest of the paper is outlined as follows: Section \ref{background}
-provides further information about PIPA and Palau, section \ref{methods}
-describes our data and empirical strategy, section \ref{results}
-presents our results, in section \ref{discussion} we discuss our
-findings and provide management recommendations.
-
-\section{Background}\label{background}
-
-\section{Methods}\label{methods}
-
-\subsection{Data}\label{data}
-
-Number of vessels
-
-Explain BACI strict
-
-Analyses being run
-
-Correct number of vessels in tables
-
-Add figure legends
-
-The Global Fishing Watch (GFW) data contain 235 vessels that have fished
-within PIPA waters \footnote{Perhaps some of these vessels only fished
-  there for a couple hours one year. Therefore, I would need to further
-  identify which ones were transient vs constant fishing events using
-  some cutoff. For now, I run regressions for all vessels and for
-  vessels that fly the Kiribati flag (n = 12). The true number of
-  impacted vessels must lie between these two groups, but it provides a
-  starting point.}. From these, 206 did so at least once before 2015.
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-33}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
-\centering
-\begin{tabular}[t]{l|l|r|r|r}
-\hline
-Gear & Treated & Before & After & Change (A / B)\\
-\hline
-drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
-\hline
-drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
-\hline
-purse\_seines & FALSE & 49 & 89 & 1.8163265\\
-\hline
-purse\_seines & TRUE & 78 & 81 & 1.0384615\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-34}Mean fishing hours for each gear before and after}
-\centering
-\begin{tabular}[t]{l|l|r|r|r}
-\hline
-Gear & Treated & Before & After & Change (A / B)\\
-\hline
-drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
-\hline
-drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
-\hline
-purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
-\hline
-purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
-\hline
-\end{tabular}
-\end{table}
-
-Then, I look at the entire fishing effort of vessels that fished at
-least once in PIPA before 2015. In other words, I use GFW data to track
-vessel-level activities inside and outside PIPA before and after 2015.
-However, all boats included in this case fished at least once in PIPA
-before 2015 (\emph{i.e.} no control group). First I look at vessels
-whose \texttt{mmsi} code starts with \texttt{529}, indicating that they
-come from Kiribati \footnote{link:
-  \url{http://www.vtexplorer.com/mmsi-mid-codes-en/}}. The overall
-pattern for fishing time (total and mean) show a downward trend that
-initiated well before 2015 (Fig. \ref{fig:kir_vessels}). The number of
-vessels as given by unique mmsi numbers shows a maximum near the end of
-2014, and then decreases after 2015.
-
-\subsection{Analysis}\label{analysis}
-
-\subsubsection{To do}\label{to-do}
+\section{To do}\label{to-do}
 
@@
   {[} {]} Where do PIPA vessels go?
+\item
+  {[} {]} Make sure I have full tracks of all mmsis
 \end{itemize}
+
+\clearpage
+
+\section{Methods}\label{methods}
+
+\subsection{Data}\label{data}
+
+The Global Fishing Watch (GFW) data contain 233 vessels that have fished
+within PIPA waters. From these, 217 did so at least once before 2015,
+but only 183 continued to fish after 2015. The 34 missing vessels might
+tell us something about the impact of PIPA. However, they might have
+gone to other areas (i.e.~outside of PNA countries). I must dig deeper
+into this.
+
+Accounting for the fact that vessels that fished within PIPA before
+implementation might stop fishing afterwards, or that vessels entered
+the fishery after PIPA closure, I define my treatment and control groups
+as follows. The treatment group contains all vessels that fished within
+PIPA at least once before the closure, and that continued to fish
+elsewhere afterwards. The Control group has vessels that never fished
+within PIPA waters, belong to other PNA countries, and have fished in
+surroinding areas before and after PIPA closure. Tables
+\ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the
+number of vessels, number of vessels following a BACI design, and
+fishing hours, respectively. Tables show data grouped by gear
+(longlines, purse seines), group (treated, control), and period (before,
+after). The relative change (After / Before) is also shown. Table
+\ref{tab:baci_n} shows information for all fishing vessels in the
+dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show
+information for vessels that meet the BACI design (i.e.~excludes vessels
+that only appear at one point in time).
+
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-4}\label{tab:baci_n}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
+\centering
+\begin{tabular}[t]{llrrr}
+\toprule
+Gear & Treatment & Before & After & Change (A / B)\\
+\midrule
+drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
+drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
+purse\_seines & FALSE & 49 & 89 & 1.8163265\\
+purse\_seines & TRUE & 78 & 81 & 1.0384615\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
+\centering
+\begin{tabular}[t]{llrrr}
+\toprule
+Gear & Treatment & Before & After & Change (A / B)\\
+\midrule
+drifting\_longlines & FALSE & 88 & 88 & 1\\
+drifting\_longlines & TRUE & 115 & 115 & 1\\
+purse\_seines & FALSE & 38 & 38 & 1\\
+purse\_seines & TRUE & 68 & 68 & 1\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours for each gear before and after}
+\centering
+\begin{tabular}[t]{llrrr}
+\toprule
+Gear & Treatment & Before & After & Change (A / B)\\
+\midrule
+drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
+drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
+purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
+purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Analysis}\label{analysis}
 
@@
 
-Our model specification uses a difference-in-differences approach. In
-this case, we interact the before-after dummy with a treatment dummy.
-The treatment-control groups follow our definition in the data
-description. The model takes the form of:
+Our model specification uses a DiD approach. In this case, we interact
+the before-after dummy with a treatment dummy. The treatment and control
+groups follow our definition in the data description. The model takes
+the form of:
 
 \[
-H_{ijk} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \epsilon_{ijk}
+H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
 \]
+
+Where \(\mu_j\), \(\phi_k\), and \(\gamma_l\) represent month-, year-,
+and flag-level fixed effects. I use total hours at the vessel-month
+level.
 
@@
 
-In this section I present some of the preliminary results of regressions
-similar to what you have conducted for US MNMs using hours as an
-estimate of fishing effort. First, I explore patterns of fishing effort
-only inside PIPA (Fig. \ref{fig:blue_para}). Consistent with the blue
-paradox \citep{mcdermott_2018}, we see an increase in the number of
-vessels, total hours, mean hours, and number of data points between 2014
-and 2015. Shortly after that, all measures decrease in 2015.
+Fig. \ref{fig:all_vessels} shows that mean fishing hours for purse
+seiners have an abrupt increase, just before January 1st, 2015. This
+trend is observed for both treated and control groups. Longliners,
+however, show a more stable trend. The number of mmsi codes increases
+through time. This can largel be explained by the addition of more
+satellits, which increasedetectability of vessels. As expected total
+fishing hours follow a similar trend to that of mmsi numbers. Results of
+the regressions for each gear type are shown in Tables \ref{tab:purse}
+and \ref{tab:long}. Column (1) presents the DiD regression with no fixed
+effects, column (2) includes month fixed effects, column (3) includes
+month and year fixed effects, and column (4) includes month, year, and
+flag fixed effects. Figures \ref{fig:puse} and \ref{fig:long} represent
+the same coefficient estimates.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
-\caption{\label{fig:unnamed-chunk-35}\label{fig:blue_para}Monthly hours,
-number of vessels, and data points observed inside PIPA. These clearly
-show the blue-paradox effect.}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
+number of vessels by month for all vessels. Vertical dashed line
+indicates PIPA closure.}
 \end{figure}
@@
 
-Given the similar trends observed in total fishing hours and mean
-fishing hours, I calculate total fishing hours at the year-month-vessel
-level and regress that on a \texttt{post} dummy that indicates years
-before or after 2015, which is interacted with a \texttt{treated} dummy
-that indicates if vessels fished at least once within PIPA or only in
-PNA waters. Results of this regression are presented in Table
-\ref{tab:kir_vessels}. In this table, column (1) presents the regression
-only against the policy dummy, column (2) includes month fixed effects,
-column (3) includes month and year fixed effects, and column (4)
-includes month, year, and vessel fixed effects. All three specifications
-show negative coefficients. The full model explains 71\% of the variance
-in monthly fishing hours by vessel. This specification has the lowest
-policy coefficient (labeled \texttt{post}), and it is not different from
-zero at the \(\alpha = 0.05\) level.
-
-\clearpage
-
-I then repeat a similar analysis but for all fishing vessels that fished
-at least once inside PIPA before 2015. In this case this likely
-represents an underestimate of the effect, as it could include vessels
-who once fished inside PIPA, but are not even in the region any more.
-The number of unique mmsi codes (Fig. \ref{fig:all_vessels}) follows a
-similar pattern as in the previous case. However, mean hours and total
-hours show stable trends before and after. As opposed to only Kiribati
-vessels who seemed to reduce the number of fishing hours, a similar
-analysis of all vessels shows positive coefficients that are not
-statistically significant (\(alpha < 0.05\)). Results of the regressions
-are shown in Table \ref{tab:all_vessels}. Like before, column (1)
-presents the regression only against the policy dummy, column (2)
-includes month fixed effects, column (3) includes month and year fixed
-effects, and column (4) includes month, year, and vessel fixed effects.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
-\caption{\label{fig:unnamed-chunk-36}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels that fished inside PIPA
-at least once.}
-\end{figure}
-
 \subsection{Purse seiners}\label{purse-seiners}
@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+  \caption{\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
 Asterisks indicate significance levels.
@@
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{\label{fig:unnamed-chunk-9}\label{fig:puse}Coefficient estimates
+for each model. Top pannel indicates variable, x-axis represents model
+specification, and y-axis coefficient estimate.}
+\end{figure}
+
+\clearpage
 
@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment)..
 Asterisks indicate significance levels.
@@
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
-
-\section{Discusion}\label{discusion}
-
-\clearpage
-
-\subsubsection{Further work}\label{further-work}
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}\label{fig:long}Coefficient estimates
+for each model. Top pannel indicates variable, x-axis represents model
+specification, and y-axis coefficient estimate.}
+\end{figure}
 

### 2018-09-14 rmd/Manuscript.Rmd
Updated analyses

@@
 ---
-title: "Displacement effects and implications of Large-Scale Marine Protected Areas"
-author: |
-  Juan Carlos Villaseñor-Derbez ^1^
-  John Lynham ^2^
-date: |
-  ^1^ Bren School of Environmental Science & Management, University of California, Santa Barbara
-  ^2^ Department of Economics, Saunders Hall 532, University of Hawai`i at Manoa
-abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
+title: "Displacement effects in PIPA"
+author: "Juan Carlos Villaseñor-Derbez"
+# abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
 Literature shows that fishing effort is effectively eliminated in this protected areas upon implementation.
@@
   - \usepackage{float}
-  - \floatplacement{figure}{H}
+  - \floatplacement{figure,table}{H}
 bibliography: references.bib
@@
 
-# Introduction
+# To do
 
-The rest of the paper is outlined as follows: Section \ref{background} provides further information about PIPA and Palau, section \ref{methods} describes our data and empirical strategy, section \ref{results} presents our results, in section \ref{discussion} we discuss our findings and provide management recommendations.
+- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
+- [x] Identify two counterfactuals:
+    -  [x] A: PNA, similar vessel, never fished inside PIPA
+    - [ ] B: Taiwan, Never in PNA, Similar region
+- [x] Change in fishing hours before vs after
+- [ ] ~~Change in total hours before vs after~~
+- [ ] Change in distance before vs after
+- [ ] Where do PIPA vessels go?
+- [ ] Make sure I have full tracks of all mmsis
 
-# Background
+\clearpage
 
@@
 ## Data
-
-Number of vessels
-
-Explain BACI strict
-
-Analyses being run
-
-Correct number of vessels in tables
-
-Add figure legends
 
@@
 # Just to get pipa vessels that fished inside pipa before 2015
-pipa_vessels <- read.csv(here::here("data", "vessels_inside_pipa.csv"))
+pipa_vessels <- effort_by_vessel %>% 
+  filter(treated) %$%
+  unique(mmsi) %>% 
+  length()
 
-n_prev <- pipa_vessels %>% 
-  filter(year < 2015) %>%
-  group_by(year, mmsi) %>% 
-  summarize(n_points = sum(n_points),
-            hours = sum(total_fishing_hours))
+n_prev <- effort_by_vessel %>% 
+  filter(treated, !post) %$%
+  unique(mmsi) %>% 
+  length()
 
-mmsis <- unique(n_prev$mmsi)
+n_post <- effort_by_vessel %>% 
+  filter(treated, post, baci_strict) %$%
+  unique(mmsi) %>% 
+  length()
+
 ```
 
-The Global Fishing Watch (GFW) data contain `r length(unique(pipa_vessels$mmsi))` vessels that have fished within PIPA waters [^3]. From these, `r length(mmsis)` did so at least once before 2015.
+The Global Fishing Watch (GFW) data contain `r pipa_vessels` vessels that have fished within PIPA waters.
+From these, `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015.
+The `r n_prev - n_post` missing vessels might tell us something about the impact of PIPA.
+However, they might have gone to other areas (i.e.
+outside of PNA countries).
+I must dig deeper into this.
 
-[^3]: Perhaps some of these vessels only fished there for a couple hours one year.
-Therefore, I would need to further identify which ones were transient vs constant fishing events using some cutoff.
-For now, I run regressions for all vessels and for vessels that fly the Kiribati flag (n = 12).
-The true number of impacted vessels must lie between these two groups, but it provides a starting point.
+Accounting for the fact that vessels that fished within PIPA before implementation might stop fishing afterwards, or that vessels entered the fishery after PIPA closure, I define my treatment and control groups as follows.
+The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
+The Control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surroinding areas before and after PIPA closure.
+Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively.
+Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after).
+The relative change (After / Before) is also shown.
+Table \ref{tab:baci_n} shows information for all fishing vessels in the dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show information for vessels that meet the BACI design (i.e.
+excludes vessels that only appear at one point in time).
 
@@
 effort_by_vessel %>% 
+  # filter(baci_strict) %>%
   group_by(gear, treated, post, mmsi) %>% 
@@
   mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
-               caption = "Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.")
+  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
+               caption = "\\label{tab:baci_n}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.",
+               booktabs = T) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+```{r}
+effort_by_vessel %>% 
+  filter(baci_strict) %>%
+  group_by(gear, treated, post, mmsi) %>% 
+  count() %>% 
+  ungroup() %>% 
+  group_by(gear, treated, post) %>% 
+  summarize(boats = n()) %>% 
+  spread(post, boats) %>% 
+  mutate(change = `TRUE` / `FALSE`) %>% 
+  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
+               caption = "\\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.",
+               booktabs = T) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
   mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treated", "Before", "After", "Change (A / B)"),
-               caption = "Mean fishing hours for each gear before and after")
+  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
+               caption = "\\label{tab:baci_h}Mean fishing hours for each gear before and after",
+               booktabs = T) %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
 
-Then, I look at the entire fishing effort of vessels that fished at least once in PIPA before 2015.
-In other words, I use GFW data to track vessel-level activities inside and outside PIPA before and after 2015.
-However, all boats included in this case fished at least once in PIPA before 2015 (*i.e.* no control group).
-First I look at vessels whose `mmsi` code starts with `529`, indicating that they come from Kiribati [^4].
-The overall pattern for fishing time (total and mean) show a downward trend that initiated well before 2015 (Fig.
-\ref{fig:kir_vessels}).
-The number of vessels as given by unique mmsi numbers shows a maximum near the end of 2014, and then decreases after 2015.
-
-[^4]: link: [http://www.vtexplorer.com/mmsi-mid-codes-en/](http://www.vtexplorer.com/mmsi-mid-codes-en/)
-
 ## Analysis
-
-### To do
-
-- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
-- [x] Identify two counterfactuals:
-    -  [x] A: PNA, similar vessel, never fished inside PIPA
-    - [ ] B: Taiwan, Never in PNA, Similar region
-- [x] Change in fishing hours before vs after
-- [ ] ~~Change in total hours before vs after~~
-- [ ] Change in distance before vs after
-- [ ] Where do PIPA vessels go?
 
@@
 
-Our model specification uses a difference-in-differences approach.
+Our model specification uses a DiD approach.
 In this case, we interact the before-after dummy with a treatment dummy.
-The treatment-control groups follow our definition in the data description.
+The treatment and control groups follow our definition in the data description.
 The model takes the form of:
@@
 $$
-H_{ijk} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \epsilon_{ijk}
+H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
 $$
+
+Where $\mu_j$, $\phi_k$, and $\gamma_l$ represent month-, year-, and flag-level fixed effects. I use total hours at the vessel-month level.
 
@@
 
-In this section I present some of the preliminary results of regressions similar to what you have conducted for US MNMs using hours as an estimate of fishing effort.
-First, I explore patterns of fishing effort only inside PIPA (Fig.
-\ref{fig:blue_para}).
-Consistent with the blue paradox \citep{mcdermott_2018}, we see an increase in the number of vessels, total hours, mean hours, and number of data points between 2014 and 2015.
-Shortly after that, all measures decrease in 2015.
+Fig.
+\ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
+This trend is observed for both treated and control groups.
+Longliners, however, show a more stable trend.
+The number of mmsi codes increases through time.
+This can largel be explained by the addition of more satellits, which increasedetectability of vessels.
+As expected total fishing hours follow a similar trend to that of mmsi numbers.
+Results of the regressions for each gear type are shown in Tables \ref{tab:purse} and \ref{tab:long}.
+Column (1) presents the DiD regression with no fixed effects, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and flag fixed effects.
+Figures \ref{fig:puse} and \ref{fig:long} represent the same coefficient estimates.
 
-```{r, echo = F, fig.cap = "\\label{fig:blue_para}Monthly hours, number of vessels, and data points observed inside PIPA. These clearly show the blue-paradox effect.", fig.height = 3, fig.width = 6}
-# This is just to show the blue paradox, no need to include this figure
-pipa_vessels %>% 
-  group_by(year, month, mmsi) %>% 
-  summarize(n_points = sum(n_points),
-            hours = sum(total_fishing_hours)) %>% 
-  group_by(year, month) %>% 
-  summarize(total_hours = sum(hours),
-            mean_hours = mean(hours),
-            n_points = sum(n_points),
-            n_mmsi = n()) %>% 
-  ungroup() %>% 
-  mutate(date = lubridate::date(paste(year, month, "01", sep = "/")),
-         post = year >= 2015) %>% 
-  select(-year) %>% 
-  gather(variable, value, -c(date, month, post)) %>% 
-  ggplot(aes(x = date, y = value)) +
-  geom_line() +
-  geom_point(aes(color = post)) +
-  facet_wrap(~variable, scales = "free", ncol = 2) +
-  theme_bw() +
-  scale_color_brewer(palette = "Set1")
-```
-
-\clearpage
-
-Given the similar trends observed in total fishing hours and mean fishing hours, I calculate total fishing hours at the year-month-vessel level and regress that on a `post` dummy that indicates years before or after 2015, which is interacted with a `treated` dummy that indicates if vessels fished at least once within PIPA or only in PNA waters.
-Results of this regression are presented in Table \ref{tab:kir_vessels}.
-In this table, column (1) presents the regression only against the policy dummy, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and vessel fixed effects.
-All three specifications show negative coefficients.
-The full model explains 71% of the variance in monthly fishing hours by vessel.
-This specification has the lowest policy coefficient (labeled `post`), and it is not different from zero at the $\alpha = 0.05$ level.
-
-\clearpage
-
-I then repeat a similar analysis but for all fishing vessels that fished at least once inside PIPA before 2015.
-In this case this likely represents an underestimate of the effect, as it could include vessels who once fished inside PIPA, but are not even in the region any more.
-The number of unique mmsi codes (Fig.
-\ref{fig:all_vessels}) follows a similar pattern as in the previous case.
-However, mean hours and total hours show stable trends before and after.
-As opposed to only Kiribati vessels who seemed to reduce the number of fishing hours, a similar analysis of all vessels shows positive coefficients that are not statistically significant ($alpha < 0.05$).
-Results of the regressions are shown in Table \ref{tab:all_vessels}.
-Like before, column (1) presents the regression only against the policy dummy, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and vessel fixed effects.
-
-```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels that fished inside PIPA at least once."}
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
 effort_by_vessel %>% 
@@
   gather(variable, value, -c(date, month, post, gear, treated)) %>% 
-  ggplot(aes(x = date, y = value, group = treated)) +
-  geom_line(aes(linetype = treated)) +
-  geom_point(aes(color = post)) +
+  ggplot(aes(x = date, y = value, color = treated)) +
+  geom_line() +
+  geom_point() +
   facet_wrap(gear~variable, scales = "free", ncol = 3) +
   theme_bw() +
-  scale_color_brewer(palette = "Set1")
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
 ```
+
+\clearpage
 
@@
                      header = F,
-                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
 Asterisks indicate significance levels.
 Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
+```
 
+```{r, fig.cap = "\\label{fig:puse}Coefficient estimates for each model. Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
 map_df(models, broom::tidy, .id = "model") %>%
@@
 ```
+
+\clearpage
 
@@
                      header = F,
-                     title = "\\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA.
+                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment)..
 Asterisks indicate significance levels.
 Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
+```
 
+```{r, fig.cap = "\\label{fig:long}Coefficient estimates for each model. Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
 map_df(models, broom::tidy, .id = "model") %>%
@@
 
-# Discusion
+<!-- # Discusion -->
 
-\clearpage
-
-### Further work
+<!-- ### Further work -->
 
@@
 Ideally, this would get rid of vessels that sporadically fished for insignificant time in PIPA, and are therefore unlikely to be affected.
-This would include between 12 and `r length(unique(n_prev$mmsi))` vessels (number of Kiribati vessels vs.
+This would include between 12 and  vessels (number of Kiribati vessels vs.
 number of all vessels who fished in PIPA at least once before 2015).

### 2018-09-27 docs/Manuscript.tex
Updated scripts and manuscript

@@
 \hypersetup{unicode=true,
-            pdftitle={Displacement effects in PIPA},
-            pdfauthor={Juan Carlos Villaseñor-Derbez},
+            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
             pdfborder={0 0 0},
@@
 \setlength{\droptitle}{-2em}
-  \title{Displacement effects in PIPA}
+
+  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
     \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-  \author{Juan Carlos Villaseñor-Derbez}
+  \subtitle{Updated on 2018-09-27}
+  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
+Lynham\textsuperscript{2}}
     \preauthor{\centering\large\emph}
   \postauthor{\par}
-  \date{}
-  \predate{}\postdate{}
+      \predate{\centering\large\emph}
+  \postdate{\par}
+    \date{\textsuperscript{1} Bren School of Environmental Science and Management,
+University of California Santa Barbara, Santa Barbara, CA
+\textsuperscript{2} Department of Economics, University of Hawaii at
+Manoa, Honolulu, HI}
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
 \maketitle
+\begin{abstract}
+Large-scale Marine Protected Areas (LSMPAs) have seen a significant
+increase over the last years. Fishing effort is effectively eliminated
+within these protected areas upon implementation. The benefits of
+reducing effort have been largely studied, and include increases in
+abundance, biomass, and diversity within the bounded regions. These
+no-take zones may produce spillover effects, which provide fish for
+outside areas. However, the economic and ecological implications of
+displacing fishing effort are not yet fully understood. Novel data
+products that track fishing effort at the vessel-level allow us to
+identify changes in fleet- and vessel-level behavior upon the
+implementation of protected areas, as well as how these redistribute.
+This papers evaluates the implications of implementing LSMPA, by
+evaluating changes in fishing hours, showing that vessels in the
+effected region reduce fishing effort after the implementation of PIPA.
+Our results are robust to a set of specifications. We also track the
+relative spatial allocation of fishing events thorugh time, and identify
+that areas closer to PIPA show an increase in relative fishing hourse
+due to the displacement of PIPA-fishing vessels. Our results not only
+provide an impact evaluation of the effect of LSMPAs on fishing
+activity, but provide insights into vessel redistribution dynamics,
+which may have ecological and economic implications.
+\end{abstract}
 
@@
 }
-\emph{Last update: 2018-09-14}
-
 \section{To do}\label{to-do}
@@
   \item
-    {[} {]} B: Taiwan, Never in PNA, Similar region
+    {[} {]} \sout{B: Taiwan, Never in PNA, Similar region}
   \end{itemize}
@@
 \item
-  {[} {]} Where do PIPA vessels go?
+  {[}x{]} Where do PIPA vessels go?
 \item
-  {[} {]} Make sure I have full tracks of all mmsis
+  {[}x{]} Make sure I have full tracks of all mmsis
 \end{itemize}
@@
 
+\section{Introduction}\label{introduction}
+
+This work identifies the behavioral changes of fishing vessels due to
+the implementation of PIPA. Not only can we identify temporal changes in
+fishing patterns (\emph{i.e.} time and distance), but also spatial
+patterns. Our vessel-level tracks allow us to see where PIPA-fishing
+vessels go after the closure, providing empirical insights about the
+redistribution of fishing effort after the implementaion of a MPA.
+
 \section{Methods}\label{methods}
+
+This section is divided into two main parts. First, we provide a general
+description of AIS data and the process of identification of
+vessel-level events done by Global Fishing Watch \footnote{\href{globalfishingwatch.org}{Global
+  Fishing Watch}}. Alongside, we describe the subset of data that we use
+for these analyses. When relevant, we also point out possible
+shortcommings in the data, or factors that must be considered in the
+later analyses. Then we move on to explain our identification strategy,
+and the main analyses that we undertake.
 
@@
 
-The Global Fishing Watch (GFW) data contain 233 vessels that have fished
-within PIPA waters. From these, 217 did so at least once before 2015,
-but only 183 continued to fish after 2015. The 34 missing vessels might
-tell us something about the impact of PIPA. However, they might have
-gone to other areas (i.e.~outside of PNA countries). I must dig deeper
-into this.
+\subsubsection{AIS data}\label{ais-data}
 
-Accounting for the fact that vessels that fished within PIPA before
-implementation might stop fishing afterwards, or that vessels entered
-the fishery after PIPA closure, I define my treatment and control groups
-as follows. The treatment group contains all vessels that fished within
+Automatic Identification Systems are on-board devices intended to
+provide at-sea saftey and prevent ship collisions by broadcasting vessel
+locations to surrounding vessels. These broadcasted positions can be
+recorded by satellites and land-based antenas. GFW uses a neural network
+to infer vessel characteristics and whether each broadcasted position
+represents a fishing event, thus allowing us to estimate near real-time
+fishing events globally \citep{kroodsma_2018}. The recent addition of
+satellites that can receive AIS signals causes an apparent increase in
+the number of broadcasted AIS messages (\emph{i.e.} points) and
+therefore fishing hours. It is therefore important to be cautious when
+comparing temporal trends. The variability in AIS data and dynamic ocean
+conditions require that temporal trends be taken into account. We do
+that by incorporating a series of controls, which are defined in the
+following section.
+
+\subsubsection{PIPA data}\label{pipa-data}
+
+The GFW data contain 233 purse seiners and longliners that have fished
+within PIPA waters. From these, only 217 did so at least once before
+2015, but only 183 continued to fish after 2015\footnote{The 34 missing
+  vessels might have exited the fishery, been decomissioned or sold
+  (therefore chaning their AIS and mmsi), or turned off their AIS
+  transmiters. On either case, we are not able to observe these.}.
+Vessels that fished within PIPA before implementation might stop fishing
+afterwards, therefore not being observable in the post-treatment period.
+New vessels might have also entered the fishery after PIPA closure, and
+were likely not exposed to the policy intervention in the pre-treatment
+period. Therefore, we define our treatment and control groups as
+follows. The treatment group contains all vessels that fished within
 PIPA at least once before the closure, and that continued to fish
-elsewhere afterwards. The Control group has vessels that never fished
+elsewhere afterwards. The control group has vessels that never fished
 within PIPA waters, belong to other PNA countries, and have fished in
-surroinding areas before and after PIPA closure. Tables
-\ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the
-number of vessels, number of vessels following a BACI design, and
+surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
+closure. Figure \ref{fig:baci_strict} provides a visual representation
+of the vessel-level that make up each of group through time.
+
+Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show
+the number of vessels, number of vessels following a BACI design, and
 fishing hours, respectively. Tables show data grouped by gear
@@
 that only appear at one point in time).
+
+\begin{figure}
+\centering
+\includegraphics{../img/BACI_strict_gear.png}
+\caption{\label{fig:baci_strict}Stream of fishing events by vessels
+(stacked on the y-axis due to space) through time (x-axis). Each dot
+represent a vessel-month, with colors indicating the pre and post
+periods, and pannels separating between gear and treated or control
+groups.}
+\end{figure}
 

### 2018-09-27 rmd/Manuscript.Rmd
Updated scripts and manuscript

@@
 ---
-title: "Displacement effects in PIPA"
-author: "Juan Carlos Villaseñor-Derbez"
-# abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
-Literature shows that fishing effort is effectively eliminated in this protected areas upon implementation.
+title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
+subtitle: "Updated on `r Sys.Date()`"
+author: |
+  Juan Carlos Villaseñor-Derbez^1^
+  John Lynham^2^
+abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
+Fishing effort is effectively eliminated within these protected areas upon implementation.
 The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions.
-In terms of the fishing implication, no-take zones may produce spillover that provide fish for outside areas.
-The implications of displacement of fishing effort are not yet fully understood.
-Evidence suggests that fishing effort re-distributes along the borders of the MPA, following an ideal free distribution.
-Novel data products allow us to track fishing effort at the vessel-level, allowing us to identify changes in behavior at both the fleet and vessel level.
-This papers evaluates the implications of implementing a LMPA, the Phoenix Islands Protected Area (PIPA).
-We evaluate changes in fishing effort, and track vessels to see where they go after the implementation of PIPA.
-Our results show that vessels in the effected region increase fishing effort after the implementation of PIPA.
-THey are redistributed to X.
-These findings have major implications for MPA implementation, especially as countries rush to meet the goals of 10% ocean protection as mandated by the SDG."
+These no-take zones may produce spillover effects, which provide fish for outside areas.
+However, the economic and ecological implications of displacing fishing effort are not yet fully understood.
+Novel data products that track fishing effort at the vessel-level allow us to identify changes in fleet- and vessel-level behavior upon the implementation of protected areas, as well as how these redistribute.
+This papers evaluates the implications of implementing LSMPA, by evaluating changes in fishing hours, showing that vessels in the effected region reduce fishing effort after the implementation of PIPA.
+Our results are robust to a set of specifications.
+We also track the relative spatial allocation of fishing events thorugh time, and identify that areas closer to PIPA show an increase in relative fishing hourse due to the displacement of PIPA-fishing vessels.
+Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
+date: |
+  ^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA
+  ^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI
 output:
@@
 
-*Last update: `r Sys.Date()`*
-
 ```{r, echo = F, message = F, warning = F}
@@
                       message = FALSE)
+
+options(knitr.table.format = "latex")
 ```
-
-# To do
-
-- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
-- [x] Identify two counterfactuals:
-    -  [x] A: PNA, similar vessel, never fished inside PIPA
-    - [ ] B: Taiwan, Never in PNA, Similar region
-- [x] Change in fishing hours before vs after
-- [ ] ~~Change in total hours before vs after~~
-- [ ] Change in distance before vs after
-- [ ] Where do PIPA vessels go?
-- [ ] Make sure I have full tracks of all mmsis
 
@@
 
+# Introduction
+
+This work identifies the behavioral changes of fishing vessels due to the implementation of PIPA.
+Not only can we identify temporal changes in fishing patterns (*i.e.* time and distance), but also spatial patterns.
+Our vessel-level tracks allow us to see where PIPA-fishing vessels go after the closure, providing empirical insights about the redistribution of fishing effort after the implementaion of a MPA.
+
 # Methods
 
+This section is divided into two main parts.
+First, we provide a general description of AIS data and the process of identification of vessel-level events done by Global Fishing Watch [^1].
+Alongside, we describe the subset of data that we use for these analyses.
+When relevant, we also point out possible shortcommings in the data, or factors that must be considered in the later analyses.
+Then we move on to explain our identification strategy, and the main analyses that we undertake.
+
+[^1]: [Global Fishing Watch](globalfishingwatch.org)
+
 ## Data
+
+### AIS data
+
+Automatic Identification Systems are on-board devices intended to provide at-sea saftey and prevent ship collisions by broadcasting vessel locations to surrounding vessels.
+These broadcasted positions can be recorded by satellites and land-based antenas.
+GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally \citep{kroodsma_2018}.
+The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points) and therefore fishing hours.
+It is therefore important to be cautious when comparing temporal trends.
+The variability in AIS data and dynamic ocean conditions require that temporal trends be taken into account.
+We do that by incorporating a series of controls, which are defined in the following section.
+
+### PIPA data
 
@@
   length()
-
 ```
 
-The Global Fishing Watch (GFW) data contain `r pipa_vessels` vessels that have fished within PIPA waters.
-From these, `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015.
-The `r n_prev - n_post` missing vessels might tell us something about the impact of PIPA.
-However, they might have gone to other areas (i.e.
-outside of PNA countries).
-I must dig deeper into this.
+The GFW data contain `r pipa_vessels` purse seiners and longliners that have fished within PIPA waters.
+From these, only `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015[^2].
+Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period.
+New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period.
+Therefore, we define our treatment and control groups as follows.
+The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
+The control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
+Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level that make up each of group through time.
 
-Accounting for the fact that vessels that fished within PIPA before implementation might stop fishing afterwards, or that vessels entered the fishery after PIPA closure, I define my treatment and control groups as follows.
-The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
-The Control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surroinding areas before and after PIPA closure.
 Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively.
@@
 excludes vessels that only appear at one point in time).
+
+![\label{fig:baci_strict}Stream of fishing events by vessels (stacked on the y-axis due to space) through time (x-axis).
+Each dot represent a vessel-month, with colors indicating the pre and post periods, and pannels separating between gear and treated or control groups.](../img/BACI_strict_gear.png)
+
+[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore chaning their AIS and mmsi), or turned off their AIS transmiters.
+On either case, we are not able to observe these.
 
@@
 
-The current approach is to estimate what percentage of fishing effort from the PNA was displaced by PIPA and use this to infer something about Palau.
-While this provides a measure of the displacement, it does not fully address the possibility of costs increasing.
-I believ we can use individual tracks (as opposed to just the gridded effort) and obtain show how their behavior changed (*i.e.* are they fishing further away, are they fishing more, where are they now?).
+### Change in behavior
 
-### Model specifications
+The first analysis focuses on identifying the response of fishing vessels to PIPA closure.
+Our variables of interests are fishing effort, indicated by total fishing hours per month, and distance traveled (Km) on every fishing trip.
+We compare fishing hours[^3] before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation.
+Our specification is the following:
+
+$$
+y_{i,t} = \alpha + \beta Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{it}
+$$
+
+Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$.
+$\alpha$ is the standard intercept, and $\beta$ is our parameter of interest: de DiD estimate capturing the treatment effect.
+A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation date.
+$Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group.
+Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.
+
+[^3]: And soon, distance
 
@@
 
-Our model specification uses a DiD approach.
-In this case, we interact the before-after dummy with a treatment dummy.
-The treatment and control groups follow our definition in the data description.
-The model takes the form of:
-
-$$
-H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
-$$
-
-Where $\mu_j$, $\phi_k$, and $\gamma_l$ represent month-, year-, and flag-level fixed effects. I use total hours at the vessel-month level.
+### Vessel displacement and redistribution
 

### 2018-09-27 scripts/st_rotate.R

@@ -1,0 +1,9 @@
+st_rotate <- function(x){
+  x2 <- (sf::st_geometry(x) + c(360,90)) %% c(360) - c(0,90) 
+  x3 <- sf::st_wrap_dateline(sf::st_set_crs(x2 - c(180,0), 4326)) + c(180,0)
+  x4 <- sf::st_set_crs(x3, 4326)
+  
+  x <- sf::st_set_geometry(x, x4)
+  
+  return(x)
+}

### 2018-09-28 rmd/Manuscript.Rmd
Update Manuscript.Rmd

@@
 From these, only `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015[^2].
-Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period.
+**What do you mean by continued to fish?
+Specifically, what is the spatial definition?
+Continued to fish in Kiribati EEZ/PNA EEZs/anywhere in the world?** Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period.
 New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period.
@@
 The control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
-Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level that make up each of group through time.
+**Vessels in the control group satisfy all three of these condiitons or at least one of them?** Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level that make up each of group through time.
 
 Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively.
-Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after).
+**Is the larger number of longliners surprising?
+I thought PIPA was known as a purse seining ground and less so for longlining.** Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after).
 The relative change (After / Before) is also shown.
@@
 
-[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore chaning their AIS and mmsi), or turned off their AIS transmiters.
-On either case, we are not able to observe these.
+[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmiters.
+In either case, we are not able to observe these.
 
@@
 
+**Need to include separate dummy variables for Post and Treat above**
+
 Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$.
@@
 Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.
+**year fixed effects are going to soak up a lot of the variation in treatment status but we should certianly have at least one column of results that includes them.
+Why no analysis with vessel fixed effects?**
 
@@
 \ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
-This trend is observed for both treated and control groups.
+**Do we know what is causing this?
+I'm guessing this can't be Blue Paradox stuff because we see it for the control group as well who are supposed to have never fished within PIPA.** This trend is observed for both treated and control groups.
 Longliners, however, show a more stable trend.
 The number of mmsi codes increases through time.
-This can largel be explained by the addition of more satellits, which increasedetectability of vessels.
+This can largely be explained by the addition of more satellites, which increases the detectability of vessels.
 As expected total fishing hours follow a similar trend to that of mmsi numbers.
@@
 Figures \ref{fig:puse} and \ref{fig:long} represent the same coefficient estimates.
+
+**We should have a discussion (over the phone and in the paper) about whether a decrease in fishing hours represents a positive or negative impact of PIPA.
+Without data on catch it might be hard to really know.**
+
+**An additional test to add to the wish list is to see if vessels are fishing closer to each other following the PIPA closure.**
+
+**Nice work so far!**
 
@@
 Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
+Numbers in parentheses represent heteroskedasticity-robust standard errors.")
 ```
@@
                      header = F,
-                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment)..
+                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
 Asterisks indicate significance levels.

### 2018-09-28 docs/Manuscript.tex
Updated methos, still need to include Johns comments, finalize empirical specification and proof read

@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\usepackage[normalem]{ulem}
-% avoid problems with \sout in headers with hyperref:
-\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
 \IfFileExists{parskip.sty}{%
@@
   \postdate{\par}
-    \date{\textsuperscript{1} Bren School of Environmental Science and Management,
+    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
 University of California Santa Barbara, Santa Barbara, CA
-\textsuperscript{2} Department of Economics, University of Hawaii at
+\textsuperscript{2}Department of Economics, University of Hawaii at
 Manoa, Honolulu, HI}
@@
 \floatplacement{figure,table}{H}
+\usepackage{lineno}
+\linenumbers
 
@@
 }
-\section{To do}\label{to-do}
-
-\begin{itemize}
-\tightlist
-\item
-  {[}x{]} Divide pipa vessels by type of boat (longline vs.~purse seine)
-\item
-  {[}x{]} Identify two counterfactuals:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
-  \item
-    {[} {]} \sout{B: Taiwan, Never in PNA, Similar region}
-  \end{itemize}
-\item
-  {[}x{]} Change in fishing hours before vs after
-\item
-  {[} {]} \sout{Change in total hours before vs after}
-\item
-  {[} {]} Change in distance before vs after
-\item
-  {[}x{]} Where do PIPA vessels go?
-\item
-  {[}x{]} Make sure I have full tracks of all mmsis
-\end{itemize}
-
 \clearpage
@@
 
-The current approach is to estimate what percentage of fishing effort
-from the PNA was displaced by PIPA and use this to infer something about
-Palau. While this provides a measure of the displacement, it does not
-fully address the possibility of costs increasing. I believ we can use
-individual tracks (as opposed to just the gridded effort) and obtain
-show how their behavior changed (\emph{i.e.} are they fishing further
-away, are they fishing more, where are they now?).
+\subsubsection{Change in behavior}\label{change-in-behavior}
 
-\subsubsection{Model specifications}\label{model-specifications}
-
-Our model specification uses a DiD approach. In this case, we interact
-the before-after dummy with a treatment dummy. The treatment and control
-groups follow our definition in the data description. The model takes
-the form of:
+The first analysis focuses on identifying the response of fishing
+vessels to PIPA closure. Our variables of interests are fishing effort,
+indicated by total fishing hours per month, and distance traveled (Km)
+on every fishing trip. We compare fishing hours\footnote{And soon,
+  distance} before and after the implementation of PIPA using a
+Difference-in-Differences approach, where we track the variable of
+interest for vessels that used to fish inside PIPA and vessels that
+never fished inside PIPA, before and after PIPA implementation. Our
+specification is the following:
 
 \[
-H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
 \]
 
-Where \(\mu_j\), \(\phi_k\), and \(\gamma_l\) represent month-, year-,
-and flag-level fixed effects. I use total hours at the vessel-month
-level.
+Where \(y_{ijkl}\) is the variable of interest for vessel \(i\) in time
+period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
+dates prior to PIPA implementation and a value of 1 por all dates
+including and following PIPA implementation. \(Treat_i\) is a dummy
+variable indicating whether a vessel belongs to the control
+(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
+the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
+\(\beta_2\) captures the difference between treated and control groups,
+and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
+the treatment effect. Finally, \(\mu_t\), \(\phi_t\), and \(\gamma_i\)
+represent month-, year-, and flag-level dummies that account for
+seasonality or country-level management interventions.
+
+\subsubsection{Vessel displacement and
+redistribution}\label{vessel-displacement-and-redistribution}
+
+Our second part of the analyses focuses on the redistribution of fishing
+effort. In other words, identifying where do vessels that used to fish
+inside PIPA go after its establishment. We calculate the monthly
+relative distribution of fishing hours by all treated vessels across all
+fished EEZs and the high seas. These trends are shown in Figure
+\ref{fig:redist_trend}. EEZs that had sproadic fishing events were
+pooled into a group of ``others'', leaving us with a total of n = 12
+spatially defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'').
+Figure \ref{fig:redist_trend_spa} shows the yearly average of the
+relative spatial allocation of fishing efforts; this is the spatial
+representation of \ref{fig:redist_trend} averaged by year.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{\label{fig:unnamed-chunk-9}\label{fig:redist_trend}}
+\end{figure}
+
+To evaluate this change in effort allocation, we regress our variable of
+interest, fishing hours, on the interaction between a dummy variable
+indicating the policy intervention and a dummy variable for countries,
+to obtain the by-country change in proportional allocation of fishing
+effort:
+
+\[
+y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
+\]
+
+Our variable of interest, \(y_{i,t}\) represents the proportion of
+fishing hours that country \(i\) receives at time \(t\). \(Post\) also
+represents a policy dummy that takes the value of 0 for all dates before
+implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
+for countries, interpreted as individual EEZs, the high seas, and a
+group of ``other EEZs''. Our parameter of interest is \(\beta_3\), which
+captures the country-level change in proportional fishing effort.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels. Vertical dashed line
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels. Vertical dashed line
 indicates PIPA closure.}
@@
 
-\subsection{Purse seiners}\label{purse-seiners}
+\subsection{Change in behavior}\label{change-in-behavior-1}
+
+\subsubsection{Purse seiners}\label{purse-seiners}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\label{fig:unnamed-chunk-9}\label{fig:puse}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:puse}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 
-\subsection{Longliners}\label{longliners}
+\subsubsection{Longliners}\label{longliners}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 \end{figure}
+
+\subsection{Effort displacement and
+redistribution}\label{effort-displacement-and-redistribution}
+
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
 

### 2018-09-28 rmd/Manuscript.Rmd
Updated methos, still need to include Johns comments, finalize empirical specification and proof read

--- 2018-09-27 rmd/Manuscript.Rmd
@@
   - \floatplacement{figure,table}{H}
+  - \usepackage{lineno}
+  - \linenumbers
 bibliography: references.bib
@@
   library(startR)
+  library(sf)
   library(tidyverse)
@@
 options(knitr.table.format = "latex")
+
+source(here::here("scripts", "st_rotate.R"))
+source(here::here("scripts", "sfc_as_cols.R"))
 ```
@@
 $$
-y_{i,t} = \alpha + \beta Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{it}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
 $$
@@
 Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$.
-$\alpha$ is the standard intercept, and $\beta$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation date.
+A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation.
 $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group.
+$\alpha$ is the standard intercept, $\beta_1$ captures the *ex post* change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
 Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.
@@
 
-<!-- $$ -->
-<!-- H_{ijk} = \alpha + \beta Post_i + \mu_j + \phi_k + \epsilon_{ijk} -->
-<!-- $$ -->
+### Vessel displacement and redistribution
 
-<!-- Where $H_{ijk}$ is a measure of effort (*.i.e.* total hours, fishing hours, distance traveled), $\beta$ captures the change for before ($Post_i = 0$) and after ($Post_i = 1$) implementation of PIPA, $mu_j$ captures the month fixed-effects, and $\phi_k$ captures vessel-level fixed-effects.
-We use this general model and the nested specifications which drop the month and vessel-level fixed effects to test for differences.
--->
+```{r}
+displacement_data <- readRDS(file = here::here("data", "displacement_data.rds"))
+```
 
-### Vessel displacement and redistribution
+Our second part of the analyses focuses on the redistribution of fishing effort.
+In other words, identifying where do vessels that used to fish inside PIPA go after its establishment.
+We calculate the monthly relative distribution of fishing hours by all treated vessels across all fished EEZs and the high seas.
+These trends are shown in Figure \ref{fig:redist_trend}.
+EEZs that had sproadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country))` spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs").
+Figure \ref{fig:redist_trend_spa} shows the yearly average of the relative spatial allocation of fishing efforts; this is the spatial representation of \ref{fig:redist_trend} averaged by year.
+
+<!-- Explicar cuales EEZs habia en total y cuales quedaron en un pie de nota o algo asi -->
+
+```{r}
+country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV")
+
+eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"), layer = "EEZ_subset")
+
+pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
+                layer = "PIPA") %>% 
+  mutate(inside = T) %>% 
+  select(inside) %>% 
+  st_rotate()
+```
+
+```{r, fig.cap = "\\label{fig:redist_trend}"}
+displacement_data %>% 
+  ggplot(aes(x = date, y = h_prop, group = post)) +
+  geom_smooth(method = "lm") +
+  geom_point() +
+  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
+  scale_fill_brewer(palette = "Paired") +
+  ggtheme_plot() +
+  facet_wrap(~country, scales = "free_y")
+```
+
+```{r, fig.cap = "\\label{fig:redist_trend_spa}Proportion of fishing hours that all vessels spent on each of the EEZs and the high seas.", eval = F}
+pipa_map_disp <- pipa %>% 
+  mutate(country = "PIPA") %>% 
+  left_join(displacement_data, by = "country")
+
+# Los colores del mapa deben estar dados por el Post:Country
+eez %>% 
+  left_join(displacement_data, by = c("ISO_Ter1" = "country")) %>%
+  group_by(year) %>% 
+  summarize(h_prop = mean(h_prop, na.rm = T)) %>% 
+  ggplot() +
+  geom_sf(aes(fill = h_prop, linetype = PNA), size = 1, color = "black") +
+  geom_sf(data = pipa_map_ba_disp, aes(fill = h_prop), linetype = "dashed", color = "red") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10)) +
+  facet_wrap(~year)
+```
+
+<!-- Meter tabla ba_disp aqui -->
+
+To evaluate this change in effort allocation, we regress our variable of interest, fishing hours, on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries, to obtain the by-country change in proportional allocation of fishing effort:
+
+$$
+y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
+$$
+
+Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that country $i$ receives at time $t$.
+$Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise.
+$Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs".
+Our parameter of interest is $\beta_3$, which captures the country-level change in proportional fishing effort.
 
@@
 
-## Purse seiners
+## Change in behavior
+
+### Purse seiners
 
@@
 
-## Longliners
+### Longliners
 
@@
   theme_bw()
+```
+
+## Effort displacement and redistribution
+
+```{r}
+ba_disp <- displacement_data %>% 
+  group_by(country, post) %>% 
+  summarize(h_prop_m = mean(h_prop)) %>% 
+  spread(post, h_prop_m) %>% 
+  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
+  select(country, change)
+
+pipa_map_ba_disp <- pipa %>% 
+  mutate(country = "PIPA") %>% 
+  left_join(ba_disp, by = "country")
+
+# Los colores del mapa deben estar dados por el Post:Country
+eez %>% 
+  left_join(ba_disp, by = c("ISO_Ter1" = "country")) %>%
+  filter(!is.na(change)) %>% 
+  ggplot() +
+  geom_sf(aes(fill = change), size = 1, color = "black") +
+  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
+```
+
+```{r, eval = F}
+# Dont have this here. Just write the model specification
+
+displacement_data %>% 
+  filter(!is.na(country)) %>% 
+  lm(h_prop ~ post*country, data = .) %>% 
+  summary()
 ```

### 2018-09-29 docs/Manuscript.tex
Updated latest analyses and manuscript

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 \usepackage{natbib}
-\bibliographystyle{nature}
+\bibliographystyle{plainnat}
 \usepackage{longtable,booktabs}
@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-09-27}
+  \subtitle{Updated on 2018-09-28}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
     \date{\textsuperscript{1}Bren School of Environmental Science and Management,
-University of California Santa Barbara, Santa Barbara, CA
-\textsuperscript{2}Department of Economics, University of Hawaii at
-Manoa, Honolulu, HI}
+University of California Santa Barbara, Santa Barbara,
+CA\newline\textsuperscript{2}Department of Economics, University of
+Hawaii at Manoa, Honolulu, HI}
 
 \usepackage{float}
-\floatplacement{figure,table}{H}
+\floatplacement{figure}{H}
 \usepackage{lineno}
@@
 
-{
-\setcounter{tocdepth}{4}
-\tableofcontents
-}
 \clearpage
@@
 description of AIS data and the process of identification of
-vessel-level events done by Global Fishing Watch \footnote{\href{globalfishingwatch.org}{Global
-  Fishing Watch}}. Alongside, we describe the subset of data that we use
-for these analyses. When relevant, we also point out possible
-shortcommings in the data, or factors that must be considered in the
-later analyses. Then we move on to explain our identification strategy,
-and the main analyses that we undertake.
+vessel-level events done by Global Fishing Watch\footnote{Global Fishing
+  Watch: \url{globalfishingwatch.org}}. Alongside, we describe the
+subset of data that we use for these analyses. When relevant, we also
+point out possible shortcommings in the data, or factors that must be
+considered in the later analyses. Then we move on to explain our
+identification strategy, and the main analyses that we undertake.
 
@@
 represents a fishing event, thus allowing us to estimate near real-time
-fishing events globally \citep{kroodsma_2018}. The recent addition of
-satellites that can receive AIS signals causes an apparent increase in
-the number of broadcasted AIS messages (\emph{i.e.} points) and
-therefore fishing hours. It is therefore important to be cautious when
-comparing temporal trends. The variability in AIS data and dynamic ocean
+fishing events globally since 2012 \citep{kroodsma_2018}. The recent
+addition of satellites that can receive AIS signals causes an apparent
+increase in the number of broadcasted AIS messages (\emph{i.e.} points)
+and therefore fishing hours. The variability in AIS data and ocean
 conditions require that temporal trends be taken into account. We do
@@
 
-The GFW data contain 233 purse seiners and longliners that have fished
-within PIPA waters. From these, only 217 did so at least once before
-2015, but only 183 continued to fish after 2015\footnote{The 34 missing
-  vessels might have exited the fishery, been decomissioned or sold
-  (therefore chaning their AIS and mmsi), or turned off their AIS
-  transmiters. On either case, we are not able to observe these.}.
-Vessels that fished within PIPA before implementation might stop fishing
-afterwards, therefore not being observable in the post-treatment period.
-New vessels might have also entered the fishery after PIPA closure, and
-were likely not exposed to the policy intervention in the pre-treatment
-period. Therefore, we define our treatment and control groups as
-follows. The treatment group contains all vessels that fished within
+Our data contain over 45 million individual AIS messages for 371 purse
+seiners and longliners. A total of 233 vessels have fished within PIPA
+waters; 217 did so at least once before 2015. However, not all vessels
+continued to fish elsewhere after PIPA implementation: 34 vessels have
+no recorded AIS messages after 2015\footnote{The 0 missing vessels might
+  have exited the fishery, been decomissioned or sold (therefore
+  changing their AIS and mmsi), or turned off their AIS transmiters. In
+  either case, we are not able to observe these.}, leaving us with 183
+vessels that fished inside PIPA before its implementation, and continued
+to fish elsewhere afterward. Vessels that fished within PIPA before
+implementation might stop fishing afterwards, therefore not being
+observable in the post-treatment period. New vessels might have also
+entered the fishery after PIPA closure, and were likely not exposed to
+the policy intervention in the pre-treatment period. Therefore, we
+define our treatment and control groups as follows.
+
+The treatment group contains all vessels (n = 183) that fished within
 PIPA at least once before the closure, and that continued to fish
-elsewhere afterwards. The control group has vessels that never fished
-within PIPA waters, belong to other PNA countries, and have fished in
+elsewhere afterwards. Vessels in the control group meet al three of the
+following conditions: i) Vessels never fished within PIPA waters, ii)
+vessels belong to other PNA countries, and iii) vessels have fished in
 surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
-closure. Figure \ref{fig:baci_strict} provides a visual representation
-of the vessel-level that make up each of group through time.
-
-Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show
-the number of vessels, number of vessels following a BACI design, and
+closure. For each vessel meeting these characteristics, we calculate
+their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
+a visual representation of the vessel-level streams of fishing events
+that make up each group through time. Tables \ref{tab:baci_n_s} and
+\ref{tab:baci_h} show the number of vessels following a BACI design, and
 fishing hours, respectively. Tables show data grouped by gear
 (longlines, purse seines), group (treated, control), and period (before,
-after). The relative change (After / Before) is also shown. Table
-\ref{tab:baci_n} shows information for all fishing vessels in the
-dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show
-information for vessels that meet the BACI design (i.e.~excludes vessels
-that only appear at one point in time).
+after). The relative change in fishing hours (After / Before) is also
+shown.
 
@@
 \centering
-\includegraphics{../img/BACI_strict_gear.png}
-\caption{\label{fig:baci_strict}Stream of fishing events by vessels
-(stacked on the y-axis due to space) through time (x-axis). Each dot
-represent a vessel-month, with colors indicating the pre and post
-periods, and pannels separating between gear and treated or control
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
+events by vessels through time. Each line represents a vessel, with dots
+indicating months with fishing activity and colors indicating the pre
+and post periods. Pannels separating between gear and treated or control
 groups.}
@@
 
-\caption{\label{tab:unnamed-chunk-4}\label{tab:baci_n}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.}
 \centering
-\begin{tabular}[t]{llrrr}
+\begin{tabular}[t]{llr}
 \toprule
-Gear & Treatment & Before & After & Change (A / B)\\
+Gear & Treatment & n\\
 \midrule
-drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
-drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
-purse\_seines & FALSE & 49 & 89 & 1.8163265\\
-purse\_seines & TRUE & 78 & 81 & 1.0384615\\
+drifting\_longlines & FALSE & 85\\
+drifting\_longlines & TRUE & 115\\
+purse\_seines & FALSE & 36\\
+purse\_seines & TRUE & 68\\
 \bottomrule
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.}
 \centering
@@
 \midrule
-drifting\_longlines & FALSE & 88 & 88 & 1\\
-drifting\_longlines & TRUE & 115 & 115 & 1\\
-purse\_seines & FALSE & 38 & 38 & 1\\
-purse\_seines & TRUE & 68 & 68 & 1\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours for each gear before and after}
-\centering
-\begin{tabular}[t]{llrrr}
-\toprule
-Gear & Treatment & Before & After & Change (A / B)\\
-\midrule
-drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
-drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
-purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
-purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
+drifting\_longlines & FALSE & 474.47780 & 462.5491 & 0.9748593\\
+drifting\_longlines & TRUE & 544.61935 & 522.8392 & 0.9600085\\
+purse\_seines & FALSE & 59.49026 & 154.5776 & 2.5983673\\
+purse\_seines & TRUE & 52.91534 & 131.5452 & 2.4859561\\
 \bottomrule
@@
 \subsection{Analysis}\label{analysis}
-
-\subsubsection{Change in behavior}\label{change-in-behavior}
 
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
 \]
 
-Where \(y_{ijkl}\) is the variable of interest for vessel \(i\) in time
+Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
 period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
@@
 and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
-the treatment effect. Finally, \(\mu_t\), \(\phi_t\), and \(\gamma_i\)
-represent month-, year-, and flag-level dummies that account for
-seasonality or country-level management interventions.
-
-\subsubsection{Vessel displacement and
-redistribution}\label{vessel-displacement-and-redistribution}
+the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
+for a second order polynomial for years (\(Y_t\))\footnote{An earlier
+  specification included years as a dummy variable. Such results are
+  included in the appendx.}, while \(\phi_t\) and \(\gamma_i\) represent
+month-, and flag-level dummies that account for seasonality or
+country-level management interventions.
 
@@
 relative distribution of fishing hours by all treated vessels across all
-fished EEZs and the high seas. These trends are shown in Figure
-\ref{fig:redist_trend}. EEZs that had sproadic fishing events were
-pooled into a group of ``others'', leaving us with a total of n = 12
-spatially defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'').
-Figure \ref{fig:redist_trend_spa} shows the yearly average of the
-relative spatial allocation of fishing efforts; this is the spatial
-representation of \ref{fig:redist_trend} averaged by year.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\label{fig:unnamed-chunk-9}\label{fig:redist_trend}}
-\end{figure}
+fished EEZs and the high seas. These trends are shown in Figures
+\ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the
+relative change is presented in Table \ref{tab:ba_disp}. EEZs that had
+sproadic fishing events were pooled into a group of ``others'', leaving
+us with a total of n = 12 and n = 10 spatially defined regions
+(\emph{i.e.} EEZs, High Seas, ``other EEZs'') for purse seiners and
+longliners, respectively.
 
@@
 
+All regression coefficients were estimatedd via ordinary least squares,
+and heteroskedastic-robust standard errors were calculated. All analyses
+were performed in R version 3.5.1) \citep{rcore_2018}. Raw data and code
+used in this work are available on
+\href{https://github.com/jcvdav/MPA_displacement}{github}.
+
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}}
+\centering
+\begin{tabular}[t]{lrr}
+\toprule
+country & Longliners & Purse seiners\\
+\midrule
+PIPA & -11.48 & -8.54\\
+KIR & 1.28 & 2.76\\
+HS & 0.00 & 0.00\\
+COK & 0.00 & 0.34\\
+FSM & 0.00 & 0.55\\
+\addlinespace
+MHL & NA & -0.55\\
+NRU & 0.00 & 0.16\\
+PNG & 0.00 & -10.02\\
+SLB & -8.48 & 2.13\\
+TKL & NA & 0.19\\
+\addlinespace
+TUV & 7.23 & 1.47\\
+others & 22.55 & 11.51\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\clearpage
+
 \section{Results}\label{results}
 
-Fig. \ref{fig:all_vessels} shows that mean fishing hours for purse
-seiners have an abrupt increase, just before January 1st, 2015. This
-trend is observed for both treated and control groups. Longliners,
-however, show a more stable trend. The number of mmsi codes increases
-through time. This can largel be explained by the addition of more
-satellits, which increasedetectability of vessels. As expected total
-fishing hours follow a similar trend to that of mmsi numbers. Results of
-the regressions for each gear type are shown in Tables \ref{tab:purse}
-and \ref{tab:long}. Column (1) presents the DiD regression with no fixed
-effects, column (2) includes month fixed effects, column (3) includes
-month and year fixed effects, and column (4) includes month, year, and
-flag fixed effects. Figures \ref{fig:puse} and \ref{fig:long} represent
-the same coefficient estimates.
+Our data suggest that purseiners and longliners have different responses
+to the implementation of a Large-Scale Marine Protected Area. Fig.
+\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
+have an abrupt increase, just before January 1st, 2015. This trend is
+observed for both treated and control groups. Longliners, however, show
+a more stable trend. The number of mmsi codes increases through time.
+This can largely be explained by the addition of more satellites, which
+increase detectability of vessels. As expected, total fishing hours
+follow a similar trend to that of mmsi numbers.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
 and number of vessels by month for all vessels. Vertical dashed line
@@
 
-\clearpage
+Our DiD anaylsis shows that treated purse seiners reduce their fishing
+effort after PIPA implementation in the order of 16 hours per month.
+This result is robust and significant (\emph{p \textless{} 0.05}) for
+all model specifications, with the effect varying between
+\(\beta_3 = -16.457\) and \(\beta_3 = -18.709\). Model specifications
+that include the year polynomial show lower values for the \(\beta_1\)
+coefficient associated to the \(Post_t\) policy dummy, and show positive
+and negative values for \(\mu_1\) and \(\mu_2\), the linear and
+cuadratic terms, respectively. These effectively represent the patterns
+observed in Figure \{fig:all\_vessels\}.
 
-\subsection{Change in behavior}\label{change-in-behavior-1}
+Longliners show a similar pattern of effort reduction. However, the
+magnitude of the \(\beta_3\) coefficient is smaller (ranging from
+\(\beta_3 = -9.851\) to \(\beta_3 = -14.850\)) and not significant
+across all model specifications. This, along with higher standard error
+values suggest that longliners have a smaller and more variable response
+to the implementation of LSMPAs.
 
-\subsubsection{Purse seiners}\label{purse-seiners}
+Regressions coefficients for each gear type are shown in Tables
+\ref{tab:purse} and \ref{tab:long}. Column (1) presents the DiD
+regression with no fixed effects, column (2) includes month fixed
+effects, column (3) includes month and the second degree polynomial for
+years, and column (4) includes all of the above and country-level fixed
+effects.
 
@@
   \caption{\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.}
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ post & 95.087$^{***}$ & 99.232$^{***}$ & 38.349$^{***}$ & 41.920$^{***}$ \\ 
+  & (5.877) & (5.453) & (7.423) & (8.214) \\ 
+  & & & & \\ 
+ treated & $-$6.575 & $-$5.597 & $-$3.811 & 6.541 \\ 
+  & (4.985) & (4.564) & (4.247) & (5.195) \\ 
+  & & & & \\ 
+ year &  &  & 12,828.900$^{***}$ & 16,665.590$^{***}$ \\ 
+  &  &  & (2,451.444) & (3,717.658) \\ 
+  & & & & \\ 
+ year2 &  &  & $-$3.178$^{***}$ & $-$4.131$^{***}$ \\ 
+  &  &  & (0.609) & (0.923) \\ 
+  & & & & \\ 
+ post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$17.304$^{***}$ & $-$18.709$^{***}$ \\ 
+  & (6.856) & (6.460) & (6.254) & (6.787) \\ 
+  & & & & \\ 
+ Constant & 59.490$^{***}$ & 65.485$^{***}$ & $-$12,946,334.000$^{***}$ & $-$16,807,078.000$^{***}$ \\ 
+  & (4.422) & (6.132) & (2,473,372.000) & (3,759,572.000) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & No & Yes & Yes & Yes \\ 
+Flag FE & No & No & No & Yes \\ 
+Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
+R$^{2}$ & 0.171 & 0.243 & 0.281 & 0.299 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.}
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ post & $-$11.929 & $-$6.968 & $-$15.550 & $-$6.761 \\ 
+  & (7.969) & (7.975) & (10.181) & (11.289) \\ 
+  & & & & \\ 
+ treated & 70.142$^{***}$ & 72.314$^{***}$ & 71.985$^{***}$ & 14.026$^{*}$ \\ 
+  & (7.200) & (7.200) & (7.279) & (7.988) \\ 
+  & & & & \\ 
+ year &  &  & $-$6,673.971$^{*}$ & 21,188.090$^{***}$ \\ 
+  &  &  & (3,606.793) & (5,631.642) \\ 
+  & & & & \\ 
+ year2 &  &  & 1.657$^{*}$ & $-$5.259$^{***}$ \\ 
+  &  &  & (0.894) & (1.398) \\ 
+  & & & & \\ 
+ post:treated & $-$9.851 & $-$12.290 & $-$12.779 & $-$14.850 \\ 
+  & (9.294) & (9.262) & (9.334) & (9.563) \\ 
+  & & & & \\ 
+ Constant & 474.478$^{***}$ & 449.960$^{***}$ & 6,719,355.000$^{*}$ & $-$21,341,371.000$^{***}$ \\ 
+  & (6.328) & (9.440) & (3,633,994.000) & (5,644,837.000) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & No & Yes & Yes & Yes \\ 
+Flag FE & No & No & No & Yes \\ 
+Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
+R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+Recall that to evaluate the redistribution of fishing effort we only
+track fishing vessels that belong to the treated group. In this case, we
+calculate the prportion of fishing effort allocated every month to each
+spatially explicit region outlined by EEZs and the high seas. For purse
+seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
+of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
+relative fishing hours that each region received by all 183 treated
+vessels. The top-left pannel shows the change in fishing effort inside
+PIPA, including the preemtive fishing and immediate reduction previously
+reported \citep{mcdermott_2018}.
+
+The change in the relative allocation fishing effort by purse seiners
+increases in eight of the 12 regions after PIPA implementation
+\ref{tab:disp_mod}. The largest increase is observed for the I-Kiribati
+EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
+other words, the redistribution of treated vessels caused a 10\%
+increase in the \emph{relative} allocation of fishing effort within
+I-Kiribati waters. The only decrease is observed for Papua New Guinea,
+but the coefficient is not significant. Figure \ref{fig:map_change_ps}
+provides a spatial representation of these changes. It is evident that
+the increase in relative fishing effort is greater for for regions
+closer to PIPA.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
+\caption{\label{fig:unnamed-chunk-19}\label{fig:map_change_ps}}
+\end{figure}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region.
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.}
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & h\_prop \\ 
+\hline \\[-1.8ex] 
+ post & $-$0.085$^{***}$ (0.018) \\ 
+  countryKIR & 0.251$^{***}$ (0.036) \\ 
+  countryHS & $-$0.089$^{***}$ (0.018) \\ 
+  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
+  countryFSM & $-$0.034 (0.021) \\ 
+  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
+  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
+  countryPNG & 0.098$^{***}$ (0.034) \\ 
+  countrySLB & $-$0.023 (0.026) \\ 
+  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
+  countryTUV & $-$0.024 (0.021) \\ 
+  countryothers & 0.016 (0.021) \\ 
+  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
+  post:countryHS & 0.085$^{***}$ (0.018) \\ 
+  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
+  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
+  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
+  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
+  post:countryPNG & $-$0.015 (0.037) \\ 
+  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
+  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
+  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
+  post:countryothers & 0.201$^{***}$ (0.028) \\ 
+  Constant & 0.089$^{***}$ (0.018) \\ 
+ \hline \\[-1.8ex] 
+Month FE & No \\ 
+Observations & 864 \\ 
+R$^{2}$ & 0.557 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\section{Discusion}\label{discusion}
+
+Our findings provide interesting insights into the effect that LSMPAs
+can have on vessel behavior and the redistribution of fishing effort.
+These collection of results shows that the implementation of PIPA caused
+treated vessels to redeuce their fishing hours, and that this effect is
+greater for purse seiners. Even though treated vessels fish less, their
+relative allocation of fishing hours increased for all other fishing
+grouds. This fidnings does not imply that there is more fishing effort,
+but rather that each region receives a greater portion of the post-PIPA
+fishing effort (which is lower than pre-PIPA). In this section we
+discuss the implications of vessel-level reductions in fishing effort
+and the increase in relative allocation of the remaining effort through
+space. We also provide plausible explanations as to why purse seiners
+seem to be more reactive to the spatial closure.
+
+Previous studies on insular environments suggest that vessels move to
+distant places, which might be translated as increased costs
+\citep{stevenson_2013}. Nevertheless, this study does not use
+counterfactuals that could help account for system- or fleet-level
+changes that occur through time. Others have used similar
+satellite-tracking systems to show that fishing effort accumulates near
+the edges ospatial closures, yielding greater catches
+\citep{murawski_2005}. Yet, these vessel tracks do not cover the
+pre-reserve period, making it difficult identify the contribution of
+spatial closures to the observed spatial distribution of fishing
+vessels. Recent work by \citet{elahi_2018} identified that total fishing
+effort in a focal region where a short-term MPA was implemented showed
+little change, likely indicating that fishers redistributed fishing
+effort to compensate for the reduction in available space. Our data is
+assambled in a similar way, with fishing positions before and after the
+implementation of PIPA and vessels grouped into treated and control
+groups. Our BACI design, along with our difference-in-differences
+analysis allows us to make causal inferences about the effect that large
+scale marine protected areas have on fishing effort.
+
+The different responses observed between purse seiners and longliners
+might have two possible explanations. It is likely that PIPA did not
+contain habitat that longliners would consider optimal. Therefore, the
+sporadic fishing events that occurred there are of little importance to
+the fleet, and it is unlikely that the implementation of PIPA has an
+effect on them. Alternatively, the differences may be due to the nature
+of each fishing gear. Purse seiners are often constrained by seafloor
+and termocline depth, and often operate in more restricted areas
+\citep{kroodsma_2018}. Tuna purse seiners are known to have greater
+proportion of null sets (\emph{i.e.} where the purse seine is
+effectively casted arround tuna, but no catch is obtained) during El
+Niño years, where the termocline deepens in the Eastern Pacific
+\citep{dreyfusleon_2015}. On the other hand, longliners may be more
+flexible as to where they can deploy their longlines.
+\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic
+longline fleet, and suggest that the fleet may be underutilizing the
+ocean, meaning that they can easily redistribute elsewhere.
+
+\section{References}\label{references}
+
+\hypertarget{refs}{}
+
+\clearpage
+
+\section{Appendix}\label{appendix}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
 Asterisks indicate significance levels.
@@
 \hline \\[-1.8ex] 
- post & 105.873$^{***}$ & 107.859$^{***}$ & 113.466$^{***}$ & 102.890$^{***}$ \\ 
-  & (5.532) & (5.364) & (5.887) & (6.076) \\ 
+ post & 95.087$^{***}$ & 99.232$^{***}$ & 146.372$^{***}$ & 119.222$^{***}$ \\ 
+  & (5.877) & (5.453) & (6.926) & (6.717) \\ 
   & & & & \\ 
- treated & $-$9.632$^{**}$ & $-$8.924$^{**}$ & $-$8.334$^{**}$ & $-$3.076 \\ 
-  & (4.257) & (4.023) & (3.725) & (4.540) \\ 
+ treated & $-$6.575 & $-$5.597 & $-$6.050 & 2.925 \\ 
+  & (4.985) & (4.564) & (4.095) & (5.052) \\ 
   & & & & \\ 
- post:treated & $-$16.544$^{**}$ & $-$16.889$^{***}$ & $-$17.235$^{***}$ & $-$11.150$^{*}$ \\ 
-  & (6.481) & (6.358) & (6.126) & (6.162) \\ 
+ post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$14.748$^{**}$ & $-$16.231$^{**}$ \\ 
+  & (6.856) & (6.460) & (6.152) & (6.692) \\ 
   & & & & \\ 
- Constant & 66.505$^{***}$ & 61.758$^{***}$ & 40.085$^{***}$ & 61.569$^{***}$ \\ 
-  & (3.780) & (5.352) & (5.699) & (9.753) \\ 
+ Constant & 59.490$^{***}$ & 65.485$^{***}$ & 36.643$^{***}$ & 53.138$^{***}$ \\ 
+  & (4.422) & (6.132) & (6.462) & (10.394) \\ 
   & & & & \\ 
@@
 Flag FE & No & No & No & Yes \\ 
-Observations & 3,692 & 3,692 & 3,692 & 3,692 \\ 
-R$^{2}$ & 0.238 & 0.262 & 0.312 & 0.339 \\ 
+Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
+R$^{2}$ & 0.171 & 0.243 & 0.301 & 0.320 \\ 
 \hline 
@@
 \end{table}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:puse}Coefficient estimates
-for each model. Top pannel indicates variable, x-axis represents model
-specification, and y-axis coefficient estimate.}
-\end{figure}
-
-\clearpage
-
-\subsubsection{Longliners}\label{longliners}
 
@@
 \hline \\[-1.8ex] 
- post & $-$7.843 & $-$4.894 & $-$7.580 & 24.708$^{***}$ \\ 
-  & (7.514) & (7.480) & (9.336) & (9.315) \\ 
+ post & $-$11.929 & $-$6.968 & 8.201 & 17.751$^{*}$ \\ 
+  & (7.969) & (7.975) & (11.119) & (10.388) \\ 
   & & & & \\ 
- treated & 66.801$^{***}$ & 69.434$^{***}$ & 69.959$^{***}$ & 18.878$^{***}$ \\ 
-  & (6.541) & (6.549) & (6.603) & (7.257) \\ 
+ treated & 70.142$^{***}$ & 72.314$^{***}$ & 72.243$^{***}$ & 13.875$^{*}$ \\ 
+  & (7.200) & (7.200) & (7.283) & (7.992) \\ 
   & & & & \\ 
- post:treated & $-$15.571$^{*}$ & $-$17.806$^{**}$ & $-$18.340$^{**}$ & $-$25.775$^{***}$ \\ 
-  & (8.958) & (8.899) & (8.936) & (8.743) \\ 
+ post:treated & $-$9.851 & $-$12.290 & $-$13.287 & $-$14.750 \\ 
+  & (9.294) & (9.262) & (9.344) & (9.569) \\ 
   & & & & \\ 
- Constant & 481.425$^{***}$ & 450.475$^{***}$ & 447.866$^{***}$ & 430.947$^{***}$ \\ 
-  & (5.733) & (9.239) & (10.280) & (24.476) \\ 
+ Constant & 474.478$^{***}$ & 449.960$^{***}$ & 449.666$^{***}$ & 429.919$^{***}$ \\ 
+  & (6.328) & (9.440) & (11.122) & (27.606) \\ 
   & & & & \\ 
@@
 Flag FE & No & No & No & Yes \\ 
-Observations & 8,558 & 8,558 & 8,558 & 8,558 \\ 
-R$^{2}$ & 0.026 & 0.044 & 0.044 & 0.107 \\ 
+Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
+R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
 \hline 
@@
 
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:long}Coefficient estimates
-for each model. Top pannel indicates variable, x-axis represents model
-specification, and y-axis coefficient estimate.}
-\end{figure}
-
-\subsection{Effort displacement and
-redistribution}\label{effort-displacement-and-redistribution}
-
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
-
-\renewcommand\refname{References}
 \bibliography{references.bib}

### 2018-09-29 rmd/Manuscript.Rmd
Updated latest analyses and manuscript

@@
 Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
-date: |
-  ^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA
-  ^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI
+date: "^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA\\newline^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI"
 output:
   bookdown::pdf_document2:
-    toc: yes
-    toc_depth: 4
+    toc: no
     citation_package: natbib
@@
     number_sections: no
+fontsize: 12pt
 header-includes:
   - \usepackage{float}
-  - \floatplacement{figure,table}{H}
+  - \floatplacement{figure}{H}
   - \usepackage{lineno}
@@
 bibliography: references.bib
-biblio-style: nature
+# biblio-style: nature
 ---
@@
 This section is divided into two main parts.
-First, we provide a general description of AIS data and the process of identification of vessel-level events done by Global Fishing Watch [^1].
+First, we provide a general description of AIS data and the process of identification of vessel-level events done by Global Fishing Watch[^1].
 Alongside, we describe the subset of data that we use for these analyses.
@@
 
-[^1]: [Global Fishing Watch](globalfishingwatch.org)
+[^1]: Global Fishing Watch: [globalfishingwatch.org](globalfishingwatch.org)
 
@@
 These broadcasted positions can be recorded by satellites and land-based antenas.
-GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally \citep{kroodsma_2018}.
+GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally since 2012 \citep{kroodsma_2018}.
 The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points) and therefore fishing hours.
-It is therefore important to be cautious when comparing temporal trends.
-The variability in AIS data and dynamic ocean conditions require that temporal trends be taken into account.
+The variability in AIS data and ocean conditions require that temporal trends be taken into account.
 We do that by incorporating a series of controls, which are defined in the following section.
@@
 ```{r}
-effort_by_vessel <- read.csv(file = here::here("data", "effort_by_vessel.csv"))
+effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
+  filter(year < 2018)
 ```
@@
   length()
-
-n_prev <- effort_by_vessel %>% 
-  filter(treated, !post) %$%
-  unique(mmsi) %>% 
-  length()
-
-n_post <- effort_by_vessel %>% 
-  filter(treated, post, baci_strict) %$%
-  unique(mmsi) %>% 
-  length()
 ```
 
-The GFW data contain `r pipa_vessels` purse seiners and longliners that have fished within PIPA waters.
-From these, only `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015[^2].
+Our data contain over 45 million individual AIS messages for 371 purse seiners and longliners.
+A total of 233 vessels have fished within PIPA waters; 217 did so at least once before 2015.
+However, not all vessels continued to fish elsewhere after PIPA implementation: 34 vessels have no recorded AIS messages after 2015[^2], leaving us with `r pipa_vessels` vessels that fished inside PIPA before its implementation, and continued to fish elsewhere afterward.
 Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period.
@@
 Therefore, we define our treatment and control groups as follows.
-The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
-The control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
-Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level that make up each of group through time.
 
-Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively.
+The treatment group contains all vessels (n = `r pipa_vessels`) that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
+Vessels in the control group meet al three of the following conditions: i) Vessels never fished within PIPA waters, ii) vessels belong to other PNA countries, and iii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
+For each vessel meeting these characteristics, we calculate their total monthly fishing hours.
+Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level streams of fishing events that make up each group through time.
+Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show the number of vessels following a BACI design, and fishing hours, respectively.
 Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after).
-The relative change (After / Before) is also shown.
-Table \ref{tab:baci_n} shows information for all fishing vessels in the dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show information for vessels that meet the BACI design (i.e.
-excludes vessels that only appear at one point in time).
+The relative change in fishing hours (After / Before) is also shown.
 
-![\label{fig:baci_strict}Stream of fishing events by vessels (stacked on the y-axis due to space) through time (x-axis).
-Each dot represent a vessel-month, with colors indicating the pre and post periods, and pannels separating between gear and treated or control groups.](../img/BACI_strict_gear.png)
+<!-- **Do we know what is causing this?
+[first sentence in fist paragraph of results] I'm guessing this can't be Blue Paradox stuff because we see it for the control group as well who are supposed to have never fished within PIPA.** -->
 
-[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore chaning their AIS and mmsi), or turned off their AIS transmiters.
-On either case, we are not able to observe these.
+<!-- **Is the larger number of longliners surprising? I thought PIPA was known as a purse seining ground and less so for longlining.** -->
 
-```{r}
-effort_by_vessel %>% 
-  # filter(baci_strict) %>%
-  group_by(gear, treated, post, mmsi) %>% 
-  count() %>% 
+[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmiters.
+In either case, we are not able to observe these.
+
+```{r, fig.width = 8, fig.height = 6, fig.cap = "\\label{fig:baci_strict}Stream of fishing events by vessels through time.
+Each line represents a vessel, with dots indicating months with fishing activity and colors indicating the pre and post periods.
+Pannels separating between gear and treated or control groups."}
+filter(effort_by_vessel, baci_strict) %>% 
+  mutate(gear = ifelse(gear == "purse_seines", "Purse seiners", "Drifting longliners")) %>% 
+  group_by(mmsi, date, gear, post, treated) %>%
+  summarize(h = sum(hours, na.rm = T)) %>%
   ungroup() %>% 
-  group_by(gear, treated, post) %>% 
-  summarize(boats = n()) %>% 
-  spread(post, boats) %>% 
-  mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_n}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.",
-               booktabs = T) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
+  arrange(treated, post, mmsi) %>%
+  mutate(vessel = group_indices(., paste(gear, treated, mmsi)),
+         treated = ifelse(treated, "Treated", "Control")) %>% 
+  ggplot(aes(
+    x = date,
+    y = vessel,
+    fill = post,
+    color = post,
+    group = paste(vessel, post)
+    )) +
+  geom_point(size = 1) +
+  theme_bw() +
+  facet_wrap(gear ~ treated, scales = "free_y") +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  scale_y_continuous(breaks = NULL, labels = NULL) +
+  theme(legend.position = "none")
 ```
@@
   filter(baci_strict) %>%
-  group_by(gear, treated, post, mmsi) %>% 
+  group_by(gear, treated, mmsi) %>% 
   count() %>% 
   ungroup() %>% 
-  group_by(gear, treated, post) %>% 
+  group_by(gear, treated) %>% 
   summarize(boats = n()) %>% 
-  spread(post, boats) %>% 
-  mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.",
+  knitr::kable(col.names = c("Gear", "Treatment", "n"),
+               caption = "\\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.",
                booktabs = T) %>% 
@@
   knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_h}Mean fishing hours for each gear before and after",
+               caption = "\\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.",
                booktabs = T) %>% 
@@
 ## Analysis
-
-### Change in behavior
 
@@
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
 $$
 
-Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$.
+Where $y_{i,t}$ is the variable of interest for vessel $i$ in time period $t$.
 A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation.
@@
 $\alpha$ is the standard intercept, $\beta_1$ captures the *ex post* change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.
+Finally, $\mu_1$ and $\mu_2$ are coefficients for a second order polynomial for years ($Y_t$)[^4], while $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions.
 
@@
 
-### Vessel displacement and redistribution
+[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendx.
 
 ```{r}
-displacement_data <- readRDS(file = here::here("data", "displacement_data.rds"))
+displacement_data <- readRDS(file = here::here("data", "displacement_data.rds")) %>% 
+  filter(year < 2018)
 ```
@@
 We calculate the monthly relative distribution of fishing hours by all treated vessels across all fished EEZs and the high seas.
-These trends are shown in Figure \ref{fig:redist_trend}.
-EEZs that had sproadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country))` spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs").
-Figure \ref{fig:redist_trend_spa} shows the yearly average of the relative spatial allocation of fishing efforts; this is the spatial representation of \ref{fig:redist_trend} averaged by year.
+These trends are shown in Figures \ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the relative change is presented in Table \ref{tab:ba_disp}.
+EEZs that had sproadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country[displacement_data$gear == "purse_seines"]))` and n = `r length(unique(displacement_data$country[!displacement_data$gear == "purse_seines"]))` spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs") for purse seiners and longliners, respectively.
+
+To evaluate this change in effort allocation, we regress our variable of interest, fishing hours, on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries, to obtain the by-country change in proportional allocation of fishing effort:
+
+$$
+y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
+$$
+
+Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that country $i$ receives at time $t$.
+$Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise.
+$Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs".
+Our parameter of interest is $\beta_3$, which captures the country-level change in proportional fishing effort.
+
+<!-- Like before, we include a dummy variable for months and allow for a second degree polynomial trend through time. -->
+
+All regression coefficients were estimatedd via ordinary least squares, and heteroskedastic-robust standard errors were calculated.
+All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")`) \citep{rcore_2018}.
+Raw data and code used in this work are available on [github](https://github.com/jcvdav/MPA_displacement).
+
+<!-- Figure \ref{fig:redist_trend_spa} shows the yearly average of the relative spatial allocation of fishing efforts; this is the spatial representation of \ref{fig:redist_trend} averaged by year.
+-->
 
@@
 
-eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"), layer = "EEZ_subset")
+eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"),
+               layer = "EEZ_subset")
 
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend}"}
+```{r}
+ba_disp_ps <- displacement_data %>% 
+  filter(gear == "purse_seines") %>% 
+  group_by(country, post) %>% 
+  summarize(h_prop_m = mean(h_prop)) %>% 
+  spread(post, h_prop_m) %>% 
+  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
+  select(country, change)
+
+ba_disp_ll <- displacement_data %>% 
+  filter(!gear == "purse_seines") %>% 
+  group_by(country, post) %>% 
+  summarize(h_prop_m = mean(h_prop)) %>% 
+  spread(post, h_prop_m) %>% 
+  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
+  select(country, change)
+
+ba_disp_ps %>% 
+  mutate(gear = "Purse seiners") %>% 
+  rbind(mutate(ba_disp_ll, gear = "Longliners")) %>% 
+  spread(gear, change) %>% 
+  knitr::kable(digits = 2,
+               booktabs = T,
+               caption = "\\label{tab:ba_disp}") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
+<!-- **An additional test to add to the wish list is to see if vessels are fishing closer to each other following the PIPA closure.** -->
+
+\clearpage
+
+# Results
+
+Our data suggest that purseiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Area.
+Fig.
+\ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
+This trend is observed for both treated and control groups.
+Longliners, however, show a more stable trend.
+The number of mmsi codes increases through time.
+This can largely be explained by the addition of more satellites, which increase detectability of vessels.
+As expected, total fishing hours follow a similar trend to that of mmsi numbers.
+
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
+effort_by_vessel %>% 
+  filter(baci_strict) %>%
+  group_by(year, gear, treated, post, month) %>% 
+  summarize(total_hours = sum(hours),
+            mean_hours = mean(hours),
+            n_mmsi = n()) %>% 
+  ungroup() %>% 
+  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
+  select(-year) %>% 
+  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
+  ggplot(aes(x = date, y = value, color = treated)) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(gear~variable, scales = "free", ncol = 3) +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
+```
+
+Our DiD anaylsis shows that treated purse seiners reduce their fishing effort after PIPA implementation in the order of 16 hours per month.
+This result is robust and significant (*p < 0.05*) for all model specifications, with the effect varying between $\beta_3 = -16.457$ and $\beta_3 = -18.709$.
+Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and cuadratic terms, respectively.
+These effectively represent the patterns observed in Figure {fig:all_vessels}.
+
+Longliners show a similar pattern of effort reduction.
+However, the magnitude of the $\beta_3$ coefficient is smaller (ranging from  $\beta_3 = -9.851$ to $\beta_3 = -14.850$) and not significant across all model specifications.
+This, along with higher standard error values suggest that longliners have a smaller and more variable response to the implementation of LSMPAs.
+
+Regressions coefficients for each gear type are shown in Tables \ref{tab:purse} and \ref{tab:long}.
+Column (1) presents the DiD regression with no fixed effects, column (2) includes month fixed effects, column (3) includes month and the second degree polynomial for years, and column (4) includes all of the above and country-level fixed effects.
+
+```{r, results = "asis", echo = F}
+
+model_data <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year^2,
+         mmsi_c = as.factor(mmsi))
+
+m1 <- lm(hours ~ post*treated, data = model_data)
+m2 <- lm(hours ~ post*treated + month_c, data = model_data)
+m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
+m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
+
+models <- list(m1, m2, m3, m4)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+```
+
+```{r, fig.width = 5, fig.height = 3, fig.cap = "\\label{fig:puse}Coefficient estimates for each model.
+Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate.", eval = F}
+map_df(models, broom::tidy, .id = "model") %>%
+  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
+  ggplot(aes(x = model, y = estimate)) +
+  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
+                size = 1,
+                width = 0,
+                color = "red") +
+  geom_point(color = "steelblue", size = 3) +
+  facet_wrap(~term, scale = "free") +
+  ggtheme_plot()
+```
+
+```{r, results = "asis"}
+
+model_data <- effort_by_vessel %>% 
+  filter(baci_strict,
+         !gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year^2,
+         mmsi_c = as.factor(mmsi))
+
+m1 <- lm(hours ~ post*treated, data = model_data)
+m2 <- lm(hours ~ post*treated + month_c, data = model_data)
+m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
+m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
+
+models <- list(m1, m2, m3, m4)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+```
+
+```{r, fig.width = 5, fig.height = 3, fig.cap = "\\label{fig:long}Coefficient estimates for each model.
+Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate.", eval = F}
+map_df(models, broom::tidy, .id = "model") %>%
+  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
+  ggplot(aes(x = model, y = estimate)) +
+  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
+                size = 1,
+                width = 0,
+                color = "red") +
+  geom_point(color = "steelblue", size = 3) +
+  facet_wrap(~term, scale = "free") +
+  ggtheme_plot()
+```
+
+<!-- ## Effort displacement and redistribution -->
+
+Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.
+In this case, we calculate the prportion of fishing effort allocated every month to each spatially explicit region outlined by EEZs and the high seas.
+For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs.
+Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels.
+The top-left pannel shows the change in fishing effort inside PIPA, including the preemtive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
+
+The change in the relative allocation fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation \ref{tab:disp_mod}.
+The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*).
+In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters.
+The only decrease is observed for Papua New Guinea, but the coefficient is not significant.
+Figure \ref{fig:map_change_ps} provides a spatial representation of these changes.
+It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA.
+
+```{r, fig.cap = "\\label{fig:redist_trend_ps}"}
 displacement_data %>% 
+  filter(gear == "purse_seines") %>% 
+  ggplot(aes(x = date, y = h_prop, group = post)) +
+  geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
+  geom_point(size = 1) +
+  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
+  scale_fill_brewer(palette = "Paired") +
+  ggtheme_plot() +
+  facet_wrap(~country, scales = "free_y")
+```
+
+```{r, fig.cap = "\\label{fig:redist_trend_ll}", eval = F}
+displacement_data %>% 
+  filter(!gear == "purse_seines") %>% 
   ggplot(aes(x = date, y = h_prop, group = post)) +
@@
 
-<!-- Meter tabla ba_disp aqui -->
+```{r, fig.cap = "\\label{fig:map_change_ps}"}
+pipa_map_ba_disp <- pipa %>% 
+  mutate(country = "PIPA") %>% 
+  left_join(ba_disp_ps, by = "country")
 
-To evaluate this change in effort allocation, we regress our variable of interest, fishing hours, on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries, to obtain the by-country change in proportional allocation of fishing effort:
+# Los colores del mapa deben estar dados por el Post:Country
+eez %>% 
+  left_join(ba_disp_ps, by = c("ISO_Ter1" = "country")) %>%
+  filter(!is.na(change)) %>% 
+  ggplot() +
+  geom_sf(aes(fill = change), color = "black") +
+  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
+```
 
-$$
-y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
-$$
+```{r, fig.cap = "\\label{fig:map_change_ps}"}
+pipa_map_ba_disp <- pipa %>% 
+  mutate(country = "PIPA") %>% 
+  left_join(ba_disp_ll, by = "country")
 
-Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that country $i$ receives at time $t$.
-$Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise.
-$Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs".
-Our parameter of interest is $\beta_3$, which captures the country-level change in proportional fishing effort.
+# Los colores del mapa deben estar dados por el Post:Country
+eez %>% 
+  left_join(ba_disp_ll, by = c("ISO_Ter1" = "country")) %>%
+  filter(!is.na(change)) %>% 
+  ggplot() +
+  geom_sf(aes(fill = change), color = "black") +
+  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
+```
 
-# Results
+```{r, results = "asis"}
+# Dont have this here. Just write the model specification
 
-Fig.
-\ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
-This trend is observed for both treated and control groups.
-Longliners, however, show a more stable trend.
-The number of mmsi codes increases through time.
-This can largel be explained by the addition of more satellits, which increasedetectability of vessels.
-As expected total fishing hours follow a similar trend to that of mmsi numbers.
-Results of the regressions for each gear type are shown in Tables \ref{tab:purse} and \ref{tab:long}.
-Column (1) presents the DiD regression with no fixed effects, column (2) includes month fixed effects, column (3) includes month and year fixed effects, and column (4) includes month, year, and flag fixed effects.
-Figures \ref{fig:puse} and \ref{fig:long} represent the same coefficient estimates.
+disp_mod_ps_data <- displacement_data %>% 
+  filter(!is.na(country),
+         gear == "purse_seines") %>% 
+  mutate(post = post *1,
+         year2 = year^2,
+         month_c = as.character(month))
 
-```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
-effort_by_vessel %>% 
-  filter(baci_strict) %>%
-  group_by(year, gear, treated, post, month) %>% 
-  summarize(total_hours = sum(hours),
-            mean_hours = mean(hours),
-            n_mmsi = n()) %>% 
-  ungroup() %>% 
-  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
-  select(-year) %>% 
-  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
-  ggplot(aes(x = date, y = value, color = treated)) +
-  geom_line() +
-  geom_point() +
-  facet_wrap(gear~variable, scales = "free", ncol = 3) +
-  theme_bw() +
-  scale_color_brewer(palette = "Set1") +
-  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
+disp_mod_ps1 <- lm(h_prop ~ post*country, data = disp_mod_ps_data)
+
+models <- list(disp_mod_ps1)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = "month",
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes")),
+                     header = F,
+                     single.row = T,
+                     title = "\\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region.
+Asterisks indicate significance levels.
+Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+
 ```
+
+# Discusion
+
+Our findings provide interesting insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
+These collection of results shows that the implementation of PIPA caused treated vessels to redeuce their fishing hours, and that this effect is greater for purse seiners.
+Even though treated vessels fish less, their relative allocation of fishing hours increased for all other fishing grouds.
+This fidnings does not imply that there is more fishing effort, but rather that each region receives a greater portion of the post-PIPA fishing effort (which is lower than pre-PIPA).
+In this section we discuss the implications of vessel-level reductions in fishing effort and the increase in relative allocation of the remaining effort through space.
+We also provide plausible explanations as to why purse seiners seem to be more reactive to the spatial closure.
+
+<!-- **We should have a discussion (over the phone and in the paper) about whether a decrease in fishing hours represents a positive or negative impact of PIPA.
+Without data on catch it might be hard to really know.** -->
+
+Previous studies on insular environments suggest that vessels move to distant places, which might be translated as increased costs \citep{stevenson_2013}.
+Nevertheless, this study does not use counterfactuals that could help account for system- or fleet-level changes that occur through time.
+Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges ospatial closures, yielding greater catches \citep{murawski_2005}.
+Yet, these vessel tracks do not cover the pre-reserve period, making it difficult identify the contribution of spatial closures to the observed spatial distribution of fishing vessels.
+Recent work by \citet{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space.
+Our data is assambled in a similar way, with fishing positions before and after the implementation of PIPA and vessels grouped into treated and control groups.
+Our BACI design, along with our difference-in-differences analysis allows us to make causal inferences about the effect that large scale marine protected areas have on fishing effort.
+
+The different responses observed between purse seiners and longliners might have two possible explanations.
+It is likely that PIPA did not contain habitat that longliners would consider optimal.
+Therefore, the sporadic fishing events that occurred there are of little importance to the fleet, and it is unlikely that the implementation of PIPA has an effect on them.
+Alternatively, the differences may be due to the nature of each fishing gear.
+Purse seiners are often constrained by seafloor and termocline depth, and often operate in more restricted areas \citep{kroodsma_2018}.
+Tuna purse seiners are known to have greater proportion of null sets (*i.e.* where the purse seine is effectively casted arround tuna, but no catch is obtained) during El Niño years, where the termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}.
+On the other hand, longliners may be more flexible as to where they can deploy their longlines.
+\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be underutilizing the ocean, meaning that they can easily redistribute elsewhere.
+
+<!-- # Notes and things to do -->
+
+<!-- Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time. -->
+
+<div id = "refs"> </div>
 
@@
 
-## Change in behavior
-
-### Purse seiners
+# Appendix
 
@@
   mutate(post = post * 1,
-         treated = treated * 1) %>% 
-  mutate_at(.vars = vars(month, year, mmsi), .funs = as.character)
+         treated = treated * 1,
+         mmsi_c = as.factor(mmsi))
 
 m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month, data = model_data)
-m3 <- lm(hours ~ post*treated + month + year, data = model_data)
-m4 <- lm(hours ~ post*treated + month + year + flag, data = model_data)
+m2 <- lm(hours ~ post*treated + month_c, data = model_data)
+m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
+m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
 
@@
                      header = F,
-                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
+                     title = "\\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
 Asterisks indicate significance levels.
@@
 ```
-
-```{r, fig.cap = "\\label{fig:puse}Coefficient estimates for each model. Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
-map_df(models, broom::tidy, .id = "model") %>%
-  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
-  ggplot(aes(x = model, y = estimate)) +
-  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
-                size = 1,
-                width = 0,
-                color = "red") +
-  geom_point(color = "steelblue", size = 3) +
-  facet_wrap(~term, scale = "free") +
-  theme_bw()
-```
-
-\clearpage
-
-### Longliners
 
@@
 ```
-
-```{r, fig.cap = "\\label{fig:long}Coefficient estimates for each model. Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
-map_df(models, broom::tidy, .id = "model") %>%
-  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
-  ggplot(aes(x = model, y = estimate)) +
-  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
-                size = 1,
-                width = 0,
-                color = "red") +
-  geom_point(color = "steelblue", size = 3) +
-  facet_wrap(~term, scale = "free") +
-  theme_bw()
-```
-
-## Effort displacement and redistribution
-
-```{r}
-ba_disp <- displacement_data %>% 
-  group_by(country, post) %>% 
-  summarize(h_prop_m = mean(h_prop)) %>% 
-  spread(post, h_prop_m) %>% 
-  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
-  select(country, change)
-
-pipa_map_ba_disp <- pipa %>% 
-  mutate(country = "PIPA") %>% 
-  left_join(ba_disp, by = "country")
-
-# Los colores del mapa deben estar dados por el Post:Country
-eez %>% 
-  left_join(ba_disp, by = c("ISO_Ter1" = "country")) %>%
-  filter(!is.na(change)) %>% 
-  ggplot() +
-  geom_sf(aes(fill = change), size = 1, color = "black") +
-  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
-  ggtheme_plot() +
-  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
-```
-
-```{r, eval = F}
-# Dont have this here. Just write the model specification
-
-displacement_data %>% 
-  filter(!is.na(country)) %>% 
-  lm(h_prop ~ post*country, data = .) %>% 
-  summary()
-```
-
-<!-- # Discusion -->
-
-<!-- ### Further work -->
-
-<!-- In order to strengthen this analysis, I would like to identify an appropriate sample of vessels that acccurately represent the PNA.
-This vessels must meet at least these two points: i) belong to the PNA and ii) Have fished for a significant amount of time inside PIPA, to count as "treated".
-Ideally, this would get rid of vessels that sporadically fished for insignificant time in PIPA, and are therefore unlikely to be affected.
-This would include between 12 and  vessels (number of Kiribati vessels vs.
-number of all vessels who fished in PIPA at least once before 2015).
--->
-
-<!-- I would also like to explore the possibility of identifying a plausible counterfactual.
-That way we could do something like a DiD.
-I think it is possible to identify counterfactual boats.
-I would start by identifying vessels who meet at least these four criteria: i) fish in near-by regions, ii) have same gear as vessels from PIPA, and iii) having similar length of data, and iv) never fished inside PIPA.
-Perhaps an additional one would be that they belong to the PNA.
--->
-
-<!-- Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time. -->
-
-<!-- \clearpage -->
-
-<!-- # Possible contributions -->
-
-<!-- As I understand the efforts made so far, there are two straightforward ways in which I could contribute to this study.
-For the first one I would help strengthen the analysis of NOAA Observer and GFW data for the US PNMs.
-The second one would involve conducting the analysis of GFW data for PIPA, and translating the results into implications for Palau.
-I discuss these two in greater detail in the next paragraphs.
--->
-
-<!-- ## US Pacific Monuments -->
-
-<!-- In this section I include possible analysis in which I could help.
-When relevant, I include quotes to provide context.
-Comments are organized with headings similar to the ones included in the original manuscript.
-I believe my suggestions would compliment (rather than replace) current analysis, and I acknowledged that you might have already tried some or that due to data constraints not all of them are possible.
--->
-
-<!-- ### Total revenue -->
-
-<!-- "It is very clear from the figure that total catch of bigeye has not declined as a result of the 2014 or -->
-<!-- 2016 expansions".
-Of course, I have not reviewed the data.
-But is it safe to conclude this?
-At least through time there isn't an evident decrease, but what would have catches looked like had PMNM not been expanded?
--->
-
-<!-- Not sure if the spatial resolution (*i.e.* Catch Blocks) in logbooks allows this comparison, but it would be interesting to see what proportion of catches (or at least sets / hours) originally came from waters inside the PMNM.
-Perhaps the georeferenced catches from NOAA Observer data can provide insights into this (if not for the entire fleet, at least for the 20% quasi-random subset), or we can use GFW data to see if the proportion of fishing hours inside PMNM roughly corresponds to 10M in revenues (we can test different "catch rates" to account for the fact that catches inside vs outside may not map 1:1).
-Perhaps this catch efficiency ratio can be extracted from the NOAA Observer data?
--->
-
-<!-- On aggregate the fleet brought in more money in 2015 and 1016 than in previous year, but you discuss the possibility that the distributional effects of this might be different.
-I would assume that vessels who fished the most in the PMNM area were the ones who took the toughest hit.
-If possible, it might be interesting to birefly look at distributional effects for the discussion.
--->
-
-<!-- ### Total costs (TC) -->
-
-<!-- So far this section describes the available data, but it it's not clear whether the empirical strategy is fully developed.
-Just like the datasets, a there isn't a single best analysis that provides the answer, but looking at it from as many was as possible might help paint a full picture of the effects that vLPAs have had.Here I provide some ideas in which we could use the two main datasets (NOAA and GFW data) to indirectly test the claims made by the fleet.
--->
-
-<!-- #### TC from NOAA Observer program -->
-
-<!-- You mention that a drawback of this dataset is that you only observe fishing events, and not the entire trip (*i.e.* the search and travel).
-It might be worth looking into combining this with GFW data.
-NOAA observer program would provide real fishing events (as opposed to the ones predicted by GFW's neural net), and GFW would provide the entire track.
-Given that NOAA data cover 20% and GFW only contain 60 boats, we will not get full coverage.
-If this doesn't yield better data, it would at least help determine if the three-day space between sets is an appropriate way of grouping them into "trips".
--->
-
-<!-- Results in your table 3 suggest that there's been a change of ~ 20 miles (positive or negative depending on model specification), and not significant.
-Perhaps linking this data to GFW would provide full tracks (of a smaller portion of the fleet) to then account for distance between fishing points but also during the search and set activities.
--->
-
-<!-- #### TC form GFW Data -->
-
-<!-- We could also test the increased cost claim by looking at the almost 60 vessels and calculate an estimate of fuel consumption (following @sala_2018), which, paired with fuel prices, might provide cost estimates[^1].
-Initially this would just be a regression with a policy dummy (and appropriate vessel- and month-level FE's).
-We could look into GFW data to identify plausible counterfactuals to include  a control group[^2].
--->
-
-<!-- [^1]: Of course, there are additional costs (*e.g.* crew, ice, bait, gear), but fuel should represent a large portion of this and should scale with some measures of fishing effort (time and distance).
-If this is not enough, the previous comparison of catches (sets) that came from PMNM waters before the implementation could provide some insights.
--->
-
-<!-- [^2]: GFW increased coverage when they added from more satellites, particularly towards the end of 2016 and throughout 2017, I believe.
-I think it would be important to use counterfactuals in any GFW-related analyses to account for the expected temporal trend in increased effort.
--->
-
-<!-- # Other details -->
-
-<!-- - The introduction states that the main objective is to quantify the economic impacts of vLPAs and compare the cost per hectare to vLPAs on land.
-I think this would provide an interesting benchmark on cost of conservation per unit area in land vs sea.
-I would perhaps highlight the part about predicting the possible effects of the Palau MPA.
--->
-
-<!-- - I think the novelty of the paper can be highlighted even more.
-@stevenson_2013 evaluated the consequences of fishing displacement from MPAs in Hawaii (a smaller network and totally different fleet).
-They show that fishing effort was indeed displaced to places further away from ports representing increased costs, but that CPUE also increased.
-Overall, they don't find a negative impact on the *perceived* socioeconomic well-being of fishers.
-However, they do not have plausible counterfacutals and rely on before-after comparisons of perceptions.
-I think the novelty of this paper is not only the size, resolution, and quality of the data, but the fact that it has a BACI design enabling the identification of the net effect that vLPAs have on fishers.
-And also the larger contribution to vLPAs (and MPAs in general) literature.
--->
-<!-- - Recent work by @sala_2018 shows that a large portion of high-seas fishing is only profitable thanks to subsidies. This could compliment @white_2014 and @sumaila_2015 in the introduction. -->
-
-<!-- - "Neither of these datasets is perfect but hopefully combined they will paint a clear picture of what the impact has been".
-I find this to be a modest (or humble?) and powerful sentence that highlights the efforts made to identify effects from different sources, and that acknowledges possible data limitations.
-This sentence should be included alongside the "novelty" in the last paragraph of the introduction.
--->
-
-<!-- - Findings by @smith_2006 show negative effects, but the reserves were only in place for a short period.
-I believe they talk about this in their discussion.
-@edgar_2014-UO and @difranco_2016-Xw show how the effects (at least inside vs outside the reserve) can take up to 10 years.
--->
-
-<!-- - I would be cautious on the interpretation of results by @sumaila_2015.
-They do show that < 0.01% of catch and landed values come *exclusively* from the high seas, but also that 67% and 72% (catch and value) come from Both EEZs and High seas, and the remaining from EEZs only.
-@pauly_2016 show that ~6% of landings come from the high seas (Fig.
-\ref{fig:eez-hs}).
-It's perhaps a minor detail, but thought I'd point it out.
--->
-
-# References

### 2018-09-29 docs/Manuscript.tex
Added changes after proof reading, waiting for spatial analysis to be done before sending it out to John

@@
 
-\clearpage
+\section{Introduction}\label{introduction}
 
-\section{Introduction}\label{introduction}
+Mpas are being implemented like crazy
+
+Debate on LSMPA the devil you know
+
+Where do vessels go is the key part of it
 
@@
 description of AIS data and the process of identification of
-vessel-level events done by Global Fishing Watch\footnote{Global Fishing
-  Watch: \url{globalfishingwatch.org}}. Alongside, we describe the
-subset of data that we use for these analyses. When relevant, we also
-point out possible shortcommings in the data, or factors that must be
-considered in the later analyses. Then we move on to explain our
-identification strategy, and the main analyses that we undertake.
+vessel-level fishing events done by Global Fishing Watch\footnote{Global
+  Fishing Watch: \url{globalfishingwatch.org}}. Alongside, we describe
+the subset of data that we use for these analyses. When relevant, we
+also point out possible shortcommings in the data, or factors that must
+be considered in the later analyses. We then move on to explain our
+empirical strategy for the identification of the behaviorial changes and
+redistribution of fishing effort.
 
@@
 
-\subsubsection{AIS data}\label{ais-data}
-
 Automatic Identification Systems are on-board devices intended to
 provide at-sea saftey and prevent ship collisions by broadcasting vessel
-locations to surrounding vessels. These broadcasted positions can be
-recorded by satellites and land-based antenas. GFW uses a neural network
-to infer vessel characteristics and whether each broadcasted position
-represents a fishing event, thus allowing us to estimate near real-time
-fishing events globally since 2012 \citep{kroodsma_2018}. The recent
-addition of satellites that can receive AIS signals causes an apparent
-increase in the number of broadcasted AIS messages (\emph{i.e.} points)
-and therefore fishing hours. The variability in AIS data and ocean
-conditions require that temporal trends be taken into account. We do
-that by incorporating a series of controls, which are defined in the
-following section.
+position, course, and activities to surrounding vessels. These
+broadcasted messages can be received by satellites and land-based
+antenas. GFW uses a neural network to infer vessel characteristics and
+whether each broadcasted position represents a fishing event, thus
+allowing us to estimate near real-time fishing events globally since
+2012 \citep{kroodsma_2018}. Our data contain information for 2012 -
+2017. The recent addition of satellites that can receive AIS signals
+causes an apparent increase in the number of broadcasted AIS messages
+(\emph{i.e.} points), and therefore number of vessels and fishing hours.
+The variability in AIS data and ocean conditions require that temporal
+trends be taken into account. We do that by obtaining a subset of data
+that meet a BACI design, which gives us the full tracks for vessels
+affected and unaffected by the implementation of PIPA.
 
-\subsubsection{PIPA data}\label{pipa-data}
-
-Our data contain over 45 million individual AIS messages for 371 purse
-seiners and longliners. A total of 233 vessels have fished within PIPA
-waters; 217 did so at least once before 2015. However, not all vessels
-continued to fish elsewhere after PIPA implementation: 34 vessels have
-no recorded AIS messages after 2015\footnote{The 0 missing vessels might
-  have exited the fishery, been decomissioned or sold (therefore
-  changing their AIS and mmsi), or turned off their AIS transmiters. In
-  either case, we are not able to observe these.}, leaving us with 183
-vessels that fished inside PIPA before its implementation, and continued
-to fish elsewhere afterward. Vessels that fished within PIPA before
-implementation might stop fishing afterwards, therefore not being
-observable in the post-treatment period. New vessels might have also
-entered the fishery after PIPA closure, and were likely not exposed to
-the policy intervention in the pre-treatment period. Therefore, we
-define our treatment and control groups as follows.
+Our data contain over 45 million individual AIS messages (\emph{i.e.}
+positions) for 371 purse seiners and longliners. A total of 233 vessels
+have fished within PIPA waters; 217 did so at least once before 2015.
+However, not all vessels continued to fish elsewhere after PIPA
+implementation: 34 vessels have no recorded AIS messages after
+2015\footnote{The 34 missing vessels might have exited the fishery, been
+  decomissioned or sold (therefore changing their AIS and mmsi), or
+  turned off their AIS transmiters. In either case, we are not able to
+  observe these.}, leaving us with 183 vessels that fished inside PIPA
+before its implementation, and continued to fish elsewhere afterward.
+New vessels might have also entered the fishery after PIPA closure, and
+were likely not exposed to the policy intervention in the pre-treatment
+period. To account for this, we identify a subset of vessels which we
+track since before the implementation of PIPA, and categorize them as
+treated or control vessels. Our treatment and control groups are defined
+as follows.
 
@@
 PIPA at least once before the closure, and that continued to fish
-elsewhere afterwards. Vessels in the control group meet al three of the
-following conditions: i) Vessels never fished within PIPA waters, ii)
+elsewhere afterwards. Vessels in the control group meet all three of the
+following conditions: i) vessels never fished within PIPA waters, ii)
 vessels belong to other PNA countries, and iii) vessels have fished in
@@
 their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
-a visual representation of the vessel-level streams of fishing events
-that make up each group through time. Tables \ref{tab:baci_n_s} and
-\ref{tab:baci_h} show the number of vessels following a BACI design, and
-fishing hours, respectively. Tables show data grouped by gear
-(longlines, purse seines), group (treated, control), and period (before,
-after). The relative change in fishing hours (After / Before) is also
-shown.
+a visual representation of the vessel-level fishing events that make up
+each group through time. Table \ref{tab:baci_n_s} shows the number of
+vessels following a BACI design, as well as the fishing hours, before
+and after PIPA.
 
@@
 indicating months with fishing activity and colors indicating the pre
-and post periods. Pannels separating between gear and treated or control
-groups.}
+and post periods.}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.}
+\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{llrrrr}
 \toprule
-Gear & Treatment & n\\
+Gear & Treatment & n & Before & After & Change (A / B)\\
 \midrule
-drifting\_longlines & FALSE & 85\\
-drifting\_longlines & TRUE & 115\\
-purse\_seines & FALSE & 36\\
-purse\_seines & TRUE & 68\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.}
-\centering
-\begin{tabular}[t]{llrrr}
-\toprule
-Gear & Treatment & Before & After & Change (A / B)\\
-\midrule
-drifting\_longlines & FALSE & 474.47780 & 462.5491 & 0.9748593\\
-drifting\_longlines & TRUE & 544.61935 & 522.8392 & 0.9600085\\
-purse\_seines & FALSE & 59.49026 & 154.5776 & 2.5983673\\
-purse\_seines & TRUE & 52.91534 & 131.5452 & 2.4859561\\
+drifting\_longlines & FALSE & 85 & 474.47780 & 462.5491 & 0.9748593\\
+drifting\_longlines & TRUE & 115 & 544.61935 & 522.8392 & 0.9600085\\
+purse\_seines & FALSE & 36 & 59.49026 & 154.5776 & 2.5983673\\
+purse\_seines & TRUE & 68 & 52.91534 & 131.5452 & 2.4859561\\
 \bottomrule
@@
 Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
-period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
+period \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
 dates prior to PIPA implementation and a value of 1 por all dates
@@
 (\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
-the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
+the standard intercept, \(\beta_1\) captures the temporal trend change,
 \(\beta_2\) captures the difference between treated and control groups,
@@
 the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
-for a second order polynomial for years (\(Y_t\))\footnote{An earlier
-  specification included years as a dummy variable. Such results are
-  included in the appendx.}, while \(\phi_t\) and \(\gamma_i\) represent
-month-, and flag-level dummies that account for seasonality or
-country-level management interventions.
+for a second order polynomial for years (\(Y_t\)), while \(\phi_t\) and
+\(\gamma_i\) represent month-, and flag-level dummies that account for
+seasonality or country-level management interventions\footnote{An
+  earlier specification included years as a dummy variable. Such results
+  are included in the appendx, but are similar to the ones found under
+  current specification.}.
 
@@
 relative distribution of fishing hours by all treated vessels across all
-fished EEZs and the high seas. These trends are shown in Figures
-\ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the
-relative change is presented in Table \ref{tab:ba_disp}. EEZs that had
-sproadic fishing events were pooled into a group of ``others'', leaving
-us with a total of n = 12 and n = 10 spatially defined regions
-(\emph{i.e.} EEZs, High Seas, ``other EEZs'') for purse seiners and
-longliners, respectively.
+fished EEZs and the high seas. These trends are shown in Figure
+\ref{fig:redist_trend_ps}, and the relative temporal change is presented
+in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
+pooled into a group of ``others'', leaving us with a total of n = 12 and
+n = 10\footnote{This number is likely to change upon finalizing the
+  spatial analysis of longliners, which is currently running.} spatially
+defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
+for purse seiners and longliners, respectively.
 
 To evaluate this change in effort allocation, we regress our variable of
-interest, fishing hours, on the interaction between a dummy variable
-indicating the policy intervention and a dummy variable for countries,
-to obtain the by-country change in proportional allocation of fishing
-effort:
+interest (\emph{i.e.}fishing hours) on the interaction between a dummy
+variable indicating the policy intervention and a dummy variable for
+countries. This gives us the by-country change in proportional
+allocation of fishing effort:
 
 \[
-y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 \]
@@
 for countries, interpreted as individual EEZs, the high seas, and a
-group of ``other EEZs''. Our parameter of interest is \(\beta_3\), which
-captures the country-level change in proportional fishing effort.
+group of ``other EEZs''. Our parameter of interest is \(\beta_{3,i}\),
+which captures the country-level change in proportional fishing effort.
 
@@
 and heteroskedastic-robust standard errors were calculated. All analyses
-were performed in R version 3.5.1) \citep{rcore_2018}. Raw data and code
+were performed in R version 3.5.1 \citep{rcore_2018}. Raw data and code
 used in this work are available on
@@
 
-\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}}
+\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
 \centering
@@
 Our data suggest that purseiners and longliners have different responses
-to the implementation of a Large-Scale Marine Protected Area. Fig.
+to the implementation of a Large-Scale Marine Protected Areas. Fig.
 \ref{fig:all_vessels} shows that mean fishing hours for purse seiners
 have an abrupt increase, just before January 1st, 2015. This trend is
-observed for both treated and control groups. Longliners, however, show
-a more stable trend. The number of mmsi codes increases through time.
-This can largely be explained by the addition of more satellites, which
-increase detectability of vessels. As expected, total fishing hours
-follow a similar trend to that of mmsi numbers.
+observed for both treated and control groups. The pattern closely
+corresponds with the increase in total hours, but the total number of
+vessels doesn't entirely follow this pattern. The increase in fishing
+hours might be caused by the increased number of satellites\footnote{Need
+  to check this. Not sure any satellites were incorporated during 2014.
+  It is also possible that PNA countries started enforcing the
+  requirement of having an AIS unit. On either case, both treatment and
+  control groups seem to be affected equally.}. Longliners, however,
+show no apparent trend with a clear seasonality
+\citep{ortuocrespo_2018}. The number of mmsi codes also increases
+slightly through time, but becomes stable after 2015. For both gears and
+across all measures, the treatment and control vessels follow similar
+patterns, confirming our claim that the control group provides a
+plausible counterfactual.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels. Vertical dashed line
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
+number of vessels by month for all vessels. Vertical dashed line
 indicates PIPA closure.}
@@
 and negative values for \(\mu_1\) and \(\mu_2\), the linear and
-cuadratic terms, respectively. These effectively represent the patterns
-observed in Figure \{fig:all\_vessels\}.
+cuadratic terms for \(Y_t\), respectively. These effectively represent
+the patterns observed in Figure \ref{fig:all_vessels}.
 
@@
 
-The change in the relative allocation fishing effort by purse seiners
-increases in eight of the 12 regions after PIPA implementation
-\ref{tab:disp_mod}. The largest increase is observed for the I-Kiribati
+The change in the relative allocation of fishing effort by purse seiners
+increases in eight of the 12 regions after PIPA implementation (Table
+\ref{tab:disp_mod}). The largest increase is observed for the I-Kiribati
 EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
+relative allocation of fishing effort by PIPA-fishing vessels before and
+after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
+representation of the mean change in the monthly allocation of fishing
+effort for purse seiners.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
-\caption{\label{fig:unnamed-chunk-19}\label{fig:map_change_ps}}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
+representation of the mean change in the monthly allocation of fishing
+effort for longliners. \textbf{This are preliminar results, contingent
+on the spatial analysis currently being run}}
 \end{figure}
@@
  \hline \\[-1.8ex] 
-Month FE & No \\ 
 Observations & 864 \\ 
@@
 
+\clearpage
+
 \section{Discusion}\label{discusion}
@@
 treated vessels to redeuce their fishing hours, and that this effect is
-greater for purse seiners. Even though treated vessels fish less, their
-relative allocation of fishing hours increased for all other fishing
-grouds. This fidnings does not imply that there is more fishing effort,
-but rather that each region receives a greater portion of the post-PIPA
-fishing effort (which is lower than pre-PIPA). In this section we
-discuss the implications of vessel-level reductions in fishing effort
-and the increase in relative allocation of the remaining effort through
-space. We also provide plausible explanations as to why purse seiners
-seem to be more reactive to the spatial closure.
+greater for purse seiners than longliners. Even though treated vessels
+fish less, their relative allocation of fishing hours increased for all
+other fishing grouds. This does not imply that there is more fishing
+effort exherted by treated vessels, but rather that each region receives
+a greater portion of the post-PIPA fishing effort of these same vessels,
+which is lower than pre-PIPA levels. In this section we discuss the
+implications of vessel-level reductions in fishing effort and the
+increase in relative allocation of the remaining effort through space.
+We also provide plausible explanations as to why purse seiners seem to
+be more reactive to the spatial closure.
 
@@
 distant places, which might be translated as increased costs
-\citep{stevenson_2013}. Nevertheless, this study does not use
-counterfactuals that could help account for system- or fleet-level
-changes that occur through time. Others have used similar
-satellite-tracking systems to show that fishing effort accumulates near
-the edges ospatial closures, yielding greater catches
-\citep{murawski_2005}. Yet, these vessel tracks do not cover the
-pre-reserve period, making it difficult identify the contribution of
-spatial closures to the observed spatial distribution of fishing
-vessels. Recent work by \citet{elahi_2018} identified that total fishing
-effort in a focal region where a short-term MPA was implemented showed
-little change, likely indicating that fishers redistributed fishing
-effort to compensate for the reduction in available space. Our data is
-assambled in a similar way, with fishing positions before and after the
-implementation of PIPA and vessels grouped into treated and control
-groups. Our BACI design, along with our difference-in-differences
-analysis allows us to make causal inferences about the effect that large
-scale marine protected areas have on fishing effort.
+\citep{stevenson_2013}. Nevertheless, they do not use counterfactuals
+that could help account for system- or fleet-level changes that occur
+through time. Others have used similar satellite-tracking systems to
+show that fishing effort accumulates near the edges ospatial closures,
+yielding greater catches \citep{murawski_2005}. Yet, these vessel tracks
+do not cover the pre-reserve period, making it difficult identify the
+contribution of spatial closures to the observed spatial distribution of
+fishing vessels. Recent work by \citet{elahi_2018} identified that total
+fishing effort in a focal region where a short-term MPA was implemented
+showed little change, likely indicating that fishers redistributed
+fishing effort to compensate for the reduction in available space. Our
+data is assambled in a similar way, with fishing positions before and
+after the implementation of PIPA and vessels grouped into treated and
+control groups. Our BACI design, along with our
+difference-in-differences analysis allows us to make causal inferences
+about the effect that large scale marine protected areas have on fishing
+effort.
+
+A major shortcomming of our analyses is that we do not observe catches
+or revenues, which ultimately are the factors that guide the decission
+making process of profit-maximizing agents. \textbf{Expandir aqui}
 
@@
 of each fishing gear. Purse seiners are often constrained by seafloor
-and termocline depth, and often operate in more restricted areas
+and termocline depth, and have a smaller spatial footpring
 \citep{kroodsma_2018}. Tuna purse seiners are known to have greater
@@
 ocean, meaning that they can easily redistribute elsewhere.
+\textbf{Further research shoudl focus on identifying the implications.
+So what? What happens?}
 
-\section{References}\label{references}
-
-\hypertarget{refs}{}
+Que mas dice Elahi o Wizaka (fishing the line) en su discusion? Que
+aportes tiene este trabajo????
 
@@
 
+\clearpage
+
 \bibliography{references.bib}

### 2018-09-29 rmd/Manuscript.Rmd
Added changes after proof reading, waiting for spatial analysis to be done before sending it out to John

@@
 
-\clearpage
+# Introduction
 
-# Introduction
+Mpas are being implemented like crazy
+
+Debate on LSMPA the devil you know
+
+Where do vessels go is the key part of it
 
@@
 This section is divided into two main parts.
-First, we provide a general description of AIS data and the process of identification of vessel-level events done by Global Fishing Watch[^1].
+First, we provide a general description of AIS data and the process of identification of vessel-level fishing events done by Global Fishing Watch[^1].
 Alongside, we describe the subset of data that we use for these analyses.
 When relevant, we also point out possible shortcommings in the data, or factors that must be considered in the later analyses.
-Then we move on to explain our identification strategy, and the main analyses that we undertake.
+We then move on to explain our empirical strategy for the identification of the behaviorial changes and redistribution of fishing effort.
 
@@
 
-### AIS data
-
-Automatic Identification Systems are on-board devices intended to provide at-sea saftey and prevent ship collisions by broadcasting vessel locations to surrounding vessels.
-These broadcasted positions can be recorded by satellites and land-based antenas.
+Automatic Identification Systems are on-board devices intended to provide at-sea saftey and prevent ship collisions by broadcasting vessel position, course, and activities to surrounding vessels.
+These broadcasted messages can be received by satellites and land-based antenas.
 GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally since 2012 \citep{kroodsma_2018}.
-The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points) and therefore fishing hours.
+Our data contain information for 2012 - 2017.
+The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points), and therefore number of vessels and fishing hours.
 The variability in AIS data and ocean conditions require that temporal trends be taken into account.
-We do that by incorporating a series of controls, which are defined in the following section.
-
-### PIPA data
+We do that by obtaining a subset of data that meet a BACI design, which gives us the full tracks for vessels affected and unaffected by the implementation of PIPA.
 
@@
 
-Our data contain over 45 million individual AIS messages for 371 purse seiners and longliners.
+Our data contain over 45 million individual AIS messages (*i.e.* positions) for 371 purse seiners and longliners.
 A total of 233 vessels have fished within PIPA waters; 217 did so at least once before 2015.
 However, not all vessels continued to fish elsewhere after PIPA implementation: 34 vessels have no recorded AIS messages after 2015[^2], leaving us with `r pipa_vessels` vessels that fished inside PIPA before its implementation, and continued to fish elsewhere afterward.
-Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period.
 New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period.
-Therefore, we define our treatment and control groups as follows.
+To account for this, we identify a subset of vessels which we track since before the implementation of PIPA, and categorize them as treated or control vessels.
+Our treatment and control groups are defined as follows.
 
 The treatment group contains all vessels (n = `r pipa_vessels`) that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
-Vessels in the control group meet al three of the following conditions: i) Vessels never fished within PIPA waters, ii) vessels belong to other PNA countries, and iii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
+Vessels in the control group meet all three of the following conditions: i) vessels never fished within PIPA waters, ii) vessels belong to other PNA countries, and iii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
 For each vessel meeting these characteristics, we calculate their total monthly fishing hours.
-Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level streams of fishing events that make up each group through time.
-Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show the number of vessels following a BACI design, and fishing hours, respectively.
-Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after).
-The relative change in fishing hours (After / Before) is also shown.
+Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level fishing events that make up each group through time.
+Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
 
@@
 
-[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmiters.
+[^2]: The 34 missing vessels might have exited the fishery, been decomissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmiters.
 In either case, we are not able to observe these.
@@
 ```{r, fig.width = 8, fig.height = 6, fig.cap = "\\label{fig:baci_strict}Stream of fishing events by vessels through time.
-Each line represents a vessel, with dots indicating months with fishing activity and colors indicating the pre and post periods.
-Pannels separating between gear and treated or control groups."}
+Each line represents a vessel, with dots indicating months with fishing activity and colors indicating the pre and post periods."}
 filter(effort_by_vessel, baci_strict) %>% 
@@
 ```{r}
+hours <- effort_by_vessel %>%
+  filter(baci_strict) %>%
+  group_by(gear, treated, post) %>% 
+  summarize(hours = mean(hours, na.rm = T)) %>% 
+  spread(post, hours) %>% 
+  mutate(change = `TRUE` / `FALSE`)
+
 effort_by_vessel %>% 
@@
   summarize(boats = n()) %>% 
-  knitr::kable(col.names = c("Gear", "Treatment", "n"),
-               caption = "\\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.",
-               booktabs = T) %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
-
-```{r}
-effort_by_vessel %>%
-  filter(baci_strict) %>%
-  group_by(gear, treated, post) %>% 
-  summarize(hours = mean(hours, na.rm = T)) %>% 
-  spread(post, hours) %>% 
-  mutate(change = `TRUE` / `FALSE`) %>% 
-  knitr::kable(col.names = c("Gear", "Treatment", "Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.",
+  left_join(hours, by = c("gear", "treated")) %>% 
+  knitr::kable(col.names = c("Gear", "Treatment", "n" ,"Before", "After", "Change (A / B)"),
+               caption = "\\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.",
                booktabs = T) %>% 
@@
 Where $y_{i,t}$ is the variable of interest for vessel $i$ in time period $t$.
-A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation.
+A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation.
 $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group.
-$\alpha$ is the standard intercept, $\beta_1$ captures the *ex post* change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\mu_1$ and $\mu_2$ are coefficients for a second order polynomial for years ($Y_t$)[^4], while $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions.
+$\alpha$ is the standard intercept, $\beta_1$ captures the temporal trend change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
+Finally, $\mu_1$ and $\mu_2$ are coefficients for a second order polynomial for years ($Y_t$), while $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions[^4].
 
@@
 
-[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendx.
+[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendx, but are similar to the ones found under current specification.
 
@@
 We calculate the monthly relative distribution of fishing hours by all treated vessels across all fished EEZs and the high seas.
-These trends are shown in Figures \ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the relative change is presented in Table \ref{tab:ba_disp}.
-EEZs that had sproadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country[displacement_data$gear == "purse_seines"]))` and n = `r length(unique(displacement_data$country[!displacement_data$gear == "purse_seines"]))` spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs") for purse seiners and longliners, respectively.
+These trends are shown in Figure \ref{fig:redist_trend_ps}, and the relative temporal change is presented in Table \ref{tab:ba_disp}.
+EEZs that had sporadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country[displacement_data$gear == "purse_seines"]))` and n = `r length(unique(displacement_data$country[!displacement_data$gear == "purse_seines"]))`[^5] spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs", and PIPA) for purse seiners and longliners, respectively.
 
-To evaluate this change in effort allocation, we regress our variable of interest, fishing hours, on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries, to obtain the by-country change in proportional allocation of fishing effort:
+[^5]: This number is likely to change upon finalizing the spatial analysis of longliners, which is currently running.
+
+To evaluate this change in effort allocation, we regress our variable of interest (*i.e.*fishing hours) on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries.
+This gives us the by-country change in proportional allocation of fishing effort:
 
 $$
-y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 $$
@@
 $Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs".
-Our parameter of interest is $\beta_3$, which captures the country-level change in proportional fishing effort.
+Our parameter of interest is $\beta_{3,i}$, which captures the country-level change in proportional fishing effort.
 
@@
 All regression coefficients were estimatedd via ordinary least squares, and heteroskedastic-robust standard errors were calculated.
-All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")`) \citep{rcore_2018}.
+All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
 Raw data and code used in this work are available on [github](https://github.com/jcvdav/MPA_displacement).
@@
                booktabs = T,
-               caption = "\\label{tab:ba_disp}") %>% 
+               caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-Our data suggest that purseiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Area.
+Our data suggest that purseiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Areas.
 Fig.
@@
 This trend is observed for both treated and control groups.
-Longliners, however, show a more stable trend.
-The number of mmsi codes increases through time.
-This can largely be explained by the addition of more satellites, which increase detectability of vessels.
-As expected, total fishing hours follow a similar trend to that of mmsi numbers.
+The pattern closely corresponds with the increase in total hours, but the total number of vessels doesn't entirely follow this pattern.
+The increase in fishing hours might be caused by the increased number of satellites[^6].
+Longliners, however, show no apparent trend with a clear seasonality \citep{ortuocrespo_2018}.
+The number of mmsi codes also increases slightly through time, but becomes stable after 2015.
+For both gears and across all measures, the treatment and control vessels follow similar patterns, confirming our claim that the control group provides a plausible counterfactual.
+
+[^6]: Need to check this.
+Not sure any satellites were incorporated during 2014.
+It is also possible that PNA countries started enforcing the requirement of having an AIS unit.
+On either case, both treatment and control groups seem to be affected equally.
 
@@
 This result is robust and significant (*p < 0.05*) for all model specifications, with the effect varying between $\beta_3 = -16.457$ and $\beta_3 = -18.709$.
-Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and cuadratic terms, respectively.
-These effectively represent the patterns observed in Figure {fig:all_vessels}.
+Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and cuadratic terms for $Y_t$, respectively.
+These effectively represent the patterns observed in Figure \ref{fig:all_vessels}.
 
@@
 
-The change in the relative allocation fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation \ref{tab:disp_mod}.
+The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}).
 The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*).
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend_ps}"}
+```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'."}
 displacement_data %>% 
@@
 
-```{r, fig.cap = "\\label{fig:map_change_ps}"}
+```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
 pipa_map_ba_disp <- pipa %>% 
@@
 
-```{r, fig.cap = "\\label{fig:map_change_ps}"}
+```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for longliners.
+**This are preliminar results, contingent on the spatial analysis currently being run**"}
 pipa_map_ba_disp <- pipa %>% 
@@
                      omit.stat = c("adj.rsq", "f", "ser"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes")),
                      header = F,
@@
 
+\clearpage
+
 # Discusion
@@
 Our findings provide interesting insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
-These collection of results shows that the implementation of PIPA caused treated vessels to redeuce their fishing hours, and that this effect is greater for purse seiners.
+These collection of results shows that the implementation of PIPA caused treated vessels to redeuce their fishing hours, and that this effect is greater for purse seiners than longliners.
 Even though treated vessels fish less, their relative allocation of fishing hours increased for all other fishing grouds.
-This fidnings does not imply that there is more fishing effort, but rather that each region receives a greater portion of the post-PIPA fishing effort (which is lower than pre-PIPA).
+This does not imply that there is more fishing effort exherted by treated vessels, but rather that each region receives a greater portion of the post-PIPA fishing effort of these same vessels, which is lower than pre-PIPA levels.
 In this section we discuss the implications of vessel-level reductions in fishing effort and the increase in relative allocation of the remaining effort through space.
@@
 Previous studies on insular environments suggest that vessels move to distant places, which might be translated as increased costs \citep{stevenson_2013}.
-Nevertheless, this study does not use counterfactuals that could help account for system- or fleet-level changes that occur through time.
+Nevertheless, they do not use counterfactuals that could help account for system- or fleet-level changes that occur through time.
 Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges ospatial closures, yielding greater catches \citep{murawski_2005}.
@@
 
+A major shortcomming of our analyses is that we do not observe catches or revenues, which ultimately are the factors that guide the decission making process of profit-maximizing agents.
+**Expandir aqui**
+
 The different responses observed between purse seiners and longliners might have two possible explanations.
@@
 Alternatively, the differences may be due to the nature of each fishing gear.
-Purse seiners are often constrained by seafloor and termocline depth, and often operate in more restricted areas \citep{kroodsma_2018}.
+Purse seiners are often constrained by seafloor and termocline depth, and have a smaller spatial footpring \citep{kroodsma_2018}.
 Tuna purse seiners are known to have greater proportion of null sets (*i.e.* where the purse seine is effectively casted arround tuna, but no catch is obtained) during El Niño years, where the termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}.
@@
 \citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be underutilizing the ocean, meaning that they can easily redistribute elsewhere.
+**Further research shoudl focus on identifying the implications.
+So what?
+What happens?**
+
+Que mas dice Elahi o Wizaka (fishing the line) en su discusion? Que aportes tiene este trabajo????
 
@@
 <!-- Additionally, run similar regressions on distance traveled, and total vessel hours (not just fishing hours), that could account for the extended "search" time. -->
-
-<div id = "refs"> </div>
 
@@
 ```
+
+\clearpage

### 2018-09-29 docs/Manuscript.tex
Updated manuscript, ready for John

@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-09-28}
+  \subtitle{Updated on 2018-09-29}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 
-Mpas are being implemented like crazy
+Marine Protected Areas (MPAs) are intended to safeguard parts of the
+ocean from extractive activities such as fishing. Current international
+goals aim to ``effectively protect 10\% of the ocean environments by
+2020''. In an effort to meet this target, the world has seen a rapid
+increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
+part of this rapid increase can be attributed to the designation of a
+small number of Large Scale Marine Protected Areas {[}LSMPAs;
+\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
+km\textsuperscript{2} \citep{toonen_2013} in extension, and are often
+implemented in the pelagic environment, where the dominant human
+activity is industrial fishing \citep{gray_2017}.
 
-Debate on LSMPA the devil you know
+Due to weak property rights, limited habitat transformation, and
+potentially lower management costs, pelagic MPAs provide a great
+opportunity to safeguard the oceans \citet{game_2009}{[}\^{}d{]}. A
+growing body of literature has also shown that closing the high seas to
+all fishing -effectively, turning them into a LSMPA- could increase
+fishery yields and profitability of fisheries, without negligible costs
+to food security
+\citep{white_2014,sumaila_2015,sala_2018,schiller_2018}. However, as
+with customary MPAs, it is important that we understand the
+socioeconomic implications of management interventions.
 
-Where do vessels go is the key part of it
+Given the relatively recent establishment of most LSMPAs, very little is
+known about their human dimensions and implication for fisheries
+\citep{gray_2017}. LSMPAs were erroneously assumed to have little social
+implications due to their remoteness \citep{agardy_2011,gray_2017}.
+However, the anticipation of a LSMPA can lead to preemptive overfishing,
+which can erode or delay the expected benefits of the intervention
+\citep{mcdermott_2018}. LSMPAs have received great attention in terms of
+governance and enforcement, but are yet to be the focus of economic
+analyses \citep{gray_2017}. For example, \citet{mcdermott_2018} show
+that fishing effort within the Phoenix Islands Marine Protected Area
+(PIPA) is effectively reduced after implementation, and describe changes
+in fishing behavior pre-implementation. \citet{cabral_2017} analyse the
+redistribution of fishing and non-fishing vessels following the
+implementation of MPAs in California, and find that responses are
+idiosyncratic; commercial dive boats follow a fishing-the-line pattern,
+while some fishing boats follow an ideal free distribution. The way in
+which fishers react to a spatial closure can have major implications in
+its outcome \citep{hilborn_2006,krueck_2017,viana_2017}. This highlights
+the need to understand how fishers react to the implementation of a
+LSMPA, and fishing effort changes and is spatially redistributed.
 
-This work identifies the behavioral changes of fishing vessels due to
-the implementation of PIPA. Not only can we identify temporal changes in
-fishing patterns (\emph{i.e.} time and distance), but also spatial
-patterns. Our vessel-level tracks allow us to see where PIPA-fishing
-vessels go after the closure, providing empirical insights about the
-redistribution of fishing effort after the implementaion of a MPA.
+The main objective of this paper is to identify how fishers adapt to the
+implementation of LSMPAs. We combine novel vessel tracking technologies
+and causal inference techniques to identify behavioral changes of
+fishing vessels due to the implementation of PIPA. We focus on fishing
+hours and distance traveled as outcome variables that fishers might
+adjust following implementation of a LSMPA in an impact-evaluation
+fashion. Additionally, we evaluate the spatial redistribution of fishing
+effort that existed within PIPA before its implementation. This work
+provides novel empirical insights into fisher's responses to the
+implementation of LSMPAs, and can help guide future interventions.
 
@@
 the subset of data that we use for these analyses. When relevant, we
-also point out possible shortcommings in the data, or factors that must
+also point out possible shortcomings in the data, or factors that must
 be considered in the later analyses. We then move on to explain our
-empirical strategy for the identification of the behaviorial changes and
+empirical strategy for the identification of the behavioral changes and
 redistribution of fishing effort.
@@
 Automatic Identification Systems are on-board devices intended to
-provide at-sea saftey and prevent ship collisions by broadcasting vessel
+provide at-sea safety and prevent ship collisions by broadcasting vessel
 position, course, and activities to surrounding vessels. These
 broadcasted messages can be received by satellites and land-based
-antenas. GFW uses a neural network to infer vessel characteristics and
+antennas. GFW uses a neural network to infer vessel characteristics and
 whether each broadcasted position represents a fishing event, thus
@@
 2015\footnote{The 34 missing vessels might have exited the fishery, been
-  decomissioned or sold (therefore changing their AIS and mmsi), or
-  turned off their AIS transmiters. In either case, we are not able to
+  decommissioned or sold (therefore changing their AIS and mmsi), or
+  turned off their AIS transmitters. In either case, we are not able to
   observe these.}, leaving us with 183 vessels that fished inside PIPA
@@
 
+\clearpage
+
 \subsection{Analysis}\label{analysis}
@@
 period \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
-dates prior to PIPA implementation and a value of 1 por all dates
+dates prior to PIPA implementation and a value of 1 for all dates
 including and following PIPA implementation. \(Treat_i\) is a dummy
@@
   earlier specification included years as a dummy variable. Such results
-  are included in the appendx, but are similar to the ones found under
+  are included in the appendix, but are similar to the ones found under
   current specification.}.
@@
 
-All regression coefficients were estimatedd via ordinary least squares,
+All regression coefficients were estimated via ordinary least squares,
 and heteroskedastic-robust standard errors were calculated. All analyses
@@
 
-Our data suggest that purseiners and longliners have different responses
-to the implementation of a Large-Scale Marine Protected Areas. Fig.
-\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
-have an abrupt increase, just before January 1st, 2015. This trend is
-observed for both treated and control groups. The pattern closely
-corresponds with the increase in total hours, but the total number of
-vessels doesn't entirely follow this pattern. The increase in fishing
-hours might be caused by the increased number of satellites\footnote{Need
-  to check this. Not sure any satellites were incorporated during 2014.
-  It is also possible that PNA countries started enforcing the
-  requirement of having an AIS unit. On either case, both treatment and
-  control groups seem to be affected equally.}. Longliners, however,
-show no apparent trend with a clear seasonality
+Our data suggest that purse seiners and longliners have different
+responses to the implementation of a Large-Scale Marine Protected Areas.
+Fig. \ref{fig:all_vessels} shows that mean fishing hours for purse
+seiners have an abrupt increase, just before January 1st, 2015. This
+trend is observed for both treated and control groups. The pattern
+closely corresponds with the increase in total hours, but the total
+number of vessels doesn't entirely follow this pattern. The increase in
+fishing hours might be caused by the increased number of
+satellites\footnote{Need to check this. Not sure any satellites were
+  incorporated during 2014. It is also possible that PNA countries
+  started enforcing the requirement of having an AIS unit. On either
+  case, both treatment and control groups seem to be affected equally.}.
+Longliners, however, show no apparent trend with a clear seasonality
 \citep{ortuocrespo_2018}. The number of mmsi codes also increases
@@
 
-Our DiD anaylsis shows that treated purse seiners reduce their fishing
+Our DiD analysis shows that treated purse seiners reduce their fishing
 effort after PIPA implementation in the order of 16 hours per month.
@@
 and negative values for \(\mu_1\) and \(\mu_2\), the linear and
-cuadratic terms for \(Y_t\), respectively. These effectively represent
+quadratic terms for \(Y_t\), respectively. These effectively represent
 the patterns observed in Figure \ref{fig:all_vessels}.
@@
 track fishing vessels that belong to the treated group. In this case, we
-calculate the prportion of fishing effort allocated every month to each
+calculate the proportion of fishing effort allocated every month to each
 spatially explicit region outlined by EEZs and the high seas. For purse
@@
 relative fishing hours that each region received by all 183 treated
-vessels. The top-left pannel shows the change in fishing effort inside
-PIPA, including the preemtive fishing and immediate reduction previously
-reported \citep{mcdermott_2018}.
+vessels. The top-left panel shows the change in fishing effort inside
+PIPA, including the preemptive fishing and immediate reduction
+previously reported \citep{mcdermott_2018}.
 
@@
 These collection of results shows that the implementation of PIPA caused
-treated vessels to redeuce their fishing hours, and that this effect is
+treated vessels to reduce their fishing hours, and that this effect is
 greater for purse seiners than longliners. Even though treated vessels
 fish less, their relative allocation of fishing hours increased for all
-other fishing grouds. This does not imply that there is more fishing
-effort exherted by treated vessels, but rather that each region receives
+other fishing grounds. This does not imply that there is more fishing
+effort exerted by treated vessels, but rather that each region receives
 a greater portion of the post-PIPA fishing effort of these same vessels,
@@
 
+A major shortcoming of our analyses is that we do not observe catches or
+revenues, which ultimately are the factors that guide the decision
+making process of profit-maximizing agents. Therefore, it is difficult
+to know whether the reduction in fishing effort represents a positive or
+negative impact. A decrease in fishing effort is associated to an
+increase in catches (and therefore greater CPUE) only when the entire
+fleet does it, and if previous levels of effort were greater than
+\(F_{MEY}\) (\emph{i.e.} the effort that would yield the maximum
+economic yield). Therefore, it is plausible that the reduction of
+fishing hours is not done by choice, but rather results from fishers
+having to increase search time. Upon being relocated, fishers may not
+identify the best fishing grounds as easily as before, and therefore
+invest a greater proportion of their time searching for their catch.
+Further analysis of temporal trends in non-fishing hours, as well as
+distance traveled should provide us with insights as to why fishers
+reduced fishing hours.
+
 Previous studies on insular environments suggest that vessels move to
@@
 through time. Others have used similar satellite-tracking systems to
-show that fishing effort accumulates near the edges ospatial closures,
+show that fishing effort accumulates near the edges of spatial closures,
 yielding greater catches \citep{murawski_2005}. Yet, these vessel tracks
@@
 fishing effort to compensate for the reduction in available space. Our
-data is assambled in a similar way, with fishing positions before and
+data is assembled in a similar way, with fishing positions before and
 after the implementation of PIPA and vessels grouped into treated and
@@
 effort.
-
-A major shortcomming of our analyses is that we do not observe catches
-or revenues, which ultimately are the factors that guide the decission
-making process of profit-maximizing agents. \textbf{Expandir aqui}
 
@@
 of each fishing gear. Purse seiners are often constrained by seafloor
-and termocline depth, and have a smaller spatial footpring
+and termocline depth, and have a smaller spatial footprint
 \citep{kroodsma_2018}. Tuna purse seiners are known to have greater
-proportion of null sets (\emph{i.e.} where the purse seine is
-effectively casted arround tuna, but no catch is obtained) during El
-Niño years, where the termocline deepens in the Eastern Pacific
-\citep{dreyfusleon_2015}. On the other hand, longliners may be more
-flexible as to where they can deploy their longlines.
-\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic
-longline fleet, and suggest that the fleet may be underutilizing the
-ocean, meaning that they can easily redistribute elsewhere.
-\textbf{Further research shoudl focus on identifying the implications.
-So what? What happens?}
+proportion of null sets (\emph{i.e.} where purse seines effectively cast
+their nets, but no catch is obtained) during El Niño years, where the
+termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}. On
+the other hand, longliners may be more flexible as to where they can
+deploy their longlines. \citet{ortuocrespo_2018} evaluated the
+ecological niche of the pelagic longline fleet, and suggest that the
+fleet may be under-utilizing the ocean, meaning that they can easily
+redistribute elsewhere.
 
-Que mas dice Elahi o Wizaka (fishing the line) en su discusion? Que
-aportes tiene este trabajo????
+Our work suggests that the implementation of LSMPAs can have important
+implications for purse seiners, and less so for longliners. We also show
+that fishing effort is redistributed to areas close by. Future
+management interventions that aim to close large portion of the oceans
+should consider how fishing effort will change in space and through
+time, and the ecological implications of this redistribution to ensure
+that fishing effort is not just displaced elsewhere, leading to
+overfishing in adjacent waters.
 

### 2018-09-29 rmd/Manuscript.Rmd
Updated manuscript, ready for John

@@
 
-Mpas are being implemented like crazy
+Marine Protected Areas (MPAs) are intended to safeguard parts of the ocean from extractive activities such as fishing.
+Current international goals aim to "effectively protect 10\% of the ocean environments by 2020".
+In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018b}.
+A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas [LSMPAs; \citep{gray_2017}].
+These are defined as MPAS with at least 250,000 km^2^ \citep{toonen_2013} in extension, and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{gray_2017}.
 
-Debate on LSMPA the devil you know
+Due to weak property rights, limited habitat transformation, and potentially lower management costs, pelagic MPAs provide a great opportunity to safeguard the oceans \citet{game_2009}[^d].
+A growing body of literature has also shown that closing the high seas to all fishing -effectively, turning them into a LSMPA- could increase fishery yields and profitability of fisheries, without negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018,schiller_2018}.
+However, as with customary MPAs, it is important that we understand the socioeconomic implications of management interventions.
 
-Where do vessels go is the key part of it
+Given the relatively recent establishment of most LSMPAs, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
+LSMPAs were erroneously assumed to have little social implications due to their remoteness \citep{agardy_2011,gray_2017}.
+However, the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention \citep{mcdermott_2018}.
+LSMPAs have received great attention in terms of governance and enforcement, but are yet to be the focus of economic analyses \citep{gray_2017}.
+For example, \citet{mcdermott_2018} show that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) is effectively reduced after implementation, and describe changes in fishing behavior pre-implementation.
+\citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of MPAs in California, and find that responses are idiosyncratic; commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
+The way in which fishers react to a spatial closure can have major implications in its outcome \citep{hilborn_2006,krueck_2017,viana_2017}.
+This highlights the need to understand how fishers react to the implementation of a LSMPA, and fishing effort changes and is spatially redistributed.
 
-This work identifies the behavioral changes of fishing vessels due to the implementation of PIPA.
-Not only can we identify temporal changes in fishing patterns (*i.e.* time and distance), but also spatial patterns.
-Our vessel-level tracks allow us to see where PIPA-fishing vessels go after the closure, providing empirical insights about the redistribution of fishing effort after the implementaion of a MPA.
+The main objective of this paper is to identify how fishers adapt to the implementation of LSMPAs.
+We combine novel vessel tracking technologies and causal inference techniques to identify behavioral changes of fishing vessels due to the implementation of PIPA.
+We focus on fishing hours and distance traveled as outcome variables that fishers might adjust following implementation of a LSMPA in an impact-evaluation fashion.
+Additionally, we evaluate the spatial redistribution of fishing effort that existed within PIPA before its implementation.
+This work provides novel empirical insights into fisher's responses to the implementation of LSMPAs, and can help guide future interventions.
 
@@
 Alongside, we describe the subset of data that we use for these analyses.
-When relevant, we also point out possible shortcommings in the data, or factors that must be considered in the later analyses.
-We then move on to explain our empirical strategy for the identification of the behaviorial changes and redistribution of fishing effort.
+When relevant, we also point out possible shortcomings in the data, or factors that must be considered in the later analyses.
+We then move on to explain our empirical strategy for the identification of the behavioral changes and redistribution of fishing effort.
 
@@
 
-Automatic Identification Systems are on-board devices intended to provide at-sea saftey and prevent ship collisions by broadcasting vessel position, course, and activities to surrounding vessels.
-These broadcasted messages can be received by satellites and land-based antenas.
+Automatic Identification Systems are on-board devices intended to provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activities to surrounding vessels.
+These broadcasted messages can be received by satellites and land-based antennas.
 GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally since 2012 \citep{kroodsma_2018}.
@@
 
-[^2]: The 34 missing vessels might have exited the fishery, been decomissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmiters.
+[^2]: The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
 In either case, we are not able to observe these.
@@
 
+\clearpage
+
 ## Analysis
@@
 Where $y_{i,t}$ is the variable of interest for vessel $i$ in time period $t$.
-A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation.
+A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates including and following PIPA implementation.
 $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group.
@@
 
-[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendx, but are similar to the ones found under current specification.
+[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendix, but are similar to the ones found under current specification.
 
@@
 
-All regression coefficients were estimatedd via ordinary least squares, and heteroskedastic-robust standard errors were calculated.
+All regression coefficients were estimated via ordinary least squares, and heteroskedastic-robust standard errors were calculated.
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
@@
 
-Our data suggest that purseiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Areas.
+Our data suggest that purse seiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Areas.
 Fig.
@@
 
-Our DiD anaylsis shows that treated purse seiners reduce their fishing effort after PIPA implementation in the order of 16 hours per month.
+Our DiD analysis shows that treated purse seiners reduce their fishing effort after PIPA implementation in the order of 16 hours per month.
 This result is robust and significant (*p < 0.05*) for all model specifications, with the effect varying between $\beta_3 = -16.457$ and $\beta_3 = -18.709$.
-Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and cuadratic terms for $Y_t$, respectively.
+Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and quadratic terms for $Y_t$, respectively.
 These effectively represent the patterns observed in Figure \ref{fig:all_vessels}.
@@
 Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.
-In this case, we calculate the prportion of fishing effort allocated every month to each spatially explicit region outlined by EEZs and the high seas.
+In this case, we calculate the proportion of fishing effort allocated every month to each spatially explicit region outlined by EEZs and the high seas.
 For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs.
 Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels.
-The top-left pannel shows the change in fishing effort inside PIPA, including the preemtive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
+The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
 
@@
 Our findings provide interesting insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
-These collection of results shows that the implementation of PIPA caused treated vessels to redeuce their fishing hours, and that this effect is greater for purse seiners than longliners.
-Even though treated vessels fish less, their relative allocation of fishing hours increased for all other fishing grouds.
-This does not imply that there is more fishing effort exherted by treated vessels, but rather that each region receives a greater portion of the post-PIPA fishing effort of these same vessels, which is lower than pre-PIPA levels.
+These collection of results shows that the implementation of PIPA caused treated vessels to reduce their fishing hours, and that this effect is greater for purse seiners than longliners.
+Even though treated vessels fish less, their relative allocation of fishing hours increased for all other fishing grounds.
+This does not imply that there is more fishing effort exerted by treated vessels, but rather that each region receives a greater portion of the post-PIPA fishing effort of these same vessels, which is lower than pre-PIPA levels.
 In this section we discuss the implications of vessel-level reductions in fishing effort and the increase in relative allocation of the remaining effort through space.
 We also provide plausible explanations as to why purse seiners seem to be more reactive to the spatial closure.
+
+A major shortcoming of our analyses is that we do not observe catches or revenues, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
+Therefore, it is difficult to know whether the reduction in fishing effort represents a positive or negative impact.
+A decrease in fishing effort is associated to an increase in catches (and therefore greater CPUE) only when the entire fleet does it, and if previous levels of effort were greater than $F_{MEY}$ (*i.e.* the effort that would yield the maximum economic yield).
+Therefore, it is plausible that the reduction of fishing hours is not done by choice, but rather results from fishers having to increase search time.
+Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch.
+Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours.
 
@@
 Nevertheless, they do not use counterfactuals that could help account for system- or fleet-level changes that occur through time.
-Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges ospatial closures, yielding greater catches \citep{murawski_2005}.
+Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges of spatial closures, yielding greater catches \citep{murawski_2005}.
 Yet, these vessel tracks do not cover the pre-reserve period, making it difficult identify the contribution of spatial closures to the observed spatial distribution of fishing vessels.
 Recent work by \citet{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space.
-Our data is assambled in a similar way, with fishing positions before and after the implementation of PIPA and vessels grouped into treated and control groups.
+Our data is assembled in a similar way, with fishing positions before and after the implementation of PIPA and vessels grouped into treated and control groups.
 Our BACI design, along with our difference-in-differences analysis allows us to make causal inferences about the effect that large scale marine protected areas have on fishing effort.
-
-A major shortcomming of our analyses is that we do not observe catches or revenues, which ultimately are the factors that guide the decission making process of profit-maximizing agents.
-**Expandir aqui**
 
@@
 Alternatively, the differences may be due to the nature of each fishing gear.
-Purse seiners are often constrained by seafloor and termocline depth, and have a smaller spatial footpring \citep{kroodsma_2018}.
-Tuna purse seiners are known to have greater proportion of null sets (*i.e.* where the purse seine is effectively casted arround tuna, but no catch is obtained) during El Niño years, where the termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}.
+Purse seiners are often constrained by seafloor and termocline depth, and have a smaller spatial footprint \citep{kroodsma_2018}.
+Tuna purse seiners are known to have greater proportion of null sets (*i.e.* where purse seines effectively cast their nets, but no catch is obtained) during El Niño years, where the termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}.
 On the other hand, longliners may be more flexible as to where they can deploy their longlines.
-\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be underutilizing the ocean, meaning that they can easily redistribute elsewhere.
-**Further research shoudl focus on identifying the implications.
-So what?
-What happens?**
+\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be under-utilizing the ocean, meaning that they can easily redistribute elsewhere.
 
-Que mas dice Elahi o Wizaka (fishing the line) en su discusion? Que aportes tiene este trabajo????
+Our work suggests that the implementation of LSMPAs can have important implications for purse seiners, and less so for longliners.
+We also show that fishing effort is redistributed to areas close by.
+Future management interventions that aim to close large portion of the oceans should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
 

### 2018-10-03 rmd/Manuscript.Rmd
Updated displacement data scritps

@@
 Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
-date: "^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA\\newline^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI"
+date: "
+^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA\\newline
+^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI"
 output:
@@
 A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas [LSMPAs; \citep{gray_2017}].
-These are defined as MPAS with at least 250,000 km^2^ \citep{toonen_2013} in extension, and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{gray_2017}.
+These are defined as MPAS with at least 250,000 km^2^ in extension \citep{toonen_2013}, and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{gray_2017}.
 

### 2018-10-03 scripts/displacement_data.R

@@ -1,96 +1,6 @@
-library(startR)
-library(magrittr)
-library(sf)
-library(tidyverse)
 
-# Custom functions that should be part of startR
-source(here::here("scripts", "st_rotate.R"))
-source(here::here("scripts", "sfc_as_cols.R"))
-
-vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds"))
-
-country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "HS")
-
-eez <- read_sf(dsn = here::here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
-  filter(ISO_Ter1 %in% unique(vessel_tracks$eez_iso3)) %>% 
-  mutate(PNA = ISO_Ter1 %in% c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV")) %>% 
-  st_rotate()
-
-pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
-                layer = "PIPA") %>% 
-  mutate(inside = T) %>% 
-  select(inside) %>% 
-  st_rotate()
-
-# Cuales estan dentro de PIPA
-
-ps <- vessel_tracks %>% 
-  filter(gear == "purse_seines",
-         treated,
-         fishing) %>% 
-  st_as_sf(coords = c(7, 8), crs = "+proj=longlat +datum=WGS84 +no_defs") %>%
-  st_rotate() %>% 
-  st_join(pipa) %>% 
-  sfc_as_cols(names = c("lon", "lat")) %>% 
-  st_set_geometry(value = NULL) %>%
-  mutate(country = ifelse(is.na(eez_iso3), "HS", eez_iso3),
-         country = ifelse(eez_iso3 %in% country_groups, eez_iso3, "others"),
-         country = ifelse(is.na(inside), country, "PIPA")) %>%
-  group_by(year, month) %>% 
-  mutate(total_hours = sum(hours)) %>% 
-  ungroup() %>% 
-  group_by(year, month, country, total_hours) %>%
-  summarize(h = sum(hours)) %>% 
-  mutate(h_prop = h / total_hours) %>% 
-  ungroup()
-
-displacement_data_ps <- expand.grid(country = c(unique(ps$country), "HS"),
-                                 year = 2012:2017,
-                                 month = 1:12) %>% 
-  arrange(country, year, month) %>%
-  as.tibble() %>%
[…]

### 2018-10-04 rmd/Manuscript.tex
Finally got the redistribution data ready. Will run spatial analyses tomorrow

--- 2018-09-29 docs/Manuscript.tex
@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-09-29}
+  \subtitle{Updated on 2018-10-03}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 University of California Santa Barbara, Santa Barbara,
-CA\newline\textsuperscript{2}Department of Economics, University of
+CA\newline \textsuperscript{2}Department of Economics, University of
 Hawaii at Manoa, Honolulu, HI}
+
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
 
@@
 
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 \citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
-km\textsuperscript{2} \citep{toonen_2013} in extension, and are often
+km\textsuperscript{2} in extension \citep{toonen_2013}, and are often
 implemented in the pelagic environment, where the dominant human
@@
 
-\section{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
-\subsection{Data}\label{data}
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
@@
 
-\subsection{Analysis}\label{analysis}
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
 
@@
 in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
-pooled into a group of ``others'', leaving us with a total of n = 12 and
-n = 10\footnote{This number is likely to change upon finalizing the
+pooled into a group of ``others'', leaving us with a total of n = 31 and
+n = 33\footnote{This number is likely to change upon finalizing the
   spatial analysis of longliners, which is currently running.} spatially
@@
 \midrule
-PIPA & -11.48 & -8.54\\
-KIR & 1.28 & 2.76\\
-HS & 0.00 & 0.00\\
-COK & 0.00 & 0.34\\
+PIPA & -6.68 & -8.54\\
+KIR & -8.14 & 2.76\\
+HS & 13.76 & 11.03\\
+ASM & 0.00 & -0.08\\
+CHN & 0.02 & 0.01\\
+\addlinespace
+COK & 0.32 & 0.34\\
+ECU & NA & 0.01\\
+FJI & 0.02 & 0.01\\
 FSM & 0.00 & 0.55\\
+GUM & NA & 0.00\\
 \addlinespace
-MHL & NA & -0.55\\
+JPN & -0.01 & 0.01\\
+KOR & 0.00 & 0.00\\
+MEX & NA & 0.00\\
+MHL & 0.00 & -0.55\\
+NIU & NA & 0.00\\
+\addlinespace
 NRU & 0.00 & 0.16\\
+NZL & NA & 0.59\\
+PAN & NA & 0.01\\
+PHL & NA & 0.00\\
 PNG & 0.00 & -10.02\\
-SLB & -8.48 & 2.13\\
-TKL & NA & 0.19\\
 \addlinespace
-TUV & 7.23 & 1.47\\
-others & 22.55 & 11.51\\
+PYF & 0.00 & 0.02\\
+SEN & NA & 0.01\\
+SLB & -3.00 & 2.13\\
+SYC & 0.06 & 0.07\\
+TKL & 0.00 & 0.19\\
+\addlinespace
+TON & 0.00 & 0.01\\
+TUV & 2.08 & 1.47\\
+TWN & 0.00 & 0.00\\
+UMI & 0.05 & -0.20\\
+WLF & 0.00 & 0.00\\
+\addlinespace
+WSM & NA & 0.04\\
+ATF & 0.00 & NA\\
+CHL & 0.00 & NA\\
+COM & 0.00 & NA\\
+GHA & 0.00 & NA\\
+\addlinespace
+MDG & -0.08 & NA\\
+MNP & 0.00 & NA\\
+MOZ & 1.29 & NA\\
+MUS & 0.27 & NA\\
+PCN & 0.00 & NA\\
+\addlinespace
+TZA & 0.04 & NA\\
+ZAF & 0.00 & NA\\
 \bottomrule
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
 \caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
 \caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
 \caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
@@
   countryKIR & 0.251$^{***}$ (0.036) \\ 
-  countryHS & $-$0.089$^{***}$ (0.018) \\ 
+  countryHS & 0.003 (0.019) \\ 
+  countryASM & $-$0.087$^{***}$ (0.018) \\ 
+  countryCHN & $-$0.089$^{***}$ (0.018) \\ 
   countryCOK & $-$0.085$^{***}$ (0.018) \\ 
+  countryECU & $-$0.088$^{***}$ (0.018) \\ 
+  countryFJI & $-$0.089$^{***}$ (0.018) \\ 
   countryFSM & $-$0.034 (0.021) \\ 
+  countryGUM & $-$0.089$^{***}$ (0.018) \\ 
+  countryJPN & $-$0.089$^{***}$ (0.018) \\ 
+  countryKOR & $-$0.089$^{***}$ (0.018) \\ 
+  countryMEX & $-$0.089$^{***}$ (0.018) \\ 
   countryMHL & $-$0.063$^{***}$ (0.019) \\ 
+  countryNIU & $-$0.089$^{***}$ (0.018) \\ 
   countryNRU & $-$0.039$^{**}$ (0.020) \\ 
+  countryNZL & $-$0.080$^{***}$ (0.019) \\ 
+  countryPAN & $-$0.089$^{***}$ (0.018) \\ 
+  countryPHL & $-$0.089$^{***}$ (0.018) \\ 
   countryPNG & 0.098$^{***}$ (0.034) \\ 
+  countryPYF & $-$0.089$^{***}$ (0.018) \\ 
+  countrySEN & $-$0.089$^{***}$ (0.018) \\ 
   countrySLB & $-$0.023 (0.026) \\ 
+  countrySYC & $-$0.089$^{***}$ (0.018) \\ 
   countryTKL & $-$0.072$^{***}$ (0.018) \\ 
+  countryTON & $-$0.089$^{***}$ (0.018) \\ 
   countryTUV & $-$0.024 (0.021) \\ 
-  countryothers & 0.016 (0.021) \\ 
+  countryTWN & $-$0.089$^{***}$ (0.018) \\ 
+  countryUMI & $-$0.086$^{***}$ (0.018) \\ 
+  countryWLF & $-$0.089$^{***}$ (0.018) \\ 
+  countryWSM & $-$0.089$^{***}$ (0.018) \\ 
   post:countryKIR & 0.113$^{**}$ (0.045) \\ 
-  post:countryHS & 0.085$^{***}$ (0.018) \\ 
+  post:countryHS & 0.196$^{***}$ (0.023) \\ 
+  post:countryASM & 0.085$^{***}$ (0.018) \\ 
+  post:countryCHN & 0.085$^{***}$ (0.018) \\ 
   post:countryCOK & 0.089$^{***}$ (0.018) \\ 
+  post:countryECU & 0.085$^{***}$ (0.018) \\ 
+  post:countryFJI & 0.086$^{***}$ (0.018) \\ 
   post:countryFSM & 0.091$^{***}$ (0.025) \\ 
+  post:countryGUM & 0.085$^{***}$ (0.018) \\ 
+  post:countryJPN & 0.085$^{***}$ (0.018) \\ 
+  post:countryKOR & 0.085$^{***}$ (0.018) \\ 
+  post:countryMEX & 0.085$^{***}$ (0.018) \\ 
   post:countryMHL & 0.080$^{***}$ (0.021) \\ 
+  post:countryNIU & 0.085$^{***}$ (0.018) \\ 
   post:countryNRU & 0.087$^{***}$ (0.021) \\ 
+  post:countryNZL & 0.091$^{***}$ (0.019) \\ 
+  post:countryPAN & 0.085$^{***}$ (0.018) \\ 
+  post:countryPHL & 0.085$^{***}$ (0.018) \\ 
   post:countryPNG & $-$0.015 (0.037) \\ 
+  post:countryPYF & 0.086$^{***}$ (0.018) \\ 
+  post:countrySEN & 0.085$^{***}$ (0.018) \\ 
   post:countrySLB & 0.107$^{***}$ (0.031) \\ 
+  post:countrySYC & 0.086$^{***}$ (0.018) \\ 
   post:countryTKL & 0.087$^{***}$ (0.019) \\ 
+  post:countryTON & 0.086$^{***}$ (0.018) \\ 
   post:countryTUV & 0.100$^{***}$ (0.025) \\ 
-  post:countryothers & 0.201$^{***}$ (0.028) \\ 
+  post:countryTWN & 0.085$^{***}$ (0.018) \\ 
+  post:countryUMI & 0.083$^{***}$ (0.018) \\ 
+  post:countryWLF & 0.085$^{***}$ (0.018) \\ 
+  post:countryWSM & 0.086$^{***}$ (0.018) \\ 
   Constant & 0.089$^{***}$ (0.018) \\ 
  \hline \\[-1.8ex] 
-Observations & 864 \\ 
-R$^{2}$ & 0.557 \\ 
+Observations & 2,304 \\ 
+R$^{2}$ & 0.638 \\ 
 \hline 
@@
 
-\section{Discusion}\label{discusion}
+\hypertarget{discusion}{%
+\section{Discusion}\label{discusion}}
 
@@
 
-\section{Appendix}\label{appendix}
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
 

### 2018-10-04 slides/ERE_lunch.Rmd
Finally got the redistribution data ready. Will run spatial analyses tomorrow

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
author:
  - Juan Carlos Villaseñor-Derbez^1^
  - John Lynham^2^
institute:
  - ^1^Bren School of Environmental Science and Management, UC Santa Barbara
  - ^2^Department of Economics, University of Hawaii at Manoa
date: "5/10/2018"
output: 
  beamer_presentation: 
    toc: yes
    slide_level: 2
    citation_package: biblatex
bibliography: references.bib
biblio-style: authoryear
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      eval = TRUE)

suppressPackageStartupMessages({
  library(startR)
  library(sf)
  library(tidyverse)
})

source(here::here("scripts", "st_rotate.R"))
```

# Background

## MPAs

- Marine Protected Areas (MPAs): Spatial management of fishing effort
-Areas > 250,000 Km^2^ are Large Scale (LSMPAs) \footcite{toonen_2013}
  - Implemented in the pelagic environment
  - Dominant human activity is industrial fishing \footcite{gray_2017}

```{r}
mpas <- sf::read_sf(here::here("raw_data", "spatial", "WDPA_Mar2018"),
        layer = "WDPA_Mar2018_marine-shapefile-polygons",
        quiet = T,
        stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(gis_m_area > 250000)

coast <- rnaturalearth::ne_countries(returnclass = "sf")
```

```{r, fig.height = 3.5}
ggplot() +
  geom_sf(data = coast) +
  geom_sf(data = mpas, fill = "red") +
  ggtheme_plot()
```

## PIPA

- Phoenix Island Protected Area
  - Part of Kiribati EEZ
  - Implemented in 2015
  - Kiribati is part of the PNA, along with other 8 countries

```{r}
eez <- sf::read_sf(dsn = here::here("data", "spatial", "PNA_EEZ"), layer = "PNA_EEZ") %>% 
  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_rotate() %>% 
  st_buffer(0) %>% 
  group_by(ISO_Ter1) %>% 
  summarize()

pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_rotate()
```

```{r, fig.height = 4}
ggplot() +
  geom_sf(data = eez, fill = "gray", alpha = 0.5) +
  geom_sf(data = pipa, fill = "red") +
  ggtheme_plot()
```

## PIPA

- Phoenix Island Protected Area
  - Part of Kiribati EEZ
  - Implemented in 2015
  - Kiribati is part of the PNA, along with other 8 countries

- Recent focus of *Blue paradox* \footcite{mcdermott_2018}

```{r, fig.height = 4}
displacement_data <- readRDS(file = here::here("data", "displacement_data.rds")) %>% 
  filter(year < 2017)

displacement_data %>% 
  filter(gear == "purse_seines",
         country == "PIPA") %>% 
  ggplot(aes(x = date, y = h_prop, group = post)) +
  geom_smooth(method = "loess", color = "black", linetype = "dashed") +
  geom_point(aes(color = post), size = 2) +
  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
  scale_fill_brewer(palette = "Paired") +
  ggtheme_plot() +
  ylab("Proportion of total hours by vessels") +
  scale_y_continuous(labels = scales::percent) +
  scale_color_brewer(palette = "Set1")
```

```{r}
effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
  filter(year < 2018)
```

# Objectives

- How do vessel-level behavior change due to PIPA implementation?
- What happens to the displaced fishing effort?

# Methods

## Data

## Analyses

$$
y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
$$

$$
y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
$$

# Preliminary results

# Future work

# References

### 2018-10-04 scripts/displacement_data_ll.R

@@ -1,0 +1,74 @@
+library(startR)
+library(magrittr)
+library(sf)
+library(tidyverse)
+
+# Custom functions that should be part of startR
+source(here::here("scripts", "st_rotate.R"))
+source(here::here("scripts", "sfc_as_cols.R"))
+
+vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds"))
+
+eez <- read_sf(dsn = here::here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
+  filter(ISO_Ter1 %in% unique(vessel_tracks$eez_iso3)) %>% 
+  mutate(PNA = ISO_Ter1 %in% c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV")) %>% 
+  st_rotate()
+
+pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
+                layer = "PIPA") %>% 
+  mutate(inside = T) %>% 
+  select(inside) %>% 
+  st_rotate()
+
+# Longliners
+
+memory.limit(size = 8e6)
+
+ll_rest <- vessel_tracks %>% 
+  filter(!gear == "purse_seines",
+         treated,
+         fishing,
+         !eez_iso3 %in% c("KIR")) %>% 
+  st_as_sf(coords = c(7, 8), crs = "+proj=longlat +datum=WGS84 +no_defs") %>%
+  st_rotate() %>% 
+  mutate(inside = NA) %>% 
+  sfc_as_cols(names = c("lon", "lat")) %>%
+  st_set_geometry(value = NULL) %>%
+  mutate(country = ifelse(is.na(eez_iso3), "HS", eez_iso3))
+
+ll <- vessel_tracks %>% 
+  filter(!gear == "purse_seines",
+         treated,
+         fishing,
+         eez_iso3 == "KIR") %>% 
+  st_as_sf(coords = c(7, 8), crs = "+proj=longlat +datum=WGS84 +no_defs") %>%
+  st_rotate() %>% 
+  st_join(pipa) %>% 
+  sfc_as_cols(names = c("lon", "lat")) %>% 
+  st_set_geometry(value = NULL) %>%
+  mutate(country = ifelse(is.na(inside), eez_iso3, "PIPA")) %>%
+  rbind(ll_rest) %>% 
+  group_by(year, month) %>% 
+  mutate(total_hours = sum(hours)) %>% 
[…]

### 2018-10-04 scripts/displacement_data_ps.R

@@ -1,0 +1,58 @@
+library(startR)
+library(magrittr)
+library(sf)
+library(tidyverse)
+
+# Custom functions that should be part of startR
+source(here::here("scripts", "st_rotate.R"))
+source(here::here("scripts", "sfc_as_cols.R"))
+
+vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds"))
+
+eez <- read_sf(dsn = here::here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
+  filter(ISO_Ter1 %in% unique(vessel_tracks$eez_iso3)) %>% 
+  mutate(PNA = ISO_Ter1 %in% c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV")) %>% 
+  st_rotate()
+
+pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
+                layer = "PIPA") %>% 
+  mutate(inside = T) %>% 
+  select(inside) %>% 
+  st_rotate()
+
+# Cuales estan dentro de PIPA
+
+ps <- vessel_tracks %>% 
+  filter(gear == "purse_seines",
+         treated,
+         fishing) %>% 
+  st_as_sf(coords = c(7, 8), crs = "+proj=longlat +datum=WGS84 +no_defs") %>%
+  st_rotate() %>% 
+  st_join(pipa) %>% 
+  sfc_as_cols(names = c("lon", "lat")) %>% 
+  st_set_geometry(value = NULL) %>%
+  mutate(country = ifelse(is.na(eez_iso3), "HS", eez_iso3),
+         country = ifelse(is.na(inside), country, "PIPA")) %>%
+  group_by(year, month) %>% 
+  mutate(total_hours = sum(hours)) %>% 
+  ungroup() %>% 
+  group_by(year, month, country, total_hours) %>%
+  summarize(h = sum(hours)) %>% 
+  mutate(h_prop = h / total_hours) %>% 
+  ungroup()
+
+displacement_data_ps <- expand.grid(country = c(unique(ps$country), "HS"),
+                                    year = 2012:2017,
+                                    month = 1:12) %>% 
+  arrange(country, year, month) %>%
+  as.tibble() %>%
+  left_join(ps, by = c("country", "year", "month")) %>% 
+  mutate(h_prop = ifelse(is.na(h_prop), 0, h_prop)) %>% 
+  mutate(date = lubridate::date(paste(year, month, 1, sep = "/")),
[…]

### 2018-10-05 rmd/Manuscript.Rmd
Added some slides for ERE lunch

@@
 displacement_data %>% 
-  filter(gear == "purse_seines") %>% 
+  filter(gear == "purse_seines",
+         h_prop > 0) %>%
+  mutate(country = as.character(country),
+         country = ifelse(country %in% c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"), country, "OTH"),
+         country = forcats::fct_relevel(country, "OTH", after = Inf)) %>% 
   ggplot(aes(x = date, y = h_prop, group = post)) +

### 2018-10-05 slides/ERE_lunch.Rmd
Added some slides for ERE lunch

@@
   beamer_presentation: 
-    toc: yes
     slide_level: 2
@@
 biblio-style: authoryear
+header-includes:
+  - \usepackage{booktabs}
 ---
@@
 
+options(knitr.table.format = "latex")
+
 suppressPackageStartupMessages({
@@
 source(here::here("scripts", "st_rotate.R"))
+source(here::here("scripts", "sfc_as_cols.R"))
 ```
@@
 - Marine Protected Areas (MPAs): Spatial management of fishing effort
--Areas > 250,000 Km^2^ are Large Scale (LSMPAs) \footcite{toonen_2013}
-  - Implemented in the pelagic environment
-  - Dominant human activity is industrial fishing \footcite{gray_2017}
+- Areas > 250,000 Km^2^ are Large Scale (LSMPAs) \footcite{toonen_2013}
+  - Industrial fishing largest human activity in pelagic environment \footcite{gray_2017}
+  - Recent widespread implementation, unknown implication for fisheries
 
 ```{r}
+countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI")
+
 mpas <- sf::read_sf(here::here("raw_data", "spatial", "WDPA_Mar2018"),
@@
 coast <- rnaturalearth::ne_countries(returnclass = "sf")
+
+small_coast <- coast %>% 
+  filter(sov_a3 %in% countries)
+
+eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"),
+               layer = "EEZ_subset") %>% 
+  filter(ISO_Ter1 %in% countries) %>% 
+  mutate(KIR = ISO_Ter1 == "KIR")
+
+pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
+  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_rotate()
+
+effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
+  filter(year < 2017)
+
+displacement_data <- readRDS(file = here::here("data", "displacement_data.rds")) %>% 
+  filter(year < 2017)
 ```
@@
 
-## PIPA
+## LSMPAs
 
-- Phoenix Island Protected Area
-  - Part of Kiribati EEZ
-  - Implemented in 2015
-  - Kiribati is part of the PNA, along with other 8 countries
+- Erroneously assumed to have little social implications due to their remoteness \footcite{agardy_2011}
+- *Blue paradox* shows preemptive fishing\footcite{mcdermott_2018}:
 
-```{r}
-eez <- sf::read_sf(dsn = here::here("data", "spatial", "PNA_EEZ"), layer = "PNA_EEZ") %>% 
-  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
-  st_rotate() %>% 
-  st_buffer(0) %>% 
-  group_by(ISO_Ter1) %>% 
-  summarize()
-
-pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
-  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
-  st_rotate()
+```{r, fig.cap = "Preemtive fishing due to MPA implementation (Modified from McDermott et al (2018))", out.width = "180px"}
+knitr::include_graphics(path = "img/BlueParadox.jpg")
 ```
 
-```{r, fig.height = 4}
-ggplot() +
-  geom_sf(data = eez, fill = "gray", alpha = 0.5) +
-  geom_sf(data = pipa, fill = "red") +
-  ggtheme_plot()
-```
+## MPAs and fishing effort
+
+Models range from *cookie-cutter* approach to spatially explicit reallocation of fishing effort based on habitat characteristics:
+
+- All these focus on the long term equilibrium \footcite{white_2013}
+- Resource users may show idiosyncratic responses \footcite{cabral_2017}
+- Redistribution of fishing effort may not be optimal, especially over the first years \footcite{stevenson_2013}
+- Not accounting for fisher's behavior may lead to unexpected outcomes \footcite{smith_2003}
 
@@
 - Phoenix Island Protected Area
-  - Part of Kiribati EEZ
+  - Belongs to Kiribati
   - Implemented in 2015
@@
 
-- Recent focus of *Blue paradox* \footcite{mcdermott_2018}
-
 ```{r, fig.height = 4}
-displacement_data <- readRDS(file = here::here("data", "displacement_data.rds")) %>% 
-  filter(year < 2017)
-
-displacement_data %>% 
-  filter(gear == "purse_seines",
-         country == "PIPA") %>% 
-  ggplot(aes(x = date, y = h_prop, group = post)) +
-  geom_smooth(method = "loess", color = "black", linetype = "dashed") +
-  geom_point(aes(color = post), size = 2) +
-  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
-  scale_fill_brewer(palette = "Paired") +
+ggplot() +
+  geom_sf(data = small_coast) +
+  geom_sf(data = eez, aes(color = KIR, linetype = !PNA), fill = "transparent") +
+  geom_sf(data = pipa, fill = "red") +
   ggtheme_plot() +
-  ylab("Proportion of total hours by vessels") +
-  scale_y_continuous(labels = scales::percent) +
-  scale_color_brewer(palette = "Set1")
+  scale_color_manual(values = c("black", "red")) +
+  theme(legend.position = "none")
 ```
 
-```{r}
-effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
-  filter(year < 2018)
-```
+# Questions
 
-# Objectives
+## Questions
 
-- How do vessel-level behavior change due to PIPA implementation?
+- How does vessel-level behavior change due to PIPA implementation?
 - What happens to the displaced fishing effort?
@@
 
+- On-board Automatic Identification Systems (AIS)
+- Global georeferenced vessel positions (3.1 billion and growing):
+  - Activity (fishing / not fishing)
+  - Time (hours)
+  - Vessel characteristics (flag, gear, length, width)
+
+```{r, fig.cap = "Sample track of Chinese longliner (10K fishing points of ~400K total)", fig.height = 4}
+readRDS(file = "small_data/sample_track.rds") %>% 
+  ggplot() +
+  geom_sf(data = small_coast) +
+  geom_sf(data = eez, aes(color = KIR, linetype = !PNA), fill = "transparent") +
+  geom_sf(data = pipa, fill = "red") +
+  geom_point(aes(x = lon, y = lat), shape = ".") +
+  ggtheme_plot() +
+  scale_color_manual(values = c("black", "red")) +
+  theme(legend.position = "none")
+```
+
+## Data
+
+Two groups:
+
+- Treated
+  - Vessels who fished inside PIPA at least once before closure
+  - Continued to fish elsewhere after implementation of PIPA
+- Control:
+  - Vessels never fished within PIPA waters
+  - Vessels belong to other PNA countries
+  - Vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure
+
+- Over 45 million individual AIS messages (positions)
+
+## Data
+
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
+effort_by_vessel %>% 
+  filter(baci_strict) %>%
+  group_by(year, gear, treated, post, month) %>% 
+  summarize(total_hours = sum(hours),
+            mean_hours = mean(hours),
+            n_mmsi = n()) %>% 
+  ungroup() %>% 
+  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
+  select(-year) %>% 
+  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
+  ggplot(aes(x = date, y = value, color = treated)) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(gear~variable, scales = "free", ncol = 3) +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
+```
+
 ## Analyses
 
+### Change in vessel-level behavior with a DiD
+
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \epsilon_{i,t}
 $$
+
+- $y_{i,t}$ monthly fishing hours by vessel $i$ in time period $t$
+- $Post_t$ before-after PIPA dummy
+- $Treat_i$ treatment dummy
+- $\beta_3$ is our DiD estimate
+- month, flag, year controls
+
+## Analyses
+
+### Spatial redistribution
+
+- Treated vessels only
 
@@
 
-# Preliminary results
+- $y_{i,t}$ proportion of fishing hours that country $i$ receives at time $t$
+- $Post_t$ before-after PIPA dummy
+- $Country_i$ country dummy
 
-# Future work
+# Preliminary results \newline (Focusing on purse seiners for now)
+
+## Change in fishing
+
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure.", fig.heihgt = 3.5}
+
+effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
+  arrange(!treated) %>% 
+  ggplot(aes(x = date, y = hours, color = treated)) +
+  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
+  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.5) +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
+```
+
+## Change in fishing
+
+```{r, results = "asis"}
+model_data <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year^2,
+         mmsi_c = as.factor(mmsi))
+
+m1 <- lm(hours ~ post*treated, data = model_data)
+m2 <- lm(hours ~ post*treated + month_c, data = model_data)
+m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
+m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
+
+models <- list(m1, m2, m3, m4)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("year", "flag", "month_c"),
+                     add.lines = list(c("Months", "No", "Yes", "Yes", "Yes"),
+                                      c("Year", "No", "No", "Yes", "Yes"),
+                                      c("Country", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).",
+                     column.sep.width = "1pt",
+                     font.size = "tiny")
+```
+
+## Effort redistribution
+
+```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-vessels.", fig.height = 4}
+displacement_data %>% 
+  filter(gear == "purse_seines",
+         h_prop > 0) %>%
+  mutate(country = as.character(country),
+         country = ifelse(country %in% countries, country, "OTH"),
+         country = forcats::fct_relevel(country, c("PIPA", "KIR", "HS")),
+         country = forcats::fct_relevel(country, "OTH", after = Inf)) %>% 
+  ggplot(aes(x = date, y = h_prop, group = post)) +
+  geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
+  geom_point(size = 1) +
+  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
+  scale_fill_brewer(palette = "Paired") +
+  ggtheme_plot() +
+  facet_wrap(~country, scales = "free_y")
+```
+
+## Displacement
+
+```{r}
+# Dont have this here. Just write the model specification
+
+disp_mod_ps_data <- displacement_data %>% 
+  filter(gear == "purse_seines",
+         h_prop > 0) %>%
+  mutate(country = as.character(country),
+         country = ifelse(country %in% countries, country, "OTH"),
+         country = forcats::fct_relevel(country, c("PIPA", "KIR", "HS")),
+         country = forcats::fct_relevel(country, "OTH", after = Inf),
+         post = post *1,
+         year2 = year^2,
+         month_c = as.character(month))
+
+disp_mod_ps1 <- lm(h_prop ~ post * country, data = disp_mod_ps_data)
+
+commarobust::commarobust(disp_mod_ps1) %>% 
+  as.data.frame() %>% 
+  mutate(term = rownames(.)) %>% 
+  mutate(b = str_detect(term, "Intercept"),
+         c = str_detect(term, "post"),
+         a = b*c,
+         p = `Pr(>|t|)`,
+         p1 = ifelse(p < 0.1, "*", ""),
+         p2 = ifelse(p < 0.05, "*", ""),
+         p3 = ifelse(p < 0.01, "*", ""),
+    h_prop = paste0(formatC(Estimate, digits = 3, format = "f"), p1, p2, p3)) %>% 
+  filter(b+c > 0) %>% 
+  select(term, h_prop) %>% 
+  knitr::kable(booktabs = T,
+               caption = "Change in the relative allocation of fishing hours by purse seiners") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position",
+                            font_size = 7)
+```
+
+$R^2 = 0.544^{***}; n = 707$
+
+## Displacement
+
+```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort.", fig.height = 4}
+ba_disp_ps <- displacement_data %>% 
+  filter(gear == "purse_seines") %>% 
+  group_by(country, post) %>% 
+  summarize(h_prop_m = mean(h_prop)) %>% 
+  spread(post, h_prop_m) %>% 
+  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
+  select(country, change)
+
+pipa_map_ba_disp <- pipa %>% 
+  mutate(country = "PIPA",
+         PNA = F) %>% 
+  left_join(ba_disp_ps, by = "country") %>% 
+  select(country, change, PNA)
+
+HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
+                  ncol=2,
+                  byrow=TRUE) %>%
+  list() %>%
+  st_polygon() %>% 
+  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")
+
+HS_disp <- data.frame(country = "HS",
+                      PNA = F) %>% 
+  left_join(ba_disp_ps, by = "country") %>% 
+  st_set_geometry(HS_disp_poly)
+
+# Los colores del mapa deben estar dados por el Post:Country
+eez %>% 
+  left_join(ba_disp_ps, by = c("ISO_Ter1" = "country")) %>%
+  filter(!is.na(change)) %>% 
+  select(country = ISO_Ter1, change, PNA) %>% 
+  rbind(pipa_map_ba_disp) %>% 
+  rbind(HS_disp) %>% 
+  ggplot() +
+  geom_sf(aes(fill = change, linetype = !PNA), color = "black") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
+```
+
+## Displacement
+
+```{r, fig.cap = "Spatial representation of the mean change in the monthly allocation of fishing effort.", fig.height = 4}
+eez %>% 
+  left_join(ba_disp_ps, by = c("ISO_Ter1" = "country")) %>%
+  filter(!is.na(change)) %>% 
+  select(country = ISO_Ter1, change, PNA) %>% 
+  rbind(pipa_map_ba_disp) %>% 
+  rbind(HS_disp) %>% 
+  filter(!country %in% c("HS", "PNG")) %>% 
+  ggplot() +
+  geom_sf(aes(fill = change, linetype = !PNA), color = "black") +
+  ggtheme_plot() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
+```
+
+## Recap
+
+- Treated vessels fish less post-implementation
+  - Only significant for purse seiners
+
+- EEZs receive proportionally more fishing effort than before
+  - Proportional change increases with proximity to PIPA
+
+## Future work
+
+Change in behavior
+
+- Distance traveled
+- non-fishing at-sea hours
+- proportion of fishing / searching
+
+Spatial redistribution
+
+- Proportion is bounded, might try a binomial GLM
+- Measure of "crowdness"
+
+Concerns
+
+- Spillover effects / treatment affecting control
 

### 2018-10-11 rmd/Lit Review.Rmd
Modified little details in the manuscript

---
title: "Lit Review"
author: "Villaseñor-Derbez, J.C."
date: "Compiled on `r date()` by `r Sys.info()['user']`"
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 1
    citation_package: biblatex
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
bibliography: references.bib
---

# \citeauthor{white_2013}

## \citetitle{white_2013}

MPA modeles are often developed at a smaller spatial scale than stock assessments. To date, most MPA works focused on idealized coastlines, with few stie-specific cases. These works often seek to maximize population persistance by selecting number and sizes of reserves, leaving economics on the side.

The paper describes and syntesizes two complementary approaches to including economic and population dunamic factors in the evaluantion of potential MPA networks:

- Static assessment f potential maximum short-term economic impacts that is agnostic to external fishery management and assumes no spillover of fish from reserves to fished areas, or **reallocation of fishing effort**. It does take into account fishing effort, real local catches, and economic values.
- A dynamic bioeconomic model of the long-term equilibrium outcomes that explicitly accounts for fish population dynamics, spillover, **fisher movement**, and fishery management outside the MPAs.

The static analysis provided 4 type of results:

- Percentage of fishing grounds closed, and their value to fisheries, ports, and study region.
- Maximum potential first order economic impacts (worst-case scenarios) at the port-level. (Immediate cost of MPAs)
- An assessment of outliers,fisheries likely to experience disproportionate impacts,measured in terms of significant deviation from other values in thesample.
- Convergence analysis

For the dynamic bioeconomic model, due to the lack of spatially-explicit data on biomass and fishing effort, they focus on the long-term equilibrium, because this level does not depend on the starting conditions. Biomass inside MPAs was compared to a model run with no fishing (i.e. all as MPAs), and yield was compared to a model run with MSY management. These produces two types of results:

- Maps with spatially explicit model outputs
- The second type of result was ranking each MPA proposal ineach evaluation round to compare the overall performance of each metric

- Mention the importance of understanding the level of fishing effort outside the MPAs: "simply observing that a given MPA has not produced an increase in biomass does not reveal what went wrong: was the MPA too small, was enforcement insufficient, wastoo muchfishing allowed outside the MPA, or has insufficient timeelapsed to observe an effect?"
- "This dataset could also be reanalyzed to predict the reallocation offishing effort after implementation: **in theory the fishing fleet should shift effort to the next best set offishing grounds closest to the high value areas now in MPAs**."

# \citeauthor{costello_2010}

## \citetitle{costello_2010}

Previous research focused on the effect of MPAs on limited entry or open access fisheries \footcite{sanchirico_2001,sanchirico_2002,smith_2003}. \citeauthor{smith_2003} find that after accounting for the spatial behavior of fishermen, imposed MPAs lead to a decrease in fishery profits.

Chris models exogenously imposed MPAs on a system already managed by TURFs. They find that:

- Fully coordinated TURFs can include private MPAs, even without government interventions
- Imposing additional MPAs decreases system-wide profits under full coordination
- Abundance will typically increase under exogenous MPA placement in both coordinated and uncoordinated TURF fisheries
- Profits can increase with imposed MPAs in the absence of coordination
- Optimal MPA networks in uncoordinated TURF fisheries may be larger than optimap MPA networks in coordinated TURF fisheries.

### 2018-10-11 rmd/Manuscript.Rmd
Modified little details in the manuscript

--- 2018-10-03 rmd/Manuscript.Rmd
@@
 pipa_vessels <- effort_by_vessel %>% 
-  filter(treated) %$%
+  filter(treated, baci_strict) %$%
   unique(mmsi) %>% 
@@
 
-eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"),
-               layer = "EEZ_subset")
+eez <- read_sf(dsn = here::here("data", "spatial", "regions"),
+               layer = "regions")
 
@@
 displacement_data %>% 
-  filter(gear == "purse_seines") %>% 
+  filter(gear == "purse_seines",
+         h_prop > 0) %>%
+  # mutate(country = as.character(country),
+         # country = ifelse(country %in% c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"), country, "OTH"),
+         # country = forcats::fct_relevel(country, "OTH", after = Inf)) %>% 
   ggplot(aes(x = date, y = h_prop, group = post)) +
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend_spa}Proportion of fishing hours that all vessels spent on each of the EEZs and the high seas.", eval = F}
-pipa_map_disp <- pipa %>% 
-  mutate(country = "PIPA") %>% 
-  left_join(displacement_data, by = "country")
+```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
 
@@
 eez %>% 
-  left_join(displacement_data, by = c("ISO_Ter1" = "country")) %>%
-  group_by(year) %>% 
-  summarize(h_prop = mean(h_prop, na.rm = T)) %>% 
-  ggplot() +
-  geom_sf(aes(fill = h_prop, linetype = PNA), size = 1, color = "black") +
-  geom_sf(data = pipa_map_ba_disp, aes(fill = h_prop), linetype = "dashed", color = "red") +
-  ggtheme_plot() +
-  scale_fill_gradientn(colors = colorRamps::matlab.like(10)) +
-  facet_wrap(~year)
-```
-
-```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
-pipa_map_ba_disp <- pipa %>% 
-  mutate(country = "PIPA") %>% 
-  left_join(ba_disp_ps, by = "country")
-
-# Los colores del mapa deben estar dados por el Post:Country
-eez %>% 
-  left_join(ba_disp_ps, by = c("ISO_Ter1" = "country")) %>%
-  filter(!is.na(change)) %>% 
+  left_join(ba_disp_ps, by = c("id" = "country")) %>%
+  # filter(!is.na(change)) %>% 
   ggplot() +
   geom_sf(aes(fill = change), color = "black") +
-  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
   ggtheme_plot() +

### 2018-10-11 slides/ERE_lunch.Rmd
Modified little details in the manuscript

@@
   beamer_presentation: 
+    citation_package: biblatex
     slide_level: 2
-    citation_package: biblatex
+    theme: Berkeley
 bibliography: references.bib

### 2018-10-11 rmd/Manuscript.Rmd
Updated effort data

@@
   filter(baci_strict) %>%
-  group_by(year, gear, treated, post, month) %>% 
+  group_by(year, gear, treated, post, month, date) %>% 
   summarize(total_hours = sum(hours),
@@
   ungroup() %>% 
-  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
+  # mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
   select(-year) %>% 
@@
 
-model_data <- effort_by_vessel %>% 
+model_data1 <- effort_by_vessel %>% 
   filter(baci_strict,
@@
          treated = treated * 1,
-         year2 = year^2,
-         mmsi_c = as.factor(mmsi))
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter))
 
-m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month_c, data = model_data)
-m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
-m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
+model_data2 <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines",
+         experiment1) %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter))
 
-models <- list(m1, m2, m3, m4)
+model_data3 <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines",
+         experiment2) %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter))
+
+model_data4 <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines",
+         experiment3) %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter))
+
+m1.1 <- lm(hours ~ post*treated, data = model_data1)
+m2.1 <- lm(hours ~ year_month_c*treated, data = model_data1)
+m3.1 <- lm(hours ~ quarter_c*treated, data = model_data1)
+
+m1.2 <- lm(hours ~ post*treated, data = model_data2)
+m2.2 <- lm(hours ~ year_month_c*treated, data = model_data2)
+m3.2 <- lm(hours ~ quarter_c*treated, data = model_data2)
+
+m1.3 <- lm(hours ~ post*treated, data = model_data3)
+m2.3 <- lm(hours ~ year_month_c*treated, data = model_data3)
+m3.3 <- lm(hours ~ quarter_c*treated, data = model_data3)
+
+m1.4 <- lm(hours ~ post*treated, data = model_data4)
+m2.4 <- lm(hours ~ year_month_c*treated, data = model_data4)
+m3.4 <- lm(hours ~ quarter_c*treated, data = model_data4)
+
+models <- list(m1.1, m1.2, m1.3, m1.4)
 
@@
                      header = F,
-                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+                     title = "DiD",
+                     out = "DID.html")
+
+models <- list(m2.1, m2.2, m2.3, m2.4)
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "DiD - months",
+                     out = "months.html")
+
+models <- list(m3.1, m2.2, m3.3, m3.4)
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
+                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "DiD - quarters",
+                     out = "quarters.html")
 ```

### 2018-10-12 rmd/Manuscript.Rmd
Updated manuscript rmd and deleted erroneous files

--- 2018-10-11 rmd/Manuscript.Rmd
@@
 ```{r}
-displacement_data <- readRDS(file = here::here("data", "displacement_data.rds")) %>% 
+displacement_data <- readRDS(file = here::here("data", "displacement_data_ps.rds")) %>% 
   filter(year < 2018)
@@
                layer = "regions")
-
-pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
-                layer = "PIPA") %>% 
-  mutate(inside = T) %>% 
-  select(inside) %>% 
-  st_rotate()
 ```
@@
 
-ba_disp_ll <- displacement_data %>% 
-  filter(!gear == "purse_seines") %>% 
-  group_by(country, post) %>% 
-  summarize(h_prop_m = mean(h_prop)) %>% 
-  spread(post, h_prop_m) %>% 
-  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
-  select(country, change)
-
-ba_disp_ps %>% 
-  mutate(gear = "Purse seiners") %>% 
-  rbind(mutate(ba_disp_ll, gear = "Longliners")) %>% 
-  spread(gear, change) %>% 
-  knitr::kable(digits = 2,
-               booktabs = T,
-               caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
+# ba_disp_ll <- displacement_data %>% 
+#   filter(!gear == "purse_seines") %>% 
+#   group_by(country, post) %>% 
+#   summarize(h_prop_m = mean(h_prop)) %>% 
+#   spread(post, h_prop_m) %>% 
+#   mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
+#   select(country, change)
+# 
+# ba_disp_ps %>% 
+#   mutate(gear = "Purse seiners") %>% 
+#   rbind(mutate(ba_disp_ll, gear = "Longliners")) %>% 
+#   spread(gear, change) %>% 
+#   knitr::kable(digits = 2,
+#                booktabs = T,
+#                caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>% 
+#   kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 
-model_data <- effort_by_vessel %>% 
+model_base <- effort_by_vessel %>% 
   filter(baci_strict,
@@
          treated = treated * 1,
-         year2 = year^2,
-         mmsi_c = as.factor(mmsi))
+         year2 = year * year,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter),
+         flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
+         flag_fe_oth = flag_fe & !flag == "OTH")
 
-m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month_c, data = model_data)
-m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
-m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
+# See file combine_vessel_info_and_effort to see how experiment columns are created ~line 70
+## Controls are PNA
+experiment1 <- model_base %>% 
+  filter(experiment1)
 
-models <- list(m1, m2, m3, m4)
+## Controls are Taiwanese
+experiment2 <- model_base %>% 
+  filter(experiment2)
 
+## Controls are everything BUT Chinese
+experiment3 <- model_base %>% 
+  filter(experiment3)
+
+## Fit the models
+
+source(here::here("scripts", "did.R"))
+source(here::here("scripts", "did_quarter.R"))
+source(here::here("scripts", "did_yearmonth.R"))
+source(here::here("scripts", "termplot.R"))
+
+## Simple dids for each data
+models_exp0_did <- model_base %>% did()
+models_exp1_did <- experiment1 %>% did()
+models_exp2_did <- experiment2 %>% did()
+models_exp3_did <- experiment3 %>% did()
+
+# Quarterly did
+models_exp0_did_q <- model_base %>% did_quarter()
+models_exp1_did_q <- experiment1 %>% did_quarter()
+models_exp2_did_q <- experiment2 %>% did_quarter()
+models_exp3_did_q <- experiment3 %>% did_quarter()
+
+# Monthly did
+models_exp0_did_ym <- model_base %>% did_yearmonth()
+models_exp1_did_ym <- experiment1 %>% did_yearmonth()
+models_exp2_did_ym <- experiment2 %>% did_yearmonth()
+models_exp3_did_ym <- experiment3 %>% did_yearmonth()
+
+# map(models_exp3_did, summary)
+```
+
+```{r, eval = F}
 stargazer::stargazer(models,
@@
                      header = F,
-                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.")
-```
-
-```{r, fig.width = 5, fig.height = 3, fig.cap = "\\label{fig:puse}Coefficient estimates for each model.
-Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate.", eval = F}
-map_df(models, broom::tidy, .id = "model") %>%
-  filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
-  ggplot(aes(x = model, y = estimate)) +
-  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
-                size = 1,
-                width = 0,
-                color = "red") +
-  geom_point(color = "steelblue", size = 3) +
-  facet_wrap(~term, scale = "free") +
-  ggtheme_plot()
-```
-
-```{r, results = "asis"}
-
-model_data <- effort_by_vessel %>% 
-  filter(baci_strict,
-         !gear == "purse_seines") %>% 
-  mutate(post = post * 1,
-         treated = treated * 1,
-         year2 = year^2,
-         mmsi_c = as.factor(mmsi))
-
-m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month_c, data = model_data)
-m3 <- lm(hours ~ post*treated + month_c + year + year2, data = model_data)
-m4 <- lm(hours ~ post*treated + month_c + year + year2 + flag, data = model_data)
-
-models <- list(m1, m2, m3, m4)
-
-stargazer::stargazer(models,
-                     se = commarobust::makerobustseslist(models),
-                     t.auto = T,
-                     p.auto = T,
-                     type = "latex",
-                     omit = c("flag", "month"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
-                                      c("Flag FE", "No", "No", "No", "Yes")),
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+                     title = "DiD",
+                     out = "DID.html")
 ```
@@
   left_join(ba_disp_ps, by = c("id" = "country")) %>%
-  # filter(!is.na(change)) %>% 
+  filter(!is.na(change)) %>%
   ggplot() +
@@
 ```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for longliners.
-**This are preliminar results, contingent on the spatial analysis currently being run**"}
+**This are preliminar results, contingent on the spatial analysis currently being run**", eval = F}
 pipa_map_ba_disp <- pipa %>% 
@@
 
+## Other model specifications
+
+### Year as dummy variables
+
 ```{r, results = "asis", echo = F}
@@
 
+```{r}
+models_exp0_did
+models_exp1_did
+models_exp2_did
+models_exp3_did
+```
+
+```{r}
+# Quarterly did
+models_exp0_did_q %>% termplot(q = T)
+models_exp1_did_q %>% termplot(q = T)
+models_exp2_did_q %>% termplot(q = T)
+models_exp3_did_q %>% termplot(q = T)
+```
+
+```{r}
+# Monthly did
+models_exp0_did_ym %>% termplot()
+models_exp1_did_ym %>% termplot()
+models_exp2_did_ym %>% termplot()
+models_exp3_did_ym %>% termplot()
+```
+
 \clearpage

### 2018-10-12 docs/Manuscript.tex
Updated manuscript figures and tables, will update the rest tomorrow

@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-09-29}
+  \subtitle{Updated on 2018-10-11}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 University of California Santa Barbara, Santa Barbara,
-CA\newline\textsuperscript{2}Department of Economics, University of
+CA\newline \textsuperscript{2}Department of Economics, University of
 Hawaii at Manoa, Honolulu, HI}
@@
   turned off their AIS transmitters. In either case, we are not able to
-  observe these.}, leaving us with 183 vessels that fished inside PIPA
+  observe these.}, leaving us with 176 vessels that fished inside PIPA
 before its implementation, and continued to fish elsewhere afterward.
@@
 
-The treatment group contains all vessels (n = 183) that fished within
+The treatment group contains all vessels (n = 176) that fished within
 PIPA at least once before the closure, and that continued to fish
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
-events by vessels through time. Each line represents a vessel, with dots
-indicating months with fishing activity and colors indicating the pre
-and post periods.}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
+\caption{\label{fig:unnamed-chunk-20}\label{fig:baci_strict}Stream of
+fishing events by vessels through time. Each line represents a vessel,
+with dots indicating months with fishing activity and colors indicating
+the pre and post periods.}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
+\caption{\label{tab:unnamed-chunk-21}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
 \centering
@@
 \midrule
-drifting\_longlines & FALSE & 85 & 474.47780 & 462.5491 & 0.9748593\\
-drifting\_longlines & TRUE & 115 & 544.61935 & 522.8392 & 0.9600085\\
-purse\_seines & FALSE & 36 & 59.49026 & 154.5776 & 2.5983673\\
-purse\_seines & TRUE & 68 & 52.91534 & 131.5452 & 2.4859561\\
+drifting\_longlines & FALSE & 77 & 39.03181 & 37.79044 & 0.9681958\\
+drifting\_longlines & TRUE & 115 & 41.62659 & 40.43857 & 0.9714600\\
+purse\_seines & FALSE & 26 & 11.73804 & 20.13247 & 1.7151474\\
+purse\_seines & TRUE & 61 & 10.66939 & 18.36289 & 1.7210820\\
 \bottomrule
@@
 in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
-pooled into a group of ``others'', leaving us with a total of n = 12 and
-n = 10\footnote{This number is likely to change upon finalizing the
+pooled into a group of ``others'', leaving us with a total of n = 23 and
+n = 0\footnote{This number is likely to change upon finalizing the
   spatial analysis of longliners, which is currently running.} spatially
@@
 
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
-\centering
-\begin{tabular}[t]{lrr}
-\toprule
-country & Longliners & Purse seiners\\
-\midrule
-PIPA & -11.48 & -8.54\\
-KIR & 1.28 & 2.76\\
-HS & 0.00 & 0.00\\
-COK & 0.00 & 0.34\\
-FSM & 0.00 & 0.55\\
-\addlinespace
-MHL & NA & -0.55\\
-NRU & 0.00 & 0.16\\
-PNG & 0.00 & -10.02\\
-SLB & -8.48 & 2.13\\
-TKL & NA & 0.19\\
-\addlinespace
-TUV & 7.23 & 1.47\\
-others & 22.55 & 11.51\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \clearpage
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels. Vertical dashed line
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels. Vertical dashed line
 indicates PIPA closure.}
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- post & 95.087$^{***}$ & 99.232$^{***}$ & 38.349$^{***}$ & 41.920$^{***}$ \\ 
-  & (5.877) & (5.453) & (7.423) & (8.214) \\ 
-  & & & & \\ 
- treated & $-$6.575 & $-$5.597 & $-$3.811 & 6.541 \\ 
-  & (4.985) & (4.564) & (4.247) & (5.195) \\ 
-  & & & & \\ 
- year &  &  & 12,828.900$^{***}$ & 16,665.590$^{***}$ \\ 
-  &  &  & (2,451.444) & (3,717.658) \\ 
-  & & & & \\ 
- year2 &  &  & $-$3.178$^{***}$ & $-$4.131$^{***}$ \\ 
-  &  &  & (0.609) & (0.923) \\ 
-  & & & & \\ 
- post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$17.304$^{***}$ & $-$18.709$^{***}$ \\ 
-  & (6.856) & (6.460) & (6.254) & (6.787) \\ 
-  & & & & \\ 
- Constant & 59.490$^{***}$ & 65.485$^{***}$ & $-$12,946,334.000$^{***}$ & $-$16,807,078.000$^{***}$ \\ 
-  & (4.422) & (6.132) & (2,473,372.000) & (3,759,572.000) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & No & Yes & Yes & Yes \\ 
-Flag FE & No & No & No & Yes \\ 
-Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
-R$^{2}$ & 0.171 & 0.243 & 0.281 & 0.299 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- post & $-$11.929 & $-$6.968 & $-$15.550 & $-$6.761 \\ 
-  & (7.969) & (7.975) & (10.181) & (11.289) \\ 
-  & & & & \\ 
- treated & 70.142$^{***}$ & 72.314$^{***}$ & 71.985$^{***}$ & 14.026$^{*}$ \\ 
-  & (7.200) & (7.200) & (7.279) & (7.988) \\ 
-  & & & & \\ 
- year &  &  & $-$6,673.971$^{*}$ & 21,188.090$^{***}$ \\ 
-  &  &  & (3,606.793) & (5,631.642) \\ 
-  & & & & \\ 
- year2 &  &  & 1.657$^{*}$ & $-$5.259$^{***}$ \\ 
-  &  &  & (0.894) & (1.398) \\ 
-  & & & & \\ 
- post:treated & $-$9.851 & $-$12.290 & $-$12.779 & $-$14.850 \\ 
-  & (9.294) & (9.262) & (9.334) & (9.563) \\ 
-  & & & & \\ 
- Constant & 474.478$^{***}$ & 449.960$^{***}$ & 6,719,355.000$^{*}$ & $-$21,341,371.000$^{***}$ \\ 
-  & (6.328) & (9.440) & (3,633,994.000) & (5,644,837.000) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & No & Yes & Yes & Yes \\ 
-Flag FE & No & No & No & Yes \\ 
-Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
-R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
 Recall that to evaluate the redistribution of fishing effort we only
@@
 of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
-relative fishing hours that each region received by all 183 treated
+relative fishing hours that each region received by all 176 treated
 vessels. The top-left panel shows the change in fishing effort inside
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
+\caption{\label{fig:unnamed-chunk-29}\label{fig:redist_trend_ps}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
-\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
+\caption{\label{fig:unnamed-chunk-31}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
 effort for purse seiners.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
-representation of the mean change in the monthly allocation of fishing
-effort for longliners. \textbf{This are preliminar results, contingent
-on the spatial analysis currently being run}}
 \end{figure}
@@
 \hline \\[-1.8ex] 
- post & $-$0.085$^{***}$ (0.018) \\ 
-  countryKIR & 0.251$^{***}$ (0.036) \\ 
-  countryHS & $-$0.089$^{***}$ (0.018) \\ 
-  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
-  countryFSM & $-$0.034 (0.021) \\ 
-  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
-  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
-  countryPNG & 0.098$^{***}$ (0.034) \\ 
-  countrySLB & $-$0.023 (0.026) \\ 
-  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
-  countryTUV & $-$0.024 (0.021) \\ 
-  countryothers & 0.016 (0.021) \\ 
-  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
-  post:countryHS & 0.085$^{***}$ (0.018) \\ 
-  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
-  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
-  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
-  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
-  post:countryPNG & $-$0.015 (0.037) \\ 
-  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
-  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
-  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
-  post:countryothers & 0.201$^{***}$ (0.028) \\ 
-  Constant & 0.089$^{***}$ (0.018) \\ 
+ post & 0.005$^{***}$ (0.001) \\ 
+  countryEEZ FSM 1 & 0.052$^{***}$ (0.001) \\ 
+  countryEEZ KIR 1 & 0.067$^{***}$ (0.002) \\ 
+  countryEEZ KIR 2 & 0.020$^{***}$ (0.001) \\ 
+  countryEEZ KIR 3 & 0.250$^{***}$ (0.003) \\ 
+  countryEEZ MHL 1 & 0.022$^{***}$ (0.001) \\ 
+  countryEEZ NRU 1 & 0.049$^{***}$ (0.001) \\ 
+  countryEEZ PNG 2 & 0.184$^{***}$ (0.004) \\ 
+  countryEEZ SLB 1 & 0.062$^{***}$ (0.002) \\ 
+  countryEEZ TUV 1 & 0.059$^{***}$ (0.001) \\ 
+  countryHS & 0.073$^{***}$ (0.001) \\ 
+  countryHS COK 1 & 0.001$^{***}$ (0.0004) \\ 
+  countryHS FSM 1 & $-$0.004$^{***}$ (0.0003) \\ 
+  countryHS KIR 1 & 0.015$^{***}$ (0.001) \\ 
+  countryHS KIR 2 & $-$0.001$^{*}$ (0.0003) \\ 
+  countryHS KIR 3 & 0.002$^{***}$ (0.0004) \\ 
+  countryHS MHL 1 & $-$0.004$^{***}$ (0.0003) \\ 
+  countryHS MUS 1 & $-$0.004$^{***}$ (0.0003) \\ 
+  countryHS NRU 1 & $-$0.003$^{***}$ (0.001) \\ 
+  countryHS PNG 2 & $-$0.001$^{*}$ (0.001) \\ 
+  countryHS SLB 1 & $-$0.003$^{***}$ (0.0003) \\ 
+  countryHS TUV 1 & $-$0.003$^{***}$ (0.0003) \\ 
+  countryPIPA PIPA 1 & 0.083$^{***}$ (0.002) \\ 
+  post:countryEEZ FSM 1 & 0.003 (0.002) \\ 
+  post:countryEEZ KIR 1 & $-$0.007$^{***}$ (0.002) \\ 
+  post:countryEEZ KIR 2 & 0.040$^{***}$ (0.003) \\ 
+  post:countryEEZ KIR 3 & $-$0.033$^{***}$ (0.005) \\ 
+  post:countryEEZ MHL 1 & $-$0.010$^{***}$ (0.002) \\ 
+  post:countryEEZ NRU 1 & $-$0.005$^{***}$ (0.002) \\ 
+  post:countryEEZ PNG 2 & $-$0.096$^{***}$ (0.004) \\ 
+  post:countryEEZ SLB 1 & 0.026$^{***}$ (0.004) \\ 
+  post:countryEEZ TUV 1 & 0.007$^{***}$ (0.002) \\ 
+  post:countryHS & 0.034$^{***}$ (0.002) \\ 
+  post:countryHS COK 1 & $-$0.005$^{***}$ (0.001) \\ 
+  post:countryHS FSM 1 & $-$0.005$^{***}$ (0.001) \\ 
+  post:countryHS KIR 1 & 0.024$^{***}$ (0.001) \\ 
+  post:countryHS KIR 2 & 0.005$^{***}$ (0.001) \\ 
+  post:countryHS KIR 3 & 0.020$^{***}$ (0.001) \\ 
+  post:countryHS MHL 1 & $-$0.004$^{***}$ (0.001) \\ 
+  post:countryHS MUS 1 & $-$0.005$^{***}$ (0.001) \\ 
+  post:countryHS NRU 1 & $-$0.006$^{***}$ (0.001) \\ 
+  post:countryHS PNG 2 & $-$0.007$^{***}$ (0.001) \\ 
+  post:countryHS SLB 1 & $-$0.006$^{***}$ (0.001) \\ 
+  post:countryHS TUV 1 & $-$0.005$^{***}$ (0.001) \\ 
+  post:countryPIPA PIPA 1 & $-$0.088$^{***}$ (0.002) \\ 
+  Constant & 0.004$^{***}$ (0.0003) \\ 
  \hline \\[-1.8ex] 
-Observations & 864 \\ 
-R$^{2}$ & 0.557 \\ 
+Observations & 69,048 \\ 
+R$^{2}$ & 0.370 \\ 
 \hline 
@@
 
-\section{Appendix}\label{appendix}
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{other-model-specifications}{%
+\subsection{Other model
+specifications}\label{other-model-specifications}}
+
+\hypertarget{year-as-dummy-variables}{%
+\subsubsection{Year as dummy variables}\label{year-as-dummy-variables}}
 
@@
 \hline \\[-1.8ex] 
- post & 95.087$^{***}$ & 99.232$^{***}$ & 146.372$^{***}$ & 119.222$^{***}$ \\ 
-  & (5.877) & (5.453) & (6.926) & (6.717) \\ 
+ post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
+  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
   & & & & \\ 
- treated & $-$6.575 & $-$5.597 & $-$6.050 & 2.925 \\ 
-  & (4.985) & (4.564) & (4.095) & (5.052) \\ 
+ treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
+  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
   & & & & \\ 
- post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$14.748$^{**}$ & $-$16.231$^{**}$ \\ 
-  & (6.856) & (6.460) & (6.152) & (6.692) \\ 
+ post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
+  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
   & & & & \\ 
- Constant & 59.490$^{***}$ & 65.485$^{***}$ & 36.643$^{***}$ & 53.138$^{***}$ \\ 
-  & (4.422) & (6.132) & (6.462) & (10.394) \\ 
+ Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
+  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
   & & & & \\ 
@@
 Flag FE & No & No & No & Yes \\ 
-Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
-R$^{2}$ & 0.171 & 0.243 & 0.301 & 0.320 \\ 
+Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
+R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
 \hline 
@@
 \hline \\[-1.8ex] 
- post & $-$11.929 & $-$6.968 & 8.201 & 17.751$^{*}$ \\ 
-  & (7.969) & (7.975) & (11.119) & (10.388) \\ 
+ post & $-$1.241$^{***}$ & $-$1.026$^{***}$ & $-$0.944$^{***}$ & 13.292$^{***}$ \\ 
+  & (0.116) & (0.116) & (0.157) & (0.330) \\ 
   & & & & \\ 
- treated & 70.142$^{***}$ & 72.314$^{***}$ & 72.243$^{***}$ & 13.875$^{*}$ \\ 
-  & (7.200) & (7.200) & (7.283) & (7.992) \\ 
+ treated & 2.595$^{***}$ & 2.708$^{***}$ & 2.639$^{***}$ & 1.493$^{***}$ \\ 
+  & (0.101) & (0.101) & (0.102) & (0.116) \\ 
   & & & & \\ 
- post:treated & $-$9.851 & $-$12.290 & $-$13.287 & $-$14.750 \\ 
-  & (9.294) & (9.262) & (9.344) & (9.569) \\ 
+ post:treated & 0.053 & $-$0.069 & $-$0.029 & $-$0.060 \\ 
+  & (0.133) & (0.133) & (0.134) & (0.135) \\ 
   & & & & \\ 
- Constant & 474.478$^{***}$ & 449.960$^{***}$ & 449.666$^{***}$ & 429.919$^{***}$ \\ 
-  & (6.328) & (9.440) & (11.122) & (27.606) \\ 
+ Constant & 39.032$^{***}$ & 38.105$^{***}$ & 38.388$^{***}$ & 36.993$^{***}$ \\ 
+  & (0.089) & (0.131) & (0.150) & (0.178) \\ 
   & & & & \\ 
@@
 Flag FE & No & No & No & Yes \\ 
-Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
-R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
+Observations & 227,873 & 227,873 & 227,873 & 227,873 \\ 
+R$^{2}$ & 0.010 & 0.015 & 0.016 & 0.030 \\ 
 \hline 
@@
 
+\begin{verbatim}
+## [[1]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated  post:treated  
+##      11.7380        8.3944       -1.0687       -0.7009  
+## 
+## 
+## [[2]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##      11.2808        9.3338       -0.7699        2.8855        3.6875  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##       3.0010       -0.9889       -2.2384       -3.6433       -4.5904  
+##     month_c6      month_c7      month_c8      month_c9  post:treated  
+##      -4.4198       -3.5805        0.3173        2.8648       -0.8990  
+## 
+## 
+## [[3]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##     13.94161       9.13865       0.04064       2.63902       3.55558  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##      2.59370      -1.06244      -2.41158      -4.00798      -4.91378  
+##     month_c6      month_c7      month_c8      month_c9       flagECU  
+##     -4.97737      -3.35106       0.20410       2.30467      -6.18817  
+##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
+##     -2.94857      -4.72899      -3.70832      -1.87867      -2.24359  
+##      flagTWN  post:treated  
+##     -2.49301      -0.90817
+\end{verbatim}
+
+\begin{verbatim}
+## [[1]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated  post:treated  
+##     11.41504       8.22194      -0.01516      -2.01435  
+## 
+## 
+## [[2]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##      10.9718        8.6646        0.0589        3.1399        4.2030  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##       2.8778       -0.8801       -2.1805       -4.0561       -4.0234  
+##     month_c6      month_c7      month_c8      month_c9  post:treated  
+##      -4.7427       -4.4566        0.9716        4.9466       -2.0474  
+## 
+## 
+## [[3]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##        8.160         8.923         2.910         3.489         4.775  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##        3.087        -1.082        -1.776        -4.186        -4.108  
+##     month_c6      month_c7      month_c8      month_c9       flagMHL  
+##       -5.336        -4.115         1.249         4.322         2.969  
+## post:treated  
+##       -2.984
+\end{verbatim}
+
+\begin{verbatim}
+## [[1]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated  post:treated  
+##      11.1998        9.0182       -0.5304       -1.3247  
+## 
+## 
+## [[2]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##     10.74814      10.57403      -0.03924       2.43719       3.37646  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##      2.62526      -1.19664      -2.77934      -3.76747      -4.65285  
+##     month_c6      month_c7      month_c8      month_c9  post:treated  
+##     -4.79738      -3.64640       0.15290       3.15125      -2.13569  
+## 
+## 
+## [[3]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##      14.3391       10.4923        0.4295        2.2241        3.1505  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##       2.0719       -1.2564       -2.8501       -4.0129       -5.0320  
+##     month_c6      month_c7      month_c8      month_c9       flagECU  
+##      -5.3231       -3.4871       -0.2020        2.2869       -5.4622  
+##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
+##      -3.3566       -1.4486       -4.2977       -2.3611       -3.3106  
+##      flagTWN  post:treated  
+##      -3.2657       -2.2534
+\end{verbatim}
+
+\begin{verbatim}
+## [[1]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated  post:treated  
+##      11.4202        7.8750       -0.7508       -0.1815  
+## 
+## 
+## [[2]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c, data = data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##      10.9725        8.7780       -0.4452        2.8476        3.6473  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##       3.0113       -1.1434       -2.4295       -3.5424       -4.4423  
+##     month_c6      month_c7      month_c8      month_c9  post:treated  
+##      -4.5243       -3.6704        0.2277        3.0019       -0.3310  
+## 
+## 
+## [[3]]
+## 
+## Call:
+## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
+## 
+## Coefficients:
+##  (Intercept)          post       treated     month_c10     month_c11  
+##    14.036151      8.770151      0.557241      2.444760      3.320156  
+##    month_c12      month_c2      month_c3      month_c4      month_c5  
+##     2.456643     -1.307835     -2.707138     -4.024565     -4.841901  
+##     month_c6      month_c7      month_c8      month_c9       flagECU  
+##    -5.275270     -3.545459      0.001697      2.319940     -6.396277  
+##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
+##    -3.432356     -4.833825     -4.212230     -1.836510     -3.284000  
+##      flagTWN  post:treated  
+##    -2.637666     -0.454598
+\end{verbatim}
+
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-4.pdf}
+
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-4.pdf}
+
 \clearpage

### 2018-10-13 docs/Manuscript.tex
Updated intro

@@
-\documentclass[12pt,]{article}
+\documentclass[11pt,]{article}
 \usepackage{lmodern}
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 % Redefines (sub)paragraphs to behave more like sections
@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-10-11}
+  \subtitle{Updated on 2018-10-12}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 Marine Protected Areas (MPAs) are intended to safeguard parts of the
-ocean from extractive activities such as fishing. Current international
-goals aim to ``effectively protect 10\% of the ocean environments by
-2020''. In an effort to meet this target, the world has seen a rapid
-increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
-part of this rapid increase can be attributed to the designation of a
-small number of Large Scale Marine Protected Areas {[}LSMPAs;
-\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
-km\textsuperscript{2} in extension \citep{toonen_2013}, and are often
-implemented in the pelagic environment, where the dominant human
-activity is industrial fishing \citep{gray_2017}.
+ocean from fishing and other extractive activities. Current
+international goals aim to ``effectively protect 10\% of the ocean
+environments by 2020''. In an effort to meet this target, the world has
+seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}. A
+significant part of this rapid increase can be attributed to the
+designation of a small number of Large Scale Marine Protected Areas
+{[}LSMPAs; \citep{gray_2017}{]}. These are defined as MPAS with at least
+250,000 Km\textsuperscript{2} in extension (Fig. \ref{fig:LSMPAs_map}),
+and are often implemented in the pelagic environment, where the dominant
+human activity is industrial fishing
+\citep{toonen_2013,gray_2017,kroodsma_2018}.
 
 Due to weak property rights, limited habitat transformation, and
-potentially lower management costs, pelagic MPAs provide a great
-opportunity to safeguard the oceans \citet{game_2009}{[}\^{}d{]}. A
-growing body of literature has also shown that closing the high seas to
-all fishing -effectively, turning them into a LSMPA- could increase
-fishery yields and profitability of fisheries, without negligible costs
-to food security
-\citep{white_2014,sumaila_2015,sala_2018,schiller_2018}. However, as
+potentially lower management costs, pelagic MPAs provide an opportunity
+to safeguard the oceans \citet{game_2009}. A growing body of literature
+has shown that closing the high seas to all fishing -effectively,
+turning them into a LSMPA- could increase fishery yields and
+profitability of fisheries, with negligible costs to food security
+\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. However, as
 with customary MPAs, it is important that we understand the
@@
 governance and enforcement, but are yet to be the focus of economic
-analyses \citep{gray_2017}. For example, \citet{mcdermott_2018} show
-that fishing effort within the Phoenix Islands Marine Protected Area
-(PIPA) is effectively reduced after implementation, and describe changes
-in fishing behavior pre-implementation. \citet{cabral_2017} analyse the
-redistribution of fishing and non-fishing vessels following the
-implementation of MPAs in California, and find that responses are
-idiosyncratic; commercial dive boats follow a fishing-the-line pattern,
-while some fishing boats follow an ideal free distribution. The way in
-which fishers react to a spatial closure can have major implications in
-its outcome \citep{hilborn_2006,krueck_2017,viana_2017}. This highlights
-the need to understand how fishers react to the implementation of a
-LSMPA, and fishing effort changes and is spatially redistributed.
+analyses \citep{gray_2017}.
 
-The main objective of this paper is to identify how fishers adapt to the
-implementation of LSMPAs. We combine novel vessel tracking technologies
-and causal inference techniques to identify behavioral changes of
-fishing vessels due to the implementation of PIPA. We focus on fishing
-hours and distance traveled as outcome variables that fishers might
-adjust following implementation of a LSMPA in an impact-evaluation
-fashion. Additionally, we evaluate the spatial redistribution of fishing
-effort that existed within PIPA before its implementation. This work
-provides novel empirical insights into fisher's responses to the
-implementation of LSMPAs, and can help guide future interventions.
+Research on LSMPAs have been the focus of analysing X, Y, and Z.
+However, no studies look into displacement of fishing effort.
+Redistribution of fishing effort has been evaluated in ssf by X, Y ,and
+Z. \citet{cabral_2017} analyse the redistribution of fishing and
+non-fishing vessels following the implementation of MPAs in California,
+and find that responses are idiosyncratic; commercial dive boats follow
+a fishing-the-line pattern, while some fishing boats follow an ideal
+free distribution. The way in which fishers react to a spatial closure
+can have major implications in its outcome
+\citep{smith_2003,hilborn_2006}. This highlights the need to understand
+how fishers react to the implementation of a LSMPA, and fishing effort
+changes and is spatially redistributed.
+
+The main objective of this paper is to identify how fishers change their
+behavior due to the implementation of LSMPAs. We combine novel vessel
+tracking technologies and causal inference techniques to identify
+behavioral changes of fishing vessels due to the implementation of PIPA.
+We focus on fishing hours and distance traveled as outcome variables
+that fishers might adjust following implementation of a LSMPA in an
+impact-evaluation fashion. Additionally, we evaluate the spatial
+redistribution of fishing effort that existed within PIPA before its
+implementation. This work provides novel empirical insights into
+fisher's responses to the implementation of LSMPAs, and can help guide
+future interventions. Our work is novel in the sense that it provides
+empirical evidence of the effect of large-acale Marine Protected Areas
+in fishing behavior and distribution.
+
+The next sections are as follows: Section \ref{background} provides an
+overview of the Nauru Agreement and associated countries, a description
+of the fleet that operates in the region, and a brief history of PIPA.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion}
+provides an extension of our results to other LSMPAs and discusses our
+results.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}}
+\end{figure}
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+The Nauru Agreement was established in 1982 by Pacific island nations to
+manage their important tuna resources. PNA Members include Federated
+States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua
+New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated
+access of foreign vessels (\emph{i.e.} those from non-PNA countries).
+Holding \textasciitilde{}80\% of the historical purse seining grounds
+within their Exclusive Economic Zones, PNA countries gained bargaining
+power when providing access to foreign fleets \citep{havice_2010}.
+
+The cooperation that emerged thanks to the PNA allowed for subsequent
+agreements that strengthened fisheries management, like the Palau
+Agreement, which limited the number of purse seiners at 205 vessels from
+1995-2007\footnote{See \citet{havice_2010} for a detailed description of
+  the Nauru, Palau, and Federal States of Micronesia agreements, their
+  objectives, and outcomes.}. However, the most notable regulation is
+their approach to manage fishing effort: a Vessel Day Scheme (VDS)
+implemented in 2007 \citep{havice_2013}. This effectively modified how
+fishing effort was managed, from number of vessels under the Palau
+Agreement to fishing hours. The VDS works as follows: Each year,
+scientific advisors recomend a total number of fishing vessel-days per
+year. Hours are allocated to each PNA country based on catch history,
+and they then sell fishing rights to other non-PNA countries
+\citep{aqorau_2018}. While the effectiveness of this scheme has been
+debated in terms of meeting their fishery management and conservation
+objectives, the licensing significantly contributes to the economy of
+these island nations \citep{havice_2010}.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}}
+\end{figure}
+
+The main tuna species caught in the region are skipjack
+(\emph{Katsuwonus pelamis}), yellowfin (\emph{Thunnus albacares}),
+albacore (\emph{Thunnus alalunga}) and bigeye (\emph{Thunnus obesus}).
+From these, the first two are amongst the top-10 species represented in
+global fisheries production statistics, with catches increasing relative
+to the 2005-2014 average \citep{fao_2018}. The pacific region has
+historically accounted for a large portion of tuna species production
+\citep{aqorau_1997}. Today, the PNA controls close to 50\% of the global
+skipjack tuna production \citep{pna_website_2018}. A large portion of
+these catches derive from purse seine vessels licensed under the VDS.
+Fishing vessels from Australia, New Zeland, China, France, Korea, Japan,
+the Philippines, Taiwan and the United States participate in the
+purse-seining vessel day schemes.
+
+For example, \citet{mcdermott_2018} show that fishing effort within the
+Phoenix Islands Marine Protected Area (PIPA) is effectively reduced
+after implementation, and describe changes in fishing behavior
+pre-implementation.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-\caption{\label{fig:unnamed-chunk-20}\label{fig:baci_strict}Stream of
-fishing events by vessels through time. Each line represents a vessel,
-with dots indicating months with fishing activity and colors indicating
-the pre and post periods.}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:unnamed-chunk-6}\label{fig:baci_strict}Stream of fishing
+events by vessels through time. Each line represents a vessel, with dots
+indicating months with fishing activity and colors indicating the pre
+and post periods.}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-21}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
+\caption{\label{tab:unnamed-chunk-7}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:all_vessels}Fishing hours
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
 and number of vessels by month for all vessels. Vertical dashed line
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
-\caption{\label{fig:unnamed-chunk-29}\label{fig:redist_trend_ps}Monthly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
-\caption{\label{fig:unnamed-chunk-31}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
@@
 
-\hypertarget{discusion}{%
-\section{Discusion}\label{discusion}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 \begin{verbatim}
-## [[1]]
 ## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.7380        8.3944       -1.0687       -0.7009  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      11.2808        9.3338       -0.7699        2.8855        3.6875  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       3.0010       -0.9889       -2.2384       -3.6433       -4.5904  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.4198       -3.5805        0.3173        2.8648       -0.8990  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##     13.94161       9.13865       0.04064       2.63902       3.55558  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##      2.59370      -1.06244      -2.41158      -4.00798      -4.91378  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##     -4.97737      -3.35106       0.20410       2.30467      -6.18817  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##     -2.94857      -4.72899      -3.70832      -1.87867      -2.24359  
-##      flagTWN  post:treated  
-##     -2.49301      -0.90817
+## % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+## % Date and time: vie., oct. 12, 2018 - 06:16:13 p. m.
+## \begin{table}[!htbp] \centering 
+##   \caption{} 
+##   \label{} 
+## \begin{tabular}{@{\extracolsep{5pt}}lccc} 
+## \\[-1.8ex]\hline 
+## \hline \\[-1.8ex] 
+##  & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+## \cline{2-4} 
+## \\[-1.8ex] & \multicolumn{3}{c}{hours} \\ 
+## \\[-1.8ex] & (1) & (2) & (3)\\ 
+## \hline \\[-1.8ex] 
+##  post & 8.394$^{***}$ & 9.334$^{***}$ & 9.139$^{***}$ \\ 
+##   & (0.271) & (0.265) & (0.300) \\ 
+##   & & & \\ 
+##  treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & 0.041 \\ 
+##   & (0.259) & (0.253) & (0.317) \\ 
+##   & & & \\ 
+##  month\_c10 &  & 2.885$^{***}$ & 2.639$^{***}$ \\ 
+##   &  & (0.302) & (0.335) \\ 
+##   & & & \\ 
+##  month\_c11 &  & 3.687$^{***}$ & 3.556$^{***}$ \\ 
+##   &  & (0.304) & (0.335) \\ 
+##   & & & \\ 
+##  month\_c12 &  & 3.001$^{***}$ & 2.594$^{***}$ \\ 
+##   &  & (0.309) & (0.339) \\ 
+##   & & & \\ 
+##  month\_c2 &  & $-$0.989$^{***}$ & $-$1.062$^{***}$ \\ 
+##   &  & (0.308) & (0.334) \\ 
+##   & & & \\ 
+##  month\_c3 &  & $-$2.238$^{***}$ & $-$2.412$^{***}$ \\ 
+##   &  & (0.313) & (0.340) \\ 
+##   & & & \\ 
+##  month\_c4 &  & $-$3.643$^{***}$ & $-$4.008$^{***}$ \\ 
+##   &  & (0.317) & (0.345) \\ 
+##   & & & \\ 
+##  month\_c5 &  & $-$4.590$^{***}$ & $-$4.914$^{***}$ \\ 
+##   &  & (0.316) & (0.349) \\ 
+##   & & & \\ 
+##  month\_c6 &  & $-$4.420$^{***}$ & $-$4.977$^{***}$ \\ 
+##   &  & (0.332) & (0.368) \\ 
+##   & & & \\ 
+##  month\_c7 &  & $-$3.580$^{***}$ & $-$3.351$^{***}$ \\ 
+##   &  & (0.336) & (0.366) \\ 
+##   & & & \\ 
+##  month\_c8 &  & 0.317 & 0.204 \\ 
+##   &  & (0.311) & (0.346) \\ 
+##   & & & \\ 
+##  month\_c9 &  & 2.865$^{***}$ & 2.305$^{***}$ \\ 
+##   &  & (0.309) & (0.341) \\ 
+##   & & & \\ 
+##  flagECU &  &  & $-$6.188$^{***}$ \\ 
+##   &  &  & (0.434) \\ 
+##   & & & \\ 
+##  flagESP &  &  & $-$2.949$^{***}$ \\ 
+##   &  &  & (0.497) \\ 
+##   & & & \\ 
+##  flagFSM &  &  & $-$4.729$^{***}$ \\ 
+##   &  &  & (0.470) \\ 
+##   & & & \\ 
+##  flagKOR &  &  & $-$3.708$^{***}$ \\ 
+##   &  &  & (0.289) \\ 
+##   & & & \\ 
+##  flagMHL &  &  & $-$1.879$^{***}$ \\ 
+##   &  &  & (0.310) \\ 
+##   & & & \\ 
+##  flagOTH &  &  & $-$2.244$^{***}$ \\ 
+##   &  &  & (0.290) \\ 
+##   & & & \\ 
+##  flagTWN &  &  & $-$2.493$^{***}$ \\ 
+##   &  &  & (0.332) \\ 
+##   & & & \\ 
+##  post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.908$^{***}$ \\ 
+##   & (0.314) & (0.306) & (0.344) \\ 
+##   & & & \\ 
+##  Constant & 11.738$^{***}$ & 11.281$^{***}$ & 13.942$^{***}$ \\ 
+##   & (0.229) & (0.313) & (0.422) \\ 
+##   & & & \\ 
+## \hline \\[-1.8ex] 
+## Observations & 37,840 & 37,840 & 30,359 \\ 
+## R$^{2}$ & 0.087 & 0.136 & 0.151 \\ 
+## Adjusted R$^{2}$ & 0.087 & 0.136 & 0.150 \\ 
+## Residual Std. Error & 12.752 (df = 37836) & 12.405 (df = 37825) & 12.257 (df = 30337) \\ 
+## F Statistic & 1,203.929$^{***}$ (df = 3; 37836) & 427.020$^{***}$ (df = 14; 37825) & 256.286$^{***}$ (df = 21; 30337) \\ 
+## \hline 
+## \hline \\[-1.8ex] 
+## \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+## \end{tabular} 
+## \end{table}
 \end{verbatim}
@@
 \begin{verbatim}
-## [[1]]
 ## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##     11.41504       8.22194      -0.01516      -2.01435  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      10.9718        8.6646        0.0589        3.1399        4.2030  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       2.8778       -0.8801       -2.1805       -4.0561       -4.0234  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.7427       -4.4566        0.9716        4.9466       -2.0474  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##        8.160         8.923         2.910         3.489         4.775  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##        3.087        -1.082        -1.776        -4.186        -4.108  
-##     month_c6      month_c7      month_c8      month_c9       flagMHL  
-##       -5.336        -4.115         1.249         4.322         2.969  
-## post:treated  
-##       -2.984
+## % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+## % Date and time: vie., oct. 12, 2018 - 06:16:13 p. m.
+## \begin{table}[!htbp] \centering 
+##   \caption{} 
+##   \label{} 
+## \begin{tabular}{@{\extracolsep{5pt}}lccc} 
+## \\[-1.8ex]\hline 
+## \hline \\[-1.8ex] 
+##  & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+## \cline{2-4} 
+## \\[-1.8ex] & \multicolumn{3}{c}{hours} \\ 
+## \\[-1.8ex] & (1) & (2) & (3)\\ 
+## \hline \\[-1.8ex] 
+##  post & 8.222$^{***}$ & 8.665$^{***}$ & 8.923$^{***}$ \\ 
+##   & (0.444) & (0.431) & (0.429) \\ 
+##   & & & \\ 
+##  treated & $-$0.015 & 0.059 & 2.910$^{***}$ \\ 
+##   & (0.475) & (0.462) & (0.602) \\ 
+##   & & & \\ 
+##  month\_c10 &  & 3.140$^{***}$ & 3.489$^{***}$ \\ 
+##   &  & (0.711) & (0.877) \\ 
+##   & & & \\ 
+##  month\_c11 &  & 4.203$^{***}$ & 4.775$^{***}$ \\ 
+##   &  & (0.695) & (0.828) \\ 
+##   & & & \\ 
+##  month\_c12 &  & 2.878$^{***}$ & 3.087$^{***}$ \\ 
+##   &  & (0.699) & (0.837) \\ 
+##   & & & \\ 
+##  month\_c2 &  & $-$0.880 & $-$1.082 \\ 
+##   &  & (0.739) & (0.885) \\ 
+##   & & & \\ 
+##  month\_c3 &  & $-$2.181$^{***}$ & $-$1.776$^{**}$ \\ 
+##   &  & (0.740) & (0.891) \\ 
+##   & & & \\ 
+##  month\_c4 &  & $-$4.056$^{***}$ & $-$4.186$^{***}$ \\ 
+##   &  & (0.745) & (0.893) \\ 
+##   & & & \\ 
+##  month\_c5 &  & $-$4.023$^{***}$ & $-$4.108$^{***}$ \\ 
+##   &  & (0.730) & (0.891) \\ 
+##   & & & \\ 
+##  month\_c6 &  & $-$4.743$^{***}$ & $-$5.336$^{***}$ \\ 
+##   &  & (0.779) & (0.968) \\ 
+##   & & & \\ 
+##  month\_c7 &  & $-$4.457$^{***}$ & $-$4.115$^{***}$ \\ 
+##   &  & (0.815) & (1.022) \\ 
+##   & & & \\ 
+##  month\_c8 &  & 0.972 & 1.249 \\ 
+##   &  & (0.724) & (0.895) \\ 
+##   & & & \\ 
+##  month\_c9 &  & 4.947$^{***}$ & 4.322$^{***}$ \\ 
+##   &  & (0.714) & (0.878) \\ 
+##   & & & \\ 
+##  flagMHL &  &  & 2.969$^{***}$ \\ 
+##   &  &  & (0.467) \\ 
+##   & & & \\ 
+##  post:treated & $-$2.014$^{***}$ & $-$2.047$^{***}$ & $-$2.984$^{***}$ \\ 
+##   & (0.610) & (0.592) & (0.766) \\ 
+##   & & & \\ 
+##  Constant & 11.415$^{***}$ & 10.972$^{***}$ & 8.160$^{***}$ \\ 
+##   & (0.342) & (0.616) & (0.835) \\ 
+##   & & & \\ 
+## \hline \\[-1.8ex] 
+## Observations & 7,756 & 7,756 & 5,288 \\ 
+## R$^{2}$ & 0.069 & 0.132 & 0.145 \\ 
+## Adjusted R$^{2}$ & 0.069 & 0.131 & 0.142 \\ 
+## Residual Std. Error & 13.095 (df = 7752) & 12.652 (df = 7741) & 12.518 (df = 5272) \\ 
+## F Statistic & 191.591$^{***}$ (df = 3; 7752) & 84.244$^{***}$ (df = 14; 7741) & 59.406$^{***}$ (df = 15; 5272) \\ 
+## \hline 
+## \hline \\[-1.8ex] 
+## \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+## \end{tabular} 
+## \end{table}
 \end{verbatim}
@@
 \begin{verbatim}
-## [[1]]
 ## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.1998        9.0182       -0.5304       -1.3247  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##     10.74814      10.57403      -0.03924       2.43719       3.37646  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##      2.62526      -1.19664      -2.77934      -3.76747      -4.65285  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##     -4.79738      -3.64640       0.15290       3.15125      -2.13569  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      14.3391       10.4923        0.4295        2.2241        3.1505  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       2.0719       -1.2564       -2.8501       -4.0129       -5.0320  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##      -5.3231       -3.4871       -0.2020        2.2869       -5.4622  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##      -3.3566       -1.4486       -4.2977       -2.3611       -3.3106  
-##      flagTWN  post:treated  
-##      -3.2657       -2.2534
+## % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+## % Date and time: vie., oct. 12, 2018 - 06:16:14 p. m.
+## \begin{table}[!htbp] \centering 
+##   \caption{} 
+##   \label{} 
+## \begin{tabular}{@{\extracolsep{5pt}}lccc} 
+## \\[-1.8ex]\hline 
+## \hline \\[-1.8ex] 
+##  & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+## \cline{2-4} 
+## \\[-1.8ex] & \multicolumn{3}{c}{hours} \\ 
+## \\[-1.8ex] & (1) & (2) & (3)\\ 
+## \hline \\[-1.8ex] 
+##  post & 9.018$^{***}$ & 10.574$^{***}$ & 10.492$^{***}$ \\ 
+##   & (0.746) & (0.727) & (0.722) \\ 
+##   & & & \\ 
+##  treated & $-$0.530 & $-$0.039 & 0.430 \\ 
+##   & (0.629) & (0.612) & (0.683) \\ 
+##   & & & \\ 
+##  month\_c10 &  & 2.437$^{***}$ & 2.224$^{***}$ \\ 
+##   &  & (0.347) & (0.386) \\ 
+##   & & & \\ 
+##  month\_c11 &  & 3.376$^{***}$ & 3.150$^{***}$ \\ 
+##   &  & (0.350) & (0.389) \\ 
+##   & & & \\ 
+##  month\_c12 &  & 2.625$^{***}$ & 2.072$^{***}$ \\ 
+##   &  & (0.357) & (0.394) \\ 
+##   & & & \\ 
+##  month\_c2 &  & $-$1.197$^{***}$ & $-$1.256$^{***}$ \\ 
+##   &  & (0.354) & (0.386) \\ 
+##   & & & \\ 
+##  month\_c3 &  & $-$2.779$^{***}$ & $-$2.850$^{***}$ \\ 
+##   &  & (0.360) & (0.395) \\ 
+##   & & & \\ 
+##  month\_c4 &  & $-$3.767$^{***}$ & $-$4.013$^{***}$ \\ 
+##   &  & (0.361) & (0.397) \\ 
+##   & & & \\ 
+##  month\_c5 &  & $-$4.653$^{***}$ & $-$5.032$^{***}$ \\ 
+##   &  & (0.362) & (0.402) \\ 
+##   & & & \\ 
+##  month\_c6 &  & $-$4.797$^{***}$ & $-$5.323$^{***}$ \\ 
+##   &  & (0.381) & (0.426) \\ 
+##   & & & \\ 
+##  month\_c7 &  & $-$3.646$^{***}$ & $-$3.487$^{***}$ \\ 
+##   &  & (0.381) & (0.417) \\ 
+##   & & & \\ 
+##  month\_c8 &  & 0.153 & $-$0.202 \\ 
+##   &  & (0.358) & (0.399) \\ 
+##   & & & \\ 
+##  month\_c9 &  & 3.151$^{***}$ & 2.287$^{***}$ \\ 
+##   &  & (0.354) & (0.393) \\ 
+##   & & & \\ 
+##  flagECU &  &  & $-$5.462$^{***}$ \\ 
+##   &  &  & (0.585) \\ 
+##   & & & \\ 
+##  flagESP &  &  & $-$3.357$^{***}$ \\ 
+##   &  &  & (0.557) \\ 
+##   & & & \\ 
+##  flagFSM &  &  & $-$1.449$^{**}$ \\ 
+##   &  &  & (0.675) \\ 
+##   & & & \\ 
+##  flagKOR &  &  & $-$4.298$^{***}$ \\ 
+##   &  &  & (0.379) \\ 
+##   & & & \\ 
+##  flagMHL &  &  & $-$2.361$^{***}$ \\ 
+##   &  &  & (0.501) \\ 
+##   & & & \\ 
+##  flagOTH &  &  & $-$3.311$^{***}$ \\ 
+##   &  &  & (0.402) \\ 
+##   & & & \\ 
+##  flagTWN &  &  & $-$3.266$^{***}$ \\ 
+##   &  &  & (0.473) \\ 
+##   & & & \\ 
+##  post:treated & $-$1.325$^{*}$ & $-$2.136$^{***}$ & $-$2.253$^{***}$ \\ 
+##   & (0.762) & (0.742) & (0.742) \\ 
+##   & & & \\ 
+##  Constant & 11.200$^{***}$ & 10.748$^{***}$ & 14.339$^{***}$ \\ 
+##   & (0.617) & (0.654) & (0.812) \\ 
+##   & & & \\ 
+## \hline \\[-1.8ex] 
+## Observations & 28,315 & 28,315 & 22,766 \\ 
+## R$^{2}$ & 0.083 & 0.134 & 0.144 \\ 
+## Adjusted R$^{2}$ & 0.083 & 0.133 & 0.143 \\ 
+## Residual Std. Error & 12.672 (df = 28311) & 12.322 (df = 28300) & 12.231 (df = 22744) \\ 
+## F Statistic & 857.512$^{***}$ (df = 3; 28311) & 311.587$^{***}$ (df = 14; 28300) & 182.169$^{***}$ (df = 21; 22744) \\ 
+## \hline 
+## \hline \\[-1.8ex] 
+## \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+## \end{tabular} 
+## \end{table}
 \end{verbatim}
@@
 \begin{verbatim}
-## [[1]]
 ## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.4202        7.8750       -0.7508       -0.1815  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      10.9725        8.7780       -0.4452        2.8476        3.6473  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       3.0113       -1.1434       -2.4295       -3.5424       -4.4423  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.5243       -3.6704        0.2277        3.0019       -0.3310  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##    14.036151      8.770151      0.557241      2.444760      3.320156  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##     2.456643     -1.307835     -2.707138     -4.024565     -4.841901  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##    -5.275270     -3.545459      0.001697      2.319940     -6.396277  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##    -3.432356     -4.833825     -4.212230     -1.836510     -3.284000  
-##      flagTWN  post:treated  
-##    -2.637666     -0.454598
+## % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+## % Date and time: vie., oct. 12, 2018 - 06:16:14 p. m.
+## \begin{table}[!htbp] \centering 
+##   \caption{} 
+##   \label{} 
+## \begin{tabular}{@{\extracolsep{5pt}}lccc} 
+## \\[-1.8ex]\hline 
+## \hline \\[-1.8ex] 
+##  & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
+## \cline{2-4} 
+## \\[-1.8ex] & \multicolumn{3}{c}{hours} \\ 
+## \\[-1.8ex] & (1) & (2) & (3)\\ 
+## \hline \\[-1.8ex] 
+##  post & 7.875$^{***}$ & 8.778$^{***}$ & 8.770$^{***}$ \\ 
+##   & (0.303) & (0.296) & (0.336) \\ 
+##   & & & \\ 
+##  treated & $-$0.751$^{***}$ & $-$0.445$^{*}$ & 0.557 \\ 
+##   & (0.269) & (0.262) & (0.345) \\ 
+##   & & & \\ 
+##  month\_c10 &  & 2.848$^{***}$ & 2.445$^{***}$ \\ 
+##   &  & (0.317) & (0.356) \\ 
+##   & & & \\ 
+##  month\_c11 &  & 3.647$^{***}$ & 3.320$^{***}$ \\ 
+##   &  & (0.319) & (0.355) \\ 
+##   & & & \\ 
+##  month\_c12 &  & 3.011$^{***}$ & 2.457$^{***}$ \\ 
+##   &  & (0.324) & (0.358) \\ 
+##   & & & \\ 
+##  month\_c2 &  & $-$1.143$^{***}$ & $-$1.308$^{***}$ \\ 
+##   &  & (0.326) & (0.357) \\ 
+##   & & & \\ 
+##  month\_c3 &  & $-$2.430$^{***}$ & $-$2.707$^{***}$ \\ 
+##   &  & (0.331) & (0.364) \\ 
+##   & & & \\ 
+##  month\_c4 &  & $-$3.542$^{***}$ & $-$4.025$^{***}$ \\ 
+##   &  & (0.332) & (0.365) \\ 
+##   & & & \\ 
+##  month\_c5 &  & $-$4.442$^{***}$ & $-$4.842$^{***}$ \\ 
+##   &  & (0.332) & (0.371) \\ 
+##   & & & \\ 
+##  month\_c6 &  & $-$4.524$^{***}$ & $-$5.275$^{***}$ \\ 
+##   &  & (0.349) & (0.392) \\ 
+##   & & & \\ 
+##  month\_c7 &  & $-$3.670$^{***}$ & $-$3.545$^{***}$ \\ 
+##   &  & (0.354) & (0.389) \\ 
+##   & & & \\ 
+##  month\_c8 &  & 0.228 & 0.002 \\ 
+##   &  & (0.328) & (0.368) \\ 
+##   & & & \\ 
+##  month\_c9 &  & 3.002$^{***}$ & 2.320$^{***}$ \\ 
+##   &  & (0.324) & (0.362) \\ 
+##   & & & \\ 
+##  flagECU &  &  & $-$6.396$^{***}$ \\ 
+##   &  &  & (0.515) \\ 
+##   & & & \\ 
+##  flagESP &  &  & $-$3.432$^{***}$ \\ 
+##   &  &  & (0.552) \\ 
+##   & & & \\ 
+##  flagFSM &  &  & $-$4.834$^{***}$ \\ 
+##   &  &  & (0.553) \\ 
+##   & & & \\ 
+##  flagKOR &  &  & $-$4.212$^{***}$ \\ 
+##   &  &  & (0.378) \\ 
+##   & & & \\ 
+##  flagMHL &  &  & $-$1.837$^{***}$ \\ 
+##   &  &  & (0.442) \\ 
+##   & & & \\ 
+##  flagOTH &  &  & $-$3.284$^{***}$ \\ 
+##   &  &  & (0.401) \\ 
+##   & & & \\ 
+##  flagTWN &  &  & $-$2.638$^{***}$ \\ 
+##   &  &  & (0.439) \\ 
+##   & & & \\ 
+##  post:treated & $-$0.182 & $-$0.331 & $-$0.455 \\ 
+##   & (0.342) & (0.333) & (0.379) \\ 
+##   & & & \\ 
+##  Constant & 11.420$^{***}$ & 10.972$^{***}$ & 14.036$^{***}$ \\ 
+##   & (0.239) & (0.329) & (0.548) \\ 
+##   & & & \\ 
+## \hline \\[-1.8ex] 
+## Observations & 34,489 & 34,489 & 27,008 \\ 
+## R$^{2}$ & 0.082 & 0.133 & 0.147 \\ 
+## Adjusted R$^{2}$ & 0.082 & 0.132 & 0.147 \\ 
+## Residual Std. Error & 12.712 (df = 34485) & 12.359 (df = 34474) & 12.188 (df = 26986) \\ 
+## F Statistic & 1,031.434$^{***}$ (df = 3; 34485) & 377.251$^{***}$ (df = 14; 34474) & 222.044$^{***}$ (df = 21; 26986) \\ 
+## \hline 
+## \hline \\[-1.8ex] 
+## \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+## \end{tabular} 
+## \end{table}
 \end{verbatim}
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-4.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-4.pdf}
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-4.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-4.pdf}
 

### 2018-10-13 rmd/Manuscript.Rmd
Updated intro

@@
     keep_tex: yes
-    number_sections: no
-fontsize: 12pt
+    number_sections: true
+fontsize: 11pt
 header-includes:
@@
 
-Marine Protected Areas (MPAs) are intended to safeguard parts of the ocean from extractive activities such as fishing.
+Marine Protected Areas (MPAs) are intended to safeguard parts of the ocean from fishing and other extractive activities.
 Current international goals aim to "effectively protect 10\% of the ocean environments by 2020".
-In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018b}.
+In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}.
 A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas [LSMPAs; \citep{gray_2017}].
-These are defined as MPAS with at least 250,000 km^2^ in extension \citep{toonen_2013}, and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{gray_2017}.
+These are defined as MPAS with at least 250,000 Km^2^ in extension (Fig.
+\ref{fig:LSMPAs_map}), and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{toonen_2013,gray_2017,kroodsma_2018}.
 
-Due to weak property rights, limited habitat transformation, and potentially lower management costs, pelagic MPAs provide a great opportunity to safeguard the oceans \citet{game_2009}[^d].
-A growing body of literature has also shown that closing the high seas to all fishing -effectively, turning them into a LSMPA- could increase fishery yields and profitability of fisheries, without negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018,schiller_2018}.
+Due to weak property rights, limited habitat transformation, and potentially lower management costs, pelagic MPAs provide an opportunity to safeguard the oceans \citet{game_2009}.
+A growing body of literature has shown that closing the high seas to all fishing -effectively, turning them into a LSMPA- could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
 However, as with customary MPAs, it is important that we understand the socioeconomic implications of management interventions.
@@
 LSMPAs have received great attention in terms of governance and enforcement, but are yet to be the focus of economic analyses \citep{gray_2017}.
-For example, \citet{mcdermott_2018} show that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) is effectively reduced after implementation, and describe changes in fishing behavior pre-implementation.
+
+Research on LSMPAs have been the focus of analysing X, Y, and Z.
+However, no studies look into displacement of fishing effort.
+Redistribution of fishing effort has been evaluated in ssf by X, Y ,and Z.
 \citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of MPAs in California, and find that responses are idiosyncratic; commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
-The way in which fishers react to a spatial closure can have major implications in its outcome \citep{hilborn_2006,krueck_2017,viana_2017}.
+The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006}.
 This highlights the need to understand how fishers react to the implementation of a LSMPA, and fishing effort changes and is spatially redistributed.
 
-The main objective of this paper is to identify how fishers adapt to the implementation of LSMPAs.
+The main objective of this paper is to identify how fishers change their behavior due to the implementation of LSMPAs.
 We combine novel vessel tracking technologies and causal inference techniques to identify behavioral changes of fishing vessels due to the implementation of PIPA.
@@
 This work provides novel empirical insights into fisher's responses to the implementation of LSMPAs, and can help guide future interventions.
+Our work is novel in the sense that it provides empirical evidence of the effect of large-acale Marine Protected Areas in fishing behavior and distribution.
+
+The next sections are as follows: Section \ref{background} provides an overview of the Nauru Agreement and associated countries, a description of the fleet that operates in the region, and a brief history of PIPA.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion} provides an extension of our results to other LSMPAs and discusses our results.
+
+```{r, fig.cap = "\\label{fig:LSMPAs_map}"}
+
+mpas <- read_sf(dsn = here::here("data", "spatial", "LSMPAs"), layer = "LSMPAs") %>% 
+  st_rotate() %>% 
+  mutate(PIPA = wdpaid == 309888)
+
+coast <- map_data('world', wrap=c(-20,340), ylim=c(-85,75))%>%
+  select(group, lat, long) %>%
+  st_as_sf(coords = c("long", "lat"), crs = 4326) %>%
+  group_by(group) %>% 
+  summarize(geometry = st_combine(geometry)) %>%
+  st_cast("POLYGON") %>% 
+  mutate(a = 1) %>% 
+  group_by(a) %>% 
+  summarize() %>% 
+  ungroup()
+
+pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
+  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_rotate()
+
+ggplot() +
+  geom_sf(data = coast) +
+  geom_sf(data = mpas, fill = "transparent", color = "black", size = 1) +
+  geom_sf(data = mpas, aes(fill = PIPA), color = "transparent") +
+  ggtheme_map() +
+  scale_fill_brewer(palette = "Set1", direction = -1) +
+  theme(legend.position = "none")
+```
+
+# Background
+
+The Nauru Agreement was established in 1982 by Pacific island nations to manage their important tuna resources.
+PNA Members include Federated States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated access of foreign vessels (*i.e.* those from non-PNA countries).
+Holding ~80% of the historical purse seining grounds within their Exclusive Economic Zones, PNA countries gained bargaining power when providing access to foreign fleets \citep{havice_2010}.
+
+The cooperation that emerged thanks to the PNA allowed for subsequent agreements that strengthened fisheries management, like the Palau Agreement, which limited the number of purse seiners at 205 vessels from 1995-2007[^a].
+However, the most notable regulation is their approach to manage fishing effort: a Vessel Day Scheme (VDS) implemented in 2007 \citep{havice_2013}.
+This effectively modified how fishing effort was managed, from number of vessels under the Palau Agreement to fishing hours.
+The VDS works as follows: Each year, scientific advisors recomend a total number of fishing vessel-days per year.
+Hours are allocated to each PNA country based on catch history, and they then sell fishing rights to other non-PNA countries \citep{aqorau_2018}.
+While the effectiveness of this scheme has been debated in terms of meeting their fishery management and conservation objectives, the licensing significantly contributes to the economy of these island nations \citep{havice_2010}.
+
+[^a]: See \citet{havice_2010} for a detailed description of the Nauru, Palau, and Federal States of Micronesia agreements, their objectives, and outcomes.
+
+```{r, fig.cap = "\\label{fig:PNA_map}"}
+countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI")
+
+small_coast <- rnaturalearth::ne_countries(returnclass = "sf") %>% 
+  filter(sov_a3 %in% countries) %>% 
+  st_rotate()
+
+eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"),
+               layer = "EEZ_subset") %>% 
+  filter(ISO_Ter1 %in% countries) %>% 
+  mutate(KIR = ISO_Ter1 == "KIR") %>% 
+  group_by(ISO_Ter1, PNA, KIR) %>% 
+  summarize()
+
+ggplot() +
+  geom_sf(data = small_coast) +
+  geom_sf(data = eez, aes(color = KIR, linetype = !PNA), fill = "transparent") +
+  geom_sf(data = pipa, fill = "red") +
+  ggtheme_plot() +
+  scale_color_manual(values = c("black", "red")) +
+  theme(legend.position = "none")
+```
+
+The main tuna species caught in the region are skipjack (*Katsuwonus pelamis*), yellowfin (*Thunnus albacares*), albacore (*Thunnus alalunga*) and bigeye (*Thunnus obesus*).
+From these, the first two are amongst the top-10 species represented in global fisheries production statistics, with catches increasing relative to the 2005-2014 average \citep{fao_2018}.
+The pacific region has historically accounted for a large portion of tuna species production \citep{aqorau_1997}.
+Today, the PNA controls close to 50% of the global skipjack tuna production \citep{pna_website_2018}.
+A large portion of these catches derive from purse seine vessels licensed under the VDS.
+Fishing vessels from Australia, New Zeland, China, France, Korea, Japan, the Philippines, Taiwan and the United States participate in the purse-seining vessel day schemes.
+
+For example, \citet{mcdermott_2018} show that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) is effectively reduced after implementation, and describe changes in fishing behavior pre-implementation.
 
@@
 
-```{r}
+```{r, eval = T}
 effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
@@
 
-```{r}
+```{r, eval = T}
 # Just to get pipa vessels that fished inside pipa before 2015
@@
 
-# Discusion
+# Discussion
 
@@
 ```{r}
-models_exp0_did
-models_exp1_did
-models_exp2_did
-models_exp3_did
+models_exp0_did %>% stargazer::stargazer()
+models_exp1_did %>% stargazer::stargazer()
+models_exp2_did %>% stargazer::stargazer()
+models_exp3_did %>% stargazer::stargazer()
 ```

### 2018-10-17 docs/Manuscript.tex
Updated manuscript intro and methods

--- 2018-10-12 docs/Manuscript.tex
@@
 \usepackage{natbib}
-\bibliographystyle{plainnat}
+\bibliographystyle{chicago}
 \usepackage{longtable,booktabs}
@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-10-11}
+  \subtitle{Updated on 2018-10-16}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 \linenumbers
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 
@@
 Marine Protected Areas (MPAs) are intended to safeguard parts of the
-ocean from extractive activities such as fishing. Current international
-goals aim to ``effectively protect 10\% of the ocean environments by
-2020''. In an effort to meet this target, the world has seen a rapid
-increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
-part of this rapid increase can be attributed to the designation of a
-small number of Large Scale Marine Protected Areas {[}LSMPAs;
-\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
-km\textsuperscript{2} in extension \citep{toonen_2013}, and are often
-implemented in the pelagic environment, where the dominant human
-activity is industrial fishing \citep{gray_2017}.
-
-Due to weak property rights, limited habitat transformation, and
-potentially lower management costs, pelagic MPAs provide a great
-opportunity to safeguard the oceans \citet{game_2009}{[}\^{}d{]}. A
-growing body of literature has also shown that closing the high seas to
-all fishing -effectively, turning them into a LSMPA- could increase
-fishery yields and profitability of fisheries, without negligible costs
-to food security
-\citep{white_2014,sumaila_2015,sala_2018,schiller_2018}. However, as
-with customary MPAs, it is important that we understand the
-socioeconomic implications of management interventions.
+ocean from fishing and other extractive activities. Current
+international goals aim to protect 10\% of the ocean environments by
+2020. In an effort to meet this target, the world has seen a rapid
+increase in MPA coverage \citep{wood_2008,sala_2018}. A significant part
+of this rapid increase can be attributed to the designation of a small
+number of Large Scale Marine Protected Areas (LSMPAs;
+\citet{boonzaier_2016,singleton_2014,gray_2017}). These are defined as
+MPAS larger than 250,000 Km\textsuperscript{2} in extension (Fig.
+\ref{fig:LSMPAs_map}), and are often implemented in the pelagic
+environment, where the dominant human activity is industrial fishing
+\citep{toonen_2013,gray_2017,kroodsma_2018}.
 
@@
 known about their human dimensions and implication for fisheries
-\citep{gray_2017}. LSMPAs were erroneously assumed to have little social
-implications due to their remoteness \citep{agardy_2011,gray_2017}.
-However, the anticipation of a LSMPA can lead to preemptive overfishing,
-which can erode or delay the expected benefits of the intervention
-\citep{mcdermott_2018}. LSMPAs have received great attention in terms of
-governance and enforcement, but are yet to be the focus of economic
-analyses \citep{gray_2017}. For example, \citet{mcdermott_2018} show
-that fishing effort within the Phoenix Islands Marine Protected Area
-(PIPA) is effectively reduced after implementation, and describe changes
-in fishing behavior pre-implementation. \citet{cabral_2017} analyse the
-redistribution of fishing and non-fishing vessels following the
-implementation of MPAs in California, and find that responses are
-idiosyncratic; commercial dive boats follow a fishing-the-line pattern,
+\citep{gray_2017}. Moreover, the world has seen a widespread increase in
+the implementation of LSMPAs, likely as a way to rapidly achieve the
+10\% target \citep{boonzaier_2016,alger_2017,sala_2018}. However, as
+with customary MPAs, it is important that we understand the
+socioeconomic implications of management interventions that result in
+the spatial displacement of fishing effort. They \textbf{key gap in the
+literature is X}. We adress it here by using new stuff and find results
+that are of relevance to policy makers and advance our knowledge, which
+should be incorporated when designing and planning for LSMPAs.
+
+Due to weak property rights, limited habitat transformation, and
+potentially lower management costs, pelagic MPAs provide an opportunity
+to safeguard the oceans \citet{game_2009}. A growing body of literature
+has shown that closing the high seas to all fishing could increase
+fishery yields and profitability of fisheries, with negligible costs to
+food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+
+The early literature on LSMPAs focused on the inherent difficulties that
+come with a pelagic (\emph{i.e.} open water) environment, where
+organisms typically have large home ranges. \citet{game_2009} suggest
+that most of the challenges can be overcome with the incorporation of
+technology, in what then became known as Dynamic Ocean Management
+\citep{maxwell_2015}. \citet{kaplan_2009} claim that very large MPAs
+would result in excessive opportunity costs and that these would be
+difficult to enforce. \citet{toonen_2013} show that just a small number
+of LSMPAs made up 80\% of the managed areas in the ocean in 2013, and
+that these can help achieve the CBD Aichi targets faster.
+\citet{singleton_2014} provide an objective discussion of pros and cons
+of LSMPAs.
+
+LSMPAs were erroneously assumed to have little social implications due
+to their remoteness. However, there have been calls to incorporate the
+human dimensions into LSMPAs management and evaluation
+\citep{agardy_2011,gray_2017}. Most research incorporating these human
+dimensions has focused on governance and enforcement of LSMPAs
+(\emph{i.e.} \citet{alger_2017,christie_2017}), but they are yet to be
+the focus of economic analyses \citep{gray_2017}. Overall, there has
+been little empirical work regarding LSMPAs. Recent technological
+advances in vessel-detection systems allows for the discovery and
+advancement of many important facets of LSMPAs. For example,
+\citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to
+preemptive overfishing, which can erode or delay the expected benefits
+of the intervention. \citet{white_2017} combine shark tags and
+vessel-tracking data to demonstrate that the fairly large Palmyra Atoll
+National Wildlife Refuge (54,000 Km\textsuperscript{2}) protectes two
+thrids of the tagged grey reef sharks by effectively excluding fishing
+effort. No studies have evaluated the displacement of fishing effort due
+to LSMPA implementation.
+
+The exclusion of these LSMPAs is likely to change fisher's behavior.
+Theoretical models of fishing effort redistribution range from the
+simplistic assumption that effort inside the bounded region disappears,
+to spatially explicit models that reallocate fishing effort based on
+habitat characteristics, presence of other vessels, and expected returns
+\citep{smith_2003,hilborn_2006}. However, these focus on the long term
+optimal equilibrium and redistribution of fishing effort may not be
+optimal, especially over the first years \citep{stevenson_2013}. The few
+empirical works suggest that resource users may show idiosyncratic
+responses. For example, \citet{stevenson_2013} show that a network of
+MPAs displaced fishing effort farther away from ports resulting in
+higher \emph{perceived} costs, but that catch per unit effort also
+increased. \citet{cabral_2017} analyse the redistribution of fishing and
+non-fishing vessels following the implementation of MPAs in California,
+and find that commercial dive boats follow a fishing-the-line pattern,
 while some fishing boats follow an ideal free distribution. The way in
 which fishers react to a spatial closure can have major implications in
-its outcome \citep{hilborn_2006,krueck_2017,viana_2017}. This highlights
-the need to understand how fishers react to the implementation of a
-LSMPA, and fishing effort changes and is spatially redistributed.
+its outcome \citep{smith_2003,hilborn_2006} highlighting the need to
+understand how fishers react to the implementation of LSMPAs, and
+fishing effort changes and is spatially redistributed.
 
-The main objective of this paper is to identify how fishers adapt to the
-implementation of LSMPAs. We combine novel vessel tracking technologies
-and causal inference techniques to identify behavioral changes of
-fishing vessels due to the implementation of PIPA. We focus on fishing
-hours and distance traveled as outcome variables that fishers might
-adjust following implementation of a LSMPA in an impact-evaluation
+The main objective of this paper is to identify behavioral responses to
+the implementation of LSMPAs. We combine novel vessel tracking
+technologies and causal inference techniques to identify behavioral
+changes of fishing vessels due to the implementation of PIPA. We focus
+on fishing hours and distance traveled as outcome variables that fishers
+might adjust following implementation of a LSMPA in an impact-evaluation
 fashion. Additionally, we evaluate the spatial redistribution of fishing
@@
 provides novel empirical insights into fisher's responses to the
-implementation of LSMPAs, and can help guide future interventions.
+implementation of LSMPAs, and can help guide future interventions. Our
+work is novel in the sense that it provides empirical evidence of the
+effect of large-acale Marine Protected Areas in fishing behavior and
+distribution.
+
+The next sections are as follows: Section \ref{background} provides an
+overview of the Nauru Agreement and associated countries, a description
+of the fleet that operates in the region, and a brief history of PIPA.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion}
+provides an extension of our results to other LSMPAs and discusses our
+results.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
+Protected Areas. The map shows all areas larger than 250,000
+Km\textsuperscript{2}. Areas in dark blue meet at least one of these
+conditions: reported no take area is greater than 0, are categorized as
+IUCN Ia or Ib, their designated english name is `Protected Area'.}
+\end{figure}
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+The Nauru Agreement was established in 1982 by Pacific island nations to
+manage their important tuna resources. PNA Members include Federated
+States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua
+New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated
+access of foreign vessels (\emph{i.e.} those from non-PNA countries).
+Holding \textasciitilde{}80\% of the historical purse seining grounds
+within their Exclusive Economic Zones, PNA countries gained bargaining
+power when providing access to foreign fleets \citep{havice_2010}.
+
+The cooperation that emerged thanks to the PNA allowed for subsequent
+agreements that strengthened fisheries management, like the Palau
+Agreement, which limited the number of purse seiners at 205 vessels from
+1995-2007\footnote{See \citet{havice_2010} for a detailed description of
+  the Nauru, Palau, and Federal States of Micronesia agreements, their
+  objectives, and outcomes.}. However, the most notable regulation is
+their approach to manage fishing effort: a Vessel Day Scheme (VDS)
+implemented in 2007 \citep{havice_2013}. This effectively modified how
+fishing effort was managed, from number of vessels under the Palau
+Agreement to fishing hours. The VDS works as follows: Each year,
+scientific advisors recomend a total number of fishing vessel-days per
+year. Hours are allocated to each PNA country based on catch history,
+and they then sell fishing rights to other non-PNA countries
+\citep{aqorau_2018}. While the effectiveness of this scheme has been
+debated in terms of meeting their fishery management and conservation
+objectives, the licensing significantly contributes to the economy of
+these island nations \citep{havice_2010}.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
+Economic Zones (EEZs) of the region of interest. A solid line indicates
+countries that belong to the PNA, while a dashed line indicates all
+others. A red line indicates the Kiribati EEZ, and a solid red polygon
+delineates PIPA.}
+\end{figure}
+
+The main tuna species caught in the region are skipjack
+(\emph{Katsuwonus pelamis}), yellowfin (\emph{Thunnus albacares}),
+albacore (\emph{Thunnus alalunga}) and bigeye (\emph{Thunnus obesus}).
+From these, the first two are amongst the top-10 species represented in
+global fisheries production statistics, with 2016 catches increasing
+relative to the 2005-2014 average \citep{fao_2018}. The pacific region
+has historically accounted for a large portion of tuna species
+production \citep{aqorau_1997}. Today, the PNA controls close to 50\% of
+the global skipjack tuna production \citep{pna_website_2018}. A large
+portion of these catches derive from purse seine vessels licensed under
+the VDS. Fishing vessels from Australia, New Zeland, China, France,
+Korea, Japan, the Philippines, Taiwan, and the United States participate
+in the purse-seining VDS.
+
+One of the most notable and recent management interventions in the
+region is the implementation of the Phoenix Island Protected Area (PIPA)
+by the government of Kiribati. PIPA was first declared in 2006, and
+established in 2008 with only 4\% of it was declared as no-take. In
+January 1\textsuperscript{st}, 2015, the no-take area within PIPA was
+expanded to a total area of 397,447 Km\textsuperscript{2}, roughly 1.5
+times the size of Ecuador. The implementation of such a large
+conservation area in one of the most important fishing regions in the
+world provides a great opportunity to evaluate the behavioral responses
+and redistribution of fishing effort by vessels that used to fish there.
+\citet{mcdermott_2018} showed that fishing effort within the Phoenix
+Islands Marine Protected Area (PIPA) increased between the anouncement
+(September 1\textsuperscript{st}, 2014) and its implementation in
+Janyary 1\textsuperscript{st}, 2015. Likewise, they demonstrate that
+fishing effort is effectively reduced after implementation. To this, we
+pose two questions: How do individual vessels respond to the sudden
+exclusion of such a big area? And where did all the vessels go? In the
+next sections we describe the data and methods used to answer this
+questions.
 
@@
 Our data contain over 45 million individual AIS messages (\emph{i.e.}
-positions) for 371 purse seiners and longliners. A total of 233 vessels
-have fished within PIPA waters; 217 did so at least once before 2015.
-However, not all vessels continued to fish elsewhere after PIPA
-implementation: 34 vessels have no recorded AIS messages after
-2015\footnote{The 34 missing vessels might have exited the fishery, been
-  decommissioned or sold (therefore changing their AIS and mmsi), or
-  turned off their AIS transmitters. In either case, we are not able to
-  observe these.}, leaving us with 176 vessels that fished inside PIPA
-before its implementation, and continued to fish elsewhere afterward.
+positions) for 371 fishing vessels that at some point fished in PNA
+waters. A total of 233 vessels have fished within PIPA waters; 217 did
+so at least once before 2015. However, not all vessels continued to fish
+elsewhere after PIPA implementation: 34 vessels have no recorded AIS
+messages after 2015, leaving us with 176 vessels that fished inside PIPA
+before its implementation, and continued to fish elsewhere
+afterward\footnote{The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
+In either case, we are not able to observe these.}.
+From these, we focus on purse seiners -the most important for PNA
+countries- and are left with 61
+vessels\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
 New vessels might have also entered the fishery after PIPA closure, and
@@
 
-The treatment group contains all vessels (n = 176) that fished within
-PIPA at least once before the closure, and that continued to fish
-elsewhere afterwards. Vessels in the control group meet all three of the
-following conditions: i) vessels never fished within PIPA waters, ii)
-vessels belong to other PNA countries, and iii) vessels have fished in
+The treatment group contains all purse seiners (n = 61) that fished
+within PIPA at least once before the anouncement (09/01/2014), and that
+continued to fish elsewhere after the January 2015 implementation.
+Vessels in the control group meet the following two conditions: i)
+vessels never fished within PIPA waters, and ii) vessels have fished in
 surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
-closure. For each vessel meeting these characteristics, we calculate
-their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
-a visual representation of the vessel-level fishing events that make up
-each group through time. Table \ref{tab:baci_n_s} shows the number of
-vessels following a BACI design, as well as the fishing hours, before
-and after PIPA.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-\caption{\label{fig:unnamed-chunk-20}\label{fig:baci_strict}Stream of
-fishing events by vessels through time. Each line represents a vessel,
-with dots indicating months with fishing activity and colors indicating
-the pre and post periods.}
-\end{figure}
+closure. This definition of control vessels provides us with 26 purse
+seiners that never fished inside PIPA but fished in other PNA waters
+before and after PIPA implementation. During our causal identification,
+we also use two more strict definitions of control groups: one with only
+vessels that belong to PNA countries (n = 7), and one that excludes
+Chinese vessels (n = 21). Our definition of treatment and control groups
+leaves us with 61 and 21 treated and control vessels, which have just
+over 22 million observations where about 22\% are identified as fishing
+events. For each of the remainig vessels, we calculate their total daily
+fishing hours and obtain a pannel data with 38,200 observations. Table
+\ref{tab:baci_n_s} shows the number of vessels following a BACI design,
+as well as the fishing hours, before and after PIPA. Figure
+\ref{fig:baci_strict} provides a visual representation of the
+vessel-level fishing events that make up each group through time.
 
@@
 
-\caption{\label{tab:unnamed-chunk-21}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
+\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
-\begin{tabular}[t]{llrrrr}
+\begin{tabular}[t]{lrrrr}
 \toprule
-Gear & Treatment & n & Before & After & Change (A / B)\\
+Group & n & Before & After & Change (A / B)\\
 \midrule
-drifting\_longlines & FALSE & 77 & 39.03181 & 37.79044 & 0.9681958\\
-drifting\_longlines & TRUE & 115 & 41.62659 & 40.43857 & 0.9714600\\
-purse\_seines & FALSE & 26 & 11.73804 & 20.13247 & 1.7151474\\
-purse\_seines & TRUE & 61 & 10.66939 & 18.36289 & 1.7210820\\
+Control & 26 & 11.74 & 20.13 & 1.72\\
+Treatment & 61 & 10.67 & 18.36 & 1.72\\
 \bottomrule
@@
 
-\clearpage
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
+\hypertarget{analyses}{%
+\subsection{Analyses}\label{analyses}}
 
 The first analysis focuses on identifying the response of fishing
-vessels to PIPA closure. Our variables of interests are fishing effort,
-indicated by total fishing hours per month, and distance traveled (Km)
-on every fishing trip. We compare fishing hours\footnote{And soon,
-  distance} before and after the implementation of PIPA using a
+vessels to PIPA closure. Our variables of interests are daily fishing
+hours, and daily distance traveled (Km). We compare our variable of
+interest before and after the implementation of PIPA using a
 Difference-in-Differences approach, where we track the variable of
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \]
@@
 and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
-the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
-for a second order polynomial for years (\(Y_t\)), while \(\phi_t\) and
-\(\gamma_i\) represent month-, and flag-level dummies that account for
-seasonality or country-level management interventions\footnote{An
-  earlier specification included years as a dummy variable. Such results
-  are included in the appendix, but are similar to the ones found under
-  current specification.}.
+the treatment effect. Finally, \(\phi_t\) and \(\gamma_i\) represent
+month-, and flag-level dummies that account for seasonality or
+country-level management
+interventions\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}
 
@@
 effort. In other words, identifying where do vessels that used to fish
-inside PIPA go after its establishment. We calculate the monthly
-relative distribution of fishing hours by all treated vessels across all
-fished EEZs and the high seas. These trends are shown in Figure
-\ref{fig:redist_trend_ps}, and the relative temporal change is presented
-in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
-pooled into a group of ``others'', leaving us with a total of n = 23 and
-n = 0\footnote{This number is likely to change upon finalizing the
-  spatial analysis of longliners, which is currently running.} spatially
-defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
-for purse seiners and longliners, respectively.
+inside PIPA go after its establishment. We discretize spatial units by
+using a polygon for PIPA
+\footnote{we would expect to see a decrease here} and distinct spatial
+units for each EEZ of each country. Some vessels might shift from EEZs
+into the High Seas, but we are interested in knowing \emph{where} in the
+High Seas, so we incorporate additional regions by using a 1 degree
+buffer of the High Seas arround each of the EEZ regions. The rest of the
+high seas are merged into a single spatial unit. For example, if we were
+to do this only for Kiribati, we would have 8 spatial units: PIPA, three
+EEZs, three 1-degree buffers of High Seas arround each EEZs, and the
+rest of the High Seas. Whenever the buffers overlapped between
+themselves, we randocmply clipped one on to the other. EEZs that had
+sporadic fishing events were pooled into a group of ``others''.
 
 To evaluate this change in effort allocation, we regress our variable of
-interest (\emph{i.e.}fishing hours) on the interaction between a dummy
+interest (\emph{i.e.} fishing hours) on the interaction between a dummy
 variable indicating the policy intervention and a dummy variable for
@@
 \[
-y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 \]
@@
 implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
-for countries, interpreted as individual EEZs, the high seas, and a
-group of ``other EEZs''. Our parameter of interest is \(\beta_{3,i}\),
-which captures the country-level change in proportional fishing effort.
+for countries for the spatial units defined above. Our parameter of
+interest is \(\beta_{1,i}\), which captures the country-level change in
+proportional fishing effort.
 
@@
 \href{https://github.com/jcvdav/MPA_displacement}{github}.
+
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
+\centering
+\begin{tabular}[t]{lr}
+\toprule
+country & change\\
+\midrule
+EEZ COK 1 & 0.53\\
+EEZ FSM 1 & 0.81\\
+EEZ KIR 1 & -0.16\\
+EEZ KIR 2 & 4.50\\
+EEZ KIR 3 & -2.79\\
+\addlinespace
+EEZ MHL 1 & -0.44\\
+EEZ NRU 1 & 0.07\\
+EEZ PNG 2 & -9.07\\
+EEZ SLB 1 & 3.18\\
+EEZ TUV 1 & 1.27\\
+\addlinespace
+HS & 3.93\\
+HS COK 1 & 0.06\\
+HS FSM 1 & 0.01\\
+HS KIR 1 & 2.96\\
+HS KIR 2 & 1.07\\
+\addlinespace
+HS KIR 3 & 2.53\\
+HS MHL 1 & 0.11\\
+HS MUS 1 & 0.00\\
+HS NRU 1 & -0.08\\
+HS PNG 2 & -0.20\\
+\addlinespace
+HS SLB 1 & -0.02\\
+HS TUV 1 & 0.01\\
+PIPA PIPA 1 & -8.25\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:all_vessels}Fishing hours
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels. Vertical dashed line
+indicates PIPA closure.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
 and number of vessels by month for all vessels. Vertical dashed line
@@
 the patterns observed in Figure \ref{fig:all_vessels}.
-
-Longliners show a similar pattern of effort reduction. However, the
-magnitude of the \(\beta_3\) coefficient is smaller (ranging from
-\(\beta_3 = -9.851\) to \(\beta_3 = -14.850\)) and not significant
-across all model specifications. This, along with higher standard error
-values suggest that longliners have a smaller and more variable response
-to the implementation of LSMPAs.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
-\caption{\label{fig:unnamed-chunk-31}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\label{fig:unnamed-chunk-16}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region.
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & h\_prop \\ 
-\hline \\[-1.8ex] 
- post & 0.005$^{***}$ (0.001) \\ 
-  countryEEZ FSM 1 & 0.052$^{***}$ (0.001) \\ 
-  countryEEZ KIR 1 & 0.067$^{***}$ (0.002) \\ 
-  countryEEZ KIR 2 & 0.020$^{***}$ (0.001) \\ 
-  countryEEZ KIR 3 & 0.250$^{***}$ (0.003) \\ 
-  countryEEZ MHL 1 & 0.022$^{***}$ (0.001) \\ 
-  countryEEZ NRU 1 & 0.049$^{***}$ (0.001) \\ 
-  countryEEZ PNG 2 & 0.184$^{***}$ (0.004) \\ 
-  countryEEZ SLB 1 & 0.062$^{***}$ (0.002) \\ 
-  countryEEZ TUV 1 & 0.059$^{***}$ (0.001) \\ 
-  countryHS & 0.073$^{***}$ (0.001) \\ 
-  countryHS COK 1 & 0.001$^{***}$ (0.0004) \\ 
-  countryHS FSM 1 & $-$0.004$^{***}$ (0.0003) \\ 
-  countryHS KIR 1 & 0.015$^{***}$ (0.001) \\ 
-  countryHS KIR 2 & $-$0.001$^{*}$ (0.0003) \\ 
-  countryHS KIR 3 & 0.002$^{***}$ (0.0004) \\ 
-  countryHS MHL 1 & $-$0.004$^{***}$ (0.0003) \\ 
-  countryHS MUS 1 & $-$0.004$^{***}$ (0.0003) \\ 
-  countryHS NRU 1 & $-$0.003$^{***}$ (0.001) \\ 
-  countryHS PNG 2 & $-$0.001$^{*}$ (0.001) \\ 
-  countryHS SLB 1 & $-$0.003$^{***}$ (0.0003) \\ 
-  countryHS TUV 1 & $-$0.003$^{***}$ (0.0003) \\ 
-  countryPIPA PIPA 1 & 0.083$^{***}$ (0.002) \\ 
-  post:countryEEZ FSM 1 & 0.003 (0.002) \\ 
-  post:countryEEZ KIR 1 & $-$0.007$^{***}$ (0.002) \\ 
-  post:countryEEZ KIR 2 & 0.040$^{***}$ (0.003) \\ 
-  post:countryEEZ KIR 3 & $-$0.033$^{***}$ (0.005) \\ 
-  post:countryEEZ MHL 1 & $-$0.010$^{***}$ (0.002) \\ 
-  post:countryEEZ NRU 1 & $-$0.005$^{***}$ (0.002) \\ 
-  post:countryEEZ PNG 2 & $-$0.096$^{***}$ (0.004) \\ 
-  post:countryEEZ SLB 1 & 0.026$^{***}$ (0.004) \\ 
-  post:countryEEZ TUV 1 & 0.007$^{***}$ (0.002) \\ 
-  post:countryHS & 0.034$^{***}$ (0.002) \\ 
-  post:countryHS COK 1 & $-$0.005$^{***}$ (0.001) \\ 
-  post:countryHS FSM 1 & $-$0.005$^{***}$ (0.001) \\ 
-  post:countryHS KIR 1 & 0.024$^{***}$ (0.001) \\ 
-  post:countryHS KIR 2 & 0.005$^{***}$ (0.001) \\ 
-  post:countryHS KIR 3 & 0.020$^{***}$ (0.001) \\ 
-  post:countryHS MHL 1 & $-$0.004$^{***}$ (0.001) \\ 
-  post:countryHS MUS 1 & $-$0.005$^{***}$ (0.001) \\ 
-  post:countryHS NRU 1 & $-$0.006$^{***}$ (0.001) \\ 
-  post:countryHS PNG 2 & $-$0.007$^{***}$ (0.001) \\ 
-  post:countryHS SLB 1 & $-$0.006$^{***}$ (0.001) \\ 
-  post:countryHS TUV 1 & $-$0.005$^{***}$ (0.001) \\ 
-  post:countryPIPA PIPA 1 & $-$0.088$^{***}$ (0.002) \\ 
-  Constant & 0.004$^{***}$ (0.0003) \\ 
- \hline \\[-1.8ex] 
-Observations & 69,048 \\ 
-R$^{2}$ & 0.370 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\begin{table}[H]
+
+\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of fishing hours by purse seiners ()}
+\centering
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+term & h\_prop\\
+
+\bottomrule
 \end{tabular}
@@
 
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
+fishing events by vessels through time. Each line represents a vessel,
+with dots indicating months with fishing activity and colors indicating
+the pre and post periods.}
+\end{figure}
+
 \hypertarget{other-model-specifications}{%
@@
 
-\begin{verbatim}
-## [[1]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.7380        8.3944       -1.0687       -0.7009  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      11.2808        9.3338       -0.7699        2.8855        3.6875  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       3.0010       -0.9889       -2.2384       -3.6433       -4.5904  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.4198       -3.5805        0.3173        2.8648       -0.8990  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##     13.94161       9.13865       0.04064       2.63902       3.55558  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##      2.59370      -1.06244      -2.41158      -4.00798      -4.91378  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##     -4.97737      -3.35106       0.20410       2.30467      -6.18817  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##     -2.94857      -4.72899      -3.70832      -1.87867      -2.24359  
-##      flagTWN  post:treated  
-##     -2.49301      -0.90817
-\end{verbatim}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-4.pdf}
 
-\begin{verbatim}
-## [[1]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##     11.41504       8.22194      -0.01516      -2.01435  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      10.9718        8.6646        0.0589        3.1399        4.2030  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       2.8778       -0.8801       -2.1805       -4.0561       -4.0234  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.7427       -4.4566        0.9716        4.9466       -2.0474  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##        8.160         8.923         2.910         3.489         4.775  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##        3.087        -1.082        -1.776        -4.186        -4.108  
-##     month_c6      month_c7      month_c8      month_c9       flagMHL  
-##       -5.336        -4.115         1.249         4.322         2.969  
-## post:treated  
-##       -2.984
-\end{verbatim}
-
-\begin{verbatim}
-## [[1]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.1998        9.0182       -0.5304       -1.3247  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##     10.74814      10.57403      -0.03924       2.43719       3.37646  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##      2.62526      -1.19664      -2.77934      -3.76747      -4.65285  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##     -4.79738      -3.64640       0.15290       3.15125      -2.13569  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      14.3391       10.4923        0.4295        2.2241        3.1505  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       2.0719       -1.2564       -2.8501       -4.0129       -5.0320  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##      -5.3231       -3.4871       -0.2020        2.2869       -5.4622  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##      -3.3566       -1.4486       -4.2977       -2.3611       -3.3106  
-##      flagTWN  post:treated  
-##      -3.2657       -2.2534
-\end{verbatim}
-
-\begin{verbatim}
-## [[1]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated  post:treated  
-##      11.4202        7.8750       -0.7508       -0.1815  
-## 
-## 
-## [[2]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c, data = data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##      10.9725        8.7780       -0.4452        2.8476        3.6473  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##       3.0113       -1.1434       -2.4295       -3.5424       -4.4423  
-##     month_c6      month_c7      month_c8      month_c9  post:treated  
-##      -4.5243       -3.6704        0.2277        3.0019       -0.3310  
-## 
-## 
-## [[3]]
-## 
-## Call:
-## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
-## 
-## Coefficients:
-##  (Intercept)          post       treated     month_c10     month_c11  
-##    14.036151      8.770151      0.557241      2.444760      3.320156  
-##    month_c12      month_c2      month_c3      month_c4      month_c5  
-##     2.456643     -1.307835     -2.707138     -4.024565     -4.841901  
-##     month_c6      month_c7      month_c8      month_c9       flagECU  
-##    -5.275270     -3.545459      0.001697      2.319940     -6.396277  
-##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
-##    -3.432356     -4.833825     -4.212230     -1.836510     -3.284000  
-##      flagTWN  post:treated  
-##    -2.637666     -0.454598
-\end{verbatim}
-
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-4.pdf}
-
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-4.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-3.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-4.pdf}
 

### 2018-10-17 rmd/Manuscript.Rmd
Updated manuscript intro and methods

@@
   - \linenumbers
+  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 bibliography: references.bib
-# biblio-style: nature
+biblio-style: chicago
 ---
@@
   library(tidyverse)
+  library(magrittr)
 })
@@
                       warning = FALSE,
-                      message = FALSE)
+                      message = FALSE,
+                      eval = TRUE)
 
@@
 Marine Protected Areas (MPAs) are intended to safeguard parts of the ocean from fishing and other extractive activities.
-Current international goals aim to "effectively protect 10\% of the ocean environments by 2020".
+Current international goals aim to protect 10\% of the ocean environments by 2020.
 In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}.
-A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas [LSMPAs; \citep{gray_2017}].
-These are defined as MPAS with at least 250,000 Km^2^ in extension (Fig.
+A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas (LSMPAs; \citet{boonzaier_2016,singleton_2014,gray_2017}).
+These are defined as MPAS larger than 250,000 Km^2^ in extension (Fig.
 \ref{fig:LSMPAs_map}), and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{toonen_2013,gray_2017,kroodsma_2018}.
 
+Given the relatively recent establishment of most LSMPAs, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
+Moreover, the world has seen a widespread increase in the implementation of LSMPAs, likely as a way to rapidly achieve the 10\% target \citep{boonzaier_2016,alger_2017,sala_2018}.
+However, as with customary MPAs, it is important that we understand the socioeconomic implications of management interventions that result in the spatial displacement of fishing effort.
+They **key gap in the literature is X**.
+We adress it here by using new stuff and find results that are of relevance to policy makers and advance our knowledge, which should be incorporated when designing and planning for LSMPAs.
+
 Due to weak property rights, limited habitat transformation, and potentially lower management costs, pelagic MPAs provide an opportunity to safeguard the oceans \citet{game_2009}.
-A growing body of literature has shown that closing the high seas to all fishing -effectively, turning them into a LSMPA- could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-However, as with customary MPAs, it is important that we understand the socioeconomic implications of management interventions.
+A growing body of literature has shown that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
 
-Given the relatively recent establishment of most LSMPAs, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
-LSMPAs were erroneously assumed to have little social implications due to their remoteness \citep{agardy_2011,gray_2017}.
-However, the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention \citep{mcdermott_2018}.
-LSMPAs have received great attention in terms of governance and enforcement, but are yet to be the focus of economic analyses \citep{gray_2017}.
+The early literature on LSMPAs focused on the inherent difficulties that come with a pelagic (*i.e.* open water) environment, where organisms typically have large home ranges.
+\citet{game_2009} suggest that most of the challenges can be overcome with the incorporation of technology, in what then became known as Dynamic Ocean Management \citep{maxwell_2015}.
+\citet{kaplan_2009} claim that very large MPAs would result in excessive opportunity costs and that these would be difficult to enforce.
+\citet{toonen_2013} show that just a small number of LSMPAs made up 80% of the managed areas in the ocean in 2013, and that these can help achieve the CBD Aichi targets faster.
+\citet{singleton_2014} provide an objective discussion of pros and cons of LSMPAs.
 
-Research on LSMPAs have been the focus of analysing X, Y, and Z.
-However, no studies look into displacement of fishing effort.
-Redistribution of fishing effort has been evaluated in ssf by X, Y ,and Z.
-\citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of MPAs in California, and find that responses are idiosyncratic; commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
-The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006}.
-This highlights the need to understand how fishers react to the implementation of a LSMPA, and fishing effort changes and is spatially redistributed.
+LSMPAs were erroneously assumed to have little social implications due to their remoteness.
+However, there have been calls to incorporate the human dimensions into LSMPAs management and evaluation \citep{agardy_2011,gray_2017}.
+Most research incorporating these human dimensions has focused on governance and enforcement of LSMPAs (*i.e.* \citet{alger_2017,christie_2017}), but they are yet to be the focus of economic analyses \citep{gray_2017}.
+Overall, there has been little empirical work regarding LSMPAs.
+Recent technological advances in vessel-detection systems allows for the discovery and advancement of many important facets of LSMPAs.
+For example, \citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention.
+\citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protectes two thrids of the tagged grey reef sharks by effectively excluding fishing effort.
+No studies have evaluated the displacement of fishing effort due to LSMPA implementation.
 
-The main objective of this paper is to identify how fishers change their behavior due to the implementation of LSMPAs.
+The exclusion of these LSMPAs is likely to change fisher's behavior.
+Theoretical models of fishing effort redistribution range from the simplistic assumption that effort inside the bounded region disappears, to spatially explicit models that reallocate fishing effort based on habitat characteristics, presence of other vessels, and expected returns \citep{smith_2003,hilborn_2006}.
+However, these focus on the long term optimal equilibrium and redistribution of fishing effort may not be optimal, especially over the first years \citep{stevenson_2013}.
+The few empirical works suggest that resource users may show idiosyncratic responses.
+For example, \citet{stevenson_2013} show that a network of MPAs displaced fishing effort farther away from ports resulting in higher *perceived* costs, but that catch per unit effort also increased.
+\citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of MPAs in California, and find that commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
+The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006} highlighting the need to understand how fishers react to the implementation of LSMPAs, and fishing effort changes and is spatially redistributed.
+
+The main objective of this paper is to identify behavioral responses to the implementation of LSMPAs.
 We combine novel vessel tracking technologies and causal inference techniques to identify behavioral changes of fishing vessels due to the implementation of PIPA.
@@
 
-```{r, fig.cap = "\\label{fig:LSMPAs_map}"}
+```{r, fig.cap = "\\label{fig:LSMPAs_map}Large Scale Marine Protected Areas.
+The map shows all areas larger than 250,000 Km^2^.
+Areas in dark blue meet at least one of these conditions: reported no take area is greater than 0, are categorized as IUCN Ia or Ib, their designated english name is 'Protected Area'."}
 
@@
   st_rotate() %>% 
-  mutate(PIPA = wdpaid == 309888)
+  filter(!desig_type == "International") %>% 
+  mutate(strict = ifelse(no_tk_area > 0 |
+                           iucn_cat %in% c("Ia", "Ib") |
+                           desig_eng == "Protected Area",
+                         "No-Take", "Others"),
+         strict = ifelse(wdpaid == 309888, "PIPA", strict),
+         Legend = fct_relevel(strict, c("No-Take", "PIPA", "Others"))) %>% 
+  filter(!name == "Longline")
 
@@
 ggplot() +
-  geom_sf(data = coast) +
+  geom_sf(data = coast, fill = "#E3E3E3") +
   geom_sf(data = mpas, fill = "transparent", color = "black", size = 1) +
-  geom_sf(data = mpas, aes(fill = PIPA), color = "transparent") +
+  geom_sf(data = mpas, aes(fill = Legend), color = "transparent") +
   ggtheme_map() +
-  scale_fill_brewer(palette = "Set1", direction = -1) +
-  theme(legend.position = "none")
+  scale_fill_manual(values = c("steelblue", "red", "steelblue1")) +
+  theme(legend.justification = c(0.5, 1),
+        legend.position = c(0.5, 0.05),
+        legend.box = "horizontal",
+        legend.background = element_blank()) +
+  guides(fill = guide_legend(ncol = 3))
 ```
@@
 
-```{r, fig.cap = "\\label{fig:PNA_map}"}
+```{r, fig.cap = "\\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
+A solid line indicates countries that belong to the PNA, while a dashed line indicates all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA."}
 countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI")
 
-small_coast <- rnaturalearth::ne_countries(returnclass = "sf") %>% 
+small_coast <- rnaturalearth::ne_countries(scale = "large", returnclass = "sf") %>% 
   filter(sov_a3 %in% countries) %>% 
@@
 ggplot() +
-  geom_sf(data = small_coast) +
   geom_sf(data = eez, aes(color = KIR, linetype = !PNA), fill = "transparent") +
   geom_sf(data = pipa, fill = "red") +
+  geom_sf(data = small_coast, size = 1, color = "black") +
   ggtheme_plot() +
@@
 The main tuna species caught in the region are skipjack (*Katsuwonus pelamis*), yellowfin (*Thunnus albacares*), albacore (*Thunnus alalunga*) and bigeye (*Thunnus obesus*).
-From these, the first two are amongst the top-10 species represented in global fisheries production statistics, with catches increasing relative to the 2005-2014 average \citep{fao_2018}.
+From these, the first two are amongst the top-10 species represented in global fisheries production statistics, with 2016 catches increasing relative to the 2005-2014 average \citep{fao_2018}.
 The pacific region has historically accounted for a large portion of tuna species production \citep{aqorau_1997}.
@@
 A large portion of these catches derive from purse seine vessels licensed under the VDS.
-Fishing vessels from Australia, New Zeland, China, France, Korea, Japan, the Philippines, Taiwan and the United States participate in the purse-seining vessel day schemes.
+Fishing vessels from Australia, New Zeland, China, France, Korea, Japan, the Philippines, Taiwan, and the United States participate in the purse-seining VDS.
 
-For example, \citet{mcdermott_2018} show that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) is effectively reduced after implementation, and describe changes in fishing behavior pre-implementation.
+One of the most notable and recent management interventions in the region is the implementation of the Phoenix Island Protected Area (PIPA) by the government of Kiribati.
+PIPA was first declared in 2006, and established in 2008 with only 4% of it was declared as no-take.
+In January 1^st^, 2015, the no-take area within PIPA was expanded to a total area of 397,447 Km^2^, roughly 1.5 times the size of Ecuador.
+The implementation of such a large conservation area in one of the most important fishing regions in the world provides a great opportunity to evaluate the behavioral responses and redistribution of fishing effort by vessels that used to fish there.
+\citet{mcdermott_2018} showed that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) increased between the anouncement (September 1^st^, 2014) and its implementation in Janyary 1^st^, 2015.
+Likewise, they demonstrate that fishing effort is effectively reduced after implementation.
+To this, we pose two questions: How do individual vessels respond to the sudden exclusion of such a big area?
+And where did all the vessels go?
+In the next sections we describe the data and methods used to answer this questions.
 
@@
   length()
+
+effort_by_vessel %<>%
+  filter(gear == "purse_seines")
 ```
 
-Our data contain over 45 million individual AIS messages (*i.e.* positions) for 371 purse seiners and longliners.
+Our data contain over 45 million individual AIS messages (*i.e.* positions) for 371 fishing vessels that at some point fished in PNA waters.
 A total of 233 vessels have fished within PIPA waters; 217 did so at least once before 2015.
-However, not all vessels continued to fish elsewhere after PIPA implementation: 34 vessels have no recorded AIS messages after 2015[^2], leaving us with `r pipa_vessels` vessels that fished inside PIPA before its implementation, and continued to fish elsewhere afterward.
+However, not all vessels continued to fish elsewhere after PIPA implementation: 34 vessels have no recorded AIS messages after 2015, leaving us with `r pipa_vessels` vessels that fished inside PIPA before its implementation, and continued to fish elsewhere afterward\footnote{The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
+In either case, we are not able to observe these.}.
+From these, we focus on purse seiners -the most important for PNA countries- and are left with 61 vessels\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
 New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period.
@@
 
-The treatment group contains all vessels (n = `r pipa_vessels`) that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards.
-Vessels in the control group meet all three of the following conditions: i) vessels never fished within PIPA waters, ii) vessels belong to other PNA countries, and iii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
-For each vessel meeting these characteristics, we calculate their total monthly fishing hours.
+The treatment group contains all purse seiners (n = 61) that fished within PIPA at least once before the anouncement (09/01/2014), and that continued to fish elsewhere after the January 2015 implementation.
+Vessels in the control group meet the following two conditions: i) vessels never fished within PIPA waters, and ii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
+This definition of control vessels provides us with 26 purse seiners that never fished inside PIPA but fished in other PNA waters before and after PIPA implementation.
+During our causal identification, we also use two more strict definitions of control groups: one with only vessels that belong to PNA countries (n = 7), and one that excludes Chinese vessels (n = 21).
+Our definition of treatment and control groups leaves us with 61 and 21 treated and control vessels, which have just over 22 million observations where about 22% are identified as fishing events.
+For each of the remainig vessels, we calculate their total daily fishing hours and obtain a pannel data with 38,200 observations.
+Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
 Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level fishing events that make up each group through time.
-Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
 
-<!-- **Do we know what is causing this?
-[first sentence in fist paragraph of results] I'm guessing this can't be Blue Paradox stuff because we see it for the control group as well who are supposed to have never fished within PIPA.** -->
-
-<!-- **Is the larger number of longliners surprising? I thought PIPA was known as a purse seining ground and less so for longlining.** -->
-
-[^2]: The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
-In either case, we are not able to observe these.
-
-```{r, fig.width = 8, fig.height = 6, fig.cap = "\\label{fig:baci_strict}Stream of fishing events by vessels through time.
-Each line represents a vessel, with dots indicating months with fishing activity and colors indicating the pre and post periods."}
-filter(effort_by_vessel, baci_strict) %>% 
-  mutate(gear = ifelse(gear == "purse_seines", "Purse seiners", "Drifting longliners")) %>% 
-  group_by(mmsi, date, gear, post, treated) %>%
-  summarize(h = sum(hours, na.rm = T)) %>%
-  ungroup() %>% 
-  arrange(treated, post, mmsi) %>%
-  mutate(vessel = group_indices(., paste(gear, treated, mmsi)),
-         treated = ifelse(treated, "Treated", "Control")) %>% 
-  ggplot(aes(
-    x = date,
-    y = vessel,
-    fill = post,
-    color = post,
-    group = paste(vessel, post)
-    )) +
-  geom_point(size = 1) +
-  theme_bw() +
-  facet_wrap(gear ~ treated, scales = "free_y") +
-  ggtheme_plot() +
-  scale_color_brewer(palette = "Set1") +
-  scale_y_continuous(breaks = NULL, labels = NULL) +
-  theme(legend.position = "none")
-```
-
-```{r}
+```{r, eval = T}
 hours <- effort_by_vessel %>%
   filter(baci_strict) %>%
-  group_by(gear, treated, post) %>% 
+  group_by(treated, post, date, mmsi) %>% 
+  summarize(hours = sum(hours, na.rm  = T)) %>% 
+  ungroup() %>% 
+  group_by(treated, post) %>% 
   summarize(hours = mean(hours, na.rm = T)) %>% 
@@
 
+# I need to group the B - A columns into something that says "hors"
+
 effort_by_vessel %>% 
   filter(baci_strict) %>%
-  group_by(gear, treated, mmsi) %>% 
+  group_by(treated, mmsi) %>% 
   count() %>% 
   ungroup() %>% 
-  group_by(gear, treated) %>% 
+  group_by(treated) %>% 
   summarize(boats = n()) %>% 
-  left_join(hours, by = c("gear", "treated")) %>% 
-  knitr::kable(col.names = c("Gear", "Treatment", "n" ,"Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.",
-               booktabs = T) %>% 
+  ungroup() %>% 
+  left_join(hours, by = c( "treated")) %>% 
+  mutate(treated = ifelse(treated, "Treatment", "Control")) %>% 
+  knitr::kable(col.names = c("Group", "n" ,"Before", "After", "Change (A / B)"),
+               caption = "\\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.",
+               booktabs = T,
+               digits = 2) %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
-\clearpage
-
-## Analysis
+## Analyses
 
 The first analysis focuses on identifying the response of fishing vessels to PIPA closure.
-Our variables of interests are fishing effort, indicated by total fishing hours per month, and distance traveled (Km) on every fishing trip.
-We compare fishing hours[^3] before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation.
+Our variables of interests are daily fishing hours, and daily distance traveled (Km).
+We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation.
 Our specification is the following:
@@
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \mu_1Y_t + \mu_2Y_t^2 + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
 $$
@@
 $\alpha$ is the standard intercept, $\beta_1$ captures the temporal trend change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\mu_1$ and $\mu_2$ are coefficients for a second order polynomial for years ($Y_t$), while $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions[^4].
+Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}
 
-[^3]: And soon, distance
-
-[^4]: An earlier specification included years as a dummy variable. Such results are included in the appendix, but are similar to the ones found under current specification.
-
-```{r}
+```{r, eval = T}
 displacement_data <- readRDS(file = here::here("data", "displacement_data_ps.rds")) %>% 
@@
 In other words, identifying where do vessels that used to fish inside PIPA go after its establishment.
-We calculate the monthly relative distribution of fishing hours by all treated vessels across all fished EEZs and the high seas.
-These trends are shown in Figure \ref{fig:redist_trend_ps}, and the relative temporal change is presented in Table \ref{tab:ba_disp}.
-EEZs that had sporadic fishing events were pooled into a group of "others", leaving us with a total of n = `r length(unique(displacement_data$country[displacement_data$gear == "purse_seines"]))` and n = `r length(unique(displacement_data$country[!displacement_data$gear == "purse_seines"]))`[^5] spatially defined regions (*i.e.* EEZs, High Seas, "other EEZs", and PIPA) for purse seiners and longliners, respectively.
+We discretize spatial units by using a polygon for PIPA \footnote{we would expect to see a decrease here} and distinct spatial units for each EEZ of each country.
+Some vessels might shift from EEZs into the High Seas, but we are interested in knowing *where* in the High Seas, so we incorporate additional regions by using a 1 degree buffer of the High Seas arround each of the EEZ regions.
+The rest of the high seas are merged into a single spatial unit.
+For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZs, three 1-degree buffers of High Seas arround each EEZs, and the rest of the High Seas.
+Whenever the buffers overlapped between themselves, we randocmply clipped one on to the other.
+EEZs that had sporadic fishing events were pooled into a group of "others".
 
-[^5]: This number is likely to change upon finalizing the spatial analysis of longliners, which is currently running.
-
-To evaluate this change in effort allocation, we regress our variable of interest (*i.e.*fishing hours) on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries.
+To evaluate this change in effort allocation, we regress our variable of interest (*i.e.* fishing hours) on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries.
 This gives us the by-country change in proportional allocation of fishing effort:
@@
 $$
-y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 $$
@@
 $Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise.
-$Country$ is a dummy variable for countries, interpreted as individual EEZs, the high seas, and a group of "other EEZs".
-Our parameter of interest is $\beta_{3,i}$, which captures the country-level change in proportional fishing effort.
+$Country$ is a dummy variable for countries for the spatial units defined above.
+Our parameter of interest is $\beta_{1,i}$, which captures the country-level change in proportional fishing effort.
 
@@
 ```{r}
-ba_disp_ps <- displacement_data %>% 
+ba_disp <- displacement_data %>% 
   filter(gear == "purse_seines") %>% 
@@
 
-# ba_disp_ll <- displacement_data %>% 
-#   filter(!gear == "purse_seines") %>% 
-#   group_by(country, post) %>% 
-#   summarize(h_prop_m = mean(h_prop)) %>% 
-#   spread(post, h_prop_m) %>% 
-#   mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
-#   select(country, change)
-# 
-# ba_disp_ps %>% 
-#   mutate(gear = "Purse seiners") %>% 
-#   rbind(mutate(ba_disp_ll, gear = "Longliners")) %>% 
-#   spread(gear, change) %>% 
-#   knitr::kable(digits = 2,
-#                booktabs = T,
-#                caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>% 
-#   kableExtra::kable_styling(latex_options = "HOLD_position")
+knitr::kable(x = ba_disp,
+             digits = 2,
+             booktabs = T,
+             caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure.", fig.heihgt = 3.5}
+
+effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
+  arrange(!treated) %>% 
+  ggplot(aes(x = date, y = hours, color = treated)) +
+  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.1) +
+  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
+```
+
 Our DiD analysis shows that treated purse seiners reduce their fishing effort after PIPA implementation in the order of 16 hours per month.
@@
 
-Longliners show a similar pattern of effort reduction.
+<!-- Longliners show a similar pattern of effort reduction.
 However, the magnitude of the $\beta_3$ coefficient is smaller (ranging from  $\beta_3 = -9.851$ to $\beta_3 = -14.850$) and not significant across all model specifications.
 This, along with higher standard error values suggest that longliners have a smaller and more variable response to the implementation of LSMPAs.
+-->
 
@@
          h_prop > 0) %>%
-  # mutate(country = as.character(country),
-         # country = ifelse(country %in% c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"), country, "OTH"),
-         # country = forcats::fct_relevel(country, "OTH", after = Inf)) %>% 
   ggplot(aes(x = date, y = h_prop, group = post)) +
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend_ll}", eval = F}
-displacement_data %>% 
-  filter(!gear == "purse_seines") %>% 
-  ggplot(aes(x = date, y = h_prop, group = post)) +
-  geom_smooth(method = "lm") +
-  geom_point() +
-  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
-  scale_fill_brewer(palette = "Paired") +
-  ggtheme_plot() +
-  facet_wrap(~country, scales = "free_y")
-```
-
 ```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
 
-# Los colores del mapa deben estar dados por el Post:Country
+HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
+                  ncol=2,
+                  byrow=TRUE) %>%
+  list() %>%
+  st_polygon() %>% 
+  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")
+
+HS_disp <- data.frame(country = "HS",
+                      PNA = F) %>% 
+  st_set_geometry(HS_disp_poly) %>% 
+  mutate(id = country, source = country, PNA = F) %>% 
+  select(id, source, PNA, country)
+
+# I AM EXCLUDING MUS WHICH SHOULD BE PUT INTO EEZ
 eez %>% 
-  left_join(ba_disp_ps, by = c("id" = "country")) %>%
-  filter(!is.na(change)) %>%
+  rbind(HS_disp) %>% 
+  left_join(ba_disp, by = c("id" = "country")) %>%
+  filter(!is.na(change),
+         !id == "HS MUS 1") %>%
   ggplot() +
   geom_sf(aes(fill = change), color = "black") +
-  ggtheme_plot() +
-  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
-```
-
-```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for longliners.
-**This are preliminar results, contingent on the spatial analysis currently being run**", eval = F}
-pipa_map_ba_disp <- pipa %>% 
-  mutate(country = "PIPA") %>% 
-  left_join(ba_disp_ll, by = "country")
-
-# Los colores del mapa deben estar dados por el Post:Country
-eez %>% 
-  left_join(ba_disp_ll, by = c("ISO_Ter1" = "country")) %>%
-  filter(!is.na(change)) %>% 
-  ggplot() +
-  geom_sf(aes(fill = change), color = "black") +
-  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
   ggtheme_plot() +
@@
          year2 = year^2,
-         month_c = as.character(month))
+         month_c = as.character(month),
+         country = fct_relevel(country, "PIPA PIPA 1"))
 
@@
 
-stargazer::stargazer(models,
-                     se = commarobust::makerobustseslist(models),
-                     t.auto = T,
-                     p.auto = T,
-                     type = "latex",
-                     omit = "month",
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     single.row = T,
-                     title = "\\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region.
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robust standard errors.")
+commarobust::commarobust_tidy(disp_mod_ps1) %>% 
+  as.data.frame() %>% 
+  mutate(term = rownames(.)) %>% 
+  mutate(b = str_detect(term, "Intercept"),
+         c = str_detect(term, "post"),
+         a = b*c,
+         p1 = ifelse(p < 0.1, "*", ""),
+         p2 = ifelse(p < 0.05, "*", ""),
+         p3 = ifelse(p < 0.01, "*", ""),
+    h_prop = paste0(formatC(est, digits = 3, format = "f"),
+                    " (",
+                    formatC(se, digits = 3, format = "f"),
+                    ")",
+                    p1,
+                    p2,
+                    p3)) %>% 
+  filter(b+c > 0) %>% 
+  select(term, h_prop) %>% 
+  knitr::kable(booktabs = T,
+               caption = "Change in the relative allocation of fishing hours by purse seiners ()") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position",
+                            font_size = 7)
 
@@
 
+\beginsupplement
+
+```{r, fig.width = 8, fig.height = 6, fig.cap = "\\label{fig:baci_strict}Stream of fishing events by vessels through time.
+Each line represents a vessel, with dots indicating months with fishing activity and colors indicating the pre and post periods.", eval = T}
+filter(effort_by_vessel, baci_strict) %>% 
+  mutate(gear = ifelse(gear == "purse_seines", "Purse seiners", "Drifting longliners")) %>% 
+  group_by(mmsi, date, gear, post, treated) %>%
+  summarize(h = sum(hours, na.rm = T)) %>%
+  ungroup() %>% 
+  arrange(treated, post, mmsi) %>%
+  mutate(vessel = group_indices(., paste(gear, treated, mmsi)),
+         treated = ifelse(treated, "Treated", "Control")) %>% 
+  ggplot(aes(
+    x = date,
+    y = vessel,
+    fill = post,
+    color = post,
+    group = paste(vessel, post)
+    )) +
+  geom_point(size = 1) +
+  theme_bw() +
+  facet_wrap(~ treated, scales = "free_y") +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  scale_y_continuous(breaks = NULL, labels = NULL) +
+  theme(legend.position = "none")
+```
+
 ## Other model specifications
@@
 ```{r, results = "asis"}
-
-model_data <- effort_by_vessel %>% 
-  filter(baci_strict,
+model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
+  filter(year < 2018,
+         baci_strict,
          !gear == "purse_seines") %>% 
@@
 
-```{r}
+```{r, results = "asis", eval = F}
 models_exp0_did %>% stargazer::stargazer()

### 2018-10-17 slides/ERE_lunch.Rmd
Updated manuscript intro and methods

@@
   janitor::clean_names() %>% 
-  filter(gis_m_area > 250000)
+  filter(gis_m_area > 250000,
+         no_tk_area > 0)
 
@@
   ggplot(aes(x = date, y = hours, color = treated)) +
+  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.1) +
   geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
-  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.5) +
   ggtheme_plot() +

### 2018-10-17 scripts/combine_vessel_info_and_effort.R

@@ -67,7 +67,7 @@ mmsi_baci_relaxed <- c(tb, ca[ca %in% cb])
 effort_by_vessel %<>%
   mutate(baci_strict = mmsi %in% mmsi_baci_strict,
          baci_relaxed = mmsi %in% mmsi_baci_relaxed,
-         experiment1 = PNA,
+         experiment1 = treated | PNA,
          experiment2 = treated | (!treated & iso3 == "TWN"),
          experiment3 = treated | (!treated & !iso3 == "CHN"),
          iso3 = ifelse(iso3 == "" | is.na(iso3), "OTH", iso3)) %>% 

### 2018-10-17 scripts/get_LSMPAs.R

@@ -1,0 +1,9 @@
+library(dplyr)
+
+sf::read_sf(here::here("raw_data", "spatial", "WDPA_Mar2018"),
+            layer = "WDPA_Mar2018_marine-shapefile-polygons",
+            quiet = T,
+            stringsAsFactors = F) %>% 
+  janitor::clean_names() %>% 
+  dplyr::filter(gis_m_area > 250000) %>% 
+  sf::st_write(dsn = here::here("data", "spatial", "LSMPAs", "LSMPAs.shp"))

### 2018-10-17 scripts/termplot.R

@@ -13,7 +13,8 @@ termplot<- function(model_list, q = F, title = deparse(substitute(model_list))){
       ggtheme_plot() +
       geom_hline(yintercept = 0, linetype = "dashed") +
       geom_vline(xintercept = 2015, linetype = "dashed") +
-      ggtitle(label = title)
+      ggtitle(label = title) +
+      scale_color_brewer(palette = "Set1")
     
   } else {
     map_df(model_list, broom::tidy, .id = "model") %>%
@@ -26,7 +27,8 @@ termplot<- function(model_list, q = F, title = deparse(substitute(model_list))){
       ggtheme_plot() +
       geom_hline(yintercept = 0, linetype = "dashed") +
       geom_vline(xintercept = lubridate::date(paste(2015, 01, 01, sep = "/")), linetype = "dashed") +
-      ggtitle(label = title)
+      ggtitle(label = title) +
+      scale_color_brewer(palette = "Set1")
     }
 }
 

### 2018-10-19 docs/Manuscript.tex
Updated manuscript draft

@@
 
-  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
+  \title{Displacement of fishing effort by Large Scale Marine Protected
+Areas\footnote{Work in progress, do not circulate}}
     \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-  \subtitle{Updated on 2018-10-16}
+  \subtitle{Updated on 2018-10-18}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 \linenumbers
+\usepackage[bottom]{footmisc}
+\usepackage{pdflscape}
 \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
@@
 
+\clearpage
+
 \hypertarget{introduction}{%
@@
 2020. In an effort to meet this target, the world has seen a rapid
-increase in MPA coverage \citep{wood_2008,sala_2018}. A significant part
-of this rapid increase can be attributed to the designation of a small
-number of Large Scale Marine Protected Areas (LSMPAs;
-\citet{boonzaier_2016,singleton_2014,gray_2017}). These are defined as
-MPAS larger than 250,000 Km\textsuperscript{2} in extension (Fig.
-\ref{fig:LSMPAs_map}), and are often implemented in the pelagic
-environment, where the dominant human activity is industrial fishing
-\citep{toonen_2013,gray_2017,kroodsma_2018}.
+increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
+a small number of Large Scale Marine Protected Areas (LSMPA)
+\citet{singleton_2014,boonzaier_2016,alger_2017}). Due to weak property
+rights, limited habitat transformation, and potentially lower management
+costs, LSMPAs provide an opportunity to safeguard the oceans
+\citet{game_2009}. Today, a small number of LSMPAs make up at least 80\%
+of the managed areas in the ocean \citet{toonen_2013}.
 
@@
 known about their human dimensions and implication for fisheries
-\citep{gray_2017}. Moreover, the world has seen a widespread increase in
-the implementation of LSMPAs, likely as a way to rapidly achieve the
-10\% target \citep{boonzaier_2016,alger_2017,sala_2018}. However, as
-with customary MPAs, it is important that we understand the
-socioeconomic implications of management interventions that result in
-the spatial displacement of fishing effort. They \textbf{key gap in the
-literature is X}. We adress it here by using new stuff and find results
-that are of relevance to policy makers and advance our knowledge, which
-should be incorporated when designing and planning for LSMPAs.
+\citep{gray_2017}. As with customary MPAs, it is important that we
+understand the socioeconomic implications of management interventions.
+One issue of particular importance is that of the displacement or
+redistribution of fishing effort, which may influence the outcomes of an
+MPA \citep{smith_2003}. Theoretical models make different assumptions
+about the way in which fishers will reallocate fishing effort after an
+area closure \citep{}. The few empirical works focus on small-scale
+fisheries and rarely incorporate spatially explicit data. Despite these
+efforts, marine conservation is yet to identify the implications of
+these management interventions.
 
-Due to weak property rights, limited habitat transformation, and
-potentially lower management costs, pelagic MPAs provide an opportunity
-to safeguard the oceans \citet{game_2009}. A growing body of literature
-has shown that closing the high seas to all fishing could increase
-fishery yields and profitability of fisheries, with negligible costs to
-food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+Here, we ask, how do fishers respond to the implementation of LSMPA?
+After a closure, and if they continue to fish, where do they reallocate
+fishing effort? We use novel satellite technologies and causal inference
+techniques to identify the behavioral changes and spatial redistribution
+of the industrial tuna purse seine fleet due to the implementation of a
+Large Scale Marine Protected Areas in the Western and Central Pacific
+Ocean (WCPO).
 
-The early literature on LSMPAs focused on the inherent difficulties that
-come with a pelagic (\emph{i.e.} open water) environment, where
-organisms typically have large home ranges. \citet{game_2009} suggest
-that most of the challenges can be overcome with the incorporation of
-technology, in what then became known as Dynamic Ocean Management
-\citep{maxwell_2015}. \citet{kaplan_2009} claim that very large MPAs
-would result in excessive opportunity costs and that these would be
-difficult to enforce. \citet{toonen_2013} show that just a small number
-of LSMPAs made up 80\% of the managed areas in the ocean in 2013, and
-that these can help achieve the CBD Aichi targets faster.
-\citet{singleton_2014} provide an objective discussion of pros and cons
-of LSMPAs.
+The cutoff at which an MPA is considered to be a LSMPA ranges from areas
+larger than 30,000 km\textsuperscript{2} as defined by
+\citet{desanto_2013} or areas larger than 250,000 km\textsuperscript{2},
+as defined by \citep{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
+LSMPAs that meet the later, and that are fully no take. LSMPAs are often
+implemented in the pelagic environment, where the dominant human
+activity is industrial fishing \citep{gray_2017,kroodsma_2018}. The
+early literature on LSMPAs focused on the inherent challenges and
+difficulties that come with a pelagic environment. \citet{kaplan_2010}
+claimed that very large MPAs would result in excessive opportunity costs
+and that these would be difficult to enforce. \citet{game_2009}
+suggested that most of the challenges could be overcome with the
+incorporation of technology, in what then became known as Dynamic Ocean
+Management \citep{maxwell_2015}. The effectiveness and difficulties of
+implementating LSMPAs are not the focus of this paper
+\footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
+Instead, we focus on the effect and implications of the ones that
+\emph{have been} implemented.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
+Protected Areas. The map shows all areas larger than 250,000
+Km\textsuperscript{2}. Areas in dark blue meet at least one of these
+conditions: reported no take area is greater than 0, are categorized as
+IUCN Ia or Ib, their designated english name is `Protected Area'.}
+\end{figure}
 
@@
 human dimensions into LSMPAs management and evaluation
-\citep{agardy_2011,gray_2017}. Most research incorporating these human
+\citep{agardy_2011,gray_2017}. Most research incorporating these
 dimensions has focused on governance and enforcement of LSMPAs
@@
 thrids of the tagged grey reef sharks by effectively excluding fishing
-effort. No studies have evaluated the displacement of fishing effort due
-to LSMPA implementation.
+effort. More recently, \citep{bradley_2018} use similar data to
+highlight cases of illegal shark fishing \emph{inside} a 2 million
+km\textsuperscript{2} shark sanctuary. To date, no studies have
+evaluated the displacement of fishing effort due to LSMPA
+implementation.
 
@@
 optimal equilibrium and redistribution of fishing effort may not be
-optimal, especially over the first years \citep{stevenson_2013}. The few
-empirical works suggest that resource users may show idiosyncratic
-responses. For example, \citet{stevenson_2013} show that a network of
-MPAs displaced fishing effort farther away from ports resulting in
-higher \emph{perceived} costs, but that catch per unit effort also
-increased. \citet{cabral_2017} analyse the redistribution of fishing and
-non-fishing vessels following the implementation of MPAs in California,
-and find that commercial dive boats follow a fishing-the-line pattern,
-while some fishing boats follow an ideal free distribution. The way in
-which fishers react to a spatial closure can have major implications in
-its outcome \citep{smith_2003,hilborn_2006} highlighting the need to
+optimal, especially over the first years \citep{stevenson_2013}. The
+empirical research that has been done in custumary sized MPAs suggest
+that resource users may show idiosyncratic responses. For example,
+\citet{stevenson_2013} show that a network of MPAs displaced fishing
+effort farther away from ports, resulting in higher \emph{perceived}
+costs, and increases in catch per unit effort. \citet{cabral_2017}
+analyse the redistribution of fishing and non-fishing vessels following
+the implementation of a network of MPAs in California, and find that
+commercial dive boats follow a fishing-the-line pattern, while some
+fishing boats follow an ideal free distribution. The way in which
+fishers react to a spatial closure can have major implications in its
+outcome \citep{smith_2003,hilborn_2006} highlighting the need to
 understand how fishers react to the implementation of LSMPAs, and
@@
 
-The main objective of this paper is to identify behavioral responses to
-the implementation of LSMPAs. We combine novel vessel tracking
-technologies and causal inference techniques to identify behavioral
-changes of fishing vessels due to the implementation of PIPA. We focus
-on fishing hours and distance traveled as outcome variables that fishers
-might adjust following implementation of a LSMPA in an impact-evaluation
-fashion. Additionally, we evaluate the spatial redistribution of fishing
-effort that existed within PIPA before its implementation. This work
-provides novel empirical insights into fisher's responses to the
-implementation of LSMPAs, and can help guide future interventions. Our
-work is novel in the sense that it provides empirical evidence of the
-effect of large-acale Marine Protected Areas in fishing behavior and
-distribution.
+Our work is novel in the sense that it provides empirical evidence of
+the effect of large-acale Marine Protected Areas in fishing behavior and
+distribution and can help guide future interventions as countries march
+towards meetings the targeted 10\% of protection. Furthermore, a growing
+body of literature suggests that closing the high seas to all fishing
+could increase fishery yields and profitability of fisheries, with
+negligible costs to food security
+\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Understanding
+how effort is displaced from LSMPAs might provide insights into how the
+industrial fleet would react to a high seas closure.
 
-The next sections are as follows: Section \ref{background} provides an
+The paper is outlined as follows: Section \ref{background} provides an
 overview of the Nauru Agreement and associated countries, a description
@@
 Section \ref{results} presents our results, section \ref{discussion}
-provides an extension of our results to other LSMPAs and discusses our
-results.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
-Protected Areas. The map shows all areas larger than 250,000
-Km\textsuperscript{2}. Areas in dark blue meet at least one of these
-conditions: reported no take area is greater than 0, are categorized as
-IUCN Ia or Ib, their designated english name is `Protected Area'.}
-\end{figure}
+provides an extension of our results to other
+LSMPAs\footnote{Not yet. but I think this would be interesting} and
+discusses our
+results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
 
@@
 
-The Nauru Agreement was established in 1982 by Pacific island nations to
-manage their important tuna resources. PNA Members include Federated
-States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua
-New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated
-access of foreign vessels (\emph{i.e.} those from non-PNA countries).
-Holding \textasciitilde{}80\% of the historical purse seining grounds
-within their Exclusive Economic Zones, PNA countries gained bargaining
-power when providing access to foreign fleets \citep{havice_2010}.
+The Nauru Agreement was established in 1982 by a select group of Pacific
+island nations to manage their important tuna resources. PNA Members
+include Federated States of Micronesia, Kiribati, Marshall Islands,
+Nauru, Palau, Papua New Guinea, Solomon Islands, and Tuvalu. The Nauru
+Agreement regulated access of foreign vessels (\emph{i.e.} those from
+non-PNA countries). Holding \textasciitilde{}80\% of the historical
+purse seining grounds within their Exclusive Economic Zones, PNA
+countries gained bargaining power when providing access to foreign
+fleets \citep{havice_2010}.
 
@@
 year. Hours are allocated to each PNA country based on catch history,
-and they then sell fishing rights to other non-PNA countries
+and they then use or sell fishing rights to other non-PNA countries
 \citep{aqorau_2018}. While the effectiveness of this scheme has been
@@
 global fisheries production statistics, with 2016 catches increasing
-relative to the 2005-2014 average \citep{fao_2018}. The pacific region
-has historically accounted for a large portion of tuna species
-production \citep{aqorau_1997}. Today, the PNA controls close to 50\% of
-the global skipjack tuna production \citep{pna_website_2018}. A large
-portion of these catches derive from purse seine vessels licensed under
-the VDS. Fishing vessels from Australia, New Zeland, China, France,
-Korea, Japan, the Philippines, Taiwan, and the United States participate
-in the purse-seining VDS.
+relative to the 2005-2014 average \citep{fao_2018}. Theis region of the
+Pacific has historically accounted for a large portion of tuna catches
+\citep{aqorau_1997}. Today, the PNA controls close to 50\% of the global
+skipjack tuna production \citep{pna_website_2018}. A large portion of
+these catches derive from purse seine vessels licensed under the VDS.
+Fishing vessels from Australia, New Zeland, China, France, Korea, Japan,
+the Philippines, Taiwan, and the United States participate in the
+purse-seining VDS.
 
@@
 January 1\textsuperscript{st}, 2015, the no-take area within PIPA was
-expanded to a total area of 397,447 Km\textsuperscript{2}, roughly 1.5
-times the size of Ecuador. The implementation of such a large
-conservation area in one of the most important fishing regions in the
-world provides a great opportunity to evaluate the behavioral responses
-and redistribution of fishing effort by vessels that used to fish there.
-\citet{mcdermott_2018} showed that fishing effort within the Phoenix
-Islands Marine Protected Area (PIPA) increased between the anouncement
-(September 1\textsuperscript{st}, 2014) and its implementation in
-Janyary 1\textsuperscript{st}, 2015. Likewise, they demonstrate that
-fishing effort is effectively reduced after implementation. To this, we
-pose two questions: How do individual vessels respond to the sudden
-exclusion of such a big area? And where did all the vessels go? In the
-next sections we describe the data and methods used to answer this
-questions.
+expanded to a total area of 397,447 km\textsuperscript{2}, roughly 1.5
+times the size of Ecuador. Figure \ref{fig:PNA_map} shows a map of the
+PNA countries and the Phoenix Island Protected Area.
+
+The implementation of such a large conservation area in one of the most
+important fishing regions in the world provides a great opportunity to
+evaluate the behavioral responses and redistribution of fishing effort
+by vessels that used to fish there. \citet{mcdermott_2018} showed that
+fishing effort within the Phoenix Islands Marine Protected Area (PIPA)
+increased between the anouncement (September 1\textsuperscript{st},
+2014) and its implementation in Janyary 1\textsuperscript{st}, 2015.
+Likewise, they demonstrate that fishing effort is effectively reduced
+after implementation. To this, we pose two questions: How do individual
+vessels respond to the sudden exclusion of such a big area? And where
+did all the vessels go? In the next sections we describe the data and
+methods used to answer this questions.
 
@@
 broadcasted messages can be received by satellites and land-based
-antennas. GFW uses a neural network to infer vessel characteristics and
-whether each broadcasted position represents a fishing event, thus
-allowing us to estimate near real-time fishing events globally since
-2012 \citep{kroodsma_2018}. Our data contain information for 2012 -
-2017. The recent addition of satellites that can receive AIS signals
-causes an apparent increase in the number of broadcasted AIS messages
-(\emph{i.e.} points), and therefore number of vessels and fishing hours.
-The variability in AIS data and ocean conditions require that temporal
-trends be taken into account. We do that by obtaining a subset of data
-that meet a BACI design, which gives us the full tracks for vessels
-affected and unaffected by the implementation of PIPA.
+antennas. GFW uses convolutional neural networks to infer vessel
+characteristics and whether each broadcasted position represents a
+fishing event, thus allowing us to estimate near real-time fishing
+events globally since 2012 \citep{kroodsma_2018}. Our data contain
+information for 2012 - 2017. The amount of data gathered is dependent on
+the number of antenas and satellites that can pick up the signals. In
+June 1\textsuperscript{st} 2014 satellite count increased from 3 to 6,
+and then to 10 in January 1\textsuperscript{st} 2016. This causes an
+apparent increase in the number of broadcasted AIS messages (\emph{i.e.}
+points), and therefore number of vessels and fishing hours. The
+variability in AIS data and ocean conditions require that temporal
+trends be taken into account. We do that by including specific controls
+in our identification strategy and using a subset of data that meet a
+BACI design -which gives us the full tracks for vessels affected and
+unaffected by the implementation of PIPA.
 
@@
 events. For each of the remainig vessels, we calculate their total daily
-fishing hours and obtain a pannel data with 38,200 observations. Table
+fishing hours and obtain pannel data with 37,800 observations. Table
 \ref{tab:baci_n_s} shows the number of vessels following a BACI design,
-as well as the fishing hours, before and after PIPA. Figure
+as well as the fishing hours, before and after PIPA. Fig.
+\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
+have an abrupt increase, just before January 1st, 2015. This trend is
+observed for both treated and control groups. Across all measures, the
+treatment and control vessels follow similar patterns, confirming our
+claim that the control group provides a plausible counterfactual. Figure
 \ref{fig:baci_strict} provides a visual representation of the
@@
 
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
+number of vessels by month for all vessels. Vertical dashed lines
+indicates dates when satellites were added, solid line indicates PIPA
+closurePIPA closure.}
+\end{figure}
+
 \hypertarget{analyses}{%
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_i + \epsilon_{i,t}
 \]
@@
 month-, and flag-level dummies that account for seasonality or
-country-level management
-interventions\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}
+country-level management interventions, and \(\theta_i\) are a set of
+dummies that account for the addition of more
+satellites\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}.
 
@@
 units for each EEZ of each country. Some vessels might shift from EEZs
-into the High Seas, but we are interested in knowing \emph{where} in the
-High Seas, so we incorporate additional regions by using a 1 degree
-buffer of the High Seas arround each of the EEZ regions. The rest of the
+into the high seas, but we are interested in knowing \emph{where} in the
+high seas, so we incorporate additional regions by using a 1 degree
+buffer of the high seas arround each of the EEZ regions. The rest of the
 high seas are merged into a single spatial unit. For example, if we were
 to do this only for Kiribati, we would have 8 spatial units: PIPA, three
-EEZs, three 1-degree buffers of High Seas arround each EEZs, and the
-rest of the High Seas. Whenever the buffers overlapped between
+EEZs, three 1-degree buffers of high seas arround each EEZs, and the
+rest of the high seas. Whenever the buffers overlapped between
 themselves, we randocmply clipped one on to the other. EEZs that had
@@
 \[
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \theta_i + \epsilon_{i,t}
 \]
@@
 interest is \(\beta_{1,i}\), which captures the country-level change in
-proportional fishing effort.
+proportional fishing effort. \(\theta_i\) accounts for the addition of
+satellites.
 
@@
 
-\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
+\caption{\label{tab:unnamed-chunk-10}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
 \centering
@@
 HS COK 1 & 0.06\\
-HS FSM 1 & 0.01\\
 HS KIR 1 & 2.96\\
 HS KIR 2 & 1.07\\
-\addlinespace
 HS KIR 3 & 2.53\\
-HS MHL 1 & 0.11\\
-HS MUS 1 & 0.00\\
-HS NRU 1 & -0.08\\
-HS PNG 2 & -0.20\\
-\addlinespace
-HS SLB 1 & -0.02\\
-HS TUV 1 & 0.01\\
 PIPA PIPA 1 & -8.25\\
@@
 \section{Results}\label{results}}
-
-Our data suggest that purse seiners and longliners have different
-responses to the implementation of a Large-Scale Marine Protected Areas.
-Fig. \ref{fig:all_vessels} shows that mean fishing hours for purse
-seiners have an abrupt increase, just before January 1st, 2015. This
-trend is observed for both treated and control groups. The pattern
-closely corresponds with the increase in total hours, but the total
-number of vessels doesn't entirely follow this pattern. The increase in
-fishing hours might be caused by the increased number of
-satellites\footnote{Need to check this. Not sure any satellites were
-  incorporated during 2014. It is also possible that PNA countries
-  started enforcing the requirement of having an AIS unit. On either
-  case, both treatment and control groups seem to be affected equally.}.
-Longliners, however, show no apparent trend with a clear seasonality
-\citep{ortuocrespo_2018}. The number of mmsi codes also increases
-slightly through time, but becomes stable after 2015. For both gears and
-across all measures, the treatment and control vessels follow similar
-patterns, confirming our claim that the control group provides a
-plausible counterfactual.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels. Vertical dashed line
-indicates PIPA closure.}
-\end{figure}
 
@@
 effects.
+
+\clearpage
+\begin{landscape}
+
+\begin{table}[!htbp] \centering 
+  \caption{Difference-in-differences estimates for 3 different controls and 3 different specifications.
+The first three columns use all data for controls.
+Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \label{} 
+\small 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{9}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-10} 
+\\[-1.8ex] & \multicolumn{9}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+\hline \\[-1.8ex] 
+ Constant & 6.345$^{***}$ & 7.863$^{***}$ & 10.322$^{***}$ & 7.124$^{***}$ & 9.007$^{***}$ & 9.933$^{***}$ & 6.057$^{***}$ & 7.584$^{***}$ & 10.194$^{***}$ \\ 
+  & (0.186) & (0.274) & (0.404) & (0.265) & (0.341) & (0.620) & (0.193) & (0.279) & (0.538) \\ 
+  & & & & & & & & & \\ 
+ post & $-$0.052 & 1.134$^{***}$ & 1.115$^{***}$ & $-$1.199$^{***}$ & $-$0.279 & 0.124 & $-$0.284 & 1.013$^{***}$ & 1.166$^{***}$ \\ 
+  & (0.303) & (0.304) & (0.339) & (0.435) & (0.429) & (0.436) & (0.318) & (0.318) & (0.357) \\ 
+  & & & & & & & & & \\ 
+ treated & $-$1.142$^{***}$ & $-$0.839$^{***}$ & 0.010 & $-$1.977$^{***}$ & $-$1.675$^{***}$ & 0.626 & $-$0.877$^{***}$ & $-$0.536$^{**}$ & 0.150 \\ 
+  & (0.214) & (0.209) & (0.281) & (0.284) & (0.274) & (0.416) & (0.221) & (0.215) & (0.297) \\ 
+  & & & & & & & & & \\ 
+ sate2 & 12.579$^{***}$ & 11.589$^{***}$ & 11.340$^{***}$ & 12.709$^{***}$ & 11.850$^{***}$ & 11.749$^{***}$ & 12.631$^{***}$ & 11.599$^{***}$ & 11.349$^{***}$ \\ 
+  & (0.197) & (0.199) & (0.232) & (0.212) & (0.213) & (0.246) & (0.199) & (0.201) & (0.235) \\ 
+  & & & & & & & & & \\ 
+ sate3 & 14.675$^{***}$ & 13.587$^{***}$ & 13.328$^{***}$ & 14.799$^{***}$ & 13.894$^{***}$ & 13.795$^{***}$ & 14.958$^{***}$ & 13.804$^{***}$ & 13.566$^{***}$ \\ 
+  & (0.260) & (0.262) & (0.307) & (0.286) & (0.287) & (0.329) & (0.264) & (0.266) & (0.315) \\ 
+  & & & & & & & & & \\ 
+ post:treated & $-$0.515$^{*}$ & $-$0.833$^{***}$ & $-$0.934$^{***}$ & 0.562 & 0.373 & $-$0.176 & $-$0.439 & $-$0.814$^{***}$ & $-$1.084$^{***}$ \\ 
+  & (0.281) & (0.276) & (0.310) & (0.413) & (0.402) & (0.407) & (0.293) & (0.287) & (0.326) \\ 
+  & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+Control & All & All & All & PNA & PNA & PNA & -CHN & -CHN & -CHN \\ 
+Month FE & No & Yes & Yes & No & Yes & Yes & No & Yes & Yes \\ 
+Flag FE & No & No & Yes & No & No & Yes & No & No & Yes \\ 
+Observations & 37,840 & 37,840 & 30,359 & 30,583 & 30,583 & 25,034 & 36,415 & 36,415 & 28,934 \\ 
+R$^{2}$ & 0.171 & 0.200 & 0.208 & 0.178 & 0.208 & 0.215 & 0.173 & 0.203 & 0.211 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\end{landscape}
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\label{fig:unnamed-chunk-14}\label{fig:long}Coefficient estimates
+for each model. Top pannel indicates variable, x-axis represents model
+specification, and y-axis coefficient estimate.}
+\end{figure}
 
@@
 
-\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of fishing hours by purse seiners ()}
+\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1), p < 0.001}
 \centering
-\fontsize{7}{9}\selectfont
 \begin{tabular}[t]{ll}
@@
 term & h\_prop\\
-
+\midrule
+(Intercept) & 0.087 (0.002)***\\
+post & -0.081 (0.003)***\\
+sate2 & -0.003 (0.001)***\\
+sate3 & -0.002 (0.001)\\
+post:countryEEZ COK 1 & 0.088 (0.002)***\\
+\addlinespace
+post:countryEEZ FSM 1 & 0.091 (0.003)***\\
+post:countryEEZ KIR 1 & 0.081 (0.003)***\\
+post:countryEEZ KIR 2 & 0.127 (0.004)***\\
+post:countryEEZ KIR 3 & 0.055 (0.005)***\\
+post:countryEEZ MHL 1 & 0.078 (0.003)***\\
+\addlinespace
+post:countryEEZ NRU 1 & 0.083 (0.003)***\\
+post:countryEEZ PNG 2 & -0.008 (0.005)*\\
+post:countryEEZ SLB 1 & 0.114 (0.004)***\\
+post:countryEEZ TUV 1 & 0.095 (0.003)***\\
+post:countryHS & 0.122 (0.003)***\\
+\addlinespace
+post:countryHS COK 1 & 0.083 (0.002)***\\
+post:countryHS KIR 1 & 0.112 (0.003)***\\
+post:countryHS KIR 2 & 0.093 (0.002)***\\
+post:countryHS KIR 3 & 0.108 (0.003)***\\
 \bottomrule
@@
 
-\hypertarget{year-as-dummy-variables}{%
-\subsubsection{Year as dummy variables}\label{year-as-dummy-variables}}
-
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
-  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
-  & & & & \\ 
- treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
-  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
-  & & & & \\ 
- post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
-  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
-  & & & & \\ 
- Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
-  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & No & Yes & Yes & Yes \\ 
-Year FE & No & No & Yes & Yes \\ 
-Flag FE & No & No & No & Yes \\ 
-Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
-R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment)..
+  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
 Asterisks indicate significance levels.
@@
 
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-2.pdf}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-3.pdf}
+
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-4.pdf}
-
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-3.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-4.pdf}
 

### 2018-10-19 rmd/Manuscript.Rmd
Updated manuscript draft

@@
 ---
-title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
+title: "Displacement of fishing effort by Large Scale Marine Protected Areas[^*]"
 subtitle: "Updated on `r Sys.Date()`"
@@
   bookdown::pdf_document2:
+    fig_height: 4
+    fig_width: 6
     toc: no
@@
   - \linenumbers
+  - \usepackage[bottom]{footmisc}
+  - \usepackage{pdflscape}
   - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
@@
 ---
+
+[^*]: Work in progress, do not circulate
+
+\clearpage
 
@@
                       message = FALSE,
-                      eval = TRUE)
+                      eval = T)
 
@@
 Current international goals aim to protect 10\% of the ocean environments by 2020.
-In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}.
-A significant part of this rapid increase can be attributed to the designation of a small number of Large Scale Marine Protected Areas (LSMPAs; \citet{boonzaier_2016,singleton_2014,gray_2017}).
-These are defined as MPAS larger than 250,000 Km^2^ in extension (Fig.
-\ref{fig:LSMPAs_map}), and are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{toonen_2013,gray_2017,kroodsma_2018}.
+In an effort to meet this target, the world has seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large Scale Marine Protected Areas (LSMPA) \citet{singleton_2014,boonzaier_2016,alger_2017}).
+Due to weak property rights, limited habitat transformation, and potentially lower management costs, LSMPAs provide an opportunity to safeguard the oceans \citet{game_2009}.
+Today, a small number of LSMPAs make up at least 80% of the managed areas in the ocean \citet{toonen_2013}.
 
 Given the relatively recent establishment of most LSMPAs, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
-Moreover, the world has seen a widespread increase in the implementation of LSMPAs, likely as a way to rapidly achieve the 10\% target \citep{boonzaier_2016,alger_2017,sala_2018}.
-However, as with customary MPAs, it is important that we understand the socioeconomic implications of management interventions that result in the spatial displacement of fishing effort.
-They **key gap in the literature is X**.
-We adress it here by using new stuff and find results that are of relevance to policy makers and advance our knowledge, which should be incorporated when designing and planning for LSMPAs.
+As with customary MPAs, it is important that we understand the socioeconomic implications of management interventions.
+One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of an MPA \citep{smith_2003}.
+Theoretical models make different assumptions about the way in which fishers will reallocate fishing effort after an area closure.
+The few empirical works focus on small-scale fisheries and rarely incorporate spatially explicit data.
+Despite these efforts, marine conservation is yet to identify the implications of these management interventions.
 
-Due to weak property rights, limited habitat transformation, and potentially lower management costs, pelagic MPAs provide an opportunity to safeguard the oceans \citet{game_2009}.
-A growing body of literature has shown that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+Here, we ask, how do fishers respond to the implementation of LSMPA?
+After a closure, and if they continue to fish, where do they reallocate fishing effort?
+We use novel satellite technologies and causal inference techniques to identify the behavioral changes and spatial redistribution of the industrial tuna purse seine fleet due to the implementation of a Large Scale Marine Protected Areas in the Western and Central Pacific Ocean (WCPO).
 
-The early literature on LSMPAs focused on the inherent difficulties that come with a pelagic (*i.e.* open water) environment, where organisms typically have large home ranges.
-\citet{game_2009} suggest that most of the challenges can be overcome with the incorporation of technology, in what then became known as Dynamic Ocean Management \citep{maxwell_2015}.
-\citet{kaplan_2009} claim that very large MPAs would result in excessive opportunity costs and that these would be difficult to enforce.
-\citet{toonen_2013} show that just a small number of LSMPAs made up 80% of the managed areas in the ocean in 2013, and that these can help achieve the CBD Aichi targets faster.
-\citet{singleton_2014} provide an objective discussion of pros and cons of LSMPAs.
-
-LSMPAs were erroneously assumed to have little social implications due to their remoteness.
-However, there have been calls to incorporate the human dimensions into LSMPAs management and evaluation \citep{agardy_2011,gray_2017}.
-Most research incorporating these human dimensions has focused on governance and enforcement of LSMPAs (*i.e.* \citet{alger_2017,christie_2017}), but they are yet to be the focus of economic analyses \citep{gray_2017}.
-Overall, there has been little empirical work regarding LSMPAs.
-Recent technological advances in vessel-detection systems allows for the discovery and advancement of many important facets of LSMPAs.
-For example, \citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention.
-\citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protectes two thrids of the tagged grey reef sharks by effectively excluding fishing effort.
-No studies have evaluated the displacement of fishing effort due to LSMPA implementation.
-
-The exclusion of these LSMPAs is likely to change fisher's behavior.
-Theoretical models of fishing effort redistribution range from the simplistic assumption that effort inside the bounded region disappears, to spatially explicit models that reallocate fishing effort based on habitat characteristics, presence of other vessels, and expected returns \citep{smith_2003,hilborn_2006}.
-However, these focus on the long term optimal equilibrium and redistribution of fishing effort may not be optimal, especially over the first years \citep{stevenson_2013}.
-The few empirical works suggest that resource users may show idiosyncratic responses.
-For example, \citet{stevenson_2013} show that a network of MPAs displaced fishing effort farther away from ports resulting in higher *perceived* costs, but that catch per unit effort also increased.
-\citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of MPAs in California, and find that commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
-The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006} highlighting the need to understand how fishers react to the implementation of LSMPAs, and fishing effort changes and is spatially redistributed.
-
-The main objective of this paper is to identify behavioral responses to the implementation of LSMPAs.
-We combine novel vessel tracking technologies and causal inference techniques to identify behavioral changes of fishing vessels due to the implementation of PIPA.
-We focus on fishing hours and distance traveled as outcome variables that fishers might adjust following implementation of a LSMPA in an impact-evaluation fashion.
-Additionally, we evaluate the spatial redistribution of fishing effort that existed within PIPA before its implementation.
-This work provides novel empirical insights into fisher's responses to the implementation of LSMPAs, and can help guide future interventions.
-Our work is novel in the sense that it provides empirical evidence of the effect of large-acale Marine Protected Areas in fishing behavior and distribution.
-
-The next sections are as follows: Section \ref{background} provides an overview of the Nauru Agreement and associated countries, a description of the fleet that operates in the region, and a brief history of PIPA.
-Section \ref{methods} describes our data and identification strategy.
-Section \ref{results} presents our results, section \ref{discussion} provides an extension of our results to other LSMPAs and discusses our results.
+The cutoff at which an MPA is considered to be a LSMPA ranges from areas larger than 30,000 km^2^ as defined by \citet{desanto_2013} or areas larger than 250,000 km^2^, as defined by \citep{toonen_2013}.
+Figure \ref{fig:LSMPAs_map} shows LSMPAs that meet the later, and that are fully no take.
+LSMPAs are often implemented in the pelagic environment, where the dominant human activity is industrial fishing \citep{gray_2017,kroodsma_2018}.
+The early literature on LSMPAs focused on the inherent challenges and difficulties that come with a pelagic environment.
+\citet{kaplan_2010} claimed that very large MPAs would result in excessive opportunity costs and that these would be difficult to enforce.
+\citet{game_2009} suggested that most of the challenges could be overcome with the incorporation of technology, in what then became known as Dynamic Ocean Management \citep{maxwell_2015}.
+The effectiveness and difficulties of implementating LSMPAs are not the focus of this paper \footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
+Instead, we focus on the effect and implications of the ones that *have been* implemented.
 
@@
 
+LSMPAs were erroneously assumed to have little social implications due to their remoteness.
+However, there have been calls to incorporate the human dimensions into LSMPAs management and evaluation \citep{agardy_2011,gray_2017}.
+Most research incorporating these dimensions has focused on governance and enforcement of LSMPAs (*i.e.* \citet{alger_2017,christie_2017}), but they are yet to be the focus of economic analyses \citep{gray_2017}.
+Overall, there has been little empirical work regarding LSMPAs.
+Recent technological advances in vessel-detection systems allows for the discovery and advancement of many important facets of LSMPAs.
+For example, \citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention.
+\citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protectes two thrids of the tagged grey reef sharks by effectively excluding fishing effort.
+More recently, \citep{bradley_2018} use similar data to highlight cases of illegal shark fishing *inside* a 2 million km^2^ shark sanctuary.
+To date, no studies have evaluated the displacement of fishing effort due to LSMPA implementation.
+
+The exclusion of these LSMPAs is likely to change fisher's behavior.
+Theoretical models of fishing effort redistribution range from the simplistic assumption that effort inside the bounded region disappears, to spatially explicit models that reallocate fishing effort based on habitat characteristics, presence of other vessels, and expected returns \citep{smith_2003,hilborn_2006}.
+However, these focus on the long term optimal equilibrium and redistribution of fishing effort may not be optimal, especially over the first years \citep{stevenson_2013}.
+The empirical research that has been done in custumary sized MPAs suggest that resource users may show idiosyncratic responses.
+For example, \citet{stevenson_2013} show that a network of MPAs displaced fishing effort farther away from ports, resulting in higher *perceived* costs, and increases in catch per unit effort.
+\citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of a network of MPAs in California, and find that commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
+The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006} highlighting the need to understand how fishers react to the implementation of LSMPAs, and fishing effort changes and is spatially redistributed.
+
+Our work is novel in the sense that it provides empirical evidence of the effect of large-acale Marine Protected Areas in fishing behavior and distribution and can help guide future interventions as countries march towards meetings the targeted 10\% of protection.
+Furthermore, a growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+Understanding how effort is displaced from LSMPAs might provide insights into how the industrial fleet would react to a high seas closure.
+
+The paper is outlined as follows: Section \ref{background} provides an overview of the Nauru Agreement and associated countries, a description of the fleet that operates in the region, and a brief history of PIPA.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion} provides an extension of our results to other LSMPAs\footnote{Not yet.
+but I think this would be interesting} and discusses our results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
+
 # Background
 
-The Nauru Agreement was established in 1982 by Pacific island nations to manage their important tuna resources.
-PNA Members include Federated States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated access of foreign vessels (*i.e.* those from non-PNA countries).
+The Nauru Agreement was established in 1982 by a select group of Pacific island nations to manage their important tuna resources.
+PNA Members include Federated States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua New Guinea, Solomon Islands, and Tuvalu.
+The Nauru Agreement regulated access of foreign vessels (*i.e.* those from non-PNA countries).
 Holding ~80% of the historical purse seining grounds within their Exclusive Economic Zones, PNA countries gained bargaining power when providing access to foreign fleets \citep{havice_2010}.
@@
 The VDS works as follows: Each year, scientific advisors recomend a total number of fishing vessel-days per year.
-Hours are allocated to each PNA country based on catch history, and they then sell fishing rights to other non-PNA countries \citep{aqorau_2018}.
+Hours are allocated to each PNA country based on catch history, and they then use or sell fishing rights to other non-PNA countries \citep{aqorau_2018}.
 While the effectiveness of this scheme has been debated in terms of meeting their fishery management and conservation objectives, the licensing significantly contributes to the economy of these island nations \citep{havice_2010}.
@@
 From these, the first two are amongst the top-10 species represented in global fisheries production statistics, with 2016 catches increasing relative to the 2005-2014 average \citep{fao_2018}.
-The pacific region has historically accounted for a large portion of tuna species production \citep{aqorau_1997}.
+Theis region of the Pacific has historically accounted for a large portion of tuna catches \citep{aqorau_1997}.
 Today, the PNA controls close to 50% of the global skipjack tuna production \citep{pna_website_2018}.
@@
 PIPA was first declared in 2006, and established in 2008 with only 4% of it was declared as no-take.
-In January 1^st^, 2015, the no-take area within PIPA was expanded to a total area of 397,447 Km^2^, roughly 1.5 times the size of Ecuador.
-The implementation of such a large conservation area in one of the most important fishing regions in the world provides a great opportunity to evaluate the behavioral responses and redistribution of fishing effort by vessels that used to fish there.
+In January 1^st^, 2015, the no-take area within PIPA was expanded to a total area of 397,447 km^2^, roughly 1.5 times the size of Ecuador.
+Figure \ref{fig:PNA_map} shows a map of the PNA countries and the Phoenix Island Protected Area.
+
+The closure of such a large area in one of the most important fishing regions in the world provides a great opportunity to evaluate the behavioral responses and redistribution of fishing effort by vessels that used to fish there.
 \citet{mcdermott_2018} showed that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) increased between the anouncement (September 1^st^, 2014) and its implementation in Janyary 1^st^, 2015.
@@
 First, we provide a general description of AIS data and the process of identification of vessel-level fishing events done by Global Fishing Watch[^1].
-Alongside, we describe the subset of data that we use for these analyses.
+Alongside, we describe the subset of data used on our analyses.
 When relevant, we also point out possible shortcomings in the data, or factors that must be considered in the later analyses.
@@
 
-Automatic Identification Systems are on-board devices intended to provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activities to surrounding vessels.
+Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
 These broadcasted messages can be received by satellites and land-based antennas.
-GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally since 2012 \citep{kroodsma_2018}.
-Our data contain information for 2012 - 2017.
-The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points), and therefore number of vessels and fishing hours.
+GFW uses convolutional neural networks to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally since 2012 \citep{kroodsma_2018}.
+
+The amount of data gathered is dependent on the number of antennas and satellites that can pick up the signals.
+In June 1^st^ 2014 satellite count increased from 3 to 6, and then to 10 in January 1^st^ 2016.
+This causes an increase in the number of *received* AIS messages (*i.e.* points), and therefore an apparent increase in the number of vessels and fishing hours.
+However, the addition of satellites "affects" all vessels in the same way.
 The variability in AIS data and ocean conditions require that temporal trends be taken into account.
-We do that by obtaining a subset of data that meet a BACI design, which gives us the full tracks for vessels affected and unaffected by the implementation of PIPA.
+We do that by including specific controls in our identification strategy and using a subset of data that meet a BACI design -which gives us the full tracks for vessels affected and unaffected by the implementation of PIPA.
 
@@
 effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
-  filter(year < 2018)
+  filter(year < 2018,
+         gear == "purse_seines")
 ```
@@
 pipa_vessels <- effort_by_vessel %>% 
-  filter(treated, baci_strict) %$%
+  filter(treated,
+         baci_strict) %$%
   unique(mmsi) %>% 
   length()
-
-effort_by_vessel %<>%
-  filter(gear == "purse_seines")
 ```
 
-Our data contain over 45 million individual AIS messages (*i.e.* positions) for 371 fishing vessels that at some point fished in PNA waters.
-A total of 233 vessels have fished within PIPA waters; 217 did so at least once before 2015.
-However, not all vessels continued to fish elsewhere after PIPA implementation: 34 vessels have no recorded AIS messages after 2015, leaving us with `r pipa_vessels` vessels that fished inside PIPA before its implementation, and continued to fish elsewhere afterward\footnote{The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
-In either case, we are not able to observe these.}.
-From these, we focus on purse seiners -the most important for PNA countries- and are left with 61 vessels\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
-New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period.
-To account for this, we identify a subset of vessels which we track since before the implementation of PIPA, and categorize them as treated or control vessels.
-Our treatment and control groups are defined as follows.
+Our analysis focuses on purse seiner vessels, the most important fishery for PNA countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
+We identify a total of 103 purse seiners that fished in PNA waters at least once before 2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore exlcuded from our analyses.}.
+These vessels represent over 26 million individual observations for the 2012 - 2017 period.
+We identify 65 vessels that have fished inside PIPA at least once since 2012.
+From these, 62 did so before the anouncement (*i.e.* 09/01/2014 *sensu* \citep{mcdermott_2018}) but are only able to track 61 for the complete periof of study before and after its implementation\footnote{1 vessel never fished again after August 18, 2013.}.
+On the other hand, 38 vessels never fished inside PIPA but we only have data for 26 vessels before and after.
 
-The treatment group contains all purse seiners (n = 61) that fished within PIPA at least once before the anouncement (09/01/2014), and that continued to fish elsewhere after the January 2015 implementation.
-Vessels in the control group meet the following two conditions: i) vessels never fished within PIPA waters, and ii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure.
-This definition of control vessels provides us with 26 purse seiners that never fished inside PIPA but fished in other PNA waters before and after PIPA implementation.
-During our causal identification, we also use two more strict definitions of control groups: one with only vessels that belong to PNA countries (n = 7), and one that excludes Chinese vessels (n = 21).
+Therefore, our treatment group contains all purse seiners (n = 61) that fished within PIPA at least once before the anouncement, and that continued to fish elsewhere after the January 2015 implementation.
+Vessels in the control group meet the following two conditions: i) vessels never fished within PIPA waters, and ii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure (n = 26).
+During our causal identification, we also use other two definitions of control groups, which further reduce our sample sizes: one with only vessels that belong to PNA countries (n = 7), and one that excludes Chinese vessels (n = 21).
 Our definition of treatment and control groups leaves us with 61 and 21 treated and control vessels, which have just over 22 million observations where about 22% are identified as fishing events.
-For each of the remainig vessels, we calculate their total daily fishing hours and obtain a pannel data with 38,200 observations.
+For each of the remainig vessels, we calculate their total daily fishing hours and obtain pannel data with 37,800 observations.
 Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
+Fig.
+\ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
+This trend is observed for both treated and control groups.
+Across all measures, the treatment and control vessels follow similar patterns, confirming our claim that the control group provides a plausible counterfactual.
 Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level fishing events that make up each group through time.
@@
 
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels.
+Vertical dashed lines indicates dates when satellites were added, solid line indicates PIPA closurePIPA closure."}
+effort_by_vessel %>% 
+  filter(baci_strict) %>%
+  group_by(year, gear, treated, post, month, date) %>% 
+  summarize(total_hours = sum(hours),
+            mean_hours = mean(hours),
+            n_mmsi = n()) %>% 
+  ungroup() %>% 
+  select(-year) %>% 
+  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
+  ggplot(aes(x = date, y = value, color = treated)) +
+  geom_point(shape = ".") +
+  facet_wrap(~variable, scales = "free", ncol = 1) +
+  ggtheme_plot() +
+  scale_color_brewer(palette = "Set1") +
+  geom_vline(xintercept = lubridate::date("2015/01/01")) +
+  geom_vline(xintercept = lubridate::date("2014/06/01"), linetype = "dashed") +
+  geom_vline(xintercept = lubridate::date("2015/12/31"), linetype = "dashed")
+```
+
 ## Analyses
+
+<!-- antes de 06/01/14 habian 3 sats, despues 6 hasta 12/31/15, luego 10 hasta 2017 y ahora hay muchos jaja -->
 
@@
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_i + \epsilon_{i,t}
 $$
@@
 $\alpha$ is the standard intercept, $\beta_1$ captures the temporal trend change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}
+Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions, and $\theta_i$ are a set of dummies that account for the addition of more satellites\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}.
 
 ```{r, eval = T}
+regions_few_points <- c("HS FSM 1", "HS MHL 1", "HS MUS 1", "HS NRU 1", "HS PNG 2", "HS SLB 1", "HS TUV 1")
+
 displacement_data <- readRDS(file = here::here("data", "displacement_data_ps.rds")) %>% 
-  filter(year < 2018)
+  filter(year < 2018,
+         !country %in% regions_few_points)
 ```
@@
 We discretize spatial units by using a polygon for PIPA \footnote{we would expect to see a decrease here} and distinct spatial units for each EEZ of each country.
-Some vessels might shift from EEZs into the High Seas, but we are interested in knowing *where* in the High Seas, so we incorporate additional regions by using a 1 degree buffer of the High Seas arround each of the EEZ regions.
+Some vessels might shift from EEZs into the high seas, but we are interested in knowing *where* in the high seas, so we incorporate additional regions by using a 1 degree buffer of the high seas arround each of the EEZ regions.
 The rest of the high seas are merged into a single spatial unit.
-For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZs, three 1-degree buffers of High Seas arround each EEZs, and the rest of the High Seas.
+For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZs, three 1-degree buffers of high seas arround each EEZs, and the rest of the high seas.
 Whenever the buffers overlapped between themselves, we randocmply clipped one on to the other.
@@
 $$
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \theta_i + \epsilon_{i,t}
 $$
@@
 Our parameter of interest is $\beta_{1,i}$, which captures the country-level change in proportional fishing effort.
+$\theta_i$ accounts for the addition of satellites.
 
@@
 ```{r}
-country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV")
+# country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV")
 
@@
 # Results
-
-Our data suggest that purse seiners and longliners have different responses to the implementation of a Large-Scale Marine Protected Areas.
-Fig.
-\ref{fig:all_vessels} shows that mean fishing hours for purse seiners have an abrupt increase, just before January 1st, 2015.
-This trend is observed for both treated and control groups.
-The pattern closely corresponds with the increase in total hours, but the total number of vessels doesn't entirely follow this pattern.
-The increase in fishing hours might be caused by the increased number of satellites[^6].
-Longliners, however, show no apparent trend with a clear seasonality \citep{ortuocrespo_2018}.
-The number of mmsi codes also increases slightly through time, but becomes stable after 2015.
-For both gears and across all measures, the treatment and control vessels follow similar patterns, confirming our claim that the control group provides a plausible counterfactual.
-
-[^6]: Need to check this.
-Not sure any satellites were incorporated during 2014.
-It is also possible that PNA countries started enforcing the requirement of having an AIS unit.
-On either case, both treatment and control groups seem to be affected equally.
-
-```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
-effort_by_vessel %>% 
-  filter(baci_strict) %>%
-  group_by(year, gear, treated, post, month, date) %>% 
-  summarize(total_hours = sum(hours),
-            mean_hours = mean(hours),
-            n_mmsi = n()) %>% 
-  ungroup() %>% 
-  # mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
-  select(-year) %>% 
-  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
-  ggplot(aes(x = date, y = value, color = treated)) +
-  geom_line() +
-  geom_point() +
-  facet_wrap(gear~variable, scales = "free", ncol = 3) +
-  ggtheme_plot() +
-  scale_color_brewer(palette = "Set1") +
-  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
-```
 
@@
 
-```{r, results = "asis", echo = F}
-
+```{r}
 model_base <- effort_by_vessel %>% 
@@
          flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
-         flag_fe_oth = flag_fe & !flag == "OTH")
+         flag_fe_oth = flag_fe & !flag == "OTH",
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3",
+                          T ~ "2"))
 
@@
 models_exp1_did <- experiment1 %>% did()
-models_exp2_did <- experiment2 %>% did()
 models_exp3_did <- experiment3 %>% did()
@@
 models_exp1_did_q <- experiment1 %>% did_quarter()
-models_exp2_did_q <- experiment2 %>% did_quarter()
 models_exp3_did_q <- experiment3 %>% did_quarter()
@@
 models_exp1_did_ym <- experiment1 %>% did_yearmonth()
-models_exp2_did_ym <- experiment2 %>% did_yearmonth()
 models_exp3_did_ym <- experiment3 %>% did_yearmonth()
-
-# map(models_exp3_did, summary)
 ```
 
-```{r, eval = F}
+\clearpage
+\begin{landscape}
+
+```{r, results = "asis"}
+
+models <- c(models_exp0_did,
+            models_exp1_did,
+            models_exp3_did)
+
 stargazer::stargazer(models,
@@
                      p.auto = T,
+                     intercept.bottom = F,
+                     column.sep.width = "1pt",
+                     font.size = "small",
                      type = "latex",
                      omit = c("flag", "month"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
-                                      c("Flag FE", "No", "No", "No", "Yes")),
+                     add.lines = list(
+                       c("Control", rep("All", 3), rep("PNA", 3), rep("-CHN", 3)),
+                       c("Month FE", rep(c("No", "Yes", "Yes"), 3)),
+                       c("Flag FE", rep(c("No", "No", "Yes"), 3))),
                      omit.stat = c("adj.rsq", "f", "ser"),
                      header = F,
-                     title = "DiD",
-                     out = "DID.html")
+                     # float.env = "sidewaystable",
+                     title = "Difference-in-differences estimates for 3 different controls and 3 different specifications.
+The first three columns use all data for controls.
+Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Numbers in parentheses are heteroskedastic-robust standard errors.")
 ```
 
+\end{landscape}
+\clearpage
+
 ```{r, fig.width = 5, fig.height = 3, fig.cap = "\\label{fig:long}Coefficient estimates for each model.
-Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate.", eval = F}
-map_df(models, broom::tidy, .id = "model") %>%
+Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
+map_df(models, commarobust::commarobust_tidy, .id = "model") %>%
   filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
-  ggplot(aes(x = model, y = estimate)) +
-  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error),
+  mutate(control = case_when(model < 4 ~ "All",
+                             model > 6 ~ "-CHN",
+                             T ~ "TWN")) %>% 
+  ggplot(aes(x = model, y = est)) +
+  geom_errorbar(aes(ymin = est - se, ymax = est + se),
                 size = 1,
                 width = 0,
-                color = "red") +
-  geom_point(color = "steelblue", size = 3) +
+                color = "black") +
+  geom_point(aes(color = control), size = 3, alpha = 0.7) +
   facet_wrap(~term, scale = "free") +
-  ggtheme_plot()
+  ggtheme_plot() +
+  geom_hline(yintercept = 0, linetype = "dashed")
 ```
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'."}
+```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'.", eval = T}
 displacement_data %>% 
@@
          h_prop > 0) %>%
-  ggplot(aes(x = date, y = h_prop, group = post)) +
-  geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
-  geom_point(size = 1) +
+  ggplot(aes(x = date, y = h_prop, group = post, color = post)) +
+  # geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
+  geom_point() +
   geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
@@
   ggtheme_plot() +
-  facet_wrap(~country, scales = "free_y")
+  facet_wrap(~country, scales = "free_y") +
+  scale_color_brewer(palette = "Set1")
 ```
@@
 
+eezs_exclude <- c("HS MUS 1", "EEZ MUS 1", "EEZ MDG 1", "EEZ MDG 2", "HS MDG 1", "HS MDG 2", "HS MOZ 1", "EEZ MOZ 1")
+
 # I AM EXCLUDING MUS WHICH SHOULD BE PUT INTO EEZ
@@
   left_join(ba_disp, by = c("id" = "country")) %>%
-  filter(!is.na(change),
-         !id == "HS MUS 1") %>%
+  filter(!id %in% eezs_exclude) %>%
   ggplot() +
@@
   filter(!is.na(country),
-         gear == "purse_seines") %>% 
+         gear == "purse_seines",
+         !country %in% regions_few_points) %>% 
   mutate(post = post *1,
@@
          month_c = as.character(month),
-         country = fct_relevel(country, "PIPA PIPA 1"))
+         country = fct_relevel(country, "PIPA PIPA 1"),
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3",
+                          T ~ "2"))
 
-disp_mod_ps1 <- lm(h_prop ~ post*country, data = disp_mod_ps_data)
-
-models <- list(disp_mod_ps1)
+disp_mod_ps1 <- lm(h_prop ~ post*country + sate, data = disp_mod_ps_data)
 
 commarobust::commarobust_tidy(disp_mod_ps1) %>% 
-  as.data.frame() %>% 
-  mutate(term = rownames(.)) %>% 
   mutate(b = str_detect(term, "Intercept"),
          c = str_detect(term, "post"),
+         d = str_detect(term, "sate"),
          a = b*c,
@@
                     p3)) %>% 
-  filter(b+c > 0) %>% 
+  filter(b+c+d > 0) %>% 
   select(term, h_prop) %>% 
   knitr::kable(booktabs = T,
-               caption = "Change in the relative allocation of fishing hours by purse seiners ()") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position",
-                            font_size = 7)
+               caption = "Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1), p < 0.001") %>% 
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 
@@
 
-### Year as dummy variables
-
-```{r, results = "asis", echo = F}
-
-model_data <- effort_by_vessel %>% 
-  filter(baci_strict,
-         gear == "purse_seines") %>% 
-  mutate(post = post * 1,
-         treated = treated * 1,
-         mmsi_c = as.factor(mmsi))
-
-m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month_c, data = model_data)
-m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
-m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
-
-models <- list(m1, m2, m3, m4)
-
-stargazer::stargazer(models,
-                     se = commarobust::makerobustseslist(models),
-                     t.auto = T,
-                     p.auto = T,
-                     type = "latex",
-                     omit = c("flag", "year", "month"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
-                                      c("Year FE", "No", "No", "Yes", "Yes"),
-                                      c("Flag FE", "No", "No", "No", "Yes")),
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     title = "\\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
-```
-
 ```{r, results = "asis"}
@@
 
-```{r, results = "asis", eval = F}
-models_exp0_did %>% stargazer::stargazer()
-models_exp1_did %>% stargazer::stargazer()
-models_exp2_did %>% stargazer::stargazer()
-models_exp3_did %>% stargazer::stargazer()
+```{r, eval = F}
+models_q <- list(models_exp0_did_q,
+                 models_exp1_did_q,
+                 models_exp3_did_q)
+
+stargazer::stargazer(models_q,
+                     se = commarobust::makerobustseslist(models_q[[1]]),
+                     t.auto = T,
+                     p.auto = T,
+                     intercept.bottom = F,
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(
+                       c("Control", rep("All", 2), rep("PNA", 2), rep("-CHN", 2)),
+                       c("Flag FE", rep(c("No", "Yes"), 3))),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     title = "Difference-in-differences estimates for 3 different controls and 3 different specifications.
+The first three columns use all data for controls.
+Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Numbers in parentheses are heteroskedastic-robust standard errors.",
+                     out = "DID_q.html")
 ```
@@
 models_exp1_did_q %>% termplot(q = T)
-models_exp2_did_q %>% termplot(q = T)
 models_exp3_did_q %>% termplot(q = T)
@@
 models_exp1_did_ym %>% termplot()
-models_exp2_did_ym %>% termplot()
 models_exp3_did_ym %>% termplot()

### 2018-10-19 docs/Manuscript.tex
updated mscrpt

@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-10-18}
+  \subtitle{Updated on 2018-10-19}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 about the way in which fishers will reallocate fishing effort after an
-area closure \citep{}. The few empirical works focus on small-scale
-fisheries and rarely incorporate spatially explicit data. Despite these
-efforts, marine conservation is yet to identify the implications of
-these management interventions.
+area closure. The few empirical works focus on small-scale fisheries and
+rarely incorporate spatially explicit data. Despite these efforts,
+marine conservation is yet to identify the implications of these
+management interventions.
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
-Protected Areas. The map shows all areas larger than 250,000
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+\caption{\label{fig:unnamed-chunk-27}\label{fig:LSMPAs_map}Large Scale
+Marine Protected Areas. The map shows all areas larger than 250,000
 Km\textsuperscript{2}. Areas in dark blue meet at least one of these
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
+\caption{\label{fig:unnamed-chunk-28}\label{fig:PNA_map}Map of the Exclusive
 Economic Zones (EEZs) of the region of interest. A solid line indicates
@@
 
-The implementation of such a large conservation area in one of the most
-important fishing regions in the world provides a great opportunity to
-evaluate the behavioral responses and redistribution of fishing effort
-by vessels that used to fish there. \citet{mcdermott_2018} showed that
-fishing effort within the Phoenix Islands Marine Protected Area (PIPA)
-increased between the anouncement (September 1\textsuperscript{st},
-2014) and its implementation in Janyary 1\textsuperscript{st}, 2015.
-Likewise, they demonstrate that fishing effort is effectively reduced
-after implementation. To this, we pose two questions: How do individual
+The closure of such a large area in one of the most important fishing
+regions in the world provides a great opportunity to evaluate the
+behavioral responses and redistribution of fishing effort by vessels
+that used to fish there. \citet{mcdermott_2018} showed that fishing
+effort within the Phoenix Islands Marine Protected Area (PIPA) increased
+between the anouncement (September 1\textsuperscript{st}, 2014) and its
+implementation in Janyary 1\textsuperscript{st}, 2015. Likewise, they
+demonstrate that fishing effort is effectively reduced after
+implementation. To this, we pose two questions: How do individual
 vessels respond to the sudden exclusion of such a big area? And where
@@
   Fishing Watch: \url{globalfishingwatch.org}}. Alongside, we describe
-the subset of data that we use for these analyses. When relevant, we
-also point out possible shortcomings in the data, or factors that must
-be considered in the later analyses. We then move on to explain our
+the subset of data used on our analyses. When relevant, we also point
+out possible shortcomings in the data, or factors that must be
+considered in the later analyses. We then move on to explain our
 empirical strategy for the identification of the behavioral changes and
@@
 
-Automatic Identification Systems are on-board devices intended to
-provide at-sea safety and prevent ship collisions by broadcasting vessel
-position, course, and activities to surrounding vessels. These
-broadcasted messages can be received by satellites and land-based
-antennas. GFW uses convolutional neural networks to infer vessel
-characteristics and whether each broadcasted position represents a
-fishing event, thus allowing us to estimate near real-time fishing
-events globally since 2012 \citep{kroodsma_2018}. Our data contain
-information for 2012 - 2017. The amount of data gathered is dependent on
-the number of antenas and satellites that can pick up the signals. In
-June 1\textsuperscript{st} 2014 satellite count increased from 3 to 6,
-and then to 10 in January 1\textsuperscript{st} 2016. This causes an
-apparent increase in the number of broadcasted AIS messages (\emph{i.e.}
-points), and therefore number of vessels and fishing hours. The
+Automatic Identification Systems (AIS) are on-board devices that provide
+at-sea safety and prevent ship collisions by broadcasting vessel
+position, course, and activity to surrounding vessels. These broadcasted
+messages can be received by satellites and land-based antennas. GFW uses
+convolutional neural networks to infer vessel characteristics and
+whether each broadcasted position represents a fishing event, thus
+allowing us to estimate near real-time fishing events globally since
+2012 \citep{kroodsma_2018}.
+
+The amount of data gathered is dependent on the number of antennas and
+satellites that can pick up the signals. In June 1\textsuperscript{st}
+2014 satellite count increased from 3 to 6, and then to 10 in January
+1\textsuperscript{st} 2016. This causes an increase in the number of
+\emph{received} AIS messages (\emph{i.e.} points), and therefore an
+apparent increase in the number of vessels and fishing hours. However,
+the addition of satellites ``affects'' all vessels in the same way. The
 variability in AIS data and ocean conditions require that temporal
@@
 
-Our data contain over 45 million individual AIS messages (\emph{i.e.}
-positions) for 371 fishing vessels that at some point fished in PNA
-waters. A total of 233 vessels have fished within PIPA waters; 217 did
-so at least once before 2015. However, not all vessels continued to fish
-elsewhere after PIPA implementation: 34 vessels have no recorded AIS
-messages after 2015, leaving us with 176 vessels that fished inside PIPA
-before its implementation, and continued to fish elsewhere
-afterward\footnote{The 34 missing vessels might have exited the fishery, been decommissioned or sold (therefore changing their AIS and mmsi), or turned off their AIS transmitters.
-In either case, we are not able to observe these.}.
-From these, we focus on purse seiners -the most important for PNA
-countries- and are left with 61
-vessels\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
-New vessels might have also entered the fishery after PIPA closure, and
-were likely not exposed to the policy intervention in the pre-treatment
-period. To account for this, we identify a subset of vessels which we
-track since before the implementation of PIPA, and categorize them as
-treated or control vessels. Our treatment and control groups are defined
-as follows.
+Our analysis focuses on purse seiner vessels, the most important fishery
+for PNA
+countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
+We identify a total of 103 purse seiners that fished in PNA waters at
+least once before
+2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore exlcuded from our analyses.}.
+These vessels represent over 26 million individual observations for the
+2012 - 2017 period. We identify 65 vessels that have fished inside PIPA
+at least once since 2012. From these, 62 did so before the anouncement
+(\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}) but are
+only able to track 61 for the complete periof of study before and after
+its
+implementation\footnote{1 vessel never fished again after August 18, 2013.}.
+On the other hand, 38 vessels never fished inside PIPA but we only have
+data for 26 vessels before and after.
 
-The treatment group contains all purse seiners (n = 61) that fished
-within PIPA at least once before the anouncement (09/01/2014), and that
+Therefore, our treatment group contains all purse seiners (n = 61) that
+fished within PIPA at least once before the anouncement, and that
 continued to fish elsewhere after the January 2015 implementation.
@@
 surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
-closure. This definition of control vessels provides us with 26 purse
-seiners that never fished inside PIPA but fished in other PNA waters
-before and after PIPA implementation. During our causal identification,
-we also use two more strict definitions of control groups: one with only
-vessels that belong to PNA countries (n = 7), and one that excludes
-Chinese vessels (n = 21). Our definition of treatment and control groups
-leaves us with 61 and 21 treated and control vessels, which have just
-over 22 million observations where about 22\% are identified as fishing
-events. For each of the remainig vessels, we calculate their total daily
-fishing hours and obtain pannel data with 37,800 observations. Table
-\ref{tab:baci_n_s} shows the number of vessels following a BACI design,
-as well as the fishing hours, before and after PIPA. Fig.
-\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
-have an abrupt increase, just before January 1st, 2015. This trend is
-observed for both treated and control groups. Across all measures, the
-treatment and control vessels follow similar patterns, confirming our
-claim that the control group provides a plausible counterfactual. Figure
-\ref{fig:baci_strict} provides a visual representation of the
-vessel-level fishing events that make up each group through time.
+closure (n = 26).
+
+We include three additional definitions of control groups as a
+robustness check: one with only vessels that belong to PNA countries (n
+= 7), and one that excludes Chinese vessels (n = 21). Our third control
+is made up of Japanese purse seiners that fish in the Pacific but that
+never fished inside PIPA (n =
+27)\footnote{Using Taiwanese vessels was the original idea, but there are only 4 vessels with pre-2015 data.
+I need to further identify propper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
+Our definition of treatment and control groups leaves us with 61 and 21
+treated and control vessels, which have just over 22 million
+observations where about 22\% are identified as fishing events.
+
+For each vessel we calculate total daily fishing hours and obtain pannel
+data with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
+of vessels following a BACI design, as well as the fishing hours, before
+and after PIPA. Fig. \ref{fig:all_vessels} shows that mean fishing hours
+for purse seiners have an abrupt increase, just before January 1st,
+2015. This trend is observed for both treated and control groups. Across
+all measures, the treatment and control vessels follow similar patterns,
+confirming our claim that the control group provides a plausible
+counterfactual. Figure \ref{fig:baci_strict} provides a visual
+representation of the vessel-level fishing events that make up each
+group through time. We use this data to answer our key questions: How do
+the 61 purse seiners modify their behavior as compared to the different
+control groups, and where do they go after the spatial closure? The
+following section describes our empirical identification strategies.
 
@@
 
-\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-31}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels. Vertical dashed lines
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
+\caption{\label{fig:unnamed-chunk-32}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels. Vertical dashed lines
 indicates dates when satellites were added, solid line indicates PIPA
@@
 vessels to PIPA closure. Our variables of interests are daily fishing
-hours, and daily distance traveled (Km). We compare our variable of
+hours, and daily distance traveled (km). We compare our variable of
 interest before and after the implementation of PIPA using a
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \]
@@
 month-, and flag-level dummies that account for seasonality or
-country-level management interventions, and \(\theta_i\) are a set of
-dummies that account for the addition of more
-satellites\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}.
+country-level management
+interventions\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
 
@@
 \[
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \theta_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 \]
@@
 interest is \(\beta_{1,i}\), which captures the country-level change in
-proportional fishing effort. \(\theta_i\) accounts for the addition of
-satellites.
+proportional fishing effort.
 
@@
 
-\caption{\label{tab:unnamed-chunk-10}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
+\caption{\label{tab:unnamed-chunk-35}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
 \centering
@@
 
+Our DiD analysis shows an overall increase in purse seine fishing hours,
+even after accounting for the introduction of new satellites (Table
+\ref{tab:did}). This coefficient estimate is consistent for different
+model specifications and across groups of treatment and controls. These
+effectively represent the patterns observed in Figure
+\ref{fig:all_vessels}. The \(\beta_3\) coefficient indicating our
+treatment effect suggests that, relative to the control, treated vessels
+fish less, in the order of 0.5 hours per day. Another way to interpret
+this is that the increase in fishing effort by treated vessels has
+ocurred at a lower rate than control vessels. This result is robust and
+significant (\(p < 0.05\)) for all model specifications using our main
+control group, with the effect varying between \(\beta_3 = -0.515\) and
+\(\beta_3 = -0.934\). These values are equivalent to a 15 - 28 reduction
+in fishing hours per month.
+
+Regressions coefficients for our DiD analysis are shown in Table
+\ref{tab:did}. Columns 1 -3 use all data for controls. Columns 4 - 6 use
+only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
+hence don't include flag FEs to avoid perfect colinearity between
+Japanese flag and
+control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
+It must be noted, however, that when reducing the linear structure of
+the \(Pre \times Post\) design and instead interacting the treatment
+dummy with quarterly or year-month combinations we are not able to
+reject the null hypotheses of no change (Figures
+\ref{fig:q1,fig:q2,fig:q3,fig:q4,fig:ym1,fig:ym2,fig:ym3,fig:ym4}).
+
 \begin{figure}
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels. Vertical dashed line
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
+\caption{\label{fig:unnamed-chunk-36}\label{fig:all_vessels}Daily fishing
+hours for all vessels in our main treatment-control groups. Solid
+straight lines show a linear trend by period (pre-psot) and treatment.
+The other red and blue lines show monthly avarages. Vertical dashed line
 indicates PIPA closure.}
 \end{figure}
-
-Our DiD analysis shows that treated purse seiners reduce their fishing
-effort after PIPA implementation in the order of 16 hours per month.
-This result is robust and significant (\emph{p \textless{} 0.05}) for
-all model specifications, with the effect varying between
-\(\beta_3 = -16.457\) and \(\beta_3 = -18.709\). Model specifications
-that include the year polynomial show lower values for the \(\beta_1\)
-coefficient associated to the \(Post_t\) policy dummy, and show positive
-and negative values for \(\mu_1\) and \(\mu_2\), the linear and
-quadratic terms for \(Y_t\), respectively. These effectively represent
-the patterns observed in Figure \ref{fig:all_vessels}.
-
-Regressions coefficients for each gear type are shown in Tables
-\ref{tab:purse} and \ref{tab:long}. Column (1) presents the DiD
-regression with no fixed effects, column (2) includes month fixed
-effects, column (3) includes month and the second degree polynomial for
-years, and column (4) includes all of the above and country-level fixed
-effects.
 
@@
 \begin{table}[!htbp] \centering 
-  \caption{Difference-in-differences estimates for 3 different controls and 3 different specifications.
+  \caption{\label{tab:did}Difference-in-differences estimates for 3 different controls and 3 different specifications.
 The first three columns use all data for controls.
-Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
   \label{} 
-\small 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
- & \multicolumn{9}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-10} 
-\\[-1.8ex] & \multicolumn{9}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+ & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-12} 
+\\[-1.8ex] & \multicolumn{11}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
 \hline \\[-1.8ex] 
- Constant & 6.345$^{***}$ & 7.863$^{***}$ & 10.322$^{***}$ & 7.124$^{***}$ & 9.007$^{***}$ & 9.933$^{***}$ & 6.057$^{***}$ & 7.584$^{***}$ & 10.194$^{***}$ \\ 
-  & (0.186) & (0.274) & (0.404) & (0.265) & (0.341) & (0.620) & (0.193) & (0.279) & (0.538) \\ 
-  & & & & & & & & & \\ 
- post & $-$0.052 & 1.134$^{***}$ & 1.115$^{***}$ & $-$1.199$^{***}$ & $-$0.279 & 0.124 & $-$0.284 & 1.013$^{***}$ & 1.166$^{***}$ \\ 
-  & (0.303) & (0.304) & (0.339) & (0.435) & (0.429) & (0.436) & (0.318) & (0.318) & (0.357) \\ 
-  & & & & & & & & & \\ 
- treated & $-$1.142$^{***}$ & $-$0.839$^{***}$ & 0.010 & $-$1.977$^{***}$ & $-$1.675$^{***}$ & 0.626 & $-$0.877$^{***}$ & $-$0.536$^{**}$ & 0.150 \\ 
-  & (0.214) & (0.209) & (0.281) & (0.284) & (0.274) & (0.416) & (0.221) & (0.215) & (0.297) \\ 
-  & & & & & & & & & \\ 
- sate2 & 12.579$^{***}$ & 11.589$^{***}$ & 11.340$^{***}$ & 12.709$^{***}$ & 11.850$^{***}$ & 11.749$^{***}$ & 12.631$^{***}$ & 11.599$^{***}$ & 11.349$^{***}$ \\ 
-  & (0.197) & (0.199) & (0.232) & (0.212) & (0.213) & (0.246) & (0.199) & (0.201) & (0.235) \\ 
-  & & & & & & & & & \\ 
- sate3 & 14.675$^{***}$ & 13.587$^{***}$ & 13.328$^{***}$ & 14.799$^{***}$ & 13.894$^{***}$ & 13.795$^{***}$ & 14.958$^{***}$ & 13.804$^{***}$ & 13.566$^{***}$ \\ 
-  & (0.260) & (0.262) & (0.307) & (0.286) & (0.287) & (0.329) & (0.264) & (0.266) & (0.315) \\ 
-  & & & & & & & & & \\ 
- post:treated & $-$0.515$^{*}$ & $-$0.833$^{***}$ & $-$0.934$^{***}$ & 0.562 & 0.373 & $-$0.176 & $-$0.439 & $-$0.814$^{***}$ & $-$1.084$^{***}$ \\ 
-  & (0.281) & (0.276) & (0.310) & (0.413) & (0.402) & (0.407) & (0.293) & (0.287) & (0.326) \\ 
-  & & & & & & & & & \\ 
+ Constant & 6.345$^{***}$ & 7.863$^{***}$ & 10.322$^{***}$ & 7.124$^{***}$ & 9.007$^{***}$ & 9.933$^{***}$ & 6.057$^{***}$ & 7.584$^{***}$ & 10.194$^{***}$ & 22.625$^{***}$ & 24.731$^{***}$ \\ 
+  & (0.186) & (0.274) & (0.404) & (0.265) & (0.341) & (0.620) & (0.193) & (0.279) & (0.538) & (0.629) & (0.683) \\ 
+  & & & & & & & & & & & \\ 
+ post & $-$0.052 & 1.134$^{***}$ & 1.115$^{***}$ & $-$1.199$^{***}$ & $-$0.279 & 0.124 & $-$0.284 & 1.013$^{***}$ & 1.166$^{***}$ & 2.330$^{***}$ & 3.991$^{***}$ \\ 
+  & (0.303) & (0.304) & (0.339) & (0.435) & (0.429) & (0.436) & (0.318) & (0.318) & (0.357) & (0.890) & (0.877) \\ 
+  & & & & & & & & & & & \\ 
+ treated & $-$1.142$^{***}$ & $-$0.839$^{***}$ & 0.010 & $-$1.977$^{***}$ & $-$1.675$^{***}$ & 0.626 & $-$0.877$^{***}$ & $-$0.536$^{**}$ & 0.150 & $-$18.190$^{***}$ & $-$18.257$^{***}$ \\ 
+  & (0.214) & (0.209) & (0.281) & (0.284) & (0.274) & (0.416) & (0.221) & (0.215) & (0.297) & (0.673) & (0.661) \\ 
+  & & & & & & & & & & & \\ 
+ sate2 & 12.579$^{***}$ & 11.589$^{***}$ & 11.340$^{***}$ & 12.709$^{***}$ & 11.850$^{***}$ & 11.749$^{***}$ & 12.631$^{***}$ & 11.599$^{***}$ & 11.349$^{***}$ & 14.346$^{***}$ & 12.967$^{***}$ \\ 
+  & (0.197) & (0.199) & (0.232) & (0.212) & (0.213) & (0.246) & (0.199) & (0.201) & (0.235) & (0.303) & (0.309) \\ 
+  & & & & & & & & & & & \\ 
+ sate3 & 14.675$^{***}$ & 13.587$^{***}$ & 13.328$^{***}$ & 14.799$^{***}$ & 13.894$^{***}$ & 13.795$^{***}$ & 14.958$^{***}$ & 13.804$^{***}$ & 13.566$^{***}$ & 15.187$^{***}$ & 13.719$^{***}$ \\ 
+  & (0.260) & (0.262) & (0.307) & (0.286) & (0.287) & (0.329) & (0.264) & (0.266) & (0.315) & (0.402) & (0.410) \\ 
+  & & & & & & & & & & & \\ 
+ post:treated & $-$0.515$^{*}$ & $-$0.833$^{***}$ & $-$0.934$^{***}$ & 0.562 & 0.373 & $-$0.176 & $-$0.439 & $-$0.814$^{***}$ & $-$1.084$^{***}$ & $-$3.209$^{***}$ & $-$3.715$^{***}$ \\ 
+  & (0.281) & (0.276) & (0.310) & (0.413) & (0.402) & (0.407) & (0.293) & (0.287) & (0.326) & (0.811) & (0.799) \\ 
+  & & & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Control & All & All & All & PNA & PNA & PNA & -CHN & -CHN & -CHN \\ 
-Month FE & No & Yes & Yes & No & Yes & Yes & No & Yes & Yes \\ 
-Flag FE & No & No & Yes & No & No & Yes & No & No & Yes \\ 
-Observations & 37,840 & 37,840 & 30,359 & 30,583 & 30,583 & 25,034 & 36,415 & 36,415 & 28,934 \\ 
-R$^{2}$ & 0.171 & 0.200 & 0.208 & 0.178 & 0.208 & 0.215 & 0.173 & 0.203 & 0.211 \\ 
+Control & All & All & All & PNA & PNA & PNA & -CHN & -CHN & -CHN & JPN & JPN \\ 
+Month FE & No & Yes & Yes & No & Yes & Yes & No & Yes & Yes & No & Yes \\ 
+Flag FE & No & No & Yes & No & No & Yes & No & No & Yes & No & No \\ 
+Observations & 37,840 & 37,840 & 30,359 & 30,583 & 30,583 & 25,034 & 36,415 & 36,415 & 28,934 & 34,047 & 34,047 \\ 
+R$^{2}$ & 0.171 & 0.200 & 0.208 & 0.178 & 0.208 & 0.215 & 0.173 & 0.203 & 0.211 & 0.260 & 0.280 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{11}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\label{fig:unnamed-chunk-14}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
+\caption{\label{fig:unnamed-chunk-38}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
-relative fishing hours that each region received by all 176 treated
+relative fishing hours that each region received by all 61 treated
 vessels. The top-left panel shows the change in fishing effort inside
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-39-1.pdf}
+\caption{\label{fig:unnamed-chunk-39}\label{fig:redist_trend_ps}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
-\caption{\label{fig:unnamed-chunk-16}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-40-1.pdf}
+\caption{\label{fig:unnamed-chunk-40}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
@@
 
-\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1), p < 0.001}
+\caption{\label{tab:unnamed-chunk-41}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
 \centering
@@
 
+\hypertarget{refs}{}
+
+\clearpage
+
 \hypertarget{appendix}{%
@@
 
+\hypertarget{stream-of-data-by-vessel-group-and-period}{%
+\subsection{Stream of data by vessel, group, and
+period}\label{stream-of-data-by-vessel-group-and-period}}
+
 \begin{figure}
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
+\caption{\label{fig:unnamed-chunk-42}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 
-\hypertarget{other-model-specifications}{%
-\subsection{Other model
-specifications}\label{other-model-specifications}}
+\clearpage
+
+\hypertarget{longliners}{%
+\subsection{Longliners}\label{longliners}}
+
+Longliners show a similar pattern of effort reduction. However, the
+magnitude of the \(\beta_3\) coefficient is smaller (ranging from
+\(\beta_3 = -0.98\) to \(\beta_3 = -1.125\)) and not significant unless
+including month and flag FEs for the general treatment-control groups,
+or when excluding Chinese vessels. This, along with higher standard
+error values suggest that longliners have a smaller and more variable
+response to the implementation of LSMPAs.
 
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
-Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.}
+  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications.
+The first three columns use all data for controls.
+Columns 4 - 6 exclude Chinese vessels.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
   \label{} 
+\small 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
+  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
+  & & & & & & \\ 
+ post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
+  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
+  & & & & & & \\ 
+ treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
+  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
+  & & & & & & \\ 
+ sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
+  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
+  & & & & & & \\ 
+ sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
+  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
+  & & & & & & \\ 
+ post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
+  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Control & All & All & All & -CHN & -CHN & -CHN \\ 
+Month FE & No & Yes & Yes & No & Yes & Yes \\ 
+Flag FE & No & No & Yes & No & No & Yes \\ 
+Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
+R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\clearpage
+
+\hypertarget{other-model-specifications-for-purse-seiners}{%
+\subsection{Other model specifications for purse
+seiners}\label{other-model-specifications-for-purse-seiners}}
+
+We include a second degree polinomial for years as:
+
+\[
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
+\]
+
+\textbackslash{}begin\{table\}{[}!htbp{]} \centering 
+\textbackslash{}caption\{\label{tab:purse}Fishing hours from GFW for
+purse\_seiners. Asterisks indicate significance levels. Numbers in
+parentheses represent heteroskedastic-robust standard errors.\} \label{}
+
 \begin{tabular}{@{\extracolsep{5pt}}lcccc} 
@@
 \hline \\[-1.8ex] 
- post & $-$1.241$^{***}$ & $-$1.026$^{***}$ & $-$0.944$^{***}$ & 13.292$^{***}$ \\ 
-  & (0.116) & (0.116) & (0.157) & (0.330) \\ 
+ post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
+  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
   & & & & \\ 
- treated & 2.595$^{***}$ & 2.708$^{***}$ & 2.639$^{***}$ & 1.493$^{***}$ \\ 
-  & (0.101) & (0.101) & (0.102) & (0.116) \\ 
+ treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
+  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
   & & & & \\ 
- post:treated & 0.053 & $-$0.069 & $-$0.029 & $-$0.060 \\ 
-  & (0.133) & (0.133) & (0.134) & (0.135) \\ 
+ post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
+  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
   & & & & \\ 
- Constant & 39.032$^{***}$ & 38.105$^{***}$ & 38.388$^{***}$ & 36.993$^{***}$ \\ 
-  & (0.089) & (0.131) & (0.150) & (0.178) \\ 
+ Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
+  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
   & & & & \\ 
@@
 Flag FE & No & No & No & Yes \\ 
-Observations & 227,873 & 227,873 & 227,873 & 227,873 \\ 
-R$^{2}$ & 0.010 & 0.015 & 0.016 & 0.030 \\ 
+Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
+R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
 \hline 
@@
 \end{tabular}
-\end{table}
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-3.pdf}
+\textbackslash{}end\{table\}
 
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-2.pdf}
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-3.pdf}
+\hypertarget{quarterly-did-interactions}{%
+\subsubsection{Quarterly DID
+interactions}\label{quarterly-did-interactions}}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-45-1.pdf}
+\caption{\label{fig:unnamed-chunk-45}\label{fig:q1}Interaction of quarters
+and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-46-1.pdf}
+\caption{\label{fig:unnamed-chunk-46}\label{fig:q2}Interaction of quarters
+and treatment. Control group is vessels from PNA.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-47-1.pdf}
+\caption{\label{fig:unnamed-chunk-47}\label{fig:q3}Interaction of quarters
+and treatment. Control group excludes Chinese vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-48-1.pdf}
+\caption{\label{fig:unnamed-chunk-48}\label{fig:q4}Interaction of quarters
+and treatment. Control group is japanese vessels.}
+\end{figure}
+
+\hypertarget{year-month-did-interactions}{%
+\subsubsection{Year-month DID
+interactions}\label{year-month-did-interactions}}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-49-1.pdf}
+\caption{\label{fig:unnamed-chunk-49}\label{fig:ym1}Interaction of
+year-month and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-50-1.pdf}
+\caption{\label{fig:unnamed-chunk-50}\label{fig:ym2}Interaction of
+year-month and treatment. Control group is vessels from PNA.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-51-1.pdf}
+\caption{\label{fig:unnamed-chunk-51}\label{fig:ym3}Interaction of
+year-month and treatment. Control group excludes Chinese vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-52-1.pdf}
+\caption{\label{fig:unnamed-chunk-52}\label{fig:ym4}Interaction of
+year-month and treatment. Control group is japanese vessels.}
+\end{figure}
 

### 2018-10-19 rmd/Manuscript.Rmd
updated mscrpt

@@
   bookdown::pdf_document2:
-    fig_height: 4
+    fig_height: 3.5
     fig_width: 6
@@
          gear == "purse_seines")
+
+effort_by_vessel_JPN <- readRDS(file = here::here("raw_data", "JPN_effort_by_vessel.rds"))
 ```
@@
 Vessels in the control group meet the following two conditions: i) vessels never fished within PIPA waters, and ii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure (n = 26).
-During our causal identification, we also use other two definitions of control groups, which further reduce our sample sizes: one with only vessels that belong to PNA countries (n = 7), and one that excludes Chinese vessels (n = 21).
+
+We include three additional definitions of control groups as a robustness check: one with only vessels that belong to PNA countries (n = 7), and one that excludes Chinese vessels (n = 21).
+Our third control is made up of Japanese purse seiners that fish in the Pacific but that never fished inside PIPA (n = 27)\footnote{Using Taiwanese vessels was the original idea, but there are only 4 vessels with pre-2015 data.
+I need to further identify propper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
 Our definition of treatment and control groups leaves us with 61 and 21 treated and control vessels, which have just over 22 million observations where about 22% are identified as fishing events.
-For each of the remainig vessels, we calculate their total daily fishing hours and obtain pannel data with 37,800 observations.
+
+For each vessel we calculate total daily fishing hours and obtain pannel data with 37,800 observations.
 Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
@@
 Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level fishing events that make up each group through time.
+We use this data to answer our key questions: How do the 61 purse seiners modify their behavior as compared to the different control groups, and where do they go after the spatial closure?
+The following section describes our empirical identification strategies.
 
@@
 The first analysis focuses on identifying the response of fishing vessels to PIPA closure.
-Our variables of interests are daily fishing hours, and daily distance traveled (Km).
+Our variables of interests are daily fishing hours, and daily distance traveled (km).
 We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation.
@@
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
 $$
@@
 $\alpha$ is the standard intercept, $\beta_1$ captures the temporal trend change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions, and $\theta_i$ are a set of dummies that account for the addition of more satellites\footnote{We test for other more complex specifications that interact a quarterly or year-month variable with the treatment group and find qualitativel the same results.}.
+Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
+
+```{r, model_fitting1}
+model_base <- effort_by_vessel %>% 
+  filter(baci_strict,
+         gear == "purse_seines") %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year * year,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter),
+         flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
+         flag_fe_oth = flag_fe & !flag == "OTH",
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3",
+                          T ~ "2"))
+
+# See file combine_vessel_info_and_effort to see how experiment columns are created ~line 70
+## Controls are PNA
+experiment1 <- model_base %>% 
+  filter(experiment1)
+
+## Controls are everything BUT Chinese
+experiment2 <- model_base %>% 
+  filter(experiment3)
+
+## Controls are Taiwanese
+experiment3 <- effort_by_vessel_JPN %>% 
+  select(-PNA) %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year * year,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter),
+         flag_fe = F,
+         flag_fe_oth = F,
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3",
+                          T ~ "2"),
+         baci_strict = T,
+         experiment1 = F,
+         experiment2 = F,
+         experiment3 = F,
+         flag = "JPN",
+         baci_relaxed = T) %>% 
+  rbind(filter(model_base, treated == 1))
+
+## Fit the models
+
+source(here::here("scripts", "did.R"))
+source(here::here("scripts", "did_quarter.R"))
+source(here::here("scripts", "did_yearmonth.R"))
+source(here::here("scripts", "termplot.R"))
+
+## Simple dids for each data
+models_exp0_did <- model_base %>% did()
+models_exp1_did <- experiment1 %>% did()
+models_exp2_did <- experiment2 %>% did()
+models_exp3_did <- experiment3 %>% did(flag_fe = F)
+
+# Quarterly did
+models_exp0_did_q <- model_base %>% did_quarter()
+models_exp1_did_q <- experiment1 %>% did_quarter()
+models_exp2_did_q <- experiment2 %>% did_quarter()
+models_exp3_did_q <- experiment3 %>% did_quarter()
+
+# Monthly did
+models_exp0_did_ym <- model_base %>% did_yearmonth()
+models_exp1_did_ym <- experiment1 %>% did_yearmonth()
+models_exp2_did_ym <- experiment2 %>% did_yearmonth()
+models_exp3_did_ym <- experiment3 %>% did_yearmonth()
+```
 
@@
 $$
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \theta_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
 $$
@@
 Our parameter of interest is $\beta_{1,i}$, which captures the country-level change in proportional fishing effort.
-$\theta_i$ accounts for the addition of satellites.
 
@@
 
-```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure.", fig.heihgt = 3.5}
+Our DiD analysis shows an overall increase in purse seine fishing hours, even after accounting for the introduction of new satellites (Table \ref{tab:did}).
+This coefficient estimate is consistent for different model specifications and across groups of treatment and controls.
+These effectively represent the patterns observed in Figure \ref{fig:all_vessels}.
+The $\beta_3$ coefficient indicating our treatment effect suggests that, relative to the control, treated vessels fish less, in the order of 0.5 hours per day.
+Another way to interpret this is that the increase in fishing effort by treated vessels has ocurred at a lower rate than control vessels.
+This result is robust and significant ($p < 0.05$) for all model specifications using our main control group, with the effect varying between $\beta_3 = -0.515$ and $\beta_3 = -0.934$.
+These values are equivalent to a 15 - 28 reduction in fishing hours per month.
 
+Regressions coefficients for our DiD analysis are shown in Table \ref{tab:did}.
+Columns 1 -3 use all data for controls.
+Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
+It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1,fig:q2,fig:q3,fig:q4,fig:ym1,fig:ym2,fig:ym3,fig:ym4}).
+
+```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Daily fishing hours for all vessels in our main treatment-control groups.
+Solid straight lines show a linear trend by period (pre-psot) and treatment.
+The other red and blue lines show monthly avarages.
+Vertical dashed line indicates PIPA closure."}
 effort_by_vessel %>% 
-  filter(baci_strict,
-         gear == "purse_seines") %>% 
-  arrange(!treated) %>% 
+  filter(baci_strict) %>% 
+  mutate(date = lubridate::date(paste(year, month, 15, sep = "/"))) %>%
   ggplot(aes(x = date, y = hours, color = treated)) +
-  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.1) +
-  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
+  geom_jitter(shape = ".", height = 0, alpha = 0.1) +
+  stat_summary(geom = "line", fun.y = mean, size = 1) +
+  geom_smooth(method = "lm", aes(group = paste(treated, post))) +
   ggtheme_plot() +
   scale_color_brewer(palette = "Set1") +
-  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
-```
-
-Our DiD analysis shows that treated purse seiners reduce their fishing effort after PIPA implementation in the order of 16 hours per month.
-This result is robust and significant (*p < 0.05*) for all model specifications, with the effect varying between $\beta_3 = -16.457$ and $\beta_3 = -18.709$.
-Model specifications that include the year polynomial show lower values for the $\beta_1$ coefficient associated to the $Post_t$ policy dummy, and show positive and negative values for $\mu_1$ and $\mu_2$, the linear and quadratic terms for $Y_t$, respectively.
-These effectively represent the patterns observed in Figure \ref{fig:all_vessels}.
-
-<!-- Longliners show a similar pattern of effort reduction.
-However, the magnitude of the $\beta_3$ coefficient is smaller (ranging from  $\beta_3 = -9.851$ to $\beta_3 = -14.850$) and not significant across all model specifications.
-This, along with higher standard error values suggest that longliners have a smaller and more variable response to the implementation of LSMPAs.
--->
-
-Regressions coefficients for each gear type are shown in Tables \ref{tab:purse} and \ref{tab:long}.
-Column (1) presents the DiD regression with no fixed effects, column (2) includes month fixed effects, column (3) includes month and the second degree polynomial for years, and column (4) includes all of the above and country-level fixed effects.
-
-```{r}
-model_base <- effort_by_vessel %>% 
-  filter(baci_strict,
-         gear == "purse_seines") %>% 
-  mutate(post = post * 1,
-         treated = treated * 1,
-         year2 = year * year,
-         year_month_c = as.character(year_month),
-         quarter_c = as.character(quarter),
-         flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
-         flag_fe_oth = flag_fe & !flag == "OTH",
-         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
-                          date > lubridate::date("2015/12/31") ~ "3",
-                          T ~ "2"))
-
-# See file combine_vessel_info_and_effort to see how experiment columns are created ~line 70
-## Controls are PNA
-experiment1 <- model_base %>% 
-  filter(experiment1)
-
-## Controls are Taiwanese
-experiment2 <- model_base %>% 
-  filter(experiment2)
-
-## Controls are everything BUT Chinese
-experiment3 <- model_base %>% 
-  filter(experiment3)
-
-## Fit the models
-
-source(here::here("scripts", "did.R"))
-source(here::here("scripts", "did_quarter.R"))
-source(here::here("scripts", "did_yearmonth.R"))
-source(here::here("scripts", "termplot.R"))
-
-## Simple dids for each data
-models_exp0_did <- model_base %>% did()
-models_exp1_did <- experiment1 %>% did()
-models_exp3_did <- experiment3 %>% did()
-
-# Quarterly did
-models_exp0_did_q <- model_base %>% did_quarter()
-models_exp1_did_q <- experiment1 %>% did_quarter()
-models_exp3_did_q <- experiment3 %>% did_quarter()
-
-# Monthly did
-models_exp0_did_ym <- model_base %>% did_yearmonth()
-models_exp1_did_ym <- experiment1 %>% did_yearmonth()
-models_exp3_did_ym <- experiment3 %>% did_yearmonth()
+  geom_vline(xintercept = lubridate::date(paste(2015, 01, 01, sep = "/")), linetype = "dashed")
 ```
@@
             models_exp1_did,
+            models_exp2_did,
             models_exp3_did)
@@
                      column.sep.width = "1pt",
-                     font.size = "small",
+                     font.size = "footnotesize",
                      type = "latex",
@@
                      add.lines = list(
-                       c("Control", rep("All", 3), rep("PNA", 3), rep("-CHN", 3)),
-                       c("Month FE", rep(c("No", "Yes", "Yes"), 3)),
-                       c("Flag FE", rep(c("No", "No", "Yes"), 3))),
+                       c("Control", rep("All", 3), rep("PNA", 3), rep("-CHN", 3), rep("JPN", 2)),
+                       c("Month FE", rep(c("No", "Yes", "Yes"), 4)),
+                       c("Flag FE", rep(c("No", "No", "Yes"), 4))),
                      omit.stat = c("adj.rsq", "f", "ser"),
@@
                      # float.env = "sidewaystable",
-                     title = "Difference-in-differences estimates for 3 different controls and 3 different specifications.
+                     title = "\\label{tab:did}Difference-in-differences estimates for 3 different controls and 3 different specifications.
 The first three columns use all data for controls.
-Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
-Numbers in parentheses are heteroskedastic-robust standard errors.")
+Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
+Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs.
+Numbers in parentheses are heteroskedastic-robust standard errors.",
+                     out = "DID.html")
 ```
@@
 Top pannel indicates variable, x-axis represents model specification, and y-axis coefficient estimate."}
-map_df(models, commarobust::commarobust_tidy, .id = "model") %>%
+map_df(models,
+       commarobust::commarobust_tidy, .id = "model") %>%
   filter(term %in% c("(Intercept)", "post", "treated", "post:treated")) %>%
-  mutate(control = case_when(model < 4 ~ "All",
-                             model > 6 ~ "-CHN",
-                             T ~ "TWN")) %>% 
+  mutate(model = as.numeric(model),
+         control = case_when(model < 4 ~ "All",
+                             model > 3 & model < 7 ~ "PNA",
+                             model > 6 & model < 10 ~ "-CHN",
+                             T ~ "JPN")) %>% 
   ggplot(aes(x = model, y = est)) +
@@
   ggtheme_plot() +
-  geom_hline(yintercept = 0, linetype = "dashed")
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  scale_color_brewer(palette = "Set1")
 ```
@@
   ggplot(aes(x = date, y = h_prop, group = post, color = post)) +
-  # geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
   geom_point() +
@@
 ```{r, results = "asis"}
-# Dont have this here. Just write the model specification
-
 disp_mod_ps_data <- displacement_data %>% 
@@
   knitr::kable(booktabs = T,
-               caption = "Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1), p < 0.001") %>% 
+               caption = "Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
+<div id = "refs"></div>
+
+\clearpage
+
 # Appendix
@@
 \beginsupplement
+
+## Stream of data by vessel, group, and period
 
@@
 
-## Other model specifications
+\clearpage
+
+## Longliners
+
+Longliners show a similar pattern of effort reduction.
+However, the magnitude of the $\beta_3$ coefficient is smaller (ranging from  $\beta_3 = -0.98$ to $\beta_3 = -1.125$) and not significant unless including month and flag FEs for the general treatment-control groups, or when excluding Chinese vessels.
+This, along with higher standard error values suggest that longliners have a smaller and more variable response to the implementation of LSMPAs.
+
+```{r, results = "asis"}
+model_base <- effort_by_vessel <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>% 
+  filter(year < 2018,
+         !gear == "purse_seines",
+         baci_strict) %>% 
+  mutate(post = post * 1,
+         treated = treated * 1,
+         year2 = year * year,
+         year_month_c = as.character(year_month),
+         quarter_c = as.character(quarter),
+         flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
+         flag_fe_oth = flag_fe & !flag == "OTH",
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3",
+                          T ~ "2"))
+
+# See file combine_vessel_info_and_effort to see how experiment columns are created ~line 70
+
+## Controls are everything BUT Chinese
+experiment2 <- model_base %>% 
+  filter(experiment3)
+
+## Simple dids for each data
+ll_models_exp0_did <- model_base %>% did()
+ll_models_exp2_did <- experiment2 %>% did()
+
+models <- c(ll_models_exp0_did,
+            ll_models_exp2_did)
+
+stargazer::stargazer(models,
+                     se = commarobust::makerobustseslist(models),
+                     t.auto = T,
+                     p.auto = T,
+                     intercept.bottom = F,
+                     column.sep.width = "1pt",
+                     font.size = "small",
+                     type = "latex",
+                     omit = c("flag", "month"),
+                     add.lines = list(
+                       c("Control", rep("All", 3), rep("-CHN", 3), rep("JPN", 2)),
+                       c("Month FE", rep(c("No", "Yes", "Yes"), 3)),
+                       c("Flag FE", rep(c("No", "No", "Yes"), 3))),
+                     omit.stat = c("adj.rsq", "f", "ser"),
+                     header = F,
+                     # float.env = "sidewaystable",
+                     title = "\\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications.
+The first three columns use all data for controls.
+Columns 4 - 6 exclude Chinese vessels.
+Numbers in parentheses are heteroskedastic-robust standard errors.",
+                     out = "DID_ll.html")
+```
+
+\clearpage
+
+## Other model specifications for purse seiners
+
+We include a second degree polinomial for years as:
+
+$$
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
+$$
 
@@
          baci_strict,
-         !gear == "purse_seines") %>% 
+         gear == "purse_seines") %>% 
   mutate(post = post * 1,
@@
                      header = F,
-                     title = "\\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).
+                     title = "\\label{tab:purse}Fishing hours from GFW for purse_seiners.
 Asterisks indicate significance levels.
-Numbers in parenthesis represent heteroskedastic-robuste standard errors.")
+Numbers in parentheses represent heteroskedastic-robust standard errors.")
 ```
 
-```{r, eval = F}
-models_q <- list(models_exp0_did_q,
-                 models_exp1_did_q,
-                 models_exp3_did_q)
+### Quarterly DID interactions
 
-stargazer::stargazer(models_q,
-                     se = commarobust::makerobustseslist(models_q[[1]]),
-                     t.auto = T,
-                     p.auto = T,
-                     intercept.bottom = F,
-                     type = "latex",
-                     omit = c("flag", "month"),
-                     add.lines = list(
-                       c("Control", rep("All", 2), rep("PNA", 2), rep("-CHN", 2)),
-                       c("Flag FE", rep(c("No", "Yes"), 3))),
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     title = "Difference-in-differences estimates for 3 different controls and 3 different specifications.
-The first three columns use all data for controls.
-Columns 4 - 6 use only Taiwanese vessels as controls, and columns 7 - 9 exclude Chinese vessels.
-Numbers in parentheses are heteroskedastic-robust standard errors.",
-                     out = "DID_q.html")
+```{r, fig.cap = "\\label{fig:q1}Interaction of quarters and treatment. Control group is all vessels."}
+# Quarterly did
+termplot(models_exp0_did_q, q = T)
 ```
 
-```{r}
-# Quarterly did
-models_exp0_did_q %>% termplot(q = T)
-models_exp1_did_q %>% termplot(q = T)
-models_exp3_did_q %>% termplot(q = T)
+```{r, fig.cap = "\\label{fig:q2}Interaction of quarters and treatment. Control group is vessels from PNA."}
+termplot(models_exp1_did_q, q = T)
 ```
 
-```{r}
+```{r, fig.cap = "\\label{fig:q3}Interaction of quarters and treatment. Control group excludes Chinese vessels."}
+termplot(models_exp2_did_q, q = T)
+```
+
+```{r, fig.cap = "\\label{fig:q4}Interaction of quarters and treatment. Control group is japanese vessels."}
+termplot(models_exp3_did_q, q = T)
+```
+
+### Year-month DID interactions
+
+```{r, fig.cap = "\\label{fig:ym1}Interaction of year-month and treatment. Control group is all vessels."}
 # Monthly did
-models_exp0_did_ym %>% termplot()
-models_exp1_did_ym %>% termplot()
-models_exp3_did_ym %>% termplot()
+termplot(models_exp0_did_ym)
+```
+
+```{r, fig.cap = "\\label{fig:ym2}Interaction of year-month and treatment. Control group is vessels from PNA."}
+termplot(models_exp1_did_ym)
+```
+
+```{r, fig.cap = "\\label{fig:ym3}Interaction of year-month and treatment. Control group excludes Chinese vessels."}
+termplot(models_exp2_did_ym)
+```
+
+```{r, fig.cap = "\\label{fig:ym4}Interaction of year-month and treatment. Control group is japanese vessels."}
+termplot(models_exp3_did_ym)
 ```

### 2018-10-19 scripts/JPN_tracks_download.R

@@ -1,0 +1,63 @@
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+BQc <- bigrquery::dbConnect(drv = bigrquery::bigquery(), 
+                            project = "ucsb-gfw", 
+                            dataset = "mpa_displacement", 
+                            allowLargeResults = TRUE)
+
+DBI::dbListTables(BQc)
+
+vessel_tracks <- dplyr::tbl(BQc, "JPN_tracks") %>% 
+  collect()
+
+vessel_tracks %<>% 
+  mutate(year = lubridate::year(timestamp),
+         month = lubridate::month(timestamp),
+         date = lubridate::date(timestamp),
+         post = year >= 2015,
+         fishing = nnet_score >= 0.5) %>% 
+  select(year,
+         month,
+         date,
+         timestamp,
+         mmsi,
+         gear,
+         lon,
+         lat,
+         hours,
+         fishing,
+         treated,
+         post,
+         nnet_score,
+         eez_iso3,
+         distance_from_port,
+         distance_from_shore)
+
+before <- vessel_tracks %>% 
+  filter(date < lubridate::date("2014/09/01")) %$%
+  unique(mmsi)
+
+after <- vessel_tracks %>% 
+  filter(post) %$%
+  mmsi %>%
+  unique()
+
+saveRDS(vessel_tracks, file = here::here("raw_data", "JPN_tracks.rds"))
+
+effort_by_vessel <- vessel_tracks %>% 
+  filter(fishing) %>% 
+  group_by(post, treated, year, month, date, gear, mmsi) %>% 
+  summarize(hours = sum(hours, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(month_c = as.character(month),
+         year_c = as.character(year),
+         year_month = lubridate::date(paste(year, month, 1, sep = "/")),
+         quarter = lubridate::quarter(date, with_year = T),
+         PNA = FALSE)
+
+saveRDS(effort_by_vessel, file = here::here("raw_data", "JPN_effort_by_vessel.rds"))
+

### 2018-10-19 scripts/did_yearmonth.R

@@ -9,8 +9,8 @@ did_yearmonth <- function(data, filter_oth = F){
   flag_data <- data %>% 
     filter(flag_fe)
   
-  m1 <- lm(hours ~ year_month_c*treated, data = data)
-  m2 <- lm(hours ~ year_month_c*treated + flag, data = flag_data)
+  m1 <- lm(hours ~ year_month_c*treated + sate, data = data)
+  m2 <- lm(hours ~ year_month_c*treated + sate + flag, data = flag_data)
   
   return(list(m1, m2))
 }

### 2018-10-19 docs/Manuscript.tex
Added more intuition to spatial redistribution

@@
 \citet{game_2009}. Today, a small number of LSMPAs make up at least 80\%
-of the managed areas in the ocean \citet{toonen_2013}.
+of the managed areas in the ocean \citet{toonen_2013}. LSMPAs may be
+instrumental in helping us achieve the 10\% target by 2020
+\citep{mccauley_2016}.
 
@@
 rarely incorporate spatially explicit data. Despite these efforts,
-marine conservation is yet to identify the implications of these
-management interventions.
-
-Here, we ask, how do fishers respond to the implementation of LSMPA?
-After a closure, and if they continue to fish, where do they reallocate
-fishing effort? We use novel satellite technologies and causal inference
-techniques to identify the behavioral changes and spatial redistribution
-of the industrial tuna purse seine fleet due to the implementation of a
-Large Scale Marine Protected Areas in the Western and Central Pacific
-Ocean (WCPO).
+marine conservation is yet to identify the response in fishing effort
+and its management implications.
+
+Recent advances in satellite tracking technologies and near real-time
+identification of fishing activity provide us with an opportunity to
+tackle increase governance and answer long-lasting questions. Here, we
+ask, how do fishers respond to the implementation of LSMPA? After a
+closure, and if they continue to fish, where do they reallocate fishing
+effort? We use identification of fishing activity via Automatic
+Identification Systems (AIS) and causal inference techniques to describe
+the behavioral changes and spatial redistribution of the industrial tuna
+purse seine fleet due to the implementation of a Large Scale Marine
+Protected Areas in the Pacific Ocean.
+
+Our work is novel in the sense that it provides empirical evidence of
+the effect of Large Scale Marine Protected Areas in fishing behavior and
+distribution and can help guide future interventions as countries march
+towards meeting the targeted 10\% of ocean protection. Understanding how
+effort is displaced from LSMPAs might provide insights into how the
+industrial fleet would react to a high seas closure.
+
+The paper is outlined as follows: Section \ref{background} provides more
+information on Large Scale Marine Protected Areas and background on
+empirical studies of effort redistribution. An overview of the Nauru
+Agreement and associated countries, a description of the fleet that
+operates in the region, and a brief history of PIPA is also included.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion}
+provides an extension of our results to other
+LSMPAs\footnote{Not yet. but I think this would be interesting} and
+discusses our
+results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+\hypertarget{large-scale-marine-protected-areas}{%
+\subsection{Large Scale Marine Protected
+Areas}\label{large-scale-marine-protected-areas}}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-\caption{\label{fig:unnamed-chunk-27}\label{fig:LSMPAs_map}Large Scale
-Marine Protected Areas. The map shows all areas larger than 250,000
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:LSMPAs_map}Large Scale Marine
+Protected Areas. The map shows all areas larger than 250,000
 Km\textsuperscript{2}. Areas in dark blue meet at least one of these
@@
 effort. More recently, \citep{bradley_2018} use similar data to
-highlight cases of illegal shark fishing \emph{inside} a 2 million
-km\textsuperscript{2} shark sanctuary. To date, no studies have
+highlight cases of potential illegal shark fishing \emph{inside} a 2
+million km\textsuperscript{2} shark sanctuary. To date, no studies have
 evaluated the displacement of fishing effort due to LSMPA
@@
 
-The exclusion of these LSMPAs is likely to change fisher's behavior.
-Theoretical models of fishing effort redistribution range from the
-simplistic assumption that effort inside the bounded region disappears,
-to spatially explicit models that reallocate fishing effort based on
-habitat characteristics, presence of other vessels, and expected returns
-\citep{smith_2003,hilborn_2006}. However, these focus on the long term
-optimal equilibrium and redistribution of fishing effort may not be
-optimal, especially over the first years \citep{stevenson_2013}. The
-empirical research that has been done in custumary sized MPAs suggest
-that resource users may show idiosyncratic responses. For example,
-\citet{stevenson_2013} show that a network of MPAs displaced fishing
-effort farther away from ports, resulting in higher \emph{perceived}
-costs, and increases in catch per unit effort. \citet{cabral_2017}
-analyse the redistribution of fishing and non-fishing vessels following
-the implementation of a network of MPAs in California, and find that
-commercial dive boats follow a fishing-the-line pattern, while some
-fishing boats follow an ideal free distribution. The way in which
-fishers react to a spatial closure can have major implications in its
-outcome \citep{smith_2003,hilborn_2006} highlighting the need to
-understand how fishers react to the implementation of LSMPAs, and
-fishing effort changes and is spatially redistributed.
-
-Our work is novel in the sense that it provides empirical evidence of
-the effect of large-acale Marine Protected Areas in fishing behavior and
-distribution and can help guide future interventions as countries march
-towards meetings the targeted 10\% of protection. Furthermore, a growing
-body of literature suggests that closing the high seas to all fishing
-could increase fishery yields and profitability of fisheries, with
-negligible costs to food security
-\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Understanding
-how effort is displaced from LSMPAs might provide insights into how the
-industrial fleet would react to a high seas closure.
-
-The paper is outlined as follows: Section \ref{background} provides an
-overview of the Nauru Agreement and associated countries, a description
-of the fleet that operates in the region, and a brief history of PIPA.
-Section \ref{methods} describes our data and identification strategy.
-Section \ref{results} presents our results, section \ref{discussion}
-provides an extension of our results to other
-LSMPAs\footnote{Not yet. but I think this would be interesting} and
-discusses our
-results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
+Spatial closures of this magnitude are likely to induce changes in
+fishers' behavior. Theoretical models of fishing effort redistribution
+range from the simplistic assumption that effort inside the bounded
+region disappears, to spatially explicit models that reallocate fishing
+effort based on habitat characteristics, presence of other vessels, and
+expected returns \citep{smith_2003,hilborn_2006}. However, these focus
+on the long term optimal equilibrium, and redistribution of fishing
+effort may not always be optimal, especially over the first years
+\citep{stevenson_2013}.
+
+The empirical research that has been done in custumary sized MPAs
+suggest that resource users may show idiosyncratic responses. For
+example, \citet{stevenson_2013} show that a network of MPAs displaced
+fishing effort farther away from ports, resulting in higher
+\emph{perceived} costs, and increases in catch per unit effort.
+\citet{cabral_2017} analyse the redistribution of fishing and
+non-fishing vessels following the implementation of a network of MPAs in
+California, and find that commercial dive boats follow a
+fishing-the-line pattern, while some fishing boats follow an ideal free
+distribution. More recently \citet{elahi_2018} used satellite tracking
+data to show that a temporal spatial closure caused trawlers to maintain
+effort but apply it more intensively elsewhere, particularly along the
+borders and closer to shore. The way in which fishers react to a spatial
+closure can have major implications in its outcome
+\citep{smith_2003,hilborn_2006} highlighting the need to understand how
+fishers react to the implementation of LSMPAs, and fishing effort
+changes and is spatially redistributed. However, all these closures took
+place within Exlcusive Economic Zones, where other regulations exist.
+This may not always be the case for LSMPAs, where often the entire EEZ
+is converted into a LSMPA, leaving fishers with the options of moving to
+the high seas or other countries' EEZs.
+
+\hypertarget{nauru-agreement-and-the-phoenix-island-protected-area}{%
+\subsection{Nauru agreement and the Phoenix Island Protected
+Area}\label{nauru-agreement-and-the-phoenix-island-protected-area}}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
-\caption{\label{fig:unnamed-chunk-28}\label{fig:PNA_map}Map of the Exclusive
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}\label{fig:PNA_map}Map of the Exclusive
 Economic Zones (EEZs) of the region of interest. A solid line indicates
@@
 behavioral responses and redistribution of fishing effort by vessels
-that used to fish there. \citet{mcdermott_2018} showed that fishing
-effort within the Phoenix Islands Marine Protected Area (PIPA) increased
-between the anouncement (September 1\textsuperscript{st}, 2014) and its
-implementation in Janyary 1\textsuperscript{st}, 2015. Likewise, they
-demonstrate that fishing effort is effectively reduced after
-implementation. To this, we pose two questions: How do individual
-vessels respond to the sudden exclusion of such a big area? And where
-did all the vessels go? In the next sections we describe the data and
-methods used to answer this questions.
+that used to fish there. PIPA has been the focus of previous research,
+showing that fishing effort is effectively reduced after implementation
+\citep{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
+How do individual vessels respond to the sudden exclusion of such a big
+area? And where did all the vessels go? In the next sections we describe
+the data and methods used to answer this questions.
 
@@
 
-Our analysis focuses on purse seiner vessels, the most important fishery
+Our analysis focuses on purse seine vessels, the most important fishery
 for PNA
@@
 
-\caption{\label{tab:unnamed-chunk-31}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-7}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
-\caption{\label{fig:unnamed-chunk-32}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels. Vertical dashed lines
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
+number of vessels by month for all vessels. Vertical dashed lines
 indicates dates when satellites were added, solid line indicates PIPA
@@
 The first analysis focuses on identifying the response of fishing
-vessels to PIPA closure. Our variables of interests are daily fishing
+vessels to PIPA closure. A spatial closure might cause fishers to modify
+their behavior as they adapt to a new state of the world. Some may have
+to travel further distances to find new fishing grounds, which would
+lead them to fish harder to compensate for the associated extra fuel
+costs. If fishers had developed experience for fishing in particular
+sites, being excluded might impose a learning cost on them, as they
+identify new fishing grounds. This would result in increased search
+times. However, if the area of influence of a vessel is significantly
+larger than that of the spatial closure, they might already know other
+places and times where to fish. Our variables of interests intend to
+caputre these possible reactions.
+
+We use daily fishing hours, daily proportion of fishing vs.~non-fishing
 hours, and daily distance traveled (km). We compare our variable of
@@
 Difference-in-Differences approach, where we track the variable of
-interest for vessels that used to fish inside PIPA and vessels that
-never fished inside PIPA, before and after PIPA implementation. Our
+interest for vessels described in the previous section. Our
 specification is the following:
@@
 effort. In other words, identifying where do vessels that used to fish
-inside PIPA go after its establishment. We discretize spatial units by
-using a polygon for PIPA
+inside PIPA go after its establishment.
+
+Furthermore, the presence and reaction of other vessels may in turn
+affect a fishers decission making process, seeking to avoid crowded
+areas. Additionally, if fishers show high site fidelity or their ability
+to fish is highly linkted to a few spatial portions, there might be an
+associated cost of learning to identify new suitable fishing grounds.
+For example, \citet{elahi_2018} showed that redistributed effort was
+higher along the borders of the closure, indicative of a possible
+habitat-dependency.
+
+However, the role of institutions must also be considered. The spatial
+closure described by \citet{elahi_2018} occured within an EEZ. As stated
+before LSMPAs, often span the entirety of an EEZ. In the case of purse
+seining in the PNA, vessels purchase access to the fishery at the
+beginning of the season. If a vessel decides to fish within the PNA,
+they've already made the decission to pay for access, expecting higher
+returns from fishing there than in the High Seas. In the particular case
+of PIPA, one would expect that a vessel holding a permit to fish in
+I-Kiribati waters would then move to other fishing grounds within
+Kiribati after the closure. Alternatively, if a vessel fishes illegaly
+in I-Kiribati waters before the implementation, one would expect them to
+reallocate to other where probability of being caught is equal or lower.
+In this case, they might then choose to move to other I-Kiribati waters,
+waters of countries that have similar enforcement levels, or the High
+Seas.
+
+We discretize spatial units by using a polygon for PIPA
 \footnote{we would expect to see a decrease here} and distinct spatial
@@
 
-\caption{\label{tab:unnamed-chunk-35}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
+\caption{\label{tab:unnamed-chunk-10}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
-\caption{\label{fig:unnamed-chunk-36}\label{fig:all_vessels}Daily fishing
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Daily fishing
 hours for all vessels in our main treatment-control groups. Solid
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
-\caption{\label{fig:unnamed-chunk-38}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-39-1.pdf}
-\caption{\label{fig:unnamed-chunk-39}\label{fig:redist_trend_ps}Monthly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-40-1.pdf}
-\caption{\label{fig:unnamed-chunk-40}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\label{fig:unnamed-chunk-16}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
@@
 
-\caption{\label{tab:unnamed-chunk-41}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
+\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
 \centering
@@
 
+Furthermore, a growing body of literature suggests that closing the high
+seas to all fishing could increase fishery yields and profitability of
+fisheries, with negligible costs to food security
+\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+
 \clearpage
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
-\caption{\label{fig:unnamed-chunk-42}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-45-1.pdf}
-\caption{\label{fig:unnamed-chunk-45}\label{fig:q1}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+\caption{\label{fig:unnamed-chunk-21}\label{fig:q1}Interaction of quarters
 and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-46-1.pdf}
-\caption{\label{fig:unnamed-chunk-46}\label{fig:q2}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
+\caption{\label{fig:unnamed-chunk-22}\label{fig:q2}Interaction of quarters
 and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-47-1.pdf}
-\caption{\label{fig:unnamed-chunk-47}\label{fig:q3}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\caption{\label{fig:unnamed-chunk-23}\label{fig:q3}Interaction of quarters
 and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-48-1.pdf}
-\caption{\label{fig:unnamed-chunk-48}\label{fig:q4}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\caption{\label{fig:unnamed-chunk-24}\label{fig:q4}Interaction of quarters
 and treatment. Control group is japanese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-49-1.pdf}
-\caption{\label{fig:unnamed-chunk-49}\label{fig:ym1}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:ym1}Interaction of
 year-month and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-50-1.pdf}
-\caption{\label{fig:unnamed-chunk-50}\label{fig:ym2}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
+\caption{\label{fig:unnamed-chunk-26}\label{fig:ym2}Interaction of
 year-month and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-51-1.pdf}
-\caption{\label{fig:unnamed-chunk-51}\label{fig:ym3}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+\caption{\label{fig:unnamed-chunk-27}\label{fig:ym3}Interaction of
 year-month and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-52-1.pdf}
-\caption{\label{fig:unnamed-chunk-52}\label{fig:ym4}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
+\caption{\label{fig:unnamed-chunk-28}\label{fig:ym4}Interaction of
 year-month and treatment. Control group is japanese vessels.}

### 2018-10-19 rmd/Manuscript.Rmd
Added more intuition to spatial redistribution

@@
 Today, a small number of LSMPAs make up at least 80% of the managed areas in the ocean \citet{toonen_2013}.
+LSMPAs may be instrumental in helping us achieve the 10\% target by 2020 \citep{mccauley_2016}.
 
@@
 The few empirical works focus on small-scale fisheries and rarely incorporate spatially explicit data.
-Despite these efforts, marine conservation is yet to identify the implications of these management interventions.
+Despite these efforts, marine conservation is yet to identify the response in fishing effort and its management implications.
 
+Recent advances in satellite tracking technologies and near real-time identification of fishing activity provide us with an opportunity to tackle increase governance and answer long-lasting questions.
 Here, we ask, how do fishers respond to the implementation of LSMPA?
 After a closure, and if they continue to fish, where do they reallocate fishing effort?
-We use novel satellite technologies and causal inference techniques to identify the behavioral changes and spatial redistribution of the industrial tuna purse seine fleet due to the implementation of a Large Scale Marine Protected Areas in the Western and Central Pacific Ocean (WCPO).
+We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to describe the behavioral changes and spatial redistribution of the industrial tuna purse seine fleet due to the implementation of a Large Scale Marine Protected Areas in the Pacific Ocean.
+
+Our work is novel in the sense that it provides empirical evidence of the effect of Large Scale Marine Protected Areas in fishing behavior and distribution and can help guide future interventions as countries march towards meeting the targeted 10\% of ocean protection.
+Understanding how effort is displaced from LSMPAs might provide insights into how the industrial fleet would react to a high seas closure.
+
+The paper is outlined as follows: Section \ref{background} provides more information on Large Scale Marine Protected Areas and background on empirical studies of effort redistribution.
+An overview of the Nauru Agreement and associated countries, a description of the fleet that operates in the region, and a brief history of PIPA is also included.
+Section \ref{methods} describes our data and identification strategy.
+Section \ref{results} presents our results, section \ref{discussion} provides an extension of our results to other LSMPAs\footnote{Not yet.
+but I think this would be interesting} and discusses our results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
+
+# Background
+
+## Large Scale Marine Protected Areas
 
@@
 \citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protectes two thrids of the tagged grey reef sharks by effectively excluding fishing effort.
-More recently, \citep{bradley_2018} use similar data to highlight cases of illegal shark fishing *inside* a 2 million km^2^ shark sanctuary.
+More recently, \citep{bradley_2018} use similar data to highlight cases of potential illegal shark fishing *inside* a 2 million km^2^ shark sanctuary.
 To date, no studies have evaluated the displacement of fishing effort due to LSMPA implementation.
 
-The exclusion of these LSMPAs is likely to change fisher's behavior.
+Spatial closures of this magnitude are likely to induce changes in fishers' behavior.
 Theoretical models of fishing effort redistribution range from the simplistic assumption that effort inside the bounded region disappears, to spatially explicit models that reallocate fishing effort based on habitat characteristics, presence of other vessels, and expected returns \citep{smith_2003,hilborn_2006}.
-However, these focus on the long term optimal equilibrium and redistribution of fishing effort may not be optimal, especially over the first years \citep{stevenson_2013}.
+However, these focus on the long term optimal equilibrium, and redistribution of fishing effort may not always be optimal, especially over the first years \citep{stevenson_2013}.
+
 The empirical research that has been done in custumary sized MPAs suggest that resource users may show idiosyncratic responses.
@@
 \citet{cabral_2017} analyse the redistribution of fishing and non-fishing vessels following the implementation of a network of MPAs in California, and find that commercial dive boats follow a fishing-the-line pattern, while some fishing boats follow an ideal free distribution.
+More recently \citet{elahi_2018} used satellite tracking data to show that a temporal spatial closure caused trawlers to maintain effort but apply it more intensively elsewhere, particularly along the borders and closer to shore.
 The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006} highlighting the need to understand how fishers react to the implementation of LSMPAs, and fishing effort changes and is spatially redistributed.
+However, all these closures took place within Exlcusive Economic Zones, where other regulations exist.
+This may not always be the case for LSMPAs, where often the entire EEZ is converted into a LSMPA, leaving fishers with the options of moving to the high seas or other countries' EEZs.
 
-Our work is novel in the sense that it provides empirical evidence of the effect of large-acale Marine Protected Areas in fishing behavior and distribution and can help guide future interventions as countries march towards meetings the targeted 10\% of protection.
-Furthermore, a growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-Understanding how effort is displaced from LSMPAs might provide insights into how the industrial fleet would react to a high seas closure.
-
-The paper is outlined as follows: Section \ref{background} provides an overview of the Nauru Agreement and associated countries, a description of the fleet that operates in the region, and a brief history of PIPA.
-Section \ref{methods} describes our data and identification strategy.
-Section \ref{results} presents our results, section \ref{discussion} provides an extension of our results to other LSMPAs\footnote{Not yet.
-but I think this would be interesting} and discusses our results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
-
-# Background
+## Nauru agreement and the Phoenix Island Protected Area
 
@@
 The closure of such a large area in one of the most important fishing regions in the world provides a great opportunity to evaluate the behavioral responses and redistribution of fishing effort by vessels that used to fish there.
-\citet{mcdermott_2018} showed that fishing effort within the Phoenix Islands Marine Protected Area (PIPA) increased between the anouncement (September 1^st^, 2014) and its implementation in Janyary 1^st^, 2015.
-Likewise, they demonstrate that fishing effort is effectively reduced after implementation.
+PIPA has been the focus of previous research, showing that fishing effort is effectively reduced after implementation \citep{mccauley_2016,mcdermott_2018}.
 To this, we pose two questions: How do individual vessels respond to the sudden exclusion of such a big area?
@@
 
-Our analysis focuses on purse seiner vessels, the most important fishery for PNA countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
+Our analysis focuses on purse seine vessels, the most important fishery for PNA countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
 We identify a total of 103 purse seiners that fished in PNA waters at least once before 2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore exlcuded from our analyses.}.
@@
 The first analysis focuses on identifying the response of fishing vessels to PIPA closure.
-Our variables of interests are daily fishing hours, and daily distance traveled (km).
-We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation.
+A spatial closure might cause fishers to modify their behavior as they adapt to a new state of the world.
+Some may have to travel further distances to find new fishing grounds, which would lead them to fish harder to compensate for the associated extra fuel costs.
+If fishers had developed experience for fishing in particular sites, being excluded might impose a learning cost on them, as they identify new fishing grounds.
+This would result in increased search times.
+However, if the area of influence of a vessel is significantly larger than that of the spatial closure, they might already know other places and times where to fish.
+Our variables of interests intend to caputre these possible reactions.
+
+We use daily fishing hours, daily proportion of fishing vs.
+non-fishing hours, and daily distance traveled (km).
+We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels described in the previous section.
 Our specification is the following:
@@
 Our second part of the analyses focuses on the redistribution of fishing effort.
-In other words, identifying where do vessels that used to fish inside PIPA go after its establishment.
+The role of institutions may play an important role.
+As stated before, LSMPAs often span the entirety of an EEZ.
+In the case of purse seining in the PNA, vessels purchase access to the fishery at the beginning of the season.
+If a vessel decides to fish within the PNA, they've already made the decission to pay for access, expecting higher returns from fishing there than in the High Seas.
+In the particular case of PIPA, one would expect that a vessel holding a permit to fish in I-Kiribati waters would then move to other fishing grounds within Kiribati after the closure.
+Alternatively, if a vessel fishes illegaly in I-Kiribati waters before the implementation, one would expect them to reallocate to other regions with equal or less enforcement.
+In this case, they might then choose to move to other I-Kiribati waters, waters of countries that have similar enforcement levels, or the High Seas.
+
 We discretize spatial units by using a polygon for PIPA \footnote{we would expect to see a decrease here} and distinct spatial units for each EEZ of each country.
@@
 <!-- Explicar cuales EEZs habia en total y cuales quedaron en un pie de nota o algo asi -->
-
-```{r}
-# country_groups <- c("COK", "FSM", "KIR", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV")
-
-eez <- read_sf(dsn = here::here("data", "spatial", "regions"),
-               layer = "regions")
-```
 
@@
 
+```{r, fig.width = 6, fig.height = 9}
+mpas_WCPO <- mpas %>% 
+  filter(wdpaid %in% c(309888, 400011))
+
+fishing_raster <- readRDS(here::here("data", "fishing_raster_BACI.rds"))
+
+ggplot() +
+  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
+  geom_sf(data = eez, fill = "transparent", color = "black") +
+  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
+  # geom_sf(data = small_coast, color = "black") +
+  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
+  scale_fill_viridis_c(trans = "log10") +
+  facet_grid(year~treated, switch = "y") +
+  # coord_equal() +
+  ggtheme_map() +
+  theme(legend.position = "bottom")
+```
+
 ```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'.", eval = T}
@@
 
+regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
+               layer = "regions")
+
 # I AM EXCLUDING MUS WHICH SHOULD BE PUT INTO EEZ
-eez %>% 
+regions %>% 
   rbind(HS_disp) %>% 
@@
 Future management interventions that aim to close large portion of the oceans should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
+
+Furthermore, a growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
 

### 2018-10-20 docs/Manuscript.tex
Slight changes to manuscript, major results coming

@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\label{fig:LSMPAs_map}Large Scale Marine
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
 Protected Areas. The map shows all areas larger than 250,000
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\label{fig:PNA_map}Map of the Exclusive
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
 Economic Zones (EEZs) of the region of interest. A solid line indicates
@@
 
-\caption{\label{tab:unnamed-chunk-7}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
 number of vessels by month for all vessels. Vertical dashed lines
@@
 Our second part of the analyses focuses on the redistribution of fishing
-effort. In other words, identifying where do vessels that used to fish
-inside PIPA go after its establishment.
-
-Furthermore, the presence and reaction of other vessels may in turn
-affect a fishers decission making process, seeking to avoid crowded
-areas. Additionally, if fishers show high site fidelity or their ability
-to fish is highly linkted to a few spatial portions, there might be an
-associated cost of learning to identify new suitable fishing grounds.
-For example, \citet{elahi_2018} showed that redistributed effort was
-higher along the borders of the closure, indicative of a possible
-habitat-dependency.
-
-However, the role of institutions must also be considered. The spatial
-closure described by \citet{elahi_2018} occured within an EEZ. As stated
-before LSMPAs, often span the entirety of an EEZ. In the case of purse
+effort. The role of institutions may play an important role. As stated
+before, LSMPAs often span the entirety of an EEZ. In the case of purse
 seining in the PNA, vessels purchase access to the fishery at the
@@
 in I-Kiribati waters before the implementation, one would expect them to
-reallocate to other where probability of being caught is equal or lower.
-In this case, they might then choose to move to other I-Kiribati waters,
-waters of countries that have similar enforcement levels, or the High
-Seas.
+reallocate to other regions with equal or less enforcement. In this
+case, they might then choose to move to other I-Kiribati waters, waters
+of countries that have similar enforcement levels, or the High Seas.
 
@@
 
-\caption{\label{tab:unnamed-chunk-10}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
+\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Daily fishing
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
 hours for all vessels in our main treatment-control groups. Solid
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 Recall that to evaluate the redistribution of fishing effort we only
-track fishing vessels that belong to the treated group. In this case, we
-calculate the proportion of fishing effort allocated every month to each
-spatially explicit region outlined by EEZs and the high seas. For purse
-seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
-of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
-relative fishing hours that each region received by all 61 treated
-vessels. The top-left panel shows the change in fishing effort inside
-PIPA, including the preemptive fishing and immediate reduction
-previously reported \citep{mcdermott_2018}.
-
-The change in the relative allocation of fishing effort by purse seiners
-increases in eight of the 12 regions after PIPA implementation (Table
-\ref{tab:disp_mod}). The largest increase is observed for the I-Kiribati
-EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
-other words, the redistribution of treated vessels caused a 10\%
-increase in the \emph{relative} allocation of fishing effort within
-I-Kiribati waters. The only decrease is observed for Papua New Guinea,
-but the coefficient is not significant. Figure \ref{fig:map_change_ps}
-provides a spatial representation of these changes. It is evident that
-the increase in relative fishing effort is greater for for regions
-closer to PIPA.
-
+track fishing vessels that belong to the treated group. Figure
+\ref{fig:fishing_raster} provides a spatial representation of these
+changes. Note that 2013 effort distribution is roughly similar across
+vessels. Then in 2014 there is a sharp increase in fishing hours by
+treated vessels inside PIPA (blue paradox). In 2015 treated vessels then
+allocate more effort to the easternmost Kiribati EEZ (see Figure
+\label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of
+fishing effort is again similar across groups. It is evident that the
+increase in relative fishing effort is greater for for regions closer to
+PIPA, and.
+
+Four our empirical identification we calculated the proportion of
+fishing effort allocated every month to each spatially explicit regions
+defined in section \ref{methods}. For purse seiners, these represent 9
+main EEZs, PIPA, the high seas, and a group of other EEZs. Figure
+\ref{fig:redist_trend_ps} shows the monthly relative fishing hours that
+each region received by all 61 treated vessels. The top-left panel shows
+the change in fishing effort inside PIPA, including the preemptive
+fishing and immediate reduction previously reported
+\citep{mcdermott_2018}. The change in the relative allocation of fishing
+effort by purse seiners increases in eight of the 12 regions after PIPA
+implementation (Table \ref{tab:disp_mod}, fig:map\_change\_ps). The
+largest increase is observed for the I-Kiribati EEZ, with an average
+increase of 0.11 (\emph{p \textless{} 0.001}). In other words, the
+redistribution of treated vessels caused a 10\% increase in the
+\emph{relative} allocation of fishing effort within I-Kiribati waters.
+The only decrease is observed for Papua New Guinea, but the coefficient
+is not significant.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
+spatial distribution of fishing effort by treated and control vessels.
+Colors have been adjusted relative to the maximum observed by group and
+year.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
+\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
-\caption{\label{fig:unnamed-chunk-16}\label{fig:map_change_ps}Spatial
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:map_change_ps}Spatial
 representation of the mean change in the monthly allocation of fishing
@@
 
-\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
+\caption{\label{tab:unnamed-chunk-16}\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\label{fig:unnamed-chunk-17}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 \centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
+\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
+and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\caption{\label{fig:unnamed-chunk-21}\label{fig:q1}Interaction of quarters
-and treatment. Control group is all vessels.}
+\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
+and treatment. Control group is vessels from PNA.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-\caption{\label{fig:unnamed-chunk-22}\label{fig:q2}Interaction of quarters
-and treatment. Control group is vessels from PNA.}
+\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
+and treatment. Control group excludes Chinese vessels.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\caption{\label{fig:unnamed-chunk-23}\label{fig:q3}Interaction of quarters
-and treatment. Control group excludes Chinese vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-\caption{\label{fig:unnamed-chunk-24}\label{fig:q4}Interaction of quarters
+\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
 and treatment. Control group is japanese vessels.}
@@
 \centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
+year-month and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:ym1}Interaction of
-year-month and treatment. Control group is all vessels.}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
+year-month and treatment. Control group is vessels from PNA.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-\caption{\label{fig:unnamed-chunk-26}\label{fig:ym2}Interaction of
-year-month and treatment. Control group is vessels from PNA.}
+\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
+year-month and treatment. Control group excludes Chinese vessels.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-\caption{\label{fig:unnamed-chunk-27}\label{fig:ym3}Interaction of
-year-month and treatment. Control group excludes Chinese vessels.}
-\end{figure}
+\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
+year-month and treatment. Control group is japanese vessels.}
+\end{figure}
+
+\hypertarget{fishing-raster}{%
+\subsubsection{Fishing raster}\label{fishing-raster}}
 
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
-\caption{\label{fig:unnamed-chunk-28}\label{fig:ym4}Interaction of
-year-month and treatment. Control group is japanese vessels.}
+\caption{\label{fig:unnamed-chunk-28}\label{fig:fishing_raster_full}}
 \end{figure}

### 2018-10-20 rmd/Manuscript.Rmd
Slight changes to manuscript, major results coming

@@
 Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.
-In this case, we calculate the proportion of fishing effort allocated every month to each spatially explicit region outlined by EEZs and the high seas.
+Figure \ref{fig:fishing_raster} provides a spatial representation of these changes.
+Note that 2013 effort distribution is roughly similar across vessels.
+Then in 2014 there is a sharp increase in fishing hours by treated vessels inside PIPA (blue paradox).
+In 2015 treated vessels then allocate more effort to the easternmost Kiribati EEZ (see Figure \label{fig:PNA_map}) and the high seas.
+In 2016 spatial distribution of fishing effort is again similar across groups.
+It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA, and.
+
+Four our empirical identification we calculated the proportion of fishing effort allocated every month to each spatially explicit regions defined in section \ref{methods}.
 For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs.
@@
 The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
-
-The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}).
+The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}, fig:map_change_ps).
 The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*).
@@
 The only decrease is observed for Papua New Guinea, but the coefficient is not significant.
-Figure \ref{fig:map_change_ps} provides a spatial representation of these changes.
-It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA.
 
-```{r, fig.width = 6, fig.height = 9}
+```{r, fig.width = 7.5, fig.height = 9, fig.cap = "\\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels.
+Colors have been adjusted relative to the maximum observed by group and year.
+"}
 mpas_WCPO <- mpas %>% 
@@
 
+fishing_raster %>% 
+  filter(between(year, 2013, 2016)) %>% 
   ggplot() +
-  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
+  geom_raster(mapping = aes(x = lon, y = lat, fill = hours_norm)) +
   geom_sf(data = eez, fill = "transparent", color = "black") +
@@
 ```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
-
 HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
@@
   knitr::kable(booktabs = T,
-               caption = "Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
+               caption = "\\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 
+### Fishing raster
+
+```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}"}
+ggplot() +
+  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
+  geom_sf(data = eez, fill = "transparent", color = "black") +
+  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
+  geom_sf(data = small_coast, color = "black") +
+  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
+  scale_fill_viridis_c(trans = "log10") +
+  facet_grid(year~treated, switch = "y") +
+  # coord_equal() +
+  ggtheme_map() +
+  theme(legend.position = "bottom")
+```
+
 \clearpage

### 2018-10-20 docs/Manuscript.tex
Obtained monthly treatment level rasters and updated ms

@@
 
-Four our empirical identification we calculated the proportion of
-fishing effort allocated every month to each spatially explicit regions
-defined in section \ref{methods}. For purse seiners, these represent 9
-main EEZs, PIPA, the high seas, and a group of other EEZs. Figure
-\ref{fig:redist_trend_ps} shows the monthly relative fishing hours that
-each region received by all 61 treated vessels. The top-left panel shows
-the change in fishing effort inside PIPA, including the preemptive
-fishing and immediate reduction previously reported
-\citep{mcdermott_2018}. The change in the relative allocation of fishing
-effort by purse seiners increases in eight of the 12 regions after PIPA
-implementation (Table \ref{tab:disp_mod}, fig:map\_change\_ps). The
-largest increase is observed for the I-Kiribati EEZ, with an average
-increase of 0.11 (\emph{p \textless{} 0.001}). In other words, the
-redistribution of treated vessels caused a 10\% increase in the
-\emph{relative} allocation of fishing effort within I-Kiribati waters.
-The only decrease is observed for Papua New Guinea, but the coefficient
-is not significant.
+For our empirical identification we \ldots{} The XXX shows the change in
+fishing effort inside PIPA, including the preemptive fishing and
+immediate reduction previously reported \citep{mcdermott_2018}. The
+change in the relative allocation of fishing effort by purse seiners
+increases for most regions after PIPA implementation (Table
+\ref{tab:disp_mod}, \ref{fig:mean_change}). The largest increase is
+observed for the I-Kiribati EEZ, with an average increase of 0.11
+(\emph{p \textless{} 0.001}). In other words, the redistribution of
+treated vessels caused a 10\% increase in the \emph{relative} allocation
+of fishing effort within I-Kiribati waters. The only decrease is
+observed for Papua New Guinea, but the coefficient is not significant.
 
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:map_change_ps}Spatial
-representation of the mean change in the monthly allocation of fishing
-effort for purse seiners.}
-\end{figure}
-
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-16}\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
-\centering
-\begin{tabular}[t]{ll}
-\toprule
-term & h\_prop\\
-\midrule
-(Intercept) & 0.087 (0.002)***\\
-post & -0.081 (0.003)***\\
-sate2 & -0.003 (0.001)***\\
-sate3 & -0.002 (0.001)\\
-post:countryEEZ COK 1 & 0.088 (0.002)***\\
-\addlinespace
-post:countryEEZ FSM 1 & 0.091 (0.003)***\\
-post:countryEEZ KIR 1 & 0.081 (0.003)***\\
-post:countryEEZ KIR 2 & 0.127 (0.004)***\\
-post:countryEEZ KIR 3 & 0.055 (0.005)***\\
-post:countryEEZ MHL 1 & 0.078 (0.003)***\\
-\addlinespace
-post:countryEEZ NRU 1 & 0.083 (0.003)***\\
-post:countryEEZ PNG 2 & -0.008 (0.005)*\\
-post:countryEEZ SLB 1 & 0.114 (0.004)***\\
-post:countryEEZ TUV 1 & 0.095 (0.003)***\\
-post:countryHS & 0.122 (0.003)***\\
-\addlinespace
-post:countryHS COK 1 & 0.083 (0.002)***\\
-post:countryHS KIR 1 & 0.112 (0.003)***\\
-post:countryHS KIR 2 & 0.093 (0.002)***\\
-post:countryHS KIR 3 & 0.108 (0.003)***\\
-\bottomrule
-\end{tabular}
-\end{table}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}}
+\end{figure}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
-\caption{\label{fig:unnamed-chunk-17}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\label{fig:unnamed-chunk-16}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 \centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
+\caption{\label{fig:unnamed-chunk-19}\label{fig:q1}Interaction of quarters
+and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
-and treatment. Control group is all vessels.}
+\caption{\label{fig:unnamed-chunk-20}\label{fig:q2}Interaction of quarters
+and treatment. Control group is vessels from PNA.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
-and treatment. Control group is vessels from PNA.}
+\caption{\label{fig:unnamed-chunk-21}\label{fig:q3}Interaction of quarters
+and treatment. Control group excludes Chinese vessels.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
-and treatment. Control group excludes Chinese vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
+\caption{\label{fig:unnamed-chunk-22}\label{fig:q4}Interaction of quarters
 and treatment. Control group is japanese vessels.}
@@
 \centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\caption{\label{fig:unnamed-chunk-23}\label{fig:ym1}Interaction of
+year-month and treatment. Control group is all vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
-year-month and treatment. Control group is all vessels.}
+\caption{\label{fig:unnamed-chunk-24}\label{fig:ym2}Interaction of
+year-month and treatment. Control group is vessels from PNA.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
-year-month and treatment. Control group is vessels from PNA.}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:ym3}Interaction of
+year-month and treatment. Control group excludes Chinese vessels.}
 \end{figure}
@@
 \includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
-year-month and treatment. Control group excludes Chinese vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
+\caption{\label{fig:unnamed-chunk-26}\label{fig:ym4}Interaction of
 year-month and treatment. Control group is japanese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
-\caption{\label{fig:unnamed-chunk-28}\label{fig:fishing_raster_full}}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+\caption{\label{fig:unnamed-chunk-27}\label{fig:fishing_raster_full}}
 \end{figure}

### 2018-10-20 rmd/Manuscript.Rmd
Obtained monthly treatment level rasters and updated ms

@@
 A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA."}
-countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI")
+countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"< "FJI")
 
@@
 Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
-It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1,fig:q2,fig:q3,fig:q4,fig:ym1,fig:ym2,fig:ym3,fig:ym4}).
+It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1}-\ref{fig:ym4}).
 
@@
 
-Four our empirical identification we calculated the proportion of fishing effort allocated every month to each spatially explicit regions defined in section \ref{methods}.
-For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs.
-Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels.
-The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
-The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}, fig:map_change_ps).
+For our empirical identification we ...
+The XXX shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
+The change in the relative allocation of fishing effort by purse seiners increases for most regions after PIPA implementation (Table \ref{tab:disp_mod}, \ref{fig:mean_change}).
 The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*).
@@
 
-fishing_raster <- readRDS(here::here("data", "fishing_raster_BACI.rds"))
+fishing_raster <- readRDS(file = here::here("data", "rasterized_effort_by_region.rds"))
 
@@
   ggplot() +
-  geom_raster(mapping = aes(x = lon, y = lat, fill = hours_norm)) +
+  geom_raster(mapping = aes(x = x, y = y, fill = hours_norm)) +
   geom_sf(data = eez, fill = "transparent", color = "black") +
   geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
-  # geom_sf(data = small_coast, color = "black") +
+  geom_sf(data = small_coast, color = "black") +
   # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
@@
 
-```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
-HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
-                  ncol=2,
-                  byrow=TRUE) %>%
-  list() %>%
-  st_polygon() %>% 
-  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")
+```{r, fig.cap = "\\label{fig:mean_change}"}
+raster_month_region <- readRDS(file = here::here("data", "monthly_rasterized_effort_by_region.rds"))
 
-HS_disp <- data.frame(country = "HS",
-                      PNA = F) %>% 
-  st_set_geometry(HS_disp_poly) %>% 
-  mutate(id = country, source = country, PNA = F) %>% 
-  select(id, source, PNA, country)
+model <- lm(hours ~ year_c * id, data = raster_month_region)
 
-eezs_exclude <- c("HS MUS 1", "EEZ MUS 1", "EEZ MDG 1", "EEZ MDG 2", "HS MDG 1", "HS MDG 2", "HS MOZ 1", "EEZ MOZ 1")
+pd <- position_dodge(width = 0.2)
 
-regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
-               layer = "regions")
-
-# I AM EXCLUDING MUS WHICH SHOULD BE PUT INTO EEZ
-regions %>% 
-  rbind(HS_disp) %>% 
-  left_join(ba_disp, by = c("id" = "country")) %>%
-  filter(!id %in% eezs_exclude) %>%
-  ggplot() +
-  geom_sf(aes(fill = change), color = "black") +
+commarobust::commarobust_tidy(model) %>%
+  filter(str_detect(term, ":")) %>%
+  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
+         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
+         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05")) %>%
+  ggplot(aes(x = year, y = est, color = term)) +
+  geom_errorbar(aes(ymin = est - se, ymax = est + se), width = 0, position = pd, size = 1) +
+  geom_point(aes(shape = p), size = 2, position = pd) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
   ggtheme_plot() +
-  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
-```
-
-```{r, results = "asis"}
-disp_mod_ps_data <- displacement_data %>% 
-  filter(!is.na(country),
-         gear == "purse_seines",
-         !country %in% regions_few_points) %>% 
-  mutate(post = post *1,
-         year2 = year^2,
-         month_c = as.character(month),
-         country = fct_relevel(country, "PIPA PIPA 1"),
-         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
-                          date > lubridate::date("2015/12/31") ~ "3",
-                          T ~ "2"))
-
-disp_mod_ps1 <- lm(h_prop ~ post*country + sate, data = disp_mod_ps_data)
-
-commarobust::commarobust_tidy(disp_mod_ps1) %>% 
-  mutate(b = str_detect(term, "Intercept"),
-         c = str_detect(term, "post"),
-         d = str_detect(term, "sate"),
-         a = b*c,
-         p1 = ifelse(p < 0.1, "*", ""),
-         p2 = ifelse(p < 0.05, "*", ""),
-         p3 = ifelse(p < 0.01, "*", ""),
-    h_prop = paste0(formatC(est, digits = 3, format = "f"),
-                    " (",
-                    formatC(se, digits = 3, format = "f"),
-                    ")",
-                    p1,
-                    p2,
-                    p3)) %>% 
-  filter(b+c+d > 0) %>% 
-  select(term, h_prop) %>% 
-  knitr::kable(booktabs = T,
-               caption = "\\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-
+  guides(color = guide_legend(ncol = 2, order = 2),
+         shape = guide_legend(order = 1))
 ```
@@
 
-```{r, results = "asis"}
+```{r}
 model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
@@
 m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
+```
 
+```{r, results = "asis"}
 models <- list(m1, m2, m3, m4)
@@
 ggplot() +
-  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
+  geom_raster(data = fishing_raster, mapping = aes(x = x, y = y, fill = hours_norm)) +
   geom_sf(data = eez, fill = "transparent", color = "black") +

### 2018-10-20 scripts/get_EEZ_subset.R

@@ -16,7 +16,9 @@ pipa <- read_sf(dsn = here::here("data", "spatial", "PIPA"),
 
 vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds")) %>% 
   filter(fishing,
-         !is.na(eez_iso3)) %>% 
+         gear == "purse_seines",
+         !is.na(eez_iso3),
+         year < 2018) %>% 
   group_by(eez_iso3) %>% 
   summarize(h = sum(hours)) %>% 
   arrange(desc(h)) %>% 
@@ -24,7 +26,7 @@ vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds")) %>%
   filter(prop <= 0.99)
 
 eez <- read_sf(dsn = here::here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
-  filter(ISO_Ter1 %in% unique(vessel_tracks$eez_iso3)) %>% 
+  filter(ISO_Ter1 %in% c(unique(vessel_tracks$eez_iso3), "FJI")) %>% 
   st_rotate() %>% 
   select(ISO_Ter1) %>%
   group_by(ISO_Ter1) %>%

### 2018-10-20 scripts/monthly_rasterized_effort_by_region.R

@@ -1,0 +1,147 @@
+library(raster)
+library(fasterize)
+library(sf)
+library(tidyverse)
+source(here::here("scripts", "st_rotate.R"))
+
+rasterize_df <- function(x, r, fun = "sum"){
+  x2 <- x %>%
+    select(lon, lat, hours) %>% 
+    mutate(lon = ifelse(lon < 0, lon + 180, lon - 180) + 180) %>% 
+    as.matrix()
+  
+  rasterize(x = x2[,1:2],
+            y = r,
+            field = x2[,3],
+            fun = fun) %>% 
+    return()
+}
+
+extract_raster <- function(r, year, month = NULL){
+  as.data.frame(r, xy = T) %>%
+    rename(hours = layer) %>% 
+    mutate(year = year,
+           month = month) %>% 
+    return()
+}
+
+eezs_exclude <- c("HS MUS 1", "EEZ MUS 1", "EEZ MDG 1", "EEZ MDG 2", "HS MDG 1", "HS MDG 2", "HS MOZ 1", "EEZ MOZ 1")
+
+regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
+                   layer = "regions") %>% 
+  filter(!id %in% eezs_exclude)
+
+regions_raster <- regions %>%
+  mutate(unique = group_indices(., id)) %>%
+  fasterize(sf = .,
+            raster = raster(., res = 1),
+            field = "unique",
+            background = 0)
+
+regions_with_HS <- regions %>%
+  mutate(unique = group_indices(., id)) %>% 
+  st_set_geometry(NULL) %>% 
+  rbind(data.frame(id = "HS HS 1", source = "HS", PNA = 0, country = "HS", unique = 0))
+
+regions_raster_df <- as.data.frame(regions_raster, xy = T) %>% 
+  left_join(regions_with_HS, by = c("layer" = "unique"))
+
+monthly_vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds")) %>% 
+  filter(gear == "purse_seines",
+         year < 2018,
+         fishing,
+         treated) %>% 
+  drop_na(hours, fishing) %>% 
+  mutate(date = lubridate::date(paste(year, month, 1, sep = "/")))
+
+# Vector of dates to iterate over
+dates <- sort(unique(monthly_vessel_tracks$date))
+
+# iniialize empty df
+monthly_effort_raster <- data.frame(x = NULL,
+                                    y = NULL,
+                                    hours = NULL,
[…]

### 2018-10-21 docs/Manuscript.tex
Updated all

@@
   \posttitle{\par}
-  \subtitle{Updated on 2018-10-19}
+  \subtitle{Updated on 2018-10-20}
   \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
@@
 within these protected areas upon implementation. The benefits of
-reducing effort have been largely studied, and include increases in
-abundance, biomass, and diversity within the bounded regions. These
-no-take zones may produce spillover effects, which provide fish for
-outside areas. However, the economic and ecological implications of
-displacing fishing effort are not yet fully understood. Novel data
-products that track fishing effort at the vessel-level allow us to
-identify changes in fleet- and vessel-level behavior upon the
-implementation of protected areas, as well as how these redistribute.
-This papers evaluates the implications of implementing LSMPA, by
-evaluating changes in fishing hours, showing that vessels in the
-effected region reduce fishing effort after the implementation of PIPA.
-Our results are robust to a set of specifications. We also track the
-relative spatial allocation of fishing events thorugh time, and identify
-that areas closer to PIPA show an increase in relative fishing hourse
-due to the displacement of PIPA-fishing vessels. Our results not only
-provide an impact evaluation of the effect of LSMPAs on fishing
-activity, but provide insights into vessel redistribution dynamics,
-which may have ecological and economic implications.
+reducing effort have been largely studied, but little empirical works
+evaluate what happens to the effort after an MPA is created. The
+economic and ecological implications of displacing fishing effort are
+not yet fully understood. We use identification of fishing activity via
+Automatic Identification Systems (AIS) and causal inference techniques
+to provide the first analyses of behavioral changes and spatial
+redistribution of tuna purse seiners due to the implementation of a
+Large Scale Marine Protected Area in the Pacific Ocean. Our work
+provides three main findings: 1) aggregate fishing effort remains
+relatively unaffected; 2) Vessels that fished inside the protected area
+redistribute to adjacent waters; and 3) We observe a crowding effect for
+the first years after implementation. Our results not only provide an
+impact evaluation of the effect of LSMPAs on fishing activity, but
+provide insights into vessel redistribution dynamics, which may have
+ecological and economic implications. As countries continue to implement
+LSMPAs as a way to reach the stated 10\% target of ocean protection,
+managers should consider how fishing effort will change in space and
+through time to ensure that fishing effort is not just displaced
+elsewhere, leading to overfishing in adjacent waters. While LSMPAs can
+provide a wide range of benefits, their implementation must be
+accompained with traditional fisheries management to maximize their
+effectiveness.
 \end{abstract}
@@
 Management \citep{maxwell_2015}. The effectiveness and difficulties of
-implementating LSMPAs are not the focus of this paper
+implementing LSMPAs are not the focus of this paper
 \footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
-Protected Areas. The map shows all areas larger than 250,000
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:LSMPAs_map}Large Scale
+Marine Protected Areas. The map shows all areas larger than 250,000
 Km\textsuperscript{2}. Areas in dark blue meet at least one of these
@@
 vessel-tracking data to demonstrate that the fairly large Palmyra Atoll
-National Wildlife Refuge (54,000 Km\textsuperscript{2}) protectes two
-thrids of the tagged grey reef sharks by effectively excluding fishing
+National Wildlife Refuge (54,000 Km\textsuperscript{2}) protects two
+thirds of the tagged grey reef sharks by effectively excluding fishing
 effort. More recently, \citep{bradley_2018} use similar data to
@@
 
-The empirical research that has been done in custumary sized MPAs
+The empirical research that has been done in customary sized MPAs
 suggest that resource users may show idiosyncratic responses. For
@@
 changes and is spatially redistributed. However, all these closures took
-place within Exlcusive Economic Zones, where other regulations exist.
+place within Exclusive Economic Zones, where other regulations exist.
 This may not always be the case for LSMPAs, where often the entire EEZ
@@
 Agreement to fishing hours. The VDS works as follows: Each year,
-scientific advisors recomend a total number of fishing vessel-days per
+scientific advisers recommend a total number of fishing vessel-days per
 year. Hours are allocated to each PNA country based on catch history,
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
-Economic Zones (EEZs) of the region of interest. A solid line indicates
-countries that belong to the PNA, while a dashed line indicates all
-others. A red line indicates the Kiribati EEZ, and a solid red polygon
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\label{fig:unnamed-chunk-14}\label{fig:PNA_map}Map of the Exclusive
+Economic Zones (EEZs) of the region of interest. Countries that belong
+to the PNA are shown in blue, while empty polygons indicates all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon
 delineates PIPA.}
@@
 global fisheries production statistics, with 2016 catches increasing
-relative to the 2005-2014 average \citep{fao_2018}. Theis region of the
+relative to the 2005-2014 average \citep{fao_2018}. This region of the
 Pacific has historically accounted for a large portion of tuna catches
@@
 these catches derive from purse seine vessels licensed under the VDS.
-Fishing vessels from Australia, New Zeland, China, France, Korea, Japan,
-the Philippines, Taiwan, and the United States participate in the
+Fishing vessels from Australia, New Zealand, China, France, Korea,
+Japan, the Philippines, Taiwan, and the United States participate in the
 purse-seining VDS.
@@
 least once before
-2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore exlcuded from our analyses.}.
+2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses.}.
 These vessels represent over 26 million individual observations for the
 2012 - 2017 period. We identify 65 vessels that have fished inside PIPA
-at least once since 2012. From these, 62 did so before the anouncement
+at least once since 2012. From these, 62 did so before the announcement
 (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}) but are
-only able to track 61 for the complete periof of study before and after
+only able to track 61 for the complete period of study before and after
 its
@@
 Therefore, our treatment group contains all purse seiners (n = 61) that
-fished within PIPA at least once before the anouncement, and that
+fished within PIPA at least once before the announcement, and that
 continued to fish elsewhere after the January 2015 implementation.
@@
 27)\footnote{Using Taiwanese vessels was the original idea, but there are only 4 vessels with pre-2015 data.
-I need to further identify propper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
+I need to further identify proper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
 Our definition of treatment and control groups leaves us with 61 and 21
@@
 
-For each vessel we calculate total daily fishing hours and obtain pannel
+For each vessel we calculate total daily fishing hours and obtain panel
 data with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
@@
 
-\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-17}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels. Vertical dashed lines
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:all_vessels}Fishing hours
+and number of vessels by month for all vessels. Vertical dashed lines
 indicates dates when satellites were added, solid line indicates PIPA
@@
 places and times where to fish. Our variables of interests intend to
-caputre these possible reactions.
+capture these possible reactions.
 
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
 \]
@@
 the treatment effect. Finally, \(\phi_t\) and \(\gamma_i\) represent
-month-, and flag-level dummies that account for seasonality or
-country-level management
-interventions\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
+month- and flag-level dummies that account for seasonality or
+country-level management interventions. \(\theta_t\) are dummies to
+account for the addition of more satellites.
+\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
 
@@
 beginning of the season. If a vessel decides to fish within the PNA,
-they've already made the decission to pay for access, expecting higher
+they've already made the decision to pay for access, expecting higher
 returns from fishing there than in the High Seas. In the particular case
@@
 I-Kiribati waters would then move to other fishing grounds within
-Kiribati after the closure. Alternatively, if a vessel fishes illegaly
+Kiribati after the closure. Alternatively, if a vessel fishes illegally
 in I-Kiribati waters before the implementation, one would expect them to
@@
 
-We discretize spatial units by using a polygon for PIPA
-\footnote{we would expect to see a decrease here} and distinct spatial
-units for each EEZ of each country. Some vessels might shift from EEZs
-into the high seas, but we are interested in knowing \emph{where} in the
-high seas, so we incorporate additional regions by using a 1 degree
-buffer of the high seas arround each of the EEZ regions. The rest of the
-high seas are merged into a single spatial unit. For example, if we were
-to do this only for Kiribati, we would have 8 spatial units: PIPA, three
-EEZs, three 1-degree buffers of high seas arround each EEZs, and the
-rest of the high seas. Whenever the buffers overlapped between
-themselves, we randocmply clipped one on to the other. EEZs that had
-sporadic fishing events were pooled into a group of ``others''.
-
-To evaluate this change in effort allocation, we regress our variable of
-interest (\emph{i.e.} fishing hours) on the interaction between a dummy
-variable indicating the policy intervention and a dummy variable for
-countries. This gives us the by-country change in proportional
-allocation of fishing effort:
+We discretize spatial units by using a polygon for
+PIPA\footnote{we would expect to see a decrease here} and distinct
+spatial units for each EEZ of each country. Some vessels might shift
+from EEZs into the high seas, but we are interested in knowing
+\emph{where} in the high seas, so we incorporate additional regions by
+using a 1 degree buffer of the high seas around each of the EEZ regions.
+The rest of the high seas are merged into a single spatial unit. For
+example, if we were to do this only for Kiribati, we would have 8
+spatial units: PIPA, three EEZs, three 1-degree buffers of high seas
+around each EEZs, and the rest of the high seas. Whenever the buffers
+overlapped between themselves, we randomly clipped one on to the other.
+
+We then take this spatial polygons and rasterize them to a 1-degree grid
+(See Figure \ref{fig:raster_rgn}), which we then use to rasterize points
+of fishing activity. For each cell, we calculate the total monthly
+fishing hours by treated and control vessels (See Figure
+\ref{fig:fishing_raster}). Since we are interested in the redistribution
+of fishing effort, we use this gridded data to calculate the proportion
+of fishing hours that each region receives each month relative to the
+total fishing hours observed across all regions and all cells in that
+month.
+
+We use this measure to evaluate the change in effort allocation by
+regressing it on the interaction between a year dummy and a dummy for
+regions:
 
 \[
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
 \]
@@
 Our variable of interest, \(y_{i,t}\) represents the proportion of
-fishing hours that country \(i\) receives at time \(t\). \(Post\) also
-represents a policy dummy that takes the value of 0 for all dates before
-implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
-for countries for the spatial units defined above. Our parameter of
-interest is \(\beta_{1,i}\), which captures the country-level change in
-proportional fishing effort.
+fishing hours that region \(i\) receives at time \(t\). Years are
+modelled as factors (\(Year_t\)), using 2012 as the reference level.
+\(Region\) is a dummy variable for regions defined above. Our parameter
+of interest is \(\beta_{3,i}\), which captures the yearly by-country
+change in proportional allocation of fishing effort relative to 2012.
 
@@
 
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
-\centering
-\begin{tabular}[t]{lr}
-\toprule
-country & change\\
-\midrule
-EEZ COK 1 & 0.53\\
-EEZ FSM 1 & 0.81\\
-EEZ KIR 1 & -0.16\\
-EEZ KIR 2 & 4.50\\
-EEZ KIR 3 & -2.79\\
-\addlinespace
-EEZ MHL 1 & -0.44\\
-EEZ NRU 1 & 0.07\\
-EEZ PNG 2 & -9.07\\
-EEZ SLB 1 & 3.18\\
-EEZ TUV 1 & 1.27\\
-\addlinespace
-HS & 3.93\\
-HS COK 1 & 0.06\\
-HS KIR 1 & 2.96\\
-HS KIR 2 & 1.07\\
-HS KIR 3 & 2.53\\
-PIPA PIPA 1 & -8.25\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \clearpage
@@
 \section{Results}\label{results}}
-
-Our DiD analysis shows an overall increase in purse seine fishing hours,
-even after accounting for the introduction of new satellites (Table
-\ref{tab:did}). This coefficient estimate is consistent for different
-model specifications and across groups of treatment and controls. These
-effectively represent the patterns observed in Figure
-\ref{fig:all_vessels}. The \(\beta_3\) coefficient indicating our
-treatment effect suggests that, relative to the control, treated vessels
-fish less, in the order of 0.5 hours per day. Another way to interpret
-this is that the increase in fishing effort by treated vessels has
-ocurred at a lower rate than control vessels. This result is robust and
-significant (\(p < 0.05\)) for all model specifications using our main
-control group, with the effect varying between \(\beta_3 = -0.515\) and
-\(\beta_3 = -0.934\). These values are equivalent to a 15 - 28 reduction
-in fishing hours per month.
 
@@
 Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
-hence don't include flag FEs to avoid perfect colinearity between
-Japanese flag and
+hence don't include flag fixed-effects to avoid perfect colinearity
+between Japanese flag and
 control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
-It must be noted, however, that when reducing the linear structure of
-the \(Pre \times Post\) design and instead interacting the treatment
-dummy with quarterly or year-month combinations we are not able to
-reject the null hypotheses of no change (Figures
-\ref{fig:q1,fig:q2,fig:q3,fig:q4,fig:ym1,fig:ym2,fig:ym3,fig:ym4}).
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
+Our DiD analysis shows an overall increase in purse seine fishing hours,
+even after accounting for the introduction of new satellites (Table
+\ref{tab:did}). This coefficient estimate is consistent for different
+model specifications and across groups of treatment and controls, and
+effectively represents the patterns observed in Figure
+\ref{fig:all_vessels}.
+
+The \(\beta_3\) coefficient indicating our treatment effect suggests
+that, relative to the control, treated vessels fish less, in the order
+of 0.5 hours per day. Another way to interpret this is that the increase
+in fishing effort by treated vessels has occurred at a lower rate than
+control vessels. The effect varying between \(\beta_3 = -0.515\) and
+\(\beta_3 = -0.934\). These values are equivalent to a 15 - 28 reduction
+in fishing hours per month. However, this result is only robust and
+significant (\(p < 0.01\)) in the simplest specification of the
+Diff-in-Diff. When reducing the linear structure of the
+\(Pre \times Post\) design and instead interacting the treatment dummy
+with quarterly or year-month combinations we are not able to reject the
+null hypotheses of no change, suggesting that the total fishing hours
+remains similar for the displaced vessels (Figs.
+\ref{fig:q1}-\ref{fig:ym4}). Since vessels don't seem to be fishing less
+(or at least not much less), an obvious question arises: where are they
+fishing now?
+
+Figure \ref{fig:fishing_raster} provides a spatial representation of
+these changes. Note that 2013 effort distribution is roughly similar
+across vessels. Then in 2014 there is a sharp increase in fishing hours
+by treated vessels inside PIPA (blue paradox). In 2015 treated vessels
+then allocate more effort to the easternmost Kiribati EEZ (see Figure
+\label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of
+fishing effort is again similar across groups. It is evident that the
+increase in relative fishing effort is greater for for regions closer to
+PIPA.
+
+Along a similar line, Figure \ref{fig:redist_trend} shows a detailed
+temporal evolution of the relative allocation of fishing
+effort\footnote{Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.}.
+It shows shows the change in fishing effort inside PIPA, including the
+preemptive fishing and immediate reduction previously reported
+\citep{mcdermott_2018}. I-Kiribati waters in KIR 1 and KIR 2 show an
+increase in fishing effort for 2015; the same pattern is observed for
+their respective High Seas buffers, and the general High Seas. Other
+regions farther away from PIPA don't show a clear pattern under visual
+inspection.
+
+We then move on to our regression results, presented as a figure showing
+the year-region interaction coefficient estimates for each region as a
+stream of changes through time (Fig. \ref{fig:mean_change} and Table
+\ref{tab:mean_change}). As noted before, the marginal change in the
+relative allocation of fishing effort relative to 2012 increases in 2014
+for PIPA. Most coefficients are not statistically significant, but
+follow the same trends previously discussed, with a tendency for regions
+closer to PIPA to show an increase in the relative allocation of fishing
+effort in the post-implementation period. The largest increase is
+observed for the I-Kiribati EEZ 2, where the redistribution of treated
+vessels caused a 15\% increase in the \emph{relative} allocation of
+fishing effort within I-Kiribati waters. This displacement is likely
+causing a crowding effect after PIPA-fishing vessels redistribute to
+other areas.
+
+We use the rasterized effort to evaluate if the PIPA closure increased
+crowdness otuside the LSMPA. We count the number of raster cells that
+had both treated and control vessels each year (Fig.
+\ref{fig:sp_corr}A). The pattern observed here could just be an artifact
+of satellite detections increasing though time. Thereforem we also
+calculate a spatial correlation of presence/absence and observe similar
+patterns (Fig. \ref{fig:sp_corr}B). While this are at the year level and
+cannot assure that vessels were in effect at the same time in the same
+vessel, it provides an accurate depiction of what we would expect to
+find if our claims of displacement are true. Spatial overlap increases
+in 2015 as vessels from PIPA are excluded, and that measure slowly
+returns to its previous state.
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+\caption{\label{fig:unnamed-chunk-21}\label{fig:all_vessels}Daily fishing
 hours for all vessels in our main treatment-control groups. Solid
 straight lines show a linear trend by period (pre-psot) and treatment.
-The other red and blue lines show monthly avarages. Vertical dashed line
-indicates PIPA closure.}
+The other red and blue lines show monthly avarages. Vertical dashed
+lines indicates dates when satellites were added, solid line indicates
+PIPA closurePIPA closure.}
 \end{figure}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\caption{\label{fig:unnamed-chunk-23}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 
-Recall that to evaluate the redistribution of fishing effort we only
-track fishing vessels that belong to the treated group. Figure
-\ref{fig:fishing_raster} provides a spatial representation of these
-changes. Note that 2013 effort distribution is roughly similar across
-vessels. Then in 2014 there is a sharp increase in fishing hours by
-treated vessels inside PIPA (blue paradox). In 2015 treated vessels then
-allocate more effort to the easternmost Kiribati EEZ (see Figure
-\label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of
-fishing effort is again similar across groups. It is evident that the
-increase in relative fishing effort is greater for for regions closer to
-PIPA, and.
-
-For our empirical identification we \ldots{} The XXX shows the change in
-fishing effort inside PIPA, including the preemptive fishing and
-immediate reduction previously reported \citep{mcdermott_2018}. The
-change in the relative allocation of fishing effort by purse seiners
-increases for most regions after PIPA implementation (Table
-\ref{tab:disp_mod}, \ref{fig:mean_change}). The largest increase is
-observed for the I-Kiribati EEZ, with an average increase of 0.11
-(\emph{p \textless{} 0.001}). In other words, the redistribution of
-treated vessels caused a 10\% increase in the \emph{relative} allocation
-of fishing effort within I-Kiribati waters. The only decrease is
-observed for Papua New Guinea, but the coefficient is not significant.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\caption{\label{fig:unnamed-chunk-24}\label{fig:fishing_raster}Yearly
 spatial distribution of fishing effort by treated and control vessels.
 Colors have been adjusted relative to the maximum observed by group and
-year.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
+year. Red polygons show LGMPAs in the region. For visualization purpose
+sonly some years are presented, the full 2012 - 2017 period is shown in
+Figure \ref{fig:fishing_raster_full}.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:redist_trend}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
-after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}}
+after PIPA by region. Colors indicate the pre-post period. Solid line
+across points shows local mean with a region-specific loess smoother.
+Vertical dashed lines indicates dates when satellites were added, solid
+line indicates PIPA closurePIPA closure. Note that inflection points of
+the loess smoother are not affected by the addition of satellites.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
+\caption{\label{fig:unnamed-chunk-26}\label{fig:mean_change}Coefficient
+estimates for the redistribution regression. Each pannel shows the
+region-specific coefficients, with heteroskedastick-robust standard
+errors as error bars. The horizontal dashed line represents 0 chenge
+relative to the 2012 region-specific levels.}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-27}\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
+Each row represents a region, each color a year.
+Numbers in parentheses are heteroskedatic-robust standard errors.
+R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001).
+* < 0.1; ** p < 0.05; ***p < 0.01.}
+\centering
+\begin{tabular}[t]{llllll}
+\toprule
+term & 2013 & 2014 & 2015 & 2016 & 2017\\
+\midrule
+PIPA PIPA 1 & -0.062 (0.026)** & 0.085 (0.043)** & -0.086 (0.026)*** & -0.079 (0.025)*** & -0.074 (0.025)***\\
+EEZ KIR 1 & -0.034 (0.030) & 0.035 (0.038) & 0.042 (0.045) & -0.035 (0.031) & -0.023 (0.032)\\
+EEZ KIR 2 & 0.001 (0.009) & 0.032 (0.019)* & 0.142 (0.061)** & 0.014 (0.013) & 0.014 (0.015)\\
+EEZ KIR 3 & -0.188 (0.075)** & -0.061 (0.072) & -0.118 (0.069)* & -0.093 (0.083) & -0.098 (0.083)\\
+HS KIR 1 & -0.003 (0.011) & 0.016 (0.012) & 0.038 (0.013)*** & 0.004 (0.013) & 0.037 (0.018)**\\
+\addlinespace
+HS KIR 2 & 0.009 (0.006) & 0.004 (0.006) & -0.000 (0.009) & 0.022 (0.010)** & 0.008 (0.006)\\
+HS KIR 3 & -0.002 (0.009) & 0.003 (0.009) & -0.008 (0.011) & 0.022 (0.011)* & 0.064 (0.024)***\\
+HS HS 1 & 0.021 (0.015) & 0.027 (0.017) & 0.045 (0.017)*** & 0.030 (0.017)* & 0.014 (0.015)\\
+EEZ FSM 1 & 0.018 (0.033) & -0.015 (0.025) & 0.000 (0.037) & 0.012 (0.025) & -0.001 (0.021)\\
+EEZ MHL 1 & 0.037 (0.022) & 0.025 (0.010)** & -0.006 (0.009) & 0.052 (0.032) & -0.000 (0.006)\\
+\addlinespace
+EEZ NRU 1 & 0.046 (0.021)** & 0.044 (0.020)** & 0.003 (0.017) & 0.033 (0.015)** & 0.050 (0.025)**\\
+EEZ PNG 2 & 0.196 (0.072)*** & -0.106 (0.041)*** & -0.132 (0.043)*** & -0.064 (0.048) & 0.001 (0.049)\\
+EEZ SLB 1 & 0.083 (0.056) & -0.019 (0.032) & -0.009 (0.038) & 0.081 (0.053) & 0.076 (0.046)*\\
+EEZ TUV 1 & -0.055 (0.037) & -0.033 (0.040) & -0.063 (0.037)* & 0.018 (0.046) & -0.026 (0.038)\\
+HS COK 1 & -0.003 (0.008) & -0.004 (0.008) & -0.003 (0.011) & -0.007 (0.008) & -0.003 (0.008)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
+\caption{\label{fig:unnamed-chunk-28}\label{fig:sp_corr}Number of cells that
+had treated and control vessels (A) and spatial correlation in the
+presence-absence of treated and control vessels per cell (B).}
 \end{figure}
@@
 can have on vessel behavior and the redistribution of fishing effort.
-These collection of results shows that the implementation of PIPA caused
-treated vessels to reduce their fishing hours, and that this effect is
-greater for purse seiners than longliners. Even though treated vessels
-fish less, their relative allocation of fishing hours increased for all
-other fishing grounds. This does not imply that there is more fishing
-effort exerted by treated vessels, but rather that each region receives
-a greater portion of the post-PIPA fishing effort of these same vessels,
-which is lower than pre-PIPA levels. In this section we discuss the
-implications of vessel-level reductions in fishing effort and the
+These collection of results show that the implementation of PIPA had
+little effect on the effort exerted by purse seiners. However, regions
+adjacent to PIPA show an increase in the relative amount of fishing
+effort, suggesting that effort is simply redisplaced to closeby areas.
+This does not imply that there is more fishing effort exerted by treated
+vessels, but rather that each region receives a greater portion of the
+post-PIPA fishing effort of these same vessels, which is lower than
+pre-PIPA levels. Additionally, we show that post-PIPA there is a
+concentration of effort leading to crowding. In this section we discuss
+the implications of vessel-level reductions in fishing effort and the
 increase in relative allocation of the remaining effort through space.
@@
 be more reactive to the spatial closure.
-
-A major shortcoming of our analyses is that we do not observe catches or
-revenues, which ultimately are the factors that guide the decision
-making process of profit-maximizing agents. Therefore, it is difficult
-to know whether the reduction in fishing effort represents a positive or
-negative impact. A decrease in fishing effort is associated to an
-increase in catches (and therefore greater CPUE) only when the entire
-fleet does it, and if previous levels of effort were greater than
-\(F_{MEY}\) (\emph{i.e.} the effort that would yield the maximum
-economic yield). Therefore, it is plausible that the reduction of
-fishing hours is not done by choice, but rather results from fishers
-having to increase search time. Upon being relocated, fishers may not
-identify the best fishing grounds as easily as before, and therefore
-invest a greater proportion of their time searching for their catch.
-Further analysis of temporal trends in non-fishing hours, as well as
-distance traveled should provide us with insights as to why fishers
-reduced fishing hours.
 
@@
 fishing effort to compensate for the reduction in available space. Our
-data is assembled in a similar way, with fishing positions before and
-after the implementation of PIPA and vessels grouped into treated and
-control groups. Our BACI design, along with our
-difference-in-differences analysis allows us to make causal inferences
-about the effect that large scale marine protected areas have on fishing
-effort.
-
-The different responses observed between purse seiners and longliners
-might have two possible explanations. It is likely that PIPA did not
-contain habitat that longliners would consider optimal. Therefore, the
-sporadic fishing events that occurred there are of little importance to
-the fleet, and it is unlikely that the implementation of PIPA has an
-effect on them. Alternatively, the differences may be due to the nature
-of each fishing gear. Purse seiners are often constrained by seafloor
-and termocline depth, and have a smaller spatial footprint
-\citep{kroodsma_2018}. Tuna purse seiners are known to have greater
-proportion of null sets (\emph{i.e.} where purse seines effectively cast
-their nets, but no catch is obtained) during El Niño years, where the
-termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}. On
-the other hand, longliners may be more flexible as to where they can
-deploy their longlines. \citet{ortuocrespo_2018} evaluated the
-ecological niche of the pelagic longline fleet, and suggest that the
-fleet may be under-utilizing the ocean, meaning that they can easily
-redistribute elsewhere.
-
-Our work suggests that the implementation of LSMPAs can have important
-implications for purse seiners, and less so for longliners. We also show
-that fishing effort is redistributed to areas close by. Future
-management interventions that aim to close large portion of the oceans
-should consider how fishing effort will change in space and through
-time, and the ecological implications of this redistribution to ensure
-that fishing effort is not just displaced elsewhere, leading to
-overfishing in adjacent waters.
-
-Furthermore, a growing body of literature suggests that closing the high
-seas to all fishing could increase fishery yields and profitability of
-fisheries, with negligible costs to food security
-\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-
-\clearpage
-
-\hypertarget{refs}{}
+data, which is assembled in a similar way, allows us to make similar
+inferences about the unobserved change in aggregate fishing effort and
+its spatial redistribution.
+
+The role of the institutions at play is evident. Vessels that fished
+inside PIPA before the implementation were, ultimately, fishing in
+I-Kiribati waters likely under a VDS license. Uppon the implementation,
+some of these redistribute to other areas of the I-Kiribat EEZ and the
+high seas for the year immediately after the closure. As stated before,
+it is reasonable for a vessel holding a license to fish in I-Kiribati
+waters to simply reallocate their effor to other parts of that EEZ.
+However, the shift to the high seas may not follow the same logic.
+Instead, it is possible that vessels that redistribute to the high seas
+were opperating in I-Kiribati illegally, and decide to reallocate in the
+high seas to continue fishing without a license. These patterns provide
+us with interesting insight sinto fishing behavior, which may become
+useful in tackling Illegal, Unreported and Unregulted (IUU) fisheries.
+
+A major shortcoming of our analyses is that we do not observe catches or
+revenues, which ultimately are the factors that guide the decision
+making process of profit-maximizing agents. Therefore, it is difficult
+to know whether lack of change in fishing hours represents a positive or
+negative impact. An additional thing that we are yet to test is the
+changes in non-fishing hours sepnt at sea. It is plausible that fishing
+hours remain constant, but vessels have to increase search time. Upon
+being relocated, fishers may not identify the best fishing grounds as
+easily as before, and therefore invest a greater proportion of their
+time searching for their catch. Further analysis of temporal trends in
+non-fishing hours, as well as distance traveled should provide us with
+insights as to why fishers reduced fishing hours. However, the
+widespread footprint of the treated fleet may suggest that they are well
+aqquainted with the region (See Fig. \ref{fig:fishing_raster}), and its
+unlikely that they would need to learn or identify new fishing grounds.
+
+Our work suggests that the implementation of LSMPAs has little impact on
+purse seiners fishng effort. We also show that fishing effort is
+redistributed to areas close by, and that this leads to a potentially
+negative crowding effect. A growing body of literature suggests that
+closing the high seas to all fishing could increase fishery yields and
+profitability of fisheries, with negligible costs to food security
+\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Such
+management interventions should consider how fishing effort will change
+in space and through time, and the ecological implications of this
+redistribution to ensure that fishing effort is not just displaced
+elsewhere, leading to overfishing in adjacent waters. While LSMPAs can
+provide a wide range of benefits, their implementation must be
+accompained with traditional fisheries management to maximize
+effectiveness.
+
+\hypertarget{further-work}{%
+\section{Further work}\label{further-work}}
+
+\begin{itemize}
+\tightlist
+\item
+  Distance traveled
+\item
+  Non-fishing hours at sea
+\item
+  Monthly crowdnes??
+\item
+  Repeat raster exercise for Revillagigedo and other recently
+  implemented LSMPAs. It would be great to have a pannel figure of 3 or
+  4 other LSMPAs that show wher effort was and where it went to
+  generalize our results.
+\item
+  John talked about this being relevant to Palau (their upcoming LSMPA).
+  We might want to talk about where the vessels that are there would go.
+\end{itemize}
+
+\bibliography{references.bib}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
-\caption{\label{fig:unnamed-chunk-16}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
+\caption{\label{fig:unnamed-chunk-29}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 
-We include a second degree polinomial for years as:
+We include a second degree polynomial for years as:
 
@@
 
+\clearpage
+
 \hypertarget{quarterly-did-interactions}{%
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
-\caption{\label{fig:unnamed-chunk-19}\label{fig:q1}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-33-1.pdf}
+\caption{\label{fig:unnamed-chunk-33}\label{fig:q1}Interaction of quarters
 and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-\caption{\label{fig:unnamed-chunk-20}\label{fig:q2}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-34-1.pdf}
+\caption{\label{fig:unnamed-chunk-34}\label{fig:q2}Interaction of quarters
 and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\caption{\label{fig:unnamed-chunk-21}\label{fig:q3}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
+\caption{\label{fig:unnamed-chunk-35}\label{fig:q3}Interaction of quarters
 and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-\caption{\label{fig:unnamed-chunk-22}\label{fig:q4}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
+\caption{\label{fig:unnamed-chunk-36}\label{fig:q4}Interaction of quarters
 and treatment. Control group is japanese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\caption{\label{fig:unnamed-chunk-23}\label{fig:ym1}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
+\caption{\label{fig:unnamed-chunk-37}\label{fig:ym1}Interaction of
 year-month and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-\caption{\label{fig:unnamed-chunk-24}\label{fig:ym2}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
+\caption{\label{fig:unnamed-chunk-38}\label{fig:ym2}Interaction of
 year-month and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:ym3}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-39-1.pdf}
+\caption{\label{fig:unnamed-chunk-39}\label{fig:ym3}Interaction of
 year-month and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-\caption{\label{fig:unnamed-chunk-26}\label{fig:ym4}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-40-1.pdf}
+\caption{\label{fig:unnamed-chunk-40}\label{fig:ym4}Interaction of
 year-month and treatment. Control group is japanese vessels.}
+\end{figure}
+
+\hypertarget{effort-redistribution}{%
+\subsection{Effort redistribution}\label{effort-redistribution}}
+
+\hypertarget{rasterized-regions}{%
+\subsection{Rasterized regions}\label{rasterized-regions}}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-41-1.pdf}
+\caption{\label{fig:unnamed-chunk-41}\label{fig:raster_rgn}Rasterized
+regions. Each color (number) indicates a distinct region.}
 \end{figure}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-\caption{\label{fig:unnamed-chunk-27}\label{fig:fishing_raster_full}}
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
+\caption{\label{fig:unnamed-chunk-42}\label{fig:fishing_raster_full}Yearly
+rasters of fishing hours for each group.}
 \end{figure}
@@
 
-\bibliography{references.bib}
-
 \end{document}

### 2018-10-21 rmd/Manuscript.Rmd
Updated all

@@
 Fishing effort is effectively eliminated within these protected areas upon implementation.
-The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions.
-These no-take zones may produce spillover effects, which provide fish for outside areas.
-However, the economic and ecological implications of displacing fishing effort are not yet fully understood.
-Novel data products that track fishing effort at the vessel-level allow us to identify changes in fleet- and vessel-level behavior upon the implementation of protected areas, as well as how these redistribute.
-This papers evaluates the implications of implementing LSMPA, by evaluating changes in fishing hours, showing that vessels in the effected region reduce fishing effort after the implementation of PIPA.
-Our results are robust to a set of specifications.
-We also track the relative spatial allocation of fishing events thorugh time, and identify that areas closer to PIPA show an increase in relative fishing hourse due to the displacement of PIPA-fishing vessels.
-Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
+The benefits of reducing effort have been largely studied, but little empirical works evaluate what happens to the effort after an MPA is created.
+The economic and ecological implications of displacing fishing effort are not yet fully understood.
+We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to provide the first analyses of behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a Large Scale Marine Protected Area in the Pacific Ocean.
+Our work provides three main findings: 1) aggregate fishing effort remains relatively unaffected; 2) Vessels that fished inside the protected area redistribute to adjacent waters; and 3) We observe a crowding effect for the first years after implementation.
+Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications.
+As countries continue to implement LSMPAs as a way to reach the stated 10% target of ocean protection, managers should consider how fishing effort will change in space and through time to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize their effectiveness."
 date: "
@@
   - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-bibliography: references.bib
+# bibliography: references.bib
 biblio-style: chicago
@@
 suppressPackageStartupMessages({
+  library(raster)
   library(startR)
@@
 \citet{game_2009} suggested that most of the challenges could be overcome with the incorporation of technology, in what then became known as Dynamic Ocean Management \citep{maxwell_2015}.
-The effectiveness and difficulties of implementating LSMPAs are not the focus of this paper \footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
+The effectiveness and difficulties of implementing LSMPAs are not the focus of this paper \footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
 Instead, we focus on the effect and implications of the ones that *have been* implemented.
@@
 For example, \citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to preemptive overfishing, which can erode or delay the expected benefits of the intervention.
-\citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protectes two thrids of the tagged grey reef sharks by effectively excluding fishing effort.
+\citet{white_2017} combine shark tags and vessel-tracking data to demonstrate that the fairly large Palmyra Atoll National Wildlife Refuge (54,000 Km^2^) protects two thirds of the tagged grey reef sharks by effectively excluding fishing effort.
 More recently, \citep{bradley_2018} use similar data to highlight cases of potential illegal shark fishing *inside* a 2 million km^2^ shark sanctuary.
@@
 
-The empirical research that has been done in custumary sized MPAs suggest that resource users may show idiosyncratic responses.
+The empirical research that has been done in customary sized MPAs suggest that resource users may show idiosyncratic responses.
 For example, \citet{stevenson_2013} show that a network of MPAs displaced fishing effort farther away from ports, resulting in higher *perceived* costs, and increases in catch per unit effort.
@@
 The way in which fishers react to a spatial closure can have major implications in its outcome \citep{smith_2003,hilborn_2006} highlighting the need to understand how fishers react to the implementation of LSMPAs, and fishing effort changes and is spatially redistributed.
-However, all these closures took place within Exlcusive Economic Zones, where other regulations exist.
+However, all these closures took place within Exclusive Economic Zones, where other regulations exist.
 This may not always be the case for LSMPAs, where often the entire EEZ is converted into a LSMPA, leaving fishers with the options of moving to the high seas or other countries' EEZs.
@@
 This effectively modified how fishing effort was managed, from number of vessels under the Palau Agreement to fishing hours.
-The VDS works as follows: Each year, scientific advisors recomend a total number of fishing vessel-days per year.
+The VDS works as follows: Each year, scientific advisers recommend a total number of fishing vessel-days per year.
 Hours are allocated to each PNA country based on catch history, and they then use or sell fishing rights to other non-PNA countries \citep{aqorau_2018}.
@@
 ```{r, fig.cap = "\\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
-A solid line indicates countries that belong to the PNA, while a dashed line indicates all others.
+Countries that belong to the PNA are shown in blue, while empty polygons indicates all others.
 A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA."}
-countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"< "FJI")
+countries <- c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI", "FJI", "NIU", "TON", "WSM", "WLF", "VUT", "NCL")
 
@@
   filter(ISO_Ter1 %in% countries) %>% 
-  mutate(KIR = ISO_Ter1 == "KIR") %>% 
+  mutate(KIR = ISO_Ter1 == "KIR",
+         PNA = ifelse(PNA, "PNA", "Non-PNA")) %>% 
   group_by(ISO_Ter1, PNA, KIR) %>% 
@@
 ggplot() +
-  geom_sf(data = eez, aes(color = KIR, linetype = !PNA), fill = "transparent") +
+  geom_sf(data = eez, aes(color = KIR, fill = PNA), alpha = 0.5) +
   geom_sf(data = pipa, fill = "red") +
@@
   scale_color_manual(values = c("black", "red")) +
+  scale_fill_manual(values = c("transparent", "steelblue")) +
   theme(legend.position = "none")
@@
 From these, the first two are amongst the top-10 species represented in global fisheries production statistics, with 2016 catches increasing relative to the 2005-2014 average \citep{fao_2018}.
-Theis region of the Pacific has historically accounted for a large portion of tuna catches \citep{aqorau_1997}.
+This region of the Pacific has historically accounted for a large portion of tuna catches \citep{aqorau_1997}.
 Today, the PNA controls close to 50% of the global skipjack tuna production \citep{pna_website_2018}.
 A large portion of these catches derive from purse seine vessels licensed under the VDS.
-Fishing vessels from Australia, New Zeland, China, France, Korea, Japan, the Philippines, Taiwan, and the United States participate in the purse-seining VDS.
+Fishing vessels from Australia, New Zealand, China, France, Korea, Japan, the Philippines, Taiwan, and the United States participate in the purse-seining VDS.
 
@@
 Our analysis focuses on purse seine vessels, the most important fishery for PNA countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
-We identify a total of 103 purse seiners that fished in PNA waters at least once before 2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore exlcuded from our analyses.}.
+We identify a total of 103 purse seiners that fished in PNA waters at least once before 2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses.}.
 These vessels represent over 26 million individual observations for the 2012 - 2017 period.
 We identify 65 vessels that have fished inside PIPA at least once since 2012.
-From these, 62 did so before the anouncement (*i.e.* 09/01/2014 *sensu* \citep{mcdermott_2018}) but are only able to track 61 for the complete periof of study before and after its implementation\footnote{1 vessel never fished again after August 18, 2013.}.
+From these, 62 did so before the announcement (*i.e.* 09/01/2014 *sensu* \citep{mcdermott_2018}) but are only able to track 61 for the complete period of study before and after its implementation\footnote{1 vessel never fished again after August 18, 2013.}.
 On the other hand, 38 vessels never fished inside PIPA but we only have data for 26 vessels before and after.
 
-Therefore, our treatment group contains all purse seiners (n = 61) that fished within PIPA at least once before the anouncement, and that continued to fish elsewhere after the January 2015 implementation.
+Therefore, our treatment group contains all purse seiners (n = 61) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
 Vessels in the control group meet the following two conditions: i) vessels never fished within PIPA waters, and ii) vessels have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure (n = 26).
@@
 Our third control is made up of Japanese purse seiners that fish in the Pacific but that never fished inside PIPA (n = 27)\footnote{Using Taiwanese vessels was the original idea, but there are only 4 vessels with pre-2015 data.
-I need to further identify propper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
+I need to further identify proper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
 Our definition of treatment and control groups leaves us with 61 and 21 treated and control vessels, which have just over 22 million observations where about 22% are identified as fishing events.
 
-For each vessel we calculate total daily fishing hours and obtain pannel data with 37,800 observations.
+For each vessel we calculate total daily fishing hours and obtain panel data with 37,800 observations.
 Table \ref{tab:baci_n_s} shows the number of vessels following a BACI design, as well as the fishing hours, before and after PIPA.
@@
 However, if the area of influence of a vessel is significantly larger than that of the spatial closure, they might already know other places and times where to fish.
-Our variables of interests intend to caputre these possible reactions.
+Our variables of interests intend to capture these possible reactions.
 
@@
 $$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
 $$
@@
 $\alpha$ is the standard intercept, $\beta_1$ captures the temporal trend change, $\beta_2$ captures the difference between treated and control groups, and $\beta_3$ is our parameter of interest: de DiD estimate capturing the treatment effect.
-Finally, $\phi_t$ and $\gamma_i$ represent month-, and flag-level dummies that account for seasonality or country-level management interventions\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
+Finally, $\phi_t$ and $\gamma_i$ represent month- and flag-level dummies that account for seasonality or country-level management interventions.
+$\theta_t$ are dummies to account for the addition of more satellites.
+\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
 
@@
 In the case of purse seining in the PNA, vessels purchase access to the fishery at the beginning of the season.
-If a vessel decides to fish within the PNA, they've already made the decission to pay for access, expecting higher returns from fishing there than in the High Seas.
+If a vessel decides to fish within the PNA, they've already made the decision to pay for access, expecting higher returns from fishing there than in the High Seas.
 In the particular case of PIPA, one would expect that a vessel holding a permit to fish in I-Kiribati waters would then move to other fishing grounds within Kiribati after the closure.
-Alternatively, if a vessel fishes illegaly in I-Kiribati waters before the implementation, one would expect them to reallocate to other regions with equal or less enforcement.
+Alternatively, if a vessel fishes illegally in I-Kiribati waters before the implementation, one would expect them to reallocate to other regions with equal or less enforcement.
 In this case, they might then choose to move to other I-Kiribati waters, waters of countries that have similar enforcement levels, or the High Seas.
 
-We discretize spatial units by using a polygon for PIPA \footnote{we would expect to see a decrease here} and distinct spatial units for each EEZ of each country.
-Some vessels might shift from EEZs into the high seas, but we are interested in knowing *where* in the high seas, so we incorporate additional regions by using a 1 degree buffer of the high seas arround each of the EEZ regions.
+We discretize spatial units by using a polygon for PIPA\footnote{we would expect to see a decrease here} and distinct spatial units for each EEZ of each country.
+Some vessels might shift from EEZs into the high seas, but we are interested in knowing *where* in the high seas, so we incorporate additional regions by using a 1 degree buffer of the high seas around each of the EEZ regions.
 The rest of the high seas are merged into a single spatial unit.
-For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZs, three 1-degree buffers of high seas arround each EEZs, and the rest of the high seas.
-Whenever the buffers overlapped between themselves, we randocmply clipped one on to the other.
-EEZs that had sporadic fishing events were pooled into a group of "others".
+For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZs, three 1-degree buffers of high seas around each EEZs, and the rest of the high seas.
+Whenever the buffers overlapped between themselves, we randomly clipped one on to the other.
 
-To evaluate this change in effort allocation, we regress our variable of interest (*i.e.* fishing hours) on the interaction between a dummy variable indicating the policy intervention and a dummy variable for countries.
-This gives us the by-country change in proportional allocation of fishing effort:
+We then take this spatial polygons and rasterize them to a 1-degree grid (See Figure \ref{fig:raster_rgn}), which we then use to rasterize points of fishing activity.
+For each cell, we calculate the total monthly fishing hours by treated and control vessels (See Figure \ref{fig:fishing_raster}).
+Since we are interested in the redistribution of fishing effort, we use this gridded data to  calculate the proportion of fishing hours that each region receives each month relative to the total fishing hours observed across all regions and all cells in that month.
+
+We use this measure to evaluate the change in effort allocation by regressing it on the interaction between a year dummy and a dummy for regions:
 
 $$
-y_{i,t} = \alpha + \beta_1Post + \beta_{2,i}Country + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
 $$
 
-Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that country $i$ receives at time $t$.
-$Post$ also represents a policy dummy that takes the value of 0 for all dates before implementation of PIPA, and 1 otherwise.
-$Country$ is a dummy variable for countries for the spatial units defined above.
-Our parameter of interest is $\beta_{1,i}$, which captures the country-level change in proportional fishing effort.
-
-<!-- Like before, we include a dummy variable for months and allow for a second degree polynomial trend through time. -->
+Our variable of interest, $y_{i,t}$ represents the proportion of fishing hours that region $i$ receives at time $t$.
+Years are modelled as factors ($Year_t$), using 2012 as the reference level.
+$Region$ is a dummy variable for regions defined above.
+Our parameter of interest is $\beta_{3,i}$, which captures the yearly by-country change in proportional allocation of fishing effort relative to 2012.
 
@@
 
+<!-- ## Effort displacement and redistribution -->
+
 ```{r}
-ba_disp <- displacement_data %>% 
-  filter(gear == "purse_seines") %>% 
-  group_by(country, post) %>% 
-  summarize(h_prop_m = mean(h_prop)) %>% 
-  spread(post, h_prop_m) %>% 
-  mutate(change = (`TRUE` - `FALSE`) * 100) %>% 
-  select(country, change)
+# Monthly  for analyses
+raster_month_region <- readRDS(file = here::here("data", "monthly_rasterized_effort_by_region.rds"))
 
-knitr::kable(x = ba_disp,
-             digits = 2,
-             booktabs = T,
-             caption = "\\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.") %>%
-  kableExtra::kable_styling(latex_options = "HOLD_position")
+# Yearly for visualization purposes
+fishing_raster <- readRDS(file = here::here("data", "rasterized_effort_by_region.rds"))
+
+redistribution_model_data <-
+  expand.grid(id = unique(raster_month_region$id),
+              year = 2012:2017,
+              month = 1:12) %>% 
+  arrange(id, year, month) %>%
+  as.tibble() %>%
+  left_join(raster_month_region, by = c("id", "year", "month")) %>% 
+  group_by(year, month) %>% 
+  mutate(total_hours = sum(hours, na.rm = t)) %>% 
+  ungroup() %>% 
+  group_by(year, month, id, total_hours) %>%
+  summarize(h = sum(hours, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(h_prop = h / total_hours) %>% 
+  mutate(h_prop = ifelse(is.na(h_prop), 0, h_prop)) %>% 
+  mutate(date = lubridate::date(paste(year, month, 1, sep = "/")),
+         post = year >= 2015,
+         sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                          date > lubridate::date("2015/12/31") ~ "3"),
+         year_c = as.factor(year))
+
+model <- lm(h_prop ~ year_c * id, data = redistribution_model_data)
 ```
@@
 
-Our DiD analysis shows an overall increase in purse seine fishing hours, even after accounting for the introduction of new satellites (Table \ref{tab:did}).
-This coefficient estimate is consistent for different model specifications and across groups of treatment and controls.
-These effectively represent the patterns observed in Figure \ref{fig:all_vessels}.
-The $\beta_3$ coefficient indicating our treatment effect suggests that, relative to the control, treated vessels fish less, in the order of 0.5 hours per day.
-Another way to interpret this is that the increase in fishing effort by treated vessels has ocurred at a lower rate than control vessels.
-This result is robust and significant ($p < 0.05$) for all model specifications using our main control group, with the effect varying between $\beta_3 = -0.515$ and $\beta_3 = -0.934$.
-These values are equivalent to a 15 - 28 reduction in fishing hours per month.
-
 Regressions coefficients for our DiD analysis are shown in Table \ref{tab:did}.
@@
 Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
-Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
-It must be noted, however, that when reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change (Figures \ref{fig:q1}-\ref{fig:ym4}).
+Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag fixed-effects to avoid perfect colinearity between Japanese flag and control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
+Our DiD analysis shows an overall increase in purse seine fishing hours, even after accounting for the introduction of new satellites (Table \ref{tab:did}).
+This coefficient estimate is consistent for different model specifications and across groups of treatment and controls, and effectively represents the patterns observed in Figure \ref{fig:all_vessels}.
+
+The $\beta_3$ coefficient indicating our treatment effect suggests that, relative to the control, treated vessels fish less, in the order of 0.5 hours per day.
+Another way to interpret this is that the increase in fishing effort by treated vessels has occurred at a lower rate than control vessels.
+The effect varying between $\beta_3 = -0.515$ and $\beta_3 = -0.934$.
+These values are equivalent to a 15 - 28 reduction in fishing hours per month.
+However, this result is only robust and significant ($p < 0.01$) in the simplest specification of the Diff-in-Diff.
+When reducing the linear structure of the $Pre \times Post$ design and instead interacting the treatment dummy with quarterly or year-month combinations we are not able to reject the null hypotheses of no change, suggesting that the total fishing hours remains similar for the displaced vessels (Figs.
+\ref{fig:q1}-\ref{fig:ym4}).
+Since vessels don't seem to be fishing less (or at least not much less), an obvious question arises: where are they fishing now?
+
+Figure \ref{fig:fishing_raster} provides a spatial representation of these changes.
+Note that 2013 effort distribution is roughly similar across vessels.
+Then in 2014 there is a sharp increase in fishing hours by treated vessels inside PIPA (blue paradox).
+In 2015 treated vessels then allocate more effort to the easternmost Kiribati EEZ (see Figure \label{fig:PNA_map}) and the high seas.
+In 2016 spatial distribution of fishing effort is again similar across groups.
+It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA.
+
+Along a similar line, Figure \ref{fig:redist_trend} shows a detailed temporal evolution of the relative allocation of fishing effort\footnote{Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.}.
+It shows shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
+I-Kiribati waters in KIR 1 and KIR 2 show an increase in fishing effort for 2015; the same pattern is observed for their respective High Seas buffers, and the general High Seas.
+Other regions farther away from PIPA don't show a clear pattern under visual inspection.
+
+We then move on to our regression results, presented as a figure showing the year-region interaction coefficient estimates for each region as a stream of changes through time (Fig.
+\ref{fig:mean_change} and Table \ref{tab:mean_change}).
+As noted before, the marginal change in the relative allocation of fishing effort relative to 2012 increases in 2014 for PIPA.
+Most coefficients are not statistically significant, but follow the same trends previously discussed, with a tendency for regions closer to PIPA to show an increase in the relative allocation of fishing effort in the post-implementation period.
+The largest increase is observed for the I-Kiribati EEZ 2, where the redistribution of treated vessels caused a 15\% increase in the *relative* allocation of fishing effort within I-Kiribati waters.
+This displacement is likely causing a crowding effect after PIPA-fishing vessels redistribute to other areas.
+
+We use the rasterized effort to evaluate if the PIPA closure increased crowdness otuside the LSMPA.
+We count the number of raster cells that had both treated and control vessels each year (Fig.
+\ref{fig:sp_corr}A).
+The pattern observed here could just be an artifact of satellite detections increasing though time.
+Thereforem we also calculate a spatial correlation of presence/absence and observe similar patterns (Fig.
+\ref{fig:sp_corr}B).
+While this are at the year level and cannot assure that vessels were in effect at the same time in the same vessel, it provides an accurate depiction of what we would expect to find if our claims of displacement are true.
+Spatial overlap increases in 2015 as vessels from PIPA are excluded, and that measure slowly returns to its previous state.
 
@@
 The other red and blue lines show monthly avarages.
-Vertical dashed line indicates PIPA closure."}
+Vertical dashed lines indicates dates when satellites were added, solid line indicates PIPA closurePIPA closure."}
 effort_by_vessel %>% 
@@
   scale_color_brewer(palette = "Set1") +
-  geom_vline(xintercept = lubridate::date(paste(2015, 01, 01, sep = "/")), linetype = "dashed")
+  geom_vline(xintercept = lubridate::date("2015/01/01")) +
+  geom_vline(xintercept = lubridate::date("2014/06/01"), linetype = "dashed") +
+  geom_vline(xintercept = lubridate::date("2015/12/31"), linetype = "dashed")
 ```
@@
 ```{r, results = "asis"}
+# Presenting results for change in behavior. (This should be the year-month ones?)
 
@@
 
-<!-- ## Effort displacement and redistribution -->
-
-Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.
-Figure \ref{fig:fishing_raster} provides a spatial representation of these changes.
-Note that 2013 effort distribution is roughly similar across vessels.
-Then in 2014 there is a sharp increase in fishing hours by treated vessels inside PIPA (blue paradox).
-In 2015 treated vessels then allocate more effort to the easternmost Kiribati EEZ (see Figure \label{fig:PNA_map}) and the high seas.
-In 2016 spatial distribution of fishing effort is again similar across groups.
-It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA, and.
-
-For our empirical identification we ...
-The XXX shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.
-The change in the relative allocation of fishing effort by purse seiners increases for most regions after PIPA implementation (Table \ref{tab:disp_mod}, \ref{fig:mean_change}).
-The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*).
-In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters.
-The only decrease is observed for Papua New Guinea, but the coefficient is not significant.
-
 ```{r, fig.width = 7.5, fig.height = 9, fig.cap = "\\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels.
 Colors have been adjusted relative to the maximum observed by group and year.
-"}
+Red polygons show LGMPAs in the region.
+For visualization purpose sonly some years are presented, the full 2012 - 2017 period is shown in Figure \\ref{fig:fishing_raster_full}."}
 mpas_WCPO <- mpas %>% 
   filter(wdpaid %in% c(309888, 400011))
-
-fishing_raster <- readRDS(file = here::here("data", "rasterized_effort_by_region.rds"))
 
@@
 
-```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'.", eval = T}
-displacement_data %>% 
-  filter(gear == "purse_seines",
-         h_prop > 0) %>%
-  ggplot(aes(x = date, y = h_prop, group = post, color = post)) +
-  geom_point() +
-  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
-  scale_fill_brewer(palette = "Paired") +
+```{r, fig.cap = "\\label{fig:redist_trend}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA by region.
+Colors indicate the pre-post period.
+Solid line across points shows local mean with a region-specific loess smoother.
+Vertical dashed lines indicates dates when satellites were added, solid line indicates PIPA closurePIPA closure.
+Note that inflection points of the loess smoother are not affected by the addition of satellites.", eval = T, fig.height = 5, fig.widht = 6}
+terms_order <- c("PIPA PIPA 1", "EEZ KIR 1", "EEZ KIR 2", "EEZ KIR 3", "HS KIR 1", "HS KIR 2", "HS KIR 3", "HS HS 1")
+
+redistribution_model_data %>% 
+  mutate(id = fct_relevel(id, terms_order)) %>%
+  ggplot(aes(x = date, y = h_prop)) +
+  geom_point(aes(color = post)) +
+  scale_color_brewer(palette = "Set1") +
+  geom_smooth(method = "loess", color = "black") +
+  geom_vline(xintercept = lubridate::date("2015/01/01")) +
+  geom_vline(xintercept = lubridate::date("2014/06/01"), linetype = "dashed") +
+  geom_vline(xintercept = lubridate::date("2015/12/31"), linetype = "dashed") +
   ggtheme_plot() +
-  facet_wrap(~country, scales = "free_y") +
-  scale_color_brewer(palette = "Set1")
+  facet_wrap(~id, scales = "free_y") +
+  theme(legend.position = "none")
 ```
 
-```{r, fig.cap = "\\label{fig:mean_change}"}
-raster_month_region <- readRDS(file = here::here("data", "monthly_rasterized_effort_by_region.rds"))
-
-model <- lm(hours ~ year_c * id, data = raster_month_region)
-
-pd <- position_dodge(width = 0.2)
+```{r, fig.cap = "\\label{fig:mean_change}Coefficient estimates for the redistribution regression.
+Each pannel shows the region-specific coefficients, with heteroskedastick-robust standard errors as error bars.
+The horizontal dashed line represents 0 chenge relative to the 2012 region-specific levels."}
 
@@
          term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
-         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05")) %>%
-  ggplot(aes(x = year, y = est, color = term)) +
-  geom_errorbar(aes(ymin = est - se, ymax = est + se), width = 0, position = pd, size = 1) +
-  geom_point(aes(shape = p), size = 2, position = pd) +
+         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05"),
+         term = str_replace(term, "id", ""),
+         term = fct_relevel(term, terms_order)) %>%
+  ggplot(aes(x = year, y = est, color = p, group = term)) +
+  geom_errorbar(aes(ymin = est - se, ymax = est + se), width = 0, size = 1) +
+  geom_line(color = "black") +
+  geom_point(size = 2) +
   geom_hline(yintercept = 0, linetype = "dashed") +
   ggtheme_plot() +
-  guides(color = guide_legend(ncol = 2, order = 2),
-         shape = guide_legend(order = 1))
+  theme(legend.justification = c(0, 0.3),
+        legend.position = c(0.8, 0)) +
+  guides(color = guide_legend(title = "p-value")) +
+  facet_wrap(~term, scales = "free_y") +
+  scale_color_brewer(palette = "Set1")
+```
+
+```{r}
+commarobust::commarobust_tidy(model) %>%
+  filter(str_detect(term, ":")) %>%
+  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
+         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
+         term = str_replace(term, "id", ""),
+         term = fct_relevel(term, terms_order)) %>% 
+  mutate(est = formatC(est, digits = 3, format = "f"),
+         se = formatC(se, digits = 3, format = "f"),
+         p1 = ifelse(p < 0.1, "*", ""),
+         p2 = ifelse(p < 0.05, "*", ""),
+         p3 = ifelse(p < 0.01, "*", ""),
+         p = paste0(p1, p2, p3),
+         est = paste0(est, " (", se, ")", p)) %>% 
+  select(year, term, est) %>% 
+  spread(year, est) %>% 
+  knitr::kable(format = "latex",
+               caption = "\\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
+Each row represents a region, each color a year.
+Numbers in parentheses are heteroskedatic-robust standard errors.
+R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001).
+* < 0.1; ** p < 0.05; ***p < 0.01.",
+               booktabs = T)
+```
+
+```{r, fig.cap = "\\label{fig:sp_corr}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B)."}
+files <- list.files(path = here::here("data", "spatial", "yearly_rasterized_effort_by_region"))
+rs <- stack(here::here("data", "spatial", "yearly_rasterized_effort_by_region", files))
+
+corr <- raster::as.data.frame(rs, xy = T) %>%
+  gather(group, hours, -c(x, y)) %>%
+  mutate(year = as.numeric(str_extract(group, "[:digit:]+")),
+         group = str_replace_all(group, "_[:digit:]+", ""),
+         hours = ifelse(hours > 0, 1, 0)) %>%
+  spread(group, hours, fill = 0) %>% 
+  mutate(both = (Control > 0 & Treated > 0) * 1,
+         post = year > 2014)
+
+n_both <- corr %>%
+  filter(both > 0) %>% 
+  group_by(year, post) %>% 
+  summarize(n = sum(both)) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = year, y = n)) +
+  geom_line() +
+  geom_point(aes(color = post), size = 4) +
+  scale_color_brewer(palette = "Set1") +
+  ggtheme_plot() +
+  theme(legend.position = "none")
+
+corr_both <- corr %>%
+  drop_na() %>%
+  group_by(year, post) %>%
+  summarize(cor = cor(Control, Treated)) %>% 
+  ggplot(aes(x = year, y = cor)) +
+  geom_line() +
+  geom_point(aes(color = post), size = 4) +
+  scale_color_brewer(palette = "Set1") +
+  ggtheme_plot() +
+  theme(legend.position = c(0.2, 0.8))
+
+cowplot::plot_grid(n_both, corr_both, ncol = 2, labels = "AUTO")
 ```
@@
 Our findings provide interesting insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
-These collection of results shows that the implementation of PIPA caused treated vessels to reduce their fishing hours, and that this effect is greater for purse seiners than longliners.
-Even though treated vessels fish less, their relative allocation of fishing hours increased for all other fishing grounds.
+These collection of results show that the implementation of PIPA had little effect on the effort exerted by purse seiners.
+However, regions adjacent to PIPA show an increase in the relative amount of fishing effort, suggesting that effort is simply redisplaced to closeby areas.
 This does not imply that there is more fishing effort exerted by treated vessels, but rather that each region receives a greater portion of the post-PIPA fishing effort of these same vessels, which is lower than pre-PIPA levels.
+Additionally, we show that post-PIPA there is a concentration of effort leading to crowding.
 In this section we discuss the implications of vessel-level reductions in fishing effort and the increase in relative allocation of the remaining effort through space.
 We also provide plausible explanations as to why purse seiners seem to be more reactive to the spatial closure.
-
-A major shortcoming of our analyses is that we do not observe catches or revenues, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
-Therefore, it is difficult to know whether the reduction in fishing effort represents a positive or negative impact.
-A decrease in fishing effort is associated to an increase in catches (and therefore greater CPUE) only when the entire fleet does it, and if previous levels of effort were greater than $F_{MEY}$ (*i.e.* the effort that would yield the maximum economic yield).
-Therefore, it is plausible that the reduction of fishing hours is not done by choice, but rather results from fishers having to increase search time.
-Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch.
-Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours.
-
-<!-- **We should have a discussion (over the phone and in the paper) about whether a decrease in fishing hours represents a positive or negative impact of PIPA.
-Without data on catch it might be hard to really know.** -->
 
@@
 Recent work by \citet{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space.
-Our data is assembled in a similar way, with fishing positions before and after the implementation of PIPA and vessels grouped into treated and control groups.
-Our BACI design, along with our difference-in-differences analysis allows us to make causal inferences about the effect that large scale marine protected areas have on fishing effort.
+Our data, which is assembled in a similar way, allows us to make similar inferences about the unobserved change in aggregate fishing effort and its spatial redistribution.
 
-The different responses observed between purse seiners and longliners might have two possible explanations.
-It is likely that PIPA did not contain habitat that longliners would consider optimal.
-Therefore, the sporadic fishing events that occurred there are of little importance to the fleet, and it is unlikely that the implementation of PIPA has an effect on them.
-Alternatively, the differences may be due to the nature of each fishing gear.
-Purse seiners are often constrained by seafloor and termocline depth, and have a smaller spatial footprint \citep{kroodsma_2018}.
-Tuna purse seiners are known to have greater proportion of null sets (*i.e.* where purse seines effectively cast their nets, but no catch is obtained) during El Niño years, where the termocline deepens in the Eastern Pacific \citep{dreyfusleon_2015}.
-On the other hand, longliners may be more flexible as to where they can deploy their longlines.
-\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be under-utilizing the ocean, meaning that they can easily redistribute elsewhere.
+The role of the institutions at play is evident.
+Vessels that fished inside PIPA before the implementation were, ultimately, fishing in I-Kiribati waters likely under a VDS license.
+Uppon the implementation, some of these redistribute to other areas of the I-Kiribat EEZ and the high seas for the year immediately after the closure.
+As stated before, it is reasonable for a vessel holding a license to fish in I-Kiribati waters to simply reallocate their effor to other parts of that EEZ.
+However, the shift to the high seas may not follow the same logic.
+Instead, it is possible that vessels that redistribute to the high seas were opperating in I-Kiribati illegally, and decide to reallocate in the high seas to continue fishing without a license.
+These patterns provide us with interesting insight sinto fishing behavior, which may become useful in tackling Illegal, Unreported and Unregulted (IUU) fisheries.
 
-Our work suggests that the implementation of LSMPAs can have important implications for purse seiners, and less so for longliners.
-We also show that fishing effort is redistributed to areas close by.
-Future management interventions that aim to close large portion of the oceans should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
+A major shortcoming of our analyses is that we do not observe catches or revenues, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
+Therefore, it is difficult to know whether lack of change in fishing hours represents a positive or negative impact.
+An additional thing that we are yet to test is the changes in non-fishing hours sepnt at sea.
+It is plausible that fishing hours remain constant, but vessels have to increase search time.
+Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch.
+Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours.
+However, the widespread footprint of the treated fleet may suggest that they are well aqquainted with the region (See Fig.
+\ref{fig:fishing_raster}), and its unlikely that they would need to learn or identify new fishing grounds.
 
-Furthermore, a growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+<!-- Our analyses suggest that treated vessels dont change their fishing effort, and that the aggregate levels of fishing effort remains unchanged.
+Instead, we show that PIPA simply redistributed fishing effort to other areas inside the I-Kiribati EEZ and the high seas.
+While this implies that  PIPA failed to reduce total fishing effort, this LSMPA may still produce significant ecological benefits for unexploited and by-caught species that live there.
+-->
+
+Our work suggests that the implementation of LSMPAs has little impact on purse seiners fishng effort.
+We also show that fishing effort is redistributed to areas close by, and that this leads to a potentially negative crowding effect.
+A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness.
+
+<!-- \citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic longline fleet, and suggest that the fleet may be under-utilizing the ocean, meaning that they can easily redistribute elsewhere.
+-->
 
@@
 
-\clearpage
+# Further work
 
-<div id = "refs"></div>
+- Distance traveled
+- Non-fishing hours at sea
+- Monthly crowdnes??
+- Repeat raster exercise for Revillagigedo and other recently implemented LSMPAs.
+It would be great to have a pannel figure of 3 or 4 other LSMPAs that show wher effort was and where it went to generalize our results.
+- John talked about this being relevant to Palau (their upcoming LSMPA). We might want to talk about where the vessels that are there would go.
+
+\bibliography{references.bib}
 
@@
 
+\clearpage
+
 ### Quarterly DID interactions
@@
 
+## Effort redistribution
+
+## Rasterized regions
+
+```{r, fig.cap = "\\label{fig:raster_rgn}Rasterized regions. Each color (number) indicates a distinct region."}
+raster::raster(here::here("data", "spatial", "regions_raster.tif")) %>% 
+  raster::as.data.frame(xy = T) %>% 
+  ggplot() +
+  geom_raster(aes(x = x, y = y, fill = regions_raster)) +
+  ggtheme_map() +
+  geom_sf(data = eez, fill = "transparent", color = "black") +
+  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
+  geom_sf(data = small_coast, color = "black")
+```
+
 ### Fishing raster
 
-```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}"}
+```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}Yearly rasters of fishing hours for each group."}
 ggplot() +
@@
   # coord_equal() +
-  ggtheme_map() +
-  theme(legend.position = "bottom")
+  ggtheme_map()
 ```

### 2018-10-21 docs/Manuscript.tex
Updated manuscritp, sent to John

@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:LSMPAs_map}Large Scale
-Marine Protected Areas. The map shows all areas larger than 250,000
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
+Protected Areas. The map shows all areas larger than 250,000
 Km\textsuperscript{2}. Areas in dark blue meet at least one of these
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\label{fig:unnamed-chunk-14}\label{fig:PNA_map}Map of the Exclusive
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
 Economic Zones (EEZs) of the region of interest. Countries that belong
@@
 
-\caption{\label{tab:unnamed-chunk-17}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
+\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
 \centering
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:all_vessels}Fishing hours
-and number of vessels by month for all vessels. Vertical dashed lines
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
+number of vessels by month for all vessels. Vertical dashed lines
 indicates dates when satellites were added, solid line indicates PIPA
@@
 We use daily fishing hours, daily proportion of fishing vs.~non-fishing
-hours, and daily distance traveled (km). We compare our variable of
-interest before and after the implementation of PIPA using a
-Difference-in-Differences approach, where we track the variable of
-interest for vessels described in the previous section. Our
+hours, daily distance traveled (km), distance from shore (km) and
+distance from
+port(km)\footnote{Results are presented for fishing hours, bur preliminary results for distance form shore and distance from port are shown in Tables \ref{tab:dist_shore} and \ref{tab:dist_port}}.
+We compare our variable of interest before and after the implementation
+of PIPA using a Difference-in-Differences approach, where we track the
+variable of interest for vessels described in the previous section. Our
 specification is the following:
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\caption{\label{fig:unnamed-chunk-21}\label{fig:all_vessels}Daily fishing
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
 hours for all vessels in our main treatment-control groups. Solid
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\caption{\label{fig:unnamed-chunk-23}\label{fig:long}Coefficient estimates
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
 for each model. Top pannel indicates variable, x-axis represents model
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-\caption{\label{fig:unnamed-chunk-24}\label{fig:fishing_raster}Yearly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
 spatial distribution of fishing effort by treated and control vessels.
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:redist_trend}Monthly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-\caption{\label{fig:unnamed-chunk-26}\label{fig:mean_change}Coefficient
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}Coefficient
 estimates for the redistribution regression. Each pannel shows the
@@
 
-\caption{\label{tab:unnamed-chunk-27}\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
+\caption{\label{tab:unnamed-chunk-16}\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
 Each row represents a region, each color a year.
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
-\caption{\label{fig:unnamed-chunk-28}\label{fig:sp_corr}Number of cells that
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\label{fig:unnamed-chunk-17}\label{fig:sp_corr}Number of cells that
 had treated and control vessels (A) and spatial correlation in the
@@
 \item
-  Monthly crowdnes??
+  Monthly crowdnes (same approach as now, but monthly instead of yearly)
+\item
+  Number of vessels per cell as another measure of crowdness (this is a
+  more real one)
 \item
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
-\caption{\label{fig:unnamed-chunk-29}\label{fig:baci_strict}Stream of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
 fishing events by vessels through time. Each line represents a vessel,
@@
 
-\hypertarget{other-model-specifications-for-purse-seiners}{%
-\subsection{Other model specifications for purse
-seiners}\label{other-model-specifications-for-purse-seiners}}
-
-We include a second degree polynomial for years as:
-
-\[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
-\]
-
-\textbackslash{}begin\{table\}{[}!htbp{]} \centering 
-\textbackslash{}caption\{\label{tab:purse}Fishing hours from GFW for
-purse\_seiners. Asterisks indicate significance levels. Numbers in
-parentheses represent heteroskedastic-robust standard errors.\} \label{}
-
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
-  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
-  & & & & \\ 
- treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
-  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
-  & & & & \\ 
- post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
-  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
-  & & & & \\ 
- Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
-  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & No & Yes & Yes & Yes \\ 
-Year FE & No & No & Yes & Yes \\ 
-Flag FE & No & No & No & Yes \\ 
-Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
-R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular}
-
-\textbackslash{}end\{table\}
-
-\clearpage
-
 \hypertarget{quarterly-did-interactions}{%
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-33-1.pdf}
-\caption{\label{fig:unnamed-chunk-33}\label{fig:q1}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
+\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
 and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-34-1.pdf}
-\caption{\label{fig:unnamed-chunk-34}\label{fig:q2}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
 and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
-\caption{\label{fig:unnamed-chunk-35}\label{fig:q3}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
+\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
 and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
-\caption{\label{fig:unnamed-chunk-36}\label{fig:q4}Interaction of quarters
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
 and treatment. Control group is japanese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
-\caption{\label{fig:unnamed-chunk-37}\label{fig:ym1}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
 year-month and treatment. Control group is all vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
-\caption{\label{fig:unnamed-chunk-38}\label{fig:ym2}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
 year-month and treatment. Control group is vessels from PNA.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-39-1.pdf}
-\caption{\label{fig:unnamed-chunk-39}\label{fig:ym3}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
+\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
 year-month and treatment. Control group excludes Chinese vessels.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-40-1.pdf}
-\caption{\label{fig:unnamed-chunk-40}\label{fig:ym4}Interaction of
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
 year-month and treatment. Control group is japanese vessels.}
 \end{figure}
+
+\hypertarget{other-measures-of-change-in-behavior}{%
+\subsection{Other measures of change in
+behavior}\label{other-measures-of-change-in-behavior}}
+
+Global Fishing Watch data includes two variables of interest that are
+readily available: distance from shore and distance from port. We use
+these as variables of interest and perform the following regression:
+
+\[
+y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
+\]
+
+Where \(y\) is our variable of interest, \(Year\) represent year
+dummies, with 2012 as the reference level, and \(Treated\) indicates
+wether a vessel belongs to the treated or control group.
+
+\clearpage
+
+\hypertarget{distance-from-shore}{%
+\subsubsection{Distance from shore}\label{distance-from-shore}}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & distance\_from\_shore \\ 
+\hline \\[-1.8ex] 
+ Constant & 233,057.900$^{***}$ \\ 
+  & (1,558.294) \\ 
+  & \\ 
+ year\_c2013 & $-$818.044 \\ 
+  & (2,623.263) \\ 
+  & \\ 
+ year\_c2014 & 14,220.260$^{***}$ \\ 
+  & (1,701.637) \\ 
+  & \\ 
+ year\_c2015 & 140,980.200$^{***}$ \\ 
+  & (1,668.140) \\ 
+  & \\ 
+ year\_c2016 & 32,557.750$^{***}$ \\ 
+  & (1,584.182) \\ 
+  & \\ 
+ year\_c2017 & 168,283.100$^{***}$ \\ 
+  & (1,653.912) \\ 
+  & \\ 
+ treated & $-$11,371.280$^{***}$ \\ 
+  & (1,688.879) \\ 
+  & \\ 
+ year\_c2013:treated & 62,899.900$^{***}$ \\ 
+  & (3,274.205) \\ 
+  & \\ 
+ year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
+  & (1,834.090) \\ 
+  & \\ 
+ year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
+  & (1,821.587) \\ 
+  & \\ 
+ year\_c2016:treated & 72,512.980$^{***}$ \\ 
+  & (1,739.976) \\ 
+  & \\ 
+ year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
+  & (1,805.322) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 4,937,666 \\ 
+R$^{2}$ & 0.032 \\ 
+Adjusted R$^{2}$ & 0.032 \\ 
+Residual Std. Error & 297,128.600 (df = 4937654) \\ 
+F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+TRUE \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+TRUE \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+\clearpage
+
+\hypertarget{distance-from-ports}{%
+\subsubsection{Distance from ports}\label{distance-from-ports}}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_port}Regression results for distance from shore} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & distance\_from\_port \\ 
+\hline \\[-1.8ex] 
+ Constant & 362.707$^{***}$ \\ 
+  & (1.971) \\ 
+  & \\ 
+ year\_c2013 & 9.082$^{***}$ \\ 
+  & (3.198) \\ 
+  & \\ 
+ year\_c2014 & 105.414$^{***}$ \\ 
+  & (2.148) \\ 
+  & \\ 
+ year\_c2015 & 357.746$^{***}$ \\ 
+  & (2.113) \\ 
+  & \\ 
+ year\_c2016 & 112.441$^{***}$ \\ 
+  & (2.009) \\ 
+  & \\ 
+ year\_c2017 & 356.506$^{***}$ \\ 
+  & (2.099) \\ 
+  & \\ 
+ treated & 149.653$^{***}$ \\ 
+  & (2.249) \\ 
+  & \\ 
+ year\_c2013:treated & 26.366$^{***}$ \\ 
+  & (4.125) \\ 
+  & \\ 
+ year\_c2014:treated & 50.808$^{***}$ \\ 
+  & (2.453) \\ 
+  & \\ 
+ year\_c2015:treated & $-$151.268$^{***}$ \\ 
+  & (2.422) \\ 
+  & \\ 
+ year\_c2016:treated & $-$49.445$^{***}$ \\ 
+  & (2.311) \\ 
+  & \\ 
+ year\_c2017:treated & $-$252.334$^{***}$ \\ 
+  & (2.390) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 4,937,666 \\ 
+R$^{2}$ & 0.047 \\ 
+Adjusted R$^{2}$ & 0.047 \\ 
+Residual Std. Error & 391.757 (df = 4937654) \\ 
+F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_port}Regression results for distance from shore} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+TRUE \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:dist_port}Regression results for distance from shore} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+TRUE \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
 
@@
 \hypertarget{rasterized-regions}{%
-\subsection{Rasterized regions}\label{rasterized-regions}}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-41-1.pdf}
-\caption{\label{fig:unnamed-chunk-41}\label{fig:raster_rgn}Rasterized
+\subsubsection{Rasterized regions}\label{rasterized-regions}}
+
+\begin{figure}
+\centering
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
+\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
 regions. Each color (number) indicates a distinct region.}
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-42-1.pdf}
-\caption{\label{fig:unnamed-chunk-42}\label{fig:fishing_raster_full}Yearly
+\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
+\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
 rasters of fishing hours for each group.}

### 2018-10-21 rmd/Manuscript.Rmd
Updated manuscritp, sent to John

@@
 We use daily fishing hours, daily proportion of fishing vs.
-non-fishing hours, and daily distance traveled (km).
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from port(km)\footnote{Results are presented for fishing hours, bur preliminary results for distance form shore and distance from port are shown in Tables \ref{tab:dist_shore} and \ref{tab:dist_port}}.
 We compare our variable of interest before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels described in the previous section.
@@
 - Non-fishing hours at sea
-- Monthly crowdnes??
+- Monthly crowdnes (same approach as now, but monthly instead of yearly)
+- Number of vessels per cell as another measure of crowdness (this is a more real one)
 - Repeat raster exercise for Revillagigedo and other recently implemented LSMPAs.
@@
 
-## Other model specifications for purse seiners
-
-We include a second degree polynomial for years as:
-
-$$
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \omega Y_t + \Omega Y_t^2 + \epsilon_{i,t}
-$$
-
-```{r}
-model_data <- readRDS(file = here::here("data", "effort_by_vessel.rds")) %>%
-  filter(year < 2018,
-         baci_strict,
-         gear == "purse_seines") %>% 
-  mutate(post = post * 1,
-         treated = treated * 1,
-         mmsi_c = as.factor(mmsi))
-
-m1 <- lm(hours ~ post*treated, data = model_data)
-m2 <- lm(hours ~ post*treated + month_c, data = model_data)
-m3 <- lm(hours ~ post*treated + month_c + year_c, data = model_data)
-m4 <- lm(hours ~ post*treated + month_c + year_c + flag, data = model_data)
-```
-
-```{r, results = "asis"}
-models <- list(m1, m2, m3, m4)
-
-stargazer::stargazer(models,
-                     se = commarobust::makerobustseslist(models),
-                     t.auto = T,
-                     p.auto = T,
-                     type = "latex",
-                     omit = c("flag", "year", "month"),
-                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
-                                      c("Year FE", "No", "No", "Yes", "Yes"),
-                                      c("Flag FE", "No", "No", "No", "Yes")),
-                     omit.stat = c("adj.rsq", "f", "ser"),
-                     header = F,
-                     title = "\\label{tab:purse}Fishing hours from GFW for purse_seiners.
-Asterisks indicate significance levels.
-Numbers in parentheses represent heteroskedastic-robust standard errors.")
-```
-
-\clearpage
-
 ### Quarterly DID interactions
@@
 
+## Other measures of change in behavior
+
+Global Fishing Watch data includes two variables of interest that are readily available: distance from shore and distance from port.
+We use these as variables of interest and perform the following regression:
+
+$$
+y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
+$$
+
+Where $y$ is our variable of interest, $Year$ represent year dummies, with 2012 as the reference level, and $Treated$ indicates wether a vessel belongs to the treated or control group.
+
+\clearpage
+
+### Distance from shore
+
+```{r}
+vessel_tracks <- readRDS(file = here::here("raw_data", "vessel_tracks.rds")) %>% 
+  filter(year < 2018,
+         fishing,
+         gear == "purse_seines") %>% 
+  mutate(year_c = as.factor(year))
+
+```
+
+```{r, results = "asis"}
+lm(distance_from_shore ~ year_c * treated, data = vessel_tracks) %>% 
+  stargazer::stargazer(se = commarobust::makerobustseslist(.),
+                       pauto = T,
+                       tauto = T, title = "\\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.",
+                       intercept.bottom = F,
+                       type = "latex",
+                       header = F)
+```
+
+\clearpage
+
+### Distance from ports
+
+```{r, results = "asis"}
+lm(distance_from_port ~ year_c * treated, data = vessel_tracks) %>% 
+  stargazer::stargazer(se = commarobust::makerobustseslist(.),
+                       pauto = T,
+                       tauto = T, title = "\\label{tab:dist_port}Regression results for distance from shore",
+                       intercept.bottom = F,
+                       type = "latex",
+                       header = F)
+```
+
 ## Effort redistribution
 
-## Rasterized regions
+### Rasterized regions
 

### 2019-01-10 rmd/Manuscript.Rmd
Added the monthly crowding to the MS

@@
   John Lynham^2^
-abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years.
+abstract: "The number of Large-scale Marine Protected Areas (LSMPAs) has significantly increased over the last years.
 Fishing effort is effectively eliminated within these protected areas upon implementation.
-The benefits of reducing effort have been largely studied, but little empirical works evaluate what happens to the effort after an MPA is created.
-The economic and ecological implications of displacing fishing effort are not yet fully understood.
-We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to provide the first analyses of behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a Large Scale Marine Protected Area in the Pacific Ocean.
-Our work provides three main findings: 1) aggregate fishing effort remains relatively unaffected; 2) Vessels that fished inside the protected area redistribute to adjacent waters; and 3) We observe a crowding effect for the first years after implementation.
-Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications.
-As countries continue to implement LSMPAs as a way to reach the stated 10% target of ocean protection, managers should consider how fishing effort will change in space and through time to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
-While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize their effectiveness."
+The benefits of reducing fishing mortality within the bounded regions have been largely studied, but little empirical work has evaluated what happens to the effort after an MPA is created.
+The economic and ecological implications of displacing fishing effort as well as the differential responses under different institutional settings are not yet fully understood.
+We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to provide the first analyses of behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of Large Scale Marine Protected Areas that operate under different institutional settings.
+Our work provides three main findings: 1) aggregate fishing effort remains relatively unaffected when effort is not caped; 2) Vessels that fished inside the protected area before its implementation redistribute to adjacent waters, but responses are idiosyncratic; and 3) We observe a crowding effect outside the LSMPA over the first years after implementation.
+Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity but provide insights into vessel redistribution dynamics.
+As countries continue to implement LSMPAs as a way to reach the stated 10% target of ocean protection, managers should consider how existing institutions interact with the creation of an MPA.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompanied with traditional fisheries management to maximize their effectiveness."
 date: "
@@
 Vertical dashed lines indicates dates when satellites were added, solid line indicates PIPA closurePIPA closure.
-Note that inflection points of the loess smoother are not affected by the addition of satellites.", eval = T, fig.height = 5, fig.widht = 6}
+Note that inflection points of the loess smoother are not affected by the addition of satellites.", eval = T, fig.height = 5, fig.width = 6}
 terms_order <- c("PIPA PIPA 1", "EEZ KIR 1", "EEZ KIR 2", "EEZ KIR 3", "HS KIR 1", "HS KIR 2", "HS KIR 3", "HS HS 1")
@@
   scale_color_brewer(palette = "Set1")
+```
+
+```{r, eval = F}
+# Map with color of each shapefile representing the change for 2015
+change_2015_by_region <- commarobust::commarobust_tidy(model) %>%
+  filter(str_detect(term, ":")) %>%
+  mutate(year = as.numeric(str_extract(term, "[:digit:]+")),
+         term = str_extract(term, pattern = "[:alpha:]+ [:alpha:]+ [:digit:]"),
+         p = ifelse(p < 0.05, "p < 0.05", "p > 0.05"),
+         term = str_replace(term, "id", ""),
+         term = fct_relevel(term, terms_order)) %>% 
+  filter(year == 2015) %>%
+  rename(id = term)
+
+eezs_exclude <- c("HS MUS 1", "EEZ MUS 1", "EEZ MDG 1", "EEZ MDG 2", "HS MDG 1", "HS MDG 2", "HS MOZ 1", "EEZ MOZ 1", "EEZ PNG 1", "EEZ PNG 2", "HS PNG 1", "HS PNG 2")
+
+regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
+                   layer = "regions") %>% 
+  filter(!id %in% eezs_exclude) %>%
+  left_join(change_2015_by_region, by = "id")
+
+ggplot() +
+  geom_sf(data = regions, aes(fill = est)) +
+  scale_fill_gradientn(colours = colorRamps::matlab.like(20)) +
+  ggtheme_plot() +
+  guides(fill = guide_colorbar(title = bquote(Delta)))
+
 ```
@@
 ```{r, fig.cap = "\\label{fig:sp_corr}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B)."}
-files <- list.files(path = here::here("data", "spatial", "yearly_rasterized_effort_by_region"))
-rs <- stack(here::here("data", "spatial", "yearly_rasterized_effort_by_region", files))
+files <- list.files(path = here::here("data", "spatial", "monthly_rasterized_effort_by_region"))
+rs <- stack(here::here("data", "spatial", "monthly_rasterized_effort_by_region", files))
 
@@
   gather(group, hours, -c(x, y)) %>%
-  mutate(year = as.numeric(str_extract(group, "[:digit:]+")),
-         group = str_replace_all(group, "_[:digit:]+", ""),
+  mutate(
+    year = as.numeric(
+      str_extract(group, "[:digit:]+")
+    ),
+    month = as.numeric(
+      str_replace_all(
+        str_extract(group, "\\.[:digit:]+\\."),
+        "\\.", "")
+    ),
+    group = str_extract(group, "[:alpha:]+"),
     hours = ifelse(hours > 0, 1, 0)) %>%
@@
   mutate(both = (Control > 0 & Treated > 0) * 1,
-         post = year > 2014)
+         post = year > 2014,
+         date = lubridate::date(paste(year, month, 01, sep = "-")))
 
@@
   filter(both > 0) %>% 
-  group_by(year, post) %>% 
+  group_by(year, month, date, post) %>% 
   summarize(n = sum(both)) %>% 
   ungroup() %>% 
-  ggplot(aes(x = year, y = n)) +
-  geom_line() +
+  ggplot(aes(x = date, y = n)) +
+  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = "black", size = 1) +
   geom_point(aes(color = post), size = 4) +
@@
   drop_na() %>%
-  group_by(year, post) %>%
+  group_by(year, month, date, post) %>%
   summarize(cor = cor(Control, Treated)) %>% 
-  ggplot(aes(x = year, y = cor)) +
-  geom_line() +
+  ggplot(aes(x = date, y = cor)) +
+  geom_vline(xintercept = lubridate::date("2015-01-01"), linetype = "dashed", color = "black", size = 1) +
+  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = "black", size = 1) +
   geom_point(aes(color = post), size = 4) +
@@
   ggtheme_plot() +
-  theme(legend.position = c(0.2, 0.8))
+  theme(legend.position = c(0.1, 0.9))
 
@@
 
-\clearpage
+### Yearly rowding
+
+```{r, fig.cap = "\\label{fig:sp_corry}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B)."}
+files <- list.files(path = here::here("data", "spatial", "yearly_rasterized_effort_by_region"))
+rs <- stack(here::here("data", "spatial", "yearly_rasterized_effort_by_region", files))
+corr <- raster::as.data.frame(rs, xy = T) %>%
+  gather(group, hours, -c(x, y)) %>%
+  mutate(year = as.numeric(str_extract(group, "[:digit:]+")),
+         group = str_replace_all(group, "_[:digit:]+", ""),
+         hours = ifelse(hours > 0, 1, 0)) %>%
+  spread(group, hours, fill = 0) %>% 
+  mutate(both = (Control > 0 & Treated > 0) * 1,
+         post = year > 2014)
+
+n_both <- corr %>%
+  filter(both > 0) %>% 
+  group_by(year, post) %>% 
+  summarize(n = sum(both)) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = year, y = n)) +
+  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = "black", size = 1) +
+  geom_point(aes(color = post), size = 4) +
+  scale_color_brewer(palette = "Set1") +
+  ggtheme_plot() +
+  theme(legend.position = "none")
+
+corr_both <- corr %>%
+  drop_na() %>%
+  group_by(year, post) %>%
+  summarize(cor = cor(Control, Treated)) %>% 
+  ggplot(aes(x = year, y = cor)) +
+  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = "black", size = 1) +
+  geom_point(aes(color = post), size = 4) +
+  scale_color_brewer(palette = "Set1") +
+  ggtheme_plot() +
+  theme(legend.position = c(0.2, 0.9))
+
+cowplot::plot_grid(n_both, corr_both, ncol = 2, labels = "AUTO")
+```

### 2019-01-10 slides/ERE_lunch.Rmd
Updated slides

@@
     slide_level: 2
-    theme: Berkeley
 bibliography: references.bib

### 2019-01-21 docs/TWEEDS_abstract.tex
Added the abstract we sent to TWEEDs

\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}

\title{Large-Scale Marine Protected Areas displace fishing
effort and induce behavioral changes in fishing vessels}

\author{
  Juan CarlosVillase\~{n}or-Derbez\footnote{Bren School of Environmental Science \& Management, University of California Santa Barbara, Santa Barbara, CA} \\
  \texttt{juancarlos@ucsb.edu}
  \and
 John Lynham\footnote{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
  \texttt{lynham@hawaii.edu }
}

\date{}

\begin{document}
\maketitle
\begin{abstract}
Large-scale Marine Protected Areas (LSMPAs) have seen a significant
increase over the last years. Fishing effort is effectively eliminated
within these protected areas upon implementation. The benefits of
reducing effort have been largely studied, but little empirical works
evaluate how vessels react and redistribute after an MPA is created. The
economic and ecological implications of displacing fishing effort are
not yet fully understood. We use identification of fishing activity via
Automatic Identification Systems (AIS) and causal inference techniques
to provide the first analysis of behavioral changes and spatial
redistribution of tuna purse seiners due to the implementation of a
Large Scale Marine Protected Area in the Pacific Ocean. Our work
provides three main findings: 1) aggregate fishing effort remains
relatively unaffected; 2) vessels that fished inside the protected area
redistribute to adjacent waters; and 3) we observe a crowding effect for
the first months after implementation. Our results not only provide an
impact evaluation of the effect of LSMPAs on fishing activity, but
provide insights into vessel redistribution dynamics, which may have
ecological and economic implications for marine conservation and fisheries
management. As countries continue to implement LSMPAs as a way to
reach the stated 10\% target of ocean protection, managers should
consider how fishing effort will change in space and through time to
ensure that fishing effort is not just displaced elsewhere, leading to
overfishing in adjacent waters. While LSMPAs can provide a wide
range of benefits, their implementation must be accompained with
traditional fisheries management to maximize their effectiveness.
\end{abstract}

\end{document}

### 2019-01-21 docs/PIPA_Palau.tex
Added manuscript with comments from John

--- 2018-10-21 docs/Manuscript.tex
@@
-\documentclass[11pt,]{article}
+\documentclass[11pt,english]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
 \fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
 \usepackage[margin=1in]{geometry}
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
+\title{Large Scale Marine Protected Areas}
+
+\author{
+  Juan CarlosVillase\~{n}or-Derbez\footnote{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA} \\
+  \texttt{juancarlos@ucsb.edu}
+  \and
+ John Lynham\footnote{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
+  \texttt{lynham@hawaii.edu }
 }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Displacement of fishing effort by Large Scale Marine Protected
-Areas\footnote{Work in progress, do not circulate}}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \subtitle{Updated on 2018-10-20}
-  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
-Lynham\textsuperscript{2}}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
-University of California Santa Barbara, Santa Barbara,
-CA\newline \textsuperscript{2}Department of Economics, University of
-Hawaii at Manoa, Honolulu, HI}
+
+\date{Updated on: \today}
 
@@
 
+% John's additional packages below
+
+\usepackage{graphicx}
+\graphicspath{{figures/}} %Setting the graphicspath
+
 \begin{document}
@@
 reducing effort have been largely studied, but little empirical works
-evaluate what happens to the effort after an MPA is created. The
+evaluate how vessels react and redistribute after an MPA is created. The
 economic and ecological implications of displacing fishing effort are
@@
 Automatic Identification Systems (AIS) and causal inference techniques
-to provide the first analyses of behavioral changes and spatial
+to provide the first analysis of behavioral changes and spatial
 redistribution of tuna purse seiners due to the implementation of a
@@
 provides three main findings: 1) aggregate fishing effort remains
-relatively unaffected; 2) Vessels that fished inside the protected area
-redistribute to adjacent waters; and 3) We observe a crowding effect for
-the first years after implementation. Our results not only provide an
+relatively unaffected; 2) vessels that fished inside the protected area
+redistribute to adjacent waters; and 3) we observe a crowding effect for
+the first months after implementation. Our results not only provide an
 impact evaluation of the effect of LSMPAs on fishing activity, but
 provide insights into vessel redistribution dynamics, which may have
-ecological and economic implications. As countries continue to implement
-LSMPAs as a way to reach the stated 10\% target of ocean protection,
-managers should consider how fishing effort will change in space and
-through time to ensure that fishing effort is not just displaced
-elsewhere, leading to overfishing in adjacent waters. While LSMPAs can
-provide a wide range of benefits, their implementation must be
-accompained with traditional fisheries management to maximize their
-effectiveness.
+ecological and economic implications for marine conservation and fisheries
+management. As countries continue to implement LSMPAs as a way to
+reach the stated 10\% target of ocean protection, managers should
+consider how fishing effort will change in space and through time to
+ensure that fishing effort is not just displaced elsewhere, leading to
+overfishing in adjacent waters. While LSMPAs can provide a wide
+range of benefits, their implementation must be accompained with
+traditional fisheries management to maximize their effectiveness.
+
+We do not observe an increase in daily fishing hours for vessels that used to fish within PIPA, compared to a control
+group of vessels.
+Thus, for vessels that have chosen to continue to operate following the closure, we do not observe evidence that they are being forced to exert more effort as a result of the closure.
+Unfortunately, without detailed data on vessel catch, we cannot conclude whether vessels are better or worse off financially following the closure.
+
+Our results suggest that PIPA has displaced some vessels to the high seas just outside the EEZ of Kiribati.
+This might imply a drop in demand for Kiribati fishing rights and a decline in revenue.
+We also uncover evidence that there is more congestion immediately following the closure, but this is declining over time.
 \end{abstract}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+Next steps: I think we need to make the buffers around the EEZs 5 degrees instead of 1 degree (redistribution of effort section)
+Might change the specification of the redistribution regression
+
+\section{Introduction}\label{introduction}
 
@@
 ocean from fishing and other extractive activities. Current
-international goals aim to protect 10\% of the ocean environments by
-2020. In an effort to meet this target, the world has seen a rapid
-increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
-a small number of Large Scale Marine Protected Areas (LSMPA)
-\citet{singleton_2014,boonzaier_2016,alger_2017}). Due to weak property
-rights, limited habitat transformation, and potentially lower management
-costs, LSMPAs provide an opportunity to safeguard the oceans
-\citet{game_2009}. Today, a small number of LSMPAs make up at least 80\%
-of the managed areas in the ocean \citet{toonen_2013}. LSMPAs may be
-instrumental in helping us achieve the 10\% target by 2020
-\citep{mccauley_2016}.
+international goals aim to protect 10\% of the ocean environment by
+2020. In an effort to meet this target, there has been a rapid
+increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
+a small number of Large Scale Marine Protected Areas (LSMPAs).\footnote{See, for example, \citet{game_2009},  \citet{singleton_2014},\citet{boonzaier_2016}, \citet{mccauley_2016}, and \citet{alger_2017}.}
+). Today, a small number of LSMPAs make up at least 80\%
+of the managed areas in the ocean \citep{toonen_2013}.
 
@@
 known about their human dimensions and implication for fisheries
-\citep{gray_2017}. As with customary MPAs, it is important that we
+\citep{gray_2017}. As with smaller MPAs, it is important that we
 understand the socioeconomic implications of management interventions.
@@
 MPA \citep{smith_2003}. Theoretical models make different assumptions
-about the way in which fishers will reallocate fishing effort after an
-area closure. The few empirical works focus on small-scale fisheries and
-rarely incorporate spatially explicit data. Despite these efforts,
-marine conservation is yet to identify the response in fishing effort
-and its management implications.
+about the ways in which fishers will reallocate fishing effort after an
+area closure, which often determine whether or not MPAs produce negative or positive impacts on fisheries.
+The existing empirical literature focuses on small MPAs and has been criticized for confounding correlation with causation \citep{ferraro2018causal}.
 
 Recent advances in satellite tracking technologies and near real-time
-identification of fishing activity provide us with an opportunity to
-tackle increase governance and answer long-lasting questions. Here, we
-ask, how do fishers respond to the implementation of LSMPA? After a
-closure, and if they continue to fish, where do they reallocate fishing
-effort? We use identification of fishing activity via Automatic
+identification of fishing activity provide us with an opportunity to ask, how do fishers respond to the implementation of an LSMPA?
+Does effort increase or decrease and where does it go?
+We use identification of fishing activity via Automatic
 Identification Systems (AIS) and causal inference techniques to describe
 the behavioral changes and spatial redistribution of the industrial tuna
-purse seine fleet due to the implementation of a Large Scale Marine
-Protected Areas in the Pacific Ocean.
+purse seine fleet due to the implementation of the Phoenix Islands Protected Area. We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
 
 Our work is novel in the sense that it provides empirical evidence of
-the effect of Large Scale Marine Protected Areas in fishing behavior and
-distribution and can help guide future interventions as countries march
-towards meeting the targeted 10\% of ocean protection. Understanding how
-effort is displaced from LSMPAs might provide insights into how the
-industrial fleet would react to a high seas closure.
-
-The paper is outlined as follows: Section \ref{background} provides more
-information on Large Scale Marine Protected Areas and background on
+the effect of Large Scale Marine Protected Areas on fishing behavior and
+distribution and can help guide future interventions. Understanding how
+effort is displaced from LSMPAs might provide insights into how distant water fishing fleets would react to a high seas closure.
+
+The paper is organized as follows: Section \ref{background} provides more
+information on Large Scale Marine Protected Areas and some background on
 empirical studies of effort redistribution. An overview of the Nauru
 Agreement and associated countries, a description of the fleet that
-operates in the region, and a brief history of PIPA is also included.
+operates in the region, and a brief history of PIPA and PNMS is also included.
 Section \ref{methods} describes our data and identification strategy.
-Section \ref{results} presents our results, section \ref{discussion}
-provides an extension of our results to other
-LSMPAs\footnote{Not yet. but I think this would be interesting} and
+Section \ref{results} presents our results, and Section \ref{discussion}
 discusses our
-results\footnote{I might also include a section, after the background, where I explain the different theoretical models of effort redistribution and behavioral responses}.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
+results.
+
+\section{Background}\label{background}
 
@@
 as defined by \citep{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
-LSMPAs that meet the later, and that are fully no take. LSMPAs are often
+LSMPAs that meet the latter condition, and are also fully no-take. LSMPAs are often
 implemented in the pelagic environment, where the dominant human
@@
 incorporation of technology, in what then became known as Dynamic Ocean
-Management \citep{maxwell_2015}. The effectiveness and difficulties of
-implementing LSMPAs are not the focus of this paper
-\footnote{But see \citet{singleton_2014}, who provide an objective discussion of pros and cons of LSMPAs.}.
-Instead, we focus on the effect and implications of the ones that
-\emph{have been} implemented.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+Management \citep{maxwell_2015}.\footnote{See \citet{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
 \caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
@@
 conditions: reported no take area is greater than 0, are categorized as
-IUCN Ia or Ib, their designated english name is `Protected Area'.}
+IUCN Ia or Ib, their designated English name is `Protected Area'.}
 \end{figure}
@@
 advancement of many important facets of LSMPAs. For example,
-\citep{mcdermott_2018} show that the anticipation of a LSMPA can lead to
+\citet{mcdermott_2018} show that the anticipation of a LSMPA can lead to
 preemptive overfishing, which can erode or delay the expected benefits
@@
 on the long term optimal equilibrium, and redistribution of fishing
-effort may not always be optimal, especially over the first years
+effort may not always be optimal, especially over the first few years
 \citep{stevenson_2013}.
 
-The empirical research that has been done in customary sized MPAs
-suggest that resource users may show idiosyncratic responses. For
+The empirical research that has been done in smaller sized MPAs
+suggests that resource users may show idiosyncratic responses. For
 example, \citet{stevenson_2013} show that a network of MPAs displaced
@@
 \emph{perceived} costs, and increases in catch per unit effort.
-\citet{cabral_2017} analyse the redistribution of fishing and
+\citet{cabral_2017} analyze the redistribution of fishing and
 non-fishing vessels following the implementation of a network of MPAs in
-California, and find that commercial dive boats follow a
+California, and find that commercial dive boats (??????) follow a
 fishing-the-line pattern, while some fishing boats follow an ideal free
@@
 borders and closer to shore. The way in which fishers react to a spatial
-closure can have major implications in its outcome
-\citep{smith_2003,hilborn_2006} highlighting the need to understand how
-fishers react to the implementation of LSMPAs, and fishing effort
-changes and is spatially redistributed. However, all these closures took
+closure can have major implications for its outcome
+\citep{smith_2003,hilborn_2006}, highlighting the need to understand how
+fishers react to the implementation of LSMPAs, how fishing effort
+changes, and how it is spatially redistributed. All these closures took
 place within Exclusive Economic Zones, where other regulations exist.
 This may not always be the case for LSMPAs, where often the entire EEZ
-is converted into a LSMPA, leaving fishers with the options of moving to
+is converted into a LSMPA, leaving fishers with the option of moving to
 the high seas or other countries' EEZs.
@@
 \hypertarget{nauru-agreement-and-the-phoenix-island-protected-area}{%
-\subsection{Nauru agreement and the Phoenix Island Protected
+\subsection{Nauru agreement and the Phoenix Islands Protected
 Area}\label{nauru-agreement-and-the-phoenix-island-protected-area}}
@@
 The Nauru Agreement was established in 1982 by a select group of Pacific
-island nations to manage their important tuna resources. PNA Members
-include Federated States of Micronesia, Kiribati, Marshall Islands,
-Nauru, Palau, Papua New Guinea, Solomon Islands, and Tuvalu. The Nauru
+island nations to manage their important tuna resources more effectively. Parties to the Nauru Agreement (PNA) Members
+include the Federated States of Micronesia, Kiribati, the Marshall Islands,
+Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu. The Nauru
 Agreement regulated access of foreign vessels (\emph{i.e.} those from
@@
 purse seining grounds within their Exclusive Economic Zones, PNA
-countries gained bargaining power when providing access to foreign
+countries gained greater bargaining power when providing fishing access to foreign
 fleets \citep{havice_2010}.
 
-The cooperation that emerged thanks to the PNA allowed for subsequent
+The cooperation that emerged under the Nauru Agreement allowed for subsequent
 agreements that strengthened fisheries management, like the Palau
@@
 1995-2007\footnote{See \citet{havice_2010} for a detailed description of
-  the Nauru, Palau, and Federal States of Micronesia agreements, their
-  objectives, and outcomes.}. However, the most notable regulation is
+  the Nauru, Palau, and Federal States of Micronesia agreements.}. However, the most notable regulation is
 their approach to manage fishing effort: a Vessel Day Scheme (VDS)
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
@@
 One of the most notable and recent management interventions in the
-region is the implementation of the Phoenix Island Protected Area (PIPA)
+region is the implementation of the Phoenix Islands Protected Area (PIPA)
 by the government of Kiribati. PIPA was first declared in 2006, and
-established in 2008 with only 4\% of it was declared as no-take. In
+established in 2008 with only 4\% of the area declared as no-take. On
 January 1\textsuperscript{st}, 2015, the no-take area within PIPA was
@@
 times the size of Ecuador. Figure \ref{fig:PNA_map} shows a map of the
-PNA countries and the Phoenix Island Protected Area.
+PNA countries and the Phoenix Islands Protected Area.
 
 The closure of such a large area in one of the most important fishing
-regions in the world provides a great opportunity to evaluate the
+regions in the world provides a unique opportunity to evaluate the
 behavioral responses and redistribution of fishing effort by vessels
-that used to fish there. PIPA has been the focus of previous research,
+that used to fish there. PIPA has been the focus of previous research
 showing that fishing effort is effectively reduced after implementation
 \citep{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
-How do individual vessels respond to the sudden exclusion of such a big
-area? And where did all the vessels go? In the next sections we describe
-the data and methods used to answer this questions.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+How did individual vessels respond to the sudden exclusion of such a big
+area? Where did all the vessels go? And what does this imply for revenues from
+selling VDS for both Kiribati and the PNA as a whole?
+
+A spatial closure might cause fishers to modify
+their behavior as they adapt to a new state of the world. For example, some may have
+to travel further distances to find new fishing grounds, increasing their fuel
+costs. If fishers had developed experience for fishing in particular
+sites, being excluded might impose a learning cost on them, as they
+identify new fishing grounds. This might result in increased search
+times. However, if the area of knowledge of a vessel is significantly
+larger than that of the spatial closure, they might already know other
+places to fish. In the next sections we describe
+the data and methods used to answer these questions.
+
+\section{Methods}\label{methods}
 
@@
 description of AIS data and the process of identification of
-vessel-level fishing events done by Global Fishing Watch\footnote{Global
-  Fishing Watch: \url{globalfishingwatch.org}}. Alongside, we describe
-the subset of data used on our analyses. When relevant, we also point
+vessel-level fishing events performed by Global Fishing Watch.\footnote{Global
+	Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe
+the subset of data used in our analysis. We also point
 out possible shortcomings in the data, or factors that must be
-considered in the later analyses. We then move on to explain our
-empirical strategy for the identification of the behavioral changes and
-redistribution of fishing effort.
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+considered in the analysis. We then move on to explain our
+empirical strategy for the identification of behavioral changes and
+the redistribution of fishing effort.
+
+\subsection{Data}\label{data}
 
@@
 at-sea safety and prevent ship collisions by broadcasting vessel
-position, course, and activity to surrounding vessels. These broadcasted
-messages can be received by satellites and land-based antennas. GFW uses
-convolutional neural networks to infer vessel characteristics and
-whether each broadcasted position represents a fishing event, thus
-allowing us to estimate near real-time fishing events globally since
-2012 \citep{kroodsma_2018}.
-
-The amount of data gathered is dependent on the number of antennas and
-satellites that can pick up the signals. In June 1\textsuperscript{st}
-2014 satellite count increased from 3 to 6, and then to 10 in January
+position, course, and activity to surrounding vessels. These broadcast
+messages can be received by satellites and land-based antennas. GFW then uses 
+machine learning techniques (convolutional neural networks) on the broadcast messages
+to infer what type of fishing is taking place and where it is taking place, thus
+allowing the estimation of near real-time fishing events globally \citep{kroodsma_2018}.
+
+The amount of data gathered by GFW is dependent on the number of antennas and
+satellites that can receive signals. The total satellite count increased from 3 to 6 on 
+June 1\textsuperscript{st}
+2014 , and then from 6 to 10 on January
 1\textsuperscript{st} 2016. This causes an increase in the number of
@@
 apparent increase in the number of vessels and fishing hours. However,
-the addition of satellites ``affects'' all vessels in the same way. The
-variability in AIS data and ocean conditions require that temporal
-trends be taken into account. We do that by including specific controls
-in our identification strategy and using a subset of data that meet a
-BACI design -which gives us the full tracks for vessels affected and
-unaffected by the implementation of PIPA.
+the addition of new satellites affects all vessels in the same way.
 
@@
 for PNA
-countries\footnote{We perform some of the same analyses for longliners and include them in the Appendix}.
+countries.\footnote{We perform some of the same analyses for longliners and include them in the Appendix}
 We identify a total of 103 purse seiners that fished in PNA waters at
@@
 at least once since 2012. From these, 62 did so before the announcement
-(\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}) but are
+(\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}) but we are
 only able to track 61 for the complete period of study before and after
 its
-implementation\footnote{1 vessel never fished again after August 18, 2013.}.
+implementation.\footnote{1 vessel never fished again after August 18, 2013.}
 On the other hand, 38 vessels never fished inside PIPA but we only have
-data for 26 vessels before and after.
+data for 26 of these vessels both before and after MPA implementation.
 
@@
 Vessels in the control group meet the following two conditions: i)
-vessels never fished within PIPA waters, and ii) vessels have fished in
+never fished within PIPA waters from 2012-2015, and ii) vessels have fished in
 surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
@@
 
-We include three additional definitions of control groups as a
-robustness check: one with only vessels that belong to PNA countries (n
-= 7), and one that excludes Chinese vessels (n = 21). Our third control
-is made up of Japanese purse seiners that fish in the Pacific but that
+We include three additional control groups as a
+robustness check. The first group contains only vessels that belong to PNA countries (n
+= 7). The second group excludes Chinese vessels (n = 21). Our third control
+is made up of Japanese purse seiners that fish in the Pacific but have
 never fished inside PIPA (n =
-27)\footnote{Using Taiwanese vessels was the original idea, but there are only 4 vessels with pre-2015 data.
-I need to further identify proper Taiwanese vessels, as I am currently using the entire Pacific ocean}.
-Our definition of treatment and control groups leaves us with 61 and 21
-treated and control vessels, which have just over 22 million
-observations where about 22\% are identified as fishing events.
-
-For each vessel we calculate total daily fishing hours and obtain panel
-data with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
-of vessels following a BACI design, as well as the fishing hours, before
+27).\footnote{We also considered a control group of Taiwanese flagged vessels but there are only 4 vessels with pre-2015 data.}
+Our main definition of treatment and control groups leaves us with 61 treated and 26
+control vessels, which have just over 22 million
+observations with about 22\% of these observations identified as fishing events by the neural network classification.
+
+For each vessel, we calculate total daily fishing hours and build a daily panel
+with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
+of vessels following a Before-After-Control-Impact (BACI) design, as well as the fishing hours, before
 and after PIPA. Fig. \ref{fig:all_vessels} shows that mean fishing hours
@@
 confirming our claim that the control group provides a plausible
-counterfactual. Figure \ref{fig:baci_strict} provides a visual
+counterfactual. Figure \ref{fig:baci_strict} in the Appendix provides a visual
 representation of the vessel-level fishing events that make up each
-group through time. We use this data to answer our key questions: How do
-the 61 purse seiners modify their behavior as compared to the different
-control groups, and where do they go after the spatial closure? The
-following section describes our empirical identification strategies.
+group through time. We use this panel data to answer our key research questions: 
+Are the 61 purse seiners that used to fish within PIPA affected by the closure? If so, how?
+What are they doing differently and where are they going that they didn't go to before?
+The following section describes our empirical identification strategy.
 
@@
 \centering
-\begin{tabular}[t]{lrrrr}
+\begin{tabular}[t]{lcccc}
 \toprule
@@
 \midrule
-Control & 26 & 11.74 & 20.13 & 1.72\\
+Control & 26 & 11.74 & 20.13 & 1.71\\
 Treatment & 61 & 10.67 & 18.36 & 1.72\\
@@
 
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
-number of vessels by month for all vessels. Vertical dashed lines
-indicates dates when satellites were added, solid line indicates PIPA
-closurePIPA closure.}
-\end{figure}
-
-\hypertarget{analyses}{%
-\subsection{Analyses}\label{analyses}}
-
-The first analysis focuses on identifying the response of fishing
-vessels to PIPA closure. A spatial closure might cause fishers to modify
-their behavior as they adapt to a new state of the world. Some may have
-to travel further distances to find new fishing grounds, which would
-lead them to fish harder to compensate for the associated extra fuel
-costs. If fishers had developed experience for fishing in particular
-sites, being excluded might impose a learning cost on them, as they
-identify new fishing grounds. This would result in increased search
-times. However, if the area of influence of a vessel is significantly
-larger than that of the spatial closure, they might already know other
-places and times where to fish. Our variables of interests intend to
-capture these possible reactions.
-
-We use daily fishing hours, daily proportion of fishing vs.~non-fishing
+\subsection{Analyses}\label{analyses}
+
+Our first analysis focuses on identifying the response of 
+vessels to the PIPA closure. We use daily fishing hours, daily proportion of fishing vs.~non-fishing
 hours, daily distance traveled (km), distance from shore (km) and
-distance from
-port(km)\footnote{Results are presented for fishing hours, bur preliminary results for distance form shore and distance from port are shown in Tables \ref{tab:dist_shore} and \ref{tab:dist_port}}.
-We compare our variable of interest before and after the implementation
-of PIPA using a Difference-in-Differences approach, where we track the
-variable of interest for vessels described in the previous section. Our
+distance from home
+port(km) as our main outcomes of interest.
+We compare these outcomes before and after the implementation
+of PIPA using a Difference-in-Differences approach. Our main
 specification is the following:
@@
 \[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
+y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t},
 \]
 
-Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
-period \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
+where \(y_{i,t}\) is the outcome of interest for vessel \(i\) on day \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
 dates prior to PIPA implementation and a value of 1 for all dates
-including and following PIPA implementation. \(Treat_i\) is a dummy
-variable indicating whether a vessel belongs to the control
-(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
-the standard intercept, \(\beta_1\) captures the temporal trend change,
-\(\beta_2\) captures the difference between treated and control groups,
-and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
+following PIPA implementation. \(Treat_i\) is a dummy
+variable indicating whether a vessel belongs to the treatment (\(Treat_i = 1\)) or control
+(\(Treat_i = 0\)) group. \(\alpha\) is
+the standard intercept term, \(\beta_1\) captures the temporal trend,
+\(\beta_2\) captures the initial difference between treated and control groups,
+and \(\beta_3\) is our parameter of interest: the Difference-in-Differences estimate capturing
 the treatment effect. Finally, \(\phi_t\) and \(\gamma_i\) represent
-month- and flag-level dummies that account for seasonality or
-country-level management interventions. \(\theta_t\) are dummies to
-account for the addition of more satellites.
-\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}.
-
-Our second part of the analyses focuses on the redistribution of fishing
+month and flag dummies that account for seasonality or
+country-level management interventions. \(\theta_t\) are time dummies to
+account for the addition of more satellites over time.\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}
+
+Our second part of the analysis focuses on the redistribution of fishing
 effort. The role of institutions may play an important role. As stated
@@
 seining in the PNA, vessels purchase access to the fishery at the
-beginning of the season. If a vessel decides to fish within the PNA,
+beginning of the season (QUESTION FOR JC: WHEN IS THIS? And wasn't the closure expected?). If a vessel decides to fish within the PNA,
 they've already made the decision to pay for access, expecting higher
-returns from fishing there than in the High Seas. In the particular case
-of PIPA, one would expect that a vessel holding a permit to fish in
-I-Kiribati waters would then move to other fishing grounds within
-Kiribati after the closure. Alternatively, if a vessel fishes illegally
-in I-Kiribati waters before the implementation, one would expect them to
+returns from fishing there than in the high seas. In the particular case
+of PIPA, one would expect that a vessel previously holding a permit to fish in
+Kiribati waters would 
+most likely continue to purchase access to PNA waters (either in Kiribati's remaining open areas or a nearby EEZ). Alternatively, if a vessel fishes illegally
+in Kiribati waters before the implementation, one would expect them to
 reallocate to other regions with equal or less enforcement. In this
-case, they might then choose to move to other I-Kiribati waters, waters
-of countries that have similar enforcement levels, or the High Seas.
-
-We discretize spatial units by using a polygon for
-PIPA\footnote{we would expect to see a decrease here} and distinct
-spatial units for each EEZ of each country. Some vessels might shift
+case, they might then choose to move to other Kiribati waters, waters
+of countries that have similar enforcement levels, or to the high seas.
+
+We discretize spatial units by creating a polygon for
+PIPA and distinct
+spatial units for each geographically separate EEZ of each country. Some vessels might shift
 from EEZs into the high seas, but we are interested in knowing
@@
 example, if we were to do this only for Kiribati, we would have 8
-spatial units: PIPA, three EEZs, three 1-degree buffers of high seas
-around each EEZs, and the rest of the high seas. Whenever the buffers
-overlapped between themselves, we randomly clipped one on to the other.
-
-We then take this spatial polygons and rasterize them to a 1-degree grid
-(See Figure \ref{fig:raster_rgn}), which we then use to rasterize points
+spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas
+around each EEZ, and the rest of the high seas. Whenever the buffer units
+overlap, we randomly clip one on to the other (QUESTION FOR JC: WHAT DOES THIS MEAN?).
+
+We then take these spatial polygons and rasterize them to a 1-degree grid
+(see Figure \ref{fig:raster_rgn} in the Appendix), which we then use to rasterize points
 of fishing activity. For each cell, we calculate the total monthly
-fishing hours by treated and control vessels (See Figure
+fishing hours by treated and control vessels (see Figure
 \ref{fig:fishing_raster}). Since we are interested in the redistribution
@@
 fishing hours that region \(i\) receives at time \(t\). Years are
-modelled as factors (\(Year_t\)), using 2012 as the reference level.
-\(Region\) is a dummy variable for regions defined above. Our parameter
+modeled as factors (\(Year_t\)), using 2012 as the reference level.
+\(Region\) is a dummy variable for regions defined above. Our parameter (QUESTION FOR JC: VECTOR?)
 of interest is \(\beta_{3,i}\), which captures the yearly by-country
@@
 All regression coefficients were estimated via ordinary least squares,
-and heteroskedastic-robust standard errors were calculated. All analyses
+and heteroskedasticity-robust standard errors were calculated. All analyses
 were performed in R version 3.5.1 \citep{rcore_2018}. Raw data and code
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Regressions coefficients for our DiD analysis are shown in Table
-\ref{tab:did}. Columns 1 -3 use all data for controls. Columns 4 - 6 use
+\section{Results}\label{results}
+
+Regression coefficients for our DiD analysis are shown in Table
+\ref{tab:did}. Columns 1 -3 use our primary control group. Columns 4 - 6 use
 only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
 Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
-hence don't include flag fixed-effects to avoid perfect colinearity
-between Japanese flag and
-control\footnote{Results of the same analysis is shown for longliners in \ref{tab:long}}.
+don't include flag fixed-effects to avoid perfect collinearity
+between the Japanese flag and
+control group status.
 Our DiD analysis shows an overall increase in purse seine fishing hours,
 even after accounting for the introduction of new satellites (Table
-\ref{tab:did}). This coefficient estimate is consistent for different
-model specifications and across groups of treatment and controls, and
+\ref{tab:did}).\footnote{Results of the same analysis is shown for longliners in Table \ref{tab:long}} This 
+\emph{post} coefficient estimate is consistent across different
+model specifications and across controls, and
 effectively represents the patterns observed in Figure
@@
 The \(\beta_3\) coefficient indicating our treatment effect suggests
-that, relative to the control, treated vessels fish less, in the order
-of 0.5 hours per day. Another way to interpret this is that the increase
+that, relative to the control, treated vessels fish less: to the order
+of 0.5-3.7 hours per day. In 6 out of 11 specifications, there is a statistically significant decrease in daily fishing hours. Another way to interpret this is that the increase
 in fishing effort by treated vessels has occurred at a lower rate than
-control vessels. The effect varying between \(\beta_3 = -0.515\) and
-\(\beta_3 = -0.934\). These values are equivalent to a 15 - 28 reduction
-in fishing hours per month. However, this result is only robust and
+control vessels. These values are equivalent to a reduction of 15 - 111 fishing hours per month. However, this result is only robust and
 significant (\(p < 0.01\)) in the simplest specification of the
@@
 \(Pre \times Post\) design and instead interacting the treatment dummy
-with quarterly or year-month combinations we are not able to reject the
-null hypotheses of no change, suggesting that the total fishing hours
+with quarterly or year-month combinations, we are not able to reject the
+null hypothesis of no change, suggesting that the total fishing hours
 remains similar for the displaced vessels (Figs.
-\ref{fig:q1}-\ref{fig:ym4}). Since vessels don't seem to be fishing less
-(or at least not much less), an obvious question arises: where are they
+\ref{fig:q1}-\ref{fig:ym4}). Since vessels don't seem to be fishing a lot less, an obvious question arises: where are they
 fishing now?
@@
 Figure \ref{fig:fishing_raster} provides a spatial representation of
-these changes. Note that 2013 effort distribution is roughly similar
-across vessels. Then in 2014 there is a sharp increase in fishing hours
-by treated vessels inside PIPA (blue paradox). In 2015 treated vessels
-then allocate more effort to the easternmost Kiribati EEZ (see Figure
-\label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of
+these changes. Note that the 2013 effort distribution is roughly similar
+across vessels. Then, in 2014, there is a sharp increase in fishing hours
+by treated vessels inside PIPA (the so-called Blue Paradox). In 2015, treated vessels
+then allocate more effort to the easternmost Kiribati EEZ and the high seas. In 2016, the spatial distribution of
 fishing effort is again similar across groups. It is evident that the
-increase in relative fishing effort is greater for for regions closer to
+increase in relative fishing effort is greater for regions closer to
 PIPA.
@@
 temporal evolution of the relative allocation of fishing
-effort\footnote{Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.}.
-It shows shows the change in fishing effort inside PIPA, including the
+effort.\footnote{Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.}
+It shows the change in fishing effort inside PIPA, including the
 preemptive fishing and immediate reduction previously reported
-\citep{mcdermott_2018}. I-Kiribati waters in KIR 1 and KIR 2 show an
+\citep{mcdermott_2018}. Kiribati waters in KIR 1 and KIR 2 show an
 increase in fishing effort for 2015; the same pattern is observed for
@@
 regions farther away from PIPA don't show a clear pattern under visual
-inspection.
+inspection. This suggests fishing effort inside PIPA has moved to the high seas around Kiribati instead of paying to fish within alternative Kiribati EEZ waters.
 
@@
 the year-region interaction coefficient estimates for each region as a
-stream of changes through time (Fig. \ref{fig:mean_change} and Table
+stream of changes through time (Figure \ref{fig:mean_change} and Table
 \ref{tab:mean_change}). As noted before, the marginal change in the
@@
 effort in the post-implementation period. The largest increase is
-observed for the I-Kiribati EEZ 2, where the redistribution of treated
+observed for the Kiribati EEZ 2, where the redistribution of treated
 vessels caused a 15\% increase in the \emph{relative} allocation of
-fishing effort within I-Kiribati waters. This displacement is likely
+fishing effort within Kiribati waters. This displacement is likely
 causing a crowding effect after PIPA-fishing vessels redistribute to
@@
 We use the rasterized effort to evaluate if the PIPA closure increased
-crowdness otuside the LSMPA. We count the number of raster cells that
+crowding outside the LSMPA. We count the number of raster cells that
 had both treated and control vessels each year (Fig.
 \ref{fig:sp_corr}A). The pattern observed here could just be an artifact
-of satellite detections increasing though time. Thereforem we also
+of satellite detections increasing though time. Therefore we also
 calculate a spatial correlation of presence/absence and observe similar
-patterns (Fig. \ref{fig:sp_corr}B). While this are at the year level and
+patterns (Fig. \ref{fig:sp_corr}B). While this is at the year level and
 cannot assure that vessels were in effect at the same time in the same
-vessel, it provides an accurate depiction of what we would expect to
+place, it provides a of what we would expect to
 find if our claims of displacement are true. Spatial overlap increases
-in 2015 as vessels from PIPA are excluded, and that measure slowly
-returns to its previous state.
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+in 2015 as vessels from PIPA are excluded, but then starts to decline.
+[QUESTIONS FOR JC: Is this significant?
+Can we do a daily measure?
+What about mean or shortest distance between vessels.
+Treated/Control/Combined]
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
 \caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
 hours for all vessels in our main treatment-control groups. Solid
-straight lines show a linear trend by period (pre-psot) and treatment.
+straight lines show a linear trend by period (pre-post) and treatment.
 The other red and blue lines show monthly avarages. Vertical dashed
-lines indicates dates when satellites were added, solid line indicates
-PIPA closurePIPA closure.}
+lines indicate dates when satellites were added, solid line indicates
+PIPA closure.}
 \end{figure}
@@
   \caption{\label{tab:did}Difference-in-differences estimates for 3 different controls and 3 different specifications.
-The first three columns use all data for controls.
+The first three columns use our primary control group.
 Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
 Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
+Numbers in parentheses are heteroskedasticity-robust standard errors.}
   \label{} 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
 \caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
-for each model. Top pannel indicates variable, x-axis represents model
-specification, and y-axis coefficient estimate.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+for each model. Top panel indicates variable, x-axis represents model
+specification, and y-axis coefficient estimate. [QUESTION FOR JC: delete the intercept panel.]}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
 \caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
@@
 Colors have been adjusted relative to the maximum observed by group and
-year. Red polygons show LGMPAs in the region. For visualization purpose
-sonly some years are presented, the full 2012 - 2017 period is shown in
-Figure \ref{fig:fishing_raster_full}.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
+year. Red polygons show LGMPAs in the region. For visualization purposes
+only some years are presented, the full 2012 - 2017 period is shown in
+Figure \ref{fig:fishing_raster_full}.
+[QUESTION FOR JC: we should include all years in the main text.
+Is there a way to normalize this, e,g.
+color corresponds to \% of total fishing effort, so it's easier to compare?]}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
 \caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
-after PIPA by region. Colors indicate the pre-post period. Solid line
+after PIPA by region. Colors indicate the pre- and post- periods. Solid line
 across points shows local mean with a region-specific loess smoother.
-Vertical dashed lines indicates dates when satellites were added, solid
-line indicates PIPA closurePIPA closure. Note that inflection points of
-the loess smoother are not affected by the addition of satellites.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
+Vertical dashed lines indicates dates when satellites were added, solid vertical
+line indicates PIPA closure. Note that inflection points of
+the loess smoother are not affected by the addition of satellites.
+[QUESTION FOR JC: this figure needs a lot of work.
+subplot titles need to be more intuitive.
+I would combine all EEZ KIR into one group and all HS KIR into one group.]}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
 \caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}Coefficient
-estimates for the redistribution regression. Each pannel shows the
-region-specific coefficients, with heteroskedastick-robust standard
-errors as error bars. The horizontal dashed line represents 0 chenge
-relative to the 2012 region-specific levels.}
+estimates for the redistribution regression. Each panel shows the
+region-specific coefficients, with heteroskedasticity-robust standard
+errors as error bars. The horizontal dashed line represents 0 change
+relative to the 2012 region-specific levels. [QUESTION FOR JC: just do 95\% confidence intervals.]}
 \end{figure}
@@
 \caption{\label{tab:unnamed-chunk-16}\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
-Each row represents a region, each color a year.
-Numbers in parentheses are heteroskedatic-robust standard errors.
+Each row represents a region, each column a year.
+Numbers in parentheses are heteroskedaticity-robust standard errors.
 R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001).
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
 \caption{\label{fig:unnamed-chunk-17}\label{fig:sp_corr}Number of cells that
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Our findings provide interesting insights into the effect that LSMPAs
+\section{Palau National Marine Sanctuary}\label{PNMS}
+
+%\begin{figure}[h]
+%	\caption{Map of the Four Protected Areas}
+%	\label{fig:maps}
+%	\includegraphics[width=0.8\textwidth]{Color_V1.png}
+%	Notes: ... .
+%\end{figure}
+
+On October 28, 2015 the President of Palau, H.E.
+Tommy E.
+Remengesau Jr., signed into law the Palau National Marine Sanctuary Act.
+Starting in December 2020, this will close 193,000 square miles to commercial fishing activities, creating the 14th largest protected area in the world.
+
+\subsection{Background on Commercial Fishing in Palau}\label{Palau_back}
+
+Foreign tuna fishing in Palau’s EEZ began before WWI.
+Pole and line was the initial gear used to target skipjack tuna by the Japanese.
+Foreign fishing activities stopped during WWII and started again in the 1960s when the Japanese returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
+The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna during the same time.
+During the 1980s, longline fishing began to set their lines deeper, shifting their targets to bigeye tuna.
+During the 1980s Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
+There are currently three transshipment companies operating in Palau.
+
+\subsubsection{Purse seine fishing}
+
+Purse seine vessels target schools of skipjack tuna that are used for canning.
+Compared to other EEZs in the Pacific, Palau’s EEZ is not known to be preferred for purse seining (Sisior, pers.
+comm.).
+Currently all purse seine boats fishing in Palau’s EEZ are Japanese and do not land their catches in Palau Table \ref{tab:palau_purse}.
+
+%\input{palau_purse}
+
+\subsubsection{Longline fishing}
+
+All longline vessels fishing in Palau’s EEZ are foreign owned (Table 2).
+Japanese longline vessels do not land their catches in Palau.
+Locally based, foreign owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI), Kuniyoshi Fishing Company (KFC)) (Table 2).
+Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan, upon landing in Koror.
+Most of the discards, or portion of the catch that is of too low quality to export, is either sold or donated in Palau.
+A very small portion of the discards is frozen and transported to Taiwan when the vessels return to their home ports.
+
+%\input{palau_long}
+
+\subsubsection{Access fees}
+
+An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covers three methods of fishing (longline, purse seine, pole and line) and has allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
+Japan pays 4-5\% of catch returns, but there was no way to validate their catch \citep{Tewid2013}.
+Between 2010 and 2014, Japan has paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
+Currently, these access fees have been replaced by the vessel day schemes (described in section 3).
+
+\subsubsection{Uniform Longline Agreement for locally based vessels (ULA)}
+
+Agreements between the Republic of Palau and foreign owned, local based companies (PITI and KFC) \citep{Tewid2013}.
+Vessels under these agreements are internationally owned, locally based vessels that have payed for annual licenses per vessel based on the size of the vessel.
+These are the vessels in Table \ref{tab:palau_long} (excluding the Japanese vessels).
+So, for example, 38 vessels in 2016.
+Between 2010 and 2014, total licensing fee revenue was between \$219,000-\$284,600 per year \citep{Gillett2016}.
+Currently, these access fees have been replaced by the vessel day scheme (described in section 3).
+
+\subsubsection{US Multilateral Tuna Treaty and Federated States of Micronesia Arrangement}
+
+These two multilateral treaties grant preferential access to the US and FSM flagged purse seine boats, respectively.
+The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees (more in section 3).
+Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds.
+Some Pacific Island countries treat this money as foreign aid, not for fishing access \citep{Gillett2016}.
+
+\subsubsection{Other sources of revenue from pelagic fisheries}
+
+The export tax for all commercial tuna and billfish, either fresh or frozen is \$0.35/kg.
+Average revenues from export taxes was approximately \$500,000 annually from 2011-2014 \citep{Gillett2016}.
+Otherwise there is little additional revenue from pelagic fisheries, especially considering that very few jobs are created by the fishery.
+Between 80-90 people are employed by offshore fisheries, of these only ~20\% are Palauans and average wages are ~50\% average wages in the country \citep{Gillett2016}.
+
+\subsubsection{Parties to the Nauru Agreement and the Vessel Day Scheme}
+
+The Parties to the Nauru Agreement (PNA) is an agreement between Federated States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua New Guinea, Solomon Islands and Tuvalu to manage the largest tuna fishery in the world.
+The Purse Seine Vessel Day Scheme (PS VDS), established in 2006 with the Palau Agreement, is the current method used by the PNA to manage effort in the fishery.
+Although not a PNA member, Tokelau joined the PS VDS in 2014, with 1,000 transferrable days \citep{PNA2014}.
+
+In the PS VDS, a total number of annual vessel days for the entire fishery is agreed upon by the parties.
+Each party’s allowable effort (PAE) is then calculated based on historic effort and biomass within each party’s EEZ.
+Sixty percent of the PAE is calculated based on the party’s effort over the last seven years and 40\% of the PAE is calculated based on the 10 year average of the party’s share of estimated skipjack and yellowfin biomass within its EEZ (as explained in Article 12.5 of the 2012 Amendment to the Palau Agreement and in Hagrannsoknir sf 2014).
+A minimum benchmark fee is set for purse seine vessel days (PS VD) which each party can transfer (i.e., sell to another PNA member) or sell to the highest bidder (i.e., sell to fishing company).
+Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties VD allocation \citep{PNA2016}.
+The process of transferring days between parties is described in Article 7 of the Management Scheme \citep{PNA2016}.
+The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}.
+A minimum benchmark fee of \$8,000/day was set from 2015 \citep{PNA2014a}.
+Detailed records on sales or transfers of vessel days are not publicly available \citep{havice_2013,yeeting2018stabilising}.
+\cite{yeeting2018stabilising} summarize the PNA ‘implementing arrangements’ as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \citep{PNA2016}.
+Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \citep{PNA2016}.
+As described in the Palau Arrangement \citep{PNA2016}, fishing days by vessels shorter than 50m or longer than 80m count as 0.5 and 1.5 vessel days, respectively.
+Parties are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within the PAE.
+Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \citep{PNA2016}.
+However, there are criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the SP VDS \citep{Arnason2014,yeeting2018stabilising}.
+In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism.
+Palau’s currently PS VD allotment is reportedly ~700 vessel days annually (Sisior, pers.
+comm., \cite{Pojas2018}), though historically, this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}.
+Palau sells most of its vessel days to the US for \$12,500 each (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
+The remainder of Palau’s PS vessel days are sold for between \$9-10,000 each.
+When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
+Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred PS VD to is Papua New Guinea \citep{Tewid2013} and this year, PS VD have been sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
+This year, Palau has brought in approximately \$9 million USD in PS VDS revenue (Sisior pers.
+comm.).
+
+The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing at the country-scale.
+Palau was the first party to implement the VDS for the longline fishery in 2017.
+In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers.
+comm.).
+Since 2016, the number of allowed longline VDs has been a fraction of the 2014 days, reducing each year as stipulated in the PNMS Act.
+Palau sells its LL VD for \$150-\$250 (Sisior pers.
+comm.).
+Because the LL VDS is still new and has yet to be fully implemented by all parties, LL VD are not currently transferable between PNA member EEZs.
+
+\subsubsection{The Palau National Marine Sanctuary Act}
+
+In 2015, Palau enacted a policy to protect 500 thousand square kilometers of its ocean, representing 80\% of its exclusive economic zone (EEZ), by 2020.
+The policy’s goal is to preserve and manage the stocks, health, and beauty of Palau’s waters and natural resources by limiting fishing in its deep ocean waters.
+State waters hugging the coasts of the archipelago are not affected by the policy.
+Commercial fishing will still be allowed within the open 20\% that surrounds the main islands of Koror and Babeldaob, but all catch must be landed in Palau and exports of pelagic fish will be prohibited.
+Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
+
+\subsubsection{Future of pelagic fisheries under the PNMS}
+
+To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
+This appears to be occurring for the LL VDS, but it is uncertain whether this is being followed for the PS VDS, because PS VD can be transferred for use in other EEZs.
+There has been no official statement on what will happen to Palau’s vessel days upon full implementation of PNMS.
+However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
+comm.).
+In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \citep{Senase2015}.
+Further, other PNA members have not been penalized for other protected area closures (e.g., Phoenix Islands Protected Area in Kiribati) (Hanich, pers.
+comm.).
+Table 3 estimates the potential losses of revenue under full enactment of the PNMS under four scenarios.
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
+Scenario 1 is likely if Palau retains its PAE, but the US no longer purchases its days (note, US is currently purchasing days at \$12,500).
+Scenario 2 is the same as the first scenario, except instead of being able to transfer its days at the current benchmark price, it is able to transfer its days for \$12,000 (to account for current price to US of \$12,500, which will increase in accordance with the US Treaty, and also the general increasing trend in the value of PS vessel days).
+It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
+In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,000/day, respectively.
+In all scenarios, all longline vessel day and export tax revenue are lost.
+Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
+Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+
+%\input{revenue_loss}
+
+\subsubsection{Plans for a domestic pelagic fishery}
+
+In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch Plans for domestic fishery \citep{Gillett2016}.
+The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers.
+comm.).
+Otherwise, there are no domestic vessels dedicated to full-time offshore fishing.
+A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes (although Phil James with SPC has results that should come out soon).
+Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
+There are several possible scenarios for domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
+
+We will use aggregated GFW data at the 1km * 1km level to estimate what \% of fishing effort under the PNA is currently taking place in the proposed sanctuary?
+This will estimate the impact on foreign-flagged fleets that used to fish in Palau waters.
+We are currently in possession of this data.
+In terms of the impact on PNA payments, it is our understanding that the allocation will not be reduced (in the near future) but perhaps the price received per VDS will be lower.
+But we do not have good information on prices paid for VDS.
+We also don’t yet have good data on local fishers in Palau that are likely to be positively impacted since they will be allowed to fish in the sanctuary.
+
+\section{Conclusion}\label{conclude}
+
+\begin{figure}[h]
+	\caption{Fishing Effort in Palau Relative to the Total PNA Area}
+%	\includegraphics[width=0.75\textwidth]{Fishing_effort_Palau_relative_PNA}
+\end{figure}
+
+\begin{figure}[h]
+	\caption{Fishing Effort in Palau Relative to the Total PNA Area By Distant Water Fishing Fleet}
+%	\includegraphics[width=0.75\textwidth]{By_flag_Fishing_effort_Palau_relative_PNA}
+\end{figure}
+
+\clearpage
+
+\section{Discussion}\label{discussion}
+
+Our findings provide insights into the effect that LSMPAs
 can have on vessel behavior and the redistribution of fishing effort.
-These collection of results show that the implementation of PIPA had
-little effect on the effort exerted by purse seiners. However, regions
+These results show that the implementation of PIPA had
+little effect on the total fishing effort exerted by purse seiners. However, regions
 adjacent to PIPA show an increase in the relative amount of fishing
-effort, suggesting that effort is simply redisplaced to closeby areas.
+effort, suggesting that effort is simply displaced to nearby areas.
 This does not imply that there is more fishing effort exerted by treated
@@
 pre-PIPA levels. Additionally, we show that post-PIPA there is a
-concentration of effort leading to crowding. In this section we discuss
+concentration of effort leading to crowding. In this section, we discuss
 the implications of vessel-level reductions in fishing effort and the
@@
 
-Previous studies on insular environments suggest that vessels move to
+Previous studies on protected areas around Pacific islands suggest that vessels move to
 distant places, which might be translated as increased costs
-\citep{stevenson_2013}. Nevertheless, they do not use counterfactuals
-that could help account for system- or fleet-level changes that occur
-through time. Others have used similar satellite-tracking systems to
+\citep{stevenson_2013}. Others have used similar satellite-tracking systems to
 show that fishing effort accumulates near the edges of spatial closures,
-yielding greater catches \citep{murawski_2005}. Yet, these vessel tracks
-do not cover the pre-reserve period, making it difficult identify the
+yielding greater catches over time \citep{murawski_2005}. But these vessel tracks
+do not cover the pre-reserve period, making it difficult to identify the
 contribution of spatial closures to the observed spatial distribution of
@@
 The role of the institutions at play is evident. Vessels that fished
-inside PIPA before the implementation were, ultimately, fishing in
-I-Kiribati waters likely under a VDS license. Uppon the implementation,
-some of these redistribute to other areas of the I-Kiribat EEZ and the
+inside PIPA before the implementation were likely fishing in
+Kiribati waters under a VDS license. Upon implementation,
+some vessels redistribute to other areas of the Kiribati EEZ and the adjacent
 high seas for the year immediately after the closure. As stated before,
-it is reasonable for a vessel holding a license to fish in I-Kiribati
-waters to simply reallocate their effor to other parts of that EEZ.
+it is reasonable for a vessel holding a license to fish in Kiribati
+waters to simply reallocate their effort to other parts of that EEZ.
 However, the shift to the high seas may not follow the same logic.
 Instead, it is possible that vessels that redistribute to the high seas
-were opperating in I-Kiribati illegally, and decide to reallocate in the
-high seas to continue fishing without a license. These patterns provide
-us with interesting insight sinto fishing behavior, which may become
-useful in tackling Illegal, Unreported and Unregulted (IUU) fisheries.
-
-A major shortcoming of our analyses is that we do not observe catches or
+were operating in Kiribati illegally, and decide to reallocate in the
+high seas to continue fishing without a license. Or they are now not willing to pay Kiribati to fish in the remaining open areas.
+
+A major shortcoming of our analysis is that we do not observe catches or
 revenues, which ultimately are the factors that guide the decision
 making process of profit-maximizing agents. Therefore, it is difficult
-to know whether lack of change in fishing hours represents a positive or
-negative impact. An additional thing that we are yet to test is the
-changes in non-fishing hours sepnt at sea. It is plausible that fishing
+to know whether the small change in fishing hours represents a positive or
+negative impact. An additional factor that we are yet to test is the
+change in non-fishing hours spent at sea. It is plausible that fishing
 hours remain constant, but vessels have to increase search time. Upon
@@
 widespread footprint of the treated fleet may suggest that they are well
-aqquainted with the region (See Fig. \ref{fig:fishing_raster}), and its
-unlikely that they would need to learn or identify new fishing grounds.
+acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's
+unlikely that they would need to invest much time to identify new fishing grounds.
 
 Our work suggests that the implementation of LSMPAs has little impact on
-purse seiners fishng effort. We also show that fishing effort is
+total fishing effort. We also show that fishing effort is
 redistributed to areas close by, and that this leads to a potentially
@@
 
-\bibliography{references.bib}
+\bibliography{references}
 
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
 \caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
@@
 
+\begin{figure}
+	\centering
+	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
+		number of vessels by month for all vessels. Vertical dashed lines
+		indicates dates when satellites were added, solid line indicates PIPA
+		closurePIPA closure.}
+\end{figure}
+
+\clearpage
+
 \hypertarget{longliners}{%
@@
 Longliners show a similar pattern of effort reduction. However, the
-magnitude of the \(\beta_3\) coefficient is smaller (ranging from
-\(\beta_3 = -0.98\) to \(\beta_3 = -1.125\)) and not significant unless
+magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
 including month and flag FEs for the general treatment-control groups,
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
 \caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
 \caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
 \caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
 \caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
 \caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
 \caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
 \caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
 \caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-TRUE \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-TRUE \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
 \clearpage
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_port}Regression results for distance from shore} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-TRUE \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_port}Regression results for distance from shore} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-TRUE \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
 \hypertarget{effort-redistribution}{%
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
 \caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
@@
 \centering
-\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
 \caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly

### 2019-01-22 docs/tab/main_DID.tex
Updated tables 1 and 2

\begin{table}[!htbp] \centering 
  \caption{\label{tab:did}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 2.148$^{***}$ & 3.723$^{***}$ & 2.148$^{***}$ & 2.670$^{***}$ & 5.218$^{***}$ & 11.130$^{***}$ & 12.909$^{***}$ & 12.909$^{***}$ & 0.520$^{***}$ & 0.869$^{***}$ \\ 
  & (0.019) & (0.004) & (0.019) & (0.040) & (0.022) & (0.032) & (0.014) & (0.014) & (0.021) & (0.004) \\ 
  & & & & & & & & & & \\ 
 Post & 0.589$^{***}$ & $-$0.224$^{***}$ & 0.589$^{***}$ & 1.280$^{***}$ & $-$0.216$^{***}$ & $-$0.288$^{***}$ & 0.157$^{***}$ & 0.157$^{***}$ & $-$0.056$^{**}$ & $-$0.097$^{***}$ \\ 
  & (0.022) & (0.006) & (0.022) & (0.045) & (0.032) & (0.046) & (0.016) & (0.016) & (0.027) & (0.012) \\ 
  & & & & & & & & & & \\ 
 Treated & $-$0.112$^{***}$ & 0.021$^{***}$ & $-$0.112$^{***}$ & $-$0.153$^{***}$ & 0.239$^{***}$ & 0.053 & $-$0.059$^{***}$ & $-$0.059$^{***}$ & 0.088$^{***}$ & $-$0.043$^{***}$ \\ 
  & (0.022) & (0.004) & (0.022) & (0.045) & (0.025) & (0.037) & (0.015) & (0.015) & (0.023) & (0.006) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & 0.017 & 0.019$^{***}$ & 0.017 & $-$0.132$^{**}$ & $-$0.156$^{***}$ & $-$0.114$^{**}$ & $-$0.001 & $-$0.001 & 0.006 & 0.055$^{***}$ \\ 
  & (0.025) & (0.007) & (0.025) & (0.052) & (0.038) & (0.054) & (0.018) & (0.018) & (0.031) & (0.014) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 38,607 & 114,195 & 38,607 & 36,939 & 114,967 & 114,967 & 38,607 & 38,607 & 2,135 & 3,130 \\ 
R$^{2}$ & 0.083 & 0.040 & 0.083 & 0.087 & 0.004 & 0.002 & 0.013 & 0.013 & 0.028 & 0.028 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-01-22 docs/PIPA_Palau.tex
Deleted old rmd manuscript and updated tex file

@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
+\includegraphics{img/LSMPAs_map.pdf}
+\caption{\label{fig:LSMPAs_map}Large Scale Marine
 Protected Areas. The map shows all areas larger than 250,000
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
+\includegraphics{img/PNA_map.pdf}
+\caption{\label{fig:PNA_map}Map of the Exclusive
 Economic Zones (EEZs) of the region of interest. Countries that belong
@@
 description of AIS data and the process of identification of
-vessel-level fishing events performed by Global Fishing Watch.\footnote{Global
-	Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe
+vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}}
+Alongside, we describe
 the subset of data used in our analysis. We also point
@@
 of vessels following a Before-After-Control-Impact (BACI) design, as well as the fishing hours, before
-and after PIPA. Fig. \ref{fig:all_vessels} shows that mean fishing hours
+and after PIPA. Fig. \ref{fig:all_panels} shows that mean fishing hours
 for purse seiners have an abrupt increase, just before January 1st,
@@
 
-\begin{table}[H]
-
-\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
-\centering
-\begin{tabular}[t]{lcccc}
-\toprule
-Group & n & Before & After & Change (A / B)\\
-\midrule
-Control & 26 & 11.74 & 20.13 & 1.71\\
-Treatment & 61 & 10.67 & 18.36 & 1.72\\
-\bottomrule
-\end{tabular}
-\end{table}
+\input{tab/baci_n_s}
 
@@
 
-\clearpage
-
 \section{Results}\label{results}
@@
 effectively represents the patterns observed in Figure
-\ref{fig:all_vessels}.
+\ref{fig:all_panels}.
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
-hours for all vessels in our main treatment-control groups. Solid
-straight lines show a linear trend by period (pre-post) and treatment.
-The other red and blue lines show monthly avarages. Vertical dashed
-lines indicate dates when satellites were added, solid line indicates
-PIPA closure.}
+\includegraphics{img/all_panels.pdf}
+\caption{\label{fig:all_panels}Time seri showing mean monthly values es for our 10 variables of interest:
+A) Fishing hours, B)Non-fishing hours at-sea,
+C) Proportion of fishing hours to total hours at-sea,
+D) Distance traveled, E) Mean distance from port,
+F) Mean distance from shore,
+G) Mean distance from port for fishing events,
+H) Mean distance from shore for fishing events,
+I) Proportion of hours spent in Kiribati waters,
+J) Proportion of fishing hours spent in PNA waters.}
 \end{figure}
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:did}Difference-in-differences estimates for 3 different controls and 3 different specifications.
-The first three columns use our primary control group.
-Columns 4 - 6 use only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
-Columns 10 and 11 use Japanese vessels in the Pacific as controls, and hence don't include flag FEs.
-Numbers in parentheses are heteroskedasticity-robust standard errors.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-12} 
-\\[-1.8ex] & \multicolumn{11}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
-\hline \\[-1.8ex] 
- Constant & 6.345$^{***}$ & 7.863$^{***}$ & 10.322$^{***}$ & 7.124$^{***}$ & 9.007$^{***}$ & 9.933$^{***}$ & 6.057$^{***}$ & 7.584$^{***}$ & 10.194$^{***}$ & 22.625$^{***}$ & 24.731$^{***}$ \\ 
-  & (0.186) & (0.274) & (0.404) & (0.265) & (0.341) & (0.620) & (0.193) & (0.279) & (0.538) & (0.629) & (0.683) \\ 
-  & & & & & & & & & & & \\ 
- post & $-$0.052 & 1.134$^{***}$ & 1.115$^{***}$ & $-$1.199$^{***}$ & $-$0.279 & 0.124 & $-$0.284 & 1.013$^{***}$ & 1.166$^{***}$ & 2.330$^{***}$ & 3.991$^{***}$ \\ 
-  & (0.303) & (0.304) & (0.339) & (0.435) & (0.429) & (0.436) & (0.318) & (0.318) & (0.357) & (0.890) & (0.877) \\ 
-  & & & & & & & & & & & \\ 
- treated & $-$1.142$^{***}$ & $-$0.839$^{***}$ & 0.010 & $-$1.977$^{***}$ & $-$1.675$^{***}$ & 0.626 & $-$0.877$^{***}$ & $-$0.536$^{**}$ & 0.150 & $-$18.190$^{***}$ & $-$18.257$^{***}$ \\ 
-  & (0.214) & (0.209) & (0.281) & (0.284) & (0.274) & (0.416) & (0.221) & (0.215) & (0.297) & (0.673) & (0.661) \\ 
-  & & & & & & & & & & & \\ 
- sate2 & 12.579$^{***}$ & 11.589$^{***}$ & 11.340$^{***}$ & 12.709$^{***}$ & 11.850$^{***}$ & 11.749$^{***}$ & 12.631$^{***}$ & 11.599$^{***}$ & 11.349$^{***}$ & 14.346$^{***}$ & 12.967$^{***}$ \\ 
-  & (0.197) & (0.199) & (0.232) & (0.212) & (0.213) & (0.246) & (0.199) & (0.201) & (0.235) & (0.303) & (0.309) \\ 
-  & & & & & & & & & & & \\ 
- sate3 & 14.675$^{***}$ & 13.587$^{***}$ & 13.328$^{***}$ & 14.799$^{***}$ & 13.894$^{***}$ & 13.795$^{***}$ & 14.958$^{***}$ & 13.804$^{***}$ & 13.566$^{***}$ & 15.187$^{***}$ & 13.719$^{***}$ \\ 
-  & (0.260) & (0.262) & (0.307) & (0.286) & (0.287) & (0.329) & (0.264) & (0.266) & (0.315) & (0.402) & (0.410) \\ 
-  & & & & & & & & & & & \\ 
- post:treated & $-$0.515$^{*}$ & $-$0.833$^{***}$ & $-$0.934$^{***}$ & 0.562 & 0.373 & $-$0.176 & $-$0.439 & $-$0.814$^{***}$ & $-$1.084$^{***}$ & $-$3.209$^{***}$ & $-$3.715$^{***}$ \\ 
-  & (0.281) & (0.276) & (0.310) & (0.413) & (0.402) & (0.407) & (0.293) & (0.287) & (0.326) & (0.811) & (0.799) \\ 
-  & & & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-Control & All & All & All & PNA & PNA & PNA & -CHN & -CHN & -CHN & JPN & JPN \\ 
-Month FE & No & Yes & Yes & No & Yes & Yes & No & Yes & Yes & No & Yes \\ 
-Flag FE & No & No & Yes & No & No & Yes & No & No & Yes & No & No \\ 
-Observations & 37,840 & 37,840 & 30,359 & 30,583 & 30,583 & 25,034 & 36,415 & 36,415 & 28,934 & 34,047 & 34,047 \\ 
-R$^{2}$ & 0.171 & 0.200 & 0.208 & 0.178 & 0.208 & 0.215 & 0.173 & 0.203 & 0.211 & 0.260 & 0.280 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{11}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
+\input{tab/main_DID}
 
@@
 	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
+	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
 		number of vessels by month for all vessels. Vertical dashed lines

### 2019-01-23 docs/tab/main_DID.tex
Added a bunch of graphs and tables

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:did}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 2.148$^{***}$ & 3.723$^{***}$ & 2.148$^{***}$ & 2.670$^{***}$ & 5.218$^{***}$ & 11.130$^{***}$ & 12.909$^{***}$ & 12.909$^{***}$ & 0.520$^{***}$ & 0.869$^{***}$ \\ 
-  & (0.019) & (0.004) & (0.019) & (0.040) & (0.022) & (0.032) & (0.014) & (0.014) & (0.021) & (0.004) \\ 
+ Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 12.535$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
+  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.021) & (0.021) & (0.041) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Post & 0.589$^{***}$ & $-$0.224$^{***}$ & 0.589$^{***}$ & 1.280$^{***}$ & $-$0.216$^{***}$ & $-$0.288$^{***}$ & 0.157$^{***}$ & 0.157$^{***}$ & $-$0.056$^{**}$ & $-$0.097$^{***}$ \\ 
-  & (0.022) & (0.006) & (0.022) & (0.045) & (0.032) & (0.046) & (0.016) & (0.016) & (0.027) & (0.012) \\ 
+ Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.232$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
+  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Treated & $-$0.112$^{***}$ & 0.021$^{***}$ & $-$0.112$^{***}$ & $-$0.153$^{***}$ & 0.239$^{***}$ & 0.053 & $-$0.059$^{***}$ & $-$0.059$^{***}$ & 0.088$^{***}$ & $-$0.043$^{***}$ \\ 
-  & (0.022) & (0.004) & (0.022) & (0.045) & (0.025) & (0.037) & (0.015) & (0.015) & (0.023) & (0.006) \\ 
+ Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & $-$0.013 & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
+  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
   & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.017 & 0.019$^{***}$ & 0.017 & $-$0.132$^{**}$ & $-$0.156$^{***}$ & $-$0.114$^{**}$ & $-$0.001 & $-$0.001 & 0.006 & 0.055$^{***}$ \\ 
-  & (0.025) & (0.007) & (0.025) & (0.052) & (0.038) & (0.054) & (0.018) & (0.018) & (0.031) & (0.014) \\ 
+ Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.047$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
+  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
   & & & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 38,607 & 114,195 & 38,607 & 36,939 & 114,967 & 114,967 & 38,607 & 38,607 & 2,135 & 3,130 \\ 
-R$^{2}$ & 0.083 & 0.040 & 0.083 & 0.087 & 0.004 & 0.002 & 0.013 & 0.013 & 0.028 & 0.028 \\ 
+Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
+R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.272 & 0.272 & 0.081 & 0.283 \\ 
 \hline 

### 2019-01-23 docs/tab/sp_corr.tex
Added a bunch of graphs and tables

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 76.695$^{***}$ (4.382) & 76.695$^{***}$ (4.382) \\ 
  Months & 4.342$^{***}$ (0.419) & 4.342$^{***}$ (0.419) \\ 
  Months $^2$ & $-$0.026$^{***}$ (0.007) & $-$0.026$^{***}$ (0.007) \\ 
  Months $^3$ & $-$0.003$^{***}$ (0.0004) & $-$0.003$^{***}$ (0.0004) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 72 & 72 \\ 
R$^{2}$ & 0.704 & 0.704 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-01-23 scripts/content/sp_corr.R

@@ -1,0 +1,127 @@
+###############
+#   sp_corr   #
+###############
+
+################################################################
+# Generates some measures of crowding like the bumber of cells
+# with BOTH treated and control vessels and the spatial correlation
+# between treated and control for a given month.
+# 
+# Number of cells that had treated and control vessels (A) and
+# spatial correlation in the presence-absence of treated and
+# control vessels per cell (B).
+################################################################
+
+#### SET UP ######################################################################################
+
+# Load packages
+library(raster)
+library(tidyverse)
+
+
+## Load data
+
+# Find files
+files <- list.files(path = here::here("data", "spatial", "monthly_rasterized_effort_by_region"))
+
+# Stack files
+rs <- stack(here::here("data", "spatial", "monthly_rasterized_effort_by_region", files))
+
+
+##### CALCULATIONS #########################################################################
+
+# Put into a data.frame
+corr <- raster::as.data.frame(rs, xy = T) %>%
+  gather(group, hours, -c(x, y)) %>%
+  mutate(year = as.numeric(
+    str_extract(group, "[:digit:]+")),
+    month = as.numeric(str_replace_all(str_extract(group, "\\.[:digit:]+\\."), "\\.", "")),
+    group = str_extract(group, "[:alpha:]+"),
+    hours = ifelse(hours > 0, 1, 0)) %>%
+  spread(group, hours, fill = 0) %>% 
+  mutate(both = (Control > 0 & Treated > 0) * 1,
+         post = year > 2014,
+         date = lubridate::date(paste(year, month, 01, sep = "-")))
+
+# Calculate number of cells with both vessels
+n_both <- corr %>%
+  filter(both > 0) %>% 
+  group_by(year, month, date, post) %>% 
+  summarize(n = sum(both)) %>% 
+  ungroup() %>% 
+  mutate(dif = lubridate::interval(lubridate::date("2015-01-01"), date)%/% months(1))
+
+
+# Calculate spatial correlation
+corr_both <- corr %>%
+  drop_na() %>%
+  group_by(year, month, date, post) %>%
+  summarize(cor = cor(Control, Treated)) %>% 
+  ungroup(dif = lubridate::interval(lubridate::date("2015-01-01"), date)%/% months(1))
+
+
+
+#### FIT THE MODELS ######################################################################
+
+n_model <- lm(n ~ dif + I(dif^2) + I(dif^3), data = n_both)
+corr_model <- lm(n ~ dif + I(dif^2) + I(dif^3), data = n_both)
+
+
[…]

### 2019-01-23 scripts/content/spatial_redistribution.R

@@ -1,0 +1,178 @@
+###############################
+#   spatial_redistribution    #
+###############################
+
+
+########################################################################
+# This script calculates the change in proportion of allocation of
+# fishing effort from TREATED vessels across the units of space that
+# we defined when we rasterized the shapefiles.
+########################################################################
+
+#### SET UP ############################################################
+# Load packages
+library(tidyverse)
+
+# Monthly  for analyses
+raster_month_region <- readRDS(file = here::here("data", "monthly_rasterized_effort_by_region.rds")) %>% 
+  filter(treated == "Treated")
+
+
+redistribution_model_data <-
+  expand.grid(id = unique(raster_month_region$id),
+              year = 2012:2017,
+              month = 1:12) %>% 
+  arrange(id, year, month) %>%
+  as.tibble() %>%
+  left_join(raster_month_region, by = c("id", "year", "month")) %>% 
+  group_by(year, month) %>% 
+  mutate(total_hours = sum(hours, na.rm = t)) %>% 
+  ungroup() %>% 
+  group_by(year, month, id, total_hours) %>%
+  summarize(h = sum(hours, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(h_prop = h / total_hours) %>% 
+  mutate(h_prop = ifelse(is.na(h_prop), 0, h_prop)) %>% 
+  mutate(date = lubridate::date(paste(year, month, 1, sep = "/")),
+         post = year >= 2015,
+         year_c = as.factor(year)) %>% 
+  group_by(id) %>% 
+  mutate(max_p = max(h_prop)) %>% 
+  ungroup() %>% 
+  filter(max_p > 0.07)
+
+model <- lm(h_prop ~ year_c * id, data = redistribution_model_data)
+
+
+## FIGURES #################################################################
+
+##########################################################################
+# Monthly relative allocation of fishing effort by PIPA-fishing vessels
+# before and after PIPA by region. Colors indicate the pre-post period.
+# Solid line across points shows local mean with a region-specific loess
+# smoother. Solid line indicates PIPA closurePIPA closure.
+###########################################################################
+
+
+terms_order <- c("PIPA-PIPA",
+                 "EEZ-KIR",
+                 "HS-KIR",
+                 "HS-HS")
+
[…]

### 2019-01-23 docs/PIPA_Palau.tex
Updated manuscript, ready to print and proof read before sending to John

@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
-for each model. Top panel indicates variable, x-axis represents model
-specification, and y-axis coefficient estimate. [QUESTION FOR JC: delete the intercept panel.]}
+\includegraphics{img/other_specifications.pdf}
+\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
+for our variables of interest using different model specifications. Table \ref{tab:main_DID}
+reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
 \end{figure}
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
+\includegraphics{img/fishing_raster.png}
+\caption{\label{fig:fishing_raster}Yearly
 spatial distribution of fishing effort by treated and control vessels.
-Colors have been adjusted relative to the maximum observed by group and
-year. Red polygons show LGMPAs in the region. For visualization purposes
-only some years are presented, the full 2012 - 2017 period is shown in
-Figure \ref{fig:fishing_raster_full}.
-[QUESTION FOR JC: we should include all years in the main text.
-Is there a way to normalize this, e,g.
-color corresponds to \% of total fishing effort, so it's easier to compare?]}
+Color corresponds to \% of total fishing effort in each panel.
+Red polygons show LSMPAs in the region.}
 \end{figure}
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend}Monthly
+\includegraphics{img/redist_trend.pdf}
+\caption{\label{fig:redist_trend}Monthly
 relative allocation of fishing effort by PIPA-fishing vessels before and
@@
 line indicates PIPA closure. Note that inflection points of
-the loess smoother are not affected by the addition of satellites.
-[QUESTION FOR JC: this figure needs a lot of work.
-subplot titles need to be more intuitive.
-I would combine all EEZ KIR into one group and all HS KIR into one group.]}
+the loess smoother are not affected by the addition of satellites.}
 \end{figure}
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\label{fig:unnamed-chunk-15}\label{fig:mean_change}Coefficient
+\includegraphics{img/mean_change.pdf}
+\caption{\label{fig:mean_change}Coefficient
 estimates for the redistribution regression. Each panel shows the
-region-specific coefficients, with heteroskedasticity-robust standard
-errors as error bars. The horizontal dashed line represents 0 change
-relative to the 2012 region-specific levels. [QUESTION FOR JC: just do 95\% confidence intervals.]}
+region-specific coefficients, with 95\% condifence intervals
+as error bars. The horizontal dashed line represents 0 change
+relative to the 2012 region-specific levels.}
 \end{figure}
 
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-16}\label{tab:mean_change}Coefficient estimates for the interaction of year and region.
-Each row represents a region, each column a year.
-Numbers in parentheses are heteroskedaticity-robust standard errors.
-R2 = 0.47 (F(95, 1056) = 9.99; p < 0.001).
-* < 0.1; ** p < 0.05; ***p < 0.01.}
-\centering
-\begin{tabular}[t]{llllll}
-\toprule
-term & 2013 & 2014 & 2015 & 2016 & 2017\\
-\midrule
-PIPA PIPA 1 & -0.062 (0.026)** & 0.085 (0.043)** & -0.086 (0.026)*** & -0.079 (0.025)*** & -0.074 (0.025)***\\
-EEZ KIR 1 & -0.034 (0.030) & 0.035 (0.038) & 0.042 (0.045) & -0.035 (0.031) & -0.023 (0.032)\\
-EEZ KIR 2 & 0.001 (0.009) & 0.032 (0.019)* & 0.142 (0.061)** & 0.014 (0.013) & 0.014 (0.015)\\
-EEZ KIR 3 & -0.188 (0.075)** & -0.061 (0.072) & -0.118 (0.069)* & -0.093 (0.083) & -0.098 (0.083)\\
-HS KIR 1 & -0.003 (0.011) & 0.016 (0.012) & 0.038 (0.013)*** & 0.004 (0.013) & 0.037 (0.018)**\\
-\addlinespace
-HS KIR 2 & 0.009 (0.006) & 0.004 (0.006) & -0.000 (0.009) & 0.022 (0.010)** & 0.008 (0.006)\\
-HS KIR 3 & -0.002 (0.009) & 0.003 (0.009) & -0.008 (0.011) & 0.022 (0.011)* & 0.064 (0.024)***\\
-HS HS 1 & 0.021 (0.015) & 0.027 (0.017) & 0.045 (0.017)*** & 0.030 (0.017)* & 0.014 (0.015)\\
-EEZ FSM 1 & 0.018 (0.033) & -0.015 (0.025) & 0.000 (0.037) & 0.012 (0.025) & -0.001 (0.021)\\
-EEZ MHL 1 & 0.037 (0.022) & 0.025 (0.010)** & -0.006 (0.009) & 0.052 (0.032) & -0.000 (0.006)\\
-\addlinespace
-EEZ NRU 1 & 0.046 (0.021)** & 0.044 (0.020)** & 0.003 (0.017) & 0.033 (0.015)** & 0.050 (0.025)**\\
-EEZ PNG 2 & 0.196 (0.072)*** & -0.106 (0.041)*** & -0.132 (0.043)*** & -0.064 (0.048) & 0.001 (0.049)\\
-EEZ SLB 1 & 0.083 (0.056) & -0.019 (0.032) & -0.009 (0.038) & 0.081 (0.053) & 0.076 (0.046)*\\
-EEZ TUV 1 & -0.055 (0.037) & -0.033 (0.040) & -0.063 (0.037)* & 0.018 (0.046) & -0.026 (0.038)\\
-HS COK 1 & -0.003 (0.008) & -0.004 (0.008) & -0.003 (0.011) & -0.007 (0.008) & -0.003 (0.008)\\
-\bottomrule
-\end{tabular}
-\end{table}
+\clearpage
+\begin{landscape}
+
+\input{tab/mean_change}
+
+\end{landscape}
+\clearpage
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
-\caption{\label{fig:unnamed-chunk-17}\label{fig:sp_corr}Number of cells that
+\includegraphics{img/sp_corr.pdf}
+\caption{\label{fig:sp_corr}Number of cells that
 had treated and control vessels (A) and spatial correlation in the
@@
 \end{figure}
+
+\input{tab/sp_corr}
 
@@
 
-\clearpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\hypertarget{stream-of-data-by-vessel-group-and-period}{%
-\subsection{Stream of data by vessel, group, and
-period}\label{stream-of-data-by-vessel-group-and-period}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
-fishing events by vessels through time. Each line represents a vessel,
-with dots indicating months with fishing activity and colors indicating
-the pre and post periods.}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-	\centering
-	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
-		number of vessels by month for all vessels. Vertical dashed lines
-		indicates dates when satellites were added, solid line indicates PIPA
-		closurePIPA closure.}
-\end{figure}
-
-\clearpage
-
-\hypertarget{longliners}{%
-\subsection{Longliners}\label{longliners}}
-
-Longliners show a similar pattern of effort reduction. However, the
-magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
-including month and flag FEs for the general treatment-control groups,
-or when excluding Chinese vessels. This, along with higher standard
-error values suggest that longliners have a smaller and more variable
-response to the implementation of LSMPAs.
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications.
+%\clearpage
+%
+%\hypertarget{appendix}{%
+%\section{Appendix}\label{appendix}}
+%
+%\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+%
+%\hypertarget{stream-of-data-by-vessel-group-and-period}{%
+%\subsection{Stream of data by vessel, group, and
+%period}\label{stream-of-data-by-vessel-group-and-period}}
+
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
+%\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
+%fishing events by vessels through time. Each line represents a vessel,
+%with dots indicating months with fishing activity and colors indicating
+%the pre and post periods.}
+%\end{figure}
+
+%\clearpage
+
+%\begin{figure}
+%	\centering
+%	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+%	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
+%		number of vessels by month for all vessels. Vertical dashed lines
+%		indicates dates when satellites were added, solid line indicates PIPA
+%		closurePIPA closure.}
+%\end{figure}
+
+%\clearpage
+
+%\hypertarget{longliners}{%
+%\subsection{Longliners}\label{longliners}}
+
+%Longliners show a similar pattern of effort reduction. However, the
+%magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
+%including month and flag FEs for the general treatment-control groups,
+%or when excluding Chinese vessels. This, along with higher standard
+%error values suggest that longliners have a smaller and more variable
+%response to the implementation of LSMPAs.
+
+%\begin{table}[!htbp] \centering 
+%  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications.
 The first three columns use all data for controls.
@@
 Numbers in parentheses are heteroskedastic-robust standard errors.}
-  \label{} 
-\small 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-7} 
-\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
-\hline \\[-1.8ex] 
- Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
-  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
-  & & & & & & \\ 
- post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
-  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
-  & & & & & & \\ 
- treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
-  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
-  & & & & & & \\ 
- sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
-  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
-  & & & & & & \\ 
- sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
-  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
-  & & & & & & \\ 
- post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
-  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
-  & & & & & & \\ 
-\hline \\[-1.8ex] 
-Control & All & All & All & -CHN & -CHN & -CHN \\ 
-Month FE & No & Yes & Yes & No & Yes & Yes \\ 
-Flag FE & No & No & Yes & No & No & Yes \\ 
-Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
-R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\clearpage
-
-\hypertarget{quarterly-did-interactions}{%
-\subsubsection{Quarterly DID
-interactions}\label{quarterly-did-interactions}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
-and treatment. Control group is all vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
-and treatment. Control group is vessels from PNA.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
-and treatment. Control group excludes Chinese vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
-and treatment. Control group is japanese vessels.}
-\end{figure}
-
-\hypertarget{year-month-did-interactions}{%
-\subsubsection{Year-month DID
-interactions}\label{year-month-did-interactions}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
-year-month and treatment. Control group is all vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
-year-month and treatment. Control group is vessels from PNA.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
-year-month and treatment. Control group excludes Chinese vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
-year-month and treatment. Control group is japanese vessels.}
-\end{figure}
-
-\hypertarget{other-measures-of-change-in-behavior}{%
-\subsection{Other measures of change in
-behavior}\label{other-measures-of-change-in-behavior}}
-
-Global Fishing Watch data includes two variables of interest that are
-readily available: distance from shore and distance from port. We use
-these as variables of interest and perform the following regression:
-
-\[
-y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
-\]
-
-Where \(y\) is our variable of interest, \(Year\) represent year
-dummies, with 2012 as the reference level, and \(Treated\) indicates
-wether a vessel belongs to the treated or control group.
-
-\clearpage
-
-\hypertarget{distance-from-shore}{%
-\subsubsection{Distance from shore}\label{distance-from-shore}}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & distance\_from\_shore \\ 
-\hline \\[-1.8ex] 
- Constant & 233,057.900$^{***}$ \\ 
-  & (1,558.294) \\ 
-  & \\ 
- year\_c2013 & $-$818.044 \\ 
-  & (2,623.263) \\ 
-  & \\ 
- year\_c2014 & 14,220.260$^{***}$ \\ 
-  & (1,701.637) \\ 
-  & \\ 
- year\_c2015 & 140,980.200$^{***}$ \\ 
-  & (1,668.140) \\ 
-  & \\ 
- year\_c2016 & 32,557.750$^{***}$ \\ 
-  & (1,584.182) \\ 
-  & \\ 
- year\_c2017 & 168,283.100$^{***}$ \\ 
-  & (1,653.912) \\ 
-  & \\ 
- treated & $-$11,371.280$^{***}$ \\ 
-  & (1,688.879) \\ 
-  & \\ 
- year\_c2013:treated & 62,899.900$^{***}$ \\ 
-  & (3,274.205) \\ 
-  & \\ 
- year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
-  & (1,834.090) \\ 
-  & \\ 
- year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
-  & (1,821.587) \\ 
-  & \\ 
- year\_c2016:treated & 72,512.980$^{***}$ \\ 
-  & (1,739.976) \\ 
-  & \\ 
- year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
-  & (1,805.322) \\ 
-  & \\ 
-\hline \\[-1.8ex] 
-Observations & 4,937,666 \\ 
-R$^{2}$ & 0.032 \\ 
-Adjusted R$^{2}$ & 0.032 \\ 
-Residual Std. Error & 297,128.600 (df = 4937654) \\ 
-F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\clearpage
-
-\hypertarget{distance-from-ports}{%
-\subsubsection{Distance from ports}\label{distance-from-ports}}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:dist_port}Regression results for distance from shore} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & distance\_from\_port \\ 
-\hline \\[-1.8ex] 
- Constant & 362.707$^{***}$ \\ 
-  & (1.971) \\ 
-  & \\ 
- year\_c2013 & 9.082$^{***}$ \\ 
-  & (3.198) \\ 
-  & \\ 
- year\_c2014 & 105.414$^{***}$ \\ 
-  & (2.148) \\ 
-  & \\ 
- year\_c2015 & 357.746$^{***}$ \\ 
-  & (2.113) \\ 
-  & \\ 
- year\_c2016 & 112.441$^{***}$ \\ 
-  & (2.009) \\ 
-  & \\ 
- year\_c2017 & 356.506$^{***}$ \\ 
-  & (2.099) \\ 
-  & \\ 
- treated & 149.653$^{***}$ \\ 
-  & (2.249) \\ 
-  & \\ 
- year\_c2013:treated & 26.366$^{***}$ \\ 
-  & (4.125) \\ 
-  & \\ 
- year\_c2014:treated & 50.808$^{***}$ \\ 
-  & (2.453) \\ 
-  & \\ 
- year\_c2015:treated & $-$151.268$^{***}$ \\ 
-  & (2.422) \\ 
-  & \\ 
- year\_c2016:treated & $-$49.445$^{***}$ \\ 
-  & (2.311) \\ 
-  & \\ 
- year\_c2017:treated & $-$252.334$^{***}$ \\ 
-  & (2.390) \\ 
-  & \\ 
-\hline \\[-1.8ex] 
-Observations & 4,937,666 \\ 
-R$^{2}$ & 0.047 \\ 
-Adjusted R$^{2}$ & 0.047 \\ 
-Residual Std. Error & 391.757 (df = 4937654) \\ 
-F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\hypertarget{effort-redistribution}{%
-\subsection{Effort redistribution}\label{effort-redistribution}}
-
-\hypertarget{rasterized-regions}{%
-\subsubsection{Rasterized regions}\label{rasterized-regions}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
-\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
-regions. Each color (number) indicates a distinct region.}
-\end{figure}
-
-\hypertarget{fishing-raster}{%
-\subsubsection{Fishing raster}\label{fishing-raster}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
-\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
-rasters of fishing hours for each group.}
-\end{figure}
-
-\clearpage
+%  \label{} 
+%\small 
+%\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
+%\\[-1.8ex]\hline 
+%\hline \\[-1.8ex] 
+% & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+%\cline{2-7} 
+%\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
+%\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+%\hline \\[-1.8ex] 
+% Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
+%  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
+%  & & & & & & \\ 
+% post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
+%  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
+%  & & & & & & \\ 
+% treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
+%  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
+%  & & & & & & \\ 
+% sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
+%  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
+%  & & & & & & \\ 
+% sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
+%  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
+%  & & & & & & \\ 
+% post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
+%  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
+%  & & & & & & \\ 
+%\hline \\[-1.8ex] 
+%Control & All & All & All & -CHN & -CHN & -CHN \\ 
+%Month FE & No & Yes & Yes & No & Yes & Yes \\ 
+%Flag FE & No & No & Yes & No & No & Yes \\ 
+%Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
+%R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
+%\hline 
+%\hline \\[-1.8ex] 
+%\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+%\end{tabular} 
+%\end{table}
+%
+%\clearpage
+%
+%\hypertarget{quarterly-did-interactions}{%
+%\subsubsection{Quarterly DID
+%interactions}\label{quarterly-did-interactions}}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
+%\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
+%and treatment. Control group is all vessels.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
+%\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
+%and treatment. Control group is vessels from PNA.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
+%\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
+%and treatment. Control group excludes Chinese vessels.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
+%\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
+%and treatment. Control group is japanese vessels.}
+%\end{figure}
+%
+%\hypertarget{year-month-did-interactions}{%
+%\subsubsection{Year-month DID
+%interactions}\label{year-month-did-interactions}}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
+%\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
+%year-month and treatment. Control group is all vessels.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
+%\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
+%year-month and treatment. Control group is vessels from PNA.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
+%\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
+%year-month and treatment. Control group excludes Chinese vessels.}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
+%\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
+%year-month and treatment. Control group is japanese vessels.}
+%\end{figure}
+%
+%\hypertarget{other-measures-of-change-in-behavior}{%
+%\subsection{Other measures of change in
+%behavior}\label{other-measures-of-change-in-behavior}}
+%
+%Global Fishing Watch data includes two variables of interest that are
+%readily available: distance from shore and distance from port. We use
+%these as variables of interest and perform the following regression:
+%
+%\[
+%y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
+%\]
+%
+%Where \(y\) is our variable of interest, \(Year\) represent year
+%dummies, with 2012 as the reference level, and \(Treated\) indicates
+%wether a vessel belongs to the treated or control group.
+%
+%\clearpage
+%
+%\hypertarget{distance-from-shore}{%
+%\subsubsection{Distance from shore}\label{distance-from-shore}}
+%
+%\begin{table}[!htbp] \centering 
+%  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
+%  \label{} 
+%\begin{tabular}{@{\extracolsep{5pt}}lc} 
+%\\[-1.8ex]\hline 
+%\hline \\[-1.8ex] 
+% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+%\cline{2-2} 
+%\\[-1.8ex] & distance\_from\_shore \\ 
+%\hline \\[-1.8ex] 
+% Constant & 233,057.900$^{***}$ \\ 
+%  & (1,558.294) \\ 
+%  & \\ 
+% year\_c2013 & $-$818.044 \\ 
+%  & (2,623.263) \\ 
+%  & \\ 
+% year\_c2014 & 14,220.260$^{***}$ \\ 
+%  & (1,701.637) \\ 
+%  & \\ 
+% year\_c2015 & 140,980.200$^{***}$ \\ 
+%  & (1,668.140) \\ 
+%  & \\ 
+% year\_c2016 & 32,557.750$^{***}$ \\ 
+%  & (1,584.182) \\ 
+%  & \\ 
+% year\_c2017 & 168,283.100$^{***}$ \\ 
+%  & (1,653.912) \\ 
+%  & \\ 
+% treated & $-$11,371.280$^{***}$ \\ 
+%  & (1,688.879) \\ 
+%  & \\ 
+% year\_c2013:treated & 62,899.900$^{***}$ \\ 
+%  & (3,274.205) \\ 
+%  & \\ 
+% year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
+%  & (1,834.090) \\ 
+%  & \\ 
+% year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
+%  & (1,821.587) \\ 
+%  & \\ 
+% year\_c2016:treated & 72,512.980$^{***}$ \\ 
+%  & (1,739.976) \\ 
+%  & \\ 
+% year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
+%  & (1,805.322) \\ 
+%  & \\ 
+%\hline \\[-1.8ex] 
+%Observations & 4,937,666 \\ 
+%R$^{2}$ & 0.032 \\ 
+%Adjusted R$^{2}$ & 0.032 \\ 
+%Residual Std. Error & 297,128.600 (df = 4937654) \\ 
+%F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
+%\hline 
+%\hline \\[-1.8ex] 
+%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+%\end{tabular} 
+%\end{table}
+%
+%\clearpage
+%
+%\hypertarget{distance-from-ports}{%
+%\subsubsection{Distance from ports}\label{distance-from-ports}}
+%
+%\begin{table}[!htbp] \centering 
+%  \caption{\label{tab:dist_port}Regression results for distance from shore} 
+%  \label{} 
+%\begin{tabular}{@{\extracolsep{5pt}}lc} 
+%\\[-1.8ex]\hline 
+%\hline \\[-1.8ex] 
+% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+%\cline{2-2} 
+%\\[-1.8ex] & distance\_from\_port \\ 
+%\hline \\[-1.8ex] 
+% Constant & 362.707$^{***}$ \\ 
+%  & (1.971) \\ 
+%  & \\ 
+% year\_c2013 & 9.082$^{***}$ \\ 
+%  & (3.198) \\ 
+%  & \\ 
+% year\_c2014 & 105.414$^{***}$ \\ 
+%  & (2.148) \\ 
+%  & \\ 
+% year\_c2015 & 357.746$^{***}$ \\ 
+%  & (2.113) \\ 
+%  & \\ 
+% year\_c2016 & 112.441$^{***}$ \\ 
+%  & (2.009) \\ 
+%  & \\ 
+% year\_c2017 & 356.506$^{***}$ \\ 
+%  & (2.099) \\ 
+%  & \\ 
+% treated & 149.653$^{***}$ \\ 
+%  & (2.249) \\ 
+%  & \\ 
+% year\_c2013:treated & 26.366$^{***}$ \\ 
+%  & (4.125) \\ 
+%  & \\ 
+% year\_c2014:treated & 50.808$^{***}$ \\ 
+%  & (2.453) \\ 
+%  & \\ 
+% year\_c2015:treated & $-$151.268$^{***}$ \\ 
+%  & (2.422) \\ 
+%  & \\ 
+% year\_c2016:treated & $-$49.445$^{***}$ \\ 
+%  & (2.311) \\ 
+%  & \\ 
+% year\_c2017:treated & $-$252.334$^{***}$ \\ 
+%  & (2.390) \\ 
+%  & \\ 
+%\hline \\[-1.8ex] 
+%Observations & 4,937,666 \\ 
+%R$^{2}$ & 0.047 \\ 
+%Adjusted R$^{2}$ & 0.047 \\ 
+%Residual Std. Error & 391.757 (df = 4937654) \\ 
+%F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
+%\hline 
+%\hline \\[-1.8ex] 
+%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+%\end{tabular} 
+%\end{table}
+%
+%\hypertarget{effort-redistribution}{%
+%\subsection{Effort redistribution}\label{effort-redistribution}}
+%
+%\hypertarget{rasterized-regions}{%
+%\subsubsection{Rasterized regions}\label{rasterized-regions}}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
+%\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
+%regions. Each color (number) indicates a distinct region.}
+%\end{figure}
+%
+%\hypertarget{fishing-raster}{%
+%\subsubsection{Fishing raster}\label{fishing-raster}}
+%
+%\begin{figure}
+%\centering
+%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
+%\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
+%rasters of fishing hours for each group.}
+%\end{figure}
+%
+%\clearpage
 

### 2019-01-24 docs/PIPA_Palau.tex
Updated manuscript

@@
-\documentclass[11pt,english]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{natbib}
-\bibliographystyle{chicago}
-\usepackage{longtable,booktabs}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+\documentclass[9pttwoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
+
+\templatetype{pnasresearcharticle} % Choose template 
+% {pnasresearcharticle} = Template for a two-column research article
+% {pnasmathematics} %= Template for a one-column mathematics article
+% {pnasinvited} %= Template for a PNAS invited submission
 
@@
 
-\author{
-  Juan CarlosVillase\~{n}or-Derbez\footnote{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA} \\
-  \texttt{juancarlos@ucsb.edu}
-  \and
- John Lynham\footnote{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
-  \texttt{lynham@hawaii.edu }
-}
-
-\date{Updated on: \today}
-
-\usepackage{float}
-\floatplacement{figure}{H}
-\usepackage{lineno}
-\linenumbers
-\usepackage[bottom]{footmisc}
-\usepackage{pdflscape}
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
-% John's additional packages below
-
-\usepackage{graphicx}
-\graphicspath{{figures/}} %Setting the graphicspath
-
-\begin{document}
-\maketitle
+% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[a,1]{Juan CarlosVillase\~{n}or-Derbez}
+\author[b,1]{John Lynham}
+
+\affil[a]{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA}
+\affil[b]{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Villase\~{n}or-Derbez}
+
+% Please add here a significance statement to explain the relevance of your work
+\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality.
+The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership.
+The Significance Statement appears in the paper itself and is required for all research papers.}
+
+% Please include corresponding author, author contribution and author declaration information
+\authorcontributions{All authors contributed equally to this work}
+\authordeclaration{The authors declare that they have no conflicts of interest}
+\equalauthors{\textsuperscript{1}J.C.V.D. and J.L. contributed equally to this work.}
+\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: juancarlos\@ucsb.edu}
+
+% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
+\keywords{Marine Protected Areas $|$ Fisheries $|$ Purse Seining $|$ Marine Conservation}
+
 \begin{abstract}
@@
 
-\clearpage
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+
+\usepackage{pdflscape}
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+
+\begin{document}
+
+\maketitle
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section{Introduction}\label{introduction}
-
-Marine Protected Areas (MPAs) are intended to safeguard parts of the
+\dropcap{M}arine Protected Areas (MPAs) are intended to safeguard parts of the
 ocean from fishing and other extractive activities. Current
@@
 increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
-a small number of Large Scale Marine Protected Areas (LSMPAs).\footnote{See, for example, \citet{game_2009},  \citet{singleton_2014},\citet{boonzaier_2016}, \citet{mccauley_2016}, and \citet{alger_2017}.}
-). Today, a small number of LSMPAs make up at least 80\%
+a small number of Large Scale Marine Protected Areas (LSMPAs)\footnote{See, for example, \citep{game_2009,singleton_2014,boonzaier_2016,mccauley_2016,alger_2017}.}.
+Today, a small number of LSMPAs make up at least 80\%
 of the managed areas in the ocean \citep{toonen_2013}.
@@
 non-fishing vessels following the implementation of a network of MPAs in
-California, and find that commercial dive boats (??????) follow a
+California, and find that dive boats follow a
 fishing-the-line pattern, while some fishing boats follow an ideal free
@@
 
-\[
-y_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t},
-\]
+\begin{figure*}[h]
+\begin{align*}
+log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
+\label{eqn:did}
+\end{align*}
+\end{figure*}
 
@@
 example, if we were to do this only for Kiribati, we would have 8
-spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas
-around each EEZ, and the rest of the high seas. Whenever the buffer units
-overlap, we randomly clip one on to the other (QUESTION FOR JC: WHAT DOES THIS MEAN?).
+spatial units: PIPA, three EEZ units, three 1-degree\footnote{Currently running the 5-degree version too} buffers of high seas
+around each EEZ, and the rest of the high seas. We clipped any overlapping
+high seas buffers to avoid duplication.
 
@@
 
-\[
+\begin{figure*}[h]
+\begin{align*}
 y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
-\]
-
-Our variable of interest, \(y_{i,t}\) represents the proportion of
-fishing hours that region \(i\) receives at time \(t\). Years are
-modeled as factors (\(Year_t\)), using 2012 as the reference level.
-\(Region\) is a dummy variable for regions defined above. Our parameter (QUESTION FOR JC: VECTOR?)
-of interest is \(\beta_{3,i}\), which captures the yearly by-country
+\end{align*}
+\end{figure*}
+
+Our variable of interest, $y_{i,t}$ represents the proportion of
+fishing hours that region $i$ receives at time $t$. Years are
+modeled as factors ($Year_t$), using 2012 as the reference level.
+\(Region\) is a dummy variable for regions defined above. Our vector of parameters of
+of interest is $\beta_{3,i}$, which captures the yearly by-country
 change in proportional allocation of fishing effort relative to 2012.
+
+Finally, we inspect the crowding effects that may arise due to the reduction
+in total fishing area. We use the rasterized fishing effort and calculate two
+potential indices of crowding. For the first one, we count the number of cells
+that had fishing activity from both groups over a given month. For the second one,
+we calculate the correlation of presence/absence of fishing for both groups
+over one month. If the implementation of the reserve induces a crowding effect,
+we would expect to observe bo clear trend before the implementation of the reserve.
+The implementation would be followed by an increase in these measures, which, 
+if vessels avoid crowding, should then come back down. We therefore expect to
+have three inflection points: 1) when there is an initial increase due to MPA
+implementation, 2) When the crowding has reached its maximum and then decreases,
+and 3) when the decrease in the measure levels off, pressumably to pre-MPA levels.
+For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
+centering our time series of crowding indices on the day of implementation. Our
+explanatory variable is then the number of months before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 
+has a value of -1, whicle Feb of 2015 would receive a value of 1.
+
+\begin{figure*}[h]
+\begin{align*}
+y_t = \alpha + \beta_1 month_t + \beta_2 month_t^2 + \beta_3 month_t^3 + \beta_4 month_t ^4 + \epsilon_t
+\end{align*}
+\end{figure*}
 
@@
 crowding outside the LSMPA. We count the number of raster cells that
-had both treated and control vessels each year (Fig.
+had both treated and control vessels each month (Fig.
 \ref{fig:sp_corr}A). The pattern observed here could just be an artifact
@@
 calculate a spatial correlation of presence/absence and observe similar
-patterns (Fig. \ref{fig:sp_corr}B). While this is at the year level and
-cannot assure that vessels were in effect at the same time in the same
-place, it provides a of what we would expect to
-find if our claims of displacement are true. Spatial overlap increases
+patterns (Fig. \ref{fig:sp_corr}B). Spatial overlap increases
 in 2015 as vessels from PIPA are excluded, but then starts to decline.
-[QUESTIONS FOR JC: Is this significant?
-Can we do a daily measure?
-What about mean or shortest distance between vessels.
-Treated/Control/Combined]
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{img/VDS_year.pdf}
+\caption{\label{fig:VDS_year}Vessel-days for all PNA countries (including Tokelau).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/VDS_country_year.pdf}
+\caption{\label{fig:VDS_country_year}Vessel-days for all PNA countries (including Tokelau) by country.
+The top panel shows vessel days in absolute numbers, while the bottom panel shows the proportion
+of each year. The left and right columns show fishing and non-fishing hours.
+[JOHN: I prefer the absolute hours one, but what do you prefer?]}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/hist_kir_fishing.pdf}
+\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place
+within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel
+}
+\end{figure}
+
 \clearpage
@@
 
-%\begin{figure}[h]
-%	\caption{Map of the Four Protected Areas}
-%	\label{fig:maps}
-%	\includegraphics[width=0.8\textwidth]{Color_V1.png}
-%	Notes: ... .
-%\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
+	\caption{Map of the Four Protected Areas}
+	\label{fig:maps}
+\end{figure}
 
@@
 
-\section{Conclusion}\label{conclude}
-
 \begin{figure}[h]
+	\includegraphics[width=0.75\textwidth]{img/Fishing_effort_Palau_relative_PNA}
 	\caption{Fishing Effort in Palau Relative to the Total PNA Area}
-%	\includegraphics[width=0.75\textwidth]{Fishing_effort_Palau_relative_PNA}
 \end{figure}
@@
 \begin{figure}[h]
+	\includegraphics[width=0.75\textwidth]{img/By_flag_Fishing_effort_Palau_relative_PNA}
 	\caption{Fishing Effort in Palau Relative to the Total PNA Area By Distant Water Fishing Fleet}
-%	\includegraphics[width=0.75\textwidth]{By_flag_Fishing_effort_Palau_relative_PNA}
 \end{figure}
@@
 
-\hypertarget{further-work}{%
-\section{Further work}\label{further-work}}
-
-\begin{itemize}
-\tightlist
-\item
-  Distance traveled
-\item
-  Non-fishing hours at sea
-\item
-  Monthly crowdnes (same approach as now, but monthly instead of yearly)
-\item
-  Number of vessels per cell as another measure of crowdness (this is a
-  more real one)
-\item
-  Repeat raster exercise for Revillagigedo and other recently
-  implemented LSMPAs. It would be great to have a pannel figure of 3 or
-  4 other LSMPAs that show wher effort was and where it went to
-  generalize our results.
-\item
-  John talked about this being relevant to Palau (their upcoming LSMPA).
-  We might want to talk about where the vessels that are there would go.
-\end{itemize}
-
+\section{Conclusion}\label{conclude}
+
+\clearpage
+
+\section{References}\label{references}
 \bibliography{references}

### 2019-01-24 docs/tab/sp_corr.tex
Updated manuscript

@@
 \hline \\[-1.8ex] 
- Constant & 76.695$^{***}$ (4.382) & 76.695$^{***}$ (4.382) \\ 
-  Months & 4.342$^{***}$ (0.419) & 4.342$^{***}$ (0.419) \\ 
-  Months $^2$ & $-$0.026$^{***}$ (0.007) & $-$0.026$^{***}$ (0.007) \\ 
-  Months $^3$ & $-$0.003$^{***}$ (0.0004) & $-$0.003$^{***}$ (0.0004) \\ 
+ Constant & 65.538$^{***}$ (5.878) & 0.409$^{***}$ (0.016) \\ 
+  Months & 4.429$^{***}$ (0.402) & 0.010$^{***}$ (0.001) \\ 
+  Months $^2$ & 0.060$^{*}$ (0.033) & 0.00003 (0.0001) \\ 
+  Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
+  I(dif$\hat{\mkern6mu}$4) & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
  \hline \\[-1.8ex] 
@@
 Observations & 72 & 72 \\ 
-R$^{2}$ & 0.704 & 0.704 \\ 
+R$^{2}$ & 0.741 & 0.631 \\ 
 \hline 

### 2019-01-24 rmd/Manuscript.Rmd
Updated manuscript

@@
 
-<!-- antes de 06/01/14 habian 3 sats, despues 6 hasta 12/31/15, luego 10 hasta 2017 y ahora hay muchos jaja -->
-
 The first analysis focuses on identifying the response of fishing vessels to PIPA closure.
@@
          term = str_replace(term, "id", ""),
-         term = fct_relevel(term, terms_order)) %>% 
+         term = fct_relevel(term, terms_order2)) %>% 
   filter(year == 2015) %>%
@@
                    layer = "regions") %>% 
-  filter(!id %in% eezs_exclude) %>%
+  # filter(!id %in% eezs_exclude) %>%
   left_join(change_2015_by_region, by = "id")
@@
   scale_fill_gradientn(colours = colorRamps::matlab.like(20)) +
-  ggtheme_plot() +
+  # ggtheme_plot() +
   guides(fill = guide_colorbar(title = bquote(Delta)))

### 2019-01-24 docs/template.tex
Added PNAS LaTeX templates

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\title{Template for preparing your research report submission to PNAS using Overleaf}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,c,1]{Author One}
\author[b,1,2]{Author Two} 
\author[a]{Author Three}

\affil[a]{Affiliation One}
\affil[b]{Affiliation Two}
\affil[c]{Affiliation Three}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{T}his PNAS journal template is provided to help you write your work in the correct journal format.  Instructions for use are provided below.

Note: please start your introduction without including the word ``Introduction'' as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.

\section*{Guide to using this template on Overleaf}

Please note that whilst this template provides a preview of the typeset manuscript for submission, to help in this preparation, it will not necessarily be the final publication layout. For more detailed information please see the \href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information for Authors}.

If you have a question while using this template on Overleaf, please use the help menu (``?'') on the top bar to search for \href{https://www.overleaf.com/help}{help and tutorials}. You can also \href{https://www.overleaf.com/contact}{contact the Overleaf support team} at any time with specific questions about your manuscript or feedback on the template.

\subsection*{Author Affiliations}

Include department, institution, and complete address, with the ZIP/postal code, for each author. Use lower case letters to match authors with institutions, as shown in the example. Authors with an ORCID ID may supply this information at submission.

\subsection*{Submitting Manuscripts}

All authors must submit their articles at \href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you are using Overleaf to write your article, you can use the ``Submit to PNAS'' option in the top bar of the editor window.

\subsection*{Format}

Many authors find it useful to organize their manuscripts with the following order of sections;  Title, Author Affiliation, Keywords, Abstract, Significance Statement, Results, Discussion, Materials and methods, Acknowledgments, and References. Other orders and headings are permitted.

\subsection*{Manuscript Length}

PNAS generally uses a two-column format averaging 67 characters, including spaces, per line. The maximum length of a Direct Submission research article is six pages and a Direct Submission Plus research article is ten pages including all text, spaces, and the number of characters displaced by figures, tables, and equations.  When submitting tables, figures, and/or equations in addition to text, keep the text for your manuscript under 39,000 characters (including spaces) for Direct Submissions and 72,000 characters (including spaces) for Direct Submission Plus.

\subsection*{References}

References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric}. All references should be included in the main manuscript file.

\subsection*{Data Archival}

PNAS must be able to archive the data essential to a published article. Where such archiving is not possible, deposition of data in public databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata, and others outlined in the Information for Authors, is acceptable.

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/site/authors/language-editing.xhtml). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{img/LSMPAs_map.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:frog}
\end{figure}

\begin{SCfigure*}[\sidecaptionrelwidth][t]
\centering
\includegraphics[width=11.4cm,height=11.4cm]{img/LSMPAs_map.pdf}
\caption{This caption would be placed at the side of the figure, rather than below it.}\label{fig:side}
\end{SCfigure*}

\subsection*{Digital Figures}

Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for figures that will appear in the main text, and images must be final size. Authors may submit U3D or PRC files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format.  Color images must be in RGB (red, green, blue) mode. Include the font files for any text.

Figures and Tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

Figure \ref{fig:frog} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide. Use \verb|\begin{SCfigure*}...\end{SCfigure*}| for a wide figure with side captions.

\subsection*{Tables}
In addition to including your tables within this manuscript file, PNAS requires that each table be uploaded to the submission separately as Table file.  Please ensure that each table .tex file contains a preamble, the \verb|\begin{document}| command, and the \verb|\end{document}| command. This is necessary so that the submission system can convert each file to PDF.

\subsection*{Single column equations}

Authors may use 1- or 2-column equations in their article, according to their preference.

To allow an equation to span both columns, use the \verb|\begin{figure*}...\end{figure*}| environment mentioned above for figures.

Note that the use of the \verb|widetext| environment for equations is not recommended, and should not be used.

\begin{figure*}[bt!]
\begin{align*}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \numberthis \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3. 
\end{align*}
\end{figure*}

\begin{table}%[tbhp]
\centering
\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}

\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

\subsection*{Supporting Information (SI)}

Authors should submit SI as a single separate PDF file, combining all text, figures, tables, movie legends, and SI references.  PNAS will publish SI uncomposed, as the authors have provided it.  Additional details can be found here: \href{http://www.pnas.org/page/authors/journal-policies}{policy on SI}.  For SI formatting instructions click \href{https://www.pnascentral.org/cgi-bin/main.plex?form_type=display_auth_si_instructions}{here}.  The PNAS Overleaf SI template can be found \href{https://www.overleaf.com/latex/templates/pnas-template-for-supplementary-information/wqfsfqwyjtsd}{here}.  Refer to the SI Appendix in the manuscript at an appropriate point in the text. Number supporting figures and tables starting with S1, S2, etc.

Authors who place detailed materials and methods in an SI Appendix must provide sufficient detail in the main text methods to enable a reader to follow the logic of the procedures and results and also must reference the SI methods. If a paper is fundamentally a study of a new method or technique, then the methods must be described completely in the main text.

\subsubsection*{SI Datasets}

Supply Excel (.xls), RTF, or PDF files. This file type will be published in raw format and will not be edited or composed.

\subsubsection*{SI Movies}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and submit a brief legend for each movie in a Word or RTF file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.

\subsubsection*{3D Figures}

Supply a composable U3D or PRC file so that it may be edited and composed. Authors may submit a PDF file but please note it will be published in raw format and will not be edited or composed.

\matmethods{Please describe your materials and methods here. This can be more than one paragraph, and may contain subsections and equations as required. Authors should include a statement in the methods section describing how readers will be able to access the data in the paper.

\subsection*{Subsection for Method}
Example text for subsection.
}

\showmatmethods{} % Display the Materials and Methods section

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

\showacknow{} % Display the acknowledgments section

% Bibliography
\bibliography{references}

\end{document}

### 2019-01-24 docs/PIPA_Palau.tex
Updated some figures and tables that had some details. Updated manuscript to send to John

@@
 Large-scale Marine Protected Areas (LSMPAs) have seen a significant
-increase over the last years. Fishing effort is effectively eliminated
-within these protected areas upon implementation. The benefits of
-reducing effort have been largely studied, but little empirical works
-evaluate how vessels react and redistribute after an MPA is created. The
-economic and ecological implications of displacing fishing effort are
-not yet fully understood. We use identification of fishing activity via
+increase over the last years. The benefits of
+reducing effort have been largely studied, but little empirical work has
+evaluated how vessels react and redistribute after an MPA is created.
+We use identification of fishing activity via
 Automatic Identification Systems (AIS) and causal inference techniques
@@
 
-\usepackage{pdflscape}
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
+\usepackage{lscape}
 \begin{document}
@@
 
+(QUESTION FOR JC: WHEN IS THIS (selling of rVDS rights)? And wasn't the closure expected?).
+
 \section{Introduction}\label{introduction}
+
 \dropcap{M}arine Protected Areas (MPAs) are intended to safeguard parts of the
@@
 
-\hypertarget{large-scale-marine-protected-areas}{%
-\subsection{Large Scale Marine Protected
-Areas}\label{large-scale-marine-protected-areas}}
+\subsection{Large Scale Marine Protected Areas}\label{lsmpas}
 
@@
 
+\clearpage
+
 \section{Methods}\label{methods}
@@
 \emph{received} AIS messages (\emph{i.e.} points), and therefore an
-apparent increase in the number of vessels and fishing hours. However,
-the addition of new satellites affects all vessels in the same way.
-
-Our analysis focuses on purse seine vessels, the most important fishery
+apparent increase in the number of vessels.
+The addition of new satellites affects all vessels in the same way.
+
+Our analysis focuses on tune purse seine vessels, the most important fishery
 for PNA
 countries.\footnote{We perform some of the same analyses for longliners and include them in the Appendix}
-We identify a total of 103 purse seiners that fished in PNA waters at
-least once before
-2015\footnote{New vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses.}.
-These vessels represent over 26 million individual observations for the
-2012 - 2017 period. We identify 65 vessels that have fished inside PIPA
-at least once since 2012. From these, 62 did so before the announcement
-(\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}) but we are
-only able to track 61 for the complete period of study before and after
-its
-implementation.\footnote{1 vessel never fished again after August 18, 2013.}
-On the other hand, 38 vessels never fished inside PIPA but we only have
-data for 26 of these vessels both before and after MPA implementation.
-
-Therefore, our treatment group contains all purse seiners (n = 61) that
+We identify a total of 186 purse seiners that fished in PNA waters at
+least once before 2015. Vessels that entered the fishery after 2015 were not
+exposed to the policy intervention in the pre-treatment period and are
+therefore excluded from our analyses, leaving us with 125 vessels.
+We identify 90 vessels that have fished inside PIPA
+at least once since 2012; 72 did so before the announcement
+of the closure (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}).
+From these, we only observe before and after data for 64 tuna purse seiners.
+On the other hand, 45 vessels never fished inside PIPA during the 2012 - 2015 period, 
+but we only observe befora and after data for 28 of these.
+
+Therefore, our treatment group contains all purse seiners (n = 64) that
 fished within PIPA at least once before the announcement, and that
@@
 surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
-closure (n = 26).
+closure (n = 28). Together, these vessels represent more than 20 million georeferenced positions
+for which we know activity (fishing or not fishing).
 
@@
 robustness check. The first group contains only vessels that belong to PNA countries (n
-= 7). The second group excludes Chinese vessels (n = 21). Our third control
+= 7). The second group excludes all Chinese vessels (n = 12). Our third control
 is made up of Japanese purse seiners that fish in the Pacific but have
-never fished inside PIPA (n =
-27).\footnote{We also considered a control group of Taiwanese flagged vessels but there are only 4 vessels with pre-2015 data.}
-Our main definition of treatment and control groups leaves us with 61 treated and 26
-control vessels, which have just over 22 million
+never fished inside PIPA (n = 27). Our main definition of treatment and control
+groups leaves us with 64 treated and 28 control vessels, which have just over 22 million
 observations with about 22\% of these observations identified as fishing events by the neural network classification.
 
-For each vessel, we calculate total daily fishing hours and build a daily panel
-with 37,800 observations. Table \ref{tab:baci_n_s} shows the number
-of vessels following a Before-After-Control-Impact (BACI) design, as well as the fishing hours, before
-and after PIPA. Fig. \ref{fig:all_panels} shows that mean fishing hours
-for purse seiners have an abrupt increase, just before January 1st,
-2015. This trend is observed for both treated and control groups. Across
-all measures, the treatment and control vessels follow similar patterns,
+The behavioral responses that vessels can have to a spatial closure may occurr in different ways.
+For example, displacement to new fishing grounds may represent a cost, as fishers search the ocean
+to identify the most suitable fishing places. This may result in increased fuel and labor costs. Therefore,
+we are interested in three key measures that could capture a captain's response to a spatial closure:
+daily fishing hours, daily non-fishing at-sea hours, and the proportion of fishing to non-fishing hours at sea.
+We calculate these measures for each vessel, and build a daily panel
+with 152,802 observations. Table \ref{tab:baci_n_s} shows the number
+of vessels following a Before-After-Control-Impact (BACI) design, as well as the mean fishing hours, before
+and after PIPA was implemented.
+
+Following the idea behind increased search time, we also use each vessel's track to compute
+the total daily distance traveled (km) by calculating the distance between every observation.
+Additionally, we include the daily mean distance to the nearest port and mean distance to shore
+for all positions and for fishing events only. Finally, we calculate the monthly proportion of each vessel's
+fishing time that was allocated to Kiribati waters and PNA waters
+
+Fig. \ref{fig:all_panels} shows that monthly mean values of the 10 variables that we use,
+for treated and control vessels.  Across all measures, the treatment and control vessels follow similar patterns,
 confirming our claim that the control group provides a plausible
-counterfactual. Figure \ref{fig:baci_strict} in the Appendix provides a visual
-representation of the vessel-level fishing events that make up each
-group through time. We use this panel data to answer our key research questions: 
-Are the 61 purse seiners that used to fish within PIPA affected by the closure? If so, how?
-What are they doing differently and where are they going that they didn't go to before?
-The following section describes our empirical identification strategy.
+counterfactual.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{img/all_panels.pdf}
+\caption{\label{fig:all_panels}Time series showing mean monthly values es for our 10 variables of interest:
+A) Fishing hours, B)Non-fishing hours at-sea,
+C) Proportion of fishing hours to total hours at-sea,
+D) Distance traveled, E) Mean distance from port,
+F) Mean distance from shore,
+G) Mean distance from port for fishing events,
+H) Mean distance from shore for fishing events,
+I) Proportion of hours spent in Kiribati waters,
+J) Proportion of fishing hours spent in PNA waters.}
+\end{figure}
+
+\clearpage
+
 \subsection{Analyses}\label{analyses}
@@
 Our first analysis focuses on identifying the response of 
-vessels to the PIPA closure. We use daily fishing hours, daily proportion of fishing vs.~non-fishing
-hours, daily distance traveled (km), distance from shore (km) and
-distance from home
-port(km) as our main outcomes of interest.
+vessels to the PIPA closure. We use daily fishing and non-fishing hours,
+daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), 
+distance from shore (km) and distance from home port(km) for fishing and non-fishing events,
+and proportion of total fishing hours allocated to Kiribati waters and PNA waters
+as our main outcomes of interest.
 We compare these outcomes before and after the implementation
@@
 \begin{align*}
-log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \theta_t + \epsilon_{i,t}
+log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \label{eqn:did}
@@
 
-where \(y_{i,t}\) is the outcome of interest for vessel \(i\) on day \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
+where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
+A dummy variable $Post_t$ takes the value of 0 for all
 dates prior to PIPA implementation and a value of 1 for all dates
-following PIPA implementation. \(Treat_i\) is a dummy
-variable indicating whether a vessel belongs to the treatment (\(Treat_i = 1\)) or control
-(\(Treat_i = 0\)) group. \(\alpha\) is
-the standard intercept term, \(\beta_1\) captures the temporal trend,
-\(\beta_2\) captures the initial difference between treated and control groups,
-and \(\beta_3\) is our parameter of interest: the Difference-in-Differences estimate capturing
-the treatment effect. Finally, \(\phi_t\) and \(\gamma_i\) represent
+following PIPA implementation. $Treat_i$ is a dummy
+variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control
+($Treat_i = 0$) group. $\alpha$ is
+the standard intercept term, $beta_1$ captures the temporal trend,
+$beta_2$ captures the initial difference between treated and control groups,
+and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing
+the treatment effect. Finally, $phi_t$ and $\gamma_i$ represent
 month and flag dummies that account for seasonality or
-country-level management interventions. \(\theta_t\) are time dummies to
-account for the addition of more satellites over time.\footnote{We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results.}
+country-level management interventions. We test for other more complex specifications
+that interact a quarterly dummy or year-month dummies with the treatment group
+and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
 
 Our second part of the analysis focuses on the redistribution of fishing
-effort. The role of institutions may play an important role. As stated
+effort, where institutions may play an important role. As stated
 before, LSMPAs often span the entirety of an EEZ. In the case of purse
 seining in the PNA, vessels purchase access to the fishery at the
-beginning of the season (QUESTION FOR JC: WHEN IS THIS? And wasn't the closure expected?). If a vessel decides to fish within the PNA,
+beginning of the season. If a vessel decides to fish within the PNA,
 they've already made the decision to pay for access, expecting higher
@@
 Kiribati waters would 
-most likely continue to purchase access to PNA waters (either in Kiribati's remaining open areas or a nearby EEZ). Alternatively, if a vessel fishes illegally
+most likely continue to purchase access to PNA waters (either in Kiribati's
+remaining open areas or a nearby EEZ). Alternatively, if a vessel fishes illegally
 in Kiribati waters before the implementation, one would expect them to
@@
 \emph{where} in the high seas, so we incorporate additional regions by
-using a 1 degree buffer of the high seas around each of the EEZ regions.
+using a 1-degree buffer of the high seas\footnote{Currently running the 5-degree version too}
 The rest of the high seas are merged into a single spatial unit. For
 example, if we were to do this only for Kiribati, we would have 8
-spatial units: PIPA, three EEZ units, three 1-degree\footnote{Currently running the 5-degree version too} buffers of high seas
+spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas  around each of the EEZ regions.
 around each EEZ, and the rest of the high seas. We clipped any overlapping
@@
 of fishing activity. For each cell, we calculate the total monthly
-fishing hours by treated and control vessels (see Figure
-\ref{fig:fishing_raster}). Since we are interested in the redistribution
+fishing hours by treated and control vessels (Fig. \ref{fig:fishing_raster}).
+Since we are interested in the redistribution
 of fishing effort, we use this gridded data to calculate the proportion
@@
 modeled as factors ($Year_t$), using 2012 as the reference level.
-\(Region\) is a dummy variable for regions defined above. Our vector of parameters of
+$Region$ is a dummy variable for regions defined above. Our vector of parameters of
 of interest is $\beta_{3,i}$, which captures the yearly by-country
@@
 
-Finally, we inspect the crowding effects that may arise due to the reduction
-in total fishing area. We use the rasterized fishing effort and calculate two
+Finally, we inspect the crowding effects that may arise due to the net reduction
+in fishing area. We use the rasterized fishing effort and calculate two
 potential indices of crowding. For the first one, we count the number of cells
-that had fishing activity from both groups over a given month. For the second one,
-we calculate the correlation of presence/absence of fishing for both groups
+that had fishing activity from treated and control vessels over a given month. For the second one,
+we calculate the correlation of presence/absence of fishing events between both groups
 over one month. If the implementation of the reserve induces a crowding effect,
-we would expect to observe bo clear trend before the implementation of the reserve.
-The implementation would be followed by an increase in these measures, which, 
+we would expect to observe no trend before the implementation of the reserve.
+The implementation would lead to an increase in these measures, which, 
 if vessels avoid crowding, should then come back down. We therefore expect to
-have three inflection points: 1) when there is an initial increase due to MPA
-implementation, 2) When the crowding has reached its maximum and then decreases,
-and 3) when the decrease in the measure levels off, pressumably to pre-MPA levels.
+have three inflection points: 1) in the transition between no trend and initial crowding due to MPA
+implementation, 2) When the crowding has reached its maximum and starts to decrease,
+and 3) when the decrease levels off, pressumably to pre-MPA levels.
 For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
 centering our time series of crowding indices on the day of implementation. Our
-explanatory variable is then the number of months before or after the implementation.
+explanatory variable is therefore the number of months before or after the implementation.
 For example, since PIPA was implemented in January 1st of 2015, December of 2014 
-has a value of -1, whicle Feb of 2015 would receive a value of 1.
+has a value of -1, and Feb of 2015 would receive a value of 1.
 
@@
 Regression coefficients for our DiD analysis are shown in Table
-\ref{tab:did}. Columns 1 -3 use our primary control group. Columns 4 - 6 use
-only PNA vessels as controls, and columns 7 - 9 exclude Chinese vessels.
-Columns 10 and 11 use Japanese vessels in the Pacific as controls, and
-don't include flag fixed-effects to avoid perfect collinearity
-between the Japanese flag and
-control group status.
-Our DiD analysis shows an overall increase in purse seine fishing hours,
-even after accounting for the introduction of new satellites (Table
-\ref{tab:did}).\footnote{Results of the same analysis is shown for longliners in Table \ref{tab:long}} This 
-\emph{post} coefficient estimate is consistent across different
-model specifications and across controls, and
-effectively represents the patterns observed in Figure
-\ref{fig:all_panels}.
-
-The \(\beta_3\) coefficient indicating our treatment effect suggests
-that, relative to the control, treated vessels fish less: to the order
-of 0.5-3.7 hours per day. In 6 out of 11 specifications, there is a statistically significant decrease in daily fishing hours. Another way to interpret this is that the increase
-in fishing effort by treated vessels has occurred at a lower rate than
-control vessels. These values are equivalent to a reduction of 15 - 111 fishing hours per month. However, this result is only robust and
-significant (\(p < 0.01\)) in the simplest specification of the
-Diff-in-Diff. When reducing the linear structure of the
-\(Pre \times Post\) design and instead interacting the treatment dummy
-with quarterly or year-month combinations, we are not able to reject the
-null hypothesis of no change, suggesting that the total fishing hours
-remains similar for the displaced vessels (Figs.
-\ref{fig:q1}-\ref{fig:ym4}). Since vessels don't seem to be fishing a lot less, an obvious question arises: where are they
+\ref{tab:main_DID}. Our DiD analysis shows that PIPA closure
+had no effect on the number of fishing hours, but that it caused
+non-fishing at-sea hours to increase by 1\%, This coefficient is
+only marginally significant. The proportion of
+fishing to non-fishing hours shows a positive change, but it is not
+significant. However, treated vessels travel on average 19\% less
+than control vessels, and opperate closer to shore and port.
+Furthermore, PIPA implementation caused fishing events of treated
+vessel to occur 23\% and 4\% closer to port and to shore, respectively.
+Other specificationf that exclude fixed effects produce similar estimates (Fig. \ref{fig:other_specifications})
+Since vessels don't seem to be fishing a lot less, an obvious question arises: where are they
 fishing now?
+
+%When reducing the linear structure of the
+%\(Pre \times Post\) design and instead interacting the treatment dummy
+%with quarterly or year-month combinations, we are not able to reject the
+%null hypothesis of no change, suggesting that the total fishing hours
+%remains similar for the displaced vessels (Figs.
+%\ref{fig:q1}-\ref{fig:ym4}).
 
@@
 across vessels. Then, in 2014, there is a sharp increase in fishing hours
-by treated vessels inside PIPA (the so-called Blue Paradox). In 2015, treated vessels
-then allocate more effort to the easternmost Kiribati EEZ and the high seas. In 2016, the spatial distribution of
+by treated vessels inside PIPA. In 2015, treated vessels
+then allocate more effort to the easternmost Kiribati EEZ and the high seas.
+In 2016, the spatial distribution of
 fishing effort is again similar across groups. It is evident that the
@@
 temporal evolution of the relative allocation of fishing
-effort.\footnote{Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group.}
-It shows the change in fishing effort inside PIPA, including the
+effort.  It shows the change in fishing effort inside PIPA, including the
 preemptive fishing and immediate reduction previously reported
-\citep{mcdermott_2018}. Kiribati waters in KIR 1 and KIR 2 show an
-increase in fishing effort for 2015; the same pattern is observed for
-their respective High Seas buffers, and the general High Seas. Other
-regions farther away from PIPA don't show a clear pattern under visual
-inspection. This suggests fishing effort inside PIPA has moved to the high seas around Kiribati instead of paying to fish within alternative Kiribati EEZ waters.
+\citep{mcdermott_2018}. Recall that to evaluate the redistribution of fishing effort
+we only track fishing vessels that belong to the treated group.
+Kiribati waters show an increase in fishing effort for 2015;
+the same pattern is observed for their respective High Seas buffers,
+and the general High Seas. This suggests fishing effort inside PIPA has moved to the
+high seas around Kiribati instead of paying to fish within alternative Kiribati EEZ waters.
 
@@
 the year-region interaction coefficient estimates for each region as a
-stream of changes through time (Figure \ref{fig:mean_change} and Table
+stream of changes through time (Fig. \ref{fig:mean_change} and Table
 \ref{tab:mean_change}). As noted before, the marginal change in the
 relative allocation of fishing effort relative to 2012 increases in 2014
-for PIPA. Most coefficients are not statistically significant, but
+for PIPA, followed by an abrupt reduction in 2015 and afterwards. This 
+reduction confirms that effort within PIPA has been virtually eliminated.
+Most coefficients are not statistically significant, but
 follow the same trends previously discussed, with a tendency for regions
@@
 effort in the post-implementation period. The largest increase is
-observed for the Kiribati EEZ 2, where the redistribution of treated
-vessels caused a 15\% increase in the \emph{relative} allocation of
-fishing effort within Kiribati waters. This displacement is likely
+observed for the Kiribati EEZ 2 (Kiribati's easternmost EEZ), where the
+redistribution of treated vessels caused a 10\% increase in the \emph{relative} allocation of
+fishing effort within Kiribati waters. The high seas around Kiribati's EEZ exhibit
+similar increases the year of implementation or the year after. Overall, the high seas
+receive an incresse in the order of 5\% for 2015.This displacement is likely
 causing a crowding effect after PIPA-fishing vessels redistribute to
@@
 in 2015 as vessels from PIPA are excluded, but then starts to decline.
-
-\begin{figure}
-\centering
-\includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time seri showing mean monthly values es for our 10 variables of interest:
-A) Fishing hours, B)Non-fishing hours at-sea,
-C) Proportion of fishing hours to total hours at-sea,
-D) Distance traveled, E) Mean distance from port,
-F) Mean distance from shore,
-G) Mean distance from port for fishing events,
-H) Mean distance from shore for fishing events,
-I) Proportion of hours spent in Kiribati waters,
-J) Proportion of fishing hours spent in PNA waters.}
-\end{figure}
+Our 4th degree polynomial shows the expected patterh of a relative
+constant trend before implementation which is followed by rapid increased
+and subsequent decrease.
 
@@
 	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place
-within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel
+				within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.
 }
@@
 
-%\clearpage
-%
-%\hypertarget{appendix}{%
-%\section{Appendix}\label{appendix}}
-%
-%\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+\clearpage
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
 %
@@
 %
-%\hypertarget{effort-redistribution}{%
-%\subsection{Effort redistribution}\label{effort-redistribution}}
-%
-%\hypertarget{rasterized-regions}{%
-%\subsubsection{Rasterized regions}\label{rasterized-regions}}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
-%\caption{\label{fig:unnamed-chunk-31}\label{fig:raster_rgn}Rasterized
-%regions. Each color (number) indicates a distinct region.}
-%\end{figure}
+\hypertarget{effort-redistribution}{%
+\subsection{Effort redistribution}\label{effort-redistribution}}
+
+\hypertarget{rasterized-regions}{%
+\subsubsection{Rasterized regions}\label{rasterized-regions}}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
+\caption{\label{fig:raster_rgn}Rasterized regions. Each color (number) indicates a distinct region.}
+\end{figure}
 %

### 2019-01-24 docs/tab/main_DID.tex
Updated some figures and tables that had some details. Updated manuscript to send to John

@@
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 12.535$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.021) & (0.021) & (0.041) & (0.013) \\ 
+ Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 6.161$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
+  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.023) & (0.023) & (0.041) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.232$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
+ Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.309$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
   & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & $-$0.013 & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
+ Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & 0.163$^{***}$ & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
   & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
   & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.047$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
+ Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.238$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
   & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
@@
 Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.272 & 0.272 & 0.081 & 0.283 \\ 
+R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.157 & 0.157 & 0.081 & 0.283 \\ 
 \hline 

### 2019-01-24 docs/tab/sp_corr.tex
Updated some figures and tables that had some details. Updated manuscript to send to John

@@
   Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
-  I(dif$\hat{\mkern6mu}$4) & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
+  Months $^4$ & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
  \hline \\[-1.8ex] 

### 2019-01-24 scripts/content/app_raster_rgn.R

@@ -1,0 +1,14 @@
+
+
+
+raster_rgn <- raster::raster(here::here("data", "spatial", "regions_raster.tif")) %>% 
+  raster::as.data.frame(xy = T) %>% 
+  ggplot() +
+  geom_raster(aes(x = x, y = y, fill = regions_raster)) +
+  theme_bw() +
+  geom_sf(data = eez, fill = "transparent", color = "black") +
+  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
+  geom_sf(data = small_coast, color = "black")
+
+
+raster_rgn

### 2019-01-24 scripts/content/hist_kir_fishing.R

@@ -34,17 +34,6 @@ kir_fishing <- tracks %>%
   mutate(prop_hours = kir_hours / total_hours) %>% 
   arrange(year, mmsi)
 
-kir_n <- tracks %>% 
-  filter(eez_iso3 == "KIR") %>% 
-  group_by(year, treated) %>% 
-  summarize(n = n_distinct(mmsi)) %>% 
-  ungroup() %>% 
-  spread(treated, n) %>% 
-  magrittr::set_colnames(c("year", "control", "treated")) %>% 
-  mutate(label = paste("C = ", control, "; T = ", treated),
-         hours = 1.1,
-         year = year + 0.8)
-
 #### THE PLOT ########################################################################
 
 hist_kir_fishing <- ggplot() +
@@ -55,8 +44,7 @@ hist_kir_fishing <- ggplot() +
         axis.text = element_text(size = 8),
         legend.position = "none")+
   guides(fill = guide_legend(title = "Year")) +
-  labs(x = "Fishing hours", y = "Year") +
-  geom_text(data = kir_n, aes(x = hours, y = year, label = label)) +
+  labs(x = "Proportion of fishing hours in KIR", y = "Year") +
 scale_x_continuous(labels = scales::percent_format(accuracy = 1))
 
 ggsave(hist_kir_fishing, filename = here::here("docs", "img", "hist_kir_fishing.pdf"), width = 6, height = 3.5)

### 2019-01-24 scripts/content/sp_corr.R

@@ -76,7 +76,7 @@ stargazer::stargazer(models,
                      p.auto = T,
                      single.row = T,
                      intercept.bottom = F,
-                     covariate.labels = c("Constant", "Months", "Months $^2$", "Months $^3$"),
+                     covariate.labels = c("Constant", "Months", "Months $^2$", "Months $^3$", "Months $^4$"),
                      dep.var.caption = "",
                      dep.var.labels.include = F,
                      column.sep.width = "1pt",

### 2019-01-24 scripts/content/vessel_model_fitting.R

@@ -145,7 +145,7 @@ dist_port_fishing_didq <- did_quarter(distance_port_fishing)
 dist_port_fishing_didym <- did_yearmonth(distance_port_fishing)
 
 # Distance from shore
-dist_port_fishing_did <- did(distance_shore_fishing)
+dist_shore_fishing_did <- did(distance_shore_fishing)
 dist_shore_fishing_didq <- did_quarter(distance_shore_fishing)
 dist_shore_fishing_didym <- did_yearmonth(distance_shore_fishing)
 

### 2019-01-27 docs/revenue_loss.tex
Added new missing tables from John

\begin{table}[htbp] \centering 
	\caption{Estimated revenue losses under different scenarios of PNMS (in USD)} 
	\label{tab:revenue_loss}

\begin{tabular}{l*{5}c}

\hline
\hline
Scenario	&	PS VDS	&	LL VDS	&	Export tax	&	Total revenue loss	\\
\hline
	1	&	0	&	-2,100,000	&	-482,236	&	-2,582,236	\\
	2	&	-3,150,000	&	-2,100,000	&	-482,236	&	-5,732,236	\\
	3	&	-5,600,000	&	-2,100,000	&	-482,236	&	-8,182,236	\\
	4	&	-8,750,000	&	-2,100,000	&	-482,236	&	-11,332,236 	\\

	\hline 
	\hline

\end{tabular}

\end{table}

### 2019-01-27 docs/PIPA_Palau.tex
Added changes to MS from John

@@
 
-\title{Large Scale Marine Protected Areas}
+\usepackage{placeins}
+
+\title{Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery}
 
@@
 \begin{abstract}
-Large-scale Marine Protected Areas (LSMPAs) have seen a significant
-increase over the last years. The benefits of
-reducing effort have been largely studied, but little empirical work has
-evaluated how vessels react and redistribute after an MPA is created.
+The Parties to the Nauru Agreement (PNA) is a system for managing the world's largest skipjack tuna fishery, covering an area of ~14.6 million km\textsuperscript{2} in the Pacific Ocean.
+Countries within the PNA have recently started to prohibit fishing within large parts of the PNA area.
+It is still unclear what the effects of these prohibitions have been and what effects are likely to occur in the future.
 We use identification of fishing activity via
@@
 redistribution of tuna purse seiners due to the implementation of a
-Large Scale Marine Protected Area in the Pacific Ocean. Our work
+Large-Scale Marine Protected Area (LSMPA) in the Pacific Ocean. Our work
 provides three main findings: 1) aggregate fishing effort remains
 relatively unaffected; 2) vessels that fished inside the protected area
-redistribute to adjacent waters; and 3) we observe a crowding effect for
-the first months after implementation. Our results not only provide an
+redistribute to adjacent waters (including the high seas); and 3) we observe a crowding effect for
+the first months after implementation. This suggests that rights to fish in PNA waters might now be less valuable. Our results not only provide an
 impact evaluation of the effect of LSMPAs on fishing activity, but
@@
 management. As countries continue to implement LSMPAs as a way to
-reach the stated 10\% target of ocean protection, managers should
+reach ocean protection targets, managers should
 consider how fishing effort will change in space and through time to
 ensure that fishing effort is not just displaced elsewhere, leading to
-overfishing in adjacent waters. While LSMPAs can provide a wide
-range of benefits, their implementation must be accompained with
-traditional fisheries management to maximize their effectiveness.
-
-We do not observe an increase in daily fishing hours for vessels that used to fish within PIPA, compared to a control
+overfishing in adjacent waters. We do not observe an increase in daily fishing hours for vessels that used to fish within the LSMPA, compared to a control
 group of vessels.
@@
 Unfortunately, without detailed data on vessel catch, we cannot conclude whether vessels are better or worse off financially following the closure.
-
-Our results suggest that PIPA has displaced some vessels to the high seas just outside the EEZ of Kiribati.
-This might imply a drop in demand for Kiribati fishing rights and a decline in revenue.
-We also uncover evidence that there is more congestion immediately following the closure, but this is declining over time.
+We use our results to inform predictions of the impacts of a proposed LSMPA in Palau (a PNA member).
+Our estimates of the potential losses range from \$2.5 to \$11 million annually.
+This wide range hinges on what Palau's future PNA allocation will be and the extent to which US aid will continue through non-fishing channels.
 \end{abstract}
@@
 
-\usepackage{lscape}
+\usepackage{pdflscape}
 \begin{document}
@@
 
-Next steps: I think we need to make the buffers around the EEZs 5 degrees instead of 1 degree (redistribution of effort section)
-Might change the specification of the redistribution regression
-
-(QUESTION FOR JC: WHEN IS THIS (selling of rVDS rights)? And wasn't the closure expected?).
+%Next steps: I think we need to make the buffers around the EEZs 5 degrees instead of 1 degree (redistribution of effort section)
+%Might change the specification of the redistribution regression
+%
+%(QUESTION FOR JC: WHEN IS THIS (selling of rVDS rights)? And wasn't the closure expected?).
 
@@
 increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
-a small number of Large Scale Marine Protected Areas (LSMPAs)\footnote{See, for example, \citep{game_2009,singleton_2014,boonzaier_2016,mccauley_2016,alger_2017}.}.
+a small number of Large-Scale Marine Protected Areas (LSMPAs).\footnote{See, for example, \citep{game_2009,singleton_2014,boonzaier_2016,mccauley_2016,alger_2017}.}
 Today, a small number of LSMPAs make up at least 80\%
@@
 Recent advances in satellite tracking technologies and near real-time
-identification of fishing activity provide us with an opportunity to ask, how do fishers respond to the implementation of an LSMPA?
+identification of fishing activity provide us with an opportunity to ask: how do fishers respond to the implementation of an LSMPA?
 Does effort increase or decrease and where does it go?
@@
 the behavioral changes and spatial redistribution of the industrial tuna
-purse seine fleet due to the implementation of the Phoenix Islands Protected Area. We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
+purse seine fleet due to the implementation of the Phoenix Islands Protected Area.
+We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
+These are two of the largest protected areas on the planet and both are within the Parties to the Nauru Agreement (PNA) region, which is a group of (originally eight and now) nine Pacific Islands countries that collectively manage their valuable tuna stocks.
 
@@
 
-\subsection{Large Scale Marine Protected Areas}\label{lsmpas}
+\subsection{Large-Scale Marine Protected Areas}\label{lsmpas}
 
@@
 larger than 30,000 km\textsuperscript{2} as defined by
-\citet{desanto_2013} or areas larger than 250,000 km\textsuperscript{2},
-as defined by \citep{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
+\cite{desanto_2013} or areas larger than 250,000 km\textsuperscript{2},
+as defined by \cite{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
 LSMPAs that meet the latter condition, and are also fully no-take. LSMPAs are often
 implemented in the pelagic environment, where the dominant human
-activity is industrial fishing \citep{gray_2017,kroodsma_2018}. The
+activity is industrial fishing \cite{gray_2017,kroodsma_2018}. The
 early literature on LSMPAs focused on the inherent challenges and
-difficulties that come with a pelagic environment. \citet{kaplan_2010}
+difficulties that come with a pelagic environment. \cite{kaplan_2010}
 claimed that very large MPAs would result in excessive opportunity costs
-and that these would be difficult to enforce. \citet{game_2009}
+and that these would be difficult to enforce. \cite{game_2009}
 suggested that most of the challenges could be overcome with the
 incorporation of technology, in what then became known as Dynamic Ocean
-Management \citep{maxwell_2015}.\footnote{See \citet{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.}
+Management \citep{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.}
 
@@
 \centering
-\includegraphics{img/LSMPAs_map.pdf}
+\includegraphics{img/LSMPAs_map.png}
 \caption{\label{fig:LSMPAs_map}Large Scale Marine
@@
 
-LSMPAs were erroneously assumed to have little social implications due
-to their remoteness. However, there have been calls to incorporate the
-human dimensions into LSMPAs management and evaluation
+LSMPAs were initially assumed to have little social implications due
+to their general remoteness. However, there have been calls to incorporate the
+human dimensions into LSMPA management and evaluation
 \citep{agardy_2011,gray_2017}. Most research incorporating these
 dimensions has focused on governance and enforcement of LSMPAs
-(\emph{i.e.} \citet{alger_2017,christie_2017}), but they are yet to be
+\cite{alger_2017,christie_2017}, but they are yet to be
 the focus of economic analyses \citep{gray_2017}. Overall, there has
@@
 advancement of many important facets of LSMPAs. For example,
-\citet{mcdermott_2018} show that the anticipation of a LSMPA can lead to
+\cite{mcdermott_2018} show that the anticipation of a LSMPA can lead to
 preemptive overfishing, which can erode or delay the expected benefits
-of the intervention. \citet{white_2017} combine shark tags and
+of the intervention. \cite{white_2017} combine shark tags and
 vessel-tracking data to demonstrate that the fairly large Palmyra Atoll
 National Wildlife Refuge (54,000 Km\textsuperscript{2}) protects two
-thirds of the tagged grey reef sharks by effectively excluding fishing
+thirds of tagged gray reef sharks by effectively excluding fishing
 effort. More recently, \citep{bradley_2018} use similar data to
@@
 on the long term optimal equilibrium, and redistribution of fishing
-effort may not always be optimal, especially over the first few years
+effort may not always be optimally distributed, especially over the first few years
 \citep{stevenson_2013}.
@@
 suggests that resource users may show idiosyncratic responses. For
-example, \citet{stevenson_2013} show that a network of MPAs displaced
+example, \cite{stevenson_2013} show that a network of MPAs displaced
 fishing effort farther away from ports, resulting in higher
 \emph{perceived} costs, and increases in catch per unit effort.
-\citet{cabral_2017} analyze the redistribution of fishing and
+\cite{cabral_2017} analyze the redistribution of fishing and
 non-fishing vessels following the implementation of a network of MPAs in
@@
 fishing-the-line pattern, while some fishing boats follow an ideal free
-distribution. More recently \citet{elahi_2018} used satellite tracking
+distribution. More recently \cite{elahi_2018} used satellite tracking
 data to show that a temporal spatial closure caused trawlers to maintain
@@
 fishers react to the implementation of LSMPAs, how fishing effort
-changes, and how it is spatially redistributed. All these closures took
-place within Exclusive Economic Zones, where other regulations exist.
+changes, and how it is spatially redistributed. All these studies evaluate relatively small closures within Exclusive Economic Zones, where other regulations exist.
 This may not always be the case for LSMPAs, where often the entire EEZ
 is converted into a LSMPA, leaving fishers with the option of moving to
-the high seas or other countries' EEZs.
+the high seas or other countries' EEZs, with potentially very different fishing regulations.
 
@@
 include the Federated States of Micronesia, Kiribati, the Marshall Islands,
-Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu. The Nauru
-Agreement regulated access of foreign vessels (\emph{i.e.} those from
-non-PNA countries). Holding \textasciitilde{}80\% of the historical
-purse seining grounds within their Exclusive Economic Zones, PNA
-countries gained greater bargaining power when providing fishing access to foreign
-fleets \citep{havice_2010}.
+Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu. Tokelau joined in PNA group in 2012 and started selling access rights in 2013. The Nauru
+Agreement regulates access of foreign vessels (\emph{i.e.} those from
+non-PNA countries). Holding \textasciitilde{}80\% of historical
+skipjack tuna purse seine grounds within their Exclusive Economic Zones, PNA
+countries have achieved greater bargaining power when providing fishing access to foreign
+fleets \cite{havice_2010}.
 
@@
 Agreement, which limited the number of purse seiners at 205 vessels from
-1995-2007\footnote{See \citet{havice_2010} for a detailed description of
-  the Nauru, Palau, and Federal States of Micronesia agreements.}. However, the most notable regulation is
-their approach to manage fishing effort: a Vessel Day Scheme (VDS)
+1995-2007.\footnote{See \cite{havice_2010} for a detailed description of
+	the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is
+the approach to manage fishing effort: a Vessel Day Scheme (VDS)
 implemented in 2007 \citep{havice_2013}. This effectively modified how
-fishing effort was managed, from number of vessels under the Palau
-Agreement to fishing hours. The VDS works as follows: Each year,
-scientific advisers recommend a total number of fishing vessel-days per
-year. Hours are allocated to each PNA country based on catch history,
-and they then use or sell fishing rights to other non-PNA countries
-\citep{aqorau_2018}. While the effectiveness of this scheme has been
-debated in terms of meeting their fishery management and conservation
+fishing effort was managed, from total number of vessels (under the Palau
+Agreement) to total fishing hours. 
+Under the purse seine VDS, a total number of annual vessel days for the entire fishery is agreed upon by the PNA parties.
+Each party’s allowable effort (PAE) is then calculated based on historic effort and biomass within each party’s EEZ.
+Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% of the PAE is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
+A minimum benchmark fee is set for purse seine vessel days which each party can transfer (i.e., sell to another PNA member) or sell to the highest bidder (i.e., sell to a fishing company).
+Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}.
+Although detailed records on sales or transfers of vessel days are not publicly available \citep{havice_2013,yeeting2018stabilising}, a minimum benchmark fee of \$8,000/day was set from 2015 \citep{PNA2014a}.
+
+\cite{yeeting2018stabilising} summarize the PNA implementing arrangements as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \citep{PNA2016}.
+Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \citep{PNA2016}.
+As described in the Palau Arrangement, fishing days by vessels shorter than 50m (longer than 80m) count as 0.5 (1.5) vessel days.
+Countries are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within their PAE.
+Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \citep{PNA2016}.
+There are some criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the program \citep{Arnason2014,yeeting2018stabilising}.
+While the effectiveness of this scheme has been
+debated in terms of meeting fishery management and conservation
 objectives, the licensing significantly contributes to the economy of
@@
 \centering
-\includegraphics{img/PNA_map.pdf}
+\includegraphics{img/PNA_map.png}
 \caption{\label{fig:PNA_map}Map of the Exclusive
@@
 Pacific has historically accounted for a large portion of tuna catches
-\citep{aqorau_1997}. Today, the PNA controls close to 50\% of the global
-skipjack tuna production \citep{pna_website_2018}. A large portion of
-these catches derive from purse seine vessels licensed under the VDS.
+\cite{aqorau_1997}. Today, the PNA controls close to 50\% of global
+skipjack tuna production \cite{pna_website_2018} and the combined area of all EEZs involved is 14.6 million km\textsuperscript{2}, larger than the land mass of the United States of America.
+A large portion of global skipjack
+catch derives from purse seine vessels licensed under the VDS.
 Fishing vessels from Australia, New Zealand, China, France, Korea,
@@
 times the size of Ecuador. Figure \ref{fig:PNA_map} shows a map of the
-PNA countries and the Phoenix Islands Protected Area.
+PNA countries (excluding Palau) and the Phoenix Islands Protected Area.
 
@@
 The top panel shows vessel days in absolute numbers, while the bottom panel shows the proportion
-of each year. The left and right columns show fishing and non-fishing hours.
-[JOHN: I prefer the absolute hours one, but what do you prefer?]}
+of each year. The left and right columns show fishing and non-fishing hours.}
 \end{figure}
@@
 
-\begin{figure}[h]
-	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
-	\caption{Map of the Four Protected Areas}
-	\label{fig:maps}
-\end{figure}
-
-On October 28, 2015 the President of Palau, H.E.
+%\begin{figure}[h]
+%	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
+%	\caption{Map of the Four Protected Areas}
+%	\label{fig:maps}
+%\end{figure}
+
+On October 28, 2015, the President of Palau, H.E.
 Tommy E.
-Remengesau Jr., signed into law the Palau National Marine Sanctuary Act.
-Starting in December 2020, this will close 193,000 square miles to commercial fishing activities, creating the 14th largest protected area in the world.
+Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
+The sanctuary will fully protect about 80 percent of the nation’s EEZ.
+The remaining 20\% of Palau’s EEZ (close to the most heavily populated islands: Koror and Babeldaob) will become a Domestic Fishing Zone in which traditional and domestic fishing activities will be allowed to provide fish solely for the domestic market (\emph{i.e.} exports of pelagic fish will be prohibited).
+Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
+In this section, we use our preceding analysis on the ex-post impacts of PIPA to attempt to make some \emph{ex ante} predictions about the potential impacts of PNMS.
+We start by giving some background on the fishing that is currently taking place inside the future PNMS.
 
@@
 Foreign tuna fishing in Palau’s EEZ began before WWI.
-Pole and line was the initial gear used to target skipjack tuna by the Japanese.
-Foreign fishing activities stopped during WWII and started again in the 1960s when the Japanese returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
-The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna during the same time.
-During the 1980s, longline fishing began to set their lines deeper, shifting their targets to bigeye tuna.
-During the 1980s Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
+Pole and line was the initial gear used to target skipjack tuna by Japanese vessels.
+Foreign fishing activities stopped during WWII and started again in the 1960s when Japanese fishers returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
+The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna developed during the same time.
+During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna.
+During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
 There are currently three transshipment companies operating in Palau.
 
-\subsubsection{Purse seine fishing}
-
-Purse seine vessels target schools of skipjack tuna that are used for canning.
-Compared to other EEZs in the Pacific, Palau’s EEZ is not known to be preferred for purse seining (Sisior, pers.
+Purse seine vessels target schools of skipjack tuna that are then canned.
+Compared to other EEZs in the Pacific, especially the PNA EEZs, Palau’s EEZ is not known to be a preferred fishing ground for purse seining (Sisior, pers.
 comm.).
-Currently all purse seine boats fishing in Palau’s EEZ are Japanese and do not land their catches in Palau Table \ref{tab:palau_purse}.
-
-%\input{palau_purse}
-
-\subsubsection{Longline fishing}
-
-All longline vessels fishing in Palau’s EEZ are foreign owned (Table 2).
-Japanese longline vessels do not land their catches in Palau.
-Locally based, foreign owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI), Kuniyoshi Fishing Company (KFC)) (Table 2).
-Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan, upon landing in Koror.
-Most of the discards, or portion of the catch that is of too low quality to export, is either sold or donated in Palau.
-A very small portion of the discards is frozen and transported to Taiwan when the vessels return to their home ports.
-
-%\input{palau_long}
-
-\subsubsection{Access fees}
-
-An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covers three methods of fishing (longline, purse seine, pole and line) and has allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
-Japan pays 4-5\% of catch returns, but there was no way to validate their catch \citep{Tewid2013}.
-Between 2010 and 2014, Japan has paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
-Currently, these access fees have been replaced by the vessel day schemes (described in section 3).
-
-\subsubsection{Uniform Longline Agreement for locally based vessels (ULA)}
-
-Agreements between the Republic of Palau and foreign owned, local based companies (PITI and KFC) \citep{Tewid2013}.
-Vessels under these agreements are internationally owned, locally based vessels that have payed for annual licenses per vessel based on the size of the vessel.
-These are the vessels in Table \ref{tab:palau_long} (excluding the Japanese vessels).
-So, for example, 38 vessels in 2016.
-Between 2010 and 2014, total licensing fee revenue was between \$219,000-\$284,600 per year \citep{Gillett2016}.
-Currently, these access fees have been replaced by the vessel day scheme (described in section 3).
-
-\subsubsection{US Multilateral Tuna Treaty and Federated States of Micronesia Arrangement}
-
-These two multilateral treaties grant preferential access to the US and FSM flagged purse seine boats, respectively.
-The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees (more in section 3).
+This can be seen in Figure \ref{fig:VDS_country_year}.
+Currently all purse seine boats fishing in Palau’s EEZ are Japanese and they do not land their catch in Palau (Table \ref{tab:palau_purse}).
+
+\input{palau_purse}
+
+All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}).
+Japanese longline vessels do not land their catch in Palau.
+Locally-based, foreign-owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI) and Kuniyoshi Fishing Company (KFC)).
+Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan upon landing in Koror (the largest town in and former capital of Palau).
+Most of the discards are either sold or donated in Palau.
+A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.
+
+\input{palau_long}
+
+\subsubsection{Access fees and taxes}
+
+An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
+Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \citep{Tewid2013}.
+Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
+Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
+
+There used to be a number of agreements between the Republic of Palau and foreign owned, local based companies, in particular PITI and KFC, to allow longline fishing \cite{Tewid2013}.
+Vessels under these agreements were internationally-owned, locally-based vessels that paid for annual licenses based on the size of each vessel.
+These are the vessels shown in Table \ref{tab:palau_long} (excluding the Japanese vessels).
+So, for example, there were 38 vessels as part of these agreements in 2016.
+Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \citep{Gillett2016}.
+These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
+
+There are two multilateral treaties that grant preferential access to Palau waters to US and Federated States of Micronesia (FSM) flagged purse seine boats: the US Multilateral Tuna Treaty and the Federated States of Micronesia Arrangement.
+The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees.
 Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds.
-Some Pacific Island countries treat this money as foreign aid, not for fishing access \citep{Gillett2016}.
-
-\subsubsection{Other sources of revenue from pelagic fisheries}
-
-The export tax for all commercial tuna and billfish, either fresh or frozen is \$0.35/kg.
-Average revenues from export taxes was approximately \$500,000 annually from 2011-2014 \citep{Gillett2016}.
-Otherwise there is little additional revenue from pelagic fisheries, especially considering that very few jobs are created by the fishery.
-Between 80-90 people are employed by offshore fisheries, of these only ~20\% are Palauans and average wages are ~50\% average wages in the country \citep{Gillett2016}.
+These agreements have been described by some commentators as foreign aid, with little connection to underlying fish stocks \cite{Gillett2016}.
+
+The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \citep{Gillett2016}. 
+Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery.
+Between 80 to 90 people are employed by offshore fisheries, and of these only around 20\% are Palauans, earning wages that are only 50\% of average wages in Palau \cite{Gillett2016}.
 
@@
 
-The Parties to the Nauru Agreement (PNA) is an agreement between Federated States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua New Guinea, Solomon Islands and Tuvalu to manage the largest tuna fishery in the world.
-The Purse Seine Vessel Day Scheme (PS VDS), established in 2006 with the Palau Agreement, is the current method used by the PNA to manage effort in the fishery.
-Although not a PNA member, Tokelau joined the PS VDS in 2014, with 1,000 transferrable days \citep{PNA2014}.
-
-In the PS VDS, a total number of annual vessel days for the entire fishery is agreed upon by the parties.
-Each party’s allowable effort (PAE) is then calculated based on historic effort and biomass within each party’s EEZ.
-Sixty percent of the PAE is calculated based on the party’s effort over the last seven years and 40\% of the PAE is calculated based on the 10 year average of the party’s share of estimated skipjack and yellowfin biomass within its EEZ (as explained in Article 12.5 of the 2012 Amendment to the Palau Agreement and in Hagrannsoknir sf 2014).
-A minimum benchmark fee is set for purse seine vessel days (PS VD) which each party can transfer (i.e., sell to another PNA member) or sell to the highest bidder (i.e., sell to fishing company).
-Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties VD allocation \citep{PNA2016}.
-The process of transferring days between parties is described in Article 7 of the Management Scheme \citep{PNA2016}.
-The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}.
-A minimum benchmark fee of \$8,000/day was set from 2015 \citep{PNA2014a}.
-Detailed records on sales or transfers of vessel days are not publicly available \citep{havice_2013,yeeting2018stabilising}.
-\cite{yeeting2018stabilising} summarize the PNA ‘implementing arrangements’ as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \citep{PNA2016}.
-Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \citep{PNA2016}.
-As described in the Palau Arrangement \citep{PNA2016}, fishing days by vessels shorter than 50m or longer than 80m count as 0.5 and 1.5 vessel days, respectively.
-Parties are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within the PAE.
-Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \citep{PNA2016}.
-However, there are criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the SP VDS \citep{Arnason2014,yeeting2018stabilising}.
 In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism.
-Palau’s currently PS VD allotment is reportedly ~700 vessel days annually (Sisior, pers.
-comm., \cite{Pojas2018}), though historically, this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}.
-Palau sells most of its vessel days to the US for \$12,500 each (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
-The remainder of Palau’s PS vessel days are sold for between \$9-10,000 each.
+Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers.
+comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}).
+Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
+The remainder of Palau’s purse seine vessel days are sold for between \$9-10,000 each.
 When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
-Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred PS VD to is Papua New Guinea \citep{Tewid2013} and this year, PS VD have been sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
-This year, Palau has brought in approximately \$9 million USD in PS VDS revenue (Sisior pers.
+Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \citep{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
+In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers.
 comm.).
 
-The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing at the country-scale.
-Palau was the first party to implement the VDS for the longline fishery in 2017.
+The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing it at the country-scale.
+Palau was the first party to implement the VDS for longline fishing in 2017.
 In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers.
@@
 
-\subsubsection{The Palau National Marine Sanctuary Act}
-
-In 2015, Palau enacted a policy to protect 500 thousand square kilometers of its ocean, representing 80\% of its exclusive economic zone (EEZ), by 2020.
-The policy’s goal is to preserve and manage the stocks, health, and beauty of Palau’s waters and natural resources by limiting fishing in its deep ocean waters.
-State waters hugging the coasts of the archipelago are not affected by the policy.
-Commercial fishing will still be allowed within the open 20\% that surrounds the main islands of Koror and Babeldaob, but all catch must be landed in Palau and exports of pelagic fish will be prohibited.
-Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
-
-\subsubsection{Future of pelagic fisheries under the PNMS}
+\subsubsection{Potential Revenue Loss under the PNMS}
 
 To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
-This appears to be occurring for the LL VDS, but it is uncertain whether this is being followed for the PS VDS, because PS VD can be transferred for use in other EEZs.
-There has been no official statement on what will happen to Palau’s vessel days upon full implementation of PNMS.
+This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
+There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
 However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
 comm.).
-In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \citep{Senase2015}.
-Further, other PNA members have not been penalized for other protected area closures (e.g., Phoenix Islands Protected Area in Kiribati) (Hanich, pers.
+In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
+Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
 comm.).
-Table 3 estimates the potential losses of revenue under full enactment of the PNMS under four scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
-Scenario 1 is likely if Palau retains its PAE, but the US no longer purchases its days (note, US is currently purchasing days at \$12,500).
-Scenario 2 is the same as the first scenario, except instead of being able to transfer its days at the current benchmark price, it is able to transfer its days for \$12,000 (to account for current price to US of \$12,500, which will increase in accordance with the US Treaty, and also the general increasing trend in the value of PS vessel days).
+
+Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
+Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
 It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
-In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,000/day, respectively.
-In all scenarios, all longline vessel day and export tax revenue are lost.
+In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel day and export tax revenues are lost.
 Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
@@
 
-%\input{revenue_loss}
+\input{revenue_loss}
 
@@
 
-In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch Plans for domestic fishery \citep{Gillett2016}.
+In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch \cite{Gillett2016}.
 The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers.
@@
 Otherwise, there are no domestic vessels dedicated to full-time offshore fishing.
-A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes (although Phil James with SPC has results that should come out soon).
+A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes.
 Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
-There are several possible scenarios for domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
-
-We will use aggregated GFW data at the 1km * 1km level to estimate what \% of fishing effort under the PNA is currently taking place in the proposed sanctuary?
-This will estimate the impact on foreign-flagged fleets that used to fish in Palau waters.
-We are currently in possession of this data.
-In terms of the impact on PNA payments, it is our understanding that the allocation will not be reduced (in the near future) but perhaps the price received per VDS will be lower.
-But we do not have good information on prices paid for VDS.
-We also don’t yet have good data on local fishers in Palau that are likely to be positively impacted since they will be allowed to fish in the sanctuary.
-
-\begin{figure}[h]
-	\includegraphics[width=0.75\textwidth]{img/Fishing_effort_Palau_relative_PNA}
-	\caption{Fishing Effort in Palau Relative to the Total PNA Area}
-\end{figure}
-
-\begin{figure}[h]
-	\includegraphics[width=0.75\textwidth]{img/By_flag_Fishing_effort_Palau_relative_PNA}
-	\caption{Fishing Effort in Palau Relative to the Total PNA Area By Distant Water Fishing Fleet}
-\end{figure}
+There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
 
@@
 contribution of spatial closures to the observed spatial distribution of
-fishing vessels. Recent work by \citet{elahi_2018} identified that total
+fishing vessels. Recent work by \cite{elahi_2018} identified that total
 fishing effort in a focal region where a short-term MPA was implemented
@@
 \clearpage
+
+\FloatBarrier
 

### 2019-02-05 docs/tab/main_DID.tex
Updated the values for model 7 after fixing the bug in the code that used distance from port twice instead of using ditance from shore

--- 2019-01-23 docs/tab/main_DID.tex
@@
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 12.535$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.021) & (0.021) & (0.041) & (0.013) \\ 
+ Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
+  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.023) & (0.021) & (0.041) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.232$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
+ Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
   & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
   & & & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & $-$0.013 & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
+ Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
   & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
   & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.047$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
+ Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
   & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
@@
 Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.272 & 0.272 & 0.081 & 0.283 \\ 
+R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.157 & 0.272 & 0.081 & 0.283 \\ 
 \hline 

### 2019-02-05 docs/PIPA_Palau.tex
Updated all images and tables

@@
 \centering
-	\includegraphics{img/VDS_year.pdf}
-	\caption{\label{fig:VDS_year}Vessel-days for all PNA countries (including Tokelau).}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/VDS_country_year.pdf}
-	\caption{\label{fig:VDS_country_year}Vessel-days for all PNA countries (including Tokelau) by country.
-The top panel shows vessel days in absolute numbers, while the bottom panel shows the proportion
-of each year. The left and right columns show fishing and non-fishing hours.}
+	\includegraphics{img/all_PS_VDS_cty_year.pdf}
+	\caption{\label{fig:VDS_year}a)Vessel-days for all PNA countries (including Tokelau).
+	B) Vessel-days for all PNA countries (including Tokelau) by country.}
 \end{figure}

### 2019-02-07 docs/PIPA_Palau.tex
Updated figures and MS

@@
-\documentclass[9pttwoside,lineno]{pnas-new}
+\documentclass[9pt,twoside,lineno]{pnas-new}
 % Use the lineno option to display guide line numbers if required.
@@
 \begin{abstract}
-The Parties to the Nauru Agreement (PNA) is a system for managing the world's largest skipjack tuna fishery, covering an area of ~14.6 million km\textsuperscript{2} in the Pacific Ocean.
-Countries within the PNA have recently started to prohibit fishing within large parts of the PNA area.
-It is still unclear what the effects of these prohibitions have been and what effects are likely to occur in the future.
-We use identification of fishing activity via
-Automatic Identification Systems (AIS) and causal inference techniques
-to provide the first analysis of behavioral changes and spatial
-redistribution of tuna purse seiners due to the implementation of a
-Large-Scale Marine Protected Area (LSMPA) in the Pacific Ocean. Our work
-provides three main findings: 1) aggregate fishing effort remains
-relatively unaffected; 2) vessels that fished inside the protected area
-redistribute to adjacent waters (including the high seas); and 3) we observe a crowding effect for
-the first months after implementation. This suggests that rights to fish in PNA waters might now be less valuable. Our results not only provide an
-impact evaluation of the effect of LSMPAs on fishing activity, but
-provide insights into vessel redistribution dynamics, which may have
-ecological and economic implications for marine conservation and fisheries
-management. As countries continue to implement LSMPAs as a way to
-reach ocean protection targets, managers should
-consider how fishing effort will change in space and through time to
-ensure that fishing effort is not just displaced elsewhere, leading to
-overfishing in adjacent waters. We do not observe an increase in daily fishing hours for vessels that used to fish within the LSMPA, compared to a control
-group of vessels.
+The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean.
+In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Island Protected Area (397,447 km\textsuperscript{2}).
+It is still unclear what the effects of such a big MPA have been and what effects are likely to occur in the future.
+We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques evaluate the behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a Large-Scale Marine Protected Area.
+Our work provides three main findings: 1) we observe a crowding effect for the first months after implementation, 2) aggregate fishing effort remains relatively constant; and 3) vessels that fished inside the protected area redistribute to adjacent waters, including the high seas.
+This suggests that rights to fish in PNA waters might now be less valuable.
+We do not observe an increase in daily fishing hours for vessels that used to fish within the LSMPA, compared to a control group of vessels.
 Thus, for vessels that have chosen to continue to operate following the closure, we do not observe evidence that they are being forced to exert more effort as a result of the closure.
@@
 This wide range hinges on what Palau's future PNA allocation will be and the extent to which US aid will continue through non-fishing channels.
+Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications for marine conservation and fisheries management.
+As countries continue to implement LSMPAs as a way to reach ocean protection targets, managers should consider how fishing effort will change in space and time to ensure that fishing effort is not just displaced elsewhere.
 \end{abstract}
@@
 
-%Next steps: I think we need to make the buffers around the EEZs 5 degrees instead of 1 degree (redistribution of effort section)
-%Might change the specification of the redistribution regression
-%
 %(QUESTION FOR JC: WHEN IS THIS (selling of rVDS rights)? And wasn't the closure expected?).
@@
 
-\begin{figure}
+\begin{SCfigure*}
 \centering
@@
 IUCN Ia or Ib, their designated English name is `Protected Area'.}
-\end{figure}
+\end{SCfigure*}
 
@@
 
-\hypertarget{nauru-agreement-and-the-phoenix-island-protected-area}{%
-\subsection{Nauru agreement and the Phoenix Islands Protected
-Area}\label{nauru-agreement-and-the-phoenix-island-protected-area}}
+\subsection{Nauru agreement and the Phoenix Islands Protected Area}
+\label{nauru-agreement-and-the-phoenix-island-protected-area}
 
 The Nauru Agreement was established in 1982 by a select group of Pacific
-island nations to manage their important tuna resources more effectively. Parties to the Nauru Agreement (PNA) Members
+island nations to manage their important tuna resources more effectively.
+Parties to the Nauru Agreement (PNA) Members
 include the Federated States of Micronesia, Kiribati, the Marshall Islands,
-Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu. Tokelau joined in PNA group in 2012 and started selling access rights in 2013. The Nauru
+Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu.
+Tokelau joined the PNA group in 2012 and started selling access rights in 2013. The Nauru
 Agreement regulates access of foreign vessels (\emph{i.e.} those from
@@
 Agreement, which limited the number of purse seiners at 205 vessels from
-1995-2007.\footnote{See \cite{havice_2010} for a detailed description of
-	the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is
+1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is
 the approach to manage fishing effort: a Vessel Day Scheme (VDS)
@@
 fishing effort was managed, from total number of vessels (under the Palau
-Agreement) to total fishing hours. 
+Agreement) to total vessel-days. 
 Under the purse seine VDS, a total number of annual vessel days for the entire fishery is agreed upon by the PNA parties.
@@
 Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% of the PAE is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
-A minimum benchmark fee is set for purse seine vessel days which each party can transfer (i.e., sell to another PNA member) or sell to the highest bidder (i.e., sell to a fishing company).
+A minimum benchmark fee is set for purse seine vessel days which each party can transfer (\emph{i.e.} sell to another PNA member) or sell to the highest bidder (\emph{i.e.} sell to a fishing company).
 Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}.
@@
 delineates PIPA.}
-\end{figure}
+\end{SCfigure*}
 
@@
 	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:VDS_year}a)Vessel-days for all PNA countries (including Tokelau).
-	B) Vessel-days for all PNA countries (including Tokelau) by country.}
+	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all VDS countries by fishing and non-fishing days. B) Observed vessel-days for all VDS countries by country.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
+	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside VDS waters by group of vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/PS_VDS_KIR_by_year.pdf}
+	\caption{\label{fig:PS_VDS_KIR_by_year}Vessel days spent inside Kiribati waters by group of vessels.}
 \end{figure}
@@
 	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place
-				within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.
-}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
 \end{figure}
-
-\clearpage
-
-\section{Palau National Marine Sanctuary}\label{PNMS}
-
-%\begin{figure}[h]
-%	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
-%	\caption{Map of the Four Protected Areas}
-%	\label{fig:maps}
-%\end{figure}
-
-On October 28, 2015, the President of Palau, H.E.
-Tommy E.
-Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
-The sanctuary will fully protect about 80 percent of the nation’s EEZ.
-The remaining 20\% of Palau’s EEZ (close to the most heavily populated islands: Koror and Babeldaob) will become a Domestic Fishing Zone in which traditional and domestic fishing activities will be allowed to provide fish solely for the domestic market (\emph{i.e.} exports of pelagic fish will be prohibited).
-Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
-In this section, we use our preceding analysis on the ex-post impacts of PIPA to attempt to make some \emph{ex ante} predictions about the potential impacts of PNMS.
-We start by giving some background on the fishing that is currently taking place inside the future PNMS.
-
-\subsection{Background on Commercial Fishing in Palau}\label{Palau_back}
-
-Foreign tuna fishing in Palau’s EEZ began before WWI.
-Pole and line was the initial gear used to target skipjack tuna by Japanese vessels.
-Foreign fishing activities stopped during WWII and started again in the 1960s when Japanese fishers returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
-The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna developed during the same time.
-During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna.
-During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
-There are currently three transshipment companies operating in Palau.
-
-Purse seine vessels target schools of skipjack tuna that are then canned.
-Compared to other EEZs in the Pacific, especially the PNA EEZs, Palau’s EEZ is not known to be a preferred fishing ground for purse seining (Sisior, pers.
-comm.).
-This can be seen in Figure \ref{fig:VDS_country_year}.
-Currently all purse seine boats fishing in Palau’s EEZ are Japanese and they do not land their catch in Palau (Table \ref{tab:palau_purse}).
-
-\input{palau_purse}
-
-All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}).
-Japanese longline vessels do not land their catch in Palau.
-Locally-based, foreign-owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI) and Kuniyoshi Fishing Company (KFC)).
-Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan upon landing in Koror (the largest town in and former capital of Palau).
-Most of the discards are either sold or donated in Palau.
-A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.
-
-\input{palau_long}
-
-\subsubsection{Access fees and taxes}
-
-An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
-Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \citep{Tewid2013}.
-Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
-Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
-
-There used to be a number of agreements between the Republic of Palau and foreign owned, local based companies, in particular PITI and KFC, to allow longline fishing \cite{Tewid2013}.
-Vessels under these agreements were internationally-owned, locally-based vessels that paid for annual licenses based on the size of each vessel.
-These are the vessels shown in Table \ref{tab:palau_long} (excluding the Japanese vessels).
-So, for example, there were 38 vessels as part of these agreements in 2016.
-Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \citep{Gillett2016}.
-These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
-
-There are two multilateral treaties that grant preferential access to Palau waters to US and Federated States of Micronesia (FSM) flagged purse seine boats: the US Multilateral Tuna Treaty and the Federated States of Micronesia Arrangement.
-The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees.
-Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds.
-These agreements have been described by some commentators as foreign aid, with little connection to underlying fish stocks \cite{Gillett2016}.
-
-The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \citep{Gillett2016}. 
-Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery.
-Between 80 to 90 people are employed by offshore fisheries, and of these only around 20\% are Palauans, earning wages that are only 50\% of average wages in Palau \cite{Gillett2016}.
-
-\subsubsection{Parties to the Nauru Agreement and the Vessel Day Scheme}
-
-In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism.
-Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers.
-comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}).
-Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
-The remainder of Palau’s purse seine vessel days are sold for between \$9-10,000 each.
-When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
-Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \citep{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
-In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers.
-comm.).
-
-The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing it at the country-scale.
-Palau was the first party to implement the VDS for longline fishing in 2017.
-In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers.
-comm.).
-Since 2016, the number of allowed longline VDs has been a fraction of the 2014 days, reducing each year as stipulated in the PNMS Act.
-Palau sells its LL VD for \$150-\$250 (Sisior pers.
-comm.).
-Because the LL VDS is still new and has yet to be fully implemented by all parties, LL VD are not currently transferable between PNA member EEZs.
-
-\subsubsection{Potential Revenue Loss under the PNMS}
-
-To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
-This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
-There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
-However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
-comm.).
-In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
-Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
-comm.).
-
-Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
-Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
-It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
-In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel day and export tax revenues are lost.
-Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
-Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
-
-\input{revenue_loss}
-
-\subsubsection{Plans for a domestic pelagic fishery}
-
-In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch \cite{Gillett2016}.
-The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers.
-comm.).
-Otherwise, there are no domestic vessels dedicated to full-time offshore fishing.
-A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes.
-Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
-There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
 
@@
 \section{References}\label{references}
+
 \bibliography{references}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\section{Appendix}\label{appendix}
 
@@
 \setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
+\section{Palau National Marine Sanctuary}\label{PNMS}
+
+\begin{figure}[h]
+	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
+	\caption{Map of the Four Protected Areas}
+	\label{fig:maps}
+\end{figure}
+
+On October 28, 2015, the President of Palau, H.E.
+Tommy E.
+Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
+The sanctuary will fully protect about 80 percent of the nation’s EEZ.
+The remaining 20\% of Palau’s EEZ (close to the most heavily populated islands: Koror and Babeldaob) will become a Domestic Fishing Zone in which traditional and domestic fishing activities will be allowed to provide fish solely for the domestic market (\emph{i.e.} exports of pelagic fish will be prohibited).
+Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
+In this section, we use our preceding analysis on the ex-post impacts of PIPA to attempt to make some \emph{ex ante} predictions about the potential impacts of PNMS.
+We start by giving some background on the fishing that is currently taking place inside the future PNMS.
+
+\subsection{Background on Commercial Fishing in Palau}\label{Palau_back}
+
+Foreign tuna fishing in Palau’s EEZ began before WWI.
+Pole and line was the initial gear used to target skipjack tuna by Japanese vessels.
+Foreign fishing activities stopped during WWII and started again in the 1960s when Japanese fishers returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
+The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna developed during the same time.
+During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna.
+During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
+There are currently three transshipment companies operating in Palau.
+
+Purse seine vessels target schools of skipjack tuna that are then canned.
+Compared to other EEZs in the Pacific, especially the PNA EEZs, Palau’s EEZ is not known to be a preferred fishing ground for purse seining (Sisior, pers.
+comm.).
+This can be seen in Figure \ref{fig:VDS_country_year}.
+Currently all purse seine boats fishing in Palau’s EEZ are Japanese and they do not land their catch in Palau (Table \ref{tab:palau_purse}).
+
+\input{palau_purse}
+
+All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}).
+Japanese longline vessels do not land their catch in Palau.
+Locally-based, foreign-owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI) and Kuniyoshi Fishing Company (KFC)).
+Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan upon landing in Koror (the largest town in and former capital of Palau).
+Most of the discards are either sold or donated in Palau.
+A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.
+
+\input{palau_long}
+
+\subsubsection{Access fees and taxes}
+
+An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
+Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \citep{Tewid2013}.
+Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
+Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
+
+There used to be a number of agreements between the Republic of Palau and foreign owned, local based companies, in particular PITI and KFC, to allow longline fishing \cite{Tewid2013}.
+Vessels under these agreements were internationally-owned, locally-based vessels that paid for annual licenses based on the size of each vessel.
+These are the vessels shown in Table \ref{tab:palau_long} (excluding the Japanese vessels).
+So, for example, there were 38 vessels as part of these agreements in 2016.
+Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \citep{Gillett2016}.
+These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
+
+There are two multilateral treaties that grant preferential access to Palau waters to US and Federated States of Micronesia (FSM) flagged purse seine boats: the US Multilateral Tuna Treaty and the Federated States of Micronesia Arrangement.
+The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees.
+Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds.
+These agreements have been described by some commentators as foreign aid, with little connection to underlying fish stocks \cite{Gillett2016}.
+
+The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \citep{Gillett2016}. 
+Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery.
+Between 80 to 90 people are employed by offshore fisheries, and of these only around 20\% are Palauans, earning wages that are only 50\% of average wages in Palau \cite{Gillett2016}.
+
+\subsubsection{Parties to the Nauru Agreement and the Vessel Day Scheme}
+
+In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism.
+Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers.
+comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}).
+Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
+The remainder of Palau’s purse seine vessel days are sold for between \$9-10,000 each.
+When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
+Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \citep{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
+In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers.
+comm.).
+
+The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing it at the country-scale.
+Palau was the first party to implement the VDS for longline fishing in 2017.
+In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers.
+comm.).
+Since 2016, the number of allowed longline VDs has been a fraction of the 2014 days, reducing each year as stipulated in the PNMS Act.
+Palau sells its LL VD for \$150-\$250 (Sisior pers.
+comm.).
+Because the LL VDS is still new and has yet to be fully implemented by all parties, LL VD are not currently transferable between PNA member EEZs.
+
+\subsubsection{Potential Revenue Loss under the PNMS}
+
+To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
+This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
+There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
+However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
+comm.).
+In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
+Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
+comm.).
+
+Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
+Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
+It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
+In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel day and export tax revenues are lost.
+Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
+Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+
+\input{revenue_loss}
+
+\subsubsection{Plans for a domestic pelagic fishery}
+
+In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch \cite{Gillett2016}.
+The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers.
+comm.).
+Otherwise, there are no domestic vessels dedicated to full-time offshore fishing.
+A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes.
+Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
+There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
 

### 2019-02-13 docs/tab/DID_without_CHN.tex
Added new tables and figures for controls

\begin{table}[H] \centering 
  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 5.513$^{***}$ & 10.647$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
  & (0.038) & (0.007) & (0.009) & (0.045) & (0.054) & (0.088) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
  & & & & & & & & & & \\ 
 Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & $-$0.077$^{*}$ & $-$0.201$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
  & (0.026) & (0.008) & (0.007) & (0.036) & (0.042) & (0.061) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
  & & & & & & & & & & \\ 
 Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.059 & 0.087 & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
  & (0.028) & (0.006) & (0.007) & (0.032) & (0.037) & (0.055) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.248$^{***}$ & $-$0.267$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
  & (0.030) & (0.009) & (0.007) & (0.040) & (0.048) & (0.069) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 25,073 & 74,600 & 25,073 & 73,265 & 74,995 & 74,995 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.019 & 0.013 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-02-13 docs/tab/DID_without_PNA.tex
Added new tables and figures for controls

\begin{table}[H] \centering 
  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 2.438$^{***}$ & 3.602$^{***}$ & 0.362$^{***}$ & 4.575$^{***}$ & 5.007$^{***}$ & 11.149$^{***}$ & 6.400$^{***}$ & 12.771$^{***}$ & 2.842$^{***}$ & 3.659$^{***}$ \\ 
  & (0.042) & (0.012) & (0.011) & (0.051) & (0.056) & (0.080) & (0.030) & (0.028) & (0.238) & (0.187) \\ 
  & & & & & & & & & & \\ 
 Post & 0.466$^{***}$ & $-$0.173$^{***}$ & 0.095$^{***}$ & $-$0.174$^{***}$ & $-$0.636$^{***}$ & $-$0.771$^{***}$ & 0.096$^{***}$ & 0.006 & 1.794$^{***}$ & 1.778$^{***}$ \\ 
  & (0.037) & (0.010) & (0.010) & (0.048) & (0.051) & (0.076) & (0.025) & (0.024) & (0.197) & (0.164) \\ 
  & & & & & & & & & & \\ 
 Treated & $-$0.142$^{***}$ & 0.023$^{***}$ & $-$0.059$^{***}$ & 0.450$^{***}$ & 0.048 & 0.158$^{**}$ & 0.077$^{***}$ & $-$0.164$^{***}$ & 0.570$^{***}$ & 0.443$^{***}$ \\ 
  & (0.037) & (0.007) & (0.009) & (0.040) & (0.043) & (0.067) & (0.025) & (0.025) & (0.197) & (0.164) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & 0.152$^{***}$ & $-$0.031$^{***}$ & 0.061$^{***}$ & $-$0.236$^{***}$ & 0.275$^{***}$ & 0.253$^{***}$ & $-$0.072$^{***}$ & 0.139$^{***}$ & $-$0.910$^{***}$ & $-$0.728$^{***}$ \\ 
  & (0.040) & (0.011) & (0.010) & (0.052) & (0.056) & (0.082) & (0.027) & (0.026) & (0.216) & (0.177) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 21,523 & 63,902 & 21,523 & 61,827 & 64,224 & 64,224 & 21,523 & 21,523 & 1,280 & 1,759 \\ 
R$^{2}$ & 0.137 & 0.073 & 0.148 & 0.015 & 0.020 & 0.015 & 0.165 & 0.316 & 0.187 & 0.271 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-02-13 docs/tab/DID_without_USA_TWN.tex
Added new tables and figures for controls

\begin{table}[H] \centering 
  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 2.343$^{***}$ & 3.624$^{***}$ & 0.327$^{***}$ & 4.599$^{***}$ & 4.860$^{***}$ & 11.030$^{***}$ & 6.176$^{***}$ & 12.513$^{***}$ & 3.246$^{***}$ & 4.062$^{***}$ \\ 
  & (0.035) & (0.010) & (0.009) & (0.045) & (0.052) & (0.071) & (0.025) & (0.023) & (0.208) & (0.160) \\ 
  & & & & & & & & & & \\ 
 Post & 0.599$^{***}$ & $-$0.211$^{***}$ & 0.139$^{***}$ & $-$0.167$^{***}$ & $-$0.364$^{***}$ & $-$0.532$^{***}$ & 0.338$^{***}$ & 0.261$^{***}$ & 1.477$^{***}$ & 1.457$^{***}$ \\ 
  & (0.027) & (0.008) & (0.007) & (0.034) & (0.042) & (0.059) & (0.017) & (0.018) & (0.148) & (0.122) \\ 
  & & & & & & & & & & \\ 
 Treated & $-$0.065$^{**}$ & 0.007 & $-$0.025$^{***}$ & 0.326$^{***}$ & 0.040 & 0.099$^{*}$ & 0.158$^{***}$ & $-$0.010 & 0.375$^{**}$ & 0.116 \\ 
  & (0.029) & (0.006) & (0.007) & (0.031) & (0.037) & (0.054) & (0.019) & (0.019) & (0.150) & (0.126) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & 0.017 & 0.003 & 0.015$^{**}$ & $-$0.187$^{***}$ & 0.070 & 0.077 & $-$0.274$^{***}$ & $-$0.072$^{***}$ & $-$0.562$^{***}$ & $-$0.353$^{**}$ \\ 
  & (0.031) & (0.009) & (0.008) & (0.039) & (0.048) & (0.068) & (0.020) & (0.020) & (0.170) & (0.139) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 24,152 & 73,259 & 24,152 & 73,001 & 73,668 & 73,668 & 24,152 & 24,152 & 1,420 & 1,998 \\ 
R$^{2}$ & 0.143 & 0.075 & 0.154 & 0.014 & 0.021 & 0.015 & 0.157 & 0.291 & 0.174 & 0.246 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-02-13 docs/tab/main_DID.tex
Added new tables and figures for controls

--- 2019-01-23 docs/tab/main_DID.tex
@@
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 12.535$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.021) & (0.021) & (0.041) & (0.013) \\ 
+ Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 4.532$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 3.120$^{***}$ & 3.879$^{***}$ \\ 
+  & (0.033) & (0.010) & (0.008) & (0.044) & (0.050) & (0.068) & (0.023) & (0.021) & (0.197) & (0.151) \\ 
   & & & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.232$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
-  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
+ Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & $-$0.087$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & 1.563$^{***}$ & 1.587$^{***}$ \\ 
+  & (0.024) & (0.007) & (0.006) & (0.032) & (0.038) & (0.053) & (0.015) & (0.015) & (0.135) & (0.107) \\ 
   & & & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & $-$0.013 & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
-  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
+ Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.291$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & $-$0.013 & 0.395$^{***}$ & 0.210$^{*}$ \\ 
+  & (0.026) & (0.006) & (0.007) & (0.030) & (0.034) & (0.050) & (0.017) & (0.017) & (0.138) & (0.111) \\ 
   & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.047$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
-  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
+ Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.246$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.047$^{***}$ & $-$0.582$^{***}$ & $-$0.452$^{***}$ \\ 
+  & (0.028) & (0.008) & (0.007) & (0.037) & (0.044) & (0.061) & (0.018) & (0.018) & (0.158) & (0.125) \\ 
   & & & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.272 & 0.272 & 0.081 & 0.283 \\ 
+Observations & 28,067 & 82,242 & 28,067 & 80,319 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
+R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.012 & 0.019 & 0.013 & 0.157 & 0.272 & 0.194 & 0.276 \\ 
 \hline 

### 2019-02-13 docs/tab/main_DID.tex
All documents have been updated

--- 2019-02-05 docs/tab/main_DID.tex
@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+\begin{table}[H] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly hours spent in Kiribati waters, 10) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.023) & (0.021) & (0.041) & (0.013) \\ 
+ Constant & 2.343$^{***}$ & 3.624$^{***}$ & 0.327$^{***}$ & 4.599$^{***}$ & 4.860$^{***}$ & 11.030$^{***}$ & 6.176$^{***}$ & 12.513$^{***}$ & 3.246$^{***}$ & 4.062$^{***}$ \\ 
+  & (0.035) & (0.010) & (0.009) & (0.045) & (0.052) & (0.071) & (0.025) & (0.023) & (0.208) & (0.160) \\ 
   & & & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
-  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
+ Post & 0.599$^{***}$ & $-$0.211$^{***}$ & 0.139$^{***}$ & $-$0.167$^{***}$ & $-$0.364$^{***}$ & $-$0.532$^{***}$ & 0.338$^{***}$ & 0.261$^{***}$ & 1.477$^{***}$ & 1.457$^{***}$ \\ 
+  & (0.027) & (0.008) & (0.007) & (0.034) & (0.042) & (0.059) & (0.017) & (0.018) & (0.148) & (0.122) \\ 
   & & & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
-  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
+ Treated & $-$0.065$^{**}$ & 0.007 & $-$0.025$^{***}$ & 0.326$^{***}$ & 0.040 & 0.099$^{*}$ & 0.158$^{***}$ & $-$0.010 & 0.375$^{**}$ & 0.116 \\ 
+  & (0.029) & (0.006) & (0.007) & (0.031) & (0.037) & (0.054) & (0.019) & (0.019) & (0.150) & (0.126) \\ 
   & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
-  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
+ Post $\times$ Treated & 0.017 & 0.003 & 0.015$^{**}$ & $-$0.187$^{***}$ & 0.070 & 0.077 & $-$0.274$^{***}$ & $-$0.072$^{***}$ & $-$0.562$^{***}$ & $-$0.353$^{**}$ \\ 
+  & (0.031) & (0.009) & (0.008) & (0.039) & (0.048) & (0.068) & (0.020) & (0.020) & (0.170) & (0.139) \\ 
   & & & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.157 & 0.272 & 0.081 & 0.283 \\ 
+Observations & 24,152 & 73,259 & 24,152 & 73,001 & 73,668 & 73,668 & 24,152 & 24,152 & 1,420 & 1,998 \\ 
+R$^{2}$ & 0.143 & 0.075 & 0.154 & 0.014 & 0.021 & 0.015 & 0.157 & 0.291 & 0.174 & 0.246 \\ 
 \hline 

### 2019-02-15 docs/PIPA_Palau.tex
All documents have been updated
Modified figure sizes and aspects, ready to start working on the manuscript

@@
-\documentclass[9pt,twoside,lineno]{pnas-new}
+\documentclass[9p,twocolumn,twoside,lineno]{pnas-new}
 % Use the lineno option to display guide line numbers if required.
@@
 
-\begin{SCfigure*}
-\centering
-\includegraphics{img/LSMPAs_map.png}
+\begin{figure}
+\centering
+\includegraphics{img/LSMPAs_map.pdf}
 \caption{\label{fig:LSMPAs_map}Large Scale Marine
@@
 IUCN Ia or Ib, their designated English name is `Protected Area'.}
-\end{SCfigure*}
+\end{figure}
 
@@
 
-\begin{SCfigure*}
-\centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive
-Economic Zones (EEZs) of the region of interest. Countries that belong
-to the PNA are shown in blue, while empty polygons indicates all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon
-delineates PIPA.}
-\end{SCfigure*}
-
 The main tuna species caught in the region are skipjack
@@
 \clearpage
-\begin{landscape}
 
@@
 
-\end{landscape}
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics{img/other_specifications.pdf}
-\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
-for our variables of interest using different model specifications. Table \ref{tab:main_DID}
-reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/fishing_raster.png}
-\caption{\label{fig:fishing_raster}Yearly
-spatial distribution of fishing effort by treated and control vessels.
-Color corresponds to \% of total fishing effort in each panel.
-Red polygons show LSMPAs in the region.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/redist_trend.pdf}
-\caption{\label{fig:redist_trend}Monthly
-relative allocation of fishing effort by PIPA-fishing vessels before and
-after PIPA by region. Colors indicate the pre- and post- periods. Solid line
-across points shows local mean with a region-specific loess smoother.
-Vertical dashed lines indicates dates when satellites were added, solid vertical
-line indicates PIPA closure. Note that inflection points of
-the loess smoother are not affected by the addition of satellites.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/mean_change.pdf}
-\caption{\label{fig:mean_change}Coefficient
-estimates for the redistribution regression. Each panel shows the
-region-specific coefficients, with 95\% condifence intervals
-as error bars. The horizontal dashed line represents 0 change
-relative to the 2012 region-specific levels.}
-\end{figure}
-
-\clearpage
-\begin{landscape}
-
 \input{tab/mean_change}
 
-\end{landscape}
 \clearpage
@@
 	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all VDS countries by fishing and non-fishing days. B) Observed vessel-days for all VDS countries by country.}
+	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all countries by treated, control, and excluded vessels. B) Observed vessel-days for all vessels by country.}
 \end{figure}
@@
 \centering
-	\includegraphics{img/PS_VDS_KIR_by_year.pdf}
-	\caption{\label{fig:PS_VDS_KIR_by_year}Vessel days spent inside Kiribati waters by group of vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
+	\includegraphics{img/financial_indicators.pdf}
+	\caption{\label{fig:financial_indicators}Financial indicators for PNA countries.
+A) Revenue from fishing licenses fees, B) Catches in each countrie's EEZ, and C) Value of those catches.
+Vertical dashed line denotes implementation of PIPA.}
 \end{figure}
@@
 
+\begin{figure}
+\centering
+\includegraphics{img/PNA_map.png}
+\caption{\label{fig:PNA_map}Map of the Exclusive
+Economic Zones (EEZs) of the region of interest. Countries that belong
+to the PNA are shown in blue, while empty polygons indicates all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon
+delineates PIPA.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/other_specifications.pdf}
+\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
+for our variables of interest using different model specifications. Table \ref{tab:main_DID}
+reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/fishing_raster.png}
+\caption{\label{fig:fishing_raster}Yearly
+spatial distribution of fishing effort by treated and control vessels.
+Color corresponds to \% of total fishing effort in each panel.
+Red polygons show LSMPAs in the region.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/redist_trend.pdf}
+\caption{\label{fig:redist_trend}Monthly
+relative allocation of fishing effort by PIPA-fishing vessels before and
+after PIPA by region. Colors indicate the pre- and post- periods. Solid line
+across points shows local mean with a region-specific loess smoother.
+Vertical dashed lines indicates dates when satellites were added, solid vertical
+line indicates PIPA closure. Note that inflection points of
+the loess smoother are not affected by the addition of satellites.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/mean_change.pdf}
+\caption{\label{fig:mean_change}Coefficient
+estimates for the redistribution regression. Each panel shows the
+region-specific coefficients, with 95\% condifence intervals
+as error bars. The horizontal dashed line represents 0 change
+relative to the 2012 region-specific levels.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/PS_VDS_KIR_by_year.pdf}
+	\caption{\label{fig:PS_VDS_KIR_by_year}Vessel days spent inside Kiribati waters by group of vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/hist_kir_fishing.pdf}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
+\end{figure}
+
 \section{Palau National Marine Sanctuary}\label{PNMS}
@@
 
-%
-%\hypertarget{stream-of-data-by-vessel-group-and-period}{%
-%\subsection{Stream of data by vessel, group, and
-%period}\label{stream-of-data-by-vessel-group-and-period}}
-
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
-%\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
-%fishing events by vessels through time. Each line represents a vessel,
-%with dots indicating months with fishing activity and colors indicating
-%the pre and post periods.}
-%\end{figure}
-
-%\clearpage
-
-%\begin{figure}
-%	\centering
-%	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-%	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
-%		number of vessels by month for all vessels. Vertical dashed lines
-%		indicates dates when satellites were added, solid line indicates PIPA
-%		closurePIPA closure.}
-%\end{figure}
-
-%\clearpage
-
-%\hypertarget{longliners}{%
-%\subsection{Longliners}\label{longliners}}
-
-%Longliners show a similar pattern of effort reduction. However, the
-%magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
-%including month and flag FEs for the general treatment-control groups,
-%or when excluding Chinese vessels. This, along with higher standard
-%error values suggest that longliners have a smaller and more variable
-%response to the implementation of LSMPAs.
-
-%\begin{table}[!htbp] \centering 
-%  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications.
-The first three columns use all data for controls.
-Columns 4 - 6 exclude Chinese vessels.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
-%  \label{} 
-%\small 
-%\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
-%\\[-1.8ex]\hline 
-%\hline \\[-1.8ex] 
-% & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
-%\cline{2-7} 
-%\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
-%\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
-%\hline \\[-1.8ex] 
-% Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
-%  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
-%  & & & & & & \\ 
-% post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
-%  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
-%  & & & & & & \\ 
-% treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
-%  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
-%  & & & & & & \\ 
-% sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
-%  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
-%  & & & & & & \\ 
-% sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
-%  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
-%  & & & & & & \\ 
-% post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
-%  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
-%  & & & & & & \\ 
-%\hline \\[-1.8ex] 
-%Control & All & All & All & -CHN & -CHN & -CHN \\ 
-%Month FE & No & Yes & Yes & No & Yes & Yes \\ 
-%Flag FE & No & No & Yes & No & No & Yes \\ 
-%Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
-%R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
-%\hline 
-%\hline \\[-1.8ex] 
-%\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-%\end{tabular} 
-%\end{table}
-%
-%\clearpage
-%
-%\hypertarget{quarterly-did-interactions}{%
-%\subsubsection{Quarterly DID
-%interactions}\label{quarterly-did-interactions}}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
-%\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
-%and treatment. Control group is all vessels.}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
-%\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
-%and treatment. Control group is vessels from PNA.}
-%\end{figure}
-%
+\clearpage
+
+\section{Alternative Controls}
+\subsection{Excluding all Chinese vessels}
+
+\input{tab/DID_without_CHN.tex}
+
+\clearpage
+\subsection{Excluding all PNA vessels}
+
+\input{tab/DID_without_PNA.tex}
+
+\clearpage
+\subsection{Excluding all USA and TWN vessels}
+
+\input{tab/DID_without_USA_TWN}
+
 %\begin{figure}

### 2019-02-15 scripts/content/fig_LSMPAs_map.R

@@ -29,7 +29,8 @@ mpas <- read_sf(dsn = here::here("data", "spatial", "LSMPAs"), layer = "LSMPAs")
          strict = ifelse(is.na(strict), "Others", strict),
          strict = ifelse(wdpaid == 309888, "PIPA", strict),
          Legend = fct_relevel(strict, c("No-Take", "PIPA", "Others"))) %>% 
-  filter(!name == "Longline")
+  filter(!name == "Longline",
+         !strict == "Others")
 
 coast <- map_data('world', wrap=c(-20,340), ylim=c(-85,75))%>%
   select(group, lat, long) %>%
@@ -43,19 +44,23 @@ coast <- map_data('world', wrap=c(-20,340), ylim=c(-85,75))%>%
   ungroup()
 
 plot <- ggplot() +
-  geom_sf(data = coast, fill = "#E3E3E3") +
-  geom_sf(data = mpas, fill = "transparent", color = "black", size = 1) +
+  geom_sf(data = coast, fill = "#E3E3E3", color = "black") +
+  geom_sf(data = mpas, fill = "transparent", color = "black") +
   geom_sf(data = mpas, aes(fill = Legend), color = "transparent") +
-  ggtheme_map() +
+  theme_nothing() +
   scale_fill_manual(values = c("steelblue", "red", "steelblue1")) +
-  theme(legend.justification = c(0.5, 1),
-        legend.position = c(0.5, 0.05),
-        legend.box = "horizontal",
-        legend.background = element_blank()) +
-  guides(fill = guide_legend(ncol = 3))
+  theme(legend.position = "none",
+        panel.grid.major = element_line(color = "transparent")) +
+  scale_x_continuous(expand=c(0,0)) +
+  scale_y_continuous(expand=c(0,0)) +
+  labs(x = NULL, y = NULL)
 
-ggsave(plot, filename = here::here("docs", "img", "LSMPAs_map.png"), width = 6, height = 3.5)
-ggsave(plot, filename = here::here("docs", "img", "LSMPAs_map.pdf"), width = 6, height = 3.5)
+ggsave(plot, filename = here::here("docs", "img", "LSMPAs_map.png"),
+       width = 3.4,
+       height = 1.7)
+ggsave(plot, filename = here::here("docs", "img", "LSMPAs_map.pdf"),
+       width = 3.4,
+       height = 1.7)
 
 
 

### 2019-02-15 scripts/content/fig_all_panels.R

@@ -47,7 +47,7 @@ fishing_hours <- effort_by_vessel %>%
   filter(fishing) %>%
   varplot(hours, "hours") +
   theme(legend.justification = c(0, 1),
-        legend.position = c(0, 1.2))
+        legend.position = c(0, 1.1))
 
 # Plot of nonfishing hours
 nonfishing_hours <- effort_by_vessel %>% 
@@ -155,7 +155,9 @@ plot <- cowplot::plot_grid(
 )
 
 # Export figure
-ggsave(plot, filename = here::here("docs", "img", "all_panels.pdf"), width = 6, height = 8)
+ggsave(plot, filename = here::here("docs", "img", "all_panels.pdf"),
+       width = 7,
+       height = 9.3)
 
 
 

### 2019-02-15 scripts/content/included_PS_VDS_DiDs.R

@@ -35,8 +35,7 @@ vessel_activity <- readRDS(file = here::here("raw_data",
   mutate(fishing = ifelse(is.na(fishing), F, fishing),
          fishing = ifelse(fishing, "Fishing", "Non-fishing"),
          group = ifelse(treated, "Treatment", "Control"),
-         group = ifelse(is.na(treated), "Others", group),
-         group = fct_relevel(group, c("Treatment", "Control", "Others")))
+         group = ifelse(is.na(treated), "Others", group))
 
 #### CREATE THE DATA ################################################
 
@@ -56,19 +55,24 @@ vessel_activity_year_country_included <- vessel_activity %>%
   ungroup()
 
 # Plot for yearly PS VDS by activity by included vessels
-p1 <- ggplot(vessel_activity_year_included, aes(x = year, y = days, color = group)) +
+p1 <- ggplot(vessel_activity_year_included, aes(x = year, y = days/1000, color = group)) +
   geom_line() +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_manual(values = c("#E41A1C", "#4DAF4A", "#377EB8")) +
   cowplot::theme_cowplot() +
+  guides(color = guide_legend(title = "Group")) +
   theme(text = element_text(size = 10),
-        axis.text = element_text(size = 8))+
-  labs(x = "Year", y = "Vessel-days")
+        axis.text = element_text(size = 8),
+        legend.text = element_text(size = 8),
+        legend.justification = c(1, 0),
+        legend.position = c(1, -0.05))+
+  labs(x = "Year", y = "Vessel-days (Ths)") +
+  geom_vline(xintercept = 2015, linetype = "dashed")
 
 #Save plot
 ggsave(p1,
        filename = here::here("docs", "img", "included_PS_VDS_year_DiD.pdf"),
-       width = 6,
-       height = 3.5)
+       width = 3.4,
+       height = 2.2)
 
 
 # Plot for yearly PS VDS by country

### 2019-02-15 scripts/get_LSMPAs.R

@@ -1,21 +1,0 @@
-###################
-#   get_LSMPAs    #
-###################
-
-###############################################
-# This script reads in the WDPA and keeps only
-# MPAs larger than 250000 in marine area.
-##############################################
-
-# Load magrittr to have the pipe
-library(magrittr)
-
-# Load the database
-sf::read_sf(here::here("raw_data", "spatial", "WDPA_Jan2019"),
-            layer = "WDPA_Jan2019_marine-shapefile-polygons",
-            quiet = T,
-            stringsAsFactors = F) %>% 
-  dplyr::filter(GIS_M_AREA > 250000) %>% #Keep large MPAs
-  sf::st_write(dsn = here::here("data", "spatial", "LSMPAs", "LSMPAs.shp")) #Save to file
-
-# END OF SCRIPT

### 2019-02-15 docs/PIPA_Palau.tex
Updated manuscript and resized some figures

@@
 We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques evaluate the behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a Large-Scale Marine Protected Area.
-Our work provides three main findings: 1) we observe a crowding effect for the first months after implementation, 2) aggregate fishing effort remains relatively constant; and 3) vessels that fished inside the protected area redistribute to adjacent waters, including the high seas.
+Our work provides three main findings: 1) we observe a crowding effect for the first months after implementation, 2) aggregate fishing effort remains relatively constant; and 3) vessels that fished inside the protected area redistribute to adjacent waters, including the high seas, 4) the redistribution of vessels results in a reduction of 2500 vessel-days into Kiribati, which represents a loss of ~30 million USD.
 This suggests that rights to fish in PNA waters might now be less valuable.
-We do not observe an increase in daily fishing hours for vessels that used to fish within the LSMPA, compared to a control group of vessels.
-Thus, for vessels that have chosen to continue to operate following the closure, we do not observe evidence that they are being forced to exert more effort as a result of the closure.
 Unfortunately, without detailed data on vessel catch, we cannot conclude whether vessels are better or worse off financially following the closure.
-We use our results to inform predictions of the impacts of a proposed LSMPA in Palau (a PNA member).
-Our estimates of the potential losses range from \$2.5 to \$11 million annually.
-This wide range hinges on what Palau's future PNA allocation will be and the extent to which US aid will continue through non-fishing channels.
-Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications for marine conservation and fisheries management.
+We use our results to inform predictions of the impacts of a proposed LSMPA in Palau (a PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
+Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have large ecological and economic implications for marine conservation and fisheries management in developing countries.
 As countries continue to implement LSMPAs as a way to reach ocean protection targets, managers should consider how fishing effort will change in space and time to ensure that fishing effort is not just displaced elsewhere.
@@
 
-%(QUESTION FOR JC: WHEN IS THIS (selling of rVDS rights)? And wasn't the closure expected?).
-
 \section{Introduction}\label{introduction}
 
-\dropcap{M}arine Protected Areas (MPAs) are intended to safeguard parts of the
-ocean from fishing and other extractive activities. Current
-international goals aim to protect 10\% of the ocean environment by
-2020. In an effort to meet this target, there has been a rapid
-increase recently in MPA coverage \citep{wood_2008,sala_2018}, largely driven by
-a small number of Large-Scale Marine Protected Areas (LSMPAs).\footnote{See, for example, \citep{game_2009,singleton_2014,boonzaier_2016,mccauley_2016,alger_2017}.}
-Today, a small number of LSMPAs make up at least 80\%
-of the managed areas in the ocean \citep{toonen_2013}.
-
-Given the relatively recent establishment of most LSMPAs, very little is
-known about their human dimensions and implication for fisheries
-\citep{gray_2017}. As with smaller MPAs, it is important that we
-understand the socioeconomic implications of management interventions.
-One issue of particular importance is that of the displacement or
-redistribution of fishing effort, which may influence the outcomes of an
-MPA \citep{smith_2003}. Theoretical models make different assumptions
-about the ways in which fishers will reallocate fishing effort after an
-area closure, which often determine whether or not MPAs produce negative or positive impacts on fisheries.
-The existing empirical literature focuses on small MPAs and has been criticized for confounding correlation with causation \citep{ferraro2018causal}.
+\dropcap{H}umans are increasingly utilizing the oceans.
+Conservation and development targets are likely to cause activities such as off-shore aquaculture, conservation, deep-sea mining and and fisheries to compete for space.
+As we move forward in the blue economy, we must understand the potential effects of displacing one activity over the other.
+For example, global international goals aim to protect 10\% of the ocean environment by 2020.
+In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which ocurr in the world's largest fishing grounds for tuna.
+While today a small number of LSMPAs make up at least 80\% of the managed areas in the ocean \citep{toonen_2013}, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
+One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure \citep{smith_2003}.
+
+One of the most notable Large-Scale Marine Protected Areas recently implemented is the Phoenix Island Protected Area (PIPA) in Kiribati.
+The area implemented in January 1st of 2015 has an extension of 397,447 km\textsuperscript{2} and represents was implemented within an area that produces 50\% of the World's tuna.
+Tuna purse seine fisheries in the region are collectively managed under a Vessel-day scheme (VDS) by nine countries commonly refered to as the Parties to the Nauru Agreement (PNA).
+Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu.
+Tokelau joined the PNA group in 2012 and started selling access rights in 2013.
+The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
+Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}.
+The revenue from access fees represents up to 50\% of government revenue from some of this countries.
+
+LSMPAs were initially assumed to have little social implications due to their general remoteness.
+However, there have been calls to incorporate the human dimensions into LSMPA management and evaluation \citep{agardy_2011,gray_2017}.
+Most research incorporating these dimensions has focused on governance and enforcement of LSMPAs \cite{alger_2017,christie_2017}, but they are yet to be the focus of economic analyses \citep{gray_2017}.
+For example, the anticipation of PIPA lead to preemptive overfishing, which will likely erod or delay the expected benefits of the intervention \cite{mcdermott_2018}.
+However, a reduction in fishing area without proper adjustments to the total vessel-days permited every year is likely to increase fishing intensity in the remaining open waters.
+While no studies have assessed the immplications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020.
+
+Here we evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati.
+We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
+These are two of the largest protected areas on the planet and both are controled by PNA countries, where the largest tuna fisheries ocurr.
+
+We use identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters.
+We continuously observe 92 vessels for the 2012 - 2018 period.
+Of these, 64 vessels fished within PIPA at least once prior to its implementation.
+The remaining 28 vessels never fished in PIPA these waters.
+We refer to these groups as treated and control groups.
+
+\begin{figure}
+\centering
+\includegraphics{img/LSMPAs_map.pdf}
+\caption{\label{fig:LSMPAs_map}Large Scale Marine Protected Areas. The map shows all areas larger than 30,000 Km\textsuperscript{2}. The Phoenix Island Protected Area is shown in red.}
+\end{figure}
+
+\section{Results}\label{results}
+
+\subsection{Crowding effect}
+
+We first inspect the crowding effects that may arise due to the net reduction in fishing area.
+We produced rasters of monthly fishing effort for our treatment and control groups, and calculated two indices of spatial overlap: 1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.
+We find that the two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
+\ref{fig:sp_corr}).
+The number of vessels with presence from both fleets and spatial correlations increase by a factor of four and three, respectively.
+This increase in crowding is likely to increase the encounter rates within vessels, and reduce the efficienvy of fishing opperations, resulting in a nusicance to vessels.
+This would cause vessels to leave curent fishing grounds, which might explain the pattern we observe of an increase and subsequent decrease back to pre-implementation levels.
+
+\begin{figure}
+\centering
+\includegraphics{img/sp_corr.pdf}
+\caption{\label{fig:sp_corr}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}}
+\end{figure}
+
+\input{tab/sp_corr}
+
+\subsection{Behavioral changes}
+
+The behavioral responses that vessels can have to a spatial closure may occurr in different ways.
+For example, displacement to new fishing grounds may represent a cost as fishers search the ocean
+to identify the most suitable fishing places.
+This may result in increased fuel and labor costs.
+For every vessel we calculate in eight key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters and Kiribati waters (Fig.
+\ref{fig:all_panels}).
+We leverage our BACI design and implement a log-linear difference-in-differences analyses to evaluate how these measures change for treated vessels after implementation of PIPA, relative to the trends observed for control vessels.
+
+We find no evidence of treated vessels fishing for mor hours after PIPA implementation, and a slight increase of 1\% more time at sea ($p < 0.05$; Table \ref{tab:main_DID}).
+Treated vesseks traveled 20\% less, with fishing events ocurring 23.8\% closer to shore and 5\% closer to port.
+These changes in distance from shore and port ar elikely caused by redistribution, as we observe that treated vessels fish 58\% and 45\% less in PNA and Kiribati waters, compared to the trend observed for control vessels ($p < 0.01$).
+The fact that vessel fishing hours did not decrease but that their time spent in PNA and Kiribati waters decreases suggests that these vessels have re-distributed elsewhere.
+
+\subsection{Economic impacts}
+
+The crowding effect combined with the reduction of hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy access fees from PNA countries.
+To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by all PNA countries (Fig.
+\ref{fig:all_PS_VDS_year}).
+In this case we look at all 313 vessels, but continue to group them as treated and control vessels, as well as other vessels that we do not observe continuously or came into the fishery after the implementation of PIPA.
+We term this last group as ``others''.
+We find that the treated vessels spent 3,600 less days in PNA waters when comparing 2016 and 2017, while control and other vessels increased their PNA fishing by 411 and 1687 for the same period, respectively (Figs.
+\ref{fig:all_PS_VDS_year}A and \ref{fig:included_PS_VDS_year_DiD}).
+Furthermore, in 2017 treated vessels exhibit the lowest allocation of hours to PNA waters at just 10,026 vessel-days.
+This is lower than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
+The 3,600 vessel-day reduction by treated between 2016 and 2017 vessels corresponds to \$43.2 million USD at an average vessel-day price of \$12,000 USD.
+The 2,526 vessel-day reduction would then represent forgone profits in the order of 30.3 million USD.
+%We need to come up with an identification strategy for this, I believe.
+I simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort (current DiD estimate of these data suggest a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects).
+
+Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
+\ref{fig:all_PS_VDS_year}B).
+
+From the government side, we combine annual license revenue and EEZ-specific catch statistics compiled from the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}).
+
+\begin{figure}
+\centering
+	\includegraphics{img/all_PS_VDS_year.pdf}
+	\caption{\label{fig:all_PS_VDS_year}A)Observed vessel-days for all countries by treated, control, and excluded vessels.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
+	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by group of vessels.}
+\end{figure}
+
+\subsection{Potential Revenue Loss Palau}
+
+On October 28, 2015, the President of Palau, H.E.
+Tommy E.
+Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
+The sanctuary will fully protect about 80 percent of the nation’s EEZ.
+To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
+This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
+There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
+However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
+comm.).
+In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
+Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
+comm.).
+
+Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
+Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
+It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
+In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel day and export tax revenues are lost.
+Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
+Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+
+\input{revenue_loss}
+
+\begin{figure}
+\centering
+	\includegraphics{img/financial_indicators.pdf}
+	\caption{\label{fig:financial_indicators}Financial indicators for PNA countries.
+A) Revenue from fishing licenses fees, B) Catches in each countrie's EEZ.
+Vertical dashed line denotes implementation of PIPA.}
+\end{figure}
+
+\clearpage
+\begin{figure}
+\centering
+\includegraphics{img/all_panels.pdf}
+\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
+\end{figure}
+\clearpage
+
+\input{tab/main_DID}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve.
+The implementation would lead to an increase in these measures, which, 
+if vessels avoid crowding, should then come back down. We therefore expect to
+have three inflection points: 1) in the transition between no trend and initial crowding due to MPA
+implementation, 2) When the crowding has reached its maximum and starts to decrease,
+and 3) when the decrease levels off, pressumably to pre-MPA levels.
+For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
+centering our time series of crowding indices on the day of implementation. Our
+explanatory variable is therefore the number of months before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 
+has a value of -1, and Feb of 2015 would receive a value of 1.
+
+The pattern observed here could just be an artifact
+of satellite detections increasing though time. Therefore we also
+calculate a spatial correlation of presence/absence and observe similar
+patterns (Fig. \ref{fig:sp_corr}B). Spatial overlap increases
+in 2015 as vessels from PIPA are excluded, but then starts to decline.
+Our 4th degree polynomial shows the expected patterh of a relative
+constant trend before implementation which is followed by rapid increased
+and subsequent decrease.
 
@@
 Does effort increase or decrease and where does it go?
-We use identification of fishing activity via Automatic
-Identification Systems (AIS) and causal inference techniques to describe
+We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to describe
 the behavioral changes and spatial redistribution of the industrial tuna
@@
 effort is displaced from LSMPAs might provide insights into how distant water fishing fleets would react to a high seas closure.
+
+The existing empirical literature focuses on small MPAs and has been criticized for confounding correlation with causation \citep{ferraro2018causal}.
 
@@
 Management \citep{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.}
-
-\begin{figure}
-\centering
-\includegraphics{img/LSMPAs_map.pdf}
-\caption{\label{fig:LSMPAs_map}Large Scale Marine
-Protected Areas. The map shows all areas larger than 250,000
-Km\textsuperscript{2}. Areas in dark blue meet at least one of these
-conditions: reported no take area is greater than 0, are categorized as
-IUCN Ia or Ib, their designated English name is `Protected Area'.}
-\end{figure}
-
-LSMPAs were initially assumed to have little social implications due
-to their general remoteness. However, there have been calls to incorporate the
-human dimensions into LSMPA management and evaluation
-\citep{agardy_2011,gray_2017}. Most research incorporating these
-dimensions has focused on governance and enforcement of LSMPAs
-\cite{alger_2017,christie_2017}, but they are yet to be
-the focus of economic analyses \citep{gray_2017}. Overall, there has
-been little empirical work regarding LSMPAs. Recent technological
-advances in vessel-detection systems allows for the discovery and
-advancement of many important facets of LSMPAs. For example,
-\cite{mcdermott_2018} show that the anticipation of a LSMPA can lead to
-preemptive overfishing, which can erode or delay the expected benefits
-of the intervention. \cite{white_2017} combine shark tags and
-vessel-tracking data to demonstrate that the fairly large Palmyra Atoll
-National Wildlife Refuge (54,000 Km\textsuperscript{2}) protects two
-thirds of tagged gray reef sharks by effectively excluding fishing
-effort. More recently, \citep{bradley_2018} use similar data to
-highlight cases of potential illegal shark fishing \emph{inside} a 2
-million km\textsuperscript{2} shark sanctuary. To date, no studies have
-evaluated the displacement of fishing effort due to LSMPA
-implementation.
 
@@
 
-The Nauru Agreement was established in 1982 by a select group of Pacific
-island nations to manage their important tuna resources more effectively.
-Parties to the Nauru Agreement (PNA) Members
-include the Federated States of Micronesia, Kiribati, the Marshall Islands,
-Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu.
-Tokelau joined the PNA group in 2012 and started selling access rights in 2013. The Nauru
-Agreement regulates access of foreign vessels (\emph{i.e.} those from
-non-PNA countries). Holding \textasciitilde{}80\% of historical
-skipjack tuna purse seine grounds within their Exclusive Economic Zones, PNA
-countries have achieved greater bargaining power when providing fishing access to foreign
-fleets \cite{havice_2010}.
-
 The cooperation that emerged under the Nauru Agreement allowed for subsequent
@@
 
-The behavioral responses that vessels can have to a spatial closure may occurr in different ways.
-For example, displacement to new fishing grounds may represent a cost, as fishers search the ocean
-to identify the most suitable fishing places. This may result in increased fuel and labor costs. Therefore,
-we are interested in three key measures that could capture a captain's response to a spatial closure:
-daily fishing hours, daily non-fishing at-sea hours, and the proportion of fishing to non-fishing hours at sea.
-We calculate these measures for each vessel, and build a daily panel
-with 152,802 observations. Table \ref{tab:baci_n_s} shows the number
-of vessels following a Before-After-Control-Impact (BACI) design, as well as the mean fishing hours, before
-and after PIPA was implemented.
-
-Following the idea behind increased search time, we also use each vessel's track to compute
-the total daily distance traveled (km) by calculating the distance between every observation.
-Additionally, we include the daily mean distance to the nearest port and mean distance to shore
-for all positions and for fishing events only. Finally, we calculate the monthly proportion of each vessel's
-fishing time that was allocated to Kiribati waters and PNA waters
-
-Fig. \ref{fig:all_panels} shows that monthly mean values of the 10 variables that we use,
-for treated and control vessels.  Across all measures, the treatment and control vessels follow similar patterns,
-confirming our claim that the control group provides a plausible
-counterfactual.
-
 \input{tab/baci_n_s}
-
-\begin{figure}
-\centering
-\includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time series showing mean monthly values es for our 10 variables of interest:
-A) Fishing hours, B)Non-fishing hours at-sea,
-C) Proportion of fishing hours to total hours at-sea,
-D) Distance traveled, E) Mean distance from port,
-F) Mean distance from shore,
-G) Mean distance from port for fishing events,
-H) Mean distance from shore for fishing events,
-I) Proportion of hours spent in Kiribati waters,
-J) Proportion of fishing hours spent in PNA waters.}
-\end{figure}
 
@@
 
-\section{Results}\label{results}
+\section{Results2}
 
@@
 fishing now?
-
-%When reducing the linear structure of the
-%\(Pre \times Post\) design and instead interacting the treatment dummy
-%with quarterly or year-month combinations, we are not able to reject the
-%null hypothesis of no change, suggesting that the total fishing hours
-%remains similar for the displaced vessels (Figs.
-%\ref{fig:q1}-\ref{fig:ym4}).
 
@@
 had both treated and control vessels each month (Fig.
-\ref{fig:sp_corr}A). The pattern observed here could just be an artifact
-of satellite detections increasing though time. Therefore we also
-calculate a spatial correlation of presence/absence and observe similar
-patterns (Fig. \ref{fig:sp_corr}B). Spatial overlap increases
-in 2015 as vessels from PIPA are excluded, but then starts to decline.
-Our 4th degree polynomial shows the expected patterh of a relative
-constant trend before implementation which is followed by rapid increased
-and subsequent decrease.
-
-\clearpage
-
-\input{tab/main_DID}
+\ref{fig:sp_corr}A).
+
+\clearpage
 
@@
 \clearpage
-
-\begin{figure}
-\centering
-\includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that
-had treated and control vessels (A) and spatial correlation in the
-presence-absence of treated and control vessels per cell (B).}
-\end{figure}
-
-\input{tab/sp_corr}
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all countries by treated, control, and excluded vessels. B) Observed vessel-days for all vessels by country.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
-	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside VDS waters by group of vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/financial_indicators.pdf}
-	\caption{\label{fig:financial_indicators}Financial indicators for PNA countries.
-A) Revenue from fishing licenses fees, B) Catches in each countrie's EEZ, and C) Value of those catches.
-Vertical dashed line denotes implementation of PIPA.}
-\end{figure}
 
@@
 
-\subsubsection{Potential Revenue Loss under the PNMS}
-
-To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
-This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
-There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
-However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
-comm.).
-In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
-Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
-comm.).
-
-Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
-Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
-It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
-In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel day and export tax revenues are lost.
-Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
-Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
-
-\input{revenue_loss}
-
 \subsubsection{Plans for a domestic pelagic fishery}

### 2019-02-15 docs/tab/main_DID.tex
Updated manuscript and resized some figures

--- 2019-02-05 docs/tab/main_DID.tex
@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.023) & (0.021) & (0.041) & (0.013) \\ 
-  & & & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
-  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
-  & & & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
-  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
-  & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
-  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
-  & & & & & & & & & & \\ 
+ Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 4.532$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 3.120$^{***}$ & 3.879$^{***}$ \\ 
+  & (0.033) & (0.010) & (0.008) & (0.044) & (0.023) & (0.021) & (0.197) & (0.151) \\ 
+  & & & & & & & & \\ 
+ Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & $-$0.087$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & 1.563$^{***}$ & 1.587$^{***}$ \\ 
+  & (0.024) & (0.007) & (0.006) & (0.032) & (0.015) & (0.015) & (0.135) & (0.107) \\ 
+  & & & & & & & & \\ 
+ Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.291$^{***}$ & 0.163$^{***}$ & $-$0.013 & 0.395$^{***}$ & 0.210$^{*}$ \\ 
+  & (0.026) & (0.006) & (0.007) & (0.030) & (0.017) & (0.017) & (0.138) & (0.111) \\ 
+  & & & & & & & & \\ 
+ Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.246$^{***}$ & $-$0.238$^{***}$ & $-$0.047$^{***}$ & $-$0.582$^{***}$ & $-$0.452$^{***}$ \\ 
+  & (0.028) & (0.008) & (0.007) & (0.037) & (0.018) & (0.018) & (0.158) & (0.125) \\ 
+  & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.157 & 0.272 & 0.081 & 0.283 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 28,067 & 82,242 & 28,067 & 80,319 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
+R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.012 & 0.157 & 0.272 & 0.194 & 0.276 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-02-15 scripts/content/PS_VDS_PNA_by_year_eez.R

@@ -95,7 +95,7 @@ p2 <- ggplot(vessel_activity_year_country, aes(x = year, y = days/1000, fill = e
   scale_fill_brewer(palette = "Set1") +
   geom_hline(yintercept = 45, linetype = "dashed") +
   cowplot::theme_cowplot() +
-  guides(fill = guide_legend(title = "Group")) +
+  guides(fill = guide_legend(title = "Country")) +
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8),
         legend.text = element_text(size = 8))+
@@ -103,6 +103,12 @@ p2 <- ggplot(vessel_activity_year_country, aes(x = year, y = days/1000, fill = e
 
 # Combine plots
 p12 <- cowplot::plot_grid(p1, p2, labels = "AUTO", ncol = 1)
+
+#Save plot
+ggsave(p1,
+       filename = here::here("docs", "img", "all_PS_VDS_year.pdf"),
+       width = 3.4,
+       height = 2.1)
 
 #Save plot
 ggsave(p12,

### 2019-02-15 scripts/content/plot_financial_indicators.R

@@ -1,0 +1,107 @@
+##################################
+#   plot_financial_indicators    #
+#################################
+
+##################################################################
+# This script produces plots of financial indicators
+# related to each PNA country. The data com from the
+# FFA (https://www.ffa.int/node/2050). The PDF report is in the
+# /reports folder.
+##################################################################
+
+####### SET UP #########################
+
+# Load libraries
+library(cowplot)
+library(here)
+library(tidyverse)
+
+financial_data <- read.csv(file = here("data", "financial_data.csv")) %>% 
+  mutate(country = fct_relevel(country, "KIR"))
+
+# Plot licenses
+p1 <- financial_data %>% 
+  drop_na(revenue) %>% 
+  ggplot(mapping = aes(x = year, y = revenue, fill = country)) +
+  geom_line() +
+  geom_point(shape = 21,
+             color = "black",
+             size = 2) +
+  # facet_wrap(~country, scales = "free_y") +
+  geom_vline(xintercept = 2015,
+             linetype = "dashed") +
+  theme_cowplot() +
+  scale_fill_brewer(palette = "Set1") +
+  labs(x = "Year",
+       y = "Revenue from licenses\n(Million USD)") +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8),
+        strip.background = element_blank(),
+        legend.position = "none")
+
+# Plot for catches
+p2 <- ggplot(data = financial_data,
+             mapping = aes(x = year, y = catches/1000, fill = country)) +
+  geom_line() +
+  geom_point(shape = 21,
+             color = "black",
+             size = 2) +
+  # facet_wrap(~country, scales = "free_y") +
+  geom_vline(xintercept = 2015,
+             linetype = "dashed") +
+  theme_cowplot() +
+  scale_fill_brewer(palette = "Set1") +
+  guides(legend = guide_legend(title = "Country")) +
+  labs(x = "Year",
+       y = "Catches in EEZ\n(Thousand Tonnes)") +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8),
+        strip.background = element_blank(),
+        legend.justification = c(0, 1),
+        legend.position = c(0, 1.15)) +
+  guides(fill = guide_legend(title = "Country", ncol = 2))
+
+# Plot for value
+p3 <- ggplot(data = financial_data,
[…]

### 2019-02-15 scripts/processing/get_LSMPAs.R

@@ -1,0 +1,21 @@
+###################
+#   get_LSMPAs    #
+###################
+
+###############################################
+# This script reads in the WDPA and keeps only
+# MPAs larger than 250000 in marine area.
+##############################################
+
+# Load magrittr to have the pipe
+library(magrittr)
+
+# Load the database
+sf::read_sf(here::here("raw_data", "spatial", "WDPA_Jan2019"),
+            layer = "WDPA_Jan2019_marine-shapefile-polygons",
+            quiet = T,
+            stringsAsFactors = F) %>% 
+  dplyr::filter(GIS_M_AREA > 30000) %>% #Keep large MPAs
+  sf::st_write(dsn = here::here("data", "spatial", "LSMPAs", "LSMPAs.shp")) #Save to file
+
+# END OF SCRIPT

### 2019-02-15 scripts/processing/join_financial_indicators.R

@@ -1,0 +1,61 @@
+##################################
+#   join_financial_indicators    #
+#################################
+
+##################################################################
+# This script produces combines financial indicators
+# related to each PNA country. The data com from the
+# FFA (https://www.ffa.int/node/2050). The PDF report is in the
+# /reports folder.
+##################################################################
+
+####### SET UP #########################
+
+# Load libraries
+library(countrycode)
+library(here)
+library(tidyverse)
+
+# List of PNA countries
+PNA <- c("FSM",
+         "KIR",
+         "MHL",
+         "NRU",
+         "PLW",
+         "PNG",
+         "SLB",
+         "TUV",
+         "TKL")
+
+####  PLOT VALUE AND CATCHES ####
+
+# Load catch data
+catches <- read_csv(here("raw_data", "FFA", "catches_by_eez.csv"),
+                    col_types = cols()) %>% 
+  gather(year, catches, -country) %>% 
+  mutate(year = as.numeric(year))
+
+# Load value data and join to catch data
+catches_and_value <- read_csv(here("raw_data", "FFA", "value_of_catches_by_eez.csv"),
+                              col_types = cols()) %>% 
+  gather(year, value, -country) %>% 
+  mutate(year = as.numeric(year)) %>% 
+  left_join(catches, by = c("country", "year")) %>% 
+  select(year, country, catches, value) %>% 
+  mutate(country = countrycode(sourcevar = country,
+                               origin = "country.name",
+                               destination = "iso3c"),
+         country = fct_relevel(country, "KIR"),
+         value = value / 1e6) %>% 
+  filter(country %in% PNA)
+
+licenses <- read_csv(here("raw_data", "FFA", "revenue_from_fees.csv"),
+                     col_types = cols()) %>% 
+  gather(year, revenue, -Country) %>% 
+  rename(country = Country) %>% 
+  mutate(year = as.numeric(year)) %>% 
+  filter(country %in% PNA)
+
+financial_data <- left_join(catches_and_value, licenses, by = c("country", "year"))
+
+write.csv(financial_data, file = here("data", "financial_data.csv"))

### 2019-02-19 docs/PIPA_Palau.tex
Added new figures and updated MS

@@
 % Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Marine Protected Areas $|$ Fisheries $|$ Purse Seining $|$ Marine Conservation}
+\keywords{Marine Spatial Planning $|$ Fisheries $|$ Marine Conservation}
 
@@
 The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean.
-In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Island Protected Area (397,447 km\textsuperscript{2}).
-It is still unclear what the effects of such a big MPA have been and what effects are likely to occur in the future.
-We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques evaluate the behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a Large-Scale Marine Protected Area.
-Our work provides three main findings: 1) we observe a crowding effect for the first months after implementation, 2) aggregate fishing effort remains relatively constant; and 3) vessels that fished inside the protected area redistribute to adjacent waters, including the high seas, 4) the redistribution of vessels results in a reduction of 2500 vessel-days into Kiribati, which represents a loss of ~30 million USD.
-This suggests that rights to fish in PNA waters might now be less valuable.
-Unfortunately, without detailed data on vessel catch, we cannot conclude whether vessels are better or worse off financially following the closure.
+In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Island Protected Area (PIPA, 397,447 km\textsuperscript{2}).
+We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the behavioral changes and spatial redistribution of tuna purse seiners due to the implementation of a PIPA.
+Our work provides three main findings: 1) we observe a crowding effect for the first months after implementation, 2) vessels fish with similar intensity after the implementation, 3) vessels that fished inside the protected area redistribute to adjacent waters, including the high seas, and 4) the redistribution of vessels results in a reduction of ~2500 vessel-days in Kiribati, which represents a loss of ~30 million USD.
 We use our results to inform predictions of the impacts of a proposed LSMPA in Palau (a PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
-Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have large ecological and economic implications for marine conservation and fisheries management in developing countries.
 As countries continue to implement LSMPAs as a way to reach ocean protection targets, managers should consider how fishing effort will change in space and time to ensure that fishing effort is not just displaced elsewhere.
@@
 \dropcap{H}umans are increasingly utilizing the oceans.
-Conservation and development targets are likely to cause activities such as off-shore aquaculture, conservation, deep-sea mining and and fisheries to compete for space.
-As we move forward in the blue economy, we must understand the potential effects of displacing one activity over the other.
-For example, global international goals aim to protect 10\% of the ocean environment by 2020.
+Multiple ocean uses such as off-shore aquaculture, conservation, energy harvesting, deep-sea mining, and fisheries are likely to compete for space.
+As we move forward with blue growth, we must understand the potential effects of activities displacing each other and etablish causal links between past management interventions and their outcomes \citep{burgess_2018}.
+
+Global international goals aim to protect 10\% of the ocean environment by 2020.
 In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which ocurr in the world's largest fishing grounds for tuna.
@@
 One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure \citep{smith_2003}.
+
+LSMPAs were initially assumed to have little social implications due to their general remoteness.
+However, there have been calls to incorporate the human dimensions into LSMPA management and evaluation \citep{agardy_2011,gray_2017}.
+Most research incorporating these dimensions has focused on governance and enforcement of LSMPAs \cite{alger_2017,christie_2017}, but they are yet to be the focus of economic analyses \citep{gray_2017}.
+For example, the anticipation of LSMPAs may lead to preemptive overfishing, which will likely erodes or delay the expected benefits of an intervention \cite{mcdermott_2018}.
 
@@
 The revenue from access fees represents up to 50\% of government revenue from some of this countries.
-
-LSMPAs were initially assumed to have little social implications due to their general remoteness.
-However, there have been calls to incorporate the human dimensions into LSMPA management and evaluation \citep{agardy_2011,gray_2017}.
-Most research incorporating these dimensions has focused on governance and enforcement of LSMPAs \cite{alger_2017,christie_2017}, but they are yet to be the focus of economic analyses \citep{gray_2017}.
-For example, the anticipation of PIPA lead to preemptive overfishing, which will likely erod or delay the expected benefits of the intervention \cite{mcdermott_2018}.
-However, a reduction in fishing area without proper adjustments to the total vessel-days permited every year is likely to increase fishing intensity in the remaining open waters.
 While no studies have assessed the immplications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020.
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-
-\input{tab/sp_corr}
 
@@
 We term this last group as ``others''.
-We find that the treated vessels spent 3,600 less days in PNA waters when comparing 2016 and 2017, while control and other vessels increased their PNA fishing by 411 and 1687 for the same period, respectively (Figs.
+We find that the treated vessels spent 2,310 less days in PNA waters when comparing 2015 and 2016, while control and other vessels increased their activities in PNA waters by 5,489 and 4,447 days for the same period, respectively (Figs.
 \ref{fig:all_PS_VDS_year}A and \ref{fig:included_PS_VDS_year_DiD}).
-Furthermore, in 2017 treated vessels exhibit the lowest allocation of hours to PNA waters at just 10,026 vessel-days.
-This is lower than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
-The 3,600 vessel-day reduction by treated between 2016 and 2017 vessels corresponds to \$43.2 million USD at an average vessel-day price of \$12,000 USD.
-The 2,526 vessel-day reduction would then represent forgone profits in the order of 30.3 million USD.
-%We need to come up with an identification strategy for this, I believe.
-I simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort (current DiD estimate of these data suggest a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects).
+The 2,310 vessel-day reduction by treated vessels between 2015 and 2017 corresponds to \$27.7 million USD at an average price of \$12,000 USD per vessel-day.
+Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
+\ref{fig:all_PS_VDS_cty_year}).
+Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allcoation to PNA waters at just 10,026 vessel-days.
+This is 2,526 vessel-days lower (~\$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
+% Do you think we need to come up with an identification strategy for this?.
+A simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort (current DiD estimate of these data suggests a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects).
 
-Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
-\ref{fig:all_PS_VDS_year}B).
-
-From the government side, we combine annual license revenue and EEZ-specific catch statistics compiled from the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}).
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_year.pdf}
-	\caption{\label{fig:all_PS_VDS_year}A)Observed vessel-days for all countries by treated, control, and excluded vessels.}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[ht]
 \centering
@@
 
-\subsection{Potential Revenue Loss Palau}
+We compliment our analysis of change in vessel-days by looking at country-level data.
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig.
+\ref{fig:revenues}).
+We find that by 2016, Kiribati's revenue decreased from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a change in 30.5 million USD.
+We use a local polynomial regression fit to obtain a trend line for the total (\emph{i.e.} summing across countries) revenues between 2008 and 2015, and extrapolate the trend to obtain an expected value for 2016.
+Our model suggests that revenue should be in the order of \$463.5 million USD, but we observe only \$423.5 million, suggesting that potential losses to the entire PNA are in the order of \$40 million USD.
+
+Catches for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
+\ref{fig:catches}).
+Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
+Similar decreases were observed for The Federal States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
+In contrast, Tokelau (due south of Kiribati) showed a 22.3\% increase in catches over the same period.
+
+\begin{figure}[ht]
+\centering
+	\includegraphics{img/revenues.pdf}
+	\caption{\label{fig:revenues}Financial indicators for PNA countries.
+A) Revenue from fishing licenses fees, B) Total annual revenues for all 9 PNA countries with dashed line showing the local polynomial regression fit to the 2008 - 2015 data and the red dot representing the prediction from this regression.
+Vertical dashed line in both plots denotes implementation of PIPA.}
+\end{figure}
+
+\subsection{Potential Revenue Loss for Palau}
 
@@
 
-\begin{figure}
-\centering
-	\includegraphics{img/financial_indicators.pdf}
-	\caption{\label{fig:financial_indicators}Financial indicators for PNA countries.
-A) Revenue from fishing licenses fees, B) Catches in each countrie's EEZ.
-Vertical dashed line denotes implementation of PIPA.}
-\end{figure}
+\section{Discussion}
+
+Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
+These results show that the implementation of PIPA had little effect on the total fishing effort exerted by purse seiners.
+However, regions adjacent to PIPA show an increase in the relative amount of fishing effort, suggesting that effort is simply displaced to nearby areas.
+This does not imply that there is more fishing effort exerted by treated vessels, but rather that each region receives a greater portion of the post-PIPA fishing effort of these same vessels, which is lower than pre-PIPA levels.
+Additionally, we show that post-PIPA there is a concentration of effort leading to crowding.
+In this section, we discuss the implications of vessel-level reductions in fishing effort and the increase in relative allocation of the remaining effort through space.
+We also provide plausible explanations as to why purse seiners seem to be more reactive to the spatial closure.
+
+Previous studies on protected areas around Pacific islands suggest that vessels move to distant places, which might be translated as increased costs \citep{stevenson_2013}.
+Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges of spatial closures, yielding greater catches over time \citep{murawski_2005}.
+But these vessel tracks do not cover the pre-reserve period, making it difficult to identify the contribution of spatial closures to the observed spatial distribution of fishing vessels.
+Recent work by \cite{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space.
+Our data, which is assembled in a similar way, allows us to make similar inferences about the unobserved change in aggregate fishing effort and its spatial redistribution.
+
+The role of the institutions at play is evident.
+Vessels that fished inside PIPA before the implementation were likely fishing in Kiribati waters under a VDS license.
+Upon implementation, some vessels redistribute to other areas of the Kiribati EEZ and the adjacent high seas for the year immediately after the closure.
+As stated before, it is reasonable for a vessel holding a license to fish in Kiribati waters to simply reallocate their effort to other parts of that EEZ.
+However, the shift to the high seas may not follow the same logic.
+Instead, it is possible that vessels that redistribute to the high seas were operating in Kiribati illegally, and decide to reallocate in the high seas to continue fishing without a license.
+Or they are now not willing to pay Kiribati to fish in the remaining open areas.
+
+A major shortcoming of our analysis is that we do not observe catches or revenues, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
+Therefore, it is difficult to know whether the small change in fishing hours represents a positive or negative impact.
+An additional factor that we are yet to test is the change in non-fishing hours spent at sea.
+It is plausible that fishing hours remain constant, but vessels have to increase search time.
+Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch.
+Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours.
+However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.
+
+Our work suggests that the implementation of LSMPAs has little impact on total fishing effort.
+We also show that fishing effort is redistributed to areas close by, and that this leads to a potentially negative crowding effect.
+A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
+Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere, leading to overfishing in adjacent waters.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness.
+
+\section{Conclusions}
+
+\section{References}
+
+\bibliography{references}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \clearpage
-\begin{figure}
-\centering
-\includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
-\end{figure}
+
+\onecolumn
+
+\FloatBarrier
+
+\section{Appendix}\label{appendix}
+
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
+\section{Supplementary tables and figures}
+
+\clearpage
+
+\input{tab/sp_corr}
+
 \clearpage
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics{img/PNA_map.png}
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
+Countries that belong to the PNA are shown in blue, while empty polygons indicates all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{img/all_panels.pdf}
+\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+	\includegraphics{img/all_PS_VDS_year.pdf}
+	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all countries by treated, control, and excluded vessels.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+	\includegraphics{img/all_PS_VDS_cty_year.pdf}
+	\caption{\label{fig:all_PS_VDS_cty_year}Observed vessel days by country and year}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+	\includegraphics{img/hist_kir_fishing.pdf}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+	\includegraphics{img/catches.pdf}
+	\caption{\label{fig:catches}Financial indicators for PNA countries.
+A) Annual catches by EEZ and, B) Annual value of catches by EEZ.
+Vertical dashed line in both plots denotes implementation of PIPA.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{img/other_specifications.pdf}
+\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
+for our variables of interest using different model specifications. Table \ref{tab:main_DID}
+reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{img/fishing_raster.png}
+\caption{\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels.
+Color corresponds to \% of total fishing effort in each panel.
+Red polygons show LSMPAs in the region.}
+\end{figure}
+
+\clearpage
+
+\section{Palau National Marine Sanctuary}\label{PNMS}
+
+\begin{figure}
+	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
+	\caption{Map of the Four Protected Areas}
+	\label{fig:maps}
+\end{figure}
+
+\clearpage
+
+\section{Alternative Controls}
+\subsection{Excluding all Chinese vessels}
+
+\input{tab/DID_without_CHN.tex}
+
+\clearpage
+\subsection{Excluding all PNA vessels}
+
+\input{tab/DID_without_PNA.tex}
+
+\clearpage
+
+\subsection{Excluding all USA and TWN vessels}
+
+\input{tab/DID_without_USA_TWN}
+
+\clearpage
+
+\section{Additional methods}
+
+This section is divided into two main parts.
+First, we provide a general description of AIS data and the process of identification of vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe the subset of data used in our analysis.
+We also point out possible shortcomings in the data, or factors that must be considered in the analysis.
+We then move on to explain our empirical strategy for the identification of behavioral changes and the redistribution of fishing effort.
+
+\subsection{Data}
+
+Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
+These broadcast messages can be received by satellites and land-based antennas.
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer what type of fishing is taking place and where it is taking place, thus allowing the estimation of near real-time fishing events globally \citep{kroodsma_2018}.
+
+The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
+The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
+This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
+The addition of new satellites affects all vessels in the same way.
+
+% All numbers in the following paragraph need to be updated
+Our analysis focuses on tune purse seine vessels, the most important fishery for PNA countries.
+We identify a total of 186 purse seiners that fished in PNA waters at least once before 2015.
+Vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses, leaving us with 125 vessels.
+We identify 90 vessels that have fished inside PIPA at least once since 2012; 72 did so before the announcement of the closure (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}).
+From these, we only observe before and after data for 64 tuna purse seiners.
+On the other hand, 45 vessels never fished inside PIPA during the 2012 - 2015 period, but we only observe befor and after data for 28 of these.
+
+Therefore, our treatment group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
+Vessels in the control group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
+Together, these vessels represent more than 20 million georeferenced positions for which we know activity (fishing or not fishing).
+
+We include three additional control groups as a robustness check.
+The first group contains only vessels that belong to PNA countries (n = 7).
+The second group excludes all Chinese vessels (n = 12).
+Our third control is made up of Japanese purse seiners that fish in the Pacific but have never fished inside PIPA (n = 27).
+Our main definition of treatment and control groups leaves us with 64 treated and 28 control vessels, which have just over 22 million observations with about 22\% of these observations identified as fishing events by the neural network classification.
+
+\clearpage
+
+\input{tab/baci_n_s}
+
+\clearpage
+
+\subsection{Analyses}
+
+\subsubsection{crowding effect}
 
 If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve.
-The implementation would lead to an increase in these measures, which, 
-if vessels avoid crowding, should then come back down. We therefore expect to
-have three inflection points: 1) in the transition between no trend and initial crowding due to MPA
-implementation, 2) When the crowding has reached its maximum and starts to decrease,
-and 3) when the decrease levels off, pressumably to pre-MPA levels.
-For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
-centering our time series of crowding indices on the day of implementation. Our
-explanatory variable is therefore the number of months before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 
-has a value of -1, and Feb of 2015 would receive a value of 1.
+The implementation would lead to an increase in these measures, which,  if vessels avoid crowding, should then come back down.
+We therefore expect to have three inflection points: 1) in the transition between no trend and initial crowding due to MPA implementation, 2) When the crowding has reached its maximum and starts to decrease, and 3) when the decrease levels off, pressumably to pre-MPA levels.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1, and Feb of 2015 would receive a value of 1.
 
-The pattern observed here could just be an artifact
-of satellite detections increasing though time. Therefore we also
-calculate a spatial correlation of presence/absence and observe similar
-patterns (Fig. \ref{fig:sp_corr}B). Spatial overlap increases
-in 2015 as vessels from PIPA are excluded, but then starts to decline.
-Our 4th degree polynomial shows the expected patterh of a relative
-constant trend before implementation which is followed by rapid increased
-and subsequent decrease.
+\begin{figure*}[h]
+\begin{align*}
+y_t = \alpha + \beta_1 month_t + \beta_2 month_t^2 + \beta_3 month_t^3 + \beta_4 month_t ^4 + \epsilon_t
+\end{align*}
+\end{figure*}
 
-Recent advances in satellite tracking technologies and near real-time
-identification of fishing activity provide us with an opportunity to ask: how do fishers respond to the implementation of an LSMPA?
-Does effort increase or decrease and where does it go?
-We use identification of fishing activity via Automatic Identification Systems (AIS) and causal inference techniques to describe
-the behavioral changes and spatial redistribution of the industrial tuna
-purse seine fleet due to the implementation of the Phoenix Islands Protected Area.
-We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are within the Parties to the Nauru Agreement (PNA) region, which is a group of (originally eight and now) nine Pacific Islands countries that collectively manage their valuable tuna stocks.
+\subsubsection{Behavioral changes}
 
-Our work is novel in the sense that it provides empirical evidence of
-the effect of Large Scale Marine Protected Areas on fishing behavior and
-distribution and can help guide future interventions. Understanding how
-effort is displaced from LSMPAs might provide insights into how distant water fishing fleets would react to a high seas closure.
+We then focus on identifying the response of vessels to the PIPA closure.
+We use daily fishing and non-fishing hours, daily proportion of fishing vs.
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port(km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
+We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
+Our main specification is the following:
 
-The existing empirical literature focuses on small MPAs and has been criticized for confounding correlation with causation \citep{ferraro2018causal}.
+\begin{figure*}[h]
+\begin{align*}
+log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
+\label{eqn:did}
+\end{align*}
+\end{figure*}
 
-The paper is organized as follows: Section \ref{background} provides more
-information on Large Scale Marine Protected Areas and some background on
-empirical studies of effort redistribution. An overview of the Nauru
-Agreement and associated countries, a description of the fleet that
-operates in the region, and a brief history of PIPA and PNMS is also included.
-Section \ref{methods} describes our data and identification strategy.
-Section \ref{results} presents our results, and Section \ref{discussion}
-discusses our
-results.
+Where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
+A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
+$Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group.
+$\alpha$ is the standard intercept term, $beta_1$ captures the temporal trend, $beta_2$ captures the initial difference between treated and control groups, and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
+Finally, $phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
+We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
 
-\section{Background}\label{background}
+We discretize spatial units by creating a polygon for PIPA and distinct spatial units for each geographically separate EEZ of each country.
+Some vessels might shift from EEZs into the high seas, but we are interested in knowing \emph{where} in the high seas, so we incorporate additional regions by using a 5-degree buffer of the high seas.
+The rest of the high seas are merged into a single spatial unit.
+For example, if we were to do this only for Kiribati, we would have 8 spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas  around each of the EEZ regions.
+around each EEZ, and the rest of the high seas.
+We clipped any overlapping high seas buffers to avoid duplication.
+
+All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
+All analyses were performed in R version 3.5.1 \citep{rcore_2018}.
+Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
+
+\clearpage
+
+\section{Old Text}
 
@@
 \subsection{Nauru agreement and the Phoenix Islands Protected Area}
-\label{nauru-agreement-and-the-phoenix-island-protected-area}
 
@@
 
-\clearpage
+\subsection{Palau}
 
-\section{Methods}\label{methods}
-
-This section is divided into two main parts. First, we provide a general
-description of AIS data and the process of identification of
-vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}}
-Alongside, we describe
-the subset of data used in our analysis. We also point
-out possible shortcomings in the data, or factors that must be
-considered in the analysis. We then move on to explain our
-empirical strategy for the identification of behavioral changes and
-the redistribution of fishing effort.
-
-\subsection{Data}\label{data}
-
-Automatic Identification Systems (AIS) are on-board devices that provide
-at-sea safety and prevent ship collisions by broadcasting vessel
-position, course, and activity to surrounding vessels. These broadcast
-messages can be received by satellites and land-based antennas. GFW then uses 
-machine learning techniques (convolutional neural networks) on the broadcast messages
-to infer what type of fishing is taking place and where it is taking place, thus
-allowing the estimation of near real-time fishing events globally \citep{kroodsma_2018}.
-
-The amount of data gathered by GFW is dependent on the number of antennas and
-satellites that can receive signals. The total satellite count increased from 3 to 6 on 
-June 1\textsuperscript{st}
-2014 , and then from 6 to 10 on January
-1\textsuperscript{st} 2016. This causes an increase in the number of
-\emph{received} AIS messages (\emph{i.e.} points), and therefore an
-apparent increase in the number of vessels.
-The addition of new satellites affects all vessels in the same way.
-
-Our analysis focuses on tune purse seine vessels, the most important fishery
-for PNA
-countries.\footnote{We perform some of the same analyses for longliners and include them in the Appendix}
-We identify a total of 186 purse seiners that fished in PNA waters at
-least once before 2015. Vessels that entered the fishery after 2015 were not
-exposed to the policy intervention in the pre-treatment period and are
-therefore excluded from our analyses, leaving us with 125 vessels.
-We identify 90 vessels that have fished inside PIPA
-at least once since 2012; 72 did so before the announcement
-of the closure (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}).
-From these, we only observe before and after data for 64 tuna purse seiners.
-On the other hand, 45 vessels never fished inside PIPA during the 2012 - 2015 period, 
-but we only observe befora and after data for 28 of these.
-
-Therefore, our treatment group contains all purse seiners (n = 64) that
-fished within PIPA at least once before the announcement, and that
-continued to fish elsewhere after the January 2015 implementation.
-Vessels in the control group meet the following two conditions: i)
-never fished within PIPA waters from 2012-2015, and ii) vessels have fished in
-surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
-closure (n = 28). Together, these vessels represent more than 20 million georeferenced positions
-for which we know activity (fishing or not fishing).
-
-We include three additional control groups as a
-robustness check. The first group contains only vessels that belong to PNA countries (n
-= 7). The second group excludes all Chinese vessels (n = 12). Our third control
-is made up of Japanese purse seiners that fish in the Pacific but have
-never fished inside PIPA (n = 27). Our main definition of treatment and control
-groups leaves us with 64 treated and 28 control vessels, which have just over 22 million
-observations with about 22\% of these observations identified as fishing events by the neural network classification.
-
-\input{tab/baci_n_s}
-
-\clearpage
-
-\subsection{Analyses}\label{analyses}
-
-Our first analysis focuses on identifying the response of 
-vessels to the PIPA closure. We use daily fishing and non-fishing hours,
-daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), 
-distance from shore (km) and distance from home port(km) for fishing and non-fishing events,
-and proportion of total fishing hours allocated to Kiribati waters and PNA waters
-as our main outcomes of interest.
-We compare these outcomes before and after the implementation
-of PIPA using a Difference-in-Differences approach. Our main
-specification is the following:
-
-\begin{figure*}[h]
-\begin{align*}
-log(y)_{i,t} = \alpha + \beta_1 Post_t + \beta_2 Treat_i + \beta_3 Post_t \times Treat_i + \phi_t + \gamma_i + \epsilon_{i,t}
-\label{eqn:did}
-\end{align*}
-\end{figure*}
-
-where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
-A dummy variable $Post_t$ takes the value of 0 for all
-dates prior to PIPA implementation and a value of 1 for all dates
-following PIPA implementation. $Treat_i$ is a dummy
-variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control
-($Treat_i = 0$) group. $\alpha$ is
-the standard intercept term, $beta_1$ captures the temporal trend,
-$beta_2$ captures the initial difference between treated and control groups,
-and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing
-the treatment effect. Finally, $phi_t$ and $\gamma_i$ represent
-month and flag dummies that account for seasonality or
-country-level management interventions. We test for other more complex specifications
-that interact a quarterly dummy or year-month dummies with the treatment group
-and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
-
-Our second part of the analysis focuses on the redistribution of fishing
-effort, where institutions may play an important role. As stated
-before, LSMPAs often span the entirety of an EEZ. In the case of purse
-seining in the PNA, vessels purchase access to the fishery at the
-beginning of the season. If a vessel decides to fish within the PNA,
-they've already made the decision to pay for access, expecting higher
-returns from fishing there than in the high seas. In the particular case
-of PIPA, one would expect that a vessel previously holding a permit to fish in
-Kiribati waters would 
-most likely continue to purchase access to PNA waters (either in Kiribati's
-remaining open areas or a nearby EEZ). Alternatively, if a vessel fishes illegally
-in Kiribati waters before the implementation, one would expect them to
-reallocate to other regions with equal or less enforcement. In this
-case, they might then choose to move to other Kiribati waters, waters
-of countries that have similar enforcement levels, or to the high seas.
-
-We discretize spatial units by creating a polygon for
-PIPA and distinct
-spatial units for each geographically separate EEZ of each country. Some vessels might shift
-from EEZs into the high seas, but we are interested in knowing
-\emph{where} in the high seas, so we incorporate additional regions by
-using a 1-degree buffer of the high seas\footnote{Currently running the 5-degree version too}
-The rest of the high seas are merged into a single spatial unit. For
-example, if we were to do this only for Kiribati, we would have 8
-spatial units: PIPA, three EEZ units, three 1-degree buffers of high seas  around each of the EEZ regions.
-around each EEZ, and the rest of the high seas. We clipped any overlapping
-high seas buffers to avoid duplication.
-
-We then take these spatial polygons and rasterize them to a 1-degree grid
-(see Figure \ref{fig:raster_rgn} in the Appendix), which we then use to rasterize points
-of fishing activity. For each cell, we calculate the total monthly
-fishing hours by treated and control vessels (Fig. \ref{fig:fishing_raster}).
-Since we are interested in the redistribution
-of fishing effort, we use this gridded data to calculate the proportion
-of fishing hours that each region receives each month relative to the
-total fishing hours observed across all regions and all cells in that
-month.
-
-We use this measure to evaluate the change in effort allocation by
-regressing it on the interaction between a year dummy and a dummy for
-regions:
-
-\begin{figure*}[h]
-\begin{align*}
-y_{i,t} = \alpha + \beta_1Year_t + \beta_{2,i}Region_i + \beta_{3,i}Year_t \times Region_i+ \epsilon_{i,t}
-\end{align*}
-\end{figure*}
-
-Our variable of interest, $y_{i,t}$ represents the proportion of
-fishing hours that region $i$ receives at time $t$. Years are
-modeled as factors ($Year_t$), using 2012 as the reference level.
-$Region$ is a dummy variable for regions defined above. Our vector of parameters of
-of interest is $\beta_{3,i}$, which captures the yearly by-country
-change in proportional allocation of fishing effort relative to 2012.
-
-Finally, we inspect the crowding effects that may arise due to the net reduction
-in fishing area. We use the rasterized fishing effort and calculate two
-potential indices of crowding. For the first one, we count the number of cells
-that had fishing activity from treated and control vessels over a given month. For the second one,
-we calculate the correlation of presence/absence of fishing events between both groups
-over one month. If the implementation of the reserve induces a crowding effect,
-we would expect to observe no trend before the implementation of the reserve.
-The implementation would lead to an increase in these measures, which, 
-if vessels avoid crowding, should then come back down. We therefore expect to
-have three inflection points: 1) in the transition between no trend and initial crowding due to MPA
-implementation, 2) When the crowding has reached its maximum and starts to decrease,
-and 3) when the decrease levels off, pressumably to pre-MPA levels.
-For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by
-centering our time series of crowding indices on the day of implementation. Our
-explanatory variable is therefore the number of months before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 
-has a value of -1, and Feb of 2015 would receive a value of 1.
-
-\begin{figure*}[h]
-\begin{align*}
-y_t = \alpha + \beta_1 month_t + \beta_2 month_t^2 + \beta_3 month_t^3 + \beta_4 month_t ^4 + \epsilon_t
-\end{align*}
-\end{figure*}
-
-All regression coefficients were estimated via ordinary least squares,
-and heteroskedasticity-robust standard errors were calculated. All analyses
-were performed in R version 3.5.1 \citep{rcore_2018}. Raw data and code
-used in this work are available on
-\href{https://github.com/jcvdav/MPA_displacement}{github}.
-
-\section{Results2}
-
-Regression coefficients for our DiD analysis are shown in Table
-\ref{tab:main_DID}. Our DiD analysis shows that PIPA closure
-had no effect on the number of fishing hours, but that it caused
-non-fishing at-sea hours to increase by 1\%, This coefficient is
-only marginally significant. The proportion of
-fishing to non-fishing hours shows a positive change, but it is not
-significant. However, treated vessels travel on average 19\% less
-than control vessels, and opperate closer to shore and port.
-Furthermore, PIPA implementation caused fishing events of treated
-vessel to occur 23\% and 4\% closer to port and to shore, respectively.
-Other specificationf that exclude fixed effects produce similar estimates (Fig. \ref{fig:other_specifications})
-Since vessels don't seem to be fishing a lot less, an obvious question arises: where are they
-fishing now?
-
-Figure \ref{fig:fishing_raster} provides a spatial representation of
-these changes. Note that the 2013 effort distribution is roughly similar
-across vessels. Then, in 2014, there is a sharp increase in fishing hours
-by treated vessels inside PIPA. In 2015, treated vessels
-then allocate more effort to the easternmost Kiribati EEZ and the high seas.
-In 2016, the spatial distribution of
-fishing effort is again similar across groups. It is evident that the
-increase in relative fishing effort is greater for regions closer to
-PIPA.
-
-Along a similar line, Figure \ref{fig:redist_trend} shows a detailed
-temporal evolution of the relative allocation of fishing
-effort.  It shows the change in fishing effort inside PIPA, including the
-preemptive fishing and immediate reduction previously reported
-\citep{mcdermott_2018}. Recall that to evaluate the redistribution of fishing effort
-we only track fishing vessels that belong to the treated group.
-Kiribati waters show an increase in fishing effort for 2015;
-the same pattern is observed for their respective High Seas buffers,
-and the general High Seas. This suggests fishing effort inside PIPA has moved to the
-high seas around Kiribati instead of paying to fish within alternative Kiribati EEZ waters.
-
-We then move on to our regression results, presented as a figure showing
-the year-region interaction coefficient estimates for each region as a
-stream of changes through time (Fig. \ref{fig:mean_change} and Table
-\ref{tab:mean_change}). As noted before, the marginal change in the
-relative allocation of fishing effort relative to 2012 increases in 2014
-for PIPA, followed by an abrupt reduction in 2015 and afterwards. This 
-reduction confirms that effort within PIPA has been virtually eliminated.
-Most coefficients are not statistically significant, but
-follow the same trends previously discussed, with a tendency for regions
-closer to PIPA to show an increase in the relative allocation of fishing
-effort in the post-implementation period. The largest increase is
-observed for the Kiribati EEZ 2 (Kiribati's easternmost EEZ), where the
-redistribution of treated vessels caused a 10\% increase in the \emph{relative} allocation of
-fishing effort within Kiribati waters. The high seas around Kiribati's EEZ exhibit
-similar increases the year of implementation or the year after. Overall, the high seas
-receive an incresse in the order of 5\% for 2015.This displacement is likely
-causing a crowding effect after PIPA-fishing vessels redistribute to
-other areas.
-
-We use the rasterized effort to evaluate if the PIPA closure increased
-crowding outside the LSMPA. We count the number of raster cells that
-had both treated and control vessels each month (Fig.
-\ref{fig:sp_corr}A).
-
-\clearpage
-
-\input{tab/mean_change}
-
-\clearpage
-
-\clearpage
-
-\section{Discussion}\label{discussion}
-
-Our findings provide insights into the effect that LSMPAs
-can have on vessel behavior and the redistribution of fishing effort.
-These results show that the implementation of PIPA had
-little effect on the total fishing effort exerted by purse seiners. However, regions
-adjacent to PIPA show an increase in the relative amount of fishing
-effort, suggesting that effort is simply displaced to nearby areas.
-This does not imply that there is more fishing effort exerted by treated
-vessels, but rather that each region receives a greater portion of the
-post-PIPA fishing effort of these same vessels, which is lower than
-pre-PIPA levels. Additionally, we show that post-PIPA there is a
-concentration of effort leading to crowding. In this section, we discuss
-the implications of vessel-level reductions in fishing effort and the
-increase in relative allocation of the remaining effort through space.
-We also provide plausible explanations as to why purse seiners seem to
-be more reactive to the spatial closure.
-
-Previous studies on protected areas around Pacific islands suggest that vessels move to
-distant places, which might be translated as increased costs
-\citep{stevenson_2013}. Others have used similar satellite-tracking systems to
-show that fishing effort accumulates near the edges of spatial closures,
-yielding greater catches over time \citep{murawski_2005}. But these vessel tracks
-do not cover the pre-reserve period, making it difficult to identify the
-contribution of spatial closures to the observed spatial distribution of
-fishing vessels. Recent work by \cite{elahi_2018} identified that total
-fishing effort in a focal region where a short-term MPA was implemented
-showed little change, likely indicating that fishers redistributed
-fishing effort to compensate for the reduction in available space. Our
-data, which is assembled in a similar way, allows us to make similar
-inferences about the unobserved change in aggregate fishing effort and
-its spatial redistribution.
-
-The role of the institutions at play is evident. Vessels that fished
-inside PIPA before the implementation were likely fishing in
-Kiribati waters under a VDS license. Upon implementation,
-some vessels redistribute to other areas of the Kiribati EEZ and the adjacent
-high seas for the year immediately after the closure. As stated before,
-it is reasonable for a vessel holding a license to fish in Kiribati
-waters to simply reallocate their effort to other parts of that EEZ.
-However, the shift to the high seas may not follow the same logic.
-Instead, it is possible that vessels that redistribute to the high seas
-were operating in Kiribati illegally, and decide to reallocate in the
-high seas to continue fishing without a license. Or they are now not willing to pay Kiribati to fish in the remaining open areas.
-
-A major shortcoming of our analysis is that we do not observe catches or
-revenues, which ultimately are the factors that guide the decision
-making process of profit-maximizing agents. Therefore, it is difficult
-to know whether the small change in fishing hours represents a positive or
-negative impact. An additional factor that we are yet to test is the
-change in non-fishing hours spent at sea. It is plausible that fishing
-hours remain constant, but vessels have to increase search time. Upon
-being relocated, fishers may not identify the best fishing grounds as
-easily as before, and therefore invest a greater proportion of their
-time searching for their catch. Further analysis of temporal trends in
-non-fishing hours, as well as distance traveled should provide us with
-insights as to why fishers reduced fishing hours. However, the
-widespread footprint of the treated fleet may suggest that they are well
-acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's
-unlikely that they would need to invest much time to identify new fishing grounds.
-
-Our work suggests that the implementation of LSMPAs has little impact on
-total fishing effort. We also show that fishing effort is
-redistributed to areas close by, and that this leads to a potentially
-negative crowding effect. A growing body of literature suggests that
-closing the high seas to all fishing could increase fishery yields and
-profitability of fisheries, with negligible costs to food security
-\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Such
-management interventions should consider how fishing effort will change
-in space and through time, and the ecological implications of this
-redistribution to ensure that fishing effort is not just displaced
-elsewhere, leading to overfishing in adjacent waters. While LSMPAs can
-provide a wide range of benefits, their implementation must be
-accompained with traditional fisheries management to maximize
-effectiveness.
-
-\section{Conclusion}\label{conclude}
-
-\clearpage
-
-\section{References}\label{references}
-
-\bibliography{references}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\FloatBarrier
-
-\section{Appendix}\label{appendix}
-
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\begin{figure}
-\centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive
-Economic Zones (EEZs) of the region of interest. Countries that belong
-to the PNA are shown in blue, while empty polygons indicates all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon
-delineates PIPA.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/other_specifications.pdf}
-\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
-for our variables of interest using different model specifications. Table \ref{tab:main_DID}
-reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/fishing_raster.png}
-\caption{\label{fig:fishing_raster}Yearly
-spatial distribution of fishing effort by treated and control vessels.
-Color corresponds to \% of total fishing effort in each panel.
-Red polygons show LSMPAs in the region.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/redist_trend.pdf}
-\caption{\label{fig:redist_trend}Monthly
-relative allocation of fishing effort by PIPA-fishing vessels before and
-after PIPA by region. Colors indicate the pre- and post- periods. Solid line
-across points shows local mean with a region-specific loess smoother.
-Vertical dashed lines indicates dates when satellites were added, solid vertical
-line indicates PIPA closure. Note that inflection points of
-the loess smoother are not affected by the addition of satellites.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/mean_change.pdf}
-\caption{\label{fig:mean_change}Coefficient
-estimates for the redistribution regression. Each panel shows the
-region-specific coefficients, with 95\% condifence intervals
-as error bars. The horizontal dashed line represents 0 change
-relative to the 2012 region-specific levels.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/PS_VDS_KIR_by_year.pdf}
-	\caption{\label{fig:PS_VDS_KIR_by_year}Vessel days spent inside Kiribati waters by group of vessels.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
-\end{figure}
-
-\section{Palau National Marine Sanctuary}\label{PNMS}
-
-\begin{figure}[h]
-	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
-	\caption{Map of the Four Protected Areas}
-	\label{fig:maps}
-\end{figure}
+\subsubsection{Palau National Monument}
 
@@
 
-\subsection{Background on Commercial Fishing in Palau}\label{Palau_back}
+\subsubsection{Background on Commercial Fishing in Palau}
 
@@
 
-\clearpage
-
-\section{Alternative Controls}
-\subsection{Excluding all Chinese vessels}
-
-\input{tab/DID_without_CHN.tex}
-
-\clearpage
-\subsection{Excluding all PNA vessels}
-
-\input{tab/DID_without_PNA.tex}
-
-\clearpage
-\subsection{Excluding all USA and TWN vessels}
-
-\input{tab/DID_without_USA_TWN}
-
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
-%\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
-%and treatment. Control group excludes Chinese vessels.}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
-%\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
-%and treatment. Control group is japanese vessels.}
-%\end{figure}
-%
-%\hypertarget{year-month-did-interactions}{%
-%\subsubsection{Year-month DID
-%interactions}\label{year-month-did-interactions}}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
-%\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
-%year-month and treatment. Control group is all vessels.}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
-%\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
-%year-month and treatment. Control group is vessels from PNA.}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
-%\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
-%year-month and treatment. Control group excludes Chinese vessels.}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
-%\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
-%year-month and treatment. Control group is japanese vessels.}
-%\end{figure}
-%
-%\hypertarget{other-measures-of-change-in-behavior}{%
-%\subsection{Other measures of change in
-%behavior}\label{other-measures-of-change-in-behavior}}
-%
-%Global Fishing Watch data includes two variables of interest that are
-%readily available: distance from shore and distance from port. We use
-%these as variables of interest and perform the following regression:
-%
-%\[
-%y = \beta_1Year + \beta_2Treated + \beta_3Year \ Treated + \epsilon
-%\]
-%
-%Where \(y\) is our variable of interest, \(Year\) represent year
-%dummies, with 2012 as the reference level, and \(Treated\) indicates
-%wether a vessel belongs to the treated or control group.
-%
-%\clearpage
-%
-%\hypertarget{distance-from-shore}{%
-%\subsubsection{Distance from shore}\label{distance-from-shore}}
-%
-%\begin{table}[!htbp] \centering 
-%  \caption{\label{tab:dist_shore}Regression results for distance from shore. Numbers in parentheses are heteroskedastic-robust standard errors.} 
-%  \label{} 
-%\begin{tabular}{@{\extracolsep{5pt}}lc} 
-%\\[-1.8ex]\hline 
-%\hline \\[-1.8ex] 
-% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-%\cline{2-2} 
-%\\[-1.8ex] & distance\_from\_shore \\ 
-%\hline \\[-1.8ex] 
-% Constant & 233,057.900$^{***}$ \\ 
-%  & (1,558.294) \\ 
-%  & \\ 
-% year\_c2013 & $-$818.044 \\ 
-%  & (2,623.263) \\ 
-%  & \\ 
-% year\_c2014 & 14,220.260$^{***}$ \\ 
-%  & (1,701.637) \\ 
-%  & \\ 
-% year\_c2015 & 140,980.200$^{***}$ \\ 
-%  & (1,668.140) \\ 
-%  & \\ 
-% year\_c2016 & 32,557.750$^{***}$ \\ 
-%  & (1,584.182) \\ 
-%  & \\ 
-% year\_c2017 & 168,283.100$^{***}$ \\ 
-%  & (1,653.912) \\ 
-%  & \\ 
-% treated & $-$11,371.280$^{***}$ \\ 
-%  & (1,688.879) \\ 
-%  & \\ 
-% year\_c2013:treated & 62,899.900$^{***}$ \\ 
-%  & (3,274.205) \\ 
-%  & \\ 
-% year\_c2014:treated & $-$17,499.020$^{***}$ \\ 
-%  & (1,834.090) \\ 
-%  & \\ 
-% year\_c2015:treated & $-$34,356.840$^{***}$ \\ 
-%  & (1,821.587) \\ 
-%  & \\ 
-% year\_c2016:treated & 72,512.980$^{***}$ \\ 
-%  & (1,739.976) \\ 
-%  & \\ 
-% year\_c2017:treated & $-$62,350.120$^{***}$ \\ 
-%  & (1,805.322) \\ 
-%  & \\ 
-%\hline \\[-1.8ex] 
-%Observations & 4,937,666 \\ 
-%R$^{2}$ & 0.032 \\ 
-%Adjusted R$^{2}$ & 0.032 \\ 
-%Residual Std. Error & 297,128.600 (df = 4937654) \\ 
-%F Statistic & 14,649.360$^{***}$ (df = 11; 4937654) \\ 
-%\hline 
-%\hline \\[-1.8ex] 
-%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-%\end{tabular} 
-%\end{table}
-%
-%\clearpage
-%
-%\hypertarget{distance-from-ports}{%
-%\subsubsection{Distance from ports}\label{distance-from-ports}}
-%
-%\begin{table}[!htbp] \centering 
-%  \caption{\label{tab:dist_port}Regression results for distance from shore} 
-%  \label{} 
-%\begin{tabular}{@{\extracolsep{5pt}}lc} 
-%\\[-1.8ex]\hline 
-%\hline \\[-1.8ex] 
-% & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-%\cline{2-2} 
-%\\[-1.8ex] & distance\_from\_port \\ 
-%\hline \\[-1.8ex] 
-% Constant & 362.707$^{***}$ \\ 
-%  & (1.971) \\ 
-%  & \\ 
-% year\_c2013 & 9.082$^{***}$ \\ 
-%  & (3.198) \\ 
-%  & \\ 
-% year\_c2014 & 105.414$^{***}$ \\ 
-%  & (2.148) \\ 
-%  & \\ 
-% year\_c2015 & 357.746$^{***}$ \\ 
-%  & (2.113) \\ 
-%  & \\ 
-% year\_c2016 & 112.441$^{***}$ \\ 
-%  & (2.009) \\ 
-%  & \\ 
-% year\_c2017 & 356.506$^{***}$ \\ 
-%  & (2.099) \\ 
-%  & \\ 
-% treated & 149.653$^{***}$ \\ 
-%  & (2.249) \\ 
-%  & \\ 
-% year\_c2013:treated & 26.366$^{***}$ \\ 
-%  & (4.125) \\ 
-%  & \\ 
-% year\_c2014:treated & 50.808$^{***}$ \\ 
-%  & (2.453) \\ 
-%  & \\ 
-% year\_c2015:treated & $-$151.268$^{***}$ \\ 
-%  & (2.422) \\ 
-%  & \\ 
-% year\_c2016:treated & $-$49.445$^{***}$ \\ 
-%  & (2.311) \\ 
-%  & \\ 
-% year\_c2017:treated & $-$252.334$^{***}$ \\ 
-%  & (2.390) \\ 
-%  & \\ 
-%\hline \\[-1.8ex] 
-%Observations & 4,937,666 \\ 
-%R$^{2}$ & 0.047 \\ 
-%Adjusted R$^{2}$ & 0.047 \\ 
-%Residual Std. Error & 391.757 (df = 4937654) \\ 
-%F Statistic & 22,351.480$^{***}$ (df = 11; 4937654) \\ 
-%\hline 
-%\hline \\[-1.8ex] 
-%\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-%\end{tabular} 
-%\end{table}
-%
-\hypertarget{effort-redistribution}{%
-\subsection{Effort redistribution}\label{effort-redistribution}}
-
-\hypertarget{rasterized-regions}{%
-\subsubsection{Rasterized regions}\label{rasterized-regions}}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
-\caption{\label{fig:raster_rgn}Rasterized regions. Each color (number) indicates a distinct region.}
-\end{figure}
-%
-%\hypertarget{fishing-raster}{%
-%\subsubsection{Fishing raster}\label{fishing-raster}}
-%
-%\begin{figure}
-%\centering
-%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-32-1.pdf}
-%\caption{\label{fig:unnamed-chunk-32}\label{fig:fishing_raster_full}Yearly
-%rasters of fishing hours for each group.}
-%\end{figure}
-%
-%\clearpage
-
 \end{document}

### 2019-02-19 docs/tab/main_DID.tex
Added new figures and updated MS

@@
 \hline \\[-1.8ex] 
- Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 4.532$^{***}$ & 6.161$^{***}$ & 12.535$^{***}$ & 3.120$^{***}$ & 3.879$^{***}$ \\ 
-  & (0.033) & (0.010) & (0.008) & (0.044) & (0.023) & (0.021) & (0.197) & (0.151) \\ 
+ Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
+  & (0.038) & (0.007) & (0.009) & (0.045) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
   & & & & & & & & \\ 
- Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & $-$0.087$^{***}$ & 0.309$^{***}$ & 0.232$^{***}$ & 1.563$^{***}$ & 1.587$^{***}$ \\ 
-  & (0.024) & (0.007) & (0.006) & (0.032) & (0.015) & (0.015) & (0.135) & (0.107) \\ 
+ Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
+  & (0.026) & (0.008) & (0.007) & (0.036) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
   & & & & & & & & \\ 
- Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.291$^{***}$ & 0.163$^{***}$ & $-$0.013 & 0.395$^{***}$ & 0.210$^{*}$ \\ 
-  & (0.026) & (0.006) & (0.007) & (0.030) & (0.017) & (0.017) & (0.138) & (0.111) \\ 
+ Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
+  & (0.028) & (0.006) & (0.007) & (0.032) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.246$^{***}$ & $-$0.238$^{***}$ & $-$0.047$^{***}$ & $-$0.582$^{***}$ & $-$0.452$^{***}$ \\ 
-  & (0.028) & (0.008) & (0.007) & (0.037) & (0.018) & (0.018) & (0.158) & (0.125) \\ 
+ Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
+  & (0.030) & (0.009) & (0.007) & (0.040) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 28,067 & 82,242 & 28,067 & 80,319 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
-R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.012 & 0.157 & 0.272 & 0.194 & 0.276 \\ 
+Observations & 25,073 & 74,600 & 25,073 & 73,265 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
+R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
 \hline 

### 2019-02-19 docs/tab/sp_corr.tex
Updated manuscript and resized some figures
Added new figures and updated MS

--- 2019-01-23 docs/tab/sp_corr.tex
@@
 \hline \\[-1.8ex] 
- Constant & 76.695$^{***}$ (4.382) & 76.695$^{***}$ (4.382) \\ 
-  Months & 4.342$^{***}$ (0.419) & 4.342$^{***}$ (0.419) \\ 
-  Months $^2$ & $-$0.026$^{***}$ (0.007) & $-$0.026$^{***}$ (0.007) \\ 
-  Months $^3$ & $-$0.003$^{***}$ (0.0004) & $-$0.003$^{***}$ (0.0004) \\ 
+ Constant & 67.152$^{***}$ (5.727) & 0.357$^{***}$ (0.014) \\ 
+  Months & 4.592$^{***}$ (0.422) & 0.008$^{***}$ (0.001) \\ 
+  Months $^2$ & 0.062$^{*}$ (0.033) & 0.0001 (0.0001) \\ 
+  Months $^3$ & $-$0.004$^{***}$ (0.0005) & $-$0.00001$^{***}$ (0.00000) \\ 
+  Months $^4$ & $-$0.0001$^{***}$ (0.00003) & $-$0.00000$^{*}$ (0.00000) \\ 
  \hline \\[-1.8ex] 
@@
 Observations & 72 & 72 \\ 
-R$^{2}$ & 0.704 & 0.704 \\ 
+R$^{2}$ & 0.743 & 0.566 \\ 
 \hline 

### 2019-02-19 scripts/content/PS_VDS_PNA_by_year_eez.R

@@ -86,7 +86,8 @@ p1 <- ggplot(vessel_activity_year, aes(x = year, y = days / 1000, fill = group))
   guides(fill = guide_legend(title = "Group")) +
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8),
-        legend.text = element_text(size = 8))+
+        legend.text = element_text(size = 8),
+        legend.position = "top")+
   labs(x = "Year", y = "Vessel-days (Ths)")
 
 # Plot for yearly PS VDS by country
@@ -108,13 +109,13 @@ p12 <- cowplot::plot_grid(p1, p2, labels = "AUTO", ncol = 1)
 ggsave(p1,
        filename = here::here("docs", "img", "all_PS_VDS_year.pdf"),
        width = 3.4,
-       height = 2.1)
+       height = 2.6)
 
 #Save plot
-ggsave(p12,
+ggsave(p2,
        filename = here::here("docs", "img", "all_PS_VDS_cty_year.pdf"),
        width = 3.4,
-       height = 4.2)
+       height = 2.1)
 
 # Plot for yearly PS VDS by activity by included vessels
 p1.1 <- ggplot(vessel_activity_year_included, aes(x = year, y = days, fill = fishing)) +

### 2019-02-19 scripts/content/plot_financial_indicators.R

@@ -39,6 +39,49 @@ p1 <- financial_data %>%
         strip.background = element_blank(),
         legend.position = "none")
 
+## Annual revenues total PNA
+annual_revenues <- drop_na(financial_data) %>%
+  group_by(year) %>%
+  summarize(revenue = sum(revenue, na.rm = T)) %>%
+  ungroup()
+
+loess_revenue <- annual_revenues %>% 
+  filter(year < 2016) %>% 
+  loess(formula = revenue ~ year, data = ., surface = "direct")
+
+p2 <- annual_revenues %>% 
+  mutate(prediction = predict(loess_revenue, .),
+         predicted_point = ifelse(year == 2016, prediction, NA)) %>% 
+  ggplot(aes(x = year)) +
+  geom_point(aes(y = revenue),
+             shape = 21,
+             color = "black",
+             fill = "steelblue",
+             size = 4,
+             alpha = 0.8) + 
+  geom_line(aes(y = prediction),
+            linetype = "dashed",
+            size = 1) +
+  geom_point(aes(y = predicted_point),
+             shape = 21,
+             color = "black",
+             fill = "red",
+             size = 4,
+             alpha = 0.8) +
+  labs(x = "Year",
+       y = "Revenue from licenses\n(Million USD)") +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8),
+        strip.background = element_blank())
+
+# Put together
+p <- plot_grid(p1, p2, ncol = 1, labels = "AUTO")
+
+# Save plot
+ggsave(p, filename = here::here("docs", "img", "revenues.pdf"),
+       width = 3.4,
+       height = 5.2)
+
 # Plot for catches
 p2 <- ggplot(data = financial_data,
              mapping = aes(x = year, y = catches/1000, fill = country)) +
@@ -78,19 +121,16 @@ p3 <- ggplot(data = financial_data,
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8),
         strip.background = element_blank(),
-        legend.justification = c(0, 1),
-        legend.position = c(0, 1)) +
+        legend.position = "none") +
   guides(fill = guide_legend(title = "Country", ncol = 2))
 
 # Put together
-p <- plot_grid(p1, p2, ncol = 1, labels = "AUTO")
+p <- plot_grid(p2, p3, ncol = 1, labels = "AUTO")
 
 # Save plot
[…]

### 2019-02-25 docs/tab/sp_corr.tex
Updated MS and sent to John
Updated and added scripts for 2018 data

--- 2019-01-24 docs/tab/sp_corr.tex
@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding.
+  \caption{\label{tab:sp_corr}Coefficient estimates for a third-polinomial fit to the measures of crowding.
 The first column shows coefficients for the number of cells with treated and control vessels during the same month.
@@
 \hline \\[-1.8ex] 
- Constant & 65.538$^{***}$ (5.878) & 0.409$^{***}$ (0.016) \\ 
-  Months & 4.429$^{***}$ (0.402) & 0.010$^{***}$ (0.001) \\ 
-  Months $^2$ & 0.060$^{*}$ (0.033) & 0.00003 (0.0001) \\ 
-  Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
-  Months $^4$ & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
+ Constant & 67.894$^{***}$ (5.363) & 0.448$^{***}$ (0.014) \\ 
+  Months & 3.301$^{***}$ (0.317) & 0.009$^{***}$ (0.001) \\ 
+  Months $^2$ & 0.007 (0.023) & $-$0.0001$^{**}$ (0.00005) \\ 
+  Months $^3$ & $-$0.002$^{***}$ (0.0003) & $-$0.00001$^{***}$ (0.00000) \\ 
+  Months $^4$ & 0.00001 (0.00002) & 0.00000$^{**}$ (0.00000) \\ 
  \hline \\[-1.8ex] 
@@
 Flag FE & Yes & Yes \\ 
-Observations & 72 & 72 \\ 
-R$^{2}$ & 0.741 & 0.631 \\ 
+Observations & 83 & 84 \\ 
+R$^{2}$ & 0.681 & 0.683 \\ 
 \hline 

### 2019-02-25 scripts/collection/activity_by_vessel_year_eez_download.R

@@ -1,0 +1,38 @@
+##################################
+#   activity_by_vessel_year_eez  #
+##################################
+
+########################################################################
+# This script downloads activity_by_vessel_year_eez dataset from
+# Google BigQuery. I queried the database in GBQ to get the activity of
+# all vessels that ever fished inside PNA using the latest tables.
+########################################################################
+
+# Load the packages that I need
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+# Create a connection to Google BigQuery
+# For this to run, you require authentication and be part of ucsb-gfw
+BQc <- bigrquery::dbConnect(
+  drv = bigrquery::bigquery(),
+  project = "ucsb-gfw", # This is the project, to which you must belong
+  dataset = "mpa_displacement", # This is the dataset, where I keep all the tables
+  allowLargeResults = TRUE #We're downloading about 10 GB of data
+)
+
+# List all tables to test the connection
+DBI::dbListTables(BQc)
+
+
+# DOWNLOAD THE DATA
+# Create a tbl pointing to vessel tracks
+vessel_activity <- dplyr::tbl(BQc, "activity_by_vessel_year_eez") %>%
+  collect() # collect brings the information out of the database and into memory
+
+# Save it to disk
+saveRDS(vessel_activity,
+        file = here::here("raw_data", "activity_by_vessel_year_eez.rds"))

### 2019-02-25 scripts/collection/vessel_tracks_2012_2018_download.R

@@ -1,0 +1,101 @@
+#########################################
+#   vessel_tracks_2012_2018_download    #
+#########################################
+
+########################################################################
+# This script downloads the vessel_tracks_2012_2018 dataset from Google
+# BigQuery. I queried the database in GBQ to get the tracks of all
+# vessels we need using the updated pipe_production_b_fishing.
+# 
+# After downloading the data, I add a couple of features that will come
+# in handy in the processing and fine-tuning of the next scripts. These
+# are basically getting rid of the few duplicate records, adding some
+# variables like factors for time-variables, and arranging the columns
+# in the order I want them (for now).
+########################################################################
+
+# Load the packages that I need
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+# Create a connection to Google BigQuery
+# For this to run, you require authentication and be part of ucsb-gfw
+BQc <- bigrquery::dbConnect(
+  drv = bigrquery::bigquery(),
+  project = "ucsb-gfw", # This is the project, to which you must belong
+  dataset = "mpa_displacement", # This is the dataset, where I keep all the tables
+  allowLargeResults = TRUE #We're downloading about 10 GB of data
+)
+
+# List all tables to test the connection
+DBI::dbListTables(BQc)
+
+
+# DOWNLOAD THE DATA
+# Create a tbl pointing to vessel tracks
+vessel_tracks <- dplyr::tbl(BQc, "vessel_tracks_2012_2018") %>%
+  collect() # collect brings the information out of the database and into memory
+
+# ADD FEATURES
+# First I define a set of variables of interest,
+# like the countries that belong to the PNA.
+
+# List of PNA countries
+PNA_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV")
+
+# List of countries that hold VDS rights (and then sell to others)
+VDS_countries <- c(PNA_countries, "TKL")
+
+# Set a large memory size for when this code runs on Windows
+if(unname(Sys.info()[1] == "Windows")){
+  memory.limit(size = 8e6)
+}
+
+# Modify the data
+vessel_tracks <- vessel_tracks %>% 
+  distinct() %>%
+  mutate(
+    date = lubridate::date(timestamp),
+    post = year >= 2015,
[…]

### 2019-02-25 scripts/content/example_treated_control_vessels.R

@@ -1,0 +1,42 @@
+
+# Load the packages that I need
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+source(here::here("scripts", "functions", "st_rotate.R"))
+
+# Create a connection to Google BigQuery
+# For this to run, you require authentication and be part of ucsb-gfw
+BQc <- bigrquery::dbConnect(
+  drv = bigrquery::bigquery(),
+  project = "ucsb-gfw", # This is the project, to which you must belong
+  dataset = "mpa_displacement", # This is the dataset, where I keep all the tables
+  allowLargeResults = TRUE #We're downloading about 10 GB of data
+)
+
+# List all tables to test the connection
+DBI::dbListTables(BQc)
+
+
+# DOWNLOAD THE DATA
+# Create a tbl pointing to vessel tracks
+vessel_tracks <- dplyr::tbl(BQc, "sample_treated_control_vessels") %>%
+  collect() # collect brings the information out of the database and into memory
+
+pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
+  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_rotate()
+
+vessel_tracks %>% 
+  mutate(year = lubridate::year(timestamp),
+         lon = ifelse(lon < 0, lon + 360, lon)) %>% 
+  filter(fishing, year < 2015) %>% 
+  ggplot() +
+  geom_point(aes(x = lon, y = lat, color = treated)) +
+  geom_sf(data = pipa, fill = "transparent", color = "red", size = 1) +
+  cowplot::theme_cowplot() +
+  scale_color_brewer(palette = "Set1") +
+  guides(color = guide_legend(title = "Group"))

### 2019-02-25 scripts/content/figs_all_PS_VDS_2012_2018.R

@@ -1,0 +1,140 @@
+###############################
+#   PS_VDS_PNA_by_year_eez    #
+###############################
+
+
+##########################################################################
+# This script calculates the number of total hours that ALL purse seiners
+# spent in PNA waters (PNA includes TKL).
+##########################################################################
+
+#### SETUP ########################################################
+# Load packages
+library(tidyverse)
+
+PNA_without_KIR <- c("FSM",
+         # "KIR",
+         "MHL",
+         "NRU",
+         "PLW",
+         "PNG",
+         "SLB",
+         "TUV",
+         "TKL")
+
+
+# Load data
+vessel_activity <- readRDS(file = here::here("raw_data",
+                                             "activity_by_vessel_year_eez.rds")) %>% 
+  filter(best_vessel_class == "tuna_purse_seines") %>% 
+  mutate(treated = ifelse(treated, "treated", "control"),
+         group = ifelse(is.na(treated), "others", treated),
+         location = case_when(eez_iso3 == "KIR" ~ "KIR",
+                              eez_iso3 %in% PNA_without_KIR ~ "PNA countries",
+                              eez_iso3 == "HS" ~"HS",
+                              T ~ "Other countries"),
+         days = hours / 24)
+
+#### CREATE THE DATA ################################################
+
+
+# Data for eez-level proportional allocations
+vessel_prop_activity_year_loc <- vessel_activity %>% 
+  group_by(year, group, ssvid, location) %>% 
+  summarize(days = sum(days, na.rm = T)) %>% 
+  ungroup() %>% 
+  group_by(year, group, ssvid) %>% 
+  mutate(total = sum(days, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(proportion = days/total)
+
+# Data for eez-level proportional
+vessel_activity_year_loc <- vessel_activity %>% 
+  group_by(year, group, location) %>% 
+  summarize(days = sum(days, na.rm = T)) %>% 
+  ungroup()
+
+#### PLOTS ########################################################
+
+ggplot(data = vessel_prop_activity_year_loc,
+       mapping = aes(x = proportion, y = as.character(year), fill = group)) +
[…]

### 2019-02-25 scripts/content/sp_corr.R

@@ -12,7 +12,7 @@
 # control vessels per cell (B).
 ################################################################
 
-#### SET UP ######################################################################################
+#### SET UP ######################################################
 
 # Load packages
 library(raster)
@@ -22,13 +22,16 @@ library(tidyverse)
 ## Load data
 
 # Find files
-files <- list.files(path = here::here("data", "spatial", "monthly_rasterized_effort_by_region"), pattern = "*.tif")
+files <- list.files(path = here::here("data",
+                                      "spatial",
+                                      "monthly_rasterized_effort_by_region"),
+                    pattern = "*.tif")
 
 # Stack files
 rs <- stack(here::here("data", "spatial", "monthly_rasterized_effort_by_region", files))
 
 
-##### CALCULATIONS #########################################################################
+##### CALCULATIONS ######################################################
 
 # Put into a data.frame
 corr <- raster::as.data.frame(rs, xy = T) %>%
@@ -62,7 +65,7 @@ corr_both <- corr %>%
 
 
 
-#### FIT THE MODELS ######################################################################
+#### FIT THE MODELS ######################################################
 
 n_model <- lm(n ~ dif + I(dif^2) + I(dif^3) + I(dif^4), data = n_both)
 corr_model <- lm(cor ~ dif + I(dif^2) + I(dif^3) + I(dif^4), data = corr_both)
@@ -93,7 +96,7 @@ stargazer::stargazer(models,
                      out = here::here("docs", "tab", "sp_corr.tex"))
 
 
-#### PLOT THEM ##########################################################################
+#### PLOT THEM #########################################################
 
 # Plot for number of cells with vessels from BOTH groups
 n_both_plot <- ggplot(data = n_both, aes(x = date, y = n)) +
@@ -141,6 +144,9 @@ plot <- cowplot::plot_grid(n_both_plot, corr_both_plot,
                            ncol = 1,
                            labels = "AUTO")
 
-ggsave(plot, filename = here::here("docs", "img", "sp_corr.pdf"), height = 5.5, width = 3.4)
+ggsave(plot,
+       filename = here::here("docs", "img", "sp_corr.pdf"),
+       height = 5.5,
+       width = 3.4)
 
 

### 2019-02-26 docs/tab/DID_without_CHN.tex
Updated figures

@@
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
 \hline \\[-1.8ex] 
- Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 5.513$^{***}$ & 10.647$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
-  & (0.038) & (0.007) & (0.009) & (0.045) & (0.054) & (0.088) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
-  & & & & & & & & & & \\ 
- Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & $-$0.077$^{*}$ & $-$0.201$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
-  & (0.026) & (0.008) & (0.007) & (0.036) & (0.042) & (0.061) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
-  & & & & & & & & & & \\ 
- Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.059 & 0.087 & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
-  & (0.028) & (0.006) & (0.007) & (0.032) & (0.037) & (0.055) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
-  & & & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.248$^{***}$ & $-$0.267$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
-  & (0.030) & (0.009) & (0.007) & (0.040) & (0.048) & (0.069) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
-  & & & & & & & & & & \\ 
+ Constant & 2.449$^{***}$ & 3.325$^{***}$ & 0.314$^{***}$ & 6.177$^{***}$ & 13.800$^{***}$ & 13.159$^{***}$ & 3.979$^{***}$ & 4.644$^{***}$ \\ 
+  & (0.061) & (0.031) & (0.014) & (0.042) & (0.047) & (0.065) & (0.392) & (0.343) \\ 
+  & & & & & & & & \\ 
+ Post & 0.336$^{***}$ & $-$0.353$^{***}$ & 0.083$^{***}$ & 0.105$^{***}$ & 0.398$^{***}$ & 0.352$^{***}$ & 1.151$^{***}$ & 1.240$^{***}$ \\ 
+  & (0.024) & (0.015) & (0.006) & (0.020) & (0.016) & (0.016) & (0.157) & (0.125) \\ 
+  & & & & & & & & \\ 
+ Treated & $-$0.085$^{***}$ & 0.060$^{***}$ & $-$0.028$^{***}$ & 0.259$^{***}$ & 0.259$^{***}$ & 0.163$^{***}$ & 0.435$^{***}$ & 0.082 \\ 
+  & (0.027) & (0.014) & (0.007) & (0.020) & (0.018) & (0.018) & (0.163) & (0.133) \\ 
+  & & & & & & & & \\ 
+ Post $\times$ Treated & 0.036 & $-$0.052$^{***}$ & 0.019$^{***}$ & $-$0.296$^{***}$ & $-$0.342$^{***}$ & $-$0.199$^{***}$ & $-$0.481$^{***}$ & $-$0.335$^{**}$ \\ 
+  & (0.028) & (0.017) & (0.007) & (0.024) & (0.020) & (0.019) & (0.179) & (0.142) \\ 
+  & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 25,073 & 74,600 & 25,073 & 73,265 & 74,995 & 74,995 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
-R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.019 & 0.013 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 25,004 & 51,724 & 25,004 & 52,767 & 25,004 & 25,004 & 1,399 & 2,010 \\ 
+R$^{2}$ & 0.066 & 0.092 & 0.067 & 0.011 & 0.073 & 0.095 & 0.141 & 0.230 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-02-26 docs/tab/DID_without_PNA.tex
Updated figures

@@
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
 \hline \\[-1.8ex] 
- Constant & 2.438$^{***}$ & 3.602$^{***}$ & 0.362$^{***}$ & 4.575$^{***}$ & 5.007$^{***}$ & 11.149$^{***}$ & 6.400$^{***}$ & 12.771$^{***}$ & 2.842$^{***}$ & 3.659$^{***}$ \\ 
-  & (0.042) & (0.012) & (0.011) & (0.051) & (0.056) & (0.080) & (0.030) & (0.028) & (0.238) & (0.187) \\ 
-  & & & & & & & & & & \\ 
- Post & 0.466$^{***}$ & $-$0.173$^{***}$ & 0.095$^{***}$ & $-$0.174$^{***}$ & $-$0.636$^{***}$ & $-$0.771$^{***}$ & 0.096$^{***}$ & 0.006 & 1.794$^{***}$ & 1.778$^{***}$ \\ 
-  & (0.037) & (0.010) & (0.010) & (0.048) & (0.051) & (0.076) & (0.025) & (0.024) & (0.197) & (0.164) \\ 
-  & & & & & & & & & & \\ 
- Treated & $-$0.142$^{***}$ & 0.023$^{***}$ & $-$0.059$^{***}$ & 0.450$^{***}$ & 0.048 & 0.158$^{**}$ & 0.077$^{***}$ & $-$0.164$^{***}$ & 0.570$^{***}$ & 0.443$^{***}$ \\ 
-  & (0.037) & (0.007) & (0.009) & (0.040) & (0.043) & (0.067) & (0.025) & (0.025) & (0.197) & (0.164) \\ 
-  & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.152$^{***}$ & $-$0.031$^{***}$ & 0.061$^{***}$ & $-$0.236$^{***}$ & 0.275$^{***}$ & 0.253$^{***}$ & $-$0.072$^{***}$ & 0.139$^{***}$ & $-$0.910$^{***}$ & $-$0.728$^{***}$ \\
-  & (0.040) & (0.011) & (0.010) & (0.052) & (0.056) & (0.082) & (0.027) & (0.026) & (0.216) & (0.177) \\ 
-  & & & & & & & & & & \\ 
+ Constant & 2.637$^{***}$ & 3.247$^{***}$ & 0.404$^{***}$ & 5.016$^{***}$ & 13.177$^{***}$ & 12.684$^{***}$ & 3.259$^{***}$ & 4.096$^{***}$ \\ 
+  & (0.042) & (0.021) & (0.011) & (0.044) & (0.028) & (0.025) & (0.270) & (0.206) \\ 
+  & & & & & & & & \\ 
+ Post & 0.283$^{***}$ & $-$0.443$^{***}$ & 0.048$^{***}$ & 0.628$^{***}$ & 0.164$^{***}$ & 0.077$^{***}$ & 1.347$^{***}$ & 1.586$^{***}$ \\ 
+  & (0.039) & (0.021) & (0.011) & (0.044) & (0.024) & (0.022) & (0.234) & (0.188) \\ 
+  & & & & & & & & \\ 
+ Treated & $-$0.091$^{**}$ & $-$0.051$^{***}$ & $-$0.052$^{***}$ & 0.683$^{***}$ & 0.137$^{***}$ & $-$0.020 & 0.697$^{***}$ & 0.477$^{***}$ \\ 
+  & (0.040) & (0.019) & (0.011) & (0.041) & (0.024) & (0.022) & (0.233) & (0.184) \\ 
+  & & & & & & & & \\ 
+ Post $\times$ Treated & 0.081$^{*}$ & 0.021 & 0.055$^{***}$ & $-$0.880$^{***}$ & $-$0.153$^{***}$ & 0.017 & $-$0.691$^{***}$ & $-$0.706$^{***}$ \\ 
+  & (0.042) & (0.023) & (0.011) & (0.046) & (0.027) & (0.024) & (0.251) & (0.202) \\ 
+  & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 21,523 & 63,902 & 21,523 & 61,827 & 64,224 & 64,224 & 21,523 & 21,523 & 1,280 & 1,759 \\ 
-R$^{2}$ & 0.137 & 0.073 & 0.148 & 0.015 & 0.020 & 0.015 & 0.165 & 0.316 & 0.187 & 0.271 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 19,971 & 42,555 & 19,971 & 43,068 & 19,971 & 19,971 & 1,207 & 1,696 \\ 
+R$^{2}$ & 0.064 & 0.097 & 0.066 & 0.032 & 0.059 & 0.071 & 0.133 & 0.217 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-02-26 docs/tab/DID_without_USA_TWN.tex
Updated figures

@@
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters.
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
 \hline \\[-1.8ex] 
- Constant & 2.343$^{***}$ & 3.624$^{***}$ & 0.327$^{***}$ & 4.599$^{***}$ & 4.860$^{***}$ & 11.030$^{***}$ & 6.176$^{***}$ & 12.513$^{***}$ & 3.246$^{***}$ & 4.062$^{***}$ \\ 
-  & (0.035) & (0.010) & (0.009) & (0.045) & (0.052) & (0.071) & (0.025) & (0.023) & (0.208) & (0.160) \\ 
-  & & & & & & & & & & \\ 
- Post & 0.599$^{***}$ & $-$0.211$^{***}$ & 0.139$^{***}$ & $-$0.167$^{***}$ & $-$0.364$^{***}$ & $-$0.532$^{***}$ & 0.338$^{***}$ & 0.261$^{***}$ & 1.477$^{***}$ & 1.457$^{***}$ \\ 
-  & (0.027) & (0.008) & (0.007) & (0.034) & (0.042) & (0.059) & (0.017) & (0.018) & (0.148) & (0.122) \\ 
-  & & & & & & & & & & \\ 
- Treated & $-$0.065$^{**}$ & 0.007 & $-$0.025$^{***}$ & 0.326$^{***}$ & 0.040 & 0.099$^{*}$ & 0.158$^{***}$ & $-$0.010 & 0.375$^{**}$ & 0.116 \\ 
-  & (0.029) & (0.006) & (0.007) & (0.031) & (0.037) & (0.054) & (0.019) & (0.019) & (0.150) & (0.126) \\ 
-  & & & & & & & & & & \\ 
- Post $\times$ Treated & 0.017 & 0.003 & 0.015$^{**}$ & $-$0.187$^{***}$ & 0.070 & 0.077 & $-$0.274$^{***}$ & $-$0.072$^{***}$ & $-$0.562$^{***}$ & $-$0.353$^{**}$ \\ 
-  & (0.031) & (0.009) & (0.008) & (0.039) & (0.048) & (0.068) & (0.020) & (0.020) & (0.170) & (0.139) \\ 
-  & & & & & & & & & & \\ 
+ Constant & 2.661$^{***}$ & 3.154$^{***}$ & 0.393$^{***}$ & 5.256$^{***}$ & 12.977$^{***}$ & 12.434$^{***}$ & 3.776$^{***}$ & 4.722$^{***}$ \\ 
+  & (0.031) & (0.019) & (0.008) & (0.032) & (0.023) & (0.021) & (0.216) & (0.165) \\ 
+  & & & & & & & & \\ 
+ Post & 0.313$^{***}$ & $-$0.371$^{***}$ & 0.075$^{***}$ & 0.244$^{***}$ & 0.394$^{***}$ & 0.332$^{***}$ & 1.096$^{***}$ & 0.978$^{***}$ \\ 
+  & (0.024) & (0.014) & (0.006) & (0.022) & (0.016) & (0.016) & (0.158) & (0.127) \\ 
+  & & & & & & & & \\ 
+ Treated & $-$0.154$^{***}$ & 0.040$^{***}$ & $-$0.049$^{***}$ & 0.455$^{***}$ & 0.223$^{***}$ & 0.137$^{***}$ & 0.422$^{**}$ & $-$0.062 \\ 
+  & (0.027) & (0.014) & (0.007) & (0.022) & (0.018) & (0.018) & (0.166) & (0.129) \\ 
+  & & & & & & & & \\ 
+ Post $\times$ Treated & 0.067$^{**}$ & $-$0.047$^{***}$ & 0.031$^{***}$ & $-$0.482$^{***}$ & $-$0.335$^{***}$ & $-$0.179$^{***}$ & $-$0.475$^{***}$ & $-$0.117 \\ 
+  & (0.028) & (0.017) & (0.007) & (0.025) & (0.020) & (0.019) & (0.179) & (0.145) \\ 
+  & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 24,152 & 73,259 & 24,152 & 73,001 & 73,668 & 73,668 & 24,152 & 24,152 & 1,420 & 1,998 \\ 
-R$^{2}$ & 0.143 & 0.075 & 0.154 & 0.014 & 0.021 & 0.015 & 0.157 & 0.291 & 0.174 & 0.246 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 24,005 & 50,737 & 24,005 & 52,825 & 24,005 & 24,005 & 1,375 & 1,981 \\ 
+R$^{2}$ & 0.065 & 0.095 & 0.067 & 0.029 & 0.072 & 0.096 & 0.129 & 0.194 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-02-26 docs/tab/main_DID.tex
Updated figures

@@
 \hline \\[-1.8ex] 
- Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
-  & (0.038) & (0.007) & (0.009) & (0.045) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
+ Constant & 2.630$^{***}$ & 3.167$^{***}$ & 0.388$^{***}$ & 5.236$^{***}$ & 12.973$^{***}$ & 12.464$^{***}$ & 3.646$^{***}$ & 4.476$^{***}$ \\ 
+  & (0.029) & (0.018) & (0.008) & (0.031) & (0.021) & (0.020) & (0.202) & (0.159) \\ 
   & & & & & & & & \\ 
- Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
-  & (0.026) & (0.008) & (0.007) & (0.036) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
+ Post & 0.313$^{***}$ & $-$0.380$^{***}$ & 0.073$^{***}$ & 0.259$^{***}$ & 0.359$^{***}$ & 0.305$^{***}$ & 1.158$^{***}$ & 1.206$^{***}$ \\ 
+  & (0.022) & (0.013) & (0.006) & (0.021) & (0.015) & (0.015) & (0.143) & (0.115) \\ 
   & & & & & & & & \\ 
- Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
-  & (0.028) & (0.006) & (0.007) & (0.032) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
+ Treated & $-$0.106$^{***}$ & 0.020 & $-$0.038$^{***}$ & 0.401$^{***}$ & 0.214$^{***}$ & 0.120$^{***}$ & 0.483$^{***}$ & 0.104 \\ 
+  & (0.025) & (0.013) & (0.006) & (0.021) & (0.016) & (0.016) & (0.150) & (0.120) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
-  & (0.030) & (0.009) & (0.007) & (0.040) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
+ Post $\times$ Treated & 0.051$^{**}$ & $-$0.024 & 0.028$^{***}$ & $-$0.451$^{***}$ & $-$0.287$^{***}$ & $-$0.151$^{***}$ & $-$0.509$^{***}$ & $-$0.314$^{**}$ \\ 
+  & (0.026) & (0.015) & (0.007) & (0.024) & (0.018) & (0.017) & (0.165) & (0.133) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 25,073 & 74,600 & 25,073 & 73,265 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
-R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
+Observations & 28,136 & 57,783 & 28,136 & 58,787 & 28,136 & 28,136 & 1,601 & 2,275 \\ 
+R$^{2}$ & 0.062 & 0.092 & 0.061 & 0.024 & 0.071 & 0.085 & 0.138 & 0.218 \\ 
 \hline 

### 2019-02-28 docs/tab/main_DID.tex
Updated tables for spatial redistribution and main DID

--- 2019-02-19 docs/tab/main_DID.tex
@@
 \hline \\[-1.8ex] 
- Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
-  & (0.038) & (0.007) & (0.009) & (0.045) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
+ Constant & 0.497$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 5.203$^{***}$ & 12.997$^{***}$ & 12.461$^{***}$ & 3.678$^{***}$ & 4.445$^{***}$ \\ 
+  & (0.022) & (0.012) & (0.004) & (0.029) & (0.021) & (0.019) & (0.192) & (0.151) \\ 
   & & & & & & & & \\ 
- Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
-  & (0.026) & (0.008) & (0.007) & (0.036) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
+ Post & 0.839$^{***}$ & $-$0.228$^{***}$ & 0.137$^{***}$ & 0.304$^{***}$ & 0.326$^{***}$ & 0.296$^{***}$ & 1.059$^{***}$ & 1.180$^{***}$ \\ 
+  & (0.016) & (0.008) & (0.003) & (0.019) & (0.014) & (0.014) & (0.140) & (0.109) \\ 
   & & & & & & & & \\ 
- Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
-  & (0.028) & (0.006) & (0.007) & (0.032) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
+ Treated & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.400$^{***}$ & 0.223$^{***}$ & 0.116$^{***}$ & 0.534$^{***}$ & 0.149 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.020) & (0.016) & (0.016) & (0.148) & (0.118) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
-  & (0.030) & (0.009) & (0.007) & (0.040) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
+ Post $\times$ Treated & $-$0.244$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.483$^{***}$ & $-$0.281$^{***}$ & $-$0.155$^{***}$ & $-$0.565$^{***}$ & $-$0.399$^{***}$ \\ 
+  & (0.019) & (0.009) & (0.003) & (0.022) & (0.017) & (0.017) & (0.161) & (0.127) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 25,073 & 74,600 & 25,073 & 73,265 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
-R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
+Observations & 83,052 & 83,052 & 83,051 & 64,387 & 32,055 & 32,055 & 1,814 & 2,588 \\ 
+R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.028 & 0.062 & 0.080 & 0.113 & 0.198 \\ 
 \hline 

### 2019-02-28 docs/tab/DID_without_CHN.tex
Updated manu figures

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 2.449$^{***}$ & 3.325$^{***}$ & 0.314$^{***}$ & 6.177$^{***}$ & 13.800$^{***}$ & 13.159$^{***}$ & 3.979$^{***}$ & 4.644$^{***}$ \\ 
-  & (0.061) & (0.031) & (0.014) & (0.042) & (0.047) & (0.065) & (0.392) & (0.343) \\ 
+ Constant & 0.060$^{***}$ & 3.864$^{***}$ & $-$0.003 & 6.149$^{***}$ & 13.775$^{***}$ & 13.146$^{***}$ & 3.896$^{***}$ & 4.484$^{***}$ \\ 
+  & (0.019) & (0.008) & (0.003) & (0.043) & (0.044) & (0.058) & (0.341) & (0.303) \\ 
   & & & & & & & & \\ 
- Post & 0.336$^{***}$ & $-$0.353$^{***}$ & 0.083$^{***}$ & 0.105$^{***}$ & 0.398$^{***}$ & 0.352$^{***}$ & 1.151$^{***}$ & 1.240$^{***}$ \\ 
-  & (0.024) & (0.015) & (0.006) & (0.020) & (0.016) & (0.016) & (0.157) & (0.125) \\ 
+ Post & 0.817$^{***}$ & $-$0.258$^{***}$ & 0.136$^{***}$ & 0.125$^{***}$ & 0.365$^{***}$ & 0.344$^{***}$ & 1.056$^{***}$ & 1.205$^{***}$ \\ 
+  & (0.018) & (0.009) & (0.003) & (0.019) & (0.015) & (0.016) & (0.154) & (0.120) \\ 
   & & & & & & & & \\ 
- Treated & $-$0.085$^{***}$ & 0.060$^{***}$ & $-$0.028$^{***}$ & 0.259$^{***}$ & 0.259$^{***}$ & 0.163$^{***}$ & 0.435$^{***}$ & 0.082 \\ 
-  & (0.027) & (0.014) & (0.007) & (0.020) & (0.018) & (0.018) & (0.163) & (0.133) \\ 
+ Treated & 0.108$^{***}$ & 0.009 & 0.012$^{***}$ & 0.294$^{***}$ & 0.268$^{***}$ & 0.157$^{***}$ & 0.489$^{***}$ & 0.148 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.020) & (0.017) & (0.017) & (0.162) & (0.132) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & 0.036 & $-$0.052$^{***}$ & 0.019$^{***}$ & $-$0.296$^{***}$ & $-$0.342$^{***}$ & $-$0.199$^{***}$ & $-$0.481$^{***}$ & $-$0.335$^{**}$ \\ 
-  & (0.028) & (0.017) & (0.007) & (0.024) & (0.020) & (0.019) & (0.179) & (0.142) \\ 
+ Post $\times$ Treated & $-$0.212$^{***}$ & 0.039$^{***}$ & $-$0.031$^{***}$ & $-$0.318$^{***}$ & $-$0.335$^{***}$ & $-$0.203$^{***}$ & $-$0.547$^{***}$ & $-$0.409$^{***}$ \\ 
+  & (0.021) & (0.010) & (0.004) & (0.023) & (0.019) & (0.018) & (0.174) & (0.137) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 25,004 & 51,724 & 25,004 & 52,767 & 25,004 & 25,004 & 1,399 & 2,010 \\ 
-R$^{2}$ & 0.066 & 0.092 & 0.067 & 0.011 & 0.073 & 0.095 & 0.141 & 0.230 \\ 
+Observations & 75,327 & 75,327 & 75,326 & 58,129 & 28,449 & 28,449 & 1,570 & 2,279 \\ 
+R$^{2}$ & 0.102 & 0.073 & 0.108 & 0.011 & 0.063 & 0.089 & 0.114 & 0.207 \\ 
 \hline 

### 2019-02-28 docs/tab/DID_without_PNA.tex
Updated manu figures

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 2.637$^{***}$ & 3.247$^{***}$ & 0.404$^{***}$ & 5.016$^{***}$ & 13.177$^{***}$ & 12.684$^{***}$ & 3.259$^{***}$ & 4.096$^{***}$ \\ 
-  & (0.042) & (0.021) & (0.011) & (0.044) & (0.028) & (0.025) & (0.270) & (0.206) \\ 
+ Constant & 0.513$^{***}$ & 3.559$^{***}$ & 0.083$^{***}$ & 5.002$^{***}$ & 13.189$^{***}$ & 12.672$^{***}$ & 3.307$^{***}$ & 4.068$^{***}$ \\ 
+  & (0.024) & (0.013) & (0.004) & (0.044) & (0.027) & (0.025) & (0.264) & (0.202) \\ 
   & & & & & & & & \\ 
- Post & 0.283$^{***}$ & $-$0.443$^{***}$ & 0.048$^{***}$ & 0.628$^{***}$ & 0.164$^{***}$ & 0.077$^{***}$ & 1.347$^{***}$ & 1.586$^{***}$ \\ 
-  & (0.039) & (0.021) & (0.011) & (0.044) & (0.024) & (0.022) & (0.234) & (0.188) \\ 
+ Post & 0.772$^{***}$ & $-$0.159$^{***}$ & 0.121$^{***}$ & 0.630$^{***}$ & 0.136$^{***}$ & 0.074$^{***}$ & 1.237$^{***}$ & 1.546$^{***}$ \\ 
+  & (0.021) & (0.011) & (0.004) & (0.043) & (0.023) & (0.022) & (0.230) & (0.181) \\ 
   & & & & & & & & \\ 
- Treated & $-$0.091$^{**}$ & $-$0.051$^{***}$ & $-$0.052$^{***}$ & 0.683$^{***}$ & 0.137$^{***}$ & $-$0.020 & 0.697$^{***}$ & 0.477$^{***}$ \\ 
-  & (0.040) & (0.019) & (0.011) & (0.041) & (0.024) & (0.022) & (0.233) & (0.184) \\ 
+ Treated & 0.203$^{***}$ & 0.040$^{***}$ & 0.019$^{***}$ & 0.676$^{***}$ & 0.147$^{***}$ & $-$0.018 & 0.747$^{***}$ & 0.514$^{***}$ \\ 
+  & (0.015) & (0.009) & (0.003) & (0.041) & (0.024) & (0.022) & (0.232) & (0.183) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & 0.081$^{*}$ & 0.021 & 0.055$^{***}$ & $-$0.880$^{***}$ & $-$0.153$^{***}$ & 0.017 & $-$0.691$^{***}$ & $-$0.706$^{***}$ \\ 
-  & (0.042) & (0.023) & (0.011) & (0.046) & (0.027) & (0.024) & (0.251) & (0.202) \\ 
+ Post $\times$ Treated & $-$0.220$^{***}$ & $-$0.055$^{***}$ & $-$0.023$^{***}$ & $-$0.893$^{***}$ & $-$0.148$^{***}$ & 0.015 & $-$0.753$^{***}$ & $-$0.792$^{***}$ \\ 
+  & (0.024) & (0.012) & (0.004) & (0.045) & (0.026) & (0.024) & (0.246) & (0.195) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 19,971 & 42,555 & 19,971 & 43,068 & 19,971 & 19,971 & 1,207 & 1,696 \\ 
-R$^{2}$ & 0.064 & 0.097 & 0.066 & 0.032 & 0.059 & 0.071 & 0.133 & 0.217 \\ 
+Observations & 64,560 & 64,560 & 64,559 & 47,375 & 22,654 & 22,654 & 1,366 & 1,928 \\ 
+R$^{2}$ & 0.093 & 0.069 & 0.099 & 0.030 & 0.055 & 0.066 & 0.109 & 0.198 \\ 
 \hline 

### 2019-02-28 docs/tab/DID_without_USA_TWN.tex
Updated manu figures

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 2.661$^{***}$ & 3.154$^{***}$ & 0.393$^{***}$ & 5.256$^{***}$ & 12.977$^{***}$ & 12.434$^{***}$ & 3.776$^{***}$ & 4.722$^{***}$ \\ 
-  & (0.031) & (0.019) & (0.008) & (0.032) & (0.023) & (0.021) & (0.216) & (0.165) \\ 
+ Constant & 0.536$^{***}$ & 3.600$^{***}$ & 0.082$^{***}$ & 5.237$^{***}$ & 12.995$^{***}$ & 12.435$^{***}$ & 3.808$^{***}$ & 4.703$^{***}$ \\ 
+  & (0.023) & (0.012) & (0.004) & (0.031) & (0.022) & (0.020) & (0.206) & (0.157) \\ 
   & & & & & & & & \\ 
- Post & 0.313$^{***}$ & $-$0.371$^{***}$ & 0.075$^{***}$ & 0.244$^{***}$ & 0.394$^{***}$ & 0.332$^{***}$ & 1.096$^{***}$ & 0.978$^{***}$ \\ 
-  & (0.024) & (0.014) & (0.006) & (0.022) & (0.016) & (0.016) & (0.158) & (0.127) \\ 
+ Post & 0.795$^{***}$ & $-$0.218$^{***}$ & 0.130$^{***}$ & 0.278$^{***}$ & 0.360$^{***}$ & 0.321$^{***}$ & 0.985$^{***}$ & 0.961$^{***}$ \\ 
+  & (0.018) & (0.009) & (0.003) & (0.021) & (0.015) & (0.016) & (0.153) & (0.119) \\ 
   & & & & & & & & \\ 
- Treated & $-$0.154$^{***}$ & 0.040$^{***}$ & $-$0.049$^{***}$ & 0.455$^{***}$ & 0.223$^{***}$ & 0.137$^{***}$ & 0.422$^{**}$ & $-$0.062 \\ 
-  & (0.027) & (0.014) & (0.007) & (0.022) & (0.018) & (0.018) & (0.166) & (0.129) \\ 
+ Treated & 0.142$^{***}$ & 0.016$^{**}$ & 0.015$^{***}$ & 0.461$^{***}$ & 0.231$^{***}$ & 0.128$^{***}$ & 0.481$^{***}$ & $-$0.021 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.022) & (0.018) & (0.017) & (0.163) & (0.127) \\ 
   & & & & & & & & \\ 
- Post $\times$ Treated & 0.067$^{**}$ & $-$0.047$^{***}$ & 0.031$^{***}$ & $-$0.482$^{***}$ & $-$0.335$^{***}$ & $-$0.179$^{***}$ & $-$0.475$^{***}$ & $-$0.117 \\ 
-  & (0.028) & (0.017) & (0.007) & (0.025) & (0.020) & (0.019) & (0.179) & (0.145) \\ 
+ Post $\times$ Treated & $-$0.212$^{***}$ & $-$0.002 & $-$0.029$^{***}$ & $-$0.526$^{***}$ & $-$0.328$^{***}$ & $-$0.184$^{***}$ & $-$0.525$^{***}$ & $-$0.222 \\ 
+  & (0.021) & (0.010) & (0.004) & (0.024) & (0.019) & (0.018) & (0.175) & (0.138) \\ 
   & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 24,005 & 50,737 & 24,005 & 52,825 & 24,005 & 24,005 & 1,375 & 1,981 \\ 
-R$^{2}$ & 0.065 & 0.095 & 0.067 & 0.029 & 0.072 & 0.096 & 0.129 & 0.194 \\ 
+Observations & 73,717 & 73,717 & 73,716 & 57,806 & 26,920 & 26,920 & 1,546 & 2,236 \\ 
+R$^{2}$ & 0.095 & 0.072 & 0.102 & 0.029 & 0.061 & 0.090 & 0.100 & 0.166 \\ 
 \hline 

### 2019-02-28 docs/tab/main_DID.tex
Updated manu figures

--- 2019-02-19 docs/tab/main_DID.tex
@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
 \hline \\[-1.8ex] 
- Constant & 1.875$^{***}$ & 3.860$^{***}$ & 0.198$^{***}$ & 4.878$^{***}$ & 7.199$^{***}$ & 13.886$^{***}$ & 2.497$^{***}$ & 2.624$^{***}$ \\ 
-  & (0.038) & (0.007) & (0.009) & (0.045) & (0.026) & (0.028) & (0.281) & (0.255) \\ 
-  & & & & & & & & \\ 
- Post & 0.654$^{***}$ & $-$0.243$^{***}$ & 0.157$^{***}$ & $-$0.099$^{***}$ & 0.336$^{***}$ & 0.248$^{***}$ & 1.537$^{***}$ & 1.556$^{***}$ \\ 
-  & (0.026) & (0.008) & (0.007) & (0.036) & (0.016) & (0.017) & (0.154) & (0.119) \\ 
-  & & & & & & & & \\ 
- Treated & 0.008 & 0.008 & $-$0.007 & 0.275$^{***}$ & 0.180$^{***}$ & $-$0.018 & 0.393$^{***}$ & 0.244$^{**}$ \\ 
-  & (0.028) & (0.006) & (0.007) & (0.032) & (0.017) & (0.018) & (0.151) & (0.119) \\ 
-  & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.020 & 0.033$^{***}$ & 0.0002 & $-$0.250$^{***}$ & $-$0.281$^{***}$ & $-$0.059$^{***}$ & $-$0.531$^{***}$ & $-$0.368$^{***}$ \\ 
-  & (0.030) & (0.009) & (0.007) & (0.040) & (0.019) & (0.019) & (0.175) & (0.135) \\ 
-  & & & & & & & & \\ 
+ Constant & 0.497$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 5.203$^{***}$ & 12.997$^{***}$ & 12.461$^{***}$ & 3.678$^{***}$ & 4.445$^{***}$ & 2.420$^{***}$ \\ 
+  & (0.022) & (0.012) & (0.004) & (0.029) & (0.021) & (0.019) & (0.192) & (0.151) & (0.421) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.839$^{***}$ & $-$0.228$^{***}$ & 0.137$^{***}$ & 0.304$^{***}$ & 0.326$^{***}$ & 0.296$^{***}$ & 1.059$^{***}$ & 1.180$^{***}$ & 0.920$^{***}$ \\ 
+  & (0.016) & (0.008) & (0.003) & (0.019) & (0.014) & (0.014) & (0.140) & (0.109) & (0.273) \\ 
+  & & & & & & & & & \\ 
+ Treated & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.400$^{***}$ & 0.223$^{***}$ & 0.116$^{***}$ & 0.534$^{***}$ & 0.149 & $-$0.244 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.020) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Treated & $-$0.244$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.483$^{***}$ & $-$0.281$^{***}$ & $-$0.155$^{***}$ & $-$0.565$^{***}$ & $-$0.399$^{***}$ & 0.338 \\ 
+  & (0.019) & (0.009) & (0.003) & (0.022) & (0.017) & (0.017) & (0.161) & (0.127) & (0.288) \\ 
+  & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 25,073 & 74,600 & 25,073 & 73,265 & 25,073 & 25,073 & 1,460 & 2,056 \\ 
-R$^{2}$ & 0.141 & 0.075 & 0.151 & 0.011 & 0.163 & 0.293 & 0.198 & 0.282 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 83,052 & 83,052 & 83,051 & 64,387 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
+R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.028 & 0.062 & 0.080 & 0.113 & 0.198 & 0.233 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-02-28 docs/tab/sp_corr.tex
Updated manu figures

@@
 \hline \\[-1.8ex] 
- Constant & 67.894$^{***}$ (5.363) & 0.448$^{***}$ (0.014) \\ 
-  Months & 3.301$^{***}$ (0.317) & 0.009$^{***}$ (0.001) \\ 
-  Months $^2$ & 0.007 (0.023) & $-$0.0001$^{**}$ (0.00005) \\ 
-  Months $^3$ & $-$0.002$^{***}$ (0.0003) & $-$0.00001$^{***}$ (0.00000) \\ 
-  Months $^4$ & 0.00001 (0.00002) & 0.00000$^{**}$ (0.00000) \\ 
+ Constant & 59.999$^{***}$ (15.581) & 0.370$^{***}$ (0.062) \\ 
+  Months & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
+  Months $^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
+  Months $^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
+  Months $^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
+  sate1 & 22.342 (19.528) & 0.057 (0.076) \\ 
+  sate2 & 5.413 (18.860) & $-$0.015 (0.035) \\ 
  \hline \\[-1.8ex] 
@@
 Observations & 83 & 84 \\ 
-R$^{2}$ & 0.681 & 0.683 \\ 
+R$^{2}$ & 0.791 & 0.709 \\ 
 \hline 

### 2019-02-28 scripts/content/fig_all_panels.R

@@ -12,6 +12,7 @@
 
 
 #Load packages
+library(here)
 library(cowplot)
 library(tidyverse)
 
@@ -36,7 +37,7 @@ varplot <- function(data, var, y_lab){
 
 ## FISHING HOURS ##################################################################
 # Load data
-effort_by_vessel <- readRDS(file = here::here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
+effort_by_vessel <- readRDS(file = here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
          gear == "tuna_purse_seines") %>% 
   mutate(date = lubridate::date(paste(year, month, 15, sep = "/")),
@@ -57,7 +58,7 @@ nonfishing_hours <- effort_by_vessel %>%
 ## PROPORTIONFISHING HOURS ##################################################################
 # Load data
 prop_fishing_by_vessel <-
-  readRDS(file = here::here("data", "panels", "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
+  readRDS(file = here("data", "panels", "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
          gear == "tuna_purse_seines") %>% 
   mutate(date = lubridate::date(paste(year, month, 15, sep = "/")),
@@ -67,7 +68,7 @@ prop_fishing_by_vessel <-
 
 ## DISTANCE TRAVELED ##################################################################
 #Load data
-distance_traveled <- readRDS(file = here::here("data",
+distance_traveled <- readRDS(file = here("data",
                                                 "panels",
                                                 "daily_distance_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
@@ -80,7 +81,7 @@ distance_traveled <- readRDS(file = here::here("data",
 
 ## DISTANCE FROM PORT AND SHORE ##################################################################
 # Load data
-distance_port_shore <- readRDS(file = here::here("data",
+distance_port_shore <- readRDS(file = here("data",
                                                  "panels",
                                                  "distance_from_port_shore_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
@@ -103,7 +104,7 @@ distance_from_shore <- distance_port_shore %>%
[…]

### 2019-02-28 scripts/content/robustness/analyses_on_controls_excluding_CHN.R

@@ -22,7 +22,7 @@ source(here::here("scripts", "functions", "termplot.R"))
 effort_by_vessel <- readRDS(file = here::here("data",
                                               "panels",
                                               "daily_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag == "CHN")
 
@@ -58,7 +58,7 @@ nonfish_didym <- did_yearmonth(nonfishing_hours)
 prop_fishing_by_vessel <- readRDS(file = here::here("data",
                                                     "panels",
                                                     "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag == "CHN") %>% 
   model_data_prep(prop_fishing)
@@ -76,7 +76,7 @@ prop_fish_didym <- did_yearmonth(prop_fishing_by_vessel)
 distance_traveled <- readRDS(file = here::here("data",
                                                "panels",
                                                "daily_distance_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !mmsi %in% c(345050700,412328731,416238800, 512000089),
          !flag == "CHN") %>% 
@@ -96,7 +96,7 @@ dist_didym <- did_yearmonth(distance_traveled)
 distance_port_shore <- readRDS(file = here::here("data",
                                                  "panels",
                                                  "distance_from_port_shore_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag == "CHN")
 
@@ -129,7 +129,7 @@ dist_shore_didym <- did_yearmonth(distance_shore)
 distance_port_shore_fishing <- readRDS(file = here::here("data",
                                                          "panels",
                                                          "distance_from_port_shore_fishing_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag == "CHN")
 
@@ -160,7 +160,7 @@ dist_shore_fishing_didym <- did_yearmonth(distance_shore_fishing)
 ##### PROPORTION FISHING IN KIR ########################################################
 # Load the data
[…]

### 2019-02-28 scripts/content/robustness/analyses_on_controls_excluding_USA_TWN.R

@@ -23,7 +23,7 @@ source(here::here("scripts", "functions", "termplot.R"))
 effort_by_vessel <- readRDS(file = here::here("data",
                                               "panels",
                                               "daily_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag %in% c("USA", "TWN"))
 
@@ -59,7 +59,7 @@ nonfish_didym <- did_yearmonth(nonfishing_hours)
 prop_fishing_by_vessel <- readRDS(file = here::here("data",
                                                     "panels",
                                                     "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag %in% c("USA", "TWN")) %>% 
   model_data_prep(prop_fishing)
@@ -77,7 +77,7 @@ prop_fish_didym <- did_yearmonth(prop_fishing_by_vessel)
 distance_traveled <- readRDS(file = here::here("data",
                                                "panels",
                                                "daily_distance_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !mmsi %in% c(345050700,412328731,416238800, 512000089),
          !flag %in% c("USA", "TWN")) %>% 
@@ -97,7 +97,7 @@ dist_didym <- did_yearmonth(distance_traveled)
 distance_port_shore <- readRDS(file = here::here("data",
                                                  "panels",
                                                  "distance_from_port_shore_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag %in% c("USA", "TWN"))
 
@@ -130,7 +130,7 @@ dist_shore_didym <- did_yearmonth(distance_shore)
 distance_port_shore_fishing <- readRDS(file = here::here("data",
                                                          "panels",
                                                          "distance_from_port_shore_fishing_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
+  filter(year < 2019,
          gear == "tuna_purse_seines",
          !flag %in% c("USA", "TWN"))
 
@@ -161,7 +161,7 @@ dist_shore_fishing_didym <- did_yearmonth(distance_shore_fishing)
[…]

### 2019-02-28 scripts/content/sp_corr.R

@@ -15,6 +15,8 @@
 #### SET UP ######################################################
 
 # Load packages
+library(lubridate)
+library(here)
 library(raster)
 library(tidyverse)
 
@@ -22,13 +24,13 @@ library(tidyverse)
 ## Load data
 
 # Find files
-files <- list.files(path = here::here("data",
-                                      "spatial",
-                                      "monthly_rasterized_effort_by_region"),
+files <- list.files(path = here("data",
+                                "spatial",
+                                "monthly_rasterized_effort_by_region"),
                     pattern = "*.tif")
 
 # Stack files
-rs <- stack(here::here("data", "spatial", "monthly_rasterized_effort_by_region", files))
+rs <- stack(here("data", "spatial", "monthly_rasterized_effort_by_region", files))
 
 
 ##### CALCULATIONS ######################################################
@@ -44,31 +46,33 @@ corr <- raster::as.data.frame(rs, xy = T) %>%
   spread(group, hours, fill = 0) %>% 
   mutate(both = (Control > 0 & Treated > 0) * 1,
          post = year > 2014,
-         date = lubridate::date(paste(year, month, 01, sep = "-")))
+         date = date(paste(year, month, 01, sep = "-")),
+         sate1 = (date > date("2014-06-01")) * 1,
+         sate2 = (date > date("2015-12-31")) * 1)
 
 # Calculate number of cells with both vessels
 n_both <- corr %>%
   filter(both > 0) %>% 
-  group_by(year, month, date, post) %>% 
+  group_by(year, month, date, post, sate1, sate2) %>% 
   summarize(n = sum(both)) %>% 
   ungroup() %>% 
-  mutate(dif = lubridate::interval(lubridate::date("2015-01-01"), date)%/% months(1))
+  mutate(dif = interval(date("2015-01-01"), date)%/% months(1))
 
 
 # Calculate spatial correlation
 corr_both <- corr %>%
   drop_na() %>%
-  group_by(year, month, date, post) %>%
+  group_by(year, month, date, post, sate1, sate2) %>%
   summarize(cor = cor(Control, Treated)) %>% 
   ungroup() %>% 
-  mutate(dif = lubridate::interval(lubridate::date("2015-01-01"), date)%/% months(1))
+  mutate(dif = interval(date("2015-01-01"), date)%/% months(1))
 
 
 
 #### FIT THE MODELS ######################################################
 
[…]

### 2019-03-01 docs/PIPA_Palau022819.tex
Updated fig 5 to include reported vs observed

\documentclass[9p,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\usepackage{placeins}

\title{Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Juan CarlosVillase\~{n}or-Derbez}
\author[b]{John Lynham}

\affil[a]{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA}
\affil[b]{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}

% Please give the surname of the lead author for the running footer
\leadauthor{Villase\~{n}or-Derbez}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{The oceans are becoming increasingly crowded, with different activities competing for space, but little research has been done to understand how activities displace each other. Marine Protected Areas are inherently spatial and have the sole objective of conserving bounded waters through the displacement of fishing effort. Our work shows that displacement of fishing effort occurs, but that it comes at a cost to countries that would have otherwise been able to charge a price for vessels to fish in the now-protected areas. With global conservation targets seeking to protect 10\% of the world’s ocean by 2020 and the expansion of offshore aquaculture, it is important that the spatial displacement of economic activities is fully considered.}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{All authors contributed equally to this work}
\authordeclaration{The authors declare that they have no conflicts of interest}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: juancarlos@ucsb.edu}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Marine Spatial Planning $|$ Fisheries $|$ Marine Conservation}

\begin{abstract}
The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean. The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters. In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities. Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as induce costs (due to the reduction in fishable area) to Kiribati. We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution, behavior, and costs to Kiribati and the PNA. We find a crowding effect within PNA waters after the implementation of the protected area. Vessels continue to fish with similar intensity after the implementation. In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold. However, from 2016 onwards there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue. At the same time, fishing effort increases in other parts of the PNA. This redistribution of fishing effort eventually results in a reduction of 2,310 vessel-days in Kiribati, which represents a loss of \$27.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD). We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually. PNA members who indirectly benefit from MPAs should consider mechanisms that reward such conservation actions.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{introduction}

\dropcap{H}umans are increasingly utilizing the oceans. Multiple ocean uses such as off-shore aquaculture, conservation, energy harvesting, deep-sea mining, and fisheries are likely to compete for space. As we move forward with blue growth, we must understand the potential effects of activities displacing each other and establish causal links between past management interventions and their outcomes \citep{burgess_2018}. One of the most notable spatial interventions is the creation of no-take Marine Protected Areas (MPAs), which seek to conserve the environment by eliminating fishing effort within their waters.

Global international goals aim to protect 10\% of the ocean environment by 2020. In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which occur in the world's largest fishing grounds for tuna. While today a small number of LSMPAs make up at least 80\% of the managed areas in the ocean \citep{toonen_2013}, very little is known about their human dimensions and implications for fisheries \citep{gray_2017}. Furthermore, most of the research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications. One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure and represent large opportunity costs \citep{smith_2003,smith_2010}.

The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas. Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area that produces approximately 50\% of the world's tuna. Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly refered to as the Parties to the Nauru Agreement (PNA). Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the PNA group in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}). The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries). Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}. The revenue from access fees may represent up to 50\% of government revenue for some of the members.

A spatial closure of such dimensions is likely to cause changes in spatial distribution and behavior of fishing vessels. For example, the anticipation of LSMPAs may lead to preemptive overfishing, which will likely erodes or delay the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}. After a spatial closure, users can exhibit idiosyncratic responses driven by different incentives \cite{cabral_2017}. Moreover, this reduction in total fishing area within one country's EEZ is likely to result in selling less fishing licenses. While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (i.e. Palau). We evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati. We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary. These are two of the largest protected areas on the planet and both are controled by PNA countries, where the largest tuna fisheries occur.

We use identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018. We continuously observe 92 vessels for the 2012 - 2018 period. Of these, 64 vessels fished within PIPA at least once prior to its implementation. The remaining 28 vessels never fished in PIPA waters. We refer to these groups as the treated and control groups. The group with the remaining 221 vessels contains vessels that were not observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.

\begin{figure}
\centering
\includegraphics{img/LSMPAs_map.pdf}
\caption{\label{fig:LSMPAs_map}Large Scale Marine Protected Areas. The map shows all areas larger than 30,000 Km\textsuperscript{2}. The Phoenix Islands Protected Area is shown in red.}
\end{figure}

\section{Results}\label{results}

\subsection{Crowding effect}

We first inspect the crowding effects that may arise due to the net reduction in fishing area. We produced 1-degree rasters of monthly fishing effort for our treatment and control groups, and calculated two indices of spatial overlap between them: 1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month. We find that the two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig. \ref{fig:sp_corr}). The number of cells with presence from both fleets and spatial correlations increase by a factor of four and three, respectively. This increase in crowding is likely to increase the encounter rates with other vessels, and reduce the efficiency of fishing operations. This might cause vessels to leave their current fishing grounds and re-optimize their spatial effort, leading to a subsequent decrease as the crowding measures return towards pre-implementation levels.

\begin{figure}[H]
\centering
\includegraphics{img/sp_corr.pdf}
\caption{\label{fig:sp_corr}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B). The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}}
\end{figure}

\subsection{Behavioral changes}

The behavioral responses that vessels can have to a spatial closure may occurr in different ways. For example, displacement to new fishing grounds may represent a cost as fishers search the ocean to identify the most suitable fishing spots. This may result in increased fuel and labor costs. For every vessel in each group, we calculate eight key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters and Kiribati waters (Fig. \ref{fig:all_panels}). We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for treated vessels after implementation of PIPA, relative to the trends observed for control vessels (see the Methods section for our empirical specification).

We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}). Treated vessels traveled less, with fishing events occurring closer to shore and closer to port following PIPA implementation. These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$). We do not observe a statistically significant increase in fishing hours on the high seas.

The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in Kiribati and PNA waters decreases suggests that these vessels have re-distributed elsewhere. This is consistent with the eventual decrease in crowding meassures.

\subsection{Economic impacts}

The crowding effect combined with the reduction of hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy access fees from PNA countries. To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by all PNA countries by each group of vessels (Fig. \ref{fig:all_PS_VDS_year}). In this case we look at all 313 vessels, but continue to group them as treated (n = 64) and control (n = 28) vessels, as well as other vessels (n = 221). We find that the treated vessels spent 2,310 less days in PNA waters when comparing their values for 2015 and 2016, while control and other vessels increased their activities in PNA waters by 5,489 and 4,447 days for the same period, respectively (Fig. \ref{fig:included_PS_VDS_year_DiD}). The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD at an average price of \$12,000 USD per vessel-day. Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig. \ref{fig:all_PS_VDS_cty_year}). Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allcoation to PNA waters at just 10,026 vessel-days. This is 2,526 vessel-days lower (\~\$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}). % Do you think we need to come up with an identification strategy for this?. I think a simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort, right? Current DiD estimate of these data suggests a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects. These values would represent forgone profits of 104 to 88 million USD. Again, this is if the treated vessels were allowed to maintain an upward sloping trend as observed with the control. I am also not sure if this trend is true, or just an artifact of GFW. Could we de-trend it first so that both lines are flat before, and only treated vessels show a decrease? In that setting we can then do a DiD and calculate the gap more accurately.

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_year.pdf}
	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all countries by treated, control, and excluded vessels.}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by group of vessels.}
\end{figure}

We compliment our analysis of change in observed vessel-days by looking at country-level data. Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig. \ref{fig:revenues}A). We find that by 2016, Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD. We then calculate total annual revenues to all PNA members (Fig. \ref{fig:revenues}B). To estimate what would have been the total revenue to PNA members, we use a local polynomial regression fit to obtain a trend line for the total revenues between 2008 and 2015, and extrapolate the trend to obtain an expected value for 2016. Our model suggests that total revenues to all PNA members in 2016 should be in the order of \$463.5 million USD, but the FFA data show only \$423.5 million, suggesting that potential losses to the entire PNA are in the order of \$40 million USD.

\begin{figure}
\centering
	\includegraphics{img/revenues.pdf}
	\caption{\label{fig:revenues}Financial indicators for PNA countries. A) Revenue from fishing licenses fees, B) Total annual revenues for all 9 PNA countries with dashed line showing the local polynomial regression fit to the 2008 - 2015 data and the red dot representing the prediction from this regression. Vertical dashed line in both plots denotes implementation of PIPA.}
\end{figure}

Catches for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig. \ref{fig:catches}). Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease). Similar decreases were observed for The Federal States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%). In contrast, Tokelau (due south of Kiribati) showed a 22.3\% increase in catches over the same period.

\subsection{Potential Revenue Loss for Palau}

On October 28, 2015, the President of Palau, H.E. Tommy E. Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act. Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world. The sanctuary will fully protect about 80 percent of the nation’s EEZ. To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020. This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs. There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS. However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers. comm.). In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}. Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers. comm.).

Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios. In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day). In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day). Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.  It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero. In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively. In all scenarios, all longline vessel day and export tax revenues are lost. Longline vessel day loss is calculated using an average value of \$200 for 10,500 days. Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).

\input{revenue_loss}

\section{Discussion}

Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort. We find a short-term crowding effect after the implementation of the protected area. Behavioral analysis shows that the implementation of PIPA had little effect on the total fishing effort exerted by purse seiners. This, combined with our analysis of crowding effects that eventually return to pre-implementation levels, suggests that vessels redistribute elsewhere. Our analysis suggests that vessels that fish elsewhere represent a loss in profits of around \$27.7 million USD to Kiribati. A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD. Here, we discuss the implications of our findings and possible shortcommings in our analyses.

Previous studies on protected areas around Pacific islands suggest that vessels move to distant places, which might be translated as increased costs \citep{stevenson_2013}. Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges of spatial closures, yielding greater catches over time \citep{murawski_2005}. But these vessel tracks do not cover the pre-reserve period, making it difficult to identify the contribution of spatial closures to the observed spatial distribution of fishing vessels. Recent work by \cite{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space. Our data, which is assembled in a similar way, allows us to make similar inferences about the unobserved change in aggregate fishing effort and its spatial redistribution.

A major shortcoming of our analysis is that we do not observe catches or revenues at he vessel level, which ultimately are the factors that guide the decision making process of profit-maximizing agents. Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact. An additional factor that we are yet to test is the change in non-fishing hours spent at sea. It is plausible that fishing hours remain constant, but vessels have to increase search time. Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch. Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours. However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.

A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in large losses to countries. We also show that spatial closures lead to short-term crowding effects, which causes vessels to redistribute to areas close by. Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere. While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable mechanisms that would compensate losses and incentivize marine conservation.

\section{Methods}

\subsection{Data}

Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels. These broadcast messages can be received by satellites and land-based antennas. GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer what type and location of fishing events \citep{kroodsma_2018}.

% Numbers in this paragraph to be updated
% Our analysis focuses on tuna purse seine vessels, the most important fishery for PNA countries. We identify a total of 186 purse seiners that fished in PNA waters at least once before 2015. Vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses, leaving us with 125 vessels. We identify 90 vessels that have fished inside PIPA at least once since 2012; 72 did so before the announcement of the closure (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}). From these, we only observe before and after data for 64 tuna purse seiners.
%On the other hand, 45 vessels never fished inside PIPA during the 2012 - 2015 period, but we only observe befor and after data for 28 of these.

Our treatment group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation. Vessels in the control group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28). Together, these vessels represent more than 20 million georeferenced positions for which we know activity (fishing or not fishing). We include three additional control groups as a robustness check. The first group excludes all Chinese vessels, the second group excludes all PNA vessels, and the third group excludes US and Taiwanese vessels. Our main definition of treatment and control groups leaves us with 64 treated and 28 control vessels, which have just over 36 million observations.

\subsection{Analyses}

\subsubsection{Crowding effect}

If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve. The implementation would lead to an increase in these measures, which,  if vessels avoid crowding, should then come back down. We therefore expect to have three inflection points: 1) in the transition between no trend and initial crowding due to MPA implementation, 2) When the crowding has reached its maximum and starts to decrease, and 3) when the decrease levels off, pressumably to pre-MPA levels. For this reason, we fit a 4th degree polynomial to our monthly indices. We do so by centering our time series of crowding indices on the day of implementation. Our explanatory variable is therefore the number of months ($M$) before or after the implementation. For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1, and Feb of 2015 would receive a value of 1.

\begin{figure}
\begin{align}
y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \epsilon_t
\label{eqn:sp_corr}
\end{align}
\end{figure}

\subsubsection{Behavioral changes}

We then focus on identifying the response of vessels to the PIPA closure. We use daily fishing and non-fishing hours, daily proportion of fishing vs. non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port(km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest. We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach. Our main specification is the following:

\begin{figure}[H]
\begin{align}
log(y)_{i,t} = \alpha + \beta_1 P_t + \beta_2 T_i + \beta_3 P_t \times T_i + \phi_t + \gamma_i + \epsilon_{i,t}
\label{eqn:did}
\end{align}
\end{figure}

Where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$. A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group. $\alpha$ is the standard intercept term, $beta_1$ captures the temporal trend, $beta_2$ captures the initial difference between treated and control groups, and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect. Finally, $phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions. We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.

All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated. All analyses were performed in R version 3.5.1 \citep{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.

\subsubsection{Revenues}

Information about FFA reports here

\section{References}

\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\onecolumn

\FloatBarrier

\section{Appendix}\label{appendix}

\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}

\section{Supplementary tables and figures}

\input{tab/main_DID}

\clearpage

\input{tab/sp_corr}

\clearpage

\begin{figure}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. Countries that belong to the PNA are shown in blue, while empty polygons indicates all others. A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{img/all_panels.pdf}
\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
\end{figure}

\clearpage

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:all_PS_VDS_cty_year}Observed vessel days by country and year}
\end{figure}

\clearpage

\begin{figure}
\centering
	\includegraphics{img/hist_kir_fishing.pdf}
	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
\end{figure}

\clearpage

\begin{figure}
\centering
	\includegraphics{img/catches.pdf}
	\caption{\label{fig:catches}Financial indicators for PNA countries. A) Annual catches by EEZ and, B) Annual value of catches by EEZ. Vertical dashed line in both plots denotes implementation of PIPA.}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{img/other_specifications.pdf}
\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
for our variables of interest using different model specifications. Table \ref{tab:main_DID}
reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
\end{figure}

\clearpage

\begin{figure}
\centering
\includegraphics{img/fishing_raster.png}
\caption{\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels. Color corresponds to \% of total fishing effort in each panel. Red polygons show LSMPAs in the region.}
\end{figure}

\clearpage

\section{Palau National Marine Sanctuary}\label{PNMS}

\begin{figure}
	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
	\caption{Map of the Four Protected Areas}
	\label{fig:maps}
\end{figure}

\clearpage

\section{Alternative Controls}
\subsection{Excluding all Chinese vessels}

\input{tab/DID_without_CHN.tex}

\clearpage
\subsection{Excluding all PNA vessels}

\input{tab/DID_without_PNA.tex}

\clearpage

\subsection{Excluding all USA and TWN vessels}

\input{tab/DID_without_USA_TWN}

\clearpage

\section{Additional methods}

This section is divided into two main parts. First, we provide a general description of AIS data and the process of identification of vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe the subset of data used in our analysis. We also point out possible shortcomings in the data, or factors that must be considered in the analysis. We then move on to explain our empirical strategy for the identification of behavioral changes and the redistribution of fishing effort.

\subsection{Data}

The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals. The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016. This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels. The addition of new satellites affects all vessels in the same way.

\input{tab/baci_n_s}

%\section{Old Text}

%\subsection{Large-Scale Marine Protected Areas}\label{lsmpas}
%
%The cutoff at which an MPA is considered to be a LSMPA ranges from areas
%larger than 30,000 km\textsuperscript{2} as defined by
%\cite{desanto_2013} or areas larger than 250,000 km\textsuperscript{2},
%as defined by \cite{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
%LSMPAs that meet the latter condition, and are also fully no-take. LSMPAs are often
%implemented in the pelagic environment, where the dominant human
%activity is industrial fishing \cite{gray_2017,kroodsma_2018}. The
%early literature on LSMPAs focused on the inherent challenges and
%difficulties that come with a pelagic environment. \cite{kaplan_2010}
%claimed that very large MPAs would result in excessive opportunity costs
%and that these would be difficult to enforce. \cite{game_2009}
%suggested that most of the challenges could be overcome with the
%incorporation of technology, in what then became known as Dynamic Ocean
%Management \citep{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.} 
%
%Spatial closures of this magnitude are likely to induce changes in
%fishers' behavior. Theoretical models of fishing effort redistribution
%range from the simplistic assumption that effort inside the bounded
%region disappears, to spatially explicit models that reallocate fishing
%effort based on habitat characteristics, presence of other vessels, and
%expected returns \citep{smith_2003,hilborn_2006}. However, these focus
%on the long term optimal equilibrium, and redistribution of fishing
%effort may not always be optimally distributed, especially over the first few years
%\citep{stevenson_2013}.
%
%The empirical research that has been done in smaller sized MPAs
%suggests that resource users may show idiosyncratic responses. For
%example, \cite{stevenson_2013} show that a network of MPAs displaced
%fishing effort farther away from ports, resulting in higher
%\emph{perceived} costs, and increases in catch per unit effort.
%\cite{cabral_2017} analyze the redistribution of fishing and
%non-fishing vessels following the implementation of a network of MPAs in
%California, and find that dive boats follow a
%fishing-the-line pattern, while some fishing boats follow an ideal free
%distribution. More recently \cite{elahi_2018} used satellite tracking
%data to show that a temporal spatial closure caused trawlers to maintain
%effort but apply it more intensively elsewhere, particularly along the
%borders and closer to shore. The way in which fishers react to a spatial
%closure can have major implications for its outcome
%\citep{smith_2003,hilborn_2006}, highlighting the need to understand how
%fishers react to the implementation of LSMPAs, how fishing effort
%changes, and how it is spatially redistributed. All these studies evaluate relatively small closures within Exclusive Economic Zones, where other regulations exist.
%This may not always be the case for LSMPAs, where often the entire EEZ
%is converted into a LSMPA, leaving fishers with the option of moving to
%the high seas or other countries' EEZs, with potentially very different fishing regulations.
%
%\subsection{Nauru agreement and the Phoenix Islands Protected Area}
%
%The cooperation that emerged under the Nauru Agreement allowed for subsequent
%agreements that strengthened fisheries management, like the Palau
%Agreement, which limited the number of purse seiners at 205 vessels from
%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is
%the approach to manage fishing effort: a Vessel Day Scheme (VDS)
%implemented in 2007 \citep{havice_2013}. This effectively modified how
%fishing effort was managed, from total number of vessels (under the Palau
%Agreement) to total vessel-days. 
%Under the purse seine VDS, a total number of annual vessel days for the entire fishery is agreed upon by the PNA parties. Each party’s allowable effort (PAE) is then calculated based on historic effort and biomass within each party’s EEZ. Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% of the PAE is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}. A minimum benchmark fee is set for purse seine vessel days which each party can transfer (\emph{i.e.} sell to another PNA member) or sell to the highest bidder (\emph{i.e.} sell to a fishing company). Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}. 
%Although detailed records on sales or transfers of vessel days are not publicly available \citep{havice_2013,yeeting2018stabilising}, a minimum benchmark fee of \$8,000/day was set from 2015 \citep{PNA2014a}.
%
%\cite{yeeting2018stabilising} summarize the PNA implementing arrangements as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \citep{PNA2016}. Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \citep{PNA2016}.  As described in the Palau Arrangement, fishing days by vessels shorter than 50m (longer than 80m) count as 0.5 (1.5) vessel days. Countries are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within their PAE. Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \citep{PNA2016}. There are some criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the program \citep{Arnason2014,yeeting2018stabilising}. While the effectiveness of this scheme has been
%debated in terms of meeting fishery management and conservation
%objectives, the licensing significantly contributes to the economy of
%these island nations \citep{havice_2010}.
%
%The main tuna species caught in the region are skipjack
%(\emph{Katsuwonus pelamis}), yellowfin (\emph{Thunnus albacares}),
%albacore (\emph{Thunnus alalunga}) and bigeye (\emph{Thunnus obesus}).
%From these, the first two are amongst the top-10 species represented in
%global fisheries production statistics, with 2016 catches increasing
%relative to the 2005-2014 average \citep{fao_2018}. This region of the
%Pacific has historically accounted for a large portion of tuna catches
%\cite{aqorau_1997}. Today, the PNA controls close to 50\% of global
%skipjack tuna production \cite{pna_website_2018} and the combined area of all EEZs involved is 14.6 million km\textsuperscript{2}, larger than the land mass of the United States of America. A large portion of global skipjack
%catch derives from purse seine vessels licensed under the VDS.
%Fishing vessels from Australia, New Zealand, China, France, Korea,
%Japan, the Philippines, Taiwan, and the United States participate in the
%purse-seining VDS.
%
%One of the most notable and recent management interventions in the
%region is the implementation of the Phoenix Islands Protected Area (PIPA)
%by the government of Kiribati. PIPA was first declared in 2006, and
%established in 2008 with only 4\% of the area declared as no-take. On
%January 1\textsuperscript{st}, 2015, the no-take area within PIPA was
%expanded to a total area of 397,447 km\textsuperscript{2}, roughly 1.5
%times the size of Ecuador. Figure \ref{fig:PNA_map} shows a map of the
%PNA countries (excluding Palau) and the Phoenix Islands Protected Area.
%
%The closure of such a large area in one of the most important fishing
%regions in the world provides a unique opportunity to evaluate the
%behavioral responses and redistribution of fishing effort by vessels
%that used to fish there. PIPA has been the focus of previous research
%showing that fishing effort is effectively reduced after implementation
%\citep{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
%How did individual vessels respond to the sudden exclusion of such a big
%area? Where did all the vessels go? And what does this imply for revenues from
%selling VDS for both Kiribati and the PNA as a whole? 
%
%A spatial closure might cause fishers to modify
%their behavior as they adapt to a new state of the world. For example, some may have
%to travel further distances to find new fishing grounds, increasing their fuel
%costs. If fishers had developed experience for fishing in particular
%sites, being excluded might impose a learning cost on them, as they
%identify new fishing grounds. This might result in increased search
%times. However, if the area of knowledge of a vessel is significantly
%larger than that of the spatial closure, they might already know other
%places to fish. In the next sections we describe
%the data and methods used to answer these questions.
%
%\subsection{Palau}
%
%\subsubsection{Palau National Monument}

%On October 28, 2015, the President of Palau, H.E. Tommy E. Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act. Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world. The sanctuary will fully protect about 80 percent of the nation’s EEZ. The remaining 20\% of Palau’s EEZ (close to the most heavily populated islands: Koror and Babeldaob) will become a Domestic Fishing Zone in which traditional and domestic fishing activities will be allowed to provide fish solely for the domestic market (\emph{i.e.} exports of pelagic fish will be prohibited). Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery. In this section, we use our preceding analysis on the ex-post impacts of PIPA to attempt to make some \emph{ex ante} predictions about the potential impacts of PNMS. We start by giving some background on the fishing that is currently taking place inside the future PNMS.

%\subsubsection{Background on Commercial Fishing in Palau}

%Foreign tuna fishing in Palau’s EEZ began before WWI. Pole and line was the initial gear used to target skipjack tuna by Japanese vessels. Foreign fishing activities stopped during WWII and started again in the 1960s when Japanese fishers returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans. The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna developed during the same time. During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna. During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}. There are currently three transshipment companies operating in Palau.

%Purse seine vessels target schools of skipjack tuna that are then canned. Compared to other EEZs in the Pacific, especially the PNA EEZs, Palau’s EEZ is not known to be a preferred fishing ground for purse seining (Sisior, pers. comm.). This can be seen in Figure \ref{fig:VDS_country_year}. Currently all purse seine boats fishing in Palau’s EEZ are Japanese and they do not land their catch in Palau (Table \ref{tab:palau_purse}).

\input{palau_purse}

%All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}). Japanese longline vessels do not land their catch in Palau. Locally-based, foreign-owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI) and Kuniyoshi Fishing Company (KFC)). Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan upon landing in Koror (the largest town in and former capital of Palau). Most of the discards are either sold or donated in Palau. A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.

\input{palau_long}

%\subsubsection{Access fees and taxes}
%
%An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch. Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \citep{Tewid2013}. Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}. Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
% 
%There used to be a number of agreements between the Republic of Palau and foreign owned, local based companies, in particular PITI and KFC, to allow longline fishing \cite{Tewid2013}. Vessels under these agreements were internationally-owned, locally-based vessels that paid for annual licenses based on the size of each vessel. These are the vessels shown in Table \ref{tab:palau_long} (excluding the Japanese vessels). So, for example, there were 38 vessels as part of these agreements in 2016. Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \citep{Gillett2016}. These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
%
%There are two multilateral treaties that grant preferential access to Palau waters to US and Federated States of Micronesia (FSM) flagged purse seine boats: the US Multilateral Tuna Treaty and the Federated States of Micronesia Arrangement.  The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees. Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds. These agreements have been described by some commentators as foreign aid, with little connection to underlying fish stocks \cite{Gillett2016}. 
%
%The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \citep{Gillett2016}. 
%Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery. Between 80 to 90 people are employed by offshore fisheries, and of these only around 20\% are Palauans, earning wages that are only 50\% of average wages in Palau \cite{Gillett2016}.
%
%\subsubsection{Parties to the Nauru Agreement and the Vessel Day Scheme}
%
%In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism. Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers. comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}). Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ. The remainder of Palau’s purse seine vessel days are sold for between \$9-10,000 each. When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ). Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \citep{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \citep{Pojas2018}. In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers. comm.). 
%
%The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing it at the country-scale. Palau was the first party to implement the VDS for longline fishing in 2017. In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers. comm.). Since 2016, the number of allowed longline VDs has been a fraction of the 2014 days, reducing each year as stipulated in the PNMS Act. Palau sells its LL VD for \$150-\$250 (Sisior pers. comm.). Because the LL VDS is still new and has yet to be fully implemented by all parties, LL VD are not currently transferable between PNA member EEZs. 
%
%\subsubsection{Plans for a domestic pelagic fishery}
%
%In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch \cite{Gillett2016}. The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers. comm.). Otherwise, there are no domestic vessels dedicated to full-time offshore fishing. A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes. 
%Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing. There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.

\end{document}

### 2019-03-01 docs/tab/main_DID.tex
Updated fig 5 to include reported vs observed

@@
 \hline \\[-1.8ex] 
- Constant & 0.497$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 5.203$^{***}$ & 12.997$^{***}$ & 12.461$^{***}$ & 3.678$^{***}$ & 4.445$^{***}$ & 2.420$^{***}$ \\ 
-  & (0.022) & (0.012) & (0.004) & (0.029) & (0.021) & (0.019) & (0.192) & (0.151) & (0.421) \\ 
+ Constant & 0.497$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 5.206$^{***}$ & 12.997$^{***}$ & 12.461$^{***}$ & 3.678$^{***}$ & 4.445$^{***}$ & 2.420$^{***}$ \\ 
+  & (0.022) & (0.012) & (0.004) & (0.028) & (0.021) & (0.019) & (0.192) & (0.151) & (0.421) \\ 
   & & & & & & & & & \\ 
- Post & 0.839$^{***}$ & $-$0.228$^{***}$ & 0.137$^{***}$ & 0.304$^{***}$ & 0.326$^{***}$ & 0.296$^{***}$ & 1.059$^{***}$ & 1.180$^{***}$ & 0.920$^{***}$ \\ 
-  & (0.016) & (0.008) & (0.003) & (0.019) & (0.014) & (0.014) & (0.140) & (0.109) & (0.273) \\ 
+ Post & 0.839$^{***}$ & $-$0.228$^{***}$ & 0.137$^{***}$ & 0.298$^{***}$ & 0.326$^{***}$ & 0.296$^{***}$ & 1.059$^{***}$ & 1.180$^{***}$ & 0.920$^{***}$ \\ 
+  & (0.016) & (0.008) & (0.003) & (0.018) & (0.014) & (0.014) & (0.140) & (0.109) & (0.273) \\ 
   & & & & & & & & & \\ 
- Treated & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.400$^{***}$ & 0.223$^{***}$ & 0.116$^{***}$ & 0.534$^{***}$ & 0.149 & $-$0.244 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.020) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
+ Treated & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.413$^{***}$ & 0.223$^{***}$ & 0.116$^{***}$ & 0.534$^{***}$ & 0.149 & $-$0.244 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.019) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
   & & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.244$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.483$^{***}$ & $-$0.281$^{***}$ & $-$0.155$^{***}$ & $-$0.565$^{***}$ & $-$0.399$^{***}$ & 0.338 \\ 
+ Post $\times$ Treated & $-$0.244$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.513$^{***}$ & $-$0.281$^{***}$ & $-$0.155$^{***}$ & $-$0.565$^{***}$ & $-$0.399$^{***}$ & 0.338 \\ 
   & (0.019) & (0.009) & (0.003) & (0.022) & (0.017) & (0.017) & (0.161) & (0.127) & (0.288) \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 83,052 & 83,052 & 83,051 & 64,387 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
-R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.028 & 0.062 & 0.080 & 0.113 & 0.198 & 0.233 \\ 
+Observations & 83,052 & 83,052 & 83,051 & 66,981 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
+R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.027 & 0.062 & 0.080 & 0.113 & 0.198 & 0.233 \\ 
 \hline 

### 2019-03-01 scripts/content/fig_all_panels.R

@@ -73,7 +73,7 @@ distance_traveled <- readRDS(file = here("data",
                                                 "daily_distance_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
          gear == "tuna_purse_seines",
-         !mmsi %in% c(416242900, 440575000, 367463000)) %>% #Need to figure out why these three vessels are outliers. I think it's because they jump between 0 and 360
+         dist < quantile(dist, probs = 0.95)) %>% 
   mutate(date = lubridate::date(paste(year, month, 15, sep = "/")),
          treated = ifelse(treated, "Treated", "Control")) %>%
   varplot(dist, "dist (km)")

### 2019-03-01 scripts/content/vessel_model_fitting.R

@@ -78,7 +78,7 @@ distance_traveled <- readRDS(file = here("data",
                                                "daily_distance_by_vessel_panel.rds")) %>% 
   filter(year < 2019,
          gear == "tuna_purse_seines",
-         !mmsi %in% c(416242900, 440575000, 367463000)) %>%  #Need to figure out this vessels here and in the fig_all_panels script
+         dist < quantile(dist, probs = 0.99)) %>%  #Need to figure out this vessels here and in the fig_all_panels script
   model_data_prep(dist)
 
 # Fit the models

### 2019-03-01 scripts/processing/vessel_tracks_panel.R

@@ -152,6 +152,7 @@ dist_fxn <- function(data){
 
 # Group at the date-mmsi level
 daily_distance_by_vessel_panel <- vessel_tracks_baci %>%
+  filter(mmsi %in% c(416242900, 440575000, 367463000)) %>% 
   group_by(year,
            quarter,
            month,

### 2019-03-03 docs/tab/main_DID.tex
Updated tables in docs folder and panel of daily distance traveled

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our nine variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+Numbers in parentheses are heteroskedasticity-robust standard errors.}
   \label{} 

### 2019-03-03 docs/tab/sp_corr.tex
Updated tables in docs folder and panel of daily distance traveled

@@
 \begin{table}[!htbp] \centering 
-  \caption{\label{tab:sp_corr}Coefficient estimates for a third-polinomial fit to the measures of crowding.
+  \caption{\label{tab:sp_corr}Coefficient estimates for a fourth polynomial fit to the measures of crowding.
 The first column shows coefficients for the number of cells with treated and control vessels during the same month.
 The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels.
-The explanatory variable is the number of months before implementation of PIPA.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
+The explanatory variable is the number of months since implementation of PIPA.
+Numbers in parentheses are heteroskedasticity-robust standard errors.}
   \label{} 

### 2019-03-04 docs/PIPA_Palau030319.tex
Updated MS

--- 2019-03-01 docs/PIPA_Palau022819.tex
@@
 \usepackage{placeins}
+\usepackage{comment}
 
@@
 \author[b]{John Lynham}
+\author[a]{Christopher Costello}
 
@@
 % Please add here a significance statement to explain the relevance of your work
-\significancestatement{The oceans are becoming increasingly crowded, with different activities competing for space, but little research has been done to understand how activities displace each other.
-Marine Protected Areas are inherently spatial and have the sole objective of conserving bounded waters through the displacement of fishing effort.
-Our work shows that displacement of fishing effort occurs, but that it comes at a cost to countries that would have otherwise been able to charge a price for vessels to fish in the now-protected areas.
+\significancestatement{The oceans are becoming increasingly crowded, with different activities competing for space.
+Marine Protected Areas are inherently spatial, and have the sole objective of conserving bounded waters by displacing or limiting fishing effort.
+Our work shows that when a fishery is managed by limiting effort (\emph{e.g.} with a Vessel-Day Scheme), spatial closures displace fishing effort at a high cost to the implementing country, and that the benefits are perceived by other countries.
 With global conservation targets seeking to protect 10\% of the world’s ocean by 2020 and the expansion of offshore aquaculture, it is important that the spatial displacement of economic activities is fully considered.}
@@
 In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold.
-However, from 2016 onwards there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue.
+However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue.
 At the same time, fishing effort increases in other parts of the PNA.
@@
 Global international goals aim to protect 10\% of the ocean environment by 2020.
-In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which occur in the world's largest fishing grounds for tuna.
-While today a small number of LSMPAs make up at least 80\% of the managed areas in the ocean \citep{toonen_2013}, very little is known about their human dimensions and implications for fisheries \citep{gray_2017}.
-Furthermore, most of the research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
+In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs; areas larger than 30,000 km\textsuperscript{2} \emph{sensu} \cite{desanto_2013}).
+Today, a small number of LSMPAs represent at least 80\% of the managed areas in the ocean (Fig.
+\ref{fig:LSMPAs_map}; \citep{toonen_2013}).
+However, very little is known about their human dimensions and implications for fisheries \citep{gray_2017}.
+Furthermore, most research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
 One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure and represent large opportunity costs \citep{smith_2003,smith_2010}.
 
-The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas.
-Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area that produces approximately 50\% of the world's tuna.
-Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly refered to as the Parties to the Nauru Agreement (PNA).
-Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the PNA group in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
-The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
-Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}.
-The revenue from access fees may represent up to 50\% of government revenue for some of the members.
-
-A spatial closure of such dimensions is likely to cause changes in spatial distribution and behavior of fishing vessels.
-For example, the anticipation of LSMPAs may lead to preemptive overfishing, which will likely erodes or delay the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}.
-After a spatial closure, users can exhibit idiosyncratic responses driven by different incentives \cite{cabral_2017}.
-Moreover, this reduction in total fishing area within one country's EEZ is likely to result in selling less fishing licenses.
-While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (i.e.
-Palau).
-We evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati.
-We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are controled by PNA countries, where the largest tuna fisheries occur.
-
-We use identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018.
-We continuously observe 92 vessels for the 2012 - 2018 period.
-Of these, 64 vessels fished within PIPA at least once prior to its implementation.
-The remaining 28 vessels never fished in PIPA waters.
-We refer to these groups as the treated and control groups.
-The group with the remaining 221 vessels contains vessels that were not observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
-
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 
+The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas.
+Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area where approximately 50\% of the world's tuna is caught.
+Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA).
+Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the PNA group in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
+The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
+Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}.
+The vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016.
+The revenue from access fees may represent up to 50\% of government revenue for some of the members.
+
+A spatial closure the size of PIPA is likely to cause changes in spatial distribution and behavior of fishing vessels.
+For example, the anticipation of LSMPAs may lead to preemptive overfishing, which likely erodes or delays the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}.
+Under a VDS, a reduction in total fishing area within one country's EEZ will result in a reduction in license revenues to said country.
+However, the benefits of the spatial closure are dispersed amongst all other PNA members (through fish movement), who in turn benefit from the conservation efforts of the initial country.
+While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (\emph{i.e.} Palau).
+
+We simulate the PNA fishery with the addition of spatial closures to characterize possible outcomes of such interventions.
+We then empirically evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati.
+We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
+These are two of the largest protected areas on the planet and both are controlled by PNA countries, where the largest tuna fisheries occur.
+
+Our empirical portion uses identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018.
+We continuously observe 92 vessels for the 2012 - 2018 period.
+Of these, 64 vessels fished within PIPA at least once prior to its implementation, and refer to them as the ``displaced vessels''.
+The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
+The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/PNA_model.pdf}
+\caption{\label{fig:PNA_model}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}}
+\end{figure}
+
 \section{Results}\label{results}
+
+\subsection{PNA model with conservation}
+
+We simulate the PNA as a ten-patch meta-population system with discrete time, where Patch 1 considers the implementation of a spatial closure.
+Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
+The stock remains within a Patch during the season, but escapement (\emph{i.e.} stock minus catches) is distributed between all countries at the end of each year.
+A detailed explanation of the model is presented in the Methods section.
+We find that a spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock to moves freely between the protected and non-protected portion of the Patch.
+The loss in revenue increases with reserve size, but decreases as within-patch movement increases (Fig.
+\ref{fig:PNA_model}A).
+For all other PNA countries, however, a spatial closure in Patch 1 results beneficial, especially as within-patch movement decreases and reserve size increase (Fig.
+\ref{fig:PNA_model}B).
+The inverse effects of the spatial closure on Kiribati and the other PNA countries are driven by the redistribution of escapement.
+The stock not fished in the protected portion of Patch 1 eventually redistribute to the other patches, which increases stock size and causes vessel-day prices to increase.
+This model shows that the costs of conservation are incurred by Patch 1, but the benefits are perceived by the other eight patches.
+Moreover, the gains in revenue for other PNA countries does not compensate for the total losses to Kiribati, as a great portion of effort is redistributed to the High Seas.
 
@@
 We first inspect the crowding effects that may arise due to the net reduction in fishing area.
-We produced 1-degree rasters of monthly fishing effort for our treatment and control groups, and calculated two indices of spatial overlap between them: 1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.
+We produced 1-degree rasters of monthly fishing effort for our displaced and non-displaced vessels, and calculated two indices of spatial overlap between them: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month.
 We find that the two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
 \ref{fig:sp_corr}).
-The number of cells with presence from both fleets and spatial correlations increase by a factor of four and three, respectively.
+The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively.
 This increase in crowding is likely to increase the encounter rates with other vessels, and reduce the efficiency of fishing operations.
@@
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
@@
 
-The behavioral responses that vessels can have to a spatial closure may occurr in different ways.
+The behavioral responses that vessels can have to a spatial closure may occur in different ways.
 For example, displacement to new fishing grounds may represent a cost as fishers search the ocean to identify the most suitable fishing spots.
@@
 
-We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled less, with fishing events occurring closer to shore and closer to port following PIPA implementation.
+We find no evidence of treated vessels fishing for more hours after PIPA implementation, and in fact observe a negative effect (24.4\% decrease; $p < 0.01$; Table \ref{tab:main_DID}) relative to the non-displaced vessels.
+Likewise, we observe a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
+Treated vessels traveled less distance, with fishing events occurring closer to shore and closer to port following PIPA implementation.
 These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$).
 We do not observe a statistically significant increase in fishing hours on the high seas.
-
-The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in Kiribati and PNA waters decreases suggests that these vessels have re-distributed elsewhere.
-This is consistent with the eventual decrease in crowding meassures.
+This suggests that treated vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters.
+In summary, vessels that used to fish in PIPA are now fishing less in both Kiribati and the PNA region.
+Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters.
 
@@
 
-The crowding effect combined with the reduction of hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy access fees from PNA countries.
-To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by all PNA countries by each group of vessels (Fig.
-\ref{fig:all_PS_VDS_year}).
-In this case we look at all 313 vessels, but continue to group them as treated (n = 64) and control (n = 28) vessels, as well as other vessels (n = 221).
-We find that the treated vessels spent 2,310 less days in PNA waters when comparing their values for 2015 and 2016, while control and other vessels increased their activities in PNA waters by 5,489 and 4,447 days for the same period, respectively (Fig.
-\ref{fig:included_PS_VDS_year_DiD}).
-The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD at an average price of \$12,000 USD per vessel-day.
-Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
+The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they buy less vessel-days from PNA countries.
+To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by Kiribati and all PNA countries by each group of vessels (Fig.
+\ref{fig:all_PS_VDS_year}), and convert these to license revenues using a conservative vessel-day price of \$9,000 USD\footnote{The Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report states that ``Days are currently [2016] selling in a range between \$9,000 and \$13,000 USD.''}.
+We look at all 313 vessels to obtain a more accurate representation of total revenues, but continue to group vessels as displaced (n = 64), non-displaced (n = 28), and other vessels (n = 221).
+We find that between 2015 and 2016, displaced vessels spent 3,916 and 2,249 less vessel-days in Kiribati and PNA waters, respectively (Figs.
+\ref{fig:all_PS_VDS_year}-\ref{fig:included_PS_VDS_year_DiD}).
+Over the same period, non-displaced and other vessels spent 1,278 less days in Kiribati, but spent 9,853 more days in PNA waters overall.
+These changes result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} to the other 8 countries).
+The net reduction of vessel-days in Kiribati represents a loss of \$46.7 million USD, while the net gain at the PNA-level results in \$68 million USD in increased revenues.
+Moreover, annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018 (Fig.
+\ref{fig:all_PS_VDS_KIR_year}).
+This trend is mainly caused displaced vessels allocating less time to Kiribati (\ref{fig:hist_kir_fishing}).
+Looking at the total annual vessel-days allocated by all vessels to all countries, we see that the largest reductions occur for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
 \ref{fig:all_PS_VDS_cty_year}).
-Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allcoation to PNA waters at just 10,026 vessel-days.
-This is 2,526 vessel-days lower (\~\$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
-% Do you think we need to come up with an identification strategy for this?.
-I think a simple DID doesn't work, because the post-trend would assume that there is no upper bound to effort, right?
-Current DiD estimate of these data suggests a 8,700 vessel-days reduction; or 7,400 vessel-days if we account for the blue paradox with some fixed effects.
-These values would represent forgone profits of 104 to 88 million USD.
-Again, this is if the treated vessels were allowed to maintain an upward sloping trend as observed with the control.
-I am also not sure if this trend is true, or just an artifact of GFW.
-Could we de-trend it first so that both lines are flat before, and only treated vessels show a decrease?
-In that setting we can then do a DiD and calculate the gap more accurately.
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
 	\includegraphics{img/all_PS_VDS_year.pdf}
-	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all countries by treated, control, and excluded vessels.}
+	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by treated, control, and excluded vessels.}
 \end{figure}
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
 	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
-	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by group of vessels.}
+	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.
+The large increase for Kiribati in 2014 is likely explained by the blue paradox \cite{mcdermott_2018}}
 \end{figure}
 
-We compliment our analysis of change in observed vessel-days by looking at country-level data.
+We complement our analysis of change in observed vessel-days by looking at country-level data.
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig.
 \ref{fig:revenues}A).
-We find that by 2016, Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD.
-We then calculate total annual revenues to all PNA members (Fig.
-\ref{fig:revenues}B).
-To estimate what would have been the total revenue to PNA members, we use a local polynomial regression fit to obtain a trend line for the total revenues between 2008 and 2015, and extrapolate the trend to obtain an expected value for 2016.
-Our model suggests that total revenues to all PNA members in 2016 should be in the order of \$463.5 million USD, but the FFA data show only \$423.5 million, suggesting that potential losses to the entire PNA are in the order of \$40 million USD.
+We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD.
+However, total PNA revenues showed a net increase of \$28 million USD (Fig.
+\ref{fig:total_PNA_revenues}).
+The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
 	\includegraphics{img/revenues.pdf}
-	\caption{\label{fig:revenues}Financial indicators for PNA countries.
-A) Revenue from fishing licenses fees, B) Total annual revenues for all 9 PNA countries with dashed line showing the local polynomial regression fit to the 2008 - 2015 data and the red dot representing the prediction from this regression.
-Vertical dashed line in both plots denotes implementation of PIPA.}
+	\caption{\label{fig:revenues}
+		License revenue for PNA countries.
+A) Annual revenue from fishing license fees by country and year (2008 - 2016) B) $log_{10}$-transformed FFA-reported revenues vs.
+the revenues inferred from vessel activity observations (2012 - 2016).
+The dashed line represents line of best fit, solid line represents 1:1 line.
+The same graph using absolute values is shown in \ref{fig:revenue_FFA_GFW_linear}.}
 \end{figure}
 
-Catches for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
+Catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
 \ref{fig:catches}).
 Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federal States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of Kiribati) showed a 22.3\% increase in catches over the same period.
+Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
+In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in catch over the same period.
 
@@
 
-On October 28, 2015, the President of Palau, H.E.
-Tommy E.
-Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
+On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
 Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
-The sanctuary will fully protect about 80 percent of the nation’s EEZ.
-To prepare for full enactment of the PNMS, the act stipulates a “winding down” period, in which baseline vessel days (i.e., the number of vessel days used in 2014) were reduced by 20\% in 2016; and an additional 10\% from baseline in each subsequent year until full enactment in 2020.
-This appears to be occurring for the longline VDS, but it is uncertain whether this is being followed for the purse seine VDS, because purse seine VDS can be transferred for use in other EEZs.
-There has been no official statement on what will happen to Palau’s VDS upon full implementation of the PNMS.
-However, there is a sense that Palau will be able to keep its allotment come 2020 (Hanich, pers.
-comm.).
-In the 2015 Micronesian Presidents Summit, a letter was drafted by heads of state, calling on PNA members to be supportive of Palau as they moved forward with the PNMS Act \cite{Senase2015}.
-Further, other PNA members have not been penalized for other protected area closures (e.g., PIPA) (Hanich, pers.
-comm.).
-
+The sanctuary will fully protect about 80 percent of Palau’s EEZ.
 Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the US for (\$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other parties at the current benchmark price (\$8,000/day).
-Scenario 2 is likely if Palau retains its current PAE, but the US no longer purchases days.
-It should be noted that if PAE continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its PAE will decrease as effort in its EEZ reaches zero.
-In Scenario 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel day and export tax revenues are lost.
-Longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
-Export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the United States for under the South Pacific Tuna Treaty a.k.a.
+Multilateral Treaty on Fisheries (\$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other PNA countries at the current benchmark price (\$8,000/day).
+Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days.
+It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as effort in its EEZ reaches zero.
+In Scenarios 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel day and export tax revenues are lost,
+since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
+The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
+The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
 
@@
 
-Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
-We find a short-term crowding effect after the implementation of the protected area.
-Behavioral analysis shows that the implementation of PIPA had little effect on the total fishing effort exerted by purse seiners.
-This, combined with our analysis of crowding effects that eventually return to pre-implementation levels, suggests that vessels redistribute elsewhere.
-Our analysis suggests that vessels that fish elsewhere represent a loss in profits of around \$27.7 million USD to Kiribati.
+Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior.
+Our simulation predicts losses in revenue to countries that implement a spatial closure, increases in revenue to other countries, and an increased fishing of the high seas.
+Using vessel track data, we observe a crowding effect after the implementation of the protected area, as displaced vessels redistribute spatially.
+Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners.
+But there is considerable redistribution of effort across space and within the fleet of purse seiners.
+Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
+Our analysis suggests that the displacement of vessels results in losses to Kiribati.
 A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD.
-Here, we discuss the implications of our findings and possible shortcommings in our analyses.
+Here, we discuss the implications of our findings and possible shortcomings in our analysis.
 
@@
 
-A major shortcoming of our analysis is that we do not observe catches or revenues at he vessel level, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
+Our analysis of vessel-days from vessel tracks and loss of profits to Kiribati suggests losses of \$46.7 million USD, while revenue data show a decrease in only \$30 million USD.
+Here, we provide some plausible explanations for these discrepancies.
+First, it is possible that as waters in Kiribati became more crowded, the price of vessel-days decreased significantly bellow the \$9,000 USD estimate that we use.
+This woudl imply that vessel-day prices fell to \$5,800 in Kiribati.
+This is a number similar to what our simulation estimates provide for a closure similar to PIPA (\emph{i.e.} $R = 0.11$), which range from \$5,250 to \$6,134, depending on the movement of fish.
+Another possible explanation is that the dataset used incorrectly labeled vessels as purse seiners.
+However, the scoring algorithm has a high accuracy, and accuracy increases with the number of observations for a vessel.
+Moreover, on any given year, 90\% of total fishing activity can be explained by at least 68\% of the vessels.
+Therefore, if there are any mislabeled vessels in our data, these would contribute little to the large trends that we observe.
+Finally, vessels fishing within PNA waters can report their activity as transiting to port or solving mechanical issues; this time does not count towards a vessel's usage of days (forgot the reference).
+These explanations are not mutually exclusive, and a combination of them could certainly explain the discrepancy.
+While the magnitude is not the same, the trends and patterns through time are certainly similar.
+
+A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately are the factors that guide the decision-making process of profit-maximizing agents.
 Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
-An additional factor that we are yet to test is the change in non-fishing hours spent at sea.
-It is plausible that fishing hours remain constant, but vessels have to increase search time.
-Upon being relocated, fishers may not identify the best fishing grounds as easily as before, and therefore invest a greater proportion of their time searching for their catch.
-Further analysis of temporal trends in non-fishing hours, as well as distance traveled should provide us with insights as to why fishers reduced fishing hours.
-However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.
+Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or prices.
+Furthernore, our estimates of revenue loss for PIPA do not account for the allocation calculated each year.
+Each party’s allowable effort is calculated based on historic effort and biomass within each party’s EEZ.
+Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
 
 A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in large losses to countries.
-We also show that spatial closures lead to short-term crowding effects, which causes vessels to redistribute to areas close by.
-Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere.
-While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable mechanisms that would compensate losses and incentivize marine conservation.
+Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in losses to countries that have been receiving revenue from granting fishing access.
+We also show that spatial closures lead to crowding effects, which causes some vessels to redistribute to areas close by.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompanied with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable financing mechanisms that would compensate losses and incentivize marine conservation.
+
+\begin{scriptsize}
 
 \section{Methods}
+
+\subsection{PNA Model with Conservation}
+
+We model the PNA as a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
+Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
+The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
+The price of fish is $p$, and catchability is given by $q$.
+
+In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
+The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1]$).
+Fish move within a patch based on $\theta$, where $\theta = 0$ implies to movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed over during the fishing season.
+In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$.
+The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
+
+\begin{figure}[H]	
+	\begin{align}
+	\Pi_1(E_1,X_1,R) = pqE_1X_1(\theta + (1 - \theta)(1 - R))-cE_1^\beta
+	\end{align}
+\end{figure}
+
+And profits from fishing in Patch $j = \{2, 3, ..., 10\}$ are:
+
+\begin{figure}[H]	
+	\begin{align}
+	\Pi_j(E_j,X_j) = pqE_jX_j-cE_1^\beta
+	\end{align}
+\end{figure}
+
+The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
+
+\begin{figure}[H]	
+	\begin{align}
+	\pi_1(E_1) = pqX_1(\theta + (1 - \theta)(1 - R)) - \beta cE_1^{\beta-1}
+	\label{eqn:marginal_profit_1}
+	\\
+	\pi_j(E_j) = pqX_j - \beta cE_j^{\beta-1}
+	\label{eqn:marginal_profit_j}
+	\end{align}
+\end{figure}
+
+However, Patch 10 represents the high seas under open access dynamics.
+Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi E_{10} = 0$.
+Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:
+
+\begin{figure}[H]	
+	\begin{align}
+	E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
+	\label{eqn:effort_hs}
+	\end{align}
+\end{figure}
+
+The patch-level harvest is then determined by effort and stock size:
+
+\begin{figure}[H]	
+	\begin{align}
+	H_1 = qE_1X_1 (\theta + (1 - \theta)(1 - R))
+	\label{eqn:harvest_1}
+	\\
+	H_j = qE_jX_j
+	\label{eqn:harvest_j}
+	\end{align}
+\end{figure}
+
+Therefore, escapement in patch $i$ is the difference between initial stock size and harvests as $e_{it} = X{it} - H_{it}$. At the entire stock then grows according to:
+
+\begin{figure}[H]	
+	\begin{align}
+	X_{t+1} = e_t + \frac{(\phi + 1)}{\phi}ge_t\left(1 - \left(\frac{e_t}{K}\right) ^{\phi}\right)
+	\label{eqn:grow}
+	\end{align}
+\end{figure}
+
+After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
+
+\begin{figure}[H]	
+	\begin{align}
+	X_{it+1} = f_iX_{t+1}
+	\label{eqn:disperse}
+	\end{align}
+\end{figure}
+
+The vessel-day price that a country charges is given by $\pi_i$ from Equations \ref{eqn:marginal_profit_1} and \ref{eqn:marginal_profit_j}. Therefore, patch-level license revenues are given by:
+
+\begin{figure}[H]	
+	\begin{align}
+	\omega = \pi_iE_i
+	\label{eqn:license_revenue}
+	\end{align}
+\end{figure}
+
+Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}).
+This would cause for the stock in the high seas ($X_{10}$) to increase through the redistribution (Equation \ref{eqn:disperse}), leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}).
 
@@
 These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer what type and location of fishing events \citep{kroodsma_2018}.
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \citep{kroodsma_2018}.
 
-% Numbers in this paragraph to be updated
-% Our analysis focuses on tuna purse seine vessels, the most important fishery for PNA countries.
-We identify a total of 186 purse seiners that fished in PNA waters at least once before 2015.
-Vessels that entered the fishery after 2015 were not exposed to the policy intervention in the pre-treatment period and are therefore excluded from our analyses, leaving us with 125 vessels.
-We identify 90 vessels that have fished inside PIPA at least once since 2012; 72 did so before the announcement of the closure (\emph{i.e.} 09/01/2014 \emph{sensu} \citep{mcdermott_2018}).
-From these, we only observe before and after data for 64 tuna purse seiners.
-%On the other hand, 45 vessels never fished inside PIPA during the 2012 - 2015 period, but we only observe befor and after data for 28 of these.
+The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
+The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
+This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
+The addition of new satellites affects all vessels in the same way.
 
@@
 
-\subsection{Analyses}
+\subsection{Analysis}
 
@@
 
-If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve.
-The implementation would lead to an increase in these measures, which,  if vessels avoid crowding, should then come back down.
-We therefore expect to have three inflection points: 1) in the transition between no trend and initial crowding due to MPA implementation, 2) When the crowding has reached its maximum and starts to decrease, and 3) when the decrease levels off, pressumably to pre-MPA levels.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1, and Feb of 2015 would receive a value of 1.
-
-\begin{figure}
+\begin{figure}[H]
 	\begin{align}
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \epsilon_t
+	y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \epsilon_t
 	\label{eqn:sp_corr}
@@
 
+We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
+1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and star  ts to decrease, and 3) when this decrease potentially levels off.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
+Note that we restrict the sample to our treated and control vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which incorporated in April 1st, 2014 and December 31st, 2015.
+
 \subsubsection{Behavioral changes}
 
-We then focus on identifying the response of vessels to the PIPA closure.
+We attempt to identify the response of vessels to the PIPA closure.
 We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port(km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
 We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
+
 Our main specification is the following:
@@
 
-Where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
+\noindent where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
 A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
 $Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group.
-$\alpha$ is the standard intercept term, $beta_1$ captures the temporal trend, $beta_2$ captures the initial difference between treated and control groups, and $beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
-Finally, $phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
+$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between treated and control groups, and $\beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
+Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
+
+\begin{comment}
 We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
+\end{comment}
 
@@
 
-Information about FFA reports here
+We obtained information on license fee revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
+For countries in the PNA, we assume that all license fee revenue is coming from the sale of VDS.
+
+\end{scriptsize}
 
@@
 
-\input{tab/main_DID}
-
-\clearpage
-
 \input{tab/sp_corr}
 
-\clearpage
+\input{tab/main_DID}
 
@@
 Countries that belong to the PNA are shown in blue, while empty polygons indicates all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.}
+A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.
+Land masses are shown in gray.}
 \end{figure}
-
-\clearpage
 
@@
 \includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
+\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
+Dashed vertical lines indicate the addition of new AIS satellites.
+Solid vertical line indicates the closure of PIPA.}
 \end{figure}
 
-\clearpage
+\begin{figure}
+\centering
+\includegraphics{img/all_PS_VDS_KIR_year.pdf}
+\caption{\label{fig:all_PS_VDS_KIR_year}Annual vessel-days in Kiribati by group of vessels.}
+\end{figure}
 
@@
 	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Observed vessel days by country and year}
+	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
 \end{figure}
 
-\clearpage
+\begin{figure}
+\centering
+	\includegraphics{img/revenue_FFA_GFW_linear.pdf}
+	\caption{\label{fig:revenue_FFA_GFW_linear}Inferred revenues vs. reported revenues. The dashed line represents line of best fit, and the solid line represents a 1:1 line.}
+\end{figure}
 
@@
 
-\clearpage
+\begin{figure}
+\centering
+	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
+	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}
+
+	\begin{comment}
+	I want to work more on this graph. I think this one and the one below might help us. I just need to make them look nicer.
+	\end{comment}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/yearly_total_fishing_by_region.pdf}
+	\caption{\label{fig:yearly_total_fishing_by_region}Total fishing by region.}	
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/total_PNA_revenues.pdf}
+	\caption{\label{fig:total_PNA_revenues}Total revenues for all PNA countries combined.}
+\end{figure}
 
@@
 
-\clearpage
-
 \begin{figure}
@@
 \end{figure}
-
-\clearpage
 
@@
 
-\clearpage
-
-\section{Palau National Marine Sanctuary}\label{PNMS}
-
 \begin{figure}
-	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
-	\caption{Map of the Four Protected Areas}
-	\label{fig:maps}
+\centering
+\caption{figure that shows treated minus control effort and maybe just compare 2013 with 2017 (or 2012-2014 average with 2015-2018 average).}
 \end{figure}
 
-\clearpage
+\section{Alternative Controls}
 
-\section{Alternative Controls}
+\begin{comment}
+Need to update the captions on all the tables that follow, especially number of outcome variables, names of outcome variables, and heteroskedasticity.
+\end{comment}
+
 \subsection{Excluding all Chinese vessels}
@@
 
-\clearpage
 \subsection{Excluding all PNA vessels}
@@
 
-\clearpage
-
 \subsection{Excluding all USA and TWN vessels}
@@
 \input{tab/DID_without_USA_TWN}
-
-\clearpage
-
-\section{Additional methods}
-
-This section is divided into two main parts.
-First, we provide a general description of AIS data and the process of identification of vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe the subset of data used in our analysis.
-We also point out possible shortcomings in the data, or factors that must be considered in the analysis.
-We then move on to explain our empirical strategy for the identification of behavioral changes and the redistribution of fishing effort.
-
-\subsection{Data}
-
-The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
-The addition of new satellites affects all vessels in the same way.
-
-\input{tab/baci_n_s}
 
@@
 %Agreement, which limited the number of purse seiners at 205 vessels from
-%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federal States of Micronesia agreements.} However, the most notable regulation is
+%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federated States of Micronesia agreements.} However, the most notable regulation is
 %the approach to manage fishing effort: a Vessel Day Scheme (VDS)
@@
 
-\input{palau_purse}
-
 %All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}).
@@
 A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.
-
-\input{palau_long}
 

### 2019-03-04 docs/old_ms/PIPA_Palau.tex
Updated MS

--- 2019-03-01 docs/PIPA_Palau022819.tex
@@
 Marine Protected Areas are inherently spatial and have the sole objective of conserving bounded waters through the displacement of fishing effort.
-Our work shows that displacement of fishing effort occurs, but that it comes at a cost to countries that would have otherwise been able to charge a price for vessels to fish in the now-protected areas.
+Our work shows that displacement of fishing effort occurs, but that it comes at a large cost to countries that would have otherwise been able to charge a price for vessels to fish in the now-protected areas.
 With global conservation targets seeking to protect 10\% of the world’s ocean by 2020 and the expansion of offshore aquaculture, it is important that the spatial displacement of economic activities is fully considered.}
@@
 The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean.
-The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters.
-In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities.
+The fishery in the region operates under a vessel-day scheme (VDS), which sells access rights that allow vessels to fish in PNA waters.
+In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Island Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities.
 Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as induce costs (due to the reduction in fishable area) to Kiribati.
 We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution, behavior, and costs to Kiribati and the PNA.
-We find a crowding effect within PNA waters after the implementation of the protected area.
+We find a short-term crowding effect within PNA waters after the implementation of the protected area.
 Vessels continue to fish with similar intensity after the implementation.
-In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold.
-However, from 2016 onwards there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue.
-At the same time, fishing effort increases in other parts of the PNA.
-This redistribution of fishing effort eventually results in a reduction of 2,310 vessel-days in Kiribati, which represents a loss of \$27.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).
-We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
-PNA members who indirectly benefit from MPAs should consider mechanisms that reward such conservation actions.
+The eventual decrease in crowding within PNA waters but constant fishing intensity suggests that vessels redistribute to adjacent waters, including the high seas.
+This redistribution results in a reduction of 2,310 vessel-days in Kiribati, which represents a loss of \$27.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).
+We use our results to inform predictions of the impacts of a proposed LSMPA in Palau (a PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
+PNA members who decide to implement MPAs should consider mechanisms that reward such conservation actions.
 \end{abstract}
@@
 Multiple ocean uses such as off-shore aquaculture, conservation, energy harvesting, deep-sea mining, and fisheries are likely to compete for space.
-As we move forward with blue growth, we must understand the potential effects of activities displacing each other and establish causal links between past management interventions and their outcomes \citep{burgess_2018}.
-One of the most notable spatial interventions is the creation of no-take Marine Protected Areas (MPAs), which seek to conserve the environment by eliminating fishing effort within their waters.
+As we move forward with blue growth, we must understand the potential effects of activities displacing each other and etablish causal links between past management interventions and their outcomes \citep{burgess_2018}.
+One of the most notable spatial spatial interventions are no-take Marine Protected Areas, which seek to conserve the environment by eliminating fishing effort within their waters.
 
 Global international goals aim to protect 10\% of the ocean environment by 2020.
-In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which occur in the world's largest fishing grounds for tuna.
-While today a small number of LSMPAs make up at least 80\% of the managed areas in the ocean \citep{toonen_2013}, very little is known about their human dimensions and implications for fisheries \citep{gray_2017}.
+In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs), some of which ocurr in the world's largest fishing grounds for tuna.
+While today a small number of LSMPAs make up at least 80\% of the managed areas in the ocean \citep{toonen_2013}, very little is known about their human dimensions and implication for fisheries \citep{gray_2017}.
 Furthermore, most of the research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
@@
 
-The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas.
-Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area that produces approximately 50\% of the world's tuna.
-Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly refered to as the Parties to the Nauru Agreement (PNA).
-Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the PNA group in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
+The Phoenix Island Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas.
+Implemented in January 1st of 2015, PIPA has an extension of 397,447 km\textsuperscript{2} and was implemented within an area that produces 50\% of the World's tuna.
+Tuna purse seine fisheries in the region are collectively managed under a Vessel-day scheme (VDS) by nine countries commonly refered to as the Parties to the Nauru Agreement (PNA).
+Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu.
+Tokelau joined the PNA group in 2012 and started selling access rights in 2013.
 The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
@@
 A spatial closure of such dimensions is likely to cause changes in spatial distribution and behavior of fishing vessels.
-For example, the anticipation of LSMPAs may lead to preemptive overfishing, which will likely erodes or delay the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}.
+For example, the anticipation of LSMPAs may lead to preemptive overfishing, which will likely erodes or delay the expected benefits of an intervention \cite{mcdermott_2018}.
 After a spatial closure, users can exhibit idiosyncratic responses driven by different incentives \cite{cabral_2017}.
 Moreover, this reduction in total fishing area within one country's EEZ is likely to result in selling less fishing licenses.
-While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (i.e.
-Palau).
+While no studies have assessed the immplications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020.
 We evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati.
 We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are controled by PNA countries, where the largest tuna fisheries occur.
+These are two of the largest protected areas on the planet and both are controled by PNA countries, where the largest tuna fisheries ocurr.
 
@@
 Of these, 64 vessels fished within PIPA at least once prior to its implementation.
-The remaining 28 vessels never fished in PIPA waters.
-We refer to these groups as the treated and control groups.
+The remaining 28 vessels never fished in PIPA these waters.
+We refer to these groups as treated and control groups.
 The group with the remaining 221 vessels contains vessels that were not observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
@@
 \includegraphics{img/LSMPAs_map.pdf}
-\caption{\label{fig:LSMPAs_map}Large Scale Marine Protected Areas. The map shows all areas larger than 30,000 Km\textsuperscript{2}. The Phoenix Islands Protected Area is shown in red.}
+\caption{\label{fig:LSMPAs_map}Large Scale Marine Protected Areas. The map shows all areas larger than 30,000 Km\textsuperscript{2}. The Phoenix Island Protected Area is shown in red.}
 \end{figure}
@@
 We first inspect the crowding effects that may arise due to the net reduction in fishing area.
-We produced 1-degree rasters of monthly fishing effort for our treatment and control groups, and calculated two indices of spatial overlap between them: 1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.
+We produced 1-degree rasters of monthly fishing effort for our treatment and control groups, and calculated two indices of spatial overlap between thm: 1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.
 We find that the two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
 \ref{fig:sp_corr}).
-The number of cells with presence from both fleets and spatial correlations increase by a factor of four and three, respectively.
-This increase in crowding is likely to increase the encounter rates with other vessels, and reduce the efficiency of fishing operations.
-This might cause vessels to leave their current fishing grounds and re-optimize their spatial effort, leading to a subsequent decrease as the crowding measures return towards pre-implementation levels.
+The number of vessels with presence from both fleets and spatial correlations increase by a factor of four and three, respectively.
+This increase in crowding is likely to increase the encounter rates within vessels, and reduce the efficiency of fishing opperations, resulting in a nusicance to vessels.
+This would cause vessels to leave curent fishing grounds, leading to the subsequent decrease as the crowding measures return to pre-implementation levels.
 
@@
 The behavioral responses that vessels can have to a spatial closure may occurr in different ways.
-For example, displacement to new fishing grounds may represent a cost as fishers search the ocean to identify the most suitable fishing spots.
+For example, displacement to new fishing grounds may represent a cost as fishers search the ocean to identify the most suitable fishing places.
 This may result in increased fuel and labor costs.
-For every vessel in each group, we calculate eight key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters and Kiribati waters (Fig.
+For every vessel in each group, we calculate in eight key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters and Kiribati waters (Fig.
 \ref{fig:all_panels}).
-We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for treated vessels after implementation of PIPA, relative to the trends observed for control vessels (see the Methods section for our empirical specification).
+We leverage our BACI design and implement a log-linear difference-in-differences analyses to evaluate how these measures change for treated vessels after implementation of PIPA, relative to the trends observed for control vessels (See Methods section for our empirical specification).
 
-We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled less, with fishing events occurring closer to shore and closer to port following PIPA implementation.
-These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$).
-We do not observe a statistically significant increase in fishing hours on the high seas.
-
-The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in Kiribati and PNA waters decreases suggests that these vessels have re-distributed elsewhere.
+We find no evidence of treated vessels fishing for more hours after PIPA implementation, and a slight increase of 1\% more time at sea ($p < 0.05$; Table \ref{tab:main_DID}).
+Treated vessels traveled 20\% less, with fishing events ocurring 23.8\% closer to shore and 5\% closer to port.
+These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 58\% and 45\% less in PNA and Kiribati waters, compared to the trend observed for control vessels ($p < 0.01$).
+The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in PNA and Kiribati waters decreases suggests that these vessels have re-distributed elsewhere.
 This is consistent with the eventual decrease in crowding meassures.

### 2019-03-04 docs/tab/sp_corr.tex
Updated MS

--- 2019-02-28 docs/tab/sp_corr.tex
@@
  Constant & 59.999$^{***}$ (15.581) & 0.370$^{***}$ (0.062) \\ 
-  Months & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
-  Months $^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
-  Months $^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
-  Months $^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
-  sate1 & 22.342 (19.528) & 0.057 (0.076) \\ 
-  sate2 & 5.413 (18.860) & $-$0.015 (0.035) \\ 
+  $M$ & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
+  $M^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
+  $M^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
+  $M^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
+  $\sigma_1$ & 22.342 (19.528) & 0.057 (0.076) \\ 
+  $\sigma_2$ & 5.413 (18.860) & $-$0.015 (0.035) \\ 
  \hline \\[-1.8ex] 

### 2019-03-04 scripts/content/nvessels_to_90.R

@@ -1,0 +1,42 @@
+# nvessels to achieve 90% of activity per year
+#
+my_fun <- function(x) {
+  tot <- nrow(x)
+  x %>% mutate(c = cumsum(frac)) %>%
+    filter(c < 90) %>%
+    nrow() / tot * 100
+}
+
+PNA_without_KIR <- c("FSM",
+                     "MHL",
+                     "NRU",
+                     "PLW",
+                     "PNG",
+                     "SLB",
+                     "TUV",
+                     "TKL")
+
+PNA_countries <- c(PNA_without_KIR, "KIR")
+
+
+vessel_data <- readRDS(file = here("raw_data",
+                                   "activity_by_vessel_year_eez.rds")) %>% 
+  filter(best_vessel_class == "tuna_purse_seines", 
+         eez_iso3 %in% PNA_countries) %>% 
+  mutate(treated = ifelse(treated, "Treated", "Control"),
+         group = ifelse(is.na(treated), "Others", treated),
+         days = hours / 24) %>%
+  group_by(year, group, ssvid) %>%
+  summarize(days = sum(days)) %>%
+  arrange(year, desc(days)) %>%
+  group_by(year) %>%
+  mutate(total = sum(days)) %>%
+  ungroup() %>%
+  mutate(frac = days / total * 100) %>%
+  group_by(year) %>%
+  nest() %>% 
+  mutate(percent = map_dbl(data, my_fun)) %>% 
+  arrange(desc(percent))
+
+vessel_data
+

### 2019-03-04 scripts/content/plot_financial_indicators.R

@@ -83,7 +83,8 @@ vessel_activity <- readRDS(file = here("raw_data",
   group_by(year, eez_iso3) %>% 
   summarize(days = sum(days)) %>% 
   left_join(vds_price_per_year, by = "year") %>% 
-  mutate(inferred_revenue = price * days / 1e6) %>% 
+  mutate(inferred_revenue = price * days / 1e6,
+         days = days / 1000) %>% 
   left_join(financial_data, by = c("year", "eez_iso3" = "country")) %>% 
   drop_na(inferred_revenue, revenue) %>% 
   rename(country = eez_iso3) %>% 
@@ -91,27 +92,31 @@ vessel_activity <- readRDS(file = here("raw_data",
 
 revenue_FFA_GFW <-
   ggplot(vessel_activity, aes(x = inferred_revenue, y = revenue)) +
-  geom_point(aes(fill = country),
+  geom_point(aes(fill = country, size = days),
              shape = 21,
-             size = 3,
+             # size = 3,
              alpha = 0.7) +
   geom_smooth(method = "lm",
               linetype = "dashed",
               color = "black",
               se = F) +
   geom_abline(intercept = 0, slope = 1) +
-  scale_fill_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1", guide = F) +
   theme_cowplot()  +
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8)) +
-  guides(fill = guide_legend(title = "Country", ncol = 1)) +
+  guides(fill = guide_legend(title = "Country", ncol = 1),
+         size = guide_legend(title = "Vessel-days (1,000)", ncol = 3)) +
   labs(x = "Inferred revenue\n(million USD)",
-       y = "Reported revenue\n(million USD)")
+       y = "Reported revenue\n(million USD)") +
+  scale_size_continuous(breaks = c(1, 5, 10))
 
 log_revenue_FFA_GFW <- revenue_FFA_GFW +
   scale_x_continuous(trans = "log10", limits = c(0.09, 200)) +
   scale_y_continuous(trans = "log10", limits = c(0.09, 200)) +
-  theme(legend.position = "none")
+  theme(legend.justification = c(1, 0),
+        legend.position = c(1, 0)) +
+  guides(fill = F)
 
 # Put together
 p <- plot_grid(p1,
@@ -127,7 +132,7 @@ ggsave(p,
 
 ggsave(revenue_FFA_GFW,
[…]

### 2019-03-04 scripts/model/Costello_PNA_Model.R

@@ -50,7 +50,7 @@ Grow <- function(e) {
 Sim1 = function(R, theta) {
   Xvec <- Xstart * fvec
   Evec <- Efforts
-  tol <- 100
+  tol <- 10
   diff <- 2 * tol
   
   while (diff > tol) {
@@ -82,17 +82,20 @@ Sim1 = function(R, theta) {
                    Harvest = H_ss_vec,
                    Vessel_Days = E_ss_vec,
                    Stock = sum(X_ss_vec),
+                   Stock_i = X_ss_vec,
                    VDSprice = VDSprice_ss_vec,
                    VDSrevenue = VDSrevenue_ss_vec,
                    VDSrevenue_all = sum(VDSrevenue_ss_vec),
                    VDSrevenue_notKIR = sum(VDSrevenue_ss_vec[2:9]))
+  
   return(DF)
 }
 
+Rvec <- seq(0, 1, 0.05)
+thetavec <- seq(0.05, 1, 0.1)
+
 DF_results <- Sim1(R = 0, theta = 0)
 
-Rvec <- seq(0, 1, 0.1)
-thetavec <- seq(0, 1, 0.1)
 
 for (i in 1:length(Rvec)) {
   R <- Rvec[i]
@@ -100,62 +103,59 @@ for (i in 1:length(Rvec)) {
     theta <- thetavec[j]
     DFtmp <- Sim1(R = R, theta = theta)
     DF_results <- bind_rows(DF_results, DFtmp)
-    print(i)
-    print(j)
+    # print(i)
+    # print(j)
   }
 }
 
 DF_results <- DF_results %>% 
-  mutate_at(vars(VDSrevenue, VDSrevenue_all, VDSrevenue_notKIR), function(x){x/1e6})
+  mutate_at(vars(VDSrevenue, VDSrevenue_all, VDSrevenue_notKIR), function(x){x/1e6}) # convert all revenues to millions
 
 # Revenue in Kiribati
 DF_1 = DF_results %>%
-  filter(Country == "KIR")
+  filter(Country == "KIR") %>% 
+  mutate(change = VDSrevenue - max(VDSrevenue),
+         change_all = VDSrevenue_notKIR - min(VDSrevenue_notKIR))
 
 Plot1 = ggplot(data = DF_1) +
-  geom_line(aes(
-    x = Reserve,
-    y = VDSrevenue,
-    group = Movement,
-    color = Movement
-  ),
-  size = 1.5) +
[…]

### 2019-03-05 docs/PIPA_Palau030319.tex
Added updated figures and new MS

@@
 At the same time, fishing effort increases in other parts of the PNA.
-This redistribution of fishing effort eventually results in a reduction of 2,310 vessel-days in Kiribati, which represents a loss of \$27.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).
+This redistribution of fishing effort eventually results in a reduction of 5,195 vessel-days in Kiribati, which represents a loss of \$46.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).
 We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.

### 2019-03-05 docs/tab/sp_corr.tex
Added updated figures and new MS

@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcc} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
 \hline \\[-1.8ex] 
- Constant & 59.999$^{***}$ (15.581) & 0.370$^{***}$ (0.062) \\ 
-  $M$ & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
-  $M^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
-  $M^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
-  $M^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
-  $\sigma_1$ & 22.342 (19.528) & 0.057 (0.076) \\ 
-  $\sigma_2$ & 5.413 (18.860) & $-$0.015 (0.035) \\ 
+ Constant & 78.040$^{***}$ & 84.639$^{***}$ & 60.962$^{***}$ & 66.725$^{***}$ & 0.412$^{***}$ & 0.417$^{***}$ & 0.370$^{***}$ & 0.377$^{***}$ \\ 
+  & (5.438) & (8.990) & (15.598) & (15.988) & (0.014) & (0.032) & (0.062) & (0.066) \\ 
+  & & & & & & & & \\ 
+ M & 3.943$^{***}$ & 4.065$^{***}$ & 3.066$^{***}$ & 3.139$^{***}$ & 0.010$^{***}$ & 0.010$^{***}$ & 0.009$^{**}$ & 0.009$^{**}$ \\ 
+  & (0.302) & (0.348) & (0.966) & (1.040) & (0.001) & (0.001) & (0.003) & (0.004) \\ 
+  & & & & & & & & \\ 
+ M $^2$ & $-$0.005 & $-$0.021 & 0.008 & $-$0.008 & $-$0.0001$^{***}$ & $-$0.0001 & $-$0.0001 & $-$0.0001 \\ 
+  & (0.019) & (0.026) & (0.027) & (0.030) & (0.00004) & (0.0001) & (0.0001) & (0.0001) \\ 
+  & & & & & & & & \\ 
+ M $^3$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ \\ 
+  & (0.0003) & (0.0003) & (0.001) & (0.001) & (0.00000) & (0.00000) & (0.00000) & (0.00000) \\ 
+  & & & & & & & & \\ 
+ M $^4$ & 0.00001 & 0.00002 & 0.00000 & 0.00001 & 0.00000$^{***}$ & 0.00000$^{**}$ & 0.00000 & 0.00000 \\ 
+  & (0.00001) & (0.00002) & (0.00002) & (0.00002) & (0.00000) & (0.00000) & (0.00000) & (0.00000) \\ 
+  & & & & & & & & \\ 
+ NINO4 &  & $-$8.095 &  & $-$10.395 &  & $-$0.006 &  & $-$0.014 \\ 
+  &  & (8.287) &  & (9.481) &  & (0.029) &  & (0.031) \\ 
+  & & & & & & & & \\ 
+ $\sigma_1$ &  &  & 21.318 & 25.102 &  &  & 0.057 & 0.062 \\ 
+  &  &  & (19.493) & (22.486) &  &  & (0.076) & (0.080) \\ 
+  & & & & & & & & \\ 
+ $\sigma_2$ &  &  & 5.299 & 3.194 &  &  & $-$0.015 & $-$0.018 \\ 
+  &  &  & (18.874) & (18.670) &  &  & (0.035) & (0.035) \\ 
+  & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes \\ 
-Flag FE & Yes & Yes \\ 
-Observations & 83 & 84 \\ 
-R$^{2}$ & 0.791 & 0.709 \\ 
+NINO4 & No & Yes & No & Yes & No & Yes & No & Yes \\ 
+Satellites & No & No & Yes & Yes &  &  &  &  \\ 
+Observations & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 \\ 
+R$^{2}$ & 0.791 & 0.793 & 0.795 & 0.798 & 0.703 & 0.704 & 0.709 & 0.710 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-03-07 docs/PIPA_Palau030319.tex
Updated images, added new images, and updated MS

@@
 \includegraphics{img/PNA_model.pdf}
-\caption{\label{fig:PNA_model}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}}
+\caption{\label{fig:PNA_model}Change in revenue from the PNA model with conservation.
+Revenue is shown for Kiribati alone (A) and all other PNA countries (B) as a function of increasing proportion of patch as reserve ($R$).
+Each line (color) represents a value of the movement parameter $\theta$.}
 \end{figure}
@@
 
-\subsection{Crowding effect}
+\subsection{Empirical analysis}
+
+Spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}.
+Vessels may then redistribute across PNA countries as they track these stocks \cite{aqorau_2018}.
+To account for environmentally-driven patterns in vessel location, we incorporate the monthly NINO4 anomaly index in our analyses.
+The NINO4 index is an area-averaged measure of Sea Surface Temperature from 5S-5N and 160E-150W.
+The NINO4 anomaly index is the same, with the 1981-2010 mean removed, as made available from the Global Climate Observing System (Fig.
+\ref{fig:nino_plot}).
+
+\subsubsection{Crowding effect}
 
@@
 This might cause vessels to leave their current fishing grounds and re-optimize their spatial effort, leading to a subsequent decrease as the crowding measures return towards pre-implementation levels.
+These results are robust to a series of specifications, accounting for the addition of satellites and monthly NINO4 anomaly (Table \ref{tab:sp_corr}).
+A model fit with NINO4 anomaly as the only explanatory variable explained just 3\% and 7\% of the variation in our crowding measures.
+Similar results are obtained when repeating the exercise for Kiribati only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr})
 
@@
 \includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that had treated and control vessels (A) and spatial correlation in the presence-absence of treated and control vessels per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}}
+\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
 \end{figure}
 
-\subsection{Behavioral changes}
+\subsubsection{Behavioral changes}
 
@@
 This may result in increased fuel and labor costs.
-For every vessel in each group, we calculate eight key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters and Kiribati waters (Fig.
+For every vessel in each group, we calculate nine key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea hours, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters, Kiribati waters, and the High Seas (Fig.
 \ref{fig:all_panels}).
-We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for treated vessels after implementation of PIPA, relative to the trends observed for control vessels (see the Methods section for our empirical specification).
+We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for displaced vessels after implementation of PIPA, relative to the trends observed for non-displaced vessels (see the Methods section for our empirical specification).
+As before, our analyses incorporates monthly NINO4 anomalies to account for possible environmentaly-driven variations.
 
-We find no evidence of treated vessels fishing for more hours after PIPA implementation, and in fact observe a negative effect (24.4\% decrease; $p < 0.01$; Table \ref{tab:main_DID}) relative to the non-displaced vessels.
-Likewise, we observe a slight decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled less distance, with fishing events occurring closer to shore and closer to port following PIPA implementation.
-These changes in distance from shore and port are likely caused by redistribution, as we observe that treated vessels fish 56.5\% and 39.9\% less in Kiribati and PNA waters, compared to the trend observed for control vessels ($p < 0.01$).
-We do not observe a statistically significant increase in fishing hours on the high seas.
-This suggests that treated vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters.
+We find no evidence of displaced vessels fishing for more hours after PIPA implementation, and in fact observe a negative effect (24.3\% decrease; $p < 0.01$; Table \ref{tab:main_DID}) relative to the non-displaced vessels.
+Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
+Treated vessels traveled 21\% less distance, with fishing events occurring 28.5\% and 15.7\% closer to shore to port, respectively.
+These changes in distance from shore and port are likely caused by redistribution, as we observe that displaced vessels fish 58.6\% and 40.3\% less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
+We do not observe a statistically significant increase in fishing hours on the High Seas.
+
+These patterns suggest that displaced vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters.
 In summary, vessels that used to fish in PIPA are now fishing less in both Kiribati and the PNA region.
-Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters.
+Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters, with slight increases in the High Seas \ref{fig:fishing_raster_diff}.
+The results are robust to a set of different specifications, with interaction effects shown in Fig  \ref{fig:other_specifications}.
+We repeat this analysis for groups where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same reposnses.
 
-\subsection{Economic impacts}
+\subsubsection{Economic impacts}
 
-The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they buy less vessel-days from PNA countries.
+The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that displaced vessels have redistributed elsewhere, meaning that they buy less vessel-days from PNA countries.
 To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by Kiribati and all PNA countries by each group of vessels (Fig.
@@
 We look at all 313 vessels to obtain a more accurate representation of total revenues, but continue to group vessels as displaced (n = 64), non-displaced (n = 28), and other vessels (n = 221).
+
 We find that between 2015 and 2016, displaced vessels spent 3,916 and 2,249 less vessel-days in Kiribati and PNA waters, respectively (Figs.
-\ref{fig:all_PS_VDS_year}-\ref{fig:included_PS_VDS_year_DiD}).
+\ref{fig:all_PS_VDS_year} and \ref{fig:included_PS_VDS_year_DiD}).
 Over the same period, non-displaced and other vessels spent 1,278 less days in Kiribati, but spent 9,853 more days in PNA waters overall.
-These changes result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} to the other 8 countries).
-The net reduction of vessel-days in Kiribati represents a loss of \$46.7 million USD, while the net gain at the PNA-level results in \$68 million USD in increased revenues.
+These changes result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} the other 8 countries).
+The net reduction of vessel-days in Kiribati represents a loss of \$46.7 million USD in vessel-day licenses, while the net gain at the PNA-level results in an increase of \$68 million USD.
+
 Moreover, annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018 (Fig.
 \ref{fig:all_PS_VDS_KIR_year}).
-This trend is mainly caused displaced vessels allocating less time to Kiribati (\ref{fig:hist_kir_fishing}).
+This trend is mainly caused by displaced vessels allocating less time to Kiribati (Figs \ref{fig:all_PS_VDS_KIR_year} and \ref{fig:hist_kir_fishing}).
 Looking at the total annual vessel-days allocated by all vessels to all countries, we see that the largest reductions occur for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
@@
 	\includegraphics{img/all_PS_VDS_year.pdf}
-	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by treated, control, and excluded vessels.}
+	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by displaced, non-displaced, and other vessels.}
 \end{figure}
@@
 Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the United States for under the South Pacific Tuna Treaty a.k.a.
-Multilateral Treaty on Fisheries (\$12,500/day).
+In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the United States for under the South Pacific Tuna Treaty also known as the Multilateral Treaty on Fisheries (\$12,500/day).
 In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other PNA countries at the current benchmark price (\$8,000/day).
@@
 In Scenarios 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel day and export tax revenues are lost,
-since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
+In all scenarios, all longline vessel day and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
 The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
@@
 Using vessel track data, we observe a crowding effect after the implementation of the protected area, as displaced vessels redistribute spatially.
+We see that vessels that fished inside PIPA before the implementation redistributes to other areas within Kiribati, but also other PNA countries and the high seas.
 Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners.
-But there is considerable redistribution of effort across space and within the fleet of purse seiners.
 Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
-Our analysis suggests that the displacement of vessels results in losses to Kiribati.
-A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD.
+Our analysis suggests that the displacement of vessels results in losses to Kiribati, and that similar outcomes would be expected for Palau's Marine Sanctuary with losses in profits of up to \$11 million USD.
 Here, we discuss the implications of our findings and possible shortcomings in our analysis.
@@
 Another possible explanation is that the dataset used incorrectly labeled vessels as purse seiners.
-However, the scoring algorithm has a high accuracy, and accuracy increases with the number of observations for a vessel.
-Moreover, on any given year, 90\% of total fishing activity can be explained by at least 68\% of the vessels.
+However, the scoring algorithm has a high accuracy, and this accuracy increases with the number of observations for a vessel.
+Moreover, on any given year, 90\% of total fishing activity can be explained by 68\% to 75\% of the vessels (Fig \ref{fig:nvessels_to_90}).
 Therefore, if there are any mislabeled vessels in our data, these would contribute little to the large trends that we observe.
-Finally, vessels fishing within PNA waters can report their activity as transiting to port or solving mechanical issues; this time does not count towards a vessel's usage of days (forgot the reference).
+Another alternative is that vessels fishing within PNA waters can report their activity as transiting to port or solving mechanical issues; this time does not count towards a vessel's usage of days (forgot the reference).
+Finally, Kiribati's vessel-day allocation is in the order of 7,000 vessel-days (need reference).
+However, we observe that on any given year, Kiribati received between 3,000 and 14,900 vessel-days (Fig \ref{fig:all_PS_VDS_KIR_year}), implying that a portion of these were purchased or transfered from other PNA countries.
 These explanations are not mutually exclusive, and a combination of them could certainly explain the discrepancy.
-While the magnitude is not the same, the trends and patterns through time are certainly similar.
+While the magnitude is not the same, the trends and patterns through time are certainly similar, and all indicate a reduction of usage of Kiribati's waters.
 
-A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately are the factors that guide the decision-making process of profit-maximizing agents.
+ENSO events are known to drive the behavior of fishing vessels, especially in PNA waters, which may drive reallocation of fishing effort \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+We do our best control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking non-displaced vessels as a group that is equally affected by the environmental variation.
+For example, we observe that both displaced and non-displaced vessels shifted their effort to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
+However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
+Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself does not explain the observed patterns.
+While environmental variation certainly influences behavior, policy and management interventions such as moratorium and spatial closures can have an equally big effects \cite{kroodsma_2018}.
+
+A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guide the decision-making process of profit-maximizing agents.
 Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
@@
 
-A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in losses to countries that have been receiving revenue from granting fishing access.
-We also show that spatial closures lead to crowding effects, which causes some vessels to redistribute to areas close by.
-While LSMPAs can provide a wide range of benefits, their implementation must be accompanied with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable financing mechanisms that would compensate losses and incentivize marine conservation.
+Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses.
+The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
+The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lehodey_1997,aqorau_2018}.
+Overlaying conservation interventions over existing management schemes must be accompained by similar dialogues and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
+Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms\cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
 
@@
 Our treatment group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
-Vessels in the control group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
+Vessels in the non-displaced group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
 Together, these vessels represent more than 20 million georeferenced positions for which we know activity (fishing or not fishing).
@@
 The first group excludes all Chinese vessels, the second group excludes all PNA vessels, and the third group excludes US and Taiwanese vessels.
-Our main definition of treatment and control groups leaves us with 64 treated and 28 control vessels, which have just over 36 million observations.
+Our main definition of displaced and non-displaced groups leaves us with 64 displaced and 28 non-displaced vessels, which have just over 36 million observations.
 
@@
 	\begin{align}
-	y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \epsilon_t
+	y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
 	\label{eqn:sp_corr}
@@
 We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
-1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and star  ts to decrease, and 3) when this decrease potentially levels off.
+1) the number of cells that had fishing activity from displaced and non-displaced vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and star  ts to decrease, and 3) when this decrease potentially levels off.
 For this reason, we fit a 4th degree polynomial to our monthly indices.
@@
 For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our treated and control vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
 We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which incorporated in April 1st, 2014 and December 31st, 2015.
+The$mu$ coefficient captures the effect of the NINO4 anomaly.
 
@@
 \begin{align}
-log(y)_{i,t} = \alpha + \beta_1 P_t + \beta_2 T_i + \beta_3 P_t \times T_i + \phi_t + \gamma_i + \epsilon_{i,t}
+log(y)_{i,t} = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \label{eqn:did}
@@
 
-\noindent where $log(y_{i,t})$ is the log-transformed outcome of interest for vessel $i$ on day $t$.
+\noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$ the transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ on period $t$.
 A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
-$Treat_i$ is a dummy variable indicating whether a vessel belongs to the treatment ($Treat_i = 1$) or control ($Treat_i = 0$) group.
-$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between treated and control groups, and $\beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
+$Treat_i$ is a dummy variable indicating whether a vessel belongs to the displaced ($D_i = 1$) or non-displaced ($D_i = 0$) group.
+$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between displaced and non-displaced groups, and $\beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
 Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
@@
 
-We obtained information on license fee revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-For countries in the PNA, we assume that all license fee revenue is coming from the sale of VDS.
+We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
+For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
 
@@
 
-\section{Appendix}\label{appendix}
-
 \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
@@
 
-\input{tab/sp_corr}
-
-\input{tab/main_DID}
-
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.
-Land masses are shown in gray.}
+Land masses are shown in gray.
+Labels indicate ISO3 country codes (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
+\centering
+\includegraphics{img/nino_plot.png}
+\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Timeseries of NINO4 anomaly from January, 1980 to December, 2018.}
+\end{figure}
+
+\clearpage
+
+\input{tab/sp_corr}
+
+\input{tab/KIR_sp_corr}
+
+\begin{figure}[H]
+\centering
+\includegraphics{img/KIR_sp_corr.pdf}
+\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
+\end{figure}
+
+\input{tab/main_DID}
+
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[H]
+\centering
+\includegraphics{img/other_specifications.pdf}
+\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates for our variables of interest using different model specifications.
+Table \ref{tab:main_DID} reports estimates for models with month and flag fixed effects, and NINO4 index (\emph{i.e.} green dots).}
+\end{figure}
+
+\input{tab/DID_without_CHN}
+
+\input{tab/DID_without_PNA}
+
+\input{tab/DID_without_USA_TWN}
+
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[H]
+\centering
+	\includegraphics{img/hist_kir_fishing.pdf}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
+\end{figure}
+
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}
-
-	\begin{comment}
-	I want to work more on this graph. I think this one and the one below might help us. I just need to make them look nicer.
-	\end{comment}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/yearly_total_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_total_fishing_by_region}Total fishing by region.}	
-\end{figure}
-
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering
-\includegraphics{img/other_specifications.pdf}
-\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates
-for our variables of interest using different model specifications. Table \ref{tab:main_DID}
-reports estimates for models with month and flag fixed effects (\emph{i.e.} green dots).}
+	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
+	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}	
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
 \centering
-\includegraphics{img/fishing_raster.png}
-\caption{\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels.
-Color corresponds to \% of total fishing effort in each panel.
-Red polygons show LSMPAs in the region.}
+\includegraphics{img/fishing_raster_diff.png}
+\caption{\label{fig:fishing_raster_diff}Change in spatial footrpint of analysed vessels.
+Black lines show Exclusive Economic Zone (EEZ), red lines show existing Marine Protected Areas.
+Panels A and B show the change through time (after - before) for dislpaced and non-displaced vesels, respectively.
+Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
+Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA.}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
 \centering
-\caption{figure that shows treated minus control effort and maybe just compare 2013 with 2017 (or 2012-2014 average with 2015-2018 average).}
+\includegraphics{img/PS_VDS_PNA_by_month_eez.pdf}
+\caption{\label{PS_VDS_PNA_by_month_eez}Time series of monthly observed vessel-days for each PNA country.}
 \end{figure}
 
-\section{Alternative Controls}
+\begin{figure}[H]
+\centering
+\includegraphics{img/time_series_gear_group.pdf}
+\caption{\label{fig:time_series_gear_group}Time series of monthly observed vessel days for drifting longliners and tuna purse seiners in each EEZ belonging to Kiribati: Gilbert islands, Phoenix islands, and Line islands.
+\emph{I would take this one out, but left it here so you could see the drop in longlines happens later (2017), not aligned with PIPA at all.}}
+\end{figure}
 
-\begin{comment}
-Need to update the captions on all the tables that follow, especially number of outcome variables, names of outcome variables, and heteroskedasticity.
-\end{comment}
-
-\subsection{Excluding all Chinese vessels}
-
-\input{tab/DID_without_CHN.tex}
-
-\subsection{Excluding all PNA vessels}
-
-\input{tab/DID_without_PNA.tex}
-
-\subsection{Excluding all USA and TWN vessels}
-
-\input{tab/DID_without_USA_TWN}
+\begin{figure}[H]
+\centering
+\includegraphics{img/nvessels_to_90.pdf}
+\caption{\label{fig:nvessels_to_90}Cumulative activity (\% of total hours) as a function og increasing fraction of vessels (\% of total) by year.)}
+\end{figure}
 

### 2019-03-07 docs/tab/DID_without_CHN.tex
Updated images, added new images, and updated MS

@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 9 variables of interest after removing Chinese vessels.
+1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
 \hline \\[-1.8ex] 
- Constant & 0.060$^{***}$ & 3.864$^{***}$ & $-$0.003 & 6.149$^{***}$ & 13.775$^{***}$ & 13.146$^{***}$ & 3.896$^{***}$ & 4.484$^{***}$ \\ 
-  & (0.019) & (0.008) & (0.003) & (0.043) & (0.044) & (0.058) & (0.341) & (0.303) \\ 
-  & & & & & & & & \\ 
- Post & 0.817$^{***}$ & $-$0.258$^{***}$ & 0.136$^{***}$ & 0.125$^{***}$ & 0.365$^{***}$ & 0.344$^{***}$ & 1.056$^{***}$ & 1.205$^{***}$ \\ 
-  & (0.018) & (0.009) & (0.003) & (0.019) & (0.015) & (0.016) & (0.154) & (0.120) \\ 
-  & & & & & & & & \\ 
- Treated & 0.108$^{***}$ & 0.009 & 0.012$^{***}$ & 0.294$^{***}$ & 0.268$^{***}$ & 0.157$^{***}$ & 0.489$^{***}$ & 0.148 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.020) & (0.017) & (0.017) & (0.162) & (0.132) \\ 
-  & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.212$^{***}$ & 0.039$^{***}$ & $-$0.031$^{***}$ & $-$0.318$^{***}$ & $-$0.335$^{***}$ & $-$0.203$^{***}$ & $-$0.547$^{***}$ & $-$0.409$^{***}$ \\ 
-  & (0.021) & (0.010) & (0.004) & (0.023) & (0.019) & (0.018) & (0.174) & (0.137) \\ 
-  & & & & & & & & \\ 
+ Constant & 0.058$^{***}$ & 3.863$^{***}$ & $-$0.003 & 4.829$^{***}$ & 13.817$^{***}$ & 13.161$^{***}$ & 4.007$^{***}$ & 4.515$^{***}$ & 2.909$^{***}$ \\ 
+  & (0.019) & (0.008) & (0.003) & (0.044) & (0.044) & (0.058) & (0.347) & (0.304) & (0.274) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.824$^{***}$ & $-$0.254$^{***}$ & 0.136$^{***}$ & 0.145$^{***}$ & 0.306$^{***}$ & 0.322$^{***}$ & 0.920$^{***}$ & 1.157$^{***}$ & 0.691$^{**}$ \\ 
+  & (0.019) & (0.010) & (0.003) & (0.034) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.108$^{***}$ & 0.009 & 0.012$^{***}$ & 0.270$^{***}$ & 0.271$^{***}$ & 0.158$^{***}$ & 0.491$^{***}$ & 0.150 & $-$0.274 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.031) & (0.017) & (0.017) & (0.162) & (0.131) & (0.235) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.012 & $-$0.007 & $-$0.001 & $-$0.380$^{***}$ & 0.164$^{***}$ & 0.061$^{***}$ & 0.365$^{***}$ & 0.122$^{**}$ & 0.464$^{***}$ \\ 
+  & (0.011) & (0.005) & (0.002) & (0.018) & (0.009) & (0.008) & (0.074) & (0.060) & (0.126) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.212$^{***}$ & 0.040$^{***}$ & $-$0.031$^{***}$ & $-$0.282$^{***}$ & $-$0.338$^{***}$ & $-$0.205$^{***}$ & $-$0.558$^{***}$ & $-$0.412$^{***}$ & 0.374 \\ 
+  & (0.021) & (0.010) & (0.004) & (0.038) & (0.019) & (0.018) & (0.174) & (0.137) & (0.289) \\ 
+  & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 75,327 & 75,327 & 75,326 & 58,129 & 28,449 & 28,449 & 1,570 & 2,279 \\ 
-R$^{2}$ & 0.102 & 0.073 & 0.108 & 0.011 & 0.063 & 0.089 & 0.114 & 0.207 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 75,327 & 75,327 & 75,326 & 75,390 & 28,449 & 28,449 & 1,570 & 2,279 & 633 \\ 
+R$^{2}$ & 0.102 & 0.073 & 0.108 & 0.017 & 0.075 & 0.091 & 0.128 & 0.209 & 0.266 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-03-07 docs/tab/DID_without_USA_TWN.tex
Updated images, added new images, and updated MS

--- 2019-02-26 docs/tab/DID_without_USA_TWN.tex
@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 9 variables of interest after excluding US and Tawianese vessels.
+1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
 \hline \\[-1.8ex] 
- Constant & 2.661$^{***}$ & 3.154$^{***}$ & 0.393$^{***}$ & 5.256$^{***}$ & 12.977$^{***}$ & 12.434$^{***}$ & 3.776$^{***}$ & 4.722$^{***}$ \\ 
-  & (0.031) & (0.019) & (0.008) & (0.032) & (0.023) & (0.021) & (0.216) & (0.165) \\ 
-  & & & & & & & & \\ 
- Post & 0.313$^{***}$ & $-$0.371$^{***}$ & 0.075$^{***}$ & 0.244$^{***}$ & 0.394$^{***}$ & 0.332$^{***}$ & 1.096$^{***}$ & 0.978$^{***}$ \\ 
-  & (0.024) & (0.014) & (0.006) & (0.022) & (0.016) & (0.016) & (0.158) & (0.127) \\ 
-  & & & & & & & & \\ 
- Treated & $-$0.154$^{***}$ & 0.040$^{***}$ & $-$0.049$^{***}$ & 0.455$^{***}$ & 0.223$^{***}$ & 0.137$^{***}$ & 0.422$^{**}$ & $-$0.062 \\ 
-  & (0.027) & (0.014) & (0.007) & (0.022) & (0.018) & (0.018) & (0.166) & (0.129) \\ 
-  & & & & & & & & \\ 
- Post $\times$ Treated & 0.067$^{**}$ & $-$0.047$^{***}$ & 0.031$^{***}$ & $-$0.482$^{***}$ & $-$0.335$^{***}$ & $-$0.179$^{***}$ & $-$0.475$^{***}$ & $-$0.117 \\ 
-  & (0.028) & (0.017) & (0.007) & (0.025) & (0.020) & (0.019) & (0.179) & (0.145) \\ 
-  & & & & & & & & \\ 
+ Constant & 0.536$^{***}$ & 3.600$^{***}$ & 0.082$^{***}$ & 4.506$^{***}$ & 13.002$^{***}$ & 12.438$^{***}$ & 3.850$^{***}$ & 4.719$^{***}$ & 2.420$^{***}$ \\ 
+  & (0.023) & (0.012) & (0.004) & (0.043) & (0.022) & (0.020) & (0.209) & (0.158) & (0.419) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.796$^{***}$ & $-$0.217$^{***}$ & 0.130$^{***}$ & 0.021 & 0.290$^{***}$ & 0.291$^{***}$ & 0.870$^{***}$ & 0.894$^{***}$ & 0.732$^{**}$ \\ 
+  & (0.019) & (0.010) & (0.003) & (0.035) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.142$^{***}$ & 0.016$^{**}$ & 0.015$^{***}$ & 0.341$^{***}$ & 0.227$^{***}$ & 0.127$^{***}$ & 0.490$^{***}$ & $-$0.017 & $-$0.296 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.031) & (0.018) & (0.017) & (0.163) & (0.126) & (0.239) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.001 & $-$0.001 & 0.001 & $-$0.383$^{***}$ & 0.189$^{***}$ & 0.082$^{***}$ & 0.325$^{***}$ & 0.171$^{***}$ & 0.441$^{***}$ \\ 
+  & (0.011) & (0.006) & (0.002) & (0.019) & (0.009) & (0.008) & (0.075) & (0.063) & (0.122) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.212$^{***}$ & $-$0.002 & $-$0.029$^{***}$ & $-$0.158$^{***}$ & $-$0.328$^{***}$ & $-$0.184$^{***}$ & $-$0.533$^{***}$ & $-$0.225 & 0.339 \\ 
+  & (0.021) & (0.010) & (0.004) & (0.039) & (0.019) & (0.018) & (0.175) & (0.138) & (0.291) \\ 
+  & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 24,005 & 50,737 & 24,005 & 52,825 & 24,005 & 24,005 & 1,375 & 1,981 \\ 
-R$^{2}$ & 0.065 & 0.095 & 0.067 & 0.029 & 0.072 & 0.096 & 0.129 & 0.194 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 73,717 & 73,717 & 73,716 & 73,778 & 26,920 & 26,920 & 1,546 & 2,236 & 660 \\ 
+R$^{2}$ & 0.095 & 0.072 & 0.102 & 0.021 & 0.077 & 0.094 & 0.111 & 0.169 & 0.256 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-03-07 docs/tab/KIR_sp_corr.tex
Updated images, added new images, and updated MS

\begin{table}[H] \centering 
  \caption{\label{tab:KIR_sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for Kiribati EEZ only. The first five columns represent different specifications for number of cells with presence of both fleets. Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels. The explanatory variable is the number of months before or after implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors. The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 30.24$^{***}$ & 32.77$^{***}$ & 23.30$^{***}$ & 26.14$^{***}$ & 16.23$^{***}$ & 0.43$^{***}$ & 0.43$^{***}$ & 0.33$^{***}$ & 0.34$^{***}$ & 0.38$^{***}$ \\ 
  & (2.43) & (4.16) & (4.59) & (5.49) & (2.37) & (0.03) & (0.05) & (0.07) & (0.08) & (0.03) \\ 
  & & & & & & & & & & \\ 
 M & 1.29$^{***}$ & 1.34$^{***}$ & 1.00$^{***}$ & 1.06$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{*}$ & 0.01 &  \\ 
  & (0.14) & (0.17) & (0.27) & (0.30) &  & (0.002) & (0.002) & (0.01) & (0.01) &  \\ 
  & & & & & & & & & & \\ 
 M $^2$ & $-$0.03$^{***}$ & $-$0.04$^{***}$ & $-$0.02$^{**}$ & $-$0.03$^{***}$ &  & 0.0000 & 0.0000 & 0.0001 & 0.0001 &  \\ 
  & (0.01) & (0.01) & (0.01) & (0.01) &  & (0.0002) & (0.0002) & (0.0002) & (0.0002) &  \\ 
  & & & & & & & & & & \\ 
 M $^3$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{**}$ & $-$0.0000$^{**}$ &  \\ 
  & (0.0001) & (0.0001) & (0.0002) & (0.0002) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
  & & & & & & & & & & \\ 
 M $^4$ & 0.0000$^{***}$ & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000$^{***}$ &  & $-$0.0000 & $-$0.0000 & $-$0.0000 & $-$0.0000 &  \\ 
  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
  & & & & & & & & & & \\ 
 NINO4 &  & $-$3.10 &  & $-$4.19 & 9.93$^{***}$ &  & $-$0.001 &  & $-$0.02 & 0.11$^{***}$ \\ 
  &  & (3.97) &  & (4.16) & (3.33) &  & (0.05) &  & (0.06) & (0.03) \\ 
  & & & & & & & & & & \\ 
 $\sigma_1$ &  &  & 9.40 & 10.33 &  &  &  & 0.12 & 0.13 &  \\ 
  &  &  & (5.92) & (6.35) &  &  &  & (0.09) & (0.09) &  \\ 
  & & & & & & & & & & \\ 
 $\sigma_2$ &  &  & $-$2.46 & $-$3.84 &  &  &  & 0.02 & 0.01 &  \\ 
  &  &  & (5.70) & (5.77) &  &  &  & (0.10) & (0.11) &  \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
AIC & 654.294 & 655.536 & 655.482 & 656.125 & 724.58 & -65.872 & -63.873 & -63.481 & -61.572 & -35.895 \\ 
Observations & 84 & 84 & 84 & 84 & 84 & 75 & 75 & 75 & 75 & 75 \\ 
R$^{2}$ & 0.63 & 0.63 & 0.64 & 0.65 & 0.08 & 0.44 & 0.44 & 0.45 & 0.45 & 0.09 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-03-07 docs/tab/main_DID.tex
Updated images, added new images, and updated MS

--- 2019-03-01 docs/tab/main_DID.tex
@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+\begin{table}[H] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 9 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \hline \\[-1.8ex] 
- Constant & 0.497$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 5.206$^{***}$ & 12.997$^{***}$ & 12.461$^{***}$ & 3.678$^{***}$ & 4.445$^{***}$ & 2.420$^{***}$ \\ 
-  & (0.022) & (0.012) & (0.004) & (0.028) & (0.021) & (0.019) & (0.192) & (0.151) & (0.421) \\ 
+ Constant & 0.495$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 4.440$^{***}$ & 12.998$^{***}$ & 12.462$^{***}$ & 3.709$^{***}$ & 4.456$^{***}$ & 2.429$^{***}$ \\ 
+  & (0.022) & (0.012) & (0.004) & (0.042) & (0.021) & (0.019) & (0.195) & (0.151) & (0.415) \\ 
   & & & & & & & & & \\ 
- Post & 0.839$^{***}$ & $-$0.228$^{***}$ & 0.137$^{***}$ & 0.298$^{***}$ & 0.326$^{***}$ & 0.296$^{***}$ & 1.059$^{***}$ & 1.180$^{***}$ & 0.920$^{***}$ \\ 
-  & (0.016) & (0.008) & (0.003) & (0.018) & (0.014) & (0.014) & (0.140) & (0.109) & (0.273) \\ 
+ Post & 0.846$^{***}$ & $-$0.227$^{***}$ & 0.138$^{***}$ & 0.112$^{***}$ & 0.271$^{***}$ & 0.275$^{***}$ & 0.943$^{***}$ & 1.129$^{***}$ & 0.709$^{**}$ \\ 
+  & (0.018) & (0.009) & (0.003) & (0.031) & (0.014) & (0.014) & (0.141) & (0.110) & (0.284) \\ 
   & & & & & & & & & \\ 
- Treated & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.413$^{***}$ & 0.223$^{***}$ & 0.116$^{***}$ & 0.534$^{***}$ & 0.149 & $-$0.244 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.019) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
+ Displaced & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.255$^{***}$ & 0.225$^{***}$ & 0.117$^{***}$ & 0.549$^{***}$ & 0.153 & $-$0.280 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.029) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
   & & & & & & & & & \\ 
- Post $\times$ Treated & $-$0.244$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.513$^{***}$ & $-$0.281$^{***}$ & $-$0.155$^{***}$ & $-$0.565$^{***}$ & $-$0.399$^{***}$ & 0.338 \\ 
-  & (0.019) & (0.009) & (0.003) & (0.022) & (0.017) & (0.017) & (0.161) & (0.127) & (0.288) \\ 
+ NINO4 & $-$0.014 & $-$0.001 & $-$0.001 & $-$0.411$^{***}$ & 0.167$^{***}$ & 0.064$^{***}$ & 0.357$^{***}$ & 0.137$^{**}$ & 0.484$^{***}$ \\ 
+  & (0.011) & (0.005) & (0.002) & (0.017) & (0.008) & (0.007) & (0.068) & (0.056) & (0.122) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.243$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.210$^{***}$ & $-$0.285$^{***}$ & $-$0.157$^{***}$ & $-$0.586$^{***}$ & $-$0.403$^{***}$ & 0.338 \\ 
+  & (0.019) & (0.009) & (0.003) & (0.036) & (0.017) & (0.017) & (0.161) & (0.127) & (0.285) \\ 
   & & & & & & & & & \\ 
@@
 Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 83,052 & 83,052 & 83,051 & 66,981 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
-R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.027 & 0.062 & 0.080 & 0.113 & 0.198 & 0.233 \\ 
+Observations & 83,052 & 83,052 & 83,051 & 79,669 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
+R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.017 & 0.075 & 0.082 & 0.126 & 0.200 & 0.252 \\ 
 \hline 

### 2019-03-07 docs/tab/sp_corr.tex
Updated images, added new images, and updated MS

--- 2019-03-04 docs/tab/sp_corr.tex
@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:sp_corr}Coefficient estimates for a third-polinomial fit to the measures of crowding.
-The first column shows coefficients for the number of cells with treated and control vessels during the same month.
-The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels.
-The explanatory variable is the number of months before implementation of PIPA.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
+\begin{table}[H] \centering 
+  \caption{\label{tab:sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for all PNA waters.
+The first five columns represent different specifications for number of cells with presence of both fleets.
+Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels.
+The explanatory variable is the number of months before or after implementation of PIPA.
+Numbers in parentheses are heteroskedastic-robust standard errors.
+The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.}
   \label{} 
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcc} 
+\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2)\\ 
+\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
 \hline \\[-1.8ex] 
- Constant & 59.999$^{***}$ (15.581) & 0.370$^{***}$ (0.062) \\ 
-  $M$ & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
-  $M^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
-  $M^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
-  $M^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
-  $\sigma_1$ & 22.342 (19.528) & 0.057 (0.076) \\ 
-  $\sigma_2$ & 5.413 (18.860) & $-$0.015 (0.035) \\ 
+ Constant & 78.04$^{***}$ & 84.64$^{***}$ & 60.96$^{***}$ & 66.73$^{***}$ & 80.62$^{***}$ & 0.41$^{***}$ & 0.42$^{***}$ & 0.37$^{***}$ & 0.38$^{***}$ & 0.38$^{***}$ \\ 
+  & (5.44) & (8.99) & (15.60) & (15.99) & (7.96) & (0.01) & (0.03) & (0.06) & (0.07) & (0.02) \\ 
+  & & & & & & & & & & \\ 
+ M & 3.94$^{***}$ & 4.07$^{***}$ & 3.07$^{***}$ & 3.14$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{**}$ & 0.01$^{**}$ &  \\ 
+  & (0.30) & (0.35) & (0.97) & (1.04) &  & (0.001) & (0.001) & (0.003) & (0.004) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^2$ & $-$0.005 & $-$0.02 & 0.01 & $-$0.01 &  & $-$0.0001$^{***}$ & $-$0.0001 & $-$0.0001 & $-$0.0001 &  \\ 
+  & (0.02) & (0.03) & (0.03) & (0.03) &  & (0.0000) & (0.0001) & (0.0001) & (0.0001) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^3$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ &  \\ 
+  & (0.0003) & (0.0003) & (0.001) & (0.001) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^4$ & 0.0000 & 0.0000 & 0.0000 & 0.0000 &  & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000 & 0.0000 &  \\ 
+  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ NINO4 &  & $-$8.09 &  & $-$10.39 & 19.76$^{**}$ &  & $-$0.01 &  & $-$0.01 & 0.07$^{***}$ \\ 
+  &  & (8.29) &  & (9.48) & (9.41) &  & (0.03) &  & (0.03) & (0.02) \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_1$ &  &  & 21.32 & 25.10 &  &  &  & 0.06 & 0.06 &  \\ 
+  &  &  & (19.49) & (22.49) &  &  &  & (0.08) & (0.08) &  \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_2$ &  &  & 5.30 & 3.19 &  &  &  & $-$0.01 & $-$0.02 &  \\ 
+  &  &  & (18.87) & (18.67) &  &  &  & (0.04) & (0.03) &  \\ 
+  & & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes \\ 
-Flag FE & Yes & Yes \\ 
-Observations & 83 & 84 \\ 
-R$^{2}$ & 0.791 & 0.709 \\ 
+NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
+Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
+AIC & 796.937 & 797.991 & 799.477 & 799.97 & 919.583 & -187.208 & -185.269 & -184.916 & -183.233 & -97.386 \\ 
+Observations & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 \\ 
+R$^{2}$ & 0.79 & 0.79 & 0.79 & 0.80 & 0.03 & 0.70 & 0.70 & 0.71 & 0.71 & 0.07 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-04-22 docs/Model_with_trading.Rmd
Added new version from John

---
title: "trade"
author: "Villaseñor-Derbez J.C."
date: "22/3/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The vessel-day price for parcels that do not implement a reserve ($j = c(2, 10)$) is given by:

$$
\pi(E_j) = pqX_j - \beta c E_j ^{\beta - 1}
$$

We can solve for $E_j$:

$$
\begin{split}
\pi_j + \beta c E_j ^{\beta - 1} &= pqX_j \\
\beta c E_j ^{\beta - 1} &= pqX_j - \pi_j \\
E_j ^{\beta - 1} &= \frac{pqX_j - \pi_j}{\beta c } \\
E_j &= \left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1}}
\end{split}
$$
For the parcel that implements the reserve ($i = 1$) the same equations are given by:

$$
\pi_1(E_1) = pqX_1 (\theta + (1 - \theta)(1 - R))- \beta c E_1 ^{\beta - 1}
$$

For simplicity, we can write $\Omega = (\theta + (1 - \theta)(1 - R))$, and the baove becomes

$$
\pi_1(E_1) = pqX_1\Omega - \beta c E_1 ^{\beta - 1}
$$

We can solve for $E_i$ as in the previous casse:

$$
\begin{split}
\pi_1 + \beta c E_1 ^{\beta - 1} &= pqX_1\Omega \\
\beta c E_1 ^{\beta - 1} &= pqX_1\Omega - \pi_1 \\
E_1 ^{\beta - 1} &= \frac{pqX_1\Omega - \pi_1}{\beta c} \\
E_1 &= \left(\frac{pqX_1\Omega - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
\end{split}
$$

The total vessel-days for cells that belong to PNA countries (*i.e.* i = (1, 9)) are constrained at 45,000, which we term $\bar{E}$. Therefore, total effort can be expressed as:

$$
\bar{E} = \left(\frac{pqX_1(\theta + (1 - \theta)(1 - R)) - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}} + 
\sum_{j = 2}^9\left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1} }
$$

This parameterization shows that the cell-level effort is determined by the combination of stock size ($X_j$) and the price $\pi$. Trading between country will continue until all $\pi_i$ reach an equilibrium price of $\bar{\pi}$.

### 2019-04-22 docs/old_ms/PIPA_Palau030319.tex
Added new version from John

--- 2019-03-07 docs/PIPA_Palau030319.tex
@@
 
-ENSO events are known to drive the behavior of fishing vessels, especially in PNA waters, which may drive reallocation of fishing effort \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
 We do our best control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking non-displaced vessels as a group that is equally affected by the environmental variation.
@@
 The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
-The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lehodey_1997,aqorau_2018}.
+The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lhavice_2013,aqorau_2018}.
 Overlaying conservation interventions over existing management schemes must be accompained by similar dialogues and international cooperation, so that the benefits of conservation are captured by those incurring the costs.

### 2019-04-23 scripts/model/1_checks.Rmd
Changed script into Rmd

---
title: "Untitled"
author: "Villaseñor-Derbez J.C."
date: "22/4/2019"
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---
# Setup

## Rmd options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE)

# Clean the environment
rm(list = ls())
```

## Load packages and functions

```{r}
# Load libraries
library(startR)
library(here)
library(cowplot)
library(tidyverse)

# Load functions
source(here("scripts", "model", "grow.R"))
source(here("scripts", "model", "E_vec_fxn.R"))
source(here("scripts", "model", "pi_of_E.R"))
source(here("scripts", "model", "max_Ei.R"))
source(here("scripts", "model", "solve_pi.R"))
```

# Start checks

## Define parameters

```{r}
# Reserve properties
theta <- 1
R <- 0

# Bio
MSY <- 1875600 # 50th percentile from MSY in table 8 of SA (https://www.wcpfc.int/node/27490)
Bmsy <- 1628000 # 50th percentile from SBmsy in table 8 of SA (https://www.wcpfc.int/node/27490)
K <- 6876526 # 50th percentile from SB_f0 in table 8 of SA (https://www.wcpfc.int/node/27490)
Bc_B0 <- 0.51 # 50th percentile from SBlatest/SB_fo in table 8 of SA (https://www.wcpfc.int/node/27490)
Cnow <- 1679444 # Catches now
Bnow <- K * Bc_B0 # current Biomass (2012 - 2015 average)
r <- 0.57 # From fishbase: Prior r = 0.57, 95% CL = 0.41 - 0.78 (https://www.fishbase.in/summary/107#)

# Economic
beta <- 1.3
p <- 1100 # (1447 + 1467) / 2 #mean between thailand and japan values (Value of WCPFC-CA tuna fisheries 2017 report)
E <- 45000
q <- 12 / (0.1 * Bnow) # 2 * (0.8 * Cnow) / (E * 0.8 * Bnow)
c <- 180 # 340
```

### Calculate historical CPUE

One of the first parameters we need to define is initial biomass. To do this, we will calculate CPUE as a proxy of biomass, and then simply distribute total biomass (from the stock assessment) to create a vector of patch-specific current biomass.

```{r}
# Proportion of effort in the high seas
prop_hs <- 0.1
n_patches <- 10
fvec <- c(rep(((1 - prop_hs) / (n_patches - 1)), (n_patches - 1)), prop_hs)
```

#### Effort data

The first step is to load activity data. This dataset contains activity by vessel and EEZ through time. The following code loads the activity dat and calculates hours and proportional hours by year and eez.

```{r}
# Create vector with VDS country iso3 codes
VDS_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL")

# Load historical effort received and summarize
act <- readRDS(here("raw_data", "activity_by_vessel_year_eez.rds")) %>%
  filter(
    eez_iso3 %in% VDS_countries,
    best_vessel_class == "tuna_purse_seines"
  ) %>%
  group_by(year, eez_iso3) %>%
  summarize(days = sum(hours_length) / 24) %>%
  arrange(desc(days)) %>%
  mutate(
    days_prop = days / (sum(days) / (1 - prop_hs)),
    c_days_prop = cumsum(days_prop)
  )
```

This graph shows the data generated above

```{r}
ggplot(data = act, mapping = aes(x = year, y = days)) +
  geom_line() +
  facet_wrap(~eez_iso3, scales = "free_y") +
  labs(x = "year", y = "fishing days") +
  ggtitle("Vessel-days per country")
```

```{r}
ggplot(data = act, mapping = aes(x = year, y = days_prop)) +
  geom_line() +
  facet_wrap(~eez_iso3, scales = "free_y") +
  labs(x = "year", y = "fishing days") +
  ggtitle("Vessel-days per country") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "year", y = "Proportion of vessel-days") +
  ggtitle("Relative effort on each country")
```

#### Catch data

We can now use the FFA catch data for skipjack and estimate yearly catches by EEZ.

```{r}
# Read in the catch data
catches <- read.csv(here("raw_data", "FFA", "ps_skj_catches_spatial_timeseries.csv"), stringsAsFactors = F) %>%
  gather(year, catches, -eez_iso3) %>%
  mutate(year = as.numeric(str_remove(year, "X"))) %>%
  filter(year > 2010) %>%
  mutate(
    PNA = eez_iso3 %in% VDS_countries,
    eez_iso3 = ifelse(PNA, eez_iso3, "HS")
  ) %>%
  group_by(year, eez_iso3) %>%
  summarize(catches = sum(catches))
```

```{r}
ggplot(data = catches, mapping = aes(x = year, y = catches)) +
  geom_line() +
  facet_wrap(~eez_iso3, scales = "free_y", ncol = 3)
```

We can now take catches and divide them by effort to obtain annual CPUE for each EEZ.

```{r}
# Join both data
cpue <- left_join(act, catches, by = c("year", "eez_iso3")) %>%
  drop_na() %>%
  group_by(eez_iso3) %>%
  summarize(
    catches = sum(catches),
    days = sum(days)
  ) %>%
  mutate(cpue = catches / days) %>%
  arrange(desc(cpue)) %>%
  mutate(
    cpue_prop = cpue / (sum(cpue) / (1 - prop_hs)),
    cumsum_cpue_prop = cumsum(cpue_prop),
    eez_iso3 = fct_relevel(eez_iso3, "KIR")
  ) %>%
  arrange(eez_iso3)
```

```{r}
left_join(act, catches, by = c("year", "eez_iso3")) %>%
  drop_na() %>% 
  ggplot(mapping = aes(x = days, y = catches, color = year)) +
  geom_smooth(method = "lm", color = "black") +
  geom_point(size = 4) +
  labs(x = "Effort (days)", y = "Catches (tonnes)") +
  ggtitle("Relationship between effort and catches")
```

```{r}
fvec_cpue <- c(cpue$cpue_prop, prop_hs)
names(fvec_cpue) <- c(levels(cpue$eez_iso3), "HS")

# Chose a source for the fvec
bvec <- fvec_cpue # From CPUE data
# fvec <- fvec_h # From effort data
# Initial biomass distribution should be based on CPUE
# Then, biomass distribution vector should be based on area by EEZ (10 % to HS)
Xvec <- bvec * Bnow
names(fvec) <- names(bvec)
```

# Run some checks

```{r}
# Is there a value of E for the given possible ranges of Biomass?
tibble(X = seq(1, Bnow, length.out = 100)) %>%
  rowwise() %>%
  mutate(E = sum(max_Ei(p = p, q = q, Xvec = X, theta = theta, R = R, beta = beta, c = c))) %>%
  ggplot(aes(x = X, y = E)) +
  geom_line() +
  geom_vline(xintercept = Bmsy) +
  geom_hline(yintercept = E)
```

```{r}
# What's the aggregate demand for a given value of pi with Bmsy?
# FIrst we need to establish the maximum chargable price to plot all ranges from 0 to max_pi
max_pi <- max((p * q * Bnow * fvec))

check_E_pi <- tibble(pi = seq(0, max_pi, length.out = 100)) %>%
  rowwise() %>%
  mutate(E = list(
    tibble(
      E = E_vec_fxn(p = p, q = q, Xvec = Xvec, pi = pi, theta = theta, R = R, beta = beta, c = c),
      cty = names(fvec)
    )
  )) %>%
  unnest() %>%
  filter(!cty == "HS")
```

```{r}
ggplot(data = check_E_pi, mapping = aes(x = E, y = pi, color = cty)) +
  geom_line(size = 1) +
  geom_vline(xintercept = E, color = "red")
```

```{r}
check_E_pi %>%
  group_by(pi) %>%
  summarise(E = sum(E)) %>%
  ggplot(aes(x = E, y = pi)) +
  geom_line() +
  geom_vline(xintercept = E, color = "red") +
  geom_vline(xintercept = sum(max_Ei(p = p, q = q, Xvec = Xvec, theta = theta, R = R, beta = beta, c = c)[1:(n_patches - 1)]))
```

### 2019-04-23 scripts/model/1_checks.R

@@ -1,154 +1,0 @@
-# Clean the environment
-rm(list = ls())
-
-# Load libraries
-library(startR)
-library(here)
-library(cowplot)
-library(tidyverse)
-
-# Load functions
-source(here("scripts", "model", "grow.R"))
-source(here("scripts", "model", "E_vec_fxn.R"))
-source(here("scripts", "model", "pi_of_E.R"))
-source(here("scripts", "model", "max_Ei.R"))
-source(here("scripts", "model", "solve_pi.R"))
-source(here("scripts", "model", "PNA_with_trading.R"))
-source(here("scripts", "model", "PNA_no_trading.R"))
-
-
-
-## Parameters
-# Set up spatial stuff
-# Equal distribution across n patches
-n_patches <- 10
-fvec <- rep(1 / n_patches, n_patches)
-# Arbitrary fvec
-prop_hs <- 0.1
-fvec <- c(rep(((1 - prop_hs) / (n_patches - 1)), (n_patches - 1)), prop_hs)
-n_patches <- length(fvec) # Just as saftey
-
-# Assign fvector based on historical effort distribution
-# Create vector with VDS country iso3 codes
-VDS_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL")
-
-# Load historical effort received and summarize
-act <- readRDS(here("raw_data", "activity_by_vessel_year_eez.rds")) %>%
-  filter(
-    eez_iso3 %in% VDS_countries,
-    best_vessel_class == "tuna_purse_seines"
-  ) %>%
-  group_by(year, eez_iso3) %>%
-  summarize(h = sum(hours) / 24) %>%
-  arrange(desc(h)) %>%
-  mutate(
-    h_prop = h / (sum(h) / (1 - prop_hs)),
-    c_h_prop = cumsum(h_prop)
-  )
-
-catches <- read.csv(here("raw_data", "FFA", "ps_skj_catches_spatial_timeseries.csv"), stringsAsFactors = F) %>%
-  gather(year, catches, -eez_iso3) %>%
-  mutate(year = as.numeric(str_remove(year, "X"))) %>%
-  filter(year > 2010) %>%
-  mutate(
-    PNA = eez_iso3 %in% VDS_countries,
-    eez_iso3 = ifelse(PNA, eez_iso3, "HS")
[…]

### 2019-04-25 docs/slides/NCEAS_presentation.Rmd
Added slides for NCEAS

---
title: "Marine protected areas under effort-control management"
author:
  - Villaseñor-Derbez J.C.$^1$
  - Lynham J.$^2$
  - Costello C.$^{1, 3}$
institute: 
   - $^1$Bren School, UCSB
   - $^2$Department of Economics, UHM
   - $^3$emLAB, UCSB
subtitle: "NCEAS-Future Earth Working Group"
date: "May 6, 2019"
output: beamer_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

## Outline

- Scope of the project

- Approach: model and assumptions

- Data

- Generalizability to Palau

## Background

```{r}

suppressPackageStartupMessages({
  library(startR)
  library(here)
  library(sf)
  library(tidyverse)
  library(ggdark)
})

source(here("scripts", "functions", "st_rotate.R"))

rast <- readRDS(here("data", "rasterized_effort_by_region.rds")) %>% 
  mutate(post = fct_relevel(
    ifelse(year < 2015, "Before", "After"),
    "Before")) %>% 
  group_by(post, x, y) %>%
  summarize(days = log10(sum(hours) / 24)) %>%
  ungroup() %>% 
  filter(between(x, 160, 210),
         between(y, -15, 10))

pipa <- read_sf(dsn = here("data", "spatial", "PIPA"),
                layer = "PIPA") %>% 
  st_rotate()

pna <- read_sf(dsn = here("data", "spatial", "PNA_EEZ"),
               layer = "PNA_EEZ") %>% 
  select(ISO_Ter3) %>% 
  st_simplify(11) %>% 
  st_rotate() %>% 
  st_union(by_feature = T) %>% 
  st_crop(y = c(xmin = 160, xmax = 210, ymin = -15, ymax = 10))

colors = c(
  "#0C276C",
  "#0B3B74",
  "#0A4E7C",
  "#096284",
  "#08768C",
  "#078994",
  "#059D9B",
  "#04B0A3",
  "#03C4AB",
  "#02D8B3",
  "#01EBBB",
  "#00FFC3"
)

ggplot() +
  geom_raster(data = rast,
              mapping = aes(x = x, y = y, fill = days)) +
  geom_sf(data = pna, fill = "transparent", color = "steelblue") +
  geom_sf(data = pipa, fill = "transparent", color = "red", size = 1) +
  facet_wrap(~post, ncol = 1) +
  # scale_fill_viridis_c() +
  scale_fill_gradientn(colors = colors) +
  guides(fill = guide_colorbar(title = quo(log[10]~"(days)"),
                               frame.colour = "white",
                               ticks.colour = "white")) +
  dark_theme_minimal() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(strip.text = element_text(size = 12)) +
  labs(x = "", y = "") +
  ggtitle(label = "Phoenix Islands Protected Area (PIPA), Kiribati")
```

## Scope and Motivation

- For the countries:

  - What are the costs associated to establishing an MPA?

  - What factors drive these costs?

  - How can these costs be reduced or eliminated?

- For the fishing vessels:

  - How do they respond?

  - Where do they go?

## Approach

- 10-patch model of the fishery (9 patches under VDS, one patch under Open Access)

- Vessel-level profits for fishing in patch $i$ are:

$$
\Pi_i(E_i,X_i,R) = pqE_iX_i\Omega_i-cE_i^\beta
$$

- In patch 1, $\Omega_1 = \theta + (1 - \theta)(1 - R)$

- $\Omega = 1$ for patches $i > 1$

- Vessel-day price must equate the marginal profits from the last unit of effort in patches $i = (1, 9)$

$$
\pi_i(E_i) = pqX_i\Omega_i- \beta cE_i^{\beta-1}
$$

## Approach

- Effort is capped at 45,000 vessel-days ($\bar{E}$)

- Measure country-level demand curves

  - No trading: price is patch-specific

  - Trading: price is the same for all patches

```{r}
knitr::include_graphics(path = here("docs", "slides", "img", "demand_curves.png"))
```

## Approach

## Less movement increases costs

```{r}
knitr::include_graphics(here("docs", "slides", "img", "cost_no_trading.png"))
```

## Vessel-day trading reduces costs

```{r}
knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading.png"))
```

## Allocation rules matter

## What can we learn from PIPA

- Implemented in January, 2015

- 397,447 Km^2^

- 1.5 times area of Ecuador

- ~2% of total PNA area

- ~10% of fishing activity in PNA

## Generalizability to Palau

### 2019-04-25 scripts/model/1_checks.Rmd
Added slides for NCEAS

@@
 ---
-title: "Untitled"
+title: "Run some checks"
 author: "Villaseñor-Derbez J.C."
-date: "22/4/2019"
+date: "Updated on `r Sys.Date()`"
 output:
   html_document: 
+    code_folding: hide
     toc: yes
-    toc_float: yes
-    code_folding: show
+    toc_depth: 4
+    toc_float:
+      collapsed: false
 ---
+
+# Model description
+
+We model the PNA as a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
+Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
+The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
+The price of fish is $p$, and catchability is given by $q$.
+
+In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
+The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
+Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season.
+In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$.
+The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
+
+$$
+\begin{align}
+\Pi_1(E_1,X_1,R) = pqE_1X_1(\theta + (1 - \theta)(1 - R))-cE_1^\beta
+\end{align}
+$$
+
+And profits from fishing in Patch $j = \{2, 3, ..., 10\}$ are:
+
+$$
+\begin{align}
+\Pi_j(E_j,X_j) = pqE_jX_j-cE_j^\beta
+\end{align}
+$$
+
+The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
+
+$$
+\begin{align}
+\pi_1(E_1) = pqX_1(\theta + (1 - \theta)(1 - R)) - \beta cE_1^{\beta-1}
+\label{eqn:marginal_profit_1}
+\\
+\pi_j(E_j) = pqX_j - \beta cE_j^{\beta-1}
+\label{eqn:marginal_profit_j}
+\end{align}
+$$
+
+In practice, the effort levels in each PNA patch are given (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics.
+Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
+Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:
+
+$$
+\begin{align}
+E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
+\label{eqn:effort_hs}
+\end{align}
+$$
+
+The patch-level harvest is then determined by effort and stock size:
+
+$$
+\begin{align}
+H_1 = qE_1X_1 (\theta + (1 - \theta)(1 - R))
+\label{eqn:harvest_1}
+\\
+H_j = qE_jX_j
+\label{eqn:harvest_j}
+\end{align}
+$$
+
+Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$.
+The entire stock then grows according to:
+
+$$
+\begin{align}
+X_{t+1} = e_t + \frac{(\phi + 1)}{\phi}ge_t\left(1 - \left(\frac{e_t}{K}\right) ^{\phi}\right)
+\label{eqn:grow}
+\end{align}
+$$
+
+After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
+
+$$
+\begin{align}
+X_{it+1} = f_iX_{t+1}
+\label{eqn:disperse}
+\end{align}
+$$
+
+The vessel-day price that a country charges is given by $\pi_i$ from Equations \ref{eqn:marginal_profit_1} and \ref{eqn:marginal_profit_j}. Therefore, patch-level license revenues are given by:
+
+$$
+\begin{align}
+\omega = \pi_iE_i
+\label{eqn:license_revenue}
+\end{align}
+$$
+
+Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
+Thus, the spillover benefits of increasing $R$ are never completely captured.
+
+The vessel-day price for parcels that do not implement a reserve ($j = c(2, 10)$) is given by:
+
+$$
+\pi(E_j) = pqX_j - \beta c E_j ^{\beta - 1}
+$$
+
+We can solve for $E_j$:
+
+$$
+\begin{split}
+\pi_j + \beta c E_j ^{\beta - 1} &= pqX_j \\
+\beta c E_j ^{\beta - 1} &= pqX_j - \pi_j \\
+E_j ^{\beta - 1} &= \frac{pqX_j - \pi_j}{\beta c } \\
+E_j &= \left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1}}
+\end{split}
+$$
+
+For the parcel that implements the reserve ($i = 1$) the same equations are given by:
+
+$$
+\pi_1(E_1) = pqX_1 (\theta + (1 - \theta)(1 - R))- \beta c E_1 ^{\beta - 1}
+$$
+
+For simplicity, we can write $\Omega = (\theta + (1 - \theta)(1 - R))$, and the baove becomes
+
+$$
+\pi_1(E_1) = pqX_1\Omega - \beta c E_1 ^{\beta - 1}
+$$
+
+We can solve for $E_i$ as in the previous casse:
+
+$$
+\begin{split}
+\pi_1 + \beta c E_1 ^{\beta - 1} &= pqX_1\Omega \\
+\beta c E_1 ^{\beta - 1} &= pqX_1\Omega - \pi_1 \\
+E_1 ^{\beta - 1} &= \frac{pqX_1\Omega - \pi_1}{\beta c} \\
+E_1 &= \left(\frac{pqX_1\Omega - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+\end{split}
+$$
+
+The total vessel-days for cells that belong to PNA countries (*i.e.* i = (1, 9)) are constrained at 45,000, which we term $\bar{E}$. Therefore, total effort can be expressed as:
+
+$$
+\bar{E} = \left(\frac{pqX_1(\theta + (1 - \theta)(1 - R)) - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}} + 
+\sum_{j = 2}^9\left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1} }
+$$
+
+This parameterization shows that the cell-level effort is determined by the combination of stock size ($X_j$) and the price $\pi$.
+Trading between country will continue until all $\pi_i$ reach an equilibrium price of $\bar{\pi}$.
+
 # Setup
@@
 library(cowplot)
+library(magrittr)
 library(tidyverse)
@@
 # Load functions
-source(here("scripts", "model", "grow.R"))
 source(here("scripts", "model", "E_vec_fxn.R"))
@@
 source(here("scripts", "model", "max_Ei.R"))
-source(here("scripts", "model", "solve_pi.R"))
+
+# Some housekeeping
+update_geom_defaults("point",
+                     list(
+                       fill = "steelblue",
+                       color = "black",
+                       shape = 21,
+                       size = 3
+                     ))
+
+update_geom_defaults("line", list(color = "black",
+                                  size = 1))
+
+theme_set(startR::ggtheme_plot(font_size = 8))
 ```
-
-# Start checks
 
@@
 # Read in the catch data
-catches <- read.csv(here("raw_data", "FFA", "ps_skj_catches_spatial_timeseries.csv"), stringsAsFactors = F) %>%
+catches <- read.csv(here("raw_data", "FFA", "ps_skj_catches_spatial_timeseries.csv"),
+                    stringsAsFactors = F) %>%
   gather(year, catches, -eez_iso3) %>%
@@
 
+Let's take a look at the relationship between Effort and Catches:
+
 ```{r}
@@
   drop_na() %>% 
-  ggplot(mapping = aes(x = days, y = catches, color = year)) +
+  ggplot(mapping = aes(x = days, y = catches, fill = year)) +
   geom_smooth(method = "lm", color = "black") +
-  geom_point(size = 4) +
+  geom_point() +
   labs(x = "Effort (days)", y = "Catches (tonnes)") +
-  ggtitle("Relationship between effort and catches")
+  ggtitle("Relationship between effort and catches") +
+  scale_fill_viridis_c()
 ```
@@
 fvec_cpue <- c(cpue$cpue_prop, prop_hs)
+fvec_cpue <- c(0.12, 0.08, 0.07, 0.13, 0.07, 0.12, 0.09, 0.12, 0.1, 0.1)
 names(fvec_cpue) <- c(levels(cpue$eez_iso3), "HS")
@@
 
-# Run some checks
+# Start checks
+
+## Is there a value of $\bar{E}$ for the given possible ranges of Biomass?
+
+The following plot shows the attainable levels of effort given price, catchability and biomass for cases where pi = 0.
+In other words, this just shows if harvesting at all would be profitable even in the absence of a vessel-day price.
+
+The graph shows that for biomass levels between 1 ton and current Byomass (`r Bnow`), many values of $E$ are above $\bar{E}$ (horizontal dashed line)
 
 ```{r}
-# Is there a value of E for the given possible ranges of Biomass?
 tibble(X = seq(1, Bnow, length.out = 100)) %>%
@@
   geom_vline(xintercept = Bmsy) +
-  geom_hline(yintercept = E)
+  geom_hline(yintercept = E, linetype = "dashed") +
+  labs(x = "Biomass", y = "Effort (days)")
 ```
 
+For 95% of the values of biomass, there are attainable levels of effort that would produce positive catches.
+
 ```{r}
-# What's the aggregate demand for a given value of pi with Bmsy?
-# FIrst we need to establish the maximum chargable price to plot all ranges from 0 to max_pi
+tibble(X = seq(1, Bnow, length.out = 100)) %>%
+  rowwise() %>%
+  mutate(E_calc = sum(max_Ei(p = p, q = q, Xvec = X, theta = theta, R = R, beta = beta, c = c)),
+         Eabove = E_calc > E) %$%
+  sum(Eabove)
+```
+
+## What's the aggregate demand for a given value of pi with Bmsy?
+
+First we need to establish the maximum chargable price to plot all ranges from 0 to max_pi.
+
+```{r}
 max_pi <- max((p * q * Bnow * fvec))
+```
 
+For given values, the maximum chargable price for VDS is `r max_pi`.
+Let's create a dataframe with this data.
+This data.frame essentially contains the demand curves for each country, based on the biomass in each patch.
+Biomass comes from the cpue vector we derived.
+
+```{r}
 check_E_pi <- tibble(pi = seq(0, max_pi, length.out = 100)) %>%
@@
     tibble(
-      E = E_vec_fxn(p = p, q = q, Xvec = Xvec, pi = pi, theta = theta, R = R, beta = beta, c = c),
-      cty = names(fvec)
+      E = E_vec_fxn(p = p, q = q, Xvec = 0.9 * Xvec, pi = pi, theta = theta, R = R, beta = beta, c = c),
+      cty = names(fvec),
+      cty2 = as.character(1:length(fvec))
     )
@@
 
+The following graph shows all the demand curves for each country, given a value of E.
+The vertical dashed line shows the $\bar{E}$.
+Its intersections with each demand curve tell us how much vessels would be willing to pay to fish in each country.
+
 ```{r}
-ggplot(data = check_E_pi, mapping = aes(x = E, y = pi, color = cty)) +
+(demands <- ggplot(data = check_E_pi, mapping = aes(x = E / 1000, y = pi, color = cty2)) +
    geom_line(size = 1) +
-  geom_vline(xintercept = E, color = "red")
+   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
+   labs(x = "E (thousand vessel-days)", y = quo(pi)) +
+   guides(color = guide_legend("Patch", ncol = 2)) +
+   theme(legend.position = c(1, 1),
+         legend.justification = c(1, 1)) +
+   scale_color_brewer(palette = "Set1")
+   )
+```
+
+We can aggregate all these demand curves horizontally and obtain the total demand curve. This is essentially the curve along wich we want to find the optimal pi.
+
+```{r}
+(demands_agg <- check_E_pi %>%
+   group_by(pi) %>%
+   summarise(E = sum(E)) %>%
+   ggplot(aes(x = E / 1000, y = pi)) +
+   geom_line() +
+   geom_vline(xintercept = E / 1000, color = "red", linetype = "dashed") +
+   labs(x = "E (thousand vessel-days)", y = quo(pi))
+ )
+```
+
+```{r, fig.width = 7, fig.height = 3.5}
+(demand_curves <- plot_grid(demands, demands_agg, ncol = 2))
 ```
@@
 ```{r}
-check_E_pi %>%
-  group_by(pi) %>%
-  summarise(E = sum(E)) %>%
-  ggplot(aes(x = E, y = pi)) +
-  geom_line() +
-  geom_vline(xintercept = E, color = "red") +
-  geom_vline(xintercept = sum(max_Ei(p = p, q = q, Xvec = Xvec, theta = theta, R = R, beta = beta, c = c)[1:(n_patches - 1)]))
+ggsave(plot = demand_curves,
+       filename = here("docs", "slides", "img", "demand_curves.png"),
+       width = 4,
+       height = 2)
 ```
+
+# Reproducibility chunk
+
+```{r}
+sessionInfo()
+```

### 2019-04-25 scripts/model/2_run_model.Rmd
Added slides for NCEAS

---
title: "Run the model"
author: "Villaseñor-Derbez J.C."
date: "Updated on `r Sys.Date()`"
output:
  html_document: 
    code_folding: show
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: false
---

# Setup

## Rmd options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE)

# Clean the environment
rm(list = ls())
```

## Load packages and functions

```{r}
# Load libraries
library(startR)
library(here)
library(cowplot)
library(tidyverse)

# Load functions
source(here("scripts", "model", "grow.R"))
source(here("scripts", "model", "E_vec_fxn.R"))
source(here("scripts", "model", "pi_of_E.R"))
source(here("scripts", "model", "max_Ei.R"))
source(here("scripts", "model", "solve_pi.R"))
source(here("scripts", "model", "PNA_with_trading.R"))
source(here("scripts", "model", "PNA_no_trading.R"))

# Some housekeeping
update_geom_defaults("point",
                     list(
                       fill = "steelblue",
                       color = "black",
                       shape = 21,
                       size = 3
                     ))

update_geom_defaults("line", list(color = "black",
                                  size = 1))

theme_set(startR::ggtheme_plot())
```

## Define parameters

```{r}
# Reserve properties
theta <- 1
R <- 0

# Bio
MSY <- 1875600 # 50th percentile from MSY in table 8 of SA (https://www.wcpfc.int/node/27490)
Bmsy <- 1628000 # 50th percentile from SBmsy in table 8 of SA (https://www.wcpfc.int/node/27490)
K <- 6876526 # 50th percentile from SB_f0 in table 8 of SA (https://www.wcpfc.int/node/27490)
Bc_B0 <- 0.51 # 50th percentile from SBlatest/SB_fo in table 8 of SA (https://www.wcpfc.int/node/27490)
Cnow <- 1679444 # Catches now
Bnow <- K * Bc_B0 # current Biomass (2012 - 2015 average)
r <- 0.57 # From fishbase: Prior r = 0.57, 95% CL = 0.41 - 0.78 (https://www.fishbase.in/summary/107#)

# Economic
beta <- 1.3
p <- 1100 # (1447 + 1467) / 2 #mean between thailand and japan values (Value of WCPFC-CA tuna fisheries 2017 report)
E <- 45000
q <- 12 / (0.1 * Bnow) # 2 * (0.8 * Cnow) / (E * 0.8 * Bnow)
c <- 180 # 340

# Vectors of initial biomass and movement
# Proportional size of the high seas
prop_hs <- 0.1
# Number of patches
n_patches <- 10
# Biomass redistribution vector
fvec <- c(rep(((1 - prop_hs) / (n_patches - 1)), (n_patches - 1)), prop_hs)
# fvec <- c(0.12, 0.08, 0.07, 0.13, 0.07, 0.12, 0.09, 0.12, 0.1, 0.1)
names(fvec) <- c("KIR", "FSM", "MHL", "NRU", "PLW", "PNG", "SLB", "TKL", "TUV", "HS")
Xvec <- Bnow * fvec
```

# Cost of a reserve is governed by fish movement

> Less movement leads to higer costs

This first par uses no trading, but allows us to look at how movement ($\theta$) governs costs. The intuition is that, given the parameterization, high movement rates will lead to low costs because:

$$\Omega = \theta + (1 - \theta)(1 - R)$$

This shows that, no matter what the size of the reserve is, when $\theta = 1$, $\Omega = 1$.

## Get initial conditions

We first run a model that allows for trading to get the Effort vector that would maximize $pi$.

```{r}
Benchmark_results <-
  PNA_with_trading(
    fvec = fvec,
    theta = theta,
    R = R,
    r = r,
    K = K,
    p = p,
    q = q,
    Xvec = Xvec,
    beta = beta,
    c = c,
    E = E
  ) %>%
  select(
    Country,
    b_harvest = Harvest,
    b_vessel_days = Vessel_Days,
    b_stock = Stock,
    b_stock_i = Stock_i,
    b_vdsprice = VDSprice,
    b_vdsrevenue = VDSrevenue,
    b_vdsrevenue_all = VDSrevenue_all,
    b_vdsrevenue_notKIR = VDSrevenue_notKIR
  )
```

We then take these results, and use the observed efforts as the optimal efforts.

```{r}
Evec <- Benchmark_results$b_vessel_days

Evec
```

## Run the model

We now run the model with **NO** trading, using the Evec above as starting condition.

```{r}
# Create an empty tibble to store the results in the process
Rvec <- seq(0, 1, 0.05)
thetavec <- seq(0, 1, 0.1)

DF_results_no_trading <-
  expand.grid(R = Rvec, theta = thetavec) %>%
  mutate(
    res = map2(
      theta,
      R,
      PNA_no_trading,
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      Evec = Evec
    )
  ) %>%
  unnest()
```

We now take these results and add the benchmark results (no reserve) to calculate the cost of the reserve as the change in revenue. The proportional way of saying this is:

$$
\%C_R = \frac{\Pi_{R = 0} - \Pi_{R = r}}{\Pi_{R = 0}}
$$
Where $\Pi_{R = 0}$  is the vessel-day revenue when there is no reserve, hence the $R = 0$ subindex. The $\Pi_{R = r}$ denotes the vessel-day revenues when reserve has size ($r \in (0, 1)$). The vessel-day revenue is simply the vessel-day price times the number of vessel-days in patch $i$: $\pi \times E_i$.

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue
  )
```

We can now go ahead and plot these results. The figure below shows the $C_R$ defined above for different size of reserves $R$ in the x-axis, given values of $theta$ (colors). The graph shows how a smaller movement rate leads to increased costs to the country that implements the reserve. A movement of $\theta = 1$ implies no reserve, and thus leads to no losses. However, this parameter is unlikely. We also see how the losses are not proportional to 1. That is, a 10% closure does not lead to a 10% loss in profits.

**Is this due to the concavity in costs? i.e. the $\beta$ parameter$?**

Yes, it looks like a $\beta = 1.1$ actually reduces this.

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Costs (% of case with no reserve)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

```{r}
ggsave(plot = costs_no_trading_plot,
       filename = here("docs", "slides", "img", "cost_no_trading.png"),
       width = 3,
       height = 3)
```

# Trading affects costs

> Trading reduces costs to implementing party

We now run the same model, with same initial conditions, but allow trading as a reserve is closed.

```{r}
DF_results_with_trading <-
  expand.grid(R = Rvec, theta = thetavec) %>%
  mutate(
    res = map2(
      theta,
      R,
      PNA_with_trading,
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest()
```

Again, put it together with the reference values to calculate costs.

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue
  )
```

The following graph shows the same information as the graph above. However, in this case, the costs are significantly lower. This is because a party can sell it's original allocation to other parties. The reduction i

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot,
       filename = here("docs", "slides", "img", "cost_with_trading.png"),
       width = 3,
       height = 3)
```

## Cost reduction due to trading

```{r}
shorter_no_trading <- DF_1_no_trading %>% 
  select(Country, R, theta, Vessel_Days, VDSprice, VDSrevenue, cost, rel_cost)

shorter_trading <- DF_1_with_trading %>% 
  select(Country, R, theta, Vessel_Days_trading = Vessel_Days, pi_trading = VDSprice, VDSrevenue_trading = VDSrevenue, cost_trading = cost, rel_cost_trading = rel_cost)

both <- left_join(shorter_no_trading, shorter_trading, by = c("Country", "R", "theta")) %>% 
  mutate(delta_cost = cost - cost_trading,
         rel_delta_cost = delta_cost / cost) %>% 
  filter(!R == 0,
         !theta == 1)
```

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided by trading") +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

All together

```{r, fig.width = 4, fig.height = 7}
(cost_plot <- cowplot::plot_grid(costs_no_trading_plot,
                   costs_with_trading_plot,
                   delta_costs_plot, ncol = 1))
```

Now let's save this figure.

```{r}
ggsave(plot = cost_plot,
       filename = here("docs", "img", "cost_plot.pdf"), width = 4, height = 7)
```

## How does vessel-price change?

### When there's no trading

```{r}
DF_results_no_trading %>% 
  filter(!Country == "HS") %>% 
  mutate(Country = fct_relevel(Country, "KIR")) %>% 
  ggplot() +
  geom_line(aes(
    x = R,
    y = VDSprice,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-day Price ("~pi~")")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black")) +
  facet_wrap(~Country, scales = "free_y")
```

### When there is trading

```{r}
ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = VDSprice,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-day Price ("~pi~")")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black"))
```

## Where do vessels go?

### With no trading

```{r}
DF_results_no_trading %>% 
  filter(!Country == "HS") %>%
  mutate(Country = fct_relevel(Country, "KIR")) %>% 
  ggplot() +
  geom_line(aes(
    x = R,
    y = Vessel_Days,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-Days")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black")) +
  facet_wrap(~Country, scales = "free_y")
```

# Reproducibility chunk

```{r}
sessionInfo()
```

### 2019-04-25 scripts/model/2_run_model.R

@@ -97,7 +97,7 @@ DF_results <- DF_results %>%
 ## NO TRADING
 Evec <- Benchmark_results$b_vessel_days
 
-Benchmark_results2 <-
+Benchmark_results_no_trading <-
   PNA_no_trading(
     fvec = fvec,
     theta = theta,

### 2019-05-04 docs/slides/NCEAS_presentation.Rmd
Updatesd slides for NCEAS

@@
 ---
-title: "Marine protected areas under effort-control management"
+title: "Marine Conservation and Fishing Effort Markets"
 author:
@@
 date: "May 6, 2019"
-output: beamer_presentation
+output: 
+  beamer_presentation: 
+    theme: Darmstadt
+header-includes:
+  - \usepackage{media9}
 ---
@@
                       message = FALSE,
-                      warning = FALSE)
+                      warning = FALSE#,
+                      # fig.align = "center"
+                      )
+
+suppressPackageStartupMessages({
+  library(here)
+})
 ```
@@
 
+- Background and motivation
+
 - Scope of the project
 
-- Approach: model and assumptions
+- Approach
 
-- Data
+  - Model and assumptions
+
+  - Phoenix Island Protected Area
 
@@
 
-## Background
+# Background and motivation
 
-```{r}
+## Motivation
 
-suppressPackageStartupMessages({
-  library(startR)
-  library(here)
-  library(sf)
-  library(tidyverse)
-  library(ggdark)
-})
+\begin{center}
+	\includemedia[
+    label=video1,
+    width=300pt,height=225pt,%width=300pt,height=225pt,
+	]{}{GFW_video.swf}
 
-source(here("scripts", "functions", "st_rotate.R"))
+    \mediabutton[mediacommand=video1:playPause,
+    overface=\color{blue}{\fbox{\strut Play/Pause}},
+    downface=\color{red}{\fbox{\strut Play/Pause}}
+    ]{\fbox{\strut Play/Pause}}
+\end{center}
 
-rast <- readRDS(here("data", "rasterized_effort_by_region.rds")) %>% 
-  mutate(post = fct_relevel(
-    ifelse(year < 2015, "Before", "After"),
-    "Before")) %>% 
-  group_by(post, x, y) %>%
-  summarize(days = log10(sum(hours) / 24)) %>%
-  ungroup() %>% 
-  filter(between(x, 160, 210),
-         between(y, -15, 10))
+## Motivation
 
-pipa <- read_sf(dsn = here("data", "spatial", "PIPA"),
-                layer = "PIPA") %>% 
-  st_rotate()
+### Relationship between closure size and losses
 
-pna <- read_sf(dsn = here("data", "spatial", "PNA_EEZ"),
-               layer = "PNA_EEZ") %>% 
-  select(ISO_Ter3) %>% 
-  st_simplify(11) %>% 
-  st_rotate() %>% 
-  st_union(by_feature = T) %>% 
-  st_crop(y = c(xmin = 160, xmax = 210, ymin = -15, ymax = 10))
+Does a 30\% closure mean a 30\% loss in revenue?
 
-colors = c(
-  "#0C276C",
-  "#0B3B74",
-  "#0A4E7C",
-  "#096284",
-  "#08768C",
-  "#078994",
-  "#059D9B",
-  "#04B0A3",
-  "#03C4AB",
-  "#02D8B3",
-  "#01EBBB",
-  "#00FFC3"
-)
+# Scope and Approach
 
-ggplot() +
-  geom_raster(data = rast,
-              mapping = aes(x = x, y = y, fill = days)) +
-  geom_sf(data = pna, fill = "transparent", color = "steelblue") +
-  geom_sf(data = pipa, fill = "transparent", color = "red", size = 1) +
-  facet_wrap(~post, ncol = 1) +
-  # scale_fill_viridis_c() +
-  scale_fill_gradientn(colors = colors) +
-  guides(fill = guide_colorbar(title = quo(log[10]~"(days)"),
-                               frame.colour = "white",
-                               ticks.colour = "white")) +
-  dark_theme_minimal() +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  theme(strip.text = element_text(size = 12)) +
-  labs(x = "", y = "") +
-  ggtitle(label = "Phoenix Islands Protected Area (PIPA), Kiribati")
-```
+## Scope
 
-## Scope and Motivation
+Can economic instruments incentivize conservation?
 
@@
 
-  - How can these costs be reduced or eliminated?
+  - Can these costs be reduced or eliminated?
 
@@
 
-- 10-patch model of the fishery (9 patches under VDS, one patch under Open Access)
+- 10-patch model of the tuna purse-seine fishery
 
-- Vessel-level profits for fishing in patch $i$ are:
+  - 9 patches under VDS
+  - one patch under Open Access
 
-$$
-\Pi_i(E_i,X_i,R) = pqE_iX_i\Omega_i-cE_i^\beta
-$$
+- Profits from fishing in patch $i$ are:
 
-- In patch 1, $\Omega_1 = \theta + (1 - \theta)(1 - R)$
+$$\Pi_i(E_i,X_i,R) = pqE_iX_i\Omega_i-cE_i^\beta$$
 
-- $\Omega = 1$ for patches $i > 1$
+$$\Omega_1 = \theta + (1 - \theta)(1 - R)$$
 
@@
 
-$$
-\pi_i(E_i) = pqX_i\Omega_i- \beta cE_i^{\beta-1}
-$$
+$$\pi_i(E_i) = pqX_i\Omega_i- \beta cE_i^{\beta-1}$$
 
@@
 
+- Patch-level effort is then
+
+$$E_i = \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ { \frac{1}{\beta - 1}}$$
+
 - Effort is capped at 45,000 vessel-days ($\bar{E}$)
+
+$$\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}$$
+
+## Approach
 
@@
 ```{r}
+# Recortar para que salgan hasta 3000 y 10000 solamente
 knitr::include_graphics(path = here("docs", "slides", "img", "demand_curves.png"))
@@
 
-## Approach
+# Model predictions
 
-## Less movement increases costs
+## Model predictions
+
+### Relationship between closure size and losses
+
+Does a 30\% closure mean a 30\% loss in revenue?
+
+## Losses with no trading
 
@@
 
-## Vessel-day trading reduces costs
+## Model predictions
+
+### A market for fishing efforts
+
+- What is the effect of trading?
+
+- Can costs be reduced?
+
+## Trading significantly reduces costs
+
+```{r}
+knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading_long_axis.png"))
+```
+
+## Trading significantly reduces costs
 
@@
 
-## What can we learn from PIPA
+- Vessel-days are allocated to countries each year
+
+- Combination of biomass and in-EEZ usage
+
+$$
+E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
+(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
+$$
+
+- $\alpha$ is a weight on historical effort ($E_i$) and historical biomass ($B_i$)
+
+What is the importance of allocation rules?
+
+## "*Biomass-based*" allocation reduces costs
+
+```{r}
+knitr::include_graphics(here("docs", "slides", "img", "allocation_cost_plot.pdf"))
+```
+
+# PIPA
+
+## What can we learn from PIPA?
+
+PIPA:
 
@@
 
-- 397,447 Km^2^
+- 397,447 $Km^2$
 
-- 1.5 times area of Ecuador
+- ~2\% of total PNA area
 
-- ~2% of total PNA area
+- ~10\% of fishing activity in PNA
 
-- ~10% of fishing activity in PNA
+GFW data:
 
-## Generalizability to Palau
+- 313 tuna purse seine vessels that fished in PNA
+
+- 92 Fished both before and after PIPA implementation:
+
+  - 64 Fished within PIPA before implementation
+
+- Devideded into three groups
+
+## Two fleets
+
+```{r}
+knitr::include_graphics(here("docs", "slides", "img", "sample_tracks.png"))
+```
+
+## Effort displacement
+
+```{r}
+knitr::include_graphics(here("docs", "img", "all_PS_VDS_year.pdf"))
+```
+
+## Effort displacement in Kiribati
+
+```{r}
+knitr::include_graphics(here("docs", "img", "all_PS_VDS_KIR_year.pdf"))
+```
+
+## Effort displacement raster
+
+```{r}
+knitr::include_graphics(here("docs", "img", "rasterized_change.png"))
+```
+
+# Generalizability to Palau
+
+# Extra slides - GFW data
+
+## Effort vs catches
+
+```{r}
+knitr::include_graphics(here("docs", "slides", "img", "catch_effort_plot.png"))
+```
+
+## Effort and revenues
+
+```{r}
+knitr::include_graphics(here("docs", "img", "revenue_FFA_GFW_linear.pdf"))
+```
+
+## Vessel statistics
+
+A short table with information on number of vessels per year and class
+
+Palau-specific information about longliners

### 2019-05-04 scripts/model/1_checks.Rmd
Moved modelling scripts to Rmd files

@@
 ```{r}
-left_join(act, catches, by = c("year", "eez_iso3")) %>%
+(catch_effort_plot <- left_join(act, catches, by = c("year", "eez_iso3")) %>%
    drop_na() %>% 
-  ggplot(mapping = aes(x = days, y = catches, fill = year)) +
+   ggplot(mapping = aes(x = days, y = catches / 1000, fill = year)) +
    geom_smooth(method = "lm", color = "black") +
    geom_point() +
-  labs(x = "Effort (days)", y = "Catches (tonnes)") +
+   labs(x = "Effort (days)", y = "Catches (Thousannd tonnes)") +
    ggtitle("Relationship between effort and catches") +
-  scale_fill_viridis_c()
+   scale_fill_viridis_c() +
+   guides(fill = guide_colorbar(title = "Year",
+                                frame.colour = "black",
+                                ticks.colour = "black")))
+```
+
+```{r}
+ggsave(plot = catch_effort_plot,
+       filename = here("docs", "slides", "img", "catch_effort_plot.png"),
+       width = 4,
+       height = 3)
 ```
@@
 ```{r}
-(demands <- ggplot(data = check_E_pi, mapping = aes(x = E / 1000, y = pi, color = cty2)) +
+(demands <- ggplot(data = filter(check_E_pi, E < 300000),
+                   mapping = aes(x = E / 1000, y = pi, color = cty2)) +
    geom_line(size = 1) +
@@
    guides(color = guide_legend("Patch", ncol = 2)) +
-   theme(legend.position = c(1, 1),
-         legend.justification = c(1, 1)) +
+   theme(legend.position = "none") +
    scale_color_brewer(palette = "Set1")
@@
    summarise(E = sum(E)) %>%
+   ungroup() %>% 
+   filter(E < 300000) %>% 
    ggplot(aes(x = E / 1000, y = pi)) +

### 2019-05-04 scripts/model/2_run_model.Rmd
Moved modelling scripts to Rmd files

@@
 library(startR)
+library(magrittr)
 library(here)
 library(cowplot)
+library(furrr)
 library(tidyverse)
@@
 ```{r, fig.width = 4, fig.height = 4}
+(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
+  geom_line(aes(
+    x = R,
+    y = rel_cost,
+    group = theta,
+    color = theta
+  ),
+  size = 1
+  ) +
+  xlab("Portion of patch as reserve (R)") +
+  ylab("Costs (% of case with no reserve)") +
+  scale_color_viridis_c() +
+  startR::ggtheme_plot() +
+  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
+  theme(legend.position = "None"))
+```
+
+```{r}
+ggsave(plot = costs_with_trading_plot_long_axis,
+       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
+       width = 3,
+       height = 3)
+```
+
+```{r}
 (costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
@@
   ylab("Costs avoided by trading") +
-  scale_color_viridis_c() +
+  scale_color_viridis_c(limits = c(0, 1)) +
   theme(
@@
 
-## Where do vessels go?
-
-### With no trading
+# Allocation rules matter
 
 ```{r}
-DF_results_no_trading %>% 
-  filter(!Country == "HS") %>%
-  mutate(Country = fct_relevel(Country, "KIR")) %>% 
-  ggplot() +
-  geom_line(aes(
-    x = R,
-    y = Vessel_Days,
-    group = theta,
-    color = theta
+source(here("scripts", "model", "allocate.R"))
+source(here("scripts", "model", "allocate_wrap.R"))
+source(here("scripts", "model", "move_in_time.R"))
+source(here("scripts", "model", "move_in_time_no_trading.R"))
+```
+
+We first obtain the optimal allocation by running the model until steady state and with no reserves.
+
+```{r}
+
+alphas <- c(0, 0.25, 0.5, 0.75, 1)
+
+delta <- 1 / 1.1
+
+plan(multiprocess)
+
+allocation <-
+  expand.grid(
+    R = Rvec,
+    theta = c(0, 0.5, 1),
+    alpha = alphas,
+    trade = c(T, F)
+  ) %>%
+  as_tibble() %>%
+  mutate(
+    resutls = future_pmap(
+      .l = list(
+        alpha = alpha,
+        R = R,
+        theta = theta,
+        trade = trade
       ),
-  size = 1
-  ) +
+      .f = allocate_wrap, 
+      fvec = fvec,
+      r = r,
+      K = K,
+      p = p,
+      q = q,
+      Xvec = Xvec,
+      beta = beta,
+      c = c,
+      E = E
+    )
+  ) %>%
+  unnest() %>%
+  filter(country == "KIR") %>%
+  mutate(
+    rev_dir = Ei * pi,
+    deltaE = Ea - Ei,
+    rev_sells = deltaE * pi,
+    rev_tot = rev_dir + rev_sells,
+    fct = delta ^ year,
+    rev_tot_disc = rev_tot * fct
+  )
+
+best_rev <- allocate_wrap(
+  alpha = 0,
+  R = 0,
+  theta = 1,
+  trade = T,
+  fvec = fvec,
+  r = r,
+  K = K,
+  p = p,
+  q = q,
+  Xvec = Xvec,
+  beta = beta,
+  c = c,
+  E = E
+) %>%
+  filter(country == "KIR") %>%
+  mutate(
+    rev_dir = Ei * pi,
+    deltaE = Ea - Ei,
+    rev_sells = deltaE * pi,
+    rev_tot = rev_dir + rev_sells,
+    fct = delta ^ year,
+    rev_tot_disc = rev_tot * fct
+  ) %$%
+  sum(rev_tot_disc)
+```
+
+```{r}
+(allocation_cost_plot <- allocation %>%
+  mutate(trade = ifelse(trade, "Trading", "No Trading"),
+         theta = as.character(theta)) %>% 
+  group_by(trade, alpha, R, theta) %>%
+  summarize(rev = sum(rev_tot_disc)) %>%
+  ungroup() %>%
+  mutate(cost = (best_rev - rev) / best_rev) %>%
+  ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
+  geom_line(size = 1) +
+  scale_y_continuous(labels = scales::percent) +
   xlab("Portion of patch as reserve (R)") +
-  ylab(quo("Vessel-Days")) +
+  ylab("Costs (% of case with no reserve)") +
   scale_color_viridis_c() +
-  theme(
-    text = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  ) +
-  startR::ggtheme_plot() +
-  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
-                                ticks.colour = "black",
-                                frame.colour = "black")) +
-  facet_wrap(~Country, scales = "free_y")
+  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
+  ggtheme_plot() +
+  facet_wrap(~trade) +
+  guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")")),
+         linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"))))
+```
+
+```{r}
+ggsave(
+  plot = allocation_cost_plot,
+  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
+  width = 5,
+  height = 3
+)
+```
+
+```{r}
+allocation %>%
+  filter(!trade) %>% 
+  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
+  geom_line(size = 1) +
+  facet_grid(alpha ~ theta) +
+  scale_color_viridis_c() +
+  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
+  ggtheme_plot()
+```
+
+```{r}
+allocation %>%
+  filter(theta == 0.5, !trade) %>% 
+  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
+  geom_line(size = 1) +
+  facet_grid(~alpha) +
+  scale_color_viridis_c() +
+  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
+  ggtheme_plot()
 ```

### 2019-05-04 scripts/model/PNA_with_trading.R

@@ -33,7 +33,7 @@ PNA_with_trading <- function(fvec = NULL, theta = NULL, R = NULL, r = NULL, K = 
     err = 0
   )
   
-  tol <- 0.001 * Bnow
+  tol <- 0.0001 * Bnow
   diff <- (tol * 2)^2
   
   ct <- 1

### 2019-05-04 scripts/model/allocate_wrap.R

@@ -1,0 +1,128 @@
+#' Allocate wrap
+#' 
+#' @description This is a wrapper function to call allocate multiple
+#' times and estimate different scenarios of the input parameters
+#'
+#' @param alpha 
+#' @param R 
+#' @param theta 
+#' @param trade 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+allocate_wrap <- function(alpha, R, theta, trade = NULL, fvec = NULL, r = NULL, K = NULL, p = NULL, q = NULL, beta = NULL, c = NULL, E = NULL, Xvec = NULL) {
+  
+  # Calculate year 0, with no reserve and trading to get optimal allocations
+  no_reserve <-
+    PNA_with_trading(
+      fvec = fvec,
+      theta = 1,
+      R = 0,
+      r = r,
+      K = K,
+      p = p,
+      q = q,
+      Xvec = Xvec,
+      beta = beta,
+      c = c,
+      E = E
+    ) %>%
+    mutate(year = 0,
+           Ea = Vessel_Days) %>%
+    select(
+      year,
+      country = Country,
+      Ea,
+      Ei = Vessel_Days,
+      Xi = Stock_i,
+      pi = VDSprice
+    )
+  
+  # Xvec <- no_reserve$Xi
+  # Ea <- no_reserve$Ea
+  # no_reserve <-
+  #   move_in_time(
+  #     fvec = fvec,
+  #     theta = theta,
+  #     R = R,
+  #     r = r,
+  #     K = K,
+  #     p = p,
+  #     q = q,
+  #     Xvec = Xvec,
+  #     beta = beta,
+  #     c = c,
+  #     E = E,
+  #     Ea = Ea,
+  #     year = 0
+  #   )
+  
+  if(trade) {
+
+    ##### START TESTING
+    Xvec <- no_reserve$Xi
+    Ea <- no_reserve$Ea
+    reserve <-
+      move_in_time(
+        fvec = fvec,
+        theta = theta,
+        R = R,
+        r = r,
+        K = K,
+        p = p,
+        q = q,
+        Xvec = Xvec,
+        beta = beta,
+        c = c,
+        E = E,
+        Ea = Ea,
+        year = 1
+      )
+    
+    #### END TETING ##########
+    
+  } else {
+    # Extract optimal allocation vector of efforts
+    Evec <- no_reserve$Ei
+    
+    # Calculate effort received per patch on every year
+    reserve <- 
[…]

### 2019-05-04 scripts/short.R

@@ -277,66 +277,20 @@ test %>%
 
 
 
-check_losses <- function(alpha, R, theta) {
-  no_reserve <- PNA_with_trading(fvec = fvec, theta = theta, R = R, r = r, K = K, p = p, q = q, Xvec = Xvec, beta = beta, c = c, E = E) %>%
-    mutate(
-      year = 0,
-      Ea = Vessel_Days,
-    ) %>%
-    select(
-      year,
-      country = Country,
-      Ea,
-      Ei = Vessel_Days,
-      Xi = Stock_i,
-      pi = VDSprice
-    )
 
 
-  reserve <- PNA_with_trading(fvec = fvec, theta = 0.5, R = 0.1, r = r, K = K, p = p, q = q, Xvec = Xvec, beta = beta, c = c, E = E) %>%
-    mutate(
-      year = 1,
-      Ea = no_reserve$Ea
-    ) %>%
-    select(
-      year,
-      country = Country,
-      Ea,
-      Ei = Vessel_Days,
-      Xi = Stock_i,
-      pi = VDSprice
-    )
 
-  alloc_input <- rbind(no_reserve, reserve) %>%
-    filter(!country == "HS")
-
-  allocations <- alloc_input %>%
-    filter(year == 100)
-
-  for (i in 1:8) {
-    alloc_i <- allocate(
-      alloc_input = alloc_input,
-      alpha = alpha,
-      year = i
-    )
-    alloc_input <- rbind(alloc_input, alloc_i)
-  }
-
-  return(alloc_input)
-}
-
-
-Rs <- c(0.1, 0.3)
-thetas <- seq(0, 1, by = 0.2)
-alphas <- seq(0, 1, by = 0.1)
+thetas <- c(0)
+alphas <- c(0, 0.5, 1)
+trades <- c(T, F)
 
 delta <- 1 / 1.1
 
 plan(multiprocess)
 
-jc <- expand.grid(R = Rs, theta = thetas, alpha = alphas) %>%
+jc <- expand.grid(R = Rvec, theta = thetas, alpha = alphas, trade = trades) %>%
   as_tibble() %>%
-  mutate(resutls = furrr::future_pmap(.l = list(alpha = alpha, R = R, theta = theta), .f = check_losses)) %>%
+  mutate(resutls = future_pmap(.l = list(alpha = alpha, R = R, theta = theta, trade = trade), .f = check_losses)) %>%
   unnest() %>%
[…]

### 2019-05-14 docs/old_ms/PIPA_Palau_special.tex
Moved old ms to old ms folder

--- 2019-04-22 docs/old_ms/PIPA_Palau030319.tex
@@
 \author[b]{John Lynham}
-\author[a]{Christopher Costello}
 
@@
 \significancestatement{The oceans are becoming increasingly crowded, with different activities competing for space.
-Marine Protected Areas are inherently spatial, and have the sole objective of conserving bounded waters by displacing or limiting fishing effort.
-Our work shows that when a fishery is managed by limiting effort (\emph{e.g.} with a Vessel-Day Scheme), spatial closures displace fishing effort at a high cost to the implementing country, and that the benefits are perceived by other countries.
-With global conservation targets seeking to protect 10\% of the world’s ocean by 2020 and the expansion of offshore aquaculture, it is important that the spatial displacement of economic activities is fully considered.}
+Marine Protected Areas are inherently spatial, and have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
+Our work shows that when a fishery is managed by selling effort rights (\emph{e.g.} with a Vessel-Day Scheme), spatial closures displace fishing effort at a cost to the implementing country, with benefits to other countries.
+Costs can be offset if effort rights are tradable across countries.
+With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.}
 
@@
 The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters.
-In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities.
-Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as induce costs (due to the reduction in fishable area) to Kiribati.
-We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution, behavior, and costs to Kiribati and the PNA.
+In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities.
+Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as short-term costs (due to the reduction in fishable area).
+We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution and behavior, as well as costs to Kiribati and the PNA.
 We find a crowding effect within PNA waters after the implementation of the protected area.
-Vessels continue to fish with similar intensity after the implementation.
 In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold.
-However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue.
+However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in license and access fee revenue.
+These changes are robust to controlling for the effects of El Ni\~{n}o on spatial distribution of fishing effort.
 At the same time, fishing effort increases in other parts of the PNA.
-This redistribution of fishing effort eventually results in a reduction of 5,195 vessel-days in Kiribati, which represents a loss of \$46.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).
+This redistribution of fishing effort eventually results in a reduction of 5,195 vessel-days in Kiribati, which implies a loss of around \$50 million USD; but much lower losses are reported in official government reports (\$30.5 million USD), suggesting that the tradable nature of the VDS system is buffering the cost for Kiribati.
 We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
@@
 In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs; areas larger than 30,000 km\textsuperscript{2} \emph{sensu} \cite{desanto_2013}).
-Today, a small number of LSMPAs represent at least 80\% of the managed areas in the ocean (Fig.
+Today, a small number of LSMPAs represent at least 80\% of the protected area in the ocean (Fig.
 \ref{fig:LSMPAs_map}; \citep{toonen_2013}).
@@
 
-The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas.
+The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth.
 Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area where approximately 50\% of the world's tuna is caught.
 Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA).
-Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the PNA group in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
+Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the VDS in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
 The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
 Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}.
-The vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016.
+The vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
 The revenue from access fees may represent up to 50\% of government revenue for some of the members.
 
-A spatial closure the size of PIPA is likely to cause changes in spatial distribution and behavior of fishing vessels.
+A spatial closure the size of PIPA is likely to cause changes in the spatial distribution and behavior of fishing vessels.
 For example, the anticipation of LSMPAs may lead to preemptive overfishing, which likely erodes or delays the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}.
@@
 However, the benefits of the spatial closure are dispersed amongst all other PNA members (through fish movement), who in turn benefit from the conservation efforts of the initial country.
-While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (\emph{i.e.} Palau).
+While no studies have assessed the impact of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (\emph{i.e.} Palau).
 
@@
 We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are controlled by PNA countries, where the largest tuna fisheries occur.
+These are two of the largest protected areas on the planet and both are controlled by PNA countries.
 
-Our empirical portion uses identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018.
+Our empirical approach uses identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018.
 We continuously observe 92 vessels for the 2012 - 2018 period.
-Of these, 64 vessels fished within PIPA at least once prior to its implementation, and refer to them as the ``displaced vessels''.
+Of these, 64 vessels fished within PIPA at least once prior to its implementation, and we refer to them as the ``displaced vessels''.
 The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
@@
 Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
-The stock remains within a Patch during the season, but escapement (\emph{i.e.} stock minus catches) is distributed between all countries at the end of each year.
+The stock remains within a Patch during the season, but escapement (\emph{i.e.} stock minus catch) is distributed between all countries at the end of each year.
 A detailed explanation of the model is presented in the Methods section.
-We find that a spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock to moves freely between the protected and non-protected portion of the Patch.
+We find that a spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portion of the Patch.
 The loss in revenue increases with reserve size, but decreases as within-patch movement increases (Fig.
 \ref{fig:PNA_model}A).
-For all other PNA countries, however, a spatial closure in Patch 1 results beneficial, especially as within-patch movement decreases and reserve size increase (Fig.
+For all other PNA countries, however, a spatial closure in Patch 1 is beneficial, especially as within-patch movement decreases and reserve size increases (Fig.
 \ref{fig:PNA_model}B).
@@
 The stock not fished in the protected portion of Patch 1 eventually redistribute to the other patches, which increases stock size and causes vessel-day prices to increase.
-This model shows that the costs of conservation are incurred by Patch 1, but the benefits are perceived by the other eight patches.
-Moreover, the gains in revenue for other PNA countries does not compensate for the total losses to Kiribati, as a great portion of effort is redistributed to the High Seas.
+This model shows that the costs of conservation are incurred by Patch 1, but the benefits are perceived by the eight other patches.
+Moreover, the gains in revenue for other PNA countries does not compensate for the total losses to Kiribati, as a large portion of effort is redistributed to the High Seas.
 
@@
 To account for environmentally-driven patterns in vessel location, we incorporate the monthly NINO4 anomaly index in our analyses.
-The NINO4 index is an area-averaged measure of Sea Surface Temperature from 5S-5N and 160E-150W.
-The NINO4 anomaly index is the same, with the 1981-2010 mean removed, as made available from the Global Climate Observing System (Fig.
+The NINO4 index is an area-averaged measure of Sea Surface Temperature from 5S-5N and 160E-150W, made available by the Global Climate Observing System (Fig.
 \ref{fig:nino_plot}).
+The NINO4 anomaly index is the same index, with the 1981-2010 mean removed.
 
@@
 These results are robust to a series of specifications, accounting for the addition of satellites and monthly NINO4 anomaly (Table \ref{tab:sp_corr}).
-A model fit with NINO4 anomaly as the only explanatory variable explained just 3\% and 7\% of the variation in our crowding measures.
+A model fit with the NINO4 anomaly as the only explanatory variable explained just 3\% and 7\% of the variation in our crowding measures.
 Similar results are obtained when repeating the exercise for Kiribati only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr})
@@
 We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for displaced vessels after implementation of PIPA, relative to the trends observed for non-displaced vessels (see the Methods section for our empirical specification).
-As before, our analyses incorporates monthly NINO4 anomalies to account for possible environmentaly-driven variations.
+As before, our analyses incorporate monthly NINO4 anomalies to account for possible environmentally-driven variations.
 
@@
 Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled 21\% less distance, with fishing events occurring 28.5\% and 15.7\% closer to shore to port, respectively.
+Treated vessels traveled 21\% less distance, with fishing events occurring 28.5\% and 15.7\% closer to shore and to port, respectively.
 These changes in distance from shore and port are likely caused by redistribution, as we observe that displaced vessels fish 58.6\% and 40.3\% less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
@@
 
-These patterns suggest that displaced vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters.
-In summary, vessels that used to fish in PIPA are now fishing less in both Kiribati and the PNA region.
-Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters, with slight increases in the High Seas \ref{fig:fishing_raster_diff}.
+These patterns suggest that displaced vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters (including Kiribati).
+These vessels are also fishing closer to their home ports.
+Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters, with slight increases in the High Seas (Figure \ref{fig:fishing_raster_diff}).
 The results are robust to a set of different specifications, with interaction effects shown in Fig  \ref{fig:other_specifications}.
-We repeat this analysis for groups where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same reposnses.
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same reposnses.
 
@@
 	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
-	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.
-The large increase for Kiribati in 2014 is likely explained by the blue paradox \cite{mcdermott_2018}}
+	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.}
 \end{figure}
@@
 We complement our analysis of change in observed vessel-days by looking at country-level data.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig.
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
 \ref{fig:revenues}A).
@@
 The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.
+This is suggestive but certainly not conclusive evidence that Kiribati may have been able to lessen the impact of PIPA on their license revenues by selling their fishing days to other members of the PNA (including Papua New Guinea).
 
@@
 
-Catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
+Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
 \ref{fig:catches}).
@@
 Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in catch over the same period.
+In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
+
+%Need to change the above to Skipjack catch at some point
 
@@
 Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine vessel days (700) and is able to sell them for a similar price to what it is currently selling them to the United States for under the South Pacific Tuna Treaty also known as the Multilateral Treaty on Fisheries (\$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine vessel days (700) to transfer to other PNA countries at the current benchmark price (\$8,000/day).
+In Scenario 1, Palau is able to keep its current allotment of purse seine VDS (700) and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day).
 Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days.
-It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as effort in its EEZ reaches zero.
-In Scenarios 3 and 4, Palau loses all of its PS vessel days, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel day and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
+It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero.
+In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
 The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
@@
 Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior.
-Our simulation predicts losses in revenue to countries that implement a spatial closure, increases in revenue to other countries, and an increased fishing of the high seas.
+Our simulation model predicts losses in revenue to countries that implement a spatial closure, increases in revenue to other countries, and an increased fishing of the high seas.
 Using vessel track data, we observe a crowding effect after the implementation of the protected area, as displaced vessels redistribute spatially.
-We see that vessels that fished inside PIPA before the implementation redistributes to other areas within Kiribati, but also other PNA countries and the high seas.
+We see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also other PNA countries and the high seas.
 Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners.
 Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
-Our analysis suggests that the displacement of vessels results in losses to Kiribati, and that similar outcomes would be expected for Palau's Marine Sanctuary with losses in profits of up to \$11 million USD.
+Our analysis suggests that the displacement of vessels results in losses to Kiribati, controlling for the effect of El Ni\~{n}o, and that similar although much smaller losses would be expected for Palau's Marine Sanctuary.
 Here, we discuss the implications of our findings and possible shortcomings in our analysis.
@@
 Here, we provide some plausible explanations for these discrepancies.
-First, it is possible that as waters in Kiribati became more crowded, the price of vessel-days decreased significantly bellow the \$9,000 USD estimate that we use.
-This woudl imply that vessel-day prices fell to \$5,800 in Kiribati.
-This is a number similar to what our simulation estimates provide for a closure similar to PIPA (\emph{i.e.} $R = 0.11$), which range from \$5,250 to \$6,134, depending on the movement of fish.
-Another possible explanation is that the dataset used incorrectly labeled vessels as purse seiners.
+One possible explanation is that the dataset used incorrectly labeled vessels as purse seiners.
 However, the scoring algorithm has a high accuracy, and this accuracy increases with the number of observations for a vessel.
@@
 Therefore, if there are any mislabeled vessels in our data, these would contribute little to the large trends that we observe.
-Another alternative is that vessels fishing within PNA waters can report their activity as transiting to port or solving mechanical issues; this time does not count towards a vessel's usage of days (forgot the reference).
-Finally, Kiribati's vessel-day allocation is in the order of 7,000 vessel-days (need reference).
-However, we observe that on any given year, Kiribati received between 3,000 and 14,900 vessel-days (Fig \ref{fig:all_PS_VDS_KIR_year}), implying that a portion of these were purchased or transfered from other PNA countries.
+Another alternative is that vessels within PNA waters can report their activity as transiting to port or solving mechanical issues and this time does not count towards a vessel's usage of VDS.
+Second, Kiribati's vessel-day allocation is around 11,000 vessel-days \citep{yeeting2018stabilising}.
+Kiribati could be selling their excess VDS to other PNA countries, which would offset the drop in demand for fishing within their EEZ.
 These explanations are not mutually exclusive, and a combination of them could certainly explain the discrepancy.
@@
 ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-We do our best control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking non-displaced vessels as a group that is equally affected by the environmental variation.
-For example, we observe that both displaced and non-displaced vessels shifted their effort to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
+We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
+For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
 However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself does not explain the observed patterns.
-While environmental variation certainly influences behavior, policy and management interventions such as moratorium and spatial closures can have an equally big effects \cite{kroodsma_2018}.
+Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself it does not explain the observed patterns.
+While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
 
-A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guide the decision-making process of profit-maximizing agents.
+A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of profit-maximizing agents.
 Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
 Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or prices.
-Furthernore, our estimates of revenue loss for PIPA do not account for the allocation calculated each year.
+Furthermore, our estimates of revenue loss for PIPA do not account for the allocation calculated each year.
 Each party’s allowable effort is calculated based on historic effort and biomass within each party’s EEZ.
-Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
+Sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
 
-Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses.
+Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights.
 The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
-The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lhavice_2013,aqorau_2018}.
-Overlaying conservation interventions over existing management schemes must be accompained by similar dialogues and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
-Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms\cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
+The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}.
+Overlaying conservation interventions over existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
+Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
 
@@
 The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
-Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1]$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies to movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed over during the fishing season.
+Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
+Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season.
 In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$.
@@
 	\begin{align}
-	\Pi_j(E_j,X_j) = pqE_jX_j-cE_1^\beta
+	\Pi_j(E_j,X_j) = pqE_jX_j-cE_j^\beta
 	\end{align}
@@
 
-However, Patch 10 represents the high seas under open access dynamics.
-Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi E_{10} = 0$.
+In practice, the effort levels in each PNA patch are given (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
+effort level on the high seas ($E_{10}$) is a result of open access dynamics.
+Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
 Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:
@@
 
-Therefore, escapement in patch $i$ is the difference between initial stock size and harvests as $e_{it} = X{it} - H_{it}$. At the entire stock then grows according to:
+Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$.
+The entire stock then grows according to:
 
@@
 
-Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}).
-This would cause for the stock in the high seas ($X_{10}$) to increase through the redistribution (Equation \ref{eqn:disperse}), leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}).
+Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
+Thus, the spillover benefits of increasing $R$ are never completely captured.
 
@@
 The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
+This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels and vessel activity.
 The addition of new satellites affects all vessels in the same way.
 
-Our treatment group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
+Our displaced group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
 Vessels in the non-displaced group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
-Together, these vessels represent more than 20 million georeferenced positions for which we know activity (fishing or not fishing).
-We include three additional control groups as a robustness check.
-The first group excludes all Chinese vessels, the second group excludes all PNA vessels, and the third group excludes US and Taiwanese vessels.
-Our main definition of displaced and non-displaced groups leaves us with 64 displaced and 28 non-displaced vessels, which have just over 36 million observations.
+Together, these vessels represent more than 20 million geo-referenced positions for which we know activity (fishing or not fishing).
+We perform three sample restrictions as a robustness check.
+The first restriction excludes all Chinese vessels, the second excludes all PNA vessels, and the third excludes US and Taiwanese vessels.
 
@@
 We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and star  ts to decrease, and 3) when this decrease potentially levels off.
+1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
 For this reason, we fit a 4th degree polynomial to our monthly indices.
@@
 Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which incorporated in April 1st, 2014 and December 31st, 2015.
-The$mu$ coefficient captures the effect of the NINO4 anomaly.
+We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
+The $\mu$ coefficient captures the effect of the NINO4 anomaly.
 
@@
 We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
 We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
@@
 \begin{align}
-log(y)_{i,t} = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
+log(y_{i,t}) = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \label{eqn:did}
@@
 \noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$ the transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ on period $t$.
-A dummy variable $Post_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
-$Treat_i$ is a dummy variable indicating whether a vessel belongs to the displaced ($D_i = 1$) or non-displaced ($D_i = 0$) group.
-$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between displaced and non-displaced groups, and $\beta_3$ is our parameter of interest: the Difference-in-Differences estimate capturing the treatment effect.
+A dummy variable $P_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
+$D_i$ is a dummy variable indicating whether a vessel belongs to the displaced ($D_i = 1$) or non-displaced ($D_i = 0$) group.
+$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between displaced and non-displaced groups, and $\beta_3$ is our parameter of interest: the difference-in-differences estimate capturing the treatment effect.
 Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
@@
 \includegraphics{img/KIR_sp_corr.pdf}
-\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
+\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
 The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
@@
 	\caption{\label{fig:catches}Financial indicators for PNA countries.
-A) Annual catches by EEZ and, B) Annual value of catches by EEZ.
+A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
 Vertical dashed line in both plots denotes implementation of PIPA.}
@@
 \includegraphics{img/fishing_raster_diff.png}
-\caption{\label{fig:fishing_raster_diff}Change in spatial footrpint of analysed vessels.
+\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
 Black lines show Exclusive Economic Zone (EEZ), red lines show existing Marine Protected Areas.
-Panels A and B show the change through time (after - before) for dislpaced and non-displaced vesels, respectively.
+Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
 Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
-Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA.}
+Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
 \end{figure}
@@
 \centering
-\includegraphics{img/time_series_gear_group.pdf}
-\caption{\label{fig:time_series_gear_group}Time series of monthly observed vessel days for drifting longliners and tuna purse seiners in each EEZ belonging to Kiribati: Gilbert islands, Phoenix islands, and Line islands.
-\emph{I would take this one out, but left it here so you could see the drop in longlines happens later (2017), not aligned with PIPA at all.}}
-\end{figure}
-
-\begin{figure}[H]
-\centering
 \includegraphics{img/nvessels_to_90.pdf}
-\caption{\label{fig:nvessels_to_90}Cumulative activity (\% of total hours) as a function og increasing fraction of vessels (\% of total) by year.)}
+\caption{\label{fig:nvessels_to_90}Cumulative activity (\% of total hours) as a function of increasing fraction of vessels (\% of total) by year.)}
 \end{figure}

### 2019-05-14 docs/slides/NCEAS_presentation.Rmd
Added and updated slides for NCEAS presentation last week

@@
 ---
-title: "Marine Conservation and Fishing Effort Markets"
+title: "Marine Conservation and Fishing Effort Markets[^*]"
 author:
@@
   - \usepackage{media9}
+  - \usepackage{eso-pic,graphicx,transparent}
 ---
+
+[^*]: This is work in progress developed for the NCEAS working group. Please do not share externally. Results are yet to be refined and peer-reviewed.
+
+\AddToShipoutPictureFG{
+  \AtPageCenter{% or \AtTextCenter
+    \makebox[0pt]{\rotatebox[origin=c]{45}{%
+      \scalebox{5}{\texttransparent{0.3}{DRAFT}}%
+    }}
+  }
+}
 
@@
 
-  - Phoenix Island Protected Area
+  - Phoenix Island Protected Area*
 
@@
 
-### Relationship between closure size and losses
+### Effort displacement by large-scale MPAs
 
-Does a 30\% closure mean a 30\% loss in revenue?
+- Where was effort displaced to?
+
+- Does effort displacement imply revenue losses from VDS?
+
+- Does a 30\% closure mean a 30\% loss in revenue?
 
@@
 
-# PIPA
+# Generalizability to Palau
+
+## Palau Vessel-day schemes
+
+- Purse seine vessel-days
+
+  - 700 purse seine vessel-days
+
+  - \$5.60 - \$8.75 Million USD
+
+  - Tradable
+
+  - Trading might reduce costs, but allocation rules matter
+
+- Longline vessel-days
+
+  - 10,500 longline vessel-days
+
+  - \$2.10 Million USD
+
+  - Non-tradable
+
+## Conclusions
+
+- Under no trading, implementing a reserve is costly
+
+  - More fish movement reduces costs
+
+- Trading lessens the blow of a spatial closure
+
+  - \% costs avoided by trading decrease as biomass in implementing patch increases
+
+- Allocation rules matter
+
+  - A biomass-based allocation ($\alpha = 0$) reduces long-term costs
+
+# Extra slides
+
+## GFW summary for Palau
+
+```{r}
+knitr::include_graphics(here("docs", "slides", "img", "vessels_in_plw.png"))
+```
 
@@
 
-- ~2\% of total PNA area
+- 2.7\% of total PNA area
 
-- ~10\% of fishing activity in PNA
+- 11\% of Kiribati EEZ
+
+- 22\% of Kiribati EEZ (excluding Line Islands)
 
@@
 
-- Devideded into three groups
+- 2012 - Present
 
-## Two fleets
+## Two "fleets"
 
@@
 knitr::include_graphics(here("docs", "slides", "img", "sample_tracks.png"))
-```
-
-## Effort displacement
-
-```{r}
-knitr::include_graphics(here("docs", "img", "all_PS_VDS_year.pdf"))
 ```
@@
 
-## Effort displacement raster
+## Effort displacement in all PNA
 
 ```{r}
-knitr::include_graphics(here("docs", "img", "rasterized_change.png"))
+knitr::include_graphics(here("docs", "img", "all_PS_VDS_year.pdf"))
 ```
 
-# Generalizability to Palau
+## Displaced vessels
 
-# Extra slides - GFW data
+```{r}
+knitr::include_graphics(here("docs", "img", "fishing_raster_displaced.png"))
+```
+
+## Non-displaced vessels
+
+```{r}
+knitr::include_graphics(here("docs", "img", "fishing_raster_not_displaced.png"))
+```
+
+## Difference
+
+```{r}
+knitr::include_graphics(here("docs", "img", "fishing_raster_difference_between_groups.png"))
+```
+
+# GFW Data
 
@@
 ```
-
-## Vessel statistics
-
-A short table with information on number of vessels per year and class
-
-Palau-specific information about longliners

### 2019-05-14 scripts/model/1_checks.Rmd
Updated scripts tha generate a couple of figures

@@
 
-# Model description
+#Model for marine conservation with effort markets
 
-We model the PNA as a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
+We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
+Patches 1 - 9 opperate under a vessel-day schemePatches, and Patch 10 represents the high seas and other areas not managed under a VDS.
 The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
 The price of fish is $p$, and catchability is given by $q$.
+These parameters are held constant across patches.
+
+##Fishery dynamics
 
@@
 The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+
 Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
@@
 $$
-\begin{align}
-\Pi_1(E_1,X_1,R) = pqE_1X_1(\theta + (1 - \theta)(1 - R))-cE_1^\beta
-\end{align}
+\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_i-cE_1^\beta
 $$
 
-And profits from fishing in Patch $j = \{2, 3, ..., 10\}$ are:
+With $\Omega_i = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  (0, 1)$) and within-patch fish movement ($\theta$).
+Under this parameterization, $\Omega_{i \not 1} = 1$ since only Patch 1 implements a reserve.
+
+Profits from fishing in each Patch are:
 
 $$
-\begin{align}
-\Pi_j(E_j,X_j) = pqE_jX_j-cE_j^\beta
-\end{align}
+\Pi_i(E_i,X_i) = pqE_iX_i\Omega_i-cE_i^\beta
 $$
@@
 $$
-\begin{align}
-\pi_1(E_1) = pqX_1(\theta + (1 - \theta)(1 - R)) - \beta cE_1^{\beta-1}
-\label{eqn:marginal_profit_1}
-\\
-\pi_j(E_j) = pqX_j - \beta cE_j^{\beta-1}
-\label{eqn:marginal_profit_j}
-\end{align}
+\pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
+\label{eqn:marginal_profit}
 $$
 
-In practice, the effort levels in each PNA patch are given (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics.
+In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
+effort level on the high seas ($E_{10}$) is a result of open access dynamics.
 Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:
+Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
 
 $$
-\begin{align}
 E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
 \label{eqn:effort_hs}
-\end{align}
 $$
 
-The patch-level harvest is then determined by effort and stock size:
+Under vds-operated patches, however, profits from marginal effort must equate the cost of fishing in the patch. Therefore vessel-day price for patches under vds ($i = (1, 9)$) is  given by:
 
 $$
-\begin{align}
-H_1 = qE_1X_1 (\theta + (1 - \theta)(1 - R))
-\label{eqn:harvest_1}
-\\
-H_j = qE_jX_j
-\label{eqn:harvest_j}
-\end{align}
+\pi(E_i) = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
+$$
+
+We can solve for $E_i$ and obtain:
+
+\begin{equation}
+	\begin{split}
+		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
+		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
+		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_1}{\beta c} \\
+		E_i &= \left(\frac{pqX_i\Omega_i - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+	\end{split}
+\label{eqn:demands}
+\end{equation}
+
+Therefore, total allowable effort in the fishery is given by:
+
+$$
+\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+\label{eqn:Ebar}
+$$
+
+## Stock dynamics
+
+Patch-level harvest is then determined by effort and stock size:
+
+$$
+H_i = qE_iX_i\Omega_i
+\label{eqn:harvest}
 $$
@@
 Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$.
-The entire stock then grows according to:
+The entire stock then grows logistically according to:
 
 $$
-\begin{align}
-X_{t+1} = e_t + \frac{(\phi + 1)}{\phi}ge_t\left(1 - \left(\frac{e_t}{K}\right) ^{\phi}\right)
+X_{t+1} = e_t + e^{r \times \frac{e}{K}}
 \label{eqn:grow}
-\end{align}
 $$
+
+Where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
 
@@
 $$
-\begin{align}
 X_{it+1} = f_iX_{t+1}
 \label{eqn:disperse}
-\end{align}
 $$
 
-The vessel-day price that a country charges is given by $\pi_i$ from Equations \ref{eqn:marginal_profit_1} and \ref{eqn:marginal_profit_j}. Therefore, patch-level license revenues are given by:
+## Vessel-day revenues
+
+The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
 
 $$
-\begin{align}
 \omega = \pi_iE_i
 \label{eqn:license_revenue}
-\end{align}
 $$
 
-Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
 But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
@@
 
-The vessel-day price for parcels that do not implement a reserve ($j = c(2, 10)$) is given by:
+## Allocation rules
+
+In the second scenario above, effort from a patch with conservation is traded to other patches.
+This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
+After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time.
+At the end of every time, vessel-days are allocated to each patch based on the following rule:
 
 $$
-\pi(E_j) = pqX_j - \beta c E_j ^{\beta - 1}
+E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
+(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
 $$
 
-We can solve for $E_j$:
-
-$$
-\begin{split}
-\pi_j + \beta c E_j ^{\beta - 1} &= pqX_j \\
-\beta c E_j ^{\beta - 1} &= pqX_j - \pi_j \\
-E_j ^{\beta - 1} &= \frac{pqX_j - \pi_j}{\beta c } \\
-E_j &= \left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1}}
-\end{split}
-$$
-
-For the parcel that implements the reserve ($i = 1$) the same equations are given by:
-
-$$
-\pi_1(E_1) = pqX_1 (\theta + (1 - \theta)(1 - R))- \beta c E_1 ^{\beta - 1}
-$$
-
-For simplicity, we can write $\Omega = (\theta + (1 - \theta)(1 - R))$, and the baove becomes
-
-$$
-\pi_1(E_1) = pqX_1\Omega - \beta c E_1 ^{\beta - 1}
-$$
-
-We can solve for $E_i$ as in the previous casse:
-
-$$
-\begin{split}
-\pi_1 + \beta c E_1 ^{\beta - 1} &= pqX_1\Omega \\
-\beta c E_1 ^{\beta - 1} &= pqX_1\Omega - \pi_1 \\
-E_1 ^{\beta - 1} &= \frac{pqX_1\Omega - \pi_1}{\beta c} \\
-E_1 &= \left(\frac{pqX_1\Omega - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-\end{split}
-$$
-
-The total vessel-days for cells that belong to PNA countries (*i.e.* i = (1, 9)) are constrained at 45,000, which we term $\bar{E}$. Therefore, total effort can be expressed as:
-
-$$
-\bar{E} = \left(\frac{pqX_1(\theta + (1 - \theta)(1 - R)) - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}} + 
-\sum_{j = 2}^9\left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1} }
-$$
-
-This parameterization shows that the cell-level effort is determined by the combination of stock size ($X_j$) and the price $\pi$.
-Trading between country will continue until all $\pi_i$ reach an equilibrium price of $\bar{\pi}$.
+Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$).
+We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures.
+The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales.
+We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
 

### 2019-05-14 scripts/model/2_run_model.Rmd
Updated scripts tha generate a couple of figures

--- 2019-04-25 scripts/model/2_run_model.Rmd
@@
   html_document: 
-    code_folding: show
+    code_folding: hide
     toc: yes
@@
 
-## Define parameters
+## Description of simulations
+
+We inform our model to losely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
+
+### Define parameters
 
@@
 ```
+
+### Create and export a table of parameters and sources
+
+```{r}
+params <- tibble(
+  parameter = c(
+    "MSY",
+    "$B_{msy}$",
+    "K",
+    "$B_c/B_{msy}$",
+    "$C_{now}$",
+    "$B_{now}$",
+    "$r$",
+    "$\\beta$",
+    "p",
+    "q",
+    "c",
+    "f"
+  ),
+  value = c(MSY, Bmsy, K, Bc_B0, Cnow, Bnow, r, beta, p, q, c, 0.1),
+  source = c(
+    "50th percentile from MSY in table 8 of Stock Assessment",
+    "50th percentile from MSY in table 8 of Stock Assessment",
+    "50th percentile from MSY in table 8 of Stock Assessment",
+    "50th percentile from MSY in table 8 of Stock Assessment",
+    "Catches from Stock Assessment",
+    "Current Biomass (2012 - 2015 average)",
+    "From fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78",
+    "Standard",
+    "Mean between Thailand and Japan values (Value of WCPFC-CA tuna fisheries 2017 report)",
+    "Estimated so that efforts match catches given biomass and vessel-day prices",
+    "-",
+    "Biomass is equally distributed between patches ($f_i = 0.1$)"
+
+  )
+)
+
+params %>% 
+  knitr::kable(col.names = c("Parameter", "Value", "Source"), format = "latex", escape = F) %>% 
+  cat(file = here("docs", "tab", "parameters.tex"))
+```
+
+We use the model above run three different simulations.
+We test the model across a range reserve sizes and movement parameters.
+We use to main scenarios.
+The first scenario does not allow trading.
+In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
+For patch 10, we solve for Ei until biomass converges to match $B_{now}$.
+We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
+We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
+This produces a measure of the cost of implementing a spatial closure of size $R$ in patch 1.
+
+The second scenario allows trading.
+We start again by solving for the high seas to obtain total effort.
+Since a closure is not in effect, this equiulibrium is the same as the first step above.
+We then implement a spatial closure in patch 1.
+This essentially lowers the price fishers would be willing to pay to fish in a patch with biomass $X_i\Omega_i$, lowering demand for vessel-days in pach 1.
+Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from patch 1 are sold to patches 2 - 9.
+This increases effort in these patches, which reduces escapement and therefore biomass.
+This reduction in biomass in turn would modify the demand curves (Ei).
+We therefore iterate this process until biomass stabilizes, therefore finding the system's equilibrium.
+Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in patch 1.
 
@@
     cost = b_vdsrevenue - VDSrevenue,
-    rel_cost = cost / b_vdsrevenue
+    rel_cost = cost / b_vdsrevenue,
+    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
+    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
   )
@@
     xlab("Portion of patch as reserve (R)") +
-    ylab("Costs (% of case with no reserve)") +
+    ylab("Costs\n(% of case with R = 0)") +
     scale_color_viridis_c() +
@@
     cost = b_vdsrevenue - all_VDSrevenue,
-    rel_cost = cost / b_vdsrevenue
+    rel_cost = cost / b_vdsrevenue,
+    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
+    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
   )
@@
 ```{r, fig.width = 4, fig.height = 4}
+(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
+  geom_line(aes(
+    x = R,
+    y = rel_cost,
+    group = theta,
+    color = theta
+  ),
+  size = 1
+  ) +
+  xlab("Portion of patch as reserve (R)") +
+  ylab("Costs (% of case with R = 0)") +
+  scale_color_viridis_c() +
+  startR::ggtheme_plot() +
+  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
+  theme(legend.position = "None"))
+```
+
+```{r}
+ggsave(plot = costs_with_trading_plot_long_axis,
+       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
+       width = 3,
+       height = 3)
+```
+
+```{r}
 (costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
@@
   xlab("Portion of patch as reserve (R)") +
-  ylab("Costs (% of case with no reserve)") +
+  ylab("Costs\n(% of case with R = 0)") +
   scale_color_viridis_c() +
   startR::ggtheme_plot() +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
   theme(legend.position = "None"))
@@
   xlab("Portion of patch as reserve (R)") +
-  ylab("Costs avoided by trading") +
-  scale_color_viridis_c() +
+  ylab("Costs avoided\nby trading") +
+  scale_color_viridis_c(limits = c(0, 1)) +
   theme(
@@
   startR::ggtheme_plot() +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
   theme(legend.position = "None"))
@@
 ```{r, fig.width = 4, fig.height = 7}
-(cost_plot <- cowplot::plot_grid(costs_no_trading_plot,
+(cost_plot <- plot_grid(costs_no_trading_plot,
                         costs_with_trading_plot,
-                   delta_costs_plot, ncol = 1))
+                        delta_costs_plot,
+                        ncol = 1,
+                        labels = "AUTO"))
 ```
@@
 ggsave(plot = cost_plot,
-       filename = here("docs", "img", "cost_plot.pdf"), width = 4, height = 7)
+       filename = here("docs", "img", "PNA_model.pdf"),
+       width = 3.4,
+       height = 7)
 ```
@@
 ```{r}
+country_anom <- tibble(Country = c("KIR", "FSM", "MHL", "NRU", "PLW", "PNG", "SLB", "TKL","TUV","HS"),
+                       Country_a = 1:10)
+
+(vessel_day_price_no_trading_plot <- 
     DF_results_no_trading %>%
-  filter(!Country == "HS") %>% 
-  mutate(Country = fct_relevel(Country, "KIR")) %>% 
-  ggplot() +
+    left_join(country_anom, by = "Country") %>% 
+    filter(Country_a %in% c(1, 2)) %>% 
+    mutate(Country_a = ifelse(Country_a == 1, "Patch 1", "Patches 2 - 9"),
+           Country_a = fct_relevel(Country_a, "Patch 1")) %>% 
+    ggplot(aes(x = R, y = VDSprice, color = theta, group = theta)) +
+    geom_line(size = 1) +
+    facet_wrap( ~ Country_a, scale = "free_y") +
+    xlab("Portion of patch as reserve (R)") +
+    ylab("Vessel-day price") +
+    scale_color_viridis_c() +
+    theme(
+      text = element_text(size = 10),
+      axis.text = element_text(size = 8)
+    ) +
+    startR::ggtheme_plot() +
+    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
+                                  ticks.colour = "black", frame.colour = "black"))+
+    theme(legend.position = c(0.6, 1),
+          legend.justification = c(0, 1)))
+```
+
+```{r}
+ggsave(plot = vessel_day_price_no_trading_plot,
+       filename = here("docs", "img", "vessel_day_price_no_trading_plot.pdf"),
+       width = 6,
+       height = 3)
+```
+
+### When there is trading
+
+```{r}
+(vessel_day_price_with_trading_plot <- ggplot(data = DF_1_with_trading) +
    geom_line(aes(
@@
                                  ticks.colour = "black",
-                                frame.colour = "black")) +
-  facet_wrap(~Country, scales = "free_y")
+                                 frame.colour = "black")))
 ```
 
-### When there is trading
+```{r}
+ggsave(plot = vessel_day_price_with_trading_plot,
+       filename = here("docs", "img", "vessel_day_price_with_trading_plot.pdf"),
+       width = 6,
+       height = 4.5)
+```
+
+## What about revenue to other PNA countries?
+
+### With no trading
 
 ```{r}
-ggplot(data = DF_1_with_trading) +
+(
+  profits_PNA_notKIR_no_trading_plot <-
+    ggplot(data = DF_1_no_trading) +
     geom_line(aes(
       x = R,
-    y = VDSprice,
+      y = rel_cost_pna_not_kir,
       group = theta,
@@
     xlab("Portion of patch as reserve (R)") +
-  ylab(quo("Vessel-day Price ("~pi~")")) +
+    ylab("Additional profits (% of case with R = 0)") +
     scale_color_viridis_c() +
@@
     startR::ggtheme_plot() +
+    scale_y_continuous(labels = scales::percent) +
     guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
-                                ticks.colour = "black",
-                                frame.colour = "black"))
+                                  ticks.colour = "black", frame.colour = "black")) +
+    theme(legend.justification = c(0, 0.9),
+          legend.position = c(0, 1))
+)
 ```
 
-## Where do vessels go?
+```{r}
+ggsave(plot = profits_PNA_notKIR_no_trading_plot,
+       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot.pdf"),
+       width = 3,
+       height = 3)
+```
 
-### With no trading
+# Allocation rules matter
+
+## Allocation rules
+
+In the second scenario above, effort from a patch with conservation is traded to other patches.
+This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
+After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time.
+At the end of every time, vessel-days are allocated to each patch based on the following rule:
+
+$$
+E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
+(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
+$$
+
+Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$).
+We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures.
+The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales.
+We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
 
 ```{r}
-DF_results_no_trading %>% 
-  filter(!Country == "HS") %>%
-  mutate(Country = fct_relevel(Country, "KIR")) %>% 
-  ggplot() +
-  geom_line(aes(
-    x = R,
-    y = Vessel_Days,
-    group = theta,
-    color = theta
+source(here("scripts", "model", "allocate.R"))
+source(here("scripts", "model", "allocate_wrap.R"))
+source(here("scripts", "model", "move_in_time.R"))
+source(here("scripts", "model", "move_in_time_no_trading.R"))
+```
+
+We first obtain the optimal allocation by running the model until steady state and with no reserves.
+
+```{r}
+
+alphas <- c(0, 0.25, 0.5, 0.75, 1)
+
+delta <- 1 / 1.1
+
+plan(multiprocess)
+
+allocation <-
+  expand.grid(
+    R = Rvec,
+    theta = c(0.25, 0.5, 0.75),
+    alpha = alphas,
+    trade = T
+  ) %>%
+  as_tibble() %>%
+  mutate(
+    resutls = future_pmap(
+      .l = list(
+        alpha = alpha,
+        R = R,
+        theta = theta,
+        trade = trade
       ),
-  size = 1
-  ) +
+      .f = allocate_wrap, 
+      fvec = fvec,
+      r = r,
+      K = K,
+      p = p,
+      q = q,
+      Xvec = Xvec,
+      beta = beta,
+      c = c,
+      E = E
+    )
+  ) %>%
+  unnest() %>%
+  filter(country == "KIR") %>%
+  mutate(
+    rev_dir = Ei * pi,
+    deltaE = Ea - Ei,
+    rev_sells = deltaE * pi,
+    rev_tot = rev_dir + rev_sells,
+    fct = delta ^ year,
+    rev_tot_disc = rev_tot * fct
+  )
+
+best_rev <- allocate_wrap(
+  alpha = 0,
+  R = 0,
+  theta = 0.5,
+  trade = T,
+  fvec = fvec,
+  r = r,
+  K = K,
+  p = p,
+  q = q,
+  Xvec = Xvec,
+  beta = beta,
+  c = c,
+  E = E
+) %>%
+  filter(country == "KIR") %>%
+  mutate(
+    rev_dir = Ei * pi,
+    deltaE = Ea - Ei,
+    rev_sells = deltaE * pi,
+    rev_tot = rev_dir + rev_sells,
+    fct = delta ^ year,
+    rev_tot_disc = rev_tot * fct
+  ) %$%
+  sum(rev_tot)
+```
+
+```{r, fig.height = 3.5, fig.width = 4.5}
+(allocation_cost_plot <- allocation %>%
+   filter(R > 0,
+          trade) %>% 
+   mutate(trade = ifelse(trade, "Trading", "No Trading"),
+          theta = as.character(theta)) %>% 
+   group_by(trade, alpha, R, theta) %>%
+   summarize(rev = sum(rev_tot)) %>%
+   ungroup() %>%
+   mutate(cost = (best_rev - rev) / best_rev) %>%
+   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
+   geom_line(size = 1.5) +
+   scale_y_continuous(labels = scales::percent) +
    xlab("Portion of patch as reserve (R)") +
-  ylab(quo("Vessel-Days")) +
+   ylab("Costs\n(% of case with R = 0)") +
    scale_color_viridis_c() +
-  theme(
-    text = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  ) +
-  startR::ggtheme_plot() +
-  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
+   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
+   ggtheme_plot() +
+   # facet_wrap(~trade, ncol = 1) +
+   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                  ticks.colour = "black",
-                                frame.colour = "black")) +
-  facet_wrap(~Country, scales = "free_y")
+                                 frame.colour = "black"),
+          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
+                                  override.aes = list(size = 0.5))))
+```
+
+```{r}
+#Paper export
+ggsave(
+  plot = allocation_cost_plot,
+  filename = here("docs", "img", "allocation_cost_plot.pdf"),
+  width = 4.5,
+  height = 3.5
+)
+```
+
+```{r}
+#Slide export
+ggsave(
+  plot = allocation_cost_plot,
+  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
+  width = 5,
+  height = 3
+)
+```
+
+```{r, eval = F}
+allocation %>%
+  filter(!trade) %>% 
+  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
+  geom_line(size = 1) +
+  facet_grid(alpha ~ theta) +
+  scale_color_viridis_c() +
+  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
+  ggtheme_plot()
+```
+
+```{r, eval = F}
+allocation %>%
+  filter(theta == 0.5, !trade) %>% 
+  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
+  geom_line(size = 1) +
+  facet_grid(~alpha) +
+  scale_color_viridis_c() +
+  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
+  ggtheme_plot()
 ```

### 2019-05-14 scripts/content/fig_PNA_map.R

@@ -10,7 +10,7 @@
 
 # Load packages
 library(ggrepel)
-library(ggsflabel)
+library(ggsflabel) #devtools::install_github("yutannihilation/ggsflabel")
 library(countrycode)
 library(startR)
 library(sf)
@@ -77,11 +77,16 @@ pipa <- sf::read_sf(dsn = here("data", "spatial", "PIPA"), layer = "PIPA") %>%
   sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
   st_rotate()
 
+pnms <- read_sf(dsn = here::here("data", "spatial", "LSMPAs"), layer = "LSMPAs") %>%
+  filter(WDPAID == "555622118") %>%
+  select(WDPAID)
+
 plot <- ggplot() +
-  geom_sf(data = eez, aes(color = KIR, fill = VDS), alpha = 0.5, size = 0.1) +
+  geom_sf(data = eez, aes(color = KIR, fill = VDS), alpha = 0.5, size = 0.5) +
   geom_sf(data = pipa, fill = "red") +
+  geom_sf(data = pnms, fill = "purple", size = 0) +
   geom_sf(data = small_coast, color = "black", fill = "#E3E3E3", size = 0.1) +
-  geom_sf_label_repel(data = labels, mapping = aes(label = ISO_Ter1), force = 400, seed = 2) +
+  geom_sf_label_repel(data = labels, mapping = aes(label = ISO_Ter1), force = 40, seed = 2) +
   ggtheme_plot() +
   scale_color_manual(values = c("black", "red")) +
   scale_fill_manual(values = c("transparent", "steelblue")) +

### 2019-05-14 scripts/content/figs_all_PS_VDS_2012_2018.R

@@ -119,20 +119,31 @@ all_PS_VDS_KIR_year_plot <-
        mapping = aes(x = year, y = days, fill = group)) +
   geom_col(color = "black") +
   scale_fill_manual(values = c("#E41A1C", "#4DAF4A", "#377EB8")) +
+  geom_hline(yintercept = 11, linetype = "dashed") +
   cowplot::theme_cowplot() +
   guides(fill = guide_legend(title = "Group")) +
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8),
         legend.text = element_text(size = 8),
-        legend.justification = c(0, 1),
-        legend.position = c(0, 1))+
+        legend.position = "None")+
   labs(x = "Year", y = "Vessel-days (1,000)")
 
 #Save plot
 ggsave(all_PS_VDS_KIR_year_plot,
-       filename = here("docs", "img", "all_PS_VDS_KIR_year.pdf"),
+       filename = here("docs", "img", "all_PS_VDS_KIR_year_DID.pdf"),
        width = 6,
        height = 4)
+
+#Both bars
+p22 <- plot_grid(all_PS_VDS_year_plot,
+                 all_PS_VDS_KIR_year_plot,
+                 ncol = 1, labels = "AUTO")
+
+#Save plot
+ggsave(p22,
+       filename = here("docs", "img", "all_PS_VDS_PNA_KIR_year.pdf"),
+       width = 3.4,
+       height = 5.4)
 
 # annual PS VDS by country
 

### 2019-05-14 docs/tab/parameters.tex
Added new MS

\begin{tabular}{l|r|l}
\hline
Parameter & Value & Source\\
\hline
MSY & 1.875600e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
\hline
$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
\hline
K & 6.876526e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
\hline
$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in table 8 of Stock Assessment\\
\hline
$C_{now}$ & 1.679444e+06 & Catches from Stock Assessment\\
\hline
$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
\hline
$r$ & 5.700000e-01 & From fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
\hline
$\beta$ & 1.300000e+00 & Standard\\
\hline
p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA tuna fisheries 2017 report)\\
\hline
q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
\hline
c & 1.800000e+02 & -\\
\hline
f & 1.000000e-01 & Biomass is equally distributed between patches ($f_i = 0.1$)\\
\hline
\end{tabular}

### 2019-05-22 docs/old_ms/PIPA_Palau_Science.tex
Updated MS for John and Chris

--- 2019-05-14 docs/old_ms/PIPA_Palau_special.tex
@@
-\documentclass[9p,twocolumn,twoside,lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
+% Use only LaTeX2e, calling the article.cls class and 12-point type.
 
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
+\documentclass[12pt]{article}
 
+% Users of the {thebibliography} environment or BibTeX should use the
+% scicite.sty package, downloadable from *Science* at
+% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
+% This package should properly format in-text
+% reference calls and reference-list numbers.
+
+\usepackage{scicite}
+
+\usepackage{times}
+
+% Packages I manually added
+\usepackage{graphicx}
 \usepackage{placeins}
-\usepackage{comment}
+\usepackage{float}
+\usepackage{amsmath}
+\usepackage{hyperref}
+\usepackage{pdflscape}
 
-\title{Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery}
+% The preamble here sets up a lot of new/revised commands and
+% environments.  It's annoying, but please do *not* try to strip these
+% out into a separate .sty file (which could lead to the loss of some
+% information when we convert the file to other formats).  Instead, keep
+% them in the preamble of your main LaTeX source file.
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[a,1]{Juan CarlosVillase\~{n}or-Derbez}
-\author[b]{John Lynham}
+% The following parameters seem to provide a reasonable page setup.
 
-\affil[a]{Bren School of Environmental Science \& Management, University of California at Santa Barbara, Santa Barbara, CA}
-\affil[b]{Department of Economics, University of Hawaii at Manoa, Honolulu, HI}
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
 
-% Please give the surname of the lead author for the running footer
-\leadauthor{Villase\~{n}or-Derbez}
+%The next command sets up an environment for the abstract to your paper.
 
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{The oceans are becoming increasingly crowded, with different activities competing for space.
-Marine Protected Areas are inherently spatial, and have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
-Our work shows that when a fishery is managed by selling effort rights (\emph{e.g.} with a Vessel-Day Scheme), spatial closures displace fishing effort at a cost to the implementing country, with benefits to other countries.
-Costs can be offset if effort rights are tradable across countries.
-With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.}
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
 
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{All authors contributed equally to this work}
-\authordeclaration{The authors declare that they have no conflicts of interest}
-\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: juancarlos@ucsb.edu}
+% Include your paper's title here
 
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Marine Spatial Planning $|$ Fisheries $|$ Marine Conservation}
+\title{Marine Conservation In Fishing Effort Markets}
 
-\begin{abstract}
-The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean.
-The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters.
-In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities.
-Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as short-term costs (due to the reduction in fishable area).
-We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution and behavior, as well as costs to Kiribati and the PNA.
-We find a crowding effect within PNA waters after the implementation of the protected area.
-In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold.
-However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in license and access fee revenue.
-These changes are robust to controlling for the effects of El Ni\~{n}o on spatial distribution of fishing effort.
-At the same time, fishing effort increases in other parts of the PNA.
-This redistribution of fishing effort eventually results in a reduction of 5,195 vessel-days in Kiribati, which implies a loss of around \$50 million USD; but much lower losses are reported in official government reports (\$30.5 million USD), suggesting that the tradable nature of the VDS system is buffering the cost for Kiribati.
-We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
-PNA members who indirectly benefit from MPAs should consider mechanisms that reward such conservation actions.
-\end{abstract}
+% Place the author information here.  Please hand-code the contact
+% information and notecalls; do *not* use \footnote commands.  Let the
+% author contact information appear immediately below the author names
+% as shown.  We would also prefer that you don't change the type-size
+% settings shown here.
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+\author{Juan CarlosVillase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
+\\
+\normalsize{$^{1}$Bren School of Environmental Science \& Management,}\\
+\normalsize{University of California at Santa Barbara, Santa Barbara, CA}\\
+\normalsize{$^{2}$Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
+\\
+\normalsize{$^\ast$To whom correspondence should be addressed; E-mail: juancarlos@ucsb.edu.}
+}
+
+% Include the date command, but leave its argument blank.
+
+\date{}
+
+%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
 
@@
 
+% Double-space the manuscript.
+
+\baselineskip24pt
+
+% Make the title.
+
 \maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+% Place your abstract within the special {sciabstract} environment.
+
+\begin{sciabstract}
+Our oceans are becoming increasingly crowded and privatized as different activities compete for space.
+Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
+With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.
+A spatial closure in a vessel-day-managed fishery can potentially result in large costs to the implementing country, which might deter conservation efforts.
+We show that effort markets may reduce up to 70\% of the costs, and that allocation rules based on biomass (rather than effort) may incentivize conservation.
+We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented implemented in 2015 in Kiribati) had on vessel distribution and behavior.
+Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation.
+We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displacing fishing effort.
+We use these insights predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
+Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation.
+The Parties to the Nauru Agreement have successfully managed their fishery and developed a management scheme that allows for conservation interventions to come at a low cost.
+\end{sciabstract}
 
@@
 
-\dropcap{H}umans are increasingly utilizing the oceans.
+Humans are increasingly utilizing the oceans.
 Multiple ocean uses such as off-shore aquaculture, conservation, energy harvesting, deep-sea mining, and fisheries are likely to compete for space.
-As we move forward with blue growth, we must understand the potential effects of activities displacing each other and establish causal links between past management interventions and their outcomes \citep{burgess_2018}.
+As we move forward with blue growth, we must understand the potential effects of activities displacing each other and establish causal links between past management interventions and their outcomes \cite{burgess_2018}.
 One of the most notable spatial interventions is the creation of no-take Marine Protected Areas (MPAs), which seek to conserve the environment by eliminating fishing effort within their waters.
 
-Global international goals aim to protect 10\% of the ocean environment by 2020.
-In an effort to meet this target, there has been a rapid increase in MPA coverage \citep{wood_2008,sala_2018}, largely driven by a small number of Large-Scale Marine Protected Areas (LSMPAs; areas larger than 30,000 km\textsuperscript{2} \emph{sensu} \cite{desanto_2013}).
-Today, a small number of LSMPAs represent at least 80\% of the protected area in the ocean (Fig.
-\ref{fig:LSMPAs_map}; \citep{toonen_2013}).
-However, very little is known about their human dimensions and implications for fisheries \citep{gray_2017}.
-Furthermore, most research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
-One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure and represent large opportunity costs \citep{smith_2003,smith_2010}.
+Today, a small number of Large-scale Marine Protected Areas (LSMPAs; areas larger than 30,000 km\textsuperscript{2} \emph{sensu} \cite{desanto_2013}) represent at least 80\% of the protected area in the ocean (Fig.
+\ref{fig:LSMPAs_map}; \cite{toonen_2013}).
+However, very little is known about their human dimensions and implications for fisheries \cite{gray_2017}.
+Furthermore, research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
+One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure and represent large opportunity costs \cite{smith_2003,smith_2010}.
 
-\begin{figure}[H]
+Displacement or elimination of fishing effort within the protected area might come at a cost when fisheries are managed under an effort market.
+For example, tuna purse seine fisheries in the Pacific are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA; Figure \ref{fig:PNA_map}).
+The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 vessel-days.
+Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power \cite{havice_2010}; vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
+The revenue from access fees may represent up to 50\% of government revenue for some of the parties.
+
+The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth.
+Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2}, about 11\% of Kiribati's EEZ or 2.7\% of total PNA area, effectively displacing all fishing effort within it \cite{mcdermott_2018,mccauley_2016}.
+A pressing question is that of the costs associated to the displacement of fishing effort and possible revenue losses from the fishing license sales.
+While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs, like Palau's 80\% closure to go into effect in 2020 \cite{cimino_2019}.
+
+We develop a bioeconomic model of a fishery operating under a vessel-day scheme with spatial closures to explore the effects of effort redistribution resulting from MPA implementation.
+We characterize the likely outcomes with and without vessel-day trading between countries, as well as the effect of different allocation rules.
+We then empirically evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet operating within PNA waters after the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and implications to Kiribati.
+We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
+These are two of the largest protected areas on the planet and both are controlled by PNA countries.
+
+\section{Results}\label{results}
+
+\subsection{Fishing effort markets and marine conservation}
+
+We begin by simulating a spatial closure in a world where vessel-days can not be traded between countries.
+A spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portions of the Patch (Fig.
+\ref{fig:PNA_model}A).
+The losses are caused by a drop in vessel-day prices for Patch 1, which results from a lower portion of the stock being available for harvest (Fig.
+\ref{fig:vessel_day_price_no_trading_plot}).
+Costs increase with reserve size ($R$), and decrease as within-patch movement ($\theta$) increases.
+Given the non-linear costs ($\beta > 1$), the closure-to-cost ratio can be greater than 1:1 if within-patch movement is low (\emph{i.e.} $\theta < 0.2$).
+The spatial closure in Patch 1 results in moderate increases in revenue for Patches 2 - 9 (Fig.
+\ref{fig:profits_PNA_notKIR_no_trading_plot}).
+When countries do not trade between them, the costs of conservation are large and incurred by Patch 1, but the benefits perceived by the eight other patches.
+Importantly, the increases in revenue to other patches do not compensate for the total losses to Patch 1.
+
+The objective of a VDS is to allow for trading between parties and achieve the optimal distribution of effort in relation to fish distribution.
+In the case of the PNA, for example, spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}.
+Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties \cite{aqorau_2018}.
+We explore the effect of a spatial closure in Patch 1, but now allow for vessel-days to be traded between Patches.
+Patch-level demand for vessel days is governed by the fishable stock size (\emph{i.e.} biomass not within the reserve).
+Trading occurs until vessel-day prices are the same across patches, given a total allowable effort (\emph{i.e.} 45,000 vessel-days) is reached.
+Here, costs from a closure in Patch 1 are significantly reduced by trading (Fig.
+\ref{fig:PNA_model}B-C).
+In this case, surplus of vessel-days in Patch 1 are sold to Patches 2 - 9.
+Vessel-day prices are constant across patches and lower than when there is no reserve, but still higher than when no trading is allowed (Fig.
+\ref{fig:vessel_day_price_with_trading_plot}).
+By optimally trading vessel-days, the cost to the implementing country can be reduced as much as 97\%.
+
+Our previous analyses estimate loss in revenue from effort displacement.
+Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
+In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.
+\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
+Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
+The allocated days to the Patch with the spatial closure would eventually be reduced to the 40\% depending on biomass.
+
+We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future with.
+We used a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently to update annual allocations based on a seven-year running mean of these measures.
+Costs are greater when allocation is based only on patch-level historical effort (\emph{i.e.} $\alpha = 1$; Fig.
+\ref{fig:allocation_cost_plot}).
+However, costs can be significantly reduced when trading is allowed if allocation is based on historical biomass instead.
+When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs in a case without trading.
+
+\subsection{Phoenix Islands Protected Area}
+
+We use identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018 \cite{mccauley_2016,kroodsma_2018}.
+We track the spatial redistribution of the fleet and explore behavioral changes following the 2015 implementation of PIPA in Kiribati.
+We continuously observe 92 vessels for the 2012 - 2018 period.
+Of these, 64 vessels fished within PIPA at least once prior to its implementation, and we refer to them as the ``displaced vessels''.
+The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
+The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
+Our analyses incorporate the monthly NINO4 anomaly index (Fig.
+\ref{fig:nino_plot}) to control for the association that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+
+A market for fishing effort and allocation rules can reduce the costs of displacing fishing effort, but a spatial closure is still likely to cause behavioral changes as vessels redistribute.
+We find that between 2015 and 2016, displaced vessels spent 3,916 and 2,249 less vessel-days in Kiribati and PNA waters, respectively (Figs.
+\ref{fig:all_PS_VDS_year}).
+Over the same period, non-displaced and other vessels spent 1,278 less days in Kiribati, but spent 9,853 more days in PNA waters overall.
+These result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} the other 8 countries).
+At a vessel-day price of \$9,000 USD per day, these would represent \$46.7 and \$68 million USD, respectively.
+
+Annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018, mainly due to displaced vessels allocating less time to Kiribati (Fig.
+\ref{fig:all_PS_VDS_year}B); Fig.
+\ref{fig:hist_kir_fishing}).
+Current effort in Kiribati waters are well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}.
+However, we observe a relatively constant 45,000 vessel-days at the PNA-level, suggesting that Kiribati is, in fact, able to trade vessel-days and reduce the costs of displacement.
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels are shown in Figure \ref{fig:fishing_raster_diff}.
+
+We complement our analysis of change in observed vessel-days by looking at country-level data reported by the Pacific Islands Forum Fisheries Agency (FFA).
+We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD.
+Total PNA revenues showed a net increase of \$28 million USD (Fig.
+\ref{fig:total_PNA_revenues}).
+The largest decrease was observed for Kiribati, while the largest increase was also observed for Papua New Guinea.
+
+Total fishing effort in the PNA increased between 2015 and 2016, but fishing area decreased due to PIPA implementation (Fig.
+\ref{fig:all_PS_VDS_year}).
+We inspect the crowding effects that may arise by applying more (or the same amount of) fishing effort over less fishing area with two indices of spatial overlap between displaced and non-displaced vessels: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month.
+The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
+\ref{fig:sp_corr}).
+The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively.
+Crowding might be driven by environmental variation concentrating fish at specific locations, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton.
+We observe similar patterns when repeating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
+
+Effort displacement and crowding are likely to induce behavioral changes in the fishing fleet.
+We calculate nine vessel-level measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing at-sea hours, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters, Kiribati waters, and the High Seas (Fig.
+\ref{fig:all_panels}).
+We find no evidence of displaced vessels fishing more after PIPA implementation, and in fact observe a 27.5\% decrease ($p < 0.01$; Table \ref{tab:main_DID}) relative to non-displaced vessels.
+Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
+Treated vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
+These changes in distance from shore and port are likely caused by redistribution, as we observe that displaced vessels fished 79.67\% and 49.6\% less in Kiribati and PNA waters respectively, compared to the trend observed for non-displaced vessels ($p < 0.01$).
+We do not observe a statistically significant increase in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
+
+\subsection{Palau National Marine Sanctuary}
+
+On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80 percent of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world, effectively displacing all effort within its waters (Fig.
+\ref{fig:plw_2018} shows longline and purse seine fishing effort within PNMS for 2018).
+As part of the Nauru Agreement, Palau receives 700 purse seine vessel-days each year.
+They also  use a vessel-day scheme to manage the longline fishery  (10,500 vessel-days per year).
+Unlike the purse seine vessel days, longline vessel-days are not tradable within countries and are worth a fraction, at about \$200 USD each.
+Our previous analyses suggest that Palau should be able to lessen the costs of the closure by trading purse seine vessel-days (\$5.65 - \$8.75 million USD) with other PNA members, but might lose more than 50\% of the revenues from the longline vessel-days (\$2.1 million USD).
+
+Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
+In Scenario Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day).
+Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days.
+It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero.
+In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively.
+In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
+The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
+The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+
+% I think we need to modify the last  part of this.
+Based on our analyses, we can say that they would lose a large portion of the longline days, but not all.
+I can calculate the longline effort within the PNMS and we can describe a ``worst-case scenario''.
+Turns out that the 80% closure has only 55.75% of all fishing effort.
+Also, my understanding from the workshop is that the export ban is already in place EXCEPT for tuna purse seines.
+They also pay a 0.35 USD / Kg export tax for fish LANDED in Palau.
+The new proposal is to LIFT the export ban and push for the development of a domestic pelagic fishery (artisanal mFADs and Pole and Line).
+
+\input{revenue_loss}
+
+\clearpage
+
+\section{Discussion}
+
+Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior.
+Our analyses predicts losses in revenue to countries that implement a spatial closure.
+However, these losses can be significantly reduced by market instruments and biomass-based allocation rules.
+Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also other PNA countries and the high seas.
+Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onward.
+Redistribution lead to a crowding effect, and the spatial closure had little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous.
+Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based in biomass, not effort.
+Here, we discuss the implications of our findings and possible shortcomings in our analysis.
+
+We observe ~50\% discrepancies in our estimates of lost revenues when using tracking data and FFA data.
+Vessel-day usage through time matches the 45,000 vessel-days for the PNA and the 11,000 vessel-days allocated to Kiribati \cite{yeeting2018stabilising}.
+Moreover, the trends through time are certainly similar, and all indicate a reduction of usage of Kiribati's waters.
+A possible explanation is that we used the reported mean annual vessel-day prices in our calculations, but there is certainly a spread around these.
+Furthermore, vessels can report their activity as ``transiting to port'' or ``solving mechanical issues'' and this time does not count towards a vessel's usage of VDS, which would result in an overestimation from tracking data.
+
+ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
+For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
+However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
+Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself it does not explain the observed patterns.
+While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
+
+A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of vessel captains.
+Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
+Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or between countries or detailed vessel-day prices.
+
+Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights.
+The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
+The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}.
+Overlaying conservation interventions over existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
+Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
+
+\bibliography{references}
+
+\bibliographystyle{Science}
+
+\clearpage
+
+\FloatBarrier
+
+\section{Figures and tables}
+
+% Map of LSMPAS
+\begin{figure}[htbp]
 \centering
@@
 
-The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth.
-Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2} to fishing and was implemented within an area where approximately 50\% of the world's tuna is caught.
-Tuna purse seine fisheries in the region are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA).
-Members include the Federated States of Micronesia, Kiribati, the Marshall Islands, Nauru, Palau, Papua New Guinea, the Solomon Islands, and Tuvalu; Tokelau joined the VDS in 2012 and started selling access rights in 2013 (Figure \ref{fig:PNA_map}).
-The Nauru Agreement regulates access of foreign vessels (\emph{i.e.} those from non-PNA countries).
-Holding 80\% (14.6 million km\textsuperscript{2}) of historical skipjack tuna purse seine grounds within their Exclusive Economic Zones (EEZ), PNA countries have achieved greater bargaining power when providing fishing access to foreign fleets \cite{havice_2010}.
-The vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
-The revenue from access fees may represent up to 50\% of government revenue for some of the members.
-
-A spatial closure the size of PIPA is likely to cause changes in the spatial distribution and behavior of fishing vessels.
-For example, the anticipation of LSMPAs may lead to preemptive overfishing, which likely erodes or delays the expected benefits of an intervention \cite{mcdermott_2018,hanich2018unraveling}.
-Under a VDS, a reduction in total fishing area within one country's EEZ will result in a reduction in license revenues to said country.
-However, the benefits of the spatial closure are dispersed amongst all other PNA members (through fish movement), who in turn benefit from the conservation efforts of the initial country.
-While no studies have assessed the impact of PIPA, other PNA members have pledged the implementation of LSMPAs by 2020 (\emph{i.e.} Palau).
-
-We simulate the PNA fishery with the addition of spatial closures to characterize possible outcomes of such interventions.
-We then empirically evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet resulting from the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and impacts to Kiribati.
-We use the same data to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are controlled by PNA countries.
-
-Our empirical approach uses identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018.
-We continuously observe 92 vessels for the 2012 - 2018 period.
-Of these, 64 vessels fished within PIPA at least once prior to its implementation, and we refer to them as the ``displaced vessels''.
-The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
-The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
-
+% PNA model output for costs
 \begin{figure}[htbp]
@@
 \includegraphics{img/PNA_model.pdf}
-\caption{\label{fig:PNA_model}Change in revenue from the PNA model with conservation.
-Revenue is shown for Kiribati alone (A) and all other PNA countries (B) as a function of increasing proportion of patch as reserve ($R$).
-Each line (color) represents a value of the movement parameter $\theta$.}
+\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery (vertical axis) as a function of reserve size ($R$; horizontal axis) and movement ($\theta$; line color).
+Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
+Costs avoided by tradig are shown in (C).}
 \end{figure}
 
-\section{Results}\label{results}
+% Costs of different allocation rules
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/allocation_cost_plot.pdf}
+\caption{\label{fig:allocation_cost_plot}Cost (vertical axis) of different allocation rules (line colors) as a function of reserve  size ($R$; horizontal axis) and movement ($\theta$; line type).
+Costs are shown for Patch 1 only.}
+\end{figure}
 
-\subsection{PNA model with conservation}
+% Effort redistribution bars for Kiribati only
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/all_PS_VDS_PNA_KIR_year.pdf}
+\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all all PNA countries (A) and Kiribati (B) by displaced, non-displaced, and other vessels.
+Vessels displaced from PIPA fish less within the PNA, but non-displaced and other vessels fish more, resulting in a net increase.
+Vessels that used to fish within PIPA account for the largest effort reduction to Kiribati.
+The dashed horizontal lines represent the total allowable effort in the PNA (45,000 days) and Kiribati (11,000 days).}
+\end{figure}
 
-We simulate the PNA as a ten-patch meta-population system with discrete time, where Patch 1 considers the implementation of a spatial closure.
-Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
-The stock remains within a Patch during the season, but escapement (\emph{i.e.} stock minus catch) is distributed between all countries at the end of each year.
-A detailed explanation of the model is presented in the Methods section.
-We find that a spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portion of the Patch.
-The loss in revenue increases with reserve size, but decreases as within-patch movement increases (Fig.
-\ref{fig:PNA_model}A).
-For all other PNA countries, however, a spatial closure in Patch 1 is beneficial, especially as within-patch movement decreases and reserve size increases (Fig.
-\ref{fig:PNA_model}B).
-The inverse effects of the spatial closure on Kiribati and the other PNA countries are driven by the redistribution of escapement.
-The stock not fished in the protected portion of Patch 1 eventually redistribute to the other patches, which increases stock size and causes vessel-day prices to increase.
-This model shows that the costs of conservation are incurred by Patch 1, but the benefits are perceived by the eight other patches.
-Moreover, the gains in revenue for other PNA countries does not compensate for the total losses to Kiribati, as a large portion of effort is redistributed to the High Seas.
-
-\subsection{Empirical analysis}
-
-Spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}.
-Vessels may then redistribute across PNA countries as they track these stocks \cite{aqorau_2018}.
-To account for environmentally-driven patterns in vessel location, we incorporate the monthly NINO4 anomaly index in our analyses.
-The NINO4 index is an area-averaged measure of Sea Surface Temperature from 5S-5N and 160E-150W, made available by the Global Climate Observing System (Fig.
-\ref{fig:nino_plot}).
-The NINO4 anomaly index is the same index, with the 1981-2010 mean removed.
-
-\subsubsection{Crowding effect}
-
-We first inspect the crowding effects that may arise due to the net reduction in fishing area.
-We produced 1-degree rasters of monthly fishing effort for our displaced and non-displaced vessels, and calculated two indices of spatial overlap between them: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month.
-We find that the two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively.
-This increase in crowding is likely to increase the encounter rates with other vessels, and reduce the efficiency of fishing operations.
-This might cause vessels to leave their current fishing grounds and re-optimize their spatial effort, leading to a subsequent decrease as the crowding measures return towards pre-implementation levels.
-These results are robust to a series of specifications, accounting for the addition of satellites and monthly NINO4 anomaly (Table \ref{tab:sp_corr}).
-A model fit with the NINO4 anomaly as the only explanatory variable explained just 3\% and 7\% of the variation in our crowding measures.
-Similar results are obtained when repeating the exercise for Kiribati only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr})
-
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \centering
@@
 The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
 \end{figure}
 
-\subsubsection{Behavioral changes}
-
-The behavioral responses that vessels can have to a spatial closure may occur in different ways.
-For example, displacement to new fishing grounds may represent a cost as fishers search the ocean to identify the most suitable fishing spots.
-This may result in increased fuel and labor costs.
-For every vessel in each group, we calculate nine key measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing hours at sea hours, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters, Kiribati waters, and the High Seas (Fig.
-\ref{fig:all_panels}).
-We leverage our Before-After-Control-Impact (BACI) design and implement a log-linear difference-in-differences analysis to evaluate how these measures change for displaced vessels after implementation of PIPA, relative to the trends observed for non-displaced vessels (see the Methods section for our empirical specification).
-As before, our analyses incorporate monthly NINO4 anomalies to account for possible environmentally-driven variations.
-
-We find no evidence of displaced vessels fishing for more hours after PIPA implementation, and in fact observe a negative effect (24.3\% decrease; $p < 0.01$; Table \ref{tab:main_DID}) relative to the non-displaced vessels.
-Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled 21\% less distance, with fishing events occurring 28.5\% and 15.7\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely caused by redistribution, as we observe that displaced vessels fish 58.6\% and 40.3\% less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe a statistically significant increase in fishing hours on the High Seas.
-
-These patterns suggest that displaced vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters (including Kiribati).
-These vessels are also fishing closer to their home ports.
-Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters, with slight increases in the High Seas (Figure \ref{fig:fishing_raster_diff}).
-The results are robust to a set of different specifications, with interaction effects shown in Fig  \ref{fig:other_specifications}.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same reposnses.
-
-\subsubsection{Economic impacts}
-
-The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that displaced vessels have redistributed elsewhere, meaning that they buy less vessel-days from PNA countries.
-To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by Kiribati and all PNA countries by each group of vessels (Fig.
-\ref{fig:all_PS_VDS_year}), and convert these to license revenues using a conservative vessel-day price of \$9,000 USD\footnote{The Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report states that ``Days are currently [2016] selling in a range between \$9,000 and \$13,000 USD.''}.
-We look at all 313 vessels to obtain a more accurate representation of total revenues, but continue to group vessels as displaced (n = 64), non-displaced (n = 28), and other vessels (n = 221).
-
-We find that between 2015 and 2016, displaced vessels spent 3,916 and 2,249 less vessel-days in Kiribati and PNA waters, respectively (Figs.
-\ref{fig:all_PS_VDS_year} and \ref{fig:included_PS_VDS_year_DiD}).
-Over the same period, non-displaced and other vessels spent 1,278 less days in Kiribati, but spent 9,853 more days in PNA waters overall.
-These changes result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} the other 8 countries).
-The net reduction of vessel-days in Kiribati represents a loss of \$46.7 million USD in vessel-day licenses, while the net gain at the PNA-level results in an increase of \$68 million USD.
-
-Moreover, annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018 (Fig.
-\ref{fig:all_PS_VDS_KIR_year}).
-This trend is mainly caused by displaced vessels allocating less time to Kiribati (Figs \ref{fig:all_PS_VDS_KIR_year} and \ref{fig:hist_kir_fishing}).
-Looking at the total annual vessel-days allocated by all vessels to all countries, we see that the largest reductions occur for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
-\ref{fig:all_PS_VDS_cty_year}).
-
-\begin{figure}[ht]
-\centering
-	\includegraphics{img/all_PS_VDS_year.pdf}
-	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by displaced, non-displaced, and other vessels.}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
-	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.}
-\end{figure}
-
-We complement our analysis of change in observed vessel-days by looking at country-level data.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:revenues}A).
-We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD.
-However, total PNA revenues showed a net increase of \$28 million USD (Fig.
-\ref{fig:total_PNA_revenues}).
-The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.
-This is suggestive but certainly not conclusive evidence that Kiribati may have been able to lessen the impact of PIPA on their license revenues by selling their fishing days to other members of the PNA (including Papua New Guinea).
-
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \centering
@@
 
-Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
-\ref{fig:catches}).
-Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
+%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%Need to change the above to Skipjack catch at some point
+\clearpage
 
-\subsection{Potential Revenue Loss for Palau}
+\FloatBarrier
 
-On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
-The sanctuary will fully protect about 80 percent of Palau’s EEZ.
-Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau is able to keep its current allotment of purse seine VDS (700) and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day).
-Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days.
-It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero.
-In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
-The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
-The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 
-\input{revenue_loss}
-
-\section{Discussion}
-
-Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior.
-Our simulation model predicts losses in revenue to countries that implement a spatial closure, increases in revenue to other countries, and an increased fishing of the high seas.
-Using vessel track data, we observe a crowding effect after the implementation of the protected area, as displaced vessels redistribute spatially.
-We see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also other PNA countries and the high seas.
-Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners.
-Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
-Our analysis suggests that the displacement of vessels results in losses to Kiribati, controlling for the effect of El Ni\~{n}o, and that similar although much smaller losses would be expected for Palau's Marine Sanctuary.
-Here, we discuss the implications of our findings and possible shortcomings in our analysis.
-
-Previous studies on protected areas around Pacific islands suggest that vessels move to distant places, which might be translated as increased costs \citep{stevenson_2013}.
-Others have used similar satellite-tracking systems to show that fishing effort accumulates near the edges of spatial closures, yielding greater catches over time \citep{murawski_2005}.
-But these vessel tracks do not cover the pre-reserve period, making it difficult to identify the contribution of spatial closures to the observed spatial distribution of fishing vessels.
-Recent work by \cite{elahi_2018} identified that total fishing effort in a focal region where a short-term MPA was implemented showed little change, likely indicating that fishers redistributed fishing effort to compensate for the reduction in available space.
-Our data, which is assembled in a similar way, allows us to make similar inferences about the unobserved change in aggregate fishing effort and its spatial redistribution.
-
-Our analysis of vessel-days from vessel tracks and loss of profits to Kiribati suggests losses of \$46.7 million USD, while revenue data show a decrease in only \$30 million USD.
-Here, we provide some plausible explanations for these discrepancies.
-One possible explanation is that the dataset used incorrectly labeled vessels as purse seiners.
-However, the scoring algorithm has a high accuracy, and this accuracy increases with the number of observations for a vessel.
-Moreover, on any given year, 90\% of total fishing activity can be explained by 68\% to 75\% of the vessels (Fig \ref{fig:nvessels_to_90}).
-Therefore, if there are any mislabeled vessels in our data, these would contribute little to the large trends that we observe.
-Another alternative is that vessels within PNA waters can report their activity as transiting to port or solving mechanical issues and this time does not count towards a vessel's usage of VDS.
-Second, Kiribati's vessel-day allocation is around 11,000 vessel-days \citep{yeeting2018stabilising}.
-Kiribati could be selling their excess VDS to other PNA countries, which would offset the drop in demand for fishing within their EEZ.
-These explanations are not mutually exclusive, and a combination of them could certainly explain the discrepancy.
-While the magnitude is not the same, the trends and patterns through time are certainly similar, and all indicate a reduction of usage of Kiribati's waters.
-
-ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
-For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
-However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself it does not explain the observed patterns.
-While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
-
-A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of profit-maximizing agents.
-Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
-Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or prices.
-Furthermore, our estimates of revenue loss for PIPA do not account for the allocation calculated each year.
-Each party’s allowable effort is calculated based on historic effort and biomass within each party’s EEZ.
-Sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
-
-Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights.
-The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
-The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}.
-Overlaying conservation interventions over existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
-Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
-
-\begin{scriptsize}
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
 
@@
 
-\subsection{PNA Model with Conservation}
+\subsection{Model for marine conservation with effort markets}
 
-We model the PNA as a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries.
+We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
+Patches 1 - 9 opperate under a vessel-day schemePatches, and Patch 10 represents the high seas and other areas not managed under a VDS.
 The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
 The price of fish is $p$, and catchability is given by $q$.
+These parameters are held constant across patches.
+
+\subsubsection{Fishery dynamics}
 
@@
 
-\begin{figure}[H]	
-	\begin{align}
-	\Pi_1(E_1,X_1,R) = pqE_1X_1(\theta + (1 - \theta)(1 - R))-cE_1^\beta
-	\end{align}
-\end{figure}
+$$
+\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_i-cE_1^\beta
+$$
 
-And profits from fishing in Patch $j = \{2, 3, ..., 10\}$ are:
+With $\Omega_i = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  (0, 1)$) and within-patch fish movement ($\theta$).
+Under this parameterization, $\Omega_{i \not 1} = 1$ since only Patch 1 implements a reserve.
 
-\begin{figure}[H]	
-	\begin{align}
-	\Pi_j(E_j,X_j) = pqE_jX_j-cE_j^\beta
-	\end{align}
-\end{figure}
+Profits from fishing in each Patch are:
+
+$$
+\Pi_i(E_i,X_i) = pqE_iX_i\Omega_i-cE_i^\beta
+$$
 
@@
 
-\begin{figure}[H]	
-	\begin{align}
-	\pi_1(E_1) = pqX_1(\theta + (1 - \theta)(1 - R)) - \beta cE_1^{\beta-1}
-	\label{eqn:marginal_profit_1}
-	\\
-	\pi_j(E_j) = pqX_j - \beta cE_j^{\beta-1}
-	\label{eqn:marginal_profit_j}
-	\end{align}
-\end{figure}
+$$
+\pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
+\label{eqn:marginal_profit}
+$$
 
-In practice, the effort levels in each PNA patch are given (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
+In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
 effort level on the high seas ($E_{10}$) is a result of open access dynamics.
 Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:
+Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
 
-\begin{figure}[H]	
-	\begin{align}
+$$
 E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
 \label{eqn:effort_hs}
-	\end{align}
-\end{figure}
+$$
 
-The patch-level harvest is then determined by effort and stock size:
+Under vds-operated patches, however, profits from marginal effort must equate the cost of fishing in the patch. Therefore vessel-day price for patches under vds ($i = (1, 9)$) is  given by:
 
-\begin{figure}[H]	
-	\begin{align}
-	H_1 = qE_1X_1 (\theta + (1 - \theta)(1 - R))
-	\label{eqn:harvest_1}
-	\\
-	H_j = qE_jX_j
-	\label{eqn:harvest_j}
-	\end{align}
-\end{figure}
+$$
+\pi(E_i) = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
+$$
+
+We can solve for $E_i$ and obtain:
+
+\begin{equation}
+	\begin{split}
+		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
+		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
+		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_1}{\beta c} \\
+		E_i &= \left(\frac{pqX_i\Omega_i - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+	\end{split}
+\label{eqn:demands}
+\end{equation}
+
+Therefore, total allowable effort in the fishery is given by:
+
+$$
+\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+\label{eqn:Ebar}
+$$
+
+\subsubsection{Stock dynamics}
+
+Patch-level harvest is then determined by effort and stock size:
+
+$$
+H_i = qE_iX_i\Omega_i
+\label{eqn:harvest}
+$$
 
 Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$.
-The entire stock then grows according to:
+The entire stock then grows logistically according to:
 
-\begin{figure}[H]	
-	\begin{align}
-	X_{t+1} = e_t + \frac{(\phi + 1)}{\phi}ge_t\left(1 - \left(\frac{e_t}{K}\right) ^{\phi}\right)
+$$
+X_{t+1} = e_t + e^{r \times \frac{e}{K}}
 \label{eqn:grow}
-	\end{align}
-\end{figure}
+$$
+
+Where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
 
@@
 
-\begin{figure}[H]	
-	\begin{align}
+$$
 X_{it+1} = f_iX_{t+1}
 \label{eqn:disperse}
-	\end{align}
-\end{figure}
+$$
 
-The vessel-day price that a country charges is given by $\pi_i$ from Equations \ref{eqn:marginal_profit_1} and \ref{eqn:marginal_profit_j}. Therefore, patch-level license revenues are given by:
+\subsubsection{Vessel-day revenues}
 
-\begin{figure}[H]	
-	\begin{align}
+The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
+
+$$
 \omega = \pi_iE_i
 \label{eqn:license_revenue}
-	\end{align}
-\end{figure}
+$$
 
-Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
 But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
 Thus, the spillover benefits of increasing $R$ are never completely captured.
+
+\subsubsection{Simulations and parametrization}
+
+We inform our model to losely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
+
+\input{tab/parameters.tex}
+
+We use the model above run three different simulations.
+We test the model across a range reserve sizes and movement parameters.
+We use to main scenarios.
+The first scenario does not allow trading.
+In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
+For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
+We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
+We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
+This produces a measure of the cost of implementing a spatial closure of size $R$ in patch 1.
+
+The second scenario allows trading.
+We start again by solving for the high seas to obtain total effort.
+Since a closure is not in effect, this equiulibrium is the same as the first step above.
+We then implement a spatial closure in patch 1.
+This essentially lowers the price fishers would be willing to pay to fish in a patch with biomass $X_i\Omega_i$, lowering demand for vessel-days in pach 1.
+Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from patch 1 are sold to patches 2 - 9.
+This increases effort in these patches, which reduces escapement and therefore biomass.
+This reduction in biomass in turn would modify the demand curves (Eq \ref{eqn:demands}).
+We therefore iterate this process until biomass stabilizes, therefore finding the system's equilibrium.
+Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in patch 1.
+
+\subsection{Allocation rules}
+
+In the second scenario above, effort from a patch with conservation is traded to other patches.
+This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
+After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time.
+At the end of every time, vessel-days are allocated to each patch based on the following rule:
+
+$$
+E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
+(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
+$$
+
+Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$).
+We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures.
+The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales.
+We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
 
@@
 These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \citep{kroodsma_2018}.
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
 
@@
 
+\clearpage
+
 \subsection{Analysis}
@@
 
-\begin{figure}[H]
-	\begin{align}
+$$
 y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
 \label{eqn:sp_corr}
-	\end{align}
-\end{figure}
+$$
 
@@
 
-\begin{figure}[H]
-\begin{align}
+$$
 log(y_{i,t}) = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
 \label{eqn:did}
-\end{align}
-\end{figure}
+$$
 
@@
 
-\begin{comment}
-We test for other more complex specifications that interact a quarterly dummy or year-month dummies with the treatment group and find qualitatively the same results\footnote{I actually need more time to run these, but I don't think they'll change}.
-\end{comment}
-
 All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
-All analyses were performed in R version 3.5.1 \citep{rcore_2018}.
+All analyses were performed in R version 3.5.1 \cite{rcore_2018}.
 Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
 
-\subsubsection{Revenues}
+\subsubsection{Revenues and catches}
 
 We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
+\ref{fig:revenues}A).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
 
-\end{scriptsize}
-
-\section{References}
-
-\bibliography{references}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
+\ref{fig:catches}).
+Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
+Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
+In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
 
 \clearpage
-
-\onecolumn
-
-\FloatBarrier
-
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
 
@@
 \caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
-Countries that belong to the PNA are shown in blue, while empty polygons indicates all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.
+Countries that belong to the PNA are shown in blue, while empty polygons indicate all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon shows PIPA.
+A solid purple polygon shows PNMS.
 Land masses are shown in gray.
@@
 
-\begin{figure}[H]
+\begin{figure}
+\centering
+\includegraphics{img/vessel_day_price_no_trading_plot.pdf}
+\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
+\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) when there is no trading.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/vessel_day_price_with_trading_plot.pdf}
+\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\end{figure}
+
+\begin{figure}
 \centering
@@
 
-\input{tab/sp_corr}
-
-\input{tab/KIR_sp_corr}
-
-\begin{figure}[H]
-\centering
-\includegraphics{img/KIR_sp_corr.pdf}
-\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
-\end{figure}
-
-\input{tab/main_DID}
-
-\begin{figure}[H]
-\centering
-\includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
-Dashed vertical lines indicate the addition of new AIS satellites.
-Solid vertical line indicates the closure of PIPA.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics{img/other_specifications.pdf}
-\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates for our variables of interest using different model specifications.
-Table \ref{tab:main_DID} reports estimates for models with month and flag fixed effects, and NINO4 index (\emph{i.e.} green dots).}
-\end{figure}
-
-\input{tab/DID_without_CHN}
-
-\input{tab/DID_without_PNA}
-
-\input{tab/DID_without_USA_TWN}
-
-\begin{figure}[H]
-\centering
-\includegraphics{img/all_PS_VDS_KIR_year.pdf}
-\caption{\label{fig:all_PS_VDS_KIR_year}Annual vessel-days in Kiribati by group of vessels.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/revenue_FFA_GFW_linear.pdf}
-	\caption{\label{fig:revenue_FFA_GFW_linear}Inferred revenues vs. reported revenues. The dashed line represents line of best fit, and the solid line represents a 1:1 line.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/total_PNA_revenues.pdf}
-	\caption{\label{fig:total_PNA_revenues}Total revenues for all PNA countries combined.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/catches.pdf}
-	\caption{\label{fig:catches}Financial indicators for PNA countries.
-A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
-Vertical dashed line in both plots denotes implementation of PIPA.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}	
-\end{figure}
-
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[H]
+\begin{landscape}
+\input{tab/sp_corr}
+\end{landscape}
+
+\begin{landscape}
+\input{tab/KIR_sp_corr}
+\end{landscape}
+
+\begin{figure}
+\centering
+\includegraphics{img/KIR_sp_corr.pdf}
+\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
+\end{figure}
+
+\begin{landscape}
+\input{tab/main_DID}
+\end{landscape}
+
+\begin{figure}
+\centering
+\includegraphics{img/all_panels.pdf}
+\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing events, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
+Dashed vertical lines indicate the addition of new AIS satellites.
+Solid vertical line indicates the closure of PIPA.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{img/other_specifications.pdf}
+\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates for our variables of interest using different model specifications.
+Table \ref{tab:main_DID} reports estimates for models with month and flag fixed effects, and NINO4 index (\emph{i.e.} green dots).}
+\end{figure}
+
+\begin{landscape}
+\input{tab/DID_without_CHN}
+\end{landscape}
+
+\begin{landscape}
+\input{tab/DID_without_PNA}
+\end{landscape}
+
+\begin{landscape}
+\input{tab/DID_without_USA_TWN}
+\end{landscape}
+
+\begin{figure}
+\centering
+	\includegraphics{img/hist_kir_fishing.pdf}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/all_PS_VDS_cty_year.pdf}
+	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/revenue_FFA_GFW_linear.pdf}
+	\caption{\label{fig:revenue_FFA_GFW_linear}Inferred revenues vs. reported revenues. The dashed line represents line of best fit, and the solid line represents a 1:1 line.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/total_PNA_revenues.pdf}
+	\caption{\label{fig:total_PNA_revenues}Total revenues for all PNA countries combined.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/catches.pdf}
+	\caption{\label{fig:catches}Financial indicators for PNA countries.
+A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
+Vertical dashed line in both plots denotes implementation of PIPA.}
+\end{figure}
+
+\begin{figure}
+\centering
+	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
+	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}	
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{img/plw_2018.png}
+\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palaw during 2018 at a 0.5 degree resolution. The red polygon shows the Palau National Marine Sanctuary.}
+\end{figure}
+
+I used this figure at the workshop last week, I do not intend to use it with the current design.
+I want to have a normal white background and split it into 2 (longliners and purse seiners) to better capture the effort that would be displaced by PNMS.
+I might also break it by year (2015 - 2018) to show that patterns are consistent through time.
+
+\begin{figure}
 \centering
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 %incorporation of technology, in what then became known as Dynamic Ocean
-%Management \citep{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.} 
+%Management \cite{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.} 
 %
@@
 %effort based on habitat characteristics, presence of other vessels, and
-%expected returns \citep{smith_2003,hilborn_2006}. However, these focus
+%expected returns \cite{smith_2003,hilborn_2006}. However, these focus
 %on the long term optimal equilibrium, and redistribution of fishing
 %effort may not always be optimally distributed, especially over the first few years
-%\citep{stevenson_2013}.
+%\cite{stevenson_2013}.
 %
@@
 %closure can have major implications for its outcome
-%\citep{smith_2003,hilborn_2006}, highlighting the need to understand how
+%\cite{smith_2003,hilborn_2006}, highlighting the need to understand how
 %fishers react to the implementation of LSMPAs, how fishing effort
@@
 %the approach to manage fishing effort: a Vessel Day Scheme (VDS)
-%implemented in 2007 \citep{havice_2013}. This effectively modified how
+%implemented in 2007 \cite{havice_2013}. This effectively modified how
 %fishing effort was managed, from total number of vessels (under the Palau
@@
 A minimum benchmark fee is set for purse seine vessel days which each party can transfer (\emph{i.e.} sell to another PNA member) or sell to the highest bidder (\emph{i.e.} sell to a fishing company).
-Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \citep{havice_2013}.
-%Although detailed records on sales or transfers of vessel days are not publicly available \citep{havice_2013,yeeting2018stabilising}, a minimum benchmark fee of \$8,000/day was set from 2015 \citep{PNA2014a}.
+Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \cite{havice_2013}.
+%Although detailed records on sales or transfers of vessel days are not publicly available \cite{havice_2013,yeeting2018stabilising}, a minimum benchmark fee of \$8,000/day was set from 2015 \cite{PNA2014a}.
 %
-%\cite{yeeting2018stabilising} summarize the PNA implementing arrangements as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \citep{PNA2016}.
-Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \citep{PNA2016}.
+%\cite{yeeting2018stabilising} summarize the PNA implementing arrangements as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \cite{PNA2016}.
+Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \cite{PNA2016}.
 As described in the Palau Arrangement, fishing days by vessels shorter than 50m (longer than 80m) count as 0.5 (1.5) vessel days.
 Countries are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within their PAE.
-Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \citep{PNA2016}.
-There are some criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the program \citep{Arnason2014,yeeting2018stabilising}.
+Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \cite{PNA2016}.
+There are some criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the program \cite{Arnason2014,yeeting2018stabilising}.
 While the effectiveness of this scheme has been
@@
 %objectives, the licensing significantly contributes to the economy of
-%these island nations \citep{havice_2010}.
+%these island nations \cite{havice_2010}.
 %
@@
 %global fisheries production statistics, with 2016 catches increasing
-%relative to the 2005-2014 average \citep{fao_2018}. This region of the
+%relative to the 2005-2014 average \cite{fao_2018}. This region of the
 %Pacific has historically accounted for a large portion of tuna catches
@@
 %showing that fishing effort is effectively reduced after implementation
-%\citep{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
+%\cite{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
 %How did individual vessels respond to the sudden exclusion of such a big
@@
 During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna.
-During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \citep{chapman2000development}.
+During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \cite{chapman2000development}.
 There are currently three transshipment companies operating in Palau.
@@
 %An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
-Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \citep{Tewid2013}.
-Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \citep{Gillett2016}.
+Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \cite{Tewid2013}.
+Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \cite{Gillett2016}.
 Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
@@
 So, for example, there were 38 vessels as part of these agreements in 2016.
-Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \citep{Gillett2016}.
+Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \cite{Gillett2016}.
 These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
@@
 %
-%The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \citep{Gillett2016}. 
+%The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \cite{Gillett2016}. 
 %Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery.
@@
 Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers.
-comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \citep{Tewid2013}).
+comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \cite{Tewid2013}).
 Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
@@
 When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
-Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \citep{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \citep{Pojas2018}.
+Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \cite{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \cite{Pojas2018}.
 In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers.
@@
 %Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
-There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \citep{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
+There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \cite{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
 

### 2019-05-22 docs/old_ms/PIPA_Palau_Science_JL.tex
Updated MS for John and Chris

--- 2019-05-22 docs/old_ms/PIPA_Palau_Science.tex
@@
 \begin{sciabstract}
-Our oceans are becoming increasingly crowded and privatized as different activities compete for space.
 Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
 With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.
-A spatial closure in a vessel-day-managed fishery can potentially result in large costs to the implementing country, which might deter conservation efforts.
-We show that effort markets may reduce up to 70\% of the costs, and that allocation rules based on biomass (rather than effort) may incentivize conservation.
-We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented implemented in 2015 in Kiribati) had on vessel distribution and behavior.
+A spatial closure in a trans-boundary fishery can potentially result in costs to the implementing country and benefits to neighboring countries.
+We show that effort markets may reduce up to 70\% of the costs of Marine Protected Areas, and that allocation rules based on biomass (rather than effort) may further incentivize conservation.
+We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented in 2015 in Kiribati) had on vessel distribution and behavior.
 Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation.
-We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displacing fishing effort.
-We use these insights predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually.
+We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displaced fishing effort.
+We use these insights to predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate that effort markets could reduce the cost of implementation by as much as 77\%.
 Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation.
-The Parties to the Nauru Agreement have successfully managed their fishery and developed a management scheme that allows for conservation interventions to come at a low cost.
+The Parties to the Nauru Agreement have successfully developed a management scheme that allows for conservation interventions to come at a low cost, and could be a model for trans-boundary conservation across the globe.
 \end{sciabstract}
@@
 
-Displacement or elimination of fishing effort within the protected area might come at a cost when fisheries are managed under an effort market.
+Displacement or elimination of fishing effort within the protected area might come at a cost to the implementing party when fisheries are managed under an effort market (i.e.
+fishing rights are sold to firms).
 For example, tuna purse seine fisheries in the Pacific are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA; Figure \ref{fig:PNA_map}).
-The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 vessel-days.
-Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power \cite{havice_2010}; vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
-The revenue from access fees may represent up to 50\% of government revenue for some of the parties.
+The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 ``vessel-days'': the right for one vessel to fish for one day in a country's waters.
+Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power by working together \cite{havice_2010}; the vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
+The revenue from fisheries access fees represents up to 50\% of government revenue for some of the PNA countries.
 
@@
 Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2}, about 11\% of Kiribati's EEZ or 2.7\% of total PNA area, effectively displacing all fishing effort within it \cite{mcdermott_2018,mccauley_2016}.
-A pressing question is that of the costs associated to the displacement of fishing effort and possible revenue losses from the fishing license sales.
+A pressing question is that of the costs associated with the displacement of fishing effort and possible revenue losses from vessel-day sales.
 While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs, like Palau's 80\% closure to go into effect in 2020 \cite{cimino_2019}.
@@
 
-We begin by simulating a spatial closure in a world where vessel-days can not be traded between countries.
+We begin by simulating a spatial closure in a setting where vessel-days can not be traded between countries.
 A spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portions of the Patch (Fig.
@@
 \ref{fig:profits_PNA_notKIR_no_trading_plot}).
-When countries do not trade between them, the costs of conservation are large and incurred by Patch 1, but the benefits perceived by the eight other patches.
-Importantly, the increases in revenue to other patches do not compensate for the total losses to Patch 1.
+When countries can not trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches.
+Importantly, the increases in revenue to the other patches do not compensate for the total losses to Patch 1.
 
@@
 In the case of the PNA, for example, spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}.
-Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties \cite{aqorau_2018}.
+Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties by allowing them to sell surplus vessel-days to be used in the EEZ of another country \cite{aqorau_2018}.
 We explore the effect of a spatial closure in Patch 1, but now allow for vessel-days to be traded between Patches.
@@
 \ref{fig:PNA_model}B-C).
-In this case, surplus of vessel-days in Patch 1 are sold to Patches 2 - 9.
+In this case, the surplus of vessel-days in Patch 1 are sold to Patches 2 - 9.
 Vessel-day prices are constant across patches and lower than when there is no reserve, but still higher than when no trading is allowed (Fig.
@@
 
-Our previous analyses estimate loss in revenue from effort displacement.
+Our previous analysis predicts a loss in total revenue from effort displacement.
 Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.
-\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
-Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to the Patch with the spatial closure would eventually be reduced to the 40\% depending on biomass.
+In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
+The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
 
-We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future with.
+We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future.
 We used a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently to update annual allocations based on a seven-year running mean of these measures.
@@
 However, costs can be significantly reduced when trading is allowed if allocation is based on historical biomass instead.
-When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs in a case without trading.
+When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs.
 
@@
 Annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018, mainly due to displaced vessels allocating less time to Kiribati (Fig.
-\ref{fig:all_PS_VDS_year}B); Fig.
+\ref{fig:all_PS_VDS_year}B, Fig.
 \ref{fig:hist_kir_fishing}).
-Current effort in Kiribati waters are well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}.
+Current effort in Kiribati waters is well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}.
 However, we observe a relatively constant 45,000 vessel-days at the PNA-level, suggesting that Kiribati is, in fact, able to trade vessel-days and reduce the costs of displacement.
@@
 \ref{fig:total_PNA_revenues}).
-The largest decrease was observed for Kiribati, while the largest increase was also observed for Papua New Guinea.
+The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.
 
@@
 We inspect the crowding effects that may arise by applying more (or the same amount of) fishing effort over less fishing area with two indices of spatial overlap between displaced and non-displaced vessels: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month.
-The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr} Fig.
+The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
 \ref{fig:sp_corr}).
@@
 They also  use a vessel-day scheme to manage the longline fishery  (10,500 vessel-days per year).
-Unlike the purse seine vessel days, longline vessel-days are not tradable within countries and are worth a fraction, at about \$200 USD each.
+Unlike the purse seine vessel-days, longline vessel-days are not tradable across countries and are worth much less, at about \$200 USD each.
 Our previous analyses suggest that Palau should be able to lessen the costs of the closure by trading purse seine vessel-days (\$5.65 - \$8.75 million USD) with other PNA members, but might lose more than 50\% of the revenues from the longline vessel-days (\$2.1 million USD).
@@
 Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+In Scenario 1, Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
 In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day).
@@
 In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is planning on banning the export of fish.
+In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is currently planning on banning the export of fish.
 The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
@@
 
-Our findings provide insights into the effect that LSMPAs can have on redistribution of fishing effort and change in behavior.
-Our analyses predicts losses in revenue to countries that implement a spatial closure.
+Our findings provide insights into the effect that LSMPAs can have on the redistribution of fishing effort and changes in behavior.
+Our analyses predict losses in revenue to countries that implement a spatial closure.
 However, these losses can be significantly reduced by market instruments and biomass-based allocation rules.
-Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also other PNA countries and the high seas.
+Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also to other PNA countries and the high seas.
 Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onward.
-Redistribution lead to a crowding effect, and the spatial closure had little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous.
-Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based in biomass, not effort.
+Redistribution leads to a crowding effect, and the spatial closure has little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous.
+Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based on biomass, not effort.
 Here, we discuss the implications of our findings and possible shortcomings in our analysis.
@@
 However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself it does not explain the observed patterns.
+Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns.
 While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
@@
 Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
-Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions or between countries or detailed vessel-day prices.
+Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions between countries or detailed vessel-day prices.
 
 Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights.
-The closure caused a crowding effect, which causes some vessels to redistribute to areas close by.
+The closure caused a crowding effect, which seems to lead some vessels to redistribute to areas close by.
 The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}.
-Overlaying conservation interventions over existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
-Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
+Overlaying conservation interventions and existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
+Furthermore, implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
 

### 2019-05-22 scripts/model/2_run_model.Rmd
Added scripts

@@
     xlab("Portion of patch as reserve (R)") +
-    ylab("Costs\n(% of case with R = 0)") +
+    ylab("Losses\n(relative to R = 0)") +
     scale_color_viridis_c() +
@@
   xlab("Portion of patch as reserve (R)") +
-  ylab("Costs (% of case with R = 0)") +
+  ylab("Losses (relative to R = 0)") +
   scale_color_viridis_c() +
@@
   xlab("Portion of patch as reserve (R)") +
-  ylab("Costs\n(% of case with R = 0)") +
+  ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
@@
   startR::ggtheme_plot() +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
+                     limits = c(0.885, 1)) +
   theme(legend.position = "None"))
@@
    geom_line(size = 1.5) +
-   scale_y_continuous(labels = scales::percent) +
+   scale_y_continuous(labels = scales::percent,
+                      limits = c(0, 1)) +
    xlab("Portion of patch as reserve (R)") +

### 2019-05-22 scripts/content/fig_all_panels.R

@@ -168,7 +168,7 @@ plot <- cowplot::plot_grid(
 ggsave(plot = plot,
        filename = here("docs", "img", "all_panels.pdf"),
        width = 6.5,
-       height = 8.7)
+       height = 8)
 
 
 

### 2019-05-22 scripts/content/figs_all_PS_VDS_2012_2018.R

@@ -135,8 +135,8 @@ ggsave(all_PS_VDS_KIR_year_plot,
        height = 4)
 
 #Both bars
-p22 <- plot_grid(all_PS_VDS_year_plot,
-                 all_PS_VDS_KIR_year_plot,
+p22 <- plot_grid(all_PS_VDS_KIR_year_plot,
+                 all_PS_VDS_year_plot,
                  ncol = 1, labels = "AUTO")
 
 #Save plot

### 2019-05-22 scripts/content/plot_financial_indicators.R

@@ -79,7 +79,7 @@ vessel_activity <- readRDS(file = here("raw_data",
                                        "activity_by_vessel_year_eez.rds")) %>% 
   filter(best_vessel_class == "tuna_purse_seines",
          eez_iso3 %in% PNA_countries) %>% 
-  mutate(days = hours / 24) %>% 
+  mutate(days = hours_length / 24) %>% 
   group_by(year, eez_iso3) %>% 
   summarize(days = sum(days)) %>% 
   left_join(vds_price_per_year, by = "year") %>% 
@@ -136,6 +136,26 @@ log_revenue_FFA_GFW <-
   scale_size_continuous(breaks = c(1, 5, 10), range = c(1, 4)) +
   guides(fill = F)
 
+revenue_FFA_effort_GFW <-
+  ggplot(vessel_activity, aes(x = days, y = revenue)) +
+  geom_point(aes(fill = country, size = days),
+             shape = 21,
+             # size = 3,
+             alpha = 0.7) +
+  geom_smooth(method = "lm",
+              linetype = "dashed",
+              color = "black",
+              se = F) +
+  scale_fill_brewer(palette = "Set1", guide = F) +
+  theme_cowplot()  +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8)) +
+  guides(fill = guide_legend(title = "Country", ncol = 1),
+         size = guide_legend(title = "Vessel-days (1,000)", ncol = 3)) +
+  labs(x = "Vessel-days (1,000)",
+       y = "Reported revenue\n(million USD)") +
+  scale_size_continuous(breaks = c(1, 5, 10))
+
 # Put together
 p <- plot_grid(p1,
                log_revenue_FFA_GFW,
@@ -150,6 +170,11 @@ ggsave(p,
 
 ggsave(revenue_FFA_GFW,
        filename = here("docs", "img", "revenue_FFA_GFW_linear.pdf"),
+       width = 5.5,
+       height = 3.4)
+
+ggsave(revenue_FFA_effort_GFW,
+       filename = here("docs", "img", "revenue_FFA_effort_GFW.pdf"),
        width = 5.5,
        height = 3.4)
 

### 2019-05-28 docs/slides/GainesLab_presentation.Rmd
Added slides for gaines lab and new manuscript by John

--- 2019-05-04 docs/slides/NCEAS_presentation.Rmd
@@
 ---
-title: "Marine Conservation and Fishing Effort Markets"
+title: "Fishery Markets and Large-Scale Marine Conservation"
 author:
-  - Villaseñor-Derbez J.C.$^1$
-  - Lynham J.$^2$
-  - Costello C.$^{1, 3}$
-institute: 
-   - $^1$Bren School, UCSB
-   - $^2$Department of Economics, UHM
-   - $^3$emLAB, UCSB
-subtitle: "NCEAS-Future Earth Working Group"
-date: "May 6, 2019"
+  - Villaseñor-Derbez J.C.
+  - Lynham J.
+  - Costello C.
+subtitle: "Gaines Lab"
+date: "May 28, 2019"
 output: 
@@
 
-  - Phoenix Island Protected Area
+- Model predictions
 
-- Generalizability to Palau
+- Phoenix Island Protected Area*
+
+- Palau National Marine Sanctuary
+
+- Conclusions
 
 # Background and motivation
+
+## Motivation
+
+- Only 3\% of the ocean under "fully protected" MPAs
+
+- Goals to meet 10 - 30\%
+
+- Opportunity costs of closing areas to fishing
+
+- How do we incentize conservation?
+
+## Motivation
+
+### Guiding question
+
+- Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
+
+- Vessel-day scheme in the PNA region may hold the answer
 
@@
 
-## Motivation
-
-### Relationship between closure size and losses
-
-Does a 30\% closure mean a 30\% loss in revenue?
-
 # Scope and Approach
@@
 
+  - Does a 30\% closure mean a 30\% effort displacement and therefore a 30\% loss in revenue?
+
   - What are the costs associated to establishing an MPA?
@@
 
-  - Can these costs be reduced or eliminated?
+  - Can these costs be reduced or eliminated by appropriately designing markets?
 
@@
 
+  - Where was effort displaced to?
+
   - How do they respond?
-
-  - Where do they go?
 
@@
 
-$$\Pi_i(E_i,X_i,R) = pqE_iX_i\Omega_i-cE_i^\beta$$
+$$\Pi_i = pqE_iX_i\Omega_i-cE_i^\beta$$
 
@@
 
-# PIPA
-
 ## What can we learn from PIPA?
@@
 
-## Effort displacement raster
+## Effort displacement in all PNA
 
 ```{r}
-knitr::include_graphics(here("docs", "img", "rasterized_change.png"))
+knitr::include_graphics(here("docs", "img", "all_PS_VDS_year.pdf"))
 ```
 
-# Generalizability to Palau
+# Palau
 
-# Extra slides - GFW data
+## Palau National Marine Monument
 
-## Effort vs catches
+- Close **80\%** of its EEZ to **all** industrial fishing activities
+
+- To be closed December 2020
+
+- Have not evaluted the possible implications
+
+## Likely costs to Palau
+
+```{r, fig.widht = 4, fig.align = "left"}
+knitr::include_graphics("../img/plw_2018_slides.png")
+```
+
+## Fisheries management in Palau
+
+- Purse seine vessel-days
+
+  - 700 purse seine vessel-days
+
+  - \$5.60 - \$8.75 Million USD
+
+  - "Tradable"
+
+  - Trading might reduce costs, but allocation rules matter
+
+- Longline vessel-days
+
+  - 10,500 longline vessel-days
+
+  - \$2.10 Million USD
+
+  - Non-tradable
+
+## Conclusions
+
+### Rights-based management for conservation
+
+Two market features can eliminate costs of conservation:
+
+- Trading
+
+- Biomass-based allocation
+
+# Extra slides
+
+## GFW summary for Palau
 
 ```{r}
-knitr::include_graphics(here("docs", "slides", "img", "catch_effort_plot.png"))
+knitr::include_graphics(here("docs", "slides", "img", "vessels_in_plw.png"))
 ```
-
-## Effort and revenues
-
-```{r}
-knitr::include_graphics(here("docs", "img", "revenue_FFA_GFW_linear.pdf"))
-```
-
-## Vessel statistics
-
-A short table with information on number of vessels per year and class
-
-Palau-specific information about longliners

### 2019-05-28 scripts/model/2_run_model.Rmd
Added slides for gaines lab and new manuscript by John

@@
    xlab("Portion of patch as reserve (R)") +
-   ylab("Costs\n(% of case with R = 0)") +
+   ylab("Losses\n(relative to R = 0)") +
    scale_color_viridis_c() +

### 2019-05-28 scripts/content/plw_fishing_raster_2018_by_gear.R

@@ -102,6 +102,20 @@ ggsave(plw_2018,
        width = 7,
        height = 3.5)
 
+# For slides
+# Export plot as png
+plw_2018_slides <- plot_grid(plw_2018_ll + 
+                               theme(legend.position = "None"),
+                             plw_2018_ps + 
+                               theme(legend.position = "None"),
+                             ncol = 2,
+                             labels = c("Longlines", "Purse seines"),
+                             label_fontface = "plain",
+                             label_size = 12)
+ggsave(plw_2018_slides,
+       filename = here("docs", "img", "plw_2018_slides.png"),
+       width = 4.5,
+       height = 3)
 
 #### Effort within PNMS?
 # How much longline effort is displaced?

### 2019-05-30 scripts/model/2_run_model.Rmd
Added scripts

@@
 # Load libraries
+suppressPackageStartupMessages({
   library(startR)
@@
   library(tidyverse)
+})
 
@@
 params %>% 
-  knitr::kable(col.names = c("Parameter", "Value", "Source"), format = "latex", escape = F) %>% 
+  knitr::kable(col.names = c("Parameter", "Value", "Source"),
+               format = "latex",
+               escape = F) %>% 
+  kableExtra::kable_styling(latex_options = "scale_down") %>%
   cat(file = here("docs", "tab", "parameters.tex"))
@@
 ```{r}
-# Create an empty tibble to store the results in the process
+# Create combinations of R and theta
 Rvec <- seq(0, 1, 0.05)
@@
     cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
-    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
+    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
+    cost_all = VDSrevenue_all - b_vdsrevenue_all,
+    rel_cost_all = cost_all / b_vdsrevenue_all
   )
@@
     cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
-    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
+    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
+    cost_all = VDSrevenue_all - b_vdsrevenue_all,
+    rel_cost_all = cost_all / b_vdsrevenue_all
   )

### 2019-05-30 scripts/collection/JPN_tracks_download.R

@@ -1,0 +1,58 @@
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+BQc <- bigrquery::dbConnect(drv = bigrquery::bigquery(), 
+                            project = "ucsb-gfw", 
+                            dataset = "mpa_displacement", 
+                            allowLargeResults = TRUE)
+
+DBI::dbListTables(BQc)
+
+vessel_tracks <- dplyr::tbl(BQc, "JPN_tracks") %>% 
+  collect()
+
+# Modify the data
+vessel_tracks %<>%
+  distinct() %>%
+  mutate(
+    date = lubridate::date(timestamp),
+    post = year >= 2015,
+    nnet_score = ifelse(is.na(nnet_score), 0, nnet_score), # If there are NAs in nnet_score, convert to 0 (no fishing)
+    fishing = nnet_score >= 0.5, # Values of nnet_score > 0.5 imply fishing
+    month_c = as.character(month),
+    year_c = as.character(year),
+    year_month = lubridate::date(paste(year, month, 1, sep = "/")),
+    quarter = lubridate::quarter(
+      date,
+      with_year = T)) %>%
+  select(
+    year,
+    month,
+    day,
+    date,
+    timestamp,
+    post,
+    treated,
+    mmsi,
+    gear,
+    flag,
+    lon,
+    lat,
+    hours,
+    fishing,
+    nnet_score,
+    eez_iso3,
+    distance_from_port,
+    distance_from_shore,
+    seg_id,
+    month_c,
+    year_c,
+    year_month,
+    quarter
+  )
+
+saveRDS(vessel_tracks, file = here::here("raw_data", "JPN_tracks.rds"))
+

### 2019-05-30 scripts/content/PS_VDS_PNA_by_year_eez.R

@@ -1,0 +1,71 @@
+################################
+#   PS_VDS_PNA_by_month_eez    #
+################################
+
+
+##########################################################################
+# This script calculates the number of total hours that ALL purse seiners
+# spent in PNA waters (PNA includes TKL).
+##########################################################################
+
+#### SETUP ########################################################
+# Load packages
+library(here)
+library(tidyverse)
+
+# Load data
+# Filter to keep only purse seiners before 2018 and modify the fishing label
+vessel_activity <- readRDS(file = here("raw_data",
+                                       "vessel_tracks_ALL_vessels_fished_PNA_2012_present.rds")) %>% 
+  filter(eez_iso3 %in% c("FSM",
+                         "KIR",
+                         "MHL",
+                         "NRU",
+                         "PLW",
+                         "PNG",
+                         "SLB",
+                         "TUV",
+                         "TKL"),
+         inferred_label == "tuna_purse_seines",
+         year < 2019) %>% 
+  mutate(fishing = ifelse(is.na(fishing), F, fishing),
+         fishing = ifelse(fishing, "Fishing", "Non-fishing"),
+         group = ifelse(treated, "Treatment", "Control"),
+         group = ifelse(is.na(treated), "Others", group),
+         eez_iso3 = fct_relevel(eez_iso3, "KIR"))
+
+#### CREATE THE DATA ################################################
+# Data for monthly activity by EEZ
+vessel_activity_month_country <- vessel_activity %>% 
+  group_by(year, month, eez_iso3) %>% 
+  summarize(days = sum(days, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(date = lubridate::date(paste(year, month, 1, sep = "-")))
+
+##### MONTHLY PLOTS ##############################################
+
+# Plot of monthly vessel days per EEZ
+p3 <- ggplot(vessel_activity_month_country,
+             mapping = aes(x = date, y = days, color = eez_iso3, fill = eez_iso3)) + 
+  geom_line() +
+  geom_point(shape = 21,
+             color = "black",
+             size = 1) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  cowplot::theme_cowplot() +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8),
+        strip.background = element_blank())+
[…]

### 2019-05-30 scripts/content/example_treated_control_vessels.R

@@ -1,0 +1,50 @@
+
+# Load the packages that I need
+library(dplyr)
+library(dbplyr)
+library(DBI)
+library(bigrquery)
+library(magrittr)
+
+source(here::here("scripts", "functions", "st_rotate.R"))
+
+# DOWNLOAD THE DATA
+# Create a tbl pointing to vessel tracks
+vessel_tracks <- get_table(project = "ucsb-gfw",
+                           dataset = "mpa_displacement",
+                           table = "sample_treated_control_vessels")
+
+pipa <- sf::read_sf(dsn = here::here("data", "spatial", "PIPA"), layer = "PIPA") %>% 
+  sf::st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_rotate()
+
+pna <- read_sf(dsn = here("data", "spatial", "PNA_EEZ"),
+               layer = "PNA_EEZ") %>% 
+  select(ISO_Ter1) %>% 
+  st_simplify(10) %>% 
+  st_rotate() %>% 
+  st_union(by_feature = T)
+
+sample_tracks <- vessel_tracks %>% 
+  mutate(year = lubridate::year(timestamp),
+         lon = ifelse(lon < 0, lon + 360, lon)) %>% 
+  filter(fishing, year == 2014,
+         between(lat, -15, 17),
+         between(lon, 129, 213)) %>% 
+  ggplot() +
+  geom_sf(data = pna, fill = "gray90", alpha = 0.5, color = "black", size = 0.1) +
+  geom_point(aes(x = lon, y = lat, fill = treated),
+             size = 1,
+             shape = 21,
+             color = "black") +
+  geom_sf(data = pipa, fill = "transparent", color = "red", size = 1) +
+  ggtheme_map() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(text = element_text(size = 12),
+        legend.position = "None") +
+  labs(x = "Longitude", y = "Latitude")
+
+ggsave(plot = sample_tracks,
+       filename = here("docs", "slides", "img", "sample_tracks.png"),
+       width = 4.5,
+       height = 2.5)

### 2019-05-30 scripts/content/fig_all_panels.R

@@ -1,0 +1,195 @@
+###################
+#   all_panels   #
+###################
+
+
+###################################################################
+# Daily fishing hours for all vessels in our maintreatment-control
+# groups. Red and blue lines show monthly avarages for each group.
+# Vertical dashed lines indicates dates when satellites were added,
+# solid line indicates PIPA closurePIPA closure.
+##################################################################
+
+
+#Load packages
+library(here)
+library(cowplot)
+library(tidyverse)
+
+# Varplot
+varplot <- function(data, var, y_lab){
+  var <- enquo(var)
+  
+  ggplot(data = data, mapping = aes(x = date, y = !!var, color = treated)) +
+    # geom_jitter(shape = ".", height = 0, alpha = 0.1) +
+    stat_summary(geom = "line", fun.y = mean, size = 1) +
+    theme_cowplot() +
+    scale_color_brewer(palette = "Set1", direction = -1) +
+    guides(color = guide_legend(title = "Group")) +
+    geom_vline(xintercept = lubridate::date("2015/01/01")) +
+    geom_vline(xintercept = lubridate::date("2014/06/01"), linetype = "dashed") +
+    geom_vline(xintercept = lubridate::date("2015/12/31"), linetype = "dashed") +
+    theme(legend.position = "none",
+          text = element_text(size = 10),
+          axis.text = element_text(size = 8),
+          legend.text = element_text(size = 8)) +
+    labs(x = "Date", y = y_lab)
+}
+
+## FISHING HOURS ##################################################################
+# Load data
+effort_by_vessel <- readRDS(file = here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines") %>% 
+  mutate(date = lubridate::date(paste(year, month, 15, sep = "/")),
+         treated = ifelse(treated, "Displaced", "Non-displaced"))
+
+# Plot of fishing hours
+fishing_hours <- effort_by_vessel %>% 
+  filter(fishing) %>%
+  varplot(hours, "hours") +
+  theme(legend.justification = c(0, 1),
+        legend.position = c(0, 1.1))
+
+# Plot of nonfishing hours
+nonfishing_hours <- effort_by_vessel %>% 
+  filter(!fishing) %>%
+  varplot(hours, "hours")
+
[…]

### 2019-05-30 scripts/content/fishing_raster.R

@@ -1,0 +1,96 @@
+#######################
+#   fishing_raster    #
+#######################
+
+################################################################################
+# Yearly spatial distribution of fishing effort by treated and control vessels.
+# Colors have been adjusted relative to the maximum observed by group and year.
+# Red polygons show LGMPAs in the region.
+################################################################################
+
+#### SET UP ##################################################
+
+# Load packages
+library(here)
+library(sf)
+library(tidyverse)
+
+# Source local functions
+source(here("scripts", "functions", "st_rotate.R"))
+source(here("scripts", "functions", "sfc_as_cols.R"))
+
+##### EEZs #################################################
+# Countries I want to show
+countries <- c("PIPA",
+               "KIR",
+               "HS",
+               "ASM",
+               "COK",
+               "FSM",
+               "MHL",
+               "NRU",
+               "PNG",
+               "SLB",
+               "TKL",
+               "TUV",
+               "UMI",
+               "FJI",
+               "NIU",
+               "TON",
+               "WSM",
+               "WLF",
+               "VUT",
+               "NCL")
+# Load EEZs
+eez <- read_sf(dsn = here("data", "spatial", "EEZ_subset"),
+               layer = "EEZ_subset") %>% 
+  filter(ISO_Ter1 %in% countries) %>% 
+  mutate(KIR = ISO_Ter1 == "KIR",
+         PNA = ifelse(PNA, "PNA", "Non-PNA")) %>% 
+  group_by(ISO_Ter1, PNA, KIR) %>% 
+  summarize()
+
+##### MPAS #################################################
+# Load MPA shapefiles
+mpas <- read_sf(dsn = here("data", "spatial", "LSMPAs"), layer = "LSMPAs") %>% 
+  janitor::clean_names() %>% 
+  filter(!wdpaid %in% c(555512002, 555512001)) %>% 
+  st_transform(crs = 4326) %>% 
+  st_rotate() %>%
+  mutate(strict = ifelse(no_tk_area > 0 |
+                           iucn_cat %in% c("Ia", "Ib") |
+                           desig_eng == "Protected Area",
+                         "No-Take", "Others"),
+         strict = ifelse(is.na(strict), "Others", strict),
+         strict = ifelse(wdpaid == 309888, "PIPA", strict),
[…]

### 2019-05-30 scripts/content/plw_fishing_raster_2018_by_gear.R

@@ -1,0 +1,242 @@
+########################################
+##  plw_fishing_raster_2018_by_gear   ##
+########################################
+
+## SET UP
+# Load libraries
+library(startR)
+library(here)
+library(cowplot)
+library(raster)
+library(sf)
+library(tidyverse)
+
+# Load custom functions
+source(here("scripts", "functions", "st_rotate.R"))
+
+# Load Palauan EEZ
+plw_eez <- read_sf(here::here("data", "spatial", "PNA_EEZ"), "PNA_EEZ") %>% 
+  st_rotate() %>%
+  select(ISO_Ter1) %>% 
+  filter(ISO_Ter1 %in% c("PLW")) %>% 
+  st_simplify(100)
+
+# Load PNMS boundaries
+pnms <- read_sf(dsn = here::here("data", "spatial", "LSMPAs"), layer = "LSMPAs") %>%
+  filter(WDPAID == "555622118") %>%
+  select(WDPAID)
+
+# Get effort data from BigQuery
+plw <- get_table(dataset = "mpa_displacement",
+                 table = "plw_raster") %>% 
+  group_by(year, best_vessel_class, lon, lat) %>% 
+  summarize(days = sum(hours, na.rm = T) / 24) %>% 
+  ungroup()
+
+# Save effort data for reproducibility
+# write.csv(x = plw,
+#           file = here("raw_data", "plw_fishing_raster_2018_by_year.csv"),
+#           row.names = F)
+
+# The above call to get_table won't work because there
+# is no authetication, read in this file instead
+# plw <- read.csv(here("raw_data", "plw_fishing_raster_2018_by_year.csv"),
+#                 stringsAsFactors = F)
+
+# Plot longline fishing effort for 2018
+(plw_2018_ll <- plw %>% 
+    filter(year == 2018,
+           best_vessel_class == "drifting_longlines") %>% 
+    ggplot() +
+    geom_raster(aes(x = lon, y = lat, fill = days)) +
+    geom_sf(data = plw_eez, fill = "transparent", color = "black", size = 2) +
+    geom_sf(data = pnms, fill = "transparent", color = "red", size = 1) +
+    scale_fill_viridis_c(option = "C",
+                         trans = "log10",
+                         limits = c(0.01, 1000),
+                         breaks = c(0.01, 0.1, 1, 10, 100, 1000),
+                         labels = c(0.01, 0.1, 1, 10, 100, 1000),
[…]

### 2019-05-30 scripts/content/robustness/analyses_on_controls_excluding_CHN.R

@@ -1,0 +1,267 @@
+###########################################
+#   analyses_on_controls_excluding_CHN    #
+###########################################
+
+#########################################################
+# This fits all models for data that excludes CHN vessels
+#########################################################
+
+# Load packages
+library(here)
+library(magrittr)
+library(tidyverse)
+
+# Custom functions
+source(here("scripts", "functions", "model_data_prep.R"))
+source(here("scripts", "functions", "did.R"))
+source(here("scripts", "functions", "did_quarter.R"))
+source(here("scripts", "functions", "did_yearmonth.R"))
+source(here("scripts", "functions", "termplot.R"))
+
+# Nino4 index
+nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
+  select(year, month = month_n, nino4anom)
+
+#### FISHING AND NON FISHING HOURS ################################################################
+# Load my data
+effort_by_vessel <- readRDS(file = here("data",
+                                              "panels",
+                                              "daily_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines",
+         !flag == "CHN")
+
+## Prepare a base data
+# For fishing hours
+fishing_hours <- effort_by_vessel %>% 
+  filter(fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+# For non-fishing hours
+nonfishing_hours <- effort_by_vessel %>% 
+  filter(!fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+
+## Fit the models
+# For each set of data I fit simple did, quarterly and year-month
+# Fishing hours
+fish_did <- did(fishing_hours)
+fish_didq <- did_quarter(fishing_hours)
+fish_didym <- did_yearmonth(fishing_hours)
+
+#Non-fishing hours
+nonfish_did <- did(nonfishing_hours)
+nonfish_didq <- did_quarter(nonfishing_hours)
+nonfish_didym <- did_yearmonth(nonfishing_hours)
+
+
+
+
+#### PROPORTION FISHING HOURS ################################################################
+# Load my data
+prop_fishing_by_vessel <- readRDS(file = here("data",
+                                                    "panels",
[…]

### 2019-05-30 scripts/content/robustness/analyses_on_controls_excluding_PNA.R

@@ -1,0 +1,282 @@
+###########################################
+#   analyses_on_controls_excluding_PNA    #
+###########################################
+
+#########################################################
+# This fits all models for data that excludes vessels
+# owned by PNA members and TKL
+#########################################################
+
+# Load packages
+library(here)
+library(magrittr)
+library(tidyverse)
+
+# Custom functions
+source(here("scripts", "functions", "model_data_prep.R"))
+source(here("scripts", "functions", "did.R"))
+source(here("scripts", "functions", "did_quarter.R"))
+source(here("scripts", "functions", "did_yearmonth.R"))
+source(here("scripts", "functions", "termplot.R"))
+
+# List of countries I exclude
+PNA <- c("FSM",
+         "KIR",
+         "MHL",
+         "NRU",
+         "PLW",
+         "PNG",
+         "SLB",
+         "TUV",
+         "TKL")
+
+# Nino4 index
+nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
+  select(year, month = month_n, nino4anom)
+
+#### FISHING AND NON FISHING HOURS ################################################################
+# Load my data
+effort_by_vessel <- readRDS(file = here("data",
+                                              "panels",
+                                              "daily_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines",
+         !flag %in% PNA)
+
+## Prepare a base data
+# For fishing hours
+fishing_hours <- effort_by_vessel %>% 
+  filter(fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+# For non-fishing hours
+nonfishing_hours <- effort_by_vessel %>% 
+  filter(!fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+
+## Fit the models
+# For each set of data I fit simple did, quarterly and year-month
+# Fishing hours
+fish_did <- did(fishing_hours)
+fish_didq <- did_quarter(fishing_hours)
+fish_didym <- did_yearmonth(fishing_hours)
+
+#Non-fishing hours
+nonfish_did <- did(nonfishing_hours)
+nonfish_didq <- did_quarter(nonfishing_hours)
+nonfish_didym <- did_yearmonth(nonfishing_hours)
+
+
+
+
+#### PROPORTION FISHING HOURS ################################################################
[…]

### 2019-05-30 scripts/content/robustness/analyses_on_controls_excluding_USA_TWN.R

@@ -1,0 +1,273 @@
+###############################################
+#   analyses_on_controls_excluding_USA_TWN    #
+##############################################
+
+#########################################################
+# This fits all models for data that excludes vessels
+# owned by the US and TWN members and TKL
+#########################################################
+
+# Load packages
+library(here)
+library(magrittr)
+library(tidyverse)
+
+# Custom functions
+source(here("scripts", "functions", "model_data_prep.R"))
+source(here("scripts", "functions", "did.R"))
+source(here("scripts", "functions", "did_quarter.R"))
+source(here("scripts", "functions", "did_yearmonth.R"))
+source(here("scripts", "functions", "termplot.R"))
+
+# Nino4 index
+nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
+  select(year, month = month_n, nino4anom)
+
+#### FISHING AND NON FISHING HOURS ################################################################
+# Load my data
+effort_by_vessel <- readRDS(file = here("data",
+                                              "panels",
+                                              "daily_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines",
+         !flag %in% c("USA", "TWN"))
+
+## Prepare a base data
+# For fishing hours
+fishing_hours <- effort_by_vessel %>% 
+  filter(fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+# For non-fishing hours
+nonfishing_hours <- effort_by_vessel %>% 
+  filter(!fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+
+## Fit the models
+# For each set of data I fit simple did, quarterly and year-month
+# Fishing hours
+fish_did <- did(fishing_hours)
+fish_didq <- did_quarter(fishing_hours)
+fish_didym <- did_yearmonth(fishing_hours)
+
+#Non-fishing hours
+nonfish_did <- did(nonfishing_hours)
+nonfish_didq <- did_quarter(nonfishing_hours)
+nonfish_didym <- did_yearmonth(nonfishing_hours)
+
+
+
+
+#### PROPORTION FISHING HOURS ################################################################
+# Load my data
+prop_fishing_by_vessel <- readRDS(file = here("data",
+                                                    "panels",
[…]

### 2019-05-30 scripts/content/time_series_kir_activity.R

@@ -1,0 +1,166 @@
+################################
+##  time_series_kir_activity  ##
+################################
+
+#############################################################
+# This script generates tow figures. One shows vessel-days
+# by each patch of EEZs that Kiribati has and by gear. This
+# essentially shows that the loss in revenue from longlines
+# comes after 2016, but that fishing effort in Phoenix group
+# decreased after 2015 for both vessels. The second graph
+# generates the timeseries of all vessel-activity in Kiribati
+# by gear.
+#############################################################
+
+
+# Load libraries
+library(lubridate)
+library(here)
+library(cowplot)
+library(tidyverse)
+
+# Nino4 index
+nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
+  select(year, month = month_n, nino4anom)
+
+longline_kir <- read.csv(here("raw_data", "longlines_KIR_2012_2018.csv")) %>% 
+  mutate(date = date(paste(year, month, 1, sep = "-")),
+         days = hours / 24,
+         label = ifelse(best_vessel_class == "drifting_longlines",
+                        "Drifting Longlines",
+                        "Tuna Purse Seines")) %>% 
+  left_join(nino4, by = c("year", "month"))
+
+
+time_series_gear_group <- ggplot(data = longline_kir,
+       mapping = aes(x = date, y = days, color = territory1, fill = territory1)) +
+  geom_line() +
+  geom_point(color = "black",
+             size = 1,
+             shape = 21,
+             alpha = 0.8) +
+  cowplot::theme_cowplot() +
+  theme(text = element_text(size = 10),
+        axis.text = element_text(size = 8),
+        legend.text = element_text(size = 8),
+        strip.background = element_blank()) +
+  labs(x = "Date", y = "Vessel-days") +
+  geom_vline(xintercept = date("2015-01-01")) +
+  facet_wrap(territory1 ~ label, scales = "free_y", ncol = 2) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  guides(color = guide_legend(title = "Group"),
+         fill = guide_legend(title = "Group"))
+
+ggsave(plot = time_series_gear_group,
[…]

### 2019-05-30 scripts/content/vessel_model_fitting.R

@@ -1,0 +1,331 @@
+#############################
+#   vessel_model_fitting    #
+#############################
+
+###################################################
+# This is the script that fits all the models for
+# my panels of behavioral change.
+###################################################
+
+# Load packages
+library(here)
+library(magrittr)
+library(tidyverse)
+
+# Custom functions
+source(here("scripts", "functions", "model_data_prep.R"))
+source(here("scripts", "functions", "did.R"))
+source(here("scripts", "functions", "did_quarter.R"))
+source(here("scripts", "functions", "did_yearmonth.R"))
+source(here("scripts", "functions", "termplot.R"))
+
+# Nino4 index
+nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
+  select(year, month = month_n, nino4anom)
+
+#### FISHING AND NON FISHING HOURS ################################################################
+# Load my data
+effort_by_vessel <- readRDS(file = here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines")
+
+## Prepare a base data
+# For fishing hours
+fishing_hours <- effort_by_vessel %>% 
+  filter(fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+# For non-fishing hours
+nonfishing_hours <- effort_by_vessel %>% 
+  filter(!fishing) %>% 
+  model_data_prep() %>% 
+  left_join(nino4, by = c("year", "month"))
+
+
+## Fit the models
+# For each set of data I fit simple did, quarterly and year-month
+# Fishing hours
+fish_did <- did(fishing_hours)
+fish_didq <- did_quarter(fishing_hours)
+fish_didym <- did_yearmonth(fishing_hours)
+
+#Non-fishing hours
+nonfish_did <- did(nonfishing_hours)
+nonfish_didq <- did_quarter(nonfishing_hours)
+nonfish_didym <- did_yearmonth(nonfishing_hours)
+
+
+
+
+#### PROPORTION FISHING HOURS ################################################################
+# Load my data
+prop_fishing_by_vessel <- readRDS(file = here("data",
+                                              "panels",
+                                              "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
+  filter(year < 2019,
+         gear == "tuna_purse_seines") %>% 
+  model_data_prep(prop_fishing) %>% 
+  left_join(nino4, by = c("year", "month"))
+
+#Fit themdoels
[…]

### 2019-05-30 scripts/functions/model_data_prep.R

@@ -1,0 +1,28 @@
+#######################
+#   model_data_prep   #
+#######################
+
+##############################################
+# Takes a selected group of data and prepares
+# it to have the shape (and variables) that
+# I want for the did models.
+##############################################
+
+model_data_prep <- function(data, var = hours){
+  var <- enquo(var)
+  data %>% 
+    mutate(post = post * 1,
+           treated = treated * 1,
+           year_c = as.character(year),
+           year_c = fct_relevel(year_c, "2014"),
+           year_month_c = as.character(year_month),
+           year_month_c = fct_relevel(year_month_c, "2014-12-01"),
+           quarter_c = as.character(quarter),
+           quarter_c = fct_relevel(quarter_c, "2014.4"),
+           flag_fe = !flag %in% c("JPN", "MEX", "NIC", "NZL", "PHL", "USA", "KIR", "PNG"),
+           flag_fe_oth = flag_fe & !flag == "OTH",
+           sate = case_when(date < lubridate::date("2014/06/01") ~ "1",
+                            date > lubridate::date("2015/12/31") ~ "3",
+                            T ~ "2"),
+           log_var = log(!!var + sqrt(1 + ((!!var) ^ 2)))) #log-transformed (hyperbolic sine)
+}

### 2019-05-30 scripts/get_pna_eezs.R

@@ -1,0 +1,11 @@
+
+## RUN ONLY ONCE ! ! ! 
+
+# Take a shapefile of EEZs and filter out to keep only PNA members. These are the Federated States of Micronesia (FSM), Kiribati, Marshall Islands, Nauru, Palau (PU), Papua New Guinea, Solomon Islands and Tuvalu.
+
+library(sf)
+library(tidyverse)
+
+read_sf(dsn = here::here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
+  filter(ISO_Ter1 %in% c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL")) %>% 
+  st_write(dsn = here::here("data", "spatial", "PNA_EEZ", "PNA_EEZ.shp"))

### 2019-05-30 scripts/model/PNA_no_trading.R

@@ -1,0 +1,101 @@
+#' PNA model with no trading
+#' 
+#' @description This is essentially a wrapper function. For a given set of parameters, including a spatial closure, the function solves for equilibrium price, biomass, and effort allocation. In this case, pi is solved at a patch-level, as opposed to a global pi.
+#'
+#' @param fvec Vector of biomass distribution
+#' @param theta Movement parameter
+#' @param R Reserve size
+#' @param r intrinsic growth rate
+#' @param K carrying capacity
+#' @param p price per ton
+#' @param q catchability
+#' @param Xvec Biomass vector
+#' @param beta beta exponent for costs
+#' @param c costs
+#' @param Evec A vector of initial effort allocations
+#'
+#' @return A tibble containing the harvest, vessel-days, stock size, vessel-day price and vessel-day revenue for each country.
+#' @export
+#'
+PNA_no_trading <- function(fvec = NULL, theta = NULL, R = NULL, r = NULL, K = NULL, p = NULL, q = NULL, Xvec = NULL, beta = NULL, c = NULL, Evec = NULL) {
+  n_patches <- length(fvec)
+  
+  omega <- theta + (1 - theta) * (1 - R)
+  
+  tol <- 0.001 * Bnow
+  diff <- (tol * 2)^2
+  
+  ct <- 1
+  
+  while (diff > tol) {
+    
+    # CALCULATE HARVESST AND BIOMASS
+    ## total biomass before harvesting
+    Xnow <- sum(Xvec)
+    
+    # Modify Evec in the high seas (leakage)
+    Evec[10] <- ((p * q * Xvec[10]) / (beta * c)) ^ (1 / (beta - 1))
+    
+    ## Calculate harvest vector
+    # Initial harvest vector based on Evec
+    Hvec <- (q * Evec * Xvec)
+    # Modify harvest in patch 1 due to closure
+    Hvec[1] <- q * Evec[1] * Xvec[1] * omega
+    # Make sure that harvest does not exceed available biomass
+    Hvec <- pmin(Hvec, Xvec)
+    
+    ## Escapement
+    # Calculate patch-level escapement
+    evec <- Xvec - Hvec
+    # Calculate total escapement
+    e_all <- sum(evec)
+    
+    ## Growth
+    # Make fish grow
[…]

### 2019-05-30 scripts/model/PNA_with_trading.R

@@ -1,0 +1,182 @@
+#' PNA model with trading
+#' 
+#' @description This is essentially a wrapper function. For a given set of parameters, including a spatial closure, the function solves for equilibrium price, biomass, and effort allocation.
+#'
+#' @param fvec Vector of biomass distribution
+#' @param theta Movement parameter
+#' @param R Reserve size
+#' @param r intrinsic growth rate
+#' @param K carrying capacity
+#' @param p price per ton
+#' @param q catchability
+#' @param Xvec Biomass vector
+#' @param beta beta exponent for costs
+#' @param c costs
+#' @param E total allowable effort
+#' @param save_plot Save a convergence plot? Boolean
+#'
+#' @return A tibble containing the harvest, vessel-days, stock size, vessel-day price and vessel-day revenue for each country.
+#' @export
+#'
+PNA_with_trading <- function(fvec = NULL, theta = NULL, R = NULL, r = NULL, K = NULL, p = NULL, q = NULL, Xvec = NULL, beta = NULL, c = NULL, E = NULL, save_plot = FALSE) {
+  n_patches <- length(fvec)
+  
+  prog <- tibble(
+    ct = 1,
+    X = sum(Xvec),
+    E = 0,
+    pi = 0,
+    H = 0,
+    e = 0,
+    Xnew = 0,
+    diff = 0,
+    err = 0
+  )
+  
+  tol <- 0.0001 * Bnow
+  diff <- (tol * 2)^2
+  
+  ct <- 1
+  
+  while (diff > tol) {
+    
+    # OPTIMIZATION FOR PI
+    ## set up
+    others <- list(
+      "E" = E,
+      "p" = p,
+      "q" = q,
+      "Xvec" = Xvec,
+      "theta" = theta,
+      "R" = R,
+      "beta" = beta,
+      "c" = c
+    )
+    
+    ## run optin to get pi for given Xvec
+    opt <- nlminb(
+      start = 1000,
+      objective = solve_pi,
+      others = others,
+      lower = 0,
+      upper = 150000,
+      control = list(
+        iter.max = 1e6,
+        abs.tol = 10,
+        step.min = 10,
+        step.max = 1000
+      )
+    )
+    ## extract pi
+    pi <- opt$par[1]
+    
+    # CALCULATE HARVESST AND BIOMASS
+    ## total biomass before harvesting
[…]

### 2019-05-30 scripts/model/allocate.R

@@ -1,0 +1,78 @@
+#' Allocation function
+#' 
+#' @description This function takes a data.frame of allocations, historical usage,
+#' patch-specific stock size, and VDS price. It then calculates what would be next
+#' year's allocation based on the \code{(alpha * Ei) + ((1 - alpha) * Xi} formula
+#' which balances a 4-year running mean of biomass and catches
+#'
+#' @param alloc_input 
+#' @param alpha 
+#' @param year 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+allocate <- function(alloc_input, alpha, this_year, fvec = NULL, theta = NULL, R = NULL, r = NULL, K = NULL, p = NULL, q = NULL, beta = NULL, c = NULL, E = NULL, trade = NULL) {
+  
+  allocations <- alloc_input %>% 
+    filter(year > (this_year - 6),
+           !country == "HS") %>% 
+    group_by(country) %>%
+    summarize(
+      Xi = mean(Xi),
+      Ei = mean(Ei)
+    ) %>%
+    ungroup() %>%
+    mutate(
+      Ei = Ei / E,
+      Xi = Xi / K,
+      alloc_rule = (alpha * Ei) + ((1 - alpha) * Xi),
+      alloc_prop = alloc_rule / sum(alloc_rule),
+      Ea = E * alloc_prop
+    ) %>%
+    select(country, Ea) %>% 
+    mutate(country = fct_relevel(country, "KIR")) %>% 
+    arrange(country)
+  
+  E_hs_last <- alloc_input$Ea[alloc_input$country == "HS" & alloc_input$year == this_year]
+  Ea <- c(allocations$Ea, E_hs_last)
+  Xvec <- alloc_input$Xi[alloc_input$year == this_year]
+  
+  if(trade) {
+    out <-
+      move_in_time(
+        fvec = fvec,
+        theta = theta,
+        R = R,
+        r = r,
+        K = K,
+        p = p,
+        q = q,
+        Xvec = Xvec,
+        beta = beta,
+        c = c,
+        E = E,
+        Ea = Ea,
+        year = this_year + 1
+      )
+  } else {
+    out <-
+      move_in_time_no_trading(
+        fvec = fvec,
+        theta = theta,
+        R = R,
+        r = r,
+        K = K,
+        p = p,
+        q = q,
+        Xvec = Xvec,
+        beta = beta,
+        c = c,
+        Evec = Ea,
+        year = this_year + 1
+      )
+  }
+  
+  return(out)
+}

### 2019-05-30 scripts/model/move_in_time_no_trading.R

@@ -1,0 +1,44 @@
+move_in_time_no_trading <- function(fvec = NULL, theta = NULL, R = NULL, r = NULL, K = NULL, p = NULL, q = NULL, Xvec = NULL, beta = NULL, c = NULL, Evec = NULL, year = NULL) {
+  
+  omega <- theta + (1 - theta) * (1 - R)
+  
+  pis <- pmax(0,
+              (p * q * Xvec) - (beta * c * (Evec ^ (beta - 1))))
+  
+  pis[1] <- max(0,
+                (p * q * Xvec[1] * omega) - (beta * c * (Evec[1] ^ (beta - 1))))
+  
+  pis[10] <- 0
+  
+  ## Calculate harvest vector
+  # Initial harvest vector based on Evec
+  Hvec <- (q * Evec * Xvec)
+  # Modify harvest in patch 1 due to closure
+  Hvec[1] <- q * Evec[1] * Xvec[1] * omega
+  # Make sure that harvest does not exceed available biomass
+  Hvec <- pmin(Hvec, Xvec)
+  
+  ## Escapement
+  # Calculate patch-level escapement
+  evec <- Xvec - Hvec
+  # Calculate total escapement
+  e_all <- sum(evec)
+  
+  ## Growth
+  # Make fish grow
+  Xnew <- grow(e = e_all, r = r, K = K)
+  
+  # Generate Xvec
+  Xvec <- fvec * Xnew
+  
+  next_time <- tibble(
+    year = year,
+    country = names(fvec),
+    Ea = Evec,
+    Ei  = Evec,
+    Xi = Xvec,
+    pi = pis)
+  
+  return(next_time)
+  
+}

### 2019-05-30 scripts/model/solve_pi.R

@@ -1,0 +1,43 @@
+#' Solve for pi
+#' 
+#' @description This is the objective function used to find the equimarginal principle
+#' It is used to test (via optim) many different values of pi such that the
+#' resulting sum(Ei) = Ebar.
+#'
+#' @param par Initial value of the parameter of interest, pi
+#' @param others A named list of parameters, containing E, p, q, Xvec, theta, R, beta, and c.
+#'
+#' @return The error: squared difference between total allowable effort and predicted effort
+#' @export
+#'
+solve_pi <- function(par, others) {
+  # Extract pi
+  pi <- par[1]
+  
+  # Extract all other parameters
+  E <- others[[1]]
+  p <- others[[2]]
+  q <- others[[3]]
+  Xvec <- others[[4]]
+  theta <- others[[5]]
+  R <- others[[6]]
+  beta <- others[[7]]
+  c <- others[[8]]
+  
+  # Calculate number of patches
+  n_patches <- length(Xvec)
+  
+  # Create a vector of efforts calling the E_vec_fxn
+  E_vec <- E_vec_fxn(p = p, q = q, Xvec = Xvec, theta = theta, R = R, pi = pi, beta = beta, c = c)
+  
+  # Calculate total effort, excluding the high seas
+  E_calc <- sum(E_vec[1:(n_patches - 1)])
+  
+  # Calculate error as the squared difference between E,
+  # the total allowable effort
+  # and E_calc, the predicted total effort
+  err <- (E - E_calc)^2
+  
+  # Return the error
+  return(err)
+}

### 2019-05-30 scripts/pipa_effort_by_vessel.R

@@ -1,0 +1,87 @@
+#####################################################
+##### Load and summarize GFW data with sparklyr #####
+#####################################################
+# This script loads all raw GFW data from different #
+# CSV files found in raw_data/gfw_daily. All of     #
+# these files have the same structure. This script  #
+# will identify all vessels that fished inside PIPA #
+#####################################################
+
+########################################################################
+################### About the raw data #################################
+########################################################################
+# From https://globalfishingwatch.force.com/gfw/s/data-download:       #
+#                                                                      #
+# Daily Fishing Effort at 10th Degree Resolution by MMSI, 2012-2016    #
+# Fishing effort is binned into grid cells 0.1 degrees on a side,      #
+# and measured in units of hours. The time is calculated by assigning  #
+# an amount of time to each AIS detection (which is half the time      #
+# to the previous plus half the time to the next AIS position). To get #
+# information on each mmsi, see Global Fishing Watch data on fishing   #
+# vessels.                                                             #
+#                                                                      #
+# More documentation:                                                  #
+# https://github.com/GlobalFishingWatch/global-footprint-of-fisheries/blob/master/data_documentation/fishing_effort_byvessel.md
+
+## Load packages
+library(sparklyr) #install.packages("sparlyr")
+library(here) #install.packages("here")
+library(sf) #install.packages("sf")
+library(purrr) #install.packages("purrr")
+library(dplyr) #install.packages("dplyr")
+
+## Clear the environment
+rm(list = ls())
+
+source(here("scripts","sfc_as_cols.R"))
+
+## Install spark on computer (ncomment next line)
+# sparklyr::spark_install()
+
+## Establish a connection on sparklyr
+sc <- spark_connect(master = "local")
+
+
+## Read the first rows of a sample dataset of January 1st 2012
+gfw <- read.csv(here("raw_data","gfw_daily","2012-01-01.csv"), nrows = 10) %>% 
+  map(function(x){"character"})
+
+
+## Load all data into sparkly local session
+gfw_data <- spark_read_csv(sc = sc,
+                           name = "gfw_data",
+                           path = here("raw_data","gfw_daily"),
[…]

### 2019-05-30 scripts/processing/create_regions.R

@@ -1,0 +1,107 @@
+########################
+#   create_regions    #
+########################
+
+################################################
+# This script creates a shapefile of "regions"
+# that I use to ideintify effort redistribution.
+# It is basically a shapefile of eez plus a buffer
+# around them.
+################################################
+
+#### SET UP ################################################
+
+# Load packages
+library(here)
+library(sf)
+library(tidyverse)
+
+# Load custom functions
+source(here("scripts", "functions", "st_rotate.R"))
+
+# Define PNA countries
+PNA_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL")
+
+# Read PIPA shapefile
+pipa <- read_sf(dsn = here("data", "spatial", "PIPA"),
+                layer = "PIPA") %>% 
+  mutate(id = "PIPA 1") %>% 
+  select(id) %>% 
+  st_rotate() %>% 
+  st_buffer(dist = 0.01) %>% 
+  mutate(source = "PIPA",
+         PNA = F)
+
+# Read vessel tracks
+vessel_tracks <- readRDS(file = here("data", "vessel_tracks_2012_2018_baci.rds")) %>% 
+  filter(fishing,
+         gear == "tuna_purse_seines",
+         !is.na(eez_iso3),
+         year < 2019) %>% 
+  group_by(eez_iso3) %>% 
+  summarize(h = sum(hours)) %>% 
+  arrange(desc(h)) %>% 
+  mutate(prop = cumsum(h / sum(h))) %>%
+  filter(prop <= 0.99)
+
+eez <- read_sf(dsn = here("raw_data", "spatial", "EEZ"), layer = "eez_v10") %>% 
+  filter(ISO_Ter1 %in% c(unique(vessel_tracks$eez_iso3), "FJI")) %>% 
+  st_rotate() %>% 
+  select(ISO_Ter1) %>%
+  group_by(ISO_Ter1) %>%
+  mutate(id = paste(ISO_Ter1, row_number())) %>%
+  ungroup() %>%
+  group_by(id) %>% 
+  summarize() %>% 
+  st_buffer(0.1)
+
+eez_all <- eez %>%
+  mutate(a = 1) %>%
+  group_by(a) %>%
+  summarize() %>%
+  ungroup()
+
+hs_b <- eez %>%
+  st_buffer(dist = 5) %>% 
[…]

### 2019-05-30 scripts/processing/monthly_rasterized_effort_by_region.R

@@ -1,0 +1,191 @@
+###################################
+#   rasterize_effort_by_regions   #
+###################################
+
+
+######################################################################
+# This script takes the shapefile of EEZs and rasterizes it to a 1 deg
+# raster. I then create a yearly raster for each group of vessels, 
+# which I export as tiff.
+######################################################################
+
+
+#### SETUP ######################################################################
+
+# Load packages
+library(raster)
+library(fasterize)
+library(sf)
+library(tidyverse)
+
+# Create some functions that I only use here
+# This one converts a data.frame into a raster
+rasterize_df <- function(x, r, fun = "sum"){
+  
+  # First I "rotate" to center the image to the Pacific
+  x2 <- x %>%
+    select(lon, lat, hours) %>% 
+    mutate(lon = ifelse(lon < 0, lon + 180, lon - 180) + 180) %>% 
+    as.matrix()
+  
+  # I know rasterize the data
+  rasterize(x = x2[,1:2],
+            y = r,
+            field = x2[,3],
+            fun = fun)
+}
+
+# This function extracts the raster and converts it into a data.frame
+# I need it because I want to convert it to DF and add some metadata 
+# about the raster, like year and group to which vessels belong
+extract_raster <- function(r, year, month = NULL, treated){
+  as.data.frame(r, xy = T) %>%
+    rename(hours = layer) %>% 
+    mutate(year = year,
+           month = month,
+           treated = treated)
+}
+
+#### REGIONS RASTER ######################################################################
+
+# Read my regions shapefile
+regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
+                   layer = "regions")
+
+# Rasterize regions shapefile
+regions_raster <- regions %>%
+  mutate(unique = group_indices(., id)) %>%
+  fasterize(sf = .,
+            raster = raster(., res = 1),
+            field = "unique",
+            background = 0)
+
+# Export raster to include in Appendix
+writeRaster(x = regions_raster,
+            file = here::here("data",
+                              "spatial",
+                              "regions_raster.tif"),
+            overwrite = TRUE)
+
+# Add a HS term and convert into a data.frame used later
+regions_with_HS <- regions %>%
+  mutate(unique = group_indices(., id)) %>% 
+  st_set_geometry(NULL) %>% 
[…]

### 2019-05-30 scripts/processing/rasterize_effort_by_regions.R

@@ -1,0 +1,160 @@
+###################################
+#   rasterize_effort_by_regions   #
+###################################
+
+
+######################################################################
+# This script takes the shapefile of EEZs and rasterizes it to a 1 deg
+# raster. I then create a yearly raster for each group of vessels, 
+# which I export as tiff.
+######################################################################
+
+
+#### SETUP ######################################################################
+
+# Load packages
+library(raster)
+library(fasterize)
+library(sf)
+library(tidyverse)
+
+# Create some functions that I only use here
+
+# This one converts a data.frame into a raster
+rasterize_df <- function(x, r, fun = "sum"){
+  
+  # First I "rotate" to center the image to the Pacific
+  x2 <- x %>%
+    select(lon, lat, hours) %>% 
+    mutate(lon = ifelse(lon < 0, lon + 180, lon - 180) + 180) %>% 
+    as.matrix()
+  
+  # I know rasterize the data
+  rasterize(x = x2[,1:2],
+            y = r,
+            field = x2[,3],
+            fun = fun)
+}
+
+# This function extracts the raster and converts it into a data.frame
+# I need it because I want to convert it to DF and add some metadata 
+# about the raster, like year and group to which vessels belong
+extract_raster <- function(r, year, treated){
+  as.data.frame(r, xy = T) %>%
+    rename(hours = layer) %>% 
+    mutate(year = year,
+           treated = treated)
+}
+
+#### REGIONS RASTER ######################################################################
+# Load the regions shapefile
+regions <- read_sf(dsn = here::here("data", "spatial", "regions"),
+                   layer = "regions")
+
+# Rasterize regions
+regions_raster <- regions %>%
+  mutate(unique = group_indices(., id)) %>%
+  fasterize(sf = .,
+            raster = raster(., res = 1),
+            field = "unique",
+            background = 0)
+
+# Add the High seas manually
+regions_with_HS <- regions %>%
+  mutate(unique = group_indices(., id)) %>% 
+  st_set_geometry(NULL) %>% 
+  rbind(data.frame(id = "HS",
+                   source = "HS",
+                   PNA = 0,
+                   country = "HS",
+                   unique = 0))
+
+regions_raster_df <- as.data.frame(regions_raster, xy = T) %>% 
[…]

### 2019-05-30 scripts/processing/vessel_tracks_2012_2018_baci.R

@@ -1,0 +1,91 @@
+#######################################
+#     vessel_tracks_2012_2018_baci    #
+#######################################
+
+##################################################################################
+# The objective of this script is to clean and formalize the
+# vessel_tracks_2012_2018 data.
+#
+# That data was obtained from Google BigQuery, and I need to adjust it to ensure
+# that the panel data conforms to a proper BACI design. I also need to keep only
+# the fishing vessels we care about (purse seiners and longliners), so I will
+# subset by those gears. I then create a number of indicator variables that I can
+# use to further subset the data down the line. These include different definitions
+# of control and treatment groups, as well as additional counterfactuals. I then
+# export the dataset to use as main input for when I want to calculate other
+##################################################################################
+
+# Load packages
+library(here) 
+library(tidyverse)
+library(magrittr)
+
+# Set a large memory size for when this code runs on Windows
+if(unname(Sys.info()[1] == "Windows")){
+  memory.limit(size = 8e6)
+}
+
+# Read the tracks
+vessel_tracks <- readRDS(file = here("raw_data", "vessel_tracks.rds")) %>% 
+  mutate(fishing = ifelse(is.na(fishing), FALSE, fishing)) # Values of nnet_score are NULL imply fishing)
+
+# Identify vessels suitable for BACI
+# I want to make sure my control does not include vessels that appear after 2015
+# or that my treatment has vessels that disappeared after 2015. We use Sept 1 as
+# a way to break the treatment / control to account for the BlueParadox described
+# by McDermott et al 2018 PNAS
+
+# This gets "treated" vessels before
+tb <- vessel_tracks %>% 
+  filter(fishing, treated, !post, date < lubridate::date("2014/09/01")) %$%
+  mmsi %>%
+  unique()
+
+# This gets "treated" vessels after
+ta <- vessel_tracks %>% 
+  filter(fishing, treated, post) %$%
+  mmsi %>%
+  unique()
+
+# This gets "control" vessels after
+cb <- vessel_tracks %>% 
+  filter(fishing, !treated, !post, date < lubridate::date("2014/09/01")) %$%
+  mmsi %>%
+  unique()
+
+# This gets "control" vessels after
+ca <- vessel_tracks %>% 
+  filter(fishing, !treated, post) %$%
+  mmsi %>%
+  unique()
+
+# I have two measures of BACI
+
+## BACI STRICT
[…]

### 2019-05-30 scripts/processing/vessel_tracks_panel.R

@@ -1,0 +1,391 @@
+#############################
+#   vessel_tracks_panels    #
+#############################
+
+##################################################################################
+# This script takes the vessel_tracks_baci dataset which has already been cleaned
+# and formated. However, I still need to have a set of variables that I will use
+# response variables in the regression.
+# Since not all measures will fit in the same panel, I will create many of them.
+# The variables that I need are:
+# PANEL 1:
+# - daily fishing hours
+# - daily non-fishing hours
+# 
+# PANEL 2:
+# - daily proportion fishing hours vs. non fishing hours
+# 
+# PANEL 3:
+# - daily distance traveled
+# 
+# PANEL 4:
+# - daily mean distance from shore (min and max)
+# - daily mean distance from port (min and max)
+# 
+# PANEL 5:
+# - daily mean distance from port and shore fishing only (min and max)
+# 
+# PANEL 6:
+# - monthly fishing hours in Kiribati EEZ
+# 
+# PANEL 7:
+# - monthly fishing hours inside PNA EEZs
+# 
+# PANEL 8:
+# - monthly fishing hours in HS
+##################################################################################
+
+
+# Load packages
+library(here)
+library(magrittr)
+library(purrr)
+library(tidyverse)
+
+# Set a large memory size for when this code runs on Windows
+if(unname(Sys.info()[1] == "Windows")){
+  memory.limit(size = 8e6)
+}
+
+# Load the data
+vessel_tracks_baci <- readRDS(file = here("data","vessel_tracks_2012_2018_baci.rds")) %>%
+  filter(baci_strict)
+
+######################## BEGIN PANEL 1 ##########
+## FISHING AND NON-FISHING HOURS
+# Here I group all my variables except for hours
+daily_hours_by_vessel_panel <- vessel_tracks_baci %>%
+  group_by(year,
+           quarter,
+           month,
+           year_month,
+           day,
+           date,
+           fishing,
+           gear,
+           flag,
+           mmsi,
+           treated,
+           post,
+           month_c,
+           year_c) %>%
+  summarize(hours = sum(hours, na.rm = T)) %>%
+  ungroup() %>% 
+  arrange(date, mmsi) %>% 
+  spread(fishing, hours, fill = 0) %>% 
[…]

### 2019-05-30 scripts/spatial_panels.R

@@ -1,0 +1,135 @@
+######################
+#   spatial_panels   #
+######################
+
+##################################################################################
+# This script takes the vessel_tracks_baci dataset which has already been cleaned
+# and formated. However, I still need to have a set of variables that I will use
+# response variables in the regression.
+# Since not all measures will fit in the same panel, I will create more than one.
+# The variables that I need are:
+# PANEL 1:
+# - monthly proportion fishing hours in Kiribati EEZ with respect to all VDS hours
+# 
+# PANEL 2:
+# - monthly proportion of fishing hours inside PNA EEZs with respect to all hours
+# 
+# There are similar panels at the vessel-level, which ask the following question:
+# For a given vessel, what proportion of their fishing hours happened in month X
+# and EEZ / spatial region Y?
+# Instead, here our units are the spatial regions, and we see how fishing within
+# them changes through time, without making distinctions on the vessel that fishes
+# in those waters.
+##################################################################################
+
+
+# Load packages
+library(magrittr)
+library(tidyverse)
+
+# Set a large memory size for when this code runs on Windows
+if(unname(Sys.info()[1] == "Windows")){
+  memory.limit(size = 8e6)
+}
+
+# Load the data
+vessel_tracks_baci <- readRDS(file = here::here("data", "vessel_tracks_baci.rds")) %>% 
+  filter(baci_strict,
+         fishing)
+
+# List of PNA countries
+PNA_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV")
+
+# List of countries that hold VDS rights (and then sell to others)
+VDS_countries <- c(PNA_countries, "TKL")
+
+######### PANEL 1 ########################
+## PROPORTION OF FISHING HOURS WITHIN KIR
+
+prop_fishing_hours_kir_by_month_panel <- vessel_tracks_baci %>% 
+  filter(eez_iso3 %in% VDS_countries) %>% 
+  group_by(year,
+           quarter,
+           month,
+           year_month,
+           gear,
+           post,
+           month_c,
+           year_c) %>% 
+  mutate(total_hours = sum(hours, na.rm = T)) %>% 
+  ungroup() %>% 
+  filter(eez_iso3 == "KIR") %>% 
+  group_by(year,
+           quarter,
[…]

### 2019-05-30 scripts/vessels_inside_pna_outside_pipa.R

@@ -1,0 +1,107 @@
+#####################################################
+##### Load and summarize GFW data with sparklyr #####
+#####################################################
+# This script loads all raw GFW data from different #
+# CSV files found in raw_data/gfw_daily. All of     #
+# these files have the same structure. This script  #
+# will identify all vessels that fished inside PNA  #
+# countries, but no PIPA                            #
+#####################################################
+
+########################################################################
+################### About the raw data #################################
+########################################################################
+# From https://globalfishingwatch.force.com/gfw/s/data-download:       #
+#                                                                      #
+# Daily Fishing Effort at 10th Degree Resolution by MMSI, 2012-2016    #
+# Fishing effort is binned into grid cells 0.1 degrees on a side,      #
+# and measured in units of hours. The time is calculated by assigning  #
+# an amount of time to each AIS detection (which is half the time      #
+# to the previous plus half the time to the next AIS position). To get #
+# information on each mmsi, see Global Fishing Watch data on fishing   #
+# vessels.                                                             #
+#                                                                      #
+# More documentation:                                                  #
+# https://github.com/GlobalFishingWatch/global-footprint-of-fisheries/blob/master/data_documentation/fishing_effort_byvessel.md
+
+## Load packages
+library(sparklyr) #install.packages("sparlyr")
+library(here) #install.packages("here")
+library(sf) #install.packages("sf")
+library(purrr) #install.packages("purrr")
+library(magrittr) #install.packages("magrittr")
+library(dplyr) #install.packages("dplyr")
+
+## Clear the environment
+rm(list = ls())
+
+source(here("scripts","sfc_as_cols.R"))
+
+## Install spark on computer (ncomment next line)
+# sparklyr::spark_install()
+
+## Establish a connection on sparklyr
+sc <- spark_connect(master = "local")
+
+
+## Read the first rows of a sample dataset of January 1st 2012
[…]

### 2019-05-30 docs/Markets_Conservation_May30.tex
Added all files

--- 2019-05-22 docs/old_ms/PIPA_Palau_Science_JL.tex
@@
 
-\title{Marine Conservation In Fishing Effort Markets}
+\title{Fishery Markets and Large-Scale Marine Conservation}
 
@@
 
-\author{Juan CarlosVillase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
+\author{Juan Carlos Villase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
 \\
@@
 % Place your abstract within the special {sciabstract} environment.
-
 \begin{sciabstract}
-Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
-With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.
-A spatial closure in a trans-boundary fishery can potentially result in costs to the implementing country and benefits to neighboring countries.
-We show that effort markets may reduce up to 70\% of the costs of Marine Protected Areas, and that allocation rules based on biomass (rather than effort) may further incentivize conservation.
-We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented in 2015 in Kiribati) had on vessel distribution and behavior.
-Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation.
-We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displaced fishing effort.
-We use these insights to predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate that effort markets could reduce the cost of implementation by as much as 77\%.
-Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation.
-The Parties to the Nauru Agreement have successfully developed a management scheme that allows for conservation interventions to come at a low cost, and could be a model for trans-boundary conservation across the globe.
+Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
+We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
+Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with international commitments to expand Marine Protected Area (MPA) coverage.
+We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and spatially-explicit vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
+The answer hinges critically on two design features of the rights-based fishery market.
+First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
+Instead, if trading is forbidden, countries are likely to suffer losses from conservation.
+Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
+Otherwise, the allocation process acts as a punishment to the conserving country.
+Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
+With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
 \end{sciabstract}
@@
 
-\section{Introduction}\label{introduction}
+%%%% Other titles %%%%%%%%%%%%
+% Fishery markets enable marine conservation
+% Designing environmental markets for marine conservation
+% Large-scale marine conservation is enabled by market instruments
+% Rights-based management to promote marine conservation
 
-Humans are increasingly utilizing the oceans.
-Multiple ocean uses such as off-shore aquaculture, conservation, energy harvesting, deep-sea mining, and fisheries are likely to compete for space.
-As we move forward with blue growth, we must understand the potential effects of activities displacing each other and establish causal links between past management interventions and their outcomes \cite{burgess_2018}.
-One of the most notable spatial interventions is the creation of no-take Marine Protected Areas (MPAs), which seek to conserve the environment by eliminating fishing effort within their waters.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Today, a small number of Large-scale Marine Protected Areas (LSMPAs; areas larger than 30,000 km\textsuperscript{2} \emph{sensu} \cite{desanto_2013}) represent at least 80\% of the protected area in the ocean (Fig.
-\ref{fig:LSMPAs_map}; \cite{toonen_2013}).
-However, very little is known about their human dimensions and implications for fisheries \cite{gray_2017}.
-Furthermore, research on LSMPAs has focused on their potential ecological benefits, but have left aside the economic implications.
-One issue of particular importance is that of the displacement or redistribution of fishing effort, which may influence the outcomes of a spatial closure and represent large opportunity costs \cite{smith_2003,smith_2010}.
+Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
+Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%, 30\%, or even up to 50\% of the ocean to be off-limits to fishing.
+Fundamentally, to achieve these goals, huge swaths of sovereign nations' waters will have to be closed to fishing.
+What incentives might motivate a country to engage in such large-scale marine protection?
+Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from within its borders?
+We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: the design of fishing rights.
 
-Displacement or elimination of fishing effort within the protected area might come at a cost to the implementing party when fisheries are managed under an effort market (i.e.
-fishing rights are sold to firms).
-For example, tuna purse seine fisheries in the Pacific are collectively managed under a Vessel-Day Scheme (VDS) by nine countries commonly referred to as the Parties to the Nauru Agreement (PNA; Figure \ref{fig:PNA_map}).
-The agreement regulates the access of foreign fishing vessels to PNA waters, and control the allocation and sales of 45,000 ``vessel-days'': the right for one vessel to fish for one day in a country's waters.
-Holding 80\% of historical skipjack tuna purse seine grounds within their joint Exclusive Economic Zones (EEZ; with surface area of  14.6 million km\textsuperscript{2}), PNA countries have achieved greater bargaining power by working together \cite{havice_2010}; the vessel-day price rose from \$5,000 USD in 2012 to at least \$9,000 USD in 2016, driven by increasing price floors.
-The revenue from fisheries access fees represents up to 50\% of government revenue for some of the PNA countries.
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
+Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific Island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
+These waters collectively account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack tuna catches in the Western Central Pacific \cite{havice_2013}.
 
-The Phoenix Islands Protected Area (PIPA) in Kiribati is one of the most notable Large-Scale Marine Protected Areas on earth.
-Implemented on January 1st of 2015, PIPA closed an area of 397,447 km\textsuperscript{2}, about 11\% of Kiribati's EEZ or 2.7\% of total PNA area, effectively displacing all fishing effort within it \cite{mcdermott_2018,mccauley_2016}.
-A pressing question is that of the costs associated with the displacement of fishing effort and possible revenue losses from vessel-day sales.
-While no studies have assessed the implications of PIPA, other PNA members have pledged the implementation of LSMPAs, like Palau's 80\% closure to go into effect in 2020 \cite{cimino_2019}.
+In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
+The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
+Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
+We show how a rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
 
-We develop a bioeconomic model of a fishery operating under a vessel-day scheme with spatial closures to explore the effects of effort redistribution resulting from MPA implementation.
-We characterize the likely outcomes with and without vessel-day trading between countries, as well as the effect of different allocation rules.
-We then empirically evaluate the behavioral responses and spatial redistribution of the industrial tuna purse seine fleet operating within PNA waters after the implementation of the Phoenix Islands Protected Area, and quantify its economic ramifications and implications to Kiribati.
-We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary.
-These are two of the largest protected areas on the planet and both are controlled by PNA countries.
+To mirror the strategies and spatial connections among the nine PNA countries and the high seas, we develop a 10-patch spatial bioeconomic model.
+The fishery in nine of the patches operates under a market-based system in which ``vessel days'' are capped, closely tracked, and may be traded across countries.
+This vessel-day scheme (VDS) is actually used by the PNA; each country is given an allocation of vessel-days that can then be sold to fishing firms.
+A vessel-day owned by country $i$ entitles $i$ to lease that day to a fishing vessel, entitling it to fish in $i$'s EEZ for a 24 hour period.
+In our model, Patches 1 - 9 are countries that operate under a VDS (in which fishing days are limited) and Patch 10 represents the high seas, where fishing days are governed by economic conditions, not by the VDS.
 
-\section{Results}\label{results}
+While modeling the VDS market may be interesting in its own right, our primary purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
+To examine this, suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters as a marine reserve, in which no fishing is allowed.
+When Country 1 creates a reserve, several consequences may arise.
+Perhaps most obviously, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in $i$'s waters.
+Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
+For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
+The purpose of our model is to examine these consequences in detail, with a particular focus on how design features of the market affect Country 1's incentives to create the marine reserve.
 
-\subsection{Fishing effort markets and marine conservation}
+Not all market-based approaches to environmental management are created equal.
+A pervasive finding across a range of natural resources is that features of market design can have enormous implications for the market's functioning.
+In the context of fishery markets, two market design features stand out as important for a variety of outcomes, and we will show that they are pivotal in determining the incentives for large-scale marine conservation.
+The first design feature has to do with the trading of rights, and the second design feature concerns the allocation of rights.
+We examine the effects of large-scale conservation in Country 1 across a range of scenarios for trading and allocation of vessel day fishing rights across our nine model countries.
+In all cases we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
+We quantify the change in revenue to each PNA country from large-scale conservation in Country 1, by comparing revenues from each scenario to a benchmark scenario without any conservation action.
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement.
 
-We begin by simulating a spatial closure in a setting where vessel-days can not be traded between countries.
-A spatial closure in Patch 1 always results in a loss or no-change in revenue from vessel-days, even when the stock moves freely between the protected and non-protected portions of the Patch (Fig.
+Why would trading and allocation rules affect the incentives for conservation by Country 1?
+Invoking \emph{reductio ad absurdum}, consider the incentives for Country 1 to close 100\% of its waters.
+Such a closure would surely benefit the other countries through the increased abundance of fish.
+If Country 1 could sell its fishing rights, the other countries would likely buy them, and this could offset the foregone costs of fishing its own waters.
+But if Country 1 was not allowed to sell its rights, then it would lose all of its fishing revenue.
+This provides the simple intuition for why allowing trading across countries is so critical to conservation incentives.
+The rules for how fishing rights are allocated across the nine countries are equally important.
+Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
+This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.
+
+In our bioeconomic model, we examine the implications of conservation under alternative market designs: with, and without trading, and under alternative allocation rules.
+To test how the PNA allocates rights, we vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
+Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
+
+We begin by simulating a fishery where trading of fishing days across countries is forbidden.
+In that setting, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
 \ref{fig:PNA_model}A).
-The losses are caused by a drop in vessel-day prices for Patch 1, which results from a lower portion of the stock being available for harvest (Fig.
+Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases, allowing vessels to harvest the stock within the remaining open area.
+The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
+Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in Patch 1, which reduces a vessel's willingness to pay to fish in such waters (Fig.
 \ref{fig:vessel_day_price_no_trading_plot}).
-Costs increase with reserve size ($R$), and decrease as within-patch movement ($\theta$) increases.
-Given the non-linear costs ($\beta > 1$), the closure-to-cost ratio can be greater than 1:1 if within-patch movement is low (\emph{i.e.} $\theta < 0.2$).
-The spatial closure in Patch 1 results in moderate increases in revenue for Patches 2 - 9 (Fig.
-\ref{fig:profits_PNA_notKIR_no_trading_plot}).
-When countries can not trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches.
-Importantly, the increases in revenue to the other patches do not compensate for the total losses to Patch 1.
+When countries cannot trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches (Figure S2 shows that the increase in revenue ranges from 0\% to 6\%).
 
-The objective of a VDS is to allow for trading between parties and achieve the optimal distribution of effort in relation to fish distribution.
-In the case of the PNA, for example, spatial distribution and longitudinal shifts of tuna -particularly skipjack- have been linked to ENSO events \cite{lehodey_1997}.
-Vessels redistribute across PNA countries as they track fish, and tradable permits reduce costs to the parties by allowing them to sell surplus vessel-days to be used in the EEZ of another country \cite{aqorau_2018}.
-We explore the effect of a spatial closure in Patch 1, but now allow for vessel-days to be traded between Patches.
-Patch-level demand for vessel days is governed by the fishable stock size (\emph{i.e.} biomass not within the reserve).
-Trading occurs until vessel-day prices are the same across patches, given a total allowable effort (\emph{i.e.} 45,000 vessel-days) is reached.
-Here, costs from a closure in Patch 1 are significantly reduced by trading (Fig.
-\ref{fig:PNA_model}B-C).
-In this case, the surplus of vessel-days in Patch 1 are sold to Patches 2 - 9.
-Vessel-day prices are constant across patches and lower than when there is no reserve, but still higher than when no trading is allowed (Fig.
+How would a different market design, where trading between countries is allowed, change these results?
+To answer this we simulate the exact same fishery, but now allow for vessel-days to be traded across patches.
+A closure in Patch 1 lowers the value of vessel-days in that patch.
+Vessel-days in patches 2 - 9 are now worth more causing vessel-days from Patch 1 to be traded to Patches 2 - 9.
+Trading continues until vessel-day prices are the same across all patches (Fig.
 \ref{fig:vessel_day_price_with_trading_plot}).
-By optimally trading vessel-days, the cost to the implementing country can be reduced as much as 97\%.
+Under this market design, we find that revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
+\ref{fig:PNA_model}).
+Overall, we find that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+\ref{fig:PNA_model}C).
 
-Our previous analysis predicts a loss in total revenue from effort displacement.
-Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
+To analyze the consequences of different allocation rules on conservation incentives, we simulate an annual allocation that is a weighted function of historical fishing in a country and historical fish biomass in a country.
+If allocation rules are based only on the historical effort in a country, then trading vessel-days to other countries would imply a future reduction in allocation.
+We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
+We use a range of allocation rules to weight effort ($\alpha$) and biomass ($1 - \alpha$) and compare the revenues to a fishery operating for 50 years without any closures.
+We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in losses of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
+\ref{fig:allocation_cost_plot}).
+However, these costs are reduced as more weight is put on historical biomass.
+A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation for all reserve sizes and possible movement.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, the incentives for conservation are much greater.
 
-We explore the effect that allocation rules have through time when trading is allowed by projecting the fishery 50 years into the future.
-We used a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently to update annual allocations based on a seven-year running mean of these measures.
-Costs are greater when allocation is based only on patch-level historical effort (\emph{i.e.} $\alpha = 1$; Fig.
-\ref{fig:allocation_cost_plot}).
-However, costs can be significantly reduced when trading is allowed if allocation is based on historical biomass instead.
-When there is no trading, patch-level effort remains unchanged, and since any growth in stock is equally distributed across patches, allocation rules do not affect costs.
+We have shown that design features of a rights-based fisheries management system have enormous implications for the incentives a country faces to engage in large-scale conservation.
+Allowing trading of rights across countries, and re-allocating annual rights based on biological variables, not fishing pressure, can essentially eliminate the cost of conservation, even for very large reserves.
+We now move to an empirical setting where we combine vessel-tracking data and the implementation of one of the world's largest marine reserves to identify the effort displacement and likely costs of conservation.
 
-\subsection{Phoenix Islands Protected Area}
-
-We use identification of fishing activity via Automatic Identification Systems (AIS) to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018 \cite{mccauley_2016,kroodsma_2018}.
-We track the spatial redistribution of the fleet and explore behavioral changes following the 2015 implementation of PIPA in Kiribati.
+The Pacific island nation of Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
+\ref{fig:PNA_map}).
+With an extension of 397,447 Km\textsuperscript{2}, this 11.5\% closure effectively displaced all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+We use identification of fishing activity via Automatic Identification Systems (AIS) provided by Global Fishing Watch to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018 \cite{kroodsma_2018}.
 We continuously observe 92 vessels for the 2012 - 2018 period.
@@
 The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
-Our analyses incorporate the monthly NINO4 anomaly index (Fig.
-\ref{fig:nino_plot}) to control for the association that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
 
-A market for fishing effort and allocation rules can reduce the costs of displacing fishing effort, but a spatial closure is still likely to cause behavioral changes as vessels redistribute.
-We find that between 2015 and 2016, displaced vessels spent 3,916 and 2,249 less vessel-days in Kiribati and PNA waters, respectively (Figs.
-\ref{fig:all_PS_VDS_year}).
-Over the same period, non-displaced and other vessels spent 1,278 less days in Kiribati, but spent 9,853 more days in PNA waters overall.
-These result in a net loss of 5,195 vessel-days for Kiribati, and a net gain of 7,600 vessel-days at the PNA-level (\emph{i.e.} the other 8 countries).
-At a vessel-day price of \$9,000 USD per day, these would represent \$46.7 and \$68 million USD, respectively.
+We use the tracking data to calculate the time that vessels spent within Kiribati and PNA waters (Figs.
+\ref{fig:all_PS_VDS_year}A-B).
+Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days historically allocated to Kiribati \cite{yeeting2018stabilising}.
+We find that displaced vessels fished 922 less days (a 10\% reduction) in Kiribati between 2014 and 2015, immediately after PIPA was implemented.
+For the same period, these vessels spent just 48 days less in PNA waters, suggesting that trading might have facilitated relocation of effort within PNA waters.
+On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
+The same pattern is observed at the PNA level, with vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
+These changes result in a net decrease of fishing effort within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Figs.
+\ref{fig:all_PS_VDS_year}A).
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
-Annual vessel-days in Kiribati continued to decrease to just 7,479 in 2018, mainly due to displaced vessels allocating less time to Kiribati (Fig.
-\ref{fig:all_PS_VDS_year}B, Fig.
-\ref{fig:hist_kir_fishing}).
-Current effort in Kiribati waters is well below their 11,000 vessel-day allocation \cite{yeeting2018stabilising}.
-However, we observe a relatively constant 45,000 vessel-days at the PNA-level, suggesting that Kiribati is, in fact, able to trade vessel-days and reduce the costs of displacement.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels are shown in Figure \ref{fig:fishing_raster_diff}.
+Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's waters.
+But does this result in losses to Kiribati?
+We do not explicitly observe trading between countries, but combining different sources of information we are able to paint a comprehensive picture.
+We use country-level fisheries revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) for the 2008 - 2016 period to complement our analysis (Fig.
+\ref{fig:revenues}A).
+Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
+This increase and subsequent decrease in revenues matches the AIS patterns we observe for Kiribati in 2014 - 2016 (Fig.
+\ref{fig:all_PS_VDS_year}A), and observed AIS effort is a reliable predictor of government revenue across all PNA countries from 2008 to 2016 (Fig.
+\ref{fig:revenue_FFA_effort_GFW}).
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
+\ref{fig:total_PNA_revenues}).
 
-We complement our analysis of change in observed vessel-days by looking at country-level data reported by the Pacific Islands Forum Fisheries Agency (FFA).
-We find that Kiribati's revenue went from \$148.8 million USD in 2015 to \$118.3 million USD in 2016, representing a decrease of \$30.5 million USD.
-Total PNA revenues showed a net increase of \$28 million USD (Fig.
-\ref{fig:total_PNA_revenues}).
-The largest decrease was observed for Kiribati, while the largest increase was observed for Papua New Guinea.
+\textbf{We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface(Fig \ref{fig:fishing_raster_diff}).
+These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+\ref{fig:sp_corr}).
+The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
+Environmental variation may certainly drive this, but the NINO4 anomaly \ref{fig:nino_plot} alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation.
+We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).}
 
-Total fishing effort in the PNA increased between 2015 and 2016, but fishing area decreased due to PIPA implementation (Fig.
-\ref{fig:all_PS_VDS_year}).
-We inspect the crowding effects that may arise by applying more (or the same amount of) fishing effort over less fishing area with two indices of spatial overlap between displaced and non-displaced vessels: 1) the number of cells that had fishing activity from both groups for each month and 2) the correlation of presence/absence of fishing activity between both groups over one month.
-The two fleets significantly interact more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and spatial correlation increase by a factor of four and three, respectively.
-Crowding might be driven by environmental variation concentrating fish at specific locations, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton.
-We observe similar patterns when repeating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
+\textbf{We use multiple linear regression to measure the change in nine vessel-level measures for displaced and non-displaced vessels before and after the implementation of PIPA (Fig.
+\ref{fig:all_panels}; Table \ref{tab:main_DID})).
+We find no evidence of displaced vessels fishing more after the implementation, and in fact observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$).
+Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$).
+Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
+These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
+We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.}
 
-Effort displacement and crowding are likely to induce behavioral changes in the fishing fleet.
-We calculate nine vessel-level measures that could capture responses to spatial closures: daily fishing hours, daily non-fishing at-sea hours, the proportion of fishing to non-fishing at-sea hours, daily distance traveled, daily mean distance from shore of fishing events (km), daily mean distance from port of fishing events (km), as well as monthly hours spent in PNA waters, Kiribati waters, and the High Seas (Fig.
-\ref{fig:all_panels}).
-We find no evidence of displaced vessels fishing more after PIPA implementation, and in fact observe a 27.5\% decrease ($p < 0.01$; Table \ref{tab:main_DID}) relative to non-displaced vessels.
-Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$; Table \ref{tab:main_DID}).
-Treated vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely caused by redistribution, as we observe that displaced vessels fished 79.67\% and 49.6\% less in Kiribati and PNA waters respectively, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe a statistically significant increase in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
+A new large-scale marine protected area is being proposed in the PNA.
+On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80\% of Palau's EEZ) to commercial fishing activities \cite{cimino_2019}, creating the 14\textsuperscript{th} largest protected area in the world (Fig.
+\ref{fig:PNA_map}).
+As a PNA member, Palau receives 700 purse seine vessel-days each year.
+Their longline fishery is also managed under a vessel-day scheme, with 10,500 non-tradable vessel-days per year, which currently sell at about \$200 USD each (Fig.
+\ref{fig:PLW_GFW_ts}).
+What does an 80\% closure represent for Palau's revenue from access fees?
+AIS data (2012 - 2019) shows that PNMS would displace $65.6 \pm 0.08$\% and $82.2 \pm 0.08$\% of longline and purse seine activity (Figs.
+\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
+Palau may be able to reduce the cost of lost license revenue if purse seine vessel-days are traded with other PNA members.
+However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, which would lead to a decreased allocation through time.
+Palau, howver, might continue to sell purse seine vessel-days to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+Longline vessel days are currently not tradable, meaning that the price for longline vessel-days might decrease, leading to losses in profits.
 
-\subsection{Palau National Marine Sanctuary}
+Rights-based fisheries management can prevent fisheries collapse \cite{costello_2008}.
+Our work shows that properly designed rights-based fisheries markets can also allow and incentivize large-scale marine conservation.
+Successful implementation of large-scale Marine Protected Areas under effort markets depends on two key features: tradable fishing rights and a biomass-based allocation rule.
+Tradable fishing rights allow a country to capture the benefits of conservation, and a biomass-based allocation rule ensures that this conservation actions are rewarded in the long term.
 
-On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80 percent of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world, effectively displacing all effort within its waters (Fig.
-\ref{fig:plw_2018} shows longline and purse seine fishing effort within PNMS for 2018).
-As part of the Nauru Agreement, Palau receives 700 purse seine vessel-days each year.
-They also  use a vessel-day scheme to manage the longline fishery  (10,500 vessel-days per year).
-Unlike the purse seine vessel-days, longline vessel-days are not tradable across countries and are worth much less, at about \$200 USD each.
-Our previous analyses suggest that Palau should be able to lessen the costs of the closure by trading purse seine vessel-days (\$5.65 - \$8.75 million USD) with other PNA members, but might lose more than 50\% of the revenues from the longline vessel-days (\$2.1 million USD).
-
-Table \ref{tab:revenue_loss} presents estimates of the potential revenue losses following full enactment of the PNMS under four different scenarios.
-In Scenario 1, Palau retains its current allotment of purse seine vessel-days and is able to sell them for a similar price to what it is currently selling them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-In Scenario 2, Palau is able to keep its current allotment of purse seine VDS to transfer to other PNA countries at the current benchmark price (\$8,000/day).
-Scenario 2 is likely if Palau retains its current allocation, but the US no longer purchases days.
-It should be noted that if allocation continues to be calculated based on effort and biomass, and if Palau continues to be allocated vessel days, its allocation will decrease as purse seine effort in its EEZ eventually reaches zero.
-In Scenarios 3 and 4, Palau loses all of its purse seine VDS, at \$8,000/day and \$12,500/day, respectively.
-In all scenarios, all longline vessel days and export tax revenues are lost, since longline vessel days are currently not tradable and Palau is currently planning on banning the export of fish.
-The longline vessel day loss is calculated using an average value of \$200 for 10,500 days.
-The export tax loss is calculated given the average tax revenue from 2012-2014 (\$482,236  from \cite{Gillett2016}).
-
-% I think we need to modify the last  part of this.
-Based on our analyses, we can say that they would lose a large portion of the longline days, but not all.
-I can calculate the longline effort within the PNMS and we can describe a ``worst-case scenario''.
-Turns out that the 80% closure has only 55.75% of all fishing effort.
-Also, my understanding from the workshop is that the export ban is already in place EXCEPT for tuna purse seines.
-They also pay a 0.35 USD / Kg export tax for fish LANDED in Palau.
-The new proposal is to LIFT the export ban and push for the development of a domestic pelagic fishery (artisanal mFADs and Pole and Line).
-
-\input{revenue_loss}
-
-\clearpage
-
-\section{Discussion}
-
-Our findings provide insights into the effect that LSMPAs can have on the redistribution of fishing effort and changes in behavior.
-Our analyses predict losses in revenue to countries that implement a spatial closure.
-However, these losses can be significantly reduced by market instruments and biomass-based allocation rules.
-Using vessel tracking data, we see that vessels that fished inside PIPA before the implementation redistribute to other areas within Kiribati, but also to other PNA countries and the high seas.
-Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onward.
-Redistribution leads to a crowding effect, and the spatial closure has little effect on the \emph{total} fishing effort exerted by purse seiners, but vessel-level responses were heterogeneous.
-Our analysis suggests that losses would be expected for Palau's Marine Sanctuary, but that these can be minimized if effort is traded freely and allocations are based on biomass, not effort.
-Here, we discuss the implications of our findings and possible shortcomings in our analysis.
-
-We observe ~50\% discrepancies in our estimates of lost revenues when using tracking data and FFA data.
-Vessel-day usage through time matches the 45,000 vessel-days for the PNA and the 11,000 vessel-days allocated to Kiribati \cite{yeeting2018stabilising}.
-Moreover, the trends through time are certainly similar, and all indicate a reduction of usage of Kiribati's waters.
-A possible explanation is that we used the reported mean annual vessel-day prices in our calculations, but there is certainly a spread around these.
-Furthermore, vessels can report their activity as ``transiting to port'' or ``solving mechanical issues'' and this time does not count towards a vessel's usage of VDS, which would result in an overestimation from tracking data.
-
-ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
-For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
-However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns.
-While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
-
-A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately guides the decision-making process of vessel captains.
-Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
-Likewise, the available data from the FFA does not cover the 2017 and 2018 period, and we do not observe vessel-day transactions between countries or detailed vessel-day prices.
-
-Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses for countries that sell fishing rights.
-The closure caused a crowding effect, which seems to lead some vessels to redistribute to areas close by.
-The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{havice_2013,aqorau_2018}.
-Overlaying conservation interventions and existing management schemes must be accompanied by similar dialogue and international cooperation, so that the benefits of conservation are captured by those incurring the costs.
-Furthermore, implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms \cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
+International goals over the next decade have set ambitious targets for marine conservation.
+Plans to implement large-scale Marine Protected Areas must consider the opportunity costs that come with such interventions \cite{smith_2010}, and identify sustainable financing mechanisms that compensate losses and incentivize long-term marine conservation \cite{mallin_2019}.
+The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+By facilitating trade and modifying the re-allocation rule, they may become pioneers in effective large-scale marine conservation.
 
@@
 
-\section{Figures and tables}
-
-% Map of LSMPAS
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/LSMPAs_map.pdf}
-\caption{\label{fig:LSMPAs_map}Large Scale Marine Protected Areas. The map shows all areas larger than 30,000 Km\textsuperscript{2}. The Phoenix Islands Protected Area is shown in red.}
-\end{figure}
+\section*{Figures and tables}
 
@@
 \includegraphics{img/PNA_model.pdf}
-\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery (vertical axis) as a function of reserve size ($R$; horizontal axis) and movement ($\theta$; line color).
+\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
+Each line represents a possible value of stock movement ($\theta$; line color).
+The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and .
 Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
-Costs avoided by tradig are shown in (C).}
+Costs avoided by trading are shown in (C).
+Dashed red line in (A) is a 1:1 line.
+Trading significantly reduces the costs of a conservation intervention in Patch 1.}
 \end{figure}
@@
 \includegraphics{img/allocation_cost_plot.pdf}
-\caption{\label{fig:allocation_cost_plot}Cost (vertical axis) of different allocation rules (line colors) as a function of reserve  size ($R$; horizontal axis) and movement ($\theta$; line type).
-Costs are shown for Patch 1 only.}
+\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules.
+Each line represents the revenue losses for a combination of allocation rules ($\alpha$; color) and movement ($\theta$; line type) for different reserve sizes ($R$; horizontal axis).
+An effort-based allocation and low movement values result in the highest costs.
+Cost can be minimized for all movement values if alloction is based on biomass.}
 \end{figure}
 
-% Effort redistribution bars for Kiribati only
+% Map of LSMPAS in PNA
+\begin{figure}
+\centering
+\includegraphics{img/PNA_map.png}
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
+Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
+A red line indicates the Kiribati EEZ.
+The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuar.
+Land masses are shown in gray.
+Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
+\end{figure}
+
+% Effort redistribution bars for PNA and KIR
 \begin{figure}[htbp]
@@
 \includegraphics{img/all_PS_VDS_PNA_KIR_year.pdf}
-\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all all PNA countries (A) and Kiribati (B) by displaced, non-displaced, and other vessels.
-Vessels displaced from PIPA fish less within the PNA, but non-displaced and other vessels fish more, resulting in a net increase.
-Vessels that used to fish within PIPA account for the largest effort reduction to Kiribati.
-The dashed horizontal lines represent the total allowable effort in the PNA (45,000 days) and Kiribati (11,000 days).}
+\caption{\label{fig:all_PS_VDS_year}AIS-derived annual vessel-days for Kiribati (A) and all Parties to the Nauru Agreement (PNA; B).
+Annual effort is broken down by displaced, non-displaced, and other vessels.
+The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days) and the PNA (45,000 days).
+Note that the reduction for Kiribati is driven by displaced vessels fishing less in Kiribati's waters, but that their decrease is not as sharp for all PNA waters.
+Vessels displaced from PIPA fish less within the PNA, but non-displaced and other vessels fish more, resulting in a net increase.}
 \end{figure}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
-\end{figure}
-
+% Revenue data from FFA and GFW estimates.
 \begin{figure}[htbp]
@@
 The dashed line represents line of best fit, solid line represents 1:1 line.
-The same graph using absolute values is shown in \ref{fig:revenue_FFA_GFW_linear}.}
+The same graph using absolute values is shown in \ref{fig:revenue_FFA_GFW_linear}.
+A graph showing reported revenues vs.
+observed effort is shown in \ref{fig:revenue_FFA_effort_GFW}.}
+\end{figure}
+
+% Palau Raster and PNMS
+\begin{figure}
+\centering
+\includegraphics{img/plw_2018.png}
+\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
+The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
+Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
 \end{figure}
@@
 
-\section{Methods}
+\section{Supplementary Materials}
 
@@
 We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 opperate under a vessel-day schemePatches, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
+Patches 1 - 9 opperate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
+The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
 The price of fish is $p$, and catchability is given by $q$.
@@
 Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season.
-In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$.
+In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
 The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
@@
 $$
-\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_i-cE_1^\beta
+\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_1-cE_1^\beta
 $$
 
-With $\Omega_i = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  (0, 1)$) and within-patch fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \not 1} = 1$ since only Patch 1 implements a reserve.
+With $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
+Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
 
-Profits from fishing in each Patch are:
+Therefore, we can generalize the patch-level profit equation to:
 
 $$
-\Pi_i(E_i,X_i) = pqE_iX_i\Omega_i-cE_i^\beta
+\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
 $$
@@
 
-$$
+\begin{equation}
 \pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
 \label{eqn:marginal_profit}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
 \label{eqn:effort_hs}
-$$
+\end{equation}
 
@@
 		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
-		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_1}{\beta c} \\
-		E_i &= \left(\frac{pqX_i\Omega_i - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_i}{\beta c} \\
+		E_i &= \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
 	\end{split}
@@
 
+Equation \ref{eqn:demands} tells us patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
+A vessel-day scheme establishes a cap on total effort allowed.
+This means that fishing effort from Patches 1 - 9 must add up to this limit.
 Therefore, total allowable effort in the fishery is given by:
@@
 $$
+
+In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
 
@@
 
-We use the model above run three different simulations.
-We test the model across a range reserve sizes and movement parameters.
-We use to main scenarios.
-The first scenario does not allow trading.
+We use the model above to run simulations under two market designs.
+We test the model across a range reserve sizes and movement parameters.The first scenario does not allow trading.
 In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
@@
 We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect, this equiulibrium is the same as the first step above.
+Since a closure is not in effect and vds-managed effort is equally distributed across the 9 patches, this equiulibrium is the same as the first step above.
 We then implement a spatial closure in patch 1.
@@
 This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn would modify the demand curves (Eq \ref{eqn:demands}).
-We therefore iterate this process until biomass stabilizes, therefore finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in patch 1.
+This reduction in biomass in turn would modify the demand curves for each countruy (Eq \ref{eqn:demands}).
+We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
+Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
 
 \subsection{Allocation rules}
+
+Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
+In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
+The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
 
@@
 These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}
 
@@
 
-\clearpage
+\subsection{Analysis}
 
-\subsection{Analysis}
+ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
+For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
+However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
+Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns.
+While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
+Our analyses incorporate the monthly NINO4 anomaly index (Fig.
+\ref{fig:nino_plot}) to control for the association that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
 
@@
 
-We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
+We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
 1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
@@
 All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
-All analyses were performed in R version 3.5.1 \cite{rcore_2018}.
-Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
+
+\subsubsection{Effort redistribution}
+
+We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to understand effort redistribution.
+Non-displaced vessels serve serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
@@
 
+\subsubsection{Data and code availability}
+
+All analyses were performed in R version 3.5.3 \cite{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
+
 \clearpage
+
+\FloatBarrier
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
-Countries that belong to the PNA are shown in blue, while empty polygons indicate all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon shows PIPA.
-A solid purple polygon shows PNMS.
-Land masses are shown in gray.
-Labels indicate ISO3 country codes (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[htbp]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[htbp]
 \centering
@@
 \includegraphics{img/nino_plot.png}
-\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Timeseries of NINO4 anomaly from January, 1980 to December, 2018.}
+\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
 \end{figure}
-
-\clearpage
 
@@
 \caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zone (EEZ), red lines show existing Marine Protected Areas.
+Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas.
 Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
@@
 \end{landscape}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/sp_corr.pdf}
+\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
+\end{figure}
 
@@
 \centering
+	\includegraphics{img/revenue_FFA_effort_GFW.pdf}
+	\caption{\label{fig:revenue_FFA_effort_GFW}Observed fishing effort vs. reported revenues. The dashed line represents line of best fit.}
+\end{figure}
+
+\begin{figure}
+\centering
 	\includegraphics{img/total_PNA_revenues.pdf}
@@
 	\includegraphics{img/catches.pdf}
-	\caption{\label{fig:catches}Financial indicators for PNA countries.
+	\caption{\label{fig:catches}\textbf{Financial indicators for PNA countries.
 A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
-Vertical dashed line in both plots denotes implementation of PIPA.}
+Vertical dashed line in both plots denotes implementation of PIPA.
+- NOT REFERENCED}}
 \end{figure}
@@
 	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}	
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palaw during 2018 at a 0.5 degree resolution. The red polygon shows the Palau National Marine Sanctuary.}
-\end{figure}
-
-I used this figure at the workshop last week, I do not intend to use it with the current design.
-I want to have a normal white background and split it into 2 (longliners and purse seiners) to better capture the effort that would be displaced by PNMS.
-I might also break it by year (2015 - 2018) to show that patterns are consistent through time.
-
-\begin{figure}
-\centering
-\includegraphics{img/PS_VDS_PNA_by_month_eez.pdf}
-\caption{\label{PS_VDS_PNA_by_month_eez}Time series of monthly observed vessel-days for each PNA country.}
+	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}\textbf{Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}}	
 \end{figure}
@@
 \centering
-\includegraphics{img/nvessels_to_90.pdf}
-\caption{\label{fig:nvessels_to_90}Cumulative activity (\% of total hours) as a function of increasing fraction of vessels (\% of total) by year.)}
+\includegraphics{img/PLW_GFW_ts.pdf}
+\caption{\label{fig:PLW_GFW_ts}Time series of longline and purse seine fishing effort in Palau.}
 \end{figure}
 
-%\section{Old Text}
-
-%\subsection{Large-Scale Marine Protected Areas}\label{lsmpas}
-%
-%The cutoff at which an MPA is considered to be a LSMPA ranges from areas
-%larger than 30,000 km\textsuperscript{2} as defined by
-%\cite{desanto_2013} or areas larger than 250,000 km\textsuperscript{2},
-%as defined by \cite{toonen_2013}. Figure \ref{fig:LSMPAs_map} shows
-%LSMPAs that meet the latter condition, and are also fully no-take. LSMPAs are often
-%implemented in the pelagic environment, where the dominant human
-%activity is industrial fishing \cite{gray_2017,kroodsma_2018}. The
-%early literature on LSMPAs focused on the inherent challenges and
-%difficulties that come with a pelagic environment. \cite{kaplan_2010}
-%claimed that very large MPAs would result in excessive opportunity costs
-%and that these would be difficult to enforce. \cite{game_2009}
-%suggested that most of the challenges could be overcome with the
-%incorporation of technology, in what then became known as Dynamic Ocean
-%Management \cite{maxwell_2015}.\footnote{See \cite{singleton_2014}, who provide an objective discussion of the pros and cons of LSMPAs.} 
-%
-%Spatial closures of this magnitude are likely to induce changes in
-%fishers' behavior. Theoretical models of fishing effort redistribution
-%range from the simplistic assumption that effort inside the bounded
-%region disappears, to spatially explicit models that reallocate fishing
-%effort based on habitat characteristics, presence of other vessels, and
-%expected returns \cite{smith_2003,hilborn_2006}. However, these focus
-%on the long term optimal equilibrium, and redistribution of fishing
-%effort may not always be optimally distributed, especially over the first few years
-%\cite{stevenson_2013}.
-%
-%The empirical research that has been done in smaller sized MPAs
-%suggests that resource users may show idiosyncratic responses. For
-%example, \cite{stevenson_2013} show that a network of MPAs displaced
-%fishing effort farther away from ports, resulting in higher
-%\emph{perceived} costs, and increases in catch per unit effort.
-%\cite{cabral_2017} analyze the redistribution of fishing and
-%non-fishing vessels following the implementation of a network of MPAs in
-%California, and find that dive boats follow a
-%fishing-the-line pattern, while some fishing boats follow an ideal free
-%distribution. More recently \cite{elahi_2018} used satellite tracking
-%data to show that a temporal spatial closure caused trawlers to maintain
-%effort but apply it more intensively elsewhere, particularly along the
-%borders and closer to shore. The way in which fishers react to a spatial
-%closure can have major implications for its outcome
-%\cite{smith_2003,hilborn_2006}, highlighting the need to understand how
-%fishers react to the implementation of LSMPAs, how fishing effort
-%changes, and how it is spatially redistributed. All these studies evaluate relatively small closures within Exclusive Economic Zones, where other regulations exist.
-%This may not always be the case for LSMPAs, where often the entire EEZ
-%is converted into a LSMPA, leaving fishers with the option of moving to
-%the high seas or other countries' EEZs, with potentially very different fishing regulations.
-%
-%\subsection{Nauru agreement and the Phoenix Islands Protected Area}
-%
-%The cooperation that emerged under the Nauru Agreement allowed for subsequent
-%agreements that strengthened fisheries management, like the Palau
-%Agreement, which limited the number of purse seiners at 205 vessels from
-%1995-2007.\footnote{See \cite{havice_2010} for a detailed description of the Nauru, Palau, and Federated States of Micronesia agreements.} However, the most notable regulation is
-%the approach to manage fishing effort: a Vessel Day Scheme (VDS)
-%implemented in 2007 \cite{havice_2013}. This effectively modified how
-%fishing effort was managed, from total number of vessels (under the Palau
-%Agreement) to total vessel-days. 
-%Under the purse seine VDS, a total number of annual vessel days for the entire fishery is agreed upon by the PNA parties.
-Each party’s allowable effort (PAE) is then calculated based on historic effort and biomass within each party’s EEZ.
-Sixty percent of the PAE is calculated based on EEZ effort over the last seven years and 40\% of the PAE is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}}.
-A minimum benchmark fee is set for purse seine vessel days which each party can transfer (\emph{i.e.} sell to another PNA member) or sell to the highest bidder (\emph{i.e.} sell to a fishing company).
-Vessel days can be transferred to fish in any PNA party’s EEZ, without penalty to the transferred parties' allocations \cite{PNA2016}.\footnote{The process of transferring days between parties is described in Article 7 of the Management Scheme \cite{PNA2016}.} The mean value of a vessel day has steadily increased since 2007 \cite{havice_2013}.
-%Although detailed records on sales or transfers of vessel days are not publicly available \cite{havice_2013,yeeting2018stabilising}, a minimum benchmark fee of \$8,000/day was set from 2015 \cite{PNA2014a}.
-%
-%\cite{yeeting2018stabilising} summarize the PNA implementing arrangements as follows: “foreign vessels [are required] to be registered and licensed, report catches, maintain log books, allow observers on board and maintain transparency over their fishing activities.” Further, vessels registered with the Vessel Day Scheme are required to have Automatic Location Communicators (ALC) or Mobile Transceiver Units (MTU) that transmit their locations at least once per hour while they are within the VDS Management Area \cite{PNA2016}.
-Every entire day that a vessel is within the VDS Management Area is counted as a vessel day used, unless the vessel reports a “no fishing day” (e.g., travel, maintenance, etc.) and periods of less than 24 hours are counted as partial days \cite{PNA2016}.
-As described in the Palau Arrangement, fishing days by vessels shorter than 50m (longer than 80m) count as 0.5 (1.5) vessel days.
-Countries are responsible for ensuring registered vessels comply with the implementing arrangements and that they stay within their PAE.
-Parties that exceed their PAE should reportedly be penalized by reductions to the following year’s PAE \cite{PNA2016}.
-There are some criticisms of the PNA PS VDS claiming that there is a lack of monitoring, compliance, and transparency that could hinder the future success of the program \cite{Arnason2014,yeeting2018stabilising}.
-While the effectiveness of this scheme has been
-%debated in terms of meeting fishery management and conservation
-%objectives, the licensing significantly contributes to the economy of
-%these island nations \cite{havice_2010}.
-%
-%The main tuna species caught in the region are skipjack
-%(\emph{Katsuwonus pelamis}), yellowfin (\emph{Thunnus albacares}),
-%albacore (\emph{Thunnus alalunga}) and bigeye (\emph{Thunnus obesus}).
-%From these, the first two are amongst the top-10 species represented in
-%global fisheries production statistics, with 2016 catches increasing
-%relative to the 2005-2014 average \cite{fao_2018}. This region of the
-%Pacific has historically accounted for a large portion of tuna catches
-%\cite{aqorau_1997}. Today, the PNA controls close to 50\% of global
-%skipjack tuna production \cite{pna_website_2018} and the combined area of all EEZs involved is 14.6 million km\textsuperscript{2}, larger than the land mass of the United States of America.
-A large portion of global skipjack
-%catch derives from purse seine vessels licensed under the VDS.
-%Fishing vessels from Australia, New Zealand, China, France, Korea,
-%Japan, the Philippines, Taiwan, and the United States participate in the
-%purse-seining VDS.
-%
-%One of the most notable and recent management interventions in the
-%region is the implementation of the Phoenix Islands Protected Area (PIPA)
-%by the government of Kiribati. PIPA was first declared in 2006, and
-%established in 2008 with only 4\% of the area declared as no-take. On
-%January 1\textsuperscript{st}, 2015, the no-take area within PIPA was
-%expanded to a total area of 397,447 km\textsuperscript{2}, roughly 1.5
-%times the size of Ecuador. Figure \ref{fig:PNA_map} shows a map of the
-%PNA countries (excluding Palau) and the Phoenix Islands Protected Area.
-%
-%The closure of such a large area in one of the most important fishing
-%regions in the world provides a unique opportunity to evaluate the
-%behavioral responses and redistribution of fishing effort by vessels
-%that used to fish there. PIPA has been the focus of previous research
-%showing that fishing effort is effectively reduced after implementation
-%\cite{mccauley_2016,mcdermott_2018}. To this, we pose two questions:
-%How did individual vessels respond to the sudden exclusion of such a big
-%area? Where did all the vessels go? And what does this imply for revenues from
-%selling VDS for both Kiribati and the PNA as a whole? 
-%
-%A spatial closure might cause fishers to modify
-%their behavior as they adapt to a new state of the world. For example, some may have
-%to travel further distances to find new fishing grounds, increasing their fuel
-%costs. If fishers had developed experience for fishing in particular
-%sites, being excluded might impose a learning cost on them, as they
-%identify new fishing grounds. This might result in increased search
-%times. However, if the area of knowledge of a vessel is significantly
-%larger than that of the spatial closure, they might already know other
-%places to fish. In the next sections we describe
-%the data and methods used to answer these questions.
-%
-%\subsection{Palau}
-%
-%\subsubsection{Palau National Monument}
-
-%On October 28, 2015, the President of Palau, H.E.
-Tommy E.
-Remengesau Jr., signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} to commercial fishing activities, creating the 14th largest protected area in the world.
-The sanctuary will fully protect about 80 percent of the nation’s EEZ.
-The remaining 20\% of Palau’s EEZ (close to the most heavily populated islands: Koror and Babeldaob) will become a Domestic Fishing Zone in which traditional and domestic fishing activities will be allowed to provide fish solely for the domestic market (\emph{i.e.} exports of pelagic fish will be prohibited).
-Alongside these protections, the Palau National Marine Sanctuary (PNMS) Act will support a domestic pelagic fishery.
-In this section, we use our preceding analysis on the ex-post impacts of PIPA to attempt to make some \emph{ex ante} predictions about the potential impacts of PNMS.
-We start by giving some background on the fishing that is currently taking place inside the future PNMS.
-
-%\subsubsection{Background on Commercial Fishing in Palau}
-
-%Foreign tuna fishing in Palau’s EEZ began before WWI.
-Pole and line was the initial gear used to target skipjack tuna by Japanese vessels.
-Foreign fishing activities stopped during WWII and started again in the 1960s when Japanese fishers returned and the locally based Van Camp Seafood Company carried out fishing with boats crewed by Okinawans.
-The Japanese also began purse seine fishing in the 1960s and 1970s and limited longline fishing for yellowfin tuna developed during the same time.
-During the 1980s, longline fishers began to set their lines deeper, shifting their targets to bigeye tuna.
-During the 1980s, Korean and Taiwanese vessels also began longline fishing in Palauan waters for export to Japan \cite{chapman2000development}.
-There are currently three transshipment companies operating in Palau.
-
-%Purse seine vessels target schools of skipjack tuna that are then canned.
-Compared to other EEZs in the Pacific, especially the PNA EEZs, Palau’s EEZ is not known to be a preferred fishing ground for purse seining (Sisior, pers.
-comm.).
-This can be seen in Figure \ref{fig:VDS_country_year}.
-Currently all purse seine boats fishing in Palau’s EEZ are Japanese and they do not land their catch in Palau (Table \ref{tab:palau_purse}).
-
-%All longline vessels fishing in Palau’s EEZ are foreign owned (Table \ref{tab:palau_long}).
-Japanese longline vessels do not land their catch in Palau.
-Locally-based, foreign-owned longline boats are mostly Taiwanese vessels that are contracted by one of the two main fishing companies (Palau International Traders Incorporated (PITI) and Kuniyoshi Fishing Company (KFC)).
-Ninety-five percent of the catch from PITI and KFC contracted boats is exported to Japan upon landing in Koror (the largest town in and former capital of Palau).
-Most of the discards are either sold or donated in Palau.
-A very small portion of the discards is frozen and transported to Taiwan when vessels return to their home ports.
-
-%\subsubsection{Access fees and taxes}
-%
-%An agreement between Palau and four Japanese fishing associations\footnote{This is a single agreement between Palau and four associations—1)Federation of Japan Tuna Fisheries Cooperative Associations, 2) National Offshore Tuna Fisheries Association of Japan, 3) Japan Far Seas Purse Seine Fishing Association, 4) Federation of North Pacific District Purse Seine Fisheries Cooperative Association of Japan (Performance Audit Report on Managing Sustainable Fisheries (Tuna) 2013).} covered three methods of fishing (longline, purse seine, and pole and line) and allowed Japan to have up to 290 vessels in Palau waters with no limits on catch.
-Japan paid 4-5\% of catch returns for this access, but there was no way to validate their catch \cite{Tewid2013}.
-Between 2010 and 2014, Japan paid Palau between \$196,100- \$867,120 annually in access fees \cite{Gillett2016}.
-Currently, these access fees have been replaced by the PNA vessel day scheme (described earlier).
-% 
-%There used to be a number of agreements between the Republic of Palau and foreign owned, local based companies, in particular PITI and KFC, to allow longline fishing \cite{Tewid2013}.
-Vessels under these agreements were internationally-owned, locally-based vessels that paid for annual licenses based on the size of each vessel.
-These are the vessels shown in Table \ref{tab:palau_long} (excluding the Japanese vessels).
-So, for example, there were 38 vessels as part of these agreements in 2016.
-Between 2010 and 2014, licensing fee revenue from these agreements was between \$219,000-\$284,600 per year \cite{Gillett2016}.
-These access fees have also been replaced by a new longline-specific version of the VDS (described in more detail below).
-%
-%There are two multilateral treaties that grant preferential access to Palau waters to US and Federated States of Micronesia (FSM) flagged purse seine boats: the US Multilateral Tuna Treaty and the Federated States of Micronesia Arrangement.
-The US Treaty was renegotiated in 2016 with stipulations on minimum vessel day fees.
-Very little purse seine fishing is conducted by FSM and US vessels in Palau’s EEZ, but Palau still receives a portion of these treaty funds.
-These agreements have been described by some commentators as foreign aid, with little connection to underlying fish stocks \cite{Gillett2016}.
-%
-%The export tax for all commercial tuna and billfish, either fresh or frozen, is \$0.35/kg. Average annual revenue from export taxes was around \$500,000 from 2011-2014 \cite{Gillett2016}. 
-%Other than the access fees and tax revenue, Palau receives little additional economic benefits from pelagic fisheries, especially considering that very few jobs are created by the fishery.
-Between 80 to 90 people are employed by offshore fisheries, and of these only around 20\% are Palauans, earning wages that are only 50\% of average wages in Palau \cite{Gillett2016}.
-%
-%\subsubsection{Parties to the Nauru Agreement and the Vessel Day Scheme}
-%
-%In the case of Palau, the VDS is run by the Bureau of Marine Resources, within the Ministry of Natural Resources, Environment and Tourism.
-Palau’s current purse seine VDS allotment is reportedly around 700 vessel days annually (Sisior, pers.
-comm., \cite{Pojas2018}), although historically this number has been lower (average of 580 days between 2008-2011 \cite{Tewid2013}).
-Palau sells most of its vessel days to the US for \$12,500 per day (as negotiated in the US treaty), regardless of whether US vessels actually fish in Palau’s EEZ.
-The remainder of Palau’s purse seine vessel days are sold for between \$9-10,000 each.
-When vessel days are purchased to transfer to another EEZ, Palau charges a transfer fee (approximately \$500), for administration costs and future opportunity costs (since vessel day allotments are based partly on historical effort within the EEZ).
-Though records are confidential, it has been publicly reported that one PNA member party that Palau has transferred vessel days to is Papua New Guinea \cite{Tewid2013} and in 2018, vessel days were sold to a fishing company in the Philippines for the first time \cite{Pojas2018}.
-In 2018, Palau brought in approximately \$9 million USD in VDS revenue (Sisior pers.
-comm.).
-%
-%The longline VDS (LL VDS) is in its infancy and has not yet been fully implemented at the PNA-scale, although several countries are now implementing it at the country-scale.
-Palau was the first party to implement the VDS for longline fishing in 2017.
-In 2014, longline boats fishing in Palau’s EEZ fished 10,500 days (Sisior, pers.
-comm.).
-Since 2016, the number of allowed longline VDs has been a fraction of the 2014 days, reducing each year as stipulated in the PNMS Act.
-Palau sells its LL VD for \$150-\$250 (Sisior pers.
-comm.).
-Because the LL VDS is still new and has yet to be fully implemented by all parties, LL VD are not currently transferable between PNA member EEZs.
-%
-%\subsubsection{Plans for a domestic pelagic fishery}
-%
-%In the recent past, a single domestic pole and line vessel supplied Palau with an estimated 100mt of catch \cite{Gillett2016}.
-The vessel ceased operations in recent years when the captain became ill and passed away, but there is talk that it is gearing up to start operations again under new leadership (Sisior, pers.
-comm.).
-Otherwise, there are no domestic vessels dedicated to full-time offshore fishing.
-A number of fishers occasionally troll offshore for tuna and other pelagics, but there are no official estimates of volumes.
-%Local NGOs have sponsored short trainings on small-scale canning and proper techniques for processing high grade tuna to encourage existing fishers to devote more time to offshore fishing.
-There are several possible scenarios for a domestic fishery (including those featured in a feasibility report by FFA \cite{Skirtun2017}), but there has yet to be any official action towards a particular scenario.
+\begin{figure}
+\centering
+\includegraphics{img/plw_ts_plot.pdf}
+\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the prposed PNMS boundaries.}
+\end{figure}
 

### 2019-05-30 docs/old_ms/Markets_Conservation_May17.tex
Added all files

--- 2019-05-22 docs/old_ms/PIPA_Palau_Science_JL.tex
@@
 \begin{sciabstract}
-Marine Protected Areas have the primary objective of conserving bounded waters by displacing or limiting fishing effort.
-With global conservation targets seeking to protect 10\% of the world’s ocean by 2020, it is important that the spatial displacement of economic activities is fully considered.
-A spatial closure in a trans-boundary fishery can potentially result in costs to the implementing country and benefits to neighboring countries.
-We show that effort markets may reduce up to 70\% of the costs of Marine Protected Areas, and that allocation rules based on biomass (rather than effort) may further incentivize conservation.
-We then use identification of fishing activity via Automatic Identification Systems to evaluate the effect that the Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}, implemented in 2015 in Kiribati) had on vessel distribution and behavior.
-Aggregate fishing effort remains relatively constant following the closure, but is significantly reduced within Kiribati, especially by vessels that historically fished within PIPA before its implementation.
-We find evidence that Kiribati may be trading its surplus of vessel-days, which would significantly reduce the costs of displaced fishing effort.
-We use these insights to predict the implications of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate that effort markets could reduce the cost of implementation by as much as 77\%.
-Our work highlights the role of effort markets in enabling conservation, and the importance of allocation rules that praise, not punish, conservation.
-The Parties to the Nauru Agreement have successfully developed a management scheme that allows for conservation interventions to come at a low cost, and could be a model for trans-boundary conservation across the globe.
+Will rights-based approaches to managing natural resources facilitate, or relegate large-scale conservation?
+We study this question in the context of large-scale marine protected areas, and ask whether a country who commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
+Indeed, this is the question island (and other) nations all over the world face as they consider whether, and how, to comply with various international commitments to massively expand marine protection.
+We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel day trading scheme in the Pacific, and vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or relegates conservation.
+The answer hinges critically on two design features of the rights-based fishery market.
+First, only if trading of harvest or vessel days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation.
+Instead, if trading is forbidden, then countries are likely to suffer significant losses from conservation.
+Second, as rights are re-allocated between countries periodically, the re-allocation must depend only on biological features, and not on a country's past effort or catch.
+Otherwise, the reallocation acts as a punishment to the conserving country.
+Overall, these results show that seemingly innocuous design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
 \end{sciabstract}
@@
 \section{Introduction}\label{introduction}
+Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world.
+Currently only about 3\% of the world's ocean is strongly protected, and these commitments call for 10\%, 30\%, or even up to 50\% of the ocean to be off-limits to fishing.
+Fundamentally, to achieve these goals, huge swaths of sovereign nations' waters will have to be closed to fishing.
+What incentives might motivate a country to engage in such large-scale marine protection?
+Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from its borders?
+We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: The design of fishing rights.
+
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA), which is one of the most successful, profitable, and well-orchestrated international cartels from any sector of the economy.
+Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific Island states that collectively manages tuna fishing in its members' waters.
+These waters collectively account for XXX square km (an area larger than XXX), and YYY\% of the catch of productive tuna species such as XXX and YYY.
+
+In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits; this explains why international attention has focused there for targeted conservation efforts to help achieve the previously mentioned targets.
+But the PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, often exceeding 50\% of GDP.
+A natural concern arises: Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be enormous, and may prevent it from engaging in any meaningful conservation.
+Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
+We show how the rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
+
+OLD TEXT FROM HERE
 

### 2019-05-30 docs/old_ms/Markets_Conservation_May21.tex
Added all files

--- 2019-05-30 docs/Markets_Conservation_May30.tex
@@
 
-\author{Juan Carlos Villase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
+\author{Juan CarlosVillase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
 \\
@@
 \begin{sciabstract}
-Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
-Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with international commitments to expand Marine Protected Area (MPA) coverage.
-We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and spatially-explicit vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
+Will rights-based approaches to managing natural resources facilitate, or relegate large-scale conservation?
+We study this question in the context of large-scale marine protected areas, and ask whether a country who commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
+Indeed, this is a question island (and other) nations all over the world face as they consider whether, and how, to comply with various international commitments to massively expand marine protection.
+We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific, and vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or relegates conservation.
 The answer hinges critically on two design features of the rights-based fishery market.
-First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Instead, if trading is forbidden, countries are likely to suffer losses from conservation.
-Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
-Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
+First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation.
+Instead, if trading is forbidden, countries are likely to suffer significant losses from conservation.
+Second, as rights are re-allocated between countries periodically, the re-allocation must depend only on biological features, and not on a country's past effort or catch.
+Otherwise, the reallocation acts as a punishment to the conserving country.
+Overall, these results show that seemingly innocuous design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
 \end{sciabstract}
@@
 
-Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
+Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world.
 Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%, 30\%, or even up to 50\% of the ocean to be off-limits to fishing.
@@
 What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from within its borders?
-We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: the design of fishing rights.
+Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from its borders?
+We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: The design of fishing rights.
 
-We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA), which is one of the most successful, profitable, and well-orchestrated international cartels from any sector of the economy.
 Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific Island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
-These waters collectively account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack tuna catches in the Western Central Pacific \cite{havice_2013}.
+These waters collectively account for 14.5 million Km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack catches in the Western Central Pacific \cite{havice_2013}.
 
-In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
-A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
+In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits; this explains why international attention has focused there for targeted conservation efforts to help achieve the previously mentioned targets.
+But the PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, often exceeding 50\% of a country's revenue.
+A natural concern arises: Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be enormous, and may prevent it from engaging in any meaningful conservation.
 Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
-We show how a rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
+We show how the rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
 
-To mirror the strategies and spatial connections among the nine PNA countries and the high seas, we develop a 10-patch spatial bioeconomic model.
-The fishery in nine of the patches operates under a market-based system in which ``vessel days'' are capped, closely tracked, and may be traded across countries.
-This vessel-day scheme (VDS) is actually used by the PNA; each country is given an allocation of vessel-days that can then be sold to fishing firms.
-A vessel-day owned by country $i$ entitles $i$ to lease that day to a fishing vessel, entitling it to fish in $i$'s EEZ for a 24 hour period.
-In our model, Patches 1 - 9 are countries that operate under a VDS (in which fishing days are limited) and Patch 10 represents the high seas, where fishing days are governed by economic conditions, not by the VDS.
+We develop a 10-patch spatial bioeconomic model of a fishery operating under a vessel-day scheme (VDS), and where conservation is being considered.
+Patches 1 - 9 operate under a VDS and Patch 10 represents the high seas in open access.
+Patch 1 considers closing a portion of its waters ($R$, between 0 and 1).
+There are a total of 45,000 vessel-days, equally distributed between the 9 VDS-managed patches.
+The fishery revenue to these patches is the product of within-patch vessel-days and vessel-day price.
+Fishing vessels decide to fish in each patch based on available biomass (\emph{i.e.} biomass not within a reserve), and are willing to pay a vessel-day price that equates to their marginal profits at the last unit of effort applied.
+Total biomass is equally distributed across the 10 patches.
+The stock remains within each patch during the fishing season, but growth from escapement is equally distributed across the 10 patches.
 
-While modeling the VDS market may be interesting in its own right, our primary purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-To examine this, suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters as a marine reserve, in which no fishing is allowed.
-When Country 1 creates a reserve, several consequences may arise.
-Perhaps most obviously, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in $i$'s waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-The purpose of our model is to examine these consequences in detail, with a particular focus on how design features of the market affect Country 1's incentives to create the marine reserve.
+We test the implications of conservation under two market designs: one in which effort trading between countries is not allowed, and one where vessel-days can be traded between countries.
+On both cases we solve for the equilibrium vessel-day price and effort redistribution.
+We quantify the losses by comparing revenues from each scenario to a benchmark scenario without conservation.
+The fishery is simulated for a range of reserve sizes and assumptions about within-patch stock movement.
+We then examine the role of vessel-day allocation rules, where periodic allocation is a weighted combination of historical within-patch effort and biomass.
+Finally, we use vessel-tracking data to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
+We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary, targeting an 80\% closure of its Exclusive Economic Zone \cite{cimino_2019}.
 
-Not all market-based approaches to environmental management are created equal.
-A pervasive finding across a range of natural resources is that features of market design can have enormous implications for the market's functioning.
-In the context of fishery markets, two market design features stand out as important for a variety of outcomes, and we will show that they are pivotal in determining the incentives for large-scale marine conservation.
-The first design feature has to do with the trading of rights, and the second design feature concerns the allocation of rights.
-We examine the effects of large-scale conservation in Country 1 across a range of scenarios for trading and allocation of vessel day fishing rights across our nine model countries.
-In all cases we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
-We quantify the change in revenue to each PNA country from large-scale conservation in Country 1, by comparing revenues from each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement.
-
-Why would trading and allocation rules affect the incentives for conservation by Country 1?
-Invoking \emph{reductio ad absurdum}, consider the incentives for Country 1 to close 100\% of its waters.
-Such a closure would surely benefit the other countries through the increased abundance of fish.
-If Country 1 could sell its fishing rights, the other countries would likely buy them, and this could offset the foregone costs of fishing its own waters.
-But if Country 1 was not allowed to sell its rights, then it would lose all of its fishing revenue.
-This provides the simple intuition for why allowing trading across countries is so critical to conservation incentives.
-The rules for how fishing rights are allocated across the nine countries are equally important.
-Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
-This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.
-
-In our bioeconomic model, we examine the implications of conservation under alternative market designs: with, and without trading, and under alternative allocation rules.
-To test how the PNA allocates rights, we vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
-Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
-
-We begin by simulating a fishery where trading of fishing days across countries is forbidden.
-In that setting, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+We begin by simulating a fishery where effort is not traded between countries.
+We find that a spatial closure in Patch 1 will always result in a loss in revenues (Fig.
 \ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases, allowing vessels to harvest the stock within the remaining open area.
+Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
@@
 \ref{fig:vessel_day_price_no_trading_plot}).
-When countries cannot trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches (Figure S2 shows that the increase in revenue ranges from 0\% to 6\%).
+When countries can not trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches.
 
 How would a different market design, where trading between countries is allowed, change these results?
-To answer this we simulate the exact same fishery, but now allow for vessel-days to be traded across patches.
+To answer this we simulate the same fishery, but now allow for vessel-days to be traded between patches.
 A closure in Patch 1 lowers the value of vessel-days in that patch.
-Vessel-days in patches 2 - 9 are now worth more causing vessel-days from Patch 1 to be traded to Patches 2 - 9.
+Vessel-days in patches 2 - 9 are worth more causing vessel-days from Patch 1 to be sold to Patches 2 - 9.
 Trading continues until vessel-day prices are the same across all patches (Fig.
@@
 \ref{fig:PNA_model}).
-Overall, we find that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+This means that between 88\% and 99\% of the costs can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
 
-To analyze the consequences of different allocation rules on conservation incentives, we simulate an annual allocation that is a weighted function of historical fishing in a country and historical fish biomass in a country.
-If allocation rules are based only on the historical effort in a country, then trading vessel-days to other countries would imply a future reduction in allocation.
+A second concern about spatial closures in fishing effort markets is that of the re-allocation rules and their implications for costs and long-term sustainability of the reserves.
+If re-allocation depends on the historical patch-level effort, trading vessel-days to other countries would imply a reduction in allocations through time.
 We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
@@
 \ref{fig:allocation_cost_plot}).
-However, these costs are reduced as more weight is put on historical biomass.
-A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation for all reserve sizes and possible movement.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, the incentives for conservation are much greater.
+However, these costs are reduced as the weight on historical biomass is increased.
+A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
 
-We have shown that design features of a rights-based fisheries management system have enormous implications for the incentives a country faces to engage in large-scale conservation.
-Allowing trading of rights across countries, and re-allocating annual rights based on biological variables, not fishing pressure, can essentially eliminate the cost of conservation, even for very large reserves.
-We now move to an empirical setting where we combine vessel-tracking data and the implementation of one of the world's largest marine reserves to identify the effort displacement and likely costs of conservation.
+We have shown that rights-based fisheries management may reduce the costs of conservation if trading is allowed, and that the costs can be further reduced if the allocation of rights is based on biomass, rather than on effort.
+We now move to an empirical setting where we use the implementation of one of the world's largest MPAs (implemented in the PNA) and vessel-tracking data to identify the effort displacement and possible costs, as well as the behavioral responses of fishing vessels.
+We then combine our predictions and empirical results to provide likely outcomes of upcoming large-scale MPAs in the region.
 
-The Pacific island nation of Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
+Kiribati implemented the Phoenix Islands Protected Area in January, 2015 (Fig.
 \ref{fig:PNA_map}).
@@
 
-We use the tracking data to calculate the time that vessels spent within Kiribati and PNA waters (Figs.
+We use the tracking data to calculate the time that vessels spent within PNA waters (Figs.
 \ref{fig:all_PS_VDS_year}A-B).
-Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days historically allocated to Kiribati \cite{yeeting2018stabilising}.
+Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days allocated to Kiribati \cite{yeeting2018stabilising}.
 We find that displaced vessels fished 922 less days (a 10\% reduction) in Kiribati between 2014 and 2015, immediately after PIPA was implemented.
 For the same period, these vessels spent just 48 days less in PNA waters, suggesting that trading might have facilitated relocation of effort within PNA waters.
+
 On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
@@
 \ref{fig:all_PS_VDS_year}A).
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
-Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's waters.
+Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort applied to Kiribati.
 But does this result in losses to Kiribati?
@@
 \ref{fig:revenues}A).
-Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
-This increase and subsequent decrease in revenues matches the AIS patterns we observe for Kiribati in 2014 - 2016 (Fig.
-\ref{fig:all_PS_VDS_year}A), and observed AIS effort is a reliable predictor of government revenue across all PNA countries from 2008 to 2016 (Fig.
+We observe that Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
+This increase and subsequent decrease in revenues match the patterns we observe for Kiribati in 2014 - 2016 (Figs.
+\ref{fig:all_PS_VDS_year}A), and observed effort was a good predictor of revenue (Fig.
 \ref{fig:revenue_FFA_effort_GFW}).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
+Unless At the PNA-level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016, respectively (Fig.
 \ref{fig:total_PNA_revenues}).
 
-\textbf{We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface(Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels.These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
 \ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly \ref{fig:nino_plot} alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation.
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).}
+The number of cells with presence from both fleets and spatial correlation between fleets increase by a factor of four and three, respectively.
+Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton.
+We observe similar patterns when repplicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
 
-\textbf{We use multiple linear regression to measure the change in nine vessel-level measures for displaced and non-displaced vessels before and after the implementation of PIPA (Fig.
+We use multiple linear regression to measure the change in nine vessel-level measures for displaced and non-displaced vessels before and after the implementation of PIPA (Fig.
 \ref{fig:all_panels}; Table \ref{tab:main_DID})).
@@
 We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.}
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
 
-A new large-scale marine protected area is being proposed in the PNA.
 On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80\% of Palau's EEZ) to commercial fishing activities \cite{cimino_2019}, creating the 14\textsuperscript{th} largest protected area in the world (Fig.
+Starting in December 2020, this Act will close 500,000 Km\textsuperscript{2} (about 80\% of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world and effectively displacing all effort within its waters (Fig.
 \ref{fig:PNA_map}).
 As a PNA member, Palau receives 700 purse seine vessel-days each year.
-Their longline fishery is also managed under a vessel-day scheme, with 10,500 non-tradable vessel-days per year, which currently sell at about \$200 USD each (Fig.
+Their longline fishery is also managed under a vessel-day scheme, with 10,500 vessel-days per year (Fig.
 \ref{fig:PLW_GFW_ts}).
-What does an 80\% closure represent for Palau's revenue from access fees?
-AIS data (2012 - 2019) shows that PNMS would displace $65.6 \pm 0.08$\% and $82.2 \pm 0.08$\% of longline and purse seine activity (Figs.
-\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
-Palau may be able to reduce the cost of lost license revenue if purse seine vessel-days are traded with other PNA members.
-However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, which would lead to a decreased allocation through time.
-Palau, howver, might continue to sell purse seine vessel-days to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-Longline vessel days are currently not tradable, meaning that the price for longline vessel-days might decrease, leading to losses in profits.
+Unlike the purse seine vessel-days, longline vessel-days are not tradable across countries and are worth much less, at about \$200 USD each.
 
-Rights-based fisheries management can prevent fisheries collapse \cite{costello_2008}.
-Our work shows that properly designed rights-based fisheries markets can also allow and incentivize large-scale marine conservation.
-Successful implementation of large-scale Marine Protected Areas under effort markets depends on two key features: tradable fishing rights and a biomass-based allocation rule.
-Tradable fishing rights allow a country to capture the benefits of conservation, and a biomass-based allocation rule ensures that this conservation actions are rewarded in the long term.
+Analysis of vessel-tracking data revealed that longliners and purse seiners spent 56.2\% and 91.7\% of their time within PNMS (Fig.
+\ref{fig:plw_2018}).
+Our predictions and empirical analyses of PIPA suggest that Palau may be able to reduce the costs if purse seine vessel-days are traded with other PNA members or it continues to sell them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, suggesting that the allocation would decrease in time.
 
@@
 Plans to implement large-scale Marine Protected Areas must consider the opportunity costs that come with such interventions \cite{smith_2010}, and identify sustainable financing mechanisms that compensate losses and incentivize long-term marine conservation \cite{mallin_2019}.
+We show that by combining rights-based fisheries management, a market design that allows trading, and a biomass-based allocation rule, large-scale marine conservation can be incentivized by significantly reducing costs.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and modifying the re-allocation rule, they may become pioneers in effective large-scale marine conservation.
+By facilitating trade and modifying the re-allocation rule, they may become important leaders in effective marine conservation.
 
@@
 \includegraphics{img/PNA_model.pdf}
-\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
-Each line represents a possible value of stock movement ($\theta$; line color).
-The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and .
+\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery (vertical axis) as a function of reserve size ($R$; horizontal axis) and movement ($\theta$; line color).
 Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
-Costs avoided by trading are shown in (C).
-Dashed red line in (A) is a 1:1 line.
-Trading significantly reduces the costs of a conservation intervention in Patch 1.}
+Costs avoided by tradig are shown in (C).}
 \end{figure}
@@
 \includegraphics{img/allocation_cost_plot.pdf}
-\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules.
-Each line represents the revenue losses for a combination of allocation rules ($\alpha$; color) and movement ($\theta$; line type) for different reserve sizes ($R$; horizontal axis).
-An effort-based allocation and low movement values result in the highest costs.
-Cost can be minimized for all movement values if alloction is based on biomass.}
+\caption{\label{fig:allocation_cost_plot}Cost (vertical axis) of different allocation rules (line colors) as a function of reserve  size ($R$; horizontal axis) and movement ($\theta$; line type).
+Costs are shown for Patch 1 only.}
 \end{figure}
@@
 \caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
-Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
-A red line indicates the Kiribati EEZ.
-The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuar.
+Countries that belong to the PNA are shown in blue, while empty polygons indicate all others.
+A red line indicates the Kiribati EEZ, and a solid red polygon shows PIPA.
+A solid purple polygon shows PNMS.
 Land masses are shown in gray.
-Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
+Labels indicate ISO3 country codes (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
 \end{figure}
@@
 \includegraphics{img/all_PS_VDS_PNA_KIR_year.pdf}
-\caption{\label{fig:all_PS_VDS_year}AIS-derived annual vessel-days for Kiribati (A) and all Parties to the Nauru Agreement (PNA; B).
-Annual effort is broken down by displaced, non-displaced, and other vessels.
+\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for Kiribati (A) and all PNA countries (B) for displaced, non-displaced, and other vessels.
 The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days) and the PNA (45,000 days).
@@
 The same graph using absolute values is shown in \ref{fig:revenue_FFA_GFW_linear}.
-A graph showing reported revenues vs.
-observed effort is shown in \ref{fig:revenue_FFA_effort_GFW}.}
+A graph showing reported revenues and observed effort is shown in \ref{fig:revenue_FFA_effort_GFW}.}
 \end{figure}
@@
 \includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
-The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
-Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
+\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palaw during 2018 at a 0.5 degree resolution.
+The red polygon shows the Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.}
 \end{figure}
@@
 We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 opperate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
+Patches 1 - 9 opperate under a vessel-day schemePatches, and Patch 10 represents the high seas and other areas not managed under a VDS.
+The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually.
 The price of fish is $p$, and catchability is given by $q$.
@@
 Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season.
-In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
+In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$.
 The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
@@
 
-With $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
+With $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  (0, 1)$) and within-patch fish movement ($\theta$).
 Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
 
-Therefore, we can generalize the patch-level profit equation to:
+Therefore, profits from fishing in patches 2 - 10 are:
 
 $$
-\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
+\Pi_i(E_i,X_i) = pqE_iX_i\Omega_i-cE_i^\beta
 $$
@@
 
-\begin{equation}
+$$
 \pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
 \label{eqn:marginal_profit}
-\end{equation}
+$$
 
@@
 
-\begin{equation}
+$$
 E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
 \label{eqn:effort_hs}
-\end{equation}
+$$
 
@@
 		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
-		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_i}{\beta c} \\
-		E_i &= \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_1}{\beta c} \\
+		E_i &= \left(\frac{pqX_i\Omega_i - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
 	\end{split}
@@
 
-Equation \ref{eqn:demands} tells us patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
-A vessel-day scheme establishes a cap on total effort allowed.
-This means that fishing effort from Patches 1 - 9 must add up to this limit.
 Therefore, total allowable effort in the fishery is given by:
@@
 $$
-
-In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
 
@@
 
-We use the model above to run simulations under two market designs.
-We test the model across a range reserve sizes and movement parameters.The first scenario does not allow trading.
+We use the model above run three different simulations.
+We test the model across a range reserve sizes and movement parameters.
+We use to main scenarios.
+The first scenario does not allow trading.
 In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
@@
 We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and vds-managed effort is equally distributed across the 9 patches, this equiulibrium is the same as the first step above.
+Since a closure is not in effect, this equiulibrium is the same as the first step above.
 We then implement a spatial closure in patch 1.
@@
 This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn would modify the demand curves for each countruy (Eq \ref{eqn:demands}).
-We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
+This reduction in biomass in turn would modify the demand curves (Eq \ref{eqn:demands}).
+We therefore iterate this process until biomass stabilizes, therefore finding the system's equilibrium.
+Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in patch 1.
 
@@
 All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
-
-\subsubsection{Effort redistribution}
-
-We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to understand effort redistribution.
-Non-displaced vessels serve serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
+All analyses were performed in R version 3.5.1 \cite{rcore_2018}.
+Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
 
@@
 
-\subsubsection{Data and code availability}
-
-All analyses were performed in R version 3.5.3 \cite{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
-
 \clearpage
-
-\FloatBarrier
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 \includegraphics{img/nino_plot.png}
-\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
+\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Timeseries of NINO4 anomaly from January, 1980 to December, 2018.}
 \end{figure}
+
+\clearpage
+
+We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to understand effort redistribution.
+Non-displaced vessels serve serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
@@
 \caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas.
+Black lines show Exclusive Economic Zone (EEZ), red lines show existing Marine Protected Areas.
 Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
@@
 	\includegraphics{img/catches.pdf}
-	\caption{\label{fig:catches}\textbf{Financial indicators for PNA countries.
+	\caption{\label{fig:catches}Financial indicators for PNA countries.
 A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
-Vertical dashed line in both plots denotes implementation of PIPA.
-- NOT REFERENCED}}
+Vertical dashed line in both plots denotes implementation of PIPA.}
 \end{figure}
@@
 	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}\textbf{Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}}	
+	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}	
 \end{figure}
+
+\clearpage
 
@@
 \includegraphics{img/PLW_GFW_ts.pdf}
-\caption{\label{fig:PLW_GFW_ts}Time series of longline and purse seine fishing effort in Palau.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_ts_plot.pdf}
-\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the prposed PNMS boundaries.}
+\caption{\label{fig:PLW_GFW_ts}Timeseries of longline and purse seine fishing effort in Palaw.}
 \end{figure}

### 2019-05-30 docs/old_ms/Markets_Conservation_May23.tex
Added all files

--- 2019-05-30 docs/old_ms/Markets_Conservation_May21.tex
@@
 \begin{sciabstract}
-Will rights-based approaches to managing natural resources facilitate, or relegate large-scale conservation?
-We study this question in the context of large-scale marine protected areas, and ask whether a country who commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
-Indeed, this is a question island (and other) nations all over the world face as they consider whether, and how, to comply with various international commitments to massively expand marine protection.
-We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific, and vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or relegates conservation.
+Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
+We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
+Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with various international commitments to expand marine protection.
+We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
 The answer hinges critically on two design features of the rights-based fishery market.
-First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation.
-Instead, if trading is forbidden, countries are likely to suffer significant losses from conservation.
-Second, as rights are re-allocated between countries periodically, the re-allocation must depend only on biological features, and not on a country's past effort or catch.
-Otherwise, the reallocation acts as a punishment to the conserving country.
+First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
+Instead, if trading is forbidden, countries are likely to suffer losses from conservation.
+Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
+Otherwise, the allocation process acts as a punishment to the conserving country.
 Overall, these results show that seemingly innocuous design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
+With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
 \end{sciabstract}
@@
 What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from its borders?
-We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: The design of fishing rights.
+Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from within its borders?
+We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: the design of fishing rights.
 
-We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA), which is one of the most successful, profitable, and well-orchestrated international cartels from any sector of the economy.
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
 Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific Island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
-These waters collectively account for 14.5 million Km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack catches in the Western Central Pacific \cite{havice_2013}.
+These waters collectively account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
 
-In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits; this explains why international attention has focused there for targeted conservation efforts to help achieve the previously mentioned targets.
-But the PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, often exceeding 50\% of a country's revenue.
-A natural concern arises: Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be enormous, and may prevent it from engaging in any meaningful conservation.
+In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region.
+The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding 50\% of a country's annual revenue.
+A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
 Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
-We show how the rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
+We show how a rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
 
 We develop a 10-patch spatial bioeconomic model of a fishery operating under a vessel-day scheme (VDS), and where conservation is being considered.
+A VDS is a type of rights-based management approach used by the PNA where each country is given an allocation of vessel-days that can then be sold to fishing firms.
+A vessel-day for country $i$ gives a firm the right to have one vessel fish in country $i$'s EEZ for 24 hours.
 Patches 1 - 9 operate under a VDS and Patch 10 represents the high seas in open access.
-Patch 1 considers closing a portion of its waters ($R$, between 0 and 1).
+Patch 1 considers closing a portion of its waters as a reserve ($R$, between 0 and 1).
 There are a total of 45,000 vessel-days, equally distributed between the 9 VDS-managed patches.
-The fishery revenue to these patches is the product of within-patch vessel-days and vessel-day price.
-Fishing vessels decide to fish in each patch based on available biomass (\emph{i.e.} biomass not within a reserve), and are willing to pay a vessel-day price that equates to their marginal profits at the last unit of effort applied.
+The fishery revenue to each of these patches is the product of within-patch vessel-days and vessel-day price.
+Fishing vessels decide to fish in each patch based on available biomass (\emph{i.e.} biomass not within a reserve), and are willing to pay a vessel-day price that equates to the marginal profits of the last unit of effort applied.
 Total biomass is equally distributed across the 10 patches.
@@
 We test the implications of conservation under two market designs: one in which effort trading between countries is not allowed, and one where vessel-days can be traded between countries.
-On both cases we solve for the equilibrium vessel-day price and effort redistribution.
-We quantify the losses by comparing revenues from each scenario to a benchmark scenario without conservation.
+In both cases we solve for the equilibrium vessel-day price and effort redistribution.
+We quantify the losses by comparing revenues from each scenario to a benchmark scenario without any conservation action.
 The fishery is simulated for a range of reserve sizes and assumptions about within-patch stock movement.
-We then examine the role of vessel-day allocation rules, where periodic allocation is a weighted combination of historical within-patch effort and biomass.
-Finally, we use vessel-tracking data to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
-We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary, targeting an 80\% closure of its Exclusive Economic Zone \cite{cimino_2019}.
+The second market design feature we investigate is the allocation of rights.
+We vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
+Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
+\textbf{We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary, currently targeting an 80\% closure of its Exclusive Economic Zone \cite{cimino_2019}.}
 
 We begin by simulating a fishery where effort is not traded between countries.
-We find that a spatial closure in Patch 1 will always result in a loss in revenues (Fig.
+We find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
 \ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases.
+Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases, allowing vessels to harvest the stock within the remaining open area.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
@@
 \ref{fig:vessel_day_price_no_trading_plot}).
-When countries can not trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches.
+When countries cannot trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches (Figure S2 shows that the increase in revenue ranges from 0\% to 6\%).
 
 How would a different market design, where trading between countries is allowed, change these results?
-To answer this we simulate the same fishery, but now allow for vessel-days to be traded between patches.
+To answer this we simulate the exact same fishery, but now allow for vessel-days to be traded across patches.
 A closure in Patch 1 lowers the value of vessel-days in that patch.
-Vessel-days in patches 2 - 9 are worth more causing vessel-days from Patch 1 to be sold to Patches 2 - 9.
+Vessel-days in patches 2 - 9 are now worth more causing vessel-days from Patch 1 to be traded to Patches 2 - 9.
 Trading continues until vessel-day prices are the same across all patches (Fig.
@@
 \ref{fig:PNA_model}).
-This means that between 88\% and 99\% of the costs can be avoided if markets are designed to enable trading (Fig.
+This means that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
 
-A second concern about spatial closures in fishing effort markets is that of the re-allocation rules and their implications for costs and long-term sustainability of the reserves.
-If re-allocation depends on the historical patch-level effort, trading vessel-days to other countries would imply a reduction in allocations through time.
+A second concern about spatial closures in fishing effort markets is that of the allocation rules and their implications for costs and the long-term sustainability of the closures.
+If allocation rules updates based on the historical patch-level effort, then trading vessel-days to other countries would imply a future reduction in allocation.
 We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
@@
 We have shown that rights-based fisheries management may reduce the costs of conservation if trading is allowed, and that the costs can be further reduced if the allocation of rights is based on biomass, rather than on effort.
-We now move to an empirical setting where we use the implementation of one of the world's largest MPAs (implemented in the PNA) and vessel-tracking data to identify the effort displacement and possible costs, as well as the behavioral responses of fishing vessels.
-We then combine our predictions and empirical results to provide likely outcomes of upcoming large-scale MPAs in the region.
+We now move to an empirical setting where we use the implementation of one of the world's largest MPAs and vessel-tracking data to identify the effort displacement and possible costs of conservation.
+\textbf{We then combine our predictions and empirical results to predict the likely outcomes of upcoming large-scale MPAs in the region.}
 
-Kiribati implemented the Phoenix Islands Protected Area in January, 2015 (Fig.
+Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
 \ref{fig:PNA_map}).
@@
 \ref{fig:all_PS_VDS_year}A-B).
-Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days allocated to Kiribati \cite{yeeting2018stabilising}.
+Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days historically allocated to Kiribati \cite{yeeting2018stabilising}.
 We find that displaced vessels fished 922 less days (a 10\% reduction) in Kiribati between 2014 and 2015, immediately after PIPA was implemented.
@@
 \ref{fig:all_PS_VDS_year}A).
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
-Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort applied to Kiribati.
+Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's waters.
 But does this result in losses to Kiribati?
@@
 We observe that Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
-This increase and subsequent decrease in revenues match the patterns we observe for Kiribati in 2014 - 2016 (Figs.
-\ref{fig:all_PS_VDS_year}A), and observed effort was a good predictor of revenue (Fig.
+This increase and subsequent decrease in revenues matches the AIS patterns we observe for Kiribati in 2014 - 2016 (Fig.
+\ref{fig:all_PS_VDS_year}A), and observed AIS effort is a reliable predictor of government fishing license revenue across all PNA countries from 2008 to 2016 (Fig.
 \ref{fig:revenue_FFA_effort_GFW}).
-Unless At the PNA-level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016, respectively (Fig.
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
 \ref{fig:total_PNA_revenues}).
 
-We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels.These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels.
+These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
 \ref{fig:sp_corr}).
-The number of cells with presence from both fleets and spatial correlation between fleets increase by a factor of four and three, respectively.
+The number of cells with presence from both fleets and the spatial correlation between fleets increases by a factor of four and three, respectively.
 Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementaiton.
-We observe similar patterns when repplicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
+We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
 
@@
 
-On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 Km\textsuperscript{2} (about 80\% of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world and effectively displacing all effort within its waters (Fig.
+\textbf{On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
+Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80\% of Palau’s EEZ) to commercial fishing activities, creating the 14th largest protected area in the world (Fig.
 \ref{fig:PNA_map}).
@@
 \ref{fig:PLW_GFW_ts}).
-Unlike the purse seine vessel-days, longline vessel-days are not tradable across countries and are worth much less, at about \$200 USD each.
+Unlike the purse seine vessel-days, longline vessel-days are currently not tradable across countries and are worth much less, at about \$200 USD each.}
 
-Analysis of vessel-tracking data revealed that longliners and purse seiners spent 56.2\% and 91.7\% of their time within PNMS (Fig.
+\textbf{Analysis of vessel-tracking data revealed that longliners and purse seiners spent 56.2\% and 91.7\% of their time within PNMS (Fig.
 \ref{fig:plw_2018}).
-Our predictions and empirical analyses of PIPA suggest that Palau may be able to reduce the costs if purse seine vessel-days are traded with other PNA members or it continues to sell them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, suggesting that the allocation would decrease in time.
+Our predictions and empirical analyses of PIPA suggest that Palau may be able to reduce the cost of lost license revenue if purse seine vessel-days are traded with other PNA members or it continues to sell them to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
+However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, suggesting that the allocation would decrease over time.
+Further, the fact that longline vessel days are currently not tradable means that these losses will be larger than would be the case with trading.}
 
@@
 Plans to implement large-scale Marine Protected Areas must consider the opportunity costs that come with such interventions \cite{smith_2010}, and identify sustainable financing mechanisms that compensate losses and incentivize long-term marine conservation \cite{mallin_2019}.
-We show that by combining rights-based fisheries management, a market design that allows trading, and a biomass-based allocation rule, large-scale marine conservation can be incentivized by significantly reducing costs.
+We show that by combining rights-based fisheries management, a market design that allows trading, and a biomass-based allocation rule, large-scale marine conservation can be incentivized by eliminating the costs.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and modifying the re-allocation rule, they may become important leaders in effective marine conservation.
+By facilitating trade and modifying the re-allocation rule, they may become pioneers in effective large-scale marine conservation.
 
@@
 Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
-Costs avoided by tradig are shown in (C).}
+Costs avoided by trading are shown in (C).
+Dashed red line is a 45 degree line.}
 \end{figure}
@@
 \includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palaw during 2018 at a 0.5 degree resolution.
+\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
 The red polygon shows the Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.}

### 2019-05-30 docs/old_ms/Markets_Conservation_May28.tex
Added all files

--- 2019-05-30 docs/old_ms/Markets_Conservation_May23.tex
@@
 We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
-Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with various international commitments to expand marine protection.
+Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with international commitments to expand marine protection.
 We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
@@
 Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly innocuous design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
+Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
 With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
@@
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region.
-The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding 50\% of a country's annual revenue.
+The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
 A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
@@
 
-We develop a 10-patch spatial bioeconomic model of a fishery operating under a vessel-day scheme (VDS), and where conservation is being considered.
-A VDS is a type of rights-based management approach used by the PNA where each country is given an allocation of vessel-days that can then be sold to fishing firms.
-A vessel-day for country $i$ gives a firm the right to have one vessel fish in country $i$'s EEZ for 24 hours.
-Patches 1 - 9 operate under a VDS and Patch 10 represents the high seas in open access.
-Patch 1 considers closing a portion of its waters as a reserve ($R$, between 0 and 1).
-There are a total of 45,000 vessel-days, equally distributed between the 9 VDS-managed patches.
-The fishery revenue to each of these patches is the product of within-patch vessel-days and vessel-day price.
-Fishing vessels decide to fish in each patch based on available biomass (\emph{i.e.} biomass not within a reserve), and are willing to pay a vessel-day price that equates to the marginal profits of the last unit of effort applied.
-Total biomass is equally distributed across the 10 patches.
-The stock remains within each patch during the fishing season, but growth from escapement is equally distributed across the 10 patches.
+To mirror the strategies and spatial connections among the nine PNA countries and the high seas, we develop a 10-patch spatial bioeconomic model.
+The fishery in nine of the patches operates under a market-based system in which ``vessel days'' are capped, closely tracked, and may be traded across countries.
+This vessel-day scheme (VDS) is acutally used by the PNA; each country is given an allocation of vessel-days that can then be sold to fishing firms.
+A vessel-day owned by country $i$ entitles $i$ to lease that day to a fishing vessel, entitling it to fish in $i$'s EEZ for a 24 hour period.
+In our model, Patches 1 - 9 are countries that operate under a VDS (in which fishing days are limited) and Patch 10 represents the high seas, where fishing days are governed by economic conditions, not by the VDS.
 
-We test the implications of conservation under two market designs: one in which effort trading between countries is not allowed, and one where vessel-days can be traded between countries.
-In both cases we solve for the equilibrium vessel-day price and effort redistribution.
-We quantify the losses by comparing revenues from each scenario to a benchmark scenario without any conservation action.
-The fishery is simulated for a range of reserve sizes and assumptions about within-patch stock movement.
-The second market design feature we investigate is the allocation of rights.
-We vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
+While modeling the VDS market may be interesting in its own right, our primary purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
+To examine this, suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters as a marine reserve, in which no fishing is allowed.
+When Country 1 creates a reserve, several consequences may arise.
+Perhaps most obviously, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in $i$'s waters.
+Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
+For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
+The purpose of our model is to examine these consequences in detail, with a particular focus on how design features of the market affect Country 1's incentives to create the marine reserve.
+
+Not all market-based approaches to environmental management are created equal.
+A pervasive finding across a range of natural resources is that features of market design can have enormous implications for the market's functioning.
+In the context of fishery markets, two market design features stand out as important for a variety of outcomes, and we will show that they are pivotal in determining the incentives for large-scale marine conservation.
+The first design feature has to do with the trading of rights, and the second design feature concerns the allocation of rights.
+We examine the effects of large-scale conservation in Country 1 across a range of scenarios for trading and allocation of vessel day fishing rights across our nine model countries.
+In all cases we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock a that would be expected to occur in the market.
+We quantify the change in revenue to all PNA countries from large-scale conservation in Country 1, by comparing revenues from each scenario to a benchmark scenario without any conservation action.
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement.
+
+Why would trading and allocation rules affect the incentives for conservation by Country 1?
+Invoking reduction ad absurdum, consider the incentives for Country 1 to close 100\% of its waters.
+Such a closure would surely benefit the other countries through the increased abundance of fish.
+If Country 1 could sell its fishing rights, the other countries would likely buy them, and this could offset the foregone costs of fishing it its own waters.
+But if Country 1 was not allowed to sell its rights, then it would lose all of its fishing revenue.
+This provides the simple intuition for why allowing trading across countries is so critical to conservation incentives.
+The rules for how fishing rights are allocated across the nine countries are equally important.
+Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
+This would clearly disadvantage a conservation-minded country.
+
+In our bioeconomic model, we examine the implications of conservation under alternative market designs: with, and without trading, and under alternative allocation rules.
+To nest how the PNA allocates rights, we vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
 Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
-\textbf{We use the same data and insights from our model to hypothesize what might be the impacts of the proposed Palau National Marine Sanctuary, currently targeting an 80\% closure of its Exclusive Economic Zone \cite{cimino_2019}.}
 
-We begin by simulating a fishery where effort is not traded between countries.
-We find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+We begin by simulating a fishery where trading of fishing days across countries is forbidden.
+In that setting, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
 \ref{fig:PNA_model}A).
@@
 \ref{fig:PNA_model}).
-This means that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+Overall, we find that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
 
-A second concern about spatial closures in fishing effort markets is that of the allocation rules and their implications for costs and the long-term sustainability of the closures.
-If allocation rules updates based on the historical patch-level effort, then trading vessel-days to other countries would imply a future reduction in allocation.
+To analyze the consequences of different allocation rules on conservation incentives, we model an annual allocation that is a weighted function of historical fishing in a country and historical biomass of fish in a country.
+If allocation rules are based only on the historical effort in a country, then trading vessel-days to other countries would imply a future reduction in allocation.
 We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
@@
 A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
+This result implies that if allocation is based purely on the biological features of a stock (i.e.
+the biomass within a country's waters), and not on fishing effort, the incentives for conservation are much greater.
 
-We have shown that rights-based fisheries management may reduce the costs of conservation if trading is allowed, and that the costs can be further reduced if the allocation of rights is based on biomass, rather than on effort.
-We now move to an empirical setting where we use the implementation of one of the world's largest MPAs and vessel-tracking data to identify the effort displacement and possible costs of conservation.
-\textbf{We then combine our predictions and empirical results to predict the likely outcomes of upcoming large-scale MPAs in the region.}
+We have shown that design features of a rights-based fisheries management system have enormous implications for the incentives a country faces to engage in large-scale conservation.
+Allowing tradeing of rights across countries, and re-allocating rights annual based on biological variables, not fishing pressure, can essentially eliminate the cost of conservation - even for very large reserves.
+We now move to an empirical setting where we combine vessel-tracking data and the implementation of one of the world's largest marine reserves to identify the effort displacement and likely costs of conservation.
 
-Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
+The Pacific island nation of Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
 \ref{fig:PNA_map}).
@@
 The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
+
+COSTELLO STOPPED HERE
 

### 2019-05-30 docs/old_ms/PIPA_Palau022819.tex
Added all files

--- 2019-03-01 docs/PIPA_Palau022819.tex
@@
 We do not observe a statistically significant increase in fishing hours on the high seas.
-
-The fact that the amount of time that vessels spent at sea (fishing and non-fishing) did not decrease, and that their time spent in Kiribati and PNA waters decreases suggests that these vessels have re-distributed elsewhere.
-This is consistent with the eventual decrease in crowding meassures.
+This suggests that treated vessels are fishing less overall and this decrease is driven by a decline in fishing within PNA waters.
+In summary, vessels that used to fish in PIPA are now fishing less in both Kiribati and the PNA region.
+Vessels that did not use to fish in PIPA are fishing more in Kiribati and PNA waters.
 
@@
 
-The crowding effect combined with the reduction of hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy access fees from PNA countries.
-To quantify the potential impacts of this leakage, we estimate the total annual vessel-days received by all PNA countries by each group of vessels (Fig.
+The crowding effect combined with the reduction in hours spent in Kiribati and PNA waters overall suggests that treated vessels have redistributed elsewhere, meaning that they no longer buy VDS from PNA countries.
+To quantify the potential impacts of this leakage, we estimate the total annual Vessel-Days received by all PNA countries by each group of vessels (Fig.
 \ref{fig:all_PS_VDS_year}).
 In this case we look at all 313 vessels, but continue to group them as treated (n = 64) and control (n = 28) vessels, as well as other vessels (n = 221).
-We find that the treated vessels spent 2,310 less days in PNA waters when comparing their values for 2015 and 2016, while control and other vessels increased their activities in PNA waters by 5,489 and 4,447 days for the same period, respectively (Fig.
+We find that the treated vessels spent 2,310 less days in Kiribati waters when comparing their values for 2015 and 2016 (Fig.
 \ref{fig:included_PS_VDS_year_DiD}).
-The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD at an average price of \$12,000 USD per vessel-day.
-Looking at the total anual vessel-days allocated by all vessels to all countries, we see that the largest reductions ocurr for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
+The 2,310 vessel-day reduction by treated vessels corresponds to \$27.7 million USD if we use an average price of \$12,000 USD per vessel-day.\footnote{The Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report states that ``Days are currently selling in a range between \$9,000 and \$13,000.''} Looking at the total annual vessel-days allocated by all vessels to all countries, we see that the largest reductions occur for Kiribati, while Papua New Guinea exhibits a proportional increase (Fig.
 \ref{fig:all_PS_VDS_cty_year}).
-Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allcoation to PNA waters at just 10,026 vessel-days.
-This is 2,526 vessel-days lower (\~\$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
+Furthermore, in 2017 treated vessels exhibit the lowest vessel-day allocation to PNA waters at just 10,026 vessel-days.
+This is 2,526 vessel-days lower (approximately \$30.3 million USD) than pre-implementation levels of 2012 - 2013 (mean $\pm$ sd of 12,552.46 $\pm$ 1,396.46; we exclude 2014 due to the blue paradox effect \cite{mcdermott_2018}).
 % Do you think we need to come up with an identification strategy for this?.
@@
 	\includegraphics{img/all_PS_VDS_year.pdf}
-	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all countries by treated, control, and excluded vessels.}
+	\caption{\label{fig:all_PS_VDS_year}Observed vessel-days for all PNA countries by treated, control, and excluded vessels.}
 \end{figure}
@@
 	\includegraphics{img/included_PS_VDS_year_DiD.pdf}
-	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by group of vessels.}
+	\caption{\label{fig:included_PS_VDS_year_DiD}Vessel days spent inside A) PNA waters and B) Kiribati waters by vessel group.}
 \end{figure}
 
-We compliment our analysis of change in observed vessel-days by looking at country-level data.
+We complement our analysis of change in observed vessel-days by looking at country-level data.
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees are reported for each country (2008 - 2016; Fig.
@@
 \ref{fig:revenues}B).
-To estimate what would have been the total revenue to PNA members, we use a local polynomial regression fit to obtain a trend line for the total revenues between 2008 and 2015, and extrapolate the trend to obtain an expected value for 2016.
-Our model suggests that total revenues to all PNA members in 2016 should be in the order of \$463.5 million USD, but the FFA data show only \$423.5 million, suggesting that potential losses to the entire PNA are in the order of \$40 million USD.
 
@@
 	\includegraphics{img/revenues.pdf}
-	\caption{\label{fig:revenues}Financial indicators for PNA countries.
-A) Revenue from fishing licenses fees, B) Total annual revenues for all 9 PNA countries with dashed line showing the local polynomial regression fit to the 2008 - 2015 data and the red dot representing the prediction from this regression.
-Vertical dashed line in both plots denotes implementation of PIPA.}
+	\caption{\label{fig:revenues}
+		License revenue for PNA countries.
+A) Annual revenue from fishing license fees by country and year (2008 - 2016) B) The natural lof of FFA-reported revenues vs.
+the natural log of revenues inferred from vessel activity observations (2012 - 2016).
+The dashed line represents line of best fit, solid line represents 1:1 line.
+The same graph using absolute values is shown in the Appendix.}
 \end{figure}
 
-Catches for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
+Catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
 \ref{fig:catches}).
 Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federal States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of Kiribati) showed a 22.3\% increase in catches over the same period.
+Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
+In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in catch over the same period.
 
@@
 Our findings provide insights into the effect that LSMPAs can have on vessel behavior and the redistribution of fishing effort.
-We find a short-term crowding effect after the implementation of the protected area.
-Behavioral analysis shows that the implementation of PIPA had little effect on the total fishing effort exerted by purse seiners.
-This, combined with our analysis of crowding effects that eventually return to pre-implementation levels, suggests that vessels redistribute elsewhere.
-Our analysis suggests that vessels that fish elsewhere represent a loss in profits of around \$27.7 million USD to Kiribati.
+We find a crowding effect after the implementation of the protected area.
+Our analysis shows that the implementation of PIPA had little effect on the \emph{total} fishing effort exerted by purse seiners.
+But there is considerable redistribution of effort across space and within the fleet of purse seiners.
+Surprisingly, there is no drop off in fishing effort in Kiribati in 2015 but a noticeable drop from 2016 onwards.
+Our analysis suggests that vessels that fish elsewhere represent a loss in revenues of around \$27.7 million USD to Kiribati.
 A thought experiment for Palau's Marine Sanctuary suggests losses in profits of up to \$11 million USD.
-Here, we discuss the implications of our findings and possible shortcommings in our analyses.
+Here, we discuss the implications of our findings and possible shortcomings in our analysis.
 
@@
 
-A major shortcoming of our analysis is that we do not observe catches or revenues at he vessel level, which ultimately are the factors that guide the decision making process of profit-maximizing agents.
+A major shortcoming of our analysis is that we do not observe catch or revenue at the vessel level, which ultimately are the factors that guide the decision-making process of profit-maximizing agents.
 Therefore, it is difficult to know whether the small change in fishing hours and redistribution represents a positive or negative impact.
+
+\begin{comment}
 An additional factor that we are yet to test is the change in non-fishing hours spent at sea.
@@
 However, the widespread footprint of the treated fleet may suggest that they are well acquainted with the region (see Figure \ref{fig:fishing_raster}), and it's unlikely that they would need to invest much time to identify new fishing grounds.
+\end{comment}
 
 A growing body of literature suggests that closing the high seas to all fishing could increase fishery yields and profitability of fisheries, with negligible costs to food security \citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}.
-Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in large losses to countries.
-We also show that spatial closures lead to short-term crowding effects, which causes vessels to redistribute to areas close by.
-Such management interventions should consider how fishing effort will change in space and through time, and the ecological implications of this redistribution to ensure that fishing effort is not just displaced elsewhere.
-While LSMPAs can provide a wide range of benefits, their implementation must be accompained with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable mechanisms that would compensate losses and incentivize marine conservation.
+Our work suggests that the implementation of LSMPAs has little impact on total fishing effort, but that it may result in losses to countries that have been receiving revenue from granting fishing access.
+We also show that spatial closures lead to crowding effects, which causes some vessels to redistribute to areas close by.
+While LSMPAs can provide a wide range of benefits, their implementation must be accompanied with traditional fisheries management to maximize effectiveness, consider the opportunity costs of such closure, and identify sustainable financing mechanisms that would compensate losses and incentivize marine conservation.
 
@@
 These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer what type and location of fishing events \citep{kroodsma_2018}.
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \citep{kroodsma_2018}.
+
+The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
+The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
+This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
+The addition of new satellites affects all vessels in the same way.
 
@@
 
-If the implementation of the reserve induces a crowding effect, we would expect to observe no trend before the implementation of the reserve.
-The implementation would lead to an increase in these measures, which,  if vessels avoid crowding, should then come back down.
-We therefore expect to have three inflection points: 1) in the transition between no trend and initial crowding due to MPA implementation, 2) When the crowding has reached its maximum and starts to decrease, and 3) when the decrease levels off, pressumably to pre-MPA levels.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1, and Feb of 2015 would receive a value of 1.
-
-\begin{figure}
+\begin{figure}[H]
 	\begin{align}
@@
 
+We test for a crowding effect using the specification in Equation [\ref{eqn:sp_corr}]. We have two different outcome variables:
+1) the number of cells that had fishing activity from treated and control vessels for each month and 2) the correlation of presence/absence of fishing events between both groups over one month. 
+We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
+Note that we restrict the sample to our treated and control vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+
 \subsubsection{Behavioral changes}
 
-We then focus on identifying the response of vessels to the PIPA closure.
+We attempt to identify the response of vessels to the PIPA closure.
 We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port(km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing and non-fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
 We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
+
 Our main specification is the following:
@@
 
-Information about FFA reports here
+We obtained information on license fee revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
+For countries in the PNA, we assume that all license fee revenue is coming from the sale of VDS.
 
@@
 
-\input{tab/main_DID}
+\input{tab/sp_corr}
 
@@
 
-\input{tab/sp_corr}
+\input{tab/main_DID}
 
@@
 Countries that belong to the PNA are shown in blue, while empty polygons indicates all others.
-A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.}
+A red line indicates the Kiribati EEZ, and a solid red polygon delineates PIPA.
+Land masses are shown in gray.}
 \end{figure}
@@
 \includegraphics{img/all_panels.pdf}
-\caption{\label{fig:all_panels}Time series showing monthly averages for eight variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, I) Monthly hours spent in Kiribati waters, J) Proportion of fishing hours spent in PNA waters.}
+\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing evetns, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
+Dashed vertical lines indicate the addition of new AIS satellites.
+Solid vertical line indicates the closure of PIPA.}
 \end{figure}
@@
 	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for treated vessels where the unit of observation is an individual vessel.}
+
+	\begin{comment}
+	I would drop 2012 and 2013 and restrict 2014 to post-satellite.
+	\end{comment}
+
 \end{figure}
@@
 Red polygons show LSMPAs in the region.}
-\end{figure}
 
-\clearpage
+\begin{comment}
+Eventually we need to make a figure that shows treated minus control effort and maybe just compare 2013 with 2017 (or 2012-2014 average with 2015-2018 average).
+\end{comment}
 
-\section{Palau National Marine Sanctuary}\label{PNMS}
-
-\begin{figure}
-	\includegraphics[width=0.8\textwidth]{img/Color_V1.png}
-	\caption{Map of the Four Protected Areas}
-	\label{fig:maps}
 \end{figure}
@@
 \section{Alternative Controls}
+
+\begin{comment}
+Need to update the captions on all the tables that follow, especially number of outcome variables, names of outcome variables, and heteroskedasticity.
+\end{comment}
+
 \subsection{Excluding all Chinese vessels}
@@
 \clearpage
-
-\section{Additional methods}
-
-This section is divided into two main parts.
-First, we provide a general description of AIS data and the process of identification of vessel-level fishing events performed by Global Fishing Watch.\footnote{Global Fishing Watch: \url{globalfishingwatch.org}} Alongside, we describe the subset of data used in our analysis.
-We also point out possible shortcomings in the data, or factors that must be considered in the analysis.
-We then move on to explain our empirical strategy for the identification of behavioral changes and the redistribution of fishing effort.
-
-\subsection{Data}
-
-The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels.
-The addition of new satellites affects all vessels in the same way.
-
-\input{tab/baci_n_s}
 

### 2019-05-30 docs/slides/GainesLab_presentation.Rmd
Added all files

@@
 
+## Motivation
+
+```{r, out.width = "250px"}
+knitr::include_graphics("../img/PNA_map.png")
+```
+
 # Scope and Approach
@@
 
-- 10-patch model of the tuna purse-seine fishery
+- 10-patch spatial bioeconomic model of the tuna fishery
 
@@
 
-$$\pi_i(E_i) = pqX_i\Omega_i- \beta cE_i^{\beta-1}$$
+$$\pi_i = pqX_i\Omega_i- \beta cE_i^{\beta-1}$$
 
@@
 
-```{r}
+```{r, out.height = "200px"}
 knitr::include_graphics(here("docs", "slides", "img", "cost_no_trading.png"))
@@
 
-```{r}
+```{r, out.height = "200px"}
 knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading_long_axis.png"))
@@
 
-```{r}
+```{r, out.height = "200px"}
 knitr::include_graphics(here("docs", "slides", "img", "cost_with_trading.png"))
@@
 
-## Likely costs to Palau
+## Likely costs to Palau (2018)
 

### 2019-05-30 docs/tab/DID_without_PNA.tex
Added all files

--- 2019-02-26 docs/tab/DID_without_PNA.tex
@@
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters.
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 9 variables of interest after removing PNA vessels: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
 Numbers in parentheses are heteroskedastic-robust standard errors.}
@@
 \footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
 \hline \\[-1.8ex] 
- Constant & 2.637$^{***}$ & 3.247$^{***}$ & 0.404$^{***}$ & 5.016$^{***}$ & 13.177$^{***}$ & 12.684$^{***}$ & 3.259$^{***}$ & 4.096$^{***}$ \\ 
-  & (0.042) & (0.021) & (0.011) & (0.044) & (0.028) & (0.025) & (0.270) & (0.206) \\ 
-  & & & & & & & & \\ 
- Post & 0.283$^{***}$ & $-$0.443$^{***}$ & 0.048$^{***}$ & 0.628$^{***}$ & 0.164$^{***}$ & 0.077$^{***}$ & 1.347$^{***}$ & 1.586$^{***}$ \\ 
-  & (0.039) & (0.021) & (0.011) & (0.044) & (0.024) & (0.022) & (0.234) & (0.188) \\ 
-  & & & & & & & & \\ 
- Treated & $-$0.091$^{**}$ & $-$0.051$^{***}$ & $-$0.052$^{***}$ & 0.683$^{***}$ & 0.137$^{***}$ & $-$0.020 & 0.697$^{***}$ & 0.477$^{***}$ \\ 
-  & (0.040) & (0.019) & (0.011) & (0.041) & (0.024) & (0.022) & (0.233) & (0.184) \\ 
-  & & & & & & & & \\ 
- Post $\times$ Treated & 0.081$^{*}$ & 0.021 & 0.055$^{***}$ & $-$0.880$^{***}$ & $-$0.153$^{***}$ & 0.017 & $-$0.691$^{***}$ & $-$0.706$^{***}$ \\ 
-  & (0.042) & (0.023) & (0.011) & (0.046) & (0.027) & (0.024) & (0.251) & (0.202) \\ 
-  & & & & & & & & \\ 
+ Constant & 0.512$^{***}$ & 3.559$^{***}$ & 0.083$^{***}$ & 4.499$^{***}$ & 13.165$^{***}$ & 12.667$^{***}$ & 3.271$^{***}$ & 4.066$^{***}$ & 2.876$^{***}$ \\ 
+  & (0.024) & (0.013) & (0.004) & (0.047) & (0.028) & (0.025) & (0.263) & (0.201) & (0.434) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.781$^{***}$ & $-$0.159$^{***}$ & 0.122$^{***}$ & 0.047 & 0.114$^{***}$ & 0.070$^{***}$ & 1.168$^{***}$ & 1.481$^{***}$ & 0.295 \\ 
+  & (0.022) & (0.012) & (0.004) & (0.043) & (0.023) & (0.022) & (0.226) & (0.180) & (0.333) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.202$^{***}$ & 0.040$^{***}$ & 0.019$^{***}$ & 0.437$^{***}$ & 0.165$^{***}$ & $-$0.015 & 0.817$^{***}$ & 0.533$^{***}$ & $-$0.408$^{*}$ \\ 
+  & (0.015) & (0.009) & (0.003) & (0.037) & (0.024) & (0.022) & (0.229) & (0.182) & (0.235) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.019 & $-$0.0003 & $-$0.002 & $-$0.387$^{***}$ & 0.138$^{***}$ & 0.025$^{***}$ & 0.413$^{***}$ & 0.232$^{***}$ & 0.482$^{***}$ \\ 
+  & (0.012) & (0.006) & (0.002) & (0.020) & (0.010) & (0.009) & (0.080) & (0.066) & (0.156) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.219$^{***}$ & $-$0.055$^{***}$ & $-$0.023$^{***}$ & $-$0.246$^{***}$ & $-$0.175$^{***}$ & 0.010 & $-$0.843$^{***}$ & $-$0.821$^{***}$ & 0.729$^{**}$ \\ 
+  & (0.024) & (0.012) & (0.004) & (0.046) & (0.026) & (0.024) & (0.243) & (0.195) & (0.341) \\ 
+  & & & & & & & & & \\ 
 \hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 19,971 & 42,555 & 19,971 & 43,068 & 19,971 & 19,971 & 1,207 & 1,696 \\ 
-R$^{2}$ & 0.064 & 0.097 & 0.066 & 0.032 & 0.059 & 0.071 & 0.133 & 0.217 \\ 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 64,560 & 64,560 & 64,559 & 64,625 & 22,654 & 22,654 & 1,366 & 1,928 & 511 \\ 
+R$^{2}$ & 0.093 & 0.069 & 0.099 & 0.022 & 0.063 & 0.066 & 0.127 & 0.203 & 0.214 \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 

### 2019-06-24 docs/Markets_Conservation.tex
Ready for submission as a Report

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

\usepackage{times}

% Packages I manually added
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{float}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{pdflscape}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% Include your paper's title here

\title{Well-Designed Fishery Markets Enable Large-Scale Marine Conservation}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author{Juan Carlos Villase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
\\
\normalsize{$^{1}$Bren School of Environmental Science \& Management,}\\
\normalsize{University of California at Santa Barbara, Santa Barbara, CA}\\
\normalsize{$^{2}$Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail: juancarlos@ucsb.edu.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.
\begin{sciabstract}
Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation? We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery revenue. We use a combination of spatial bioeconomic modeling and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation. The answer hinges on two design features. First, only when trading of rights is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions. Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch. Otherwise, the allocation process acts as a punishment to the conserving country. Overall, these results show that seemingly innocuous design features of a fishery management system can have indelible impacts on a country's willingness to engage in large-scale conservation. Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves. With the right market design, countries may be able to meet international conservation goals without incurring large costs.
\end{sciabstract}

Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}. Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}. To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}. What incentives might motivate a country to engage in such large-scale marine protection? Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?

This is not just a theoretical curiosity; we are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA). Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}. These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}. In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}. Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP. Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in conservation. We show how a rights-based fisheries market can be designed or modified  to ensure that the conserving country is rewarded, not punished, for large-scale conservation.

Not all market-based approaches to environmental management are created equal. A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}. In the context of fishery markets, we find that two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation. But why would trading and allocation rules affect the incentives for conservation? Consider the incentives for a country to close 100\% of its waters. Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries. If the conserving country could sell the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters. But if the conserving country was not allowed to sell these rights, then it would lose all of its fishing revenue. The rules for how fishing rights are allocated across countries are equally important. Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year. This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.

To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas. Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked. Patch 10 represents the high seas, where fishing days are governed by economic conditions. We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries. In all cases, we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market. We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action. We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see Supplementary Materials).

A spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 if trading between countries is not allowed (Fig. 1A). Closing a greater proportion of the patch results in greater costs. Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1. The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues. Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig. S1). When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig. S2) and the high seas.

How would trading between countries change these results? We simulate the same fishery, but now allow for vessel-days to be traded across patches. As before, a closure in Patch 1 lowers the value of vessel-days in that patch. But increased biomass in other patches causes prices in Patches 2 to 8 to increase. As a result, rights from Patch 1 are traded to Patches 2 to 9, until vessel-day prices are the same across all patches (Fig. S3). Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig. 1). Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig. 1C).

However, a new problem arises. How should rights be re-allocated every year? To analyze the consequences of different allocation rules on conservation incentives, we simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass. We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures. We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig. 2). However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation. This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, countries may be incentivized to engage in large-scale marine conservation.

A recent LSMPA was implemented in PNA waters, providing the ideal empirical setting to test our predictions. In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}. We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation. Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters. The remaining 221 vessels were not continuously observed before and after but are included in our analyses, and we refer to these as ``other vessels''.

How did PIPA change fishing locations of vessels? Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig. S6). Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs. 3A-B).  The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters. On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014. The same pattern is observed at the PNA level, with non-displaced and other vessels spending an additional 3,789 and 3,691 vessel-days, respectively. By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Fig. 3A). Detailed analyses of vessel-level behavioral changes and crowding effects associated with PIPA implementation are included in our Supplementary Materials (Figs. S6, S7, S9; and Tables S5 and S1).

As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses. Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig. 3C).
The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig. 3C-D). But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%). This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig. S4). At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. S13), despite the PIPA closure.

Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA. In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig. 4). Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline (10,500 non-tradable vessel-days) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine (700 tradable vessel-days) fishing activity (Figs. S15 and S16). While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security. The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}. By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation.

International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}. Our results show that a few key design features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation. Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.

\bibliography{references}

\bibliographystyle{Science}

\clearpage

\FloatBarrier

% PNA model output for costs
\begin{figure}[htbp]
\centering
\includegraphics{img/PNA_model.pdf}
\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery. Each line represents a possible value of stock movement ($\theta$; line color). The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color). Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B). Costs avoided by trading are shown in (C). Dashed red line in (A) is a 1:1 line.}
\end{figure}

% Costs of different allocation rules
\begin{figure}[htbp]
\centering
\includegraphics{img/allocation_cost_plot.pdf}
\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules. Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis). An effort-based allocation and low movement values result in the highest costs. Cost can be minimized for all movement values if allocation is based on biomass.}
\end{figure}

% Effort redistribution bars for PNA and KIR
\begin{figure}[htbp]
\centering
\includegraphics{img/empirical.pdf}
\caption{\label{fig:empirical}Effort displacement and license revenues. Pannels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA). Annual effort is broken down by displaced, non-displaced, and other vessels. The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days). Pannel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and pannel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016). The dashed line represents line of best fit.}
\end{figure}

% Map of LSMPAS in PNA
\begin{figure}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest. Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others. A red line indicates the Kiribati EEZ. The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary. Land masses are shown in gray. Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
\end{figure}

\end{document}

### 2019-06-24 docs/Markets_Conservation_June19.tex
Ready for submission as a Report

--- 2019-05-30 docs/Markets_Conservation_May30.tex
@@
 Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
-Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with international commitments to expand Marine Protected Area (MPA) coverage.
-We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and spatially-explicit vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
-The answer hinges critically on two design features of the rights-based fishery market.
-First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Instead, if trading is forbidden, countries are likely to suffer losses from conservation.
+We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery revenue.
+We use a combination of spatial bioeconomic modeling and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation.
+The answer hinges on two design features.
+First, only when trading of rights is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
 Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
 Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
+Overall, these results show that seemingly innocuous design features of a fishery management system can have indelible impacts on a country's willingness to engage in large-scale conservation.
+Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
+With the right market design, countries may be able to meet international conservation goals without incurring large costs.
 \end{sciabstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
+Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}.
+What incentives might motivate a country to engage in such large-scale marine protection?
+Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
 
-%%%% Other titles %%%%%%%%%%%%
-% Fishery markets enable marine conservation
-% Designing environmental markets for marine conservation
-% Large-scale marine conservation is enabled by market instruments
-% Rights-based management to promote marine conservation
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
-Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%, 30\%, or even up to 50\% of the ocean to be off-limits to fishing.
-Fundamentally, to achieve these goals, huge swaths of sovereign nations' waters will have to be closed to fishing.
-What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from within its borders?
-We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: the design of fishing rights.
-
-We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific Island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
-These waters collectively account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack tuna catches in the Western Central Pacific \cite{havice_2013}.
-
-In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
-A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
-Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
-We show how a rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
-
-To mirror the strategies and spatial connections among the nine PNA countries and the high seas, we develop a 10-patch spatial bioeconomic model.
-The fishery in nine of the patches operates under a market-based system in which ``vessel days'' are capped, closely tracked, and may be traded across countries.
-This vessel-day scheme (VDS) is actually used by the PNA; each country is given an allocation of vessel-days that can then be sold to fishing firms.
-A vessel-day owned by country $i$ entitles $i$ to lease that day to a fishing vessel, entitling it to fish in $i$'s EEZ for a 24 hour period.
-In our model, Patches 1 - 9 are countries that operate under a VDS (in which fishing days are limited) and Patch 10 represents the high seas, where fishing days are governed by economic conditions, not by the VDS.
-
-While modeling the VDS market may be interesting in its own right, our primary purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-To examine this, suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters as a marine reserve, in which no fishing is allowed.
-When Country 1 creates a reserve, several consequences may arise.
-Perhaps most obviously, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in $i$'s waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-The purpose of our model is to examine these consequences in detail, with a particular focus on how design features of the market affect Country 1's incentives to create the marine reserve.
+This is not just a theoretical curiosity; we are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
+Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
+These waters account for 14.5 million km\textsuperscript{2} (four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
+In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
+Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in conservation.
+We show how a rights-based fisheries market can be designed or modified  to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
 
 Not all market-based approaches to environmental management are created equal.
-A pervasive finding across a range of natural resources is that features of market design can have enormous implications for the market's functioning.
-In the context of fishery markets, two market design features stand out as important for a variety of outcomes, and we will show that they are pivotal in determining the incentives for large-scale marine conservation.
-The first design feature has to do with the trading of rights, and the second design feature concerns the allocation of rights.
-We examine the effects of large-scale conservation in Country 1 across a range of scenarios for trading and allocation of vessel day fishing rights across our nine model countries.
-In all cases we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
-We quantify the change in revenue to each PNA country from large-scale conservation in Country 1, by comparing revenues from each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement.
-
-Why would trading and allocation rules affect the incentives for conservation by Country 1?
-Invoking \emph{reductio ad absurdum}, consider the incentives for Country 1 to close 100\% of its waters.
-Such a closure would surely benefit the other countries through the increased abundance of fish.
-If Country 1 could sell its fishing rights, the other countries would likely buy them, and this could offset the foregone costs of fishing its own waters.
-But if Country 1 was not allowed to sell its rights, then it would lose all of its fishing revenue.
-This provides the simple intuition for why allowing trading across countries is so critical to conservation incentives.
-The rules for how fishing rights are allocated across the nine countries are equally important.
+A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}.
+In the context of fishery markets, we find that two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
+But why would trading and allocation rules affect the incentives for conservation?
+Consider the incentives for a country to close 100\% of its waters.
+Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries.
+If the conserving country could sell the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+But if the conserving country was not allowed to sell these rights, then it would lose all of its fishing revenue.
+The rules for how fishing rights are allocated across countries are equally important.
 Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
@@
 
-In our bioeconomic model, we examine the implications of conservation under alternative market designs: with, and without trading, and under alternative allocation rules.
-To test how the PNA allocates rights, we vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
-Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
+To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
+Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
+Patch 10 represents the high seas, where fishing days are governed by economic conditions.
+We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries.
+In all cases, we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
+We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see Supplementary Materials).
 
-We begin by simulating a fishery where trading of fishing days across countries is forbidden.
-In that setting, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+A spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 if trading between countries is not allowed (Fig.
 \ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases, allowing vessels to harvest the stock within the remaining open area.
+Closing a greater proportion of the patch results in greater costs.
+Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in Patch 1, which reduces a vessel's willingness to pay to fish in such waters (Fig.
+Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
 \ref{fig:vessel_day_price_no_trading_plot}).
-When countries cannot trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches (Figure S2 shows that the increase in revenue ranges from 0\% to 6\%).
+When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig.
+\ref{fig:profits_PNA_notKIR_no_trading_plot}) and the high seas.
 
-How would a different market design, where trading between countries is allowed, change these results?
-To answer this we simulate the exact same fishery, but now allow for vessel-days to be traded across patches.
-A closure in Patch 1 lowers the value of vessel-days in that patch.
-Vessel-days in patches 2 - 9 are now worth more causing vessel-days from Patch 1 to be traded to Patches 2 - 9.
-Trading continues until vessel-day prices are the same across all patches (Fig.
+How would trading between countries change these results?
+We simulate the same fishery, but now allow for vessel-days to be traded across patches.
+As before, a closure in Patch 1 lowers the value of vessel-days in that patch.
+But increased biomass in other patches causes prices in Patches 2 to 8 to increase.
+As a result, rights from Patch 1 are traded to Patches 2 to 9, until vessel-day prices are the same across all patches (Fig.
 \ref{fig:vessel_day_price_with_trading_plot}).
-Under this market design, we find that revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
+Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
 \ref{fig:PNA_model}).
-Overall, we find that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
 
-To analyze the consequences of different allocation rules on conservation incentives, we simulate an annual allocation that is a weighted function of historical fishing in a country and historical fish biomass in a country.
-If allocation rules are based only on the historical effort in a country, then trading vessel-days to other countries would imply a future reduction in allocation.
-We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
-We use a range of allocation rules to weight effort ($\alpha$) and biomass ($1 - \alpha$) and compare the revenues to a fishery operating for 50 years without any closures.
-We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in losses of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
+However, a new problem arises.
+How should rights be re-allocated every year?
+To analyze the consequences of different allocation rules on conservation incentives, we simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
+We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
+We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
 \ref{fig:allocation_cost_plot}).
-However, these costs are reduced as more weight is put on historical biomass.
-A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation for all reserve sizes and possible movement.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, the incentives for conservation are much greater.
+However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, countries may be incentivized to engage in large-scale marine conservation.
 
-We have shown that design features of a rights-based fisheries management system have enormous implications for the incentives a country faces to engage in large-scale conservation.
-Allowing trading of rights across countries, and re-allocating annual rights based on biological variables, not fishing pressure, can essentially eliminate the cost of conservation, even for very large reserves.
-We now move to an empirical setting where we combine vessel-tracking data and the implementation of one of the world's largest marine reserves to identify the effort displacement and likely costs of conservation.
+A recent LSMPA was implemented in PNA waters, providing the ideal empirical setting to test our predictions.
+In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
+The remaining 221 vessels were not continuously observed before and after, and we refer to these as ``other vessels''.
 
-The Pacific island nation of Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
+How did PIPA change vessel fishing locations?
+Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff}).
+Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
+\ref{fig:empirical}A-B).
+The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
+On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
+The same pattern is observed at the PNA level, with non-displaced and other vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
+By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Fig.
+\ref{fig:empirical}A).
+Detailed analyses of vessel-level behavioral changes and crowding effects associated with PIPA implementation are included in our Supplementary Materials (Figs.
+\ref{fig:fishing_raster_diff}, \ref{fig:sp_corr}, and \ref{fig:all_panels}; and Tables \ref{tab:sp_corr} and \ref{tab:main_DID}).
+
+As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses.
+Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
+\ref{fig:empirical}C).
+The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig. \ref{fig:empirical}C-D).
+But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
+This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig.
+\ref{fig:effort_and_revenues}).
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. \ref{fig:total_PNA_revenues}), despite the PIPA closure.
+
+Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA.
+In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
 \ref{fig:PNA_map}).
-With an extension of 397,447 Km\textsuperscript{2}, this 11.5\% closure effectively displaced all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
-We use identification of fishing activity via Automatic Identification Systems (AIS) provided by Global Fishing Watch to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018 \cite{kroodsma_2018}.
-We continuously observe 92 vessels for the 2012 - 2018 period.
-Of these, 64 vessels fished within PIPA at least once prior to its implementation, and we refer to them as the ``displaced vessels''.
-The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
-The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline (10,500 non-tradable vessel-days) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine (700 tradable vessel-days) fishing activity (Figs.
+\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
+While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
+The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation.
 
-We use the tracking data to calculate the time that vessels spent within Kiribati and PNA waters (Figs.
-\ref{fig:all_PS_VDS_year}A-B).
-Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days historically allocated to Kiribati \cite{yeeting2018stabilising}.
-We find that displaced vessels fished 922 less days (a 10\% reduction) in Kiribati between 2014 and 2015, immediately after PIPA was implemented.
-For the same period, these vessels spent just 48 days less in PNA waters, suggesting that trading might have facilitated relocation of effort within PNA waters.
-On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
-The same pattern is observed at the PNA level, with vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
-These changes result in a net decrease of fishing effort within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Figs.
-\ref{fig:all_PS_VDS_year}A).
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
-
-Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's waters.
-But does this result in losses to Kiribati?
-We do not explicitly observe trading between countries, but combining different sources of information we are able to paint a comprehensive picture.
-We use country-level fisheries revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) for the 2008 - 2016 period to complement our analysis (Fig.
-\ref{fig:revenues}A).
-Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
-This increase and subsequent decrease in revenues matches the AIS patterns we observe for Kiribati in 2014 - 2016 (Fig.
-\ref{fig:all_PS_VDS_year}A), and observed AIS effort is a reliable predictor of government revenue across all PNA countries from 2008 to 2016 (Fig.
-\ref{fig:revenue_FFA_effort_GFW}).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
-\ref{fig:total_PNA_revenues}).
-
-\textbf{We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface(Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly \ref{fig:nino_plot} alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation.
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).}
-
-\textbf{We use multiple linear regression to measure the change in nine vessel-level measures for displaced and non-displaced vessels before and after the implementation of PIPA (Fig.
-\ref{fig:all_panels}; Table \ref{tab:main_DID})).
-We find no evidence of displaced vessels fishing more after the implementation, and in fact observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$).
-Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$).
-Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.}
-
-A new large-scale marine protected area is being proposed in the PNA.
-On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80\% of Palau's EEZ) to commercial fishing activities \cite{cimino_2019}, creating the 14\textsuperscript{th} largest protected area in the world (Fig.
-\ref{fig:PNA_map}).
-As a PNA member, Palau receives 700 purse seine vessel-days each year.
-Their longline fishery is also managed under a vessel-day scheme, with 10,500 non-tradable vessel-days per year, which currently sell at about \$200 USD each (Fig.
-\ref{fig:PLW_GFW_ts}).
-What does an 80\% closure represent for Palau's revenue from access fees?
-AIS data (2012 - 2019) shows that PNMS would displace $65.6 \pm 0.08$\% and $82.2 \pm 0.08$\% of longline and purse seine activity (Figs.
-\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
-Palau may be able to reduce the cost of lost license revenue if purse seine vessel-days are traded with other PNA members.
-However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, which would lead to a decreased allocation through time.
-Palau, howver, might continue to sell purse seine vessel-days to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-Longline vessel days are currently not tradable, meaning that the price for longline vessel-days might decrease, leading to losses in profits.
-
-Rights-based fisheries management can prevent fisheries collapse \cite{costello_2008}.
-Our work shows that properly designed rights-based fisheries markets can also allow and incentivize large-scale marine conservation.
-Successful implementation of large-scale Marine Protected Areas under effort markets depends on two key features: tradable fishing rights and a biomass-based allocation rule.
-Tradable fishing rights allow a country to capture the benefits of conservation, and a biomass-based allocation rule ensures that this conservation actions are rewarded in the long term.
-
-International goals over the next decade have set ambitious targets for marine conservation.
-Plans to implement large-scale Marine Protected Areas must consider the opportunity costs that come with such interventions \cite{smith_2010}, and identify sustainable financing mechanisms that compensate losses and incentivize long-term marine conservation \cite{mallin_2019}.
-The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and modifying the re-allocation rule, they may become pioneers in effective large-scale marine conservation.
+International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}.
+Our results show that a few key design features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
+Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.
 
@@
 
-\section*{Figures and tables}
+\section*{Figures}
 
@@
 Each line represents a possible value of stock movement ($\theta$; line color).
-The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and .
+The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
 Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
 Costs avoided by trading are shown in (C).
-Dashed red line in (A) is a 1:1 line.
-Trading significantly reduces the costs of a conservation intervention in Patch 1.}
+Dashed red line in (A) is a 1:1 line.}
 \end{figure}
@@
 \caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules.
-Each line represents the revenue losses for a combination of allocation rules ($\alpha$; color) and movement ($\theta$; line type) for different reserve sizes ($R$; horizontal axis).
+Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis).
 An effort-based allocation and low movement values result in the highest costs.
-Cost can be minimized for all movement values if alloction is based on biomass.}
+Cost can be minimized for all movement values if allocation is based on biomass.}
+\end{figure}
+
+% Effort redistribution bars for PNA and KIR
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/empirical.pdf}
+\caption{\label{fig:empirical}Effort displacement and license revenues.
+Pannels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA).
+Annual effort is broken down by displaced, non-displaced, and other vessels.
+The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days).
+Pannel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and pannel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
+The dashed line represents line of best fit.}
 \end{figure}
@@
 A red line indicates the Kiribati EEZ.
-The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuar.
+The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary.
 Land masses are shown in gray.
 Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
-\end{figure}
-
-% Effort redistribution bars for PNA and KIR
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/all_PS_VDS_PNA_KIR_year.pdf}
-\caption{\label{fig:all_PS_VDS_year}AIS-derived annual vessel-days for Kiribati (A) and all Parties to the Nauru Agreement (PNA; B).
-Annual effort is broken down by displaced, non-displaced, and other vessels.
-The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days) and the PNA (45,000 days).
-Note that the reduction for Kiribati is driven by displaced vessels fishing less in Kiribati's waters, but that their decrease is not as sharp for all PNA waters.
-Vessels displaced from PIPA fish less within the PNA, but non-displaced and other vessels fish more, resulting in a net increase.}
-\end{figure}
-
-% Revenue data from FFA and GFW estimates.
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/revenues.pdf}
-\caption{\label{fig:revenues}
-License revenue for PNA countries.
-A) Annual revenue from fishing license fees by country and year (2008 - 2016) B) $log_{10}$-transformed FFA-reported revenues vs.
-the revenues inferred from vessel activity observations (2012 - 2016).
-The dashed line represents line of best fit, solid line represents 1:1 line.
-The same graph using absolute values is shown in \ref{fig:revenue_FFA_GFW_linear}.
-A graph showing reported revenues vs.
-observed effort is shown in \ref{fig:revenue_FFA_effort_GFW}.}
-\end{figure}
-
-% Palau Raster and PNMS
-\begin{figure}
-\centering
-\includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
-The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
-Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
 \end{figure}
@@
 We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 opperate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
+Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
 The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
@@
 These parameters are held constant across patches.
+
+Our purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
+Suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters to all fishing; several consequences may arise.
+First, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in these waters.
+Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
+For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
+We focus on how design features of the market affect Country 1's incentives to create the marine reserve.
 
@@
 Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season.
+Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
 In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
@@
 
-With $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
+\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
 Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
@@
 
-The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
+\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
 
 \begin{equation}
-\pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
+\pi_i(E_i) = \frac{\partial \Pi_i}{\partial E_i} = pqX_i\Omega_i - \beta cE_i^{\beta-1}
 \label{eqn:marginal_profit}
@@
 
-Under vds-operated patches, however, profits from marginal effort must equate the cost of fishing in the patch. Therefore vessel-day price for patches under vds ($i = (1, 9)$) is  given by:
+Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
+Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
 
 $$
-\pi(E_i) = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
+\pi_i = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
 $$
 
-We can solve for $E_i$ and obtain:
+\noindent We can solve for $E_i$ and obtain:
 
@@
 
-$$
+\begin{equation}
 \bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
 \label{eqn:Ebar}
-$$
+\end{equation}
 
-In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
+\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
 
@@
 
-$$
+\begin{equation}
 H_i = qE_iX_i\Omega_i
 \label{eqn:harvest}
-$$
+\end{equation}
 
-Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$.
+\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
 The entire stock then grows logistically according to:
 
-$$
+\begin{equation}
 X_{t+1} = e_t + e^{r \times \frac{e}{K}}
 \label{eqn:grow}
-$$
+\end{equation}
 
-Where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
-
+\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
 After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
 
-$$
-X_{it+1} = f_iX_{t+1}
+\begin{equation}
+X_{i,t+1} = f_iX_{t+1}
 \label{eqn:disperse}
-$$
+\end{equation}
 
@@
 
-$$
-\omega = \pi_iE_i
+\begin{equation}
+\omega_i = \pi_iE_i
 \label{eqn:license_revenue}
-$$
+\end{equation}
 
-Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
-But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
+\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
+This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
 Thus, the spillover benefits of increasing $R$ are never completely captured.
 
-\subsubsection{Simulations and parametrization}
+\subsubsection{Simulations and parameterization}
 
-We inform our model to losely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
+We calibrate our model to loosely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
 
@@
 
-We use the model above to run simulations under two market designs.
-We test the model across a range reserve sizes and movement parameters.The first scenario does not allow trading.
+\noindent We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
 In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
@@
 We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
-This produces a measure of the cost of implementing a spatial closure of size $R$ in patch 1.
+This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
 
@@
 We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and vds-managed effort is equally distributed across the 9 patches, this equiulibrium is the same as the first step above.
-We then implement a spatial closure in patch 1.
-This essentially lowers the price fishers would be willing to pay to fish in a patch with biomass $X_i\Omega_i$, lowering demand for vessel-days in pach 1.
-Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from patch 1 are sold to patches 2 - 9.
+Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
+We then implement a spatial closure in Patch 1.
+This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
+Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
 This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn would modify the demand curves for each countruy (Eq \ref{eqn:demands}).
+This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
 We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
@@
 
-\subsection{Allocation rules}
-
 Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, sixty percent of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
+In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
 The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
 
-In the second scenario above, effort from a patch with conservation is traded to other patches.
+In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
 This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
-After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time.
-At the end of every time, vessel-days are allocated to each patch based on the following rule:
+After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery forward 50 years in time.
+At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
 
 $$
-E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
-(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
+E_{i,t+1}^* = \alpha
+\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{E}_{{t-\tau}}}
+	\right)
+	+
+(1 - \alpha)
+\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{X}_{t-\tau}} \right)
 $$
 
-Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$).
-We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures.
-The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales.
-We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
+\noindent where $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight on historical biomass ($B_i$).
+We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
+The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
+We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
 
@@
 These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}
+GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
 
 The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014 , and then from 6 to 10 on January 1\textsuperscript{st} 2016.
+The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014, and then from 6 to 10 on January 1\textsuperscript{st} 2016.
 This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels and vessel activity.
@@
 
-\subsection{Analysis}
+\subsection{Empirical Analysis}
 
-ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+ENSO events are known to drive the location of fish and the behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
 We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
@@
 Our analyses incorporate the monthly NINO4 anomaly index (Fig.
-\ref{fig:nino_plot}) to control for the association that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-
-\subsubsection{Crowding effect}
-
-$$
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
-\label{eqn:sp_corr}
-$$
-
-We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
-The $\mu$ coefficient captures the effect of the NINO4 anomaly.
+\ref{fig:nino_plot}) to control for the responses that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
 
@@
 We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest.
+non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest (Figure \ref{fig:all_panels}).
 We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
@@
 
-\noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$ the transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ on period $t$.
+\noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$.
+The transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ in period $t$.
 A dummy variable $P_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
@@
 Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
+All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated (Table \ref{tab:main_DID}).
 
-All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
+We find no evidence of displaced vessels fishing more after the implementation and, in fact, observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$; Fig.
+\ref{fig:all_panels}; Table \ref{tab:main_DID}).
+Likewise, we observe a 3.4\% decrease in fishing hours relative to total at-sea hours ($p < 0.01$).
+Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
+These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
+We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
+
+\subsubsection{Crowding effect}
+
+\begin{equation}
+y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
+\label{eqn:sp_corr}
+\end{equation}
+
+We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
+1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
+For example, since PIPA was implemented on January 1\textsuperscript{st} of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
+Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
+The $\mu$ coefficient captures the effect of the NINO4 anomaly.
+
+We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface (Fig \ref{fig:fishing_raster_diff}).
+These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+\ref{fig:sp_corr}).
+The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
+Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation (Table \ref{tab:sp_corr}).
+We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
 
@@
 
-We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to understand effort redistribution.
-Non-displaced vessels serve serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshal Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
+We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
+Non-displaced vessels serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas (Fig \ref{fig:fishing_raster_diff}).
 
@@
 We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:revenues}A).
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency\footnote{https://www.ffa.int/node/2050} (FFA) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
+\ref{fig:empirical}A).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
@@
 \includegraphics{img/vessel_day_price_no_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
-\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) when there is no trading.}
+\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics{img/effort_and_revenues.pdf}
+	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-patch movement ($\theta$), and with and without trading.
+With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.
+The exact opposite relationship holds without trading: effort remains fixed as revenue declines with increasing $R$.}
 \end{figure}
@@
 Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
-\end{figure}
-
-\begin{landscape}
-\input{tab/sp_corr}
-\end{landscape}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
-\end{figure}
-
-\begin{landscape}
-\input{tab/KIR_sp_corr}
-\end{landscape}
-
-\begin{figure}
-\centering
-\includegraphics{img/KIR_sp_corr.pdf}
-\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
 \end{figure}
@@
 
+\begin{landscape}
+\input{tab/sp_corr}
+\end{landscape}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/sp_corr.pdf}
+\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
+\end{figure}
+
+\begin{landscape}
+\input{tab/KIR_sp_corr}
+\end{landscape}
+
+\begin{figure}
+\centering
+\includegraphics{img/KIR_sp_corr.pdf}
+\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
+The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
+Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
+\end{figure}
+
 \begin{figure}
@@
 \centering
-	\includegraphics{img/revenue_FFA_GFW_linear.pdf}
-	\caption{\label{fig:revenue_FFA_GFW_linear}Inferred revenues vs. reported revenues. The dashed line represents line of best fit, and the solid line represents a 1:1 line.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/revenue_FFA_effort_GFW.pdf}
-	\caption{\label{fig:revenue_FFA_effort_GFW}Observed fishing effort vs. reported revenues. The dashed line represents line of best fit.}
-\end{figure}
-
-\begin{figure}
-\centering
 	\includegraphics{img/total_PNA_revenues.pdf}
@@
 \centering
-	\includegraphics{img/yearly_distribution_prop_fishing_by_region.pdf}
-	\caption{\label{fig:yearly_distribution_prop_fishing_by_region}\textbf{Ridgeplot for the density of the \% of total fishing hours that take place in each region for all vessels}}	
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/PLW_GFW_ts.pdf}
-\caption{\label{fig:PLW_GFW_ts}Time series of longline and purse seine fishing effort in Palau.}
+\includegraphics{img/plw_2018.png}
+\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
+The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
+Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
 \end{figure}
@@
 \includegraphics{img/plw_ts_plot.pdf}
-\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the prposed PNMS boundaries.}
+\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the proposed PNMS boundaries.}
 \end{figure}

### 2019-06-24 docs/Supplementary_materials.tex
Ready for submission as a Report

--- 2019-06-24 docs/Markets_Conservation_June19.tex
@@
 
-\title{Fishery Markets and Large-Scale Marine Conservation}
+\title{Supplementary Materials for: ``Well-Designed Fishery Markets Enable Large-Scale Marine Conservation''}
 
@@
 \maketitle
-
-% Place your abstract within the special {sciabstract} environment.
-\begin{sciabstract}
-Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery revenue.
-We use a combination of spatial bioeconomic modeling and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation.
-The answer hinges on two design features.
-First, only when trading of rights is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
-Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly innocuous design features of a fishery management system can have indelible impacts on a country's willingness to engage in large-scale conservation.
-Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right market design, countries may be able to meet international conservation goals without incurring large costs.
-\end{sciabstract}
-
-Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
-Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}.
-What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
-
-This is not just a theoretical curiosity; we are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
-These waters account for 14.5 million km\textsuperscript{2} (four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
-In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
-Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in conservation.
-We show how a rights-based fisheries market can be designed or modified  to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
-
-Not all market-based approaches to environmental management are created equal.
-A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}.
-In the context of fishery markets, we find that two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
-But why would trading and allocation rules affect the incentives for conservation?
-Consider the incentives for a country to close 100\% of its waters.
-Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries.
-If the conserving country could sell the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
-But if the conserving country was not allowed to sell these rights, then it would lose all of its fishing revenue.
-The rules for how fishing rights are allocated across countries are equally important.
-Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
-This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.
-
-To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
-Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
-Patch 10 represents the high seas, where fishing days are governed by economic conditions.
-We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries.
-In all cases, we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
-We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see Supplementary Materials).
-
-A spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 if trading between countries is not allowed (Fig.
-\ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs.
-Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
-The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
-\ref{fig:vessel_day_price_no_trading_plot}).
-When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig.
-\ref{fig:profits_PNA_notKIR_no_trading_plot}) and the high seas.
-
-How would trading between countries change these results?
-We simulate the same fishery, but now allow for vessel-days to be traded across patches.
-As before, a closure in Patch 1 lowers the value of vessel-days in that patch.
-But increased biomass in other patches causes prices in Patches 2 to 8 to increase.
-As a result, rights from Patch 1 are traded to Patches 2 to 9, until vessel-day prices are the same across all patches (Fig.
-\ref{fig:vessel_day_price_with_trading_plot}).
-Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
-\ref{fig:PNA_model}).
-Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
-\ref{fig:PNA_model}C).
-
-However, a new problem arises.
-How should rights be re-allocated every year?
-To analyze the consequences of different allocation rules on conservation incentives, we simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
-We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
-We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
-\ref{fig:allocation_cost_plot}).
-However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, countries may be incentivized to engage in large-scale marine conservation.
-
-A recent LSMPA was implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
-We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
-The remaining 221 vessels were not continuously observed before and after, and we refer to these as ``other vessels''.
-
-How did PIPA change vessel fishing locations?
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff}).
-Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
-\ref{fig:empirical}A-B).
-The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
-On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
-The same pattern is observed at the PNA level, with non-displaced and other vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
-By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Fig.
-\ref{fig:empirical}A).
-Detailed analyses of vessel-level behavioral changes and crowding effects associated with PIPA implementation are included in our Supplementary Materials (Figs.
-\ref{fig:fishing_raster_diff}, \ref{fig:sp_corr}, and \ref{fig:all_panels}; and Tables \ref{tab:sp_corr} and \ref{tab:main_DID}).
-
-As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses.
-Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
-\ref{fig:empirical}C).
-The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig. \ref{fig:empirical}C-D).
-But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
-This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig.
-\ref{fig:effort_and_revenues}).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. \ref{fig:total_PNA_revenues}), despite the PIPA closure.
-
-Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA.
-In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
-\ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline (10,500 non-tradable vessel-days) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine (700 tradable vessel-days) fishing activity (Figs.
-\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
-While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
-The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation.
-
-International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}.
-Our results show that a few key design features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
-Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.
-
-\bibliography{references}
-
-\bibliographystyle{Science}
-
-\clearpage
-
-\FloatBarrier
-
-\section*{Figures}
-
-% PNA model output for costs
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/PNA_model.pdf}
-\caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
-Each line represents a possible value of stock movement ($\theta$; line color).
-The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
-Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
-Costs avoided by trading are shown in (C).
-Dashed red line in (A) is a 1:1 line.}
-\end{figure}
-
-% Costs of different allocation rules
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/allocation_cost_plot.pdf}
-\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules.
-Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis).
-An effort-based allocation and low movement values result in the highest costs.
-Cost can be minimized for all movement values if allocation is based on biomass.}
-\end{figure}
-
-% Effort redistribution bars for PNA and KIR
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/empirical.pdf}
-\caption{\label{fig:empirical}Effort displacement and license revenues.
-Pannels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA).
-Annual effort is broken down by displaced, non-displaced, and other vessels.
-The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days).
-Pannel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and pannel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
-The dashed line represents line of best fit.}
-\end{figure}
-
-% Map of LSMPAS in PNA
-\begin{figure}
-\centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
-Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
-A red line indicates the Kiribati EEZ.
-The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary.
-Land masses are shown in gray.
-Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\FloatBarrier
 
@@
 \begin{equation}
-X_{t+1} = e_t + e^{r \times \frac{e}{K}}
+X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
 \label{eqn:grow}
@@
 
-\input{tab/parameters.tex}
+\begin{table}[H]
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{l|r|l}
+\hline
+Parameter & Value & Source\\
+\hline
+MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
+\hline
+$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
+\hline
+K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
+\hline
+$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
+\hline
+$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
+\hline
+$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
+\hline
+$r$ & 5.700000e-01 & From Fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
+\hline
+$\beta$ & 1.300000e+00 & Standard\\
+\hline
+p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
+\hline
+q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
+\hline
+c & 1.800000e+02 & -\\
+\hline
+f & 1.000000e-01 & Biomass is equally distributed between patches ($f_i = 0.1$)\\
+\hline
+\end{tabular}}
+\end{table}
 
@@
 The first restriction excludes all Chinese vessels, the second excludes all PNA vessels, and the third excludes US and Taiwanese vessels.
+
+Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org Shapefiles for Marine Protected Areas (PIPA and PNMS) come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
 
@@
 \begin{landscape}
-	\input{tab/main_DID}
+\begin{table}[H] \centering 
+  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 9 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+\hline \\[-1.8ex] 
+ Constant & 0.495$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 4.440$^{***}$ & 12.998$^{***}$ & 12.462$^{***}$ & 3.709$^{***}$ & 4.456$^{***}$ & 2.429$^{***}$ \\ 
+  & (0.022) & (0.012) & (0.004) & (0.042) & (0.021) & (0.019) & (0.195) & (0.151) & (0.415) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.846$^{***}$ & $-$0.227$^{***}$ & 0.138$^{***}$ & 0.112$^{***}$ & 0.271$^{***}$ & 0.275$^{***}$ & 0.943$^{***}$ & 1.129$^{***}$ & 0.709$^{**}$ \\ 
+  & (0.018) & (0.009) & (0.003) & (0.031) & (0.014) & (0.014) & (0.141) & (0.110) & (0.284) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.255$^{***}$ & 0.225$^{***}$ & 0.117$^{***}$ & 0.549$^{***}$ & 0.153 & $-$0.280 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.029) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.014 & $-$0.001 & $-$0.001 & $-$0.411$^{***}$ & 0.167$^{***}$ & 0.064$^{***}$ & 0.357$^{***}$ & 0.137$^{**}$ & 0.484$^{***}$ \\ 
+  & (0.011) & (0.005) & (0.002) & (0.017) & (0.008) & (0.007) & (0.068) & (0.056) & (0.122) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.243$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.210$^{***}$ & $-$0.285$^{***}$ & $-$0.157$^{***}$ & $-$0.586$^{***}$ & $-$0.403$^{***}$ & 0.338 \\ 
+  & (0.019) & (0.009) & (0.003) & (0.036) & (0.017) & (0.017) & (0.161) & (0.127) & (0.285) \\ 
+  & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 83,052 & 83,052 & 83,051 & 79,669 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
+R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.017 & 0.075 & 0.082 & 0.126 & 0.200 & 0.252 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 \begin{landscape}
-	\input{tab/DID_without_CHN}
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 9 variables of interest after removing Chinese vessels.
+1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+\hline \\[-1.8ex] 
+ Constant & 0.058$^{***}$ & 3.863$^{***}$ & $-$0.003 & 4.829$^{***}$ & 13.817$^{***}$ & 13.161$^{***}$ & 4.007$^{***}$ & 4.515$^{***}$ & 2.909$^{***}$ \\ 
+  & (0.019) & (0.008) & (0.003) & (0.044) & (0.044) & (0.058) & (0.347) & (0.304) & (0.274) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.824$^{***}$ & $-$0.254$^{***}$ & 0.136$^{***}$ & 0.145$^{***}$ & 0.306$^{***}$ & 0.322$^{***}$ & 0.920$^{***}$ & 1.157$^{***}$ & 0.691$^{**}$ \\ 
+  & (0.019) & (0.010) & (0.003) & (0.034) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.108$^{***}$ & 0.009 & 0.012$^{***}$ & 0.270$^{***}$ & 0.271$^{***}$ & 0.158$^{***}$ & 0.491$^{***}$ & 0.150 & $-$0.274 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.031) & (0.017) & (0.017) & (0.162) & (0.131) & (0.235) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.012 & $-$0.007 & $-$0.001 & $-$0.380$^{***}$ & 0.164$^{***}$ & 0.061$^{***}$ & 0.365$^{***}$ & 0.122$^{**}$ & 0.464$^{***}$ \\ 
+  & (0.011) & (0.005) & (0.002) & (0.018) & (0.009) & (0.008) & (0.074) & (0.060) & (0.126) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.212$^{***}$ & 0.040$^{***}$ & $-$0.031$^{***}$ & $-$0.282$^{***}$ & $-$0.338$^{***}$ & $-$0.205$^{***}$ & $-$0.558$^{***}$ & $-$0.412$^{***}$ & 0.374 \\ 
+  & (0.021) & (0.010) & (0.004) & (0.038) & (0.019) & (0.018) & (0.174) & (0.137) & (0.289) \\ 
+  & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 75,327 & 75,327 & 75,326 & 75,390 & 28,449 & 28,449 & 1,570 & 2,279 & 633 \\ 
+R$^{2}$ & 0.102 & 0.073 & 0.108 & 0.017 & 0.075 & 0.091 & 0.128 & 0.209 & 0.266 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 \begin{landscape}
-	\input{tab/DID_without_PNA}
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 9 variables of interest after removing PNA vessels: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+\hline \\[-1.8ex] 
+ Constant & 0.512$^{***}$ & 3.559$^{***}$ & 0.083$^{***}$ & 4.499$^{***}$ & 13.165$^{***}$ & 12.667$^{***}$ & 3.271$^{***}$ & 4.066$^{***}$ & 2.876$^{***}$ \\ 
+  & (0.024) & (0.013) & (0.004) & (0.047) & (0.028) & (0.025) & (0.263) & (0.201) & (0.434) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.781$^{***}$ & $-$0.159$^{***}$ & 0.122$^{***}$ & 0.047 & 0.114$^{***}$ & 0.070$^{***}$ & 1.168$^{***}$ & 1.481$^{***}$ & 0.295 \\ 
+  & (0.022) & (0.012) & (0.004) & (0.043) & (0.023) & (0.022) & (0.226) & (0.180) & (0.333) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.202$^{***}$ & 0.040$^{***}$ & 0.019$^{***}$ & 0.437$^{***}$ & 0.165$^{***}$ & $-$0.015 & 0.817$^{***}$ & 0.533$^{***}$ & $-$0.408$^{*}$ \\ 
+  & (0.015) & (0.009) & (0.003) & (0.037) & (0.024) & (0.022) & (0.229) & (0.182) & (0.235) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.019 & $-$0.0003 & $-$0.002 & $-$0.387$^{***}$ & 0.138$^{***}$ & 0.025$^{***}$ & 0.413$^{***}$ & 0.232$^{***}$ & 0.482$^{***}$ \\ 
+  & (0.012) & (0.006) & (0.002) & (0.020) & (0.010) & (0.009) & (0.080) & (0.066) & (0.156) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.219$^{***}$ & $-$0.055$^{***}$ & $-$0.023$^{***}$ & $-$0.246$^{***}$ & $-$0.175$^{***}$ & 0.010 & $-$0.843$^{***}$ & $-$0.821$^{***}$ & 0.729$^{**}$ \\ 
+  & (0.024) & (0.012) & (0.004) & (0.046) & (0.026) & (0.024) & (0.243) & (0.195) & (0.341) \\ 
+  & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 64,560 & 64,560 & 64,559 & 64,625 & 22,654 & 22,654 & 1,366 & 1,928 & 511 \\ 
+R$^{2}$ & 0.093 & 0.069 & 0.099 & 0.022 & 0.063 & 0.066 & 0.127 & 0.203 & 0.214 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 \begin{landscape}
-	\input{tab/DID_without_USA_TWN}
+\begin{table}[H] \centering 
+  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 9 variables of interest after removing US and Tawianese vessels.
+1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
+Numbers in parentheses are heteroskedastic-robust standard errors.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
+\hline \\[-1.8ex] 
+ Constant & 0.536$^{***}$ & 3.600$^{***}$ & 0.082$^{***}$ & 4.506$^{***}$ & 13.002$^{***}$ & 12.438$^{***}$ & 3.850$^{***}$ & 4.719$^{***}$ & 2.420$^{***}$ \\ 
+  & (0.023) & (0.012) & (0.004) & (0.043) & (0.022) & (0.020) & (0.209) & (0.158) & (0.419) \\ 
+  & & & & & & & & & \\ 
+ Post & 0.796$^{***}$ & $-$0.217$^{***}$ & 0.130$^{***}$ & 0.021 & 0.290$^{***}$ & 0.291$^{***}$ & 0.870$^{***}$ & 0.894$^{***}$ & 0.732$^{**}$ \\ 
+  & (0.019) & (0.010) & (0.003) & (0.035) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
+  & & & & & & & & & \\ 
+ Displaced & 0.142$^{***}$ & 0.016$^{**}$ & 0.015$^{***}$ & 0.341$^{***}$ & 0.227$^{***}$ & 0.127$^{***}$ & 0.490$^{***}$ & $-$0.017 & $-$0.296 \\ 
+  & (0.013) & (0.007) & (0.002) & (0.031) & (0.018) & (0.017) & (0.163) & (0.126) & (0.239) \\ 
+  & & & & & & & & & \\ 
+ NINO4 & $-$0.001 & $-$0.001 & 0.001 & $-$0.383$^{***}$ & 0.189$^{***}$ & 0.082$^{***}$ & 0.325$^{***}$ & 0.171$^{***}$ & 0.441$^{***}$ \\ 
+  & (0.011) & (0.006) & (0.002) & (0.019) & (0.009) & (0.008) & (0.075) & (0.063) & (0.122) \\ 
+  & & & & & & & & & \\ 
+ Post $\times$ Displaced & $-$0.212$^{***}$ & $-$0.002 & $-$0.029$^{***}$ & $-$0.158$^{***}$ & $-$0.328$^{***}$ & $-$0.184$^{***}$ & $-$0.533$^{***}$ & $-$0.225 & 0.339 \\ 
+  & (0.021) & (0.010) & (0.004) & (0.039) & (0.019) & (0.018) & (0.175) & (0.138) & (0.291) \\ 
+  & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 73,717 & 73,717 & 73,716 & 73,778 & 26,920 & 26,920 & 1,546 & 2,236 & 660 \\ 
+R$^{2}$ & 0.095 & 0.072 & 0.102 & 0.021 & 0.077 & 0.094 & 0.111 & 0.169 & 0.256 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 \begin{landscape}
-\input{tab/sp_corr}
+\begin{table}[H] \centering 
+  \caption{\label{tab:sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for all PNA waters.
+The first five columns represent different specifications for number of cells with presence of both fleets.
+Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels.
+The explanatory variable is the number of months before or after implementation of PIPA.
+Numbers in parentheses are heteroskedastic-robust standard errors.
+The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\hline \\[-1.8ex] 
+ Constant & 78.04$^{***}$ & 84.64$^{***}$ & 60.96$^{***}$ & 66.73$^{***}$ & 80.62$^{***}$ & 0.41$^{***}$ & 0.42$^{***}$ & 0.37$^{***}$ & 0.38$^{***}$ & 0.38$^{***}$ \\ 
+  & (5.44) & (8.99) & (15.60) & (15.99) & (7.96) & (0.01) & (0.03) & (0.06) & (0.07) & (0.02) \\ 
+  & & & & & & & & & & \\ 
+ M & 3.94$^{***}$ & 4.07$^{***}$ & 3.07$^{***}$ & 3.14$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{**}$ & 0.01$^{**}$ &  \\ 
+  & (0.30) & (0.35) & (0.97) & (1.04) &  & (0.001) & (0.001) & (0.003) & (0.004) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^2$ & $-$0.005 & $-$0.02 & 0.01 & $-$0.01 &  & $-$0.0001$^{***}$ & $-$0.0001 & $-$0.0001 & $-$0.0001 &  \\ 
+  & (0.02) & (0.03) & (0.03) & (0.03) &  & (0.0000) & (0.0001) & (0.0001) & (0.0001) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^3$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ &  \\ 
+  & (0.0003) & (0.0003) & (0.001) & (0.001) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^4$ & 0.0000 & 0.0000 & 0.0000 & 0.0000 &  & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000 & 0.0000 &  \\ 
+  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ NINO4 &  & $-$8.09 &  & $-$10.39 & 19.76$^{**}$ &  & $-$0.01 &  & $-$0.01 & 0.07$^{***}$ \\ 
+  &  & (8.29) &  & (9.48) & (9.41) &  & (0.03) &  & (0.03) & (0.02) \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_1$ &  &  & 21.32 & 25.10 &  &  &  & 0.06 & 0.06 &  \\ 
+  &  &  & (19.49) & (22.49) &  &  &  & (0.08) & (0.08) &  \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_2$ &  &  & 5.30 & 3.19 &  &  &  & $-$0.01 & $-$0.02 &  \\ 
+  &  &  & (18.87) & (18.67) &  &  &  & (0.04) & (0.03) &  \\ 
+  & & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
+Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
+AIC & 796.937 & 797.991 & 799.477 & 799.97 & 919.583 & -187.208 & -185.269 & -184.916 & -183.233 & -97.386 \\ 
+Observations & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 \\ 
+R$^{2}$ & 0.79 & 0.79 & 0.79 & 0.80 & 0.03 & 0.70 & 0.70 & 0.71 & 0.71 & 0.07 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 \begin{landscape}
-\input{tab/KIR_sp_corr}
+\begin{table}[H] \centering 
+  \caption{\label{tab:KIR_sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for Kiribati EEZ only.
+The first five columns represent different specifications for number of cells with presence of both fleets.
+Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels.
+The explanatory variable is the number of months before or after implementation of PIPA.
+Numbers in parentheses are heteroskedastic-robust standard errors.
+The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.}
+  \label{} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
+\hline \\[-1.8ex] 
+ Constant & 30.24$^{***}$ & 32.77$^{***}$ & 23.30$^{***}$ & 26.14$^{***}$ & 16.23$^{***}$ & 0.43$^{***}$ & 0.43$^{***}$ & 0.33$^{***}$ & 0.34$^{***}$ & 0.38$^{***}$ \\ 
+  & (2.43) & (4.16) & (4.59) & (5.49) & (2.37) & (0.03) & (0.05) & (0.07) & (0.08) & (0.03) \\ 
+  & & & & & & & & & & \\ 
+ M & 1.29$^{***}$ & 1.34$^{***}$ & 1.00$^{***}$ & 1.06$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{*}$ & 0.01 &  \\ 
+  & (0.14) & (0.17) & (0.27) & (0.30) &  & (0.002) & (0.002) & (0.01) & (0.01) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^2$ & $-$0.03$^{***}$ & $-$0.04$^{***}$ & $-$0.02$^{**}$ & $-$0.03$^{***}$ &  & 0.0000 & 0.0000 & 0.0001 & 0.0001 &  \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) &  & (0.0002) & (0.0002) & (0.0002) & (0.0002) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^3$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{**}$ & $-$0.0000$^{**}$ &  \\ 
+  & (0.0001) & (0.0001) & (0.0002) & (0.0002) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ M $^4$ & 0.0000$^{***}$ & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000$^{***}$ &  & $-$0.0000 & $-$0.0000 & $-$0.0000 & $-$0.0000 &  \\ 
+  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
+  & & & & & & & & & & \\ 
+ NINO4 &  & $-$3.10 &  & $-$4.19 & 9.93$^{***}$ &  & $-$0.001 &  & $-$0.02 & 0.11$^{***}$ \\ 
+  &  & (3.97) &  & (4.16) & (3.33) &  & (0.05) &  & (0.06) & (0.03) \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_1$ &  &  & 9.40 & 10.33 &  &  &  & 0.12 & 0.13 &  \\ 
+  &  &  & (5.92) & (6.35) &  &  &  & (0.09) & (0.09) &  \\ 
+  & & & & & & & & & & \\ 
+ $\sigma_2$ &  &  & $-$2.46 & $-$3.84 &  &  &  & 0.02 & 0.01 &  \\ 
+  &  &  & (5.70) & (5.77) &  &  &  & (0.10) & (0.11) &  \\ 
+  & & & & & & & & & & \\ 
+\hline \\[-1.8ex] 
+NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
+Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
+AIC & 654.294 & 655.536 & 655.482 & 656.125 & 724.58 & -65.872 & -63.873 & -63.481 & -61.572 & -35.895 \\ 
+Observations & 84 & 84 & 84 & 84 & 84 & 75 & 75 & 75 & 75 & 75 \\ 
+R$^{2}$ & 0.63 & 0.63 & 0.64 & 0.65 & 0.08 & 0.44 & 0.44 & 0.45 & 0.45 & 0.09 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table} 
 \end{landscape}
@@
 
+\clearpage
+
+\bibliography{references}
+
+\bibliographystyle{Science}
+
 \end{document}

### 2019-06-24 docs/old_ms/Markets_Conservation_June12.tex
Ready for submission as a Report

--- 2019-05-30 docs/Markets_Conservation_May30.tex
@@
 Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of large-scale marine protected areas, and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
-Indeed, this is a question maritime nations all over the world face as they consider whether, and how, to comply with international commitments to expand Marine Protected Area (MPA) coverage.
-We use a combination of spatial bioeconomic modeling, which accounts for fisheries markets such as the vessel-day trading scheme in the Pacific Ocean, and spatially-explicit vessel-level empirical data on fishing behavior before and after MPA implementation, to assess how market design incentivizes, or penalizes conservation.
-The answer hinges critically on two design features of the rights-based fishery market.
-First, only if trading of harvest or vessel-days is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Instead, if trading is forbidden, countries are likely to suffer losses from conservation.
+We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
+We use a combination of spatial bioeconomic modeling, and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation.
+The answer hinges on two design features.
+First, only when trading of rights is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
 Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
 Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation; these results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right design features, large-scale protected areas such as the Phoenix Islands can be achieved at close to zero cost to the implementing country.
+Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation.
+Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
+With the right market design features, countries may be able to meet international conservation without incurring in large costs.
 \end{sciabstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%% Other titles %%%%%%%%%%%%
-% Fishery markets enable marine conservation
-% Designing environmental markets for marine conservation
-% Large-scale marine conservation is enabled by market instruments
-% Rights-based management to promote marine conservation
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Recognizing a need to secure biodiversity, blue carbon, rare habitats, and other ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
-Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%, 30\%, or even up to 50\% of the ocean to be off-limits to fishing.
-Fundamentally, to achieve these goals, huge swaths of sovereign nations' waters will have to be closed to fishing.
+Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
+Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%, 30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+To achieve these goals, huge swaths of sovereign nations' waters will be closed to fishing, highlighting the importance of considering opportunity costs and reducing losses \cite{smith_2010,mallin_2019}.
 What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 20\%, 50\%, or even 100\% of its waters to fishing if this meant losing all fishing revenue from within its borders?
-We show that a country's incentives for large-scale conservation hinge critically on an unsuspected culprit: the design of fishing rights.
+Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within its borders?
 
@@
 These waters collectively account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental United States), and over 60\% of skipjack tuna catches in the Western Central Pacific \cite{havice_2013}.
-
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of other ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-The PNA member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
-A natural concern arises: even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in any meaningful conservation.
-Intuitively, then, it seems that a country's willingness to engage in large-scale conservation will depend crucially on whether it can successfully capture a sufficiently high fraction of the benefits that are derived from that conservation.
-We show how a rights-based fisheries market can be designed (if it is new) or modified (if it already exists) to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
-
-To mirror the strategies and spatial connections among the nine PNA countries and the high seas, we develop a 10-patch spatial bioeconomic model.
-The fishery in nine of the patches operates under a market-based system in which ``vessel days'' are capped, closely tracked, and may be traded across countries.
-This vessel-day scheme (VDS) is actually used by the PNA; each country is given an allocation of vessel-days that can then be sold to fishing firms.
-A vessel-day owned by country $i$ entitles $i$ to lease that day to a fishing vessel, entitling it to fish in $i$'s EEZ for a 24 hour period.
-In our model, Patches 1 - 9 are countries that operate under a VDS (in which fishing days are limited) and Patch 10 represents the high seas, where fishing days are governed by economic conditions, not by the VDS.
-
-While modeling the VDS market may be interesting in its own right, our primary purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-To examine this, suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters as a marine reserve, in which no fishing is allowed.
-When Country 1 creates a reserve, several consequences may arise.
-Perhaps most obviously, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in $i$'s waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-The purpose of our model is to examine these consequences in detail, with a particular focus on how design features of the market affect Country 1's incentives to create the marine reserve.
+Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in conservation.
+We show how a rights-based fisheries market can be designed or modified  to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
 
 Not all market-based approaches to environmental management are created equal.
-A pervasive finding across a range of natural resources is that features of market design can have enormous implications for the market's functioning.
-In the context of fishery markets, two market design features stand out as important for a variety of outcomes, and we will show that they are pivotal in determining the incentives for large-scale marine conservation.
-The first design feature has to do with the trading of rights, and the second design feature concerns the allocation of rights.
-We examine the effects of large-scale conservation in Country 1 across a range of scenarios for trading and allocation of vessel day fishing rights across our nine model countries.
-In all cases we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
-We quantify the change in revenue to each PNA country from large-scale conservation in Country 1, by comparing revenues from each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement.
-
-Why would trading and allocation rules affect the incentives for conservation by Country 1?
-Invoking \emph{reductio ad absurdum}, consider the incentives for Country 1 to close 100\% of its waters.
-Such a closure would surely benefit the other countries through the increased abundance of fish.
-If Country 1 could sell its fishing rights, the other countries would likely buy them, and this could offset the foregone costs of fishing its own waters.
-But if Country 1 was not allowed to sell its rights, then it would lose all of its fishing revenue.
-This provides the simple intuition for why allowing trading across countries is so critical to conservation incentives.
+A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have enormous implications for the market's functioning \cite{libecap_1989}.
+In the context of fishery markets, two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
+But why would trading and allocation rules affect the incentives for conservation?
+Consider the incentives for a country to close 100\% of its waters.
+Such a closure would surely benefit other countries through the increased fish biomass.
+If the conserving country could sell its fishing rights, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+But if the conserving country was not allowed to sell its rights, then it would lose all of its fishing revenue.
 The rules for how fishing rights are allocated across the nine countries are equally important.
@@
 
-In our bioeconomic model, we examine the implications of conservation under alternative market designs: with, and without trading, and under alternative allocation rules.
-To test how the PNA allocates rights, we vary the degree to which periodic allocation is based on historical within-patch effort versus the actual abundance of fish biomass in a patch.
-Finally, we use vessel-tracking data and official reports of government revenue to corroborate our results by looking at the Phoenix Islands Protected Area, implemented in 2015 by Kiribati within the PNA.
+We developed a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
+Patches 1 to 9 represent each country and operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped, traded, and closely tracked.
+Patch 10 represents the high seas, where fishing days are governed by economic conditions.
+We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries.
+In all cases, we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
+We quantify the change in revenue to Country 1 and compare each scenario to a bechmark scenario without any conservation action.
+We simulate these outcomes across a range of reserve sices and assumptions about within-patch stock movement (See Supplementary Materials).
 
-We begin by simulating a fishery where trading of fishing days across countries is forbidden.
-In that setting, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+A spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 if trading between countries is not allowed (Fig.
 \ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs, but these decrease if within-patch stock movement ($\theta$) increases, allowing vessels to harvest the stock within the remaining open area.
+Closing a greater proportion of the patch results in greater costs.
+Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in Patch 1, which reduces a vessel's willingness to pay to fish in such waters (Fig.
+Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in Patch 1 (\emph{i.e.} biomass outside the reserve), which reduces a vessel's willingness to pay to fish in such waters (Fig.
 \ref{fig:vessel_day_price_no_trading_plot}).
-When countries cannot trade, the costs of conservation are large and incurred by Patch 1, but the benefits are received by the eight other patches (Figure S2 shows that the increase in revenue ranges from 0\% to 6\%).
+When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig.
+\ref{fig:profits_PNA_notKIR_no_trading_plot}) and the high seas.
 
-How would a different market design, where trading between countries is allowed, change these results?
-To answer this we simulate the exact same fishery, but now allow for vessel-days to be traded across patches.
-A closure in Patch 1 lowers the value of vessel-days in that patch.
-Vessel-days in patches 2 - 9 are now worth more causing vessel-days from Patch 1 to be traded to Patches 2 - 9.
-Trading continues until vessel-day prices are the same across all patches (Fig.
+How would trading between countries change these results?
+We simulate the same fishery, but now allow for vessel-days to be traded across patches.
+As before, a closure in Patch 1 lowers the value of vessel-days in that patch.
+But increased biomass in other patches causes prices in Patches 2 to 8 to increase.
+As a result, rights from Patch 1 are traded to Patches 2 to 9, until vessel-day prices are the same across all patches (Fig.
 \ref{fig:vessel_day_price_with_trading_plot}).
-Under this market design, we find that revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
+Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
 \ref{fig:PNA_model}).
-Overall, we find that between 88\% and 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
 
-To analyze the consequences of different allocation rules on conservation incentives, we simulate an annual allocation that is a weighted function of historical fishing in a country and historical fish biomass in a country.
-If allocation rules are based only on the historical effort in a country, then trading vessel-days to other countries would imply a future reduction in allocation.
-We simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
-We use a range of allocation rules to weight effort ($\alpha$) and biomass ($1 - \alpha$) and compare the revenues to a fishery operating for 50 years without any closures.
-We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in losses of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
+However, a new problem arises.
+How should rights be re-allocated every year?
+To analyze the consequences of different allocation rules on conservation incentives, we simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
+We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
+We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
 \ref{fig:allocation_cost_plot}).
-However, these costs are reduced as more weight is put on historical biomass.
-A biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in costs as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation for all reserve sizes and possible movement.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, the incentives for conservation are much greater.
+However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue loss as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, countries may be able to engage in large-scale marine conservation in the long term.
 
-We have shown that design features of a rights-based fisheries management system have enormous implications for the incentives a country faces to engage in large-scale conservation.
-Allowing trading of rights across countries, and re-allocating annual rights based on biological variables, not fishing pressure, can essentially eliminate the cost of conservation, even for very large reserves.
-We now move to an empirical setting where we combine vessel-tracking data and the implementation of one of the world's largest marine reserves to identify the effort displacement and likely costs of conservation.
+A recent LSMPA was implemented in PNA waters, providing the ideal empirical setting to test our predictions.
+In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and twenty-eight ``non-displaced vessels'' never fished in PIPA waters.
+We observe these vessels before and after the implementation.
+The remaining 221 vessels were not continuously observed before and after, and we refer to these as ``other vessels''.
 
-The Pacific island nation of Kiribati implemented the Phoenix Islands Protected Area in January 2015 (Fig.
-\ref{fig:PNA_map}).
-With an extension of 397,447 Km\textsuperscript{2}, this 11.5\% closure effectively displaced all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
-We use identification of fishing activity via Automatic Identification Systems (AIS) provided by Global Fishing Watch to track 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018 \cite{kroodsma_2018}.
-We continuously observe 92 vessels for the 2012 - 2018 period.
-Of these, 64 vessels fished within PIPA at least once prior to its implementation, and we refer to them as the ``displaced vessels''.
-The remaining 28 vessels never fished in PIPA waters, and we refer to them as ``non-displaced vessels''.
-The group with the remaining 221 vessels contains vessels that were not continuously observed before and after the implementation of PIPA, and we refer to these as ``other vessels''.
-
-We use the tracking data to calculate the time that vessels spent within Kiribati and PNA waters (Figs.
-\ref{fig:all_PS_VDS_year}A-B).
-Our observations match the 45,000 vessel-days allowed at the PNA level, and roughly match the 11,000 vessel-days historically allocated to Kiribati \cite{yeeting2018stabilising}.
-We find that displaced vessels fished 922 less days (a 10\% reduction) in Kiribati between 2014 and 2015, immediately after PIPA was implemented.
-For the same period, these vessels spent just 48 days less in PNA waters, suggesting that trading might have facilitated relocation of effort within PNA waters.
+After PIPA implementation, displaced vessels fished 922 less days (a 10\% reduction) in Kiribati, but spent just 48 days less in PNA waters (Figs.
+\ref{fig:empirical}A-B).
+Displaced vessels relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands, and a minimal portion to the high seas (Fig \ref{fig:fishing_raster_diff}).
+The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
 On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
 The same pattern is observed at the PNA level, with vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
-These changes result in a net decrease of fishing effort within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Figs.
-\ref{fig:all_PS_VDS_year}A).
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands and the high seas (Fig \ref{fig:fishing_raster_diff}).
+By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Figs.
+\ref{fig:empirical}A).
+A detailed analyses of vessel-level behavioral changes and crowding effects associated to PIPA implementation are included in our Supplementary Materials (Figs.
+\ref{fig:fishing_raster_diff}, \ref{fig:sp_corr}, and \ref{fig:all_panels}; and Tables \ref{tab:sp_corr} and \ref{tab:main_DID}).
 
-Our analysis suggests that the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's waters.
-But does this result in losses to Kiribati?
-We do not explicitly observe trading between countries, but combining different sources of information we are able to paint a comprehensive picture.
-We use country-level fisheries revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) for the 2008 - 2016 period to complement our analysis (Fig.
-\ref{fig:revenues}A).
-Kiribati's reported revenue increased from \$127.3 million USD in 2014 to \$148.8 million USD in 2015, before decreasing to \$118.3 million USD in 2016.
-This increase and subsequent decrease in revenues matches the AIS patterns we observe for Kiribati in 2014 - 2016 (Fig.
-\ref{fig:all_PS_VDS_year}A), and observed AIS effort is a reliable predictor of government revenue across all PNA countries from 2008 to 2016 (Fig.
-\ref{fig:revenue_FFA_effort_GFW}).
+As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses.
+Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
+\ref{fig:empirical}C).
+This increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig.
+\ref{fig:empirical}C-D).
 At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
@@
 
-\textbf{We also inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface(Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly \ref{fig:nino_plot} alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation.
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).}
+Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA.
+In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
+\ref{fig:PNA_map}).
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline (10,500 non-tradable vessel-days) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine (700 tradable vessel-days) fishing activity (Figs.
+\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
+While trading will allow Palau, Kiribati, and other PNA members reduce revenue losses, they must advocate for a biomass-based allocation rule to ensure long-term allocations.
+The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation.
 
-\textbf{We use multiple linear regression to measure the change in nine vessel-level measures for displaced and non-displaced vessels before and after the implementation of PIPA (Fig.
-\ref{fig:all_panels}; Table \ref{tab:main_DID})).
-We find no evidence of displaced vessels fishing more after the implementation, and in fact observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$).
-Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$).
-Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.}
-
-A new large-scale marine protected area is being proposed in the PNA.
-On October 28, 2015, the President of Palau signed into law the Palau National Marine Sanctuary (PNMS) Act.
-Starting in December 2020, this Act will close 500,000 km\textsuperscript{2} (about 80\% of Palau's EEZ) to commercial fishing activities \cite{cimino_2019}, creating the 14\textsuperscript{th} largest protected area in the world (Fig.
-\ref{fig:PNA_map}).
-As a PNA member, Palau receives 700 purse seine vessel-days each year.
-Their longline fishery is also managed under a vessel-day scheme, with 10,500 non-tradable vessel-days per year, which currently sell at about \$200 USD each (Fig.
-\ref{fig:PLW_GFW_ts}).
-What does an 80\% closure represent for Palau's revenue from access fees?
-AIS data (2012 - 2019) shows that PNMS would displace $65.6 \pm 0.08$\% and $82.2 \pm 0.08$\% of longline and purse seine activity (Figs.
-\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
-Palau may be able to reduce the cost of lost license revenue if purse seine vessel-days are traded with other PNA members.
-However, the current reallocation rule for purse seine vessel-days is based on historical effort and biomass, which would lead to a decreased allocation through time.
-Palau, howver, might continue to sell purse seine vessel-days to the United States under the South Pacific Tuna Treaty (also known as the Multilateral Treaty on Fisheries; \$12,500/day).
-Longline vessel days are currently not tradable, meaning that the price for longline vessel-days might decrease, leading to losses in profits.
-
-Rights-based fisheries management can prevent fisheries collapse \cite{costello_2008}.
-Our work shows that properly designed rights-based fisheries markets can also allow and incentivize large-scale marine conservation.
-Successful implementation of large-scale Marine Protected Areas under effort markets depends on two key features: tradable fishing rights and a biomass-based allocation rule.
-Tradable fishing rights allow a country to capture the benefits of conservation, and a biomass-based allocation rule ensures that this conservation actions are rewarded in the long term.
-
-International goals over the next decade have set ambitious targets for marine conservation.
-Plans to implement large-scale Marine Protected Areas must consider the opportunity costs that come with such interventions \cite{smith_2010}, and identify sustainable financing mechanisms that compensate losses and incentivize long-term marine conservation \cite{mallin_2019}.
-The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and modifying the re-allocation rule, they may become pioneers in effective large-scale marine conservation.
+International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}.
+Our results show that seemingly benign design
+features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
+Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.
 
@@
 An effort-based allocation and low movement values result in the highest costs.
-Cost can be minimized for all movement values if alloction is based on biomass.}
+Cost can be minimized for all movement values if allocation is based on biomass.}
+\end{figure}
+
+% Effort redistribution bars for PNA and KIR
+\begin{figure}[htbp]
+\centering
+\includegraphics{img/empirical.pdf}
+\caption{\label{fig:empirical}Effort displacement and license revenues.
+Pannels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA).
+Annual effort is broken down by displaced, non-displaced, and other vessels.
+The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days).
+Pannel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and pannel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
+The dashed line represents line of best fit.}
 \end{figure}
@@
 
-\subsubsection{Crowding effect}
-
-$$
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
-\label{eqn:sp_corr}
-$$
-
-We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
-The $\mu$ coefficient captures the effect of the NINO4 anomaly.
-
 \subsubsection{Behavioral changes}
@@
 Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
+All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
 
-All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated.
+We find no evidence of displaced vessels fishing more after the implementation and, in fact, observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$; Fig.
+\ref{fig:all_panels}; Table \ref{tab:main_DID}).
+Likewise, we observe a 3.4\% decrease of fishing hours relative to total at-sea hours ($p < 0.01$).
+Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
+These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
+We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
+We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
+
+\subsubsection{Crowding effect}
+
+$$
+y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
+\label{eqn:sp_corr}
+$$
+
+We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
+1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
+For example, since PIPA was implemented in January 1st of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
+Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
+The $\mu$ coefficient captures the effect of the NINO4 anomaly.
+
+We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface(Fig \ref{fig:fishing_raster_diff}).
+These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+\ref{fig:sp_corr}).
+The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
+Environmental variation may certainly drive this, but the NINO4 anomaly \ref{fig:nino_plot} alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation.
+We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
 
@@
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\footnote{https://www.ffa.int/node/2050}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:revenues}A).
+\ref{fig:empirical}A).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.

### 2019-06-24 docs/old_ms/Markets_Conservation_June14.tex
Ready for submission as a Report

--- 2019-06-24 docs/old_ms/Markets_Conservation_June12.tex
@@
 \begin{equation}
-\pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
+\pi_i(E_i) = pqX_i\Omega_i - \beta cE_i^{\beta-1}
 \label{eqn:marginal_profit}
@@
 
-$$
+\begin{equation}
 \bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
 \label{eqn:Ebar}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 H_i = qE_iX_i\Omega_i
 \label{eqn:harvest}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 X_{t+1} = e_t + e^{r \times \frac{e}{K}}
 \label{eqn:grow}
-$$
+\end{equation}
 
@@
 
-$$
+\begin{equation}
 X_{it+1} = f_iX_{t+1}
 \label{eqn:disperse}
-$$
+\end{equation}
 
@@
 \includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
 \end{figure}

### 2019-06-24 docs/old_ms/Markets_Conservation_June17.tex
Ready for submission as a Report

--- 2019-06-24 docs/Markets_Conservation_June19.tex
@@
 Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery revenue.
+We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery income.
 We use a combination of spatial bioeconomic modeling and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation.
@@
 Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly innocuous design features of a fishery management system can have indelible impacts on a country's willingness to engage in large-scale conservation.
+Overall, these results show that seemingly benign design features of a market can have indelible impacts on a country's willingness to engage in large-scale conservation.
 Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right market design, countries may be able to meet international conservation goals without incurring large costs.
+With the right market design features, countries may be able to meet international conservation goals without incurring large costs.
 \end{sciabstract}
@@
 Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}.
+To achieve these goals, huge swaths of sovereign nations' waters will be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}.
 What incentives might motivate a country to engage in such large-scale marine protection?
@@
 
-This is not just a theoretical curiosity; we are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
 Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
@@
 A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}.
-In the context of fishery markets, we find that two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
+In the context of fishery markets, two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
 But why would trading and allocation rules affect the incentives for conservation?
@@
 
-To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
+We develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
 Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
@@
 Closing a greater proportion of the patch results in greater costs.
-Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
+Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
+Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in Patch 1 (\emph{i.e.} biomass outside the reserve), which reduces a vessel's willingness to pay to fish in such waters (Fig.
 \ref{fig:vessel_day_price_no_trading_plot}).
@@
 We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
-We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
+We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
 \ref{fig:allocation_cost_plot}).
@@
 We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and twenty-eight ``non-displaced vessels'' never fished in PIPA waters.
+We observe these vessels before and after the implementation.
 The remaining 221 vessels were not continuously observed before and after, and we refer to these as ``other vessels''.
 
-How did PIPA change vessel fishing locations?
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff}).
-Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
+After PIPA implementation, displaced vessels fished 922 less days (a 10\% reduction) in Kiribati, but spent just 48 days less in PNA waters (Figs.
 \ref{fig:empirical}A-B).
+Displaced vessels relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands, and a minimal portion to the high seas (Fig \ref{fig:fishing_raster_diff}).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
@@
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
-This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig.
+This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship will hold (Fig.
 \ref{fig:effort_and_revenues}).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. \ref{fig:total_PNA_revenues}), despite the PIPA closure.
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. \ref{fig:total_PNA_revenues}).
 
@@
 \ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
-While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
+While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, they must advocate for a biomass-based allocation rule to ensure long-term financial security.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
@@
 International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}.
-Our results show that a few key design features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
+Our results show that seemingly benign design
+features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
 Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.
@@
 
-\begin{equation}
-\omega_i = \pi_iE_i
+$$
+\omega = \pi_iE_i
 \label{eqn:license_revenue}
-\end{equation}
+$$
 
-\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
+Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
 This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.

### 2019-06-24 docs/tab/parameters.tex
Ready for submission as a Report

@@
+\begin{table}[H]
+\centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}{l|r|l}
@@
 \hline
-MSY & 1.875600e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
+MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
 \hline
-$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
+$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
 \hline
-K & 6.876526e+06 & 50th percentile from MSY in table 8 of Stock Assessment\\
+K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
 \hline
-$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in table 8 of Stock Assessment\\
+$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
 \hline
-$C_{now}$ & 1.679444e+06 & Catches from Stock Assessment\\
+$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
 \hline
@@
 \hline
-$r$ & 5.700000e-01 & From fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
+$r$ & 5.700000e-01 & From Fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
 \hline
@@
 \hline
-p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA tuna fisheries 2017 report)\\
+p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
 \hline
@@
 \hline
-\end{tabular}
+\end{tabular}}
+\end{table}

### 2019-06-24 scripts/model/2_run_model.Rmd
Ready for submission as a Report

@@
 
+Create a table
+
 ```{r}
@@
 
+params %>% 
+  knitr::kable(col.names = c("Parameter", "Value", "Source"),
+               format = "html",
+               escape = F) %>% 
+  kableExtra::kable_styling(latex_options = "scale_down")
+```
+
+Export the table
+
+```{r}
 params %>% 
@@
 shorter_trading <- DF_1_with_trading %>% 
-  select(Country, R, theta, Vessel_Days_trading = Vessel_Days, pi_trading = VDSprice, VDSrevenue_trading = VDSrevenue, cost_trading = cost, rel_cost_trading = rel_cost)
+  select(Country, R, theta, Vessel_Days_trading = Vessel_Days, pi_trading = VDSprice, VDSrevenue_trading = all_VDSrevenue, cost_trading = cost, rel_cost_trading = rel_cost)
 
@@
        height = 7)
+```
+
+# Change in effort and revenue with and without trading
+
+```{r}
+# Create a data.frame of effort by scenario
+effort <- both %>% select(R, theta, Vessel_Days, Vessel_Days_trading) %>%
+  gather(model, effort, -c(R, theta)) %>%
+  mutate(model = ifelse(str_detect(model, "trading"), "Trading", "No trading"))
+
+# Repeat for revenues and merge
+revenues <- both %>% select(R, theta, VDSrevenue, VDSrevenue_trading) %>%
+  gather(model, revenues, -c(R, theta)) %>%
+  mutate(model = ifelse(str_detect(model, "trading"), "Trading", "No trading")) %>%
+  left_join(effort, by = c("R", "theta", "model"))
+```
+
+Plot it
+
+```{r, fig.width = 6, fig.height = 4}
+(
+  effort_and_revenues <- ggplot(data = revenues,
+                                mapping = aes(x = effort / 1e3,
+                                              y = revenues / 1e6,
+                                              fill = theta,
+                                              size = R,
+                                              shape = model)) +
+    geom_point(color = "black") +
+    scale_fill_viridis_c() +
+    scale_shape_manual(values = c(24, 21)) +
+    labs(x = "Vessel-days (1,000)", y = "Revenue (million US$)") +
+    guides(shape = guide_legend(title = "Scenario"),
+           size = guide_legend(title = "Reserve size (R)"),
+           fill = guide_colorbar(title = quo("Movement ("~theta~")"),
+                                 frame.colour = "black",
+                                 ticks.colour = "black"))
+)
+```
+
+Save it
+
+```{r}
+ggsave(plot = effort_and_revenues,
+       file = here("docs", "img","effort_and_revenues.pdf"),
+       width = 6,
+       height = 4)
 ```
@@
 
-alphas <- c(0, 0.25, 0.5, 0.75, 1)
+alphas <- c(0, 0.5, 1)
 
@@
     R = Rvec,
-    theta = c(0.25, 0.5, 0.75),
+    theta = c(0, 0.25, 0.5, 0.75, 1),
     alpha = alphas,
@@
 
-```{r, fig.height = 3.5, fig.width = 4.5}
+```{r, fig.height = 3.5, fig.width = 5.5}
 (allocation_cost_plot <- allocation %>%
@@
    mutate(trade = ifelse(trade, "Trading", "No Trading"),
-          theta = as.character(theta)) %>% 
+          alpha = as.character(alpha)) %>% 
    group_by(trade, alpha, R, theta) %>%
@@
    mutate(cost = (best_rev - rev) / best_rev) %>%
-   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
+   ggplot(aes(x = R, y = cost, color = theta, group = paste(alpha, theta), linetype = alpha)) +
    geom_line(size = 1.5) +
@@
    ggtheme_plot() +
-   # facet_wrap(~trade, ncol = 1) +
-   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
+   guides(color = guide_colorbar(title = bquote("Movement ("~theta~")"),
                                  ticks.colour = "black",
                                  frame.colour = "black"),
-          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
+          linetype = guide_legend(title = bquote("Allocaion ("~alpha~")"),
                                   override.aes = list(size = 0.5))))
@@
   filename = here("docs", "img", "allocation_cost_plot.pdf"),
-  width = 4.5,
+  width = 5.5,
   height = 3.5
@@
 
-```{r, eval = F}
-allocation %>%
-  filter(!trade) %>% 
-  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
-  geom_line(size = 1) +
-  facet_grid(alpha ~ theta) +
-  scale_color_viridis_c() +
-  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
-  ggtheme_plot()
-```
-
-```{r, eval = F}
-allocation %>%
-  filter(theta == 0.5, !trade) %>% 
-  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
-  geom_line(size = 1) +
-  facet_grid(~alpha) +
-  scale_color_viridis_c() +
-  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
-  ggtheme_plot()
-```
-
 # Reproducibility chunk

### 2019-06-24 scripts/content/fig_PNA_map.R

@@ -65,7 +65,6 @@ eez <- read_sf(dsn = here("data", "spatial", "EEZ_subset"),
 
 labels <- eez %>% 
   filter(ISO_Ter1 %in% VDS_countries) %>% 
-  # lwgeom::st_make_valid() %>% 
     mutate(label = countrycode(sourcevar = ISO_Ter1,
                                origin = "iso3c",
                                destination = "country.name"),
@@ -90,7 +89,8 @@ plot <- ggplot() +
   ggtheme_plot() +
   scale_color_manual(values = c("black", "red")) +
   scale_fill_manual(values = c("transparent", "steelblue")) +
-  theme(legend.position = "none")
+  theme(legend.position = "none") +
+  labs(x = "", y = "")
 
 ggsave(plot = plot,
        filename = here("docs", "img", "PNA_map.png"),

### 2019-08-02 docs/MS_behavioral.tex
Updated the MS for Nature submission

--- 2019-06-24 docs/Supplementary_materials.tex
@@
-% Use only LaTeX2e, calling the article.cls class and 12-point type.
-
 \documentclass[12pt]{article}
-
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-\usepackage{scicite}
 
@@
 
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
+%%% The "real" document content comes below...
 
-% The following parameters seem to provide a reasonable page setup.
-
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm
-\textheight 21cm
-\footskip 1.0cm
-
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
-% Include your paper's title here
-
-\title{Supplementary Materials for: ``Well-Designed Fishery Markets Enable Large-Scale Marine Conservation''}
-
-% Place the author information here.  Please hand-code the contact
-% information and notecalls; do *not* use \footnote commands.  Let the
-% author contact information appear immediately below the author names
-% as shown.  We would also prefer that you don't change the type-size
-% settings shown here.
-
-\author{Juan Carlos Villase\~{n}or-Derbez,$^{1\ast}$ John Lynham,$^{2}$ Christopher Costello$^{1}$\\
-\\
-\normalsize{$^{1}$Bren School of Environmental Science \& Management,}\\
-\normalsize{University of California at Santa Barbara, Santa Barbara, CA}\\
-\normalsize{$^{2}$Department of Economics, University of Hawaii at Manoa, Honolulu, HI}\\
-\\
-\normalsize{$^\ast$To whom correspondence should be addressed; E-mail: juancarlos@ucsb.edu.}
-}
-
-% Include the date command, but leave its argument blank.
-
-\date{}
-
-%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
+\title{Behavioral changes in fleet dynamics due to MPAs}
+\author{The Author}
+%\date{} % Activate to display a given date or no date (if empty),
+         % otherwise the current date is printed
 
 \begin{document}
-
-% Double-space the manuscript.
-
-\baselineskip24pt
-
-% Make the title.
-
 \maketitle
 
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\begin{abstract}
+A
+\end{abstract}
 
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\section{Supplementary Materials}
-
-\subsection{Model for marine conservation with effort markets}
-
-We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
-The price of fish is $p$, and catchability is given by $q$.
-These parameters are held constant across patches.
-
-Our purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-Suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters to all fishing; several consequences may arise.
-First, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in these waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-We focus on how design features of the market affect Country 1's incentives to create the marine reserve.
-
-\subsubsection{Fishery dynamics}
-
-In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
-The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
-
-Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
-In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
-The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
-
-$$
-\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_1-cE_1^\beta
-$$
-
-\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
-
-Therefore, we can generalize the patch-level profit equation to:
-
-$$
-\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
-$$
-
-\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
-
-\begin{equation}
-\pi_i(E_i) = \frac{\partial \Pi_i}{\partial E_i} = pqX_i\Omega_i - \beta cE_i^{\beta-1}
-\label{eqn:marginal_profit}
-\end{equation}
-
-In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
-effort level on the high seas ($E_{10}$) is a result of open access dynamics.
-Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
-
-\begin{equation}
-E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
-\label{eqn:effort_hs}
-\end{equation}
-
-Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
-Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
-
-$$
-\pi_i = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
-$$
-
-\noindent We can solve for $E_i$ and obtain:
-
-\begin{equation}
-	\begin{split}
-		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
-		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
-		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_i}{\beta c} \\
-		E_i &= \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-	\end{split}
-\label{eqn:demands}
-\end{equation}
-
-Equation \ref{eqn:demands} tells us patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
-A vessel-day scheme establishes a cap on total effort allowed.
-This means that fishing effort from Patches 1 - 9 must add up to this limit.
-Therefore, total allowable effort in the fishery is given by:
-
-\begin{equation}
-\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-\label{eqn:Ebar}
-\end{equation}
-
-\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
-
-\subsubsection{Stock dynamics}
-
-Patch-level harvest is then determined by effort and stock size:
-
-\begin{equation}
-H_i = qE_iX_i\Omega_i
-\label{eqn:harvest}
-\end{equation}
-
-\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
-The entire stock then grows logistically according to:
-
-\begin{equation}
-X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
-\label{eqn:grow}
-\end{equation}
-
-\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
-After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
-
-\begin{equation}
-X_{i,t+1} = f_iX_{t+1}
-\label{eqn:disperse}
-\end{equation}
-
-\subsubsection{Vessel-day revenues}
-
-The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
-
-\begin{equation}
-\omega_i = \pi_iE_i
-\label{eqn:license_revenue}
-\end{equation}
-
-\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
-This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
-But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
-Thus, the spillover benefits of increasing $R$ are never completely captured.
-
-\subsubsection{Simulations and parameterization}
-
-We calibrate our model to loosely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
-
-\begin{table}[H]
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{l|r|l}
-\hline
-Parameter & Value & Source\\
-\hline
-MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
-\hline
-$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
-\hline
-K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
-\hline
-$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
-\hline
-$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
-\hline
-$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
-\hline
-$r$ & 5.700000e-01 & From Fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
-\hline
-$\beta$ & 1.300000e+00 & Standard\\
-\hline
-p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
-\hline
-q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
-\hline
-c & 1.800000e+02 & -\\
-\hline
-f & 1.000000e-01 & Biomass is equally distributed between patches ($f_i = 0.1$)\\
-\hline
-\end{tabular}}
-\end{table}
-
-\noindent We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
-In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
-For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
-We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
-We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
-This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
-
-The second scenario allows trading.
-We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
-We then implement a spatial closure in Patch 1.
-This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
-Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
-This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
-We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
-
-Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
-
-In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
-This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
-After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery forward 50 years in time.
-At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
-
-$$
-E_{i,t+1}^* = \alpha
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{E}_{{t-\tau}}}
-	\right)
-	+
-(1 - \alpha)
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{X}_{t-\tau}} \right)
-$$
-
-\noindent where $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight on historical biomass ($B_i$).
-We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
-The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
-We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
-
-\subsection{Data}
-
-Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
-These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
-
-The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014, and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels and vessel activity.
-The addition of new satellites affects all vessels in the same way.
-
-Our displaced group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
-Vessels in the non-displaced group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
-Together, these vessels represent more than 20 million geo-referenced positions for which we know activity (fishing or not fishing).
-We perform three sample restrictions as a robustness check.
-The first restriction excludes all Chinese vessels, the second excludes all PNA vessels, and the third excludes US and Taiwanese vessels.
-
-Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org Shapefiles for Marine Protected Areas (PIPA and PNMS) come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
-
-\subsection{Empirical Analysis}
+\section{Placeholder here}
 
@@
 \ref{fig:nino_plot}) to control for the responses that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
+
+\begin{figure}
+\centering
+\includegraphics{img/nino_plot.png}
+\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
+\end{figure}
 
@@
 We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
-
-\subsubsection{Crowding effect}
-
-\begin{equation}
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
-\label{eqn:sp_corr}
-\end{equation}
-
-We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented on January 1\textsuperscript{st} of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
-The $\mu$ coefficient captures the effect of the NINO4 anomaly.
-
-We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface (Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation (Table \ref{tab:sp_corr}).
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
-
-\subsubsection{Effort redistribution}
-
-We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
-Non-displaced vessels serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas (Fig \ref{fig:fishing_raster_diff}).
-
-\subsubsection{Revenues and catches}
-
-We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency\footnote{https://www.ffa.int/node/2050} (FFA) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}A).
-For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
-
-Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
-\ref{fig:catches}).
-Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
-
-\subsubsection{Data and code availability}
-
-All analyses were performed in R version 3.5.3 \cite{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
-
-\clearpage
-
-\FloatBarrier
-
-\section{Supplementary tables and figures}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/vessel_day_price_no_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
-\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) when there is no trading.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/effort_and_revenues.pdf}
-	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-patch movement ($\theta$), and with and without trading.
-With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.
-The exact opposite relationship holds without trading: effort remains fixed as revenue declines with increasing $R$.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/nino_plot.png}
-\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/fishing_raster_diff.png}
-\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas.
-Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
-Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
-Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
-\end{figure}
 
@@
 
+\subsubsection{Crowding effect}
+
+\begin{equation}
+y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
+\label{eqn:sp_corr}
+\end{equation}
+
+We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
+1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
+For this reason, we fit a 4th degree polynomial to our monthly indices.
+We do so by centering our time series of crowding indices on the day of implementation.
+Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
+For example, since PIPA was implemented on January 1\textsuperscript{st} of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
+Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
+We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
+The $\mu$ coefficient captures the effect of the NINO4 anomaly.
+
+We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface (Fig \ref{fig:fishing_raster_diff}).
+These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
+\ref{fig:sp_corr}).
+The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
+Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation (Table \ref{tab:sp_corr}).
+We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
+
 \begin{landscape}
@@
 
-\begin{figure}
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/total_PNA_revenues.pdf}
-	\caption{\label{fig:total_PNA_revenues}Total revenues for all PNA countries combined.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/catches.pdf}
-	\caption{\label{fig:catches}Financial indicators for PNA countries.
-A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
-Vertical dashed line in both plots denotes implementation of PIPA.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
-The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
-Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_ts_plot.pdf}
-\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the proposed PNMS boundaries.}
-\end{figure}
-
 \clearpage
@@
 \bibliography{references}
-
-\bibliographystyle{Science}
+\bibliographystyle{nature}
 

### 2019-08-02 docs/Markets_Conservation_aug_02.tex
Updated the MS for Nature submission

--- 2019-06-24 docs/Markets_Conservation_June19.tex
@@
 \documentclass[12pt]{article}
-
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-\usepackage{scicite}
 
@@
 \usepackage{hyperref}
-\usepackage{pdflscape}
-
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
-
-% The following parameters seem to provide a reasonable page setup.
 
@@
 
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
-% Include your paper's title here
-
-\title{Fishery Markets and Large-Scale Marine Conservation}
+\title{Well-Designed Environmental Markets Enable Conservation}
 
@@
 % Place your abstract within the special {sciabstract} environment.
-\begin{sciabstract}
+\begin{abstract}
 Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of Large-Scale Marine Protected Areas (LSMPAs), and ask whether a country that commits to large-scale conservation is destined to suffer commensurate losses in fishery revenue.
-We use a combination of spatial bioeconomic modeling and vessel-tracking data from before and after LSMPA implementation to assess how market design incentivizes, or penalizes conservation.
-The answer hinges on two design features.
-First, only when trading of rights is allowed across countries can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Second, when rights are allocated between countries, the allocation must depend only on biological features, and not on economic factors such as a country's past effort or catch.
-Otherwise, the allocation process acts as a punishment to the conserving country.
-Overall, these results show that seemingly innocuous design features of a fishery management system can have indelible impacts on a country's willingness to engage in large-scale conservation.
-Our results are confirmed with an empirical case study from the Phoenix Islands Protected Area, one of the world's largest marine reserves.
-With the right market design, countries may be able to meet international conservation goals without incurring large costs.
-\end{sciabstract}
+We study this question in the context of environmental markets for fishing rights and Marine Protected Areas.
+We combine spatial bioeconomic modeling and real-world vessel-tracking data to assess how market design incentivizes or penalizes conservation.
+We show that the answer hinges on two design features of the market.
+First, only when trading of rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
+Second, allocation of rights must depend only on biological features, and not on economic factors such as a country's past effort or catch.
+Overall, these results show that environmental markets can incentivize conservation, but that seemingly innocuous design features of environmental markets can have indelible impacts on a nation's willingness to engage in large-scale conservation.
+\end{abstract}
 
-Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world \cite{dinerstein_2019}.
-Currently only about 3\% of the world's ocean is strongly protected \cite{sala_2018}, and these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, highlighting the importance of considering potential losses \cite{smith_2010,mallin_2019}.
+\clearpage
+
+\section{Main}
+
+Environmental markets have been proposed as instruments for resource management and conservation \cite{arsel_2012,sullivan_2013}.
+Rights-based approaches internalize the social costs and can solve a diverse set of environmental issues \cite{libecap_2009}.
+For example, implementation of individual transferable quotas in fisheries management can prevent fisheries collapse and reduce the ``race to fish'' \cite{costello_2008,birkenbach_2017}, and tradable emissions permits can reduce air pollution \cite{joskow_1998}.
+Rights-based resource management can facilitate management and incentivize investments, but will it facilitate or impede conservation?
+The answer must depend on how markets are designed, which ultimately shape incentives and the decission making process.
+We explore the role of market design features in incentivizing or limitting conservation in the context of markets for fishing rights and Marine Protected Areas (MPAs).
+
+Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world\cite{oleary_2016}.
+Currently only about 3\% of the world's oceans are strongly protected \cite{sala_2018}, but these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing.
 What incentives might motivate a country to engage in such large-scale marine protection?
 Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
+Fishing effort markets, where nations sell fishing rights to fishing vessels, may provide a mechanism to incentivize large-scale marine conservation.
+Here we show how the market can be designed (if new) or modified (if already existing) to incentivize large-scale marine conservation.
 
-This is not just a theoretical curiosity; we are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a nine-country coalition of Pacific island states that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
-These waters account for 14.5 million km\textsuperscript{2} (four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
+We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
+Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
+These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
+The PNA manages the tuna purse seine fishery using a vessel-day scheme (VDS) where total fishing effort is capped at 45,000 vessel-days.
+These are allocated across the nine nations, which then sell them to fishing vessels.
+Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
-Even if the closure creates net benefits to the world, and perhaps even to tuna fisheries Pacific-wide, the economic loss to the conserving country could still be extremely large, and may prevent it from engaging in conservation.
-We show how a rights-based fisheries market can be designed or modified  to ensure that the conserving country is rewarded, not punished, for large-scale conservation.
+In 2015, Kiribati implemented the Phoenix Islands Protected Area and Palau will close 80 of it's national waters by December 2020.
+We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solutions can incentivize conservation.
 
@@
 A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}.
-In the context of fishery markets, we find that two market design features, trading and allocation rules, are pivotal in determining the incentives for large-scale marine conservation.
-But why would trading and allocation rules affect the incentives for conservation?
+In the context of fishing effort markets, we find that two market design features are pivotal in determining the incentives for large-scale marine conservation: trading and allocation rules.
+But why would these affect the incentives for conservation?
 Consider the incentives for a country to close 100\% of its waters.
@@
 The rules for how fishing rights are allocated across countries are equally important.
-Suppose rights are allocated each year based on the previous year's fishing - the more a country fishes, the more it gets allocated the next year.
+Suppose rights are allocated each year based on the previous year's fishing effort: the more a country fishes, the more it gets allocated the next year.
 This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.
 
-To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA countries and the high seas.
+\subsection{Designing markets for conservation}
+
+To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
 Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
@@
 We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see Supplementary Materials).
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see the Methods section for a details).
 
-A spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 if trading between countries is not allowed (Fig.
+We first simulate a fishery where trading between countries is not allowed, and find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
 \ref{fig:PNA_model}A).
-Closing a greater proportion of the patch results in greater costs.
 Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock, a reserve reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
-\ref{fig:vessel_day_price_no_trading_plot}).
+Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
+S1).
 When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig.
-\ref{fig:profits_PNA_notKIR_no_trading_plot}) and the high seas.
+S2) and the high seas.
 
@@
 But increased biomass in other patches causes prices in Patches 2 to 8 to increase.
-As a result, rights from Patch 1 are traded to Patches 2 to 9, until vessel-day prices are the same across all patches (Fig.
-\ref{fig:vessel_day_price_with_trading_plot}).
+As a result, vessel-days from Patch 1 are traded to Patches 2 to 9, until prices are the same across all patches (Fig.
+S3).
 Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
-\ref{fig:PNA_model}).
+\ref{fig:PNA_model}B).
+With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
+S4).
 Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
@@
 
+We have shown that trading significantly reduces the costs of conservation.
 However, a new problem arises.
 How should rights be re-allocated every year?
-To analyze the consequences of different allocation rules on conservation incentives, we simulate the fishery 50 years into the future and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
 We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
@@
 However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{i.e.} the biomass within a country's waters), and not on fishing effort, countries may be incentivized to engage in large-scale marine conservation.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing effort, the incentives are sustained through time.
 
-A recent LSMPA was implemented in PNA waters, providing the ideal empirical setting to test our predictions.
+\subsection{Markets and conservation in practice}
+
+An MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
 In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
@@
 Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
-The remaining 221 vessels were not continuously observed before and after, and we refer to these as ``other vessels''.
+The remaining 221 vessels were not continuously observed before and after but are included in our analyses, and we refer to these as ``other vessels''.
 
-How did PIPA change vessel fishing locations?
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff}).
+Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, and into other PNA countries' waters (Fig.
+S5 - S6).
 Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
-\ref{fig:empirical}A-B).
+\ref{fig:empirical}).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
@@
 \ref{fig:empirical}A).
-Detailed analyses of vessel-level behavioral changes and crowding effects associated with PIPA implementation are included in our Supplementary Materials (Figs.
-\ref{fig:fishing_raster_diff}, \ref{fig:sp_corr}, and \ref{fig:all_panels}; and Tables \ref{tab:sp_corr} and \ref{tab:main_DID}).
 
@@
 \ref{fig:empirical}C).
-The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig. \ref{fig:empirical}C-D).
+The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig.
+\ref{fig:empirical}D).
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
 This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig.
-\ref{fig:effort_and_revenues}).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. \ref{fig:total_PNA_revenues}), despite the PIPA closure.
+S4).
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
+S8), despite the PIPA closure.
 
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline (10,500 non-tradable vessel-days) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine (700 tradable vessel-days) fishing activity (Figs.
-\ref{fig:plw_2018} and \ref{fig:plw_ts_plot}).
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
+S10-S11).
 While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
@@
 
-International goals over the next decade have set ambitious targets for marine conservation which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,roberts_2017,dinerstein_2019,ban_2019}.
-Our results show that a few key design features of a market can have indelible impacts on a country’s willingness to engage in large-scale conservation.
-Just like property rights can prevent fisheries collapse \cite{costello_2008}, properly designed fishery markets can reduce costs and provide the right incentives for effective large-scale marine conservation.
+In our study, only one of the countries considers the implementation of a protected area.
+However, an important aspect to consider is that of cooperative conservation.
+Consider the case where two nations contain high and low proportions of habitat that must be protected.
+Should both nations try to attain the same conservation targets of say, 30\% protection of their respective extension?
+Or is there a more cost-effective scenario that maximizes conservation but minimizes costs, and what would the role of environmental markets be in achieving it?
+Furthrer research should explore the role of heterogeneous costs and benefits between users, and the way in which these can shape conservation outcomes.
+
+The use of environmental markets for conservation is a common but contended approach among conservation scientists \cite{sandbrook_2019}.
+One of the driving concerns is that markets may create the wrong incentives that would lead to undesirable outcomes.
+Effective environmental markets should be designed to incentivize and sustain conservation \cite{adams_2014}.
+We show that rights-based management can provide incentives for large-scale conservation.
+However, we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
+In the case of fishing rigths and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
+
+International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}.
+Our work shows how well-designed environmental markets can reduce costs and provide the right incentives for effective large-scale conservation.
+
+\clearpage
+
+\section{Methods}
+
+\subsection{Bioeconomic model}
+
+We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
+Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
+The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
+The price of fish is $p$, and catchability is given by $q$.
+These parameters are held constant across patches.
+
+\subsubsection{Fishery dynamics}
+
+In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
+The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+
+Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
+Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
+In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
+The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
+
+$$
+\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_1-cE_1^\beta
+$$
+
+\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
+Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
+
+Therefore, we can generalize the patch-level profit equation to:
+
+$$
+\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
+$$
+
+\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
+
+\begin{equation}
+\pi_i(E_i) = \frac{\partial \Pi_i}{\partial E_i} = pqX_i\Omega_i - \beta cE_i^{\beta-1}
+\label{eqn:marginal_profit}
+\end{equation}
+
+In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics.
+Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
+Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
+
+\begin{equation}
+E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
+\label{eqn:effort_hs}
+\end{equation}
+
+Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
+Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
+
+$$
+\pi_i = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
+$$
+
+\noindent Solving for $E_i$ we obtain:
+
+\begin{equation}
+E_i = \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+\label{eqn:demands}
+\end{equation}
+
+Equation \ref{eqn:demands} tells us the patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
+A vessel-day scheme establishes a cap on total effort allowed.
+This means that fishing effort from Patches 1 - 9 must add up to this limit (45,000 vessel-days).
+Therefore, total allowable effort in the fishery is given by:
+
+\begin{equation}
+\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
+\label{eqn:Ebar}
+\end{equation}
+
+\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
+
+\subsubsection{Stock dynamics}
+
+Patch-level harvest is then determined by effort and stock size:
+
+\begin{equation}
+H_i = qE_iX_i\Omega_i
+\label{eqn:harvest}
+\end{equation}
+
+\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
+The entire stock then grows logistically according to:
+
+\begin{equation}
+X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
+\label{eqn:grow}
+\end{equation}
+
+\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
+After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
+
+\begin{equation}
+X_{i,t+1} = f_iX_{t+1}
+\label{eqn:disperse}
+\end{equation}
+
+\subsubsection{Vessel-day revenues}
+
+The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
+
+\begin{equation}
+\omega_i = \pi_iE_i
+\label{eqn:license_revenue}
+\end{equation}
+
+\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
+This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
+Thus, the spillover benefits of increasing $R$ are never completely captured.
+Information on model parameterization is provided in our Supplementary Materials.
+
+\subsubsection{Simulations}
+
+We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
+In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
+For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
+We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
+We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
+This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
+
+The second scenario allows trading.
+We start again by solving for the high seas to obtain total effort.
+Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
+We then implement a spatial closure in Patch 1.
+This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
+Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
+This increases effort in these patches, which reduces escapement and therefore biomass.
+This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
+We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
+Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
+
+Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
+In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
+Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
+The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
+
+In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
+This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
+To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
+At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
+
+$$
+E_{i,t+1}^* = \alpha
+\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{E}_{{t-\tau}}}
+	\right)
+	+
+(1 - \alpha)
+\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{X}_{t-\tau}} \right)
+$$
+
+\noindent where $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight on historical biomass ($B_i$).
+We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
+The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
+We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
+
+\subsection{Empirical case study}
+
+\subsubsection{Vessel tracking data and MPAs}
+
+Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
+These broadcast messages can be received by satellites and land-based antennas.
+We use AIS data provided by Global Fishing Watch \cite{kroodsma_2018} to track 313 tuna purse seiners that fished within the PNA.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, 28 ``non-displaced vessels'' never fished in PIPA waters, and  221 ``other vessels'' were not continuously observed before and after.
+Together, these vessels represent more than 20 million geo-referenced positions.
+
+We use these data to calculate the number of vessel-days that the 313 purse seiners spent in each PNA country and in PNA waters as a whole.
+The vessel-day equivalent of a day of fishing depends on vessel size, a measure used to control for effort creep.
+A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
+Vessel length is an observable characteristic in our dataset, and therefore we make the pertinent corrections when calculating vessel days.
+
+Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org.
+Shapefiles for Marine Protected Areas (Phoenix Islands Protected Area and Palau National Marine Sanctuary) come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
+All analyses were performed in R version 3.5.3 \cite{rcore_2018}.
+
+\subsubsection{Revenues and catches}
+
+We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
+\ref{fig:empirical}C; Fig.
+S8 - S9).
+For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
 
 \bibliography{references}
+\bibliographystyle{nature}
 
-\bibliographystyle{Science}
+\section{Supplementary Information}
+
+Supplementary Information is linked to the online version of the paper at www.nature.com/nature
+
+\section{Acknowledgements}
+
+Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program.
+
+\section{Author Contributions}
+
+All authors contributed equally.
+
+\section{Author information}
+
+Reprints and permissions information is available at www.nature.com/reprints.
+The authors declare no competing interests.
+Correspondence and requests for materials should be addressed to juancarlos@ucsb.edu.
 
@@
 \FloatBarrier
-
-\section*{Figures}
 
@@
 \includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA.
 Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 BEGIN APPENDIX		 %%%%%%%%%%%%%
-%%%%%%%%%%%%%		 					 %%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\FloatBarrier
-
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
-
-\section{Supplementary Materials}
-
-\subsection{Model for marine conservation with effort markets}
-
-We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
-The price of fish is $p$, and catchability is given by $q$.
-These parameters are held constant across patches.
-
-Our purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-Suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters to all fishing; several consequences may arise.
-First, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in these waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-We focus on how design features of the market affect Country 1's incentives to create the marine reserve.
-
-\subsubsection{Fishery dynamics}
-
-In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
-The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
-
-Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
-In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
-The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
-
-$$
-\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_1-cE_1^\beta
-$$
-
-\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
-
-Therefore, we can generalize the patch-level profit equation to:
-
-$$
-\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
-$$
-
-\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
-
-\begin{equation}
-\pi_i(E_i) = \frac{\partial \Pi_i}{\partial E_i} = pqX_i\Omega_i - \beta cE_i^{\beta-1}
-\label{eqn:marginal_profit}
-\end{equation}
-
-In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
-effort level on the high seas ($E_{10}$) is a result of open access dynamics.
-Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
-
-\begin{equation}
-E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
-\label{eqn:effort_hs}
-\end{equation}
-
-Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
-Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
-
-$$
-\pi_i = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
-$$
-
-\noindent We can solve for $E_i$ and obtain:
-
-\begin{equation}
-	\begin{split}
-		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
-		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
-		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_i}{\beta c} \\
-		E_i &= \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-	\end{split}
-\label{eqn:demands}
-\end{equation}
-
-Equation \ref{eqn:demands} tells us patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
-A vessel-day scheme establishes a cap on total effort allowed.
-This means that fishing effort from Patches 1 - 9 must add up to this limit.
-Therefore, total allowable effort in the fishery is given by:
-
-\begin{equation}
-\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-\label{eqn:Ebar}
-\end{equation}
-
-\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
-
-\subsubsection{Stock dynamics}
-
-Patch-level harvest is then determined by effort and stock size:
-
-\begin{equation}
-H_i = qE_iX_i\Omega_i
-\label{eqn:harvest}
-\end{equation}
-
-\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
-The entire stock then grows logistically according to:
-
-\begin{equation}
-X_{t+1} = e_t + e^{r \times \frac{e}{K}}
-\label{eqn:grow}
-\end{equation}
-
-\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
-After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
-
-\begin{equation}
-X_{i,t+1} = f_iX_{t+1}
-\label{eqn:disperse}
-\end{equation}
-
-\subsubsection{Vessel-day revenues}
-
-The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
-
-\begin{equation}
-\omega_i = \pi_iE_i
-\label{eqn:license_revenue}
-\end{equation}
-
-\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
-This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
-But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
-Thus, the spillover benefits of increasing $R$ are never completely captured.
-
-\subsubsection{Simulations and parameterization}
-
-We calibrate our model to loosely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.
-
-\input{tab/parameters.tex}
-
-\noindent We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
-In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
-For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
-We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
-We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
-This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
-
-The second scenario allows trading.
-We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
-We then implement a spatial closure in Patch 1.
-This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
-Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
-This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
-We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
-
-Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
-
-In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
-This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
-After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery forward 50 years in time.
-At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
-
-$$
-E_{i,t+1}^* = \alpha
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{E}_{{t-\tau}}}
-	\right)
-	+
-(1 - \alpha)
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{X}_{t-\tau}} \right)
-$$
-
-\noindent where $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight on historical biomass ($B_i$).
-We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
-The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
-We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
-
-\subsection{Data}
-
-Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
-These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
-
-The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014, and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels and vessel activity.
-The addition of new satellites affects all vessels in the same way.
-
-Our displaced group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
-Vessels in the non-displaced group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
-Together, these vessels represent more than 20 million geo-referenced positions for which we know activity (fishing or not fishing).
-We perform three sample restrictions as a robustness check.
-The first restriction excludes all Chinese vessels, the second excludes all PNA vessels, and the third excludes US and Taiwanese vessels.
-
-\subsection{Empirical Analysis}
-
-ENSO events are known to drive the location of fish and the behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
-For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
-However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns.
-While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
-Our analyses incorporate the monthly NINO4 anomaly index (Fig.
-\ref{fig:nino_plot}) to control for the responses that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-
-\subsubsection{Behavioral changes}
-
-We attempt to identify the response of vessels to the PIPA closure.
-We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest (Figure \ref{fig:all_panels}).
-We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
-
-Our main specification is the following:
-
-$$
-log(y_{i,t}) = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
-\label{eqn:did}
-$$
-
-\noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$.
-The transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ in period $t$.
-A dummy variable $P_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
-$D_i$ is a dummy variable indicating whether a vessel belongs to the displaced ($D_i = 1$) or non-displaced ($D_i = 0$) group.
-$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between displaced and non-displaced groups, and $\beta_3$ is our parameter of interest: the difference-in-differences estimate capturing the treatment effect.
-Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
-All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated (Table \ref{tab:main_DID}).
-
-We find no evidence of displaced vessels fishing more after the implementation and, in fact, observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$; Fig.
-\ref{fig:all_panels}; Table \ref{tab:main_DID}).
-Likewise, we observe a 3.4\% decrease in fishing hours relative to total at-sea hours ($p < 0.01$).
-Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
-
-\subsubsection{Crowding effect}
-
-\begin{equation}
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
-\label{eqn:sp_corr}
-\end{equation}
-
-We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented on January 1\textsuperscript{st} of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
-The $\mu$ coefficient captures the effect of the NINO4 anomaly.
-
-We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface (Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation (Table \ref{tab:sp_corr}).
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
-
-\subsubsection{Effort redistribution}
-
-We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
-Non-displaced vessels serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas (Fig \ref{fig:fishing_raster_diff}).
-
-\subsubsection{Revenues and catches}
-
-We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency\footnote{https://www.ffa.int/node/2050} (FFA) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}A).
-For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
-
-Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
-\ref{fig:catches}).
-Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
-
-\subsubsection{Data and code availability}
-
-All analyses were performed in R version 3.5.3 \cite{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
-
-\clearpage
-
-\FloatBarrier
-
-\section{Supplementary tables and figures}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/vessel_day_price_no_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
-\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) when there is no trading.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/effort_and_revenues.pdf}
-	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-patch movement ($\theta$), and with and without trading.
-With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.
-The exact opposite relationship holds without trading: effort remains fixed as revenue declines with increasing $R$.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/nino_plot.png}
-\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/fishing_raster_diff.png}
-\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas.
-Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
-Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
-Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
-\end{figure}
-
-\begin{landscape}
-	\input{tab/main_DID}
-\end{landscape}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/all_panels.pdf}
-	\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing events, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
-Dashed vertical lines indicate the addition of new AIS satellites.
-Solid vertical line indicates the closure of PIPA.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/other_specifications.pdf}
-	\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates for our variables of interest using different model specifications.
-Table \ref{tab:main_DID} reports estimates for models with month and flag fixed effects, and NINO4 index (\emph{i.e.} green dots).}
-\end{figure}
-
-\begin{landscape}
-	\input{tab/DID_without_CHN}
-\end{landscape}
-
-\begin{landscape}
-	\input{tab/DID_without_PNA}
-\end{landscape}
-
-\begin{landscape}
-	\input{tab/DID_without_USA_TWN}
-\end{landscape}
-
-\begin{landscape}
-\input{tab/sp_corr}
-\end{landscape}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
-\end{figure}
-
-\begin{landscape}
-\input{tab/KIR_sp_corr}
-\end{landscape}
-
-\begin{figure}
-\centering
-\includegraphics{img/KIR_sp_corr.pdf}
-\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/total_PNA_revenues.pdf}
-	\caption{\label{fig:total_PNA_revenues}Total revenues for all PNA countries combined.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/catches.pdf}
-	\caption{\label{fig:catches}Financial indicators for PNA countries.
-A) Total annual purse seine catch by EEZ and, B) Total annual value of purse seine catch by EEZ.
-Vertical dashed line in both plots denotes implementation of PIPA.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_2018.png}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
-The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
-Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_ts_plot.pdf}
-\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the proposed PNMS boundaries.}
-\end{figure}
-
 \end{document}

### 2019-08-02 docs/Supplementary_materials.tex
Updated the MS for Nature submission

@@
 \usepackage{hyperref}
-\usepackage{pdflscape}
+
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm
+\textheight 21cm
+\footskip 1.0cm
 
@@
 
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm
-\textheight 21cm
-\footskip 1.0cm
-
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
 % Include your paper's title here
 
-\title{Supplementary Materials for: ``Well-Designed Fishery Markets Enable Large-Scale Marine Conservation''}
+\title{Supplementary Materials for: ``Well-Designed Environmental Markets Enable Conservation''}
 
@@
 
-\subsection{Model for marine conservation with effort markets}
-
-We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
-The price of fish is $p$, and catchability is given by $q$.
-These parameters are held constant across patches.
-
-Our purpose is to examine how the VDS affects a country's incentives for large-scale conservation.
-Suppose that Country 1 considers closing a portion $R$ (between 0 and 1) of its waters to all fishing; several consequences may arise.
-First, the area available to fish in Country 1 is now limited, which could reduce the amount of money fishing firms are willing to pay for a day of fishing in these waters.
-Second, to the extent that catch is reduced in Country 1, fish may become more abundant elsewhere; this could imply an increase in the lease price to fish in the other eight PNA countries' waters because the VDS price reflects the profit from fishing in a country, which depends crucially on the abundance of fish.
-For the same reason, the increase in abundance could attract new entrants on the high seas, who could quickly dissipate the benefits there.
-We focus on how design features of the market affect Country 1's incentives to create the marine reserve.
-
-\subsubsection{Fishery dynamics}
-
-In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
-The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
-
-Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
-In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
-The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
-
-$$
-\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_1-cE_1^\beta
-$$
-
-\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
-
-Therefore, we can generalize the patch-level profit equation to:
-
-$$
-\Pi_i(E_i,X_i, R_i) = pqE_iX_i\Omega_i-cE_i^\beta
-$$
-
-\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
-
-\begin{equation}
-\pi_i(E_i) = \frac{\partial \Pi_i}{\partial E_i} = pqX_i\Omega_i - \beta cE_i^{\beta-1}
-\label{eqn:marginal_profit}
-\end{equation}
-
-In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
-effort level on the high seas ($E_{10}$) is a result of open access dynamics.
-Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
-
-\begin{equation}
-E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
-\label{eqn:effort_hs}
-\end{equation}
-
-Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
-Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
-
-$$
-\pi_i = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
-$$
-
-\noindent We can solve for $E_i$ and obtain:
-
-\begin{equation}
-	\begin{split}
-		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
-		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
-		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_i}{\beta c} \\
-		E_i &= \left(\frac{pqX_i\Omega_i - \pi_i}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-	\end{split}
-\label{eqn:demands}
-\end{equation}
-
-Equation \ref{eqn:demands} tells us patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
-A vessel-day scheme establishes a cap on total effort allowed.
-This means that fishing effort from Patches 1 - 9 must add up to this limit.
-Therefore, total allowable effort in the fishery is given by:
-
-\begin{equation}
-\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
-\label{eqn:Ebar}
-\end{equation}
-
-\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
-
-\subsubsection{Stock dynamics}
-
-Patch-level harvest is then determined by effort and stock size:
-
-\begin{equation}
-H_i = qE_iX_i\Omega_i
-\label{eqn:harvest}
-\end{equation}
-
-\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
-The entire stock then grows logistically according to:
-
-\begin{equation}
-X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
-\label{eqn:grow}
-\end{equation}
-
-\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
-After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
-
-\begin{equation}
-X_{i,t+1} = f_iX_{t+1}
-\label{eqn:disperse}
-\end{equation}
-
-\subsubsection{Vessel-day revenues}
-
-The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
-
-\begin{equation}
-\omega_i = \pi_iE_i
-\label{eqn:license_revenue}
-\end{equation}
-
-\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
-This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
-But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
-Thus, the spillover benefits of increasing $R$ are never completely captured.
-
-\subsubsection{Simulations and parameterization}
+\subsection{Model parameterization}
 
@@
 \hline
-$B_c/B_{msy}$ & 5.100000e-01 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
+$B_c/B_{msy}$ & 0.51 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
 \hline
@@
 \hline
-$r$ & 5.700000e-01 & From Fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
+$r$ & 0.57 & From FishBase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
 \hline
-$\beta$ & 1.300000e+00 & Standard\\
+$\beta$ & 1.3 & Standard\\
 \hline
-p & 1.100000e+03 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
+p & 1100 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
 \hline
@@
 \hline
-c & 1.800000e+02 & -\\
+c & 1800 & Estimated to match cost and revenue structures\\
 \hline
-f & 1.000000e-01 & Biomass is equally distributed between patches ($f_i = 0.1$)\\
+f & 0.1 & Biomass is equally distributed between patches\\
 \hline
@@
 
-\noindent We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
-In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
-For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
-We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
-We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
-This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
-
-The second scenario allows trading.
-We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
-We then implement a spatial closure in Patch 1.
-This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
-Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
-This increases effort in these patches, which reduces escapement and therefore biomass.
-This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
-We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
-
-Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
-In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ.\footnote{This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}.} Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
-
-In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
-This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
-After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery forward 50 years in time.
-At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
-
-$$
-E_{i,t+1}^* = \alpha
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{E}_{{t-\tau}}}
-	\right)
-	+
-(1 - \alpha)
-\left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\sum_{\tau = 0}^{\hat{\tau}}\bar{X}_{t-\tau}} \right)
-$$
-
-\noindent where $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight on historical biomass ($B_i$).
-We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
-The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
-We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
-
-\subsection{Data}
-
-Automatic Identification Systems (AIS) are on-board devices that provide at-sea safety and prevent ship collisions by broadcasting vessel position, course, and activity to surrounding vessels.
-These broadcast messages can be received by satellites and land-based antennas.
-GFW then uses machine learning algorithms (convolutional neural networks) on the broadcast messages to infer type and location of fishing events \cite{kroodsma_2018}.
-
-The amount of data gathered by GFW is dependent on the number of antennas and satellites that can receive signals.
-The total satellite count increased from 3 to 6 on June 1\textsuperscript{st} 2014, and then from 6 to 10 on January 1\textsuperscript{st} 2016.
-This causes an increase in the number of \emph{received} AIS messages (\emph{i.e.} points), and therefore an apparent increase in the number of vessels and vessel activity.
-The addition of new satellites affects all vessels in the same way.
-
-Our displaced group contains all purse seiners (n = 64) that fished within PIPA at least once before the announcement, and that continued to fish elsewhere after the January 2015 implementation.
-Vessels in the non-displaced group meet the following two conditions: i) never fished within PIPA waters from 2012-2015, and ii) vessels have fished in surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA closure (n = 28).
-Together, these vessels represent more than 20 million geo-referenced positions for which we know activity (fishing or not fishing).
-We perform three sample restrictions as a robustness check.
-The first restriction excludes all Chinese vessels, the second excludes all PNA vessels, and the third excludes US and Taiwanese vessels.
-
-Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org Shapefiles for Marine Protected Areas (PIPA and PNMS) come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
-
 \subsection{Empirical Analysis}
-
-ENSO events are known to drive the location of fish and the behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-We do our best to control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking the non-displaced vessels as a ``control'' group that is equally affected by the environmental variation.
-For example, we observe that both displaced and non-displaced vessels shifted their effort post-PIPA to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu.
-However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}).
-Our analysis shows that sea surface temperature variation does have an effect on our crowding and behavioral outcomes, but that by itself it does not explain the observed patterns.
-While environmental variation certainly influences fishing behavior, policy and management interventions such as moratoriums and spatial closures can have even larger effects \cite{kroodsma_2018}.
-Our analyses incorporate the monthly NINO4 anomaly index (Fig.
-\ref{fig:nino_plot}) to control for the responses that fish and vessels might have to environmental variation \cite{lehodey_1997,kroodsma_2018,aqorau_2018}.
-
-\subsubsection{Behavioral changes}
-
-We attempt to identify the response of vessels to the PIPA closure.
-We use daily fishing and non-fishing hours, daily proportion of fishing vs.
-non-fishing hours, daily distance traveled (km), distance from shore (km) and distance from home port (km) for fishing events, and proportion of total fishing hours allocated to Kiribati waters and PNA waters as our main outcomes of interest (Figure \ref{fig:all_panels}).
-We compare these outcomes before and after the implementation of PIPA using a Difference-in-Differences approach.
-
-Our main specification is the following:
-
-$$
-log(y_{i,t}) = \alpha + \beta_1 P_t + \beta_2 D_i + \beta_3 P_t \times D_i + \phi_t + \gamma_i + \epsilon_{i,t}
-\label{eqn:did}
-$$
-
-\noindent where $log(y_{i,t})$ is the hyperbolic-sine transformation\footnote{$ln\left(y + \sqrt{1 + y^2}\right)\rightarrow ln(2y)$.
-The transformation was not applied to the proportion of fishing to non-fishing hours.} of the outcome of interest for vessel $i$ in period $t$.
-A dummy variable $P_t$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 for all dates following PIPA implementation.
-$D_i$ is a dummy variable indicating whether a vessel belongs to the displaced ($D_i = 1$) or non-displaced ($D_i = 0$) group.
-$\alpha$ is the standard intercept term, $\beta_1$ captures the temporal trend, $\beta_2$ captures the initial difference between displaced and non-displaced groups, and $\beta_3$ is our parameter of interest: the difference-in-differences estimate capturing the treatment effect.
-Finally, $\phi_t$ and $\gamma_i$ represent month and flag dummies that account for seasonality or country-level management interventions.
-All regression coefficients were estimated via ordinary least squares, and heteroskedasticity-robust standard errors were calculated (Table \ref{tab:main_DID}).
-
-We find no evidence of displaced vessels fishing more after the implementation and, in fact, observe a 27.5\% decrease relative to non-displaced vessels ($p < 0.01$; Fig.
-\ref{fig:all_panels}; Table \ref{tab:main_DID}).
-Likewise, we observe a 3.4\% decrease in fishing hours relative to total at-sea hours ($p < 0.01$).
-Displaced vessels traveled 23.3\% less distance, and fishing events occurred 32.9\% and 16.9\% closer to shore and to port, respectively.
-These changes in distance from shore and port are likely explained by redistribution, as we observe that displaced vessels fished less in Kiribati and PNA waters, compared to the trend observed for non-displaced vessels ($p < 0.01$).
-We do not observe changes in non-fishing at-sea hours (\emph{i.e.} a proxy for search time) and fishing hours on the High Seas.
-We repeat this analysis for sample restrictions where we exclude all Chinese vessels (Table \ref{tab:DID_without_CHN}), all PNA-owned vessels (Table \ref{tab:DID_without_PNA}) and all Taiwanese and USA vessels (Table \ref{tab:DID_without_USA_TWN}) and find qualitatively the same responses.
-
-\subsubsection{Crowding effect}
-
-\begin{equation}
-y_t = \alpha + \beta_1 M_t + \beta_2 M_t^2 + \beta_3 M_t^3 + \beta_4 M_t ^4 + \sigma_s + \mu N_t + \epsilon_t
-\label{eqn:sp_corr}
-\end{equation}
-
-We test for a crowding effect using the specification in Equation \ref{eqn:sp_corr}. We have two different outcome variables:
-1) the number of cells that had fishing activity from displaced and non-displaced vessels per month and 2) the correlation of presence/absence of fishing events between both groups over one month.We allow for the possibility of three inflection points: 1) initial crowding due to MPA implementation, 2) When the crowding has reached its peak and starts to decrease, and 3) when this decrease potentially levels off.
-For this reason, we fit a 4th degree polynomial to our monthly indices.
-We do so by centering our time series of crowding indices on the day of implementation.
-Our explanatory variable is therefore the number of months ($M$) before or after the implementation.
-For example, since PIPA was implemented on January 1\textsuperscript{st} of 2015, December of 2014 has a value of -1 and Feb of 2015 would receive a value of 1.
-Note that we restrict the sample to our displaced and non-displaced vessels (vessels that show up in the dataset before PIPA implementation) to try to minimize bias from more and more vessels using AIS over time.
-We also include controls ($\sigma_s$) that captures the effect of additional satellites receiving AIS signals, which occurred on April 1st, 2014 and December 31st, 2015.
-The $\mu$ coefficient captures the effect of the NINO4 anomaly.
-
-We inspect the crowding effects that may arise by applying more (or the same) fishing effort over less fishing area by inspecting the spatial overlap between displaced and non-displaced vessels over a gridded surface (Fig \ref{fig:fishing_raster_diff}).
-These groups interacted more with each other after the implementation of PIPA (Table \ref{tab:sp_corr}, Fig.
-\ref{fig:sp_corr}).
-The number of cells with presence from both fleets and the spatial correlation between groups increases by a factor of four and three, respectively.
-Environmental variation may certainly drive this, but the NINO4 anomaly alone explained just 3\% and 7\% of the variation in our crowding measures, compared to the 70\% variation explained when accounting for PIPA implementation (Table \ref{tab:sp_corr}).
-We observe similar patterns when replicating the crowding exercise for Kiribati's EEZ only (Table \ref{tab:KIR_sp_corr}, Fig \ref{fig:KIR_sp_corr}).
 
@@
 
-\subsubsection{Revenues and catches}
-
-We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency\footnote{https://www.ffa.int/node/2050} (FFA) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}A).
-For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
-
-Total purse seine catch for each country's EEZ for the 1997 - 2016 period were also obtained from the FFA (Fig.
-\ref{fig:catches}).
-Catches in Kiribati waters decreased from 24,051 to 12,894 tonnes between 2015 and 2016 (46.3\% decrease).
-Similar decreases were observed for The Federated States of Micronesia (60.9\%), Papua New Guinea (43.4\%) and the Solomon Islands (58.5\%).
-In contrast, Tokelau (due south of PIPA) showed a 22.3\% increase in purse seine catch over the same period.
-
 \subsubsection{Data and code availability}
 
-All analyses were performed in R version 3.5.3 \cite{rcore_2018}. Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
+Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
 
@@
 \includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_with_trading_plot}PNA-wide vessel-day prices (vertical axis) with trading, for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$).}
 \end{figure}
@@
 \centering
-\includegraphics{img/nino_plot.png}
-\caption{\label{fig:nino_plot}NINO4 anomaly index. A) Map of the NINO4 region (5S-5N and 160E-150W). B) Time series of NINO4 anomaly from January, 1980 to December, 2018.}
-\end{figure}
-
-\begin{figure}
-\centering
 \includegraphics{img/fishing_raster_diff.png}
@@
 
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 9 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
-\hline \\[-1.8ex] 
- Constant & 0.495$^{***}$ & 3.607$^{***}$ & 0.075$^{***}$ & 4.440$^{***}$ & 12.998$^{***}$ & 12.462$^{***}$ & 3.709$^{***}$ & 4.456$^{***}$ & 2.429$^{***}$ \\ 
-  & (0.022) & (0.012) & (0.004) & (0.042) & (0.021) & (0.019) & (0.195) & (0.151) & (0.415) \\ 
-  & & & & & & & & & \\ 
- Post & 0.846$^{***}$ & $-$0.227$^{***}$ & 0.138$^{***}$ & 0.112$^{***}$ & 0.271$^{***}$ & 0.275$^{***}$ & 0.943$^{***}$ & 1.129$^{***}$ & 0.709$^{**}$ \\ 
-  & (0.018) & (0.009) & (0.003) & (0.031) & (0.014) & (0.014) & (0.141) & (0.110) & (0.284) \\ 
-  & & & & & & & & & \\ 
- Displaced & 0.136$^{***}$ & 0.014$^{**}$ & 0.015$^{***}$ & 0.255$^{***}$ & 0.225$^{***}$ & 0.117$^{***}$ & 0.549$^{***}$ & 0.153 & $-$0.280 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.029) & (0.016) & (0.016) & (0.148) & (0.118) & (0.236) \\ 
-  & & & & & & & & & \\ 
- NINO4 & $-$0.014 & $-$0.001 & $-$0.001 & $-$0.411$^{***}$ & 0.167$^{***}$ & 0.064$^{***}$ & 0.357$^{***}$ & 0.137$^{**}$ & 0.484$^{***}$ \\ 
-  & (0.011) & (0.005) & (0.002) & (0.017) & (0.008) & (0.007) & (0.068) & (0.056) & (0.122) \\ 
-  & & & & & & & & & \\ 
- Post $\times$ Displaced & $-$0.243$^{***}$ & 0.013 & $-$0.034$^{***}$ & $-$0.210$^{***}$ & $-$0.285$^{***}$ & $-$0.157$^{***}$ & $-$0.586$^{***}$ & $-$0.403$^{***}$ & 0.338 \\ 
-  & (0.019) & (0.009) & (0.003) & (0.036) & (0.017) & (0.017) & (0.161) & (0.127) & (0.285) \\ 
-  & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 83,052 & 83,052 & 83,051 & 79,669 & 32,055 & 32,055 & 1,814 & 2,588 & 684 \\ 
-R$^{2}$ & 0.102 & 0.072 & 0.107 & 0.017 & 0.075 & 0.082 & 0.126 & 0.200 & 0.252 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/all_panels.pdf}
-	\caption{\label{fig:all_panels}Time series showing monthly averages for our nine variables of interest: A) Fishing hours, B) Non-fishing hours at-sea, C) Proportion of fishing hours to total hours at-sea, D) Distance traveled, E) Mean distance from port for fishing events, F) Mean distance from shore for fishing events, G) Monthly hours spent in Kiribati waters, H) Monthly hours spent in PNA waters, I) Monthly hours spent on the high seas.
-Dashed vertical lines indicate the addition of new AIS satellites.
-Solid vertical line indicates the closure of PIPA.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics{img/other_specifications.pdf}
-	\caption{\label{fig:other_specifications}Alternative difference-in-differences estimates for our variables of interest using different model specifications.
-Table \ref{tab:main_DID} reports estimates for models with month and flag fixed effects, and NINO4 index (\emph{i.e.} green dots).}
-\end{figure}
-
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_CHN}Difference-in-differences estimates for our 9 variables of interest after removing Chinese vessels.
-1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
-\hline \\[-1.8ex] 
- Constant & 0.058$^{***}$ & 3.863$^{***}$ & $-$0.003 & 4.829$^{***}$ & 13.817$^{***}$ & 13.161$^{***}$ & 4.007$^{***}$ & 4.515$^{***}$ & 2.909$^{***}$ \\ 
-  & (0.019) & (0.008) & (0.003) & (0.044) & (0.044) & (0.058) & (0.347) & (0.304) & (0.274) \\ 
-  & & & & & & & & & \\ 
- Post & 0.824$^{***}$ & $-$0.254$^{***}$ & 0.136$^{***}$ & 0.145$^{***}$ & 0.306$^{***}$ & 0.322$^{***}$ & 0.920$^{***}$ & 1.157$^{***}$ & 0.691$^{**}$ \\ 
-  & (0.019) & (0.010) & (0.003) & (0.034) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
-  & & & & & & & & & \\ 
- Displaced & 0.108$^{***}$ & 0.009 & 0.012$^{***}$ & 0.270$^{***}$ & 0.271$^{***}$ & 0.158$^{***}$ & 0.491$^{***}$ & 0.150 & $-$0.274 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.031) & (0.017) & (0.017) & (0.162) & (0.131) & (0.235) \\ 
-  & & & & & & & & & \\ 
- NINO4 & $-$0.012 & $-$0.007 & $-$0.001 & $-$0.380$^{***}$ & 0.164$^{***}$ & 0.061$^{***}$ & 0.365$^{***}$ & 0.122$^{**}$ & 0.464$^{***}$ \\ 
-  & (0.011) & (0.005) & (0.002) & (0.018) & (0.009) & (0.008) & (0.074) & (0.060) & (0.126) \\ 
-  & & & & & & & & & \\ 
- Post $\times$ Displaced & $-$0.212$^{***}$ & 0.040$^{***}$ & $-$0.031$^{***}$ & $-$0.282$^{***}$ & $-$0.338$^{***}$ & $-$0.205$^{***}$ & $-$0.558$^{***}$ & $-$0.412$^{***}$ & 0.374 \\ 
-  & (0.021) & (0.010) & (0.004) & (0.038) & (0.019) & (0.018) & (0.174) & (0.137) & (0.289) \\ 
-  & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 75,327 & 75,327 & 75,326 & 75,390 & 28,449 & 28,449 & 1,570 & 2,279 & 633 \\ 
-R$^{2}$ & 0.102 & 0.073 & 0.108 & 0.017 & 0.075 & 0.091 & 0.128 & 0.209 & 0.266 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_PNA}Difference-in-differences estimates for our 9 variables of interest after removing PNA vessels: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
-\hline \\[-1.8ex] 
- Constant & 0.512$^{***}$ & 3.559$^{***}$ & 0.083$^{***}$ & 4.499$^{***}$ & 13.165$^{***}$ & 12.667$^{***}$ & 3.271$^{***}$ & 4.066$^{***}$ & 2.876$^{***}$ \\ 
-  & (0.024) & (0.013) & (0.004) & (0.047) & (0.028) & (0.025) & (0.263) & (0.201) & (0.434) \\ 
-  & & & & & & & & & \\ 
- Post & 0.781$^{***}$ & $-$0.159$^{***}$ & 0.122$^{***}$ & 0.047 & 0.114$^{***}$ & 0.070$^{***}$ & 1.168$^{***}$ & 1.481$^{***}$ & 0.295 \\ 
-  & (0.022) & (0.012) & (0.004) & (0.043) & (0.023) & (0.022) & (0.226) & (0.180) & (0.333) \\ 
-  & & & & & & & & & \\ 
- Displaced & 0.202$^{***}$ & 0.040$^{***}$ & 0.019$^{***}$ & 0.437$^{***}$ & 0.165$^{***}$ & $-$0.015 & 0.817$^{***}$ & 0.533$^{***}$ & $-$0.408$^{*}$ \\ 
-  & (0.015) & (0.009) & (0.003) & (0.037) & (0.024) & (0.022) & (0.229) & (0.182) & (0.235) \\ 
-  & & & & & & & & & \\ 
- NINO4 & $-$0.019 & $-$0.0003 & $-$0.002 & $-$0.387$^{***}$ & 0.138$^{***}$ & 0.025$^{***}$ & 0.413$^{***}$ & 0.232$^{***}$ & 0.482$^{***}$ \\ 
-  & (0.012) & (0.006) & (0.002) & (0.020) & (0.010) & (0.009) & (0.080) & (0.066) & (0.156) \\ 
-  & & & & & & & & & \\ 
- Post $\times$ Displaced & $-$0.219$^{***}$ & $-$0.055$^{***}$ & $-$0.023$^{***}$ & $-$0.246$^{***}$ & $-$0.175$^{***}$ & 0.010 & $-$0.843$^{***}$ & $-$0.821$^{***}$ & 0.729$^{**}$ \\ 
-  & (0.024) & (0.012) & (0.004) & (0.046) & (0.026) & (0.024) & (0.243) & (0.195) & (0.341) \\ 
-  & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 64,560 & 64,560 & 64,559 & 64,625 & 22,654 & 22,654 & 1,366 & 1,928 & 511 \\ 
-R$^{2}$ & 0.093 & 0.069 & 0.099 & 0.022 & 0.063 & 0.066 & 0.127 & 0.203 & 0.214 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:DID_without_USA_TWN}Difference-in-differences estimates for our 9 variables of interest after removing US and Tawianese vessels.
-1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port for fishing events, 6) Daily mean distance from shore for fishing events, 7) Monthly fishing hours spent in Kiribati waters, 8) Monthly fishing hours spent in PNA waters, and 9) Monthly fishing hours in the high seas.
-Numbers in parentheses are heteroskedastic-robust standard errors.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{1pt}}lccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\ 
-\hline \\[-1.8ex] 
- Constant & 0.536$^{***}$ & 3.600$^{***}$ & 0.082$^{***}$ & 4.506$^{***}$ & 13.002$^{***}$ & 12.438$^{***}$ & 3.850$^{***}$ & 4.719$^{***}$ & 2.420$^{***}$ \\ 
-  & (0.023) & (0.012) & (0.004) & (0.043) & (0.022) & (0.020) & (0.209) & (0.158) & (0.419) \\ 
-  & & & & & & & & & \\ 
- Post & 0.796$^{***}$ & $-$0.217$^{***}$ & 0.130$^{***}$ & 0.021 & 0.290$^{***}$ & 0.291$^{***}$ & 0.870$^{***}$ & 0.894$^{***}$ & 0.732$^{**}$ \\ 
-  & (0.019) & (0.010) & (0.003) & (0.035) & (0.016) & (0.016) & (0.156) & (0.121) & (0.291) \\ 
-  & & & & & & & & & \\ 
- Displaced & 0.142$^{***}$ & 0.016$^{**}$ & 0.015$^{***}$ & 0.341$^{***}$ & 0.227$^{***}$ & 0.127$^{***}$ & 0.490$^{***}$ & $-$0.017 & $-$0.296 \\ 
-  & (0.013) & (0.007) & (0.002) & (0.031) & (0.018) & (0.017) & (0.163) & (0.126) & (0.239) \\ 
-  & & & & & & & & & \\ 
- NINO4 & $-$0.001 & $-$0.001 & 0.001 & $-$0.383$^{***}$ & 0.189$^{***}$ & 0.082$^{***}$ & 0.325$^{***}$ & 0.171$^{***}$ & 0.441$^{***}$ \\ 
-  & (0.011) & (0.006) & (0.002) & (0.019) & (0.009) & (0.008) & (0.075) & (0.063) & (0.122) \\ 
-  & & & & & & & & & \\ 
- Post $\times$ Displaced & $-$0.212$^{***}$ & $-$0.002 & $-$0.029$^{***}$ & $-$0.158$^{***}$ & $-$0.328$^{***}$ & $-$0.184$^{***}$ & $-$0.533$^{***}$ & $-$0.225 & 0.339 \\ 
-  & (0.021) & (0.010) & (0.004) & (0.039) & (0.019) & (0.018) & (0.175) & (0.138) & (0.291) \\ 
-  & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 73,717 & 73,717 & 73,716 & 73,778 & 26,920 & 26,920 & 1,546 & 2,236 & 660 \\ 
-R$^{2}$ & 0.095 & 0.072 & 0.102 & 0.021 & 0.077 & 0.094 & 0.111 & 0.169 & 0.256 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{9}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for all PNA waters.
-The first five columns represent different specifications for number of cells with presence of both fleets.
-Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels.
-The explanatory variable is the number of months before or after implementation of PIPA.
-Numbers in parentheses are heteroskedastic-robust standard errors.
-The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
-\hline \\[-1.8ex] 
- Constant & 78.04$^{***}$ & 84.64$^{***}$ & 60.96$^{***}$ & 66.73$^{***}$ & 80.62$^{***}$ & 0.41$^{***}$ & 0.42$^{***}$ & 0.37$^{***}$ & 0.38$^{***}$ & 0.38$^{***}$ \\ 
-  & (5.44) & (8.99) & (15.60) & (15.99) & (7.96) & (0.01) & (0.03) & (0.06) & (0.07) & (0.02) \\ 
-  & & & & & & & & & & \\ 
- M & 3.94$^{***}$ & 4.07$^{***}$ & 3.07$^{***}$ & 3.14$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{**}$ & 0.01$^{**}$ &  \\ 
-  & (0.30) & (0.35) & (0.97) & (1.04) &  & (0.001) & (0.001) & (0.003) & (0.004) &  \\ 
-  & & & & & & & & & & \\ 
- M $^2$ & $-$0.005 & $-$0.02 & 0.01 & $-$0.01 &  & $-$0.0001$^{***}$ & $-$0.0001 & $-$0.0001 & $-$0.0001 &  \\ 
-  & (0.02) & (0.03) & (0.03) & (0.03) &  & (0.0000) & (0.0001) & (0.0001) & (0.0001) &  \\ 
-  & & & & & & & & & & \\ 
- M $^3$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ &  \\ 
-  & (0.0003) & (0.0003) & (0.001) & (0.001) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
-  & & & & & & & & & & \\ 
- M $^4$ & 0.0000 & 0.0000 & 0.0000 & 0.0000 &  & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000 & 0.0000 &  \\ 
-  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
-  & & & & & & & & & & \\ 
- NINO4 &  & $-$8.09 &  & $-$10.39 & 19.76$^{**}$ &  & $-$0.01 &  & $-$0.01 & 0.07$^{***}$ \\ 
-  &  & (8.29) &  & (9.48) & (9.41) &  & (0.03) &  & (0.03) & (0.02) \\ 
-  & & & & & & & & & & \\ 
- $\sigma_1$ &  &  & 21.32 & 25.10 &  &  &  & 0.06 & 0.06 &  \\ 
-  &  &  & (19.49) & (22.49) &  &  &  & (0.08) & (0.08) &  \\ 
-  & & & & & & & & & & \\ 
- $\sigma_2$ &  &  & 5.30 & 3.19 &  &  &  & $-$0.01 & $-$0.02 &  \\ 
-  &  &  & (18.87) & (18.67) &  &  &  & (0.04) & (0.03) &  \\ 
-  & & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
-Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
-AIC & 796.937 & 797.991 & 799.477 & 799.97 & 919.583 & -187.208 & -185.269 & -184.916 & -183.233 & -97.386 \\ 
-Observations & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 \\ 
-R$^{2}$ & 0.79 & 0.79 & 0.79 & 0.80 & 0.03 & 0.70 & 0.70 & 0.71 & 0.71 & 0.07 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{img/sp_corr.pdf}
-\caption{\label{fig:sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B).
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies similar to those in the pre-PIPA period, but crowding effect does not decline to pre-implementation level and seems to stabilize.}
-\end{figure}
-
-\begin{landscape}
-\begin{table}[H] \centering 
-  \caption{\label{tab:KIR_sp_corr}Coefficient estimates for a fourth-degree polynomial fit to the measures of crowding for Kiribati EEZ only.
-The first five columns represent different specifications for number of cells with presence of both fleets.
-Columns 6 - 10 show coefficients for the spatial correlation for presence / absence of displaced and non-displaced vessels.
-The explanatory variable is the number of months before or after implementation of PIPA.
-Numbers in parentheses are heteroskedastic-robust standard errors.
-The last column of each group presents fits with only NINO4 anomaly index as an explanatory variable.}
-  \label{} 
-\footnotesize 
-\begin{tabular}{@{\extracolsep{0.1pt}}lcccccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\\[-1.8ex] & \multicolumn{5}{c}{Number of cells} & \multicolumn{5}{c}{Pearson's correlation coefficient} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
-\hline \\[-1.8ex] 
- Constant & 30.24$^{***}$ & 32.77$^{***}$ & 23.30$^{***}$ & 26.14$^{***}$ & 16.23$^{***}$ & 0.43$^{***}$ & 0.43$^{***}$ & 0.33$^{***}$ & 0.34$^{***}$ & 0.38$^{***}$ \\ 
-  & (2.43) & (4.16) & (4.59) & (5.49) & (2.37) & (0.03) & (0.05) & (0.07) & (0.08) & (0.03) \\ 
-  & & & & & & & & & & \\ 
- M & 1.29$^{***}$ & 1.34$^{***}$ & 1.00$^{***}$ & 1.06$^{***}$ &  & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{*}$ & 0.01 &  \\ 
-  & (0.14) & (0.17) & (0.27) & (0.30) &  & (0.002) & (0.002) & (0.01) & (0.01) &  \\ 
-  & & & & & & & & & & \\ 
- M $^2$ & $-$0.03$^{***}$ & $-$0.04$^{***}$ & $-$0.02$^{**}$ & $-$0.03$^{***}$ &  & 0.0000 & 0.0000 & 0.0001 & 0.0001 &  \\ 
-  & (0.01) & (0.01) & (0.01) & (0.01) &  & (0.0002) & (0.0002) & (0.0002) & (0.0002) &  \\ 
-  & & & & & & & & & & \\ 
- M $^3$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ &  & $-$0.0000$^{***}$ & $-$0.0000$^{***}$ & $-$0.0000$^{**}$ & $-$0.0000$^{**}$ &  \\ 
-  & (0.0001) & (0.0001) & (0.0002) & (0.0002) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
-  & & & & & & & & & & \\ 
- M $^4$ & 0.0000$^{***}$ & 0.0000$^{***}$ & 0.0000$^{**}$ & 0.0000$^{***}$ &  & $-$0.0000 & $-$0.0000 & $-$0.0000 & $-$0.0000 &  \\ 
-  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  & (0.0000) & (0.0000) & (0.0000) & (0.0000) &  \\ 
-  & & & & & & & & & & \\ 
- NINO4 &  & $-$3.10 &  & $-$4.19 & 9.93$^{***}$ &  & $-$0.001 &  & $-$0.02 & 0.11$^{***}$ \\ 
-  &  & (3.97) &  & (4.16) & (3.33) &  & (0.05) &  & (0.06) & (0.03) \\ 
-  & & & & & & & & & & \\ 
- $\sigma_1$ &  &  & 9.40 & 10.33 &  &  &  & 0.12 & 0.13 &  \\ 
-  &  &  & (5.92) & (6.35) &  &  &  & (0.09) & (0.09) &  \\ 
-  & & & & & & & & & & \\ 
- $\sigma_2$ &  &  & $-$2.46 & $-$3.84 &  &  &  & 0.02 & 0.01 &  \\ 
-  &  &  & (5.70) & (5.77) &  &  &  & (0.10) & (0.11) &  \\ 
-  & & & & & & & & & & \\ 
-\hline \\[-1.8ex] 
-NINO4 & No & Yes & No & Yes & Yes & No & Yes & No & Yes & Yes \\ 
-Satellites & No & No & Yes & Yes & No &  &  &  &  &  \\ 
-AIC & 654.294 & 655.536 & 655.482 & 656.125 & 724.58 & -65.872 & -63.873 & -63.481 & -61.572 & -35.895 \\ 
-Observations & 84 & 84 & 84 & 84 & 84 & 75 & 75 & 75 & 75 & 75 \\ 
-R$^{2}$ & 0.63 & 0.63 & 0.64 & 0.65 & 0.08 & 0.44 & 0.44 & 0.45 & 0.45 & 0.09 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table} 
-\end{landscape}
-
-\begin{figure}
-\centering
-\includegraphics{img/KIR_sp_corr.pdf}
-\caption{\label{fig:KIR_sp_corr}Number of cells that had displaced and non-displaced vessels (A) and spatial correlation in the presence-absence of each group per cell (B) for Kiribati's EEZ only.
-The solid lines represent the 4\textsuperscript{th} degree polynomial fit reported in \ref{tab:sp_corr}.
-Note that the late 2016 and early 2017 showed negative or neutral NINO4 anomalies, similar to those in the pre-PIPA period.}
-\end{figure}
-
 \begin{figure}
@@
 	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that take place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.}
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.
+The vertical lines represent the median of each year.}
 \end{figure}
@@
 
-\bibliography{references}
-
-\bibliographystyle{Science}
-
 \end{document}

### 2019-08-02 docs/old_ms/Markets_Conservation_july19.tex
Updated the MS for Nature submission

--- 2019-08-02 docs/Markets_Conservation_aug_02.tex
@@
 Rights-based approaches internalize the social costs and can solve a diverse set of environmental issues \cite{libecap_2009}.
-For example, implementation of individual transferable quotas in fisheries management can prevent fisheries collapse and reduce the ``race to fish'' \cite{costello_2008,birkenbach_2017}, and tradable emissions permits can reduce air pollution \cite{joskow_1998}.
+For example, individual transferable quotas in fisheries prevent fisheries collapse and reduce the ``race to fish'' \cite{costello_2008,birkenbach_2017}, and tradable emissions permits reduce air pollution \cite{joskow_1998}.
 Rights-based resource management can facilitate management and incentivize investments, but will it facilitate or impede conservation?
-The answer must depend on how markets are designed, which ultimately shape incentives and the decission making process.
+The answer must depend on how markets are designed.
 We explore the role of market design features in incentivizing or limitting conservation in the context of markets for fishing rights and Marine Protected Areas (MPAs).
@@
 We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see the Methods section for a details).
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see Methods).
 
@@
 \ref{fig:PNA_model}B).
-With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
-S4).
 Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
@@
 
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, and into other PNA countries' waters (Fig.
-S5 - S6).
+Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, but into other PNA countries' waters (Fig.
+S6).
 Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
-\ref{fig:empirical}).
+3A-B).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
@@
 By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Fig.
-\ref{fig:empirical}A).
+3A).
 
@@
 Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
-\ref{fig:empirical}C).
+3C).
 The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig.
-\ref{fig:empirical}D).
+3C-D).
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
@@
 At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
-S8), despite the PIPA closure.
+S13), despite the PIPA closure.
 
@@
 In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
-\ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
-S10-S11).
+4).
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Figs.
+S15 and S16).
 While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
@@
 Effective environmental markets should be designed to incentivize and sustain conservation \cite{adams_2014}.
-We show that rights-based management can provide incentives for large-scale conservation.
-However, we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
+We show rights-based management can provide incentives for large-scale conservation, but we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
 In the case of fishing rigths and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
@@
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}C; Fig.
-S8 - S9).
+\ref{fig:empirical}C).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
@@
 \includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA.
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) of the region of interest.
 Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.

### 2019-09-08 docs/Markets_Conservation_sept_07.tex
Moved docs around and finalized MS for submission to Nature

--- 2019-08-02 docs/Markets_Conservation_aug_02.tex
@@
 
-\title{Well-Designed Environmental Markets Enable Conservation}
+\title{Well-Designed Environmental Markets Enable Large-Scale Marine Conservation}
 
@@
 \begin{abstract}
-Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of environmental markets for fishing rights and Marine Protected Areas.
-We combine spatial bioeconomic modeling and real-world vessel-tracking data to assess how market design incentivizes or penalizes conservation.
-We show that the answer hinges on two design features of the market.
-First, only when trading of rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Second, allocation of rights must depend only on biological features, and not on economic factors such as a country's past effort or catch.
-Overall, these results show that environmental markets can incentivize conservation, but that seemingly innocuous design features of environmental markets can have indelible impacts on a nation's willingness to engage in large-scale conservation.
+While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas in their own waters.
+When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
+While this may be more-than-made-up-for through spillover of protected fish, these benefits typically accrue to other countries or the high seas.
+We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale marine conservation.
+By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are pivotal to encouraging such conservation.
+First, only when trading of fishing rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
+Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished.
+Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
 \end{abstract}
@@
 
-Environmental markets have been proposed as instruments for resource management and conservation \cite{arsel_2012,sullivan_2013}.
-Rights-based approaches internalize the social costs and can solve a diverse set of environmental issues \cite{libecap_2009}.
-For example, implementation of individual transferable quotas in fisheries management can prevent fisheries collapse and reduce the ``race to fish'' \cite{costello_2008,birkenbach_2017}, and tradable emissions permits can reduce air pollution \cite{joskow_1998}.
-Rights-based resource management can facilitate management and incentivize investments, but will it facilitate or impede conservation?
-The answer must depend on how markets are designed, which ultimately shape incentives and the decission making process.
-We explore the role of market design features in incentivizing or limitting conservation in the context of markets for fishing rights and Marine Protected Areas (MPAs).
+Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by making 30\% of the oceans off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy.
+But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
+At first glance, the answer is probably ``no''.
+Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who have been suggested as viable candidates for large closures \cite{mcleod_2019}.
+On the other hand, the closure may generate substantial ``spillover'' of fish and other benefits into adjacent waters which could, in principle, offset these losses.
+The problem with this argument is that for very large MPAs, these spillover benefits would accrue to other nations, with no obvious mechanism for the conserving country to recoup them.
+A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other.
+Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
 
-Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world\cite{oleary_2016}.
-Currently only about 3\% of the world's oceans are strongly protected \cite{sala_2018}, but these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing.
-What incentives might motivate a country to engage in such large-scale marine protection?
-Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
-Fishing effort markets, where nations sell fishing rights to fishing vessels, may provide a mechanism to incentivize large-scale marine conservation.
-Here we show how the market can be designed (if new) or modified (if already existing) to incentivize large-scale marine conservation.
-
-We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
+We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA).
+Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018}.
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
-The PNA manages the tuna purse seine fishery using a vessel-day scheme (VDS) where total fishing effort is capped at 45,000 vessel-days.
-These are allocated across the nine nations, which then sell them to fishing vessels.
-Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days.
+Vessel-days are allocated across the nine nations, which then lease them to fishing vessels.
+A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
+Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-In 2015, Kiribati implemented the Phoenix Islands Protected Area and Palau will close 80 of it's national waters by December 2020.
-We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solutions can incentivize conservation.
+In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020.
+We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how the market can be designed to incentivize conservation.
 
@@
 In the context of fishing effort markets, we find that two market design features are pivotal in determining the incentives for large-scale marine conservation: trading and allocation rules.
-But why would these affect the incentives for conservation?
+But why would these design features of a fisheries market affect the incentives for conservation?
 Consider the incentives for a country to close 100\% of its waters.
-Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries.
-If the conserving country could sell the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
-But if the conserving country was not allowed to sell these rights, then it would lose all of its fishing revenue.
+Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
+If the conserving country could lease the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
 The rules for how fishing rights are allocated across countries are equally important.
@@
 This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior.
+In the following section, we will show how trading and allocation rules can shape the incentives that may facilitate or hinder large-scale conservation.
+We will then make use of vessel-tracking data to analyze a real-world case of large-scale marine conservation under fishing effort markets.
 
@@
 
-To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
-Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
-Patch 10 represents the high seas, where fishing days are governed by economic conditions.
-We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries.
-In all cases, we solve for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
+To examine how market design incentivizes or punishes large scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
+Countries 1 to 9 represent the PNA countries, which operate under a vessel-day scheme where vessel-days are capped for each country and closely tracked.
+``Country'' 10 represents the high seas, where fishing days are unregulated and determined by prevailing economic conditions.
+We examine the effects of large-scale conservation in a single country (Country 1) under markets with and without trading between countries.
+In all cases, we solve the bioeconomic model for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
 We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see the Methods section for a details).
+We simulate these outcomes across a range of reserve sizes and assumptions about within-country stock movement (see the Methods section for details).
 
-We first simulate a fishery where trading between countries is not allowed, and find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+We first simulate a fishery where trading between countries is not allowed.
+This represents the status quo of any nation unilaterally engaging in large-scale conservation.
+Intuitively, we find that a spatial closure in Country 1 will always result in a loss in revenues to Country 1 (Fig.
 \ref{fig:PNA_model}A).
-Higher within-patch stock movement ($\theta$ = 0 implies no within-patch movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
+Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
 The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving patch (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
+Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
 S1).
-When countries cannot trade, the costs of conservation are incurred by Patch 1, but the benefits are received by the eight other patches (revenues increase between 0\% and 6\%; Fig.
+When countries cannot trade, the costs of conservation are incurred by Country 1, but the benefits are received by the eight other countries (revenues increase between 0\% and 6\% each; Fig.
 S2) and the high seas.
+This benchmark simulation highlights the misalignment of incentives, where a conservation-minded country incurs large costs and provides public benefits to other nations with no mechanism for recouping these benefits.
 
 How would trading between countries change these results?
-We simulate the same fishery, but now allow for vessel-days to be traded across patches.
-As before, a closure in Patch 1 lowers the value of vessel-days in that patch.
-But increased biomass in other patches causes prices in Patches 2 to 8 to increase.
-As a result, vessel-days from Patch 1 are traded to Patches 2 to 9, until prices are the same across all patches (Fig.
+We simulate the same fishery, but now allow for vessel-days to be traded across countries (as is the case for the PNA).
+As before, a closure in Country 1 lowers the value of vessel-days in that country (because the fishable water shrinks).
+But increased biomass in other countries causes their vessel day prices to increase.
+As a result, vessel-days from Country 1 are traded to Countries 2 to 9, until prices equalize across countries (Fig.
 S3).
-Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
-\ref{fig:PNA_model}B).
+Under this market design, revenue losses are less than 1\%, compared to the base case with no reserve (Fig.
+\ref{fig:PNA_model}B; note that the horizontal axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
+\ref{fig:PNA_model}A).
 With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
 S4).
-Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to allow trading (Fig.
 \ref{fig:PNA_model}C).
@@
 We have shown that trading significantly reduces the costs of conservation.
-However, a new problem arises.
-How should rights be re-allocated every year?
-We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
+However, a new question arises.
+How should rights be re-allocated every year once a country starts closing its waters to fishing?
+Customarily, the allocation of fishing effort rights is some formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}.
+We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation.
+We simulate a fishery operating with closures for 50 years and compare the resulting revenues to a fishery without any closures.
 We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
@@
 However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing effort, the incentives are sustained through time.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing effort, the incentives for conservation are sustained through time.
 
@@
 
-An MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
+In January 2015, Kiribati closed 11.5\% of its EEZ, effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}.
+By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}.
 We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters but fished within Kiribati's EEZ.
 The remaining 221 vessels were not continuously observed before and after but are included in our analyses, and we refer to these as ``other vessels''.
 
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, and into other PNA countries' waters (Fig.
-S5 - S6).
-Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
+Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, and into other PNA countries' waters (Figs.
+S5 - S7).
+Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Fig.
 \ref{fig:empirical}).
-The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters.
+The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.
 On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
@@
 \ref{fig:empirical}C).
-The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati in 2014 to 2016 (Fig.
+The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig.
 \ref{fig:empirical}D).
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
-This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the exact opposite relationship would hold (Fig.
+This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
 S4).
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
 S10-S11).
-While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
+
+While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model suggests that they must also adopt a biomass-based allocation rule to ensure long-term financial security in the presence of large-scale conservation.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation.
+By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation in a market-based setting.
 
 In our study, only one of the countries considers the implementation of a protected area.
-However, an important aspect to consider is that of cooperative conservation.
-Consider the case where two nations contain high and low proportions of habitat that must be protected.
-Should both nations try to attain the same conservation targets of say, 30\% protection of their respective extension?
-Or is there a more cost-effective scenario that maximizes conservation but minimizes costs, and what would the role of environmental markets be in achieving it?
-Furthrer research should explore the role of heterogeneous costs and benefits between users, and the way in which these can shape conservation outcomes.
+However, an interesting extension would be cooperative conservation.
+In that setting, a group of countries could coordinate on an optimized large-scale strategical closure, perhaps using vessel-day trading as a means of compensation, in a matter similar to the model above.
+Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting.
 
-The use of environmental markets for conservation is a common but contended approach among conservation scientists \cite{sandbrook_2019}.
-One of the driving concerns is that markets may create the wrong incentives that would lead to undesirable outcomes.
-Effective environmental markets should be designed to incentivize and sustain conservation \cite{adams_2014}.
-We show that rights-based management can provide incentives for large-scale conservation.
-However, we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
-In the case of fishing rigths and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
-
+The use of environmental markets for conservation is a common but contentious approach among conservation scientists and resource managers \cite{sandbrook_2019}.
+One of the driving concerns is that markets may create incentives that lead to undesirable outcomes, thus emphasizing the need for careful design.
+We show that individual countries have little incentive to undertake large-scale marine conservation, but that this incentive can be reversed if those countries are in an appropriately-designed market-based setting.
+For the market to create these incentives, certain design features are paramount.
+In the case of fishing rights and MPAs, cross-country transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the conservation incentive.
 International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}.
-Our work shows how well-designed environmental markets can reduce costs and provide the right incentives for effective large-scale conservation.
+Our work shows how well-designed environmental markets can provide the right incentives for effective large-scale marine conservation.
 
@@
 
-We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure.
-Patches 1 - 9 operate under a vessel-day scheme, and Patch 10 represents the high seas and other areas not managed under a VDS.
-The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all patches annually.
+We model a 10 country discrete-time meta-population system, where Country 1 is considering a spatial closure.
+Countries 1 - 9 operate under a vessel-day scheme, and Country 10 represents the high seas and other areas not managed under a VDS.
+The stock of fish in each country is relatively stationary within a single fishing season, but  growth from escapement redistributes across all countries annually.
 The price of fish is $p$, and catchability is given by $q$.
-These parameters are held constant across patches.
+These parameters are held constant across countries.
 
@@
 
-In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period.
-The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+In the absence of a reserve, the revenue for vessels in country $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in country $i$ at the beginning of a period.
+The cost of fishing in country $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
 
-Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$).
-Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the patch.
-In this patch, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
-The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:
+Country 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total country ($R \in[0,1)$).
+Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country.
+In this country, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
+The parameterization of movement and reserve size imply that profit from fishing Country 1 is given by:
 
@@
 
-\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  [0, 1)$) and within-patch fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Patch 1 implements a reserve.
+\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of country ($R =  [0, 1)$) and within-country fish movement ($\theta$).
+Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Country 1 implements a reserve.
 
-Therefore, we can generalize the patch-level profit equation to:
+Therefore, we can generalize the country-level profit equation to:
 
@@
 
-\noindent The above equations imply that the marginal profit from the last unit of effort in a patch are given by:
+\noindent The above equations imply that the marginal profit from the last unit of effort in a country are given by:
 
@@
 
-In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics.
-Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
+In practice, the effort levels in each country are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics.
+Therefore, we assume that effort continues to enter Country 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
 Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
@@
 
-Under VDS-operated patches, however, profits from the marginal unit of effort should equate to the price of fishing in the patch.
-Therefore vessel-day price for patches under VDS ($i = (1, 9)$) is  given by:
+Under VDS-operated countries, however, profits from the marginal unit of effort should equate to the price of fishing in the country.
+Therefore vessel-day price for countries under VDS ($i = (1, 9)$) is  given by:
 
@@
 
-Equation \ref{eqn:demands} tells us the patch-level effort for a given patch-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
+Equation \ref{eqn:demands} tells us the country-level effort for a given country-specific stock size ($X_i$) and vessel-day price ($\pi_i$).
 A vessel-day scheme establishes a cap on total effort allowed.
-This means that fishing effort from Patches 1 - 9 must add up to this limit (45,000 vessel-days).
+This means that fishing effort from Countries 1 - 9 must add up to this limit (45,000 vessel-days).
 Therefore, total allowable effort in the fishery is given by:
@@
 
-\noindent In the above Equation, vessel-day price is the same across all patches when trading is allowed; the subindex is dropped for this parameter.
+\noindent In the above Equation, vessel-day price is the same across all countries when trading is allowed; the subindex is dropped for this parameter.
 
@@
 
-Patch-level harvest is then determined by effort and stock size:
+Country-level harvest is then determined by effort and stock size:
 
@@
 
-\noindent Therefore, escapement in patch $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
+\noindent Therefore, escapement in country $i$ in time period $t$ is the difference between initial stock size and harvest given by $e_{i,t} = X_{i,t} - H_{i,t}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{i,t}$.
 The entire stock then grows logistically according to:
@@
 \noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
-After the stock grows, a constant and patch-specific fraction $f_i$ of the total stock redistributes to patch $i$, so:
+After the stock grows, a constant and country-specific fraction $f_i$ of the total stock redistributes to country $i$, so:
 
@@
 
-The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:
+The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, country-level license revenues are given by:
 
@@
 
-\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Patch 1, for a given level of effort and stock size.
-This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches.
+\noindent Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would decrease harvest and increase escapement in Country 1, for a given level of effort and stock size.
+This would lead to an increase in total stock size (Equation \ref{eqn:grow}) and a benefit to all the other countries.
 But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents.
@@
 
-We run simulations under two market designs and test the model across a range of reserve sizes and within-patch movement parameters.The first scenario does not allow trading.
-In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9.
-For patch 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
-We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest.
+We run simulations under two market designs and test the model across a range of reserve sizes and within-country movement parameters.The first scenario does not allow trading.
+In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among Countries 1-9.
+For Country 10, we solve for Eq \ref{eqn:effort_hs} until biomass converges to match $B_{now}$.
+We then proceed to ``close'' a portion of Country 1, and calculate the vessel-day price in Country 1 given that only $X_i\Omega_i$ biomass is available for harvest.
 We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$).
-This produces a measure of the cost of implementing a spatial closure of size $R$ in Patch 1.
+This produces a measure of the cost of implementing a spatial closure of size $R$ in Country 1.
 
@@
 We start again by solving for the high seas to obtain total effort.
-Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 patches, this equilibrium is the same as the first step above.
-We then implement a spatial closure in Patch 1.
-This essentially lowers the price fishers would be willing to pay to fish in a patch with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Patch 1.
-Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Patch 1 are sold to Patches 2 - 9.
-This increases effort in these patches, which reduces escapement and therefore biomass.
+Since a closure is not in effect and VDS-managed effort is equally distributed across the 9 countries, this equilibrium is the same as the first step above.
+We then implement a spatial closure in Country 1.
+This essentially lowers the price fishers would be willing to pay to fish in a country with only biomass $X_i\Omega_i$, lowering demand for vessel-days in Country 1.
+Countries 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from Country 1 are sold to Countries 2 - 9.
+This increases effort in these countries, which reduces escapement and therefore biomass.
 This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
 We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
-Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in Patch 1.
+Like before, we calculate vessel-day revenues to each country and compare them to a case with no reserve in Country 1.
 
-Annual vessel-days are often allocated based on a combination of historical within-patch effort and biomass.
+Annual vessel-days are often allocated based on a combination of historical within-country effort and biomass.
 In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
-Trading vessel-days to other countries would imply that historical within-patch effort declines through time.
-The allocated days to a patch with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
+Trading vessel-days to other countries would imply that historical within-country effort declines through time.
+The allocated days to a country with a full spatial closure would eventually be reduced to just the 40\% based on biomass.
 
-In the trading scenario above, effort from Patch 1 (with the reserve) is traded to other patches.
+In the trading scenario above, effort from Country 1 (with the reserve) is traded to other countries.
 This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
-To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of patch-level effort and biomass.
-At the end of every time period (a year), vessel-days are re-allocated to each patch based on the following rule:
+To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of country-level effort and biomass.
+At the end of every time period (a year), vessel-days are re-allocated to each country based on the following rule:
 
@@
 We use $\hat{\tau}= 6$ to obtain a moving mean of 7 years for these measures.
-The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Patch 1 are the sales.
+The difference between allocated days ($E_i^*$) and used days (determined by Equation \ref{eqn:demands}) for Country 1 are the sales.
 We then calculate vessel-day revenues to each country over the 50-year time horizon and compare to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).
@@
 
-Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program.
+Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program. John Lynham was supported by the Conservation Strategy Fund.
 
@@
 Each line represents a possible value of stock movement ($\theta$; line color).
-The revenue losses to Patch 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
-Costs are shown for Patch 1 when there is no trading (A) and when trading is allowed (B).
+The revenue losses to Country 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
+Costs are shown for Country 1 when there is no trading (A) and when trading is allowed (B).
 Costs avoided by trading are shown in (C).
@@
 \includegraphics{img/allocation_cost_plot.pdf}
-\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Patch 1 under different allocation rules.
+\caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Country 1 under different allocation rules.
 Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis).

### 2019-09-08 docs/Supplementary_materials.tex
Moved docs around and finalized MS for submission to Nature

@@
 
-\title{Supplementary Materials for: ``Well-Designed Environmental Markets Enable Conservation''}
+\title{Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''}
 
@@
 \hline
-f & 0.1 & Biomass is equally distributed between patches\\
+f & 0.1 & Biomass is equally distributed between countries\\
 \hline
@@
 \includegraphics{img/vessel_day_price_no_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) for the patch with spatial closure and other patches (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) for the country with spatial closure and other countries (left - right, respectively) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
-\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for patches 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$) when there is no trading.}
+\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for countries 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}PNA-wide vessel-day prices (vertical axis) with trading, for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-patch movement ($\theta$).}
+\caption{\label{fig:vessel_day_price_with_trading_plot}PNA-wide vessel-day prices (vertical axis) with trading, for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$).}
 \end{figure}
@@
 	\includegraphics{img/effort_and_revenues.pdf}
-	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-patch movement ($\theta$), and with and without trading.
+	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading.
 With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.

### 2019-09-08 docs/old_ms/Markets_Conservation_aug_26.tex
Moved docs around and finalized MS for submission to Nature

--- 2019-08-02 docs/Markets_Conservation_aug_02.tex
@@
 \begin{abstract}
-Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?
-We study this question in the context of environmental markets for fishing rights and Marine Protected Areas.
-We combine spatial bioeconomic modeling and real-world vessel-tracking data to assess how market design incentivizes or penalizes conservation.
-We show that the answer hinges on two design features of the market.
+While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have been unwilling to unilaterally undertake large-scale conservation in their waters.
+When a country closes a significant fraction of its waters to fishing, it loses significant fishery revenue; while this may be more-than-made-up-for through spillover of fish, those benefits typically accrue to other countries, rendering the large-scale marine conservation proposition untenable.
+In the context of expansive marine conservation in the Pacific, we show that thoughtful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale conservation.
+By combining vessel-level data before and after conservation is implemented, with a model of cross-country trading of rights, we show that two market design features are crucial.
 First, only when trading of rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Second, allocation of rights must depend only on biological features, and not on economic factors such as a country's past effort or catch.
-Overall, these results show that environmental markets can incentivize conservation, but that seemingly innocuous design features of environmental markets can have indelible impacts on a nation's willingness to engage in large-scale conservation.
+Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished.
+Overall, these results provide a pathway that incentivizes countries to engage in large-scale marine conservation in a market-based setting.
 \end{abstract}
@@
 
-Environmental markets have been proposed as instruments for resource management and conservation \cite{arsel_2012,sullivan_2013}.
-Rights-based approaches internalize the social costs and can solve a diverse set of environmental issues \cite{libecap_2009}.
-For example, implementation of individual transferable quotas in fisheries management can prevent fisheries collapse and reduce the ``race to fish'' \cite{costello_2008,birkenbach_2017}, and tradable emissions permits can reduce air pollution \cite{joskow_1998}.
-Rights-based resource management can facilitate management and incentivize investments, but will it facilitate or impede conservation?
-The answer must depend on how markets are designed, which ultimately shape incentives and the decission making process.
-We explore the role of market design features in incentivizing or limitting conservation in the context of markets for fishing rights and Marine Protected Areas (MPAs).
-
 Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world\cite{oleary_2016}.
 Currently only about 3\% of the world's oceans are strongly protected \cite{sala_2018}, but these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing.
-What incentives might motivate a country to engage in such large-scale marine protection?
+To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, yet few studies examine the incentives or economic mechanisms that would motivate a country to engage in such large-scale marine protection.
 Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
-Fishing effort markets, where nations sell fishing rights to fishing vessels, may provide a mechanism to incentivize large-scale marine conservation.
+If all countries acted unilaterally, the answer is probably ``no''.
+Losing this important source of revenue would cripple many fishing-dependent economies and the spillover benefits from conservation would accrue to others.
+
+How would this answer change if fishing countries were able to capture the benefits of this spillover?
+We find that fishing effort markets, where nations trade the right to fish for a certain number of days, may provide a viable mechanism that incentivizes large-scale marine conservation.
 Here we show how the market can be designed (if new) or modified (if already existing) to incentivize large-scale marine conservation.
@@
 The PNA manages the tuna purse seine fishery using a vessel-day scheme (VDS) where total fishing effort is capped at 45,000 vessel-days.
-These are allocated across the nine nations, which then sell them to fishing vessels.
+These are allocated across the nine nations, which then lease them to fishing vessels.
 Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
@@
 In 2015, Kiribati implemented the Phoenix Islands Protected Area and Palau will close 80 of it's national waters by December 2020.
-We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solutions can incentivize conservation.
+We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solutions can be designed to incentivize conservation.
 
@@
 Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries.
-If the conserving country could sell the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
-But if the conserving country was not allowed to sell these rights, then it would lose all of its fishing revenue.
+If the conserving country could lease the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
 The rules for how fishing rights are allocated across countries are equally important.
@@
 S10-S11).
-While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
+
+While trading will allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model suggests that they must also advocate for a biomass-based allocation rule to ensure long-term financial security.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
@@
 Or is there a more cost-effective scenario that maximizes conservation but minimizes costs, and what would the role of environmental markets be in achieving it?
-Furthrer research should explore the role of heterogeneous costs and benefits between users, and the way in which these can shape conservation outcomes.
+Further research should explore the role of heterogeneous costs and benefits between users, and the way in which these can shape conservation outcomes.
 
-The use of environmental markets for conservation is a common but contended approach among conservation scientists \cite{sandbrook_2019}.
+The use of environmental markets for conservation is a common but contentious approach among conservation scientists \cite{sandbrook_2019}.
 One of the driving concerns is that markets may create the wrong incentives that would lead to undesirable outcomes.
@@
 However, we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
-In the case of fishing rigths and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
+In the case of fishing rights and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
 

### 2019-09-08 docs/old_ms/Markets_Conservation_july27.tex
Moved docs around and finalized MS for submission to Nature

--- 2019-08-02 docs/old_ms/Markets_Conservation_july19.tex
@@
 Thus, the spillover benefits of increasing $R$ are never completely captured.
-Information on model parameterization is provided in our Supplementary Materials.
 
-\subsubsection{Simulations}
+\subsubsection{Simulations and parameterization}
 
@@
 The vessel-day equivalent of a day of fishing depends on vessel size, a measure used to control for effort creep.
-A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
-Vessel length is an observable characteristic in our dataset, and therefore we make the pertinent corrections when calculating vessel days.
+A day of activity by vessels smaller than 50 m long counts as half a vessel-day, a day of activity by vessels 50 - 80 m counts as one day, and a day of activity by vessels larger than 80 m counts as 1.5 vessel-days.
+Vessel length is an observable variable in our dataset, and therefore we make the pertinent corrections for vessel days.
 

### 2019-09-08 docs/old_ms/Markets_Conservation_sept_03.tex
Moved docs around and finalized MS for submission to Nature

--- 2019-09-08 docs/old_ms/Markets_Conservation_aug_26.tex
@@
 \begin{abstract}
-While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have been unwilling to unilaterally undertake large-scale conservation in their waters.
-When a country closes a significant fraction of its waters to fishing, it loses significant fishery revenue; while this may be more-than-made-up-for through spillover of fish, those benefits typically accrue to other countries, rendering the large-scale marine conservation proposition untenable.
+While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have been unwilling to unilaterally undertake large-scale conservation in their own waters.
+When a country closes a significant fraction of its waters to fishing, it loses significant fishery revenue; while this may be more-than-made-up-for through spillover of protected fish, these benefits typically accrue to other countries or the high seas.
 In the context of expansive marine conservation in the Pacific, we show that thoughtful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale conservation.
-By combining vessel-level data before and after conservation is implemented, with a model of cross-country trading of rights, we show that two market design features are crucial.
+By combining a model of cross-country trading of rights
+with vessel-level data before and after a large-scale conservation action is implemented, we show that two market design features are crucial.
 First, only when trading of rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
 Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished.
-Overall, these results provide a pathway that incentivizes countries to engage in large-scale marine conservation in a market-based setting.
+Overall, these results provide a
+template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
 \end{abstract}
@@
 
-Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world\cite{oleary_2016}.
+Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protected areas around the world \cite{oleary_2016}.
 Currently only about 3\% of the world's oceans are strongly protected \cite{sala_2018}, but these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
@@
 If all countries acted unilaterally, the answer is probably ``no''.
-Losing this important source of revenue would cripple many fishing-dependent economies and the spillover benefits from conservation would accrue to others.
-
+Losing this important source of revenue would cripple many fishing-dependent economies and the spillover benefits from conservation would accrue to weakly regulated fisheries on the high seas.
 How would this answer change if fishing countries were able to capture the benefits of this spillover?
-We find that fishing effort markets, where nations trade the right to fish for a certain number of days, may provide a viable mechanism that incentivizes large-scale marine conservation.
+We find that international fishing effort markets, where nations trade the right to fish with each other, may provide a viable mechanism that incentivizes large-scale marine conservation.
 Here we show how the market can be designed (if new) or modified (if already existing) to incentivize large-scale marine conservation.
 
-We are motivated by a real-world institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna fishing in its members' waters\cite{havice_2013,aqorau_2018}.
+We are motivated by a real-world but relatively unknown institution called the Parties to the Nauru Agreement (PNA).
+Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna fishing in its members' waters \cite{havice_2013,aqorau_2018}.
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
-The PNA manages the tuna purse seine fishery using a vessel-day scheme (VDS) where total fishing effort is capped at 45,000 vessel-days.
-These are allocated across the nine nations, which then lease them to fishing vessels.
-Member nations derive enormous benefits from leasing tuna fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days.
+A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
+Vessel-days are allocated across the nine nations, which then lease them to fishing vessels.
+Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-In 2015, Kiribati implemented the Phoenix Islands Protected Area and Palau will close 80 of it's national waters by December 2020.
-We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solutions can be designed to incentivize conservation.
+In 2015, Kiribati created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020.
+We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solution can be designed to incentivize conservation.
 
@@
 Consider the incentives for a country to close 100\% of its waters.
-Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of the other countries.
+Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
 If the conserving country could lease the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
@@
 To examine how market design incentivizes or punishes large scale conservation, we develop a 10-patch spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
-Patches 1 to 9 represent each country and they operate under a ``vessel-day scheme'' (VDS), where vessel-days are capped for each country and closely tracked.
-Patch 10 represents the high seas, where fishing days are governed by economic conditions.
+Patches 1 to 9 represent each country and they operate under a vessel-day scheme, where vessel-days are capped for each country and closely tracked.
+Patch 10 represents the high seas, where fishing days are determined by prevailing economic conditions.
 We examine the effects of large-scale conservation in Country 1 under markets with and without trading between countries.
@@
 We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
-We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see the Methods section for a details).
+We simulate these outcomes across a range of reserve sizes and assumptions about within-patch stock movement (see the Methods section for details).
 
@@
 Under this market design, revenue losses are less than 1\%, compared to the benchmark scenario with no reserve (Fig.
-\ref{fig:PNA_model}B).
+\ref{fig:PNA_model}B; note that the horizontal axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
+\ref{fig:PNA_model}A).
 With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
@@
 We have shown that trading significantly reduces the costs of conservation.
-However, a new problem arises.
-How should rights be re-allocated every year?
-We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently, and compare the resulting revenues to a fishery operating for 50 years without any closures.
+However, a new question arises.
+How should rights be re-allocated every year once a country starts closing its waters to fishing?
+We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for rights allocation, and compare the resulting revenues to a fishery operating for 50 years without any closures.
 We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
@@
 
-An MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ (397,447 km\textsuperscript{2}), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
+In January 2015, Kiribati closed 11.5\% of its EEZ, effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
 We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters.
+Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters but fished within Kiribati's EEZ.
 The remaining 221 vessels were not continuously observed before and after but are included in our analyses, and we refer to these as ``other vessels''.
@@
 S5 - S6).
-Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Figs.
+Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Fig.
 \ref{fig:empirical}).
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace $65.6 \pm 0.08$\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and $82.2 \pm 0.08$\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
 S10-S11).
@@
 However, an important aspect to consider is that of cooperative conservation.
-Consider the case where two nations contain high and low proportions of habitat that must be protected.
+Consider the case where two nations contain high and low proportions of habitat that should be protected.
 Should both nations try to attain the same conservation targets of say, 30\% protection of their respective extension?
@@
 We show that rights-based management can provide incentives for large-scale conservation.
-However, we must emphasize that design features of a market can have indelible impacts on a country’s willingness to engage in such projects.
-In the case of fishing rights and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcomes.
-
+However, we must emphasize that the design features of a market can have indelible impacts on a country's willingness to engage in such projects.
+In the case of fishing rights and MPAs, transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the desired outcome of zero-cost conservation.
 International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}.

### 2019-09-08 docs/old_ms/Markets_Conservation_sept_04.tex
Moved docs around and finalized MS for submission to Nature

--- 2019-09-08 docs/old_ms/Markets_Conservation_sept_03.tex
@@
 \begin{abstract}
-While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have been unwilling to unilaterally undertake large-scale conservation in their own waters.
-When a country closes a significant fraction of its waters to fishing, it loses significant fishery revenue; while this may be more-than-made-up-for through spillover of protected fish, these benefits typically accrue to other countries or the high seas.
-In the context of expansive marine conservation in the Pacific, we show that thoughtful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale conservation.
-By combining a model of cross-country trading of rights
-with vessel-level data before and after a large-scale conservation action is implemented, we show that two market design features are crucial.
-First, only when trading of rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
+While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to undertake large-scale conservation in their own waters.
+When a country closes a large fraction of its waters to fishing, it may lose significant fishery revenue.
+While this may be more-than-made-up-for through spillover of protected fish, in the context of very large Marine Protected Areas these benefits typically accrue to other countries or the high seas.
+We show that thoughtful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale conservation.
+By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are crucial.
+First, only when trading of fishing rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
 Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished.
-Overall, these results provide a
-template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
+Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
 \end{abstract}
@@
 
-Recognizing a need to protect biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protected areas around the world \cite{oleary_2016}.
-Currently only about 3\% of the world's oceans are strongly protected \cite{sala_2018}, but these commitments call for 10\%-30\% of the ocean to be off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
-To achieve these goals, huge swaths of sovereign nations' waters must be closed to fishing, yet few studies examine the incentives or economic mechanisms that would motivate a country to engage in such large-scale marine protection.
-Would any country rationally close 10\%, 30\%, or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
-If all countries acted unilaterally, the answer is probably ``no''.
-Losing this important source of revenue would cripple many fishing-dependent economies and the spillover benefits from conservation would accrue to weakly regulated fisheries on the high seas.
-How would this answer change if fishing countries were able to capture the benefits of this spillover?
-We find that international fishing effort markets, where nations trade the right to fish with each other, may provide a viable mechanism that incentivizes large-scale marine conservation.
-Here we show how the market can be designed (if new) or modified (if already existing) to incentivize large-scale marine conservation.
+Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by making 30\% of the oceans off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy.
+But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
+At first glance, the answer is probably ``no''.
+Losing this important source of revenue would cripple many fishing-dependent economies.
+On the other hand, the closure may generate substantial ``spillover'' of fish and other benefits into adjacent waters which could, in principle, offset these losses.
+The problem with this argument is that for very large MPAs, these spillover benefits would accrue to other nations, with no obvious mechanism for the conserving country to recoup them.
+A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other.
+Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
 
 We are motivated by a real-world but relatively unknown institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna fishing in its members' waters \cite{havice_2013,aqorau_2018}.
+Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018}.
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
 The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days.
+Vessel-days are allocated across the nine nations, which then lease them to fishing vessels.
 A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
-Vessel-days are allocated across the nine nations, which then lease them to fishing vessels.
 Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
@@
 In 2015, Kiribati created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020.
-We draw from the PNA approach to managing tuna fisheries and build on it to show how a market-based solution can be designed to incentivize conservation.
+We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how the market can be designed to incentivize conservation.
 
@@
 
-We first simulate a fishery where trading between countries is not allowed, and find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
+We first simulate a fishery where trading between countries is not allowed.
+This represents the status quo of any nation unilaterally engaging in large-scale conservation.
+Intuitively, we find that a spatial closure in Patch 1 will always result in a loss in revenues to Patch 1 (Fig.
 \ref{fig:PNA_model}A).
@@
 S2) and the high seas.
+This first simulated fishery show the misalignment of incentives, where a conservation-minded country incurs large costs and provides public benefits to other nations for free.
 
@@
 S4).
-Overall, 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
+Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to enable trading (Fig.
 \ref{fig:PNA_model}C).
@@
 How should rights be re-allocated every year once a country starts closing its waters to fishing?
-We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for rights allocation, and compare the resulting revenues to a fishery operating for 50 years without any closures.
+Customarily, the allocation of fishing effort rights is some formula that combines historical fishing effort and biomass in a nation's waters \cite{havice_2013}.
+We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for rights allocation.
+We simulate a fishery operating with closures for 50 years and compare the resulting revenues to a fishery without any closures.
 We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig.
@@
 A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ, effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
+In January 2015, Kiribati closed 11.5\% of its EEZ, effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}.
+By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}.
 We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.

### 2019-10-15 scripts/3_model/2_run_model.Rmd
Renamed script that creates fig 3 of main paper

--- 2019-06-24 scripts/model/2_run_model.Rmd
@@
                                  frame.colour = "black"),
-          linetype = guide_legend(title = bquote("Allocaion ("~alpha~")"),
+          linetype = guide_legend(title = bquote("Allocation ("~alpha~")"),
                                   override.aes = list(size = 0.5))))

### 2019-10-15 docs/tab/balance_table.tex
Updated tables

\begin{table}[t]

\caption{\label{tab:}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p < 0.1; ** p< 0.05; *** p < 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Non-displaced & Displaced & Difference\\
\hline
Crew size (n) & 30.46 (6.25) & 26.38 (3.94) & -4.08 (-6.49) ***\\
\hline
Engine Power (KW) & 2559.89 (588.28) & 2983.6 (558.76) & 423.71 (5.36) ***\\
\hline
Length (m) & 68.97 (8.42) & 74.23 (9.71) & 5.25 (3.97) ***\\
\hline
Tonnage (GT) & 1383.41 (533.56) & 1718.14 (653.38) & 334.73 (3.79) ***\\
\hline
\end{tabular}
\end{table}

### 2019-10-15 docs/Markets_Conservation_revised.tex
Updated MS version

--- 2019-09-08 docs/Markets_Conservation_sept_07.tex
@@
 Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who have been suggested as viable candidates for large closures \cite{mcleod_2019}.
-On the other hand, the closure may generate substantial ``spillover'' of fish and other benefits into adjacent waters which could, in principle, offset these losses.
+On the other hand, the closure may generate substantial ``spill-over'' of fish and other benefits into adjacent waters which could, in principle, offset these losses.
 The problem with this argument is that for very large MPAs, these spillover benefits would accrue to other nations, with no obvious mechanism for the conserving country to recoup them.
 A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other.
+The design and effectivness of fishing effort markets for fisheries management have been explore before \cite{havice_2010,havice_2013}, but little attention has been given to the role that markets can play in conservation.
 Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
@@
 We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA).
-Like an OPEC for tuna, the PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018}.
+The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018}.
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
@@
 Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
-If the conserving country could lease the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+If the conserving country could trade the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
 But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
@@
 
-To examine how market design incentivizes or punishes large scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
+To examine how market design incentivizes or punishes large-scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
 Countries 1 to 9 represent the PNA countries, which operate under a vessel-day scheme where vessel-days are capped for each country and closely tracked.
@@
 Under this market design, revenue losses are less than 1\%, compared to the base case with no reserve (Fig.
-\ref{fig:PNA_model}B; note that the horizontal axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
+\ref{fig:PNA_model}B; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
 \ref{fig:PNA_model}A).
@@
 How should rights be re-allocated every year once a country starts closing its waters to fishing?
-Customarily, the allocation of fishing effort rights is some formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}.
+Customarily, the allocation of fishing effort rights is a formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}.
 We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation.
@@
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
-This confirms a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
+This supports a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
 S4).
@@
 \caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
-Each line represents a possible value of stock movement ($\theta$; line color).
+Each line represents a possible value of within-country stock movement ($\theta$; line color).
 The revenue losses to Country 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
@@
 An effort-based allocation and low movement values result in the highest costs.
-Cost can be minimized for all movement values if allocation is based on biomass.}
+Cost can be minimized for all movement values if allocation is based on biomass within each country’s waters.}
 \end{figure}
@@
 \caption{\label{fig:empirical}Effort displacement and license revenues.
-Pannels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA).
-Annual effort is broken down by displaced, non-displaced, and other vessels.
+Panels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA) by 313 tuna purse seine vessels.
+Annual effort is broken down by displaced (n = 64), non-displaced (n = 28), and other vessels (n = 221).
 The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days).
-Pannel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and pannel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
+Panel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and panel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
 The dashed line represents line of best fit.}

### 2019-10-15 docs/Supplementary_materials.tex
Updated docs folder

@@
 
+We observe four characteristics for every vessel: crew size, engine power, vessel length, and tonnage capacity.
+Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels.
+Table \ref{tab:balance_table} present the mean, and standard deviation of each observable.
+Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.
+
+\begin{table}[h]
+
+\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254).
+Numbers in parentheses indicate standard deviation.
+The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p < 0.1; ** p< 0.05; *** p < 0.01).}
+\centering
+\begin{tabular}{l|l|l|l}
+\hline
+Characteristic & Non-displaced & Displaced & Difference\\
+\hline
+Crew size (n) & 30.46 (6.25) & 26.38 (3.94) & -4.08 (-6.49) ***\\
+\hline
+Engine Power (KW) & 2559.89 (588.28) & 2983.6 (558.76) & 423.71 (5.36) ***\\
+\hline
+Length (m) & 68.97 (8.42) & 74.23 (9.71) & 5.25 (3.97) ***\\
+\hline
+Tonnage (GT) & 1383.41 (533.56) & 1718.14 (653.38) & 334.73 (3.79) ***\\
+\hline
+\end{tabular}
+\end{table}
+
 \subsubsection{Effort redistribution}
@@
 
-\section{Supplementary tables and figures}
+\section{Supplementary figures}
 
@@
 	\includegraphics{img/effort_and_revenues.pdf}
-	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading.
+	\caption{\label{fig:effort_and_revenues}Effort and revenue in Country 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading.
 With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.
@@
 \centering
+\includegraphics{img/balance_density_plot.pdf}
+\caption{\label{fig:balance_density_plot}Distribution of observable characteristics by vessel for displaced (n = 64), non-displaced vessels (n = 254).}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{img/fishing_raster_diff.png}
 \caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas.
-Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B).
+Black lines show Exclusive Economic Zones (EEZ), red lines show proposed and existing Marine Protected Areas.
+Panels A and B show the change through time (after - before) for displaced (panel A; n = 64) and non-displaced vessels (panel B; n = 28).
 Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
@@
 	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel.
+	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel (n = 64).
 The vertical lines represent the median of each year.}
@@
 	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
+	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
 \end{figure}

### 2019-10-19 docs/Markets_Conservation_revised.tex
Updated code and docs

@@
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While this may be more-than-made-up-for through spillover of protected fish, these benefits typically accrue to other countries or the high seas.
+While this may be more-than-made-up-for through spillover, these benefits typically accrue to other countries or the high seas.
 We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale marine conservation.
@@
 
-Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by making 30\% of the oceans off-limits to fishing \cite{oleary_2016,dinerstein_2019}.
+Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, and that large portions of these will be entirely no-take \cite{sala_2017,sala_2018}.
 While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy.
@@
 At first glance, the answer is probably ``no''.
-Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who have been suggested as viable candidates for large closures \cite{mcleod_2019}.
-On the other hand, the closure may generate substantial ``spill-over'' of fish and other benefits into adjacent waters which could, in principle, offset these losses.
-The problem with this argument is that for very large MPAs, these spillover benefits would accrue to other nations, with no obvious mechanism for the conserving country to recoup them.
+Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who are viewed as viable candidates for large closures \cite{mcleod_2019}.
+On the other hand, the closure may generate substantial ``spillover'' of larvae and adult fish \cite{ramesh_2019,hernndez_2019} and other benefits into adjacent waters which could, in principle, offset these losses.
+The problem with this argument is that for very large MPAs, these spillover benefits could accrue to other nations and the high seas \cite{agardy_2018}, with no obvious mechanism for the conserving country to recoup them.
 A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other.
-The design and effectivness of fishing effort markets for fisheries management have been explore before \cite{havice_2010,havice_2013}, but little attention has been given to the role that markets can play in conservation.
+The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role that markets can play in conservation.
 Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
@@
 We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA).
-The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018}.
+The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters (Fig.
+\ref{fig:PNA_map}) \cite{havice_2013,aqorau_2018}.
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
@@
 Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
-If the conserving country could trade the rights to catch the fish that spill-over, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+If the conserving country could trade the rights to catch the fish that spillover, other countries would likely buy them, offsetting the costs of not fishing its own waters.
 But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
@@
 Customarily, the allocation of fishing effort rights is a formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}.
-We test a range of allocation rules that weight effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation.
+We test a range of allocation rules that weigh effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation.
 We simulate a fishery operating with closures for 50 years and compare the resulting revenues to a fishery without any closures.
@@
 A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ, effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}.
+In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Island Protected Area (PIPA), effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}.
 By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}.
-We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data \cite{ffa_2017} to quantify the displacement of fishing effort and the likely costs of conservation.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 28 ``non-displaced vessels'' never fished in PIPA waters but fished within Kiribati's EEZ.
-The remaining 221 vessels were not continuously observed before and after but are included in our analyses, and we refer to these as ``other vessels''.
+We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation.
+Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within the PNA waters.
+We use the tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.
 
-Consistent with our models' prediction, PIPA caused vessels to relocate largely outside of Kiribati, and into other PNA countries' waters (Figs.
-S5 - S7).
-Indeed, displaced vessels fished 922 fewer days (a 10\% reduction) in Kiribati, but spent just 48 fewer days in PNA waters (Fig.
+Consistent with our models' prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs.
+S6).
+Indeed, from 2014 to 2015, displaced vessels spent 2,115 fewer vessel-days (a 25\% reduction) in Kiribati, and 2,298 fewer vessel-days in PNA waters (a 17 \% reduction; Fig.
 \ref{fig:empirical}).
-The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.
-On the other hand, non-displaced and other vessels spent 1,621 and 2,034 additional days in Kiribati in 2015, relative to 2014.
-The same pattern is observed at the PNA level, with non-displaced and other vessels spending an additional 3,789 and 3,691 vessel-days, respectively.
-By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,282 in 2014 to just 7,542 in 2018, with displaced vessels driving the decrease (Fig.
+On the other hand, non-displaced vessels spent 4,656 additional days in Kiribati during 2015, and an additional 9,598 vessel-days in PNA waters.
+By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,671 in 2014 to just 7,677 in 2018, with displaced vessels driving the decrease (Fig.
 \ref{fig:empirical}A).
+However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Fig S7).
+The reduction in effort to Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.
+
+The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels.
+For example, as El Niño events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}.
+However, the total decrease that we observe for Kiribati in Fig.
+\ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not the entire fleet.
+One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati.
+For example, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig.
+S5).
+However, displaced vessels gradually reduce their time spent in PNA waters too.
 
@@
 Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA.
-In December 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
+In January 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig.
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS would displace 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries contain 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
 S10-S11).
 
-While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model suggests that they must also adopt a biomass-based allocation rule to ensure long-term financial security in the presence of large-scale conservation.
+%%%% PLEASE TAKE A LOOK AT THE SECOND SENTENCE OF THIS PARAGRAPH %%%%
+While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from a 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
+However, it is worth mentioning that we did not empirically test this prediction, as this would imply modifying the allocation rule in the real world.
 The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
@@
 
-In our study, only one of the countries considers the implementation of a protected area.
-However, an interesting extension would be cooperative conservation.
-In that setting, a group of countries could coordinate on an optimized large-scale strategical closure, perhaps using vessel-day trading as a means of compensation, in a matter similar to the model above.
+There are, however, a series of important considerations to take into account.
+Firstly, in our study only one of the countries considers the implementation of a protected area.
+However, an interesting extension would be that of cooperative conservation.
+In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above.
 Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting.
+A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}.
+Any spillover from into the high seas could potentially be eroded by the prevailing open access conditions.
+Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.
 
@@
 
-We model a 10 country discrete-time meta-population system, where Country 1 is considering a spatial closure.
+We model a 10 country discrete-time meta-population system, where Country 1 considers a spatial closure.
 Countries 1 - 9 operate under a vessel-day scheme, and Country 10 represents the high seas and other areas not managed under a VDS.
@@
 In the absence of a reserve, the revenue for vessels in country $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in country $i$ at the beginning of a period.
-The cost of fishing in country $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.
+The cost of fishing in country $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions that assume increasing units of effort are increasingly costly to apply \cite{costello_2016}.
 
 Country 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total country ($R \in[0,1)$).
-Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country.
+Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country (see the \emph{Notes on within-country fish movement} section below).
 In this country, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
@@
 
+\subsubsection{Notes on within-country fish movement}
+
+In our model parameterization, the proportion of biomass ``available'' for harvest is given by  $\Omega_1 = (\theta + (1 - \theta)(1 - R))$.
+This implies that for a given country with stock size $X_i$, the total biomass available for harvest will be given by $\Omega X_i$.
+Consider the case of a sesile fish with $\theta = 0$.
+If the country were to close 50\% of its waters to fishing ($R = 0.5$), only 50\% of the stock would be available for harvest (\emph{i.e.} $0 + (1 - 0) * (1 - 0.5) = 0.5$).
+Now, consider the same closure is applied with a stock with high mobility, so $\theta = 0.9$.
+In this case, despite the closure, fish constantly swim between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$).
+As derived in the bioeconomic model above, a vessel's willingness to pay to fish in a given patch will be determined by the amount of biomass available for harvest.
+Within-patch stock movement therefore plays an important role in determinig a vessel's willingness to pay in the remaining open waters: a vessel will be willing to pay more to fish in waters where 95\% of biomass is available for harvest, than when only 50\% of biomass is available for harvest.
+
 \subsubsection{Simulations}
@@
 Annual vessel-days are often allocated based on a combination of historical within-country effort and biomass.
-In the PNA, for example, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated skipjack and yellowfin biomass within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
+In the PNA, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated biomass (of skipjack and yellowfin tuna) within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
 Trading vessel-days to other countries would imply that historical within-country effort declines through time.
@@
 These broadcast messages can be received by satellites and land-based antennas.
-We use AIS data provided by Global Fishing Watch \cite{kroodsma_2018} to track 313 tuna purse seiners that fished within the PNA.
-Of the 313 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, 28 ``non-displaced vessels'' never fished in PIPA waters, and  221 ``other vessels'' were not continuously observed before and after.
-Together, these vessels represent more than 20 million geo-referenced positions.
+We use AIS data provided by Global Fishing Watch \cite{kroodsma_2018} to track 318 tuna purse seiners that fished within the PNA.
+For every georeferenced position, we observe the time spent (defined as the time since the last position), and whether the vessel was activly fishing versus only transiting.
+Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, the remianing 254 ``non-displaced vessels'' never fished in PIPA waters.
+Our dataset contains more than 37 million geo-referenced positions for these 318 tuna purse seiners.
+We use these data to calculate vessel-days (the metric used by the PNA), and to track the spatial redistribution of displaced vessels.
+A comparision of vessel characteristics between displaced and non-displaced vessels is presented in Table S2 and Figure S5.
 
-We use these data to calculate the number of vessel-days that the 313 purse seiners spent in each PNA country and in PNA waters as a whole.
+We use these data to calculate the number of vessel-days that the 318 purse seiners spent in each PNA country and in PNA waters as a whole (Fig.
+\ref{fig:empirical}).
 The vessel-day equivalent of a day of fishing depends on vessel size, a measure used to control for effort creep.
 A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
-Vessel length is an observable characteristic in our dataset, and therefore we make the pertinent corrections when calculating vessel days.
+Vessel length is an observable characteristic in our dataset, and therefore vessel-days calculated in our analyses correspond to the PNA definition of vessel-days.
 
-Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org.
-Shapefiles for Marine Protected Areas (Phoenix Islands Protected Area and Palau National Marine Sanctuary) come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
-All analyses were performed in R version 3.5.3 \cite{rcore_2018}.
+We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
+Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Niño \cite{hanich2018unraveling,aqorau_2018}.
+
+We begin by filtering the data to keep only positions labeled as fishing events.
+We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell, resulting in 14 (7 years for two groups) gridded datasets of fishing hours.
+For each group of vessels, we then calculate the average fishing hours before (2012 - 2014, inclusive) and after (2015 - 2018, inclusive) the implementation of PIPA, resulting in 4 datasets of mean fishing effort (before and after for displaced and non-displaced vessels).
+We then calculate the change in effort allocation between these two periods (after minus before) for each group (Fig.
+\ref{fig:fishing_raster_diff}A-B).
+The redistribution by non-displaced vessels (Fig.
+\ref{fig:fishing_raster_diff}B) therefore provides a baseline of redistribution.
+We then compare the changes of displaced vessels to those by non-displaced vessels (Fig.
+\ref{fig:fishing_raster_diff}C).
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas.
 
@@
 We obtained information on revenues from the Pacific Islands Forum Fisheries Agency \emph{Tuna Development Indicators 2016} report.
-Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA\cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
+Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA \cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
 \ref{fig:empirical}C; Fig.
@@
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
+
+Shapefiles of Exclusive Economic Zones were obtained through Marine Ecoregions of The World, we use World EEZ v10 (2018-02-21) available for download at: http://www.marineregions.org.
+Shapefiles for Marine Protected Areas come from the World Database of Protected Areas, and were downloaded in March 2019 from: https://www.protectedplanet.net.
+All analyses were performed in R version 3.6.1 and RStudio 1.2.5.001 \cite{rcore_2019}.
 
@@
 
-Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program. John Lynham was supported by the Conservation Strategy Fund.
+Juan Carlos Villaseñor-Derbez was supported by UCMexus-CONACyT (CVU: 669403) and the Latin American Fisheries Fellowship Program.
+John Lynham was supported by the Conservation Strategy Fund, with a grant from the Pew Charitable Trusts and Pew Bertarelli Ocean Legacy.
+John Lynham and Christopher Costello wish to acknowledge The Nature Conservancy.
 
@@
 
+% Map of LSMPAS in PNA
+\begin{figure}
+\centering
+\includegraphics{img/PNA_map.png}
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA, the bottom-left inset presents provides a reference for the area.
+Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
+A red line indicates the Kiribati EEZ.
+The solid red polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary to be implemented in 2020.
+Land masses are shown in gray.
+Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
+\end{figure}
+
 % PNA model output for costs
@@
 \caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
-Each line represents a possible value of within-country stock movement ($\theta$; line color).
-The revenue losses to Country 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis) and movement (color).
-Costs are shown for Country 1 when there is no trading (A) and when trading is allowed (B).
+Each line represents a possible value of within-country stock movement ($\theta$; line colors), with $\theta = 0$ representing a stock that doesn't move to $\theta = 1$ depicting a stock that continuously moves between the reserve and the fishing zone.
+The revenue losses to Country 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis), from no reserve ($R = 0$) to closing the entire Exclusive Economic Zone ($R = 1$).
+Costs are shown for Country 1 when there is no trading (A) and when trading is allowed (B; note the change in axis limits).
 Costs avoided by trading are shown in (C).
-Dashed red line in (A) is a 1:1 line.}
+Dashed red line in (A) is a 1:1 line.
+When trading between countries occurs, 88\% to 99\% of revenue losses can be avoided.}
 \end{figure}
@@
 Each line represents the revenue losses for a combination of allocation rules ($\alpha$; line type) and movement ($\theta$; color) for different reserve sizes ($R$; horizontal axis).
-An effort-based allocation and low movement values result in the highest costs.
+A value of $\alpha = 1$ implies that allocations are based entirely on historical effort, while a value of $\alpha = 0$ implies a 100\% biomass-based allocation rule.
+A value of $\theta = 0$ represents a stock that doesn't move, and $\theta = 1$ depics a stock that continuously moves between the reserve and the fishing zone.
+The proportion of the Exclusive Economic Zone closd to fishing is given by $R$.
+An effort-based allocation and low within-country movement values result in the highest costs.
 Cost can be minimized for all movement values if allocation is based on biomass within each country’s waters.}
@@
 \caption{\label{fig:empirical}Effort displacement and license revenues.
-Panels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA) by 313 tuna purse seine vessels.
-Annual effort is broken down by displaced (n = 64), non-displaced (n = 28), and other vessels (n = 221).
-The dashed horizontal lines represent the total allowable effort in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 days).
+Panels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA) by 318 tuna purse seine vessels.
+Annual effort is broken down by displaced (n = 64) and non-displaced (n = 254) vessels.
+The dashed horizontal lines represent the total allowable vessel-days in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 vessel-days).
 Panel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and panel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
-The dashed line represents line of best fit.}
+The dashed line in panel (D) represents line of best fit, and the shaded area represents the standard error around the regression.
+Colors in panels (C) and (D) are given by ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
 \end{figure}
 
-% Map of LSMPAS in PNA
+% Redistribution of effort
 \begin{figure}
 \centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA.
-Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
-A red line indicates the Kiribati EEZ.
-The solid red and purple polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary.
-Land masses are shown in gray.
-Labels indicate ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
+\includegraphics{img/fishing_raster_diff.png}
+\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of fishing activity bu 318 tuna purse seines.
+Black lines show Exclusive Economic Zones (EEZ), red lines show proposed and existing Marine Protected Areas.
+Panels A and B show the change through time (after - before) for displaced (panel A; n = 64) and non-displaced vessels (panel B; n = 254).
+Panel C shows the relative difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
+Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
 \end{figure}

### 2019-10-19 docs/Supplementary_materials.tex
Updated code and docs

@@
 
-\section{Supplementary Materials}
-
-\subsection{Model parameterization}
+\section{Model parameterization}
 
@@
 
-\subsection{Empirical Analysis}
+\section{Balance on observables}
 
@@
 Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels.
-Table \ref{tab:balance_table} present the mean, and standard deviation of each observable.
+Table \ref{tab:balance_table} presentsibut the mean, and standard deviation of each observable.
 Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.
 
-\begin{table}[h]
+\begin{table}[H]
 
@@
 \hline
-Characteristic & Non-displaced & Displaced & Difference\\
+Characteristic & Displaced & Non-displaced & Difference\\
 \hline
-Crew size (n) & 30.46 (6.25) & 26.38 (3.94) & -4.08 (-6.49) ***\\
+Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
 \hline
-Engine Power (KW) & 2559.89 (588.28) & 2983.6 (558.76) & 423.71 (5.36) ***\\
+Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
 \hline
-Length (m) & 68.97 (8.42) & 74.23 (9.71) & 5.25 (3.97) ***\\
+Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
 \hline
-Tonnage (GT) & 1383.41 (533.56) & 1718.14 (653.38) & 334.73 (3.79) ***\\
+Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
 \hline
@@
 
-\subsubsection{Effort redistribution}
-
-We can compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
-Non-displaced vessels serve as a control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as ENSO.
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas (Fig \ref{fig:fishing_raster_diff}).
-
-\subsubsection{Data and code availability}
+\section{Data and code availability}
 
@@
 \centering
-\includegraphics{img/fishing_raster_diff.png}
-\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels.
-Black lines show Exclusive Economic Zones (EEZ), red lines show proposed and existing Marine Protected Areas.
-Panels A and B show the change through time (after - before) for displaced (panel A; n = 64) and non-displaced vessels (panel B; n = 28).
-Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
-Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
+	\includegraphics{img/all_PS_VDS_cty_year.pdf}
+	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
 \end{figure}
@@
 \centering
-	\includegraphics{img/hist_kir_fishing.pdf}
-	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel (n = 64).
-The vertical lines represent the median of each year.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
+	\includegraphics{img/fishing_the_line_by_year.pdf}
+	\caption{\label{fig:fishing_the_line_by_year}Annual fishing effort (hours) on a 1-degree grid around PIPA (red polygon) and Kiribati (black polygons).
+There is no clear evidence of a ``fishing the line'' effect, with the greatest effort applied on the Gilbert islands (Kiribati) after 2015.}
 \end{figure}

### 2019-10-19 scripts/4_content/fig_PNA_map.R

@@ -11,6 +11,7 @@
 # Load packages
 library(ggrepel)
 library(ggsflabel) #devtools::install_github("yutannihilation/ggsflabel")
+library(cowplot)
 library(countrycode)
 library(startR)
 library(sf)
@@ -18,8 +19,8 @@ library(here)
 library(tidyverse)
 
 # Source local functions
-source(here("scripts", "functions", "st_rotate.R"))
-source(here("scripts", "functions", "sfc_as_cols.R"))
+source(here("scripts", "0_functions", "st_rotate.R"))
+source(here("scripts", "0_functions", "sfc_as_cols.R"))
 
 # List of countries
 countries <- c("PIPA",
@@ -42,7 +43,8 @@ countries <- c("PIPA",
                "WLF",
                "VUT",
                "NCL",
-               "PLW")
+               "PLW",
+               "IDN")
 
 # List of PNA countries
 PNA_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL")
@@ -50,18 +52,20 @@ PNA_countries <- c("FSM", "KIR", "MHL", "NRU", "PLW", "PNG", "SLB", "TUV", "TKL"
 # List of countries that hold VDS rights (and then sell to others)
 VDS_countries <- c(PNA_countries, "TKL")
 
-# Get coastline
-small_coast <- rnaturalearth::ne_countries(scale = "large", returnclass = "sf") %>% 
-  filter(sov_a3 %in% countries) %>% 
-  st_rotate()
-
-eez <- read_sf(dsn = here("data", "spatial", "EEZ_subset"),
-               layer = "EEZ_subset") %>% 
+eez <- read_sf(dsn = here("raw_data", "spatial", "EEZ"),
+               layer = "EEZ_v10") %>% 
   filter(ISO_Ter1 %in% countries) %>% 
+  rmapshaper::ms_simplify(keep_shapes = T) %>% 
+  st_rotate() %>% 
   mutate(KIR = ISO_Ter1 == "KIR",
          VDS = ifelse(ISO_Ter1 %in% VDS_countries, "VDS", "Non-PNA")) %>% 
   group_by(ISO_Ter1, VDS, KIR) %>% 
   summarize()
+
+# Get coastline
+small_coast <- rnaturalearth::ne_countries(scale = "large", returnclass = "sf") %>% 
+  filter(sov_a3 %in% countries) %>% 
+  st_rotate()
 
[…]

### 2019-10-19 scripts/4_content/fig_fishing_raster_diff.R

@@ -24,7 +24,6 @@ source(here("scripts", "0_functions", "sfc_as_cols.R"))
 # Countries I want to show
 countries <- c("PIPA",
                "KIR",
-               "HS",
                "ASM",
                "COK",
                "FSM",
@@ -44,14 +43,13 @@ countries <- c("PIPA",
                "NCL",
                "PLW")
 # Load EEZs
-eez <- read_sf(dsn = here("data", "spatial", "EEZ_subset"),
-               layer = "EEZ_subset") %>% 
+eez <- read_sf(dsn = here("raw_data", "spatial", "EEZ"),
+               layer = "EEZ_v10") %>% 
   filter(ISO_Ter1 %in% countries) %>% 
-  mutate(KIR = ISO_Ter1 == "KIR",
-         PNA = ifelse(PNA, "PNA", "Non-PNA")) %>% 
-  group_by(ISO_Ter1, PNA, KIR) %>% 
-  summarize() %>% 
-  rmapshaper::ms_simplify()
+  rmapshaper::ms_simplify(keep_shapes = T) %>% 
+  st_rotate() %>% 
+  group_by(ISO_Ter1) %>% 
+  summarize()
 
 ##### MPAS #################################################
 # Load MPA shapefiles
@@ -78,15 +76,16 @@ yearly_effort_raster <-readRDS(file = here("raw_data", "rasterized_effort_by_gro
                                  lon_bin_center + 180,
                                  lon_bin_center - 180) + 180) %>% 
   filter(between(lon_bin_center, 129, 213),
-         between(lat_bin_center, -26.5, 23))
+         between(lat_bin_center, -26.5, 23)) %>% 
+  mutate(hours = hours_length)
 
 # change for displaced
 change_displaced <- yearly_effort_raster %>% 
   filter(group == "displaced") %>%
   group_by(lon_bin_center, lat_bin_center, post) %>% 
-  summarize(days = mean(hours, na.rm = T) / 24) %>% 
+  summarize(hours = mean(hours, na.rm = T)) %>% 
   ungroup() %>% 
-  spread(post, days, fill = 0) %>% 
+  spread(post, hours, fill = 0) %>% 
   mutate(dif = Post - Pre) %>% 
   ggplot() +
   geom_tile(mapping = aes(x = lon_bin_center, y = lat_bin_center, fill = dif)) +
@@ -97,10 +96,11 @@ change_displaced <- yearly_effort_raster %>%
   theme(text = element_text(size = 10),
         axis.text = element_text(size = 8),
[…]

### 2019-10-19 scripts/4_content/sup_mat_fishing_the_line_by_year.R

@@ -1,0 +1,42 @@
+
+
+
+source(here("scripts", "0_functions", "st_rotate.R"))
+
+eez <- st_read(here("data", "spatial", "PNA_EEZ.gpkg")) %>% 
+  filter(MRGID %in% c(8450, 8441, 8488)) %>% # Keep Phoenix islands only
+  st_rotate()
+
+pipa <- st_read(here("data", "spatial", "PIPA.gpkg")) %>% 
+  st_rotate()
+
+bbox <- st_bbox(eez)
+
+yearly_effort_raster <-
+  readRDS(file = here("raw_data", "rasterized_effort_by_group.rds")) %>% 
+  mutate(lon_bin_center = ifelse(lon_bin_center < 0,
+                                 lon_bin_center + 180,
+                                 lon_bin_center - 180) + 180) %>% 
+  filter(between(lon_bin_center, bbox[1], bbox[3]),
+         between(lat_bin_center, bbox[2], bbox[4])) %>% 
+  group_by(year, lat_bin_center, lon_bin_center) %>% 
+  summarize(hours = sum(hours, na.rm = T))
+
+plot <- ggplot(yearly_effort_raster) +
+  geom_raster(aes(x = lon_bin_center, y = lat_bin_center, fill = hours)) +
+  geom_sf(data = eez, fill = "transparent", color = "black") +
+  geom_sf(data = pipa, color = "red", fill = "transparent") +
+  facet_wrap(~ year, ncol = 2) +
+  scale_fill_gradientn(colours = gfw_palette(25, name = "map_effort", type = "continuous")) +
+  ggtheme_map()  +
+  guides(fill = guide_colorbar(title = "Fishing hours",
+                               ticks.colour = "black",
+                               frame.colour = "black")) +
+  labs(x = "", y = "")
+
+ggsave(plot = plot,
+       filename = here("docs", "img", "fishing_the_line_by_year.pdf"),
+       width = 6,
+       height = 6)
+
+

### 2019-10-19 scripts/4_content/sup_mat_hist_kir_fishing.R

@@ -12,28 +12,25 @@
 #### SET UP ###########################################################################
 
 # Load packages
+library(here)
 library(tidyverse)
 library(ggridges)
 
 # Load data
 # I only want fishing tracks of purse seiners inside KIR before 2018
-tracks <- readRDS(file = here::here("data", "vessel_tracks_baci.rds")) %>% 
-  filter(gear == "tuna_purse_seines",
-         between(year, 2014, 2018),
-         fishing) 
+tracks <- readRDS(file = here("raw_data", "activity_by_vessel_year_eez.rds")) %>% 
+  filter(group == "displaced",
+         year > 2013,
+         eez_iso3 == "KIR")
 
 #### THE DATA ########################################################################
 
 # Generate the data
 kir_fishing <- tracks %>% 
-  group_by(mmsi, year, year_c) %>% 
-  mutate(total_hours = sum(hours)) %>% 
-  filter(eez_iso3 == "KIR") %>% 
-  group_by(mmsi, year, year_c, total_hours) %>% 
-  summarize(kir_hours = sum(hours)) %>% 
-  ungroup() %>% 
-  mutate(prop_hours = kir_hours / total_hours) %>% 
-  arrange(year, mmsi)
+  select(ssvid, year, contains("hours")) %>% 
+  mutate(prop_hours = fishing_hours / fishing_hours_in_PNA) %>% 
+  arrange(year, ssvid) %>% 
+  mutate(year_c = as.character(year))
 
 #### THE PLOT ########################################################################
 

### 2019-10-22 docs/Markets_Conservation_revised_Oct22.tex
Added changes by Chris

--- 2019-10-19 docs/Markets_Conservation_revised.tex
@@
 While this may be more-than-made-up-for through spillover, these benefits typically accrue to other countries or the high seas.
-We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale marine conservation.
+We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than hinder, large scale marine conservation.
 By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are pivotal to encouraging such conservation.
@@
 At first glance, the answer is probably ``no''.
-Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who are viewed as viable candidates for large closures \cite{mcleod_2019}.
+Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who are viewed by many as viable candidates for large closures \cite{mcleod_2019}.
 On the other hand, the closure may generate substantial ``spillover'' of larvae and adult fish \cite{ramesh_2019,hernndez_2019} and other benefits into adjacent waters which could, in principle, offset these losses.
 The problem with this argument is that for very large MPAs, these spillover benefits could accrue to other nations and the high seas \cite{agardy_2018}, with no obvious mechanism for the conserving country to recoup them.
-A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other.
-The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role that markets can play in conservation.
+A viable solution may lie in international fishing effort markets, where nations trade the right to fish.
+The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role these markets can play in conservation.
 Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
@@
 The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days.
-Vessel-days are allocated across the nine nations, which then lease them to fishing vessels.
+Vessel-days are allocated across the nine nations, which then lease them to (mostly foreign) fishing vessels.
 A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
-Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP (XXX).
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
@@
 
-Not all market-based approaches to environmental management are created equal.
+Not all market-based approaches to environmental management contain the same conservation incentives.
 A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}.
@@
 Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
-If the conserving country could trade the rights to catch the fish that spillover, other countries would likely buy them, offsetting the costs of not fishing its own waters.
+If the conserving country could lease the rights to that spillover to adjacent countries, this could offset the foregone fisheries revenue.
 But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
@@
 We examine the effects of large-scale conservation in a single country (Country 1) under markets with and without trading between countries.
-In all cases, we solve the bioeconomic model for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market.
+In all cases, we solve the bioeconomic model for the equilibrium vessel-day price, fishing effort redistribution across countries, and fish stock that would be expected to occur in the market.
 We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action.
@@
 Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
-The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
+The closure-to-cost ratio for any reserve size is greater than 1:1 (XXX Why) when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
 Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
@@
 S3).
-Under this market design, revenue losses are less than 1\%, compared to the base case with no reserve (Fig.
+Under this market design, revenue losses to Country 1 are less than 1\%, compared to the base case with no reserve (Fig.
 \ref{fig:PNA_model}B; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
@@
 However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing effort, the incentives for conservation are sustained through time.
+This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing intensity, the incentives for conservation can be sustained through time.
 
@@
 
-Consistent with our models' prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs.
+Consistent with our model's prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs.
 S6).
@@
 The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels.
-For example, as El Niño events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}.
+For example, as El Ni\~no events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}.
 However, the total decrease that we observe for Kiribati in Fig.
-\ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not the entire fleet.
+\ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not by the entire fleet.
 One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati.
@@
 S5).
-However, displaced vessels gradually reduce their time spent in PNA waters too.
+However, displaced vessels gradually reduce their time spent in PNA waters.
 
-As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses.
+As predicted by our model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses.
 Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries contain 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig.
+Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig.
 S10-S11).
@@
 There are, however, a series of important considerations to take into account.
-Firstly, in our study only one of the countries considers the implementation of a protected area.
+First, in our study only one of the countries considers the implementation of a protected area.
 However, an interesting extension would be that of cooperative conservation.
@@
 A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}.
-Any spillover from into the high seas could potentially be eroded by the prevailing open access conditions.
+Any spillover into the high seas could potentially be eroded by the prevailing open access conditions.
 Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.
+Finally, our work focuses on fisheries and large-scale conservation, but the framework could potentially be expanded and applied to other systems and natural resources.
+For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivise users to conserve the resource in question.
 
@@
 We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
-Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Niño \cite{hanich2018unraveling,aqorau_2018}.
+Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.
 
@@
 All analyses were performed in R version 3.6.1 and RStudio 1.2.5.001 \cite{rcore_2019}.
+
+\subsection{Data availability}
+
+The data and code that support the findings of this study are available on \href{https://github.com/jcvdav/MPA_displacement}{GitHub}
 

### 2019-10-22 docs/Supplementary_materials.tex
Added changes by Chris

@@
 \hline
-$\beta$ & 1.3 & Standard\\
+$\beta$ & 1.3 & Standard \cite{costello_2016}\\
 \hline
@@
 Numbers in parentheses indicate standard deviation.
-The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p < 0.1; ** p< 0.05; *** p < 0.01).}
+The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
 \centering
@@
 \end{table}
-
-\section{Data and code availability}
-
-Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.
 
@@
 	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
+	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 318 tuna purse seiners.}
 \end{figure}
@@
 
+\bibliography{references}
+\bibliographystyle{nature}
+
 \end{document}

### 2019-10-23 scripts/3_model/1_checks.Rmd
Deleted a bunch of old files

--- 2019-05-14 scripts/model/1_checks.Rmd
@@
 # Load functions
-source(here("scripts", "model", "E_vec_fxn.R"))
-source(here("scripts", "model", "pi_of_E.R"))
-source(here("scripts", "model", "max_Ei.R"))
+source(here("scripts", "3_model", "E_vec_fxn.R"))
+source(here("scripts", "3_model", "pi_of_E.R"))
+source(here("scripts", "3_model", "max_Ei.R"))
 
@@
 act <- readRDS(here("raw_data", "activity_by_vessel_year_eez.rds")) %>%
-  filter(
-    eez_iso3 %in% VDS_countries,
-    best_vessel_class == "tuna_purse_seines"
-  ) %>%
+  filter(eez_iso3 %in% VDS_countries) %>%
   group_by(year, eez_iso3) %>%
@@
   arrange(desc(days)) %>%
-  mutate(
-    days_prop = days / (sum(days) / (1 - prop_hs)),
-    c_days_prop = cumsum(days_prop)
-  )
+  mutate(days_prop = days / (sum(days)))
 ```

### 2019-10-23 scripts/3_model/2_run_model.Rmd
Deleted a bunch of old files

@@
 # Load functions
-source(here("scripts", "model", "grow.R"))
-source(here("scripts", "model", "E_vec_fxn.R"))
-source(here("scripts", "model", "pi_of_E.R"))
-source(here("scripts", "model", "max_Ei.R"))
-source(here("scripts", "model", "solve_pi.R"))
-source(here("scripts", "model", "PNA_with_trading.R"))
-source(here("scripts", "model", "PNA_no_trading.R"))
+source(here("scripts", "3_model", "grow.R"))
+source(here("scripts", "3_model", "E_vec_fxn.R"))
+source(here("scripts", "3_model", "pi_of_E.R"))
+source(here("scripts", "3_model", "max_Ei.R"))
+source(here("scripts", "3_model", "solve_pi.R"))
+source(here("scripts", "3_model", "PNA_with_trading.R"))
+source(here("scripts", "3_model", "PNA_no_trading.R"))
 
@@
 ```{r}
-source(here("scripts", "model", "allocate.R"))
-source(here("scripts", "model", "allocate_wrap.R"))
-source(here("scripts", "model", "move_in_time.R"))
-source(here("scripts", "model", "move_in_time_no_trading.R"))
+source(here("scripts", "3_model", "allocate.R"))
+source(here("scripts", "3_model", "allocate_wrap.R"))
+source(here("scripts", "3_model", "move_in_time.R"))
+source(here("scripts", "3_model", "move_in_time_no_trading.R"))
 ```

### 2019-10-25 scripts/4_content/4_supp_mat_balance_on_observables.R
Updated balance checks after John's suggestions

@@ -20,8 +20,15 @@ library(tidyverse)
 vessel_info <- readRDS(file = here("raw_data",
                                    "vessel_info_pna_purse_seines.rds"))
 
+vessel_activity <- readRDS(file = here("raw_data",
+                                       "activity_by_vessel_year_eez.rds")) %>% 
+  filter(year == 2014) %>% 
+  select(ssvid, group, fishing_hours_in_PNA) %>% 
+  distinct()
+
 # Combien both datasets, and clean-up
 balance_table <- vessel_info %>% 
+  left_join(vessel_activity, by = c("ssvid", "group")) %>% 
   mutate(group = ifelse(group == "displaced", "Displaced", "Non-displaced"),
          group = fct_relevel(group, "Non-displaced")) %>% 
   select(-c(flag)) %>% 
@@ -29,6 +36,7 @@ balance_table <- vessel_info %>%
   mutate(measure = case_when(measure == "crew_size" ~ "Crew size (n)",
                              measure == "engine_power_kw" ~ "Engine Power (KW)",
                              measure == "length_m" ~ "Length (m)",
+                             measure == "fishing_hours_in_PNA" ~ "PNA fishing in 2014 (hours)",
                              T ~ "Tonnage (GT)"))
 
 
@@ -55,8 +63,8 @@ ggsave(plot = density_plot,
 
 # Create a function that returns mean (sd) for a variable
 mean_sd <- function(x) {
-  m <- round(mean(x), 2)
-  sd <- round(sd(x), 2)
+  m <- round(mean(x, na.rm = T), 2)
+  sd <- round(sd(x, na.rm = T), 2)
   
   paste0(m, " (", sd, ")")
 }
@@ -108,8 +116,30 @@ balance_table %>%
 
 
 
+# Create a graph for flag proportions
+flags <- c("ESP", "TWN", "JPN", "CHN")
 
-
+vessel_info %>% 
+  mutate(group = ifelse(group == "displaced", "Displaced", "Non-displaced"),
+         group = fct_relevel(group, "Non-displaced")) %>% 
+  select(group, flag) %>% 
+  mutate(flag = ifelse(is.na(flag), "Not reported", flag)) %>%
+  group_by(group) %>% 
+  mutate(n = n()) %>% 
+  ungroup() %>% 
+  group_by(group, flag, n) %>% 
+  summarize(n2 = n()) %>% 
+  ungroup() %>% 
+  mutate(prop = n2 / n * 100) %>% 
[…]

### 2019-10-25 docs/Markets_Conservation_revised_Oct24.tex
Updated docs folder

--- 2019-10-22 docs/Markets_Conservation_revised_Oct22.tex
@@
 Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within the PNA waters.
-We use the tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.
+We use the vessel-tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.
 
@@
 
-The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels.
+The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive the distribution of target species and fishing vessels.
 For example, as El Ni\~no events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}.
-However, the total decrease that we observe for Kiribati in Fig.
-\ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not by the entire fleet.
+However, the aggregate decrease that we observe for Kiribati in Fig.
+\ref{fig:empirical} is driven by the relocation of vessels that historically fished within PIPA, not by the entire fleet.
+Oceanographic conditions should be influencing the entire fleet whereas the closure of PIPA should have a stronger impact on vessels that used to fish there.
+Thus, the large drop in effort within Kiribati for the displaced vessels (relative to the non-displaced vessels) is consistent with the argument that PIPA displaced these vessels to waters outside of Kiribati.
 One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati.
-For example, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig.
+It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig.
 S5).
-However, displaced vessels gradually reduce their time spent in PNA waters.
+Another alternative explanation is a change in international relations between Kiribati (or other PNA countries) and the flag country of a particular vessel.
+Ruling out alternative explanations for observed effects is an important component of careful empirical evaluation of MPAs \cite{ferraro2018causal}: as such, our results should not be interpreted as the direct causal impacts of PIPA but are better viewed as patterns that are consistent with the predictions of our theoretical model.
 
@@
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
-This supports a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
+This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
 S4).
@@
 While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from a 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
-However, it is worth mentioning that we did not empirically test this prediction, as this would imply modifying the allocation rule in the real world.
-The Parties to the Nauru Agreement have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
-By facilitating trade and allocating rights based on biomass, they may become pioneers in effective large-scale marine conservation in a market-based setting.
+This is a model prediction that cannot be empirically tested in the PNA because the rule has not been experimentally modified.
+The PNA countries have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+By facilitating trade and allocating rights based on biomass, they may also have become pioneers in effective large-scale marine conservation in a market-based setting.
 
 There are, however, a series of important considerations to take into account.
-First, in our study only one of the countries considers the implementation of a protected area.
-However, an interesting extension would be that of cooperative conservation.
+First, in our model only one of the countries considers the implementation of a protected area.
+An interesting extension could consider cooperative conservation.
 In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above.
 Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting.
-A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}.
-Any spillover into the high seas could potentially be eroded by the prevailing open access conditions.
+A second consideration is the role of the high seas: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}.
+Benefits accruing to the high seas could potentially be eroded by the prevailing open access conditions.
 Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.
@@
 One of the driving concerns is that markets may create incentives that lead to undesirable outcomes, thus emphasizing the need for careful design.
-We show that individual countries have little incentive to undertake large-scale marine conservation, but that this incentive can be reversed if those countries are in an appropriately-designed market-based setting.
+We show that without cross country markets, individual countries have little incentive to undertake large-scale marine conservation, but that this incentive can be reversed if those countries are in an appropriately-designed market-based setting.
 For the market to create these incentives, certain design features are paramount.
@@
 Fish move within a country based on $\theta$, where $\theta = 0$ implies no movement within the country, and $\theta = 1$ implies that fish move so much that they can be caught from anywhere within the country (see the \emph{Notes on within-country fish movement} section below).
-In this country, revenues are given by $pqE_1X_1(\theta + (1 - \theta)(1 - R))$.
+In this country, revenues are given by $pqE_1X_1(\theta R + (1 - R))$.
+The parenthetical term is the fishable fraction of biomass in Country 1.
+It assumes that fraction $\theta$ of fish inside the reserve at the beginning of the fishing season are fishable outside the reserve at some point during the course of the fishing season.
 The parameterization of movement and reserve size imply that profit from fishing Country 1 is given by:
@@
 
-\noindent with $\Omega_1 = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of country ($R =  [0, 1)$) and within-country fish movement ($\theta$).
-Under this parameterization, $\Omega_{i \neq 1} = 1$ since only Country 1 implements a reserve.
+\noindent where $\Omega_1 = (\theta R + (1 - R))$. Also note that $\Omega_{i \neq 1} = 1$ since only Country 1 implements a reserve.
 
@@
 
-\noindent The above equations imply that the marginal profit from the last unit of effort in a country are given by:
+\noindent The above equations imply that the marginal profit from the last unit of effort in a country is given by:
 
@@
 Therefore, we assume that effort continues to enter Country 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$.
-Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
+Setting Equation \ref{eqn:marginal_profit} (for $i = 10$) equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:
 
@@
 \begin{equation}
-X_{t+1} = e_t \times  e^{r \left(1 - \frac{e_t}{K} \right)}
+X_{t+1} = e_t \times  exp\left(r \left(1 - \frac{e_t}{K} \right)\right)
 \label{eqn:grow}
@@
 
-\noindent where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.
+\noindent where $r$ and $K$ are species-specific intrinsic growth and carrying capacity parameters (the slope $\frac{dX_{t+1}}{de_t}|_{e_t=0}=exp(r)$).
 After the stock grows, a constant and country-specific fraction $f_i$ of the total stock redistributes to country $i$, so:
@@
 
-In our model parameterization, the proportion of biomass ``available'' for harvest is given by  $\Omega_1 = (\theta + (1 - \theta)(1 - R))$.
-This implies that for a given country with stock size $X_i$, the total biomass available for harvest will be given by $\Omega X_i$.
+In our model parameterization, the proportion of biomass ``available'' for harvest in the conserving country is given by  $\Omega_1 = (\theta R + (1 - R))$.
+This implies that for a given country with stock size $X_i$, the total biomass available for harvest will be given by $\Omega_i X_i$.
 Consider the case of a sesile fish with $\theta = 0$.
@@
 Now, consider the same closure is applied with a stock with high mobility, so $\theta = 0.9$.
-In this case, despite the closure, fish constantly swim between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$).
+In this case, despite the closure, fish frequently move between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$).
 As derived in the bioeconomic model above, a vessel's willingness to pay to fish in a given patch will be determined by the amount of biomass available for harvest.
-Within-patch stock movement therefore plays an important role in determinig a vessel's willingness to pay in the remaining open waters: a vessel will be willing to pay more to fish in waters where 95\% of biomass is available for harvest, than when only 50\% of biomass is available for harvest.
+Within-patch stock movement therefore plays an important role in determining a vessel's willingness to pay in the remaining open waters: a vessel will be willing to pay more to fish in waters where 95\% of biomass is available for harvest, than when only 50\% of biomass is available for harvest.
 
@@
 
-We run simulations under two market designs and test the model across a range of reserve sizes and within-country movement parameters.The first scenario does not allow trading.
+We run simulations under various market designs and test the model across a range of reserve sizes and within-country movement parameters.The first scenario does not allow trading.
 In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among Countries 1-9.
@@
 This reduction in biomass in turn will modify the marginal profit and willingness to pay to fish in each country.
-We therefore iterate this process until biomass stabilizes, finding the system's equilibrium.
+We iterate this process until biomass stabilizes.
 Like before, we calculate vessel-day revenues to each country and compare them to a case with no reserve in Country 1.
@@
 Annual vessel-days are often allocated based on a combination of historical within-country effort and biomass.
-In the PNA, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated biomass (of skipjack and yellowfin tuna) within its EEZ (This is explained in more detail in Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
+In the PNA, 60\% of the allocation is calculated based on EEZ effort over the last seven years and 40\% is calculated based on the 10-year average of each country’s share of estimated biomass (of skipjack and yellowfin tuna) within its EEZ (see Article 12.5 of the 2012 Amendment to the Palau Agreement and in \cite{Hagrannsoknir2014}).
 Trading vessel-days to other countries would imply that historical within-country effort declines through time.
@@
 In the trading scenario above, effort from Country 1 (with the reserve) is traded to other countries.
-This means that its allocation will decrease as purse seine effort in its EEZ is reduced.
+This means that its allocation will decrease as purse seine effort in Country 1 is reduced.
 To analyze the consequences of different allocation rules when trading is allowed, we simulate a fishery 50 years into the future, and annually re-allocate vessel-days based on a 7-year running mean of country-level effort and biomass.
@@
 
-We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
+We can then compare the location of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
 Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.
@@
 John Lynham and Christopher Costello wish to acknowledge The Nature Conservancy.
+We thank Rachel Dacks for valuable research assistance.
 
@@
 A value of $\theta = 0$ represents a stock that doesn't move, and $\theta = 1$ depics a stock that continuously moves between the reserve and the fishing zone.
-The proportion of the Exclusive Economic Zone closd to fishing is given by $R$.
+The proportion of the Exclusive Economic Zone closed to fishing is given by $R$.
 An effort-based allocation and low within-country movement values result in the highest costs.
-Cost can be minimized for all movement values if allocation is based on biomass within each country’s waters.}
+Cost can be minimized for all movement values if allocation is based on biomass within each country's waters.}
 \end{figure}

### 2019-10-25 docs/Supplementary_materials.tex
Updated docs folder

@@
 \begin{table}[H]
+
+	\caption{\label{tab:param_table}Model parameters.}
 \centering
@@
 Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels.
-Table \ref{tab:balance_table} presentsibut the mean, and standard deviation of each observable.
-Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.
+Table \ref{tab:balance_table} presents the mean and standard deviation of each observable.
+On average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels.
+The largest relative difference is in terms of gross tonnage.
 
@@
 Numbers in parentheses indicate standard deviation.
-The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
+The last column contains the difference in means (t-scores), with asterisks indicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
 \centering

### 2019-10-25 docs/old_ms/Markets_Conservation_revised.tex
Updated docs folder

--- 2019-10-19 docs/Markets_Conservation_revised.tex
@@
 A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
-Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP.
+Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's revenue.
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
@@
 
+\subsection{Data availability}
+
+The data and code that support the findings of this study are available on \href{https://github.com/jcvdav/MPA_displacement}{GitHub}
+
 \bibliography{references}

### 2019-10-26 docs/Markets_Conservation_revised_Oct24.tex
Updating with John's changes

@@
 
-Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, and that large portions of these will be entirely no-take \cite{sala_2017,sala_2018}.
-While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy.
+Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, with a focus on no-take Marine Protected Areas (MPAs) \cite{sala_2017,sala_2018}.
+While most MPAs implemented to date have been small, it is widely-recognized that, to meet these goals, very large MPAs must also be part of the strategy.
 But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
@@
 The problem with this argument is that for very large MPAs, these spillover benefits could accrue to other nations and the high seas \cite{agardy_2018}, with no obvious mechanism for the conserving country to recoup them.
-A viable solution may lie in international fishing effort markets, where nations trade the right to fish.
-The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role these markets can play in conservation.
+A viable solution may lie in international fishing effort markets, where nations trade the right to fish across international boundaries.
+The design and effectiveness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role these markets can play in conservation.
 Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
@@
 In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020.
-We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how the market can be designed to incentivize conservation.
+We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how a market can be designed to incentivize conservation.
 
@@
 Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
-If the conserving country could lease the rights to that spillover to adjacent countries, this could offset the foregone fisheries revenue.
-But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue.
+If the conserving country could trade the rights to that spillover to adjacent countries, this could offset the foregone fisheries revenue.
+But if the conserving country was not allowed to trade these rights, then it would lose all of its fishing revenue.
 The rules for how fishing rights are allocated across countries are equally important.
@@
 The closure-to-cost ratio for any reserve size is greater than 1:1 (XXX Why) when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
+XXXX The intuition for why the ratio is higher than 1:1 is that fishing cost is a convex function of reserve size.
+XXXX Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
 S1).
@@
 We simulate the same fishery, but now allow for vessel-days to be traded across countries (as is the case for the PNA).
-As before, a closure in Country 1 lowers the value of vessel-days in that country (because the fishable water shrinks).
+As before, a closure in Country 1 lowers the value of vessel-days in that country (because the fishable area shrinks).
 But increased biomass in other countries causes their vessel day prices to increase.
@@
 A large-scale MPA was recently implemented in PNA waters, providing the ideal empirical setting to test our predictions.
-In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Island Protected Area (PIPA), effectively displacing all fishing effort within its boundaries\cite{mccauley_2016,mcdermott_2018}.
+In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Islands Protected Area (PIPA), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
 By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}.
-We combine vessel-tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation.
-Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within the PNA waters.
-We use the vessel-tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and the redistribution of fishing events before and after the implementation of PIPA.
+We combine vessel-level tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation.
+Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within PNA waters.
+We use the vessel-level tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and to follow the redistribution of fishing effort before and after the implementation of PIPA.
 
@@
 However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Fig S7).
-The reduction in effort to Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.
+The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicts.
 
@@
 One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati.
-It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig.
+It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, are larger than non-displaced vessels, fished more in the PNA in 2014, and are more likely to be registered to the Republic of Korea (Tables S2 and S3, Fig.
 S5).
-Another alternative explanation is a change in international relations between Kiribati (or other PNA countries) and the flag country of a particular vessel.
+Thus, another alternative explanation for the observed changes in fishing patterns is a change in international relations between Kiribati (or other PNA countries) and the flag country of a particular vessel, although we are not aware of any occurring between 2012 and 2018.
 Ruling out alternative explanations for observed effects is an important component of careful empirical evaluation of MPAs \cite{ferraro2018causal}: as such, our results should not be interpreted as the direct causal impacts of PIPA but are better viewed as patterns that are consistent with the predictions of our theoretical model.
@@
 %%%% PLEASE TAKE A LOOK AT THE SECOND SENTENCE OF THIS PARAGRAPH %%%%
-While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from a 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
-This is a model prediction that cannot be empirically tested in the PNA because the rule has not been experimentally modified.
-The PNA countries have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from the current 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
+This is a model prediction that cannot be empirically tested in the PNA context because the allocation rule has not been experimentally modified.
+Nevertheless, the PNA countries have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
 By facilitating trade and allocating rights based on biomass, they may also have become pioneers in effective large-scale marine conservation in a market-based setting.
@@
 Benefits accruing to the high seas could potentially be eroded by the prevailing open access conditions.
-Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.
+Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highlighting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.
 Finally, our work focuses on fisheries and large-scale conservation, but the framework could potentially be expanded and applied to other systems and natural resources.
-For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivise users to conserve the resource in question.
+For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivize users to conserve the resource in question.
 
@@
 We use AIS data provided by Global Fishing Watch \cite{kroodsma_2018} to track 318 tuna purse seiners that fished within the PNA.
-For every georeferenced position, we observe the time spent (defined as the time since the last position), and whether the vessel was activly fishing versus only transiting.
+For every georeferenced position, we observe the time spent (defined as the time since the last position), and whether the vessel was actively fishing versus only transiting.
 Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, the remianing 254 ``non-displaced vessels'' never fished in PIPA waters.
@@
 We use these data to calculate vessel-days (the metric used by the PNA), and to track the spatial redistribution of displaced vessels.
-A comparision of vessel characteristics between displaced and non-displaced vessels is presented in Table S2 and Figure S5.
+A comparision of vessel characteristics between displaced and non-displaced vessels is presented in Tables S2-S3 and Figure S5.
 
@@
 The vessel-day equivalent of a day of fishing depends on vessel size, a measure used to control for effort creep.
-A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
+A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters long counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
 Vessel length is an observable characteristic in our dataset, and therefore vessel-days calculated in our analyses correspond to the PNA definition of vessel-days.
@@
 \ref{fig:fishing_raster_diff}C).
-The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas.
+The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas.
 
-\subsubsection{Revenues and catches}
+\subsubsection{Revenues}
 

### 2019-10-26 docs/Supplementary_materials.tex
Updating with John's changes

--- 2019-10-22 docs/Supplementary_materials.tex
@@
 
-We observe four characteristics for every vessel: crew size, engine power, vessel length, and tonnage capacity.
-Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels.
-Table \ref{tab:balance_table} presentsibut the mean, and standard deviation of each observable.
-Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.
+We observe six characteristics for every vessel: flag, crew size, engine power, vessel length, tonnage capacity, and fishing hours within PNA waters in 2014.
+Figure \ref{fig:balance_density_plot} shows the distribution of the numeric variables for each group of vessels.
+Table \ref{tab:balance_table} presents the mean and standard deviation of each observable, and table \ref{tab:balance_table_flags} shows the composition of each group by flag.
+On average, displaced vessels have smaller crew sizes, more engine power, are larger than non-displaced vessels, and fished more in PNA waters during 2014.
+The largest relative difference is in terms of gross tonnage.
 
+%% TABLE FOR NUMERIC VARIALBES
 \begin{table}[H]
-
 \caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254).
@@
 \hline
+PNA fishing in 2014 (hours) & 667.57 (489.24) & 529.33 (380.11) & -138.24 (-1.89) *\\
+\hline
 Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
+\hline
+\end{tabular}
+\end{table}
+
+%% BALANCE TABLE FOR FLAGS
+\begin{table}[t]
+\caption{\label{tab:balance_table_flags}Proportion of vessel flags by group. Note that we do not observe the flag for two vessels (0.78\%) in the non-displaced group.}
+\centering
+\begin{tabular}{l|r|r}
+\hline
+Flag & Non-displaced & Displaced\\
+\hline
+CHN & 10.24 & 0.00\\
+\hline
+ECU & 1.57 & 4.69\\
+\hline
+ESP & 0.39 & 4.69\\
+\hline
+FSM & 8.27 & 3.12\\
+\hline
+GTM & 0.39 & 1.56\\
+\hline
+JPN & 16.93 & 0.00\\
+\hline
+KIR & 2.76 & 12.50\\
+\hline
+KOR & 3.54 & 45.31\\
+\hline
+MEX & 1.18 & 0.00\\
+\hline
+MHL & 3.54 & 1.56\\
+\hline
+NIC & 0.39 & 0.00\\
+\hline
+NRU & 0.39 & 0.00\\
+\hline
+NZL & 1.18 & 3.12\\
+\hline
+PAN & 0.79 & 0.00\\
+\hline
+PHL & 7.87 & 1.56\\
+\hline
+PNG & 11.42 & 1.56\\
+\hline
+SLB & 1.57 & 0.00\\
+\hline
+SLV & 0.79 & 0.00\\
+\hline
+TWN & 11.81 & 3.12\\
+\hline
+USA & 12.20 & 17.19\\
+\hline
+VUT & 1.97 & 0.00\\
+\hline
+Not reported & 0.79 & 0.00\\
+\hline
+Total & 100.00 & 100.00\\
 \hline

### 2019-10-26 scripts/3_model/2_run_model.Rmd
Updated scripts and plots to have panels in lower case letters

@@
                         ncol = 1,
-                        labels = "AUTO"))
+                        labels = "auto"))
 ```

### 2019-10-26 scripts/4_content/1_fig_PNA_map.R

@@ -29,7 +29,8 @@ VDS_countries <- c(PNA_countries, "TKL")
 
 eez <- read_sf(dsn = here("data", "spatial", "EEZ_subset.gpkg")) %>% 
   mutate(KIR = ISO_Ter1 == "KIR",
-         VDS = ISO_Ter1 %in% VDS_countries)
+         VDS = ISO_Ter1 %in% VDS_countries) %>% 
+  lwgeom::st_make_valid()
 
 # Extract ISO3 codes for countries present
 countries <- eez$ISO_Ter1
@@ -45,7 +46,8 @@ labels <- eez %>%
     mutate(label = countrycode(sourcevar = ISO_Ter1,
                                origin = "iso3c",
                                destination = "country.name"),
-           label = ifelse(ISO_Ter1 == "FSM", "Federal States\nof Micronesia", label))
+           label = ifelse(ISO_Ter1 == "FSM", "Federal States\nof Micronesia", label)) %>% 
+  lwgeom::st_make_valid()
 
 # Load PIPA
 pipa <- st_read(dsn = here("data", "spatial", "PIPA.gpkg"))

### 2019-10-26 scripts/4_content/2_fig_empirical.R

@@ -143,7 +143,7 @@ p <- plot_grid(all_PS_VDS_KIR_year_plot,
                license_revenues,
                revenue_FFA_GFW,
                ncol = 2,
-               labels = "AUTO")
+               labels = "auto")
 
 #Save plot
 ggsave(p,

### 2019-10-26 scripts/4_content/3_fig_fishing_raster_diff.R

@@ -139,7 +139,7 @@ plot_change <- plot_grid(change_displaced,
                          change_not_displaced,
                          difference_between_groups,
                          ncol = 1,
-                         labels = "AUTO")
+                         labels = "auto")
 
 ggsave(plot = plot_change,
        file = here("docs", "img", "fishing_raster_diff.png"),

### 2019-10-28 docs/Supplementary_materials.tex
Updated supplementary materials

@@
 \centering
-\includegraphics{img/plw_2018.png}
+\includegraphics{img/plw_2018.pdf}
 \caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.

### 2019-11-13 docs/old_ms/Markets_Conservation_revised_Oct24.tex
Organized files to start addressing final comments

--- 2019-10-26 docs/Markets_Conservation_revised_Oct24.tex
@@
 \begin{abstract}
-While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas in their own waters.
+While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas (MPAs) in their own waters.
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While this may be more-than-made-up-for through spillover, these benefits typically accrue to other countries or the high seas.
-We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than hinder, large scale marine conservation.
-By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are pivotal to encouraging such conservation.
-First, only when trading of fishing rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions.
-Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished.
+While this may be more-than-made-up-for through spillover, benefits from large-scale MPAs typically accrue to other countries or the high seas.
+We show that careful design of cross-country rights-based approaches to fisheries management can actually incentivize, rather than hinder, large scale marine conservation.
+By combining a model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that cross-country transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation.
 Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
@@
 Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, with a focus on no-take Marine Protected Areas (MPAs) \cite{sala_2017,sala_2018}.
-While most MPAs implemented to date have been small, it is widely-recognized that, to meet these goals, very large MPAs must also be part of the strategy.
+While most MPAs implemented to date have been small, it is widely-recognized that very large MPAs must also be part of the strategy if we are to meet these goals.
 But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area?
@@
 The design and effectiveness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role these markets can play in conservation.
-Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.
+Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale MPAs.
 
 We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA).
-The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters (Fig.
-\ref{fig:PNA_map}) \cite{havice_2013,aqorau_2018}.
+The PNA is a coalition of nine Pacific Island Nations that collectively manages tuna purse seine fishing in its members' waters\cite{havice_2013,aqorau_2018} (Fig.
+\ref{fig:PNA_map}).
 These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}.
@@
 A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA.
-Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP (XXX).
+Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP \cite{ffa_2017b}.
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
@@
 Intuitively, we find that a spatial closure in Country 1 will always result in a loss in revenues to Country 1 (Fig.
-\ref{fig:PNA_model}A).
+\ref{fig:PNA_model}a).
 Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
-The closure-to-cost ratio for any reserve size is greater than 1:1 (XXX Why) when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues.
-XXXX The intuition for why the ratio is higher than 1:1 is that fishing cost is a convex function of reserve size.
-XXXX Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
+Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
 S1).
@@
 Under this market design, revenue losses to Country 1 are less than 1\%, compared to the base case with no reserve (Fig.
-\ref{fig:PNA_model}B; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
-\ref{fig:PNA_model}A).
-With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
+\ref{fig:PNA_model}b; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig.
+\ref{fig:PNA_model}a).
+This shows that, with trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
 S4).
 Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to allow trading (Fig.
-\ref{fig:PNA_model}C).
+\ref{fig:PNA_model}c).
 
@@
 In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Islands Protected Area (PIPA), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
-By protecting important tuna spawning habitat, PIPA may provide important recruitment and biomass benefits to adjacent waters \cite{hernndez_2019}.
+By protecting important tuna spawning habitat\cite{hernndez_2019}, PIPA may provide important recruitment and biomass benefits to adjacent waters.
 We combine vessel-level tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation.
 Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation and 254 ``non-displaced vessels'' never fished in PIPA waters but fished within PNA waters.
-We use the vessel-level tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details) and to follow the redistribution of fishing effort before and after the implementation of PIPA.
+We use the vessel-level tracking data to calculate vessel-days in the same way that the PNA does (see Methods for details).
+We present descriptive statistics on the redistribution of fishing activity before and after the implementation of PIPA.
 
-Consistent with our model's prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs.
-S6).
+Consistent with our model's prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig.
+\ref{fig:fishing_raster_diff}).
 Indeed, from 2014 to 2015, displaced vessels spent 2,115 fewer vessel-days (a 25\% reduction) in Kiribati, and 2,298 fewer vessel-days in PNA waters (a 17 \% reduction; Fig.
-\ref{fig:empirical}).
+\ref{fig:empirical}a-b).
 On the other hand, non-displaced vessels spent 4,656 additional days in Kiribati during 2015, and an additional 9,598 vessel-days in PNA waters.
 By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,671 in 2014 to just 7,677 in 2018, with displaced vessels driving the decrease (Fig.
-\ref{fig:empirical}A).
-However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Fig S7).
+\ref{fig:empirical}a).
+However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Figs.
+S6 and S7).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicts.
@@
 However, the aggregate decrease that we observe for Kiribati in Fig.
-\ref{fig:empirical} is driven by the relocation of vessels that historically fished within PIPA, not by the entire fleet.
+\ref{fig:empirical}a is driven by the relocation of vessels that historically fished within PIPA, not by the entire fleet.
 Oceanographic conditions should be influencing the entire fleet whereas the closure of PIPA should have a stronger impact on vessels that used to fish there.
@@
 Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig.
-\ref{fig:empirical}C).
+\ref{fig:empirical}c).
 The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig.
-\ref{fig:empirical}D).
-But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%).
+\ref{fig:empirical}d).
+But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in vessel-days (35\%).
 This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig.
+Vessel-tracking data (2012 to 2018) shows that, on average, the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig.
 S10-S11).
 
-%%%% PLEASE TAKE A LOOK AT THE SECOND SENTENCE OF THIS PARAGRAPH %%%%
 While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from the current 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
@@
 For the market to create these incentives, certain design features are paramount.
-In the case of fishing rights and MPAs, cross-country transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the conservation incentive.
+In the case of fishing rights and large-scale MPAs, cross-country transferable fishing rights and a biomass-based allocation rule are two necessary conditions to achieve the conservation incentive.
 International goals over the next decade have set ambitious targets for terrestrial and marine conservation, which will provide benefits ranging from preserving biodiversity to enhancing human well-being \cite{oleary_2016,dinerstein_2019,roberts_2017,ban_2019}.
@@
 
-We model a 10 country discrete-time meta-population system, where Country 1 considers a spatial closure.
+We model a 10-country discrete-time meta-population system, where Country 1 considers a spatial closure.
 Countries 1 - 9 operate under a vessel-day scheme, and Country 10 represents the high seas and other areas not managed under a VDS.
@@
 Consider the case of a sesile fish with $\theta = 0$.
-If the country were to close 50\% of its waters to fishing ($R = 0.5$), only 50\% of the stock would be available for harvest (\emph{i.e.} $0 + (1 - 0) * (1 - 0.5) = 0.5$).
+If the country were to close 50\% of its waters to fishing ($R = 0.5$), only 50\% of the stock would be available for harvest (\emph{i.e.} $(0 \times 0.5) + (1 - 0.5) = 0.5$).
 Now, consider the same closure is applied with a stock with high mobility, so $\theta = 0.9$.
-In this case, despite the closure, fish frequently move between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $0.9 + (1 - 0.9) * (1 - 0.5) = 0.95$).
+In this case, despite the closure, fish frequently move between the reserve and fishing grounds making 95\% of biomass available for harvest (\emph{i.e.} $(0.9 \times 0.5) + (1 - 0.5) = 0.95$).
 As derived in the bioeconomic model above, a vessel's willingness to pay to fish in a given patch will be determined by the amount of biomass available for harvest.
@@
 For every georeferenced position, we observe the time spent (defined as the time since the last position), and whether the vessel was actively fishing versus only transiting.
-Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, the remianing 254 ``non-displaced vessels'' never fished in PIPA waters.
+Of the 318 tuna purse seine vessels that fished in PNA waters between 2012 and 2018, 64 ``displaced'' vessels fished within PIPA at least once prior to its implementation, the remaining 254 ``non-displaced vessels'' never fished in PIPA waters.
 Our dataset contains more than 37 million geo-referenced positions for these 318 tuna purse seiners.
 We use these data to calculate vessel-days (the metric used by the PNA), and to track the spatial redistribution of displaced vessels.
-A comparision of vessel characteristics between displaced and non-displaced vessels is presented in Tables S2-S3 and Figure S5.
+A comparison of vessel characteristics between displaced and non-displaced vessels is presented in Tables S2-S3 and Figure S5.
 
@@
 The vessel-day equivalent of a day of fishing depends on vessel size, a measure used to control for effort creep.
-A day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters long counts as one day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
+The Palau Arrangement for the Management of the Western Pacific Fishery Management Scheme \cite{pna_2016} states that a day of activity by vessels smaller than 50 meters long counts as half a vessel-day, a day of activity by vessels 50 - 80 meters long counts as one vessel-day, and a day of activity by vessels larger than 80 meters counts as 1.5 vessel-days.
 Vessel length is an observable characteristic in our dataset, and therefore vessel-days calculated in our analyses correspond to the PNA definition of vessel-days.
 
-We can then compare the location of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
+We can also compare the location of fishing activity by displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution.
 Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.
@@
 We begin by filtering the data to keep only positions labeled as fishing events.
-We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell, resulting in 14 (7 years for two groups) gridded datasets of fishing hours.
+We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell.
+This process results in 14 gridded datasets of fishing hours (7 years, for two groups).
 For each group of vessels, we then calculate the average fishing hours before (2012 - 2014, inclusive) and after (2015 - 2018, inclusive) the implementation of PIPA, resulting in 4 datasets of mean fishing effort (before and after for displaced and non-displaced vessels).
-We then calculate the change in effort allocation between these two periods (after minus before) for each group (Fig.
-\ref{fig:fishing_raster_diff}A-B).
+We then calculate the change in effort allocation between these two periods (after minus before) for each group, and normalize the value of each grid cell by diving it by the largest within-group absolute change:
+
+\begin{equation}
+h_i = \frac{(h_{i, a} - h_{i, b})}{\mathrm{max}(|(h_{i, a} - h_{i, b})|)}
+\end{equation}
+
+Where, for a given group of vessels, $i$ is a subindex for each cell, and $a$ and $b$ indicate after and before.
+The resulting gridded differences are shown in Fig.
+\ref{fig:fishing_raster_diff}a-b.
 The redistribution by non-displaced vessels (Fig.
-\ref{fig:fishing_raster_diff}B) therefore provides a baseline of redistribution.
+\ref{fig:fishing_raster_diff}b) therefore provides a baseline of redistribution.
 We then compare the changes of displaced vessels to those by non-displaced vessels (Fig.
-\ref{fig:fishing_raster_diff}C).
+\ref{fig:fishing_raster_diff}c).
 The spatial redistribution patterns of displaced vessels relative to non-displaced vessels suggest that some relocated to other waters in Kiribati (\emph{i.e.} the Gilbert islands and Line islands), but also the Marshall Islands, Tuvalu, Nauru, and the high seas.
@@
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA \cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}C; Fig.
+\ref{fig:empirical}c; Fig.
 S8 - S9).
@@
 \centering
-\includegraphics{img/PNA_map.png}
-\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA, the bottom-left inset presents provides a reference for the area.
+\includegraphics{img/PNA_map.pdf}
+\caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA, the bottom-left inset provides a reference for the area.
 Parties to the Nauru Agreement (PNA) are shown in blue, while empty polygons indicate all others.
-A red line indicates the Kiribati EEZ.
-The solid red polygons show The Phoenix Islands Protected Area implemented in 2015 and the proposed Palau National Marine Sanctuary to be implemented in 2020.
+A red line outlines the three EEZs of Kiribati.
+The solid red polygons show The Phoenix Islands Protected Area (PIPA) implemented in 2015 and the proposed Palau National Marine Sanctuary (PNMS) to be implemented in 2020.
 Land masses are shown in gray.
@@
 The revenue losses to Country 1 (vertical axis) are relative to a fishery with no spatial closures, and are shown as a function of reserve size ($R$; horizontal axis), from no reserve ($R = 0$) to closing the entire Exclusive Economic Zone ($R = 1$).
-Costs are shown for Country 1 when there is no trading (A) and when trading is allowed (B; note the change in axis limits).
-Costs avoided by trading are shown in (C).
-Dashed red line in (A) is a 1:1 line.
+Costs are shown for Country 1 when there is no trading (a) and when trading is allowed (b; note the change in axis limits).
+Costs avoided by trading are shown in (c).
+Dashed red line in (a) is a 1:1 line.
 When trading between countries occurs, 88\% to 99\% of revenue losses can be avoided.}
@@
 
+% Redistribution of effort
+\begin{figure}
+\centering
+\includegraphics{img/fishing_raster_diff.pdf}
+\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of fishing activity by 318 tuna purse seiners.
+Black lines show Exclusive Economic Zones (EEZ), and red line outlines the Phoenix Island Protected Area (PIPA).
+Panels a and b show the normalized change in average fishing hours through time for displaced (panel a; n = 64) and non-displaced vessels (panel b; n = 254).
+Panel c shows the difference between a and b, highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
+Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands (part of Kiribati's EEZs), but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
+\end{figure}
+
 % Effort redistribution bars for PNA and KIR
@@
 \caption{\label{fig:empirical}Effort displacement and license revenues.
-Panels (A) and (B) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA) by 318 tuna purse seine vessels.
+Panels (a) and (b) show AIS-derived annual vessel-days for Kiribati and for all Parties to the Nauru Agreement (PNA) by 318 tuna purse seine vessels.
 Annual effort is broken down by displaced (n = 64) and non-displaced (n = 254) vessels.
 The dashed horizontal lines represent the total allowable vessel-days in Kiribati (11,000 days \cite{yeeting2018stabilising}) and the PNA (45,000 vessel-days).
-Panel (C) shows annual revenue from fishing license fees by country and year (2008 - 2016) and panel (D) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
-The dashed line in panel (D) represents line of best fit, and the shaded area represents the standard error around the regression.
-Colors in panels (C) and (D) are given by ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
-\end{figure}
-
-% Redistribution of effort
-\begin{figure}
-\centering
-\includegraphics{img/fishing_raster_diff.png}
-\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of fishing activity bu 318 tuna purse seines.
-Black lines show Exclusive Economic Zones (EEZ), red lines show proposed and existing Marine Protected Areas.
-Panels A and B show the change through time (after - before) for displaced (panel A; n = 64) and non-displaced vessels (panel B; n = 254).
-Panel C shows the relative difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels.
-Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
+Panel (c) shows annual revenue from fishing license fees by country and year (2008 - 2016) and panel (d) shows the correspondence between FFA-reported revenues and AIS-derived vessel-day observations (2012 - 2016).
+The dashed line in panel (d) represents line of best fit, and the shaded area represents the standard error around the regression.
+Colors in panels (c) and (d) are given by ISO3 country codes for PNA members (PLW: Palau, PNG: Papua New Guinea, FSM: Federal States of Micronesia, SLB: Solomon Islands, NRU: Nauru, MHL: Marshal Islands, KIR: Kiribati, TUV: Tuvalu, TKL: Tokelau).}
 \end{figure}

### 2019-11-13 docs/Markets_Conservation_revised_Nov13.tex
Added new version of the MS

--- 2019-11-13 docs/old_ms/Markets_Conservation_revised_Oct24.tex
@@
 
-\title{Well-Designed Environmental Markets Enable Large-Scale Marine Conservation}
+\title{Environmental Market Design for Large-Scale Marine Conservation}
 
@@
 \begin{abstract}
-While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas (MPAs) in their own waters.
+It is commonly agreed that marine conservation should expand dramatically around the world.
+However, most countries have yet to implement large-scale no-take Marine Protected Areas (MPAs).
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While this may be more-than-made-up-for through spillover, benefits from large-scale MPAs typically accrue to other countries or the high seas.
-We show that careful design of cross-country rights-based approaches to fisheries management can actually incentivize, rather than hinder, large scale marine conservation.
+While biodiversity and spillover fishing benefits may far exceed these loses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
+To overcome this dilemma, we design and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.
 By combining a model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that cross-country transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation.
+Our work focuses on the Vessel-Day Scheme, an environmental market employed by the Parties to the Nauru Agreement (a group of nine Pacific Island Nations) to manage their tuna fisheries, and where large-scale conservation interventions have taken place.
 Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
@@
 In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}.
-In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020.
+In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by January 2020.
 We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how a market can be designed to incentivize conservation.
@@
 Consider the incentives for a country to close 100\% of its waters.
-Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
+Such a closure might benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries.
 If the conserving country could trade the rights to that spillover to adjacent countries, this could offset the foregone fisheries revenue.
@@
 We will then make use of vessel-tracking data to analyze a real-world case of large-scale marine conservation under fishing effort markets.
+
+\section{Results}
 
@@
 However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation.
-This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing intensity, the incentives for conservation can be sustained through time.
+This result implies that if allocation is based purely on the biomass within a nation's waters, and not on fishing intensity, the incentives for conservation can be sustained through time.
 
@@
 
+\section{Discussion}
+
 Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA.
@@
 While trading would allow Palau, Kiribati, and other PNA members to reduce revenue losses from large-scale conservation, our model indicates that moving from the current 40\% biomass-based allocation rule to a 100\% biomass-based rule would ensure long-term financial security in the presence of large-scale MPAs, and further incentivize conservation within the PNA.
+A 100\% biomass-based allocation rule means that fishing rights will be distributed between nations based on the proportion of total biomass within their waters, regardless of historical fishing intensity.
+Furthermore, an effort-based allocation would reward undesirable behavior by granting more fishing rights to a country that fishes the most.
 This is a model prediction that cannot be empirically tested in the PNA context because the allocation rule has not been experimentally modified.
-Nevertheless, the PNA countries have shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
+Nevertheless, the PNA countries have already shown that rights-based management of transboundary resources can result in large management and economic benefits \cite{havice_2013,aqorau_2018}.
 By facilitating trade and allocating rights based on biomass, they may also have become pioneers in effective large-scale marine conservation in a market-based setting.
@@
 
-We use these data to calculate the number of vessel-days that the 318 purse seiners spent in each PNA country and in PNA waters as a whole (Fig.
+We use these data to calculate the number of vessel-days that the 318 purse seiners spent fishing in each PNA country and in PNA waters as a whole (Fig.
 \ref{fig:empirical}).
@@
 We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell.
+We use a 1-degree grid as a reasonable compromise between higher resolutions that would result in a more granular but noisy footprint, and the simple estimation of vessel-days at the EEZ-level (as in Fig S6, but represented spatially).
 This process results in 14 gridded datasets of fishing hours (7 years, for two groups).
@@
 
+\subsection{Code availability}
+
+The data and code that support the findings of this study are available on \href{https://github.com/jcvdav/MPA_displacement}{GitHub}
+
 \bibliography{references}
@@
 Correspondence and requests for materials should be addressed to juancarlos@ucsb.edu.
+
+\subsection{Competing interests}
+
+The authors declare no competing interests.
 

### 2019-11-13 scripts/1_collection/old/time_series_kir_activity_by_vessel_download.R

@@ -1,44 +1,0 @@
-#############################
-#   vessel_tracks_download  #
-#############################
-
-########################################################################
-# This script downloads the vessel_tracks dataset from Google BigQuery.
-# I queried the database in GBQ to get the tracks of all vessels we need.
-# That table (vessel_tracks) was made with scripts/vessel_tracks.sql.
-# After downloading the data, I add a couple of features that will come
-# in handy in the processing and fine-tuning of the next scripts. These
-# are basically getting rid of the few duplicate records, adding some
-# variables like factors for time-variables, and arranging the columns
-# in the order I want them (for now).
-########################################################################
-
-# Load the packages that I need
-library(dplyr)
-library(dbplyr)
-library(DBI)
-library(bigrquery)
-library(magrittr)
-
-# Create a connection to Google BigQuery
-# For this to run, you require authentication and be part of ucsb-gfw
-BQc <- bigrquery::dbConnect(
-  drv = bigrquery::bigquery(),
-  project = "ucsb-gfw", # This is the project, to which you must belong
-  dataset = "mpa_displacement", # This is the dataset, where I keep all the tables
-  allowLargeResults = TRUE #We're downloading about 10 GB of data
-)
-
-# List all tables to test the connection
-DBI::dbListTables(BQc)
-
-
-# DOWNLOAD THE DATA
-# Create a tbl pointing to vessel tracks
-data <- dplyr::tbl(BQc, "time_series_kir_activity_by_vessel") %>%
-  collect() # collect brings the information out of the database and into memory
-
-
-# Save it to disk
-saveRDS(data,
-        file = here("raw_data", "time_series_kir_activity_by_vessel.rds"))

### 2019-11-13 scripts/4_content/old/PS_VDS_KIR_by_year.R

@@ -1,50 +1,0 @@
-###########################
-#   PS_VDS_KIR_by_year_   #
-###########################
-
-
-##########################################################################
-# This script calculates the number of total hours that ALL purse seiners
-# spent in KIR waters.
-##########################################################################
-
-#### SETUP ########################################################
-# Load packages
-library(tidyverse)
-
-# Load data
-# Filter to keep only purse seiners before 2018 and modify the fishing label
-vessel_activity <- readRDS(file = here::here("raw_data",
-                                             "vessel_tracks_ALL_vessels_fished_PNA_2012_present.rds")) %>% 
-  filter(eez_iso3 == "KIR",
-         inferred_label == "tuna_purse_seines",
-         year < 2018) %>% 
-  mutate(fishing = ifelse(is.na(fishing), F, fishing),
-         fishing = ifelse(fishing, "Fishing", "Non-fishing"),
-         group = ifelse(treated, "Treatment", "Control"),
-         group = ifelse(is.na(treated), "Others", group),
-         group = fct_relevel(group, c("Treatment", "Control", "Others")))
-
-#### CREATE THE DATA ################################################
-
-## All Vessels yearly #########
-
-# Data for yearly vessel activity (fishing not fishing)
-vessel_activity_year <- vessel_activity %>% 
-  group_by(year, group) %>% 
-  summarize(days = sum(days, na.rm = T)) %>% 
-  ungroup()
-
-#### PLOTS ##########################################################
-# Plot for yearly PS VDS by activity
-p1 <- ggplot(vessel_activity_year, aes(x = year, y = days, color = group)) +
-  geom_line() +
-  scale_color_brewer(palette = "Set1") +
-  cowplot::theme_cowplot() +
-  theme(text = element_text(size = 10),
-        axis.text = element_text(size = 8))+
-  labs(x = "Year", y = "Vessel-days")
-
-#Save plot
-ggsave(p1, filename = here::here("docs", "img", "PS_VDS_KIR_by_year.pdf"), width = 6, height = 3.5)
-

### 2019-11-13 scripts/4_content/old/figs_all_PS_VDS_2012_2018.R

@@ -1,63 +1,0 @@
-#################################
-#   figs_all_PS_VDS_2012_2018   #
-#################################
-
-
-###########################################################
-# This script generates VDS allocation by country and year
-###########################################################
-
-#### SETUP ########################################################
-# Load packages
-library(here)
-library(ggridges)
-library(cowplot)
-library(tidyverse)
-
-PNA_without_KIR <- c("FSM",
-         "MHL",
-         "NRU",
-         "PLW",
-         "PNG",
-         "SLB",
-         "TUV",
-         "TKL")
-
-PNA_countries <- c(PNA_without_KIR, "KIR")
-
-
-# Load data
-vessel_activity <- readRDS(file = here("raw_data",
-                                       "activity_by_vessel_year_eez.rds")) %>% 
-  mutate(group = ifelse(group == "displaced", "Displaced", "Non-displaced"),
-         group = fct_relevel(group, "Non-displaced"),
-         location = case_when(eez_iso3 == "KIR" ~ "KIR",
-                              eez_iso3 %in% PNA_without_KIR ~ "other PNA countries",
-                              eez_iso3 == "HS" ~"HS",
-                              T ~ "Other countries"),
-         days = hours_length / 24)
-
-# annual PS VDS by country
-all_PS_VDS_cty_year_data <- vessel_activity %>% 
-  filter(eez_iso3 %in% PNA_countries) %>% 
-  group_by(year, eez_iso3) %>% 
-  summarize(days = sum(days, na.rm = T) / 1000) %>% 
-  ungroup()
-
-all_PS_VDS_cty_year_plot <-
-  ggplot(data = all_PS_VDS_cty_year_data,
-         mapping = aes(x = year, y = days, fill = eez_iso3)) + 
-  geom_col(color = "black") +
-  scale_fill_brewer(palette = "Set1") +
-  geom_hline(yintercept = 45, linetype = "dashed") +
-  cowplot::theme_cowplot() +
-  guides(fill = guide_legend(title = "Country")) +
-  theme(text = element_text(size = 10),
-        axis.text = element_text(size = 8),
-        legend.text = element_text(size = 8))+
-  labs(x = "Year", y = "Vessel-days (1,000)")
-
-ggsave(all_PS_VDS_cty_year_plot,
-       filename = here("docs", "img", "all_PS_VDS_cty_year.pdf"),
-       width = 6,
-       height = 4)

### 2019-11-13 scripts/4_content/old/included_PS_VDS_DiDs.R

@@ -1,115 +1,0 @@
-#############################
-#   included_PS_VDS_DiDs    #
-#############################
-
-##########################################################
-# This script creates two plots. The first plot compares
-# the number of yearly vessel-days applied by the treated and
-# control fleets to PNA countries and TKL. The figure shows
-# the how treated vessels (the ones that fished inside PIPA)
-# eventually leave the PNA, while control vessels continue
-# to fish in PNA waters. 
-# The second figure does the same, but by country. This other
-# figure shows us who won and lost VDS after PIPA.
-##########################################################
-
-#### SETUP ########################################################
-# Load packages
-library(cowplot)
-library(tidyverse)
-
-# Load data
-# Filter to keep only purse seiners before 2018 and modify the fishing label
-vessel_activity <- readRDS(file = here::here("raw_data",
-                                             "vessel_tracks_ALL_vessels_fished_PNA_2012_present.rds")) %>% 
-  filter(eez_iso3 %in% c("FSM",
-                         "KIR",
-                         "MHL",
-                         "NRU",
-                         "PLW",
-                         "PNG",
-                         "SLB",
-                         "TUV",
-                         "TKL"),
-         inferred_label == "tuna_purse_seines",
-         year < 2018) %>% 
-  mutate(fishing = ifelse(is.na(fishing), F, fishing),
-         fishing = ifelse(fishing, "Fishing", "Non-fishing"),
-         group = ifelse(treated, "Treatment", "Control"),
-         group = ifelse(is.na(treated), "Others", group))
-
-#### CREATE THE DATA ################################################
-
-
-## Treated Vessels yearly ####
-
-# Data for yearly vessel activity (fishing not fishing) for included / excluded
-vessel_activity_year_included <- vessel_activity %>% 
-  group_by(year, group) %>% 
-  summarize(days = sum(days, na.rm = T)) %>% 
-  ungroup()
-
-# Data for yearly vessel activity (fishing not fishing) for included / excluded
-vessel_activity_year_included_KIR <- vessel_activity %>% 
-  filter(eez_iso3 == "KIR") %>% 
-  group_by(year, group) %>% 
[…]

### 2019-11-13 scripts/4_content/old/tab_baci_n_s.R

@@ -1,51 +1,0 @@
-#################
-#   baci_n_s    #
-#################
-
-#######################################################
-# Number of fishing vessels and mean daily fishing
-# hours by group before and after PIPA implementation.
-#######################################################
-
-
-# Load packages
-library(startR)
-library(tidyverse)
-
-
-
-# Source local functions
-source(here::here("scripts", "my_kable.R"))
-
-
-effort_by_vessel <- readRDS(file = here::here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2018,
-         gear == "tuna_purse_seines",
-         fishing)
-
-hours <- effort_by_vessel %>%
-  group_by(treated, post, date, mmsi) %>% 
-  summarize(hours = sum(hours, na.rm  = T)) %>% 
-  ungroup() %>% 
-  group_by(treated, post) %>% 
-  summarize(hours = mean(hours, na.rm = T)) %>% 
-  spread(post, hours) %>% 
-  mutate(change = `TRUE` / `FALSE`)
-
-effort_by_vessel %>% 
-  group_by(treated, mmsi) %>% 
-  count() %>% 
-  ungroup() %>% 
-  group_by(treated) %>% 
-  summarize(boats = n()) %>% 
-  ungroup() %>% 
-  left_join(hours, by = c( "treated")) %>% 
-  mutate(treated = ifelse(treated, "Treatment", "Control")) %>% 
-  knitr::kable(col.names = c("Group", "n" ,"Before", "After", "Change (A / B)"),
-               caption = "\\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.",
-               # label = "baci_n_s",
-               booktabs = T,
-               digits = 2,
-               format = "latex") %>% 
-  kableExtra::kable_styling(latex_options = "HOLD_position") %>% 
-  cat(file = here::here("docs", "tab", "baci_n_s.tex"))

### 2019-11-13 scripts/4_content/old/vessel_model_fitting.R

@@ -1,331 +1,0 @@
-#############################
-#   vessel_model_fitting    #
-#############################
-
-###################################################
-# This is the script that fits all the models for
-# my panels of behavioral change.
-###################################################
-
-# Load packages
-library(here)
-library(magrittr)
-library(tidyverse)
-
-# Custom functions
-source(here("scripts", "functions", "model_data_prep.R"))
-source(here("scripts", "functions", "did.R"))
-source(here("scripts", "functions", "did_quarter.R"))
-source(here("scripts", "functions", "did_yearmonth.R"))
-source(here("scripts", "functions", "termplot.R"))
-
-# Nino4 index
-nino4 <- read.csv(here("data", "all_indices.csv")) %>% 
-  select(year, month = month_n, nino4anom)
-
-#### FISHING AND NON FISHING HOURS ################################################################
-# Load my data
-effort_by_vessel <- readRDS(file = here("data", "panels", "daily_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2019,
-         gear == "tuna_purse_seines")
-
-## Prepare a base data
-# For fishing hours
-fishing_hours <- effort_by_vessel %>% 
-  filter(fishing) %>% 
-  model_data_prep() %>% 
-  left_join(nino4, by = c("year", "month"))
-
-# For non-fishing hours
-nonfishing_hours <- effort_by_vessel %>% 
-  filter(!fishing) %>% 
-  model_data_prep() %>% 
-  left_join(nino4, by = c("year", "month"))
-
-
-## Fit the models
-# For each set of data I fit simple did, quarterly and year-month
-# Fishing hours
-fish_did <- did(fishing_hours)
-fish_didq <- did_quarter(fishing_hours)
-fish_didym <- did_yearmonth(fishing_hours)
-
-#Non-fishing hours
-nonfish_did <- did(nonfishing_hours)
-nonfish_didq <- did_quarter(nonfishing_hours)
-nonfish_didym <- did_yearmonth(nonfishing_hours)
-
-
-
-
-#### PROPORTION FISHING HOURS ################################################################
-# Load my data
-prop_fishing_by_vessel <- readRDS(file = here("data",
-                                              "panels",
-                                              "daily_prop_fishing_hours_by_vessel_panel.rds")) %>% 
-  filter(year < 2019,
-         gear == "tuna_purse_seines") %>% 
-  model_data_prep(prop_fishing) %>% 
-  left_join(nino4, by = c("year", "month"))
-
-#Fit themdoels
[…]

### 2019-11-13 scripts/4_content/sup_mat_hist_kir_fishing.R

@@ -1,58 +1,0 @@
-#########################
-#   hist_fishing_kir    #
-#########################
-
-###########################################################################
-# Make histograms of the % of total fishing hours that take place within
-# Kiribati EEZ waters by year for treated vessels where the unit of
-# observation is an individual vessel
-###########################################################################
-
-
-#### SET UP ###########################################################################
-
-# Load packages
-library(startR)
-library(here)
-library(tidyverse)
-library(ggridges)
-
-# Load data
-# I only want fishing tracks of purse seiners inside KIR before 2018
-tracks <- readRDS(file = here("raw_data", "activity_by_vessel_year_eez.rds")) %>% 
-  filter(group == "displaced",
-         year > 2013,
-         eez_iso3 == "KIR")
-
-#### THE DATA ########################################################################
-
-# Generate the data
-kir_fishing <- tracks %>% 
-  select(ssvid, year, contains("hours")) %>% 
-  mutate(prop_hours = fishing_hours / fishing_hours_in_PNA) %>% 
-  arrange(year, ssvid) %>% 
-  mutate(year_c = as.character(year))
-
-#### THE PLOT ########################################################################
-
-hist_kir_fishing <- ggplot() +
-  geom_density_ridges(data = kir_fishing,
-                      aes(x = prop_hours, y = year, fill = year_c),
-                      alpha = 0.5,
-                      quantile_lines = TRUE,
-                      quantiles = 2) +
-  scale_fill_brewer(palette = "Set1") +
-  cowplot::theme_cowplot() +
-  theme(text = element_text(size = 10),
-        axis.text = element_text(size = 8),
-        legend.position = "none")+
-  guides(fill = guide_legend(title = "Year")) +
-  labs(x = "Proportion of fishing hours in KIR", y = "Year") +
-scale_x_continuous(labels = scales::percent_format(accuracy = 1))
-
-# Save the plot
-ggsave(plot = hist_kir_fishing,
-       filename = here::here("docs", "img", "hist_kir_fishing.pdf"),
-       width = 6, height = 3.5)
-
-

### 2019-11-20 scripts/3_model/2_run_model.Rmd
Updated figure names exported in the model Rmd

@@
 
+```{r}
+ggsave(plot = effort_and_revenues,
+       file = here("docs", "img","effort_and_revenues_ED_Fig4.tiff"),
+       width = 6,
+       height = 4)
+```
+
 ## How does vessel-price change?
@@
 
+```{r}
+ggsave(plot = vessel_day_price_no_trading_plot,
+       filename = here("docs", "img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
+       width = 6,
+       height = 3)
+```
+
 ### When there is trading
@@
        filename = here("docs", "img", "vessel_day_price_with_trading_plot.pdf"),
+       width = 6,
+       height = 4.5)
+```
+
+```{r}
+ggsave(plot = vessel_day_price_with_trading_plot,
+       filename = here("docs", "img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
        width = 6,
@@
        filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot.pdf"),
+       width = 3,
+       height = 3)
+```
+
+```{r}
+ggsave(plot = profits_PNA_notKIR_no_trading_plot,
+       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
        width = 3,
@@
   filename = here("docs", "img", "allocation_cost_plot.pdf"),
-  width = 5.5,
+  width = 5,
   height = 3.5

### 2019-11-20 docs/Markets_Conservation_final.tex
Updated MS for resubmission

--- 2019-11-13 docs/Markets_Conservation_revised_Nov13.tex
@@
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While biodiversity and spillover fishing benefits may far exceed these loses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
-To overcome this dilemma, we design and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.
-By combining a model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that cross-country transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation.
+While biodiversity and spillover fishing benefits may far exceed these losses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
+To overcome this dilemma, we simulate and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.
+By combining a bioeconomic model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation under this market-based setting.
 Our work focuses on the Vessel-Day Scheme, an environmental market employed by the Parties to the Nauru Agreement (a group of nine Pacific Island Nations) to manage their tuna fisheries, and where large-scale conservation interventions have taken place.
@@
 We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA).
-The PNA is a coalition of nine Pacific Island Nations that collectively manages tuna purse seine fishing in its members' waters\cite{havice_2013,aqorau_2018} (Fig.
+The PNA is a coalition of nine Pacific Island Nations that collectively manages tuna purse seine fishing in its members' waters \cite{havice_2013,aqorau_2018} (Fig.
 \ref{fig:PNA_map}).
@@
 In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by January 2020.
-We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how a market can be designed to incentivize conservation.
+We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how an environmental market can be designed to incentivize conservation.
 
@@
 
-To examine how market design incentivizes or punishes large-scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
+To examine how market design incentivizes or hinders large-scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas.
 Countries 1 to 9 represent the PNA countries, which operate under a vessel-day scheme where vessel-days are capped for each country and closely tracked.
@@
 Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1.
-Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig.
-S1).
-When countries cannot trade, the costs of conservation are incurred by Country 1, but the benefits are received by the eight other countries (revenues increase between 0\% and 6\% each; Fig.
-S2) and the high seas.
+Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Supplementary Figure 1).
+When countries cannot trade, the costs of conservation are incurred by Country 1, but the benefits are received by the eight other countries (revenues increase between 0\% and 6\% each; Supplementary Figure 2) and the high seas.
 This benchmark simulation highlights the misalignment of incentives, where a conservation-minded country incurs large costs and provides public benefits to other nations with no mechanism for recouping these benefits.
@@
 But increased biomass in other countries causes their vessel day prices to increase.
-As a result, vessel-days from Country 1 are traded to Countries 2 to 9, until prices equalize across countries (Fig.
-S3).
+As a result, vessel-days from Country 1 are traded to Countries 2 to 9, until prices equalize across countries (Supplementary Figure 3).
 Under this market design, revenue losses to Country 1 are less than 1\%, compared to the base case with no reserve (Fig.
@@
 \ref{fig:PNA_model}a).
-This shows that, with trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig.
-S4).
+This shows that, with trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Supplementary Figure 4).
 Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to allow trading (Fig.
@@
 In January 2015, Kiribati closed 11.5\% of its EEZ to implement the Phoenix Islands Protected Area (PIPA), effectively displacing all fishing effort within its boundaries \cite{mccauley_2016,mcdermott_2018}.
-By protecting important tuna spawning habitat\cite{hernndez_2019}, PIPA may provide important recruitment and biomass benefits to adjacent waters.
+By protecting important tuna spawning habitat \cite{hernndez_2019}, PIPA may provide important recruitment and biomass benefits to adjacent waters.
 We combine vessel-level tracking data \cite{kroodsma_2018} and country-level license revenue data reported by the Pacific Islands Forum Fisheries Agency (FFA) \cite{ffa_2017} to quantify the displacement of vessel-days and the likely costs of conservation.
@@
 \ref{fig:empirical}a).
-However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Figs.
-S6 and S7).
+However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Extended Data Figures 1 - 2).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicts.
@@
 One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati.
-It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, are larger than non-displaced vessels, fished more in the PNA in 2014, and are more likely to be registered to the Republic of Korea (Tables S2 and S3, Fig.
-S5).
+It should be noted that, on average, displaced vessels have smaller crew sizes, more engine power, are larger than non-displaced vessels, fished more in the PNA in 2014, and are more likely to be registered to the Republic of Korea (Supplementary Tables 2-3 and Supplementary Figure 5).
 Thus, another alternative explanation for the observed changes in fishing patterns is a change in international relations between Kiribati (or other PNA countries) and the flag country of a particular vessel, although we are not aware of any occurring between 2012 and 2018.
@@
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in vessel-days (35\%).
-This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
-S4).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
-S8), despite the PIPA closure.
+This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Supplementary Figure 4).
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Supplementary Figure 6), despite the PIPA closure.
 
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that, on average, the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig.
-S10-S11).
+Vessel-tracking data (2012 to 2018) shows that, on average, the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Extended Data Figures 3 - 4).
 
@@
 A 100\% biomass-based allocation rule means that fishing rights will be distributed between nations based on the proportion of total biomass within their waters, regardless of historical fishing intensity.
-Furthermore, an effort-based allocation would reward undesirable behavior by granting more fishing rights to a country that fishes the most.
+In contrast, an effort-based allocation would reward undesirable behavior by granting more fishing rights to a country that fishes the most.
 This is a model prediction that cannot be empirically tested in the PNA context because the allocation rule has not been experimentally modified.
@@
 We use these data to calculate vessel-days (the metric used by the PNA), and to track the spatial redistribution of displaced vessels.
-A comparison of vessel characteristics between displaced and non-displaced vessels is presented in Tables S2-S3 and Figure S5.
+A comparison of vessel characteristics between displaced and non-displaced vessels is presented in Supplementary Tables 2-3 and Supplementary Figure 5.
 
@@
 We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell.
-We use a 1-degree grid as a reasonable compromise between higher resolutions that would result in a more granular but noisy footprint, and the simple estimation of vessel-days at the EEZ-level (as in Fig S6, but represented spatially).
+We use a 1-degree grid as a reasonable compromise between higher resolutions that would result in a more granular but noisy footprint, and the simple estimation of vessel-days at the EEZ-level (as in Extended Data Figure 1, but represented spatially).
 This process results in 14 gridded datasets of fishing hours (7 years, for two groups).
@@
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA \cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}c; Fig.
-S8 - S9).
+\ref{fig:empirical}c; Supplementary Figures 6 - 7).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.
@@
 
-\subsection{Data availability}
+\section{Data availability}
 
@@
 
-\subsection{Code availability}
+\section{Code availability}
 
@@
 
-\bibliography{references}
-\bibliographystyle{nature}
+%\bibliography{references}
+%\bibliographystyle{nature}
+
+\begin{thebibliography}{10}
+
+\bibitem{oleary_2016}
+O'Leary, B.~C., Winther-Janson, M., Bainbridge, J.~M., Aitken, J., Hawkins,
+  J.~P., and Roberts, C.~M.
+\newblock {\em Conservation letters}{ \bf 9}(6), 398--404 nov  (2016).
+
+\bibitem{dinerstein_2019}
+Dinerstein, E., Vynne, C., Sala, E., Joshi, A.~R., Fernando, S., Lovejoy,
+  T.~E., Mayorga, J., Olson, D., Asner, G.~P., Baillie, J. E.~M., Burgess,
+  N.~D., Burkart, K., Noss, R.~F., Zhang, Y.~P., Baccini, A., Birch, T., Hahn,
+  N., Joppa, L.~N., and Wikramanayake, E.
+\newblock {\em Sci. Adv.}{ \bf 5}(4), eaaw2869 apr  (2019).
+
+\bibitem{sala_2017}
+Sala, E. and Giakoumi, S.
+\newblock {\em {ICES} Journal of Marine Science}{ \bf } (2017).
+
+\bibitem{sala_2018}
+Sala, E., Lubchenco, J., Grorud-Colvert, K., Novelli, C., Roberts, C., and
+  Sumaila, U.~R.
+\newblock {\em Marine Policy}{ \bf 91}(2), 11--13 may  (2018).
+
+\bibitem{mcleod_2019}
+Mcleod, E., Bruton-Adams, M., Förster, J., Franco, C., Gaines, G., Gorong, B.,
+  James, R., Posing-Kulwaum, G., Tara, M., and Terk, E.
+\newblock {\em Frontiers in Marine Science}{ \bf } (2019).
+
+\bibitem{ramesh_2019}
+Ramesh, N., Rising, J.~A., and Oremus, K.~L.
+\newblock {\em Science}{ \bf 364}(6446), 1192--1196 jun  (2019).
+
+\bibitem{hernndez_2019}
+Hernández, C.~M., Witting, J., Willis, C., Thorrold, S.~R., Llopiz, J.~K., and
+  Rotjan, R.~D.
+\newblock {\em Scientific reports}{ \bf 9}(1), 10772 dec  (2019).
+
+\bibitem{agardy_2018}
+Agardy, T.
+\newblock {\em {ICES} Journal of Marine Science}{ \bf 75}(3), 1183--1185 may
+  (2018).
+
+\bibitem{havice_2010}
+Havice, E.
+\newblock {\em Marine Policy}{ \bf 34}(5), 979--987 sep  (2010).
+
+\bibitem{havice_2013}
+Havice, E.
+\newblock {\em Marine Policy}{ \bf 42}, 259--267 nov  (2013).
+
+\bibitem{aqorau_2018}
+Aqorau, T., Bell, J., and Kittinger, J.~N.
+\newblock {\em Science}{ \bf 361}(6408), 1208.2--1209 sep  (2018).
+
+\bibitem{ffa_2017b}
+FFA.
+\newblock Technical report, Pacific Islands Forum Fisheries Agency,  (2017).
+
+\bibitem{libecap_1989}
+Libecap, G.~D.
+\newblock {\em Journal of Institutional and Theoretical Economics}{ \bf
+  145}(1), 6--24 mar  (1989).
+
+\bibitem{mccauley_2016}
+{McCauley}, D.~J., Woods, P., Sullivan, B., Bergman, B., Jablonicky, C., Roan,
+  A., Hirshfield, M., Boerder, K., and Worm, B.
+\newblock {\em Science}{ \bf 351}(6278), 1148--1150 mar  (2016).
+
+\bibitem{mcdermott_2018}
+{McDermott}, G.~R., Meng, K.~C., {McDonald}, G.~G., and Costello, C.~J.
+\newblock {\em Proc Natl Acad Sci {USA}}{ \bf } aug  (2018).
+
+\bibitem{kroodsma_2018}
+Kroodsma, D.~A., Mayorga, J., Hochberg, T., Miller, N.~A., Boerder, K.,
+  Ferretti, F., Wilson, A., Bergman, B., White, T.~D., Block, B.~A., Woods, P.,
+  Sullivan, B., Costello, C., and Worm, B.
+\newblock {\em Science}{ \bf 359}(6378), 904--908 feb  (2018).
+
+\bibitem{ffa_2017}
+Terawasi, P. and Reid, C.
+\newblock Technical report, Pacific Islands Forum Fisheries Agency, Honaira,
+  Solomon Islands,  (2017).
+
+\bibitem{hanich2018unraveling}
+Hanich, Q., Rotjan, R., Aqorau, T., Bailey, M., Campbell, B., Gray, N., Gruby,
+  R., Hampton, J., Ota, Y., Parris, H., et~al.
+\newblock {\em Proceedings of the National Academy of Sciences}{ \bf 115}(52),
+  E12122--E12123 (2018).
+
+\bibitem{ferraro2018causal}
+Ferraro, P.~J., Sanchirico, J.~N., and Smith, M.~D.
+\newblock {\em Proceedings of the National Academy of Sciences}{ \bf },
+  201805563 (2018).
+
+\bibitem{crespo_2019}
+Crespo, G.~O., Dunn, D.~C., Gianni, M., Gjerde, K., Wright, G., and Halpin,
+  P.~N.
+\newblock {\em Nature Ecology \& Evolution}{ \bf 3}(9), 1273--1276 sep  (2019).
+
+\bibitem{rosegrant_1994}
+Rosegrant, M.~W. and Binswanger, H.~P.
+\newblock {\em World development}{ \bf 22}(11), 1613--1625 nov  (1994).
+
+\bibitem{hutton_2003}
+Hutton, J.~M. and Leader-Williams, N.
+\newblock {\em Oryx}{ \bf 37}(02) apr  (2003).
+
+\bibitem{sandbrook_2019}
+Sandbrook, C., Fisher, J., Holmes, G., Luque-Lora, R., and Keane, A.
+\newblock {\em Nat Sustain}{ \bf 2}(4), 316--323 apr  (2019).
+
+\bibitem{roberts_2017}
+Roberts, C.~M., O'Leary, B.~C., {McCauley}, D.~J., Cury, P.~M., Duarte, C.~M.,
+  Lubchenco, J., Pauly, D., S√°enz-Arroyo, A., Sumaila, U.~R., Wilson,
+  R.~W., Worm, B., and Castilla, J.~C.
+\newblock {\em Proc Natl Acad Sci {USA}}{ \bf 114}(24), 6167--6175 jun  (2017).
+
+\bibitem{ban_2019}
+Ban, N.~C., Gurney, G.~G., Marshall, N.~A., Whitney, C.~K., Mills, M., Gelcich,
+  S., Bennett, N.~J., Meehan, M.~C., Butler, C., Ban, S., Tran, T.~C., Cox,
+  M.~E., and Breslow, S.~J.
+\newblock {\em Nature Sustainability}{ \bf 2}(6), 524--532 jun  (2019).
+
+\bibitem{costello_2016}
+Costello, C., Ovando, D., Clavelle, T., Strauss, C.~K., Hilborn, R., Melnychuk,
+  M.~C., Branch, T.~A., Gaines, S.~D., Szuwalski, C.~S., Cabral, R.~B., Rader,
+  D.~N., and Leland, A.
+\newblock {\em Proceedings of the National Academy of Sciences of the United
+  States of America}{ \bf 113}(18), 5125--5129 may  (2016).
+
+\bibitem{Hagrannsoknir2014}
+Hagrannsoknir.
+\newblock Technical report, PNA Office, available at: www.pnatuna.com/sites/
+  default/files/Independent Review of the PNA Purse Seine VDS- Final Report_0.pdf,  (2014).
+
+\bibitem{pna_2016}
+PNA.
+\newblock Technical report, Parties to the Nauru Agreement,  oct  (2016).
+
+\bibitem{rcore_2019}
+{R Core Team}.
+\newblock {\em R: A Language and Environment for Statistical Computing}.
+\newblock R Foundation for Statistical Computing, Vienna, Austria,  (2019).
+
+\bibitem{yeeting2018stabilising}
+Yeeting, A.~D., Weikard, H.-P., Bailey, M., Ram-Bidesi, V., and Bush, S.~R.
+\newblock {\em Regional Environmental Change}{ \bf 18}(3), 885--897 (2018).
+
+\end{thebibliography}
 
@@
 Supplementary Information is linked to the online version of the paper at www.nature.com/nature
+
+Correspondence and requests for materials should be addressed to juancarlos@ucsb.edu.
 
@@
 
-\section{Author information}
-
-Reprints and permissions information is available at www.nature.com/reprints.
-The authors declare no competing interests.
-Correspondence and requests for materials should be addressed to juancarlos@ucsb.edu.
-
-\subsection{Competing interests}
+\section{Competing interests}
 
@@
 
-\clearpage
-
 \FloatBarrier
 
+\section{Figure Legends}
+
 % Map of LSMPAS in PNA
-\begin{figure}
+\begin{figure}[htbp]
 \centering
-\includegraphics{img/PNA_map.pdf}
+%\includegraphics{img/PNA_map.pdf}
 \caption{\label{fig:PNA_map}Map of the Exclusive Economic Zones (EEZs) and Marine Protected Areas in the PNA, the bottom-left inset provides a reference for the area.
@@
 \centering
-\includegraphics{img/PNA_model.pdf}
+%\includegraphics{img/PNA_model.pdf}
 \caption{\label{fig:PNA_model}Cost of spatial closures in a vessel-day fishery.
@@
 \centering
-\includegraphics{img/allocation_cost_plot.pdf}
+%\includegraphics{img/allocation_cost_plot.pdf}
 \caption{\label{fig:allocation_cost_plot}Costs of a spatial closure for Country 1 under different allocation rules.
@@
 \centering
-\includegraphics{img/fishing_raster_diff.pdf}
+%\includegraphics{img/fishing_raster_diff.pdf}
 \caption{\label{fig:fishing_raster_diff}Change in spatial footprint of fishing activity by 318 tuna purse seiners.
@@
 \centering
-\includegraphics{img/empirical.pdf}
+%\includegraphics{img/empirical.pdf}
 \caption{\label{fig:empirical}Effort displacement and license revenues.

### 2019-11-20 docs/Markets_Conservation_revised_Nov14.tex
Updated MS for resubmission

--- 2019-11-13 docs/Markets_Conservation_revised_Nov13.tex
@@
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While biodiversity and spillover fishing benefits may far exceed these loses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
-To overcome this dilemma, we design and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.
-By combining a model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that cross-country transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation.
+While biodiversity and spillover fishing benefits may far exceed these losses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
+To overcome this dilemma, we simulate and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.
+By combining a bioeconomic model of cross-country trading of fishing rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that cross-country transferable fishing rights and a biomass-based allocation rule are pivotal to incentivize conservation under this market-based setting.
 Our work focuses on the Vessel-Day Scheme, an environmental market employed by the Parties to the Nauru Agreement (a group of nine Pacific Island Nations) to manage their tuna fisheries, and where large-scale conservation interventions have taken place.
@@
 \ref{fig:empirical}a).
-However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Figs.
-S6 and S7).
+However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Supplementary Figures 6 - 7).
 The reduction in effort in Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicts.
@@
 But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in vessel-days (35\%).
-This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig.
-S4).
-At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig.
-S8), despite the PIPA closure.
+This supports a key prediction of our model: with trading, the relative revenue drop will be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Supplementary Figure 4).
+At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Supplementary Figure 8), despite the PIPA closure.
 
@@
 \ref{fig:PNA_map}).
-Vessel-tracking data (2012 to 2018) shows that, on average, the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig.
-S10-S11).
+Vessel-tracking data (2012 to 2018) shows that, on average, the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Supplementary Figures 10-11).
 
@@
 We then create a gridded version of the data for each year and group (\emph{i.e.} displaced and non-displaced) by binning the coordinates to a 1-degree grid and summing all fishing hours for a given grid cell.
-We use a 1-degree grid as a reasonable compromise between higher resolutions that would result in a more granular but noisy footprint, and the simple estimation of vessel-days at the EEZ-level (as in Fig S6, but represented spatially).
+We use a 1-degree grid as a reasonable compromise between higher resolutions that would result in a more granular but noisy footprint, and the simple estimation of vessel-days at the EEZ-level (as in Supplementary Figure 6, but represented spatially).
 This process results in 14 gridded datasets of fishing hours (7 years, for two groups).
@@
 Specifically, we use data compiled by the Pacific Islands Forum Fisheries Agency (FFA \cite{ffa_2017}) where annual revenues from license fees (for VDS and other access programs) are reported for each country (2008 - 2016; Fig.
-\ref{fig:empirical}c; Fig.
-S8 - S9).
+\ref{fig:empirical}c; Supplementary Figures 8 - 9).
 For countries in the PNA, these revenues show a combination of vessel-day license fees as well as joint-venture operations.

### 2019-11-20 docs/old_ms/Markets_Conservation_revised_Nov13.tex
Updated MS for resubmission

--- 2019-11-13 docs/Markets_Conservation_revised_Nov13.tex
@@
 When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue.
-While biodiversity and spillover fishing benefits may far exceed these loses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
+While biodiversity and spillover fishing benefits may far exceed these losses, benefits from large-scale MPAs typically accrue to other countries or the high seas.
 To overcome this dilemma, we design and test an international fisheries management scheme with transferable fishing rights that incentivizes, rather than hinders, large-scale marine conservation.

### 2019-11-20 docs/Supplementary_materials.tex
Added new version of the MS
Updated supplementary materials text

@@
 
-\title{Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''}
+\title{Supplementary Materials for: ``Environmental Market Design for Large-Scale Marine Conservation''}
 
@@
 
-\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+%\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 
-\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+%\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
 
-\section{Model parameterization}
+\renewcommand{\tablename}{Supplementary Table}
+\renewcommand{\figurename}{Supplementary Figure}
+
+\section{Supplementary Methods}
+
+\subsection{Model parameterization}
 
@@
 
-\section{Balance on observables}
+\subsection{Balance on observables}
 
@@
 \includegraphics{img/vessel_day_price_no_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) for the country with spatial closure and other countries (left - right, respectively) when there is no trading.}
+\caption{\label{fig:vessel_day_price_no_trading_plot}Vessel-day prices with conservation and no trading.
+Vessel-day prices (vertical axis) are shown for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) for the country with spatial closure and other countries (left - right, respectively) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/profits_PNA_notKIR_no_trading_plot.pdf}
-\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Relative change in revenue for countries 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) when there is no trading.}
+\caption{\label{fig:profits_PNA_notKIR_no_trading_plot}Change in revenues to non-conserving countries.
+Relative change in revenue for countries 2 - 9 (vertical axis) for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$) when there is no trading.}
 \end{figure}
@@
 \includegraphics{img/vessel_day_price_with_trading_plot.pdf}
-\caption{\label{fig:vessel_day_price_with_trading_plot}PNA-wide vessel-day prices (vertical axis) with trading, for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$).}
+\caption{\label{fig:vessel_day_price_with_trading_plot}Vessel-day prices with conservation and trading.
+PNA-wide vessel-day prices (vertical axis) with trading, for a combination of reserve sizes ($R$ in the horizontal-axis) and different within-country movement ($\theta$).}
 \end{figure}
@@
 	\includegraphics{img/effort_and_revenues.pdf}
-	\caption{\label{fig:effort_and_revenues}Effort and revenue in Country 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading.
+	\caption{\label{fig:effort_and_revenues}Effort and revenues to the conserving country with and without trading.
+Effort and revenue in Country 1 are shown for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading.
 With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases.
@@
 \includegraphics{img/balance_density_plot.pdf}
-\caption{\label{fig:balance_density_plot}Distribution of observable characteristics by vessel for displaced (n = 64), non-displaced vessels (n = 254).}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/all_PS_VDS_cty_year.pdf}
-	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 318 tuna purse seiners.}
-\end{figure}
-
-\begin{figure}
-\centering
-	\includegraphics{img/fishing_the_line_by_year.pdf}
-	\caption{\label{fig:fishing_the_line_by_year}Annual fishing effort (hours) on a 1-degree grid around PIPA (red polygon) and Kiribati (black polygons).
-There is no clear evidence of a ``fishing the line'' effect, with the greatest effort applied on the Gilbert islands (Kiribati) after 2015.}
+\caption{\label{fig:balance_density_plot}Vessel characteristics for 318 tuna purse seiners.
+Distribution of observable characteristics by vessel for displaced (n = 64), non-displaced vessels (n = 254).}
 \end{figure}
@@
 
-\begin{figure}
-\centering
-\includegraphics{img/plw_2018.pdf}
-\caption{\label{fig:plw_2018}Longline and purse seine fishing effort in Palau during 2018 at a 0.5 degree resolution.
-The red polygon shows the proposed Palau National Marine Sanctuary, containing 56\% and 91\% of longline and purse seine fishing effort, respectively.
-Note that the colorbars are presented in $log_{10}$ transformed scale for better visualization.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{img/plw_ts_plot.pdf}
-\caption{\label{fig:plw_ts_plot}Time series of the annual proportion of longline and purse seine effort within the proposed PNMS boundaries.}
-\end{figure}
-
 \clearpage

### 2019-12-09 scripts/3_model/2_run_model.Rmd
Added ticks to Fig2c and Fig 3 as required by the production team

@@
                      limits = c(0.885, 1)) +
+  scale_x_continuous(limi= c(0, 1)) +
   theme(legend.position = "None"))
+
+ggsave(plot = delta_costs_plot,
+       filename = here("docs", "img", "panel2c.pdf"),
+       width = 3.4, height = 2.3)
 ```
@@
                       limits = c(0, 1)) +
+   scale_x_continuous(limits = c(0, 1)) +
    xlab("Portion of patch as reserve (R)") +

### 2022-05-28 scripts/3_model/2_run_model.Rmd
Updating for dissertation

@@
     ) +
-    startR::ggtheme_plot() +
+    # startR::ggtheme_plot() +
     scale_y_continuous(labels = scales::percent) +
@@
 ggsave(plot = costs_no_trading_plot,
-       filename = here("docs", "slides", "img", "cost_no_trading.png"),
+       filename = here("docs", "diss_img", "cost_no_trading.png"),
        width = 3,
@@
   scale_color_viridis_c() +
-  startR::ggtheme_plot() +
+  # startR::ggtheme_plot() +
   scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
@@
 ggsave(plot = costs_with_trading_plot_long_axis,
-       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
+       filename = here("docs", "diss_img", "cost_with_trading_long_axis.png"),
        width = 3,
@@
   scale_color_viridis_c() +
-  startR::ggtheme_plot() +
+  # startR::ggtheme_plot() +
   scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
@@
 ggsave(plot = costs_with_trading_plot,
-       filename = here("docs", "slides", "img", "cost_with_trading.png"),
+       filename = here("docs", "diss_img", "cost_with_trading.png"),
        width = 3,
@@
   ) +
-  startR::ggtheme_plot() +
+  # startR::ggtheme_plot() +
   scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
@@
 ggsave(plot = delta_costs_plot,
-       filename = here("docs", "img", "panel2c.pdf"),
+       filename = here("docs", "diss_img", "panel2c.pdf"),
        width = 3.4, height = 2.3)
@@
 ggsave(plot = cost_plot,
-       filename = here("docs", "img", "PNA_model.pdf"),
+       filename = here("docs", "diss_img", "PNA_model.pdf"),
        width = 3.4,
@@
 ggsave(plot = effort_and_revenues,
-       file = here("docs", "img","effort_and_revenues.pdf"),
+       file = here("docs", "diss_img", "effort_and_revenues.pdf"),
        width = 6,
@@
 ggsave(plot = effort_and_revenues,
-       file = here("docs", "img","effort_and_revenues_ED_Fig4.tiff"),
+       here("docs", "diss_img", "effort_and_revenues_ED_Fig4.tiff"),
        width = 6,
@@
 ggsave(plot = vessel_day_price_no_trading_plot,
-       filename = here("docs", "img", "vessel_day_price_no_trading_plot.pdf"),
+       filename = here("docs", "diss_img", "vessel_day_price_no_trading_plot.pdf"),
        width = 6,
@@
 ggsave(plot = vessel_day_price_no_trading_plot,
-       filename = here("docs", "img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
+       here("docs", "diss_img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
        width = 6,
@@
 ggsave(plot = vessel_day_price_with_trading_plot,
-       filename = here("docs", "img", "vessel_day_price_with_trading_plot.pdf"),
+       here("docs", "diss_img", "vessel_day_price_with_trading_plot.pdf"),
        width = 6,
@@
 ggsave(plot = vessel_day_price_with_trading_plot,
-       filename = here("docs", "img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
+       here("docs", "diss_img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
        width = 6,
@@
 ggsave(plot = profits_PNA_notKIR_no_trading_plot,
-       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot.pdf"),
+       here("docs", "diss_img", "profits_PNA_notKIR_no_trading_plot.pdf"),
        width = 3,
@@
 ggsave(plot = profits_PNA_notKIR_no_trading_plot,
-       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
+       here("docs", "diss_img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
        width = 3,
@@
   plot = allocation_cost_plot,
-  filename = here("docs", "img", "allocation_cost_plot.pdf"),
+  here("docs", "diss_img", "allocation_cost_plot.pdf"),
   width = 5,
@@
   plot = allocation_cost_plot,
-  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
+  here("docs", "diss_img", "allocation_cost_plot.pdf"),
   width = 5,

### 2022-05-28 scripts/3_model/pi_of_E.R

@@ -19,6 +19,7 @@ pi_of_E <- function(p = NULL, q = NULL, X = NULL, theta = NULL, R = NULL, beta =
   
   omega <- rep(1, n_patches)
   omega[1] <- theta + ((1 - theta) * (1 - R))
+  if(R == 1) {omega[1] <- 0}
   
   pi <- (p * q * X * omega) - (beta * c * ((E)^(beta - 1)))
   

### 2022-05-31 scripts/3_model/E_vec_fxn.R
Updated omega

@@ -25,6 +25,9 @@ E_vec_fxn <- function(p = NULL, q = NULL, Xvec = NULL, theta = NULL, R = NULL, p
   # "fishable" biomass based on R and theta
   omega <- rep(1, n_patches)
   omega[1] <- theta + ((1 - theta) * (1 - R))
+  if(R == 1){
+    omega[1] <- 0
+  }
   
   # Create a vector of prices, wherte the high seas haven price (pi = 0)
   pi <- c(rep(pi, n_patches - 1), 0)

### 2022-05-31 scripts/3_model/PNA_no_trading.R

@@ -21,7 +21,9 @@ PNA_no_trading <- function(fvec = NULL, theta = NULL, R = NULL, r = NULL, K = NU
   n_patches <- length(fvec)
   
   omega <- theta + (1 - theta) * (1 - R)
-  if(R == 1){omega <- 0}
+  if(R == 1){
+    omega <- 0
+  }
   
   tol <- 0.001 * Bnow
   diff <- (tol * 2)^2

### 2022-05-31 scripts/3_model/pi_of_E.R

@@ -19,7 +19,9 @@ pi_of_E <- function(p = NULL, q = NULL, X = NULL, theta = NULL, R = NULL, beta =
   
   omega <- rep(1, n_patches)
   omega[1] <- theta + ((1 - theta) * (1 - R))
-  if(R == 1) {omega[1] <- 0}
+  if(R == 1){
+    omega[1] <- 0
+  }
   
   pi <- (p * q * X * omega) - (beta * c * ((E)^(beta - 1)))
   

### 2022-05-31 scripts/3_model/2_run_model.Rmd
Updating model runs for dissertation

@@
 
-# Clean the environment
-rm(list = ls())
 ```
@@
 
+```{r}
+no_trade_bm <- DF_results_no_trading %>% 
+  filter(R == 0, theta == 0) %>%
+  select(
+    Country,
+    b_harvest = Harvest,
+    b_vessel_days = Vessel_Days,
+    b_stock = Stock,
+    b_stock_i = Stock_i,
+    b_vdsprice = VDSprice,
+    b_vdsrevenue = VDSrevenue,
+    b_vdsrevenue_all = VDSrevenue_all,
+    b_vdsrevenue_notKIR = VDSrevenue_notKIR
+  )
+```
+
 We now take these results and add the benchmark results (no reserve) to calculate the cost of the reserve as the change in revenue. The proportional way of saying this is:
@@
   filter(Country == "KIR") %>%
-  left_join(Benchmark_results, by = "Country") %>%
+  left_join(no_trade_bm, by = "Country") %>%
   mutate(
@@
       c = c,
-      E = E
+      E = sum(Evec[1:9])
     )
@@
   unnest()
+```
+
+```{r}
+trading_bm <- DF_results_with_trading %>% 
+  filter(R == 0, theta == 0) %>%
+  select(
+    Country,
+    b_harvest = Harvest,
+    b_vessel_days = Vessel_Days,
+    b_stock = Stock,
+    b_stock_i = Stock_i,
+    b_vdsprice = VDSprice,
+    b_vdsrevenue = VDSrevenue,
+    b_vdsrevenue_all = VDSrevenue_all,
+    b_vdsrevenue_notKIR = VDSrevenue_notKIR
+  )
 ```
@@
   filter(Country == "KIR") %>%
-  left_join(Benchmark_results, by = "Country") %>%
+  left_join(trading_bm, by = "Country") %>%
   mutate(
@@
 alphas <- c(0, 0.5, 1)
-
 delta <- 1 / 1.1
@@
 
+# Numbers for main text
+
+```{r}
+# revenues increase between 0\% and 7\% each
+DF_1_no_trading %>% pull(rel_cost_pna_not_kir) %>% range() * 100
+
+# When trading between countries occurs, 88.5\% to 99.2\% of revenue losses can be avoided.
+both %>% pull(rel_delta_cost) %>% range() * 100
+
+# implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement
+allocation %>%
+    filter(R > 0,
+           trade) %>% 
+    filter(alpha == 1) %>% 
+    mutate(trade = ifelse(trade, "Trading", "No Trading"),
+           alpha = as.character(alpha)) %>% 
+    group_by(trade, alpha, R, theta) %>%
+    summarize(rev = sum(rev_tot)) %>%
+    ungroup() %>% 
+    mutate(cost = (best_rev - rev) / best_rev) %>%
+    pull(cost) %>% 
+    range() * 100
+
+#However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses of up to 0.7\%, essentially eliminating the costs of conservation.
+allocation %>%
+    filter(R > 0,
+           trade) %>% 
+    filter(alpha == 0) %>% 
+    mutate(trade = ifelse(trade, "Trading", "No Trading"),
+           alpha = as.character(alpha)) %>% 
+    group_by(trade, alpha, R, theta) %>%
+    summarize(rev = sum(rev_tot)) %>%
+    ungroup() %>% 
+    mutate(cost = (best_rev - rev) / best_rev) %>%
+    pull(cost) %>% 
+    range() * 100
+```
+
 # Reproducibility chunk

### 2022-06-03 scripts/3_model/2_run_model.Rmd
Updating images for slides

@@
     theme(legend.justification = c(0, 0.9),
-          legend.position = c(0, 1)) +
-    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
+          legend.position = c(0, 1))
 )
@@
        filename = here("docs", "diss_img", "cost_no_trading.png"),
-       width = 3,
-       height = 3)
+       width = 6,
+       height = 4.5)
 ```
@@
        filename = here("docs", "diss_img", "cost_with_trading_long_axis.png"),
-       width = 3,
-       height = 3)
+       width = 6,
+       height = 4.5)
 ```
@@
   scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
-  theme(legend.position = "None"))
+    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
+                                  ticks.colour = "black", frame.colour = "black")) +
+    theme(legend.justification = c(0, 0.9),
+          legend.position = c(0, 1))
+)
 ```
@@
        filename = here("docs", "diss_img", "cost_with_trading.png"),
-       width = 3,
-       height = 3)
+       width = 6,
+       height = 4.5)
 ```
@@
                      limits = c(0.885, 1)) +
-  scale_x_continuous(limi= c(0, 1)) +
-  theme(legend.position = "None"))
+  scale_x_continuous(limits= c(0, 1)) +
+    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
+                                  ticks.colour = "black", frame.colour = "black")) +
+    theme(legend.justification = c(0, 0.9),
+          legend.position = c(0, 1))
+)
 
+```
+
+```{r}
 ggsave(plot = delta_costs_plot,
@@
        width = 3.4, height = 2.3)
+
+ggsave(plot = delta_costs_plot,
+       filename = here("docs", "diss_img", "panel2c.png"),
+       width = 6,
+       height = 4.5)
 ```
@@
 ```{r, fig.width = 4, fig.height = 7}
-(cost_plot <- plot_grid(costs_no_trading_plot,
-                        costs_with_trading_plot,
-                        delta_costs_plot,
+(cost_plot <- plot_grid(costs_no_trading_plot +
+                          geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red"),
+                        costs_with_trading_plot +
+                          theme(legend.position = "None"),
+                        delta_costs_plot  +
+                          theme(legend.position = "None"),
                         ncol = 1,
@@
 )
+
+ggsave(
+  plot = allocation_cost_plot,
+  here("docs", "diss_img", "allocation_cost_plot.png"),
+  width = 6,
+  height = 3.5
+)
 ```

### 2022-06-03 scripts/3_model/E_vec_fxn.R

@@ -17,7 +17,7 @@
 #' @export
 #'
 E_vec_fxn <- function(p = NULL, q = NULL, Xvec = NULL, theta = NULL, R = NULL, pi = NULL, beta = NULL, c = NULL) {
-  
+  # browser()
   # Get the number of patches
   n_patches <- length(Xvec)
   
@@ -32,10 +32,11 @@ E_vec_fxn <- function(p = NULL, q = NULL, Xvec = NULL, theta = NULL, R = NULL, p
   # Create a vector of prices, wherte the high seas haven price (pi = 0)
   pi <- c(rep(pi, n_patches - 1), 0)
   
+
   # Calculate the attainable level of effort in each patch
   E_vec <- (((p * q * Xvec * omega) - pi) / (beta * c))^(1 / (beta - 1))
   
-  # These are the revenues. Prices cannot be higher than this, or would
+  # These are the marginal revenues. Prices cannot be higher than this, or would
   # imply negative efforts
   threshold <- p * q * Xvec * omega
   
